### 2020-11-10 analysis/Trabalho com o Liviao.Rmd
Add files via upload

---
title: "Discourse and Deforestation in the Amazon - Silva and Sposito"
author: "Henrique Sposito"
date: "11/10/2020"
output: html_document
---

# Premise and Research Question

# Literature Review

# Hypothesis

# Methodology and Data

```
library(stm)
library(quanteda)
library(ggplot2)

dp <- corpus(Discursos_Presidenciais, text_field = "text")

summary(dp)

kwic(dp, "Amazônia")

kwic(dp, "floresta Amazônica")

kwic (dp, c("desflorestamento", "desflorestação", "desmatamento", "Amazônia", "floresta Amazônica", "desmate", "preservação"))

stw <- readLines("C:/Users/h-spo/Downloads/stopwords.txt")

dp1 <- dfm(dp, remove = c(stopwords("portuguese"), stw)), remove_punct = TRUE, remove_url = TRUE, remove_symbols = TRUE, remove_numbers = TRUE, tolower=TRUE)

topfeatures(dp1, n = 1000)

# Amazon name is refreed to 1064 times (ranks around 950).

dp1 <- dfm_wordstem(dp1, language = "portuguese")

toks <- tokens(dp1)

data <- tokens_select(toks, selection = "remove", min_nchar = 3)

```

### 2020-11-10 analysis/STM.R
Rodrigo's script

@@ -1,0 +1,263 @@
+#Here I use a dataset of foreign affairs speeches by Brazilian ministers/presidents from 2003 to 2019.The process showed below is useful particularly for non-English text. 
+
+library(stm)
+library(quanteda)
+library(ggplot2)
+
+##PRE-PROCESSING##
+#Import data and transform to corpus
+data <- corpus(Discursos_Presidenciais2, text_field = "text")
+
+#Create tokens and select features which you want out or in and then convert tokens file to dfm (dfm allows further treatment of the tokenized text)
+toks <- tokens(data)
+
+data <- tokens_select(toks, selection = "remove", min_nchar = 3)
+
+stw1<-readLines("stopwordspt.txt")
+stw2<-readLines("stopwordspt2.txt")
+
+data <- dfm(data, remove = c(stopwords("portuguese"), stw1, stw2), remove_punct = TRUE, remove_url = TRUE, remove_symbols = TRUE, remove_numbers = TRUE, tolower=TRUE)
+
+topfeatures(data, n = 500)
+
+data <- dfm_wordstem(data, language = "portuguese") #https://github.com/quanteda/quanteda/issues/368
+
+data <- dfm_trim(data, min_docfreq = 0.075, max_docfreq = 0.90, docfreq_type = "prop") #this cuts off words above or below certain frequency
+
+topfeatures(data, n = 50)#useful to see most frequent words before proceeding into the analysis (we may decide to add or remove extra features)
+
+#Convert dfm to stm and indicate metadata. Note that this also words it you want to run LDA thans to the Quanteda package. out <- convert (data, to = °topicmodels°). In that case, you have to use the ldatuning package and proceed with model selection and use the function FindTopicsNumber and FindtopicsNumber_plot.
+out <- convert(data, to = 'stm')
+meta<-out$meta
+
+##MODEL SELECTION## 
+#The STM is a generative and inductive model. The number of topics is not known beforehand. There are certain ways to evaluate what is the "best" number of topics to be chosen. 
+many.models<-searchK(out$documents,out$vocab, K=c(20,40,60,80,100,120,140))
+print(many.models$results)
[…]

### 2021-09-30 Trabalho com o Liviao.Rmd
Deleted package structure

--- 2020-11-10 analysis/Trabalho com o Liviao.Rmd
@@
 
-topfeatures(dp1, n = 1000)
-
-# Amazon name is refreed to 1064 times (ranks around 950).
-
-dp1 <- dfm_wordstem(dp1, language = "portuguese")
+dp2 <- dfm_wordstem(dp1, language = "portuguese")
 
@@
 
+topfeatures(dp1, n = 1000)
+
+# Amazon name is refreed to 1064 times (ranks around 950). 
+# plotting occurences across time
+
+library(tidyverse)
+library(ggplot2)
+library(reshape2)
+library(scales)
+
+dat <- as.data.frame(Discursos_Presidenciais)
+
+ggplot(dat %>% group_by(date, label=TRUE)) %>%
+         summarise(A = sum(grepl("Amazônia"),
+                   B = sum(grepl("desmatamento")))) %>%
+         melt(id.var="date") +
+       aes(date) +
+  geom_line()
+
 ```

### 2021-09-30 R/Functions.R

@@ -1,1 +1,0 @@
-# Our functions go here!

### 2021-09-30 analysis/STM.R

@@ -1,263 +1,0 @@
-#Here I use a dataset of foreign affairs speeches by Brazilian ministers/presidents from 2003 to 2019.The process showed below is useful particularly for non-English text. 
-
-library(stm)
-library(quanteda)
-library(ggplot2)
-
-##PRE-PROCESSING##
-#Import data and transform to corpus
-data <- corpus(Discursos_Presidenciais2, text_field = "text")
-
-#Create tokens and select features which you want out or in and then convert tokens file to dfm (dfm allows further treatment of the tokenized text)
-toks <- tokens(data)
-
-data <- tokens_select(toks, selection = "remove", min_nchar = 3)
-
-stw1<-readLines("stopwordspt.txt")
-stw2<-readLines("stopwordspt2.txt")
-
-data <- dfm(data, remove = c(stopwords("portuguese"), stw1, stw2), remove_punct = TRUE, remove_url = TRUE, remove_symbols = TRUE, remove_numbers = TRUE, tolower=TRUE)
-
-topfeatures(data, n = 500)
-
-data <- dfm_wordstem(data, language = "portuguese") #https://github.com/quanteda/quanteda/issues/368
-
-data <- dfm_trim(data, min_docfreq = 0.075, max_docfreq = 0.90, docfreq_type = "prop") #this cuts off words above or below certain frequency
-
-topfeatures(data, n = 50)#useful to see most frequent words before proceeding into the analysis (we may decide to add or remove extra features)
-
-#Convert dfm to stm and indicate metadata. Note that this also words it you want to run LDA thans to the Quanteda package. out <- convert (data, to = °topicmodels°). In that case, you have to use the ldatuning package and proceed with model selection and use the function FindTopicsNumber and FindtopicsNumber_plot.
-out <- convert(data, to = 'stm')
-meta<-out$meta
-
-##MODEL SELECTION## 
-#The STM is a generative and inductive model. The number of topics is not known beforehand. There are certain ways to evaluate what is the "best" number of topics to be chosen. 
-many.models<-searchK(out$documents,out$vocab, K=c(20,40,60,80,100,120,140))
-print(many.models$results)
[…]

### 2021-09-30 data_wragling_and_pre_analysis.R
Added cleaned data and wrangling and analysis script

@@ -1,0 +1,15 @@
+# Inductive (pre)Analysis
+
+# Load packages
+library(dplyr)
+
+# Load data
+BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+
+# Wrangle data
+BR_Presidential_Speeches$date <- poldis::extract_date(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- poldis::extract_title(BR_Presidential_Speeches)
+
+# Text Cleaning
+
+# Text pre-analysis

### 2021-10-01 data_wragling_and_pre_analysis.R
Updated wrangling data script

@@ -2,13 +2,39 @@
 
 # Load packages
 library(dplyr)
+library(stringr)
 
 # Load data
-BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds") # your path might differ
 
 # Wrangle data
+# Get exact dates 
 BR_Presidential_Speeches$date <- poldis::extract_date(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- poldis::extract_title(BR_Presidential_Speeches)
+# There are a lot of NAs... It seems some dates in texta re missing the year.
+# Get titles (first sentence)
+BR_Presidential_Speeches$title <- poldis::extract_title(BR_Presidential_Speeches$text)
+
+# For dates that are missing the year, let's complete them!
+d <- BR_Presidential_Speeches$title
+d <- stringr::str_extract(d, "(\\S+)\\s*DE\\s*(\\S+)")
+d <- paste0(d, "-", BR_Presidential_Speeches$year)
+d <- gsub(" DE ", "-", d)
+# load months data from poldis
+load("~/GitHub/poldis/R/sysdata.rda") # your path might differ
+months <- as.data.frame(months)
+for (k in seq_len(nrow(months))) {
+  d <- gsub(paste0(months$months[k]),
+              paste0(months$number[k]),
+              d, ignore.case = TRUE,
+              perl = T)
+}
+d <- stringr::str_replace_all(d, "NA-", "?-?-")
+d <- ifelse(stringr::str_detect(d, "[A-Z]|[a-z]"), paste0("?-?-", BR_Presidential_Speeches$year), d)
+# Let's complete our dates column now
+BR_Presidential_Speeches$date <- ifelse(is.na(BR_Presidential_Speeches$date),
+                                        d, BR_Presidential_Speeches$date)
+
+min(BR_Presidential_Speeches$date)
 
 # Text Cleaning
 

### 2021-10-18 data_exploration.Rmd
Setup data_exploration rmarkdown

---
title: "Amazon in Presidential Speeches in Brazil (Inductive Analysis)"
author: "Henrique Sposito"
date: "10/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data and Filter it for Amazon related texts

```{r}
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
BR_Presidential_Speeches <- head(BR_Presidential_Speeches)
BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text
                                                   )

```

## Clean text and get most frequent terms overall, and by speaker, in time

## Simple LDA models by speakers

## Get, and compare, sentiment in time for speakers (afinn and NRC)

## Does setting matter?

### 2021-10-18 data_wragling_and_pre_analysis.R

@@ -1,61 +1,0 @@
-# Inductive (pre)Analysis
-
-# Load packages
-library(dplyr)
-library(stringr)
-
-# # Get Data, join and save into repository
-# # This portion explains how/where data was gathered and wrangled before it was saved into the package.
-# # It is commented out as it is here for transparency rather than reproduciability.
-# # Please contact authors for access to original datasets for reproduction.
-#
-# # Load BR_oral from AP repository
-# load("~/GitHub/authenticity_performances/data/BR_oral.rda") # your path my differ here
-# # Select only some variables
-# BR_oral <- BR_oral %>%
-#   dplyr::select("presid", "date", "party", "text") %>%
-#   rename(president = "presid", year = "date")
-#
-# # Wrangle data
-# # Get exact dates 
-# BR_oral$date <- poldis::extract_date(BR_oral$text)
-# # There are a lot of NAs... It seems some dates in text are missing the year...
-# # Get titles (first sentence)
-# BR_oral$title <- poldis::extract_title(BR_oral$text)
-# # For dates that are missing the year, let's complete them!
-# d <- BR_oral$title
-# d <- stringr::str_extract(d, "(\\S+)\\s*DE\\s*(\\S+)")
-# d <- paste0(d, "-", BR_oral$year)
-# d <- gsub(" DE ", "-", d)
-# # load months data from poldis
-# load("~/GitHub/poldis/R/sysdata.rda") # your path might differ
-# months <- as.data.frame(months)
-# for (k in seq_len(nrow(months))) {
-#   d <- gsub(paste0(months$months[k]),
-#               paste0(months$number[k]),
-#               d, ignore.case = TRUE,
-#               perl = T)
-# }
-# d <- stringr::str_replace_all(d, "NA-", "?-?-")
-# d <- ifelse(stringr::str_detect(d, "[A-Z]|[a-z]"), paste0("?-?-", BR_oral$year), d)
-# # Let's complete our dates column now
-# BR_oral$date <- ifelse(is.na(BR_oral$date), d, BR_oral$date)
-# 
-# # Merge with data fro missing ttexts from January 2020 until october 2021
-# BR_speeches_2020_21 <- read_excel("C:/Users/h-spo/Desktop/BR_speeches_2020-21.xlsx")
-# BR_speeches_2020_21 <- BR_speeches_2020_21 %>%
[…]

### 2021-10-18 data_wrangling.R

@@ -1,0 +1,63 @@
+# Data Wrangling
+
+# This script explains how the data was coded and where it comes from.
+# It is intended for transparency, rather than reproduciability.
+# For more information on the data, please contact the authors.
+# The dataset is available in the repository,
+# feel free to use but cite us.
+
+# # Load packages
+# library(dplyr)
+# library(stringr)
+# #Load poldis
+# remotes::install_github(henriquesposito/poldis)
+# # Get Data, join and save into repository
+# # This portion explains how/where data was gathered and wrangled before it was saved into the package.
+# # It is commented out as it is here for transparency rather than reproduciability.
+# # Please contact authors for access to original datasets for reproduction.
+#
+# # Load BR_oral from AP repository
+# # load("~/GitHub/authenticity_performances/data/BR_oral.rda") # your path my differ here
+# # Select only some variables
+# BR_oral <- BR_oral %>%
+#   dplyr::select("presid", "date", "party", "text") %>%
+#   rename(president = "presid", year = "date")
+#
+# # Wrangle data
+# # Get exact dates 
+# BR_oral$date <- poldis::extract_date(BR_oral$text)
+# # There are a lot of NAs... It seems some dates in text are missing the year...
+# # Get titles (first sentence)
+# BR_oral$title <- poldis::extract_title(BR_oral$text)
+# # For dates that are missing the year, let's complete them!
+# d <- BR_oral$title
+# d <- stringr::str_extract(d, "(\\S+)\\s*DE\\s*(\\S+)")
+# d <- paste0(d, "-", BR_oral$year)
+# d <- gsub(" DE ", "-", d)
+# # load months data from poldis
+# # load("~/GitHub/poldis/R/sysdata.rda") # your path might differ
+# months <- as.data.frame(months)
+# for (k in seq_len(nrow(months))) {
+#   d <- gsub(paste0(months$months[k]),
+#               paste0(months$number[k]),
+#               d, ignore.case = TRUE,
+#               perl = T)
+# }
+# d <- stringr::str_replace_all(d, "NA-", "?-?-")
+# d <- ifelse(stringr::str_detect(d, "[A-Z]|[a-z]"), paste0("?-?-", BR_oral$year), d)
+# # Let's complete our dates column now
+# BR_oral$date <- ifelse(is.na(BR_oral$date), d, BR_oral$date)
+# 
[…]

### 2021-10-18 data_exploration.Rmd
Updated data exploration script by subsetting data

@@
 ```{r}
+library(dplyr)
 BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
-BR_Presidential_Speeches <- head(BR_Presidential_Speeches)
-BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text
-                                                   )
-
+BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text, level = "sentences")
+Amazon_speeches <-dplyr::filter(BR_Presidential_Speeches, grepl("Amazon|Amazonica|Amazonia|Amazonas", text))
 ```

### 2021-10-20 data_exploration.Rmd
Updated data exploration rmarkdown for sentiment

--- 2021-10-18 data_exploration.Rmd
@@
 
-```{r}
+```{r amazon, warning=FALSE, message=FALSE}
+library(dplyr)
 BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
-BR_Presidential_Speeches <- head(BR_Presidential_Speeches)
-BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text
-                                                   )
-
+# BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text, level = "sentences")
+# This takes a while to run, but we get context for all matches in dataset as a variable in dataset!
+Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches,
+                                 grepl("Amazôn|Amazon|amazôn|amazon", text))
+# 861 speeches mention words related to Amazon
+summary(as.factor(Amazon_speeches$president)) # Frequency by president
+plot(Amazon_speeches$year, as.factor(Amazon_speeches$year), type = "b",
+     main = "Presidential Speeches about the Amazon in Time in Brazil",
+     xlab = "Year", ylab = "Frequency") # simple plot, but interesting!
 ```
@@
 
-## Simple LDA models by speakers
+```{r term frequency, warning=FALSE, message=FALSE}
+library(tm)
+library(tidytext)
+# Make text lower case
+Amazon_speeches$text <- tolower(Amazon_speeches$text)
+
+# Remove stopwords and punctuation
+Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
+Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text, tm::stopwords("pt"))
+
+# Transform into corpus
+Amazon_speeches <- Amazon_speeches %>%
+  dplyr::mutate(doc_id = president) %>%
+  arrange(doc_id, text)
+amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))
+
+# Get 30 most frequent words overall
+amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
+amazon_dtmm <- as.matrix(amazon_dtm)
+amazon_f <- data.frame(term = names(colSums(amazon_dtmm)),
+                       freq = colSums(amazon_dtmm))
+amazon_f <- amazon_f[order(amazon_f$freq, decreasing = T),]
+rownames(amazon_f) <- NULL
+amazon_f30 <- data.frame(head(amazon_f, 30))
+amazon_f30 # Not very informative...
+
+# Let's see if bigrams help us more here
+tamazon <- tidytext::tidy(amazon_corpus) %>%
+  unnest_tokens(bigram, text , token = "ngrams", n = 3, n_min = 2) %>%
+  dplyr::count(bigram, sort = TRUE) %>%
+  ungroup()
+tamazon # Not very informative either...
+
+# Let's get the 30 most frequent term by speaker
+amazon_presid <- aggregate(Amazon_speeches$text, list(Amazon_speeches$president), paste, collapse = " ") %>%
+  rename(doc_id = "Group.1", text = "x")
+amazon_presid_t <- tm::VCorpus(DataframeSource(amazon_presid)) %>%
+  tidy() %>% 
+  unnest_tokens(word, text) %>%
+  count(id, word, sort = TRUE)
+Sarney <- head(dplyr::filter(amazon_presid_t, id == "Sarney"), 30) %>%  mutate(Sarney = word) %>% select(Sarney)
+Collor <- head(dplyr::filter(amazon_presid_t, id == "Collor"), 30) %>%  mutate(Collor = word) %>% select(Collor)
+Itamar <- head(dplyr::filter(amazon_presid_t, id == "Itamar"), 30) %>%  mutate(Itamar = word) %>% select(Itamar)
+FHC <- head(dplyr::filter(amazon_presid_t, id == "FHC"), 30) %>%  mutate(FHC = word) %>% select(FHC)
+Lula <- head(dplyr::filter(amazon_presid_t, id == "Lula"), 30) %>%  mutate(Lula = word) %>% select(Lula)
+Dilma <- head(dplyr::filter(amazon_presid_t, id == "Dilma"), 30) %>%  mutate(Dilma = word) %>% select(Dilma)
+Temer <- head(dplyr::filter(amazon_presid_t, id == "Temer"), 30) %>%  mutate(Temer = word) %>% select(Temer)
+Bolsonaro <- head(dplyr::filter(amazon_presid_t, id == "Bolsonaro"), 30) %>%  mutate(Bolsonaro = word) %>% select(Bolsonaro)
+f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro)
+f_speaker # Not very infomartive either...
+```
+
+## Simple LDA model by speakers
+
+```{r lda, warning=FALSE, message=FALSE}
+library(topicmodels)
+library(kableExtra)
+# Fit a simple LDA model
+# Please note that we randomly set a K = 10 (10 cluster topics)
+amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))
+
+# Get the top 10 words per topic
+amazon_lda10 <- tidy(amazon_lda, matrix = "beta") %>%
+  arrange(desc(beta)) %>%
+  group_by(topic) %>%
+  filter(row_number() %in% 1:10) %>%
+  arrange(topic)
+topten_topic <- aggregate(amazon_lda10$term, list(amazon_lda10$topic), paste, collapse=", ") %>%
+  rename(Topic = "Group.1", Terms = "x") %>% 
+  kableExtra::kbl(caption = "Top 10 Words per Topic for Prsidential Speeches Mentioning the Amazon") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+topten_topic # "Meio ambiente" (environment) appears only in topic 7 ...
+
+# Let's get the gamma (percent of topic in document for speakers)
+amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
+  arrange(desc(gamma)) %>%
+  group_by(document) %>%
+  filter(row_number() %in% 1:2) %>% # get the top 3 topics per speaker
+  arrange(document)
+amazon_lda_presid$gamma <- round(amazon_lda_presid$gamma, digits = 4)
+amazon_lda_presid <- kableExtra::kbl(amazon_lda_presid, caption = "Top 2 Topics Per Speaker") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+amazon_lda_presid # Only Dilma, Sarney and Collor associated with topic that mentions "meio ambiente".
+```
 
@@
 
-## Does setting matter?
+```{r sentiment, warning=FALSE, message=FALSE}
+library(ggplot2)
+library(stringr)
+# Load internal sentiment dictionaries from poldis
+Afinn_pt <- poldis:::Afinn_pt
+nrc_portuguese <- poldis:::nrc_portuguese
+
+# Aggregate by president and year and transform into a corpus
+amazon_sent <- mutate(Amazon_speeches, doc_id = paste0(doc_id, "_", year))
+amazon_sent <- aggregate(amazon_sent$text, list(amazon_sent$doc_id), paste, collapse =" ") %>%
+  rename(doc_id = "Group.1", text = "x")
+amazon_sent_wf <- VCorpus(DataframeSource(amazon_sent)) %>%
+  tidy() %>%
+  unnest_tokens(word, text) %>%
+  count(id, word, sort = TRUE)
+
+# Get afinn sentiment
+amazon_sent_af <- inner_join(amazon_sent_wf, Afinn_pt, by = "word") %>%
+  group_by(id) %>%
+  summarize(value = sum(n)) %>%
+  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
+         president = stringr::str_remove_all(id, "_[0-9]{4}"),
+         date2 = stringr::str_extract(id, "[0-9]{2}$"))
+
+# Plot Afinn sentiment in time for speeches about the Amazon
+ggplot(amazon_sent_af, aes(x = reorder(date2, as.numeric(year)), y = value , fill = president)) +
+  geom_line(aes(group = president)) +
+  geom_point(size = 5, shape = 21) +
+  labs(x = "",
+       y = "",
+       title = "Sentiment in Presidential Speeches about the Amazon",
+       caption = "Afinn sentiment lexicon")
+# FHC and Lula more positive about in speeches about the Amazon than others...
+
+# Get NRC per speaker
+amazon_sent_nrc <- inner_join(amazon_sent_wf, nrc_portuguese, by = "word") %>%
+  group_by(id, sentiment) %>%
+  summarize(value = sum(n)) %>%
+  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
+         president = stringr::str_remove_all(id, "_[0-9]{4}"),
+         date2 = stringr::str_extract(id, "[0-9]{2}$"))
+
+# Plot NRC
+ggplot(amazon_sent_nrc, aes(x = reorder(id, as.numeric(date)), y = value, fill = sentiment)) +
+  geom_bar(position="stack", stat="identity") +
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=1)) +
+  labs(x = "",
+       y = "",
+       title = "Sentiment in Presidential Speeches about the Amazon",
+       caption = "NRC sentiment lexicon")
+```
+
+## Does location matter?

### 2021-10-20 data_exploration.Rmd
Fixed minor bug with data exploration vignette

--- 2021-10-18 data_exploration.Rmd
@@
 
-## Simple LDA models by speakers
+```{r term frequency, warning=FALSE, message=FALSE}
+library(tm)
+library(tidytext)
+library(kableExtra)
+# Make text lower case
+Amazon_speeches$text <- tolower(Amazon_speeches$text)
+
+# Remove stopwords and punctuation
+Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
+Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text, tm::stopwords("pt"))
+
+# Transform into corpus
+Amazon_speeches <- Amazon_speeches %>%
+  dplyr::mutate(doc_id = president) %>%
+  arrange(doc_id, text)
+amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))
+
+# Get 30 most frequent words overall
+amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
+amazon_dtmm <- as.matrix(amazon_dtm)
+amazon_f <- data.frame(term = names(colSums(amazon_dtmm)),
+                       freq = colSums(amazon_dtmm))
+amazon_f <- amazon_f[order(amazon_f$freq, decreasing = T),]
+rownames(amazon_f) <- NULL
+amazon_f30 <- data.frame(head(amazon_f, 30))
+amazon_f30 # Not very informative...
+
+# Let's see if bigrams help us more here
+tamazon <- tidytext::tidy(amazon_corpus) %>%
+  unnest_tokens(bigram, text , token = "ngrams", n = 3, n_min = 2) %>%
+  dplyr::count(bigram, sort = TRUE) %>%
+  ungroup()
+tamazon # Not very informative either...
+
+# Let's get the 30 most frequent term by speaker
+amazon_presid <- aggregate(Amazon_speeches$text, list(Amazon_speeches$president), paste, collapse = " ") %>%
+  rename(doc_id = "Group.1", text = "x")
+amazon_presid_t <- tm::VCorpus(DataframeSource(amazon_presid)) %>%
+  tidy() %>% 
+  unnest_tokens(word, text) %>%
+  count(id, word, sort = TRUE)
+Sarney <- head(dplyr::filter(amazon_presid_t, id == "Sarney"), 30) %>%
+  mutate(Sarney = word) %>% select(Sarney)
+Collor <- head(dplyr::filter(amazon_presid_t, id == "Collor"), 30) %>%
+  mutate(Collor = word) %>% select(Collor)
+Itamar <- head(dplyr::filter(amazon_presid_t, id == "Itamar"), 30) %>%
+  mutate(Itamar = word) %>% select(Itamar)
+FHC <- head(dplyr::filter(amazon_presid_t, id == "FHC"), 30) %>%  mutate(FHC = word) %>% select(FHC)
+Lula <- head(dplyr::filter(amazon_presid_t, id == "Lula"), 30) %>%  mutate(Lula = word) %>% select(Lula)
+Dilma <- head(dplyr::filter(amazon_presid_t, id == "Dilma"), 30) %>%  mutate(Dilma = word) %>% select(Dilma)
+Temer <- head(dplyr::filter(amazon_presid_t, id == "Temer"), 30) %>%  mutate(Temer = word) %>% select(Temer)
+Bolsonaro <- head(dplyr::filter(amazon_presid_t, id == "Bolsonaro"), 30) %>%
+  mutate(Bolsonaro = word) %>% select(Bolsonaro)
+f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro)
+f_speaker <- kableExtra::kbl(f_speaker, caption = "Top 10 Words Per President") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+f_speaker # not super informative ...
+```
+
+## Simple LDA model by speakers
+
+```{r lda, warning=FALSE, message=FALSE}
+library(topicmodels)
+# Fit a simple LDA model
+# Please note that we randomly set a K = 10 (10 cluster topics)
+amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))
+
+# Get the top 10 words per topic
+amazon_lda10 <- tidy(amazon_lda, matrix = "beta") %>%
+  arrange(desc(beta)) %>%
+  group_by(topic) %>%
+  filter(row_number() %in% 1:10) %>%
+  arrange(topic)
+topten_topic <- aggregate(amazon_lda10$term, list(amazon_lda10$topic), paste, collapse=", ") %>%
+  rename(Topic = "Group.1", Terms = "x") %>% 
+  kableExtra::kbl(caption = "Top 10 Words per Topic for Prsidential Speeches Mentioning the Amazon") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+topten_topic # "ambiente" (environment) appears only in topic 7 ...
+# Agriculture, on the other hand, is the first cluster...
+
+# Let's get the gamma (percent of topic in document for speakers)
+amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
+  arrange(desc(gamma)) %>%
+  group_by(document) %>%
+  filter(row_number() %in% 1:2) %>% # get the top 3 topics per speaker
+  arrange(document)
+amazon_lda_presid$gamma <- round(amazon_lda_presid$gamma, digits = 4)
+amazon_lda_presid <- kableExtra::kbl(amazon_lda_presid, caption = "Top 2 Topics Per Speaker") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
+```
 
@@
 
-## Does setting matter?
+```{r sentiment, warning=FALSE, message=FALSE}
+library(ggplot2)
+library(stringr)
+# library(poldis)
+# Load internal sentiment dictionaries from poldis
+Afinn_pt <- poldis:::Afinn_pt
+nrc_portuguese <- poldis:::nrc_portuguese
+
+# Aggregate by president and year and transform into a corpus
+amazon_sent <- mutate(Amazon_speeches, doc_id = paste0(doc_id, "_", year))
+amazon_sent <- aggregate(amazon_sent$text, list(amazon_sent$doc_id), paste, collapse =" ") %>%
+  rename(doc_id = "Group.1", text = "x")
+amazon_sent_wf <- VCorpus(DataframeSource(amazon_sent)) %>%
+  tidy() %>%
+  unnest_tokens(word, text) %>%
+  count(id, word, sort = TRUE)
+
+# Get afinn sentiment
+amazon_sent_af <- inner_join(amazon_sent_wf, Afinn_pt, by = "word") %>%
+  group_by(id) %>%
+  summarize(value = sum(n)) %>%
+  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
+         president = stringr::str_remove_all(id, "_[0-9]{4}"),
+         date2 = stringr::str_extract(id, "[0-9]{2}$"))
+
+# Plot Afinn sentiment in time for speeches about the Amazon
+ggplot(amazon_sent_af, aes(x = reorder(date2, as.numeric(year)), y = value , fill = president)) +
+  geom_line(aes(group = president)) +
+  geom_point(size = 5, shape = 21) +
+  labs(x = "",
+       y = "",
+       title = "Sentiment in Presidential Speeches about the Amazon",
+       caption = "Afinn sentiment lexicon")
+# Lula more positive about in speeches surrounding the Amazon than others...
+
+# Get NRC per speaker
+amazon_sent_nrc <- inner_join(amazon_sent_wf, nrc_portuguese, by = "word") %>%
+  group_by(id, sentiment) %>%
+  summarize(value = sum(n)) %>%
+  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
+         president = stringr::str_remove_all(id, "_[0-9]{4}"),
+         date2 = stringr::str_extract(id, "[0-9]{2}$"))
+
+# Plot NRC
+ggplot(amazon_sent_nrc, aes(x = reorder(id, as.numeric(year)), y = value, fill = sentiment)) +
+  geom_bar(position="stack", stat="identity") +
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=1)) +
+  labs(x = "",
+       y = "",
+       title = "Sentiment in Presidential Speeches about the Amazon",
+       caption = "NRC sentiment lexicon") +
+  coord_flip() +
+  expand_limits(y=c(0, 1000))
+```
+
+## Does location matter?

### 2021-10-21 data_exploration.Rmd
Updated data exploration script to include location portion

@@
   expand_limits(y=c(0, 1000))
+# Lula 2010 appears to have spoken more and used more "carried" words related to certain sentiment according to dictionary in texts mentioning the Amazon.
 ```
@@
 ## Does location matter?
+
+```{r}
+# Location was added with poldis::extraxt_location(), still needs to be improved...
+summary(as.factor(Amazon_speeches$location))
+
+# Let's code the Amzonian states as "local"; the other Brazilian states as "nacional";
+# and the ones delivered outside Brazil as "international".
+Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins", location) ~ "local", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Maranhao|Minas Gerais|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "national", grepl("Argentina|Chile|China|Colombia|Cuba|European|France|Hamburg|India|Israel|Jamaica|Nicaragua|Oman|ONU|Panama|Peru|Portugal|Senegal|Suriname", location) ~ "international"))
+Amazon_lc$stage <- stringr::str_replace_na(Amazon_lc$stage, "Non Identified")
+summary(as.factor(Amazon_lc$stage)) # A lot of international observations ...
+
+# Let's try an simple LDA model again
+Amazon_lc <- mutate(Amazon_lc, doc_id = stage) %>% arrange(doc_id, text)
+amazon_lcc <- tm::VCorpus(DataframeSource(Amazon_lc))
+amazon_dtm_lc  <- DocumentTermMatrix(amazon_lcc)
+amazon_lda_lc <- topicmodels::LDA(amazon_dtm_lc, k = 20, control = list(seed = 1234)) # set k = 20
+amazon_lda_lcc <- tidy(amazon_lda_lc, matrix = "beta") %>%
+  arrange(desc(beta)) %>%
+  group_by(topic) %>%
+  filter(row_number() %in% 1:10) %>%
+  arrange(topic)
+topten_lc <- aggregate(amazon_lda_lcc$term, list(amazon_lda_lcc$topic), paste, collapse=", ") %>%
+  rename(Topic = "Group.1", Terms = "x")
+
+# Get stage and merge tables
+amazon_lda_lcs <- tidy(amazon_lda_lc, matrix = "gamma") %>%
+  arrange(desc(gamma)) %>%
+  group_by(document) %>%
+  filter(row_number() %in% 1:8) %>% # get the top 3 topics per location
+  arrange(document) %>% 
+  select(-gamma) %>% 
+  distinct()
+amazon_lda_topic <- aggregate(amazon_lda_lcs$document, list(amazon_lda_lcs$topic), paste, collapse = ", ") %>% rename(Topic = "Group.1", Stage = "x") 
+amazon_lda_topic <- dplyr::left_join(topten_lc, amazon_lda_topic, by = "Topic") %>%
+  kableExtra::kbl(caption = "Top 10 Words per Topic for Stages") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+amazon_lda_topic # Do you see anything interesting?
+```

### 2021-10-28 data_exploration_2_context.Rmd
Updated data exploration for contexts markdown document

---
title: "Amazon in Presidential Speeches in Brazil: data exploration for contexts"
author: "Henrique Sposito and Livio Silva-Muller"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data and Filter it for Amazon related portions in texts

```{r amazon, warning=FALSE, message=FALSE}
library(dplyr)
library(stringi)
library(tm)

# Load data
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
# Subset for text matches
Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
# Remove accents and extra spaces
Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
# Make all lower case
Amazon_speeches$text <- tolower(Amazon_speeches$text)
# Remove extra white spaces
Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
# Get only the pertinent text chunks
Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
# Transform into a single text per row...
Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
# Plot number of speeches that mention Amazon normalized
freq_year <- data.frame(year = names(summary(as.factor(Amazon_speeches$year))),
                        freq = as.numeric(summary(as.factor(Amazon_speeches$year)))/
                          as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))
plot(freq_year$year, freq_year$freq, type = "b",
     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
     sub = "Normalized by the number of speeches per year in broader dataset",
     xlab = "Year", ylab = "Frequency")
```

We start by getting the dataset and subsetting it for the texts that mention the strings "Amazon" in it as a word or parts of words. Then, we us `{poldis}` to get the context for each mention of the "Amazon", by default one sentence before and one sentence after the sentence in which the word "Amazon" is used.

From the plot, the proportion of speeches that mention the word "Amazon" increase in frequency, in relation to the number of speeches per year in broader dataset, in the 1989 (?), around 1992 (Rion Conference), from 2005 to 2010 (Lula and preservation legislation turn), and after 2016 (deforestation rates increasing and international attention).

## Clean text and get most frequent terms overall, and by speaker, in time

```{r term frequency, warning=FALSE, message=FALSE}
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(RColorBrewer)

# Rename variables to adapt to text analysis packages' expectations
Amazon_speeches <- dplyr::rename(Amazon_speeches, fulltext = text, text = ccontext)

# Remove stopwords and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil"))
Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")

# Transform into corpus
Amazon_speeches <- Amazon_speeches %>%
  dplyr::mutate(doc_id = president) %>%
  arrange(doc_id, text)
amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))

# Get 30 most frequent words overall
amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
amazon_dtmm <- as.matrix(amazon_dtm)
amazon_f <- data.frame(term = names(colSums(amazon_dtmm)),
                       freq = colSums(amazon_dtmm))
amazon_f <- amazon_f[order(amazon_f$freq, decreasing = T),]
rownames(amazon_f) <- NULL
amazon_f30 <- data.frame(head(amazon_f, 30))
amazon_f30
# Just plot in a wordcloud for words
set.seed(1234)
wordcloud(words = amazon_f$term, freq = amazon_f$freq, min.freq = 50,
          max.words=200, random.order = FALSE, rot.per=0.35, 
          colors = brewer.pal(8, "Dark2"))

# Let's see if bigrams help us more here
tamazon <- tidytext::tidy(amazon_corpus) %>%
  unnest_tokens(bigram, text , token = "ngrams", n = 2) %>%
  dplyr::count(bigram, sort = TRUE) %>%
  ungroup()
tamazon
# A plot in a wordcloud for bigrams
set.seed(1234)
wordcloud(words = tamazon$bigram, freq = tamazon$n, min.freq = 20,
          max.words=200, random.order = FALSE, rot.per=0.35, 
          colors = brewer.pal(8, "Dark2"))

# Let's get the 30 most frequent term by speaker
amazon_presid <- aggregate(Amazon_speeches$text, list(Amazon_speeches$president), paste, collapse = " ") %>%
  rename(doc_id = "Group.1", text = "x")
amazon_presid_t <- tm::VCorpus(DataframeSource(amazon_presid)) %>%
  tidy() %>% 
  unnest_tokens(word, text) %>%
  count(id, word, sort = TRUE)
Sarney <- head(dplyr::filter(amazon_presid_t, id == "Sarney"), 30) %>%
  mutate(Sarney = word) %>% select(Sarney)
Collor <- head(dplyr::filter(amazon_presid_t, id == "Collor"), 30) %>%
  mutate(Collor = word) %>% select(Collor)
Itamar <- head(dplyr::filter(amazon_presid_t, id == "Itamar"), 30) %>%
  mutate(Itamar = word) %>% select(Itamar)
FHC <- head(dplyr::filter(amazon_presid_t, id == "FHC"), 30) %>%  mutate(FHC = word) %>% select(FHC)
Lula <- head(dplyr::filter(amazon_presid_t, id == "Lula"), 30) %>%  mutate(Lula = word) %>% select(Lula)
Dilma <- head(dplyr::filter(amazon_presid_t, id == "Dilma"), 30) %>%  mutate(Dilma = word) %>% select(Dilma)
Temer <- head(dplyr::filter(amazon_presid_t, id == "Temer"), 30) %>%  mutate(Temer = word) %>% select(Temer)
Bolsonaro <- head(dplyr::filter(amazon_presid_t, id == "Bolsonaro"), 30) %>%
  mutate(Bolsonaro = word) %>% select(Bolsonaro)
f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro) %>% 
  kableExtra::kbl(caption = "Top 10 Words Per President") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
f_speaker
```

After cleaning the text we start by getting word frequencies. Although qord frequencies do not seem very helpful, more interesting patterns start to appear with bigrams 82 words that appear together) as we see, for example, "meio ambiente" (environemnt) appear central alongside references to the Amazonian forest, the tax free zone in Manaus (capital of the Amazonas state), and references to other countries (outros paises).

When it comes to the 30 most frequent words per speaker, we see more interesting patterns as words such as development (all presdidents but Temer), integration (Collor and Itamar), security (Temer), deforestation (Lula, Dilma, and Temer), among others.

## Simple LDA model by speakers

```{r lda, warning=FALSE, message=FALSE}
library(topicmodels)

# Fit a simple LDA model
# Please note that we randomly set a K = 10 (10 cluster = topics)
amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))

# Get the top 10 words per topic
amazon_lda10 <- tidy(amazon_lda, matrix = "beta") %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  filter(row_number() %in% 1:10) %>%
  arrange(topic)
topten_topic <- aggregate(amazon_lda10$term, list(amazon_lda10$topic), paste, collapse=", ") %>%
  rename(Topic = "Group.1", Terms = "x") %>% 
  kableExtra::kbl(caption = "Top 10 Words per Topic for Prsidential Speeches Mentioning the Amazon") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
topten_topic

# Let's get the gamma (percent of topic in document for speakers)
amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:2) %>% # get the top 3 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 3)) %>%
  distinct() %>% 
  rename (president = document) %>% 
  kableExtra::kbl(caption = "Top 2 Topics Per Speaker") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
```

When it comes to the LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each document, we start to see some interesting patterns (for more information on LDA and R approches [here](https://www.tidytextmining.com/index.html)). We set the number of clusters to be found (topics) at 10, randomly. We, then, select the top ten words coded for each topic. The first three topics relate to themes of security, development, and integration. The fourth topic relates to themes of deforestation and sustainable devolopment. Topics five to nine appear to relate to themes of politics, energy, and geography. The last topic appears to relate to themes of preservation of the Amazonian forest.

Once the clusters are extracted, we can indicate, probabilisticly, how presidents' discourse fall within a topic. We see that, for example, Lula's discourses about the Amazon often is clusteres with themes of development and of deforestation. At the same time, Bolsonaro's discourses about the Amazon often is clusteres with themes of integration, energy, and the military forces. Sarney engaged with themes of preservation, while Cardoso engages with themes related to energy and integration. Others as Rousseff and Temer appear to engage with themes of geography, politics, energy; while Collor an Itamar appear to engage with themes of security, development, and integration.

## Get, and compare, sentiment in time for speakers (afinn and NRC)

```{r sentiment, warning=FALSE, message=FALSE}
library(ggplot2)
library(stringr)
# library(poldis)

# Load internal sentiment dictionaries from poldis
Afinn_pt <- poldis:::Afinn_pt
nrc_portuguese <- poldis:::nrc_portuguese

# Aggregate by president and year and transform into a corpus
amazon_sent <- mutate(Amazon_speeches, doc_id = paste0(doc_id, "_", year))
amazon_sent <- aggregate(amazon_sent$text, list(amazon_sent$doc_id), paste, collapse =" ") %>%
  rename(doc_id = "Group.1", text = "x") %>% 
  mutate(char = nchar(text))
amazon_sent_wf <- VCorpus(DataframeSource(amazon_sent)) %>%
  tidy() %>%
  unnest_tokens(word, text) %>%
  count(id, word, sort = TRUE)

# Get afinn sentiment
amazon_sent_af <- inner_join(amazon_sent_wf, Afinn_pt, by = "word") %>%
  group_by(id) %>%
  summarize(value = sum(n)) %>%
  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
         president = stringr::str_remove_all(id, "_[0-9]{4}"),
         date2 = stringr::str_extract(id, "[0-9]{2}$"),
         nvalue = value/amazon_sent$char)

# Plot Afinn sentiment in time for speeches about the Amazon
ggplot(amazon_sent_af, aes(x = reorder(date2, as.numeric(year)), y = nvalue , fill = president)) +
  geom_line(aes(group = president)) +
  geom_point(size = 5, shape = 21) +
  labs(x = "",
       y = "",
       title = "Sentiment in Presidential Speeches about the Amazon",
       subtitle = "Normalized by the number of characters in text for speaker",
       caption = "Afinn sentiment lexicon")

# Get NRC per speaker
amazon_sent_nrc <- inner_join(amazon_sent_wf, nrc_portuguese, by = "word") %>%
  filter(sentiment != "positive", sentiment != "negative") %>% 
  # removing positive and negative for more informative results
  group_by(id, sentiment) %>%
  summarize(value = sum(n)) %>%
  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
         president = stringr::str_remove_all(id, "_[0-9]{4}"),
         date2 = stringr::str_extract(id, "[0-9]{2}$"))
# Normalize (first you have to multiple each speaker value 8 times)
char <- select(amazon_sent, -text) %>% rename(id = doc_id)
amazon_sent_nrc <- left_join(amazon_sent_nrc, char, by = "id") %>%
  mutate(nvalue = (value/char)*100000)

# Plot NRC
ggplot(amazon_sent_nrc, aes(x = reorder(id, as.numeric(year)), y = nvalue, fill = sentiment)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=1)) +
  labs(x = "",
       y = "",
       title = "Sentiment in Presidential Speeches about the Amazon",
       subtitle = "Normalized by the number of characters in text for speaker",
       caption = "NRC sentiment lexicon") +
  coord_flip() +
  expand_limits(y=c(0, 1000))
```

The Afinn sentiment lexicon gets to the polarity of certain words coded by assigning a value to them, positive and negative. The scores are normalized by the number of characters in text data for speaker per year. This allow us to compare the average use of charged words coded for with the sentiment lexicon for each speaker per year. We see in the plot, for example, that Sarney from 1985-87 employs more positive words coded for sentiment on speeches that mention the Amazon than other presidents. The same can be said about Bolsonaro who used more positively charged words on average than other presidents when speaking about the Amazon according to the lexicon. Other presidents, as Cardoso, Rousseff and Lula appear more consistent in time in regards to the average polarity of terms used in Amazonian related discourses than Teme, Collor, and Itamar.

The NRC sentiment lexicon codes different sentiment for certain words. The scores for each of the sentiments soded also are normalized by the number of characters in text data for speaker per year. This allow us to compare the sentiments used according to the sentiment lexicon for each speaker per year. We see in the plot, that Lula in the early 2000s used many words coded for "trust" when speaking about the Amazon on average than other presidents/years. As well, Itamar in 1992 appeared to use more words coded for "anger" and "fear" on average than other presidents/years.

## Does location matter?

```{r}
# Location was added with poldis::extraxt_location(), still needs to be improved...
summary(as.factor(Amazon_speeches$location))

# Let's code the Amzonian states as "local"; the other Brazilian states as "nacional";
# and the ones delivered outside Brazil as "international".
Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
# Just a comparison with the proprtion of speeches per stage on the broader dataset
stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))

# Let's try an simple LDA model again
Amazon_lc <- mutate(Amazon_lc, doc_id = stage) %>% arrange(doc_id, text)
amazon_lcc <- tm::VCorpus(DataframeSource(Amazon_lc))
amazon_dtm_lc  <- DocumentTermMatrix(amazon_lcc)
amazon_lda_lc <- topicmodels::LDA(amazon_dtm_lc, k = 10, control = list(seed = 1234)) # set k = 10
amazon_lda_lcc <- tidy(amazon_lda_lc, matrix = "beta") %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  filter(row_number() %in% 1:10) %>%
  arrange(topic)
topten_lc <- aggregate(amazon_lda_lcc$term, list(amazon_lda_lcc$topic), paste, collapse=", ") %>%
  rename(Topic = "Group.1", Terms = "x")

# Get stage and merge tables
amazon_lda_lcs <- tidy(amazon_lda_lc, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:3) %>% # get the top 3 topics per location
  arrange(document) %>% 
  select(-gamma) %>% 
  distinct()
amazon_lda_topic <- aggregate(amazon_lda_lcs$document, list(amazon_lda_lcs$topic), paste, collapse = ", ") %>% rename(Topic = "Group.1", Stage = "x") 
amazon_lda_topic <- dplyr::left_join(topten_lc, amazon_lda_topic, by = "Topic") %>%
  kableExtra::kbl(caption = "Top 10 Words per Topic for Stages") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
amazon_lda_topic
```

The summary table illustrates that, as expected, more speeches that mention the Amazon proportionaly take place in Amazonian states in comparison to their proportion in all speeches. However, when it comes ot internationa settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.

We can also get the themes by setting for each of the ten topics (clusters) generated with the LDA. We see, for example, that some fo the themes related to cooperation and integration appear in Amazonian States and Non Identified stages (topic 2). While themes related to developement, deforestation, and sustainability appear in International stages (topic 4). Interestingly, themes related to preservation of the forest appear in Amazonian states and Non Amazonian States.

# Let's try and categorize the texts into a category...

```{r narratives}
# Amazon_speeches <- dplyr::mutate(Amazon_speeches, narrative = case_when(grepl("", text) ~ "", grepl("", text) ~ "", grepl("", text) ~ ""))
# summary(as.factor(Amazon_lc$narrative))
```

### 2021-10-28 data_exploration_2_context.Rmd
More updates to data exploration markdown

@@
 
-```{r}
+```{r location, warning=FALSE, message=FALSE}
 # Location was added with poldis::extraxt_location(), still needs to be improved...
@@
 
-```{r narratives}
+```{r narratives, warning=FALSE, message=FALSE}
 # Amazon_speeches <- dplyr::mutate(Amazon_speeches, narrative = case_when(grepl("", text) ~ "", grepl("", text) ~ "", grepl("", text) ~ ""))

### 2021-10-28 data_exploration_2_context.Rmd
Minor updates to data exploration context script

@@
 # Location was added with poldis::extraxt_location(), still needs to be improved...
-summary(as.factor(Amazon_speeches$location))
-
-# Let's code the Amzonian states as "local"; the other Brazilian states as "nacional";
-# and the ones delivered outside Brazil as "international".
+# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
+# Let's code the Amzonian states, the other Brazilian states, and speeches delivered outside Brazil.
 Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
@@
                          All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
+stage_rate
 

### 2021-11-01 data_exploration_2_context.Rmd
Added narratives portion to data_exploration_2 script for context. Other parts were also updated

@@
 author: "Henrique Sposito and Livio Silva-Muller"
-date: "10/28/2021"
+date: "10/29/2021"
 output: html_document
@@
 library(tm)
+library(ggplot2)
 
@@
 Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
-# Plot number of speeches that mention Amazon normalized
-freq_year <- data.frame(year = names(summary(as.factor(Amazon_speeches$year))),
-                        freq = as.numeric(summary(as.factor(Amazon_speeches$year)))/
+
+# In case you want to sample a few ramdom text observations by president
+# sample_pres <- Amazon_speeches %>% group_by(president) %>% sample_n(8) %>% select(president, year, ccontext)
+
+# Create a littale frequencies data frame
+freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
+                        freq = as.numeric(summary(as.factor(Amazon_speeches$year))),
+                        freqn = as.numeric(summary(as.factor(Amazon_speeches$year)))/
                           as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))
+
+# Simple plot of the frequncy of speeches that mention Amazon since 1985
 plot(freq_year$year, freq_year$freq, type = "b",
+     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
+     xlab = "Year", ylab = "Frequency")
+
+# Plot number of speeches that mention Amazon normalized by the number of speeches per year in broader data
+plot(freq_year$year, freq_year$freqn, type = "b",
      main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
@@
      xlab = "Year", ylab = "Frequency")
+
+# Also, let's load the data on annual rates of deforestation in the Brazilian Amazon per year
+amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
+freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year")
+ggplot(freq_year, aes(x = year)) +
+    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
+    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
+      labs(x = "Year",
+       y = "",
+       title = "Presidential Speeches that Mention the Amazon since 1985 in Brazil",
+       subtitle = "Compared to annual deforestation rates since 1988",
+       caption = "Frequencies are normalized by the number of speeches per year in dataset",
+       color = "Legend")
 ```
 
-We start by getting the dataset and subsetting it for the texts that mention the strings "Amazon" in it as a word or parts of words.
-Then, we us `{poldis}` to get the context for each mention of the "Amazon", by default one sentence before and one sentence after the sentence in which the word "Amazon" is used.
+We start by subsetting the broad dataset it for the texts that mention the strings "Amazon" in it as a word or parts of words.
+Then, we us `{poldis}` to get the context for each mention of the "Amazon", by default one sentence before and one sentence after the sentence in which the string "Amazon" is matched.
 
-From the plot, the proportion of speeches that mention the word "Amazon" increase in frequency, in relation to the number of speeches per year in broader dataset, in the 1989 (?), around 1992 (Rion Conference), from 2005 to 2010 (Lula and preservation legislation turn), and after 2016 (deforestation rates increasing and international attention).
+From the first plot, the proportion of speeches that mention the word "Amazon" increase in frequency in 1989 (possibly related to Amazon Fires coverage from the New York Times see [here](https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html) and [here](https://www.nytimes.com/1989/03/23/world/brazil-smarting-from-the-outcry-over-the-amazon-charges-foreign-plot.html)), around 1992 (likely related to the Rio Conference), from 2005 to 2010 (possibly related to the "preservation" legislation turn under the Lula Administration), and after 2016 (possibly related to increasing deforestation rates and international attention).
+Notice that the frequency is normalized by the number of speeches per year in the broader dataset.
+
+The second plot also compares mentions of Amazon and annual deforestation rates for the Brazilian Amazon [here](http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates).
+We see that for later years (2005 and afterwards), it appears that as deforestation rates go down or up we also see, often, these trends reflected in the proportional frequency to which discourses about the Amazon takes place.
 
@@
 After cleaning the text we start by getting word frequencies.
-Although qord frequencies do not seem very helpful, more interesting patterns start to appear with bigrams 82 words that appear together) as we see, for example, "meio ambiente" (environemnt) appear central alongside references to the Amazonian forest, the tax free zone in Manaus (capital of the Amazonas state), and references to other countries (outros paises).
+Although word frequencies do not seem very helpful, more interesting patterns start to appear with bigrams 82 words that appear together) as we see, for example, "meio ambiente" (environment) appear central alongside references to the Amazonian forest, the tax free zone in Manaus (capital of the state of Amazonas), and references to other countries ("outros paises").
 
-When it comes to the 30 most frequent words per speaker, we see more interesting patterns as words such as development (all presdidents but Temer), integration (Collor and Itamar), security (Temer), deforestation (Lula, Dilma, and Temer), among others.
+When it comes to the 30 most frequent words per speaker, we see more interesting patterns as words such as development (all presidents but Temer), integration (Collor and Itamar), security (Temer), deforestation (Lula, Dilma, and Temer), among others.
 
@@
   rename(Topic = "Group.1", Terms = "x") %>% 
-  kableExtra::kbl(caption = "Top 10 Words per Topic for Prsidential Speeches Mentioning the Amazon") %>%
+  kableExtra::kbl(caption = "Top 10 Words per Topic for Presidential Speeches Mentioning the Amazon") %>%
   kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
@@
 
-When it comes to the LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each document, we start to see some interesting patterns (for more information on LDA and R approches [here](https://www.tidytextmining.com/index.html)).
+When it comes to the LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each document, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
 We set the number of clusters to be found (topics) at 10, randomly.
@@
 The first three topics relate to themes of security, development, and integration.
-The fourth topic relates to themes of deforestation and sustainable devolopment.
+The fourth topic relates to themes of deforestation and sustainable development.
 Topics five to nine appear to relate to themes of politics, energy, and geography.
@@
 
-Once the clusters are extracted, we can indicate, probabilisticly, how presidents' discourse fall within a topic.
-We see that, for example, Lula's discourses about the Amazon often is clusteres with themes of development and of deforestation.
-At the same time, Bolsonaro's discourses about the Amazon often is clusteres with themes of integration, energy, and the military forces.
+Once the clusters are extracted, we can indicate, probabilistically, how presidents' discourse fall within a topic.
+We see that, for example, Lula's discourses about the Amazon often is clustered with themes of development and of deforestation.
+At the same time, Bolsonaro's discourses about the Amazon often is clustered with themes of integration, energy, and the military forces.
 Sarney engaged with themes of preservation, while Cardoso engages with themes related to energy and integration.
@@
 
-## Get, and compare, sentiment in time for speakers (afinn and NRC)
+## Get, and compare, sentiment in time for speakers (Afinn and NRC)
 
 ```{r sentiment, warning=FALSE, message=FALSE}
-library(ggplot2)
 library(stringr)
@@
 The same can be said about Bolsonaro who used more positively charged words on average than other presidents when speaking about the Amazon according to the lexicon.
-Other presidents, as Cardoso, Rousseff and Lula appear more consistent in time in regards to the average polarity of terms used in Amazonian related discourses than Teme, Collor, and Itamar.
+Other presidents, as Cardoso, Rousseff and Lula appear more consistent in time in regards to the average polarity of terms used in Amazonian related discourses than Temer, Collor, and Itamar.
 
 The NRC sentiment lexicon codes different sentiment for certain words.
-The scores for each of the sentiments soded also are normalized by the number of characters in text data for speaker per year.
+The scores for each of the sentiments coded also are normalized by the number of characters in text data for speaker per year.
 This allow us to compare the sentiments used according to the sentiment lexicon for each speaker per year.
@@
 # Let's code the Amzonian states, the other Brazilian states, and speeches delivered outside Brazil.
-Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
+Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
 summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
@@
 amazon_lda_topic
+
 ```
 
-The summary table illustrates that, as expected, more speeches that mention the Amazon proportionaly take place in Amazonian states in comparison to their proportion in all speeches.
-However, when it comes ot internationa settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.
+The summary table illustrates that, as expected, more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches.
+However, when it comes ot international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.
 
 We can also get the themes by setting for each of the ten topics (clusters) generated with the LDA.
-We see, for example, that some fo the themes related to cooperation and integration appear in Amazonian States and Non Identified stages (topic 2).
-While themes related to developement, deforestation, and sustainability appear in International stages (topic 4).
+We see, for example, that some of the themes related to cooperation and integration appear in Amazonian States and Non Identified stages (topic 2).
+While themes related to development, deforestation, and sustainability appear in International stages (topic 4).
 Interestingly, themes related to preservation of the forest appear in Amazonian states and Non Amazonian States.
 
-# Let's try and categorize the texts into a category...
+# Let's try and categorize the texts into narratives ...
+
+In this preliminary approach we attempt to count and show correlations between coded narratives, presidents, and stages.
 
 ```{r narratives, warning=FALSE, message=FALSE}
-# Amazon_speeches <- dplyr::mutate(Amazon_speeches, narrative = case_when(grepl("", text) ~ "", grepl("", text) ~ "", grepl("", text) ~ ""))
-# summary(as.factor(Amazon_lc$narrative))
+# Create the dictionary
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito")
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
+conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
+anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado") # This appears harder to operationalize than others...
+
+# Create a variable for each and count matches
+Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
+Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
+Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
+Amazon_speeches$anti_environmentalism <- stringr::str_count(Amazon_speeches$text,
+                                                            paste0("(?i)", anti_environmentalism))
+Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
+                                  Amazon_speeches$conservation == 0 & 
+                                  Amazon_speeches$anti_environmentalism == 0, 1, 0)
+
+# Visualize correlations
+ggplot(Amazon_speeches, aes(x = year)) +
+  geom_line(aes(y = sovereignty, color = "Sovereignty")) +
+  geom_line(aes(y =  development, color = "Development")) +
+  geom_line(aes(y =  conservation, color = "Conservation")) +
+  geom_line(aes(y =  anti_environmentalism, color = "Anti_environmentalism")) +
+      labs(x = "Year",
+       y = "",
+       title = "Narratives in Presidential Speeches per year since 1985 in Brazil",
+       color = "Narrative")
+
+# Narrative per president, frequency table
+pres_narratives <- Amazon_speeches %>%
+  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
+  group_by(president) %>%
+  summarise(across(everything(), sum))
+kableExtra::kbl(pres_narratives, caption = "Narratives per President in Brazil") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+
+# Same frequency table but normalized by the numbers of speeches in broader dataset
+pres_narratives_n <- pres_narratives %>%
+  mutate(n_speeches = summary(as.factor(BR_Presidential_Speeches$president))) %>%
+  mutate(across(c(2:6), .fns = ~./n_speeches)) %>%
+  select(-n_speeches) %>%
+  mutate_if(is.numeric, round, digits = 2)
+kableExtra::kbl(pres_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+
+# Table by stage
+stage_narratives <- Amazon_speeches %>%
+  mutate(stage = Amazon_lc$stage) %>%
+  select(-c(context, text, fulltext, year, party, date, title, doc_id, location, president)) %>%
+  group_by(stage) %>%
+  summarise(across(everything(), sum))
+kableExtra::kbl(stage_narratives, caption = "Narratives per President in Brazil") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+
+# Table by stage, normalized
+stage_narratives_n <- stage_narratives %>%
+  mutate(n_stages = summary(as.factor(Amazon_lc$stage))) %>%
+  mutate(across(c(2:6), .fns = ~./n_stages)) %>%
+  select(-n_stages) %>%
+  mutate_if(is.numeric, round, digits = 2)
+kableExtra::kbl(stage_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
 ```
+
+While the dictionary of terms needs to be greatly expanded to operationalize narratives in discourse, we see that some narratives appear more than others in certain periods, often in unexpected years.
+This is specially puzzling as conservationism narratives peak in the late 1980s, sovereignty narratives in the mid 1990s and development narratives in the early 2000s.
+
+Moreover, as the first few plots at the beginning of the document illustrated, Amazon related speeches during the Sarney administration were salient as a proportional of the general numbers of speeches for the president in the dataset.
+at the same time.
+we see that Sarney engages with narratives of sovereignty, development, and conservation.
+Other presidents as Itamar and Cardoso engage overwhelmingly with development related narratives, while Collor and Bolsonaro engage with conservation (though, at least in the case of Bolsonaro, I believe the dictionary is matching negative cases and it needs be improved...).
+
+When it comes to stage, all narratives are proportionally more salient within Amazonian states, as it would be expected.
+Anti-environmentalism appears slightly less in international stages in comparison to others.

### 2021-11-02 data_exploration_2_context.Rmd
updated stopword list

@@
                                           "cumprimentar", "gente", "estado", "querido", "queria",
-                                          "todos", "brasil"))
+                                          "todos", "brasil", "companheiro", "senhores", "site", 
+                                          "companheiras", "companheiros", "companheira",
+                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
+                                          "grosso", "rio", "ministro", "ministra", "josé", "paulo", "pará", "acre", "roraima",
+                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
+                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso", "janeiro",
+                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite",
+                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "porto", "bahia", "é",
+                                          "lá", "et", "in"))
+
 Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")

### 2021-11-04 data_exploration_2_context.Rmd
#created alternative data paths for me #updated stop words #tested lda #updated dictionary

--- 2021-11-01 data_exploration_2_context.Rmd
@@
 # Load data
-BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
+
 # Subset for text matches
@@
 
-# In case you want to sample a few ramdom text observations by president
+# In case you want to sample a few random text observations by president
 # sample_pres <- Amazon_speeches %>% group_by(president) %>% sample_n(8) %>% select(president, year, ccontext)
 
-# Create a littale frequencies data frame
+# Create a little frequencies data frame
 freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
@@
 
-# Simple plot of the frequncy of speeches that mention Amazon since 1985
+# Simple plot of the frequency of speeches that mention Amazon since 1985
 plot(freq_year$year, freq_year$freq, type = "b",
@@
 # Also, let's load the data on annual rates of deforestation in the Brazilian Amazon per year
-amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
+#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
+
 freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year")
@@
                                           "cumprimentar", "gente", "estado", "querido", "queria",
-                                          "todos", "brasil"))
+                                          "todos", "brasil", "companheiro", "senhores",
+                                          "companheiras", "companheiros", "companheira",
+                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
+                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
+                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
+                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
+                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
+                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
+                                          "lá", "et", "in"))
+
 Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")
@@
 amazon_f30
+
 # Just plot in a wordcloud for words
@@
 tamazon
+
 # A plot in a wordcloud for bigrams

### 2021-11-04 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#preliminary version of DRAFT_2

--- 2021-11-04 data_exploration_2_context.Rmd
@@
 ---
-title: "Amazon in Presidential Speeches in Brazil: data exploration for contexts"
-author: "Henrique Sposito and Livio Silva-Muller"
-date: "10/29/2021"
-output: html_document
+title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
+author: "Henrique Sposito & Livio Silva-Muller"
+date: "11/4/2021"
+output: pdf_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-```
 
-## Load Data and Filter it for Amazon related portions in texts
-
-```{r amazon, warning=FALSE, message=FALSE}
 library(dplyr)
@@
 #BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
 BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
 
@@
 
-# In case you want to sample a few random text observations by president
-# sample_pres <- Amazon_speeches %>% group_by(president) %>% sample_n(8) %>% select(president, year, ccontext)
-
-# Create a little frequencies data frame
-freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
-                        freq = as.numeric(summary(as.factor(Amazon_speeches$year))),
-                        freqn = as.numeric(summary(as.factor(Amazon_speeches$year)))/
-                          as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))
-
-# Simple plot of the frequency of speeches that mention Amazon since 1985
-plot(freq_year$year, freq_year$freq, type = "b",
-     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
-     xlab = "Year", ylab = "Frequency")
-
-# Plot number of speeches that mention Amazon normalized by the number of speeches per year in broader data
-plot(freq_year$year, freq_year$freqn, type = "b",
-     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
-     sub = "Normalized by the number of speeches per year in broader dataset",
-     xlab = "Year", ylab = "Frequency")
-
-# Also, let's load the data on annual rates of deforestation in the Brazilian Amazon per year
-#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
-
-freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year")
-ggplot(freq_year, aes(x = year)) +
-    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
-    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
-      labs(x = "Year",
-       y = "",
-       title = "Presidential Speeches that Mention the Amazon since 1985 in Brazil",
-       subtitle = "Compared to annual deforestation rates since 1988",
-       caption = "Frequencies are normalized by the number of speeches per year in dataset",
-       color = "Legend")
 ```
 
-We start by subsetting the broad dataset it for the texts that mention the strings "Amazon" in it as a word or parts of words.
-Then, we us `{poldis}` to get the context for each mention of the "Amazon", by default one sentence before and one sentence after the sentence in which the string "Amazon" is matched.
-
-From the first plot, the proportion of speeches that mention the word "Amazon" increase in frequency in 1989 (possibly related to Amazon Fires coverage from the New York Times see [here](https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html) and [here](https://www.nytimes.com/1989/03/23/world/brazil-smarting-from-the-outcry-over-the-amazon-charges-foreign-plot.html)), around 1992 (likely related to the Rio Conference), from 2005 to 2010 (possibly related to the "preservation" legislation turn under the Lula Administration), and after 2016 (possibly related to increasing deforestation rates and international attention).
-Notice that the frequency is normalized by the number of speeches per year in the broader dataset.
-
-The second plot also compares mentions of Amazon and annual deforestation rates for the Brazilian Amazon [here](http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates).
-We see that for later years (2005 and afterwards), it appears that as deforestation rates go down or up we also see, often, these trends reflected in the proportional frequency to which discourses about the Amazon takes place.
-
-## Clean text and get most frequent terms overall, and by speaker, in time
-
-```{r term frequency, warning=FALSE, message=FALSE}
-library(tidytext)
-library(kableExtra)
-library(stringr)
-library(wordcloud)
-library(RColorBrewer)
-
+```{r setup, include=FALSE}
 # Rename variables to adapt to text analysis packages' expectations
@@
 
-# Remove stopwords and punctuation
+# Remove stop words and punctuation
 Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
@@
 amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))
+
+```
+
+## R Markdown
+
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+## Including Plots
+
+You can also embed plots, for example:
+
+```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
+
+freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
+                        freq = as.numeric(summary(as.factor(Amazon_speeches$year))),
+                        freqn = as.numeric(summary(as.factor(Amazon_speeches$year)))/
+                          as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))
+
+plot(freq_year$year, freq_year$freqn, type = "b",
+     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
+     sub = "Normalized by the number of speeches per year",
+     xlab = "Year", ylab = "Frequency")
+
+freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
+ggplot(freq_year, aes(x = year)) +
+    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
+    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
+      labs(x = "Year",
+       y = "",
+       title = "Presidential Speeches that Mention the Amazon since 1985 in Brazil",
+       subtitle = "Compared to annual deforestation rates since 1988",
+       caption = "Frequencies normalized by the number of speeches per year in dataset",
+       color = "Legend")
+
+```
+
+```{r location, warning=FALSE, message=FALSE}
+# Location was added with poldis::extraxt_location(), still needs to be improved...
+# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
+# Let's code the Amazonian states, the other Brazilian states, and speeches delivered outside Brazil.
+Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
+summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
+# Just a comparison with the proportion of speeches per stage on the broader dataset
+stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
+stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
+                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
+                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
+stage_rate
+```
+
+```{r top words by speaker, warning=FALSE, message=FALSE}
 
@@
 f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro) %>% 
-  kableExtra::kbl(caption = "Top 10 Words Per President") %>%
+  kableExtra::kbl(caption = "Top 30 Words Per President") %>%
   kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
@@
 ```
-
-After cleaning the text we start by getting word frequencies.
-Although word frequencies do not seem very helpful, more interesting patterns start to appear with bigrams 82 words that appear together) as we see, for example, "meio ambiente" (environment) appear central alongside references to the Amazonian forest, the tax free zone in Manaus (capital of the state of Amazonas), and references to other countries ("outros paises").
-
-When it comes to the 30 most frequent words per speaker, we see more interesting patterns as words such as development (all presidents but Temer), integration (Collor and Itamar), security (Temer), deforestation (Lula, Dilma, and Temer), among others.
-
-## Simple LDA model by speakers
 
@@
 
-When it comes to the LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each document, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
-We set the number of clusters to be found (topics) at 10, randomly.
-We, then, select the top ten words coded for each topic.
-The first three topics relate to themes of security, development, and integration.
-The fourth topic relates to themes of deforestation and sustainable development.
-Topics five to nine appear to relate to themes of politics, energy, and geography.
-The last topic appears to relate to themes of preservation of the Amazonian forest.
-
-Once the clusters are extracted, we can indicate, probabilistically, how presidents' discourse fall within a topic.
-We see that, for example, Lula's discourses about the Amazon often is clustered with themes of development and of deforestation.
-At the same time, Bolsonaro's discourses about the Amazon often is clustered with themes of integration, energy, and the military forces.
-Sarney engaged with themes of preservation, while Cardoso engages with themes related to energy and integration.
-Others as Rousseff and Temer appear to engage with themes of geography, politics, energy; while Collor an Itamar appear to engage with themes of security, development, and integration.
-
-## Get, and compare, sentiment in time for speakers (Afinn and NRC)
-
-```{r sentiment, warning=FALSE, message=FALSE}
-library(stringr)
-# library(poldis)
-
-# Load internal sentiment dictionaries from poldis
-Afinn_pt <- poldis:::Afinn_pt
-nrc_portuguese <- poldis:::nrc_portuguese
-
-# Aggregate by president and year and transform into a corpus
-amazon_sent <- mutate(Amazon_speeches, doc_id = paste0(doc_id, "_", year))
-amazon_sent <- aggregate(amazon_sent$text, list(amazon_sent$doc_id), paste, collapse =" ") %>%
-  rename(doc_id = "Group.1", text = "x") %>% 
-  mutate(char = nchar(text))
-amazon_sent_wf <- VCorpus(DataframeSource(amazon_sent)) %>%
-  tidy() %>%
-  unnest_tokens(word, text) %>%
-  count(id, word, sort = TRUE)
-
-# Get afinn sentiment
-amazon_sent_af <- inner_join(amazon_sent_wf, Afinn_pt, by = "word") %>%
-  group_by(id) %>%
-  summarize(value = sum(n)) %>%
-  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
-         president = stringr::str_remove_all(id, "_[0-9]{4}"),
-         date2 = stringr::str_extract(id, "[0-9]{2}$"),
-         nvalue = value/amazon_sent$char)
-
-# Plot Afinn sentiment in time for speeches about the Amazon
-ggplot(amazon_sent_af, aes(x = reorder(date2, as.numeric(year)), y = nvalue , fill = president)) +
-  geom_line(aes(group = president)) +
-  geom_point(size = 5, shape = 21) +
-  labs(x = "",
-       y = "",
-       title = "Sentiment in Presidential Speeches about the Amazon",
-       subtitle = "Normalized by the number of characters in text for speaker",
-       caption = "Afinn sentiment lexicon")
-
-# Get NRC per speaker
-amazon_sent_nrc <- inner_join(amazon_sent_wf, nrc_portuguese, by = "word") %>%
-  filter(sentiment != "positive", sentiment != "negative") %>% 
-  # removing positive and negative for more informative results
-  group_by(id, sentiment) %>%
-  summarize(value = sum(n)) %>%
-  mutate(year = stringr::str_extract(id, "[0-9]{4}"),
-         president = stringr::str_remove_all(id, "_[0-9]{4}"),
-         date2 = stringr::str_extract(id, "[0-9]{2}$"))
-# Normalize (first you have to multiple each speaker value 8 times)
-char <- select(amazon_sent, -text) %>% rename(id = doc_id)
-amazon_sent_nrc <- left_join(amazon_sent_nrc, char, by = "id") %>%
-  mutate(nvalue = (value/char)*100000)
-
-# Plot NRC
-ggplot(amazon_sent_nrc, aes(x = reorder(id, as.numeric(year)), y = nvalue, fill = sentiment)) +
-  geom_bar(position="stack", stat="identity") +
-  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=1)) +
-  labs(x = "",
-       y = "",
-       title = "Sentiment in Presidential Speeches about the Amazon",
-       subtitle = "Normalized by the number of characters in text for speaker",
-       caption = "NRC sentiment lexicon") +
-  coord_flip() +
-  expand_limits(y=c(0, 1000))
-```
-
-The Afinn sentiment lexicon gets to the polarity of certain words coded by assigning a value to them, positive and negative.
-The scores are normalized by the number of characters in text data for speaker per year.
-This allow us to compare the average use of charged words coded for with the sentiment lexicon for each speaker per year.
-We see in the plot, for example, that Sarney from 1985-87 employs more positive words coded for sentiment on speeches that mention the Amazon than other presidents.
-The same can be said about Bolsonaro who used more positively charged words on average than other presidents when speaking about the Amazon according to the lexicon.
-Other presidents, as Cardoso, Rousseff and Lula appear more consistent in time in regards to the average polarity of terms used in Amazonian related discourses than Temer, Collor, and Itamar.
-
-The NRC sentiment lexicon codes different sentiment for certain words.
-The scores for each of the sentiments coded also are normalized by the number of characters in text data for speaker per year.
-This allow us to compare the sentiments used according to the sentiment lexicon for each speaker per year.
-We see in the plot, that Lula in the early 2000s used many words coded for "trust" when speaking about the Amazon on average than other presidents/years.
-As well, Itamar in 1992 appeared to use more words coded for "anger" and "fear" on average than other presidents/years.
-
-## Does location matter?
-
-```{r location, warning=FALSE, message=FALSE}
-# Location was added with poldis::extraxt_location(), still needs to be improved...
-# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
-# Let's code the Amzonian states, the other Brazilian states, and speeches delivered outside Brazil.
-Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
-summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
-# Just a comparison with the proprtion of speeches per stage on the broader dataset
-stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
-stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
-                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
-                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
-stage_rate
-
-# Let's try an simple LDA model again
-Amazon_lc <- mutate(Amazon_lc, doc_id = stage) %>% arrange(doc_id, text)
-amazon_lcc <- tm::VCorpus(DataframeSource(Amazon_lc))
-amazon_dtm_lc  <- DocumentTermMatrix(amazon_lcc)
-amazon_lda_lc <- topicmodels::LDA(amazon_dtm_lc, k = 10, control = list(seed = 1234)) # set k = 10
-amazon_lda_lcc <- tidy(amazon_lda_lc, matrix = "beta") %>%
-  arrange(desc(beta)) %>%
-  group_by(topic) %>%
-  filter(row_number() %in% 1:10) %>%
-  arrange(topic)
-topten_lc <- aggregate(amazon_lda_lcc$term, list(amazon_lda_lcc$topic), paste, collapse=", ") %>%
-  rename(Topic = "Group.1", Terms = "x")
-
-# Get stage and merge tables
-amazon_lda_lcs <- tidy(amazon_lda_lc, matrix = "gamma") %>%
-  arrange(desc(gamma)) %>%
-  group_by(document) %>%
-  filter(row_number() %in% 1:3) %>% # get the top 3 topics per location
-  arrange(document) %>% 
-  select(-gamma) %>% 
-  distinct()
-amazon_lda_topic <- aggregate(amazon_lda_lcs$document, list(amazon_lda_lcs$topic), paste, collapse = ", ") %>% rename(Topic = "Group.1", Stage = "x") 
-amazon_lda_topic <- dplyr::left_join(topten_lc, amazon_lda_topic, by = "Topic") %>%
-  kableExtra::kbl(caption = "Top 10 Words per Topic for Stages") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-amazon_lda_topic
-
-```
-
-The summary table illustrates that, as expected, more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches.
-However, when it comes ot international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.
-
-We can also get the themes by setting for each of the ten topics (clusters) generated with the LDA.
-We see, for example, that some of the themes related to cooperation and integration appear in Amazonian States and Non Identified stages (topic 2).
-While themes related to development, deforestation, and sustainability appear in International stages (topic 4).
-Interestingly, themes related to preservation of the forest appear in Amazonian states and Non Amazonian States.
-
-# Let's try and categorize the texts into narratives ...
-
-In this preliminary approach we attempt to count and show correlations between coded narratives, presidents, and stages.
-
-```{r narratives, warning=FALSE, message=FALSE}
+```{r narratives, warning=FALSE, message=FALSE, echo=TRUE}
 # Create the dictionary
@@
 conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
-anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado") # This appears harder to operationalize than others...
+anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...
+```
+
+```{r narratives, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 ```
-
-While the dictionary of terms needs to be greatly expanded to operationalize narratives in discourse, we see that some narratives appear more than others in certain periods, often in unexpected years.
-This is specially puzzling as conservationism narratives peak in the late 1980s, sovereignty narratives in the mid 1990s and development narratives in the early 2000s.
-
-Moreover, as the first few plots at the beginning of the document illustrated, Amazon related speeches during the Sarney administration were salient as a proportional of the general numbers of speeches for the president in the dataset.
-at the same time.
-we see that Sarney engages with narratives of sovereignty, development, and conservation.
-Other presidents as Itamar and Cardoso engage overwhelmingly with development related narratives, while Collor and Bolsonaro engage with conservation (though, at least in the case of Bolsonaro, I believe the dictionary is matching negative cases and it needs be improved...).
-
-When it comes to stage, all narratives are proportionally more salient within Amazonian states, as it would be expected.
-Anti-environmentalism appears slightly less in international stages in comparison to others.

### 2021-11-04 data_exploration_2_context.Rmd
Fixed the issue with the plot for narratives in time

@@
 library(ggplot2)
+remotes::install_github("henriquesposito/poldis")
+library(poldis)
 
 # Load data
-#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
-BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
+BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
+#BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") # Livio's path
 
@@
 # Also, let's load the data on annual rates of deforestation in the Brazilian Amazon per year
-#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
+amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
+# amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
 
@@
                                           "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
-                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
-                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
-                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
-                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
-                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
-                                          "lá", "et", "in"))
+                                          "grosso","ministro", "ministra", "josé", "pará", "acre",
+                                          "roraima", "manaus", "rondônia", "ministros", "luiz", 
+                                          "antonio", "vou", "eduardo braga", "rio de janeiro",
+                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", 
+                                          "mato grosso", "outro", "onde", "discurso", "parte", 
+                                          "anos", "cada", "todo", "porto velho", "visite site",
+                                          "site secretaria", "minas gerais", "lula silva", "inácio lula",
+                                          "amapa", "bahia", "é", "lá", "et", "in"))
 
@@
 amazon_lda_topic
-
 ```
@@
 # Visualize correlations
-ggplot(Amazon_speeches, aes(x = year)) +
-  geom_line(aes(y = sovereignty, color = "Sovereignty")) +
-  geom_line(aes(y =  development, color = "Development")) +
-  geom_line(aes(y =  conservation, color = "Conservation")) +
-  geom_line(aes(y =  anti_environmentalism, color = "Anti_environmentalism")) +
+am_narratives <- Amazon_speeches %>%
+  select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
+  tidyr::pivot_longer(sovereignty:other) %>% 
+  group_by(year, name) %>% 
+  summarise(value = sum(value)) %>% 
+  rename(narrative = name)
+ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
+  geom_line(aes(group = narrative, color = narrative), size = 1) +
   labs(x = "Year",
        y = "",
-       title = "Narratives in Presidential Speeches per year since 1985 in Brazil",
-       color = "Narrative")
+       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")
 

### 2021-11-05 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#tested knitting to pdf; needs formatting.

@@
 
-```{r setup, include=FALSE}
+```{r setup I, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 library(ggplot2)
+library(tidytext)
+library(kableExtra)
+library(stringr)
+library(wordcloud)
+library(RColorBrewer)
 
@@
 
-```{r setup, include=FALSE}
+```{r setup II, include=FALSE}
 # Rename variables to adapt to text analysis packages' expectations
@@
                                           "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
-                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
+                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
                                           "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
@@
 Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
-summary(as.factor(Amazon_lc$stage)) # A lot of missing observations still ...
 # Just a comparison with the proportion of speeches per stage on the broader dataset
@@
 
-# Just plot in a wordcloud for words
-set.seed(1234)
-wordcloud(words = amazon_f$term, freq = amazon_f$freq, min.freq = 50,
-          max.words=200, random.order = FALSE, rot.per=0.35, 
-          colors = brewer.pal(8, "Dark2"))
-
 # Let's see if bigrams help us more here
@@
 tamazon
-
-# A plot in a wordcloud for bigrams
-set.seed(1234)
-wordcloud(words = tamazon$bigram, freq = tamazon$n, min.freq = 20,
-          max.words=200, random.order = FALSE, rot.per=0.35, 
-          colors = brewer.pal(8, "Dark2"))
 
@@
 
-```{r narratives, warning=FALSE, message=FALSE, echo=TRUE}
+```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}
+
 # Create the dictionary
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito")
+
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
 development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
@@
 anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...
+
 ```

### 2021-11-05 08112021_Sposito & Silva_Muller_DRAFT.Rmd

@@
 library(RColorBrewer)
+library(tidyr)
 
@@
 #amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
+#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
 BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
+Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path
 
 # Subset for text matches
-Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
+#Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
 # Remove accents and extra spaces
-Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
+#Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
 # Make all lower case
-Amazon_speeches$text <- tolower(Amazon_speeches$text)
+#Amazon_speeches$text <- tolower(Amazon_speeches$text)
 # Remove extra white spaces
-Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
+#Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
 # Get only the pertinent text chunks
-Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
+#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
 # Transform into a single text per row...
-Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
+#Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
+#saveRDS(Amazon_speeches, file="amazon_speeches.rds")
 
@@
 You can embed an R code chunk like this:
-
-## Including Plots
-
-You can also embed plots, for example:
 

### 2021-11-05 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#structure of the paper brought to the markdown # tables still partially cut because of formatting

@@
 author: "Henrique Sposito & Livio Silva-Muller"
-date: "11/4/2021"
+date: "11/11/2021"
 output: pdf_document
 ---
+# 1 Introduction
+
+> Quote 1  
+> Quote 2
+
+# 2 Grounding Amazonian narratives in the literature
+
+## 2.1 The Brazilian Amazon in social sciences: where is culture and discourse?
+
+## 2.2 Performing Amazonian narratives: environmental historigraphy and ideal types
+
+*Sovereignty*
+
+*Developmentalism*
+
+*Conservationism*
+
+*Anti social-environmentalism*
+
+# 3 Operationalizing Amazonian narratives: data and methods
+# 4 Preliminary Analysis
 
@@
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
+```{r speech frequencies, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
     geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
-      labs(x = "Year",
-       y = "",
-       title = "Presidential Speeches that Mention the Amazon since 1985 in Brazil",
+      labs(x = "",
+       y = "Relative share of speeches per year",
+       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
        subtitle = "Compared to annual deforestation rates since 1988",
        caption = "Frequencies normalized by the number of speeches per year in dataset",
-       color = "Legend")
+       color = "")
 
@@
 
-```{r location, warning=FALSE, message=FALSE}
+```{r location, echo=FALSE, warning=FALSE, message=FALSE}
 # Location was added with poldis::extraxt_location(), still needs to be improved...
@@
 
-```{r top words by speaker, warning=FALSE, message=FALSE}
+```{r top words by speaker, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r lda, warning=FALSE, message=FALSE}
+```{r lda, warning=FALSE, echo=FALSE, message=FALSE}
 library(topicmodels)
@@
 
-```{r narratives, warning=FALSE, message=FALSE, echo=FALSE}
+```{r narratives, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 ```
+
+# 5 Bibliography

### 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#markdown

@@
 date: "11/11/2021"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 ---
@@
 # 3 Operationalizing Amazonian narratives: data and methods
+
 # 4 Preliminary Analysis
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
-Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path
+Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path to load data after poldis
 
@@
 plot(freq_year$year, freq_year$freqn, type = "b",
-     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
+     main = "Presidential Speeches mentioning the Amazon since 1985 in Brazil",
      sub = "Normalized by the number of speeches per year",
-     xlab = "Year", ylab = "Frequency")
+     xlab = "", ylab = "Frequency")
 

### 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#updated dictionary #cleaned stop words #removed redundant tables

@@
                                           "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
-                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso",
-                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite site",
-                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "bahia", "é",
-                                          "lá", "et", "in"))
+                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul",
+                                          "norte", "mato grosso","outro", "onde", "discurso", "parte", "anos", "cada", "todo", 
+                                          "porto velho", "visite site", "site secretaria", "minas gerais", "lula silva", 
+                                          "inácio lula", "amapa", "bahia", "é", "lá", "et", "in", "httpwww"))
 
@@
   group_by(document) %>%
-  filter(row_number() %in% 1:2) %>% # get the top 3 topics per speaker
+  filter(row_number() %in% 1:2) %>% # get the top 2 topics per speaker
   arrange(document) %>%
@@
 sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
-development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto")
-conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest")
-anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas") # This appears harder to operationalize than others...
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto|madeireira|produzir")
+conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteger")
+anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas|ong|xiita") # This appears harder to operationalize than others...
 
@@
        y = "",
-       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")
-
-# Narrative per president, frequency table
-pres_narratives <- Amazon_speeches %>%
-  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
-  group_by(president) %>%
-  summarise(across(everything(), sum))
-kableExtra::kbl(pres_narratives, caption = "Narratives per President in Brazil") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
+    facet_wrap(~narrative)
 

### 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#moved "Presidential speeches mentioning Amazon" to ggplot and added a smoooth

@@
 
-plot(freq_year$year, freq_year$freqn, type = "b",
-     main = "Presidential Speeches mentioning the Amazon since 1985 in Brazil",
-     sub = "Normalized by the number of speeches per year",
-     xlab = "", ylab = "Frequency")
+ggplot(freq_year, aes(year, freqn))+
+    geom_line()+
+    geom_point()+
+    geom_smooth(method=lm, color="#bab86c") +
+      labs(x = "",
+       y = "Relative share of speeches per year",
+       title = "Presidential speeches mentioning the Amazon (1985-2020)",
+       caption = "Frequencies normalized by the number of speeches per year in dataset",
+       color = "")
 
@@
        subtitle = "Compared to annual deforestation rates since 1988",
-       caption = "Frequencies normalized by the number of speeches per year in dataset",
        color = "")

### 2021-11-08 08112021_Sposito---Silva_Muller_DRAFT.Rmd
#text in #added stop words # changed freq table to plot

--- 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
@@
 am_narratives <- Amazon_speeches %>%
-  select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
+  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
   tidyr::pivot_longer(sovereignty:other) %>% 
@@
   rename(narrative = name)
+
 ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
@@
 # Same frequency table but normalized by the numbers of speeches in broader dataset
+pres_narratives <- Amazon_speeches %>%
+  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
+  group_by(president) %>%
+  summarise(across(everything(), sum))
+
 pres_narratives_n <- pres_narratives %>%
@@
 
-# Table by stage
+# Table by stage, normalized
 stage_narratives <- Amazon_speeches %>%
@@
   summarise(across(everything(), sum))
-kableExtra::kbl(stage_narratives, caption = "Narratives per President in Brazil") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
 
-# Table by stage, normalized
 stage_narratives_n <- stage_narratives %>%

### 2021-11-08 08112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#text in #added stop words # changed freq table to plot

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author: "Sposito & Silva-Muller"
date: "11th of November of 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# 1 Introduction

> “The world should understand that the Brazilian Amazon has an owner: the Brazilian people.” (Lula, May 2008)^[Taken from here: https://www.reuters.com/article/brasil-politica-lula-amazonia-pol-idBRN2634078320080526]

> “Do you know what ‘Triple A’ is? It is the Amazon, Andes and Atlantic. These represent 136 million hectares, and the first world wants to administer these areas.” (Bolsonaro, July 2019)^[Taken from here: https://g1.globo.com/politica/noticia/2018/11/28/bolsonaro-diz-que-pediu-cancelamento-da-conferencia-do-clima-no-brasil-em-2019.ghtml]

Preserving the Amazon has rarely been the top priority of Brazilian federal governments. Though deforestation rates began to steadily increase in 2012 (see Carvalho et al. 2019), after a decade of decline, they spiked in 2019 after Bolsonaro took power (INPE 2021). This is no surprise as the current federal government is weakening the foundations of the Brazilian environmental governance system through budgetary cuts, presidential appointments, and dissociating government from civil society (see Ferrante and Fearnside 2019). These factors contributed to record-high fires in the Amazon and unprecedented monthly rates of deforestation during the dry seasons of 2019, 2020, and 2021 (INPE 2021). Although policy discontinuities between Bolsonaro's Amazon agenda and previous governments have been documented by academic scholarship and specialized media (see Abessa, Famá, and Buruaem 2019; Spring 2021), we lack empirical accounts of how Amazonian discourses changed. Pokorny et. al (2021, p. 2208), for example, argue that Bolsonaro’s Amazonian discourses shifted drastically in relation to earlier governments, giving rise to a “populist neoliberal” phase of discourse and policy developments in the region. However, the authors rely on a few disconnect quotes from Bolsonaro about the Amazon to exemplify phases defined by policy discontinuities. How, then, have Amazonian presidential discourses changed in time?

Amazonian related political discourses at the top can help expand, or restrict, what types of behavior are expected and accepted in society in respect to the region. This is especially pertinent for deforestation as previous research found that expectations about government response, generated from material and discursive changes, are a crucial factor in decisions to deforest at the local level (Campbell 2015). When, for example, Bolsonaro says he will end the “industry of fines” in reference to institutions that police environmental crimes, the loud and clear message is that oversight will decrease (see Ferrante and Fearnside 2019). To study change and continuity in presidential discourses about the Amazon we build upon the environmental historiography literature which have documented cultural imaginaries of, and from, the region thoroughly, mobilized by presidents in discourse via political narratives.In so doing, we understand Amazonian narratives^[We utilize discourse and speech interchangeably, to denote general spoken communication by presidents. Narratives, on the other hand, constitute discourse.] as originating in specific historical periods, connecting the discourse to the broader social history of the region and country.

We propose four ideal type Amazon related narratives in political discourses: sovereignty, developmentalism, conservationism, and anti-environmentalism. Sovereignty narratives touch on imaginaries of threat that hail from the time of the scramble for the Amazon (see Hecht and Cockburn 1990) to contextualize or justify proposed political actions of control, occupation, and monitoring of the region. Developmentalist narratives employ imaginaries of underdevelopment and economic needs in the region, advancing political actions related to exploring economically of the region and the forest (see Acker 2013). Conservatism narratives deploy imaginaries related to the value of the standing Amazonian ecosystem to justify political actions related to preserving the forest and idigenous peoples’ rights (see Hochstetler and Keck 2007). Anti-environmentalism builds upon imaginaries related to issues with socio-environmentalism and excess preservation for even development to justify political actions related to deregulation.

To analyze Amazonian narratives across time and space, we use a dataset of presidential discourse ranging from 1985 to 2020 with 6088 speeches and a combination of natural language processing and qualitative coding. We subset the text dataset to select texts which contain words related to Amazon. We, then, build a dictionary of terms to operationalize Amazonian narratives and trace their evolution and change across presidential mandates and stages (local, national, or international). By tying Amazonian narratives in presidential discourse to environmental historiography, we provide the first historically and empirically informed account of how, when, and where Amazonian narratives are mobilized at the top.

This paper proceeds as follows: we start with a brief review of the social sciences literature on the Brazilian Amazon. We then move to our conceptual framework, which ties environmental historiography to our understanding of narratives. We provide a targeted overview of recent Amazonian historiography, which serves the purpose of identifying and grounding ideal-typical narratives. Third, we discuss the data, methods, and the operationalization of these narratives. We then present our preliminary results by contextualizing them into the last decades of environmental governance in Brazil. We conclude by providing avenues for future research connecting political discourses and environmental related outcomes.

# 2 Grounding Amazonian narratives in the literature
## 2.1 The Brazilian Amazon in social sciences: where is culture and discourse?

We contend that presidential discourse at the top matters because it expands or restricts the range of possibilities for other actors. When presidents speak about the Amazon, it makes international headlines (Brice and Smith 2021; Harris 2021; Miranda 2021), inciting international responses, and feeds into the behavior of domestic actors, from investors to agricultural giants to local farmers, who take what presidents say into consideration. When presidents mobilize Amazonian narratives that connect the region to specific imaginaries of the future and past, they are touching upon shared webs of meaning about the region. So, before dissecting Amazonian narratives, we will dwell into the arena of Amazonian related culture. But how to situate political discourse and culture in social sciences literature about the Brazilian Amazon? In the following, we provide a synthetic review of the literature to argue that while ethnographers have been particularly successful exploring the role of culture in the Brazilian Amazon, we lack accounts that situate it at the level of discourse generally.

A substantial number of studies about the Amazon try to identify causes of and remedies to deforestation. This literature is interdisciplinary, ranging from ecology, to economics, to political sciences. It assesses the effectiveness of policies their relative contribution, or how they affect decision making of actors from rather rational perspectives at various levels (Arima et al. 2014; Assunção, Gandour, and Rocha 2015; Boucher, Roquemore, and Fitzhugh 2013; Nepstad et al. 2009). As it is particularly hard to econometrically tie discourse to deforestation outcomes, there are no studies that look at the effects of political discourses on deforestation systematically. There has been a recent call, though, to better account for the role of culture in the development of land systems’ use alongside demographic, economic, technological, and governance factors (de Waroux et al., 2021). Bringing culture in might help formalize findings from single case studies, hailing from ethnographies, that explain decisions to deforest, or not, based on individual and collective values rather than utility. de Waroux et al. (2021) propose to approach culture as a shared symbolic system or ‘webs of meaning’ that play a role in cognition and other structural drivers of land-use behavior.

Another line of inquiry is interested in explaining who influences Brazilian environmental policy and how. Researchers in this line of inquiry seek to understand interest formation, resembling international political economy approaches. This line of research has identified the role transnational connections (Keck and Sikkink, 1998; Hochstetler and Keck, 2007; Silva-Muller & Faul, 2021), domestic actors’ interests (Franchini and Viola, 2019), and bureaucrats (Abers 2019; Silva-Muller, forthcoming). Some authors attempt to bring cultural dimensions to these studies through ethnographic work. Rajão and Vurdubakis (2013), for example, conduct longitudinal participant observation with the environmental police (IBAMA) to argue that the process of rendering deforestation a stable object of knowledge, that can be objectively identified and sanctioned, is deeply social and full of antagonisms. Lahsen (2004; 2009) discusses how Brazil could become a net receiver of international funds for climate mitigation, though Brazilian policymakers often ignore the scientific evidence and  push against such funding because of a national political culture of sovereignty protection inherited from the military dictatorship. Campbell (2015) proposes the concept of speculative accumulation to capture the practices of land-grabbers in the deforestation arch who make property appear and disappear based on their expectations of the future and attempts to rewrite the past through material practices (e.g. grillagem).

Nevertheless, there are very few studies looking into political discourses to explain who influence environmental police outcomes. Barros (2020), for instance, analyzes Amazonian discourse in the Brazilian Congress with the objective of identifying the main arguments put forth by congressmen. The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development). However, political discourses in the congress are less visible to the broader population than other types of political discourses at the top, such as presidential discourses. At the same time, congressional discourses have specific purposes of discussing, or proposing, legislation in a technical manner.

Except for ethnographers, who advanced multiple versions of why and how culture matters for deforestation in the Amazon and environmental policy outcomes in Brazil, we lack accounts of the importance of culture more generally. This is key as the expectations about the future regarding government’s response are a key variable in the decision to deforest or not (Campbell, 2015). Such expectations are informed by shared meanings and values (de Waroux et. al., 2021), which travel through various means including discourse at the top. Building on these studies and on cultural sociology, we propose to situate culture at the level of discursive practices and understand what narratives are mobilized, when and where.

## 2.2 Performing Amazonian narratives: environmental historigraphy and ideal types

Amazonian narratives constitute discourses that connect the region to specific imaginaries of the future and past. We argue that they touch on shared meanings about the Amazon that are available to the speaker as part of the larger social history of the region and country. To identify a few possible narratives, we utilize environmental historiography about the Amazon. We build Amazonian narratives as ideal types, that is, unified analytical constructs portraying a ‘pure’ version of a phenomenon (Weber 1949). In that sense, they rarely exist in its purest form. It serves the purpose of allocating empirical observations within a range of possibilities. The ideal types also help us deal with statements that perform different narratives. We broadly understand political discourses as performances seeking to appeal to diverse audiences across multiple political stages to project a definition of the situation (Goffman 1956, p. 3). As political stages, audiences, and time change, so do narratives. As with broader political discourses, narratives can appear together, not necessarily in consistent ways in time or across stages. As we show in section 3, our methodological strategy utilizing allows us to allocate statements within one or more ideal types, providing a more sophisticated portrayal of political discourse.

When speaking, depending on the stage, presidents have varying levels of scripted discourse. In a message to congress, for example, discourse might be carefully crafted by a handful of specialists. However, in inaugural speeches for a bridge in a small town in Brazil presidents might have more room to deliver a speech more freely. In the first case, alluding to specific Amazonian narratives might be a conscious decision. In the second case, an allusion might be more spontaneous as narratives are available as part of the larger repertoire. We adopt the idea of performing Amazonian narratives to capture this variety. In opposition to rational choice models that see speech as a function of calculated decision, performances involve both improvisation and preparation, which in turn are constrained by the set of available possibilities. We see performance as a less strict way of approaching the issue at hand. So, what Amazonian narratives can presidents perform?

*Sovereignty*

In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, a social history of the Brazilian Amazon dating 1990, Susanna Hecht and Alexander Cockburn write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites” (1991, p.1). It started with the first natural history of the New World, by Oviedo in 1535, who while naming mysterious plants and creatures, recounts the stories of conquest of local populations and gold hoarders (ibid). The dream of fortunes to be found in the Eldorado composed the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else. It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as “a […] form of nation building […]” (Hecht and Cockburn 1991, preface). The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory. In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru (Hecht, 2013, p. 8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian. While Brazilian military diplomacy was very successful, the process did not come without its traumas. A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn, 1991). This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat.

We understand claims of sovereignty as a particular narrative that touches on imaginaries of threat that hail from the time of the scramble for the Amazon. The sovereignty narrative advances the view that the Brazilian Amazon is Brazilian and foreign presence in the region needs to be monitored closely.

*Developmentalism*

The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon. This was mostly done in a particularly “high-modernist” (Scott, 1998) with military bureaucrats designing centralized policies aiming at conquering nature and developing the region. In 1966, for example, the Brazilian Military government launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2013). First, nature should be conquered by men. Second, exploiting natural resources would render the Amazon region a global powerhouse. Third, such a project would integrate the region with the rest of the country. Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry. The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2013), leading to a series of national and international enterprises settling in the Amazon region.

The developmentalist narrative advances the view that the Brazilian Amazon needs to be developed and modernized. This includes expanding the agricultural frontier through incentives, creating infrastructure as roads and dams, and fostering industries through tax-free zones. It has its origins in the policies of the 1930s that attempted to modernize the recently consolidated region (Hecht and Cockburn, 1990), but were extended throughout the 20th century. It also captures arguments of the 20th century that defended the integration of indigenous populations into the nation via assimilation and inclusion in economic life. This narrative employs imaginaries of underdevelopment and economic needs in the Amazon while, at the same time, focus on the unexplored economic potential of the region and forest.

*Conservationism*

The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) (Drummond and Barros-Platiau 2006). This is mostly because “the generals had unleashed forces beyond their control, and now the Amazon faced its apocalypse” (Hecht and Cockburn, 1990, p. 141). As deforestation, fires, and violence rose in the region and caught international attention, the military government deemed as necessary the establishment of an environmental bureaucracy. Concurrently, a new form of environmentalism in civil society consolidated in the 1990s: socio-environmentalism. Hochstetler and Keck define it as an emphasis on local livelihoods of people while protecting nature, which has its roots in the wider process of democratization of Brazil, the local advocacy and assassination of Chico Mendes, and the multi-level preparation for the 1992 Earth Summit in Rio de Janeiro (2007). The latter made many international NGOs establish their offices and presence in Brazil (e.g. WWF, GreenPeace, Friends of the Earth, Conservation International). International foundations started to increase their operations in the country and channel funds to NGOs and governmental institutions working in the Brazilian Amazon. The development of this new governance ecosystem led to increased professionalization of local NGOs which, in turn, resulted in a more systematic participation of civil society in public policy surrounding the Brazilian Amazon (Hochstetler and Keck 2007).

The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination (see Hochstetler and Keck 2007). This narrative focuses on imaginaries related to the values of a standing forest and of preserving the ecosystem of natures and peoples in the region.

*Anti socio-environmentalism*

In the early 2000s, many of the ideas developed by socio-environmentalism became public policy, leading to a sharp decrease in deforestation in the Amazon from 2004 to 2012 (Arima et al. 2014; Assunção, Gandour, and Rocha 2015; Boucher, Roquemore, and Fitzhugh 2013; Nepstad et al. 2009). Brazil boasted of an image of strong deliverer, with not only the allegedly best legislation in place but also concrete implementation results (Franchini & Viola, 2019). As deforestation rates started to increase in 2012, and more rapidly during Bolsonaro’s administration in 2019, socio-environmentalism fell under attack. Previous governments and NGOs were accused of preserving too much and having veiled financial and political interests.

The anti socio-environmentalist narrative advances views that socio-environmentalism is a problem.  It highlights the economic benefits related to exploration, while emphasizing as well as the costs of preservation. It differs from the developmentalist narrative, as it attacks NGOs and local populations for the excesses of preservation. These attacks diverge in nature, from claiming NGOs have vested international interests to stating they fake numbers or set fire to the forest.

# 3 Operationalizing Amazonian narratives: data and methods

We start with a dataset of official presidential speeches since 1985 containing 6088 speeches. This body of speeches was scrapped from the official library of the Brazilian executive branch, and it includes a range of speeches from the UN general assembly to national congress, to business associations, to small events. The beginning date, 1985, reflects the date when democracy came back to Brazil, indirectly at first at the national level. With democracy back, political discourses are assumed to reflect a broad range of interests from voters to international pressure. We extract the location and date of each speech and code for stage (Amazonian states, non-Amazonian states, other, or international) to see if frequencies of narratives change depending on the audience and time. We then clean the text by removing some punctuation, accents, and making all the text lower case.

The broad dataset is then subset to contain only speeches that mention the word Amazon, or words that stem from the words (i.e. Amazonian). We assume that these speeches are, at least partially, about the Amazonon, the rain forest, and politics in the region. We find that 861 presidential speeches mention the word Amazon at least once. Subsequently we extract the sentences before and after the word Amazon is mentioned. This creates a contextualized statement that we consider an observation of an Amazonian narrative. It is at this level that we conduct our analysis in three steps. First, we start by providing some general descriptive statistics on the word Amazon in presidential discourse. Second, we then conduct a structural topic model (unsupervised machine learning) to inductively identify the most frequent combinations of words that appear in all Amazonian narratives. Here, words clustered are assumed to be a topic. Third, we deductively operationalize the four ideal-typical Amazonian narratives in dictionaries and provide its appearance and variation across time.

# 4 Preliminary Analysis

```{r setup I, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(stringi)
library(tm)
library(ggplot2)
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(RColorBrewer)
library(tidyr)

# Load data
#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path to load data after poldis

# Subset for text matches
#Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
# Remove accents and extra spaces
#Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
# Make all lower case
#Amazon_speeches$text <- tolower(Amazon_speeches$text)
# Remove extra white spaces
#Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
# Get only the pertinent text chunks
#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
# Transform into a single text per row...
#Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
#saveRDS(Amazon_speeches, file="amazon_speeches.rds")

```

```{r setup II, include=FALSE}
# Rename variables to adapt to text analysis packages' expectations
Amazon_speeches <- dplyr::rename(Amazon_speeches, fulltext = text, text = ccontext)

# Remove stop words and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores",
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul",
                                          "norte", "mato grosso","outro", "onde", "discurso", "parte", "anos", "cada", "todo", 
                                          "porto velho", "visite site", "site secretaria", "minas gerais", "lula silva", 
                                          "inácio lula", "amapa", "bahia", "é", "lá", "et", "in", "httpwww", "vez", "vezes", "entao", "coisa", "ainda", "sobre", "apenas", "coisa",
                                          "jose", "tudo", "toda"))

Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")

# Transform into corpus
Amazon_speeches <- Amazon_speeches %>%
  dplyr::mutate(doc_id = president) %>%
  arrange(doc_id, text)
amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))

```

```{r speech frequencies, echo=FALSE, message=FALSE, warning=FALSE}

freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
                        freq = as.numeric(summary(as.factor(Amazon_speeches$year))),
                        freqn = as.numeric(summary(as.factor(Amazon_speeches$year)))/
                          as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))

ggplot(freq_year, aes(year, freqn))+
    geom_line()+
    geom_point()+
    geom_smooth(method=lm, color="#bab86c") +
      labs(x = "",
       y = "Relative share of speeches per year",
       title = "Presidential speeches mentioning the Amazon (1985-2020)",
       caption = "Frequencies normalized by the number of speeches per year in dataset",
       color = "")

freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
ggplot(freq_year, aes(x = year)) +
    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
      labs(x = "",
       y = "Relative share of speeches per year",
       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
       subtitle = "Compared to annual deforestation rates since 1988",
       color = "")

```
From the first plot, the proportion of speeches that mention the word "Amazon" increase in frequency in 1989 (possibly related to Amazon Fires coverage from the New York Times see [here](https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html) and [here](https://www.nytimes.com/1989/03/23/world/brazil-smarting-from-the-outcry-over-the-amazon-charges-foreign-plot.html)), around 1992 (likely related to the Rio Conference), from 2005 to 2010 (possibly related to the "preservation" legislation turn under the Lula Administration), and after 2016 (possibly related to increasing deforestation rates and international attention). An interesting finding here is that while there is fluctuations along time, mentions to the Amazon did not increase or decrease, maintaining a general average of around 15% appearance in speeches. A second interesting finding is that mentions to the Amazon in presidential discourse do not correlate with deforestation rates. This might be due to different reasons: first, deforestation rate data is published once a year, so international response and presidential discourse are lagged. Relatedly, wider access to this data only started in the 2000s.A more interesting measure to use would be fire data or DETER data, which comes out monthly and might drive discourse. Second, deforestation data might correlate better with specific Amazonian narratives rather than mentions in general. We will test this idea in future versions.

```{r location, echo=FALSE, warning=FALSE, message=FALSE}
# Location was added with poldis::extraxt_location(), still needs to be improved...
# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
# Let's code the Amazonian states, the other Brazilian states, and speeches delivered outside Brazil.
Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
# Just a comparison with the proportion of speeches per stage on the broader dataset
stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
stage_rate
```

The summary table illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches. However, when it comes to international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches. We find this counter-intuitive, as many scholars tend to associate Brazil's prominent role in international environmental governance. At the moment, we still can not say for sure that this finding is robust. We operationalize international stage as anything that is not Brazil, so it includes speeches in African countries for instance. We will work towards a better measure that separates international stage from other countries and re-run this to see if it still holds.

```{r top words by speaker, echo=FALSE, warning=FALSE, message=FALSE}

# Get 30 most frequent words overall

amazon_TDM  <- TermDocumentMatrix(amazon_corpus)
amazon_TDMm <- as.matrix(amazon_TDM)

Sums_a <- rowSums(amazon_TDMm)
Freq_a <- data.frame(word=names(Sums_a),frequency=Sums_a)
topWords      <- subset(Freq_a, Freq_a$frequency >= 100) 
topWords      <- topWords[order(topWords$frequency, decreasing=F),]
topWords$word <- factor(topWords$word, 
                          levels=unique(as.character(topWords$word)))

ggplot(topWords, aes(x=word, y=frequency)) + 
  geom_bar(stat="identity", fill='#bab86c') + 
  coord_flip()+
  geom_text(aes(label=frequency), colour="white",hjust=1.25, size=3.0)+
  labs(title='Most Frequent Words in Amazonian Speeches', x="", y="")

# Let's see if bigrams help us more here
tamazon <- tidytext::tidy(amazon_corpus) %>%
  unnest_tokens(bigram, text , token = "ngrams", n = 2) %>%
  dplyr::count(bigram, sort = TRUE) %>%
  ungroup()
tamazon

# Let's get the 30 most frequent term by speaker
amazon_presid <- aggregate(Amazon_speeches$text, list(Amazon_speeches$president), paste, collapse = " ") %>%
  rename(doc_id = "Group.1", text = "x")
amazon_presid_t <- tm::VCorpus(DataframeSource(amazon_presid)) %>%
  tidy() %>% 
  unnest_tokens(word, text) %>%
  count(id, word, sort = TRUE)
Sarney <- head(dplyr::filter(amazon_presid_t, id == "Sarney"), 30) %>%
  mutate(Sarney = word) %>% select(Sarney)
Collor <- head(dplyr::filter(amazon_presid_t, id == "Collor"), 30) %>%
  mutate(Collor = word) %>% select(Collor)
Itamar <- head(dplyr::filter(amazon_presid_t, id == "Itamar"), 30) %>%
  mutate(Itamar = word) %>% select(Itamar)
FHC <- head(dplyr::filter(amazon_presid_t, id == "FHC"), 30) %>%  mutate(FHC = word) %>% select(FHC)
Lula <- head(dplyr::filter(amazon_presid_t, id == "Lula"), 30) %>%  mutate(Lula = word) %>% select(Lula)
Dilma <- head(dplyr::filter(amazon_presid_t, id == "Dilma"), 30) %>%  mutate(Dilma = word) %>% select(Dilma)
Temer <- head(dplyr::filter(amazon_presid_t, id == "Temer"), 30) %>%  mutate(Temer = word) %>% select(Temer)
Bolsonaro <- head(dplyr::filter(amazon_presid_t, id == "Bolsonaro"), 30) %>%
  mutate(Bolsonaro = word) %>% select(Bolsonaro)
f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro) %>% 
  kableExtra::kbl(caption = "Top 30 Words Per President") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
f_speaker
```

```{r lda, warning=FALSE, echo=FALSE, message=FALSE}
library(topicmodels)

# Fit a simple LDA model
# Please note that we randomly set a K = 10 (10 cluster = topics)
amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))

# Get the top 10 words per topic
amazon_lda10 <- tidy(amazon_lda, matrix = "beta") %>%
  arrange(desc(beta)) %>%
  group_by(topic) %>%
  filter(row_number() %in% 1:10) %>%
  arrange(topic)
topten_topic <- aggregate(amazon_lda10$term, list(amazon_lda10$topic), paste, collapse=", ") %>%
  rename(Topic = "Group.1", Terms = "x") %>% 
  kableExtra::kbl(caption = "Top 10 Words per Topic for Presidential Speeches Mentioning the Amazon") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
topten_topic

# Let's get the gamma (percent of topic in document for speakers)
amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
  arrange(desc(gamma)) %>%
  group_by(document) %>%
  filter(row_number() %in% 1:2) %>% # get the top 2 topics per speaker
  arrange(document) %>%
  mutate(gamma = round(gamma, 3)) %>%
  distinct() %>% 
  rename (president = document) %>% 
  kableExtra::kbl(caption = "Top 2 Topics Per Speaker") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
```

```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}

# Create the dictionary

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto|madeireira|produzir")
conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteger")
anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas|ong|xiita") # This appears harder to operationalize than others...

```

```{r narratives, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}

# Create a variable for each and count matches
Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
Amazon_speeches$anti_environmentalism <- stringr::str_count(Amazon_speeches$text,
                                                            paste0("(?i)", anti_environmentalism))
Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
                                  Amazon_speeches$conservation == 0 & 
                                  Amazon_speeches$anti_environmentalism == 0, 1, 0)

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    facet_wrap(~narrative)+
    theme (legend.position="none")

# Same frequency table but normalized by the numbers of speeches in broader dataset
pres_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
  group_by(president) %>%
  summarise(across(everything(), sum))

pres_narratives_n <- pres_narratives %>%
  mutate(n_speeches = summary(as.factor(BR_Presidential_Speeches$president))) %>%
  mutate(across(c(2:6), .fns = ~./n_speeches)) %>%
  select(-n_speeches) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(pres_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")

# Table by stage, normalized
stage_narratives <- Amazon_speeches %>%
  mutate(stage = Amazon_lc$stage) %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location, president)) %>%
  group_by(stage) %>%
  summarise(across(everything(), sum))

stage_narratives_n <- stage_narratives %>%
  mutate(n_stages = summary(as.factor(Amazon_lc$stage))) %>%
  mutate(across(c(2:6), .fns = ~./n_stages)) %>%
  select(-n_stages) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(stage_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
```

# 5 Bibliography

Acker, Antoine (2013). “O maior incêndio do planeta”: como a Volkswagen e o regime militar brasileiro acidentalmente ajudaram a transformar a  Amazônia em uma arena política global.               Revista Brasileira de História, 34(68),13-33.[fecha de Consulta 5 de Noviembre de 2021]. ISSN: 0102-0188. Disponible en:   https://www.redalyc.org/articulo.oa?id=26335781002

Arima, Eugenio Y., Paulo Barreto, Elis Araújo, and Britaldo Soares-Filho. 2014. “Public Policies Can Reduce Tropical Deforestation: Lessons and Challenges from Brazil.” Land Use Policy 41         (November): 465–73. https://doi.org/10.1016/j.landusepol.2014.06.026.

Assunção, Juliano, Clarissa Gandour, and Rudi Rocha. 2015. “Deforestation Slowdown in the Brazilian Amazon: Prices or Policies?” Environment and Development Economics 20 (6): 697–722.            https://doi.org/10.1017/S1355770X15000078.

Barros, A. T. (2020). Discursos parlamentares sobre a amazônia: Sobre o que falam os deputados brasileiros. Política & Sociedade, 19(46), 299-331.                                                  doi:http://dx.doi.org/10.5007/2175-7984.2020.e66962

Boucher, Doug, Sarah Roquemore, and Estrellita Fitzhugh. 2013. “Brazil’s Success in Reducing Deforestation.” Tropical Conservation Science 6 (3): 426–45.                                           https://doi.org/10.1177/194008291300600308.

Brice, Jessica, and Michael Smith. 2021. “The Amazon Is Fast Approaching a Point of No Return.” Bloomberg.Com, July 29, 2021.                                                                       https://www.bloomberg.com/news/features/2021-07-29/amazon-rainforest-deforestation-land-grabs-surge-under-bolsonaro-in-brazil.

Drummond, J., & Barros-Platiau, A. F. (2006). Brazilian Environmental Laws and Policies, 1934–
        2002: A Critical Overview. Law & Policy, 28(1), 83–108. https://doi.org/10.1111/j.1467-
        9930.2005.00218.x

Harris, Bryan. 2021. “Drought Puts Amazon at Risk of ‘Large-Scale Dieback’, Researchers Warn.” Financial Times, July 19, 2021.                                                                     https://www.ft.com/content/02071ae7-dcf5-4c61-9c3c-b55f5aef8b0e.

Hecht, Susanna, and Raoni Rajão. 2020. “From ‘Green Hell’ to ‘Amazonia Legal’: Land Use Models and the Re-Imagination of the Rainforest as a New Development Frontier.” Land Use Policy 96         (July): 103871. https://doi.org/10.1016/j.landusepol.2019.02.030.

Hochstetler, Kathryn, and Eduardo Viola. 2012. “Brazil and the Politics of Climate Change: Beyond the Global Commons.” Environmental Politics 21 (5): 753–71.                                    https://doi.org/10.1080/09644016.2012.698884.

Franchini, M. A., Viola, E., Franchini, M. A., & Viola, E. (2019). Myths and images in global	climate	governance, conceptualization and the case of Brazil (1989—2019). Revista	Brasileira        de	Política Internacional, 62(2). https://doi.org/10.1590/0034	7329201900205

Garfield, S. (2013). In Search of the Amazon: Brazil, the United States, and the Nature of a Region.

Lahsen, Myanna. 2009. “A Science–Policy Interface in the Global South: The Politics of Carbon Sinks and Science in Brazil.” Climatic Change 97 (3–4): 339–72.                                    https://doi.org/10.1007/s10584-009-9610-6.

de Waroux, Y., Garrett, R. D., Chapman, M., Friis, C., Hoelle, J., Hodel, L., Hopping, K., & Zaehringer, J. G. (2021). The role of culture in land system science. Journal of Land Use            Science, 0(0), 1–17. https://doi.org/10.1080/1747423X.2021.1950229

Miranda, David. 2021. “Bolsonaro’s 1,000km Amazon Railway Will Cause Climate Chaos. It Must Be Stopped | David Miranda.” The Guardian, June 2021.                                                    http://www.theguardian.com/commentisfree/2021/jul/28/bolsonaro-amazon-railway-climate-chaos-must-be-stopped.

Nepstad, Daniel, Britaldo S. Soares-Filho, Frank Merry, André Lima, Paulo Moutinho, John Carter, Maria Bowman, et al. 2009. “The End of Deforestation in the Brazilian Amazon.” Science 326         (5958): 1350–51. https://doi.org/10.1126/science.1182108./

### 2021-11-08 08112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#added text to plots #formatted markdown so HTML or pdf look a bit nicer

@@
 # Please note that we randomly set a K = 10 (10 cluster = topics)
+
+amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
+amazon_dtmm <- as.matrix(amazon_dtm)
 amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))

### 2021-11-08 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#final formatting details # few more stop words

--- 2021-11-08 08112021_Sposito_and_SilvaMuller_DRAFT.Rmd
@@
 title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
-author: "Sposito & Silva-Muller"
+author:
+- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
 date: "11th of November of 2021"
@@
   pdf_document: default
+  word_document: default
   html_document:
@@
 
-# 4 Preliminary Analysis
+# 4 Exploratory analysis
+
+In the following, we will show our work in progress in terms of the empirical analysis.
+At the moment, we are trying to figure out what methods we will actually use and why.
+The number of speeches mentioning the Amazon (n=861), is not high enough to justify certain machine learning approaches as manually coding a fraction.
+We tested more inductive approaches (topic modelling), and it seems to work well, but at the same time the text volume is too small to justify.
+As there are other factors we are interested at (e.g.
+a measure of intensity, how (a)permissive and  (b)explicit is the discourse), we think a combination of manual coding and more quantitative approach might help.
 
@@
 library(tidyr)
+library(formatR)
 
@@
 
-```{r speech frequencies, echo=FALSE, message=FALSE, warning=FALSE}
+```{r speech frequencies I, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
        color = "")
+```
+
+```{r speech frequencies II, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
        subtitle = "Compared to annual deforestation rates since 1988",
-       color = "")
+       color = "")+
+       theme(legend.position ="bottom")
 
 ```
+
 From the first plot, the proportion of speeches that mention the word "Amazon" increase in frequency in 1989 (possibly related to Amazon Fires coverage from the New York Times see [here](https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html) and [here](https://www.nytimes.com/1989/03/23/world/brazil-smarting-from-the-outcry-over-the-amazon-charges-foreign-plot.html)), around 1992 (likely related to the Rio Conference), from 2005 to 2010 (possibly related to the "preservation" legislation turn under the Lula Administration), and after 2016 (possibly related to increasing deforestation rates and international attention).
@@
 
-```{r top words by speaker, echo=FALSE, warning=FALSE, message=FALSE}
+```{r top words by speaker I, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6}
 
@@
 tamazon
+```
+
+In terms of most frequent words, we already observe mentions related to the narratives we expect (develop, integrate, produce, deforestation).
+Pairs of words (bigrams) also point towards the same (meio ambiente, forcas armadas, zona franca, desenvolvimento sustentavel).
+
+```{r top words by speaker II, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
   kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-f_speaker
+
+landscape(f_speaker, margin=NULL)
 ```
+
+Moving to most mentioned words by presidents, there are some interesting anectodal findings.
+For instance, deforestation appears to be more salient in the vocabulary employed by Lula, Dilma and Temer versus their counterparts.
+The words "soberania" and "military" only appears as part of Bolsonaro's vocabulary.Desenvolvimento, on the other hand, seems to be part of all presidents vocabulary except of Temer.
 
@@
 
+The tabel 2 (above) and table 3(below) portray the result of a structural topic model.
+We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
+We set the number of clusters to be found (topics) at 10, randomly.
+We, then, select the top ten words coded for each topic.
+
+Development appears in 6 out of 10 topics, suggesting it is a cross-cutting vocabulary.
+In its purest form, we observe the developmentalist narrative in topic 1 and 3.
+Three topics relate to themes of security, development, and integration (4,7,8) and one other touches on sovereignty in its purest form (9), which combined understand as the sovereignty narrative.
+Two topics portray vocabulary that we understand as constituting the conservation narrative (2 and 10), with topic 10 being the purest form in the text.
+
+Once the clusters are extracted, we can indicate, probabilistically, how presidents' discourse fall within a topic, that's what the second table does for the 2 most salient topics per speakier.We see that, for example, Lula's discourses about the Amazon often is clustered with themes of development and of deforestation.
+At the same time, Bolsonaro's discourses about the Amazon often is clustered with themes of integration, energy, and the military forces.
+Sarney engaged with themes of preservation, while Cardoso engages with themes related to energy and integration.
+Others as Rousseff and Temer appear to engage with themes of geography, politics, energy; while Collor an Itamar appear to engage with themes of security, development, and integration.
+
 ```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}
@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
-development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integrar|integracao|zona franca|transamazonica|madeira|porto|madeireira|produzir")
-conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteger")
-anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|agricultura|producao de gado|ambientalistas|ong|xiita") # This appears harder to operationalize than others...
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|
+                ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|
+                dono|nossa")
+
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|
+                incentivos fiscais| integrar|integracao|zona franca|transamazonica|madeira|
+                porto|madeireira|produz|energia")
+
+conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|
+                 areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|
+                 protecao|proteg")
+
+anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|
+                          agricultura|producao de gado|ambientalistas|ong|xiita")
 
 ```
+
+Shifting our methodological strategy from an inductive approach to a more deductive and theoretically driven analysis of the text, leads similar results.We operationalize our narratives by deductively creating four groups of words (dictionaries) and assigning each contextualized mention to the Amazon to a narrative.
+The dictionaries are presented in the code chunk above.
+Our narratives approach, while still empirically weak, already shows some interesting trends (table 4, table 5, and narratives plots; below).
+First, the 1988 NYC pictures of the Amazon burning piked all narratives during the Sarney presidency.
+Second, while Lula was the president that most performed conservation narratives until 2010, Bolsonaro mobilized sovereignty narratives strongly.
+Third, generally the developmentalist narrative have decreased along time but has appeared most frequently during the Lula mandate, suggesting sustainable development was at its highest in those years.
+Fourth, while the anti socio-environmentalist narrative was generally not so frequent (this might be an identification problem or that it is simply a sub-type of the developmentalist narrative), it was present across all speakers with Bolsonaro using it the most.
 
@@
        title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
+    geom_smooth(method=lm, se=FALSE, color="black", linetype="dashed",size=0.5)+
     facet_wrap(~narrative)+
@@
 Lahsen, Myanna.
-2009.
+(2009).
 “A Science–Policy Interface in the Global South: The Politics of Carbon Sinks and Science in Brazil.” Climatic Change 97 (3–4): 339–72.
@@
 https://doi.org/10.1126/science.1182108./
+
+Silva-Muller, L., & Faul, M.
+(2021) “Protecting the Amazon and its people: the role of civil society in the local effectiveness of transnational partnerships”.
+In Partnerships for                        Sustainability: Pathways to Effectiveness.
+Edt.
+by Andonova, L., Faul, M.
+and Piselli, D.
+Routledge: London.
+
+Silva-Muller, L.
+(forthcoming) "Payment for ecosystem services and the practices of environmental fieldworkers in policy-implementation: the case of Bolsa Floresta in the Brazilian                        Amazon"

### 2021-11-09 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#color-blind friendly palette

@@
 - Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
-date: "11th of November of 2021"
+date: "11/11/2021"
 output:
-  pdf_document: default
-  word_document: default
   html_document:
     df_print: paged
+  pdf_document: default
 ---
@@
 However, the authors rely on a few disconnect quotes from Bolsonaro about the Amazon to exemplify phases defined by policy discontinuities.
-How, then, have Amazonian presidential discourses changed in time?
+*How, then, have Amazonian presidential discourses changed in time?*
 
@@
 
-Amazonian narratives constitute discourses that connect the region to specific imaginaries of the future and past.
+*Amazonian narratives constitute discourses that connect the region to specific imaginaries of the future and past*.
 We argue that they touch on shared meanings about the Amazon that are available to the speaker as part of the larger social history of the region and country.
@@
 This narrative employs imaginaries of underdevelopment and economic needs in the Amazon while, at the same time, focus on the unexplored economic potential of the region and forest.
-
+\newpage
 *Conservationism*
@@
 
-# 4 Exploratory analysis
+# 4 Exploratory analysis: Amazonian narratives along time
 
@@
                                           "inácio lula", "amapa", "bahia", "é", "lá", "et", "in", "httpwww", "vez", "vezes", "entao", "coisa", "ainda", "sobre", "apenas", "coisa",
-                                          "jose", "tudo", "toda"))
+                                          "jose", "tudo", "toda", "mil", "sempre", "assim", "estados", "forma", "pais", "programa", "primeiro"))
 
@@
                          All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
-stage_rate
+knitr::kable(stage_rate, caption= "Speeches by stage")
 ```
@@
   ungroup()
-tamazon
+
 ```
@@
 landscape(f_speaker, margin=NULL)
+
 ```
@@
 
-The tabel 2 (above) and table 3(below) portray the result of a structural topic model.
+  The table 2 (above) and table 4(below) portray the result of a structural topic model.
 We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
@@
 Others as Rousseff and Temer appear to engage with themes of geography, politics, energy; while Collor an Itamar appear to engage with themes of security, development, and integration.
+\newpage
 
@@
 
-```{r narratives, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
+```{r narratives I, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
     theme (legend.position="none")
+
+```
+
+```{r narratives II, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
 

### 2022-01-27 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#olduncommittedchanges

@@
 output:
+  pdf_document: default
   html_document:
     df_print: paged
-  pdf_document: default
 ---
@@
 
+cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
@@
        color = "")+
-       theme(legend.position ="bottom")
+       theme(legend.position ="bottom")+
+        scale_colour_manual(values=cbbPalette)
 
@@
 
-  The summary table illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches.
+ Table 1 illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches.
 However, when it comes to international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.
@@
   ungroup()
+tamazon
 
@@
 
-  The table 2 (above) and table 4(below) portray the result of a structural topic model.
+  The table 3 (above) and table 4(below) portray the result of a structural topic model.
 We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
@@
 # Visualize correlations
+
+cbPalette <- c("#999999", "#56B4E9", "#0072B2", "#009E73", "#F0E442", "#D55E00", "#CC79A7", "#E69F00")
+
 am_narratives <- Amazon_speeches %>%
@@
        y = "",
-       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
+       title = "Narratives in Presidential Speeches per year since 1985 in Brazil (wrapped)")+
     geom_smooth(method=lm, se=FALSE, color="black", linetype="dashed",size=0.5)+
     facet_wrap(~narrative)+
-    theme (legend.position="none")
+    theme (legend.position="none")+
+    scale_colour_manual(values=cbPalette)
+
+ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
+  geom_line(aes(group = narrative, color = narrative), size = 1) +
+  labs(x = "Year",
+       y = "",
+       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
+    theme (legend.position="bottom")+
+    scale_colour_manual(values=cbPalette)
 

### 2022-02-07 draft November 2021/11112021_Sposito_and_SilvaMuller_DRAFT.Rmd

--- 2022-01-27 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
@@
 output:
-  pdf_document: default
   html_document:
     df_print: paged
+  pdf_document: default
 ---
@@
     geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
+    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
+      labs(x = "",
+       y = "Relative share of speeches per year",
+       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
+       subtitle = "Compared to annual deforestation rates since 1988",
+       color = "")+
+       theme(legend.position ="bottom")+
+        scale_colour_manual(values=cbbPalette)
+
+ggplot(freq_year, aes(x = year)) +
     geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +

### 2022-02-07 others/data_exploration_1_full text.Rmd

--- 2021-10-21 data_exploration.Rmd
@@
 ---
-title: "Amazon in Presidential Speeches in Brazil (Inductive Analysis)"
-author: "Henrique Sposito"
+title: "Amazon in Presidential Speeches in Brazil: data exploration for full texts"
+author: "Henrique Sposito and Livio Silva-Muller"
 date: "10/15/2021"
@@
 BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
-# BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text, level = "sentences")
-# This takes a while to run, but we get context for all matches in dataset as a variable in dataset!
 Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches,
@@
 # library(poldis)
+
 # Load internal sentiment dictionaries from poldis
@@
 ```
+
+This is where I stop since, overall, this appears not to be very helpful ...
+But how about we try the a similar script with only the matches themselves instead of full texts?

### 2022-02-07 others/data_exploration_2_context.Rmd

--- 2021-11-04 data_exploration_2_context.Rmd
@@
 ```{r narratives, warning=FALSE, message=FALSE}
+library(tidyr)
+
 # Create the dictionary

### 2022-02-07 others/get_locations.R
Re-worked location variable in datasets and added get location script to facilitate with transparency

@@ -1,0 +1,41 @@
+# Get location from title and text
+BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+
+# Replace on title and text
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, " - | -| -", "-")
+
+# Replace "para" to avoid confusion with state name in Brazil
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,"^para$", "pra")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, "^para$", "pra")
+
+# Make it lower case, remove extra space, and add coma space
+BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
+
+# Make it latin SCII
+BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
+BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Speeches$title, id = "latin-ascii")
+
+# get locations from title
+BR_Presidential_Speeches$location <- poldis::extract_location(BR_Presidential_Speeches$title)
+summary(as.factor(BR_Presidential_Speeches$location))
+
+# get location from text if not found
+BR_Presidential_Speeches$location <- ifelse(grepl("^NA$", BR_Presidential_Speeches$location),
+                                            poldis::extract_location(BR_Presidential_Speeches$text),
+                                            BR_Presidential_Speeches$location)
+BR_Presidential_Speeches$location <- ifelse(grepl("", BR_Presidential_Speeches$location),
[…]

### 2022-02-07 others/get_locations.R
minor updates to get location

@@ -29,9 +29,7 @@ summary(as.factor(BR_Presidential_Speeches$location))
 BR_Presidential_Speeches$location <- ifelse(grepl("^NA$", BR_Presidential_Speeches$location),
                                             poldis::extract_location(BR_Presidential_Speeches$text),
                                             BR_Presidential_Speeches$location)
-BR_Presidential_Speeches$location <- ifelse(grepl("", BR_Presidential_Speeches$location),
-                                            poldis::extract_location(BR_Presidential_Speeches$text),
-                                            BR_Presidential_Speeches$location)
+summary(as.factor(BR_Presidential_Speeches$location))
 
 # get context and update amazon specific data
 Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text))
@@ -39,3 +37,4 @@ Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text,
 Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
 
 # Save Rds
+saveRDS(Amazon_speeches, "amazon_speeches.Rds")

### 2022-02-10 20220210_Draft.Rmd
#newrmdfornewdraft #todo/questionlist

--- 2021-11-09 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
@@
 ---
-title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
+title: "How is the Brazilian Amazon constructed as a problem at different levels? Amazonian
+  Narratives in Presidential Speeches since 1985"
 author:
@@
   pdf_document: default
+bibliography: [export-data.bib]
+csl: [apa.csl]
+
 ---
 
-# 1 Introduction
+# questions/to do
 
-> “The world should understand that the Brazilian Amazon has an owner: the Brazilian people.” (Lula, May 2008)^[Taken from here: https://www.reuters.com/article/brasil-politica-lula-amazonia-pol-idBRN2634078320080526]
+- Amazon context data up to date?
+- Can we copy location stuff from previous set?
+- Start improving dictionary: prepare sheet with large random sample of classified amazonian context for inductive analysis (speaker, year, context, classification)
 
-> “Do you know what ‘Triple A’ is?
-It is the Amazon, Andes and Atlantic.
-These represent 136 million hectares, and the first world wants to administer these areas.” (Bolsonaro, July 2019)^[Taken from here: https://g1.globo.com/politica/noticia/2018/11/28/bolsonaro-diz-que-pediu-cancelamento-da-conferencia-do-clima-no-brasil-em-2019.ghtml]
-
-Preserving the Amazon has rarely been the top priority of Brazilian federal governments.
-Though deforestation rates began to steadily increase in 2012 (see Carvalho et al.
-2019), after a decade of decline, they spiked in 2019 after Bolsonaro took power (INPE 2021).
-This is no surprise as the current federal government is weakening the foundations of the Brazilian environmental governance system through budgetary cuts, presidential appointments, and dissociating government from civil society (see Ferrante and Fearnside 2019).
-These factors contributed to record-high fires in the Amazon and unprecedented monthly rates of deforestation during the dry seasons of 2019, 2020, and 2021 (INPE 2021).
-Although policy discontinuities between Bolsonaro's Amazon agenda and previous governments have been documented by academic scholarship and specialized media (see Abessa, Famá, and Buruaem 2019; Spring 2021), we lack empirical accounts of how Amazonian discourses changed.
-Pokorny et.
-al (2021, p.
-2208), for example, argue that Bolsonaro’s Amazonian discourses shifted drastically in relation to earlier governments, giving rise to a “populist neoliberal” phase of discourse and policy developments in the region.
-However, the authors rely on a few disconnect quotes from Bolsonaro about the Amazon to exemplify phases defined by policy discontinuities.
-*How, then, have Amazonian presidential discourses changed in time?*
-
-  Amazonian related political discourses at the top can help expand, or restrict, what types of behavior are expected and accepted in society in respect to the region.
-This is especially pertinent for deforestation as previous research found that expectations about government response, generated from material and discursive changes, are a crucial factor in decisions to deforest at the local level (Campbell 2015).
-When, for example, Bolsonaro says he will end the “industry of fines” in reference to institutions that police environmental crimes, the loud and clear message is that oversight will decrease (see Ferrante and Fearnside 2019).
-To study change and continuity in presidential discourses about the Amazon we build upon the environmental historiography literature which have documented cultural imaginaries of, and from, the region thoroughly, mobilized by presidents in discourse via political narratives.In so doing, we understand Amazonian narratives^[We utilize discourse and speech interchangeably, to denote general spoken communication by presidents.
-Narratives, on the other hand, constitute discourse.] as originating in specific historical periods, connecting the discourse to the broader social history of the region and country.
-
-  We propose four ideal type Amazon related narratives in political discourses: sovereignty, developmentalism, conservationism, and anti-environmentalism.
-Sovereignty narratives touch on imaginaries of threat that hail from the time of the scramble for the Amazon (see Hecht and Cockburn 1990) to contextualize or justify proposed political actions of control, occupation, and monitoring of the region.
-Developmentalist narratives employ imaginaries of underdevelopment and economic needs in the region, advancing political actions related to exploring economically of the region and the forest (see Acker 2013).
-Conservatism narratives deploy imaginaries related to the value of the standing Amazonian ecosystem to justify political actions related to preserving the forest and idigenous peoples’ rights (see Hochstetler and Keck 2007).
-Anti-environmentalism builds upon imaginaries related to issues with socio-environmentalism and excess preservation for even development to justify political actions related to deregulation.
-
-  To analyze Amazonian narratives across time and space, we use a dataset of presidential discourse ranging from 1985 to 2020 with 6088 speeches and a combination of natural language processing and qualitative coding.
-We subset the text dataset to select texts which contain words related to Amazon.
-We, then, build a dictionary of terms to operationalize Amazonian narratives and trace their evolution and change across presidential mandates and stages (local, national, or international).
-By tying Amazonian narratives in presidential discourse to environmental historiography, we provide the first historically and empirically informed account of how, when, and where Amazonian narratives are mobilized at the top.
-
-  This paper proceeds as follows: we start with a brief review of the social sciences literature on the Brazilian Amazon.
-We then move to our conceptual framework, which ties environmental historiography to our understanding of narratives.
-We provide a targeted overview of recent Amazonian historiography, which serves the purpose of identifying and grounding ideal-typical narratives.
-Third, we discuss the data, methods, and the operationalization of these narratives.
-We then present our preliminary results by contextualizing them into the last decades of environmental governance in Brazil.
-We conclude by providing avenues for future research connecting political discourses and environmental related outcomes.
-
-# 2 Grounding Amazonian narratives in the literature
-## 2.1 The Brazilian Amazon in social sciences: where is culture and discourse?
-
-We contend that presidential discourse at the top matters because it expands or restricts the range of possibilities for other actors.
-When presidents speak about the Amazon, it makes international headlines (Brice and Smith 2021; Harris 2021; Miranda 2021), inciting international responses, and feeds into the behavior of domestic actors, from investors to agricultural giants to local farmers, who take what presidents say into consideration.
-When presidents mobilize Amazonian narratives that connect the region to specific imaginaries of the future and past, they are touching upon shared webs of meaning about the region.
-So, before dissecting Amazonian narratives, we will dwell into the arena of Amazonian related culture.
-But how to situate political discourse and culture in social sciences literature about the Brazilian Amazon?
-In the following, we provide a synthetic review of the literature to argue that while ethnographers have been particularly successful exploring the role of culture in the Brazilian Amazon, we lack accounts that situate it at the level of discourse generally.
-
-  A substantial number of studies about the Amazon try to identify causes of and remedies to deforestation.
-This literature is interdisciplinary, ranging from ecology, to economics, to political sciences.
-It assesses the effectiveness of policies their relative contribution, or how they affect decision making of actors from rather rational perspectives at various levels (Arima et al.
-2014; Assunção, Gandour, and Rocha 2015; Boucher, Roquemore, and Fitzhugh 2013; Nepstad et al.
-2009).
-As it is particularly hard to econometrically tie discourse to deforestation outcomes, there are no studies that look at the effects of political discourses on deforestation systematically.
-There has been a recent call, though, to better account for the role of culture in the development of land systems’ use alongside demographic, economic, technological, and governance factors (de Waroux et al., 2021).
-Bringing culture in might help formalize findings from single case studies, hailing from ethnographies, that explain decisions to deforest, or not, based on individual and collective values rather than utility.
-de Waroux et al.
-(2021) propose to approach culture as a shared symbolic system or ‘webs of meaning’ that play a role in cognition and other structural drivers of land-use behavior.
-
-  Another line of inquiry is interested in explaining who influences Brazilian environmental policy and how.
-Researchers in this line of inquiry seek to understand interest formation, resembling international political economy approaches.
-This line of research has identified the role transnational connections (Keck and Sikkink, 1998; Hochstetler and Keck, 2007; Silva-Muller & Faul, 2021), domestic actors’ interests (Franchini and Viola, 2019), and bureaucrats (Abers 2019; Silva-Muller, forthcoming).
-Some authors attempt to bring cultural dimensions to these studies through ethnographic work.
-Rajão and Vurdubakis (2013), for example, conduct longitudinal participant observation with the environmental police (IBAMA) to argue that the process of rendering deforestation a stable object of knowledge, that can be objectively identified and sanctioned, is deeply social and full of antagonisms.
-Lahsen (2004; 2009) discusses how Brazil could become a net receiver of international funds for climate mitigation, though Brazilian policymakers often ignore the scientific evidence and  push against such funding because of a national political culture of sovereignty protection inherited from the military dictatorship.
-Campbell (2015) proposes the concept of speculative accumulation to capture the practices of land-grabbers in the deforestation arch who make property appear and disappear based on their expectations of the future and attempts to rewrite the past through material practices (e.g.
-grillagem).
-
-  Nevertheless, there are very few studies looking into political discourses to explain who influence environmental police outcomes.
-Barros (2020), for instance, analyzes Amazonian discourse in the Brazilian Congress with the objective of identifying the main arguments put forth by congressmen.
-The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-However, political discourses in the congress are less visible to the broader population than other types of political discourses at the top, such as presidential discourses.
-At the same time, congressional discourses have specific purposes of discussing, or proposing, legislation in a technical manner.
-
-  Except for ethnographers, who advanced multiple versions of why and how culture matters for deforestation in the Amazon and environmental policy outcomes in Brazil, we lack accounts of the importance of culture more generally.
-This is key as the expectations about the future regarding government’s response are a key variable in the decision to deforest or not (Campbell, 2015).
-Such expectations are informed by shared meanings and values (de Waroux et.
-al., 2021), which travel through various means including discourse at the top.
-Building on these studies and on cultural sociology, we propose to situate culture at the level of discursive practices and understand what narratives are mobilized, when and where.
-
-## 2.2 Performing Amazonian narratives: environmental historigraphy and ideal types
-
-*Amazonian narratives constitute discourses that connect the region to specific imaginaries of the future and past*.
-We argue that they touch on shared meanings about the Amazon that are available to the speaker as part of the larger social history of the region and country.
-To identify a few possible narratives, we utilize environmental historiography about the Amazon.
-We build Amazonian narratives as ideal types, that is, unified analytical constructs portraying a ‘pure’ version of a phenomenon (Weber 1949).
-In that sense, they rarely exist in its purest form.
-It serves the purpose of allocating empirical observations within a range of possibilities.
-The ideal types also help us deal with statements that perform different narratives.
-We broadly understand political discourses as performances seeking to appeal to diverse audiences across multiple political stages to project a definition of the situation (Goffman 1956, p.
-3).
-As political stages, audiences, and time change, so do narratives.
-As with broader political discourses, narratives can appear together, not necessarily in consistent ways in time or across stages.
-As we show in section 3, our methodological strategy utilizing allows us to allocate statements within one or more ideal types, providing a more sophisticated portrayal of political discourse.
-
-  When speaking, depending on the stage, presidents have varying levels of scripted discourse.
-In a message to congress, for example, discourse might be carefully crafted by a handful of specialists.
-However, in inaugural speeches for a bridge in a small town in Brazil presidents might have more room to deliver a speech more freely.
-In the first case, alluding to specific Amazonian narratives might be a conscious decision.
-In the second case, an allusion might be more spontaneous as narratives are available as part of the larger repertoire.
-We adopt the idea of performing Amazonian narratives to capture this variety.
-In opposition to rational choice models that see speech as a function of calculated decision, performances involve both improvisation and preparation, which in turn are constrained by the set of available possibilities.
-We see performance as a less strict way of approaching the issue at hand.
-So, what Amazonian narratives can presidents perform?
-
-*Sovereignty*
-
-  In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, a social history of the Brazilian Amazon dating 1990, Susanna Hecht and Alexander Cockburn write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites” (1991, p.1).
-It started with the first natural history of the New World, by Oviedo in 1535, who while naming mysterious plants and creatures, recounts the stories of conquest of local populations and gold hoarders (ibid).
-The dream of fortunes to be found in the Eldorado composed the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as “a […] form of nation building […]” (Hecht and Cockburn 1991, preface).
-The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru (Hecht, 2013, p.
-8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn, 1991).
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat.
-
-  We understand claims of sovereignty as a particular narrative that touches on imaginaries of threat that hail from the time of the scramble for the Amazon.
-The sovereignty narrative advances the view that the Brazilian Amazon is Brazilian and foreign presence in the region needs to be monitored closely.
-
-*Developmentalism*
-
-  The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon.
-This was mostly done in a particularly “high-modernist” (Scott, 1998) with military bureaucrats designing centralized policies aiming at conquering nature and developing the region.
-In 1966, for example, the Brazilian Military government launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2013).
-First, nature should be conquered by men.
-Second, exploiting natural resources would render the Amazon region a global powerhouse.
-Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2013), leading to a series of national and international enterprises settling in the Amazon region.
-
-  The developmentalist narrative advances the view that the Brazilian Amazon needs to be developed and modernized.
-This includes expanding the agricultural frontier through incentives, creating infrastructure as roads and dams, and fostering industries through tax-free zones.
-It has its origins in the policies of the 1930s that attempted to modernize the recently consolidated region (Hecht and Cockburn, 1990), but were extended throughout the 20th century.
-It also captures arguments of the 20th century that defended the integration of indigenous populations into the nation via assimilation and inclusion in economic life.
-This narrative employs imaginaries of underdevelopment and economic needs in the Amazon while, at the same time, focus on the unexplored economic potential of the region and forest.
-\newpage
-*Conservationism*
-
-  The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) (Drummond and Barros-Platiau 2006).
-This is mostly because “the generals had unleashed forces beyond their control, and now the Amazon faced its apocalypse” (Hecht and Cockburn, 1990, p.
-141).
-As deforestation, fires, and violence rose in the region and caught international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
-Concurrently, a new form of environmentalism in civil society consolidated in the 1990s: socio-environmentalism.
-Hochstetler and Keck define it as an emphasis on local livelihoods of people while protecting nature, which has its roots in the wider process of democratization of Brazil, the local advocacy and assassination of Chico Mendes, and the multi-level preparation for the 1992 Earth Summit in Rio de Janeiro (2007).
-The latter made many international NGOs establish their offices and presence in Brazil (e.g.
-WWF, GreenPeace, Friends of the Earth, Conservation International).
-International foundations started to increase their operations in the country and channel funds to NGOs and governmental institutions working in the Brazilian Amazon.
-The development of this new governance ecosystem led to increased professionalization of local NGOs which, in turn, resulted in a more systematic participation of civil society in public policy surrounding the Brazilian Amazon (Hochstetler and Keck 2007).
-
-  The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination (see Hochstetler and Keck 2007).
-This narrative focuses on imaginaries related to the values of a standing forest and of preserving the ecosystem of natures and peoples in the region.
-
-*Anti socio-environmentalism*
-
-  In the early 2000s, many of the ideas developed by socio-environmentalism became public policy, leading to a sharp decrease in deforestation in the Amazon from 2004 to 2012 (Arima et al.
-2014; Assunção, Gandour, and Rocha 2015; Boucher, Roquemore, and Fitzhugh 2013; Nepstad et al.
-2009).
-Brazil boasted of an image of strong deliverer, with not only the allegedly best legislation in place but also concrete implementation results (Franchini & Viola, 2019).
-As deforestation rates started to increase in 2012, and more rapidly during Bolsonaro’s administration in 2019, socio-environmentalism fell under attack.
-Previous governments and NGOs were accused of preserving too much and having veiled financial and political interests.
-
-  The anti socio-environmentalist narrative advances views that socio-environmentalism is a problem.
-It highlights the economic benefits related to exploration, while emphasizing as well as the costs of preservation.
-It differs from the developmentalist narrative, as it attacks NGOs and local populations for the excesses of preservation.
-These attacks diverge in nature, from claiming NGOs have vested international interests to stating they fake numbers or set fire to the forest.
-
-# 3 Operationalizing Amazonian narratives: data and methods
-
-We start with a dataset of official presidential speeches since 1985 containing 6088 speeches.
-This body of speeches was scrapped from the official library of the Brazilian executive branch, and it includes a range of speeches from the UN general assembly to national congress, to business associations, to small events.
-The beginning date, 1985, reflects the date when democracy came back to Brazil, indirectly at first at the national level.
-With democracy back, political discourses are assumed to reflect a broad range of interests from voters to international pressure.
-We extract the location and date of each speech and code for stage (Amazonian states, non-Amazonian states, other, or international) to see if frequencies of narratives change depending on the audience and time.
-We then clean the text by removing some punctuation, accents, and making all the text lower case.
-
-The broad dataset is then subset to contain only speeches that mention the word Amazon, or words that stem from the words (i.e.
-Amazonian).
-We assume that these speeches are, at least partially, about the Amazonon, the rain forest, and politics in the region.
-We find that 861 presidential speeches mention the word Amazon at least once.
-Subsequently we extract the sentences before and after the word Amazon is mentioned.
-This creates a contextualized statement that we consider an observation of an Amazonian narrative.
-It is at this level that we conduct our analysis in three steps.
-First, we start by providing some general descriptive statistics on the word Amazon in presidential discourse.
-Second, we then conduct a structural topic model (unsupervised machine learning) to inductively identify the most frequent combinations of words that appear in all Amazonian narratives.
-Here, words clustered are assumed to be a topic.
-Third, we deductively operationalize the four ideal-typical Amazonian narratives in dictionaries and provide its appearance and variation across time.
-
-# 4 Exploratory analysis: Amazonian narratives along time
-
-In the following, we will show our work in progress in terms of the empirical analysis.
-At the moment, we are trying to figure out what methods we will actually use and why.
-The number of speeches mentioning the Amazon (n=861), is not high enough to justify certain machine learning approaches as manually coding a fraction.
-We tested more inductive approaches (topic modelling), and it seems to work well, but at the same time the text volume is too small to justify.
-As there are other factors we are interested at (e.g.
-a measure of intensity, how (a)permissive and  (b)explicit is the discourse), we think a combination of manual coding and more quantitative approach might help.
-
-```{r setup I, include=FALSE}
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 # Load data
-#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
-#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
-#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
-BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
-Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path to load data after poldis
-
-# Subset for text matches
-#Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("Amazôn|Amazon|amazôn|amazon", text))
-# Remove accents and extra spaces
-#Amazon_speeches$text <- stringi::stri_trans_general(Amazon_speeches$text, id = "Latin-ASCII")
-# Make all lower case
-#Amazon_speeches$text <- tolower(Amazon_speeches$text)
-# Remove extra white spaces
-#Amazon_speeches$text <- tm::stripWhitespace(Amazon_speeches$text)
-# Get only the pertinent text chunks
-#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
-# Transform into a single text per row...
-#Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
-#saveRDS(Amazon_speeches, file="amazon_speeches.rds")
+BR_Presidential_Speeches <- readRDS("data/BR_Presidential_Speeches.Rds")
+amazon_def_year <- readRDS("data/amazon_def_year.Rds")
+Amazon_speeches <- readRDS("data/amazon_speeches.rds")
 
@@
 
-```{r setup II, include=FALSE}
+```{r cleaning and transforming in corpus II, include=FALSE}
 # Rename variables to adapt to text analysis packages' expectations
@@
 ```
-
-```{r speech frequencies I, echo=FALSE, message=FALSE, warning=FALSE}
-
-freq_year <- data.frame(year = as.numeric(names(summary(as.factor(Amazon_speeches$year)))),
-                        freq = as.numeric(summary(as.factor(Amazon_speeches$year))),
-                        freqn = as.numeric(summary(as.factor(Amazon_speeches$year)))/
-                          as.numeric(summary(as.factor(BR_Presidential_Speeches$year))))
-
-ggplot(freq_year, aes(year, freqn))+
-    geom_line()+
-    geom_point()+
-    geom_smooth(method=lm, color="#bab86c") +
-      labs(x = "",
-       y = "Relative share of speeches per year",
-       title = "Presidential speeches mentioning the Amazon (1985-2020)",
-       caption = "Frequencies normalized by the number of speeches per year in dataset",
-       color = "")
-```
-
-```{r speech frequencies II, echo=FALSE, message=FALSE, warning=FALSE}
-
-freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
-ggplot(freq_year, aes(x = year)) +
-    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
-    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
-      labs(x = "",
-       y = "Relative share of speeches per year",
-       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
-       subtitle = "Compared to annual deforestation rates since 1988",
-       color = "")+
-       theme(legend.position ="bottom")
-
-```
-
-  From the first plot, the proportion of speeches that mention the word "Amazon" increase in frequency in 1989 (possibly related to Amazon Fires coverage from the New York Times see [here](https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html) and [here](https://www.nytimes.com/1989/03/23/world/brazil-smarting-from-the-outcry-over-the-amazon-charges-foreign-plot.html)), around 1992 (likely related to the Rio Conference), from 2005 to 2010 (possibly related to the "preservation" legislation turn under the Lula Administration), and after 2016 (possibly related to increasing deforestation rates and international attention).
-An interesting finding here is that while there is fluctuations along time, mentions to the Amazon did not increase or decrease, maintaining a general average of around 15% appearance in speeches.
-A second interesting finding is that mentions to the Amazon in presidential discourse do not correlate with deforestation rates.
-This might be due to different reasons: first, deforestation rate data is published once a year, so international response and presidential discourse are lagged.
-Relatedly, wider access to this data only started in the 2000s.A more interesting measure to use would be fire data or DETER data, which comes out monthly and might drive discourse.
-Second, deforestation data might correlate better with specific Amazonian narratives rather than mentions in general.
-We will test this idea in future versions.
-
-```{r location, echo=FALSE, warning=FALSE, message=FALSE}
-# Location was added with poldis::extraxt_location(), still needs to be improved...
-# To see the variable summary, please run: `summary(as.factor(Amazon_speeches$location))`
-# Let's code the Amazonian states, the other Brazilian states, and speeches delivered outside Brazil.
-Amazon_lc <- mutate(Amazon_speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian_States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non_Amazonian_States", grepl("NA", location) ~ "Non_Identified", !grepl("Amazonian_States|Non_Amazonian_States|Non_Identified", location) ~ "International"))
-# Just a comparison with the proportion of speeches per stage on the broader dataset
-stages <- mutate(BR_Presidential_Speeches, stage = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States", grepl("Alagoas|Bahia|Ceará|Distrito Federal|Goias|Minas Gerais|Espirito Santo|Paraiba|Parana|Pernambuco|Piaui|Rio de Janeiro|Rio Grande do Norte|Rio Grande do Sul|Santa Catarina|Sao Paulo|Brazil|Sergipe", location) ~ "Non Amazonian States", grepl("NA", location) ~ "Non Identified", !grepl("Amazonian States|Non Amazonian States|Non Identified", location) ~ "International"))
-stage_rate <- data.frame(Stage = names(summary(as.factor(Amazon_lc$stage))),
-                         Amazon_speeches = paste0(round(as.numeric(summary(as.factor(Amazon_lc$stage))/861)*100, 2)," %"),
-                         All_speeches = paste0(round(as.numeric(summary(as.factor(stages$stage))/6088)*100, 2)," %"))
-knitr::kable(stage_rate, caption= "Speeches by stage")
-```
-
-  The summary table illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches.
-However, when it comes to international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches.
-We find this counter-intuitive, as many scholars tend to associate Brazil's prominent role in international environmental governance.
-At the moment, we still can not say for sure that this finding is robust.
-We operationalize international stage as anything that is not Brazil, so it includes speeches in African countries for instance.
-We will work towards a better measure that separates international stage from other countries and re-run this to see if it still holds.
-
-```{r top words by speaker I, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6}
-
-# Get 30 most frequent words overall
-
-amazon_TDM  <- TermDocumentMatrix(amazon_corpus)
-amazon_TDMm <- as.matrix(amazon_TDM)
-
-Sums_a <- rowSums(amazon_TDMm)
-Freq_a <- data.frame(word=names(Sums_a),frequency=Sums_a)
-topWords      <- subset(Freq_a, Freq_a$frequency >= 100) 
-topWords      <- topWords[order(topWords$frequency, decreasing=F),]
-topWords$word <- factor(topWords$word, 
-                          levels=unique(as.character(topWords$word)))
-
-ggplot(topWords, aes(x=word, y=frequency)) + 
-  geom_bar(stat="identity", fill='#bab86c') + 
-  coord_flip()+
-  geom_text(aes(label=frequency), colour="white",hjust=1.25, size=3.0)+
-  labs(title='Most Frequent Words in Amazonian Speeches', x="", y="")
-
-# Let's see if bigrams help us more here
-tamazon <- tidytext::tidy(amazon_corpus) %>%
-  unnest_tokens(bigram, text , token = "ngrams", n = 2) %>%
-  dplyr::count(bigram, sort = TRUE) %>%
-  ungroup()
-
-```
-
-  In terms of most frequent words, we already observe mentions related to the narratives we expect (develop, integrate, produce, deforestation).
-Pairs of words (bigrams) also point towards the same (meio ambiente, forcas armadas, zona franca, desenvolvimento sustentavel).
-
-```{r top words by speaker II, echo=FALSE, warning=FALSE, message=FALSE}
-
-# Let's get the 30 most frequent term by speaker
-amazon_presid <- aggregate(Amazon_speeches$text, list(Amazon_speeches$president), paste, collapse = " ") %>%
-  rename(doc_id = "Group.1", text = "x")
-amazon_presid_t <- tm::VCorpus(DataframeSource(amazon_presid)) %>%
-  tidy() %>% 
-  unnest_tokens(word, text) %>%
-  count(id, word, sort = TRUE)
-Sarney <- head(dplyr::filter(amazon_presid_t, id == "Sarney"), 30) %>%
-  mutate(Sarney = word) %>% select(Sarney)
-Collor <- head(dplyr::filter(amazon_presid_t, id == "Collor"), 30) %>%
-  mutate(Collor = word) %>% select(Collor)
-Itamar <- head(dplyr::filter(amazon_presid_t, id == "Itamar"), 30) %>%
-  mutate(Itamar = word) %>% select(Itamar)
-FHC <- head(dplyr::filter(amazon_presid_t, id == "FHC"), 30) %>%  mutate(FHC = word) %>% select(FHC)
-Lula <- head(dplyr::filter(amazon_presid_t, id == "Lula"), 30) %>%  mutate(Lula = word) %>% select(Lula)
-Dilma <- head(dplyr::filter(amazon_presid_t, id == "Dilma"), 30) %>%  mutate(Dilma = word) %>% select(Dilma)
-Temer <- head(dplyr::filter(amazon_presid_t, id == "Temer"), 30) %>%  mutate(Temer = word) %>% select(Temer)
-Bolsonaro <- head(dplyr::filter(amazon_presid_t, id == "Bolsonaro"), 30) %>%
-  mutate(Bolsonaro = word) %>% select(Bolsonaro)
-f_speaker <- cbind(Sarney, Collor, Itamar, FHC, Lula, Dilma, Temer, Bolsonaro) %>% 
-  kableExtra::kbl(caption = "Top 30 Words Per President") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-
-landscape(f_speaker, margin=NULL)
-
-```
-
-  Moving to most mentioned words by presidents, there are some interesting anectodal findings.
-For instance, deforestation appears to be more salient in the vocabulary employed by Lula, Dilma and Temer versus their counterparts.
-The words "soberania" and "military" only appears as part of Bolsonaro's vocabulary.Desenvolvimento, on the other hand, seems to be part of all presidents vocabulary except of Temer.
-
-```{r lda, warning=FALSE, echo=FALSE, message=FALSE}
-library(topicmodels)
-
-# Fit a simple LDA model
-# Please note that we randomly set a K = 10 (10 cluster = topics)
-
-amazon_dtm  <- DocumentTermMatrix(amazon_corpus)
-amazon_dtmm <- as.matrix(amazon_dtm)
-amazon_lda <- topicmodels::LDA(amazon_dtm, k = 10, control = list(seed = 1234))
-
-# Get the top 10 words per topic
-amazon_lda10 <- tidy(amazon_lda, matrix = "beta") %>%
-  arrange(desc(beta)) %>%
-  group_by(topic) %>%
-  filter(row_number() %in% 1:10) %>%
-  arrange(topic)
-topten_topic <- aggregate(amazon_lda10$term, list(amazon_lda10$topic), paste, collapse=", ") %>%
-  rename(Topic = "Group.1", Terms = "x") %>% 
-  kableExtra::kbl(caption = "Top 10 Words per Topic for Presidential Speeches Mentioning the Amazon") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-topten_topic
-
-# Let's get the gamma (percent of topic in document for speakers)
-amazon_lda_presid <- tidy(amazon_lda, matrix = "gamma") %>%
-  arrange(desc(gamma)) %>%
-  group_by(document) %>%
-  filter(row_number() %in% 1:2) %>% # get the top 2 topics per speaker
-  arrange(document) %>%
-  mutate(gamma = round(gamma, 3)) %>%
-  distinct() %>% 
-  rename (president = document) %>% 
-  kableExtra::kbl(caption = "Top 2 Topics Per Speaker") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-amazon_lda_presid # Only Collor associated with topic cluster that mentions "ambiente"...
-```
-
-  The table 2 (above) and table 4(below) portray the result of a structural topic model.
-We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)).
-We set the number of clusters to be found (topics) at 10, randomly.
-We, then, select the top ten words coded for each topic.
-
-  Development appears in 6 out of 10 topics, suggesting it is a cross-cutting vocabulary.
-In its purest form, we observe the developmentalist narrative in topic 1 and 3.
-Three topics relate to themes of security, development, and integration (4,7,8) and one other touches on sovereignty in its purest form (9), which combined understand as the sovereignty narrative.
-Two topics portray vocabulary that we understand as constituting the conservation narrative (2 and 10), with topic 10 being the purest form in the text.
-
-  Once the clusters are extracted, we can indicate, probabilistically, how presidents' discourse fall within a topic, that's what the second table does for the 2 most salient topics per speakier.We see that, for example, Lula's discourses about the Amazon often is clustered with themes of development and of deforestation.
-At the same time, Bolsonaro's discourses about the Amazon often is clustered with themes of integration, energy, and the military forces.
-Sarney engaged with themes of preservation, while Cardoso engages with themes related to energy and integration.
-Others as Rousseff and Temer appear to engage with themes of geography, politics, energy; while Collor an Itamar appear to engage with themes of security, development, and integration.
-\newpage
-
-```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}
-
-# Create the dictionary
-
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|
-                ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|
-                dono|nossa")
-
-development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|
-                incentivos fiscais| integrar|integracao|zona franca|transamazonica|madeira|
-                porto|madeireira|produz|energia")
-
-conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|
-                 areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|
-                 protecao|proteg")
-
-anti_environmentalism <- ("preservamos demais|nao vamos demarcar|demarcar menos|
-                          agricultura|producao de gado|ambientalistas|ong|xiita")
-
-```
-
-  Shifting our methodological strategy from an inductive approach to a more deductive and theoretically driven analysis of the text, leads similar results.We operationalize our narratives by deductively creating four groups of words (dictionaries) and assigning each contextualized mention to the Amazon to a narrative.
-The dictionaries are presented in the code chunk above.
-Our narratives approach, while still empirically weak, already shows some interesting trends (table 4, table 5, and narratives plots; below).
-First, the 1988 NYC pictures of the Amazon burning piked all narratives during the Sarney presidency.
-Second, while Lula was the president that most performed conservation narratives until 2010, Bolsonaro mobilized sovereignty narratives strongly.
-Third, generally the developmentalist narrative have decreased along time but has appeared most frequently during the Lula mandate, suggesting sustainable development was at its highest in those years.
-Fourth, while the anti socio-environmentalist narrative was generally not so frequent (this might be an identification problem or that it is simply a sub-type of the developmentalist narrative), it was present across all speakers with Bolsonaro using it the most.
-
-```{r narratives I, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
-
-# Create a variable for each and count matches
-Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
-Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
-Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
-Amazon_speeches$anti_environmentalism <- stringr::str_count(Amazon_speeches$text,
-                                                            paste0("(?i)", anti_environmentalism))
-Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
-                                  Amazon_speeches$conservation == 0 & 
-                                  Amazon_speeches$anti_environmentalism == 0, 1, 0)
-
-# Visualize correlations
-am_narratives <- Amazon_speeches %>%
-  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
-  tidyr::pivot_longer(sovereignty:other) %>% 
-  group_by(year, name) %>% 
-  summarise(value = sum(value)) %>% 
-  rename(narrative = name)
-
-ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
-  geom_line(aes(group = narrative, color = narrative), size = 1) +
-  labs(x = "Year",
-       y = "",
-       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
-    geom_smooth(method=lm, se=FALSE, color="black", linetype="dashed",size=0.5)+
-    facet_wrap(~narrative)+
-    theme (legend.position="none")
-
-```
-
-```{r narratives II, echo=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
-
-# Same frequency table but normalized by the numbers of speeches in broader dataset
-pres_narratives <- Amazon_speeches %>%
-  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
-  group_by(president) %>%
-  summarise(across(everything(), sum))
-
-pres_narratives_n <- pres_narratives %>%
-  mutate(n_speeches = summary(as.factor(BR_Presidential_Speeches$president))) %>%
-  mutate(across(c(2:6), .fns = ~./n_speeches)) %>%
-  select(-n_speeches) %>%
-  mutate_if(is.numeric, round, digits = 2)
-kableExtra::kbl(pres_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-
-# Table by stage, normalized
-stage_narratives <- Amazon_speeches %>%
-  mutate(stage = Amazon_lc$stage) %>%
-  select(-c(context, text, fulltext, year, party, date, title, doc_id, location, president)) %>%
-  group_by(stage) %>%
-  summarise(across(everything(), sum))
-
-stage_narratives_n <- stage_narratives %>%
-  mutate(n_stages = summary(as.factor(Amazon_lc$stage))) %>%
-  mutate(across(c(2:6), .fns = ~./n_stages)) %>%
-  select(-n_stages) %>%
-  mutate_if(is.numeric, round, digits = 2)
-kableExtra::kbl(stage_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
-  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
-```
-
-# 5 Bibliography
-
-Acker, Antoine (2013).
-“O maior incêndio do planeta”: como a Volkswagen e o regime militar brasileiro acidentalmente ajudaram a transformar a  Amazônia em uma arena política global.
-Revista Brasileira de História, 34(68),13-33.[fecha de Consulta 5 de Noviembre de 2021].
-ISSN: 0102-0188.
-Disponible en:   https://www.redalyc.org/articulo.oa?id=26335781002
-
-Arima, Eugenio Y., Paulo Barreto, Elis Araújo, and Britaldo Soares-Filho.
-2014.
-“Public Policies Can Reduce Tropical Deforestation: Lessons and Challenges from Brazil.” Land Use Policy 41         (November): 465–73.
-https://doi.org/10.1016/j.landusepol.2014.06.026.
-
-Assunção, Juliano, Clarissa Gandour, and Rudi Rocha.
-2015.
-“Deforestation Slowdown in the Brazilian Amazon: Prices or Policies?” Environment and Development Economics 20 (6): 697–722.
-https://doi.org/10.1017/S1355770X15000078.
-
-Barros, A.
-T.
-(2020).
-Discursos parlamentares sobre a amazônia: Sobre o que falam os deputados brasileiros.
-Política & Sociedade, 19(46), 299-331.
-doi:http://dx.doi.org/10.5007/2175-7984.2020.e66962
-
-Boucher, Doug, Sarah Roquemore, and Estrellita Fitzhugh.
-2013.
-“Brazil’s Success in Reducing Deforestation.” Tropical Conservation Science 6 (3): 426–45.
-https://doi.org/10.1177/194008291300600308.
-
-Brice, Jessica, and Michael Smith.
-2021.
-“The Amazon Is Fast Approaching a Point of No Return.” Bloomberg.Com, July 29, 2021.
-https://www.bloomberg.com/news/features/2021-07-29/amazon-rainforest-deforestation-land-grabs-surge-under-bolsonaro-in-brazil.
-
-Drummond, J., & Barros-Platiau, A. F. (2006). Brazilian Environmental Laws and Policies, 1934–
-        2002: A Critical Overview. Law & Policy, 28(1), 83–108. https://doi.org/10.1111/j.1467-
-        9930.2005.00218.x
-
-Harris, Bryan.
-2021.
-“Drought Puts Amazon at Risk of ‘Large-Scale Dieback’, Researchers Warn.” Financial Times, July 19, 2021.
-https://www.ft.com/content/02071ae7-dcf5-4c61-9c3c-b55f5aef8b0e.
-
-Hecht, Susanna, and Raoni Rajão.
-2020.
-“From ‘Green Hell’ to ‘Amazonia Legal’: Land Use Models and the Re-Imagination of the Rainforest as a New Development Frontier.” Land Use Policy 96         (July): 103871.
-https://doi.org/10.1016/j.landusepol.2019.02.030.
-
-Hochstetler, Kathryn, and Eduardo Viola.
-2012.
-“Brazil and the Politics of Climate Change: Beyond the Global Commons.” Environmental Politics 21 (5): 753–71.
-https://doi.org/10.1080/09644016.2012.698884.
-
-Franchini, M.
-A., Viola, E., Franchini, M.
-A., & Viola, E.
-(2019).
-Myths and images in global	climate	governance, conceptualization and the case of Brazil (1989—2019).
-Revista	Brasileira        de	Política Internacional, 62(2).
-https://doi.org/10.1590/0034	7329201900205
-
-Garfield, S. (2013). In Search of the Amazon: Brazil, the United States, and the Nature of a Region.
-
-Lahsen, Myanna.
-(2009).
-“A Science–Policy Interface in the Global South: The Politics of Carbon Sinks and Science in Brazil.” Climatic Change 97 (3–4): 339–72.
-https://doi.org/10.1007/s10584-009-9610-6.
-
-de Waroux, Y., Garrett, R.
-D., Chapman, M., Friis, C., Hoelle, J., Hodel, L., Hopping, K., & Zaehringer, J.
-G.
-(2021).
-The role of culture in land system science.
-Journal of Land Use            Science, 0(0), 1–17.
-https://doi.org/10.1080/1747423X.2021.1950229
-
-Miranda, David.
-2021.
-“Bolsonaro’s 1,000km Amazon Railway Will Cause Climate Chaos.
-It Must Be Stopped | David Miranda.” The Guardian, June 2021.
-http://www.theguardian.com/commentisfree/2021/jul/28/bolsonaro-amazon-railway-climate-chaos-must-be-stopped.
-
-Nepstad, Daniel, Britaldo S.
-Soares-Filho, Frank Merry, André Lima, Paulo Moutinho, John Carter, Maria Bowman, et al.
-2009.
-“The End of Deforestation in the Brazilian Amazon.” Science 326         (5958): 1350–51.
-https://doi.org/10.1126/science.1182108./
-
-Silva-Muller, L., & Faul, M.
-(2021) “Protecting the Amazon and its people: the role of civil society in the local effectiveness of transnational partnerships”.
-In Partnerships for                        Sustainability: Pathways to Effectiveness.
-Edt.
-by Andonova, L., Faul, M.
-and Piselli, D.
-Routledge: London.
-
-Silva-Muller, L.
-(forthcoming) "Payment for ecosystem services and the practices of environmental fieldworkers in policy-implementation: the case of Bolsa Floresta in the Brazilian                        Amazon"

### 2022-02-10 20220210_Draft.Rmd
#randomsample

@@
 
-# Remove stop words and punctuation
-Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
-Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
-                                        c(tm::stopwords("pt"), "nao", "amazonas",
-                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
-                                          "no", "hoje", "presidente", "governador", "regiao", 
-                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
-                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
-                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
-                                          "cumprimentar", "gente", "estado", "querido", "queria",
-                                          "todos", "brasil", "companheiro", "senhores",
-                                          "companheiras", "companheiros", "companheira",
-                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
-                                          "grosso","ministro", "ministra", "josé", "pará", "acre", "roraima",
-                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
-                                          "rio grande do sul", "rio grande do norte", "sao paulo", "então", "pouco", "pode", "sul",
-                                          "norte", "mato grosso","outro", "onde", "discurso", "parte", "anos", "cada", "todo", 
-                                          "porto velho", "visite site", "site secretaria", "minas gerais", "lula silva", 
-                                          "inácio lula", "amapa", "bahia", "é", "lá", "et", "in", "httpwww", "vez", "vezes", "entao", "coisa", "ainda", "sobre", "apenas", "coisa",
-                                          "jose", "tudo", "toda", "mil", "sempre", "assim", "estados", "forma", "pais", "programa", "primeiro"))
+```
 
-Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")
+```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}
 
-# Transform into corpus
-Amazon_speeches <- Amazon_speeches %>%
-  dplyr::mutate(doc_id = president) %>%
-  arrange(doc_id, text)
-amazon_corpus <- tm::VCorpus(DataframeSource(Amazon_speeches))
+# Create the dictionary
+
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|
+                ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|
+                dono|nossa")
+
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|
+                incentivos fiscais| integrar|integracao|zona franca|transamazonica|madeira|
+                porto|madeireira|produz|energia")
+
+conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|
+                 areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|
+                 protecao|proteg")
+
+# Create a variable for each and count matches
+Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
+Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
+Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
+
+Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
+                                  Amazon_speeches$conservation == 0, 1, 0)
+
+#dat <- Amazon_speeches %>% sample_frac(.1)
+#dat <- apply(dat,2,as.character)
+#write.csv(dat, file = "random_sample.csv")
 

### 2022-02-10 20220210_Draft.Rmd
#todolistupdatedinrmd #random_sample.csvupdatedwithlivio'scommentonpuretypes #new_dictionary.docxcreatedwith commentstobediscussed

@@
 
-- Amazon context data up to date?
-- Can we copy location stuff from previous set?
-- Start improving dictionary: prepare sheet with large random sample of classified amazonian context for inductive analysis (speaker, year, context, classification)
+- operationalize 1st version of new dictionary.docx.
+- solve broader problems mentioned in new dictionary.docx.
+- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement.
 

### 2022-02-10 20220210_Draft.Rmd
Added an example for the unnested dataset and a few other things

@@
 csl: [apa.csl]
-
 ---
@@
 - solve broader problems mentioned in new dictionary.docx.
-- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement.
+- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement at observation=one context level
 
@@
 knitr::opts_chunk$set(echo = TRUE)
-
 library(dplyr)
@@
 
-# Load data
-BR_Presidential_Speeches <- readRDS("data/BR_Presidential_Speeches.Rds")
-amazon_def_year <- readRDS("data/amazon_def_year.Rds")
+# Load data$
 Amazon_speeches <- readRDS("data/amazon_speeches.rds")
-
 ```
@@
 Amazon_speeches <- dplyr::rename(Amazon_speeches, fulltext = text, text = ccontext)
-
 ```
@@
 ```{r narratives dictionary, warning=FALSE, message=FALSE, echo=TRUE}
-
 # Create the dictionary
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|
-                ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|
-                dono|nossa")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
 
-development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|
-                incentivos fiscais| integrar|integracao|zona franca|transamazonica|madeira|
-                porto|madeireira|produz|energia")
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais| integra|zona franca|transamazonica|madeira|porto|madeireira|produz|energia|agro|agri")
 
-conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|
-                 areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|
-                 protecao|proteg")
+conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteg")
 
@@
 Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
-
 Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
                                   Amazon_speeches$conservation == 0, 1, 0)
-
+# Notice we count each match here, is that what we want? If not, see code chunk below.
+# Visulaize totals
+tibble::tibble(Sovereignty = sum(Amazon_speeches$sovereignty),
+               Development = sum(Amazon_speeches$development),
+               Conservation = sum(Amazon_speeches$conservation),
+               Other = sum(Amazon_speeches$other))
 #dat <- Amazon_speeches %>% sample_frac(.1)
@@
 #write.csv(dat, file = "random_sample.csv")
+```
 
+```{r unnest list}
+# Here each context match become one data point in the dataset
+sum(lengths(Amazon_speeches$context)) # Check the number of passages matched
+# Unnest list into a dataframe
+AS_long <- Amazon_speeches %>%
+  select(president, year, party, title, location, date, fulltext, context) %>% 
+  unnest(cols = c(context))
+# Run the same dictionary as before but now only assign 1 if any matches and 0 if no matches
+# (no multiple matches/counts per observation)
+AS_long$sovereignty <- ifelse(stringr::str_detect(AS_long$context, paste0(sovereignty)), 1, 0)
+AS_long$development <- ifelse(stringr::str_detect(AS_long$context, paste0(development)), 1, 0)
+AS_long$conservation <- ifelse(stringr::str_detect(AS_long$context, paste0(conservation)), 1, 0)
+AS_long$other <- ifelse(AS_long$sovereignty == 0 & AS_long$development == 0 & 
+                                  AS_long$conservation == 0, 1, 0)
+# Visualize totals
+tibble::tibble(Sovereignty = sum(AS_long$sovereignty),
+               Development = sum(AS_long$development),
+               Conservation = sum(AS_long$conservation),
+               Other = sum(AS_long$other))
+# Still some overlap... 
 ```
+
+```{r lda}
+#### This is a bit useless, you can just delete it if you want...
+#### Tomorrow I will try and run a STM model to see if we can use some of the metadata better
+#### to find topics and correlations. Just in case. I will also work on dictionary further.
+# Let's jus quickly model each category and see if we find something interesting
+# This also serves as a robusteness check for ou dictionary
+# Pivot data longer to use narratives as 
+am <- AS_long %>%
+  select(president, year, location, context, sovereignty, development, conservation, other) %>% 
+  tidyr::pivot_longer(sovereignty:other) %>% 
+  dplyr::rename(doc_id = name, text = context) %>%
+  arrange(doc_id, text)
+# Remove stopwords
+am$text <- tm::removeWords(am$text, c(tm::stopwords("pt"), "nao", "amazonas",
+                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
+                                          "no", "hoje", "presidente", "governador", "regiao", 
+                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
+                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
+                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
+                                          "cumprimentar", "gente", "estado", "querido", "queria",
+                                          "todos", "brasil", "companheiro", "senhores",
+                                          "companheiras", "companheiros", "companheira",
+                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
+                                          "grosso","ministro", "ministra", "josé", "pará", "acre",
+                                          "roraima", "manaus", "rondônia", "ministros", "luiz", 
+                                          "antonio", "vou", "eduardo braga", "rio de janeiro",
+                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", 
+                                          "mato grosso", "outro", "onde", "discurso", "parte", 
+                                          "anos", "cada", "todo", "porto velho", "visite site",
+                                          "site secretaria", "minas gerais", "lula silva", "inácio", "lula",
+                                          "amapa", "bahia", "é", "lá", "et", "in", "silva", "jose",
+                                      "apenas", "tudo", "ainda", "fazendo", "sobre", "republica", 
+                                      "portanto", "mil", "toda", "site", "pais"))
+# Get corpus and DTM
+am_corpus <- tm::VCorpus(DataframeSource(am))
+am_dtm  <- DocumentTermMatrix(am_corpus)
+# Run model (4 topics since we have 4 categories)
+am_lda <- topicmodels::LDA(am_dtm, k = 4, control = list(seed = 1234))
+# Get top terms
+am_top_ten <- tidy(am_lda, matrix = "beta") %>%
+  arrange(desc(beta)) %>%
+  group_by(topic) %>%
+  filter(row_number() %in% 1:10) %>%
+  arrange(topic)
+am_top_ten <- aggregate(am_top_ten$term, list(am_top_ten$topic), paste, collapse=", ") %>%
+  rename(Topic = "Group.1", Terms = "x")
+# Get narratives and merge tables
+am_na <- tidy(am_lda, matrix = "gamma") %>%
+  arrange(desc(gamma)) %>%
+  group_by(document) %>%
+  filter(row_number() %in% 1:3) %>%
+  arrange(document) %>% 
+  select(-gamma) %>% 
+  distinct()
+am_na <- aggregate(am_na$document, list(am_na$topic), paste, collapse = ", ") %>%
+  rename(Topic = "Group.1", Narrative = "x") 
+amm <- dplyr::left_join(am_top_ten, am_na, by = "Topic") %>%
+  kableExtra::kbl(caption = "Top 10 Words per Topic for Stages") %>%
+  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
+amm
+# A lot of overlap... Presidents usually talk about more than one category in discourse (?!).
+# We need to maybe create subtopics for development and sovereinty, as well as improve dictionary...
+# Maybe we can model each narrative separately to help with developing a dictionary?
+```

### 2022-02-11 20220210_Draft.Rmd
#polishedthedictionaryabit #randomsamplefromAS_long

@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar")
 
-development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais| integra|zona franca|transamazonica|madeira|porto|madeireira|produz|energia|agro|agri")
+development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integra|zona franca|transamazonica|madeira|porto|madeireira|energia|estimulo|banco|hidreletrica|convenio|sede|fome|saude|hospital|escola|saneamento|social")
 
-conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteg")
+conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|queimada|sustentav|meio ambiente|florest|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitosambientais")
 
@@
                                   Amazon_speeches$conservation == 0, 1, 0)
+
 # Notice we count each match here, is that what we want? If not, see code chunk below.

### 2022-02-11 20220210_Draft.Rmd
#sovdictionaryupdate #codeforrandomsamplecommentedout

@@
 
-- operationalize 1st version of new dictionary.docx.
 - solve broader problems mentioned in new dictionary.docx.
-- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement at observation=one context level
 
@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar|fronteira")
 
@@
                                   AS_long$conservation == 0, 1, 0)
+#set.seed(123)
+#random_sample2 <- AS_long %>% sample_frac(.1)
+#write.csv(random_sample2, file="random_sample2.csv")
+
 # Visualize totals

### 2022-02-11 20220210_Draft.Rmd
#dictionarycorrection

@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar|fronteira")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|dono|internacionalizar|fronteira")
 

### 2022-02-11 20220210_Draft.Rmd
#fewchangestodictionary

@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|dono|internacionalizar|fronteira")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar| |internacionalizacao")
 
@@
 
-conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|queimada|sustentav|meio ambiente|florest|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitosambientais")
+conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|meio ambiente|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitos ambientais|unidades de conservacao")
 

### 2022-02-11 20220210_Draft.Rmd
Updated rmarkdown to take a look at the non matched codes (other category)

@@
 
-sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar| |internacionalizacao")
+sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar|internacionalizacao")
 
@@
                Other = sum(AS_long$other))
-# Still some overlap... 
+# Still some overlap...Also, there were 976 context units not matched at all...
+# Let's see some of which is not matched
+o <- dplyr::filter(AS_long, other == 1) %>% dplyr::select(president, year, context)
+dplyr::slice_sample(o, n = 20)
+o$context[1:20] # Number 12 and 17 (riquezas no subsolo/mineral reserves) development?
+o$context[500:520] # Number 7, development or preservation or neither?
+10 (chico mendes) preservation?
+14 sovereingty?
+15 development and sovereingty?
+17 and 18 development?
+19 and 20 conservation?
+21 development?
+o$context[940:960] # 1 (gas and niobio) development?
+3 sovereignty?
+6 development and preservation?
+7 conservation?
+A lot of Bolsonaro's mentions about the Amazonia not burning, should we code these or not?
 ```

### 2022-02-14 others/get_context_&_locations.R
Renamed get_location script to reflect better what it does, gets context and locations

@@ -36,5 +36,28 @@ Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text)
 Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
 Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
 
+# Get 2 lines before and 2 lines after
+context2 <- function(string, var) {
+  match <- paste0("([^.]+\\.){0,2}[^.]+(", string, ").*?\\.([^.]+\\.){0,2}")
+  s <- stringr::str_extract_all(var, match)
+  s
+}
+Amazon_speeches$AM2 <- context2("amazon", var = Amazon_speeches$text)
+Amazon_speeches$ID <- as.numeric(random::randomNumbers(n = 946, min = 1000, max = 2000, col = 1))
+
 # Save Rds
 saveRDS(Amazon_speeches, "amazon_speeches.Rds")
+
+# Get and save long data coding
+library(dplyr)
+amazon_speeches_long <- Amazon_speeches %>%
+  select(ID, president, year, party, title, location, date, text, AM2) %>% 
+  tidyr::unnest(cols = c(AM2))
+saveRDS(amazon_speeches_long, "amazon_speeches_long.Rds") # 2014 obs
+
+# Get a sample for hand coding
+training_set <- amazon_speeches_long %>%
+  select(ID, AM2) %>%
+  dplyr::slice_sample(n = 672)
+# export to Excel
+xlsx::write.xlsx(training_set, file = "training_set.xlsx")

### 2022-02-28 others/graph abstract.Rmd

---
title: "Graph abstract"
author: "Henrique Sposito"
date: "2/24/2022"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
# Rename variables to adapt to text analysis packages' expectations
Amazon_speeches <- dplyr::rename(amazon_speeches_long, fulltext = text, text = AM2)
# Create the dictionary
sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar|internacionalizacao")

economic_integration <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integra|zona franca|transamazonica|madeira|porto|madeireira|energia|estimulo|banco|hidreletrica|convenio")

social_dev <- ("sede|fome|saude|hospital|escola|saneamento|social|comida|dign")

conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|meio ambiente|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitos ambientais|unidades de conservacao")

# Create a variable for each and count matches
Amazon_speeches$sovereignty <- ifelse(stringr::str_detect(Amazon_speeches$text, paste0(sovereignty)), 1, 0)
Amazon_speeches$economic_integration <- ifelse(stringr::str_detect(Amazon_speeches$text, paste0(economic_integration)), 1, 0)
Amazon_speeches$social_dev <- ifelse(stringr::str_detect(Amazon_speeches$text, paste0(social_dev)), 1, 0)
Amazon_speeches$conservation <- ifelse(stringr::str_detect(Amazon_speeches$text, paste0(conservation)), 1, 0)
Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$economic_integration == 0 & 
                                  Amazon_speeches$conservation == 0 & Amazon_speeches$social_dev, 1, 0)

# Notice we count each match here, is that what we want? If not, see code chunk below.
# Visulaize totals
tibble::tibble(Sovereignty = sum(Amazon_speeches$sovereignty),
               EI = sum(Amazon_speeches$economic_integration),
               SD = sum(Amazon_speeches$social_dev),
               Conservation = sum(Amazon_speeches$conservation),
               Other = sum(Amazon_speeches$other))

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  select(-c(text, fulltext, party, date, title)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, president, name) %>%
  summarise(value = sum(value)) %>%
  rename(narrative = name)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_smooth(aes(group = narrative, color = narrative), size = 1, se = FALSE) +
  facet_wrap(~narrative, ncol = 2) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")
```

### 2022-02-28 others/clean_combined_training_set.R
Added preparation script for combined training dataset

@@ -1,0 +1,26 @@
+# Get and wrangle combined training set
+library(readxl)
+training_set_combined <- read_excel("data/training_set_combined.xlsx")
+library(dplyr)
+summary(as.factor(training_set_combined$decision_falsepositive)) # We have 3 ones ...
+summary(as.factor(training_set_combined$decision_code)) # Not consistent
+# Fix data issues first
+training_set_combined$decision_falsepositive[103] <- "false positive"
+training_set_combined$decision_falsepositive[225] <- "false positive"
+training_set_combined$decision_code <- gsub("ecnomic|only economic", "economic",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("consevation", "conservation",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("soverignty|sovereigty|sovereingty", "sovereignty",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("only", "", training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub(" and ", ", ", training_set_combined$decision_code)
+# Get categories back in as variables 
+ts <- training_set_combined %>%
+  mutate(code_check = ifelse(code_henrique == code_livio, 1, 0),
+         false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
+         sov = ifelse(grepl("sovereignty", decision_code), 1, substring(code_henrique, 0, 1)),
+         EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
+         SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
+         con = ifelse(grepl("conservation", decision_code), 1, substring(code_henrique, 4, 4))) %>%
+  select(-c(ID, check_decision_fp, check_code, decision_falsepositive, code_henrique, code_livio, decision_code))

### 2022-03-01 others/clean_combined_training_set.R
Cleaned and saved final training set data combined

@@ -23,4 +23,7 @@ ts <- training_set_combined %>%
          EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
          SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
          con = ifelse(grepl("conservation", decision_code), 1, substring(code_henrique, 4, 4))) %>%
-  select(-c(ID, check_decision_fp, check_code, decision_falsepositive, code_henrique, code_livio, decision_code))
+  select(-c(ID, decision_falsepositive, code_henrique, code_livio, decision_code)) %>%
+  mutate_all(~replace(., is.na(.), 0))
+# Save data
+saveRDS(ts, "training_set_final.Rds")

### 2022-03-01 others/clean_combined_training_set.R
Added final training dataset and reliability cehcks for categories

@@ -17,8 +17,7 @@ training_set_combined$decision_code <- gsub("only", "", training_set_combined$de
 training_set_combined$decision_code <- gsub(" and ", ", ", training_set_combined$decision_code)
 # Get categories back in as variables 
 ts <- training_set_combined %>%
-  mutate(code_check = ifelse(code_henrique == code_livio, 1, 0),
-         false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
+  mutate(false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
          sov = ifelse(grepl("sovereignty", decision_code), 1, substring(code_henrique, 0, 1)),
          EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
          SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
@@ -26,4 +25,32 @@ ts <- training_set_combined %>%
   select(-c(ID, decision_falsepositive, code_henrique, code_livio, decision_code)) %>%
   mutate_all(~replace(., is.na(.), 0))
 # Save data
-saveRDS(ts, "training_set_final.Rds")
+# saveRDS(ts, "training_set_final.Rds")
+
+# Check intercoder reliability for each category (without false positives)
+check_reliability <- training_set_combined %>%
+  filter(!grepl("^false positive$", decision_falsepositive)) %>% 
+  mutate(code_livio = ifelse(is.na(code_livio), "0000", code_livio), 
+         code_check = ifelse(code_henrique == code_livio, 1, 0),
+         sov_h = substring(code_henrique, 0, 1),
+         EI_h = substring(code_henrique, 2, 2),
+         SD_h = substring(code_henrique, 3, 3),
+         con_h = substring(code_henrique, 4, 4),
+         sov_l = substring(code_livio, 0, 1),
+         EI_l = substring(code_livio, 2, 2),
+         SD_l = substring(code_livio, 3, 3),
+         con_l = substring(code_livio, 4, 4)) %>% 
+  mutate(check_sov = ifelse(sov_h == sov_l, 1, 0),
+         check_ei = ifelse(EI_h == EI_l, 1, 0),
+         check_sd = ifelse(SD_h == SD_l, 1, 0),
+         check_con = ifelse(con_h == con_l, 1, 0)) %>% 
[…]

### 2022-03-02 others/model_classification.R
Added a model classification script and a first attempt to classify texts portions into the categories

@@ -1,0 +1,265 @@
+# Classify texts
+
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(ggplot2)
+library(pbapply)
+library(mgsub)
+library(RTextTools)
+
+# Get hand coded final training set
+training_set_final <- readRDS("~/GitHub/amazondef/data/training_set_final.Rds")
+# Get full dataset and remove hand coded observations
+amazon_speeches_long <- readRDS("~/GitHub/amazondef/data/amazon_speeches_long.Rds")
+
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
+t <- dplyr::select(training_set_final, AM2) # used to remove duplicates later
+
+# Get other texts standardize
+amazon_speeches_long$AM2 <- stringi::stri_trans_general(amazon_speeches_long$AM2, 'latin-ascii')
+amazon_speeches_long$AM2 <- stringr::str_squish(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tolower(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removeNumbers(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removePunctuation(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- trimws(amazon_speeches_long$AM2)
+
+# Remove train obs, keep only score, then rbind train and score data
+score <- amazon_speeches_long[!(amazon_speeches_long$AM2 %in% t$AM2),]
+score <- score %>%
+  select(AM2) %>%
+  mutate(sov = NA, EI = NA, SD = NA, con = NA, false_positives = NA) # Added NA for reference
+score <- rbind(train, score) # Need this cause we are working with matrixes
+
+# Let's run a classification model for false positives, just as a test
+
+# Get a corpus and DTM
[…]

### 2022-03-13 others/LSA_GLM_classification_models.R
Added coded validation set

@@ -5,6 +5,7 @@ library(stringr)
 library(glmnet)
 library(tm)
 library(yardstick)
+library(lsa)
 # Get hand coded final training set
 training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
 # Get full dataset and remove hand coded observations
@@ -39,7 +40,7 @@ txtcorp_lsa <- tm::tm_map(txtcorp_lsa, removeWords, stopwords('pt'))
 TDM_lsa <- TermDocumentMatrix(txtcorp_lsa,
                               control = list(weighting = weightTfIdf))
 # Get 20 latent topics (just for the sake of it)
-lsaTDM <- lsa(TDM_lsa, 20) # This takes a few minutes
+lsaTDM <- lsa(TDM_lsa, 30) # This takes a few minutes
 # Extract the document LSA values
 docVectors <- as.data.frame(lsaTDM$dk)
 
@@ -72,8 +73,7 @@ summary(as.factor(score_lsa_fp)) # We got 96 false positives here!!!
 # Let me take out to see:
 fp_lsa <- score[606:2014,] %>%
   select(AM2) %>%
-  mutate(fp_score = score_lsa_fp) %>% 
-  filter(score_lsa_fp == "1")
+  mutate(fp_score = score_lsa_fp)
 fp_lsa
 
 ##### Model sovereignty
@@ -104,8 +104,7 @@ summary(as.factor(score_lsa_sov)) # We got 114 here
 # Let's take out to see:
 sov_lsa <- score[606:2014,] %>%
   select(AM2) %>%
-  mutate(sov_score = score_lsa_sov) %>% 
-  filter(score_lsa_sov == "1")
+  mutate(sov_score = score_lsa_sov)
 sov_lsa # Idk here
 
 ##### Model EI
@@ -135,8 +134,7 @@ summary(as.factor(score_lsa_EI)) # We got 429 here
 # Let's take out to see:
 EI_lsa <- score[606:2014,] %>%
   select(AM2) %>%
-  mutate(EI_score = score_lsa_EI) %>% 
-  filter(score_lsa_EI == "1")
+  mutate(EI_score = score_lsa_EI)
 EI_lsa # have to check here but IDK ...
 
 # Model SD
@@ -166,8 +164,7 @@ summary(as.factor(score_lsa_SD)) # We got 140 here
 # Let's take out to see:
[…]

### 2022-03-15 others/clean_combined_training_set.R
cleaned and saved validation_final data

@@ -54,3 +54,17 @@ sum(check_reliability$check_sov)/550 # 91%
 sum(check_reliability$check_ei)/550 # 76%
 sum(check_reliability$check_sd)/550 # 86%
 sum(check_reliability$check_con)/550 #89%
+
+####### Load and clean validation set
+validation_combined <- read_excel("data/validation_combined.xlsx")
+# Split code as variables
+summary(as.factor(validation_combined$decision_code))
+validation_final <- validation_combined %>%
+  mutate(false_positives = ifelse(grepl("^fp$", decision_code), 1, 0),
+         sov = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 0, 1)),
+         EI = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 2, 2)),
+         SD = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 3, 3)),
+         con = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 4, 4))) %>%
+  select(-c(ID, code_henrique, code_livio, decision_code, com_henrique, com_livio, match, "...1"))
+# Save data
+# saveRDS(validation_final, "validation_final.Rds")

### 2022-03-15 others/20220210_Draft.Rmd
Added script for SVm and GLM comparison

--- 2022-02-11 20220210_Draft.Rmd
@@
 #### This is a bit useless, you can just delete it if you want...
-#### Tomorrow I will try and run a STM model to see if we can use some of the metadata better
-#### to find topics and correlations. Just in case. I will also work on dictionary further.
 # Let's jus quickly model each category and see if we find something interesting
@@
 ```
+
+```{r}
+# STM model, just for the sake of it, to see if we can use some of the metadata better to find topics and correlations ...
+library(stm)
+data <- AS_long %>%
+  select(title, president, year, location, context, sovereignty, development, conservation, other) %>% 
+  tidyr::pivot_longer(sovereignty:other) %>% 
+  dplyr::rename(documents = title, text = context, narrative = name) %>%
+  arrange(documents, text)
+data$text <- tm::removeWords(am$text, c(tm::stopwords("pt"), "nao", "amazonas",
+                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
+                                          "no", "hoje", "presidente", "governador", "regiao", 
+                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
+                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
+                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
+                                          "cumprimentar", "gente", "estado", "querido", "queria",
+                                          "todos", "brasil", "companheiro", "senhores",
+                                          "companheiras", "companheiros", "companheira",
+                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
+                                          "grosso","ministro", "ministra", "josé", "pará", "acre",
+                                          "roraima", "manaus", "rondônia", "ministros", "luiz", 
+                                          "antonio", "vou", "eduardo braga", "rio de janeiro",
+                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", 
+                                          "mato grosso", "outro", "onde", "discurso", "parte", 
+                                          "anos", "cada", "todo", "porto velho", "visite site",
+                                          "site secretaria", "minas gerais", "lula silva", "inácio", "lula",
+                                          "amapa", "bahia", "é", "lá", "et", "in", "silva", "jose",
+                                      "apenas", "tudo", "ainda", "fazendo", "sobre", "republica", 
+                                      "portanto", "mil", "toda", "site", "pais"))
+processed <- textProcessor(data$documents, metadata = data) 
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
+docs <- out$documents
+vocab <- out$vocab
+meta <- out$meta
+plotRemoved(processed$documents, lower.thresh = seq(1, 100, by = 100))
+out <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh = 10)
+poliblogPrevFit <- stm(documents = out$documents, vocab = out$vocab, K = 5, # five clusters
+                       prevalence = ~narrative + president, # model for narrative and president
+                       max.em.its = 75, data = out$meta, init.type = "Spectral")
+poliblogSelect <- selectModel(out$documents, out$vocab, K = 5, ~narrative + president,
+                              max.em.its = 75, data = out$meta, runs = 20, seed = 8458159)
+plotModels(poliblogSelect, pch = c(1, 2, 3, 4), legend.position = "bottomright")
+labelTopics(poliblogPrevFit, c(1, 2, 3, 4, 5)) # get labels for each model
+out$meta$narrative <- as.factor(out$meta$narrative)
+prep <- estimateEffect(1:5 ~narrative + president, poliblogPrevFit, meta = out$meta, uncertainty = "Global")
+summary(prep, topics = c(1:5)) # Ok, interesting
+plot(poliblogPrevFit, type = "summary", xlim = c(0, 0.3))
+```

### 2022-03-15 others/LSA_GLM_classification_models.R

@@ -249,4 +249,3 @@ ggplot(am_narratives, aes(x = year, y = as.numeric(value), fill = narrative)) +
 library(ggpubr)
 ggpubr::ggarrange(one, two, nrow = 2, common.legend = TRUE, legend="bottom")
 # Save
-

### 2022-03-15 others/clean_combined_training_set.R

@@ -61,10 +61,10 @@ validation_combined <- read_excel("data/validation_combined.xlsx")
 summary(as.factor(validation_combined$decision_code))
 validation_final <- validation_combined %>%
   mutate(false_positives = ifelse(grepl("^fp$", decision_code), 1, 0),
-         sov = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 0, 1)),
-         EI = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 2, 2)),
-         SD = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 3, 3)),
-         con = ifelse(grepl("^fp$", decision_code), 0, substring(code_henrique, 4, 4))) %>%
+         sov = ifelse(grepl("^fp$", decision_code), 0, substring(decision_code, 0, 1)),
+         EI = ifelse(grepl("^fp$", decision_code), 0, substring(decision_code, 2, 2)),
+         SD = ifelse(grepl("^fp$", decision_code), 0, substring(decision_code, 3, 3)),
+         con = ifelse(grepl("^fp$", decision_code), 0, substring(decision_code, 4, 4))) %>%
   select(-c(ID, code_henrique, code_livio, decision_code, com_henrique, com_livio, match, "...1"))
 # Save data
-# saveRDS(validation_final, "validation_final.Rds")
+#saveRDS(validation_final, "validation_final.Rds")

### 2022-03-15 others/test_validation_model.R

@@ -1,0 +1,258 @@
+# Validation set
+# Here we compare how the LSA/GLM model compares to the SVM when we use
+# our training set to label a validation set hand-coded
+
+############## LSA/GLM
+# LSA and GLM simple models to classify data
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get full dataset and remove hand coded observations
+validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
+# Get validation texts standardize
+validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
+validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
+validation_final$AM2 <- tolower(validation_final$AM2)
+validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
+validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
+validation_final$AM2 <- trimws(validation_final$AM2)
+# Rbind train and validation data
+score <- rbind(train, validation_final) # Need this cause we are working with matrixes
+
+##### Now let's run a simple linear model based on a LSA topic model
+# Clean and get a dtm
+txtcorp_lsa <- VCorpus(VectorSource(as.character(score$AM2)))
[…]

### 2022-03-16 others/SVM_model_final.R
Added SVM_model_final script to others folder

@@ -1,0 +1,175 @@
+# SVM model classification final
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+library(e1071)
+
+##### First, let's try to tune the model parameters in the Economic Integration variable
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get validation dataset
+validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+# Rbind train and validation data
+score <- rbind(training_set_final[,-1], validation_final)
+trainData <- score[1:605,]
+testData <- score[606:819,]
+# create matrix
+t_matrix <- create_matrix(trainData["AM2"])
+s_matrix <- create_matrix(testData["AM2"], originalMatrix = t_matrix)
+# model ei
+model_EI <- svm(x = t_matrix, y = as.numeric(trainData$EI), kernel = "linear")
+# predict EI
+pred_EI <- predict(model_EI, s_matrix)
+pred_EI <- ifelse(pred_EI > 0.5, 1, 0)
+# table ei
+table(pred = pred_EI, true = testData$EI)
+# accuracy
+yardstick::accuracy(table(true = testData$EI, pred = pred_EI))
+# ROC
+roc_svm_ei <- data.frame(cbind(tpred = as.numeric(pred_EI), label = as.numeric(testData$EI)))
+WVPlots::ROCPlot(roc_svm_ei, 'tpred', 'label', 1, title = "ROC Test Predictions SVM EI")
+# tune parameters to get better results (try with numeric and factor)
+tune_ei = tune(svm, t_matrix, as.numeric(trainData$EI),
+              ranges =list(cost=c(0.001,0.01,0.1, 1,5,10,100, 1000, 10000, 100000, 1000000)))
+tune_ei$best.model 
+# match best parameters and predict again
[…]

### 2022-03-16 others/test_validation_model.R

@@ -13,7 +13,7 @@ library(yardstick)
 library(lsa)
 # Get hand coded final training set
 training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get full dataset and remove hand coded observations
+# Get validation dataset
 validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
 # Get training texts standardized
 training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')

### 2022-03-17 final_data_preparation_script.R
Added final datasets and preparation scripts

@@ -1,0 +1,76 @@
+# Prepare final data for anylsis
+# Amazon statements dataset
+library(dplyr)
+final_alebeled_data <- readRDS("~/Documents/GitHub/amazondef/data/final_alebeled_data.Rds")
+final_alebeled_data$false_positives <- as.factor(ifelse(final_alebeled_data$false_positives > 0.5, 1, 0))
+final_alebeled_data$sov <- as.factor(ifelse(as.numeric(final_alebeled_data$sov) > 0.5, 1, 0))
+final_alebeled_data$EI <- as.factor(ifelse(as.numeric(final_alebeled_data$EI) > 0.5, 1, 0))
+final_alebeled_data$SD <- as.factor(ifelse(as.numeric(final_alebeled_data$SD) > 0.5, 1, 0))
+final_alebeled_data$con <- as.factor(ifelse(as.numeric(final_alebeled_data$con) > 0.5, 1, 0))
+summary(final_alebeled_data)
+fp <- dplyr::filter(final_alebeled_data, false_positives == "1" & sov == "0" & EI == "0" & SD == "0" & con == "0")
+final_data <- dplyr::anti_join(final_alebeled_data, fp, "AM2")
+summary(final_data)
+# re-assign location with new version of extract_location()
+# function that does not contain "Brazil" as a match
+final_data$location <- poldis::extract_location(final_data$title)
+summary(as.factor(final_data$location))
+# if NA for location in title, use full text
+final_data$location <- ifelse(grepl("^NA$", final_data$location),
+                              poldis::extract_location(final_data$text),
+                              final_data$location)
+summary(as.factor(final_data$location))
+# a few obs were not matched still, let's see them
+final_data$location <- ifelse(nchar(final_data$location) > 40, "NA", final_data$location)
+summary(as.factor(final_data$location))
+nm <- final_data %>% dplyr::filter(location == "NA") %>% select(AM2, text)
+View(nm) # we can hand code some of these
+nm$location_na <- c("Para", "Acre", "Bahia", "Para", "Para", "Para", "United States of America",
+                    "Para",  "Minas Gerais", "Rio Grande do Sul", "Para", "United States of America",
+                    "Rio Grande do Sul", "Amazonas", "Para", "NA", "Acre", "Para",
+                    "Rio Grande do Sul", "Para", "Para", "NA", "NA", "Amazonas")
+nm <- dplyr::select(nm, AM2, location_na)
[…]

### 2022-03-18 final_data_preparation_script.R
Added validation_other data for revision

@@ -1,15 +1,15 @@
 # Prepare final data for anylsis
 # Amazon statements dataset
 library(dplyr)
-final_alebeled_data <- readRDS("~/Documents/GitHub/amazondef/data/final_alebeled_data.Rds")
-final_alebeled_data$false_positives <- as.factor(ifelse(final_alebeled_data$false_positives > 0.5, 1, 0))
-final_alebeled_data$sov <- as.factor(ifelse(as.numeric(final_alebeled_data$sov) > 0.5, 1, 0))
-final_alebeled_data$EI <- as.factor(ifelse(as.numeric(final_alebeled_data$EI) > 0.5, 1, 0))
-final_alebeled_data$SD <- as.factor(ifelse(as.numeric(final_alebeled_data$SD) > 0.5, 1, 0))
-final_alebeled_data$con <- as.factor(ifelse(as.numeric(final_alebeled_data$con) > 0.5, 1, 0))
-summary(final_alebeled_data)
-fp <- dplyr::filter(final_alebeled_data, false_positives == "1" & sov == "0" & EI == "0" & SD == "0" & con == "0")
-final_data <- dplyr::anti_join(final_alebeled_data, fp, "AM2")
+final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/data/final_labeled_data.Rds")
+final_labeled_data$false_positives <- as.factor(ifelse(final_labeled_data$false_positives > 0.5, 1, 0))
+final_labeled_data$sov <- as.factor(ifelse(as.numeric(final_labeled_data$sov) > 0.5, 1, 0))
+final_labeled_data$EI <- as.factor(ifelse(as.numeric(final_labeled_data$EI) > 0.5, 1, 0))
+final_labeled_data$SD <- as.factor(ifelse(as.numeric(final_labeled_data$SD) > 0.5, 1, 0))
+final_labeled_data$con <- as.factor(ifelse(as.numeric(final_labeled_data$con) > 0.5, 1, 0))
+summary(final_labeled_data)
+fp <- dplyr::filter(final_labeled_data, false_positives == "1" & sov == "0" & EI == "0" & SD == "0" & con == "0")
+final_data <- dplyr::anti_join(final_labeled_data, fp, "AM2")
 summary(final_data)
 # re-assign location with new version of extract_location()
 # function that does not contain "Brazil" as a match

### 2022-03-18 others/SVM_model_final.R

@@ -6,6 +6,8 @@ library(tm)
 library(yardstick)
 library(lsa)
 library(e1071)
+library(RTextTools)
+library(SnowballC)
 
 ##### First, let's try to tune the model parameters in the Economic Integration variable
 # Get hand coded final training set
@@ -19,13 +21,25 @@ training_set_final$AM2 <- tolower(training_set_final$AM2)
 training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
 training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
 training_set_final$AM2 <- trimws(training_set_final$AM2)
+t <- select(training_set_final, AM2) # save for later
+# get validation standardized
+v <- select(validation_final, AM2) # save for merge later
+validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
+validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
+validation_final$AM2 <- tolower(validation_final$AM2)
+validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
+validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
+validation_final$AM2 <- trimws(validation_final$AM2)
 # Rbind train and validation data
-score <- rbind(training_set_final[,-1], validation_final)
-trainData <- score[1:605,]
-testData <- score[606:819,]
+tdata <- rbind(training_set_final[,-1], validation_final)
+tdata$AM2 <- tm::removeWords(tdata$AM2, tm::stopwords("pt"))
+tdata$AM2 <- SnowballC::wordStem(tdata$AM2, 'pt')
+tdata$AM2 <- tm::stripWhitespace(tdata$AM2)
+trainData <- tdata[1:605,]
+testData <- tdata[606:819,]
 # create matrix
-t_matrix <- create_matrix(trainData["AM2"])
-s_matrix <- create_matrix(testData["AM2"], originalMatrix = t_matrix)
+t_matrix <- create_matrix(trainData$AM2, weighting = weightTfIdf)
+s_matrix <- create_matrix(testData$AM2, originalMatrix = t_matrix, weighting = weightTfIdf)
 # model ei
 model_EI <- svm(x = t_matrix, y = as.numeric(trainData$EI), kernel = "linear")
 # predict EI
@@ -45,7 +59,7 @@ tune_ei$best.model
 # match best parameters and predict again
 model_EI <- svm(x = t_matrix, y = as.numeric(trainData$EI),
[…]

### 2022-03-28 anylysis_hs.Rmd
Preliminary analysis henrique

---
title: "Analysis_hs"
output: html_document
date: '2022-03-28'
---

## Amazon as a problem in time

```{r}
# load some packages
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggthemes)

# Get datasets
final_data_as <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")

# Get the data per president (Plot 1)
time_long <- final_data_as %>% 
  mutate(sov = as.numeric(sov), EI = as.numeric(EI),
         SD = as.numeric(SD), con = as.numeric(con), other = as.numeric(other)) %>% 
  select(-c(ID, party, title, location, date, text, AM2, false_positives, hand_coded, location_cat)) %>%
  group_by(president, year) %>% 
  summarize(across(everything(), sum)) %>%
  tidyr::pivot_longer(sov:other, "Construction")
construction_time <- ggplot(time_long, aes(x = year, y = value, fill = Construction)) +
  geom_line(aes(group = Construction, color = Construction), size = 0.5) +
  labs(x = "",
       y = "",
       title = "How the Amazon has been constructed as a problem in time?") +
  theme_classic()
construction_time

# Let's try and add a labeled and colored rectangle for periods
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020))
construction_time_color <- construction_time +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = -Inf, ymax = Inf, alpha = 0.2,
           color = c("blue", "green", "yellow", "cyan", "red", "purple", "brown", "grey"),
           fill = c("blue", "green", "yellow", "cyan", "red", "purple", "brown", "grey")) +
  annotate(geom = "text", x = hp$label, y = 150, angle = 90, alpha = 0.4, hjust = "left",
           label =  c("Sarney", "Collor", "Franco", "Cardoso", "Silva", "Rousseff", "Temer", "Bolsonaro"))
construction_time_color
# Maybe need to change colors a bit, but idea is there!
```

Plotting Amazon construction in time, without any normalization (the first two plot), appears to indicate that the frequencies for all constructions are rather consistent for the same years. That is, the frequencies in which the Amazon is constructed as different problems in time varies for across the years and for presidents, but within the same year presidents construct the Amazon as different issues with similar frequencies. Do all presidents construct the Amazon as diverse issues in rather consistent ways within the same year? Why then do we have variation in years? Could it be that the Amazon becomes a more important theme in some years than others?

Nevertheless, we do see some interesting patterns in time. For example, for Sarney and Collor it seems that the Amazon was constructed as an issue of conservation more than other constructions. This changes with Itamar who begins to focus on the Amazon as an issue of economic integration, this is accentuated for Cardoso. During the Silva years we see a switch from constructing the Amazon overwhelmingly as an issue of economic integration, in the first mandate, to focusing on conservation when talking about the Amazon by his second term. Rousseff constructs the Amazon mostly as an issue of social development. Temer appear to not mention the Amazon much in speeches, but keeps the focus on social development issues. Finally, for Bolsonaro, the Amazon is constructed as an issue of sovereignty and conservation.

```{r}
# Let's create a normalizing variable
# Say we will use the number of characters for all speeches in the large dataset for that year.
BR_presid_speeches_final <- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
normalization <- BR_presid_speeches_final %>% 
  select(c(text, year, president)) %>%
  mutate(char = nchar(text)) %>% 
  select(-text) %>% 
  group_by(year, president) %>% 
  summarize(across(everything(), sum)) %>% 
  mutate(char = char/10000) %>% 
  arrange(year)
time_long_norm <- final_data_as %>% 
  mutate(sov = as.numeric(sov), EI = as.numeric(EI),
         SD = as.numeric(SD), con = as.numeric(con), other = as.numeric(other)) %>% 
  select(-c(ID, party, title, location, date, text, AM2, false_positives, hand_coded, location_cat)) %>%
  group_by(president, year) %>% 
  summarize(across(everything(), sum)) %>% 
  arrange(year)
time_long_norm$char <- normalization$char
time_long_norm <- time_long_norm %>% 
  mutate(sov = sov/char,
         EI = EI/char,
         SD = SD/char,
         con = con/char) %>% 
  select(-c(char, other)) %>% 
  tidyr::pivot_longer(sov:con, "Construction")
construction_time_norm <- ggplot(time_long_norm, aes(x = year, y = value, fill = Construction)) +
  geom_line(aes(group = Construction, color = Construction), size = 0.5) +
  labs(x = "",
       y = "",
       title = "How the Amazon has been constructed as a problem in time?",
       subtitle = "Normalized by the number of characters in all speeches for respective year") +
  theme_classic()
construction_time_norm
# This changes things a bit!
# Let's add some colors as before
construction_time_norm_color <- construction_time_norm +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = -Inf, ymax = Inf, alpha = 0.2,
           color = c("blue", "green", "yellow", "cyan", "red", "purple", "brown", "grey"),
           fill = c("blue", "green", "yellow", "cyan", "red", "purple", "brown", "grey")) +
  annotate(geom = "text", x = hp$label, y = 2, angle = 90, alpha = 0.4, hjust = "left",
           label =  c("Sarney", "Collor", "Franco", "Cardoso", "Silva", "Rousseff", "Temer", "Bolsonaro"))
construction_time_norm_color
```

Now things have changed a bit. We see that when normalized for all the characters in all speeches by a president for a respective year, we see huge increases in the proportion in which the Amazon was constructed as problem by presidents for Sarney, Collor/Franco and Bolsonaro. Sarney was the first democratic (elected indirectly) president after the military dictatorship and it was during his administrations that the fires at the Amazon forest made international news. Collor was president of Brazil during the Rio climate conference in 1992, but was impeached that year. Franco, the vice president for Collor, took over at the was president of Brazil at the end of 1992. From 1992 onward, it appears that the Amazon became a less crucial topic in presidential discourse.

## Amazon as a problem by speaker

```{r}
# Let's get a table by president normalized
president <- time_long_norm %>%
  group_by(president, Construction) %>% 
  summarise(value = sum(value))
# Normalize by years in power
president$value_norm <- ifelse(president$president == "Bolsonaro", president$value/3, president$value)
president$value_norm <- ifelse(president$president == "Temer", president$value/2.5, president$value_norm)
president$value_norm <- ifelse(president$president == "Dilma", president$value/5.5, president$value_norm)
president$value_norm <- ifelse(president$president == "Lula", president$value/8, president$value_norm)
president$value_norm <- ifelse(president$president == "FHC", president$value/8, president$value_norm)
president$value_norm <- ifelse(president$president == "Itamar", president$value/2, president$value_norm)
president$value_norm <- ifelse(president$president == "Collor", president$value/2, president$value_norm)
president$value_norm <- ifelse(president$president == "Sarney", president$value/5, president$value_norm)
# Let's get the order right
president$order <- ifelse(president$president == "Bolsonaro", 1, 0)
president$order <- ifelse(president$president == "Temer", 2, president$order)
president$order <- ifelse(president$president == "Dilma", 3, president$order)
president$order <- ifelse(president$president == "Lula", 4, president$order)
president$order <- ifelse(president$president == "FHC", 5, president$order)
president$order <- ifelse(president$president == "Itamar", 6, president$order)
president$order <- ifelse(president$president == "Collor", 7, president$order)
president$order <- ifelse(president$president == "Sarney", 8, president$order)
# Let's get a filled bar plot
presid_construction <- ggplot(president, aes(reorder(president, -order), value, fill = Construction)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_text(aes(label = round(value, 1)), vjust = 1, hjust = 1.2, position = "stack") +
  labs(x = "President",
       y = "Value (normalized)",
       title = "How the Amazon has been constructed as a problem by presidents?",
       subtitle = "Normalized by the number of characters in all speeches for respective year and time in power") +
  theme_classic() +
  coord_flip()
presid_construction
```

At first site, this tells us a story that is consistent with the graphs above that most presidents are fairly consistent in using several constructions to talk about the Amazon in similar frequencies. However, this figure tells us something interesting about which presidents proportionally talked more about the Amazon as a problem in speeches, that is Sarney, Cardoso, and Bolsonaro. We see that for Sarney the Amazon was overwhelmingly and issue of both conservation and economic development while for Cardoso the Amazon is constructed mostly as an issue of economic integration. For Bolsonaro, issues of conservation, economic development, and sovereignty are the most salient constructions with social development much behind.

## Amazon as a problem by location

```{r}
location <- final_data_as %>% 
  mutate(sov = as.numeric(sov), EI = as.numeric(EI),
         SD = as.numeric(SD), con = as.numeric(con)) %>% 
  select(-c(president, ID, party, title, location, date, text, AM2, false_positives, hand_coded, other)) %>%
  group_by(year, location_cat) %>% 
  summarize(across(everything(), sum)) %>%
  tidyr::pivot_longer(sov:con, "Construction")
# plot
location_time <- ggplot(location, aes(x = year, y = value, fill = location_cat)) +
  geom_smooth(aes(group = location_cat, color = location_cat), size = 1, se = FALSE) +
  facet_wrap(~ Construction, ncol = 1) +
  labs(x = "",
       y = "",
       title = "How the Amazon has been constructed as a problem across locations?") +
  theme_classic()
location_time
# Maybe the oposite is better
location_time_reverse <- ggplot(location, aes(x = year, y = value, fill = Construction)) +
  geom_smooth(aes(group = Construction, color = Construction), size = 1, se = FALSE) +
  facet_wrap(~ location_cat, ncol = 1) +
  labs(x = "",
       y = "",
       title = "How the Amazon has been constructed as a problem across locations?") +
  theme_classic()
location_time_reverse
```

Consistency is the right word here... Not much to say though before it is normilized...

## A bit of modelling, just in case

```{r}
# load package
library(plm)
library(stargazer)
# get data
model_norm <- final_data_as %>% 
  mutate(sov = as.numeric(sov), EI = as.numeric(EI),
         SD = as.numeric(SD), con = as.numeric(con), other = as.numeric(other)) %>% 
  select(-c(ID, party, title, location, date, text, AM2, false_positives, hand_coded)) %>%
  group_by(president, year, location_cat) %>% 
  summarize(across(everything(), sum)) %>% 
  arrange(year)
normalization_model <- BR_presid_speeches_final %>% 
  select(c(text, year, president, location_cat)) %>%
  mutate(char = nchar(text)) %>% 
  select(-text) %>% 
  group_by(year, president, location_cat) %>% 
  summarize(across(everything(), sum)) %>% 
  mutate(char = char/10000) %>% 
  arrange(year)
model_norm <- dplyr::left_join(model_norm, normalization_model, by = c("year", "president", "location_cat"))
model_norm <- model_norm %>% 
  mutate(sov = sov/char,
         EI = EI/char,
         SD = SD/char,
         con = con/char) %>% 
  select(-c(char, other)) %>% 
  tidyr::pivot_longer(sov:con, "Construction")

model_po <- plm(value ~ as.factor(president) + as.factor(location_cat) + as.factor(Construction),
                data = model_norm, model = "pooling", index = "year")
summary(model_po)
# model_re <- plm(value ~ as.factor(president) + as.factor(location_cat) + as.factor(Construction),
#                 data = model_norm, model = "random", index = "year")
# summary(model_re) # not working for some reason
# model_fe <- plm(value ~ as.factor(president) + as.factor(location_cat) + as.factor(Construction),
#                 data = model_norm, model = "within", index = "year")
# summary(model_fe)
stargazer::stargazer(model_po, type = "text", align=TRUE)
```

So, location matters more than construction and president in many ways?!?

### 2022-03-28 analysis/analysis_livio.Rmd

---
title: "How has the Amazon been construed as a problem? Preliminary Analysis"
author: "Livio Silva-Muller"
date: "March 2022"
output:
  html_document: default
  pdf_document: default
---

## Setup, Data, Inspection

```{r setup, include=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(nnet)

Sys.setlocale("LC_ALL", "C")

options(stringsAsFactors = FALSE, scipen = 999)

cbPalette <- c("#999999", "#56B4E9", "#0072B2", "#009E73", "#F0E442", "#D55E00", "#CC79A7", "#E69F00")
```

```{r data, include=FALSE, warning=FALSE, message=FALSE}

pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")

ama <-  ama %>%
          select(-c(title, date, text, false_positives)) %>%
          rename (ei= "EI") %>%
          rename (sd= "SD")

pop <-  pop %>%
          select(-c(title, date, text, location))

```

```{r data prep for prob_construction, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)

ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)

sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)

con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)

other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)

temp <- ei %>% left_join(other) %>% 
                left_join(con) %>%
                left_join(sd) %>%
                left_join(sov) %>%
                replace(is.na(.), 0)

```

```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ama_mx <- ama %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat= case_when (mixed_type=='1_0_0_0' ~ "Pure Sovereignty",
                            mixed_type=='0_1_0_0' ~ "Pure Economic Integration",
                            mixed_type=='0_0_1_0' ~ "Pure Social Development",
                            mixed_type=='0_0_0_1' ~ "Pure Conservation",
                            mixed_type=='0_0_0_0' ~"Other",
                            mixed_type=='0_1_0_1' ~"Economic Conservation",
                            mixed_type=='0_1_1_0' ~"Economic and Social Development",
                            mixed_type=='1_0_0_1' ~"Sovereign Conservation",
                            mixed_type=='0_1_1_1' ~ "Sustainable Development",
                            mixed_type=='1_1_0_0'~ "Sovereign Integration",
                            mixed_type=='0_0_1_1' ~"Other Mixed-types",
                            mixed_type=='1_1_0_1' ~"Other Mixed-types",
                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
                            mixed_type=='1_1_1_1' ~"Other Mixed-types",
                            mixed_type=='1_1_1_0' ~"Other Mixed-types",
                            mixed_type=='1_0_1_1' ~"Other Mixed-types"))%>%
  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Other Mixed-types")))

```

```{r data prep for model 2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sov2 <- ama %>% 
  filter(sov==1) %>%
  select(c(sov, location_cat, year))%>%
  mutate(prob_constr=case_when(sov=="1"~ "sov")) %>%
  select(-c(sov))

ei2 <- ama %>% 
  filter(ei==1)%>%
  select(c(ei, location_cat, year))%>%
  mutate(prob_constr=case_when(ei=="1"~ "ei")) %>%
  select(-c(ei))

sd2 <- ama %>% 
  filter(sd==1)%>%
  select(c(sd, location_cat, year))%>%
  mutate(prob_constr=case_when(sd=="1"~ "sd")) %>%
  select(-c(sd))

con2 <- ama %>% 
  filter(con==1)%>%
  select(c(con, location_cat, year))%>%
  mutate(prob_constr=case_when(con=="1"~ "con")) %>%
  select(-c(con))

other2 <- ama %>% 
  filter(other==1)%>%
  select(c(other, location_cat, year))%>%
  mutate(prob_constr=case_when(other=="1"~ "other")) %>%
  select(-c(other))

temp2 <- rbind(sov2, con2, ei2, sd2, other2)

temp2$prob_constr <- as.factor (temp2$prob_constr)

```

```{r inspecting the data, eval=FALSE, include=FALSE}

ama %>% filter(hand_coded==0) %>% filter(sov==1) %>% select(AM2, ID) %>% sample_n(10) %>% kable()

```

## I Amazonian speeches in time, geographic location, and speaker

Question: does the incidence of Amazon differ by year and location?

Logic: compare proportion of speeches mentioning Amazon versus not mentioning it, here proportions add to 1; quite some granularity in possible categories, we either plot separately or we regress.

Normalization: yearly proportion of speeches mentioning Amazon

Take on results:

Plot 1: Interesting variation in incidence of Amazon in speeches overtime that can be easily fitted in a narrative about (1) indigenous and environmental turn in the upcoming deliberative processes related to the 1988 constitution; (2) Earth Summit in 1992; (3) substantial decreases of deforestation in late 2000s; and finally (4) substantial increase in fires and deforestation in late 2010s. This would some story-telling, but nice broad way to open analysis chapter, we add the events to the plot and discuss in relation to policies.

Plot 2: From what I see, there's not that much variation in the incidence of Amazon by speaker. Interesting that the president that mentioned it the least is Temer, right before the one that mentioned it the most. Generally, I do not see anything really interesting to engage with. Generally, I find 'by president' arguments not that interesting for this piece.

Plot 3: Some variation in incidence, but small. Location NAs seem to be biased (almost 10% more for Amazonian speeches), this could change things meaningfully, we should identify location for them. If we remove NAs and do the analysis, the Amazon appears more often in speeches in Amazonian states (obvious). All the other differences are too small to interpret in my opinion.

I would only keep plot 1 from this three and check if plot 3 changes once we correct the location NAs.

```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}

perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))

pop %>% count(amazon_speech, year) %>%
  group_by(year) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1) %>%
  ggplot(., aes(x = year, y = perc)) +
  geom_line(color="darkolivegreen")+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Plot1: Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```

```{r Amazonian speeches by president, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

perc2 <- pop %>%
  count(amazon_speech, president)%>%
  group_by(president)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, president))

pop %>% count(amazon_speech, president) %>%
  group_by(president) %>%
  left_join(perc2) %>%
  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(., aes(x = president, y = perc, fill=as.factor(amazon_speech), label= scales::percent(perc))) +
  geom_bar(stat="identity", position = "stack")+
  geom_text(size = 2.5, position = position_stack(),
    vjust = 1.5)+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Plot 2: Share of speeches mentioning the Amazon by president",
    subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```

```{r Amazonian speeches by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

perc3 <- pop %>%
  filter(location_cat != "Non Identified") %>%
  count(amazon_speech, location_cat)%>%
  group_by(amazon_speech)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, location_cat))

pop %>% 
  filter(location_cat != "Non Identified") %>%
  count(amazon_speech, location_cat) %>%
  group_by(amazon_speech) %>%
  left_join(perc3) %>%
  ggplot(., aes(x = location_cat, y = perc, fill=location_cat, label= scales::percent(perc))) +
  geom_bar(stat="identity", position = "dodge")+
  geom_text(size = 3.5, position = position_dodge(width = 1),
    vjust = 1.5)+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Plot 3: Share of speeches mentioning the Amazon by president",
    subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )+
  facet_wrap(~as.factor(amazon_speech), ncol=2)

```

## II Incidence of problem construction in time

Question: do specific problem constructions get more salient over time?

Logic: compare yearly counts of problem construction in time;

Normalization: here I changed the unit of analysis from amazonian statements to problem construction, this means we have 2400 observations (see temp), I normalize by taking the proportion of each problem construction from yearly total.

Take on results: Plot 4 is more promising, there is some nice variation. Generally, the more salient problem-constructions are economic integration and conservation. While the former piked in the late 1998 (also when deforestation was high) and then started to decrease, the latter was more salient in the up-coming of the Earth Summit and remained fairly stable. Social development starts gaining more prominence with the PT government despite an unusually high year in 1992. Sovereignty, which remained fairly stable over time, is making a come-back in the late 2010, more prominently with the presidency of Jair Bolsonaro.

Given the results presented in the pure categories of the mixed-types section, it seems like we can basically subsume this analysis in the next section.

```{r problem construction in time I, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

temp %>%
  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  mutate(problem_construction=factor(problem_construction, levels = c("sov", "ei", "sd", "con", "other"))) %>%
  ggplot(., aes(x=year, y=perc, fill=problem_construction))+
  geom_bar(stat="identity", position="dodge")+
  geom_smooth(color="black", size=.3, se= FALSE)+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Plot 4: Problem-construction over time",
    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )+
  facet_wrap(~ problem_construction, ncol=2)

```

```{r problem construction in time II, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

temp %>%
  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  ggplot(., aes(x=year, y=perc, fill=problem_construction, label=percent(perc, accuracy=.1)))+
  geom_bar(stat="identity", position="stack")+
  geom_text(size = 2, position = position_stack(vjust=.5))+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )

```

```{r problem construction in time III, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

temp %>%
  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
  ggplot(aes(x=year, y=n, fill=problem_construction))+
  geom_bar(stat="identity", position="dodge")+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )+
  facet_wrap(~ problem_construction, ncol=2)

```

## III Mixed types: more complex problems?

Question: do specific combinations characterize specific presidents? Do we see the emergence of new combinations along time?

Logic: compare proportion of yearly mixed_types in time; here proportions add to 1 because the unit of analysis is each amazonian statement unique combination of our four main codes.

From exploration plot, I conceptualize the following categories, which are the most frequent out of the 16 distinct types identified in the data (stored as mx_cat):

(1) pure-types: each one of 1000,0100,0010,0001 separately
(2) other: 0000
(3) Economic Conservation: 0101
(4) Economic & Social Development:0110
(5) Sovereign Conservation: 1001
(6) Sovereign Integration: 1100
(7) Sustainable Development:0111
(8) other mixed_types: all other combinations

Normalization: proportions of mixed_types

Take on results: Plot 5 and 6 contain some interesting things as well, but small proportions mixed_types might be something reviewers criticize. For Plot 6, I removed pure types and others so we have a more targeted analysis of the mixed_types presidents deploy despite low counts.

First, pure-types dominate and presidents tend not to mix much. We are not looking at pure-types this way in the previous analysis since the unit changed. Lula and Bolsonaro, interestingly, are the ones that have the highest shares of mixes among their problem-construction.

Second, we do observe a decrease economic integration related mixed-types and a parallel increase in conservation related mixed-types between 2000-2010, when strong policies to reduce deforestation were adopted. Specifically, complex problem-construction framing the Amazon as sustainable development came about in the 20000 reaching a local maximum in the early 2010s and decreasing afterwards. This

Finally, given that Lula and Bolsonaro uses more mixed-types, let's take a closer look. It is clear that Bolsonaro mixes sovereignty with other things more than others (Sovereign Integration, Sovereign Conservation, and pure-type sov pike with him). WHile conservation does appear alone in about 19% of Bolsonaro's speeches, all other times it appears it is always relativized by adding another problem-construction in parallel.This might be a good door to open up a more word-based look at this problem-construction around sovereignty. On the other hand, we observe the opposite with Lula.While pure sovereignty accounts for about 22.3% of Bolsonaros' statements, it's only 3.6% of Lula's. Lula's favorite mix ingredient seems to be conservation (Economic conservation, Sovereign Conservation, Sustainable Development, and pure conservation pike with him), but when he uses pure-types, economic integration dominates with about 25% of incidence.

I would make this a subsection of analysis, probably the last one, framing as the main "mixers" (they mix more than others) so we can speak only about bolsonaro versus lula.

```{r mixed-types exploration, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ama_mx %>%
  count(mixed_type)%>%
  ggplot(aes(x=reorder(mixed_type,-n), y=n, fill=mixed_type))+
  geom_bar(stat = "identity", position = "dodge")+
    labs(
    x = "", y = "", title ="Exploration Plot",
    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```

```{r mixed-types exploration II, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ama_mx %>%
  count(mx_cat)%>%
  ggplot(aes(x=reorder(mx_cat,-n), y=n, fill=mx_cat))+
  geom_bar(stat = "identity", position = "dodge")+
    labs(
    x = "", y = "", title ="Exploration Plot II",
    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```

```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

ama_mx %>%
  count(year, mx_cat)%>%
  group_by(year) %>%
  mutate(perc=n / sum(n))  %>%
  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
  geom_bar(stat="identity", position="dodge")+
  geom_smooth(color="black", size=.3, se= FALSE)+
  labs(
    x = "", y = "", title ="Plot 5: Mixed-types evolution overtime",
    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "none"
  )+
  facet_wrap(~ mx_cat, ncol=2, scales="free_y")

```

```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

ama_mx %>%
  filter(mx_cat !="Pure Types")%>%
  filter(mx_cat !="Other")%>%
  count(president, mx_cat)%>%
  group_by(president) %>%
  mutate(perc=n / sum(n)) %>%
  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
  geom_bar(stat="identity", position="stack")+
  geom_text(size = 3.5, position = position_stack(vjust=.5))+
  labs(
    x = "", y = "", title ="Plot 6: Mixed-types by President",
    subtitle = "Sample composed by 431 problem-constructions in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )
```

## IV Amazonian problem-construction in time, geographic location, and speaker

Question: do specific problem constructions differ by geographical location, speaker, and year?

Logic: see what better predicts problem constructions and mixed_types: location, speaker, year. This can be done with a multinominal logistic regression. We should add a few controls to this eventually (deforestation rates, gdp growth, approval rates, election year dummy, party affiliation/ideology), the problem is timing the variables properly.

take on results:

m1 -> not so parsimonious because of multiple mixes,  but some of the interesting significant results are
(1) pure conservation is less likely to appear in amazonian states*** and in Brazil** ; 
(2) pure social development is more likely to appear in Brazil**;
(3) pure economic integration appears more frequently in Brazil**;
(4) pure sovereignty appears more frequently in Amazonian states **.
(5) nothing very particular in mixed-types...

m2 -> this is a better model, more parsimonious. Interesting significant findings are

(1) conservation is more likely outside of Brazil and outside of amazon states (both **); -> cool,the more distanced from the Amazon, the more they highlight conservational problem.
(2) Economic integration is more likely outside of Brazil***;
(3) sovereignty is more likely outside of amazon states**.

In theory model improvement might help us finding significant coefficients for the relationships we are interested at. I think the findings of m1 related to conservation are particularly interesting, we could keep them somehow.I suppose we can include something en passant in the second sub-section of analysis that looks into problem construction overtime ( II of this document), like Kentikellenis does.

If we take a more bayesian approach, we can ignore significance and work more

### Model 1 w/ mx_cat as i.V.

i.Vs: mx_cat as i.V. for now it contains 11 levels, other is our base (unit of analysis remain each one of our 1885 Amazonian statements)

d.Vs: location_cat is to granular, for a more parsimonious model, I created two geographical dummies (amazon_state and Brazil)

```{r model 1 mx_cat as i.V., echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

ama_mx <- ama_mx %>%
    mutate(amazon_state= case_when (location_cat=='Amazonian States' ~ "Yes",
                            location_cat=='Brasilia' ~ "No",
                            location_cat=='International' ~ "No",
                            location_cat=='Non Amazonian States' ~ "No",
                            location_cat=='Non Identified' ~ "No"))%>%
    mutate(brazil= case_when (location_cat=='Amazonian States' ~ "Yes",
                            location_cat=='Brasilia' ~ "Yes",
                            location_cat=='International' ~ "No",
                            location_cat=='Non Amazonian States' ~ "Yes",
                            location_cat=='Non Identified' ~ "No"))

ama_mx$mx_cat <- relevel(ama_mx$mx_cat, ref = "Other")

m1 <- multinom(mx_cat ~ brazil + amazon_state, data = ama_mx)

z_m1 <- summary(m1)$coefficients/summary(m1)$standard.errors
p_m1 <- (1 - pnorm(abs(z_m1), 0, 1)) * 2

summary(m1)

p_m1

exp(coef(m1))

```

### Model 2 w/ problem_construction as i.V.

i.Vs: problem_construction as i.V., contains 5 levels so more parsimonious model, other as base; here unit of analysis are instances of problem_construction (n=2400)

d.Vs: location_cat is to granular, for a more parsimonious model, I created two geographical dummies (amazon_state and Brazil)

```{r model 2 prob_constr as i.V., echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

temp2 <- temp2 %>%
    mutate(amazon_state= case_when (location_cat=='Amazonian States' ~ "Yes",
                            location_cat=='Brasilia' ~ "No",
                            location_cat=='International' ~ "No",
                            location_cat=='Non Amazonian States' ~ "No",
                            location_cat=='Non Identified' ~ "No"))%>%
    mutate(brazil= case_when (location_cat=='Amazonian States' ~ "Yes",
                            location_cat=='Brasilia' ~ "Yes",
                            location_cat=='International' ~ "No",
                            location_cat=='Non Amazonian States' ~ "Yes",
                            location_cat=='Non Identified' ~ "No"))

temp2$prob_constr <- relevel(temp2$prob_constr, ref = "other")

m2 <- multinom(prob_constr ~ amazon_state + brazil, data = temp2)

z_m2 <- summary(m2)$coefficients/summary(m2)$standard.errors
p_m2 <- (1 - pnorm(abs(z_m2), 0, 1)) * 2

summary(m2)

exp(coef(m2))

p_m2

```

### 2022-03-29 analysis/analysis_livio.Rmd
#new_preliminary_plots

@@
                             mixed_type=='1_1_0_0'~ "Sovereign Integration",
-                            mixed_type=='0_0_1_1' ~"Other Mixed-types",
+                            mixed_type=='0_0_1_1' ~"Social Conservation",
                             mixed_type=='1_1_0_1' ~"Other Mixed-types",
@@
                             mixed_type=='1_0_1_1' ~"Other Mixed-types"))%>%
-  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Other Mixed-types")))
+  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Social Conservation", "Other Mixed-types"))) %>%
+mutate(mx_cat2= case_when (mixed_type=='1_0_0_0' ~ "Pure-type",
+                            mixed_type=='0_1_0_0' ~ "Pure-type",
+                            mixed_type=='0_0_1_0' ~ "Pure-type",
+                            mixed_type=='0_0_0_1' ~ "Pure-type",
+                            mixed_type=='0_0_0_0' ~"Other",
+                            mixed_type=='0_1_0_1' ~"Mixed-type",
+                            mixed_type=='0_1_1_0' ~"Mixed-type",
+                            mixed_type=='1_0_0_1' ~"Mixed-type",
+                            mixed_type=='0_1_1_1' ~ "Mixed-type",
+                            mixed_type=='1_1_0_0'~ "Mixed-type",
+                            mixed_type=='0_0_1_1' ~"Mixed-type",
+                            mixed_type=='1_1_0_1' ~"Mixed-type",
+                            mixed_type=='1_0_1_0' ~"Mixed-type",
+                            mixed_type=='1_0_1_0' ~"Mixed-type",
+                            mixed_type=='1_1_1_1' ~"Mixed-type",
+                            mixed_type=='1_1_1_0' ~"Mixed-type",
+                            mixed_type=='1_0_1_1' ~"Mixed-type"))
 
@@
 
-```{r Amazonian speeches by president, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r Amazonian speeches by president, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
 
@@
 
-```{r Amazonian speeches by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r Amazonian speeches by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
 
@@
 
-```{r mixed-types exploration II, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+```{r mixed-types exploration II, eval=FALSE, message=FALSE, warning=FALSE, include=FAlSE, paged.print=FALSE}
 
@@
   geom_bar(stat="identity", position="stack")+
-  geom_text(size = 3.5, position = position_stack(vjust=.5))+
+  geom_text(size = 2.5, position = position_stack(vjust=.5))+
   labs(
@@
   )
+```
+
+```{r pure types versus mixed-types , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+ama_mx %>%
+  count(president, mx_cat2)%>%
+  group_by(president) %>%
+  mutate(perc=n / sum(n)) %>%
+  filter(mx_cat2 !="Other")%>%
+  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(., aes(x=president, y=perc, fill=mx_cat2,label= scales::percent(perc, accuracy=.1)))+
+  geom_bar(stat="identity", position="stack")+
+  geom_text(size = 2.5, position = position_stack(vjust=.5))+
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
+  labs(
+    x = "", y = "", title ="Plot 7: Mixed-types verus Pure-types",
+    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+    caption = "") +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "bottom"
+  )
+
+```
+
+```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+ama_mx %>%
+  count(president, mx_cat, mx_cat2)%>%
+  group_by(president) %>%
+  mutate(perc=n / sum(n)) %>%
+  filter(mx_cat !="Other")%>%
+  filter(mx_cat2 == "Pure-type") %>%
+  mutate(year= case_when (president=='Sarney' ~ "1985",
+                          president=='Bolsonaro' ~ "2018",
+                          president=='Collor' ~ "1990",
+                          president=='Itamar' ~ "1993",
+                          president=='FHC' ~ "1994",
+                          president=='Lula' ~ "2003",
+                          president=='Dilma' ~ "2011",
+                          president=='Temer' ~ "2017"))%>%
+  ggplot(., aes(x=as.numeric(year), y=perc, color=mx_cat))+
+  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5)+
+  labs(
+    x = "", y = "", title ="Plot 8: Pure-types in time",
+    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+    caption = "") +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "bottom"
+  )
+
 ```

### 2022-03-30 analysis/analysis_livio.Rmd
#preliminary plots for text

@@
   labs(
-    x = "", y = "", title ="Plot 5: Mixed-types evolution overtime",
+    x = "", y = "", title ="Plot 5: Problem-construction evolution in time",
     subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
@@
   )+
-  facet_wrap(~ mx_cat, ncol=2, scales="free_y")
+  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
 
@@
   geom_bar(stat="identity", position="stack")+
-  geom_text(size = 2.5, position = position_stack(vjust=.5))+
+  geom_text(size = 3, position = position_stack(vjust=.5))+
   labs(
     x = "", y = "", title ="Plot 6: Mixed-types by President",
-    subtitle = "Sample composed by 431 problem-constructions in presidential speeches since 1985",
+    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
     caption = "") +
@@
     plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
+    legend.position = "right"
   )
@@
   labs(
-    x = "", y = "", title ="Plot 7: Mixed-types verus Pure-types",
+    x = "", y = "", title ="Plot 7: Mixed-types verus pure-types by presidents",
     subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",

### 2022-03-30 analysis/analysis_livio.Rmd
#preliminary plots for text

@@
   labs(
-    x = "", y = "", title ="Plot 5: Problem-construction evolution in time",
+    x = "", y = "", title ="Plot 5: Mixed-types evolution overtime",
     subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
@@
   )+
-  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
+  facet_wrap(~ mx_cat, ncol=2, scales="free_y")
 

### 2022-03-30 analysis/analysis_livio.Rmd
#correcting titles and axis

--- 2022-03-29 analysis/analysis_livio.Rmd
@@
   labs(
-    x = "", y = "", title ="Plot1: Share of speeches mentioning the Amazon by year",
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
     subtitle = "Sample composed by 6130 presidential speeches since 1985",
@@
   labs(
-    x = "", y = "", title ="Plot 2: Share of speeches mentioning the Amazon by president",
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
     subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
@@
   labs(
-    x = "", y = "", title ="Plot 3: Share of speeches mentioning the Amazon by president",
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
     subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
@@
   labs(
-    x = "", y = "", title ="Plot 4: Problem-construction over time",
+    x = "", y = "", title ="Problem-construction over time",
     subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
@@
   geom_smooth(color="black", size=.3, se= FALSE)+
+  scale_y_continuous(labels = percent_format(accuracy=1))+
   labs(
-    x = "", y = "", title ="Plot 5: Mixed-types evolution overtime",
+    x = "", y = "", title ="Share of different problem-constructions by year",
     subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
@@
   geom_bar(stat="identity", position="stack")+
-  geom_text(size = 2.5, position = position_stack(vjust=.5))+
+  geom_text(size = 3, position = position_stack(vjust=.5))+
   labs(
-    x = "", y = "", title ="Plot 6: Mixed-types by President",
-    subtitle = "Sample composed by 431 problem-constructions in presidential speeches since 1985",
+    x = "", y = "", title ="Share of different problem-construction by president",
+    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
     caption = "") +
@@
 
-```{r pure types versus mixed-types , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r pure types versus mixed-types , echo=FALSE, message=FALSE, warning=FALSE,include=FALSE, paged.print=FALSE}
 
@@
   labs(
-    x = "", y = "", title ="Plot 7: Mixed-types verus Pure-types",
+    x = "", y = "", title ="Share of Mixed types verus pure types by presidents",
     subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
@@
   geom_smooth(aes(color=mx_cat), se=FALSE, size=.5)+
+  scale_y_continuous(labels = percent_format(accuracy=1))+
   labs(
-    x = "", y = "", title ="Plot 8: Pure-types in time",
+    x = "", y = "", title ="Share of each pure types by year",
     subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",

### 2022-04-01 analysis/analysis_livio.Rmd

@@
 ama_mx %>%
-  filter(mx_cat !="Pure Types")%>%
-  filter(mx_cat !="Other")%>%
+  filter(mx_cat2 =="Mixed-type")%>%
   count(president, mx_cat)%>%
@@
   geom_text(size = 3, position = position_stack(vjust=.5))+
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
   labs(
-    x = "", y = "", title ="Share of different problem-construction by president",
-    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+    subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
     caption = "") +
@@
     plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
+    legend.position = "bottom"
   )
@@
   labs(
-    x = "", y = "", title ="Share of Mixed types verus pure types by presidents",
+    x = "", y = "", title ="Share of Mixed types versus pure types by presidents",
     subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",

### 2022-04-01 Full_draft_20220401.qmd
#qmddraft

---
title: "How has the Brazilian Amazon been construed as a problem? An Analysis of Presidential Speeches since 1985"
output: docx
author:
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]

date: "April 2022"
---

# 1 Introduction

# 2 Literature review and theoretical contribution: Amazonian policy-cycles, discourse, and problem-construction

## 2.1 Literature Review: sovereignty, economic integration, and conservation in the Brazilian Amazon

### 2.1.1 National sovereignty

### 2.1.2 Economic integration

### 2.1.3 Environmental conservation

### 2.1.4 Policy and discourse

## 2.2 Theoretical framework: problem-construction and presidential discourse

# 3 Research Design

## 3.1 Data and Modeling:  operationalizing Amazonian problem construction

## 3.2 Analysis: descriptive and inferential methods

# 4 How has the amazon been construed as a problem?

## 4.1 The rises and falls of the Amazon as a topic in presidential speeches

## 4.2 Amazonian problem-construction in time

## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside

# 5 Conclusion

# 6 References

### 2022-04-03 Draft_April_2022/Full_draft_20220401.qmd
#text_corrections

--- 2022-04-01 analysis/analysis_livio.Rmd
@@
 ---
-title: "How has the Amazon been construed as a problem? Preliminary Analysis"
-author: "Livio Silva-Muller"
-date: "March 2022"
-output:
-  html_document: default
-  pdf_document: default
+title: "How has the Brazilian Amazon been constructed as a problem? An analysis of presidential speeches since 1985"
+format:
+  docx:
+    toc: false
+    reference-doc: "template.docx"
+    section-numbers: true
+    highlight-style: github
+abstract: This paper ...
+output: docx
+author:
+- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
+- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+
+date: "April 2022"
+
 ---
-
-## Setup, Data, Inspection
-
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
 
-knitr::opts_chunk$set(echo = TRUE)
-
+knitr::opts_chunk$set(include = FALSE)
 library(tidyverse)
@@
 
-cbPalette <- c("#999999", "#56B4E9", "#0072B2", "#009E73", "#F0E442", "#D55E00", "#CC79A7", "#E69F00")
 ```
 
-```{r data, include=FALSE, warning=FALSE, message=FALSE}
+```{r data, message=FALSE, warning=FALSE, include=FALSE}
 
@@
 
-```{r data prep for prob_construction, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 
-```{r data prep for model 2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+# 1 Introduction
 
-sov2 <- ama %>% 
-  filter(sov==1) %>%
-  select(c(sov, location_cat, year))%>%
-  mutate(prob_constr=case_when(sov=="1"~ "sov")) %>%
-  select(-c(sov))
+# 2  Amazonian policy-cycles, discourse, and problem-construction
+## 2.1 Literature Review: policy-cycles in the Amazonian literature
 
-ei2 <- ama %>% 
-  filter(ei==1)%>%
-  select(c(ei, location_cat, year))%>%
-  mutate(prob_constr=case_when(ei=="1"~ "ei")) %>%
-  select(-c(ei))
+### 2.1.1 National sovereignty
 
-sd2 <- ama %>% 
-  filter(sd==1)%>%
-  select(c(sd, location_cat, year))%>%
-  mutate(prob_constr=case_when(sd=="1"~ "sd")) %>%
-  select(-c(sd))
+### 2.1.2 Economic integration
 
-con2 <- ama %>% 
-  filter(con==1)%>%
-  select(c(con, location_cat, year))%>%
-  mutate(prob_constr=case_when(con=="1"~ "con")) %>%
-  select(-c(con))
+### 2.1.3 Environmental conservation
 
-other2 <- ama %>% 
-  filter(other==1)%>%
-  select(c(other, location_cat, year))%>%
-  mutate(prob_constr=case_when(other=="1"~ "other")) %>%
-  select(-c(other))
+### 2.1.4 Policy and discourse
 
-temp2 <- rbind(sov2, con2, ei2, sd2, other2)
+## 2.2 Theoretical framework: problem-construction and presidential discourse
 
-temp2$prob_constr <- as.factor (temp2$prob_constr)
+# 3 Research Design
 
-```
+## 3.1 Data and modeling: operationalizing Amazonian problem construction
 
-```{r inspecting the data, eval=FALSE, include=FALSE}
+## 3.2 Analysis and limitations
 
-ama %>% filter(hand_coded==0) %>% filter(sov==1) %>% select(AM2, ID) %>% sample_n(10) %>% kable()
+# 4 How has the amazon been constructed as a problem?
 
-```
-
-## I Amazonian speeches in time, geographic location, and speaker
-
-Question: does the incidence of Amazon differ by year and location?
-
-Logic: compare proportion of speeches mentioning Amazon versus not mentioning it, here proportions add to 1; quite some granularity in possible categories, we either plot separately or we regress.
-
-Normalization: yearly proportion of speeches mentioning Amazon
-
-Take on results:
-
-Plot 1: Interesting variation in incidence of Amazon in speeches overtime that can be easily fitted in a narrative about (1) indigenous and environmental turn in the upcoming deliberative processes related to the 1988 constitution; (2) Earth Summit in 1992; (3) substantial decreases of deforestation in late 2000s; and finally (4) substantial increase in fires and deforestation in late 2010s.
-This would some story-telling, but nice broad way to open analysis chapter, we add the events to the plot and discuss in relation to policies.
-
-Plot 2: From what I see, there's not that much variation in the incidence of Amazon by speaker.
-Interesting that the president that mentioned it the least is Temer, right before the one that mentioned it the most.
-Generally, I do not see anything really interesting to engage with.
-Generally, I find 'by president' arguments not that interesting for this piece.
-
-Plot 3: Some variation in incidence, but small.
-Location NAs seem to be biased (almost 10% more for Amazonian speeches), this could change things meaningfully, we should identify location for them.
-If we remove NAs and do the analysis, the Amazon appears more often in speeches in Amazonian states (obvious).
-All the other differences are too small to interpret in my opinion.
-
-I would only keep plot 1 from this three and check if plot 3 changes once we correct the location NAs.
+## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
 
@@
 
-```{r Amazonian speeches by president, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
-
-perc2 <- pop %>%
-  count(amazon_speech, president)%>%
-  group_by(president)%>%
-  mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, president))
-
-pop %>% count(amazon_speech, president) %>%
-  group_by(president) %>%
-  left_join(perc2) %>%
-  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(., aes(x = president, y = perc, fill=as.factor(amazon_speech), label= scales::percent(perc))) +
-  geom_bar(stat="identity", position = "stack")+
-  geom_text(size = 2.5, position = position_stack(),
-    vjust = 1.5)+
-  scale_y_continuous(labels = percent_format())+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )
-
-```
-
-```{r Amazonian speeches by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
-
-perc3 <- pop %>%
-  filter(location_cat != "Non Identified") %>%
-  count(amazon_speech, location_cat)%>%
-  group_by(amazon_speech)%>%
-  mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, location_cat))
-
-pop %>% 
-  filter(location_cat != "Non Identified") %>%
-  count(amazon_speech, location_cat) %>%
-  group_by(amazon_speech) %>%
-  left_join(perc3) %>%
-  ggplot(., aes(x = location_cat, y = perc, fill=location_cat, label= scales::percent(perc))) +
-  geom_bar(stat="identity", position = "dodge")+
-  geom_text(size = 3.5, position = position_dodge(width = 1),
-    vjust = 1.5)+
-  scale_y_continuous(labels = percent_format())+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985; 1 means speech mentions Amazon",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    axis.text.x = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )+
-  facet_wrap(~as.factor(amazon_speech), ncol=2)
-
-```
-
-## II Incidence of problem construction in time
-
-Question: do specific problem constructions get more salient over time?
-
-Logic: compare yearly counts of problem construction in time;
-
-Normalization: here I changed the unit of analysis from amazonian statements to problem construction, this means we have 2400 observations (see temp), I normalize by taking the proportion of each problem construction from yearly total.
-
-Take on results: Plot 4 is more promising, there is some nice variation.
-Generally, the more salient problem-constructions are economic integration and conservation.
-While the former piked in the late 1998 (also when deforestation was high) and then started to decrease, the latter was more salient in the up-coming of the Earth Summit and remained fairly stable.
-Social development starts gaining more prominence with the PT government despite an unusually high year in 1992.
-Sovereignty, which remained fairly stable over time, is making a come-back in the late 2010, more prominently with the presidency of Jair Bolsonaro.
-
-Given the results presented in the pure categories of the mixed-types section, it seems like we can basically subsume this analysis in the next section.
-
-```{r problem construction in time I, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-temp %>%
-  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
-  group_by(year)%>%
-  mutate(perc=n / sum(n)) %>%
-  mutate(problem_construction=factor(problem_construction, levels = c("sov", "ei", "sd", "con", "other"))) %>%
-  ggplot(., aes(x=year, y=perc, fill=problem_construction))+
-  geom_bar(stat="identity", position="dodge")+
-  geom_smooth(color="black", size=.3, se= FALSE)+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Problem-construction over time",
-    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )+
-  facet_wrap(~ problem_construction, ncol=2)
-
-```
-
-```{r problem construction in time II, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-temp %>%
-  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
-  group_by(year)%>%
-  mutate(perc=n / sum(n)) %>%
-  ggplot(., aes(x=year, y=perc, fill=problem_construction, label=percent(perc, accuracy=.1)))+
-  geom_bar(stat="identity", position="stack")+
-  geom_text(size = 2, position = position_stack(vjust=.5))+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by president",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
-
-```
-
-```{r problem construction in time III, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-temp %>%
-  gather(key = "problem_construction", value = "n", ei, other, sd, con, sov)%>%
-  ggplot(aes(x=year, y=n, fill=problem_construction))+
-  geom_bar(stat="identity", position="dodge")+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )+
-  facet_wrap(~ problem_construction, ncol=2)
-
-```
-
-## III Mixed types: more complex problems?
-
-Question: do specific combinations characterize specific presidents? Do we see the emergence of new combinations along time?
-
-Logic: compare proportion of yearly mixed_types in time; here proportions add to 1 because the unit of analysis is each amazonian statement unique combination of our four main codes.
-
-From exploration plot, I conceptualize the following categories, which are the most frequent out of the 16 distinct types identified in the data (stored as mx_cat):
-
-(1) pure-types: each one of 1000,0100,0010,0001 separately
-(2) other: 0000
-(3) Economic Conservation: 0101
-(4) Economic & Social Development:0110
-(5) Sovereign Conservation: 1001
-(6) Sovereign Integration: 1100
-(7) Sustainable Development:0111
-(8) other mixed_types: all other combinations
-
-Normalization: proportions of mixed_types
-
-Take on results: Plot 5 and 6 contain some interesting things as well, but small proportions mixed_types might be something reviewers criticize.
-For Plot 6, I removed pure types and others so we have a more targeted analysis of the mixed_types presidents deploy despite low counts.
-
-First, pure-types dominate and presidents tend not to mix much.
-We are not looking at pure-types this way in the previous analysis since the unit changed.
-Lula and Bolsonaro, interestingly, are the ones that have the highest shares of mixes among their problem-construction.
-
-Second, we do observe a decrease economic integration related mixed-types and a parallel increase in conservation related mixed-types between 2000-2010, when strong policies to reduce deforestation were adopted.
-Specifically, complex problem-construction framing the Amazon as sustainable development came about in the 20000 reaching a local maximum in the early 2010s and decreasing afterwards.
-This
-
-Finally, given that Lula and Bolsonaro uses more mixed-types, let's take a closer look.
-It is clear that Bolsonaro mixes sovereignty with other things more than others (Sovereign Integration, Sovereign Conservation, and pure-type sov pike with him).
-WHile conservation does appear alone in about 19% of Bolsonaro's speeches, all other times it appears it is always relativized by adding another problem-construction in parallel.This might be a good door to open up a more word-based look at this problem-construction around sovereignty.
-On the other hand, we observe the opposite with Lula.While pure sovereignty accounts for about 22.3% of Bolsonaros' statements, it's only 3.6% of Lula's.
-Lula's favorite mix ingredient seems to be conservation (Economic conservation, Sovereign Conservation, Sustainable Development, and pure conservation pike with him), but when he uses pure-types, economic integration dominates with about 25% of incidence.
-
-I would make this a subsection of analysis, probably the last one, framing as the main "mixers" (they mix more than others) so we can speak only about bolsonaro versus lula.
-
-```{r mixed-types exploration, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-ama_mx %>%
-  count(mixed_type)%>%
-  ggplot(aes(x=reorder(mixed_type,-n), y=n, fill=mixed_type))+
-  geom_bar(stat = "identity", position = "dodge")+
-    labs(
-    x = "", y = "", title ="Exploration Plot",
-    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )
-
-```
-
-```{r mixed-types exploration II, eval=FALSE, message=FALSE, warning=FALSE, include=FAlSE, paged.print=FALSE}
-
-ama_mx %>%
-  count(mx_cat)%>%
-  ggplot(aes(x=reorder(mx_cat,-n), y=n, fill=mx_cat))+
-  geom_bar(stat = "identity", position = "dodge")+
-    labs(
-    x = "", y = "", title ="Exploration Plot II",
-    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    axis.text.x = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )
-
-```
+## 4.2 Amazonian problem-construction in time
 
@@
   facet_wrap(~ mx_cat, ncol=3, scales="free_y")
-
-```
-
-```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-ama_mx %>%
-  filter(mx_cat2 =="Mixed-type")%>%
-  count(president, mx_cat)%>%
-  group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
-  geom_bar(stat="identity", position="stack")+
-  geom_text(size = 3, position = position_stack(vjust=.5))+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
-  labs(
-    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
-    subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
-```
-
-```{r pure types versus mixed-types , echo=FALSE, message=FALSE, warning=FALSE,include=FALSE, paged.print=FALSE}
-
-ama_mx %>%
-  count(president, mx_cat2)%>%
-  group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  filter(mx_cat2 !="Other")%>%
-  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(., aes(x=president, y=perc, fill=mx_cat2,label= scales::percent(perc, accuracy=.1)))+
-  geom_bar(stat="identity", position="stack")+
-  geom_text(size = 2.5, position = position_stack(vjust=.5))+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of Mixed types versus pure types by presidents",
-    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
 
@@
 
-## IV Amazonian problem-construction in time, geographic location, and speaker
+```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
 
-Question: do specific problem constructions differ by geographical location, speaker, and year?
-
-Logic: see what better predicts problem constructions and mixed_types: location, speaker, year.
-This can be done with a multinominal logistic regression.
-We should add a few controls to this eventually (deforestation rates, gdp growth, approval rates, election year dummy, party affiliation/ideology), the problem is timing the variables properly.
-
-take on results:
-
-m1 -> not so parsimonious because of multiple mixes,  but some of the interesting significant results are
-(1) pure conservation is less likely to appear in amazonian states*** and in Brazil** ; 
-(2) pure social development is more likely to appear in Brazil**;
-(3) pure economic integration appears more frequently in Brazil**;
-(4) pure sovereignty appears more frequently in Amazonian states **.
-(5) nothing very particular in mixed-types...
-
-m2 -> this is a better model, more parsimonious. Interesting significant findings are
-
-(1) conservation is more likely outside of Brazil and outside of amazon states (both **); -> cool,the more distanced from the Amazon, the more they highlight conservational problem.
-(2) Economic integration is more likely outside of Brazil***;
-(3) sovereignty is more likely outside of amazon states**.
-
-In theory model improvement might help us finding significant coefficients for the relationships we are interested at.
-I think the findings of m1 related to conservation are particularly interesting, we could keep them somehow.I suppose we can include something en passant in the second sub-section of analysis that looks into problem construction overtime ( II of this document), like Kentikellenis does.
-
-If we take a more bayesian approach, we can ignore significance and work more
-
-### Model 1 w/ mx_cat as i.V.
-
-i.Vs: mx_cat as i.V. for now it contains 11 levels, other is our base (unit of analysis remain each one of our 1885 Amazonian statements)
-
-d.Vs: location_cat is to granular, for a more parsimonious model, I created two geographical dummies (amazon_state and Brazil)
-
-```{r model 1 mx_cat as i.V., echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-ama_mx <- ama_mx %>%
-    mutate(amazon_state= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "No",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "No",
-                            location_cat=='Non Identified' ~ "No"))%>%
-    mutate(brazil= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "Yes",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "Yes",
-                            location_cat=='Non Identified' ~ "No"))
-
-ama_mx$mx_cat <- relevel(ama_mx$mx_cat, ref = "Other")
-
-m1 <- multinom(mx_cat ~ brazil + amazon_state, data = ama_mx)
-
-z_m1 <- summary(m1)$coefficients/summary(m1)$standard.errors
-p_m1 <- (1 - pnorm(abs(z_m1), 0, 1)) * 2
-
-summary(m1)
-
-p_m1
-
-exp(coef(m1))
-
+ama_mx %>%
+  filter(mx_cat2 =="Mixed-type")%>%
+  count(president, mx_cat)%>%
+  group_by(president) %>%
+  mutate(perc=n / sum(n)) %>%
+  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
+  geom_bar(stat="identity", position="stack")+
+  geom_text(size = 3, position = position_stack(vjust=.5))+
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
+  labs(
+    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+    subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
+    caption = "") +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "bottom"
+  )
 ```
 
-### Model 2 w/ problem_construction as i.V.
+## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside
 
-i.Vs: problem_construction as i.V., contains 5 levels so more parsimonious model, other as base; here unit of analysis are instances of problem_construction (n=2400)
+# 5 Conclusion
 
-d.Vs: location_cat is to granular, for a more parsimonious model, I created two geographical dummies (amazon_state and Brazil)
-
-```{r model 2 prob_constr as i.V., echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
-
-temp2 <- temp2 %>%
-    mutate(amazon_state= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "No",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "No",
-                            location_cat=='Non Identified' ~ "No"))%>%
-    mutate(brazil= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "Yes",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "Yes",
-                            location_cat=='Non Identified' ~ "No"))
-
-temp2$prob_constr <- relevel(temp2$prob_constr, ref = "other")
-
-m2 <- multinom(prob_constr ~ amazon_state + brazil, data = temp2)
-
-z_m2 <- summary(m2)$coefficients/summary(m2)$standard.errors
-p_m2 <- (1 - pnorm(abs(z_m2), 0, 1)) * 2
-
-summary(m2)
-
-exp(coef(m2))
-
-p_m2
-
-```
+# 6 References

### 2022-04-03 Full_draft_20220401.qmd
#text_corrections

@@
 ---
-title: "How has the Brazilian Amazon been construed as a problem? An Analysis of Presidential Speeches since 1985"
+title: "How has the Brazilian Amazon been construed as a problem? An analysis of presidential speeches since 1985"
+format:
+  docx:
+    toc: false
+    section-numbers: true
+    highlight-style: github
 output: docx

### 2022-04-04 Draft_April_2022/Full_draft_20220401.qmd
Added modelling final file and a first attempt at the model

@@
 knitr::opts_chunk$set(include = FALSE)
-library(tidyverse)
+library(dplyr)
+library(ggplot2)
 library(tidyr)
@@
 library(nnet)
+library(stargazer)
 
@@
 
+```{r}
+ama_model <- ama %>% 
+  unite(mixed_type, sov:con, sep="_") %>%
+  mutate(mx_cat = as.factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
+                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
+                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
+                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
+                                      mixed_type == '0_0_0_0' ~ "Other",
+                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
+                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
+                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
+                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
+                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
+                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
+                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
+                                            mixed_type) ~ "Other Types"))) %>% 
+  mutate(mx_cat2 = case_when(!grepl("Pure Economic Integration|Pure Social Development|Pure Conservation|Pure Sovereignty|^Other$", mx_cat) ~ "Mixed Types"),
+         mx_cat2 = as.factor(ifelse(is.na(mx_cat2), paste0(mx_cat), mx_cat2)),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0)) %>% 
+  filter(location_cat != "Non Identified")  # remove the 3 obs
+# get deforestation yearly (year before) - load data and merge
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
+  rename(def_year = `area km²`)
+ama_model <- dplyr::left_join(ama_model, amazon_def_year, by = "year") # merge
+# inflation rates per year Brazil (average for year - but could be change)
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds") # source world bank
+ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
+# model
+model <- multinom(mx_cat2 ~ location_cat + election_year + def_year + AAI, data = ama_model)
+# get a nice table
+stargazer::stargazer(model, type="text", add.lines = nrow(model$residuals), title = "Amazon Contructions by Location",
+                     covariate.labels = c("Brasilia", "International", "Non-AM State",
+                                          "Election Year", "Deforastion (year)", "Avg. Inflation (year)"),
+                     column.labels = c("Other", "Conservation", "Economic Integration",
+                                       "Social Development", "Sovereignty"),
+                     dep.var.labels.include = FALSE)
+```
+
 # 5 Conclusion

### 2022-04-05 analysis/Modelling Final.Rmd
#cleaning folder

---
title: "Modelling"
output: html_document
date: '2022-04-01'
---

# The simple model

Below, we attempt to model the relationship between location (independent variable) to the Amazonian construction (dependent variable). At first, we use a simple multinomial model, since the DV is a non-ordered categorical variable, without any controls or normalization.

```{r}
# Load packages
library(dplyr)
library(tidyr)
library(kableExtra)
library(nnet)
library(plm)
library(readxl)
options(scipen=999)
# load Brazil data
pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
# Load Amazon context data
ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
# wrangle dataset
ama_model1 <-  ama %>% select(-c(title, date, text, false_positives)) %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = as.factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Types")))
# Model without any controls or normalization or time effects
model1 <- multinom(mx_cat ~ location_cat, data = ama_model1)
summary(model1)
# Get p-values
p_values1 <- round((1 - pnorm(abs(summary(model1)$coefficients/summary(model1)$standard.errors)))*2, 5)
p_values1 <- data.frame(ifelse(p_values1 < 0.05, paste0(p_values1, "** Coef (",round(summary(model1)$coefficients, 5), ")"),
                               p_values1))[,-1]
# Get a decent table
kableExtra::kable(x = p_values1, caption = "P values for Model 1",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio"))
#stargazer::stargazer(model1, type="text", add.lines = nrow(model1$residuals))
```

From this simple model, we notice some very interesting correlations. We notice, for example, that, in comparison to Amazonian States (reference category), pure conservation constructions are performed in Brasilia and on international settings with greater frequency. The same is true for pure sovereignty and sovereignty conservation constructions in Brasilia in relations to Amazonian States.

Let's add normalization and other control variables, such as yearly inflation level (economy), election year (binary), and yearly deforestation rates (for previous year) to the same model.

```{r}
ama_model2 <- ama_model1 %>% 
         mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0)) # election year
# deforestation yearly (year before) - load data and merge
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
  rename(def_year = `area km²`)
ama_model2 <- dplyr::left_join(ama_model2, amazon_def_year, by = "year") # merge
# inflation rates per year Brazil (average for year - but could be change)
average_inflation_year_BR <- read_excel("data/average_inflation_year_BR.xlsx") # source world bank
ama_model2 <- dplyr::left_join(ama_model2, average_inflation_year_BR, by = "year") # merge
# Model with some controls
model2 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model2)
summary(model2)
# Get p-values
p_values2 <- round((1 - pnorm(abs(summary(model2)$coefficients/summary(model2)$standard.errors)))*2, 5)
p_values2 <- data.frame(ifelse(p_values2 < 0.05, paste0(p_values2, "** Coef (",round(summary(model2)$coefficients, 5), ")"),
                               p_values2))[,-1]
# Get a decent table
kableExtra::kable(x = p_values2, caption = "P values for Model 2",
                  col.names = c("Brasilia", "International", "Non-AM State", "TV and Radio",
                                "Election_Year", "Deforastion_year", "Avg_inflation"))
```

Other interesting patterns arise when we control for election year, yearly deforestation rates, and average inflation per year. For example, pure conservation correlates positively with Brasilia and International locations in relation to Amazonian states, as well as correlates negatively with deforestation rates and positively with average inflation. Pure economic integration correlates positively with deforestation rates. Pure social development correlates negatively with International locations in comparison to Amazonian states and negatively with yearly deforestation rates. Pure sovereignty correlates positively with Brasilia and non-Amazonian states in relation to Amazonian states, as well as with positively election years, negatively with yearly deforestation rates, and positively with average inflation.

However, we do not know if these correlations are time specific (i.e. for a few specific election cycles). The issue here is, it does not seen that R has a function or package that handles time series mutinomial regressions (neither mlogit nor survival appear to handle well these types of data). We can we can do this for binary dependent variables, but not for multiple unordered (funny enough it appear that stata does handle these types of regression with "femlogit"). If we want to go Bayesian we can use the brms package to do this, but I am not sure this is the right approach judging by our audience. There is one, not great, way around this using the mgcv and the mixcat package in which we add the effects by hand and the odds are calculated separately for each category in regards to the reference (I tried but was not able to get it to work with our data). These approaches are not very easy to run or to understand. Let's try to run a simple ols, fixed, and random effects for each of the pure categories (as a dummy variable) and compare for now.

```{r}
ama_model3 <- ama_model2 %>% 
  mutate(pure_EI = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         pure_SD = ifelse(mx_cat == "Pure Social Development", 1, 0),
         pure_con = ifelse(mx_cat == "Pure Conservation", 1, 0),
         pure_sov = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
         pure_all = ifelse(grepl("Pure Economic Integration|Pure Social Development|Pure Conservation|Pure Sovereignty",
                                 mx_cat), 1, 0))
# OLS models
pure_EI_ols <- plm(pure_EI ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "pooling", index = "year")
pure_SD_ols <- plm(pure_SD ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "pooling", index = "year")
pure_con_ols <- plm(pure_con ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "pooling", index = "year")
pure_sov_ols <- plm(pure_sov ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "pooling", index = "year")
pure_all_ols <- plm(pure_all ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "pooling", index = "year")
# table
stargazer::stargazer(pure_EI_ols, pure_SD_ols, pure_con_ols, pure_sov_ols, pure_all_ols, type = "text",
                     title = "Pooled OLS for each Pure Type Amazonian Constructions in Time", align=TRUE)
# fixed effects
pure_EI_fe <- plm(pure_EI ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "within", index = "year")
pure_SD_fe <- plm(pure_SD ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "within", index = "year")
pure_con_fe <- plm(pure_con ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "within", index = "year")
pure_sov_fe <- plm(pure_sov ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "within", index = "year")
pure_all_fe <- plm(pure_all ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "within", index = "year")
# table
stargazer::stargazer(pure_EI_fe, pure_SD_fe, pure_con_fe, pure_sov_fe, pure_all_fe, type = "text",
                     title = "Fixed effects for each Pure Type Amazonian Constructions in Time", align=TRUE)
# Random effects
pure_EI_re <- plm(pure_EI ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "random", index = "year")
pure_SD_re <- plm(pure_SD ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "random", index = "year")
pure_con_re <- plm(pure_con ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "random", index = "year")
pure_sov_re <- plm(pure_sov ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "random", index = "year")
pure_all_re <- plm(pure_all ~ location_cat + election_year + def_year + AAI, data = ama_model3,
               model = "random", index = "year")
# table
stargazer::stargazer(pure_EI_re, pure_SD_re, pure_con_re, pure_sov_re, pure_all_re, type = "text",
                     title = "Random effects for each Pure Type Amazonian Constructions in Time", align=TRUE)
```

Though modelling is not perfect here, the question is: do we see similar significant correlations as the multinomila models above? Let's just assume for the purposes of the discussion that the OLS model is a better fit than others because it has the highest adjusted R squares. The pooled OLS method illustrates that pure conservation and pure sovereignty constructions correlate positively to Brasilia in relation to Amazonian states (reference category). Alternatively, pure economic integration and pure  social development correlate negatively to Brasilia in relation to Amazonian states. Pure social development correlate negatively to international settings while pure conservation correlate positively to international settings, in relations to Amazonian states. Pure sovereignty is correlate positively to election years. When it comes to deforestation rates, pure EI correlate positively with deforestation rates and correlate negatively to pure SD, conservation, and sovereignty. Finally, the average inflation per year correlate negatively with pure EI and positively pure conversation constructions.

These findings above are not all that different from model 2, even though model 2 is run with several other mixed types. This might indicate that time effects are not as significant and we can proceed with a multinomial model, for now.

Let us just try one last multinomial model, using only the pure types, one category for all mixed types, and a category for other.

```{r}
ama_model4 <- ama_model2 %>% 
  mutate(mx_cat2 = case_when(!grepl("Pure Economic Integration|Pure Social Development|Pure Conservation|Pure Sovereignty|^Other$", mx_cat) ~ "Mixed Types"),
         mx_cat2 = as.factor(ifelse(is.na(mx_cat2), paste0(mx_cat), mx_cat2))) %>% 
  filter(location_cat != "Non Identified")
# model
model4 <- multinom(mx_cat2 ~ location_cat + election_year + def_year + AAI, data = ama_model4)
summary(model4)
# Get p-values
p_values4 <- round((1 - pnorm(abs(summary(model4)$coefficients/summary(model4)$standard.errors)))*2, 5)
p_values4 <- data.frame(ifelse(p_values4 < 0.05, paste0(p_values4, "** Coef (",round(summary(model4)$coefficients, 5), ")"),
                               p_values4))[,-1]
# Get a decent table
kableExtra::kable(x = p_values4, caption = "Model 4 - Amazon Contructions by Location",
                  col.names = c("Brasilia", "International", "Non-AM State",
                                "Election Year", "Deforastion (year)", "Avg. Inflation (year)"))
stargazer::stargazer(model4, type="text", add.lines = nrow(model4$residuals),
                     covariate.labels = c("Brasilia", "International", "Non-AM State",
                                "Election Year", "Deforastion (year)", "Avg. Inflation (year)"),
                     column.labels = c("Other", "Conservation", "Economic Integration",
                                       "Social Development", "Sovereignty"),
                     dep.var.labels.include = FALSE)
```

### 2022-04-05 analysis/analysis_livio.Rmd
#text_corrections
#cleaning folder

@@
 
-cbPalette <- c("#999999", "#56B4E9", "#0072B2", "#009E73", "#F0E442", "#D55E00", "#CC79A7", "#E69F00")
 ```
@@
           select(-c(title, date, text, location))
+
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+
+amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>%
+  rename(def_year = "area km\u00b2")
 
@@
   left_join(perc1) %>%
+  left_join(amazon_def_year)%>%
   filter(amazon_speech==1) %>%
@@
 
-temp2 <- temp2 %>%
-    mutate(amazon_state= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "No",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "No",
-                            location_cat=='Non Identified' ~ "No"))%>%
-    mutate(brazil= case_when (location_cat=='Amazonian States' ~ "Yes",
-                            location_cat=='Brasilia' ~ "Yes",
-                            location_cat=='International' ~ "No",
-                            location_cat=='Non Amazonian States' ~ "Yes",
-                            location_cat=='Non Identified' ~ "No"))
+temp2 <- dplyr::left_join(temp2, amazon_def_year, by = "year")
 
-temp2$prob_constr <- relevel(temp2$prob_constr, ref = "other")
+temp2$prob_constr <- relevel(temp2$prob_constr, ref = "con")
 
-m2 <- multinom(prob_constr ~ amazon_state + brazil, data = temp2)
+m2 <- multinom(prob_constr ~ location_cat + def_year, data = temp2)
 

### 2022-04-05 analysis/Modelling Final.Rmd
Added four more models to modelling script

@@
 library(readxl)
+library(stargazer)
 options(scipen=999)
@@
 # inflation rates per year Brazil (average for year - but could be change)
-average_inflation_year_BR <- read_excel("data/average_inflation_year_BR.xlsx") # source world bank
-ama_model2 <- dplyr::left_join(ama_model2, average_inflation_year_BR, by = "year") # merge
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds") # source world bank
+ama_model2 <- dplyr::left_join(ama_model2, AAI, by = "year") # merge
 # Model with some controls
@@
 ```
+
+# Last few models
+
+With controls and mix types but no president...
+
+```{r}
+ama_model5 <- ama_model2 %>%
+  filter(location_cat != "Non Identified",
+         mx_cat != "Other Types") %>% 
+  mutate(mx_cat = relevel(mx_cat, ref = "Pure Conservation"))
+# model
+model5 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model5)
+summary(model5)$coefficients
+# Vizualize (just keep log odds and significance stars)
+stargazer::stargazer(model5, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
+                     covariate.labels = c("Brasilia", "International", "Non-AM state",
+                                "Election", "Deforestation", "Inflation"),
+                     column.labels = c("EI-SD", "EI-Con", "Other", "EI", "SD", "Sov",
+                                       "SD-Con", "Sov-Con", "Sov-EI", "SD-EI-Con"),
+                     dep.var.labels.include = FALSE)
+```
+
+With controls and mix types and president...
+
+```{r}
+# model
+model6 <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI + president, data = ama_model5)
+summary(model6)$coefficients
+# Vizualize (just keep log odds and significance stars)
+stargazer::stargazer(model6, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
+                     covariate.labels = c("Brasilia", "Int.", "Non-AM state", 
+                                          "Election", "Def.", "Inflation", "Collor", "Rousseff", "Cardoso",
+                                          "Franco", "Lula", "Sarney", "Temer"),
+                     column.labels = c("EI-SD", "EI-Con", "Other", "EI", "SD", "Sov",
+                                       "SD-Con", "Sov-Con", "Sov-EI", "SD-EI-Con"),
+                     dep.var.labels.include = FALSE)
+```
+
+I do not know here... I few there is a lot of significant things but I do not think we should include speaker.
+
+Let's try to recode variables and run the same model.
+
+```{r}
+sov2 <- ama %>% 
+  filter(sov==1) %>%
+  select(c(sov, location_cat, year, president))%>%
+  mutate(prob_constr=case_when(sov=="1"~ "sov")) %>%
+  select(-c(sov))
+ei2 <- ama %>% 
+  filter(EI==1)%>%
+  select(c(EI, location_cat, year, president))%>%
+  mutate(prob_constr=case_when(EI=="1"~ "EI")) %>%
+  select(-c(EI))
+sd2 <- ama %>% 
+  filter(SD==1)%>%
+  select(c(SD, location_cat, year, president))%>%
+  mutate(prob_constr=case_when(SD=="1"~ "SD")) %>%
+  select(-c(SD))
+con2 <- ama %>% 
+  filter(con==1)%>%
+  select(c(con, location_cat, year, president))%>%
+  mutate(prob_constr=case_when(con=="1"~ "con")) %>%
+  select(-c(con))
+other2 <- ama %>% 
+  filter(other==1)%>%
+  select(c(other, location_cat, year, president))%>%
+  mutate(prob_constr = case_when(other=="1"~ "other")) %>%
+  select(-c(other))
+ama_model7 <- rbind(sov2, con2, ei2, sd2, other2) %>% 
+  mutate(prob_constr = as.factor(prob_constr),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))  %>% # election year
+  filter(location_cat != "Non Identified")
+# deforestation yearly (year before)
+ama_model7 <- dplyr::left_join(ama_model7, amazon_def_year, by = "year") # merge
+# inflation rates per year Brazil (average for year - but could be change)
+ama_model7 <- dplyr::left_join(ama_model7, AAI, by = "year") # merge
+# model
+model7 <- multinom(prob_constr ~ location_cat + election_year + def_year + AAI, data = ama_model7)
+summary(model7)$coefficients
+# Vizualize (just keep log odds and significance stars)
+stargazer::stargazer(model7, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
+                     covariate.labels = c("Brasilia", "International", "Non-AM state",
+                                          "Election", "Deforestation", "Inflation"),
+                     column.labels = c("EI", "Other", "SD", "Sov"),
+                     dep.var.labels.include = FALSE)
+```
+
+I do not know if the results differ that much that we should change, what do you think?
+
+```{r}
+# model
+model8 <- multinom(prob_constr ~ location_cat + election_year + def_year + AAI + president, data = ama_model7)
+summary(model8)$coefficients
+# Vizualize (just keep log odds and significance stars)
+stargazer::stargazer(model8, type="text", apply.coef = exp, t.auto=F, p.auto = F, se = NULL, report = "vc*",
+                     covariate.labels = c("Brasilia", "International", "Non-AM state",
+                                          "Election", "Deforestation", "Inflation", "Collor", "Rousseff", "Cardoso",
+                                          "Franco", "Lula", "Sarney", "Temer"),
+                     column.labels = c("EI", "Other", "SD", "Sov"),
+                     dep.var.labels.include = FALSE)
+```

### 2022-04-05 Draft_April_2022/Full_draft_20220401.rmd
#preliminary final draft

---
title: How has the Brazilian Amazon been constructed as a problem? An analysis of
  presidential speeches since 1985
author:
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
date: "April 2022"
output: word_document
bibliography: references.bib
csl: chicago.csl
template: template.docx
abstract: This paper ...
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(nnet)
library(stargazer)

Sys.setlocale("LC_ALL", "C")

options(stringsAsFactors = FALSE, scipen = 999)

```

```{r data, message=FALSE, warning=FALSE, include=FALSE}

pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")

ama <-  ama %>%
          select(-c(title, date, text, false_positives)) %>%
          rename (ei= "EI") %>%
          rename (sd= "SD")

pop <-  pop %>%
          select(-c(title, date, text, location))

```

```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)

ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)

sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)

con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)

other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)

temp <- ei %>% left_join(other) %>% 
                left_join(con) %>%
                left_join(sd) %>%
                left_join(sov) %>%
                replace(is.na(.), 0)

```

```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ama_mx <- ama %>% 
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat= case_when (mixed_type=='1_0_0_0' ~ "Pure Sovereignty",
                            mixed_type=='0_1_0_0' ~ "Pure Economic Integration",
                            mixed_type=='0_0_1_0' ~ "Pure Social Development",
                            mixed_type=='0_0_0_1' ~ "Pure Conservation",
                            mixed_type=='0_0_0_0' ~"Other",
                            mixed_type=='0_1_0_1' ~"Economic Conservation",
                            mixed_type=='0_1_1_0' ~"Economic and Social Development",
                            mixed_type=='1_0_0_1' ~"Sovereign Conservation",
                            mixed_type=='0_1_1_1' ~ "Sustainable Development",
                            mixed_type=='1_1_0_0'~ "Sovereign Integration",
                            mixed_type=='0_0_1_1' ~"Social Conservation",
                            mixed_type=='1_1_0_1' ~"Other Mixed-types",
                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
                            mixed_type=='1_1_1_1' ~"Other Mixed-types",
                            mixed_type=='1_1_1_0' ~"Other Mixed-types",
                            mixed_type=='1_0_1_1' ~"Other Mixed-types"))%>%
  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Social Conservation", "Other Mixed-types"))) %>%
mutate(mx_cat2= case_when (mixed_type=='1_0_0_0' ~ "Pure-type",
                            mixed_type=='0_1_0_0' ~ "Pure-type",
                            mixed_type=='0_0_1_0' ~ "Pure-type",
                            mixed_type=='0_0_0_1' ~ "Pure-type",
                            mixed_type=='0_0_0_0' ~"Other",
                            mixed_type=='0_1_0_1' ~"Mixed-type",
                            mixed_type=='0_1_1_0' ~"Mixed-type",
                            mixed_type=='1_0_0_1' ~"Mixed-type",
                            mixed_type=='0_1_1_1' ~ "Mixed-type",
                            mixed_type=='1_1_0_0'~ "Mixed-type",
                            mixed_type=='0_0_1_1' ~"Mixed-type",
                            mixed_type=='1_1_0_1' ~"Mixed-type",
                            mixed_type=='1_0_1_0' ~"Mixed-type",
                            mixed_type=='1_0_1_0' ~"Mixed-type",
                            mixed_type=='1_1_1_1' ~"Mixed-type",
                            mixed_type=='1_1_1_0' ~"Mixed-type",
                            mixed_type=='1_0_1_1' ~"Mixed-type"))

```

\pagebreak

# 1 Introduction

The Amazon needs to be protected from foreign interests. The Amazon needs to be exploited for its natural resources. The Amazon should be preserved as a standing ecosystem. Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon. Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or the peoples as a particular problem. In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively. Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@hecht1990; @acker2014; @hochstetler2007\].However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem. Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes \[@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.

In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses. Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments. Although problem-construction takes place in a series of instances (e.g. policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985. We opt for presidential speeches for three reasons. First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004\]. In turn, policy perception is key for policy adoption and implementation \[@alesina2009\]. The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations \[@capobianco2021; @capobianco2019;@assunção2015 \]. Thus, understanding how policy comes about discursively is important. Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground. When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmers \[@harris2021; @miranda2021; @brice2021\]. This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground \[@capobianco2019; @campbell2015]. Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated. Finally, as our theoretical framework suggests, problem-construction varies by geographic location. Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city. Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.

To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985. We subset the dataset by identifying Amazonian related statements within these speeches. We find that 2014 sections in these discourses refer to the Amazon at least once. We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem. We use this codebook to manually code a randomly selected training set of the Amazonian related statements. Using R, we then train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements. We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.

(Summarize findings, conceptual contribution, and empirical contribution). Conceptually, our approach is underpinned by a constructivist view of policymaking, which allocates agency to different actors in building policy discursively. Empirically, we provide the first comprehensive overview of how the Brazilian Amazon has been constructed as a problem in presidential speeches.

This article proceeds as follows: first, we review Amazonian literature to identify the main ways in which it was constructed as a problem. We then propose a theoretical framework to understand problem-construction. In the methodology section, we operationalize our framework and the Amazonian problem-constructions. Section four portrays our main results over time and by speaker. Finally, we conclude by discussing our findings and proposing future research.

# 2 Amazonian policy-cycles, discourse, and problem-construction

## 2.1 Literature Review: policy-cycles in the Amazonian literature

For the purposes of this article, we understand Amazonian literature as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region. The three main policy-cycles we identify in Amazonian literature are: national sovereignty, economic integration, and environmental conservation. We tie each one of them to a specific problem and consequently a solution. We close the sub-section reviewing the relationship between policy, presidential discourse, and environmental problems.

### 2.1.1 National sovereignty

In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" (1990, p.1). It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders. The dream of fortunes to be found in the Eldorado composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else. It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" (Hecht and Cockburn 1990, preface). The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory. In the process of securing Amazonian borders, Brazil thwarted «the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru» (Hecht 2013, p.8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian. While Brazilian military diplomacy was very successful, the process did not come without its traumas. A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn, 1991). This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War \[@garfield2013\].

[^1]: B*andeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established. The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.

As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021\], the sovereignty problem becomes more varied. Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end \[@hochstetler2021; @capobianco2019; @franchini2019]. Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before. False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon. Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.

The sovereignty problem advances the view that the Brazilian Amazon is Brazilian and foreign presence, non-state presence and alleged lies are part of a broader strategy to internationalize the region. The policy solutions relate to close monitoring of the borders, strict regimes related to entry in the region, and combating alleged disinformation about the Amazon nationally and internationally.

### 2.1.2 Economic integration

The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon. In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2014). First, nature should be conquered by men. Second, exploiting natural resources would render the Amazon region a global powerhouse. Third, such a project would integrate the region with the rest of the country. Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry. The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2014), leading to a series of national and international enterprises settling in the Amazon region. Capobianco describes the period from the 1950-80 in a similar fashion (2019), referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.

The economic integration problem advances the view that the Brazilian Amazon needs to be developed and modernized. The policy solution relates to the creation of a series of policies, often centralized by the federal government and thus external to the region [@becker2005], that have at its core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.

### 2.1.3 Environmental conservation

The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006\]. A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of economic integration. \[@acker2021; @capobianco2021; @hecht1990]. As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy. This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco, 2019; Hochstetler and Keck, 2007). Hochstetler and Keck argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism (2007). They define it as an emphasis on local livelihoods of people while protecting nature. Capobianco (2019) argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.

The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination (Hochstetler and Keck 2007). The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing eco-systems through incentive schemes, and more policies facilitating indigenous environmental practices.

### 2.1.4 Policy and discourse

Different authors have proposed similar periodization for policy-cycles in the Amazon: a focus on sovereignty until the military dictatorship of 1964, followed by strong economic integration policies until the mid 1980s, and finally a shift to conservation after the 1992 Earth Summit. At the macro-historical level, the wider Amazonian vision of the 1964 military dictatorship, encompassed by the whole group of policies they adopted, for instance, did favor economic integration. Nevertheless, at the level of policies adopted, there is more variation than these periods would suggest. For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest. Framing the policy as an issue of economic integration, then, can be seen as a choice.

Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently. For historical inquiry, it is important to periodize policy cycles comprehensively and coherently. We largely agree with what the literature assigns to previous governments. However, the possibility of varied portrayals of the same policy opens possibilities of understanding agenda-setting and policy-adoption in less linear ways.

Problem-construction at the level of discourse is also more varied. They are not monolithic in time, across location, or even by the same speaker. While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse. @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen. The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).

While we find no major studies systematically looking into Amazonian related themes in Brazilian presidential speeches, we find, for example, several analyzes of environmental discourse in American presidential speeches. @calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989. Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change (ibid). He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects. In another article, @calderwood2020 tests the effect of geographic location and type of communication regarding climate change. Building prominently on @putnam1988 but also others, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt. He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on climate change does change based on location. Another example is @bevitori2015, who investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach. The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.

While these findings hold for the US, they suffice to argue that presidents can raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance. That entails the same president can combine, substitute, or change how they talk about the Amazon and these views can reflect, or not, the current political scenario, issues in the agenda, or talk to a different policy cycle at times.

## 2.2 Theoretical framework: problem-construction and presidential discourse

In "Journey towards Progress", Hirschman (1963) analyzes three policy problems in three different Latin American countries. The author draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion). Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group. Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests\[@hirschman1963, pp.388-91\].

Choosing a problem, though, entails a decision on how to represent it[@bacchi2009]. As Bacchi puts "policy has \[...\] \[a\] cultural dimension. It takes shape within specific historical and national or international contexts" \[-@bacchi2009a, pp. 10\].The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid). The alleged problem is not always explicitly stated in policy. Hirschman exemplifies chosen problems with the case of the construction of Brasilia (1975, p.388). But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three. How to represent a policy is a matter of choice. And different representations speak to different audiences.

We understand that depending on how the problem is represented to be, it can be a solution of problems that are considered pressing. Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context. Problem-construction takes place in different sites: national media, legislative bodies, international fora, among others. What eventually becomes policy is a product of a multi-faceted process in all these different sites. One avenue through which governments can emphasize the representations of a problem is discourse. We assume that problem-construction at the level of discourse is varied. They are not monolithic in time, across location, or even by the same speaker.

We argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context. In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connect the region to issues of sovereignty, economic integration, social development, or environmental conservation. Presidents choose to represent the region as a particular problem. As Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history. Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country. We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment (Bevitori, 2015) without embedding them in the histories of the term in the country.

These are the cornerstones of our framework: while governments are sometimes portrayed as proponents of a specific policy-solution, the way they construct the Amazon as a problem varies. The specific problem-constructions that we propose are embedded in Amazonian historiography and connect presidential speeches to Brazilian larger social-cultural history. We propose a framework to understand variation in problem-construction as a choice that is responsive to geographic location, time, and speaker.

# 3 Research Design

## 3.1 Data and modeling: operationalizing Amazonian problem construction

## 3.2 Analysis and limitations

# 4 How has the amazon been constructed as a problem?

This section presents the three main findings of our analysis. We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985. In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2. Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.

## 4.1 The rises and falls of the Amazon as a topic in presidential speeches

Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year. The smoothed curved controls incidence deforestation rates, economic situation, and election year (see appendix for methodological details). We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019. These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.

First, we observe a steady increase from about 5% in 1985 to 32% 1989. This is the period when the Brazilian Constitution was being written. Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories (Hecht & Cockburn, 1991). These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory. Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered, and in 1989, the New York Times published an article with pictures of the Amazon burning. Both incidents caught unprecedented international attention. President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza (Capobianco, 2021).

```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}

perc1 <- pop %>%
  count(amazon_speech, year)%>%
  group_by(year)%>%
  mutate(perc=n / sum(n)) %>%
  select(c(perc,amazon_speech, year))

pop %>% count(amazon_speech, year) %>%
  group_by(year) %>%
  left_join(perc1) %>%
  filter(amazon_speech==1) %>%
  ggplot(., aes(x = year, y = perc)) +
  geom_line(color="darkolivegreen")+
  scale_y_continuous(labels = percent_format())+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
  labs(
    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
    subtitle = "Sample composed by 6130 presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "right"
  )

```

While in 1990 there was a decrease to about 12.4%, we observe a novel increase to 15% and 25% in 1991 and 1992 respectively. The driver of this increase is likely to be the 1992 Earth Summit, which was being prepared by various state and non-state actors in the region and brought international attention to environmental topics in Brazil. One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (cite). During the Cardoso years (1994-2002), Amazonian speeches averaged at about 15% without strong variation. There were no big international or domestic events that drove the topic up.

We observe an increase from 8.5% in 2004 to 22.8% in the year of the Copenhagen Summit, 2009. This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history. Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" (Franchini & Viola, 2019), when stakes about climate change were high. A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen. From 2010 to 2014, we identify a steady decrease from 18.2% to 8.2%, which is followed by a sharp increase in the year of the COP, reaching 19.2%. These are the years when Brazil entered a long period of political and economic instability that lingers until today. Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted.

We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019. As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts, reaching unprecedented coverage. Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019. President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda. President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.

We do find evidence that deforestation rates, economic situation, elections, and simply preferential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall. However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events. We are yet to inspect, though, whether specific problem constructions about the Amazon change over time.

## 4.2 Amazonian problem-construction in time

Figure 2 portrays plots with the proportions of different problem constructions over time. We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation. At the level of the Amazonian statement, though, presidents might mix two or more together. These are what we call mixed types, in opposition to pure types. There are 16 mix types in total, and figure 2 portrays the most frequent of them. Pure problem constructions dominate, with their joint average above 55%. Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.

```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}

ama_mx %>%
  count(year, mx_cat)%>%
  group_by(year) %>%
  mutate(perc=n / sum(n))  %>%
  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
  geom_bar(stat="identity", position="dodge")+
  geom_smooth(color="black", size=.3, se= FALSE)+
  scale_y_continuous(labels = percent_format(accuracy=1))+
  labs(
    x = "", y = "", title ="Share of different problem-constructions by year",
    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "none"
  )+
  facet_wrap(~ mx_cat, ncol=3, scales="free_y")

```

The plots reveal several trends. Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s. In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005. Capobianco (2021) argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation. This is aligned with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught. As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.

Figure 3 (below) shows these shifts more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate. Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation. The starkest decrease relates to social development construction between Temer's and Bolsonaro's administration.

```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}

ama_mx %>%
  count(president, mx_cat, mx_cat2)%>%
  group_by(president) %>%
  mutate(perc=n / sum(n)) %>%
  filter(mx_cat !="Other")%>%
  filter(mx_cat2 == "Pure-type") %>%
  mutate(year= case_when (president=='Sarney' ~ "1985",
                          president=='Bolsonaro' ~ "2018",
                          president=='Collor' ~ "1990",
                          president=='Itamar' ~ "1993",
                          president=='FHC' ~ "1994",
                          president=='Lula' ~ "2003",
                          president=='Dilma' ~ "2011",
                          president=='Temer' ~ "2017"))%>%
  ggplot(., aes(x=as.numeric(year), y=perc, color=mx_cat))+
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5)+
  scale_y_continuous(labels = percent_format(accuracy=1))+
  labs(
    x = "", y = "", title ="Share of each pure types by year",
    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )

```

We now move to mixed types, which average at around 17% for all presidents in our sample: overall, presidents prefer pure problem-constructions. While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate. We focus our discussion on those with higher incidence. First, the most frequent mix overall is that of economic integration with conservation, which after reaching 25% of all problem-constructions in 1989, remained stable at 9% on average for the remainder of the period. President Lula was the most frequent user of this mix. Second, except for economic and social development appearing together in all statements made by Color in 1992, mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit. This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation. In all, we interpret the appearance of mixed types as more complex understandings of Amazonian problems. This follows a global agenda of understanding interconnections of social, environmental, and economic domains. As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals. Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation. This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 28.5% and 28.6% respectively. While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty. The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro.

```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}

ama_mx %>%
  filter(mx_cat2 =="Mixed-type")%>%
  count(president, mx_cat)%>%
  group_by(president) %>%
  mutate(perc=n / sum(n)) %>%
  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
  geom_bar(stat="identity", position="stack")+
  geom_text(size = 3, position = position_stack(vjust=.5))+
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
  labs(
    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
    subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
    caption = "") +
  theme(
    panel.background = element_rect("white", "black", .5, "solid"),
    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
    axis.text = element_text(color = "black", size = 10),
    title = element_text(color = "black", size = 10, face = "bold"),
    legend.title = element_blank(),
    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
    legend.position = "bottom"
  )
```

@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy. Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries. The costs for said economic and political benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in. Political stability, thus, can be seen as a product of the trade-off between both. Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy. With the strengthening of environmentalism in the 1990s, its most strong form being the policies adopted in the 2000s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.

While unprecedented, this new balance was not long-standing. Democratic decay is slow and the embryony of Bolsonaro's Amazonian discourse was breeding half a decade before he took office. We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s. The hard increase in sovereignty comes in the 2010s. As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations. At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.

This is not to say that those who preceded President Bolsonaro are like him. They are not, and we have shown how he is different from others already. But the political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest. Bolsonaro's problem-construction is the strongest form of this shift. Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.

## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside

# 5 Conclusion

# 6 References

### 2022-04-05 Draft_April_2022/Full_draft_20220401.rmd
#preliminary final draft

@@
 author:
-- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
+- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
 date: "April 2022"
-output: word_document
+output:
+  word_document:
+    reference_docx: template.docx
+  pdf_document: default
+  html_document:
+    df_print: paged
 bibliography: references.bib
 csl: chicago.csl
-template: template.docx
 abstract: This paper ...
@@
 In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
-Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@hecht1990; @acker2014; @hochstetler2007\].However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
-Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes \[@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.
+Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@acker2014; @hecht1990; @hochstetler2007].
+However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
+Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.
 
@@
 We opt for presidential speeches for three reasons.
-First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004\].
-In turn, policy perception is key for policy adoption and implementation \[@alesina2009\].
-The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations \[@capobianco2021; @capobianco2019;@assunção2015 \].
+First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+In turn, policy perception is key for policy adoption and implementation [@alesina2009].
+The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021].
 Thus, understanding how policy comes about discursively is important.
 Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmers \[@harris2021; @miranda2021; @brice2021\].
-This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground \[@capobianco2019; @campbell2015].
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmer[@brice2021; @harris2021; @miranda2021].
+This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015].
 Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated.
@@
 (Summarize findings, conceptual contribution, and empirical contribution).
-Conceptually, our approach is underpinned by a constructivist view of policymaking, which allocates agency to different actors in building policy discursively.
+Conceptually, our approach is underpinned by a constructivist view of policy making, which allocates agency to different actors in building policy discursively.
 Empirically, we provide the first comprehensive overview of how the Brazilian Amazon has been constructed as a problem in presidential speeches.
@@
 
-In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" (1990, p.1).
+In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" [-@hecht1990, pp.1].
 It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders.
@@
 The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted «the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru» (Hecht 2013, p.8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
+In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht2013, pp.8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
 While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn, 1991).
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War \[@garfield2013\].
+A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil[@hecht1990].
+This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War[@garfield2013].
+As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
+Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
+Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
+False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
+Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
 
@@
 The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
-
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021\], the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end \[@hochstetler2021; @capobianco2019; @franchini2019].
-Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
 
@@
 The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2014).
+In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
 First, nature should be conquered by men.
@@
 Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2014), leading to a series of national and international enterprises settling in the Amazon region.
-Capobianco describes the period from the 1950-80 in a similar fashion (2019), referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.
+The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
+@capobianco2019 describes the period from the 1950-80 in a similar fashion, referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.
 
@@
 
-The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006\].
+The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
 A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of economic integration.
-\[@acker2021; @capobianco2021; @hecht1990].
+[@acker2021; @capobianco2021; @hecht1990].
 As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
 This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco, 2019; Hochstetler and Keck, 2007).
-Hochstetler and Keck argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism (2007).
+@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
 They define it as an emphasis on local livelihoods of people while protecting nature.
-Capobianco (2019) argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.
+@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.
 
-The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination (Hochstetler and Keck 2007).
+The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
 The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing eco-systems through incentive schemes, and more policies facilitating indigenous environmental practices.
@@
 Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
-Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests\[@hirschman1963, pp.388-91\].
-
+Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests[@hirschman1963, pp.388-91].
 Choosing a problem, though, entails a decision on how to represent it[@bacchi2009].
-As Bacchi puts "policy has \[...\] \[a\] cultural dimension.
-It takes shape within specific historical and national or international contexts" \[-@bacchi2009a, pp.
-10\].The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid).
+As Bacchi puts "policy has a cultural dimension.
+It takes shape within specific historical and national or international contexts" [-@bacchi2009, pp.10].
+The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid).
 The alleged problem is not always explicitly stated in policy.
-Hirschman exemplifies chosen problems with the case of the construction of Brasilia (1975, p.388).
+Hirschman exemplifies chosen problems with the case of the construction of Brasilia [-@hirschman1975, pp.388].
 But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
@@
 This is the period when the Brazilian Constitution was being written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories (Hecht & Cockburn, 1991).
+Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories [@hecht1990].
 These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
@@
 Both incidents caught unprecedented international attention.
-President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza (Capobianco, 2021).
+President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza [@capobianco2021]
 
@@
 This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" (Franchini & Viola, 2019), when stakes about climate change were high.
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" [@franchini2019], when stakes about climate change were high.
 A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
@@
 In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005.
-Capobianco (2021) argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
 This is aligned with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.

### 2022-04-05 Draft_April_2022/Full_draft_20220401.tex
#preliminary final draft

--- 2022-04-05 Draft_April_2022/Full_draft_20220401.rmd
@@
----
-title: How has the Brazilian Amazon been constructed as a problem? An analysis of
-  presidential speeches since 1985
-author:
-- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
-date: "April 2022"
-output: word_document
-bibliography: references.bib
-csl: chicago.csl
-template: template.docx
-abstract: This paper ...
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={How has the Brazilian Amazon been constructed as a problem? An analysis of presidential speeches since 1985},
+  pdfauthor={Livio Silva-Muller; Henrique Sposito},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-```{r setup, include=FALSE, warning=FALSE, message=FALSE}
+\title{How has the Brazilian Amazon been constructed as a problem? An
+analysis of presidential speeches since 1985}
+\author{Livio Silva-Muller\footnote{Phd Candidate, The Graduate
+  Institute Geneva,
+  \href{mailto:livio.silva@graduateinstitute.ch}{\nolinkurl{livio.silva@graduateinstitute.ch}}} \and Henrique
+Sposito\footnote{Phd Candidate, The Graduate Institute Geneva,
+  \href{mailto:henrique.sposito@graduateinstitute.ch}{\nolinkurl{henrique.sposito@graduateinstitute.ch}}}}
+\date{April 2022}
 
-knitr::opts_chunk$set(include = FALSE)
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(skimr)
-library(scales)
-library(RColorBrewer)
-library(kableExtra)
-library(nnet)
-library(stargazer)
-
-Sys.setlocale("LC_ALL", "C")
-
-options(stringsAsFactors = FALSE, scipen = 999)
-
-```
-
-```{r data, message=FALSE, warning=FALSE, include=FALSE}
-
-pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
-ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
-
-ama <-  ama %>%
-          select(-c(title, date, text, false_positives)) %>%
-          rename (ei= "EI") %>%
-          rename (sd= "SD")
-
-pop <-  pop %>%
-          select(-c(title, date, text, location))
-
-```
-
-```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-sov <- ama %>% 
-  filter(sov==1) %>% 
-  count(sov, year) %>%
-  group_by(year) %>%
-  select(-c(sov))%>%
-  rename (sov = n)
-
-ei <- ama %>% 
-  filter(ei==1) %>% 
-  count(ei, year) %>%
-  group_by(year) %>%
-  select(-c(ei))%>%
-  rename (ei = n) %>%
-  ungroup() %>%
-  tibble::add_row(year = 2017, ei = 0) %>%
-  tibble::add_row(year = 2018, ei = 0)
-
-sd <- ama %>% 
-  filter(sd==1) %>% 
-  count(sd, year) %>%
-  group_by(year) %>%
-  select(-c(sd))%>%
-  rename (sd = n)
-
-con <- ama %>% 
-  filter(con==1) %>% 
-  count(con, year) %>%
-  group_by(year) %>%
-  select(-c(con))%>%
-  rename (con = n)
-
-other <- ama %>% 
-  filter(other==1) %>% 
-  count(other, year) %>%
-  group_by(year) %>%
-  select(-c(other))%>%
-  rename (other = n)
-
-temp <- ei %>% left_join(other) %>% 
-                left_join(con) %>%
-                left_join(sd) %>%
-                left_join(sov) %>%
-                replace(is.na(.), 0)
-
-```
-
-```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-ama_mx <- ama %>% 
-  unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat= case_when (mixed_type=='1_0_0_0' ~ "Pure Sovereignty",
-                            mixed_type=='0_1_0_0' ~ "Pure Economic Integration",
-                            mixed_type=='0_0_1_0' ~ "Pure Social Development",
-                            mixed_type=='0_0_0_1' ~ "Pure Conservation",
-                            mixed_type=='0_0_0_0' ~"Other",
-                            mixed_type=='0_1_0_1' ~"Economic Conservation",
-                            mixed_type=='0_1_1_0' ~"Economic and Social Development",
-                            mixed_type=='1_0_0_1' ~"Sovereign Conservation",
-                            mixed_type=='0_1_1_1' ~ "Sustainable Development",
-                            mixed_type=='1_1_0_0'~ "Sovereign Integration",
-                            mixed_type=='0_0_1_1' ~"Social Conservation",
-                            mixed_type=='1_1_0_1' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_1_1_1' ~"Other Mixed-types",
-                            mixed_type=='1_1_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_1' ~"Other Mixed-types"))%>%
-  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Social Conservation", "Other Mixed-types"))) %>%
-mutate(mx_cat2= case_when (mixed_type=='1_0_0_0' ~ "Pure-type",
-                            mixed_type=='0_1_0_0' ~ "Pure-type",
-                            mixed_type=='0_0_1_0' ~ "Pure-type",
-                            mixed_type=='0_0_0_1' ~ "Pure-type",
-                            mixed_type=='0_0_0_0' ~"Other",
-                            mixed_type=='0_1_0_1' ~"Mixed-type",
-                            mixed_type=='0_1_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_0_1' ~"Mixed-type",
-                            mixed_type=='0_1_1_1' ~ "Mixed-type",
-                            mixed_type=='1_1_0_0'~ "Mixed-type",
-                            mixed_type=='0_0_1_1' ~"Mixed-type",
-                            mixed_type=='1_1_0_1' ~"Mixed-type",
-                            mixed_type=='1_0_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_1_0' ~"Mixed-type",
-                            mixed_type=='1_1_1_1' ~"Mixed-type",
-                            mixed_type=='1_1_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_1_1' ~"Mixed-type"))
-
-```
+\begin{document}
+\maketitle
+\begin{abstract}
+This paper \ldots{}
+\end{abstract}
 
@@
 
-# 1 Introduction
+\hypertarget{introduction}{%
+\section{1 Introduction}\label{introduction}}
 
-The Amazon needs to be protected from foreign interests.
-The Amazon needs to be exploited for its natural resources.
-The Amazon should be preserved as a standing ecosystem.
-Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon.
-Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or the peoples as a particular problem.
-In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
-Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@hecht1990; @acker2014; @hochstetler2007\].However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
-Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes \[@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.
+The Amazon needs to be protected from foreign interests. The Amazon
+needs to be exploited for its natural resources. The Amazon should be
+preserved as a standing ecosystem. Historically, different Brazilian
+federal government proposed diverse policies to deal with the Amazon.
+Each of these policies contain an implicit assumption of what needs to
+be solved, or in other words, it represents the region, the forest, or
+the peoples as a particular problem. In the three examples above, the
+Amazon is represented as an issue of national sovereignty, economic
+integration, and environmental conservation, respectively. Each of these
+constructions, and their proposed solutions, have been described as
+policy cycles of Brazilian governments (Acker 2014; Hecht and Cockburn
+1990; Hochstetler and Keck 2007). However, policy cycles are usually
+represented monolithically, advancing a view that specific governments
+see the Amazon as an instance of only one specific problem. Albeit the
+current academic calls to understand the environment as a
+social-cultural construction and to identify the effect of culture for
+environmental outcomes (Polain de Waroux et al. 2021), we lack empirical
+accounts of how the Brazilian Amazon has been constructed as a problem
+over time and across locations, and how this varies.
 
-In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments.
-Although problem-construction takes place in a series of instances (e.g.
-policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985.
-We opt for presidential speeches for three reasons.
-First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004\].
-In turn, policy perception is key for policy adoption and implementation \[@alesina2009\].
-The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations \[@capobianco2021; @capobianco2019;@assunção2015 \].
-Thus, understanding how policy comes about discursively is important.
-Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmers \[@harris2021; @miranda2021; @brice2021\].
-This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground \[@capobianco2019; @campbell2015].
-Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated.
-Finally, as our theoretical framework suggests, problem-construction varies by geographic location.
-Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
+In this article, we investigate how the Brazilian Amazon has been
+constructed as a problem in political discourses. Building on Hirschman
+(1963) concept of chosen problems in policy making, we propose a
+framework to identify how problem-construction varies over time, by
+location, and between and within governments. Although
+problem-construction takes place in a series of instances (e.g.~policy
+committees, legislative bodies, media, etc.), we analyze the case of
+political discourse by Brazilian presidents since 1985. We opt for
+presidential speeches for three reasons. First, political discourses at
+the top have the power to introduce and justify public policy, as well
+as shape its perception to broad audiences (Zarefsky 2004). In turn,
+policy perception is key for policy adoption and implementation (Alesina
+and Giuliano 2009). The literature has shown that deforestation rates in
+Brazil are more responsive to the government's environmental policy than
+exogenous factors as market fluctuations (Assunção, Gandour, and Rocha
+2015; Capobianco 2019, 2021). Thus, understanding how policy comes about
+discursively is important. Second, environmental discourse at the top
+can help expand or restrict what types of behaviors are accepted in the
+ground. When Brazilian presidents speak about the Amazon it not only
+makes headlines, nationally and internationally, but also incites
+responses, shapes expectations, and feeds into the behavior of many
+actors involved with the Amazon, from investors to agribusiness to local
+farmer(Brice and Smith 2021; Harris 2021; Miranda 2021). This is
+especially pertinent for deforestation as previous research found that
+policy expectations, generated from material and discursive governmental
+practices, are a crucial factor in decisions to deforest at the ground
+(Capobianco 2019; Campbell 2015). Unpacking discourse at the top might
+help us raise hypotheses about environmental outcomes that are
+culturally situated. Finally, as our theoretical framework suggests,
+problem-construction varies by geographic location. Presidential
+discourses take place in a series of sites with diverse audiences: from
+launching a new bridge in a small municipality in the middle of the
+Amazon, to a keynote speech in a business association in São Paulo, to
+the UN general assembly in New York city. Working with presidential
+discourses allows us to identify this variation in meaningful ways and
+better how the Amazon is socially constructed.
 
-To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazonian related statements within these speeches.
-We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
-Using R, we then train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.
+To investigate how the Brazilian Amazon has been constructed as a
+problem in political discourses, we create a dataset containing 6130
+official presidential speeches by all Brazilian presidents since 1985.
+We subset the dataset by identifying Amazonian related statements within
+these speeches. We find that 2014 sections in these discourses refer to
+the Amazon at least once. We then develop a codebook grounded on
+Amazonian historiography to code how each of these statements constructs
+the Amazon as a particular problem. We use this codebook to manually
+code a randomly selected training set of the Amazonian related
+statements. Using R, we then train a supervised machine-learning model
+in the hand-coded set and automatically label the remaining set of
+Amazonian statements. We then conduct a descriptive and inferential
+analysis of this data, tying our findings to endogenous and exogenous
+events related to deforestation.
 
-(Summarize findings, conceptual contribution, and empirical contribution).
-Conceptually, our approach is underpinned by a constructivist view of policymaking, which allocates agency to different actors in building policy discursively.
-Empirically, we provide the first comprehensive overview of how the Brazilian Amazon has been constructed as a problem in presidential speeches.
+(Summarize findings, conceptual contribution, and empirical
+contribution). Conceptually, our approach is underpinned by a
+constructivist view of policy making, which allocates agency to
+different actors in building policy discursively. Empirically, we
+provide the first comprehensive overview of how the Brazilian Amazon has
+been constructed as a problem in presidential speeches.
 
-This article proceeds as follows: first, we review Amazonian literature to identify the main ways in which it was constructed as a problem.
-We then propose a theoretical framework to understand problem-construction.
-In the methodology section, we operationalize our framework and the Amazonian problem-constructions.
-Section four portrays our main results over time and by speaker.
-Finally, we conclude by discussing our findings and proposing future research.
+This article proceeds as follows: first, we review Amazonian literature
+to identify the main ways in which it was constructed as a problem. We
+then propose a theoretical framework to understand problem-construction.
+In the methodology section, we operationalize our framework and the
+Amazonian problem-constructions. Section four portrays our main results
+over time and by speaker. Finally, we conclude by discussing our
+findings and proposing future research.
 
-# 2 Amazonian policy-cycles, discourse, and problem-construction
+\hypertarget{amazonian-policy-cycles-discourse-and-problem-construction}{%
+\section{2 Amazonian policy-cycles, discourse, and
+problem-construction}\label{amazonian-policy-cycles-discourse-and-problem-construction}}
 
-## 2.1 Literature Review: policy-cycles in the Amazonian literature
+\hypertarget{literature-review-policy-cycles-in-the-amazonian-literature}{%
+\subsection{2.1 Literature Review: policy-cycles in the Amazonian
+literature}\label{literature-review-policy-cycles-in-the-amazonian-literature}}
 
-For the purposes of this article, we understand Amazonian literature as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.
-The three main policy-cycles we identify in Amazonian literature are: national sovereignty, economic integration, and environmental conservation.
-We tie each one of them to a specific problem and consequently a solution.
-We close the sub-section reviewing the relationship between policy, presidential discourse, and environmental problems.
+For the purposes of this article, we understand Amazonian literature as
+the body of research by social and environmental scientists that tells
+the story of diverse policies adopted to solve problems in the region.
+The three main policy-cycles we identify in Amazonian literature are:
+national sovereignty, economic integration, and environmental
+conservation. We tie each one of them to a specific problem and
+consequently a solution. We close the sub-section reviewing the
+relationship between policy, presidential discourse, and environmental
+problems.
 
-### 2.1.1 National sovereignty
+\hypertarget{national-sovereignty}{%
+\subsubsection{2.1.1 National sovereignty}\label{national-sovereignty}}
 
-In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" (1990, p.1).
-It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders.
-The dream of fortunes to be found in the Eldorado composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" (Hecht and Cockburn 1990, preface).
-The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted «the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru» (Hecht 2013, p.8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn, 1991).
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War \[@garfield2013\].
+In The Fate of the Forest: Developers, Destroyers, and Defenders of the
+Amazon, Hecht and Cockburn write that all over the world tropical
+forests are destroyed, but ``what imbues the case of the Amazon with
+such passion is the symbolic content of the dreams it ignites'' (1990,
+1). It started with the first natural history of the New World, by
+Oviedo in 1535, who recounts the stories of conquest of local
+populations and gold hoarders. The dream of fortunes to be found in the
+Eldorado composed the imaginaries of \emph{bandeirantes}\footnote{B\emph{andeirantes}
+  means ``flag-carriers'', the word is used to designate Portuguese
+  colonials and later Brazilian explorers, expanding the Brazilian
+  territory beyond what the Tordesillas Treaty established. The treaty
+  allocated almost the whole Amazonian territory to the Spanish Empire,
+  the bandeirantes took much of the territory afterwards.} from the
+southeast of Brazil and colonizers from everywhere else. It rendered the
+territory the venue for aspiration and object of an intense scramble in
+the subsequent centuries, defined as ``a (\ldots) form of nation
+building (\ldots)'' (Hecht and Cockburn 1990, preface). The Portuguese
+empire and subsequently the Brazilian monarchy were concerned with
+establishing their territory. In the process of securing Amazonian
+borders, Brazil thwarted ``the imperial ambitions of France, Britain,
+the United States, Belgium, Bolivia, and Peru'' (Hecht 2013, 8), and
+when the dust settled and the scramble was over, half of the Amazon
+emerged Brazilian. While Brazilian military diplomacy was very
+successful, the process did not come without its traumas. A significant
+experience were the negotiations with Bolivia in 1902 to secure the
+Amazonian state of Acre, during which they found out about American
+attempts to trick Brazil(Hecht and Cockburn 1990). This case was still
+part of the memory of the generals who led the country during the
+military dictatorship of 1964 and wanted to protect Brazil's sovereignty
+over the Amazon from the communist threat during the Cold War(Garfield
+2013). As we move from a world where non-state actors gain importance in
+environmental governance and international politics generally
+(Silva-Muller and Faul 2022; Andonova 2014; Westerwinter 2021), the
+sovereignty problem becomes more varied. Multiple non-state actors
+(NGOs, foundations, IOs, and so on) join the conversation about
+Amazonian policies more substantially as the military dictatorship
+starts to end (Hochstetler 2021; Capobianco 2019; Franchini and Viola
+2019). Threads to national sovereignty, consequently, can be interpreted
+as coming from a different set of actors than before. False claims about
+Brazilian policies in international and domestic fora, for instance, are
+often tied to strategies of `internationalizing' the Amazon. Relatedly,
+mentions of Amazonian myths which have been debunked as the `Earth of
+the Lungs', are also tied to internationalizing strategies.
 
-[^1]: B*andeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established.
-The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
+The sovereignty problem advances the view that the Brazilian Amazon is
+Brazilian and foreign presence, non-state presence and alleged lies are
+part of a broader strategy to internationalize the region. The policy
+solutions relate to close monitoring of the borders, strict regimes
+related to entry in the region, and combating alleged disinformation
+about the Amazon nationally and internationally.
 
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021\], the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end \[@hochstetler2021; @capobianco2019; @franchini2019].
-Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
+\hypertarget{economic-integration}{%
+\subsubsection{2.1.2 Economic integration}\label{economic-integration}}
 
-The sovereignty problem advances the view that the Brazilian Amazon is Brazilian and foreign presence, non-state presence and alleged lies are part of a broader strategy to internationalize the region.
-The policy solutions relate to close monitoring of the borders, strict regimes related to entry in the region, and combating alleged disinformation about the Amazon nationally and internationally.
+The dictatorships of Vargas (1937-46) and the military (1964-89) took
+over the task of modernizing the Amazon. In 1966, the Brazilian Military
+dictatorship launched Operation Amazon, a policy to modernize the region
+based on a set of assumptions (Acker 2014). First, nature should be
+conquered by men. Second, exploiting natural resources would render the
+Amazon region a global powerhouse. Third, such a project would integrate
+the region with the rest of the country. Concretely, this meant a series
+of infrastructure projects, such as roads and dams, incentives for
+settlers to develop ranches and expand the agricultural frontier, as
+well as establishing tax free zones to attract industry. The capital to
+conduct such changes, paradoxically, came from national and
+international sources (Acker 2014), leading to a series of national and
+international enterprises settling in the Amazon region. Capobianco
+(2019) describes the period from the 1950-80 in a similar fashion,
+referring to a wider range of policies of economic integration: the 1953
+Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do
+Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de
+Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa
+Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte;
+among others.
 
-### 2.1.2 Economic integration
+The economic integration problem advances the view that the Brazilian
+Amazon needs to be developed and modernized. The policy solution relates
+to the creation of a series of policies, often centralized by the
+federal government and thus external to the region (Becker 2005), that
+have at its core the development of the necessary infrastructure
+(physical, fiscal, or monetary) to integrate the region in the national
+and international economy.
 
-The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2014).
-First, nature should be conquered by men.
-Second, exploiting natural resources would render the Amazon region a global powerhouse.
-Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2014), leading to a series of national and international enterprises settling in the Amazon region.
-Capobianco describes the period from the 1950-80 in a similar fashion (2019), referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.
+\hypertarget{environmental-conservation}{%
+\subsubsection{2.1.3 Environmental
+conservation}\label{environmental-conservation}}
 
-The economic integration problem advances the view that the Brazilian Amazon needs to be developed and modernized.
-The policy solution relates to the creation of a series of policies, often centralized by the federal government and thus external to the region [@becker2005], that have at its core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.
+The rapid economic changes in the region in the 1960s, 70s, and 80s were
+matched with the birth of environmental institutions such as the New
+Forest Code (1964), the Secretary of Environment (1973), and the
+National Environment Law (1980) (Drummond and Barros-Platiau 2006). A
+common explanation for these institutions in the Amazonian literature is
+the impression of lack of control after years of economic integration.
+(Acker 2021; Capobianco 2021; Hecht and Cockburn 1990). As
+deforestation, fires, and violence rose in the region, catching
+international attention, the military government deemed as necessary the
+establishment of an environmental bureaucracy. This process accelerated
+in the late 1980s, with the birth of modern environmentalism epitomized
+in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021;
+Capobianco, 2019; Hochstetler and Keck, 2007). Hochstetler and Keck
+(2007) argue that during preparations for the summit, a new form of
+Brazilian environmentalism emerged: socio-environmentalism. They define
+it as an emphasis on local livelihoods of people while protecting
+nature. Capobianco (2019) argues in a similar line, establishing
+socio-environmentalism as the main government response in the 1990s and
+early 2000s in a series of policies: the 2001 Sistema Nacional de
+Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the
+2004 Plano de Ação para a Prevenção e Controle do Desmatamento na
+Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional
+das Mudanças Climáticas; among others.
 
-### 2.1.3 Environmental conservation
+The conservationist problem-construction advances the view that Amazon
+should be preserved, deforestation should be halted, and the sustainable
+practices of indigenous and local peoples should be maintained through
+protection of their territories and rights to self-determination
+(Hochstetler and Keck 2007). The policy solution implies more investment
+in command-and-control infrastructure (as remote-sensing technology for
+environmental outcome measurement), more investment in the valuation of
+standing eco-systems through incentive schemes, and more policies
+facilitating indigenous environmental practices.
 
-The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006\].
-A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of economic integration.
-\[@acker2021; @capobianco2021; @hecht1990].
-As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
-This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco, 2019; Hochstetler and Keck, 2007).
-Hochstetler and Keck argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism (2007).
-They define it as an emphasis on local livelihoods of people while protecting nature.
-Capobianco (2019) argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.
+\hypertarget{policy-and-discourse}{%
+\subsubsection{2.1.4 Policy and discourse}\label{policy-and-discourse}}
 
-The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination (Hochstetler and Keck 2007).
-The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing eco-systems through incentive schemes, and more policies facilitating indigenous environmental practices.
+Different authors have proposed similar periodization for policy-cycles
+in the Amazon: a focus on sovereignty until the military dictatorship of
+1964, followed by strong economic integration policies until the mid
+1980s, and finally a shift to conservation after the 1992 Earth Summit.
+At the macro-historical level, the wider Amazonian vision of the 1964
+military dictatorship, encompassed by the whole group of policies they
+adopted, for instance, did favor economic integration. Nevertheless, at
+the level of policies adopted, there is more variation than these
+periods would suggest. For example, the 1980 Programa Calha Norte did
+contain elements to ensure sovereignty, integrate the region to the
+country's economy, and preserve the forest. Framing the policy as an
+issue of economic integration, then, can be seen as a choice.
 
-### 2.1.4 Policy and discourse
+Hence, while the literature might represent governments as coherent
+proponents of a particular policy retroactively, political actors might
+have adopted strategies that outline problem-constructions of policies
+differently. For historical inquiry, it is important to periodize policy
+cycles comprehensively and coherently. We largely agree with what the
+literature assigns to previous governments. However, the possibility of
+varied portrayals of the same policy opens possibilities of
+understanding agenda-setting and policy-adoption in less linear ways.
 
-Different authors have proposed similar periodization for policy-cycles in the Amazon: a focus on sovereignty until the military dictatorship of 1964, followed by strong economic integration policies until the mid 1980s, and finally a shift to conservation after the 1992 Earth Summit.
-At the macro-historical level, the wider Amazonian vision of the 1964 military dictatorship, encompassed by the whole group of policies they adopted, for instance, did favor economic integration.
-Nevertheless, at the level of policies adopted, there is more variation than these periods would suggest.
-For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest.
-Framing the policy as an issue of economic integration, then, can be seen as a choice.
+Problem-construction at the level of discourse is also more varied. They
+are not monolithic in time, across location, or even by the same
+speaker. While governmental discourses in Brazil have been studied for
+topic such as inflation or race relations , we only find one systematic
+analysis of Amazonian discourse. Barros (2020) investigates Amazonian
+discourse in the Brazilian Congress with the objective of identifying
+the arguments put forth by congressmen. The main finding is that in
+congress the economic value of the Amazon for the cattle industry is the
+most salient narrative, leading the author to conclude there is a
+mismatch between the international debate (which focuses on
+preservation) and the national debate (which focuses on economic
+development).
 
-Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently.
-For historical inquiry, it is important to periodize policy cycles comprehensively and coherently.
-We largely agree with what the literature assigns to previous governments.
-However, the possibility of varied portrayals of the same policy opens possibilities of understanding agenda-setting and policy-adoption in less linear ways.
+While we find no major studies systematically looking into Amazonian
+related themes in Brazilian presidential speeches, we find, for example,
+several analyzes of environmental discourse in American presidential
+speeches. Calderwood (2019) examines 2919 mentions of climate change in
+American official presidential speeches since 1989. Among various
+findings, one that stands out is that American presidents frequently
+side-step the environmental aspects of climate change (ibid). He also
+identifies a shift from economic to security framing of climate issues,
+side-lining its environmental aspects. In another article, Calderwood
+(2020) tests the effect of geographic location and type of communication
+regarding climate change. Building prominently on Putnam (1988) but also
+others, he hypothesizes that presidents are more likely to mention
+climate change in foreign locations, and that location influences the
+specific discursive approach and tone they adopt. He finds evidence in
+support of his hypothesis, suggesting American presidential discourse at
+the top on climate change does change based on location. Another example
+is Bevitori (2015), who investigates how the `environment' has been
+constructed in American presidential discourse since 1960 using a more
+automated approach. The author finds that mentions of the environment
+are typically co-selected with the pronoun `our', as well as with
+`economy', `clean', and `preserve'.
 
-Problem-construction at the level of discourse is also more varied.
-They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse.
-@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+While these findings hold for the US, they suffice to argue that
+presidents can raise different points about the Amazon at local,
+national, or international settings, depending on who they assume their
+audience is at that specific instance. That entails the same president
+can combine, substitute, or change how they talk about the Amazon and
+these views can reflect, or not, the current political scenario, issues
+in the agenda, or talk to a different policy cycle at times.
 
-While we find no major studies systematically looking into Amazonian related themes in Brazilian presidential speeches, we find, for example, several analyzes of environmental discourse in American presidential speeches.
-@calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989.
-Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change (ibid).
-He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-In another article, @calderwood2020 tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988 but also others, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on climate change does change based on location.
-Another example is @bevitori2015, who investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
-The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
+\hypertarget{theoretical-framework-problem-construction-and-presidential-discourse}{%
+\subsection{2.2 Theoretical framework: problem-construction and
+presidential
+discourse}\label{theoretical-framework-problem-construction-and-presidential-discourse}}
 
-While these findings hold for the US, they suffice to argue that presidents can raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance.
-That entails the same president can combine, substitute, or change how they talk about the Amazon and these views can reflect, or not, the current political scenario, issues in the agenda, or talk to a different policy cycle at times.
+In ``Journey towards Progress'', Hirschman (1963) analyzes three policy
+problems in three different Latin American countries. The author draws a
+conceptual distinction between pressing problems (pressured from outside
+parties to the government) and chosen problems (chosen by the government
+at their own discretion). Pressing problems can be either privileged or
+neglected depending on the degree of pressure exercised by the
+interested group. Problems can change from pressing to chosen across
+time and in space as a function of solutions becoming available,
+changing level of government control in society, or top policymakers
+shifting interests(Hirschman 1963, 388--91). Choosing a problem, though,
+entails a decision on how to represent it(Bacchi 2009). As Bacchi puts
+``policy has a cultural dimension. It takes shape within specific
+historical and national or international contexts'' (2009, 10). The
+existence or proposal of a policy generally implies that there is a
+(public) problem that needs (governmental) action to be fixed (ibid).
+The alleged problem is not always explicitly stated in policy. Hirschman
+exemplifies chosen problems with the case of the construction of
+Brasilia (1975, 388). But building Brasilia can solve a problem of
+regional inequality, a problem of a dormant economy without state
+investment, a problem of political representation, or all three. How to
+represent a policy is a matter of choice. And different representations
+speak to different audiences.
 
-## 2.2 Theoretical framework: problem-construction and presidential discourse
+We understand that depending on how the problem is represented to be, it
+can be a solution of problems that are considered pressing. Different
+problem-constructions can address the demands of different
+constituencies and it is up to the discretion of the political actor to
+construct a particular problem in a particular way given context.
+Problem-construction takes place in different sites: national media,
+legislative bodies, international fora, among others. What eventually
+becomes policy is a product of a multi-faceted process in all these
+different sites. One avenue through which governments can emphasize the
+representations of a problem is discourse. We assume that
+problem-construction at the level of discourse is varied. They are not
+monolithic in time, across location, or even by the same speaker.
 
-In "Journey towards Progress", Hirschman (1963) analyzes three policy problems in three different Latin American countries.
-The author draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
-Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
-Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests\[@hirschman1963, pp.388-91\].
+We argue that presidents can employ specific problem-constructions that
+build objects as specific problems depending on the context. In the
+specific case of the Brazilian Amazon, we contend that Amazonian
+problem-construction connect the region to issues of sovereignty,
+economic integration, social development, or environmental conservation.
+Presidents choose to represent the region as a particular problem. As
+Bacchi (2009), we argue that problem-constructions touch on shared
+meanings about the region that are available to the speaker as part of
+larger social-cultural history. Thus, the ways a president speaks are
+culturally and historically mediated and need to be embedded in the
+wider history of the region and country. We consider this an advancement
+in relation to scholars looking at American presidential speeches, as
+they just count mentions to climate change (Calderwood 2019, 2020; Brown
+and Sovacool 2017) or environment (Bevitori, 2015) without embedding
+them in the histories of the term in the country.
 
-Choosing a problem, though, entails a decision on how to represent it[@bacchi2009].
-As Bacchi puts "policy has \[...\] \[a\] cultural dimension.
-It takes shape within specific historical and national or international contexts" \[-@bacchi2009a, pp.
-10\].The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid).
-The alleged problem is not always explicitly stated in policy.
-Hirschman exemplifies chosen problems with the case of the construction of Brasilia (1975, p.388).
-But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
-How to represent a policy is a matter of choice.
-And different representations speak to different audiences.
+These are the cornerstones of our framework: while governments are
+sometimes portrayed as proponents of a specific policy-solution, the way
+they construct the Amazon as a problem varies. The specific
+problem-constructions that we propose are embedded in Amazonian
+historiography and connect presidential speeches to Brazilian larger
+social-cultural history. We propose a framework to understand variation
+in problem-construction as a choice that is responsive to geographic
+location, time, and speaker.
 
-We understand that depending on how the problem is represented to be, it can be a solution of problems that are considered pressing.
-Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-Problem-construction takes place in different sites: national media, legislative bodies, international fora, among others.
-What eventually becomes policy is a product of a multi-faceted process in all these different sites.
-One avenue through which governments can emphasize the representations of a problem is discourse.
-We assume that problem-construction at the level of discourse is varied.
-They are not monolithic in time, across location, or even by the same speaker.
+\hypertarget{research-design}{%
+\section{3 Research Design}\label{research-design}}
 
-We argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context.
-In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connect the region to issues of sovereignty, economic integration, social development, or environmental conservation.
-Presidents choose to represent the region as a particular problem.
-As Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
-Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country.
-We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment (Bevitori, 2015) without embedding them in the histories of the term in the country.
+\hypertarget{data-and-modeling-operationalizing-amazonian-problem-construction}{%
+\subsection{3.1 Data and modeling: operationalizing Amazonian problem
+construction}\label{data-and-modeling-operationalizing-amazonian-problem-construction}}
 
-These are the cornerstones of our framework: while governments are sometimes portrayed as proponents of a specific policy-solution, the way they construct the Amazon as a problem varies.
-The specific problem-constructions that we propose are embedded in Amazonian historiography and connect presidential speeches to Brazilian larger social-cultural history.
-We propose a framework to understand variation in problem-construction as a choice that is responsive to geographic location, time, and speaker.
+\hypertarget{analysis-and-limitations}{%
+\subsection{3.2 Analysis and
+limitations}\label{analysis-and-limitations}}
 
-# 3 Research Design
+\hypertarget{how-has-the-amazon-been-constructed-as-a-problem}{%
+\section{4 How has the amazon been constructed as a
+problem?}\label{how-has-the-amazon-been-constructed-as-a-problem}}
 
-## 3.1 Data and modeling: operationalizing Amazonian problem construction
+This section presents the three main findings of our analysis. We open
+with a broad overview of the evolution of the incidence of Amazon in all
+presidential speeches since 1985. In section 4.2, we focus on speeches
+that mention the Amazon, introducing the specific problem-constructions
+we presented in section 2. Finally, we run a multinominal model to show
+how problem constructions change as the speaker moves further away from
+the Amazon region.
 
-## 3.2 Analysis and limitations
+\hypertarget{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}{%
+\subsection{4.1 The rises and falls of the Amazon as a topic in
+presidential
+speeches}\label{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}}
 
-# 4 How has the amazon been constructed as a problem?
+Figure 1 shows the proportion of speeches that mentions the Amazon in
+relation to all speeches in each year. The smoothed curved controls
+incidence deforestation rates, economic situation, and election year
+(see appendix for methodological details). We observe various local
+maxima: 1989, 1992, 2004, 2009, 2015, and 2019. These points coincide
+exogenous events that helps us explain the rises and falls of the Amazon
+in presidential discourse.
 
-This section presents the three main findings of our analysis.
-We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985.
-In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.
-Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.
+First, we observe a steady increase from about 5\% in 1985 to 32\% 1989.
+This is the period when the Brazilian Constitution was being written.
+Indigenous and traditional populations were instrumental in advocating
+for constitutional environmental rights and protection of their
+territories (Hecht and Cockburn 1990). These were eventually enshrined
+in article 225, which gives all Brazilians a right to a balanced
+environment, and in article 231, which grants indigenous and traditional
+populations a right over their territory. Two other factors are likely
+to explain this increase: in 1988 Chico Mendes was brutally murdered,
+and in 1989, the New York Times published an article with pictures of
+the Amazon burning. Both incidents caught unprecedented international
+attention. President Sarney responded to these publicly, and proposed a
+new set of policies to address, named Nossa Natureza (Capobianco 2021)
 
-## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
+\includegraphics{Full_draft_20220401_files/figure-latex/Amazonian speeches by year-1.pdf}
 
-Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The smoothed curved controls incidence deforestation rates, economic situation, and election year (see appendix for methodological details).
-We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019.
-These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+While in 1990 there was a decrease to about 12.4\%, we observe a novel
+increase to 15\% and 25\% in 1991 and 1992 respectively. The driver of
+this increase is likely to be the 1992 Earth Summit, which was being
+prepared by various state and non-state actors in the region and brought
+international attention to environmental topics in Brazil. One of the
+big announcements was the consolidation of the first transnational
+partnership for the Amazon, the G7 Pilot Programme, which brought a high
+number of financial resources to the region for public policy
+implementation (cite). During the Cardoso years (1994-2002), Amazonian
+speeches averaged at about 15\% without strong variation. There were no
+big international or domestic events that drove the topic up.
 
-First, we observe a steady increase from about 5% in 1985 to 32% 1989.
-This is the period when the Brazilian Constitution was being written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories (Hecht & Cockburn, 1991).
-These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered, and in 1989, the New York Times published an article with pictures of the Amazon burning.
-Both incidents caught unprecedented international attention.
-President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza (Capobianco, 2021).
+We observe an increase from 8.5\% in 2004 to 22.8\% in the year of the
+Copenhagen Summit, 2009. This coincides with the Presidency of Lula and
+the steepest decrease in deforestation rates in Brazilian history. Lula
+led the delegation to Copenhagen with a self-image of ``we do not
+promise, we deliver'' (Franchini and Viola 2019), when stakes about
+climate change were high. A somewhat different pattern can be identified
+in the lead up to the 2015 Paris COP, which was also building up to
+become a key-turn in climate politics after the failures of Copenhagen.
+From 2010 to 2014, we identify a steady decrease from 18.2\% to 8.2\%,
+which is followed by a sharp increase in the year of the COP, reaching
+19.2\%. These are the years when Brazil entered a long period of
+political and economic instability that lingers until today. Brazil went
+to the COP in Paris with deforestation numbers slightly higher than
+Copenhagen, and a perception that there was a turn towards less
+conservation after the 2011 Forest Code was adopted.
 
-```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
+We subsequently observe a steady increase from 6.4\% in 2016 to almost
+24\% in the first year of Bolsonaro's presidency, 2019. As the narrative
+of the climate crisis picks up in the late 2010s, international media
+attention about the Amazon blasts, reaching unprecedented coverage.
+Pictures of the Amazon on fire and of the red sky afternoon in São Paulo
+circulated in social media and international media outlets in 2019.
+President Bolsonaro engages in an international debacle with President
+Macron and others, which drove the topic up strongly in the presidential
+agenda. President Bolsonaro retrieves Brazil's hosting status for COP25,
+and a strong process of dismantling of environmental governance starts
+taking place.
 
-perc1 <- pop %>%
-  count(amazon_speech, year)%>%
-  group_by(year)%>%
-  mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, year))
+We do find evidence that deforestation rates, economic situation,
+elections, and simply preferential preferences affect the incidence of
+Amazon in speeches: the smoothed curve portrays lower proportions
+overall. However, international events and media coverage also correlate
+with local maxima of our curve, suggesting presidents do speak more
+about the Amazon in preparation or reaction to these events. We are yet
+to inspect, though, whether specific problem constructions about the
+Amazon change over time.
 
-pop %>% count(amazon_speech, year) %>%
-  group_by(year) %>%
-  left_join(perc1) %>%
-  filter(amazon_speech==1) %>%
-  ggplot(., aes(x = year, y = perc)) +
-  geom_line(color="darkolivegreen")+
-  scale_y_continuous(labels = percent_format())+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )
+\hypertarget{amazonian-problem-construction-in-time}{%
+\subsection{4.2 Amazonian problem-construction in
+time}\label{amazonian-problem-construction-in-time}}
 
-```
+Figure 2 portrays plots with the proportions of different problem
+constructions over time. We conceptualize four problem constructions:
+sovereignty, economic integration, social development, and conservation.
+At the level of the Amazonian statement, though, presidents might mix
+two or more together. These are what we call mixed types, in opposition
+to pure types. There are 16 mix types in total, and figure 2 portrays
+the most frequent of them. Pure problem constructions dominate, with
+their joint average above 55\%. Among the four pure types as well as the
+mixed types, we observe a strong variation over time, suggesting the
+narratives do respond differently to factors that affect Amazonian
+statements discussed in the section above.
 
-While in 1990 there was a decrease to about 12.4%, we observe a novel increase to 15% and 25% in 1991 and 1992 respectively.
-The driver of this increase is likely to be the 1992 Earth Summit, which was being prepared by various state and non-state actors in the region and brought international attention to environmental topics in Brazil.
-One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (cite).
-During the Cardoso years (1994-2002), Amazonian speeches averaged at about 15% without strong variation.
-There were no big international or domestic events that drove the topic up.
+\includegraphics{Full_draft_20220401_files/figure-latex/mixed-types in time-1.pdf}
 
-We observe an increase from 8.5% in 2004 to 22.8% in the year of the Copenhagen Summit, 2009.
-This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" (Franchini & Viola, 2019), when stakes about climate change were high.
-A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
-From 2010 to 2014, we identify a steady decrease from 18.2% to 8.2%, which is followed by a sharp increase in the year of the COP, reaching 19.2%.
-These are the years when Brazil entered a long period of political and economic instability that lingers until today.
-Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted.
+The plots reveal several trends. Pure economic integration statements,
+which were dominant, decreased in incidence as of the mid 1990s. In the
+late 1990s, pure conservation as well as pure social development
+increased; both surpassing the proportion of economic integration
+problem-construction in 2005. Capobianco (2021) argues that the
+unprecedented decrease in deforestation we observed from 2004 to 2012
+was a product of an increase in the perception of stronger federal
+policies and presence in the Amazon region, which in turn engendered a
+perception of higher risk of being caught and fined for deforestation.
+This is aligned with our findings: a higher incidence of the Amazon as a
+topic overall can generate a perception of more attention from the top,
+and a shift from economic integration to conservation can generate a
+perception of higher change of being caught. As of the early 2010s, we
+observe a reversal of the trend with a twist: economic integration
+starts picking up again in detriment of conservation and social
+development problem constructions, but with sovereignty increasing
+steadily.
 
-We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
-As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts, reaching unprecedented coverage.
-Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019.
-President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda.
-President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
+Figure 3 (below) shows these shifts more clearly and highlights the
+decrease of economic integration and increase of social and conservation
+problem constructions preceding Lula's presidential mandate. Relatedly,
+figure 3 also shows that while the reversal precedes the mandate of
+President Bolsonaro, it was with him and his dismantling of social and
+environmental policies that sovereignty and economic integration appears
+the most, in detriment of social development and environmental
+conservation. The starkest decrease relates to social development
+construction between Temer's and Bolsonaro's administration.
 
-We do find evidence that deforestation rates, economic situation, elections, and simply preferential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
-However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events.
-We are yet to inspect, though, whether specific problem constructions about the Amazon change over time.
+\includegraphics{Full_draft_20220401_files/figure-latex/pure types in time -1.pdf}
 
-## 4.2 Amazonian problem-construction in time
+We now move to mixed types, which average at around 17\% for all
+presidents in our sample: overall, presidents prefer pure
+problem-constructions. While there is some variation in time for each
+single mixed type, some of them have low counts and interpretations are
+not adequate. We focus our discussion on those with higher incidence.
+First, the most frequent mix overall is that of economic integration
+with conservation, which after reaching 25\% of all
+problem-constructions in 1989, remained stable at 9\% on average for the
+remainder of the period. President Lula was the most frequent user of
+this mix. Second, except for economic and social development appearing
+together in all statements made by Color in 1992, mixed types using
+conservation were quite frequent in the lead up and aftermath of the
+1992 Earth Summit. This includes the mix type we label sustainable
+development, which constructs the Amazon as a problem of economic
+integration, social development, and environmental conservation. In all,
+we interpret the appearance of mixed types as more complex
+understandings of Amazonian problems. This follows a global agenda of
+understanding interconnections of social, environmental, and economic
+domains. As we show that Amazonian incidence in discourse does respond
+to global issues, this is not a surprise given agendas as Millennium
+Development Goals and the Sustainable Development Goals. Nevertheless,
+as in pure types, we also observe the comeback of sovereignty being used
+in mixed types in detriment of conservation. This becomes more apparent
+in a comparison between Lula and Bolsonaro, the two presidents that mix
+the most with proportions 11\% above presidential averages: 28.5\% and
+28.6\% respectively. While the former frequently mixed conservation with
+other problem constructions, the latter prefers mixing sovereignty. The
+combination of sovereignty with economic integration, which was also
+characteristic of the military dictatorship policies for the region,
+reaches its highest level with Bolsonaro.
 
-Figure 2 portrays plots with the proportions of different problem constructions over time.
-We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
-At the level of the Amazonian statement, though, presidents might mix two or more together.
-These are what we call mixed types, in opposition to pure types.
-There are 16 mix types in total, and figure 2 portrays the most frequent of them.
-Pure problem constructions dominate, with their joint average above 55%.
-Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.
+\includegraphics{Full_draft_20220401_files/figure-latex/mixed-types by president -1.pdf}
 
-```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+Pacheco (2019) proposes that we see the Amazon frontier as a key
+analytic category to understand the Brazilian state and democracy.
+Specifically, the author states that the natural richness of the region
+has been instrumentally transformed in political support through
+resource exploration by different governments over the last centuries.
+The costs for said economic and political benefits are the livelihoods
+of indigenous and traditional populations and the ecosystems they reside
+in. Political stability, thus, can be seen as a product of the trade-off
+between both. Policies during the military dictatorship were strongly
+geared towards integrating the Amazon to the national territory and
+international economy. With the strengthening of environmentalism in the
+1990s, its most strong form being the policies adopted in the 2000s, we
+can interpret the fall of economic integration and the rise of social
+and conservation problem constructions as a new relationship between
+granting local livelihoods their rights and economic exploitation.
 
-ama_mx %>%
-  count(year, mx_cat)%>%
-  group_by(year) %>%
-  mutate(perc=n / sum(n))  %>%
-  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
-  geom_bar(stat="identity", position="dodge")+
-  geom_smooth(color="black", size=.3, se= FALSE)+
-  scale_y_continuous(labels = percent_format(accuracy=1))+
-  labs(
-    x = "", y = "", title ="Share of different problem-constructions by year",
-    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "none"
-  )+
-  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
+While unprecedented, this new balance was not long-standing. Democratic
+decay is slow and the embryony of Bolsonaro's Amazonian discourse was
+breeding half a decade before he took office. We observe the decrease in
+conservation related statements in the early 2010s, and the soft
+increase of sovereignty in form of mixes in the mid 2000s. The hard
+increase in sovereignty comes in the 2010s. As we conceptualize and
+operationalize sovereignty as boundary-making vis-à-vis internal and
+external perceived threats to the Amazon, we interpret this increase as
+attacks to indigenous and traditional populations. At the policy side,
+the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a
+turning point: political opposition to conservation got particularly
+organized and managed to lobby the executive and conquer this policy
+wins, which were largely opposed by environmentalists.
 
-```
+This is not to say that those who preceded President Bolsonaro are like
+him. They are not, and we have shown how he is different from others
+already. But the political forces in Brazilian democracy that drive
+these changes in problem-construction were long in the making, as the
+earlier and softer shifts in discourse suggest. Bolsonaro's
+problem-construction is the strongest form of this shift. Now that we've
+inspected and developed pure and mixed types, we can check if these
+specific problem constructions vary depending on where the president is
+speaking.
 
-The plots reveal several trends.
-Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s.
-In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005.
-Capobianco (2021) argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-This is aligned with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
-As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+\hypertarget{an-amazonian-three-level-game-boasting-policy-outside-talking-to-people-inside}{%
+\subsection{4.3 An Amazonian three-level game? Boasting policy outside,
+talking to people
+inside}\label{an-amazonian-three-level-game-boasting-policy-outside-talking-to-people-inside}}
 
-Figure 3 (below) shows these shifts more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
-Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation.
-The starkest decrease relates to social development construction between Temer's and Bolsonaro's administration.
+\hypertarget{conclusion}{%
+\section{5 Conclusion}\label{conclusion}}
 
-```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+\hypertarget{references}{%
+\section*{6 References}\label{references}}
+\addcontentsline{toc}{section}{6 References}
 
-ama_mx %>%
-  count(president, mx_cat, mx_cat2)%>%
-  group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  filter(mx_cat !="Other")%>%
-  filter(mx_cat2 == "Pure-type") %>%
-  mutate(year= case_when (president=='Sarney' ~ "1985",
-                          president=='Bolsonaro' ~ "2018",
-                          president=='Collor' ~ "1990",
-                          president=='Itamar' ~ "1993",
-                          president=='FHC' ~ "1994",
-                          president=='Lula' ~ "2003",
-                          president=='Dilma' ~ "2011",
-                          president=='Temer' ~ "2017"))%>%
-  ggplot(., aes(x=as.numeric(year), y=perc, color=mx_cat))+
-  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5)+
-  scale_y_continuous(labels = percent_format(accuracy=1))+
-  labs(
-    x = "", y = "", title ="Share of each pure types by year",
-    subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-acker2014}{}}%
+Acker, Antoine. 2014. {``{"}O maior incêndio do planeta{"}: como a
+Volkswagen e o regime militar brasileiro acidentalmente ajudaram a
+transformar a Amazônia em uma arena política global.''} \emph{Revista
+Brasileira de História} 34 (December): 13--33.
+\url{https://doi.org/10.1590/S0102-01882014000200002}.
 
-```
+\leavevmode\vadjust pre{\hypertarget{ref-acker2021}{}}%
+---------. 2021. {``Amazon Development,''} Oxford research encyclopedia
+of latin american history.,.
+\url{https://doi.org/10.1093/acrefore/9780199366439.013.837}.
 
-We now move to mixed types, which average at around 17% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
-While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
-We focus our discussion on those with higher incidence.
-First, the most frequent mix overall is that of economic integration with conservation, which after reaching 25% of all problem-constructions in 1989, remained stable at 9% on average for the remainder of the period.
-President Lula was the most frequent user of this mix.
-Second, except for economic and social development appearing together in all statements made by Color in 1992, mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
-This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation.
-In all, we interpret the appearance of mixed types as more complex understandings of Amazonian problems.
-This follows a global agenda of understanding interconnections of social, environmental, and economic domains.
-As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals.
-Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation.
-This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 28.5% and 28.6% respectively.
-While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty.
-The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro.
+\leavevmode\vadjust pre{\hypertarget{ref-alesina2009}{}}%
+Alesina, Alberto F., and Paola Giuliano. 2009. {``Preferences for
+Redistribution.''} \url{https://www.nber.org/papers/w14825}.
 
-```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+\leavevmode\vadjust pre{\hypertarget{ref-andonova2014}{}}%
+Andonova, Liliana B. 2014. {``Boomerangs to Partnerships? Explaining
+State Participation in Transnational Partnerships for Sustainability.''}
+\emph{Comparative Political Studies} 47 (3): 481--515.
+\url{https://doi.org/10.1177/0010414013509579}.
 
-ama_mx %>%
-  filter(mx_cat2 =="Mixed-type")%>%
-  count(president, mx_cat)%>%
-  group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
-  geom_bar(stat="identity", position="stack")+
-  geom_text(size = 3, position = position_stack(vjust=.5))+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
-  labs(
-    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
-    subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
-    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-    axis.text = element_text(color = "black", size = 10),
-    title = element_text(color = "black", size = 10, face = "bold"),
-    legend.title = element_blank(),
-    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
-```
+\leavevmode\vadjust pre{\hypertarget{ref-assunuxe7uxe3o2015}{}}%
+Assunção, Juliano, Clarissa Gandour, and Rudi Rocha. 2015.
+{``Deforestation Slowdown in the Brazilian Amazon: Prices or
+Policies?''} \emph{Environment and Development Economics} 20 (6):
+697--722. \url{https://doi.org/10.1017/S1355770X15000078}.
 
-@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
-Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
-The costs for said economic and political benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
-Political stability, thus, can be seen as a product of the trade-off between both.
-Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy.
-With the strengthening of environmentalism in the 1990s, its most strong form being the policies adopted in the 2000s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
+\leavevmode\vadjust pre{\hypertarget{ref-bacchi2009}{}}%
+Bacchi, Carol Lee. 2009. \emph{Analysing Policy: What's the Problem
+Represented to Be?} Pearson.
 
-While unprecedented, this new balance was not long-standing.
-Democratic decay is slow and the embryony of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s.
-The hard increase in sovereignty comes in the 2010s.
-As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.
-At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
+\leavevmode\vadjust pre{\hypertarget{ref-barros2020}{}}%
+Barros, Antonio Teixeira de. 2020. {``Discursos parlamentares sobre a
+Amazônia: sobre o que falam os deputados brasileiros.''} \emph{Política
+\& Sociedade} 19 (46): 299--331.
+\url{https://doi.org/10.5007/2175-7984.2020.e66962}.
 
-This is not to say that those who preceded President Bolsonaro are like him.
-They are not, and we have shown how he is different from others already.
-But the political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro's problem-construction is the strongest form of this shift.
-Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+\leavevmode\vadjust pre{\hypertarget{ref-becker2005}{}}%
+Becker, Bertha K. 2005. {``Geopolítica da Amazônia.''} \emph{Estudos
+Avançados} 19 (April): 71--86.
+\url{https://doi.org/10.1590/S0103-40142005000100005}.
 
-## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside
+\leavevmode\vadjust pre{\hypertarget{ref-bevitori2015}{}}%
+Bevitori, Cinzia. 2015. {``Discursive Constructions of the Environment
+in American Presidential Speeches 1960{\textendash}2013: A Diachronic
+Corpus-Assisted Study.''} \emph{Corpora and Discourse Studies}, 110--33.
+\url{https://doi.org/10.1057/9781137431738_6}.
 
-# 5 Conclusion
+\leavevmode\vadjust pre{\hypertarget{ref-brice2021}{}}%
+Brice, and Smith. 2021. {``The Amazon Is Fast Approaching a Point of No
+Return.''} \emph{Bloomberg.com}, July.
+\url{https://www.bloomberg.com/news/features/2021-07-29/amazon-rainforest-deforestation-land-grabs-surge-under-bolsonaro-in-brazil}.
 
-# 6 References
+\leavevmode\vadjust pre{\hypertarget{ref-brown2017}{}}%
+Brown, George, and Benjamin K. Sovacool. 2017. {``The Presidential
+Politics of Climate Discourse: Energy Frames, Policy, and Political
+Tactics from the 2016 Primaries in the United States.''} \emph{Energy
+Policy} 111 (December): 127--36.
+\url{https://doi.org/10.1016/j.enpol.2017.09.019}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calderwood2019}{}}%
+Calderwood, Kevin J. 2019. {``Discourse in the Balance: American
+Presidential Discourse about Climate Change.''} \emph{Communication
+Studies} 70 (2): 235--52.
+\url{https://doi.org/10.1080/10510974.2019.1572636}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calderwood2020}{}}%
+---------. 2020. {``Going Global: Climate Change Discourse in
+Presidential Communications.''} \emph{Environmental Communication} 14
+(1): 52--67. \url{https://doi.org/10.1080/17524032.2019.1592005}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-campbell2015}{}}%
+Campbell, Jeremy M. 2015. \emph{Conjuring Property: Speculation and
+Environmental Futures in the Brazilian Amazon}. Illustrated edition.
+Seattle: University of Washington Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-capobianco2019}{}}%
+Capobianco, João Paulo. 2019. {``Avances y retrocesos de la
+sostenibilidad en la Amazonia: un análisis de la gobernanza
+socioambiental en la Amazonia,''} January.
+\url{https://gredos.usal.es/handle/10366/139311}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-capobianco2021}{}}%
+---------. 2021. \emph{Amazônia: Uma Década de Esperança}. 1ª edição.
+São Paulo: Estação Liberdade.
+
+\leavevmode\vadjust pre{\hypertarget{ref-drummond2006}{}}%
+Drummond, Jose, and Ana Flavia Barros-Platiau. 2006. {``Brazilian
+Environmental Laws and Policies, 1934-2002: A Critical Overview.''}
+\emph{Law \textless Html{\_}ent Glyph={"}@amp;{"}
+Ascii={"}\&amp;{"}/\textgreater{} Policy} 28 (1): 83--108.
+\url{https://doi.org/10.1111/j.1467-9930.2005.00218.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-franchini2019}{}}%
+Franchini, Matias Alejandro, and Eduardo Viola. 2019. {``Myths and
+Images in Global Climate Governance, Conceptualization and the Case of
+Brazil (1989 - 2019).''} \emph{Revista Brasileira de Política
+Internacional} 62 (September).
+\url{https://doi.org/10.1590/0034-7329201900205}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-garfield2013}{}}%
+Garfield, Seth. 2013. \emph{In Search of the Amazon: Brazil, the United
+States, and the Nature of a Region}. Durham: Duke University Press
+Books.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harris2021}{}}%
+Harris, Bryan. 2021. {``Drought Puts Amazon at Risk of {`}Large-Scale
+Dieback{'}, Researchers Warn.''} \emph{Financial Times}, July.
+\url{https://www.ft.com/content/02071ae7-dcf5-4c61-9c3c-b55f5aef8b0e}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hecht2013}{}}%
+Hecht, Susanna B. 2013. \emph{The Scramble for the Amazon and the
+{"}Lost Paradise{"} of Euclides Da Cunha}. First edition. Chicago:
+University of Chicago Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hecht1990}{}}%
+Hecht, Susanna B., and Alexander Cockburn. 1990. \emph{The Fate of the
+Forest: Developers, Destroyers, and Defenders of the Amazon, Updated
+Edition}. Chicago, IL: University of Chicago Press.
+\url{https://press.uchicago.edu/ucp/books/book/chicago/F/bo10387801.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirschman1963}{}}%
+Hirschman, Albert O. 1963. \emph{Journeys Toward Progress: Studies of
+Economic Policy-Making in Latin America}. Twentieth Century Fund.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirschman1975}{}}%
+---------. 1975. {``Policymaking and Policy Analysis in Latin America: A
+Return Journey.''} \emph{Policy Sciences} 6 (4): 385--402.
+\url{https://www.jstor.org/stable/4531616}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2021}{}}%
+Hochstetler, Kathryn. 2021. {``Climate Institutions in Brazil: Three
+Decades of Building and Dismantling Climate Capacity.''}
+\emph{Environmental Politics} 30 (sup1): 49--70.
+\url{https://doi.org/10.1080/09644016.2021.1957614}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2007}{}}%
+Hochstetler, Kathryn, and Margaret E. Keck. 2007. \emph{Greening Brazil:
+Environmental Activism in State and Society}.
+\url{https://doi.org/10.1215/9780822390596}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miranda2021}{}}%
+Miranda, David. 2021. {``Bolsonaro{'}s 1,000km Amazon Railway Will Cause
+Climate Chaos. It Must Be Stopped.''} \emph{The Guardian}, July.
+\url{https://www.theguardian.com/commentisfree/2021/jul/28/bolsonaro-amazon-railway-climate-chaos-must-be-stopped}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pacheco2019}{}}%
+Pacheco, João. 2019. \emph{Ecxterminio y Tutela: Procesos de Formación
+de Alteridades En El Brasil}. UNSAM Edita. Ciencias sociales.
+\url{http://www.unsamedita.unsam.edu.ar/product/exterminio-y-tutela-procesos-de-formacion-de-alteridades-en-el-brasil/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lepolaindewaroux2021}{}}%
+Polain de Waroux, Yann le, Rachael D. Garrett, Mollie Chapman, Cecilie
+Friis, Jeffrey Hoelle, Leonie Hodel, Kelly Hopping, and Julie Gwendolin
+Zaehringer. 2021. {``The Role of Culture in Land System Science.''}
+\emph{Journal of Land Use Science} 16 (4): 450--66.
+\url{https://doi.org/10.1080/1747423X.2021.1950229}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-putnam1988}{}}%
+Putnam, Robert D. 1988. {``Diplomacy and Domestic Politics: The Logic of
+Two-Level Games.''} \emph{International Organization} 42 (3): 427--60.
+\url{https://www.jstor.org/stable/2706785}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-silva-muller2022}{}}%
+Silva-Muller, Livio, and Moira Faul. 2022. {``Protecting the Amazon and
+Its People: The Role of Civil Society in the Local Effectiveness of
+Transnational Partnerships.''} In, 1st ed., 288. Routledge Research in
+Environmental Policy and Politics. Taylor; Francis Routledge.
+\url{https://www.routledge.com/Partnerships-for-Sustainability-in-Contemporary-Global-Governance-Pathways/Andonova-Faul-Piselli/p/book/9780367708870\#:~:text=\%22Partnerships\%20for\%20Sustainability\%20provides\%20a,collaboration\%20of\%20public\%20and\%20private.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-westerwinter2021}{}}%
+Westerwinter, Oliver. 2021. {``Transnational Public-Private Governance
+Initiatives in World Politics: Introducing a New Dataset.''} \emph{The
+Review of International Organizations} 16 (1): 137--74.
+\url{https://doi.org/10.1007/s11558-019-09366-w}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zarefsky2004}{}}%
+Zarefsky, David. 2004. {``Presidential Rhetoric and the Power of
+Definition.''} \emph{Presidential Studies Quarterly} 34 (3): 607--19.
+\url{https://www.jstor.org/stable/27552615}.
+
+\end{CSLReferences}
+
+\end{document}

### 2022-04-06 Draft_April_2022/Full_draft_20220401.rmd
#newstuff
predicted figure 1; updated rmd and qmd

@@
 output:
+  html_document:
+    df_print: paged
+  pdf_document: default
   word_document:
     reference_docx: template.docx
-  pdf_document: default
-  html_document:
-    df_print: paged
 bibliography: references.bib
@@
 First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
-In turn, policy perception is key for policy adoption and implementation [@alesina2009].
+In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lópez2020].
 The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021].
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The smoothed curved controls incidence deforestation rates, economic situation, and election year (see appendix for methodological details).
+The smoothed curved controls incidence for deforestation rates, economic situation, speaker, and election year (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019.

### 2022-04-06 analysis/analysis_livio.Rmd
#newstuff
predicted figure 1; updated rmd and qmd

--- 2022-04-01 analysis/analysis_livio.Rmd
@@
           select(-c(title, date, text, location))
+
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
+
+amazon_def_year <- amazon_def_year %>% rename(def_year = "area km\u00b2")
+
+amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>%
+  rename(def_year = "area km\u00b2")
 
@@
   left_join(perc1) %>%
+  left_join(amazon_def_year)%>%
+  filter(amazon_speech==1) %>%
+  ggplot(., aes(x = year, y = perc)) +
+  geom_smooth(color="black", size=.75, se=FALSE, method="loess")+
+  geom_line(color="darkolivegreen")+
+  scale_y_continuous(labels = percent_format())+
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
+  labs(
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+    subtitle = "Sample composed by 6130 presidential speeches since 1985",
+    caption = "") +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "right"
+  )
+
+```
+
+```{r Amazonian speeches by year II, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}
+
+  perc1 <- pop %>%
+  count(amazon_speech, year)%>%
+  group_by(year)%>%
+  mutate(perc=n / sum(n)) %>%
+  select(c(perc,amazon_speech, year))
+
+pop %>% count(amazon_speech, year) %>%
+  group_by(year) %>%
+  left_join(perc1) %>%
   filter(amazon_speech==1) %>%
@@
     legend.position = "right"
+  )
+
+```
+
+```{r Amazonian speeches by year III, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}
+
+pop2 <- pop %>% count(amazon_speech, year, president) %>%
+  group_by(year, president) %>%
+  left_join(perc1) %>%
+  filter(amazon_speech==1) %>%
+  mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+
+  pop2 <- left_join(pop2, AAI, by = "year")
+  pop2 <- left_join(pop2, amazon_def_year, by = "year")
+
+model <- lm(perc ~ AAI+ def_year + president + election_year, data=pop2)
+
+pop2$predicted = predict(model, pop2)
+
+pop2 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(size=.65, aes(x=year, y=perc, color="real share"), linetype= "solid")+
+  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="dotted")+
+  scale_color_manual(values=c("real share"="darkolivegreen", "Predicted share"= "black"))+
+  scale_y_continuous(labels = percent_format())+
+  labs(
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+    subtitle = "Sample composed by 6130 presidential speeches since 1985",
+    caption = "Predicted share curve controls for yearly deforestation rates, yearly inflation, and president", color='Y series') +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "bottom"
   )

### 2022-04-06 analysis/analysis_livio.Rmd

@@
 AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
-
-amazon_def_year <- amazon_def_year %>% rename(def_year = "area km\u00b2")
 
@@
   left_join(perc1) %>%
-  filter(amazon_speech==1) %>%
-  mutate(election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+  filter(amazon_speech==1)
 
@@
 
-model <- lm(perc ~ AAI+ def_year + president + election_year, data=pop2)
+model <- lm(perc ~ AAI+ def_year + president, data=pop2)
 
@@
 pop2 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(size=.65, aes(x=year, y=perc, color="real share"), linetype= "solid")+
-  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="dotted")+
+  geom_line(size=.75, aes(x=year, y=perc, color="real share"), linetype= "solid")+
+  geom_line(size=.5, aes(x=year, y=predicted, color="Predicted share"), linetype="solid")+
   scale_color_manual(values=c("real share"="darkolivegreen", "Predicted share"= "black"))+

### 2022-04-06 Draft_April_2022/Full_draft_20220401.qmd

--- 2022-04-03 Draft_April_2022/Full_draft_20220401.qmd
@@
 ---
-title: "How has the Brazilian Amazon been constructed as a problem? An analysis of presidential speeches since 1985"
-format:
-  docx:
-    toc: false
-    reference-doc: "template.docx"
-    section-numbers: true
-    highlight-style: github
+title: How has the Brazilian Amazon been constructed as a problem? An analysis of
+  presidential speeches since 1985
+author:
+- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
+- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+date: "April 2022"
+output:
+  html_document:
+    df_print: paged
+  word_document:
+    reference_docx: template.docx
+bibliography: references.bib
+csl: chicago.csl
 abstract: This paper ...
-output: docx
-author:
-- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+---
 
-date: "April 2022"
-
----
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 
+\pagebreak
+
 # 1 Introduction
 
+The Amazon needs to be protected from foreign interests.
+The Amazon needs to be exploited for its natural resources.
+The Amazon should be preserved as a standing ecosystem.
+Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon.
+Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or the peoples as a particular problem.
+In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
+Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@acker2014; @hecht1990; @hochstetler2007].
+However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
+Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.
+
+In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
+Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments.
+Although problem-construction takes place in a series of instances (e.g.
+policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985.
+We opt for presidential speeches for three reasons.
+First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+In turn, policy perception is key for policy adoption and implementation [@alesina2009].
+The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021].
+Thus, understanding how policy comes about discursively is important.
+Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmer[@brice2021; @harris2021; @miranda2021].
+This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015].
+Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated.
+Finally, as our theoretical framework suggests, problem-construction varies by geographic location.
+Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city.
+Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
+
+To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
+We subset the dataset by identifying Amazonian related statements within these speeches.
+We find that 2014 sections in these discourses refer to the Amazon at least once.
+We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem.
+We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
+Using R, we then train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
+We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.
+
+(Summarize findings, conceptual contribution, and empirical contribution).
+Conceptually, our approach is underpinned by a constructivist view of policy making, which allocates agency to different actors in building policy discursively.
+Empirically, we provide the first comprehensive overview of how the Brazilian Amazon has been constructed as a problem in presidential speeches.
+
+This article proceeds as follows: first, we review Amazonian literature to identify the main ways in which it was constructed as a problem.
+We then propose a theoretical framework to understand problem-construction.
+In the methodology section, we operationalize our framework and the Amazonian problem-constructions.
+Section four portrays our main results over time and by speaker.
+Finally, we conclude by discussing our findings and proposing future research.
+
 # 2 Amazonian policy-cycles, discourse, and problem-construction
+
 ## 2.1 Literature Review: policy-cycles in the Amazonian literature
+
+For the purposes of this article, we understand Amazonian literature as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.
+The three main policy-cycles we identify in Amazonian literature are: national sovereignty, economic integration, and environmental conservation.
+We tie each one of them to a specific problem and consequently a solution.
+We close the sub-section reviewing the relationship between policy, presidential discourse, and environmental problems.
 
@@
 
+In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" \[-@hecht1990, pp.1\].
+It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders.
+The dream of fortunes to be found in the Eldorado composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else.
+It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" (Hecht and Cockburn 1990, preface).
+The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
+In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" \[@hecht2013, pp.8\], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
+While Brazilian military diplomacy was very successful, the process did not come without its traumas.
+A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil[@hecht1990].
+This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War[@garfield2013].
+As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
+Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
+Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
+False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
+Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
+
+[^1]: B*andeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established.
+The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
+
+The sovereignty problem advances the view that the Brazilian Amazon is Brazilian and foreign presence, non-state presence and alleged lies are part of a broader strategy to internationalize the region.
+The policy solutions relate to close monitoring of the borders, strict regimes related to entry in the region, and combating alleged disinformation about the Amazon nationally and internationally.
+
 ### 2.1.2 Economic integration
+
+The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon.
+In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
+First, nature should be conquered by men.
+Second, exploiting natural resources would render the Amazon region a global powerhouse.
+Third, such a project would integrate the region with the rest of the country.
+Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
+The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
+@capobianco2019 describes the period from the 1950-80 in a similar fashion, referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.
+
+The economic integration problem advances the view that the Brazilian Amazon needs to be developed and modernized.
+The policy solution relates to the creation of a series of policies, often centralized by the federal government and thus external to the region [@becker2005], that have at its core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.
 
@@
 
+The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
+A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of economic integration.
+[@acker2021; @capobianco2021; @hecht1990].
+As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
+This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco, 2019; Hochstetler and Keck, 2007).
+@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
+They define it as an emphasis on local livelihoods of people while protecting nature.
+@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.
+
+The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
+The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing eco-systems through incentive schemes, and more policies facilitating indigenous environmental practices.
+
 ### 2.1.4 Policy and discourse
 
+Different authors have proposed similar periodization for policy-cycles in the Amazon: a focus on sovereignty until the military dictatorship of 1964, followed by strong economic integration policies until the mid 1980s, and finally a shift to conservation after the 1992 Earth Summit.
+At the macro-historical level, the wider Amazonian vision of the 1964 military dictatorship, encompassed by the whole group of policies they adopted, for instance, did favor economic integration.
+Nevertheless, at the level of policies adopted, there is more variation than these periods would suggest.
+For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest.
+Framing the policy as an issue of economic integration, then, can be seen as a choice.
+
+Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently.
+For historical inquiry, it is important to periodize policy cycles comprehensively and coherently.
+We largely agree with what the literature assigns to previous governments.
+However, the possibility of varied portrayals of the same policy opens possibilities of understanding agenda-setting and policy-adoption in less linear ways.
+
+Problem-construction at the level of discourse is also more varied.
+They are not monolithic in time, across location, or even by the same speaker.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse.
+@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
+The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+
+While we find no major studies systematically looking into Amazonian related themes in Brazilian presidential speeches, we find, for example, several analyzes of environmental discourse in American presidential speeches.
+@calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989.
+Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change (ibid).
+He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
+In another article, @calderwood2020 tests the effect of geographic location and type of communication regarding climate change.
+Building prominently on @putnam1988 but also others, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
+He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on climate change does change based on location.
+Another example is @bevitori2015, who investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
+The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
+
+While these findings hold for the US, they suffice to argue that presidents can raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance.
+That entails the same president can combine, substitute, or change how they talk about the Amazon and these views can reflect, or not, the current political scenario, issues in the agenda, or talk to a different policy cycle at times.
+
 ## 2.2 Theoretical framework: problem-construction and presidential discourse
+
+In "Journey towards Progress", Hirschman (1963) analyzes three policy problems in three different Latin American countries.
+The author draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
+Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
+Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests\[@hirschman1963, pp.388-91\].
+Choosing a problem, though, entails a decision on how to represent it[@bacchi2009].
+As Bacchi puts "policy has a cultural dimension.
+It takes shape within specific historical and national or international contexts" \[-@bacchi2009, pp.10\].
+The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid).
+The alleged problem is not always explicitly stated in policy.
+Hirschman exemplifies chosen problems with the case of the construction of Brasilia \[-@hirschman1975, pp.388\].
+But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
+How to represent a policy is a matter of choice.
+And different representations speak to different audiences.
+
+We understand that depending on how the problem is represented to be, it can be a solution of problems that are considered pressing.
+Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
+Problem-construction takes place in different sites: national media, legislative bodies, international fora, among others.
+What eventually becomes policy is a product of a multi-faceted process in all these different sites.
+One avenue through which governments can emphasize the representations of a problem is discourse.
+We assume that problem-construction at the level of discourse is varied.
+They are not monolithic in time, across location, or even by the same speaker.
+
+We argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context.
+In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connect the region to issues of sovereignty, economic integration, social development, or environmental conservation.
+Presidents choose to represent the region as a particular problem.
+As Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
+Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country.
+We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment (Bevitori, 2015) without embedding them in the histories of the term in the country.
+
+These are the cornerstones of our framework: while governments are sometimes portrayed as proponents of a specific policy-solution, the way they construct the Amazon as a problem varies.
+The specific problem-constructions that we propose are embedded in Amazonian historiography and connect presidential speeches to Brazilian larger social-cultural history.
+We propose a framework to understand variation in problem-construction as a choice that is responsive to geographic location, time, and speaker.
 
@@
 
+This section presents the three main findings of our analysis.
+We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985.
+In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.
+Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.
+
 ## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
 
-```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}
+Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
+The smoothed curved controls incidence deforestation rates, economic situation, and election year (see appendix for methodological details).
+We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019.
+These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+
+First, we observe a steady increase from about 5% in 1985 to 32% 1989.
+This is the period when the Brazilian Constitution was being written.
+Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories [@hecht1990].
+These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
+Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered, and in 1989, the New York Times published an article with pictures of the Amazon burning.
+Both incidents caught unprecedented international attention.
+President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza [@capobianco2021]
+
+```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
 
@@
 
+While in 1990 there was a decrease to about 12.4%, we observe a novel increase to 15% and 25% in 1991 and 1992 respectively.
+The driver of this increase is likely to be the 1992 Earth Summit, which was being prepared by various state and non-state actors in the region and brought international attention to environmental topics in Brazil.
+One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (cite).
+During the Cardoso years (1994-2002), Amazonian speeches averaged at about 15% without strong variation.
+There were no big international or domestic events that drove the topic up.
+
+We observe an increase from 8.5% in 2004 to 22.8% in the year of the Copenhagen Summit, 2009.
+This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history.
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" [@franchini2019], when stakes about climate change were high.
+A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
+From 2010 to 2014, we identify a steady decrease from 18.2% to 8.2%, which is followed by a sharp increase in the year of the COP, reaching 19.2%.
+These are the years when Brazil entered a long period of political and economic instability that lingers until today.
+Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted.
+
+We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
+As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts, reaching unprecedented coverage.
+Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019.
+President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda.
+President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
+
+We do find evidence that deforestation rates, economic situation, elections, and simply preferential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
+However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events.
+We are yet to inspect, though, whether specific problem constructions about the Amazon change over time.
+
 ## 4.2 Amazonian problem-construction in time
 
-```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+Figure 2 portrays plots with the proportions of different problem constructions over time.
+We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
+At the level of the Amazonian statement, though, presidents might mix two or more together.
+These are what we call mixed types, in opposition to pure types.
+There are 16 mix types in total, and figure 2 portrays the most frequent of them.
+Pure problem constructions dominate, with their joint average above 55%.
+Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.
+
+```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
 
-```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+The plots reveal several trends.
+Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s.
+In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
+This is aligned with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
+As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+
+Figure 3 (below) shows these shifts more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
+Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation.
+The starkest decrease relates to social development construction between Temer's and Bolsonaro's administration.
+
+```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
 
-```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
+We now move to mixed types, which average at around 17% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
+While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
+We focus our discussion on those with higher incidence.
+First, the most frequent mix overall is that of economic integration with conservation, which after reaching 25% of all problem-constructions in 1989, remained stable at 9% on average for the remainder of the period.
+President Lula was the most frequent user of this mix.
+Second, except for economic and social development appearing together in all statements made by Color in 1992, mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
+This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation.
+In all, we interpret the appearance of mixed types as more complex understandings of Amazonian problems.
+This follows a global agenda of understanding interconnections of social, environmental, and economic domains.
+As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals.
+Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation.
+This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 28.5% and 28.6% respectively.
+While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty.
+The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro.
+
+```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
 
+@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
+Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
+The costs for said economic and political benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
+Political stability, thus, can be seen as a product of the trade-off between both.
+Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy.
+With the strengthening of environmentalism in the 1990s, its most strong form being the policies adopted in the 2000s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
+
+While unprecedented, this new balance was not long-standing.
+Democratic decay is slow and the embryony of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
+We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s.
+The hard increase in sovereignty comes in the 2010s.
+As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.
+At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
+
+This is not to say that those who preceded President Bolsonaro are like him.
+They are not, and we have shown how he is different from others already.
+But the political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
+Bolsonaro's problem-construction is the strongest form of this shift.
+Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+
 ## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside

### 2022-04-06 Draft_April_2022/Full_draft_20220401.rmd
#newstuff
predicted figure 1; updated rmd and qmd
Updated modeling in rmd file and some datasets

@@
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
-
 knitr::opts_chunk$set(include = FALSE)
@@
 library(stargazer)
-
 Sys.setlocale("LC_ALL", "C")
-
 options(stringsAsFactors = FALSE, scipen = 999)
-
 ```
@@
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
-
 pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
+pop <-  pop %>% select(-c(title, date, text, location))
 ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
-
-ama <-  ama %>%
-          select(-c(title, date, text, false_positives)) %>%
-          rename (ei= "EI") %>%
-          rename (sd= "SD")
-
-pop <-  pop %>%
-          select(-c(title, date, text, location))
-
+ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
 ```
@@
 ```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
 sov <- ama %>% 
@@
   rename (sov = n)
-
 ei <- ama %>% 
@@
   tibble::add_row(year = 2018, ei = 0)
-
 sd <- ama %>% 
@@
   rename (sd = n)
-
 con <- ama %>% 
@@
   rename (con = n)
-
 other <- ama %>% 
@@
   rename (other = n)
-
 temp <- ei %>% left_join(other) %>% 
@@
                 replace(is.na(.), 0)
-
 ```
@@
 ```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
 ama_mx <-  ama %>%
   unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat= case_when (mixed_type=='1_0_0_0' ~ "Pure Sovereignty",
-                            mixed_type=='0_1_0_0' ~ "Pure Economic Integration",
-                            mixed_type=='0_0_1_0' ~ "Pure Social Development",
-                            mixed_type=='0_0_0_1' ~ "Pure Conservation",
-                            mixed_type=='0_0_0_0' ~"Other",
-                            mixed_type=='0_1_0_1' ~"Economic Conservation",
-                            mixed_type=='0_1_1_0' ~"Economic and Social Development",
-                            mixed_type=='1_0_0_1' ~"Sovereign Conservation",
-                            mixed_type=='0_1_1_1' ~ "Sustainable Development",
-                            mixed_type=='1_1_0_0'~ "Sovereign Integration",
-                            mixed_type=='0_0_1_1' ~"Social Conservation",
-                            mixed_type=='1_1_0_1' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_1_1_1' ~"Other Mixed-types",
-                            mixed_type=='1_1_1_0' ~"Other Mixed-types",
-                            mixed_type=='1_0_1_1' ~"Other Mixed-types"))%>%
-  mutate(mx_cat=factor(mx_cat, levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development", "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development", "Sovereign Conservation","Sustainable Development","Sovereign Integration", "Social Conservation", "Other Mixed-types"))) %>%
-mutate(mx_cat2= case_when (mixed_type=='1_0_0_0' ~ "Pure-type",
-                            mixed_type=='0_1_0_0' ~ "Pure-type",
-                            mixed_type=='0_0_1_0' ~ "Pure-type",
-                            mixed_type=='0_0_0_1' ~ "Pure-type",
-                            mixed_type=='0_0_0_0' ~"Other",
-                            mixed_type=='0_1_0_1' ~"Mixed-type",
-                            mixed_type=='0_1_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_0_1' ~"Mixed-type",
-                            mixed_type=='0_1_1_1' ~ "Mixed-type",
-                            mixed_type=='1_1_0_0'~ "Mixed-type",
-                            mixed_type=='0_0_1_1' ~"Mixed-type",
-                            mixed_type=='1_1_0_1' ~"Mixed-type",
-                            mixed_type=='1_0_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_1_0' ~"Mixed-type",
-                            mixed_type=='1_1_1_1' ~"Mixed-type",
-                            mixed_type=='1_1_1_0' ~"Mixed-type",
-                            mixed_type=='1_0_1_1' ~"Mixed-type"))
-
+  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
+                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
+                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
+                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
+                                      mixed_type == '0_0_0_0' ~ "Other",
+                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
+                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
+                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
+                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
+                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
+                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
+                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
+                                            mixed_type) ~ "Other Mixed-types"),
+         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
+                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
+                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
+                    "Social Conservation", "Other Mixed-types")),
+         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
+                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
+                             grepl("^Other$", mx_cat) ~ "Other",
+                             grepl("Economic Conservation|Economic and Social Development|
+                                   |Sovereign Conservation|Sustainable Development|
+                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
+                                   mx_cat) ~ "Mixed-types"))
 ```
@@
 ```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
-
 perc1 <- pop %>%
@@
   select(c(perc,amazon_speech, year))
-
-pop %>% count(amazon_speech, year) %>%
+Amazon_year <- pop %>%
+  count(amazon_speech, year) %>%
   group_by(year) %>%
@@
   scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-    subtitle = "Sample composed by 6130 presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
+  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+       subtitle = "Sample composed by 6130 presidential speeches since 1985", caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "right"
-  )
-
+        legend.position = "right")
+Amazon_year
 ```
@@
 ```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
-ama_mx %>%
+prob_construction_year <- ama_mx %>%
   count(year, mx_cat)%>%
   group_by(year) %>%
-  mutate(perc=n / sum(n))  %>%
-  ggplot(., aes(x=year, y=perc, fill=mx_cat))+
-  geom_bar(stat="identity", position="dodge")+
-  geom_smooth(color="black", size=.3, se= FALSE)+
-  scale_y_continuous(labels = percent_format(accuracy=1))+
-  labs(
-    x = "", y = "", title ="Share of different problem-constructions by year",
-    subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985",
-    caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
+  mutate(perc = n / sum(n)) %>%
+  ggplot(aes(x=year, y=perc, fill=mx_cat)) +
+  geom_bar(stat="identity", position="dodge") +
+  geom_smooth(color="black", size=.3, se= FALSE) +
+  scale_y_continuous(labels = percent_format(accuracy=1)) +
+  labs(x = "", y = "", title ="Share of different problem-constructions by year",
+       subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985", caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "none"
-  )+
+        legend.position = "none") +
   facet_wrap(~ mx_cat, ncol=3, scales="free_y")
-
+prob_construction_year
 ```
@@
 ```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
-ama_mx %>%
-  count(president, mx_cat, mx_cat2)%>%
-  group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  filter(mx_cat !="Other")%>%
-  filter(mx_cat2 == "Pure-type") %>%
-  mutate(year= case_when (president=='Sarney' ~ "1985",
-                          president=='Bolsonaro' ~ "2018",
-                          president=='Collor' ~ "1990",
-                          president=='Itamar' ~ "1993",
-                          president=='FHC' ~ "1994",
-                          president=='Lula' ~ "2003",
-                          president=='Dilma' ~ "2011",
-                          president=='Temer' ~ "2017"))%>%
-  ggplot(., aes(x=as.numeric(year), y=perc, color=mx_cat))+
-  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5)+
-  scale_y_continuous(labels = percent_format(accuracy=1))+
-  labs(
-    x = "", y = "", title ="Share of each pure types by year",
+pure_types_time <- ama_mx %>%
+  count(president, mx_cat2, mx_cat, year) %>%
+  group_by(president, year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>% 
+  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
+  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
+  scale_y_continuous(labels = percent_format(accuracy=1)) +
+  labs(x = "", y = "", title ="Share of each pure types by year",
        subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
        caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
-
+        legend.position = "bottom")
+pure_types_time
 ```
@@
 ```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
-ama_mx %>%
-  filter(mx_cat2 =="Mixed-type")%>%
-  count(president, mx_cat)%>%
+mixed_types_presid <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(president, mx_cat) %>%
   group_by(president) %>%
-  mutate(perc=n / sum(n)) %>%
-  mutate(president=factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(., aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1)))+
-  geom_bar(stat="identity", position="stack")+
-  geom_text(size = 3, position = position_stack(vjust=.5))+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1)+
-  labs(
-    x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+  mutate(perc = n / sum(n)) %>%
+  mutate(president = factor(president,
+                            levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat="identity", position="stack") +
+  geom_text(size = 3, position = position_stack(vjust=.5)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
        subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
        caption = "") +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
+        legend.position = "bottom")
+mixed_types_presid
 ```
@@
 
+```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+# get data on deforestation rates per year (PRODES)
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
+# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
+# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
+# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
+adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
+amazon_def_year <- rbind(adr, amazon_def_year)
+ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
+# inflation rates per year Brazil (average for year)
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
+# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
+ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
+# remove non-identified locations and mixed-other constructions (very little data for either and not relevant)
+ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
+  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
+                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
+                                            "Economic and Social Development", "Sovereign Conservation",
+                                            "Sustainable Development","Sovereign Integration",
+                                            "Social Conservation", "Other")),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+# model
+model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE)
+# summary statistics
+model_summary <- summary(model)
+p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
+# post estimation tests
+chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
+# Chi-square p value (p-value < 0.001) tells us that our model explains a
+# significant amount of the variation in the data in comparison with a null model.
+# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
+# library(lmtest)
+# lrtest(null_model, model) # We very much reject the hypothesis
+# (i.e. the more complex model is significantly better than the null model).
+# Finally, let's get a nice output:
+stargazer::stargazer(model, type="text",
+                     covariate.labels = c("Brasilia", "International", "Non-AM state",
+                                          "Election", "Deforestation", "Inflation"),
+                     column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
+                                       "Sov-EI", "SD-Con", "Other"),
+                     dep.var.labels.include = FALSE)
+```
+
 # 5 Conclusion

### 2022-04-06 analysis/Modelling Final.Rmd
Updated modeling in rmd file and some datasets

@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
-amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>% # yearly deforestation rates only come out the year after
-  rename(def_year = `area km²`)
 ama_model2 <- dplyr::left_join(ama_model2, amazon_def_year, by = "year") # merge

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
#figure1 w/ controlled line

@@
 ```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
-perc1 <- pop %>%
-  count(amazon_speech, year)%>%
-  group_by(year)%>%
-  mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, year))
-Amazon_year <- pop %>%
-  count(amazon_speech, year) %>%
-  group_by(year) %>%
+
+pop2 <- pop %>% count(amazon_speech, year, president) %>%
+  group_by(year, president) %>%
   left_join(perc1) %>%
-  filter(amazon_speech==1) %>%
-  ggplot(., aes(x = year, y = perc)) +
-  geom_line(color="darkolivegreen")+
+  filter(amazon_speech==1)
+
+  pop2 <- left_join(pop2, AAI, by = "year")
+  pop2 <- left_join(pop2, amazon_def_year, by = "year")
+
+model <- lm(perc ~ AAI+ def_year + president, data=pop2)
+
+pop2$predicted = predict(model, pop2)
+
+Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
+  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
+  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
   scale_y_continuous(labels = percent_format())+
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= -1)+
-  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-       subtitle = "Sample composed by 6130 presidential speeches since 1985", caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
+  labs(
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+    subtitle = "Sample composed by 6130 presidential speeches since 1985",
+    caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
     panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
     plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "right")
+    legend.position = "bottom"
+  )
+
 Amazon_year

### 2022-04-07 analysis/analysis_livio.Rmd
#figure1 w/ controlled line

--- 2022-04-05 analysis/analysis_livio.Rmd
@@
 
-amazon_def_year <- mutate(amazon_def_year, year = year + 1) %>%
-  rename(def_year = "area km\u00b2")
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
 
@@
     legend.position = "right"
+  )
+
+```
+
+```{r Amazonian speeches by year III, echo=FALSE, message=FALSE, warning=TRUE, echo=FALSE, paged.print=TRUE}
+
+pop2 <- pop %>% count(amazon_speech, year, president) %>%
+  group_by(year, president) %>%
+  left_join(perc1) %>%
+  filter(amazon_speech==1)
+
+  pop2 <- left_join(pop2, AAI, by = "year")
+  pop2 <- left_join(pop2, amazon_def_year, by = "year")
+
+model <- lm(perc ~ AAI+ def_year + president, data=pop2)
+
+pop2$predicted = predict(model, pop2)
+
+pop2 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
+  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
+  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
+  scale_y_continuous(labels = percent_format())+
+  labs(
+    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+    subtitle = "Sample composed by 6130 presidential speeches since 1985",
+    caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
+  theme(
+    panel.background = element_rect("white", "black", .5, "solid"),
+    panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+    axis.text = element_text(color = "black", size = 10),
+    title = element_text(color = "black", size = 10, face = "bold"),
+    legend.title = element_blank(),
+    plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+    legend.position = "bottom"
   )

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd

@@
 output:
+  word_document:
+    reference_docx: template.docx
+  pdf_document: default
   html_document:
     df_print: paged
-  pdf_document: default
-  word_document:
-    reference_docx: template.docx
 bibliography: references.bib
@@
 ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
+AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+
 ```
@@
 The Amazon needs to be exploited for its natural resources.
-The Amazon should be preserved as a standing ecosystem.
+The Amazon needs to be preserved as a standing ecosystem.
 Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon.
-Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or the peoples as a particular problem.
+Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or its peoples as a particular problem.
 In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
@@
 However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
-Albeit the current academic calls to understand the environment as a social-cultural construction and to identify the effect of culture for environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time and across locations, and how this varies.
+Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time, by geographical location, and between and within governments
 
 In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction varies over time, by location, and between and within governments.
+Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction.
 Although problem-construction takes place in a series of instances (e.g.
@@
 First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
-In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lópez2020].
-The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assunção2015; @capobianco2019; @capobianco2021].
+In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
+The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
 Thus, understanding how policy comes about discursively is important.
 Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally, but also incites responses, shapes expectations, and feeds into the behavior of many actors involved with the Amazon, from investors to agribusiness to local farmer[@brice2021; @harris2021; @miranda2021].
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally[@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon, from investors to agribusiness to local farmer.
 This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015].
@@
 Finally, as our theoretical framework suggests, problem-construction varies by geographic location.
-Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York city.
+Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York.
 Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
@@
 
-(Summarize findings, conceptual contribution, and empirical contribution).
-Conceptually, our approach is underpinned by a constructivist view of policy making, which allocates agency to different actors in building policy discursively.
-Empirically, we provide the first comprehensive overview of how the Brazilian Amazon has been constructed as a problem in presidential speeches.
+Our findings are threefold.
+First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon.
+That seems to be the case even after controling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker.
+Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation.
+This trend is reversed in the late 2010s, with the twist of sovereignty making a strong comeback.
+Finally, using a multinominal model, we find that the farthest away the speaker is from the Amazon, be it within the country in non-Amazonian States or outside Brazil, the more likely the speaker is to construct the Amazon as a problem of environmental conservation than economic integration or social development.
 
-This article proceeds as follows: first, we review Amazonian literature to identify the main ways in which it was constructed as a problem.
-We then propose a theoretical framework to understand problem-construction.
-In the methodology section, we operationalize our framework and the Amazonian problem-constructions.
-Section four portrays our main results over time and by speaker.
+This article proceeds as follows: first, we review Amazonian literature to identify the main policy-cycles and their underlying problem construction.
+We then propose a theoretical framework to understand problem-construction and discourse.
+In the methodology section, we operationalize our framework and present the codebook.
+Section four portrays our main results.
 Finally, we conclude by discussing our findings and proposing future research.
@@
 This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War[@garfield2013].
+
+[^1]: *Bandeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established.
+The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
+
 As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
@@
 Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-False claims about Brazilian policies in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
-
-[^1]: B*andeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established.
-The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
+Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
+This might come both from foreign actors as well as domestic non-state actors.
+Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies
 
@@
 
-The dictatorships of Vargas (1937-46) and the military (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military dictatorship launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
+The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
+In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
 First, nature should be conquered by men.
@@
 
-The rapid economic changes in the region in the 1960s, 70s, and 80s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
-A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of economic integration.
-[@acker2021; @capobianco2021; @hecht1990].
+The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
+A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of centalized economic integration policies [@acker2021; @capobianco2021; @hecht1990].
 As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
-This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco, 2019; Hochstetler and Keck, 2007).
+This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
 @hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
@@
 The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
-The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing eco-systems through incentive schemes, and more policies facilitating indigenous environmental practices.
+The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
 
@@
 For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest.
-Framing the policy as an issue of economic integration, then, can be seen as a choice.
+Framing this policy as an issue of economic integration, then, can be seen as a choice.
 
 Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently.
-For historical inquiry, it is important to periodize policy cycles comprehensively and coherently.
+For historical inquiry, it is important to periodize policy cycles comprehensively.
 We largely agree with what the literature assigns to previous governments.
-However, the possibility of varied portrayals of the same policy opens possibilities of understanding agenda-setting and policy-adoption in less linear ways.
+However, the possibility of varied portrayals of the same policy opens up an understanding agenda-setting and policy-adoption that is less linear.
 
@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that in congress the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
 
-While we find no major studies systematically looking into Amazonian related themes in Brazilian presidential speeches, we find, for example, several analyzes of environmental discourse in American presidential speeches.
+We also find several analyzes of environmental discourse in American presidential speeches.
 @calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989.
@@
 Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
-Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests[@hirschman1963, pp.388-91].
-Choosing a problem, though, entails a decision on how to represent it[@bacchi2009].
+Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests [@hirschman1963, pp.388-91].
+Choosing a problem, though, entails a decision on how to represent it [@bacchi2009].
 As Bacchi puts "policy has a cultural dimension.
 It takes shape within specific historical and national or international contexts" [-@bacchi2009, pp.10].
-The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed (ibid).
+The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed.
 The alleged problem is not always explicitly stated in policy.
@@
 Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-Problem-construction takes place in different sites: national media, legislative bodies, international fora, among others.
+Problem-construction takes place in different sites: national media, legislative bodies, international fora, policy committees, among others.
 What eventually becomes policy is a product of a multi-faceted process in all these different sites.
@@
 Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country.
-We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment (Bevitori, 2015) without embedding them in the histories of the term in the country.
+We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment [@bevitori2015] without embedding them in the histories of the issue in the country.
 
@@
 We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985.
-In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.
+In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1.
 Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The smoothed curved controls incidence for deforestation rates, economic situation, speaker, and election year (see appendix for methodological details).
-We observe various local maxima: 1989, 1992, 2004, 2009, 2015, and 2019.
-These points coincide exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+The predicted share curve controls incidence for deforestation[^2], economic situation, and speaker (see appendix for methodological details).
+We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
+These points coincide with exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+
+[^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
+Matching deforestation with speech dates is a complicated endeavor.
+INPE published consolidated deforestation data with almost two years of delay until 2005 [@capobianco2021, pp.
+60].
+Preliminary data was published earlier, but with lower degrees of confidence in the findings.
+For the subsequent years, the consolidated figures for a given year tend to come out in August of the subsequent year.
+However, it also seems to be the case that the executive government have access to the data before everyone else.
+In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), circulates within the same year.
+The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988].
+Hence, we believe the most appropriate way of matching is without any lags on deforestation.
 
@@
 These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered, and in 1989, the New York Times published an article with pictures of the Amazon burning.
+Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered and the New York Times published an article with pictures of the Amazon burning [@simons1988].
 Both incidents caught unprecedented international attention.
-President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza [@capobianco2021]
+President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza [@capobianco2021].
 
-```{r Amazonian speeches by year, echo=FALSE, message=FALSE, warning=TRUE, paged.print=TRUE, include=TRUE}
+```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+
+perc1 <- pop %>%
+  count(amazon_speech, year)%>%
+  group_by(year)%>%
+  mutate(perc=n / sum(n)) %>%
+  select(c(perc,amazon_speech, year))
 
@@
 The driver of this increase is likely to be the 1992 Earth Summit, which was being prepared by various state and non-state actors in the region and brought international attention to environmental topics in Brazil.
-One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (cite).
-During the Cardoso years (1994-2002), Amazonian speeches averaged at about 15% without strong variation.
+One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
+During the Cardoso years (1994-2002), Amazonian speeches averaged at about 16% without strong variation.
 There were no big international or domestic events that drove the topic up.
+At the level of policy, though, we saw the birth of the National System of Protected Areas in 2001, and of the Amazon Regional Protected Areas Program.
+While the former created the legal framework for different types of protected areas to be created, the latter established a transnational partnership to finance the implementation of protected areas in the Amazon [@andonova2014].
 
@@
 These are the years when Brazil entered a long period of political and economic instability that lingers until today.
-Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted.
+Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted and former environmental minister Marina Silva ended her alliance with the worker's party because of disagreements related to the priority of environmental policy.
 
@@
 
-We do find evidence that deforestation rates, economic situation, elections, and simply preferential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
+We do find evidence that deforestation rates, economic situation, elections, and simply presidential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
 However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events.
@@
 
-```{r mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 2: mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 prob_construction_year <- ama_mx %>%
@@
 The plots reveal several trends.
+We start by pure-types.
 Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s.
@@
 @capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-This is aligned with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
+This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
 As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
 
-Figure 3 (below) shows these shifts more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
+Figure 3 (below) shows these shift and reversal more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
 Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation.
@@
 
-```{r pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 pure_types_time <- ama_mx %>%
@@
 
-```{r mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 mixed_types_presid <- ama_mx %>%
@@
 While unprecedented, this new balance was not long-standing.
-Democratic decay is slow and the embryony of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s.
+Democratic decay is slow and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
+We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s (figure 3) .
 The hard increase in sovereignty comes in the 2010s.

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
#text corrections

@@
 First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon.
-That seems to be the case even after controling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker.
+That seems to be the case even after controlling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker.
 Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation.
@@
 This might come both from foreign actors as well as domestic non-state actors.
-Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies
+Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
 
@@
 In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1.
-Finally, we run a multinominal model to show how problem constructions change as the speaker moves further away from the Amazon region.
+Finally, we run a multinomial model to show how problem constructions change as the speaker moves further away from the Amazon region.
 

### 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
Re-organized folders by creating a replication folder for all the important data and pertinent scripts. Fixed data mistake, re-added datasets, and re-ran the SVM model. Updated the rmarkdown folder for new paths and added data sections to it.

--- 2022-04-07 Draft_April_2022/Full_draft_20220401.rmd
@@
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
-pop<- readRDS("~/Documents/GitHub/amazondef/BR_presid_speeches_final.Rds")
+pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
 pop <-  pop %>% select(-c(title, date, text, location))
-ama <- readRDS("~/Documents/GitHub/amazondef/final_data_as.Rds")
+ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
 ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
-AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
-
+AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
 ```
@@
 
+To operationalize our theoretical framework and understand how the Brazilian Amazon has been constructed as a problem, we adopt a mixed-methods approach using manual coding and supervised machine learning.
+We explain our research design and each step of the procedure in this section.
+
 ## 3.1 Data and modeling: operationalizing Amazonian problem construction
 
+We build upon the dataset provided by Cezar (2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+We update the dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches for all the presidents of Brazil since 1985.
+We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
+We do so by detecting all speeches in which the stem “amazon” appears.
+In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We find that 946 speeches are, at least partially, about the Amazon from the 6130.
+
+Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+We opt for picking two sentences before and two sentences after, rather than words because a sentence, because sentences usually contain a cohesive idea.
+By doing so we create our unit of analysis: an Amazonian statement.
+We use Amazon statements as our unit of analysis for two main reasons.
+First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
+Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
+This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
+Notice that an Amazonian statement can contain two or more matches of the stem “amazon” (i.e.
+two consecutive sentences in which one of the words covered by the stem appears).
+In this case, we get two sentences before the first match and two sentences after the last match.
+On average, an Amazonian statement contains 123 words.
+
+After revising the literature (section 2), we selected a random sample of these Amazonian statements to develop a codebook for identifying how the Amazon is constructed as a problem in presidential discourse (see Table 1 below).
+We understand Amazonian problem-constructions as Weberian ideal types, that is, an unified analytical construct portraying a ‘pure’ version of a phenomenon.
+This serves the purpose of allocating empirical observations within a range of possibilities.
+We identify the three problem-constructions derived from the literature (national sovereignty, economic integration, and environmental conservation) in the sample of Amazonian statements.
+However, in addition to them, we inductively identified a fourth problem construction that the literature does not explicitly cover: social development.
+Presidents, for example, sometimes opt to emphasize the lack of hospitals, sanitation, and schools in relation to peoples’ constitutional rights when speaking about the Amazon.
+We saw this code category as substantially different from the other three, hence, we created the code category ‘social development’.
+In their conceptualization, each code is mutually exclusive in its conceptualization, meaning that they cover different forms of constructing the Amazon as a problem, though each Amazonian statement might be assigned to one or more codes.
+A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration or a problem of social development and conservation.
+Amazonian statements, thus, can be either coded as a pure-types or mixed-types.
+
+With the codebook in hands, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
+This amount refers to 50% of all the Amazon Statements identified.
+Inter-coder agreement for each of the four main categories was 85%, on average.
+For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
+At this stage, we also notice that a few of the Amazon statements identified were not about the Brazilian Amazon region, people, or forest.
+These are statements that mention the stem “amazon”, but are not about the Brazilian Amazon per se as the president, for example, might simply greet the Governor of the Amazonas in a speech or make a reference to the Venezuelan Amazon.
+We coded these statements as false positives.
+The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
+The training set is used to train the supervised machine-learning model that automatically classifies observations and the validation set is used to make sure the model fit is appropriate.
+
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories (see  Meyer et al.
+2021; Noble 2006).
+After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set,  we use the model to  automatically code the remaining 1007 Amazonian statements.
+The model was also trained to identify false positive observations, which we chose to delete for analysis since these are not meaningful statements about the Amazon.
+The final dataset for analysis contains 1895 Amazonian statements.
+Out of these, 237 statements are labeled as national sovereignty, 810 as economic integration, 418 as social development, and 567 as environmental conservation.
+Finally, we use poldis once more to extract locations for all speeches in the data.
+These locations represent the Brazilian state in which certain speech was given or an international country.
+
 ## 3.2 Analysis and limitations
+
+To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
+We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves.
+To test whether different problem constructions change according to location, we run a multinomial regression model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
+We also control for annual deforestation rates, annual inflation rates, and election years in the model.
+We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.
+
+These procedures come with its limitations.
+Our codebook is developed using specific Amazon related vocabulary.
+For example, a statement will be coded as economic integration if it is a meaningful support to the Zona Franca of Manaus or a Dam in the Amazon.
+However, the economy is generally a topic that presidents speak about.
+Hence, high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Hence, we might be missing statements about Amazon that do not refer to it.
+However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
+Nevertheless, our dataset covers only what is considered an official remark.
+Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently start to appear in social media.
+Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.
 
@@
 ```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
 perc1 <- pop %>%
@@
   select(c(perc,amazon_speech, year))
-
 pop2 <- pop %>% count(amazon_speech, year, president) %>%
@@
   filter(amazon_speech==1)
-
 pop2 <- left_join(pop2, AAI, by = "year")
 pop2 <- left_join(pop2, amazon_def_year, by = "year")
-
 model <- lm(perc ~ AAI+ def_year + president, data=pop2)
-
 pop2$predicted = predict(model, pop2)
-
 Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
@@
   scale_y_continuous(labels = percent_format())+
-  labs(
-    x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
        subtitle = "Sample composed by 6130 presidential speeches since 1985",
        caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
-  theme(
-    panel.background = element_rect("white", "black", .5, "solid"),
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-    legend.position = "bottom"
-  )
-
+        legend.position = "bottom")
 Amazon_year
@@
 ```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-# get data on deforestation rates per year (PRODES)
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/data/amazon_def_year.Rds")
+# data on deforestation rates per year (PRODES)
 # source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
@@
 # inflation rates per year Brazil (average for year)
-AAI <- readRDS("~/Documents/GitHub/amazondef/data/AAI.Rds")
 # source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx

### 2022-04-07 Replication_Files/data_preparation.R

@@ -1,0 +1,102 @@
+# In this script we prepare the data with some text pre-processing,
+# by extracting Amazonian statements, and 
+# by adding locations for all speeches.
+
+# Install poldis
+# devtools::install_github("henriquesposito/poldis")
+library(poldis)
+library(dplyr)
+
+# Load data
+BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+
+# Replace on title and text
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, " - | -| -", "-")
+
+# Replace "para" to avoid confusion with state name in Brazil
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,"^para$", "pra")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, "^para$", "pra")
+
+# Make it lower case, remove extra space, and add coma space
+BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
+
+# Make it latin SCII
+BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
+BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Speeches$title, id = "latin-ascii")
+
+# get context and update amazon specific data
+Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text))
+#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
[…]

### 2022-04-07 Replication_Files/supervised_machine_learning.R

@@ -1,0 +1,227 @@
+# Supervised Machine Learning Model - SVM
+
+# Load final hand coded data
+final_hand_coded_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_hand_coded_data.Rds")
+# Load final labeling data
+final_unlabeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_unlabeled_data.Rds")
+
+# Split Data into Training and Testing in R 
+sample_size = floor(0.8*nrow(final_hand_coded_data))
+set.seed(1201)
+picked <- sample(seq_len(nrow(final_hand_coded_data)), size = sample_size)
+ttrain = final_hand_coded_data[picked,]
+vvalid = final_hand_coded_data[-picked,]
+
+# Create matrixes
+train_matrix <- create_matrix(ttrain["AM2"], weighting = weightTfIdf)
+valid_matrix <- create_matrix(vvalid["AM2"], originalMatrix = train_matrix, weighting = weightTfIdf)
+score_matrix <- create_matrix(final_unlabeled_data["AM2"], originalMatrix = train_matrix, weighting = weightTfIdf)
+
+# Model fp
+tune_fp <- tune(svm, train_matrix, as.numeric(ttrain$false_positives),
+                ranges =list(cost=c(0.00001, 0.00005, 0.0001, 0.0005, 0.001,
+                                    0.005, 0.01, 0.05, 0.1, 0.5, 1, 2,
+                                    3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15,
+                                    16, 17, 18, 19, 20, 25, 30, 35, 40, 45, 50,
+                                    60, 70, 80, 90, 100, 200, 300, 400, 500, 600,
+                                    700, 800, 900, 1000, 5000, 10000, 50000,
+                                    100000, 500000, 1000000)))
+tune_fp$best.model
+# match best parameters and validate
+model_fp <- svm(x = train_matrix, y = as.numeric(ttrain$false_positives),
+                type = "eps-regression", kernel = "radial",
+                cost = 5000, gamma = 9.541985e-05, episilon = 0.1)
+# predict validation labels
+pred_fp_v <- predict(model_fp, valid_matrix)
+pred_fp_v <- ifelse(pred_fp_v > 0.4, 1, 0)
+# get metrics
+table(pred = pred_fp_v, true = vvalid$false_positives)
[…]

### 2022-04-07 messy_files/data/final_data_preparation_script.R

@@ -1,0 +1,105 @@
+# Prepare final data for anylsis
+# Amazon statements dataset
+library(dplyr)
+final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/final_labeled_data.Rds")
+final_labeled_data$false_positives <- as.factor(ifelse(final_labeled_data$false_positives > 0.45, 1, 0))
+final_labeled_data$sov <- as.factor(ifelse(as.numeric(final_labeled_data$sov) > 0.45, 1, 0))
+final_labeled_data$EI <- as.factor(ifelse(as.numeric(final_labeled_data$EI) > 0.45, 1, 0))
+final_labeled_data$SD <- as.factor(ifelse(as.numeric(final_labeled_data$SD) > 0.45, 1, 0))
+final_labeled_data$con <- as.factor(ifelse(as.numeric(final_labeled_data$con) > 0.45, 1, 0))
+summary(final_labeled_data)
+fp <- dplyr::filter(final_labeled_data, false_positives == "1" & sov == "0" & EI == "0" & SD == "0" & con == "0")
+final_data <- dplyr::anti_join(final_labeled_data, fp, "AM2")
+# Add other variable
+final_data$other <- ifelse(final_data$sov == "0" & final_data$EI == "0" & final_data$SD == "0" & final_data$con == "0", 1, 0)
+summary(final_data)
+# re-assign location with new version of extract_location()
+# function that does not contain "Brazil" as a match
+final_data$location <- poldis::extract_location(final_data$title)
+summary(as.factor(final_data$location))
+# if NA for location in title, use full text
+final_data$location <- ifelse(grepl("^NA$", final_data$location),
+                              poldis::extract_location(final_data$text),
+                              final_data$location)
+summary(as.factor(final_data$location))
+# a few obs were not matched still, let's see them
+final_data$location <- ifelse(nchar(final_data$location) > 40, "NA", final_data$location)
+summary(as.factor(final_data$location))
+nm <- final_data %>% dplyr::filter(location == "NA") %>% select(AM2, text)
+View(nm) # we can hand code some of these
+nm$location_na <- c("NA", "NA", "NA", "Amazonas", "Amazonas",
+                    "Bahia", "Para", "Para", "Acre", "Acre", "Minas Gerais", 
+                    "Rio Grande do Sul", "Rio Grande do Sul", "Para", 
+                    "Para", "Para", "Para", "Para", "Para", "Para", "Para",
[…]

### 2022-04-07 messy_files/others/LSA_GLM_classification_models.R

@@ -1,0 +1,251 @@
+# LSA and GLM simple models to classify data
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get full dataset and remove hand coded observations
+amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/data/amazon_speeches_long.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
+t <- dplyr::select(training_set_final, AM2) # used to remove duplicates later
+# Get other texts standardize
+amazon_speeches_long$AM2 <- stringi::stri_trans_general(amazon_speeches_long$AM2, 'latin-ascii')
+amazon_speeches_long$AM2 <- stringr::str_squish(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tolower(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removeNumbers(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removePunctuation(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- trimws(amazon_speeches_long$AM2)
+# Remove train obs, keep only score, then rbind train and score data
+score <- amazon_speeches_long[!(amazon_speeches_long$AM2 %in% t$AM2),]
+score <- score %>%
+  select(AM2) %>%
+  mutate(sov = NA, EI = NA, SD = NA, con = NA, false_positives = NA) # Added NA for reference
[…]

### 2022-04-07 messy_files/others/SVM_model_final.R

@@ -1,0 +1,411 @@
+# SVM model classification final
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+library(e1071)
+library(RTextTools)
+library(SnowballC)
+
+##### First, let's try to tune the model parameters in the Economic Integration variable
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get validation dataset
+validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+t <- select(training_set_final, AM2) # save for later
+# get validation standardized
+v <- select(validation_final, AM2) # save for merge later
+validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
+validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
+validation_final$AM2 <- tolower(validation_final$AM2)
+validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
+validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
+validation_final$AM2 <- trimws(validation_final$AM2)
+# Rbind train and validation data
+tdata <- rbind(training_set_final[,-1], validation_final)
+tdata$AM2 <- tm::removeWords(tdata$AM2, tm::stopwords("pt"))
+tdata$AM2 <- SnowballC::wordStem(tdata$AM2, 'pt')
+tdata$AM2 <- tm::stripWhitespace(tdata$AM2)
+trainData <- tdata[1:605,]
+testData <- tdata[606:819,]
+# create matrix
+t_matrix <- create_matrix(trainData$AM2, weighting = weightTfIdf)
+s_matrix <- create_matrix(testData$AM2, originalMatrix = t_matrix, weighting = weightTfIdf)
+# model ei
[…]

### 2022-04-07 messy_files/others/alternative_text_classification_models.R

@@ -1,0 +1,202 @@
+# Run and compare alternative models to classify texts
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(tidymodels)
+library(textrecipes)
+library(RTextTools)
+library(lsa)
+library(ggplot2)
+library(discrim)
+library(naivebayes)
+
+# First let's just get the data ready!
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+# Split the training set into train and test for testing
+data <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives)
+train_size <- floor(0.75 * nrow(data))
+in_rows <- sample(c(1:nrow(data)), size = train_size, replace = FALSE)
+train <- data[in_rows, ]
+test <- data[-in_rows, ]
+
+##### Now let's run a simple linear model based on a LSA topic model
+# Clean and get a dtm
+txtcorp_lsa <- VCorpus(VectorSource(as.character(data$AM2)))
+txtcorp_lsa <- tm::tm_map(txtcorp_lsa, removeWords, stopwords('pt'))
+TDM_lsa <- TermDocumentMatrix(txtcorp_lsa, control = list(weighting = weightTfIdf))
+# Get 20 latent topics
+lsaTDM <- lsa(TDM_lsa, 20) # This takes a few minutes
+# Extract the document LSA values
+docVectors <- as.data.frame(lsaTDM$dk)
+# Append the target var
+docVectors$false_positives <- data$false_positives
+# Sample train and test data (avoid overfitting)
+train_lsa <- docVectors[in_rows,]
+pred_score_lsa <- docVectors[-in_rows,]
+# Fit the simple model
+set.seed(1234)
[…]

### 2022-04-07 messy_files/others/clean_combined_training_set.R

@@ -1,0 +1,85 @@
+# Get and wrangle combined training set
+library(readxl)
+training_set_combined <- read_excel("data/training_set_combined.xlsx")
+library(dplyr)
+summary(as.factor(training_set_combined$decision_falsepositive)) # We have 3 ones ...
+summary(as.factor(training_set_combined$decision_code)) # Not consistent
+# Fix data issues first
+training_set_combined$decision_falsepositive[103] <- "false positive"
+training_set_combined$decision_falsepositive[225] <- "false positive"
+training_set_combined$decision_code <- gsub("ecnomic|only economic", "economic",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("consevation", "conservation",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("soverignty|sovereigty|sovereingty", "sovereignty",
+                                            training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub("only", "", training_set_combined$decision_code)
+training_set_combined$decision_code <- gsub(" and ", ", ", training_set_combined$decision_code)
+# Get categories back in as variables 
+ts <- training_set_combined %>%
+  mutate(false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
+         sov = ifelse(grepl("sovereignty", decision_code), 1, substring(code_henrique, 0, 1)),
+         EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
+         SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
+         con = ifelse(grepl("conservation", decision_code), 1, substring(code_henrique, 4, 4))) %>%
+  select(-c(ID, decision_falsepositive, code_henrique, code_livio, decision_code)) %>%
+  mutate_all(~replace(., is.na(.), 0))
+# Save data
+# saveRDS(ts, "training_set_final.Rds")
+
+# Check intercoder reliability for each category (without false positives)
+check_reliability <- training_set_combined %>%
+  filter(!grepl("^false positive$", decision_falsepositive)) %>% 
+  mutate(code_livio = ifelse(is.na(code_livio), "0000", code_livio), 
+         code_check = ifelse(code_henrique == code_livio, 1, 0),
[…]

### 2022-04-07 messy_files/others/data_wrangling.R

@@ -1,0 +1,85 @@
+# Data Wrangling
+
+# This script explains how the data was coded and where it comes from.
+# It is intended for transparency, rather than reproduciability.
+# For more information on the data, please contact the authors.
+# The dataset is available in the repository,
+# feel free to use but cite us.
+
+# # Load packages
+# library(dplyr)
+# library(stringr)
+# #Load poldis
+# remotes::install_github(henriquesposito/poldis)
+# # Get Data, join and save into repository
+# # This portion explains how/where data was gathered and wrangled before it was saved into the package.
+# # It is commented out as it is here for transparency rather than reproduciability.
+# # Please contact authors for access to original datasets for reproduction.
+#
+# # Load BR_oral from AP repository
+# # load("~/GitHub/authenticity_performances/data/BR_oral.rda") # your path my differ here
+# # Select only some variables
+# BR_oral <- BR_oral %>%
+#   dplyr::select("presid", "date", "party", "text") %>%
+#   rename(president = "presid", year = "date")
+#
+# # Wrangle data
+# # Get exact dates 
+# BR_oral$date <- poldis::extract_date(BR_oral$text)
+# # There are a lot of NAs... It seems some dates in text are missing the year...
+# # Get titles (first sentence)
+# BR_oral$title <- poldis::extract_title(BR_oral$text)
+# # For dates that are missing the year, let's complete them!
+# d <- BR_oral$title
+# d <- stringr::str_extract(d, "(\\S+)\\s*DE\\s*(\\S+)")
+# d <- paste0(d, "-", BR_oral$year)
+# d <- gsub(" DE ", "-", d)
+# # load months data from poldis
+# # load("~/GitHub/poldis/R/sysdata.rda") # your path might differ
+# months <- as.data.frame(months)
+# for (k in seq_len(nrow(months))) {
+#   d <- gsub(paste0(months$months[k]),
+#               paste0(months$number[k]),
+#               d, ignore.case = TRUE,
+#               perl = T)
+# }
+# d <- stringr::str_replace_all(d, "NA-", "?-?-")
+# d <- ifelse(stringr::str_detect(d, "[A-Z]|[a-z]"), paste0("?-?-", BR_oral$year), d)
+# # Let's complete our dates column now
+# BR_oral$date <- ifelse(is.na(BR_oral$date), d, BR_oral$date)
+# 
[…]

### 2022-04-07 messy_files/others/get_context_&_locations.R

@@ -1,0 +1,63 @@
+# Get location from title and text
+BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+
+# Replace on title and text
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, " - | -| -", "-")
+
+# Replace "para" to avoid confusion with state name in Brazil
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,"^para$", "pra")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, "^para$", "pra")
+
+# Make it lower case, remove extra space, and add coma space
+BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
+
+# Make it latin SCII
+BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
+BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Speeches$title, id = "latin-ascii")
+
+# get locations from title
+BR_Presidential_Speeches$location <- poldis::extract_location(BR_Presidential_Speeches$title)
+summary(as.factor(BR_Presidential_Speeches$location))
+
+# get location from text if not found
+BR_Presidential_Speeches$location <- ifelse(grepl("^NA$", BR_Presidential_Speeches$location),
+                                            poldis::extract_location(BR_Presidential_Speeches$text),
+                                            BR_Presidential_Speeches$location)
[…]

### 2022-04-07 messy_files/others/model_classification_elastic_net.R

@@ -1,0 +1,328 @@
+# Classify texts
+
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+
+# Get hand coded final training set
+training_set_final <- readRDS("~/GitHub/amazondef/data/training_set_final.Rds")
+# Get full dataset and remove hand coded observations
+amazon_speeches_long <- readRDS("~/GitHub/amazondef/data/amazon_speeches_long.Rds")
+
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
+t <- dplyr::select(training_set_final, AM2) # used to remove duplicates later
+
+# Get other texts standardize
+amazon_speeches_long$AM2 <- stringi::stri_trans_general(amazon_speeches_long$AM2, 'latin-ascii')
+amazon_speeches_long$AM2 <- stringr::str_squish(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tolower(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removeNumbers(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- tm::removePunctuation(amazon_speeches_long$AM2)
+amazon_speeches_long$AM2 <- trimws(amazon_speeches_long$AM2)
+
+# Remove train obs, keep only score, then rbind train and score data
+score <- amazon_speeches_long[!(amazon_speeches_long$AM2 %in% t$AM2),]
+score <- score %>%
+  select(AM2) %>%
+  mutate(sov = NA, EI = NA, SD = NA, con = NA, false_positives = NA) # Added NA for reference
+score <- rbind(train, score) # Need this cause we are working with matrixes
+
+# Let's run a classification model for false positives, just as a test
+
+# Get a corpus and DTM
+txtcorp <- VCorpus(VectorSource(as.character(score$AM2)))
[…]

### 2022-04-07 messy_files/others/test_validation_model.R

@@ -1,0 +1,258 @@
+# Validation set
+# Here we compare how the LSA/GLM model compares to the SVM when we use
+# our training set to label a validation set hand-coded
+
+############## LSA/GLM
+# LSA and GLM simple models to classify data
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+# Get hand coded final training set
+training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
+# Get validation dataset
+validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
+# Get training texts standardized
+training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
+training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
+training_set_final$AM2 <- tolower(training_set_final$AM2)
+training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
+training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
+training_set_final$AM2 <- trimws(training_set_final$AM2)
+train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
+# Get validation texts standardize
+validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
+validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
+validation_final$AM2 <- tolower(validation_final$AM2)
+validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
+validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
+validation_final$AM2 <- trimws(validation_final$AM2)
+# Rbind train and validation data
+score <- rbind(train, validation_final) # Need this cause we are working with matrixes
+
+##### Now let's run a simple linear model based on a LSA topic model
+# Clean and get a dtm
+txtcorp_lsa <- VCorpus(VectorSource(as.character(score$AM2)))
[…]

### 2022-04-07 messy_files/others/training_data_merge.R

@@ -1,0 +1,37 @@
+# First, load datasets
+library(readxl)
+training_set_Sposito <- read_excel("data/training_set_Sposito.xlsx")
+training_set_livio <- read_excel("data/training_set_livio.xlsx")
+# get variable names standardized
+library(dplyr)
+l <- training_set_livio %>%
+  dplyr::slice_head(n = 605) %>%
+  rename(sov = sovereignty, ED = 'economic development', SD = 'social development',
+         con = conservation, cm2 = 'comment 2') %>% 
+  dplyr::mutate(comments = paste0("1 -", comment, " 2 - ", cm2)) %>% 
+  dplyr::select(AM2, sov, ED, SD, con, comments)
+l <- tibble::rownames_to_column(l, "ID")
+
+h <- training_set_Sposito %>%
+  rename(sov = Sovereignty, ED = 'Economic Development', SD = 'Social Development',
+         con = Conservation, comments = Comments) %>% 
+  dplyr::select(AM2, sov, ED, SD, con, comments)
+h <- tibble::rownames_to_column(h, "ID")
+
+# Get and merge only the comments data for later
+comments <- data.frame(comments = paste0(l$comments, " 3 - ", h$comments))
+
+# Add the same comments for both datasets
+l <- select(l, -comments)
+l$comments <- comments$comments
+h <- select(h, -comments)
+h$comments <- comments$comments
+
+# Merge and remove duplicates
+ts <- rbind(l, h)
+ts <- ts %>% 
+  dplyr::distinct() %>%
+  dplyr::mutate(dup = duplicated())
+  
+# Save data in excel format
+xlsx::write.xlsx(ts, file = "ts.xlsx")

### 2022-04-07 others/LSA_GLM_classification_models.R

@@ -1,251 +1,0 @@
-# LSA and GLM simple models to classify data
-# Load packages
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-library(lsa)
-# Get hand coded final training set
-training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get full dataset and remove hand coded observations
-amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/data/amazon_speeches_long.Rds")
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
-t <- dplyr::select(training_set_final, AM2) # used to remove duplicates later
-# Get other texts standardize
-amazon_speeches_long$AM2 <- stringi::stri_trans_general(amazon_speeches_long$AM2, 'latin-ascii')
-amazon_speeches_long$AM2 <- stringr::str_squish(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tolower(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tm::removeNumbers(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tm::removePunctuation(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- trimws(amazon_speeches_long$AM2)
-# Remove train obs, keep only score, then rbind train and score data
-score <- amazon_speeches_long[!(amazon_speeches_long$AM2 %in% t$AM2),]
-score <- score %>%
-  select(AM2) %>%
-  mutate(sov = NA, EI = NA, SD = NA, con = NA, false_positives = NA) # Added NA for reference
[…]

### 2022-04-07 others/SVM_model_final.R

@@ -1,410 +1,0 @@
-# SVM model classification final
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-library(lsa)
-library(e1071)
-library(RTextTools)
-library(SnowballC)
-
-##### First, let's try to tune the model parameters in the Economic Integration variable
-# Get hand coded final training set
-training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get validation dataset
-validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-t <- select(training_set_final, AM2) # save for later
-# get validation standardized
-v <- select(validation_final, AM2) # save for merge later
-validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
-validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
-validation_final$AM2 <- tolower(validation_final$AM2)
-validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
-validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
-validation_final$AM2 <- trimws(validation_final$AM2)
-# Rbind train and validation data
-tdata <- rbind(training_set_final[,-1], validation_final)
-tdata$AM2 <- tm::removeWords(tdata$AM2, tm::stopwords("pt"))
-tdata$AM2 <- SnowballC::wordStem(tdata$AM2, 'pt')
-tdata$AM2 <- tm::stripWhitespace(tdata$AM2)
-trainData <- tdata[1:605,]
-testData <- tdata[606:819,]
-# create matrix
-t_matrix <- create_matrix(trainData$AM2, weighting = weightTfIdf)
-s_matrix <- create_matrix(testData$AM2, originalMatrix = t_matrix, weighting = weightTfIdf)
-# model ei
[…]

### 2022-04-07 others/clean_combined_training_set.R

@@ -1,70 +1,0 @@
-# Get and wrangle combined training set
-library(readxl)
-training_set_combined <- read_excel("data/training_set_combined.xlsx")
-library(dplyr)
-summary(as.factor(training_set_combined$decision_falsepositive)) # We have 3 ones ...
-summary(as.factor(training_set_combined$decision_code)) # Not consistent
-# Fix data issues first
-training_set_combined$decision_falsepositive[103] <- "false positive"
-training_set_combined$decision_falsepositive[225] <- "false positive"
-training_set_combined$decision_code <- gsub("ecnomic|only economic", "economic",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("consevation", "conservation",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("soverignty|sovereigty|sovereingty", "sovereignty",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("only", "", training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub(" and ", ", ", training_set_combined$decision_code)
-# Get categories back in as variables 
-ts <- training_set_combined %>%
-  mutate(false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
-         sov = ifelse(grepl("sovereignty", decision_code), 1, substring(code_henrique, 0, 1)),
-         EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
-         SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
-         con = ifelse(grepl("conservation", decision_code), 1, substring(code_henrique, 4, 4))) %>%
-  select(-c(ID, decision_falsepositive, code_henrique, code_livio, decision_code)) %>%
-  mutate_all(~replace(., is.na(.), 0))
-# Save data
-# saveRDS(ts, "training_set_final.Rds")
-
-# Check intercoder reliability for each category (without false positives)
-check_reliability <- training_set_combined %>%
-  filter(!grepl("^false positive$", decision_falsepositive)) %>% 
-  mutate(code_livio = ifelse(is.na(code_livio), "0000", code_livio), 
[…]

### 2022-04-07 others/get_context_&_locations.R

@@ -1,63 +1,0 @@
-# Get location from title and text
-BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
-
-# Replace on title and text
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, " - | -| -", "-")
-
-# Replace "para" to avoid confusion with state name in Brazil
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,"^para$", "pra")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, "^para$", "pra")
-
-# Make it lower case, remove extra space, and add coma space
-BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
-
-# Make it latin SCII
-BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
-BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Speeches$title, id = "latin-ascii")
-
-# get locations from title
-BR_Presidential_Speeches$location <- poldis::extract_location(BR_Presidential_Speeches$title)
-summary(as.factor(BR_Presidential_Speeches$location))
-
-# get location from text if not found
-BR_Presidential_Speeches$location <- ifelse(grepl("^NA$", BR_Presidential_Speeches$location),
-                                            poldis::extract_location(BR_Presidential_Speeches$text),
-                                            BR_Presidential_Speeches$location)
[…]

### 2022-04-07 others/model_classification_elastic_net.R

@@ -1,328 +1,0 @@
-# Classify texts
-
-# Load packages
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-
-# Get hand coded final training set
-training_set_final <- readRDS("~/GitHub/amazondef/data/training_set_final.Rds")
-# Get full dataset and remove hand coded observations
-amazon_speeches_long <- readRDS("~/GitHub/amazondef/data/amazon_speeches_long.Rds")
-
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
-t <- dplyr::select(training_set_final, AM2) # used to remove duplicates later
-
-# Get other texts standardize
-amazon_speeches_long$AM2 <- stringi::stri_trans_general(amazon_speeches_long$AM2, 'latin-ascii')
-amazon_speeches_long$AM2 <- stringr::str_squish(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tolower(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tm::removeNumbers(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- tm::removePunctuation(amazon_speeches_long$AM2)
-amazon_speeches_long$AM2 <- trimws(amazon_speeches_long$AM2)
-
-# Remove train obs, keep only score, then rbind train and score data
-score <- amazon_speeches_long[!(amazon_speeches_long$AM2 %in% t$AM2),]
-score <- score %>%
-  select(AM2) %>%
-  mutate(sov = NA, EI = NA, SD = NA, con = NA, false_positives = NA) # Added NA for reference
-score <- rbind(train, score) # Need this cause we are working with matrixes
-
-# Let's run a classification model for false positives, just as a test
-
-# Get a corpus and DTM
-txtcorp <- VCorpus(VectorSource(as.character(score$AM2)))
[…]

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd

@@
 
-To operationalize our theoretical framework and understand how the Brazilian Amazon has been constructed as a problem, we adopt a mixed-methods approach using manual coding and supervised machine learning.
+To operationalize our theoretical framework, we adopt a mixed-methods approach using manual coding and supervised machine learning.
 We explain our research design and each step of the procedure in this section.
@@
 We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
-We do so by detecting all speeches in which the stem “amazon” appears.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We do so by detecting all speeches in which the stem "amazon" appears.
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
 We find that 946 speeches are, at least partially, about the Amazon from the 6130.
 
-Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
-We opt for picking two sentences before and two sentences after, rather than words because a sentence, because sentences usually contain a cohesive idea.
+Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
+We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
 By doing so we create our unit of analysis: an Amazonian statement.
@@
 This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-Notice that an Amazonian statement can contain two or more matches of the stem “amazon” (i.e.
-two consecutive sentences in which one of the words covered by the stem appears).
-In this case, we get two sentences before the first match and two sentences after the last match.
+When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
 On average, an Amazonian statement contains 123 words.
@@
 After revising the literature (section 2), we selected a random sample of these Amazonian statements to develop a codebook for identifying how the Amazon is constructed as a problem in presidential discourse (see Table 1 below).
-We understand Amazonian problem-constructions as Weberian ideal types, that is, an unified analytical construct portraying a ‘pure’ version of a phenomenon.
+We understand Amazonian problem-constructions as Weberian ideal types, that is, an unified analytical construct portraying a 'pure' version of a phenomenon.
 This serves the purpose of allocating empirical observations within a range of possibilities.
@@
 However, in addition to them, we inductively identified a fourth problem construction that the literature does not explicitly cover: social development.
-Presidents, for example, sometimes opt to emphasize the lack of hospitals, sanitation, and schools in relation to peoples’ constitutional rights when speaking about the Amazon.
-We saw this code category as substantially different from the other three, hence, we created the code category ‘social development’.
+Presidents sometimes opt to emphasize the lack of hospitals, sanitation, and schools in relation to peoples' constitutional rights when speaking about the Amazon.
+We saw this code category as substantially different from the other three, hence, we created the code category 'social development'.
 In their conceptualization, each code is mutually exclusive in its conceptualization, meaning that they cover different forms of constructing the Amazon as a problem, though each Amazonian statement might be assigned to one or more codes.
@@
 For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
-At this stage, we also notice that a few of the Amazon statements identified were not about the Brazilian Amazon region, people, or forest.
-These are statements that mention the stem “amazon”, but are not about the Brazilian Amazon per se as the president, for example, might simply greet the Governor of the Amazonas in a speech or make a reference to the Venezuelan Amazon.
-We coded these statements as false positives.
+Statements that mention the stem "amazon", but are not about the Brazilian Amazon, for example, might a greeting to the Governor of the Amazonas, were coded as false positives.
 The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
@@
 The model was also trained to identify false positive observations, which we chose to delete for analysis since these are not meaningful statements about the Amazon.
-The final dataset for analysis contains 1895 Amazonian statements.
-Out of these, 237 statements are labeled as national sovereignty, 810 as economic integration, 418 as social development, and 567 as environmental conservation.
+The final dataset for analysis contains 1895 coded Amazonian statements.
 Finally, we use poldis once more to extract locations for all speeches in the data.
@@
 Hence, high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
 Hence, we might be missing statements about Amazon that do not refer to it.

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
First attemppt at adding codebook table to rmd file

@@
 
+```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
+                                                    "Social Development", "Environmental Conservation"),
+                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
+Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.", "This code constructs the Amazon region and/or forest as an issue of economic integration.
+It advances the view that the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
+It advances the view that Amazon is full of citizens who should have their rights guaranteed.
+This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
+This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
+Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
+This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
+The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
+                           Example = c("We can now walk the world and when we debate about the Amazon, we do not need to wait for questions, we are the ones who are going to say what we are doing in the Amazon.
+We do not need to keep on saying ‘the Amazon is ours’ just for saying it, people often say this without much conviction either.
+If the Amazon has been ours since Cabral (European discoverer of Brazil) stepped here, why do we now have to worry about the Amazon?
+(Lula 2008)", "", "", ""))
+knitr::kable(codebook, "simple")
+```
+
 With the codebook in hands, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
@@
 The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-The training set is used to train the supervised machine-learning model that automatically classifies observations and the validation set is used to make sure the model fit is appropriate.
+The training set is used to train the supervised machine-learning model that automatically classifies observations while the validation set is used to make sure the model fit is appropriate.
 

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
Updated some statistics to be consistent with new findings and added some of the footnotes and references to text

@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations^[For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
+(2021).
+For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
@@
 
-We build upon the dataset provided by Cezar (2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+We build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
 We update the dataset by scraping and adding all official speeches from 2020 and 2021.
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories (see Meyer et al.
-2021; Noble 2006).
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006]^[For more information on this please see the extended methodology.
+The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the  validation set.
+The extended methodology also includes a more detailed codebook table with further coding guidelines.].
 After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set, we use the model to automatically code the remaining 1007 Amazonian statements.
@@
 To test whether different problem constructions change according to location, we run a multinomial regression model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-We also control for annual deforestation rates, annual inflation rates, and election years in the model.
+We code 4 different location categories for where speeches take place, they are: Amazonian states, non-Amazonian states, Brasilia, and International.
+In the model, we also control for annual deforestation rates, annual inflation rates, and election years in the model as these are variables which could mitigate the correlations between problem construction and location^[See extended methodology for more information on model selection, controls and post estimation tests.].
 We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.
@@
 In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), circulates within the same year.
-The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988].
+The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures [@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988].
 Hence, we believe the most appropriate way of matching is without any lags on deforestation.
@@
 
-We now move to mixed types, which average at around 17% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
+We now move to mixed types, which average at around 21% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
 While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
@@
 Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation.
-This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 28.5% and 28.6% respectively.
+This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 29.5% and 31.3% respectively.
 While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty.
@@
 ```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mean_mt <- filter(comp_types, mx_cat2 == "Mixed-types") %>% mean(perc) # 21%
+mixed_types_lula <- filter(comp_types, president == "Lula") # 29.5%
+mixed_types_bolsonaro <- filter(comp_types, president == "Bolsonaro")# 31.3%
 mixed_types_presid <- ama_mx %>%
@@
   mutate(president = factor(president,
-                            levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+                            levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                       "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
   ggplot(aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1))) +
@@
 
+Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations.
+For locations, the reference category is Amazonian states and, for problem construction, the reference category is environmental conservation.
+From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states.
+These findings indicate that constructing the amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states.
+Additionally, pure sovereignty constructions correlate in negative statistically significant ways to international settings in relation to environmental conservation constructions in Amazonian states.
+That is, constructing the Amazon as an issue of sovereignty
+
 ```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-# data on deforestation rates per year (PRODES)
-# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
-# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
-# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
-# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-amazon_def_year <- rbind(adr, amazon_def_year)
+amazon_def_year <- rbind(adr, amazon_def_year) # data on deforestation rates per year (PRODES)
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-# inflation rates per year Brazil (average for year)
-# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
-ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
-# remove non-identified locations and mixed-other constructions (very little data for either and not relevant)
+ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # average inflation rates per year Brazil
+# remove non-identified locations, mixed-other constructions and add election years
 ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
   mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
+                                            "Pure Social Development", "Pure Sovereignty",
+                                            "Economic Conservation",
                                             "Economic and Social Development", "Sovereign Conservation",

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
More updates to draft rmd docs

@@
 It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
-                           Example = c("We can now walk the world and when we debate about the Amazon, we do not need to wait for questions, we are the ones who are going to say what we are doing in the Amazon.
-We do not need to keep on saying ‘the Amazon is ours’ just for saying it, people often say this without much conviction either.
-If the Amazon has been ours since Cabral (European discoverer of Brazil) stepped here, why do we now have to worry about the Amazon?
-(Lula 2008)", "", "", ""))
+                           Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
+I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019)", "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
+This highway will allow production in the Tax Free Zone in MAnaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)", "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+We have invested over 14 billion reais in this program, in three and a half years.
+Do you know how many electrical lines we have already built?
+One million kilometers of lines.
+(Lula 20/11/2009)", "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
+Mesquita (Sarney 20/07/1989)"))
 knitr::kable(codebook, "simple")

### 2022-04-08 Draft_April_2022/rticle/rticle.tex
More updates to rmd file and added an rticles version just in case

--- 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
@@
----
-title: How has the Brazilian Amazon been constructed as a problem? An analysis of
-  presidential speeches since 1985
-author:
-- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
-date: "April 2022"
-output:
-  word_document:
-    reference_docx: template.docx
-  pdf_document: default
-  html_document:
-    df_print: paged
-bibliography: references.bib
-csl: chicago.csl
-abstract: This paper ...
----
+% interactcadsample.tex
+% v1.03 - April 2017
 
-```{r setup, include=FALSE, warning=FALSE, message=FALSE}
-knitr::opts_chunk$set(include = FALSE)
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(skimr)
-library(scales)
-library(RColorBrewer)
-library(kableExtra)
-library(nnet)
-library(stargazer)
-Sys.setlocale("LC_ALL", "C")
-options(stringsAsFactors = FALSE, scipen = 999)
-```
+\documentclass[]{interact}
 
-```{r data, message=FALSE, warning=FALSE, include=FALSE}
-pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
-pop <-  pop %>% select(-c(title, date, text, location))
-ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
-ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
-AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-```
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage{subfigure}% Support for small, `sub' figures and tables
+%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
 
-```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-sov <- ama %>% 
-  filter(sov==1) %>% 
-  count(sov, year) %>%
-  group_by(year) %>%
-  select(-c(sov))%>%
-  rename (sov = n)
-ei <- ama %>% 
-  filter(ei==1) %>% 
-  count(ei, year) %>%
-  group_by(year) %>%
-  select(-c(ei))%>%
-  rename (ei = n) %>%
-  ungroup() %>%
-  tibble::add_row(year = 2017, ei = 0) %>%
-  tibble::add_row(year = 2018, ei = 0)
-sd <- ama %>% 
-  filter(sd==1) %>% 
-  count(sd, year) %>%
-  group_by(year) %>%
-  select(-c(sd))%>%
-  rename (sd = n)
-con <- ama %>% 
-  filter(con==1) %>% 
-  count(con, year) %>%
-  group_by(year) %>%
-  select(-c(con))%>%
-  rename (con = n)
-other <- ama %>% 
-  filter(other==1) %>% 
-  count(other, year) %>%
-  group_by(year) %>%
-  select(-c(other))%>%
-  rename (other = n)
-temp <- ei %>% left_join(other) %>% 
-                left_join(con) %>%
-                left_join(sd) %>%
-                left_join(sov) %>%
-                replace(is.na(.), 0)
-```
+\usepackage{natbib}% Citation support using natbib.sty
+\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
+\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
 
-```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-ama_mx <-  ama %>%
-  unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
-                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
-                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
-                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
-                                      mixed_type == '0_0_0_0' ~ "Other",
-                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
-                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
-                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
-                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
-                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
-                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
-                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
-                                            mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
-                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
-                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
-                    "Social Conservation", "Other Mixed-types")),
-         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
-                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
-                             grepl("^Other$", mx_cat) ~ "Other",
-                             grepl("Economic Conservation|Economic and Social Development|
-                                   |Sovereign Conservation|Sustainable Development|
-                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
-                                   mx_cat) ~ "Mixed-types"))
-```
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
 
-\pagebreak
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
 
-# 1 Introduction
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}
 
-The Amazon needs to be protected from foreign interests.
-The Amazon needs to be exploited for its natural resources.
-The Amazon needs to be preserved as a standing ecosystem.
-Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon.
-Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or its peoples as a particular problem.
-In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
-Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@acker2014; @hecht1990; @hochstetler2007].
-However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time, by geographical location, and between and within governments
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction.
-Although problem-construction takes place in a series of instances (e.g.
-policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985.
-We opt for presidential speeches for three reasons.
-First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
-In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Thus, understanding how policy comes about discursively is important.
-Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally[@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon, from investors to agribusiness to local farmer.
-This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015].
-Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated.
-Finally, as our theoretical framework suggests, problem-construction varies by geographic location.
-Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
+% From pandoc table feature
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 
-To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazonian related statements within these speeches.
-We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
-Using R, we then train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.
+\usepackage{hyperref}
+\usepackage[utf8]{inputenc}
+\def\tightlist{}
 
-Our findings are threefold.
-First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon.
-That seems to be the case even after controlling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker.
-Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation.
-This trend is reversed in the late 2010s, with the twist of sovereignty making a strong comeback.
-Finally, using a multinominal model, we find that the farthest away the speaker is from the Amazon, be it within the country in non-Amazonian States or outside Brazil, the more likely the speaker is to construct the Amazon as a problem of environmental conservation than economic integration or social development.
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
-This article proceeds as follows: first, we review Amazonian literature to identify the main policy-cycles and their underlying problem construction.
-We then propose a theoretical framework to understand problem-construction and discourse.
-In the methodology section, we operationalize our framework and present the codebook.
-Section four portrays our main results.
-Finally, we conclude by discussing our findings and proposing future research.
+\begin{document}
 
-# 2 Amazonian policy-cycles, discourse, and problem-construction
+\articletype{ARTICLE TEMPLATE}
 
-## 2.1 Literature Review: policy-cycles in the Amazonian literature
+\title{``How has the Brazilian Amazon been constructed as a problem? An
+analysis of presidential speeches since 1985''}
 
-For the purposes of this article, we understand Amazonian literature as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.
-The three main policy-cycles we identify in Amazonian literature are: national sovereignty, economic integration, and environmental conservation.
-We tie each one of them to a specific problem and consequently a solution.
-We close the sub-section reviewing the relationship between policy, presidential discourse, and environmental problems.
+\author{\name{Livio Silva-Muller$^{Graduate Institute of International
+and Development Studies}$, Henrique Sposito$^{Graduate Institute of
+International and Development Studies}$}
+\affil{$^{Graduate Institute of International and Development
+Studies}$Chemin Eugène-Rigot 2, 1202 Geneva}
+}
 
-### 2.1.1 National sovereignty
+\thanks{CONTACT Livio
+Silva-Muller. Email: \href{mailto:livio.silva@graduateinstitute.ch}{\nolinkurl{livio.silva@graduateinstitute.ch}}, Henrique
+Sposito. Email: \href{mailto:henrique.sposito@graduateinstitute.ch}{\nolinkurl{henrique.sposito@graduateinstitute.ch}}}
 
-In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" [-@hecht1990, pp.1].
-It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders.
-The dream of fortunes to be found in the Eldorado composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" (Hecht and Cockburn 1990, preface).
-The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht2013, pp.8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil[@hecht1990].
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War[@garfield2013].
+\maketitle
 
-[^1]: *Bandeirantes* means "flag-carriers", the word is used to designate Portuguese colonials and later Brazilian explorers, expanding the Brazilian territory beyond what the Tordesillas Treaty established.
-The treaty allocated almost the whole Amazonian territory to the Spanish Empire, the bandeirantes took much of the territory afterwards.
+\begin{abstract}
+This paper\ldots{}
+\end{abstract}
 
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
-Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-This might come both from foreign actors as well as domestic non-state actors.
-Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
+\begin{keywords}
+Sections; lists; figures; tables; mathematics; fonts; references;
+appendices
+\end{keywords}
 
-The sovereignty problem advances the view that the Brazilian Amazon is Brazilian and foreign presence, non-state presence and alleged lies are part of a broader strategy to internationalize the region.
-The policy solutions relate to close monitoring of the borders, strict regimes related to entry in the region, and combating alleged disinformation about the Amazon nationally and internationally.
+\hypertarget{introduction}{%
+\section{1 Introduction}\label{introduction}}
 
-### 2.1.2 Economic integration
+The Amazon needs to be protected from foreign interests. The Amazon
+needs to be exploited for its natural resources. The Amazon needs to be
+preserved as a standing ecosystem. Historically, different Brazilian
+federal government proposed diverse policies to deal with the Amazon.
+Each of these policies contain an implicit assumption of what needs to
+be solved, or in other words, it represents the region, the forest, or
+its peoples as a particular problem. In the three examples above, the
+Amazon is represented as an issue of national sovereignty, economic
+integration, and environmental conservation, respectively. Each of these
+constructions, and their proposed solutions, have been described as
+policy cycles of Brazilian governments
+\citep{acker2014, hecht1990, hochstetler2007}. However, policy cycles
+are usually represented monolithically, advancing a view that specific
+governments see the Amazon as an instance of only one specific problem.
+Albeit the current calls to understand the environment as a
+social-cultural construction and to identify the effect of culture on
+environmental outcomes \citep{lepolaindewaroux2021}, we lack empirical
+accounts of how the Brazilian Amazon has been constructed as a problem
+over time, by geographical location, and between and within governments
 
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
-First, nature should be conquered by men.
-Second, exploiting natural resources would render the Amazon region a global powerhouse.
-Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
-@capobianco2019 describes the period from the 1950-80 in a similar fashion, referring to a wider range of policies of economic integration: the 1953 Plano de Valorização Econômica da Amazônia; the 1966 Superintendência do Desenvolvimento da Amazônia; the 1967 Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande Carajás and Programa Calha Norte; among others.
+In this article, we investigate how the Brazilian Amazon has been
+constructed as a problem in political discourses. Building on
+\citet{hirschman1963} concept of chosen problems in policy making, we
+propose a framework to identify how problem-construction. Although
+problem-construction takes place in a series of instances (e.g.~policy
+committees, legislative bodies, media, etc.), we analyze the case of
+political discourse by Brazilian presidents since 1985. We opt for
+presidential speeches for three reasons. First, political discourses at
+the top have the power to introduce and justify public policy, as well
+as shape its perception to broad audiences \citep{zarefsky2004}. In
+turn, policy perception is key for policy adoption and implementation
+\citep{alesina2009, lopez2020}. The literature has shown that
+deforestation rates in Brazil are more responsive to the government's
+environmental policy than exogenous factors as market fluctuations
+\citep{assuncao2015, capobianco2019, capobianco2021}. Thus,
+understanding how policy comes about discursively is important. Second,
+environmental discourse at the top can help expand or restrict what
+types of behaviors are accepted in the ground. When Brazilian presidents
+speak about the Amazon it not only makes headlines, nationally and
+internationally\citep{brice2021, harris2021, miranda2021}, but also
+incites responses, shapes expectations, and feeds into the behavior of
+many actors involved in the Amazon, from investors to agribusiness to
+local farmer. This is especially pertinent for deforestation as previous
+research found that policy expectations, generated from material and
+discursive governmental practices, are a crucial factor in decisions to
+deforest at the ground \citep{capobianco2019, campbell2015}. Unpacking
+discourse at the top might help us raise hypotheses about environmental
+outcomes that are culturally situated. Finally, as our theoretical
+framework suggests, problem-construction varies by geographic location.
+Presidential discourses take place in a series of sites with diverse
+audiences: from launching a new bridge in a small municipality in the
+middle of the Amazon, to a keynote speech in a business association in
+São Paulo, to the UN general assembly in New York. Working with
+presidential discourses allows us to identify this variation in
+meaningful ways and better how the Amazon is socially constructed.
 
-The economic integration problem advances the view that the Brazilian Amazon needs to be developed and modernized.
-The policy solution relates to the creation of a series of policies, often centralized by the federal government and thus external to the region [@becker2005], that have at its core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.
+To investigate how the Brazilian Amazon has been constructed as a
+problem in political discourses, we create a dataset containing 6130
+official presidential speeches by all Brazilian presidents since 1985.
+We subset the dataset by identifying Amazonian related statements within
+these speeches. We find that 2014 sections in these discourses refer to
+the Amazon at least once. We then develop a codebook grounded on
+Amazonian historiography to code how each of these statements constructs
+the Amazon as a particular problem. We use this codebook to manually
+code a randomly selected training set of the Amazonian related
+statements. Using R, we then train a supervised machine-learning model
+in the hand-coded set and automatically label the remaining set of
+Amazonian statements. We then conduct a descriptive and inferential
+analysis of this data, tying our findings to endogenous and exogenous
+events related to deforestation.
 
-### 2.1.3 Environmental conservation
+Our findings are threefold. First, endogenous events as the death of
+Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the
+2015 Paris Summit, and the 2021 London Summit drive generally the
+interest in the Amazon. That seems to be the case even after controlling
+share of annual speeches mentioning the Amazon for deforestation,
+inflation, and speaker. Second, there was a sharp decrease in economic
+related problem-constructions from the late 1990 to 2010, matched by an
+increase in speeches that construct the Amazon as a problem of social
+development and environmental conservation. This trend is reversed in
+the late 2010s, with the twist of sovereignty making a strong comeback.
+Finally, using a multinominal model, we find that the farthest away the
+speaker is from the Amazon, be it within the country in non-Amazonian
+States or outside Brazil, the more likely the speaker is to construct
+the Amazon as a problem of environmental conservation than economic
+integration or social development.
 
-The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
-A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of centalized economic integration policies [@acker2021; @capobianco2021; @hecht1990].
-As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
-This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
-They define it as an emphasis on local livelihoods of people while protecting nature.
-@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies: the 2001 Sistema Nacional de Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the 2004 Plano de Ação para a Prevenção e Controle do Desmatamento na Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional das Mudanças Climáticas; among others.
+This article proceeds as follows: first, we review Amazonian literature
+to identify the main policy-cycles and their underlying problem
+construction. We then propose a theoretical framework to understand
+problem-construction and discourse. In the methodology section, we
+operationalize our framework and present the codebook. Section four
+portrays our main results. Finally, we conclude by discussing our
+findings and proposing future research.
 
-The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
-The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
+\hypertarget{amazonian-policy-cycles-discourse-and-problem-construction}{%
+\section{2 Amazonian policy-cycles, discourse, and
+problem-construction}\label{amazonian-policy-cycles-discourse-and-problem-construction}}
 
-### 2.1.4 Policy and discourse
+\hypertarget{literature-review-policy-cycles-in-the-amazonian-literature}{%
+\subsection{2.1 Literature Review: policy-cycles in the Amazonian
+literature}\label{literature-review-policy-cycles-in-the-amazonian-literature}}
 
-Different authors have proposed similar periodization for policy-cycles in the Amazon: a focus on sovereignty until the military dictatorship of 1964, followed by strong economic integration policies until the mid 1980s, and finally a shift to conservation after the 1992 Earth Summit.
-At the macro-historical level, the wider Amazonian vision of the 1964 military dictatorship, encompassed by the whole group of policies they adopted, for instance, did favor economic integration.
-Nevertheless, at the level of policies adopted, there is more variation than these periods would suggest.
-For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest.
-Framing this policy as an issue of economic integration, then, can be seen as a choice.
+For the purposes of this article, we understand Amazonian literature as
+the body of research by social and environmental scientists that tells
+the story of diverse policies adopted to solve problems in the region.
+The three main policy-cycles we identify in Amazonian literature are:
+national sovereignty, economic integration, and environmental
+conservation. We tie each one of them to a specific problem and
+consequently a solution. We close the sub-section reviewing the
+relationship between policy, presidential discourse, and environmental
+problems.
 
-Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently.
-For historical inquiry, it is important to periodize policy cycles comprehensively.
-We largely agree with what the literature assigns to previous governments.
-However, the possibility of varied portrayals of the same policy opens up an understanding agenda-setting and policy-adoption that is less linear.
+\hypertarget{national-sovereignty}{%
+\subsubsection{2.1.1 National sovereignty}\label{national-sovereignty}}
 
-Problem-construction at the level of discourse is also more varied.
-They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations^[For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
-(2021).
-For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).], we only find one systematic analysis of Amazonian discourse.
-@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+In The Fate of the Forest: Developers, Destroyers, and Defenders of the
+Amazon, Hecht and Cockburn write that all over the world tropical
+forests are destroyed, but ``what imbues the case of the Amazon with
+such passion is the symbolic content of the dreams it ignites''
+\citeyearpar[pp.1]{hecht1990}. It started with the first natural history
+of the New World, by Oviedo in 1535, who recounts the stories of
+conquest of local populations and gold hoarders. The dream of fortunes
+to be found in the Eldorado composed the imaginaries of
+\emph{bandeirantes}\footnote{\emph{Bandeirantes} means
+  ``flag-carriers'', the word is used to designate Portuguese colonials
+  and later Brazilian explorers, expanding the Brazilian territory
+  beyond what the Tordesillas Treaty established. The treaty allocated
+  almost the whole Amazonian territory to the Spanish Empire, the
+  bandeirantes took much of the territory afterwards.} from the
+southeast of Brazil and colonizers from everywhere else. It rendered the
+territory the venue for aspiration and object of an intense scramble in
+the subsequent centuries, defined as ``a (\ldots) form of nation
+building (\ldots)'' (Hecht and Cockburn 1990, preface). The Portuguese
+empire and subsequently the Brazilian monarchy were concerned with
+establishing their territory. In the process of securing Amazonian
+borders, Brazil thwarted ``the imperial ambitions of France, Britain,
+the United States, Belgium, Bolivia, and Peru'' \citep[pp.8]{hecht2013},
+and when the dust settled and the scramble was over, half of the Amazon
+emerged Brazilian. While Brazilian military diplomacy was very
+successful, the process did not come without its traumas. A significant
+experience were the negotiations with Bolivia in 1902 to secure the
+Amazonian state of Acre, during which they found out about American
+attempts to trick Brazil\citep{hecht1990}. This case was still part of
+the memory of the generals who led the country during the military
+dictatorship of 1964 and wanted to protect Brazil's sovereignty over the
+Amazon from the communist threat during the Cold
+War\citep{garfield2013}.
 
-We also find several analyzes of environmental discourse in American presidential speeches.
-@calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989.
-Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change (ibid).
-He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-In another article, @calderwood2020 tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988 but also others, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on climate change does change based on location.
-Another example is @bevitori2015, who investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
-The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
+As we move from a world where non-state actors gain importance in
+environmental governance and international politics generally
+\citep{silva-muller2022, andonova2014, westerwinter2021}, the
+sovereignty problem becomes more varied. Multiple non-state actors
+(NGOs, foundations, IOs, and so on) join the conversation about
+Amazonian policies more substantially as the military dictatorship
+starts to end \citep{hochstetler2021, capobianco2019, franchini2019}.
+Threads to national sovereignty, consequently, can be interpreted as
+coming from a different set of actors than before. Allegedly false
+claims about the Brazilian Amazon in international and domestic fora,
+for instance, are often tied to strategies of `internationalizing' the
+Amazon. This might come both from foreign actors as well as domestic
+non-state actors. Relatedly, mentions of Amazonian myths which have been
+debunked as the `Earth of the Lungs', are also tied to
+internationalizing strategies.
 
-While these findings hold for the US, they suffice to argue that presidents can raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance.
-That entails the same president can combine, substitute, or change how they talk about the Amazon and these views can reflect, or not, the current political scenario, issues in the agenda, or talk to a different policy cycle at times.
+The sovereignty problem advances the view that the Brazilian Amazon is
+Brazilian and foreign presence, non-state presence and alleged lies are
+part of a broader strategy to internationalize the region. The policy
+solutions relate to close monitoring of the borders, strict regimes
+related to entry in the region, and combating alleged disinformation
+about the Amazon nationally and internationally.
 
-## 2.2 Theoretical framework: problem-construction and presidential discourse
+\hypertarget{economic-integration}{%
+\subsubsection{2.1.2 Economic integration}\label{economic-integration}}
 
-In "Journey towards Progress", Hirschman (1963) analyzes three policy problems in three different Latin American countries.
-The author draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
-Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
-Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests [@hirschman1963, pp.388-91].
-Choosing a problem, though, entails a decision on how to represent it [@bacchi2009].
-As Bacchi puts "policy has a cultural dimension.
-It takes shape within specific historical and national or international contexts" [-@bacchi2009, pp.10].
-The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in policy.
-Hirschman exemplifies chosen problems with the case of the construction of Brasilia [-@hirschman1975, pp.388].
-But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
-How to represent a policy is a matter of choice.
-And different representations speak to different audiences.
+The Vargas dictatorship (1937-46) and the military dictatorship
+(1964-89) took over the task of modernizing the Amazon. In 1966, the
+Brazilian Military launched Operation Amazon, a policy to modernize the
+region based on a set of assumptions \citep{acker2014}. First, nature
+should be conquered by men. Second, exploiting natural resources would
+render the Amazon region a global powerhouse. Third, such a project
+would integrate the region with the rest of the country. Concretely,
+this meant a series of infrastructure projects, such as roads and dams,
+incentives for settlers to develop ranches and expand the agricultural
+frontier, as well as establishing tax free zones to attract industry.
+The capital to conduct such changes, paradoxically, came from national
+and international sources \citep{acker2014}, leading to a series of
+national and international enterprises settling in the Amazon region.
+\citet{capobianco2019} describes the period from the 1950-80 in a
+similar fashion, referring to a wider range of policies of economic
+integration: the 1953 Plano de Valorização Econômica da Amazônia; the
+1966 Superintendência do Desenvolvimento da Amazônia; the 1967
+Superintendência da Zona Franca de Manaus; the 1970 Plano de Integração
+Nacional; the 1975 Programa Polamazônia; the 1980s Programa Grande
+Carajás and Programa Calha Norte; among others.
 
-We understand that depending on how the problem is represented to be, it can be a solution of problems that are considered pressing.
-Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-Problem-construction takes place in different sites: national media, legislative bodies, international fora, policy committees, among others.
-What eventually becomes policy is a product of a multi-faceted process in all these different sites.
-One avenue through which governments can emphasize the representations of a problem is discourse.
-We assume that problem-construction at the level of discourse is varied.
-They are not monolithic in time, across location, or even by the same speaker.
+The economic integration problem advances the view that the Brazilian
+Amazon needs to be developed and modernized. The policy solution relates
+to the creation of a series of policies, often centralized by the
+federal government and thus external to the region \citep{becker2005},
+that have at its core the development of the necessary infrastructure
+(physical, fiscal, or monetary) to integrate the region in the national
+and international economy.
 
-We argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context.
-In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connect the region to issues of sovereignty, economic integration, social development, or environmental conservation.
-Presidents choose to represent the region as a particular problem.
-As Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
-Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country.
-We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment [@bevitori2015] without embedding them in the histories of the issue in the country.
+\hypertarget{environmental-conservation}{%
+\subsubsection{2.1.3 Environmental
+conservation}\label{environmental-conservation}}
 
-These are the cornerstones of our framework: while governments are sometimes portrayed as proponents of a specific policy-solution, the way they construct the Amazon as a problem varies.
-The specific problem-constructions that we propose are embedded in Amazonian historiography and connect presidential speeches to Brazilian larger social-cultural history.
-We propose a framework to understand variation in problem-construction as a choice that is responsive to geographic location, time, and speaker.
+The rapid economic changes in the region in the 1960s, 1970s, and 1980s
+were matched with the birth of environmental institutions such as the
+New Forest Code (1964), the Secretary of Environment (1973), and the
+National Environment Law (1980) \citep{drummond2006}. A common
+explanation for these institutions in the Amazonian literature is the
+impression of lack of control after years of centalized economic
+integration policies \citep{acker2021, capobianco2021, hecht1990}. As
+deforestation, fires, and violence rose in the region, catching
+international attention, the military government deemed as necessary the
+establishment of an environmental bureaucracy. This process accelerated
+in the late 1980s, with the birth of modern environmentalism epitomized
+in the 1992 Earth Summit in Rio de Janeiro
+\citep{hochstetler2021, capobianco2021}. \citet{hochstetler2007} argue
+that during preparations for the summit, a new form of Brazilian
+environmentalism emerged: socio-environmentalism. They define it as an
+emphasis on local livelihoods of people while protecting nature.
+\citet{capobianco2019} argues in a similar line, establishing
+socio-environmentalism as the main government response in the 1990s and
+early 2000s in a series of policies: the 2001 Sistema Nacional de
+Unidades de Conservação; the 2003 Programa Amanônia Sustentavel; the
+2004 Plano de Ação para a Prevenção e Controle do Desmatamento na
+Amazônia Legal; the 2004 Plano BR-163 Sustentável; the 2010 Lei Nacional
+das Mudanças Climáticas; among others.
 
-# 3 Research Design
+The conservationist problem-construction advances the view that Amazon
+should be preserved, deforestation should be halted, and the sustainable
+practices of indigenous and local peoples should be maintained through
+protection of their territories and rights to self-determination
+\citep{hochstetler2007}. The policy solution implies more investment in
+command-and-control infrastructure (as remote-sensing technology for
+environmental outcome measurement), more investment in the valuation of
+standing ecosystems through incentive schemes, and more policies
+facilitating indigenous environmental practices.
 
-To operationalize our theoretical framework, we adopt a mixed-methods approach using manual coding and supervised machine learning.
-We explain our research design and each step of the procedure in this section.
+\hypertarget{policy-and-discourse}{%
+\subsubsection{2.1.4 Policy and discourse}\label{policy-and-discourse}}
 
-## 3.1 Data and modeling: operationalizing Amazonian problem construction
+Different authors have proposed similar periodization for policy-cycles
+in the Amazon: a focus on sovereignty until the military dictatorship of
+1964, followed by strong economic integration policies until the mid
+1980s, and finally a shift to conservation after the 1992 Earth Summit.
+At the macro-historical level, the wider Amazonian vision of the 1964
+military dictatorship, encompassed by the whole group of policies they
+adopted, for instance, did favor economic integration. Nevertheless, at
+the level of policies adopted, there is more variation than these
+periods would suggest. For example, the 1980 Programa Calha Norte did
+contain elements to ensure sovereignty, integrate the region to the
+country's economy, and preserve the forest. Framing this policy as an
+issue of economic integration, then, can be seen as a choice.
 
-We build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
-We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches for all the presidents of Brazil since 1985.
-We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 946 speeches are, at least partially, about the Amazon from the 6130.
+Hence, while the literature might represent governments as coherent
+proponents of a particular policy retroactively, political actors might
+have adopted strategies that outline problem-constructions of policies
+differently. For historical inquiry, it is important to periodize policy
+cycles comprehensively. We largely agree with what the literature
+assigns to previous governments. However, the possibility of varied
+portrayals of the same policy opens up an understanding agenda-setting
+and policy-adoption that is less linear.
 
-Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
-By doing so we create our unit of analysis: an Amazonian statement.
-We use Amazon statements as our unit of analysis for two main reasons.
-First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
-This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
-On average, an Amazonian statement contains 123 words.
+Problem-construction at the level of discourse is also more varied. They
+are not monolithic in time, across location, or even by the same
+speaker. While governmental discourses in Brazil have been studied for
+topic such as inflation or race relations\footnote{For an overview on
+  how inflation and political discourse in Brazil see Porto (2007),
+  Malheiros-Poulet (2012), and Fonseca et al.~(2021). For a few studies
+  on racist and anti-racist discourses in Brazil see Htun (2004), Silva
+  and Larkins (2019) and Dijk (2020).}, we only find one systematic
+analysis of Amazonian discourse. \citet{barros2020} investigates
+Amazonian discourse in the Brazilian Congress with the objective of
+identifying the arguments put forth by congressmen. The main finding is
+that the economic value of the Amazon for the cattle industry is the
+most salient narrative, leading the author to conclude there is a
+mismatch between the international debate (which focuses on
+preservation) and the national debate (which focuses on economic
+development).
 
-After revising the literature (section 2), we selected a random sample of these Amazonian statements to develop a codebook for identifying how the Amazon is constructed as a problem in presidential discourse (see Table 1 below).
-We understand Amazonian problem-constructions as Weberian ideal types, that is, an unified analytical construct portraying a 'pure' version of a phenomenon.
-This serves the purpose of allocating empirical observations within a range of possibilities.
-We identify the three problem-constructions derived from the literature (national sovereignty, economic integration, and environmental conservation) in the sample of Amazonian statements.
-However, in addition to them, we inductively identified a fourth problem construction that the literature does not explicitly cover: social development.
-Presidents sometimes opt to emphasize the lack of hospitals, sanitation, and schools in relation to peoples' constitutional rights when speaking about the Amazon.
-We saw this code category as substantially different from the other three, hence, we created the code category 'social development'.
-In their conceptualization, each code is mutually exclusive in its conceptualization, meaning that they cover different forms of constructing the Amazon as a problem, though each Amazonian statement might be assigned to one or more codes.
-A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration or a problem of social development and conservation.
-Amazonian statements, thus, can be either coded as a pure-types or mixed-types.
+We also find several analyzes of environmental discourse in American
+presidential speeches. \citet{calderwood2019} examines 2919 mentions of
+climate change in American official presidential speeches since 1989.
+Among various findings, one that stands out is that American presidents
+frequently side-step the environmental aspects of climate change (ibid).
+He also identifies a shift from economic to security framing of climate
+issues, side-lining its environmental aspects. In another article,
+\citet{calderwood2020} tests the effect of geographic location and type
+of communication regarding climate change. Building prominently on
+\citet{putnam1988} but also others, he hypothesizes that presidents are
+more likely to mention climate change in foreign locations, and that
+location influences the specific discursive approach and tone they
+adopt. He finds evidence in support of his hypothesis, suggesting
+American presidential discourse at the top on climate change does change
+based on location. Another example is \citet{bevitori2015}, who
+investigates how the `environment' has been constructed in American
+presidential discourse since 1960 using a more automated approach. The
+author finds that mentions of the environment are typically co-selected
+with the pronoun `our', as well as with `economy', `clean', and
+`preserve'.
 
-```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
-                                                    "Social Development", "Environmental Conservation"),
-                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
-We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.", "This code constructs the Amazon region and/or forest as an issue of economic integration.
-It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
-It advances the view that Amazon is full of citizens who should have their rights guaranteed.
-This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
-This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
-This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
-                           Example = c("We can now walk the world and when we debate about the Amazon, we do not need to wait for questions, we are the ones who are going to say what we are doing in the Amazon.
-We do not need to keep on saying ‘the Amazon is ours’ just for saying it, people often say this without much conviction either.
-If the Amazon has been ours since Cabral (European discoverer of Brazil) stepped here, why do we now have to worry about the Amazon?
-(Lula 2008)", "", "", ""))
-knitr::kable(codebook, "simple")
-```
+While these findings hold for the US, they suffice to argue that
+presidents can raise different points about the Amazon at local,
+national, or international settings, depending on who they assume their
+audience is at that specific instance. That entails the same president
+can combine, substitute, or change how they talk about the Amazon and
+these views can reflect, or not, the current political scenario, issues
+in the agenda, or talk to a different policy cycle at times.
 
-With the codebook in hands, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazon Statements identified.
-Inter-coder agreement for each of the four main categories was 85%, on average.
-For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
-Statements that mention the stem "amazon", but are not about the Brazilian Amazon, for example, might a greeting to the Governor of the Amazonas, were coded as false positives.
-The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-The training set is used to train the supervised machine-learning model that automatically classifies observations while the validation set is used to make sure the model fit is appropriate.
+\hypertarget{theoretical-framework-problem-construction-and-presidential-discourse}{%
+\subsection{2.2 Theoretical framework: problem-construction and
+presidential
+discourse}\label{theoretical-framework-problem-construction-and-presidential-discourse}}
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006]^[For more information on this please see the extended methodology.
-The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the  validation set.
-The extended methodology also includes a more detailed codebook table with further coding guidelines.].
-After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set, we use the model to automatically code the remaining 1007 Amazonian statements.
-The model was also trained to identify false positive observations, which we chose to delete for analysis since these are not meaningful statements about the Amazon.
-The final dataset for analysis contains 1895 coded Amazonian statements.
-Finally, we use poldis once more to extract locations for all speeches in the data.
-These locations represent the Brazilian state in which certain speech was given or an international country.
+In ``Journey towards Progress'', Hirschman (1963) analyzes three policy
+problems in three different Latin American countries. The author draws a
+conceptual distinction between pressing problems (pressured from outside
+parties to the government) and chosen problems (chosen by the government
+at their own discretion). Pressing problems can be either privileged or
+neglected depending on the degree of pressure exercised by the
+interested group. Problems can change from pressing to chosen across
+time and in space as a function of solutions becoming available,
+changing level of government control in society, or top policymakers
+shifting interests \citep[pp.388-91]{hirschman1963}. Choosing a problem,
+though, entails a decision on how to represent it \citep{bacchi2009}. As
+Bacchi puts ``policy has a cultural dimension. It takes shape within
+specific historical and national or international contexts''
+\citeyearpar[pp.10]{bacchi2009}. The existence or proposal of a policy
+generally implies that there is a (public) problem that needs
+(governmental) action to be fixed. The alleged problem is not always
+explicitly stated in policy. Hirschman exemplifies chosen problems with
+the case of the construction of Brasilia
+\citeyearpar[pp.388]{hirschman1975}. But building Brasilia can solve a
+problem of regional inequality, a problem of a dormant economy without
+state investment, a problem of political representation, or all three.
+How to represent a policy is a matter of choice. And different
+representations speak to different audiences.
 
-## 3.2 Analysis and limitations
+We understand that depending on how the problem is represented to be, it
+can be a solution of problems that are considered pressing. Different
+problem-constructions can address the demands of different
+constituencies and it is up to the discretion of the political actor to
+construct a particular problem in a particular way given context.
+Problem-construction takes place in different sites: national media,
+legislative bodies, international fora, policy committees, among others.
+What eventually becomes policy is a product of a multi-faceted process
+in all these different sites. One avenue through which governments can
+emphasize the representations of a problem is discourse. We assume that
+problem-construction at the level of discourse is varied. They are not
+monolithic in time, across location, or even by the same speaker.
 
-To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves.
-To test whether different problem constructions change according to location, we run a multinomial regression model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-We code 4 different location categories for where speeches take place, they are: Amazonian states, non-Amazonian states, Brasilia, and International.
-In the model, we also control for annual deforestation rates, annual inflation rates, and election years in the model as these are variables which could mitigate the correlations between problem construction and location^[See extended methodology for more information on model selection, controls and post estimation tests.].
-We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.
+We argue that presidents can employ specific problem-constructions that
+build objects as specific problems depending on the context. In the
+specific case of the Brazilian Amazon, we contend that Amazonian
+problem-construction connect the region to issues of sovereignty,
+economic integration, social development, or environmental conservation.
+Presidents choose to represent the region as a particular problem. As
+Bacchi (2009), we argue that problem-constructions touch on shared
+meanings about the region that are available to the speaker as part of
+larger social-cultural history. Thus, the ways a president speaks are
+culturally and historically mediated and need to be embedded in the
+wider history of the region and country. We consider this an advancement
+in relation to scholars looking at American presidential speeches, as
+they just count mentions to climate change
+\citep{calderwood2019, calderwood2020, brown2017} or environment
+\citep{bevitori2015} without embedding them in the histories of the
+issue in the country.
 
-These procedures come with its limitations.
-Our codebook is developed using specific Amazon related vocabulary.
-For example, a statement will be coded as economic integration if it is a meaningful support to the Zona Franca of Manaus or a Dam in the Amazon.
-However, the economy is generally a topic that presidents speak about.
-Hence, high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
-Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
-Nevertheless, our dataset covers only what is considered an official remark.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently start to appear in social media.
-Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.
+These are the cornerstones of our framework: while governments are
+sometimes portrayed as proponents of a specific policy-solution, the way
+they construct the Amazon as a problem varies. The specific
+problem-constructions that we propose are embedded in Amazonian
+historiography and connect presidential speeches to Brazilian larger
+social-cultural history. We propose a framework to understand variation
+in problem-construction as a choice that is responsive to geographic
+location, time, and speaker.
 
-# 4 How has the amazon been constructed as a problem?
+\hypertarget{research-design}{%
+\section{3 Research Design}\label{research-design}}
 
-This section presents the three main findings of our analysis.
-We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985.
-In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1.
-Finally, we run a multinomial model to show how problem constructions change as the speaker moves further away from the Amazon region.
+To operationalize our theoretical framework, we adopt a mixed-methods
+approach using manual coding and supervised machine learning. We explain
+our research design and each step of the procedure in this section.
 
-## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
+\hypertarget{data-and-modeling-operationalizing-amazonian-problem-construction}{%
+\subsection{3.1 Data and modeling: operationalizing Amazonian problem
+construction}\label{data-and-modeling-operationalizing-amazonian-problem-construction}}
 
-Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^2], economic situation, and speaker (see appendix for methodological details).
-We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
-These points coincide with exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+We build upon the dataset provided by \citep{cezar2020} which contains
+all official speeches by Brazilian Presidents from 1985 to 2019 scrapped
+from the archives of the Brazilian Presidential Library. We update the
+dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches for all the presidents of
+Brazil since 1985. We then identify all speeches about the Amazon as a
+region, peoples, or forest out of the 6130 speeches. We do so by
+detecting all speeches in which the stem ``amazon'' appears. In
+Portuguese, the stem captures terms such as ``Amazonia'', ``Amazonica'',
+``Amazonidas'', ``Amazonense(s)'', ``Amazonas'', among others. We find
+that 946 speeches are, at least partially, about the Amazon from the
+6130.
 
-[^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
-Matching deforestation with speech dates is a complicated endeavor.
-INPE published consolidated deforestation data with almost two years of delay until 2005 [@capobianco2021, pp.
-60].
-Preliminary data was published earlier, but with lower degrees of confidence in the findings.
-For the subsequent years, the consolidated figures for a given year tend to come out in August of the subsequent year.
-However, it also seems to be the case that the executive government have access to the data before everyone else.
-In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), circulates within the same year.
-The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures [@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988].
-Hence, we believe the most appropriate way of matching is without any lags on deforestation.
+Using the poldis R package, we proceed to extract two sentences before
+and two sentences after the sentence in which the stem ``amazon''
+appears. We opt for picking two sentences before and two sentences
+after, rather than words, because sentences usually contain a cohesive
+idea. By doing so we create our unit of analysis: an Amazonian
+statement. We use Amazon statements as our unit of analysis for two main
+reasons. First, working at the level of statements allows us to identify
+only passages that are meaningful for our specific purpose. Second, it
+increases the number of our observations and its variety meaningfully,
+allowing for more specificity in our analysis. This process yields 2014
+unique Amazonian statements across the 946 speeches about the Amazon
+identified. When an Amazonian statement contains two or more matches of
+the stem ``amazon'', we get two sentences before the first match and two
+sentences after the last match. On average, an Amazonian statement
+contains 123 words.
 
-First, we observe a steady increase from about 5% in 1985 to 32% 1989.
+After revising the literature (section 2), we selected a random sample
+of these Amazonian statements to develop a codebook for identifying how
+the Amazon is constructed as a problem in presidential discourse (see
+Table 1 below). We understand Amazonian problem-constructions as
+Weberian ideal types, that is, an unified analytical construct
+portraying a `pure' version of a phenomenon. This serves the purpose of
+allocating empirical observations within a range of possibilities. We
+identify the three problem-constructions derived from the literature
+(national sovereignty, economic integration, and environmental
+conservation) in the sample of Amazonian statements. However, in
+addition to them, we inductively identified a fourth problem
+construction that the literature does not explicitly cover: social
+development. Presidents sometimes opt to emphasize the lack of
+hospitals, sanitation, and schools in relation to peoples'
+constitutional rights when speaking about the Amazon. We saw this code
+category as substantially different from the other three, hence, we
+created the code category `social development'. In their
+conceptualization, each code is mutually exclusive in its
+conceptualization, meaning that they cover different forms of
+constructing the Amazon as a problem, though each Amazonian statement
+might be assigned to one or more codes. A statement can, for example,
+construct the Amazon as a problem of sovereignty and a problem of
+economic integration or a problem of social development and
+conservation. Amazonian statements, thus, can be either coded as a
+pure-types or mixed-types.
+
+\begin{longtable}[]{@{}lll@{}}
+\toprule
+Problem\_Construction & Description & Example \\
+\midrule
+\endhead
+National Sovereignty & This code constructs the Amazon region and/or
+forest as an issue of national sovereignty. We understand claims of
+sovereignty as a particular problem-construction that touches on
+imaginaries of external threats to territory. Relatedly, we also
+understand sovereignty as raising concerns about wrong perspectives and
+criticism from foreign and non-state actors about
+governments\textless U+2019\textgreater{} actions related to the
+Brazilian Amazon. In all, it advances the view that the Amazon is
+Brazilian, foreign, and non-state presence in the region needs to be
+monitored closely. & Congressman, the fundamental link for Brazil to
+really head in the direction to prosperity. I would like first, Hu
+Chunhua, to thank you for the words of your ambassador to Brazil
+recognizing our sovereignty over the Amazonian region during that recent
+episode in the G7 meeting. I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words
+about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019) \\
+Economic Integration & This code constructs the Amazon region and/or
+forest as an issue of economic integration. It advances the view that
+the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives,
+creating a diverse set of infrastructure (roads, dams, internet, radio,
+energy), fostering differing industries (tourism, mining, cattle,
+agriculture and so on) through tax-free zones, as well as facilitating
+the exploitation of natural resources for developmental purposes. & If
+you allow me, in the Amazon - which for a long time stayed asleep due to
+the lack of coordinated actions - have already taken a few structuring
+actions. We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai,
+until up there, the red line {[}in a map{]} that goes all the way up in
+the direction of Venezuela, that is the so-called BR-174 highway. This
+highway will allow production in the Tax Free Zone in MAnaus to be
+competitive, not within, but outside, that is the vocation of the the
+Tax Free Zone to export; and we can even do it through the Caribbean
+(Cardoso 02/07/1997) \\
+Social Development & This code constructs the Amazon region and/or
+forest as an issue of social development. It advances the view that
+Amazon is full of citizens who should have their rights guaranteed. This
+refers to the construction of schools and universities (right to
+education), of hospitals (right to health), and of housing (right to
+house). This also includes guarantees of a dignified life with decent
+employment, access to water and sanitation, as well as access to
+electricity, internet, radio, and light. Finally, this includes
+referrals to culture and the right to vote. & The state does not work
+for profits, the state needs to guarantee dignity, we find that a
+citizen who lives in the riverside of the Amazon river, 600 kilometers
+from Manaus, has the right to have the electricity in their house, to
+owe a fridge, to owe a television where to watch the soap operas. We
+have invested over 14 billion reais in this program, in three and a half
+years. Do you know how many electrical lines we have already built? One
+million kilometers of lines. (Lula 20/11/2009) \\
+Environmental Conservation & This code constructs the Amazon region
+and/or forest as an issue of conservation. This problem-construction
+focuses on the value of a standing forest and of the preserved ecosystem
+in the region. The conservationist narrative advances the view that
+Amazon should be preserved, deforestation should be halted, and the
+practices of indigenous and traditional populations should be maintained
+and fostered. It advances the view that the emission of greenhouse
+gasses should be halted, that renewable energy should be supported, and
+that protected areas should be created. & I have put in place emergency
+measures, I have suspended the exports of wood logs, I have suspended
+the fiscal incentives and credits to projects that could damage the
+environment in the amazon and I have made a license mandatory to gold
+mining that prohibits utilizing mercury in the process. This began the
+restructuring of the governmental system of control and preservation of
+the environment, I have created the Brazilian Institute for the
+Environment and Natural Resources {[}IBAMA{]}, which will be headed by
+Dr.~Mesquita (Sarney 20/07/1989) \\
+\bottomrule
+\end{longtable}
+
+With the codebook in hands, each one of the authors, separately,
+hand-coded the same set of 1007 randomly selected Amazonian statements.
+This amount refers to 50\% of all the Amazon Statements identified.
+Inter-coder agreement for each of the four main categories was 85\%, on
+average. For each non-matching coded observation, the co-authors
+discussed and sorted their disagreements. Statements that mention the
+stem ``amazon'', but are not about the Brazilian Amazon, for example,
+might a greeting to the Governor of the Amazonas, were coded as false
+positives. The manually coded data is then randomly divided into a
+training set, containing 80\% of the hand-coded observations (806
+observations), and a validation set, containing the remaining 20\% of
+the hand-coded data (201 observations). The training set is used to
+train the supervised machine-learning model that automatically
+classifies observations while the validation set is used to make sure
+the model fit is appropriate.
+
+We chose to employ a support-vector machine (SVM) algorithm to label
+texts, that is, a non-probabilistic linear classifier that classifies
+documents by assigning points in mapped space to maximize the gap
+between binary categories \citep{meyer2021, noble2006}\footnote{For more
+  information on this please see the extended methodology. The document
+  includes a detailed discussion of how the SVM algorithm was chosen
+  over other algorithms based on evaluation of performance of trained
+  models for labeling the validation set. The extended methodology also
+  includes a more detailed codebook table with further coding
+  guidelines.}. After the SVM model is trained and tuned, and the model
+shows to appropriately fit the validation set, we use the model to
+automatically code the remaining 1007 Amazonian statements. The model
+was also trained to identify false positive observations, which we chose
+to delete for analysis since these are not meaningful statements about
+the Amazon. The final dataset for analysis contains 1895 coded Amazonian
+statements. Finally, we use poldis once more to extract locations for
+all speeches in the data. These locations represent the Brazilian state
+in which certain speech was given or an international country.
+
+\hypertarget{analysis-and-limitations}{%
+\subsection{3.2 Analysis and
+limitations}\label{analysis-and-limitations}}
+
+To analyze our data, we first present a series of different plots on
+proportions of Amazonian statements and problem-constructions over time
+and by presidents. We control proportions for factors that might affect
+the incidence of the Amazon in speeches and portray both real and
+controlled curves. To test whether different problem constructions
+change according to location, we run a multinomial regression model in
+which different problem constructions (as categories) are the dependent
+variable and location is the independent variable. We code 4 different
+location categories for where speeches take place, they are: Amazonian
+states, non-Amazonian states, Brasilia, and International. In the model,
+we also control for annual deforestation rates, annual inflation rates,
+and election years in the model as these are variables which could
+mitigate the correlations between problem construction and
+location\footnote{See extended methodology for more information on model
+  selection, controls and post estimation tests.}. We interpret the
+plots and model considering multiple Amazon related events and policies
+over the last 30 years, as well as their correlations with different
+presidents and locations, while embedding problem-construction in
+contemporary happenings.
+
+These procedures come with its limitations. Our codebook is developed
+using specific Amazon related vocabulary. For example, a statement will
+be coded as economic integration if it is a meaningful support to the
+Zona Franca of Manaus or a Dam in the Amazon. However, the economy is
+generally a topic that presidents speak about. Hence, high incidence of
+economic integration in Amazonian statements can also be related to the
+higher importance of this problem-construction in Brazil in time.
+Moreover, we classify statements as Amazonian based on a dictionary
+composed of a single lexicon stem: ``amazon''. We chose to do so knowing
+that a few speeches about the Amazon might not contain the lexicon
+``Amazon'', for example, when the president says, ``the forest'' or
+``deforestation''. Hence, we might be missing statements about Amazon
+that do not refer to it. However, we consider this safer as we cannot be
+sure that mentions of the forest or deforestation do not correspond to
+other biomes such as the Cerrado or the Mata Atlantica. Nevertheless,
+our dataset covers only what is considered an official remark.
+Presidents, though, give interviews, appear in debates, talk at campaign
+rallies, and more recently start to appear in social media.
+Problem-construction within presidential discourse, thus, also happens
+in different sites for which we do not account for in this paper.
+
+\hypertarget{how-has-the-amazon-been-constructed-as-a-problem}{%
+\section{4 How has the amazon been constructed as a
+problem?}\label{how-has-the-amazon-been-constructed-as-a-problem}}
+
+This section presents the three main findings of our analysis. We open
+with a broad overview of the evolution of the incidence of Amazon in all
+presidential speeches since 1985. In section 4.2, we focus on speeches
+that mention the Amazon, introducing the specific problem-constructions
+we presented in section 2.1. Finally, we run a multinomial model to show
+how problem constructions change as the speaker moves further away from
+the Amazon region.
+
+\hypertarget{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}{%
+\subsection{4.1 The rises and falls of the Amazon as a topic in
+presidential
+speeches}\label{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}}
+
+Figure 1 shows the proportion of speeches that mentions the Amazon in
+relation to all speeches in each year. The predicted share curve
+controls incidence for deforestation\footnote{The reasoning here is that
+  knowledge of high or low deforestation rates might drive presidents to
+  speak about the Amazon. Matching deforestation with speech dates is a
+  complicated endeavor. INPE published consolidated deforestation data
+  with almost two years of delay until 2005
+  \citep[pp.~60]{capobianco2021}. Preliminary data was published
+  earlier, but with lower degrees of confidence in the findings. For the
+  subsequent years, the consolidated figures for a given year tend to
+  come out in August of the subsequent year. However, it also seems to
+  be the case that the executive government have access to the data
+  before everyone else. In addition, other sources indicating if
+  deforestation is going up or down, as fire data or lower resolution
+  deforestation data (DETER for example), circulates within the same
+  year. The year of 1988 is particularly indicative of these
+  complications: a report dating 1988 was circulating with deforestation
+  and fire figures \citep{fearnside1990}, and a New York Times article
+  about the issue was written with comments by an INPE scientist
+  \citep{simons1988}. Hence, we believe the most appropriate way of
+  matching is without any lags on deforestation.}, economic situation,
+and speaker (see appendix for methodological details). We observe
+various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019. These
+points coincide with exogenous events that helps us explain the rises
+and falls of the Amazon in presidential discourse.
+
+First, we observe a steady increase from about 5\% in 1985 to 32\% 1989.
 This is the period when the Brazilian Constitution was being written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and protection of their territories [@hecht1990].
-These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-Two other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered and the New York Times published an article with pictures of the Amazon burning [@simons1988].
-Both incidents caught unprecedented international attention.
-President Sarney responded to these publicly, and proposed a new set of policies to address, named Nossa Natureza [@capobianco2021].
+Indigenous and traditional populations were instrumental in advocating
+for constitutional environmental rights and protection of their
+territories \citep{hecht1990}. These were eventually enshrined in
+article 225, which gives all Brazilians a right to a balanced
+environment, and in article 231, which grants indigenous and traditional
+populations a right over their territory. Two other factors are likely
+to explain this increase: in 1988 Chico Mendes was brutally murdered and
+the New York Times published an article with pictures of the Amazon
+burning \citep{simons1988}. Both incidents caught unprecedented
+international attention. President Sarney responded to these publicly,
+and proposed a new set of policies to address, named Nossa Natureza
+\citep{capobianco2021}.
 
-```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc1 <- pop %>%
-  count(amazon_speech, year)%>%
-  group_by(year)%>%
-  mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, year))
-pop2 <- pop %>% count(amazon_speech, year, president) %>%
-  group_by(year, president) %>%
-  left_join(perc1) %>%
-  filter(amazon_speech==1)
-pop2 <- left_join(pop2, AAI, by = "year")
-pop2 <- left_join(pop2, amazon_def_year, by = "year")
-model <- lm(perc ~ AAI+ def_year + president, data=pop2)
-pop2$predicted = predict(model, pop2)
-Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
-  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
-  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-       subtitle = "Sample composed by 6130 presidential speeches since 1985",
-       caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
-Amazon_year
-```
+\includegraphics[width=0.9\linewidth]{rticle_files/figure-latex/Figure 1: Amazonian speeches by year-1}
 
-While in 1990 there was a decrease to about 12.4%, we observe a novel increase to 15% and 25% in 1991 and 1992 respectively.
-The driver of this increase is likely to be the 1992 Earth Summit, which was being prepared by various state and non-state actors in the region and brought international attention to environmental topics in Brazil.
-One of the big announcements was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-During the Cardoso years (1994-2002), Amazonian speeches averaged at about 16% without strong variation.
-There were no big international or domestic events that drove the topic up.
-At the level of policy, though, we saw the birth of the National System of Protected Areas in 2001, and of the Amazon Regional Protected Areas Program.
-While the former created the legal framework for different types of protected areas to be created, the latter established a transnational partnership to finance the implementation of protected areas in the Amazon [@andonova2014].
+While in 1990 there was a decrease to about 12.4\%, we observe a novel
+increase to 15\% and 25\% in 1991 and 1992 respectively. The driver of
+this increase is likely to be the 1992 Earth Summit, which was being
+prepared by various state and non-state actors in the region and brought
+international attention to environmental topics in Brazil. One of the
+big announcements was the consolidation of the first transnational
+partnership for the Amazon, the G7 Pilot Programme, which brought a high
+number of financial resources to the region for public policy
+implementation \citep{capobianco2021}. During the Cardoso years
+(1994-2002), Amazonian speeches averaged at about 16\% without strong
+variation. There were no big international or domestic events that drove
+the topic up. At the level of policy, though, we saw the birth of the
+National System of Protected Areas in 2001, and of the Amazon Regional
+Protected Areas Program. While the former created the legal framework
+for different types of protected areas to be created, the latter
+established a transnational partnership to finance the implementation of
+protected areas in the Amazon \citep{andonova2014}.
 
-We observe an increase from 8.5% in 2004 to 22.8% in the year of the Copenhagen Summit, 2009.
-This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" [@franchini2019], when stakes about climate change were high.
-A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
-From 2010 to 2014, we identify a steady decrease from 18.2% to 8.2%, which is followed by a sharp increase in the year of the COP, reaching 19.2%.
-These are the years when Brazil entered a long period of political and economic instability that lingers until today.
-Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted and former environmental minister Marina Silva ended her alliance with the worker's party because of disagreements related to the priority of environmental policy.
+We observe an increase from 8.5\% in 2004 to 22.8\% in the year of the
+Copenhagen Summit, 2009. This coincides with the Presidency of Lula and
+the steepest decrease in deforestation rates in Brazilian history. Lula
+led the delegation to Copenhagen with a self-image of ``we do not
+promise, we deliver'' \citep{franchini2019}, when stakes about climate
+change were high. A somewhat different pattern can be identified in the
+lead up to the 2015 Paris COP, which was also building up to become a
+key-turn in climate politics after the failures of Copenhagen. From 2010
+to 2014, we identify a steady decrease from 18.2\% to 8.2\%, which is
+followed by a sharp increase in the year of the COP, reaching 19.2\%.
+These are the years when Brazil entered a long period of political and
+economic instability that lingers until today. Brazil went to the COP in
+Paris with deforestation numbers slightly higher than Copenhagen, and a
+perception that there was a turn towards less conservation after the
+2011 Forest Code was adopted and former environmental minister Marina
+Silva ended her alliance with the worker's party because of
+disagreements related to the priority of environmental policy.
 
-We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
-As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts, reaching unprecedented coverage.
-Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019.
-President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda.
-President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
+We subsequently observe a steady increase from 6.4\% in 2016 to almost
+24\% in the first year of Bolsonaro's presidency, 2019. As the narrative
+of the climate crisis picks up in the late 2010s, international media
+attention about the Amazon blasts, reaching unprecedented coverage.
+Pictures of the Amazon on fire and of the red sky afternoon in São Paulo
+circulated in social media and international media outlets in 2019.
+President Bolsonaro engages in an international debacle with President
+Macron and others, which drove the topic up strongly in the presidential
+agenda. President Bolsonaro retrieves Brazil's hosting status for COP25,
+and a strong process of dismantling of environmental governance starts
+taking place.
 
-We do find evidence that deforestation rates, economic situation, elections, and simply presidential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
-However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events.
-We are yet to inspect, though, whether specific problem constructions about the Amazon change over time.
+We do find evidence that deforestation rates, economic situation,
+elections, and simply presidential preferences affect the incidence of
+Amazon in speeches: the smoothed curve portrays lower proportions
+overall. However, international events and media coverage also correlate
+with local maxima of our curve, suggesting presidents do speak more
+about the Amazon in preparation or reaction to these events. We are yet
+to inspect, though, whether specific problem constructions about the
+Amazon change over time.
 
-## 4.2 Amazonian problem-construction in time
+\hypertarget{amazonian-problem-construction-in-time}{%
+\subsection{4.2 Amazonian problem-construction in
+time}\label{amazonian-problem-construction-in-time}}
 
-Figure 2 portrays plots with the proportions of different problem constructions over time.
-We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
-At the level of the Amazonian statement, though, presidents might mix two or more together.
-These are what we call mixed types, in opposition to pure types.
-There are 16 mix types in total, and figure 2 portrays the most frequent of them.
-Pure problem constructions dominate, with their joint average above 55%.
-Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.
+Figure 2 portrays plots with the proportions of different problem
+constructions over time. We conceptualize four problem constructions:
+sovereignty, economic integration, social development, and conservation.
+At the level of the Amazonian statement, though, presidents might mix
+two or more together. These are what we call mixed types, in opposition
+to pure types. There are 16 mix types in total, and figure 2 portrays
+the most frequent of them. Pure problem constructions dominate, with
+their joint average above 55\%. Among the four pure types as well as the
+mixed types, we observe a strong variation over time, suggesting the
+narratives do respond differently to factors that affect Amazonian
+statements discussed in the section above.
 
-```{r Figure 2: mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-prob_construction_year <- ama_mx %>%
-  count(year, mx_cat)%>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  ggplot(aes(x=year, y=perc, fill=mx_cat)) +
-  geom_bar(stat="identity", position="dodge") +
-  geom_smooth(color="black", size=.3, se= FALSE) +
-  scale_y_continuous(labels = percent_format(accuracy=1)) +
-  labs(x = "", y = "", title ="Share of different problem-constructions by year",
-       subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985", caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "none") +
-  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
-prob_construction_year
-```
+\includegraphics[width=0.9\linewidth]{rticle_files/figure-latex/Figure 2: mixed-types in time-1}
 
-The plots reveal several trends.
-We start by pure-types.
-Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s.
-In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005.
-@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
-As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+The plots reveal several trends. We start by pure-types. Pure economic
+integration statements, which were dominant, decreased in incidence as
+of the mid 1990s. In the late 1990s, pure conservation as well as pure
+social development increased; both surpassing the proportion of economic
+integration problem-construction in 2005. \citet{capobianco2021} argues
+that the unprecedented decrease in deforestation we observed from 2004
+to 2012 was a product of an increase in the perception of stronger
+federal policies and presence in the Amazon region, which in turn
+engendered a perception of higher risk of being caught and fined for
+deforestation. This correlates with our findings: a higher incidence of
+the Amazon as a topic overall can generate a perception of more
+attention from the top, and a shift from economic integration to
+conservation can generate a perception of higher change of being caught.
+As of the early 2010s, we observe a reversal of the trend with a twist:
+economic integration starts picking up again in detriment of
+conservation and social development problem constructions, but with
+sovereignty increasing steadily.
 
-Figure 3 (below) shows these shift and reversal more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
-Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation.
-The starkest decrease relates to social development construction between Temer's and Bolsonaro's administration.
+Figure 3 (below) shows these shift and reversal more clearly and
+highlights the decrease of economic integration and increase of social
+and conservation problem constructions preceding Lula's presidential
+mandate. Relatedly, figure 3 also shows that while the reversal precedes
+the mandate of President Bolsonaro, it was with him and his dismantling
+of social and environmental policies that sovereignty and economic
+integration appears the most, in detriment of social development and
+environmental conservation. The starkest decrease relates to social
+development construction between Temer's and Bolsonaro's administration.
 
-```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-pure_types_time <- ama_mx %>%
-  count(president, mx_cat2, mx_cat, year) %>%
-  group_by(president, year) %>%
-  mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat2 == "Pure-types") %>% 
-  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
-  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
-  scale_y_continuous(labels = percent_format(accuracy=1)) +
-  labs(x = "", y = "", title ="Share of each pure types by year",
-       subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
-pure_types_time
-```
+\includegraphics[width=0.9\linewidth]{rticle_files/figure-latex/Figure 3: pure types in time -1}
 
-We now move to mixed types, which average at around 21% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
-While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
-We focus our discussion on those with higher incidence.
-First, the most frequent mix overall is that of economic integration with conservation, which after reaching 25% of all problem-constructions in 1989, remained stable at 9% on average for the remainder of the period.
-President Lula was the most frequent user of this mix.
-Second, except for economic and social development appearing together in all statements made by Color in 1992, mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
-This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation.
-In all, we interpret the appearance of mixed types as more complex understandings of Amazonian problems.
-This follows a global agenda of understanding interconnections of social, environmental, and economic domains.
-As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals.
-Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation.
-This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 29.5% and 31.3% respectively.
-While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty.
-The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro.
+We now move to mixed types, which average at around 21\% for all
+presidents in our sample: overall, presidents prefer pure
+problem-constructions. While there is some variation in time for each
+single mixed type, some of them have low counts and interpretations are
+not adequate. We focus our discussion on those with higher incidence.
+First, the most frequent mix overall is that of economic integration
+with conservation, which after reaching 25\% of all
+problem-constructions in 1989, remained stable at 9\% on average for the
+remainder of the period. President Lula was the most frequent user of
+this mix. Second, except for economic and social development appearing
+together in all statements made by Color in 1992, mixed types using
+conservation were quite frequent in the lead up and aftermath of the
+1992 Earth Summit. This includes the mix type we label sustainable
+development, which constructs the Amazon as a problem of economic
+integration, social development, and environmental conservation. In all,
+we interpret the appearance of mixed types as more complex
+understandings of Amazonian problems. This follows a global agenda of
+understanding interconnections of social, environmental, and economic
+domains. As we show that Amazonian incidence in discourse does respond
+to global issues, this is not a surprise given agendas as Millennium
+Development Goals and the Sustainable Development Goals. Nevertheless,
+as in pure types, we also observe the comeback of sovereignty being used
+in mixed types in detriment of conservation. This becomes more apparent
+in a comparison between Lula and Bolsonaro, the two presidents that mix
+the most with proportions 11\% above presidential averages: 29.5\% and
+31.3\% respectively. While the former frequently mixed conservation with
+other problem constructions, the latter prefers mixing sovereignty. The
+combination of sovereignty with economic integration, which was also
+characteristic of the military dictatorship policies for the region,
+reaches its highest level with Bolsonaro.
 
-```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mean_mt <- filter(comp_types, mx_cat2 == "Mixed-types") %>% mean(perc) # 21%
-mixed_types_lula <- filter(comp_types, president == "Lula") # 29.5%
-mixed_types_bolsonaro <- filter(comp_types, president == "Bolsonaro")# 31.3%
-mixed_types_presid <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(president, mx_cat) %>%
-  group_by(president) %>%
-  mutate(perc = n / sum(n)) %>%
-  mutate(president = factor(president,
-                            levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                       "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat="identity", position="stack") +
-  geom_text(size = 3, position = position_stack(vjust=.5)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
-       subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
-       caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
-mixed_types_presid
-```
+\includegraphics[width=0.9\linewidth]{rticle_files/figure-latex/Figure 4: mixed-types by president-1}
 
-@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
-Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
-The costs for said economic and political benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
-Political stability, thus, can be seen as a product of the trade-off between both.
-Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy.
-With the strengthening of environmentalism in the 1990s, its most strong form being the policies adopted in the 2000s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
+\citet{pacheco2019} proposes that we see the Amazon frontier as a key
+analytic category to understand the Brazilian state and democracy.
+Specifically, the author states that the natural richness of the region
+has been instrumentally transformed in political support through
+resource exploration by different governments over the last centuries.
+The costs for said economic and political benefits are the livelihoods
+of indigenous and traditional populations and the ecosystems they reside
+in. Political stability, thus, can be seen as a product of the trade-off
+between both. Policies during the military dictatorship were strongly
+geared towards integrating the Amazon to the national territory and
+international economy. With the strengthening of environmentalism in the
+1990s, its most strong form being the policies adopted in the 2000s, we
+can interpret the fall of economic integration and the rise of social
+and conservation problem constructions as a new relationship between
+granting local livelihoods their rights and economic exploitation.
 
-While unprecedented, this new balance was not long-standing.
-Democratic decay is slow and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s (figure 3) .
-The hard increase in sovereignty comes in the 2010s.
-As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.
-At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
+While unprecedented, this new balance was not long-standing. Democratic
+decay is slow and the embryo of Bolsonaro's Amazonian discourse was
+breeding half a decade before he took office. We observe the decrease in
+conservation related statements in the early 2010s, and the soft
+increase of sovereignty in form of mixes in the mid 2000s (figure 3) .
+The hard increase in sovereignty comes in the 2010s. As we conceptualize
+and operationalize sovereignty as boundary-making vis-à-vis internal and
+external perceived threats to the Amazon, we interpret this increase as
+attacks to indigenous and traditional populations. At the policy side,
+the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a
+turning point: political opposition to conservation got particularly
+organized and managed to lobby the executive and conquer this policy
+wins, which were largely opposed by environmentalists.
 
-This is not to say that those who preceded President Bolsonaro are like him.
-They are not, and we have shown how he is different from others already.
-But the political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro's problem-construction is the strongest form of this shift.
-Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+This is not to say that those who preceded President Bolsonaro are like
+him. They are not, and we have shown how he is different from others
+already. But the political forces in Brazilian democracy that drive
+these changes in problem-construction were long in the making, as the
+earlier and softer shifts in discourse suggest. Bolsonaro's
+problem-construction is the strongest form of this shift. Now that we've
+inspected and developed pure and mixed types, we can check if these
+specific problem constructions vary depending on where the president is
+speaking.
 
-## 4.3 An Amazonian three-level game? Boasting policy outside, talking to people inside
+\hypertarget{an-amazonian-three-level-game-boasting-policy-outside-talking-to-people-inside}{%
+\subsection{4.3 An Amazonian three-level game? Boasting policy outside,
+talking to people
+inside}\label{an-amazonian-three-level-game-boasting-policy-outside-talking-to-people-inside}}
 
-Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations.
-For locations, the reference category is Amazonian states and, for problem construction, the reference category is environmental conservation.
-From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states.
-These findings indicate that constructing the amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states.
-Additionally, pure sovereignty constructions correlate in negative statistically significant ways to international settings in relation to environmental conservation constructions in Amazonian states.
-That is, constructing the Amazon as an issue of sovereignty
+Table 2, below, displays the multinational regression coefficients for
+the correlation between diverse problem constructions and locations. For
+locations, the reference category is Amazonian states and, for problem
+construction, the reference category is environmental conservation. From
+the outset, we notice that problem constructions of pure economic
+integration and pure social development correlate in negative
+statistically significant ways to both international settings and
+Brasilia in relation to environmental conservation problem constructions
+in Amazonian states. These findings indicate that constructing the
+amazon as an issue of environmental conservation is more likely to
+happen in international settings and in Brasilia than in Amazonian
+states. Additionally, pure sovereignty constructions correlate in
+negative statistically significant ways to international settings in
+relation to environmental conservation constructions in Amazonian
+states. That is, constructing the Amazon as an issue of sovereignty
 
-```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-amazon_def_year <- rbind(adr, amazon_def_year) # data on deforestation rates per year (PRODES)
-ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # average inflation rates per year Brazil
-# remove non-identified locations, mixed-other constructions and add election years
-ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
-  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty",
-                                            "Economic Conservation",
-                                            "Economic and Social Development", "Sovereign Conservation",
-                                            "Sustainable Development","Sovereign Integration",
-                                            "Social Conservation", "Other")),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
-# model
-model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE)
-# summary statistics
-model_summary <- summary(model)
-p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-# post estimation tests
-chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
-# library(lmtest)
-# lrtest(null_model, model) # We very much reject the hypothesis
-# (i.e. the more complex model is significantly better than the null model).
-# Finally, let's get a nice output:
-stargazer::stargazer(model, type="text",
-                     covariate.labels = c("Brasilia", "International", "Non-AM state",
-                                          "Election", "Deforestation", "Inflation"),
-                     column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-                                       "Sov-EI", "SD-Con", "Other"),
-                     dep.var.labels.include = FALSE)
-```
+\begin{verbatim}
+## # weights:  88 (70 variable)
+## initial  value 4416.923092 
+## iter  10 value 4017.522240
+## iter  20 value 3850.674388
+## iter  30 value 3699.438241
+## iter  40 value 3676.058797
+## iter  50 value 3674.521349
+## iter  60 value 3674.391978
+## final  value 3674.391362 
+## converged
+\end{verbatim}
 
-# 5 Conclusion
+\begin{verbatim}
+## 
+## ======================================================================================================================
+##                                                           Dependent variable:                                         
+##                   ----------------------------------------------------------------------------------------------------
+##                      EI         SD        Sov     EI-Con     EI-SD    Sov-Con  SD-EI-Con  Sov-EI    SD-Con     Other  
+##                      (1)       (2)        (3)       (4)       (5)       (6)       (7)       (8)       (9)      (10)   
+## ----------------------------------------------------------------------------------------------------------------------
+## Brasilia          -1.024*** -1.002***   -0.206    -0.341   -1.019***   0.420   -1.197*** -1.212*** -0.860*** -0.892***
+##                    (0.169)   (0.205)    (0.260)   (0.248)   (0.273)   (0.257)   (0.330)   (0.342)   (0.318)   (0.172) 
+##                                                                                                                       
+## International     -0.612*** -1.583***  -1.427***  -0.265   -0.980***  -0.451   -1.110*** -1.105***  -0.117   -0.774***
+##                    (0.192)   (0.303)    (0.431)   (0.292)   (0.336)   (0.367)   (0.407)   (0.395)   (0.328)   (0.202) 
+##                                                                                                                       
+## Non-AM state        0.023     -0.041     0.324     0.149     0.071   0.823***   -0.466    -0.136    -0.074    -0.159  
+##                    (0.197)   (0.230)    (0.302)   (0.296)   (0.292)   (0.306)   (0.373)   (0.366)   (0.354)   (0.206) 
+##                                                                                                                       
+## Election           -0.241     0.028    -0.684**   -0.059    -0.254    -0.573     0.064   -1.243**   -0.067   -0.451** 
+##                    (0.186)   (0.215)    (0.298)   (0.253)   (0.281)   (0.406)   (0.367)   (0.547)   (0.405)   (0.194) 
+##                                                                                                                       
+## Deforestation     0.063***   -0.031*     0.004     0.023    0.047**    0.005    -0.013    -0.001     0.011   0.059*** 
+##                    (0.013)   (0.016)    (0.019)   (0.017)   (0.019)   (0.027)   (0.026)   (0.028)   (0.026)   (0.013) 
+##                                                                                                                       
+## Inflation         -0.001*** -0.0005***  -0.0001  -0.001*** -0.0005**  0.0002   -0.001**   -0.0004   -0.001*  -0.0002* 
+##                   (0.0001)   (0.0002)  (0.0002)  (0.0002)  (0.0002)  (0.0002)  (0.0004)  (0.0004)  (0.0004)  (0.0001) 
+##                                                                                                                       
+## Constant            0.228    0.852***   -0.599*  -0.762**  -0.981*** -2.041*** -0.794**  -1.049*** -1.630***   0.164  
+##                    (0.210)   (0.252)    (0.333)   (0.312)   (0.335)   (0.332)   (0.371)   (0.347)   (0.319)   (0.217) 
+##                                                                                                                       
+## ----------------------------------------------------------------------------------------------------------------------
+## Akaike Inf. Crit. 7,488.783 7,488.783  7,488.783 7,488.783 7,488.783 7,488.783 7,488.783 7,488.783 7,488.783 7,488.783
+## ======================================================================================================================
+## Note:                                                                                      *p<0.1; **p<0.05; ***p<0.01
+\end{verbatim}
 
-# 6 References
+\hypertarget{conclusion}{%
+\section{5 Conclusion}\label{conclusion}}
+
+\input{"appendix.tex"}
+
+\end{document}

### 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
#new percentages and text in 4.2

--- 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
@@
 There are 16 mix types in total, and figure 2 portrays the most frequent of them.
-Pure problem constructions dominate, with their joint average above 55%.
+Pure problem constructions dominate, with their joint average at 55.8%.
 Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.
@@
   labs(x = "", y = "", title ="Share of different problem-constructions by year",
-       subtitle = "Sample composed by 2400 problem-constructions in 1885 Amazonian statements in presidential speeches since 1985", caption = "") +
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985", caption = "") +
   theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
 We start by pure-types.
-Pure economic integration statements, which were dominant, decreased in incidence as of the mid 1990s.
-In the late 1990s, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2005.
+Pure economic integration statements, which were dominant, decreased in incidence as of the late 1990s.
+Concurently, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2010.
 @capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught.
-As of the early 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught for illegal deforestation.
+As of the mid 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
 
@@
   scale_y_continuous(labels = percent_format(accuracy=1)) +
-  labs(x = "", y = "", title ="Share of each pure types by year",
+  labs(x = "", y = "", title ="Share of each pure type by year",
        subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
@@
 
-We now move to mixed types, which average at around 17% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
+```{r code for averages, eval=FALSE, include=FALSE}
+
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) #averages in relation to only mixed-types
+
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+
+```
+
+We now move to mixed types, which average at 17.7% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
 While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
 We focus our discussion on those with higher incidence.
-First, the most frequent mix overall is that of economic integration with conservation, which after reaching 25% of all problem-constructions in 1989, remained stable at 9% on average for the remainder of the period.
-President Lula was the most frequent user of this mix.
-Second, except for economic and social development appearing together in all statements made by Color in 1992, mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
+First, the most frequent mix overall is that of economic integration with environmental conservation, which averages at 29.15% in relation to mixed types only, and at 6.8% in relation to all Amazonian statements.
+Overall, we observe an increase along time, reaching its pike in the early 2010.
+President Dilma was the most frequent user of this mix.
+A close second is economic and social development being used together in about 22.9% of all mixed type statements and 5.4% of all statements.
+
+All other mixed types appeared less than 2.6% on average in relation to all statements.
+We can also interpret mixed types, though, by looking at what compose them the most along time.
+Mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
 This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation.
-In all, we interpret the appearance of mixed types as more complex understandings of Amazonian problems.
+We interpret the appearance of mixed types as more complex understandings of Amazonian problems.
 This follows a global agenda of understanding interconnections of social, environmental, and economic domains.
 As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals.
-Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types in detriment of conservation.
-This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 28.5% and 28.6% respectively.
-While the former frequently mixed conservation with other problem constructions, the latter prefers mixing sovereignty.
-The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro.
+Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types, mostly in detriment of conservation social development.
+This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 29.4% and 31.3% respectively.
+While the former frequently mixed conservation with other problem constructions, the latter prefers mixing with sovereignty.
+The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types.
 
@@
 Democratic decay is slow and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation related statements in the early 2010s, and the soft increase of sovereignty in form of mixes in the mid 2000s (figure 3) .
-The hard increase in sovereignty comes in the 2010s.
+We observe the decrease in conservation related statements in the mid 2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3) .
+The hard increase in sovereignty comes in the early 2010s.
 As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.

### 2022-04-08 Draft_April_2022/rticle/rticle.Rmd

--- 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? An analysis of
-  presidential speeches since 1985
+title: |
+  "How has the Brazilian Amazon been constructed as a problem? An analysis of presidential speeches since 1985"
+type: ARTICLE TEMPLATE
 author:
-- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
-date: "April 2022"
-output:
-  word_document:
-    reference_docx: template.docx
-  pdf_document: default
-  html_document:
-    df_print: paged
-bibliography: references.bib
-csl: chicago.csl
-abstract: This paper ...
+  - name: Livio Silva-Muller
+    affil: Graduate Institute of International and Development Studies
+    email: livio.silva@graduateinstitute.ch
+  - name: Henrique Sposito
+    affil: Graduate Institute of International and Development Studies
+    email: henrique.sposito@graduateinstitute.ch
+affiliation:
+  - num: Graduate Institute of International and Development Studies
+    address: |
+      Chemin Eugène-Rigot 2, 1202 Geneva
+bibliography: ""
+appendix: appendix.tex
+abstract: |
+  This paper...
+keywords: |
+  Sections; lists; figures; tables; mathematics; fonts; references; appendices
+header-includes: |
+  \usepackage{hyperref}
+  \usepackage[utf8]{inputenc}
+  \def\tightlist{}
+output: rticles::tf_article
 ---
 
-```{r setup, include=FALSE, warning=FALSE, message=FALSE}
+```{r, setup, include=FALSE}
+options(prompt = 'R> ', continue = '+ ')
 knitr::opts_chunk$set(include = FALSE)
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-```
 
-```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 sov <- ama %>% 
@@
                 replace(is.na(.), 0)
-```
 
-```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 ama_mx <-  ama %>%
@@
 ```
-
-\pagebreak
 
@@
 
-```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
+```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", paged.print=TRUE, include=TRUE}
+codebook <- tibble::tibble(Problem_Construction = c("National Sovereignty", "Economic Integration",
                                                     "Social Development", "Environmental Conservation"),
@@
 Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.", "This code constructs the Amazon region and/or forest as an issue of economic integration.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.",
+                                           "This code constructs the Amazon region and/or forest as an issue of economic integration.
 It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.",
+                                           "This code constructs the Amazon region and/or forest as an issue of social development.
 It advances the view that Amazon is full of citizens who should have their rights guaranteed.
@@
 This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
+Finally, this includes referrals to culture and the right to vote.",
+                                           "This code constructs the Amazon region and/or forest as an issue of conservation.
 This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
@@
 For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
-(Bolsonaro 25/10/2019)", "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+(Bolsonaro 25/10/2019)",
+                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
 We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in MAnaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)", "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+This highway will allow production in the Tax Free Zone in MAnaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
+                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
 We have invested over 14 billion reais in this program, in three and a half years.
@@
 One million kilometers of lines.
-(Lula 20/11/2009)", "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+(Lula 20/11/2009)",
+                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
 This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
@@
 
-```{r Figure 1: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+```{r Figure 1: Amazonian speeches by year, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 perc1 <- pop %>%
@@
 
-```{r Figure 2: mixed-types in time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 2: mixed-types in time, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 prob_construction_year <- ama_mx %>%
@@
 
-```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 3: pure types in time , echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 pure_types_time <- ama_mx %>%
@@
 
-```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 4: mixed-types by president, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+comp_types <- ama_mx %>%
+  count(president, mx_cat2)%>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n))
 mean_mt <- filter(comp_types, mx_cat2 == "Mixed-types") %>% mean(perc) # 21%
@@
 
-```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r multimonial model, echo=FALSE, message=FALSE, out.width="90%", warning=FALSE, paged.print=FALSE, include=TRUE}
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))

### 2022-04-09 Draft_April_2022/Full_draft_20220401.rmd
More updates to rmd draft file

--- 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
@@
 
-```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+```{r codebook, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
@@
 
-```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 3: pure types in time, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 pure_types_time <- ama_mx %>%
@@
 
-```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 4: mixed-types by president, out.width="90%", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+comp_types <- ama_mx %>%
+  count(president, mx_cat2)%>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n))
 mean_mt <- filter(comp_types, mx_cat2 == "Mixed-types") %>% mean(perc) # 21%
@@
 
-```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r multimonial model, echo=FALSE, out.width="90%", message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
@@
 # Finally, let's get a nice output:
-stargazer::stargazer(model, type="text",
+model_output <- stargazer::stargazer(model, type = "text",
                                      covariate.labels = c("Brasilia", "International", "Non-AM state",
@@
                                      dep.var.labels.include = FALSE)
+tibble::tibble("Dependent Variables" = c("Economic Integration vs. Environmental Conservation", 
+                                            "Social Development vs. Environmental Conservation", 
+                                            "Sovereignty vs. Environmental Conservation"),
+                  "Brasilia vs. Amazonian States" = c("-1.024***"," -1.002***", "-0.206"),
+                  "International vs. Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
+                  "Non-AM States vs. Amazonian States" = c("0.023", "-0.041", "0.324"),
+                  "Election Year" = c("-0.241", "0.028", "-0.684**"),
+                  "Annual Deforestation" = c("0.063***", "-0.031*", "0.004"),
+                  "Average Inflation" = c("-0.001***", "-0.001***", "-0.0001"))
 ```
-
 # 5 Conclusion

### 2022-04-09 Draft_April_2022/Full_draft_20220401.rmd

--- 2022-04-08 Draft_April_2022/Full_draft_20220401.rmd
@@
                                      dep.var.labels.include = FALSE)
+tibble::tibble("Dependent Variables" = c("Economic Integration vs. Environmental Conservation", 
+                                            "Social Development vs. Environmental Conservation", 
+                                            "Sovereignty vs. Environmental Conservation"),
+                  "Brasilia vs. Amazonian States" = c("-1.024***"," -1.002***", "-0.206"),
+                  "International vs. Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
+                  "Non-AM States vs. Amazonian States" = c("0.023", "-0.041", "0.324"),
+                  "Election Year" = c("-0.241", "0.028", "-0.684**"),
+                  "Annual Deforestation" = c("0.063***", "-0.031*", "0.004"),
+                  "Average Inflation" = c("-0.001***", "-0.001***", "-0.0001"))
 ```

### 2022-04-09 Draft_April_2022/Full_draft_20220401.rmd
Updates to 4.3. section

@@
 
+Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations.
+The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction.
+From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states.
+These findings indicate that constructing the Amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states.
+Additionally, pure sovereignty correlates in negative statistically significant ways to international settings in relation to conservation in Amazonian states.
+That is, constructing the Amazon as an issue of sovereignty is less likely in international settings than it is in Amazonian States.
+Interestingly, we see no statistically significant correlations between problem constructions in non-Amazonian states in relation to Amazonian states.
+This indicates that when presidents speak about the Amazon at the state level, constructions might be rather similar across different states.
+Furthermore, we also notice that some of the control variables correlate with some Amazonian problem constructions in interesting ways.
+For example, pure sovereignty constructions correlate negatively with election years in relation to conservation.
+That is, in election years conservation constructions are more likely to take place in comparison to sovereignty.
+As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation.
+This indicates that both deforestation increases and presidents are also more likely to construct the Amazon as an issue of economic integration.
+
 ```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
@@
 
+Putnam’s (1988) seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
+The author argues that both domestic and international levels need to be taken into consideration when analyzing how, often, domestic politics became entangled in international negotiations.
+The Amazon, as a region and a forest, has been the topic of international negotiations, national debates, and local policy implementation; though how the Amazon has been constructed as an issue differs on each of these three levels.
+While in Brasilia or internationally different presidents might construct the Amazon as an issue of conservation, the same presidents might construct the Amazon as an issue of economic integration or social development at the local level.
+This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” differ.
+The three level game entails that conservation might be a desirable construction when speaking internationally or in Brasilia about the Amazon, but not for local electorates.
+Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions about the issues the same policy addresses differ (see Alesina and Giuliano 2011).
+
+More broadly, these correlations between different locations and problem constructions illustrate how expectations vary for diverse audiences.
+Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what the president expects that they want to hear.
+This democratic game may indeed contribute to the advancement of ambiguous, inefficient, or contradictory public policies from the outside to the Amazon, and from the inside out the Amazon.
+Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 (cite).
+During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … Such contradictory policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
+
 # 5 Conclusion

### 2022-04-09 Draft_April_2022/Full_draft_20220401.rmd
Updated some more references and stuff

@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations ^[For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
+(2021).
+For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
@@
 ```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble('Problem Construction' = c("National Sovereignty", "Economic Integration",
+codebook <- tibble::tibble(Problem_Construction = c("National Sovereignty", "Economic Integration",
                                                     "Social Development", "Environmental Conservation"),
@@
 It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
-                           Example = c("We can now walk the world and when we debate about the Amazon, we do not need to wait for questions, we are the ones who are going to say what we are doing in the Amazon.
-We do not need to keep on saying ‘the Amazon is ours’ just for saying it, people often say this without much conviction either.
-If the Amazon has been ours since Cabral (European discoverer of Brazil) stepped here, why do we now have to worry about the Amazon?
-(Lula 2008)", "", "", ""))
-knitr::kable(codebook, "simple")
+                           Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
+I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019)",
+                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
+This highway will allow production in the Tax Free Zone in MAnaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
+                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+We have invested over 14 billion reais in this program, in three and a half years.
+Do you know how many electrical lines we have already built?
+One million kilometers of lines.
+(Lula 20/11/2009)",
+                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
+Mesquita (Sarney 20/07/1989)"))
+knitr::kable(codebook, format = "simple", caption = "Table 1 - Amazonian Problem-Construction Codebook")
 ```
@@
 The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction.
+Although all the other mixed types problem-constructions were included in the model, we choose to display and focus the analysis on the pure types.
 From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states.
@@
 # model
-model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE)
+model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE, trace = FALSE)
 # summary statistics
@@
 # Finally, let's get a nice output:
-model_output <- stargazer::stargazer(model, type = "text",
-                                     covariate.labels = c("Brasilia", "International", "Non-AM state",
-                                                          "Election", "Deforestation", "Inflation"),
-                                     column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-                                                       "Sov-EI", "SD-Con", "Other"),
-                                     dep.var.labels.include = FALSE)
-tibble::tibble("Dependent Variables" = c("Economic Integration vs. Environmental Conservation", 
+# model_output <- stargazer::stargazer(model, type = "text",
+#                                      covariate.labels = c("Brasilia", "International", "Non-AM state",
+#                                                           "Election", "Deforestation", "Inflation"),
+#                                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
+#                                                        "Sov-EI", "SD-Con", "Other"),
+#                                      dep.var.labels.include = FALSE)
+# too much information... Let's just focus on what we want here...
+md <- data.frame("Dependent Variables" = c("Economic Integration vs. Environmental Conservation",
                                            "Social Development vs. Environmental Conservation",
                                            "Sovereignty vs. Environmental Conservation"),
-                  "Brasilia vs. Amazonian States" = c("-1.024***"," -1.002***", "-0.206"),
+                 "Brasilia vs. Amazonian States" = c("-1.024***","-1.002***", "-0.206"),
                  "International vs. Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
@@
                  "Average Inflation" = c("-0.001***", "-0.001***", "-0.0001"))
+kableExtra::kable(t(md), format = "simple", caption = "Table 2 - Amazon Problem-Construction by Location")
 ```
 
-Putnam’s (1988) seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
+@putnam1988 seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
 The author argues that both domestic and international levels need to be taken into consideration when analyzing how, often, domestic politics became entangled in international negotiations.
@@
 The three level game entails that conservation might be a desirable construction when speaking internationally or in Brasilia about the Amazon, but not for local electorates.
-Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions about the issues the same policy addresses differ (see Alesina and Giuliano 2011).
+Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions about the issues the same policy addresses differ [@alesina2009; @lopez2020].
 
 More broadly, these correlations between different locations and problem constructions illustrate how expectations vary for diverse audiences.
-Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what the president expects that they want to hear.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what the president expects that they want to hear.
 This democratic game may indeed contribute to the advancement of ambiguous, inefficient, or contradictory public policies from the outside to the Amazon, and from the inside out the Amazon.

### 2022-04-10 Draft_April_2022/Full_draft_20220401.rmd
A few more minor updates

@@
 This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” differ.
-The three level game entails that conservation might be a desirable construction when speaking internationally or in Brasilia about the Amazon, but not for local electorates.
-Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions about the issues the same policy addresses differ [@alesina2009; @lopez2020].
+The three level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not for local electorates.
+Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions and expectations about the issues the same policy addresses might differ [@alesina2009; @lopez2020].
 
-More broadly, these correlations between different locations and problem constructions illustrate how expectations vary for diverse audiences.
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what the president expects that they want to hear.
-This democratic game may indeed contribute to the advancement of ambiguous, inefficient, or contradictory public policies from the outside to the Amazon, and from the inside out the Amazon.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
+This democratic game contribute to the advancement of ambiguous public policies thought from the outside to the Amazon or contradictory policies from Amazon to the outside.
 Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 (cite).
-During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … Such contradictory policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
+During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
 

### 2022-04-10 Draft_April_2022/Full_draft_20220401.rmd
#few changes to text #one new plot for exploration #comments on text for 4.3 in the google docs

@@
 output:
-  word_document:
-    reference_docx: template.docx
   pdf_document: default
@@
     df_print: paged
+  word_document:
+    reference_docx: template.docx
 bibliography: references.bib
@@
 [^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
-Matching deforestation with speech dates is a complicated endeavor.
+Nevertheless, matching deforestation with speech dates is a complicated endeavor.
 INPE published consolidated deforestation data with almost two years of delay until 2005 [@capobianco2021, pp.
@@
 Preliminary data was published earlier, but with lower degrees of confidence in the findings.
-For the subsequent years, the consolidated figures for a given year tend to come out in August of the subsequent year.
+For the subsequent years, the consolidated figures for a given year came out in August of the subsequent year.
 However, it also seems to be the case that the executive government have access to the data before everyone else.
-In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), circulates within the same year.
-The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue was written with comments by an INPE scientist [@simons1988].
+In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), or even other sources, circulated within the year the data covered.
+The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue with deforestation rates for 1988 was written with comments by an INPE scientist [@simons1988].
 Hence, we believe the most appropriate way of matching is without any lags on deforestation.
@@
 
-Table 2, below, displays the multinational regression coefficients for the correlation between diverse problem constructions and locations.
+```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
+pure_types_time_location <- ama_mx %>%
+  count(president, mx_cat2, mx_cat, year, location_cat) %>%
+  group_by(president, year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  filter(location_cat != "Non Identified") %>%
+  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
+  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
+  scale_y_continuous(labels = percent_format(accuracy=1)) +
+  labs(x = "", y = "", title ="Share of each pure type in time by location",
+       subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")+
+  facet_wrap(~location_cat, scales= "free_y", ncol=2)
+
+pure_types_time_location
+
+```
+
+Table 2, below, displays the multinomial regression coefficients for the correlation between problem constructions and locations.
 The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction.

### 2022-04-10 Draft_April_2022/Full_draft_20220401.tex
#few changes to text #one new plot for exploration #comments on text for 4.3 in the google docs

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 analysis of presidential speeches since 1985}
-\author{Livio Silva-Muller\footnote{Phd Candidate, The Graduate
-  Institute Geneva,
+\author{Livio Silva-Muller\footnote{Phd Candidate, The Geneva Graduate
+  Institute ,
   \href{mailto:livio.silva@graduateinstitute.ch}{\nolinkurl{livio.silva@graduateinstitute.ch}}} \and Henrique
-Sposito\footnote{Phd Candidate, The Graduate Institute Geneva,
+Sposito\footnote{Phd Candidate, The Geneva Graduate Institute Geneva,
   \href{mailto:henrique.sposito@graduateinstitute.ch}{\nolinkurl{henrique.sposito@graduateinstitute.ch}}}}
@@
 The Amazon needs to be protected from foreign interests. The Amazon
-needs to be exploited for its natural resources. The Amazon should be
+needs to be exploited for its natural resources. The Amazon needs to be
 preserved as a standing ecosystem. Historically, different Brazilian
@@
 be solved, or in other words, it represents the region, the forest, or
-the peoples as a particular problem. In the three examples above, the
+its peoples as a particular problem. In the three examples above, the
 Amazon is represented as an issue of national sovereignty, economic
@@
 see the Amazon as an instance of only one specific problem. Albeit the
-current academic calls to understand the environment as a
-social-cultural construction and to identify the effect of culture for
-environmental outcomes (Polain de Waroux et al. 2021), we lack empirical
-accounts of how the Brazilian Amazon has been constructed as a problem
-over time and across locations, and how this varies.
+current calls to understand the environment as a social-cultural
+construction and to identify the effect of culture on environmental
+outcomes (Waroux et al. 2021), we lack empirical accounts of how the
+Brazilian Amazon has been constructed as a problem over time, by
+geographical location, and between and within governments
 
@@
 (1963) concept of chosen problems in policy making, we propose a
-framework to identify how problem-construction varies over time, by
-location, and between and within governments. Although
+framework to identify how problem-construction. Although
 problem-construction takes place in a series of instances (e.g.~policy
@@
 policy perception is key for policy adoption and implementation (Alesina
-and Giuliano 2009). The literature has shown that deforestation rates in
-Brazil are more responsive to the government's environmental policy than
-exogenous factors as market fluctuations (Assunção, Gandour, and Rocha
-2015; Capobianco 2019, 2021). Thus, understanding how policy comes about
-discursively is important. Second, environmental discourse at the top
-can help expand or restrict what types of behaviors are accepted in the
-ground. When Brazilian presidents speak about the Amazon it not only
-makes headlines, nationally and internationally, but also incites
-responses, shapes expectations, and feeds into the behavior of many
-actors involved with the Amazon, from investors to agribusiness to local
-farmer(Brice and Smith 2021; Harris 2021; Miranda 2021). This is
-especially pertinent for deforestation as previous research found that
-policy expectations, generated from material and discursive governmental
-practices, are a crucial factor in decisions to deforest at the ground
-(Capobianco 2019; Campbell 2015). Unpacking discourse at the top might
-help us raise hypotheses about environmental outcomes that are
-culturally situated. Finally, as our theoretical framework suggests,
-problem-construction varies by geographic location. Presidential
-discourses take place in a series of sites with diverse audiences: from
-launching a new bridge in a small municipality in the middle of the
-Amazon, to a keynote speech in a business association in São Paulo, to
-the UN general assembly in New York city. Working with presidential
-discourses allows us to identify this variation in meaningful ways and
-better how the Amazon is socially constructed.
+and Giuliano 2009; López et al. 2020). The literature has shown that
+deforestation rates in Brazil are more responsive to the government's
+environmental policy than exogenous factors as market fluctuations
+(Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021). Thus,
+understanding how policy comes about discursively is important. Second,
+environmental discourse at the top can help expand or restrict what
+types of behaviors are accepted in the ground. When Brazilian presidents
+speak about the Amazon it not only makes headlines, nationally and
+internationally(Brice and Smith 2021; Harris 2021; Miranda 2021), but
+also incites responses, shapes expectations, and feeds into the behavior
+of many actors involved in the Amazon, from investors to agribusiness to
+local farmer. This is especially pertinent for deforestation as previous
+research found that policy expectations, generated from material and
+discursive governmental practices, are a crucial factor in decisions to
+deforest at the ground (Capobianco 2019; Campbell 2015). Unpacking
+discourse at the top might help us raise hypotheses about environmental
+outcomes that are culturally situated. Finally, as our theoretical
+framework suggests, problem-construction varies by geographic location.
+Presidential discourses take place in a series of sites with diverse
+audiences: from launching a new bridge in a small municipality in the
+middle of the Amazon, to a keynote speech in a business association in
+São Paulo, to the UN general assembly in New York. Working with
+presidential discourses allows us to identify this variation in
+meaningful ways and better how the Amazon is socially constructed.
 
@@
 
-(Summarize findings, conceptual contribution, and empirical
-contribution). Conceptually, our approach is underpinned by a
-constructivist view of policy making, which allocates agency to
-different actors in building policy discursively. Empirically, we
-provide the first comprehensive overview of how the Brazilian Amazon has
-been constructed as a problem in presidential speeches.
+Our findings are threefold. First, endogenous events as the death of
+Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the
+2015 Paris Summit, and the 2021 London Summit drive generally the
+interest in the Amazon. That seems to be the case even after controlling
+share of annual speeches mentioning the Amazon for deforestation,
+inflation, and speaker. Second, there was a sharp decrease in economic
+related problem-constructions from the late 1990 to 2010, matched by an
+increase in speeches that construct the Amazon as a problem of social
+development and environmental conservation. This trend is reversed in
+the late 2010s, with the twist of sovereignty making a strong comeback.
+Finally, using a multinominal model, we find that the farthest away the
+speaker is from the Amazon, be it within the country in non-Amazonian
+States or outside Brazil, the more likely the speaker is to construct
+the Amazon as a problem of environmental conservation than economic
+integration or social development.
 
 This article proceeds as follows: first, we review Amazonian literature
-to identify the main ways in which it was constructed as a problem. We
-then propose a theoretical framework to understand problem-construction.
-In the methodology section, we operationalize our framework and the
-Amazonian problem-constructions. Section four portrays our main results
-over time and by speaker. Finally, we conclude by discussing our
+to identify the main policy-cycles and their underlying problem
+construction. We then propose a theoretical framework to understand
+problem-construction and discourse. In the methodology section, we
+operationalize our framework and present the codebook. Section four
+portrays our main results. Finally, we conclude by discussing our
 findings and proposing future research.
@@
 populations and gold hoarders. The dream of fortunes to be found in the
-Eldorado composed the imaginaries of \emph{bandeirantes}\footnote{B\emph{andeirantes}
+Eldorado composed the imaginaries of \emph{bandeirantes}\footnote{\emph{Bandeirantes}
   means ``flag-carriers'', the word is used to designate Portuguese
@@
 over the Amazon from the communist threat during the Cold War(Garfield
-2013). As we move from a world where non-state actors gain importance in
+2013).
+
+As we move from a world where non-state actors gain importance in
 environmental governance and international politics generally
@@
 2019). Threads to national sovereignty, consequently, can be interpreted
-as coming from a different set of actors than before. False claims about
-Brazilian policies in international and domestic fora, for instance, are
-often tied to strategies of `internationalizing' the Amazon. Relatedly,
-mentions of Amazonian myths which have been debunked as the `Earth of
-the Lungs', are also tied to internationalizing strategies.
+as coming from a different set of actors than before. Allegedly false
+claims about the Brazilian Amazon in international and domestic fora,
+for instance, are often tied to strategies of `internationalizing' the
+Amazon. This might come both from foreign actors as well as domestic
+non-state actors. Relatedly, mentions of Amazonian myths which have been
+debunked as the `Earth of the Lungs', are also tied to
+internationalizing strategies.
 
@@
 
-The dictatorships of Vargas (1937-46) and the military (1964-89) took
-over the task of modernizing the Amazon. In 1966, the Brazilian Military
-dictatorship launched Operation Amazon, a policy to modernize the region
-based on a set of assumptions (Acker 2014). First, nature should be
-conquered by men. Second, exploiting natural resources would render the
-Amazon region a global powerhouse. Third, such a project would integrate
-the region with the rest of the country. Concretely, this meant a series
-of infrastructure projects, such as roads and dams, incentives for
-settlers to develop ranches and expand the agricultural frontier, as
-well as establishing tax free zones to attract industry. The capital to
-conduct such changes, paradoxically, came from national and
-international sources (Acker 2014), leading to a series of national and
-international enterprises settling in the Amazon region. Capobianco
+The Vargas dictatorship (1937-46) and the military dictatorship
+(1964-89) took over the task of modernizing the Amazon. In 1966, the
+Brazilian Military launched Operation Amazon, a policy to modernize the
+region based on a set of assumptions (Acker 2014). First, nature should
+be conquered by men. Second, exploiting natural resources would render
+the Amazon region a global powerhouse. Third, such a project would
+integrate the region with the rest of the country. Concretely, this
+meant a series of infrastructure projects, such as roads and dams,
+incentives for settlers to develop ranches and expand the agricultural
+frontier, as well as establishing tax free zones to attract industry.
+The capital to conduct such changes, paradoxically, came from national
+and international sources (Acker 2014), leading to a series of national
+and international enterprises settling in the Amazon region. Capobianco
 (2019) describes the period from the 1950-80 in a similar fashion,
@@
 
-The rapid economic changes in the region in the 1960s, 70s, and 80s were
-matched with the birth of environmental institutions such as the New
-Forest Code (1964), the Secretary of Environment (1973), and the
+The rapid economic changes in the region in the 1960s, 1970s, and 1980s
+were matched with the birth of environmental institutions such as the
+New Forest Code (1964), the Secretary of Environment (1973), and the
 National Environment Law (1980) (Drummond and Barros-Platiau 2006). A
 common explanation for these institutions in the Amazonian literature is
-the impression of lack of control after years of economic integration.
-(Acker 2021; Capobianco 2021; Hecht and Cockburn 1990). As
-deforestation, fires, and violence rose in the region, catching
-international attention, the military government deemed as necessary the
-establishment of an environmental bureaucracy. This process accelerated
-in the late 1980s, with the birth of modern environmentalism epitomized
-in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021;
-Capobianco, 2019; Hochstetler and Keck, 2007). Hochstetler and Keck
-(2007) argue that during preparations for the summit, a new form of
-Brazilian environmentalism emerged: socio-environmentalism. They define
-it as an emphasis on local livelihoods of people while protecting
-nature. Capobianco (2019) argues in a similar line, establishing
+the impression of lack of control after years of centalized economic
+integration policies (Acker 2021; Capobianco 2021; Hecht and Cockburn
+1990). As deforestation, fires, and violence rose in the region,
+catching international attention, the military government deemed as
+necessary the establishment of an environmental bureaucracy. This
+process accelerated in the late 1980s, with the birth of modern
+environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro
+(Hochstetler 2021; Capobianco 2021). Hochstetler and Keck (2007) argue
+that during preparations for the summit, a new form of Brazilian
+environmentalism emerged: socio-environmentalism. They define it as an
+emphasis on local livelihoods of people while protecting nature.
+Capobianco (2019) argues in a similar line, establishing
 socio-environmentalism as the main government response in the 1990s and
@@
 environmental outcome measurement), more investment in the valuation of
-standing eco-systems through incentive schemes, and more policies
+standing ecosystems through incentive schemes, and more policies
 facilitating indigenous environmental practices.
@@
 contain elements to ensure sovereignty, integrate the region to the
-country's economy, and preserve the forest. Framing the policy as an
+country's economy, and preserve the forest. Framing this policy as an
 issue of economic integration, then, can be seen as a choice.
@@
 differently. For historical inquiry, it is important to periodize policy
-cycles comprehensively and coherently. We largely agree with what the
-literature assigns to previous governments. However, the possibility of
-varied portrayals of the same policy opens possibilities of
-understanding agenda-setting and policy-adoption in less linear ways.
+cycles comprehensively. We largely agree with what the literature
+assigns to previous governments. However, the possibility of varied
+portrayals of the same policy opens up an understanding agenda-setting
+and policy-adoption that is less linear.
 
@@
 speaker. While governmental discourses in Brazil have been studied for
-topic such as inflation or race relations , we only find one systematic
+topic such as inflation or race relations \footnote{For an overview on
+  how inflation and political discourse in Brazil see Porto (2007),
+  Malheiros-Poulet (2012), and Fonseca et al.~(2021). For a few studies
+  on racist and anti-racist discourses in Brazil see Htun (2004), Silva
+  and Larkins (2019) and Dijk (2020).}, we only find one systematic
 analysis of Amazonian discourse. Barros (2020) investigates Amazonian
 discourse in the Brazilian Congress with the objective of identifying
-the arguments put forth by congressmen. The main finding is that in
-congress the economic value of the Amazon for the cattle industry is the
-most salient narrative, leading the author to conclude there is a
-mismatch between the international debate (which focuses on
-preservation) and the national debate (which focuses on economic
-development).
-
-While we find no major studies systematically looking into Amazonian
-related themes in Brazilian presidential speeches, we find, for example,
-several analyzes of environmental discourse in American presidential
-speeches. Calderwood (2019) examines 2919 mentions of climate change in
-American official presidential speeches since 1989. Among various
-findings, one that stands out is that American presidents frequently
-side-step the environmental aspects of climate change (ibid). He also
-identifies a shift from economic to security framing of climate issues,
-side-lining its environmental aspects. In another article, Calderwood
-(2020) tests the effect of geographic location and type of communication
-regarding climate change. Building prominently on Putnam (1988) but also
-others, he hypothesizes that presidents are more likely to mention
-climate change in foreign locations, and that location influences the
-specific discursive approach and tone they adopt. He finds evidence in
-support of his hypothesis, suggesting American presidential discourse at
-the top on climate change does change based on location. Another example
-is Bevitori (2015), who investigates how the `environment' has been
-constructed in American presidential discourse since 1960 using a more
-automated approach. The author finds that mentions of the environment
-are typically co-selected with the pronoun `our', as well as with
-`economy', `clean', and `preserve'.
+the arguments put forth by congressmen. The main finding is that the
+economic value of the Amazon for the cattle industry is the most salient
+narrative, leading the author to conclude there is a mismatch between
+the international debate (which focuses on preservation) and the
+national debate (which focuses on economic development).
+
+We also find several analyzes of environmental discourse in American
+presidential speeches. Calderwood (2019) examines 2919 mentions of
+climate change in American official presidential speeches since 1989.
+Among various findings, one that stands out is that American presidents
+frequently side-step the environmental aspects of climate change (ibid).
+He also identifies a shift from economic to security framing of climate
+issues, side-lining its environmental aspects. In another article,
+Calderwood (2020) tests the effect of geographic location and type of
+communication regarding climate change. Building prominently on Putnam
+(1988) but also others, he hypothesizes that presidents are more likely
+to mention climate change in foreign locations, and that location
+influences the specific discursive approach and tone they adopt. He
+finds evidence in support of his hypothesis, suggesting American
+presidential discourse at the top on climate change does change based on
+location. Another example is Bevitori (2015), who investigates how the
+`environment' has been constructed in American presidential discourse
+since 1960 using a more automated approach. The author finds that
+mentions of the environment are typically co-selected with the pronoun
+`our', as well as with `economy', `clean', and `preserve'.
 
@@
 changing level of government control in society, or top policymakers
-shifting interests(Hirschman 1963, 388--91). Choosing a problem, though,
-entails a decision on how to represent it(Bacchi 2009). As Bacchi puts
-``policy has a cultural dimension. It takes shape within specific
-historical and national or international contexts'' (2009, 10). The
-existence or proposal of a policy generally implies that there is a
-(public) problem that needs (governmental) action to be fixed (ibid).
-The alleged problem is not always explicitly stated in policy. Hirschman
+shifting interests (Hirschman 1963, 388--91). Choosing a problem,
+though, entails a decision on how to represent it (Bacchi 2009). As
+Bacchi puts ``policy has a cultural dimension. It takes shape within
+specific historical and national or international contexts'' (2009, 10).
+The existence or proposal of a policy generally implies that there is a
+(public) problem that needs (governmental) action to be fixed. The
+alleged problem is not always explicitly stated in policy. Hirschman
 exemplifies chosen problems with the case of the construction of
@@
 Problem-construction takes place in different sites: national media,
-legislative bodies, international fora, among others. What eventually
-becomes policy is a product of a multi-faceted process in all these
-different sites. One avenue through which governments can emphasize the
-representations of a problem is discourse. We assume that
+legislative bodies, international fora, policy committees, among others.
+What eventually becomes policy is a product of a multi-faceted process
+in all these different sites. One avenue through which governments can
+emphasize the representations of a problem is discourse. We assume that
 problem-construction at the level of discourse is varied. They are not
@@
 they just count mentions to climate change (Calderwood 2019, 2020; Brown
-and Sovacool 2017) or environment (Bevitori, 2015) without embedding
-them in the histories of the term in the country.
+and Sovacool 2017) or environment (Bevitori 2015) without embedding them
+in the histories of the issue in the country.
 
@@
 
+To operationalize our theoretical framework, we adopt a mixed-methods
+approach using manual coding and supervised machine learning. We explain
+our research design and each step of the procedure in this section.
+
 \hypertarget{data-and-modeling-operationalizing-amazonian-problem-construction}{%
@@
 
+We build upon the dataset provided by (Cezar 2020) which contains all
+official speeches by Brazilian Presidents from 1985 to 2019 scrapped
+from the archives of the Brazilian Presidential Library. We update the
+dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches for all the presidents of
+Brazil since 1985. We then identify all speeches about the Amazon as a
+region, peoples, or forest out of the 6130 speeches. We do so by
+detecting all speeches in which the stem ``amazon'' appears. In
+Portuguese, the stem captures terms such as ``Amazonia'', ``Amazonica'',
+``Amazonidas'', ``Amazonense(s)'', ``Amazonas'', among others. We find
+that 946 speeches are, at least partially, about the Amazon from the
+6130.
+
+Using the poldis R package, we proceed to extract two sentences before
+and two sentences after the sentence in which the stem ``amazon''
+appears. We opt for picking two sentences before and two sentences
+after, rather than words, because sentences usually contain a cohesive
+idea. By doing so we create our unit of analysis: an Amazonian
+statement. We use Amazon statements as our unit of analysis for two main
+reasons. First, working at the level of statements allows us to identify
+only passages that are meaningful for our specific purpose. Second, it
+increases the number of our observations and its variety meaningfully,
+allowing for more specificity in our analysis. This process yields 2014
+unique Amazonian statements across the 946 speeches about the Amazon
+identified. When an Amazonian statement contains two or more matches of
+the stem ``amazon'', we get two sentences before the first match and two
+sentences after the last match. On average, an Amazonian statement
+contains 123 words.
+
+After revising the literature (section 2), we selected a random sample
+of these Amazonian statements to develop a codebook for identifying how
+the Amazon is constructed as a problem in presidential discourse (see
+Table 1 below). We understand Amazonian problem-constructions as
+Weberian ideal types, that is, an unified analytical construct
+portraying a `pure' version of a phenomenon. This serves the purpose of
+allocating empirical observations within a range of possibilities. We
+identify the three problem-constructions derived from the literature
+(national sovereignty, economic integration, and environmental
+conservation) in the sample of Amazonian statements. However, in
+addition to them, we inductively identified a fourth problem
+construction that the literature does not explicitly cover: social
+development. Presidents sometimes opt to emphasize the lack of
+hospitals, sanitation, and schools in relation to peoples'
+constitutional rights when speaking about the Amazon. We saw this code
+category as substantially different from the other three, hence, we
+created the code category `social development'. In their
+conceptualization, each code is mutually exclusive in its
+conceptualization, meaning that they cover different forms of
+constructing the Amazon as a problem, though each Amazonian statement
+might be assigned to one or more codes. A statement can, for example,
+construct the Amazon as a problem of sovereignty and a problem of
+economic integration or a problem of social development and
+conservation. Amazonian statements, thus, can be either coded as a
+pure-types or mixed-types.
+
+\begin{longtable}[]{@{}lll@{}}
+\caption{Table 1 - Amazonian Problem-Construction
+Codebook}\tabularnewline
+\toprule
+Problem\_Construction & Description & Example \\
+\midrule
+\endfirsthead
+\toprule
+Problem\_Construction & Description & Example \\
+\midrule
+\endhead
+National Sovereignty & This code constructs the Amazon region and/or
+forest as an issue of national sovereignty. We understand claims of
+sovereignty as a particular problem-construction that touches on
+imaginaries of external threats to territory. Relatedly, we also
+understand sovereignty as raising concerns about wrong perspectives and
+criticism from foreign and non-state actors about
+governments\textless U+2019\textgreater{} actions related to the
+Brazilian Amazon. In all, it advances the view that the Amazon is
+Brazilian, foreign, and non-state presence in the region needs to be
+monitored closely. & Congressman, the fundamental link for Brazil to
+really head in the direction to prosperity. I would like first, Hu
+Chunhua, to thank you for the words of your ambassador to Brazil
+recognizing our sovereignty over the Amazonian region during that recent
+episode in the G7 meeting. I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words
+about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019) \\
+Economic Integration & This code constructs the Amazon region and/or
+forest as an issue of economic integration. It advances the view that
+the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives,
+creating a diverse set of infrastructure (roads, dams, internet, radio,
+energy), fostering differing industries (tourism, mining, cattle,
+agriculture and so on) through tax-free zones, as well as facilitating
+the exploitation of natural resources for developmental purposes. & If
+you allow me, in the Amazon - which for a long time stayed asleep due to
+the lack of coordinated actions - have already taken a few structuring
+actions. We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai,
+until up there, the red line {[}in a map{]} that goes all the way up in
+the direction of Venezuela, that is the so-called BR-174 highway. This
+highway will allow production in the Tax Free Zone in MAnaus to be
+competitive, not within, but outside, that is the vocation of the the
+Tax Free Zone to export; and we can even do it through the Caribbean
+(Cardoso 02/07/1997) \\
+Social Development & This code constructs the Amazon region and/or
+forest as an issue of social development. It advances the view that
+Amazon is full of citizens who should have their rights guaranteed. This
+refers to the construction of schools and universities (right to
+education), of hospitals (right to health), and of housing (right to
+house). This also includes guarantees of a dignified life with decent
+employment, access to water and sanitation, as well as access to
+electricity, internet, radio, and light. Finally, this includes
+referrals to culture and the right to vote. & The state does not work
+for profits, the state needs to guarantee dignity, we find that a
+citizen who lives in the riverside of the Amazon river, 600 kilometers
+from Manaus, has the right to have the electricity in their house, to
+owe a fridge, to owe a television where to watch the soap operas. We
+have invested over 14 billion reais in this program, in three and a half
+years. Do you know how many electrical lines we have already built? One
+million kilometers of lines. (Lula 20/11/2009) \\
+Environmental Conservation & This code constructs the Amazon region
+and/or forest as an issue of conservation. This problem-construction
+focuses on the value of a standing forest and of the preserved ecosystem
+in the region. The conservationist narrative advances the view that
+Amazon should be preserved, deforestation should be halted, and the
+practices of indigenous and traditional populations should be maintained
+and fostered. It advances the view that the emission of greenhouse
+gasses should be halted, that renewable energy should be supported, and
+that protected areas should be created. & I have put in place emergency
+measures, I have suspended the exports of wood logs, I have suspended
+the fiscal incentives and credits to projects that could damage the
+environment in the amazon and I have made a license mandatory to gold
+mining that prohibits utilizing mercury in the process. This began the
+restructuring of the governmental system of control and preservation of
+the environment, I have created the Brazilian Institute for the
+Environment and Natural Resources {[}IBAMA{]}, which will be headed by
+Dr.~Mesquita (Sarney 20/07/1989) \\
+\bottomrule
+\end{longtable}
+
+With the codebook in hands, each one of the authors, separately,
+hand-coded the same set of 1007 randomly selected Amazonian statements.
+This amount refers to 50\% of all the Amazon Statements identified.
+Inter-coder agreement for each of the four main categories was 85\%, on
+average. For each non-matching coded observation, the co-authors
+discussed and sorted their disagreements. Statements that mention the
+stem ``amazon'', but are not about the Brazilian Amazon, for example,
+might a greeting to the Governor of the Amazonas, were coded as false
+positives. The manually coded data is then randomly divided into a
+training set, containing 80\% of the hand-coded observations (806
+observations), and a validation set, containing the remaining 20\% of
+the hand-coded data (201 observations). The training set is used to
+train the supervised machine-learning model that automatically
+classifies observations while the validation set is used to make sure
+the model fit is appropriate.
+
+We chose to employ a support-vector machine (SVM) algorithm to label
+texts, that is, a non-probabilistic linear classifier that classifies
+documents by assigning points in mapped space to maximize the gap
+between binary categories (Meyer et al. 2021; Noble 2006)\footnote{For
+  more information on this please see the extended methodology. The
+  document includes a detailed discussion of how the SVM algorithm was
+  chosen over other algorithms based on evaluation of performance of
+  trained models for labeling the validation set. The extended
+  methodology also includes a more detailed codebook table with further
+  coding guidelines.}. After the SVM model is trained and tuned, and the
+model shows to appropriately fit the validation set, we use the model to
+automatically code the remaining 1007 Amazonian statements. The model
+was also trained to identify false positive observations, which we chose
+to delete for analysis since these are not meaningful statements about
+the Amazon. The final dataset for analysis contains 1895 coded Amazonian
+statements. Finally, we use poldis once more to extract locations for
+all speeches in the data. These locations represent the Brazilian state
+in which certain speech was given or an international country.
+
 \hypertarget{analysis-and-limitations}{%
@@
 limitations}\label{analysis-and-limitations}}
+
+To analyze our data, we first present a series of different plots on
+proportions of Amazonian statements and problem-constructions over time
+and by presidents. We control proportions for factors that might affect
+the incidence of the Amazon in speeches and portray both real and
+controlled curves. To test whether different problem constructions
+change according to location, we run a multinomial regression model in
+which different problem constructions (as categories) are the dependent
+variable and location is the independent variable. We also control for
+annual deforestation rates, annual inflation rates, and election years
+in the model. We interpret the plots and model considering multiple
+Amazon related events and policies over the last 30 years, as well as
+their correlations with different presidents and locations, while
+embedding problem-construction in contemporary happenings.
+
+These procedures come with its limitations. Our codebook is developed
+using specific Amazon related vocabulary. For example, a statement will
+be coded as economic integration if it is a meaningful support to the
+Zona Franca of Manaus or a Dam in the Amazon. However, the economy is
+generally a topic that presidents speak about. Hence, high incidence of
+economic integration in Amazonian statements can also be related to the
+higher importance of this problem-construction in Brazil in time.
+Moreover, we classify statements as Amazonian based on a dictionary
+composed of a single lexicon stem: ``amazon''. We chose to do so knowing
+that a few speeches about the Amazon might not contain the lexicon
+``Amazon'', for example, when the president says, ``the forest'' or
+``deforestation''. Hence, we might be missing statements about Amazon
+that do not refer to it. However, we consider this safer as we cannot be
+sure that mentions of the forest or deforestation do not correspond to
+other biomes such as the Cerrado or the Mata Atlantica. Nevertheless,
+our dataset covers only what is considered an official remark.
+Presidents, though, give interviews, appear in debates, talk at campaign
+rallies, and more recently start to appear in social media.
+Problem-construction within presidential discourse, thus, also happens
+in different sites for which we do not account for in this paper.
 
@@
 that mention the Amazon, introducing the specific problem-constructions
-we presented in section 2. Finally, we run a multinominal model to show
+we presented in section 2.1. Finally, we run a multinomial model to show
 how problem constructions change as the speaker moves further away from
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in
-relation to all speeches in each year. The smoothed curved controls
-incidence deforestation rates, economic situation, and election year
-(see appendix for methodological details). We observe various local
-maxima: 1989, 1992, 2004, 2009, 2015, and 2019. These points coincide
-exogenous events that helps us explain the rises and falls of the Amazon
-in presidential discourse.
+relation to all speeches in each year. The predicted share curve
+controls incidence for deforestation\footnote{The reasoning here is that
+  knowledge of high or low deforestation rates might drive presidents to
+  speak about the Amazon. Nevertheless, matching deforestation with
+  speech dates is a complicated endeavor. INPE published consolidated
+  deforestation data with almost two years of delay until 2005
+  (Capobianco 2021, 60). Preliminary data was published earlier, but
+  with lower degrees of confidence in the findings. For the subsequent
+  years, the consolidated figures for a given year came out in August of
+  the subsequent year. However, it also seems to be the case that the
+  executive government have access to the data before everyone else. In
+  addition, other sources indicating if deforestation is going up or
+  down, as fire data or lower resolution deforestation data (DETER for
+  example), or even other sources, circulated within the year the data
+  covered. The year of 1988 is particularly indicative of these
+  complications: a report dating 1988 was circulating with deforestation
+  and fire figures(Fearnside 1990), and a New York Times article about
+  the issue with deforestation rates for 1988 was written with comments
+  by an INPE scientist (Simons and Times 1988). Hence, we believe the
+  most appropriate way of matching is without any lags on deforestation.},
+economic situation, and speaker (see appendix for methodological
+details). We observe various local maxima: 1989, 1992, 2005, 2009, 2015,
+and 2019. These points coincide with exogenous events that helps us
+explain the rises and falls of the Amazon in presidential discourse.
 
@@
 populations a right over their territory. Two other factors are likely
-to explain this increase: in 1988 Chico Mendes was brutally murdered,
-and in 1989, the New York Times published an article with pictures of
-the Amazon burning. Both incidents caught unprecedented international
-attention. President Sarney responded to these publicly, and proposed a
-new set of policies to address, named Nossa Natureza (Capobianco 2021)
-
-\includegraphics{Full_draft_20220401_files/figure-latex/Amazonian speeches by year-1.pdf}
+to explain this increase: in 1988 Chico Mendes was brutally murdered and
+the New York Times published an article with pictures of the Amazon
+burning (Simons and Times 1988). Both incidents caught unprecedented
+international attention. President Sarney responded to these publicly,
+and proposed a new set of policies to address, named Nossa Natureza
+(Capobianco 2021).
+
+\includegraphics{Full_draft_20220401_files/figure-latex/Figure 1: Amazonian speeches by year-1.pdf}
 
@@
 number of financial resources to the region for public policy
-implementation (cite). During the Cardoso years (1994-2002), Amazonian
-speeches averaged at about 15\% without strong variation. There were no
-big international or domestic events that drove the topic up.
+implementation (Capobianco 2021). During the Cardoso years (1994-2002),
+Amazonian speeches averaged at about 16\% without strong variation.
+There were no big international or domestic events that drove the topic
+up. At the level of policy, though, we saw the birth of the National
+System of Protected Areas in 2001, and of the Amazon Regional Protected
+Areas Program. While the former created the legal framework for
+different types of protected areas to be created, the latter established
+a transnational partnership to finance the implementation of protected
+areas in the Amazon (Andonova 2014).
 
@@
 Copenhagen, and a perception that there was a turn towards less
-conservation after the 2011 Forest Code was adopted.
+conservation after the 2011 Forest Code was adopted and former
+environmental minister Marina Silva ended her alliance with the worker's
+party because of disagreements related to the priority of environmental
+policy.
 
@@
 We do find evidence that deforestation rates, economic situation,
-elections, and simply preferential preferences affect the incidence of
+elections, and simply presidential preferences affect the incidence of
 Amazon in speeches: the smoothed curve portrays lower proportions
@@
 the most frequent of them. Pure problem constructions dominate, with
-their joint average above 55\%. Among the four pure types as well as the
+their joint average at 55.8\%. Among the four pure types as well as the
 mixed types, we observe a strong variation over time, suggesting the
@@
 
-\includegraphics{Full_draft_20220401_files/figure-latex/mixed-types in time-1.pdf}
-
-The plots reveal several trends. Pure economic integration statements,
-which were dominant, decreased in incidence as of the mid 1990s. In the
-late 1990s, pure conservation as well as pure social development
-increased; both surpassing the proportion of economic integration
-problem-construction in 2005. Capobianco (2021) argues that the
-unprecedented decrease in deforestation we observed from 2004 to 2012
-was a product of an increase in the perception of stronger federal
+\includegraphics{Full_draft_20220401_files/figure-latex/Figure 2: mixed-types in time-1.pdf}
+
+The plots reveal several trends. We start by pure-types. Pure economic
+integration statements, which were dominant, decreased in incidence as
+of the late 1990s. Concurently, pure conservation as well as pure social
+development increased; both surpassing the proportion of economic
+integration problem-construction in 2010. Capobianco (2021) argues that
+the unprecedented decrease in deforestation we observed from 2004 to
+2012 was a product of an increase in the perception of stronger federal
 policies and presence in the Amazon region, which in turn engendered a
 perception of higher risk of being caught and fined for deforestation.
-This is aligned with our findings: a higher incidence of the Amazon as a
+This correlates with our findings: a higher incidence of the Amazon as a
 topic overall can generate a perception of more attention from the top,
 and a shift from economic integration to conservation can generate a
-perception of higher change of being caught. As of the early 2010s, we
-observe a reversal of the trend with a twist: economic integration
-starts picking up again in detriment of conservation and social
-development problem constructions, but with sovereignty increasing
-steadily.
-
-Figure 3 (below) shows these shifts more clearly and highlights the
-decrease of economic integration and increase of social and conservation
-problem constructions preceding Lula's presidential mandate. Relatedly,
-figure 3 also shows that while the reversal precedes the mandate of
-President Bolsonaro, it was with him and his dismantling of social and
-environmental policies that sovereignty and economic integration appears
-the most, in detriment of social development and environmental
-conservation. The starkest decrease relates to social development
-construction between Temer's and Bolsonaro's administration.
-
-\includegraphics{Full_draft_20220401_files/figure-latex/pure types in time -1.pdf}
-
-We now move to mixed types, which average at around 17\% for all
-presidents in our sample: overall, presidents prefer pure
-problem-constructions. While there is some variation in time for each
-single mixed type, some of them have low counts and interpretations are
-not adequate. We focus our discussion on those with higher incidence.
-First, the most frequent mix overall is that of economic integration
-with conservation, which after reaching 25\% of all
-problem-constructions in 1989, remained stable at 9\% on average for the
-remainder of the period. President Lula was the most frequent user of
-this mix. Second, except for economic and social development appearing
-together in all statements made by Color in 1992, mixed types using
-conservation were quite frequent in the lead up and aftermath of the
-1992 Earth Summit. This includes the mix type we label sustainable
-development, which constructs the Amazon as a problem of economic
-integration, social development, and environmental conservation. In all,
-we interpret the appearance of mixed types as more complex
-understandings of Amazonian problems. This follows a global agenda of
-understanding interconnections of social, environmental, and economic
-domains. As we show that Amazonian incidence in discourse does respond
-to global issues, this is not a surprise given agendas as Millennium
-Development Goals and the Sustainable Development Goals. Nevertheless,
-as in pure types, we also observe the comeback of sovereignty being used
-in mixed types in detriment of conservation. This becomes more apparent
+perception of higher change of being caught for illegal deforestation.
+As of the mid 2010s, we observe a reversal of the trend with a twist:
+economic integration starts picking up again in detriment of
+conservation and social development problem constructions, but with
+sovereignty increasing steadily.
+
+Figure 3 (below) shows these shift and reversal more clearly and
+highlights the decrease of economic integration and increase of social
+and conservation problem constructions preceding Lula's presidential
+mandate. Relatedly, figure 3 also shows that while the reversal precedes
+the mandate of President Bolsonaro, it was with him and his dismantling
+of social and environmental policies that sovereignty and economic
+integration appears the most, in detriment of social development and
+environmental conservation. The starkest decrease relates to social
+development construction between Temer's and Bolsonaro's administration.
+
+\includegraphics{Full_draft_20220401_files/figure-latex/Figure 3: pure types in time -1.pdf}
+
+We now move to mixed types, which average at 17.7\% for all presidents
+in our sample: overall, presidents prefer pure problem-constructions.
+While there is some variation in time for each single mixed type, some
+of them have low counts and interpretations are not adequate. We focus
+our discussion on those with higher incidence. First, the most frequent
+mix overall is that of economic integration with environmental
+conservation, which averages at 29.15\% in relation to mixed types only,
+and at 6.8\% in relation to all Amazonian statements. Overall, we
+observe an increase along time, reaching its pike in the early 2010.
+President Dilma was the most frequent user of this mix. A close second
+is economic and social development being used together in about 22.9\%
+of all mixed type statements and 5.4\% of all statements.
+
+All other mixed types appeared less than 2.6\% on average in relation to
+all statements. We can also interpret mixed types, though, by looking at
+what compose them the most along time. Mixed types using conservation
+were quite frequent in the lead up and aftermath of the 1992 Earth
+Summit. This includes the mix type we label sustainable development,
+which constructs the Amazon as a problem of economic integration, social
+development, and environmental conservation. We interpret the appearance
+of mixed types as more complex understandings of Amazonian problems.
+This follows a global agenda of understanding interconnections of
+social, environmental, and economic domains. As we show that Amazonian
+incidence in discourse does respond to global issues, this is not a
+surprise given agendas as Millennium Development Goals and the
+Sustainable Development Goals. Nevertheless, as in pure types, we also
+observe the comeback of sovereignty being used in mixed types, mostly in
+detriment of conservation social development. This becomes more apparent
 in a comparison between Lula and Bolsonaro, the two presidents that mix
-the most with proportions 11\% above presidential averages: 28.5\% and
-28.6\% respectively. While the former frequently mixed conservation with
-other problem constructions, the latter prefers mixing sovereignty. The
-combination of sovereignty with economic integration, which was also
+the most with proportions 11\% above presidential averages: 29.4\% and
+31.3\% respectively. While the former frequently mixed conservation with
+other problem constructions, the latter prefers mixing with sovereignty.
+The combination of sovereignty with economic integration, which was also
 characteristic of the military dictatorship policies for the region,
-reaches its highest level with Bolsonaro.
-
-\includegraphics{Full_draft_20220401_files/figure-latex/mixed-types by president -1.pdf}
+reaches its highest level with Bolsonaro: 22.7\% of all mixed types.
+
+\includegraphics{Full_draft_20220401_files/figure-latex/Figure 4: mixed-types by president -1.pdf}
 
@@
 While unprecedented, this new balance was not long-standing. Democratic
-decay is slow and the embryony of Bolsonaro's Amazonian discourse was
+decay is slow and the embryo of Bolsonaro's Amazonian discourse was
 breeding half a decade before he took office. We observe the decrease in
-conservation related statements in the early 2010s, and the soft
-increase of sovereignty in form of mixes in the mid 2000s. The hard
-increase in sovereignty comes in the 2010s. As we conceptualize and
-operationalize sovereignty as boundary-making vis-à-vis internal and
-external perceived threats to the Amazon, we interpret this increase as
-attacks to indigenous and traditional populations. At the policy side,
-the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a
-turning point: political opposition to conservation got particularly
-organized and managed to lobby the executive and conquer this policy
-wins, which were largely opposed by environmentalists.
+conservation related statements in the mid 2010s, and the soft increase
+of sovereignty both pure and in mixes already late 2000s (figure 3) .
+The hard increase in sovereignty comes in the early 2010s. As we
+conceptualize and operationalize sovereignty as boundary-making
+vis-à-vis internal and external perceived threats to the Amazon, we
+interpret this increase as attacks to indigenous and traditional
+populations. At the policy side, the Itaipu Dam in the late 2000s and
+the 2011 Forest code are seen as a turning point: political opposition
+to conservation got particularly organized and managed to lobby the
+executive and conquer this policy wins, which were largely opposed by
+environmentalists.
 
@@
 
+Table 2, below, displays the multinational regression coefficients for
+the correlation between diverse problem constructions and locations. The
+regression coefficients express the relative probability in relation to
+the reference categories, which are Amazonian states for location and
+environmental conservation for problem construction. Although all the
+other mixed types problem-constructions were included in the model, we
+choose to display and focus the analysis on the pure types. From the
+outset, we notice that problem constructions of pure economic
+integration and pure social development correlate in negative
+statistically significant ways to both international settings and
+Brasilia in relation to environmental conservation problem constructions
+in Amazonian states. These findings indicate that constructing the
+Amazon as an issue of environmental conservation is more likely to
+happen in international settings and in Brasilia than in Amazonian
+states. Additionally, pure sovereignty correlates in negative
+statistically significant ways to international settings in relation to
+conservation in Amazonian states. That is, constructing the Amazon as an
+issue of sovereignty is less likely in international settings than it is
+in Amazonian States. Interestingly, we see no statistically significant
+correlations between problem constructions in non-Amazonian states in
+relation to Amazonian states. This indicates that when presidents speak
+about the Amazon at the state level, constructions might be rather
+similar across different states. Furthermore, we also notice that some
+of the control variables correlate with some Amazonian problem
+constructions in interesting ways. For example, pure sovereignty
+constructions correlate negatively with election years in relation to
+conservation. That is, in election years conservation constructions are
+more likely to take place in comparison to sovereignty. As well, annual
+deforestation rates correlate positively with economic integration
+constructions in relation to conservation. This indicates that both
+deforestation increases and presidents are also more likely to construct
+the Amazon as an issue of economic integration.
+
+\begin{longtable}[]{@{}llll@{}}
+\caption{Table 2 - Amazon Problem-Construction by
+Location}\tabularnewline
+\toprule
+\endhead
+Dependent.Variables & Economic Integration vs.~Environmental
+Conservation & Social Development vs.~Environmental Conservation &
+Sovereignty vs.~Environmental Conservation \\
+Brasilia.vs..Amazonian.States & -1.024*** & -1.002*** & -0.206 \\
+International.vs..Amazonian.States & -0.612*** & -1.583*** &
+-1.427*** \\
+Non.AM.States.vs..Amazonian.States & 0.023 & -0.041 & 0.324 \\
+Election.Year & -0.241 & 0.028 & -0.684** \\
+Annual.Deforestation & 0.063*** & -0.031* & 0.004 \\
+Average.Inflation & -0.001*** & -0.001*** & -0.0001 \\
+\bottomrule
+\end{longtable}
+
+Putnam (1988) seminal article on the two level game between domestic and
+international politics analyzes how negotiations at both levels make
+policies possible. The author argues that both domestic and
+international levels need to be taken into consideration when analyzing
+how, often, domestic politics became entangled in international
+negotiations. The Amazon, as a region and a forest, has been the topic
+of international negotiations, national debates, and local policy
+implementation; though how the Amazon has been constructed as an issue
+differs on each of these three levels. While in Brasilia or
+internationally different presidents might construct the Amazon as an
+issue of conservation, the same presidents might construct the Amazon as
+an issue of economic integration or social development at the local
+level. This implies not only that audiences' priorities in each setting
+change, but that which policies are appropriate to solve the ``Amazon
+issue'' differ. The three level game entails that conservation might be
+a desirable construction when speaking internationally about the Amazon,
+but not for local electorates. Such might help explain diverse local
+implementation gaps between public policy negotiated outside and
+implemented within the Amazon as perceptions and expectations about the
+issues the same policy addresses might differ (Alesina and Giuliano
+2009; López et al. 2020).
+
+Whereas presidential discourses at the top matter to define and justify
+public policy (Zarefsky 2004), presidents shape their discourses
+according to who their audience might be and what ``they want to hear''.
+This democratic game contribute to the advancement of ambiguous public
+policies thought from the outside to the Amazon or contradictory
+policies from Amazon to the outside. Take, for example, the rural credit
+offered to local agricultural producers in Amazonian states went from
+500 million reais in 1999 to over 4 billion by 2012 (cite). During the
+same period, the money spent in fighting deforestation in the Amazonian
+states also increased from \ldots{} in \ldots{} to \ldots{} in \ldots{}
+These policies match diverse local, national, and international
+expectations and match solutions to different problem constructions
+presented at each of these levels.
+
 \hypertarget{conclusion}{%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-assunuxe7uxe3o2015}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-assuncao2015}{}}%
 Assunção, Juliano, Clarissa Gandour, and Rudi Rocha. 2015.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cezar2020}{}}%
+Cezar, Rodrigo Fagundes. 2020. {``Brazilian Presidential Speeches from
+1985 to July 2020.''}
+\url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/M9UU09}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-drummond2006}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fearnside1990}{}}%
+Fearnside, Philip M. 1990. {``The Rate and Extent of Deforestation in
+Brazilian Amazonia.''} \emph{Environmental Conservation} 17 (3):
+213--26. \url{https://doi.org/10.1017/s0376892900032355}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-franchini2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lopez2020}{}}%
+López, Matias, Graziella Moraes Silva, Chana Teeger, and Pedro Marques.
+2020. {``Economic and Cultural Determinants of Elite Attitudes Toward
+Redistribution.''} \emph{Socio-Economic Review}, May.
+\url{https://doi.org/10.1093/ser/mwaa015}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-meyer2021}{}}%
+Meyer, David, Evgenia Dimitriadou, Kurt Hornik, Andreas Weingessel, and
+Friedrich Leisch. 2021. \emph{E1071: Misc Functions of the Department of
+Statistics, Probability Theory Group (Formerly: E1071), TU Wien}.
+\url{https://CRAN.R-project.org/package=e1071}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-miranda2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-noble2006}{}}%
+Noble, William S. 2006. {``What Is a Support Vector Machine?''}
+\emph{Nature Biotechnology} 24 (12): 1565--67.
+
 \leavevmode\vadjust pre{\hypertarget{ref-pacheco2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepolaindewaroux2021}{}}%
-Polain de Waroux, Yann le, Rachael D. Garrett, Mollie Chapman, Cecilie
-Friis, Jeffrey Hoelle, Leonie Hodel, Kelly Hopping, and Julie Gwendolin
-Zaehringer. 2021. {``The Role of Culture in Land System Science.''}
-\emph{Journal of Land Use Science} 16 (4): 450--66.
-\url{https://doi.org/10.1080/1747423X.2021.1950229}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-putnam1988}{}}%
@@
 Two-Level Games.''} \emph{International Organization} 42 (3): 427--60.
-\url{https://www.jstor.org/stable/2706785}.
+\url{http://www.jstor.org/stable/2706785}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-simons1988}{}}%
+Simons, Marlise, and Special To the New York Times. 1988. {``Vast Amazon
+Fires, Man-Made, Linked to Global Warming.''} \emph{The New York Times},
+August.
+\url{https://www.nytimes.com/1988/08/12/world/vast-amazon-fires-man-made-linked-to-global-warming.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lepolaindewaroux2021}{}}%
+Waroux, Yann de, Rachael D. Garrett, Mollie Chapman, Cecilie Friis,
+Jeffrey Hoelle, Leonie Hodel, Kelly Hopping, and Julie Gwendolin
+Zaehringer. 2021. {``The Role of Culture in Land System Science.''}
+\emph{Journal of Land Use Science} 16 (4): 450--66.
+\url{https://doi.org/10.1080/1747423X.2021.1950229}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-westerwinter2021}{}}%

### 2022-04-11 Draft_April_2022/Full_draft_20220401.rmd
#structure_new

@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations ^[For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
-(2021).
-For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).], we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations [^2], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
 The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+
+[^2]: For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
+(2021).
+For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).
 
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006]^[For more information on this please see the extended methodology.
-The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the  validation set.
-The extended methodology also includes a more detailed codebook table with further coding guidelines.].
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006][^3].
 After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set, we use the model to automatically code the remaining 1007 Amazonian statements.
@@
 These locations represent the Brazilian state in which certain speech was given or an international country.
+
+[^3]: For more information on this please see the extended methodology.
+The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the validation set.
+The extended methodology also includes a more detailed codebook table with further coding guidelines.
 
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^2], economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation[^4], economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
@@
 
-[^2]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
+[^4]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
 Nevertheless, matching deforestation with speech dates is a complicated endeavor.
@@
 While in Brasilia or internationally different presidents might construct the Amazon as an issue of conservation, the same presidents might construct the Amazon as an issue of economic integration or social development at the local level.
-This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” differ.
+This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" differ.
 The three level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not for local electorates.
@@
 Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 (cite).
-During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
+During the same period, the money spent in fighting deforestation in the Amazonian states also increased from ...
+in ...
+to ...
+in ...
+These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
 
-# 5 Conclusion
+# 5 Discussion
 
-# 6 References
+# 6 Conclusion
+
+#  References

### 2022-04-11 Draft_April_2022/Full_draft_20220401.rmd
Updates to anlysis section 4.3 for modelling

--- 2022-04-10 Draft_April_2022/Full_draft_20220401.rmd
@@
   labs(x = "", y = "", title ="Share of each pure type by year",
-       subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
        caption = "") +
@@
 ```{r code for averages, eval=FALSE, include=FALSE}
-
 mmt1 <- ama_mx %>%
@@
   mutate(perc = n / sum(n)) #averages in relation to only mixed-types
-
 mmt2 <- ama_mx %>%
@@
   mutate(perc = n / sum(n)) # averages in relation to full sample
-
 ```
@@
 
+Figure 5, below, illustrates the share of pure-type problem construction by locations in Brazil.
+We divide locations into Amazonian states (i.e.
+all the Brazilian states in which the Amazon biome is present), non-Amazonian states (other brazilian states), Brasilia (the capital city in Brazil), and international (countries outside of Brazil).
+Notice that, consistently, presidents construct the Amazon as an issue of pure economic integration within Amazonian states more often than all other constructions in time.
+Alternatively, we see that pure conservation becomes increasingly less frequent in time for Amazonian states.
+As well, pure social development constructions, which were fairly frequent from the early-2000s and onwards, disappeared around 2015 after the mid-2010s in Amazonian states.
+Nonetheless, we see a large increase from the mid-2000s to the mid-2010s in the frequency in which presidents constructed the Amazon as an issue of pure social development in Brasilia and non-Amazonian states.
+In Brasilia, also, pure conservation constructions went down drastically during the 1990s, but increased steadily from the mid-2000s onwards.
+Interestingly, presidents most often constructed the Amazon as an issue of pure environmental conservation internationally only from the mid 2000s until the mid-2010s.
+Moreover, pure sovereignty constructions did appear in international settings until the mid-2000s.
+
 ```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 pure_types_time_location <- ama_mx %>%
-  count(president, mx_cat2, mx_cat, year, location_cat) %>%
-  group_by(president, year) %>%
+  count(mx_cat2, mx_cat, year, location_cat) %>%
+  group_by(year) %>%
   mutate(perc = n / sum(n)) %>% 
@@
   labs(x = "", y = "", title ="Share of each pure type in time by location",
-       subtitle = "Sample composed by 1885 Amazonian statements in presidential speeches since 1985",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
        caption = "") +
@@
   facet_wrap(~location_cat, scales= "free_y", ncol=2)
-
 pure_types_time_location
-
 ```
 
-Table 2, below, displays the multinomial regression coefficients for the correlation between problem constructions and locations.
-The regression coefficients express the relative probability in relation to the reference categories, which are Amazonian states for location and environmental conservation for problem construction.
-Although all the other mixed types problem-constructions were included in the model, we choose to display and focus the analysis on the pure types.
-From the outset, we notice that problem constructions of pure economic integration and pure social development correlate in negative statistically significant ways to both international settings and Brasilia in relation to environmental conservation problem constructions in Amazonian states.
-These findings indicate that constructing the Amazon as an issue of  environmental conservation is more likely to happen in international settings and in Brasilia than in Amazonian states.
-Additionally, pure sovereignty correlates in negative statistically significant ways to international settings in relation to conservation in Amazonian states.
-That is, constructing the Amazon as an issue of sovereignty is less likely in international settings than it is in Amazonian States.
-Interestingly, we see no statistically significant correlations between problem constructions in non-Amazonian states in relation to Amazonian states.
-This indicates that when presidents speak about the Amazon at the state level, constructions might be rather similar across different states.
-Furthermore, we also notice that some of the control variables correlate with some Amazonian problem constructions in interesting ways.
-For example, pure sovereignty constructions correlate negatively with election years in relation to conservation.
-That is, in election years conservation constructions are more likely to take place in comparison to sovereignty.
-As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation.
-This indicates that both deforestation increases and presidents are also more likely to construct the Amazon as an issue of economic integration.
+Table 2, below, displays the multinomial regression coefficients for the correlation between diverse problem constructions and locations.
+The regression coefficients express the log odds, that is, the logarithm odds to the reference categories.
+The reference categories are Amazonian states for location and environmental conservation for problem construction.
+To facilitate visualization, since the model has many more columns (i.e.
+types of problem construction), we only display the model results for the pure-type constructions, however, the model does account for both pure and mixed-type constructions.
+We keep the results for the control variables for election year, annual deforestation rates, and average yearly inflation in the table.
 
@@
 
+The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
+The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
+
+Sovereignty in the Amazon is an issue within Brazil.
+The negative statistically significant coefficient for constructing the Amazon as a problem of pure sovereignty in international settings, in relation to conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+The lack of statistically significant correlations between pure sovereignty constructions and Brasilia or other non-Amazonian states, corroborates that the Amazon as an issue of sovereignty is an internally performed issue.
+
+Constructing the Amazon as an issue of economic integration correlates with increases in deforestation rates.
+Some of the control variables correlate with some Amazonian problem constructions in interesting ways.
+For example, pure sovereignty constructions correlate negatively with election years in relation to conservation.
+That is, in election years conservation constructions are more likely to take place in comparison to sovereignty.
+As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation.
+This indicates that as deforestation increases, presidents are also more likely to construct the Amazon as an issue of economic integration, or vice-versa.
+
 @putnam1988 seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
@@
 Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
-This democratic game contribute to the advancement of ambiguous public policies thought from the outside to the Amazon or contradictory policies from Amazon to the outside.
-Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 (cite).
+This democratic game contributes to the advancement of ambiguous public policies thought from the outside to the Amazon or contradictory policies from Amazon to the outside.
+Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 [@capobianco2021].
 During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.

### 2022-04-11 Draft_April_2022/Full_draft_20220401.rmd

@@
 
-# 5 Conclusion
+# 5 Discussion
 
-# 6 References
+# 6 Conclusion
+
+# References
+
+# Appendix
+
+## Extended Methodology
+
+This appendix details the methodology employed by the authors in the article.
+
+## The Dataset
+
+We update a dataset provided by Cezar (2020), which builds upon the archives of the Brazilian Presidential Library.
+The dataset contains all official remarks by Brazilian Presidents from 1985 to 2019.
+We update the dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches.
+Overall, it covers a total of 8 presidents (Sarney, Collor, Franco, Cardoso, Silva, Rousseff, Temer, and Bolsonaro) across 8 mandates (Collor and Dilma were impeached and vice presidents Franco and Temer took over).
+
+We start by cleaning the dataset by removing all accents, non-standard Latin characters, and extra spaces.
+We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
+Our dictionary is composed of a single lexicon stem: “amazon”.
+In Portuguese, it captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says “the forest” or uses a pronoun, he or she could be referring to the Amazon.
+Also, it is likely that whenever a president mentions “deforestation” or derived vocabulary, he or she is speaking about the Amazon.
+However, as we cannot be sure all the time in those instances (i.e.
+mentions of “the forest” or “deforestation” could be referring to the Atlantic Forest or the Cerrado).
+We opt for the safer side and make sure speeches we gather are indeed about the Amazon as a region, forest, or people by only capturing “amazon” related lexicon.
+We find that 946 speeches are, at least partially, about the Amazon from the 6130.
+
+Using the poldis R package, we extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+By doing so we create our unit of analysis: an Amazonian statement.
+We use Amazon statements as our unit of analysis for three main reasons.
+First, presidential speeches can be long and cover a wide variety of topics.
+For example, the average word count for speeches that mention the stem “amazon” are 2355 words.
+Working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
+A single speech can have more than one Amazonian statement and this statement might be embedded within a different part of the speech.
+Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
+Finally, other authors adopting similar strategies, opt for picking an arbitrary number of words before and after the mention (Kentikellenis and Voeten, 2021).
+We opt for picking two sentences before and two sentences after, rather than words because a sentence, because sentences usually contain a cohesive idea.
+Opting for a word threshold, might cut a sentence in the middle and yield an incomplete idea.
+Nevertheless, this process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified previously.
+Notice that an Amazonian statement can contain two or more matches of the stem “amazon” (i.e.
+two consecutive sentences in which one of the words covered by the stem appears).
+In this case, we get two sentences before the first match and two sentences after the last match.
+On average, an Amazonian statement contains 123 words.
+
+## Operationalization
+
+We proceed to operationalize how the Amazon is constructed as a problem.
+To do so, we develop and apply a qualitative codebook to Amazonian statements.
+We do so for two reasons.
+First, and foremost, we believe that a dictionary and other “bag of words” methods might not capture nuances in the texts.
+These nuances include Amazonian statements that negate certain aspects about the Amazon or statements in which the matched words might not be not directed at the Amazonian region, peoples, or forest.
+Second, we chose to look at the statements and inductively develop a codebook to verify if the insights from the literature hold within presidential speeches and, if not, add or remove codes, as well as discuss which statements should, and not, be included in each code and why.
+
+After revising the literature (section 2), we went through a random sample of the speeches to develop the codebook.
+The three policy-cycles (sovereignty, economic integration, and conservation) were clearly identifiable in the speeches.
+However, once the coding began to take place, however, we noticed two things.
+One, that some of the Amazon statements were not about Amazon per se.
+That is, our strategy to identify Amazonian statements yielded a few false positives.
+These are statements that mention the stem “amazon”, but are not about the Brazilian Amazon region, people, or forest.
+For example, the president might greet the Governor of the Amazonas in a speech or make a reference to the Venezuelan Amazon.
+We coded these statements as false positives.
+Two, we noticed speeches often refer to social development using a different vocabulary of policies and objectives.
+Those references often differ from references to conservation or economic integration.
+Hence, we created the code category ‘social development’ as explained below.
+We consider this to be a finding, but rather than emerging from our analysis, it emerged from codebook development.
+contain a full description of each code category and the coding practices that inform our procedure.
+
+Table 1 – Qualitative Codebook
+
+Sovereignty
+Description: This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+We understand claims of sovereignty as a particular narrative that touches on imaginaries of external threats to territory.
+Relatedly, we also understand sovereignty as a particular narrative that raises concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
+In all, it advances the view that the Amazon is Brazilian and foreign presence in the region needs to be monitored closely.
+
+Coding practice: we apply this code to references to sovereignty that meaningfully reflect the description above.
+Simple mentions to the Brazilian Armed Forces, frontiers, or military technology (e.g.
+SIPAM-SIVAM), are not automatically, by themselves, understood as constructing the Amazon as a problem of sovereignty.
+When presidents question the authority or interests of someone’s arguments about Amazon, for example, we apply this code as it raises concerns about wrong perspective and criticism.
+When presidents claim external actors want to internationalize the Amazon territory, we apply this code as it touches upon external threats to territory.
+
+Example: “Senhores deputados.
+Elo fundamental para que o Brasil realmente rume em direção à prosperidade.
+Queria primeiro dizer, senhor Hu Chunhua,  eu quero agradecer as palavras do seu embaixador no Brasil reconhecendo a nossa soberania sobre a região Amazônica, no episódio ocorrido há pouco, por ocasião do encontro do G7.
+Muito obrigado ao governo chinês.
+Para nós, não têm preço esse reconhecimento público e suas palavras sobre essa região tão importante para o mundo e para o Brasil.” (Bolsonaro 25/10/2019)
+Economic Integration
+Description: This code constructs the Amazon region and/or forest as an issue of economic integration.
+It advances the view that the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.
+
+Coding practice: We apply this code to references to economic integration that meaningfully reflect the description above.
+Simple mentions of development, integration, investment, and technology are not automatically coded as economic integration.
+However, direct mentions of the words “economic development” are coded here.
+We avoid overlap between this code and social development by considering integration references as targeting infrastructure rather than peoples’ rights.
+For example, developing infrastructure for internet, radio, and energy are coded as economic integration.
+However, if the presidents speak about people’s access and rights to information (internet and radio) and electricity, we code as social development.
+Relatedly, improving macro-structural conditions of the job market is coded as economic integration,, while people’s right to a dignified job is coded as social development.
+Importantly, we make the analytical choice to include micro-finance instruments as credits and loans in economic development, while grants or donations fall within social development.
+
+Example: "Se me permitem, na Amazônia -que durante tanto tempo ficou adormecida, por falta de uma ação integrada- nós temos já algumas ações muito estruturadoras.
+Nós, na Amazônia, estamos fazendo uma ligação que passa por Manaus, passa por Boa Vista, Caracaraí, até chegar lá em cima, que é aquela lista vermelha, que vai lá para cima, na direção da Venezuela,é a estrada 174.
+Essa estrada dará possibilidade da produção da Zona Franca de Manaus ser competitiva, não aqui dentro, mas lá fora mesmo, como é a vocação natural da Zona Franca, exporte, e poderá exportar pelo Caribe.” (FHC 2/7/1997)
+Social Development
+Description: This code constructs the Amazon region and/or forest as an issue of social development.
+It advances the view that Amazon is full of citizens who should have their rights guaranteed.
+This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
+This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
+Finally, this includes referrals to culture and the right to vote.
+
+Coding practice: We apply this code to references to social development that meaningfully capture the description above.
+Simple mentions to development are not automatically coded as social development.
+However, direct mentions supporting “social development” are coded here.
+An illustrative example relates to speeches outlining the role of the armed forces in providing health services for faraway populations, which we code as social development but not sovereignty.
+
+Example: “Mas como o Estado não tem que ter lucro, o Estado precisa garantir a cidadania, nós achamos que o cidadão que mora às margens do rio Amazonas, a 600 Km de Manaus, ele tem que ter direito a ter luz na sua casa, a ter geladeira, a ter televisão e a ver sua novela.
+Já investimos 14 bilhões de reais nesse programa, em três anos e meio.
+Sabe quantos postes nós já colocamos?
+Um milhão de quilômetros de fio.” (Lula 20/11/2009)
+Conservation
+Description: This code constructs the Amazon region and/or forest as an issue of conservation.
+This narrative focuses on the value of a standing forest and of the preserved ecosystem in the region.
+The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous peoples should be maintained and fostered.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created.
+
+Coding practice: We apply this code to references to conservation that meaningfully capture the description above.
+Simple mentions of biodiesel, renewable energies, climate change, or sustainable development are not automatically coded as constructing the Amazon as a conservation problem.
+However, calls for more demarcation of territory are coded as constructing the Amazon as a conservation problem.
+While general references to tourism are coded as economic integration, references to eco-tourism are coded here.
+
+Example: “Adotei medidas de caráter emergencial, suspendi a exportação de madeiras em toras, suspendi incentivos fiscais e creditícios na Amazônia a projetos que podiam causar danos ambientais e instituí a obrigatoriedade do licenciamento para a atividade de extração de ouro com a proibição da utilização do mercúrio.
+Dando início à reestruturação do sistema governamental de controle e preservação do meio ambiente, criei o Instituto Brasileiro do Meio Ambiente e Recursos Naturais, IBAMA, que está entregue à capacidade do Dr.
+Fernando César Mesquita.” (Sarney, 20/7/1989)
+False positive
+Description: statements that were assigned as Amazonian but are about the Amazon.
+
+Example: “cumprimentar os presidentes de bancos publicos do banco do brasil alexandre abreu do bndes luciano coutinho da caixa miriam belchior do banco do nordeste marcos costa holanda do banco da amazonia valmir pedro rossi o vicepresidente do banco do brasil cesar borges da diretoria de infraestrutura queria cumprimentar as senhoras e os senhores dirigentes de agencias reguladoras dirigir um cumprimento especial ao senhor robson andrade presidente da confederacao nacional da industria por intermedio de quem cumprimento todos os empresarios das federacoes aqui presentes” (Rousseff, 9/7/2015)
+
+Each code is mutually exclusive in its conceptualization, meaning that they cover different forms of constructing the Amazon as a problem.
+Each Amazonian statement, though, might be assigned to one or more codes.
+A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration or a problem of social development and conservation, and so on.
+Amazonian statements, thus, can be either coded as a single code (ideal types) or one or more codes (mixed types).
+
+With this codebook in hands, then, each one of us manually coded the same set of 1007 randomly selected Amazonian statements.
+This amount refers to 50% of all the Amazon Statements identified.
+We coded all statements separately from each other, following inter-coder reliability procedures.
+After reading a statement, we assigned the value of one or zero to each one of the four code categories in table 1.
+Inter-coder agreement for each of the four main categories was 85%, on average.
+Most of the disagreements were on economic integration versus social development and related to the difference in emphasizing infrastructure versus emphasizing peoples’ rights.
+For each non-matching code, the co-authors discussed and sorted their disagreements to finalize the putting together a training set so that a supervised machine-learning model classifies the rest.
+
+## Supervised Machine-Learning
+
+We use this hand-coded set to train a model that codes the remaining Amazonian statements in our text corpus using R.
+To select the best approach, we use the hand-coded data to compare how several supervised-machine learning methods perform in identifying false positive observations from the training set.
+To do so, we do some simple text pre-processing in R such as removing stopwords, punctuations, signs, and empty spaces using the TM package.
+Then, we split the hand coded sample into a randomly selected training set and a validation set.
+The training set contains 80% of the observations in the hand-coded sample (806 observations) while the validation set contains the other 20% of the observations (201 observations).
+
+We use this training set to train models support-vector machine( SVM) models to label text data on the validation set.
+Table 2, below, describes how the model performs in labeling observations in the validation set in regard to accuracy and AUC scores (Area Under the Curve)..
+The SVM training algorithm is a non-probabilistic binary linear classifier that classifies documents by assigning points in mapped space to maximize the width of the gap between categories (Meyer et al.
+2021).
+SVM is a particularly appropriate machine-learning algorithm for binary text labeling since it relies on maximizing distances between two categories (see also Noble 2006).
+We rely on the e1071 package to run the SVM model due to its flexibility in regard to parameter choices and because it helps users tune parameters to better fit the label patterns in the text data.
+Once the model parameters are tuned to better fit the patterns for each code, we expect the model to perform considerably better in labeling the remaining 1007 statements automatically.
+
+Table 2 - SVM Model Performance
+
+Accuracy
+AUC
+False Positives
+0.946
+0.69
+Sovereignty
+0.866
+0.59
+Economic Integration
+0.678
+0.68
+Social Development
+0.792
+0.66
+Conservation
+0.802
+0.78
+
+After the SVM models are tuned, the probability that a certain Amazonian statement belongs to a code category is returned.
+Statements that have a probability of 0.45 or more of belonging to a code category are labeled 1 (i.e.
+belonging to a category) and statements that have a probability of 0.45 or less of belonging to a code category are labeled 0 (i.e.
+not belonging to a category).
+We find that a 0.5 threshold can be too strict while a 0.4 may generate a few false positives and, for this reason, we set the threshold at 0.45.
+The final trained models excel to label observations in some categories in comparison to others.
+We also take a random sample of 101 (10% of the automatically labeled Amazonian statements to check how the model performed.
+We find that the model performs much better than the metrics above appear to indicate in comparison to how the authors would hand code these observations.
+The final models automatically label, out of the remaining 1007 statements, 84 statements as sovereignty, 437 as economic integration, 186 as social development, and 300 as conservation.
+The model also identified 41 false positive Amazon statements out of the 1007 labeled.
+Moreover, the proportions of the automatically labeled Amazonian statements for all categories in regard to the number of observations in the set, including observations that were not labeled but were not false positives (i.e.
+others), are similar to the proportions of the coded statements for the hand coded training set.
+
+After merging the data altogether for analysis, we chose to delete the false positive Amazonian statements for analysis since these are not meaningful statements about the Amazon as a forest, peoples, or region.
+In total there were 119 false positives out of the 2014 Amazonian statements.
+The final dataset for analysis contains 1895 Amazonian statements.
+Out of these, 237 statements are labeled as national sovereignty, 810 as economic integration, 418 as social development, and 567 as environmental conservation.
+We then added metadata about each of the speeches from which these Amazonian statements were taken from.
+The metadata includes variables such as the president (speaker), the year, the speech title, and the full text for the broader speech.
+Lastly, we use poldis once again to extract locations from texts.
+These locations can represent the Brazilian state in which certain speech was given, or international country or forum (e.g.
+United Nations).
+
+## Multinomial Modeling
+
+To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
+We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves.
+To test whether different problem constructions change according to location, we run a multinomial regression model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
+We code 4 different location categories for where speeches take place, they are: Amazonian states, non-Amazonian states, Brasilia, and International.
+In the model, we also control for annual deforestation rates, annual inflation rates, and election years in the model as these are variables which could mitigate the correlations between problem construction and location.
+Annual deforestation rates data were taken from the Satellite Monitoring of Deforestation Program (PRODES).
+However, since annual deforestation rates are calculated from 1988, we input the rates of 1988 to 1985, 1986, and 1987 because these rates are consistent with most estimates (see Prates and Bracha 2010).
+The average annual inflation data is taken from the Worldwide Inflation Data.
+Election years are input as a dummy variable in which election years are marked 1 and non-election years are marked 0.
+After the model is run, post estimation tests such as the Chi-square test shows us that the model selected is highly statistically significant in explaining variance in data in comparison to a null model (i.e.
+our model explains a considerable amount of the variance).
+The likelihood ratio test also shows that the model does not suffer with issues of multicollinearity.
+
+## Limitations
+
+These procedures come with its limitations.
+Our codebook is developed using specific Amazon related vocabulary.
+For example, a statement will be coded as economic integration if it is a meaningful support to the Zona Franca of Manaus or a Dam in the Amazon.
+However, the economy is generally a topic that presidents speak about.
+Hence, high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Hence, we might be missing statements about Amazon that do not refer to it.
+However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
+Nevertheless, our dataset covers only what is considered an official remark.
+Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently start to appear in social media.
+Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.

### 2022-04-11 Draft_April_2022/Full_draft_20220401.rmd
More updates to rmd files

@@
 ```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-# data on deforestation rates per year (PRODES)
-# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
-# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
-# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
-# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
@@
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-# inflation rates per year Brazil (average for year)
-# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
 ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
-# remove non-identified locations and mixed-other constructions (very little data for either and not relevant)
 ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
@@
 chi_square <- chisq.test(ama_model$mx_cat, predict(model))
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
-# library(lmtest)
-# lrtest(null_model, model) # We very much reject the hypothesis
-# (i.e. the more complex model is significantly better than the null model).
-# Finally, let's get a nice output:
-# model_output <- stargazer::stargazer(model, type = "text",
-#                                      covariate.labels = c("Brasilia", "International", "Non-AM state",
-#                                                           "Election", "Deforestation", "Inflation"),
-#                                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-#                                                        "Sov-EI", "SD-Con", "Other"),
-#                                      dep.var.labels.include = FALSE)
 # too much information... Let's just focus on what we want here...
@@
 
+```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
+# data on deforestation rates per year (PRODES)
+# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
+# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
+# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
+# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
+# inflation rates per year Brazil (average for year)
+# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
+# post estimation tests
+chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
+# Chi-square p value (p-value < 0.001) tells us that our model explains a
+# significant amount of the variation in the data in comparison with a null model.
+# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
+# library(lmtest)
+# lrtest(null_model, model) # We very much reject the hypothesis
+# (i.e. the more complex model is significantly better than the null model).
+# too much information... Let's just focus on what we want here...
+stargazer::stargazer(model, type = "text",
+                     covariate.labels = c("Brasilia", "International", "Non-AM state",
+                                          "Election", "Deforestation", "Inflation"),
+                     column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
+                                       "Sov-EI", "SD-Con", "Other"),
+                     dep.var.labels.include = FALSE)
+```
+
 ## Limitations

### 2022-04-11 Draft_April_2022/Full_draft_20220401.rmd
#somewhat nicer tables in pdf #problems with plots, though

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? An analysis of
-  presidential speeches since 1985
+title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
 author:
@@
 output:
-  pdf_document: default
   html_document:
@@
     reference_docx: template.docx
+  pdf_document: default
 bibliography: references.bib
@@
 library(stargazer)
+library(kableExtra)
 Sys.setlocale("LC_ALL", "C")
@@
 
+\begin{landscape}
+
 ```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble(Problem_Construction = c("National Sovereignty", "Economic Integration",
-                                                    "Social Development", "Environmental Conservation"),
+
+codebook <- tibble::tibble("Problem Construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
                            Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
@@
 Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.",
-                                           "This code constructs the Amazon region and/or forest as an issue of economic integration.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
 It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.",
-                                           "This code constructs the Amazon region and/or forest as an issue of social development.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
 It advances the view that Amazon is full of citizens who should have their rights guaranteed.
@@
 This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.",
-                                           "This code constructs the Amazon region and/or forest as an issue of conservation.
+Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
 This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
 The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."),
-                           Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
 I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
@@
 Mesquita (Sarney 20/07/1989)"))
-knitr::kable(codebook, format = "simple", caption = "Table 1 - Amazonian Problem-Construction Codebook")
-```
+
+kbl(codebook, booktabs = T,caption = "Table 1 - Amazonian Problem-Construction Codebook")%>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
+  column_spec(1, width="3cm", bold=TRUE)%>%
+  column_spec(2, width="9cm") %>%
+  column_spec(3, width = "9cm")
+
+```
+
+\end{landscape}
 
@@
 
-Figure 5, below, illustrates the share of pure-type problem construction by locations in Brazil.
-We divide locations into Amazonian states (i.e.
-all the Brazilian states in which the Amazon biome is present), non-Amazonian states (other brazilian states), Brasilia (the capital city in Brazil), and international (countries outside of Brazil).
-Notice that, consistently, presidents construct the Amazon as an issue of pure economic integration within Amazonian states more often than all other constructions in time.
-Alternatively, we see that pure conservation becomes increasingly less frequent in time for Amazonian states.
-As well, pure social development constructions, which were fairly frequent from the early-2000s and onwards, disappeared around 2015 after the mid-2010s in Amazonian states.
-Nonetheless, we see a large increase from the mid-2000s to the mid-2010s in the frequency in which presidents constructed the Amazon as an issue of pure social development in Brasilia and non-Amazonian states.
-In Brasilia, also, pure conservation constructions went down drastically during the 1990s, but increased steadily from the mid-2000s onwards.
-Interestingly, presidents most often constructed the Amazon as an issue of pure environmental conservation internationally only from the mid 2000s until the mid-2010s.
-Moreover, pure sovereignty constructions did appear in international settings until the mid-2000s.
-
 ```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
@@
 
+Figure 5, above, illustrates the share of pure-type problem construction by locations in Brazil.
+We divide locations into Amazonian states (i.e.
+all the Brazilian states in which the Amazon biome is present), non-Amazonian states (other brazilian states), Brasilia (the capital city in Brazil), and international (countries outside of Brazil).
+Notice that, consistently, presidents construct the Amazon as an issue of pure economic integration within Amazonian states more often than all other constructions in time.
+Alternatively, we see that pure conservation becomes increasingly less frequent in time for Amazonian states.
+As well, pure social development constructions, which were fairly frequent from the early-2000s and onwards, disappeared around 2015 after the mid-2010s in Amazonian states.
+Nonetheless, we see a large increase from the mid-2000s to the mid-2010s in the frequency in which presidents constructed the Amazon as an issue of pure social development in Brasilia and non-Amazonian states.
+In Brasilia, also, pure conservation constructions went down drastically during the 1990s, but increased steadily from the mid-2000s onwards.
+Interestingly, presidents most often constructed the Amazon as an issue of pure environmental conservation internationally only from the mid 2000s until the mid-2010s.
+Moreover, pure sovereignty constructions did appear in international settings until the mid-2000s.
+
 Table 2, below, displays the multinomial regression coefficients for the correlation between diverse problem constructions and locations.
@@
 We keep the results for the control variables for election year, annual deforestation rates, and average yearly inflation in the table.
+
+The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
+The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
 
@@
 # too much information... Let's just focus on what we want here...
-md <- data.frame("Dependent Variables" = c("Economic Integration vs. Environmental Conservation",
-                                           "Social Development vs. Environmental Conservation",
-                                           "Sovereignty vs. Environmental Conservation"),
-                 "Brasilia vs. Amazonian States" = c("-1.024***","-1.002***", "-0.206"),
-                 "International vs. Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
-                 "Non-AM States vs. Amazonian States" = c("0.023", "-0.041", "0.324"),
+
+md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
+                                           "Social Development vs Environmental Conservation",
+                                           "Sovereignty vs Environmental Conservation"),
+                 "Brasilia vs Amazonian States" = c("-1.024***","-1.002***", "-0.206"),
+                 "International vs Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
+                 "Other States vs Amazonian States" = c("0.023", "-0.041", "0.324"),
                  "Election Year" = c("-0.241", "0.028", "-0.684**"),
@@
                  "Average Inflation" = c("-0.001***", "-0.001***", "-0.0001"))
-kableExtra::kable(t(md), format = "simple", caption = "Table 2 - Amazon Problem-Construction by Location")
-```
-
-The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
-The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
-That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
+
+kbl(t(md), booktabs = T,caption = "Table 2 - Amazon Problem-Construction by Location", align = "c")%>% kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
+  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m")%>%
+  column_spec(2, width="5cm", latex_valign = "m") %>%
+  column_spec(3, width = "5cm", latex_valign = "m") %>%
+  column_spec(4, width = "5cm", latex_valign = "m")
+
+```
 
@@
 Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 [@capobianco2021].
-During the same period, the money spent in fighting deforestation in the Amazonian states also increased from … in … to … in … These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
+During the same period, the money spent in fighting deforestation in the Amazonian states also increased from ...
+in ...
+to ...
+in ...
+These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
 
@@
 We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
-Our dictionary is composed of a single lexicon stem: “amazon”.
-In Portuguese, it captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says “the forest” or uses a pronoun, he or she could be referring to the Amazon.
-Also, it is likely that whenever a president mentions “deforestation” or derived vocabulary, he or she is speaking about the Amazon.
+Our dictionary is composed of a single lexicon stem: "amazon".
+In Portuguese, it captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says "the forest" or uses a pronoun, he or she could be referring to the Amazon.
+Also, it is likely that whenever a president mentions "deforestation" or derived vocabulary, he or she is speaking about the Amazon.
 However, as we cannot be sure all the time in those instances (i.e.
-mentions of “the forest” or “deforestation” could be referring to the Atlantic Forest or the Cerrado).
-We opt for the safer side and make sure speeches we gather are indeed about the Amazon as a region, forest, or people by only capturing “amazon” related lexicon.
+mentions of "the forest" or "deforestation" could be referring to the Atlantic Forest or the Cerrado).
+We opt for the safer side and make sure speeches we gather are indeed about the Amazon as a region, forest, or people by only capturing "amazon" related lexicon.
 We find that 946 speeches are, at least partially, about the Amazon from the 6130.
 
-Using the poldis R package, we extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+Using the poldis R package, we extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
 By doing so we create our unit of analysis: an Amazonian statement.
@@
 First, presidential speeches can be long and cover a wide variety of topics.
-For example, the average word count for speeches that mention the stem “amazon” are 2355 words.
+For example, the average word count for speeches that mention the stem "amazon" are 2355 words.
 Working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
@@
 Nevertheless, this process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified previously.
-Notice that an Amazonian statement can contain two or more matches of the stem “amazon” (i.e.
+Notice that an Amazonian statement can contain two or more matches of the stem "amazon" (i.e.
 two consecutive sentences in which one of the words covered by the stem appears).
@@
 We do so for two reasons.
-First, and foremost, we believe that a dictionary and other “bag of words” methods might not capture nuances in the texts.
+First, and foremost, we believe that a dictionary and other "bag of words" methods might not capture nuances in the texts.
 These nuances include Amazonian statements that negate certain aspects about the Amazon or statements in which the matched words might not be not directed at the Amazonian region, peoples, or forest.
@@
 That is, our strategy to identify Amazonian statements yielded a few false positives.
-These are statements that mention the stem “amazon”, but are not about the Brazilian Amazon region, people, or forest.
+These are statements that mention the stem "amazon", but are not about the Brazilian Amazon region, people, or forest.
 For example, the president might greet the Governor of the Amazonas in a speech or make a reference to the Venezuelan Amazon.
@@
 Those references often differ from references to conservation or economic integration.
-Hence, we created the code category ‘social development’ as explained below.
+Hence, we created the code category 'social development' as explained below.
 We consider this to be a finding, but rather than emerging from our analysis, it emerged from codebook development.
@@
 
-Table 1 – Qualitative Codebook
-
-Sovereignty
-Description: This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+Table 1 -- Qualitative Codebook
+
+Sovereignty Description: This code constructs the Amazon region and/or forest as an issue of national sovereignty.
 We understand claims of sovereignty as a particular narrative that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as a particular narrative that raises concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
+Relatedly, we also understand sovereignty as a particular narrative that raises concerns about wrong perspectives and criticism from foreign and non-state actors about governments' actions related to the Brazilian Amazon.
 In all, it advances the view that the Amazon is Brazilian and foreign presence in the region needs to be monitored closely.
@@
 SIPAM-SIVAM), are not automatically, by themselves, understood as constructing the Amazon as a problem of sovereignty.
-When presidents question the authority or interests of someone’s arguments about Amazon, for example, we apply this code as it raises concerns about wrong perspective and criticism.
+When presidents question the authority or interests of someone's arguments about Amazon, for example, we apply this code as it raises concerns about wrong perspective and criticism.
 When presidents claim external actors want to internationalize the Amazon territory, we apply this code as it touches upon external threats to territory.
 
-Example: “Senhores deputados.
+Example: "Senhores deputados.
 Elo fundamental para que o Brasil realmente rume em direção à prosperidade.
@@
 Muito obrigado ao governo chinês.
-Para nós, não têm preço esse reconhecimento público e suas palavras sobre essa região tão importante para o mundo e para o Brasil.” (Bolsonaro 25/10/2019)
-Economic Integration
-Description: This code constructs the Amazon region and/or forest as an issue of economic integration.
+Para nós, não têm preço esse reconhecimento público e suas palavras sobre essa região tão importante para o mundo e para o Brasil." (Bolsonaro 25/10/2019) Economic Integration Description: This code constructs the Amazon region and/or forest as an issue of economic integration.
 It advances the view that the Amazon needs to be developed and connected to the national economy.
@@
 Simple mentions of development, integration, investment, and technology are not automatically coded as economic integration.
-However, direct mentions of the words “economic development” are coded here.
-We avoid overlap between this code and social development by considering integration references as targeting infrastructure rather than peoples’ rights.
+However, direct mentions of the words "economic development" are coded here.
+We avoid overlap between this code and social development by considering integration references as targeting infrastructure rather than peoples' rights.
 For example, developing infrastructure for internet, radio, and energy are coded as economic integration.
-However, if the presidents speak about people’s access and rights to information (internet and radio) and electricity, we code as social development.
-Relatedly, improving macro-structural conditions of the job market is coded as economic integration,, while people’s right to a dignified job is coded as social development.
+However, if the presidents speak about people's access and rights to information (internet and radio) and electricity, we code as social development.
+Relatedly, improving macro-structural conditions of the job market is coded as economic integration,, while people's right to a dignified job is coded as social development.
 Importantly, we make the analytical choice to include micro-finance instruments as credits and loans in economic development, while grants or donations fall within social development.
@@
 Nós, na Amazônia, estamos fazendo uma ligação que passa por Manaus, passa por Boa Vista, Caracaraí, até chegar lá em cima, que é aquela lista vermelha, que vai lá para cima, na direção da Venezuela,é a estrada 174.
-Essa estrada dará possibilidade da produção da Zona Franca de Manaus ser competitiva, não aqui dentro, mas lá fora mesmo, como é a vocação natural da Zona Franca, exporte, e poderá exportar pelo Caribe.” (FHC 2/7/1997)
-Social Development
-Description: This code constructs the Amazon region and/or forest as an issue of social development.
+Essa estrada dará possibilidade da produção da Zona Franca de Manaus ser competitiva, não aqui dentro, mas lá fora mesmo, como é a vocação natural da Zona Franca, exporte, e poderá exportar pelo Caribe." (FHC 2/7/1997) Social Development Description: This code constructs the Amazon region and/or forest as an issue of social development.
 It advances the view that Amazon is full of citizens who should have their rights guaranteed.
@@
 Simple mentions to development are not automatically coded as social development.
-However, direct mentions supporting “social development” are coded here.
+However, direct mentions supporting "social development" are coded here.
 An illustrative example relates to speeches outlining the role of the armed forces in providing health services for faraway populations, which we code as social development but not sovereignty.
 
-Example: “Mas como o Estado não tem que ter lucro, o Estado precisa garantir a cidadania, nós achamos que o cidadão que mora às margens do rio Amazonas, a 600 Km de Manaus, ele tem que ter direito a ter luz na sua casa, a ter geladeira, a ter televisão e a ver sua novela.
+Example: "Mas como o Estado não tem que ter lucro, o Estado precisa garantir a cidadania, nós achamos que o cidadão que mora às margens do rio Amazonas, a 600 Km de Manaus, ele tem que ter direito a ter luz na sua casa, a ter geladeira, a ter televisão e a ver sua novela.
 Já investimos 14 bilhões de reais nesse programa, em três anos e meio.
 Sabe quantos postes nós já colocamos?
-Um milhão de quilômetros de fio.” (Lula 20/11/2009)
-Conservation
-Description: This code constructs the Amazon region and/or forest as an issue of conservation.
+Um milhão de quilômetros de fio." (Lula 20/11/2009) Conservation Description: This code constructs the Amazon region and/or forest as an issue of conservation.
 This narrative focuses on the value of a standing forest and of the preserved ecosystem in the region.
@@
 
-Example: “Adotei medidas de caráter emergencial, suspendi a exportação de madeiras em toras, suspendi incentivos fiscais e creditícios na Amazônia a projetos que podiam causar danos ambientais e instituí a obrigatoriedade do licenciamento para a atividade de extração de ouro com a proibição da utilização do mercúrio.
+Example: "Adotei medidas de caráter emergencial, suspendi a exportação de madeiras em toras, suspendi incentivos fiscais e creditícios na Amazônia a projetos que podiam causar danos ambientais e instituí a obrigatoriedade do licenciamento para a atividade de extração de ouro com a proibição da utilização do mercúrio.
 Dando início à reestruturação do sistema governamental de controle e preservação do meio ambiente, criei o Instituto Brasileiro do Meio Ambiente e Recursos Naturais, IBAMA, que está entregue à capacidade do Dr.
-Fernando César Mesquita.” (Sarney, 20/7/1989)
-False positive
-Description: statements that were assigned as Amazonian but are about the Amazon.
-
-Example: “cumprimentar os presidentes de bancos publicos do banco do brasil alexandre abreu do bndes luciano coutinho da caixa miriam belchior do banco do nordeste marcos costa holanda do banco da amazonia valmir pedro rossi o vicepresidente do banco do brasil cesar borges da diretoria de infraestrutura queria cumprimentar as senhoras e os senhores dirigentes de agencias reguladoras dirigir um cumprimento especial ao senhor robson andrade presidente da confederacao nacional da industria por intermedio de quem cumprimento todos os empresarios das federacoes aqui presentes” (Rousseff, 9/7/2015)
+Fernando César Mesquita." (Sarney, 20/7/1989) False positive Description: statements that were assigned as Amazonian but are about the Amazon.
+
+Example: "cumprimentar os presidentes de bancos publicos do banco do brasil alexandre abreu do bndes luciano coutinho da caixa miriam belchior do banco do nordeste marcos costa holanda do banco da amazonia valmir pedro rossi o vicepresidente do banco do brasil cesar borges da diretoria de infraestrutura queria cumprimentar as senhoras e os senhores dirigentes de agencias reguladoras dirigir um cumprimento especial ao senhor robson andrade presidente da confederacao nacional da industria por intermedio de quem cumprimento todos os empresarios das federacoes aqui presentes" (Rousseff, 9/7/2015)
 
@@
 Inter-coder agreement for each of the four main categories was 85%, on average.
-Most of the disagreements were on economic integration versus social development and related to the difference in emphasizing infrastructure versus emphasizing peoples’ rights.
+Most of the disagreements were on economic integration versus social development and related to the difference in emphasizing infrastructure versus emphasizing peoples' rights.
 For each non-matching code, the co-authors discussed and sorted their disagreements to finalize the putting together a training set so that a supervised machine-learning model classifies the rest.
@@
 
-Accuracy
-AUC
-False Positives
-0.946
-0.69
-Sovereignty
-0.866
-0.59
-Economic Integration
-0.678
-0.68
-Social Development
-0.792
-0.66
-Conservation
-0.802
-0.78
+Accuracy AUC False Positives 0.946 0.69 Sovereignty 0.866 0.59 Economic Integration 0.678 0.68 Social Development 0.792 0.66 Conservation 0.802 0.78
 

### 2022-04-12 Draft_April_2022/Full_draft_20220401.rmd
#weaved in new text for all but 4.3 #still knitting to pdf

@@
 author:
-- Livio Silva-Muller^[Phd Candidate, The Geneva Graduate Institute , livio.silva@graduateinstitute.ch]
-- Henrique Sposito^[Phd Candidate, The Geneva Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
+- Livio Silva-Muller
+- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically.
+Both of them are PhD candidates at The Geneva Graduate Institute.
+Livio is affiliated to the Albert Hirschman Centre on Democracy.
+Henrique is affiliated to the Centre for International Environmental Studies.]
 date: "April 2022"
 output:
+  pdf_document: default
   html_document:
@@
     reference_docx: template.docx
-  pdf_document: default
+always_allow_html: TRUE
 bibliography: references.bib
@@
 
-The Amazon needs to be protected from foreign interests.
-The Amazon needs to be exploited for its natural resources.
-The Amazon needs to be preserved as a standing ecosystem.
-Historically, different Brazilian federal government proposed diverse policies to deal with the Amazon.
-Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the region, the forest, or its peoples as a particular problem.
-In the three examples above, the Amazon is represented as an issue of national sovereignty, economic integration, and environmental conservation, respectively.
-Each of these constructions, and their proposed solutions, have been described as policy cycles of Brazilian governments [@acker2014; @hecht1990; @hochstetler2007].
+We need to protect the Amazon from foreign interests.
+We need to exploit the Amazon's natural resources.
+We need to provide better living standards for the people living in the Amazon.
+We need to preserve the Amazon as a standing ecosystem.
+Historically, the Brazilian federal government proposed diverse policies to deal with the Amazon.
+Each of these policies contain an implicit assumption of what needs to be solved, or in other words, it represents the Amazon region, the forest, or its peoples as a particular problem.
+In the four examples above, the Amazon is represented as an issue of national sovereignty, economic integration, social development, or environmental conservation.
+Some of these constructions, and their proposed solutions, have been described within policy cycles of Brazilian governments [@acker2014; @hecht1990; @hochstetler2007].
 However, policy cycles are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of only one specific problem.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem over time, by geographical location, and between and within governments
+Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between and within governments.
 
 In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify how problem-construction.
+Building on @hirschman1963 concept of chosen problems in policy making, we propose a framework to identify problem-constructions in political discourses.
 Although problem-construction takes place in a series of instances (e.g.
-policy committees, legislative bodies, media, etc.), we analyze the case of political discourse by Brazilian presidents since 1985.
-We opt for presidential speeches for three reasons.
-First, political discourses at the top have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+policy committees, legislative bodies, media, etc.), we analyze the case of discourses by Brazilian presidents since 1985.
+We opt for presidential speeches for two reasons.
+First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004]).
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-The literature has shown that deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon, from investors to agribusiness to local farmers.
+Deforestation rates in Brazil are more responsive to the government's environmental policy than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
+Ethnographic research has also shown that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@campbell2015].
 Thus, understanding how policy comes about discursively is important.
-Second, environmental discourse at the top can help expand or restrict what types of behaviors are accepted in the ground.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally[@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon, from investors to agribusiness to local farmer.
-This is especially pertinent for deforestation as previous research found that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground [@capobianco2019; @campbell2015].
-Unpacking discourse at the top might help us raise hypotheses about environmental outcomes that are culturally situated.
-Finally, as our theoretical framework suggests, problem-construction varies by geographic location.
-Presidential discourses take place in a series of sites with diverse audiences: from launching a new bridge in a small municipality in the middle of the Amazon, to a keynote speech in a business association in São Paulo, to the UN general assembly in New York.
+Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context.
+Problem-construction varies by geographic location.
+Presidential discourses take place in a series of sites with diverse audiences, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York.
 Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
@@
 We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
-Using R, we then train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
+Using R, we train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
 We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.
@@
 Our findings are threefold.
-First, endogenous events as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhaguen Summit, the 2015 Paris Summit, and the 2021 London Summit drive generally the interest in the Amazon.
-That seems to be the case even after controlling share of annual speeches mentioning the Amazon for deforestation, inflation, and speaker.
+First, events such as the death of Chico Mendes, the 1992 Earth Summit, the 2009 Copenhagen Summit, the 2015 Paris Summit, and the 2021 London Summit drive presidents to speak about the Amazon.
+That seems to be the case even after controlling the share of annual speeches mentioning the Amazon for deforestation, inflation, and president speaking.
 Second, there was a sharp decrease in economic related problem-constructions from the late 1990 to 2010, matched by an increase in speeches that construct the Amazon as a problem of social development and environmental conservation.
-This trend is reversed in the late 2010s, with the twist of sovereignty making a strong comeback.
-Finally, using a multinominal model, we find that the farthest away the speaker is from the Amazon, be it within the country in non-Amazonian States or outside Brazil, the more likely the speaker is to construct the Amazon as a problem of environmental conservation than economic integration or social development.
+This trend was reversed in the mid-2010s, with sovereignty making a strong comeback.
+Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move farther away from the Amazon.
 
@@
 
-## 2.1 Literature Review: policy-cycles in the Amazonian literature
-
 For the purposes of this article, we understand Amazonian literature as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.
@@
 
+## 2.1 Literature Review: policy-cycles in the Amazonian literature
+
 ### 2.1.1 National sovereignty
@@
 In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites" [-@hecht1990, pp.1].
-It started with the first natural history of the New World, by Oviedo in 1535, who recounts the stories of conquest of local populations and gold hoarders.
-The dream of fortunes to be found in the Eldorado composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else.
+These dreams of fortunes to be found in the Amazon composed the imaginaries of *bandeirantes*[^1] from the southeast of Brazil and colonizers from everywhere else.
 It rendered the territory the venue for aspiration and object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" (Hecht and Cockburn 1990, preface).
@@
 While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil[@hecht1990].
+A significant experience were the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil [@hecht1990].
 This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War[@garfield2013].
@@
 
-The sovereignty problem advances the view that the Brazilian Amazon is Brazilian and foreign presence, non-state presence and alleged lies are part of a broader strategy to internationalize the region.
-The policy solutions relate to close monitoring of the borders, strict regimes related to entry in the region, and combating alleged disinformation about the Amazon nationally and internationally.
+As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
+Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
+Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
+Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
+This might come both from foreign actors as well as domestic non-state actors.
+Relatedly, mentions of Amazonian myths which have been debunked as the 'Earth of the Lungs', are also tied to internationalizing strategies.
+
+The sovereignty policy-cycle in the Amazon advances the view that the Brazilian Amazon belongs to Brazil while any foreign or non-state, presence in the region is part of a broad strategy to take the region.
+The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combatting alleged disinformation from actors perceived as a threat.
 
@@
 Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, as well as establishing tax free zones to attract industry.
+Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, and establishing tax free zones to attract industry.
 The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
@@
 The economic integration problem advances the view that the Brazilian Amazon needs to be developed and modernized.
-The policy solution relates to the creation of a series of policies, often centralized by the federal government and thus external to the region [@becker2005], that have at its core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.
+This policy solutions are often centralized by the federal government [@becker2005] and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region in the national and international economy.
 
@@
 The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions such as the New Forest Code (1964), the Secretary of Environment (1973), and the National Environment Law (1980) [@drummond2006].
-A common explanation for these institutions in the Amazonian literature is the impression of lack of control after years of centalized economic integration policies [@acker2021; @capobianco2021; @hecht1990].
-As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of an environmental bureaucracy.
-This process accelerated in the late 1980s, with the birth of modern environmentalism epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
+A common explanation for the creation of these institutions in the Amazonian literature is the impression of lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
+As deforestation, fires, and violence rose in the region, catching international attention, the military government deemed as necessary the establishment of environmental bureaucracies.
+This process accelerated in the late 1980s, with the birth of modern environmentalism [@viola1987] in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
 @hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
@@
 
+While policy cycle periods in Amazonian literature have been widely adopted, there is more variation in Amazonian problems and policies than the literature suggests.
 Different authors have proposed similar periodization for policy-cycles in the Amazon: a focus on sovereignty until the military dictatorship of 1964, followed by strong economic integration policies until the mid 1980s, and finally a shift to conservation after the 1992 Earth Summit.
@@
 Nevertheless, at the level of policies adopted, there is more variation than these periods would suggest.
-For example, the 1980 Programa Calha Norte did contain elements to ensure sovereignty, integrate the region to the country's economy, and preserve the forest.
+For example, the 1980 Projeto Calha Norte had as objectives to protect the borders, integration of the region, and preservation of the forests.
 Framing this policy as an issue of economic integration, then, can be seen as a choice.
-
 Hence, while the literature might represent governments as coherent proponents of a particular policy retroactively, political actors might have adopted strategies that outline problem-constructions of policies differently.
@@
 We largely agree with what the literature assigns to previous governments.
-However, the possibility of varied portrayals of the same policy opens up an understanding agenda-setting and policy-adoption that is less linear.
+However, the possibility of varied portrayals of the same policy opens an understanding agenda-setting and policy-adoption that is less linear.
 
@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations [^2], we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
@@
 
-[^2]: For an overview on how inflation and political discourse in Brazil see Porto (2007), Malheiros-Poulet (2012), and Fonseca et al.
-(2021).
-For a few studies on racist and anti-racist discourses in Brazil see Htun (2004), Silva and Larkins (2019) and Dijk (2020).
+Problem-construction at the level of discourse is also more varied.
+They are not monolithic in time, across location, or even by the same speaker.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations [], we only find one systematic analysis of Amazonian discourse.
+@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
+The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
 
-We also find several analyzes of environmental discourse in American presidential speeches.
+Alternatively, several studies analyze environmental discourse in American presidential discourses.
 @calderwood2019 examines 2919 mentions of climate change in American official presidential speeches since 1989.
-Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change (ibid).
+Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change.
 He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-In another article, @calderwood2020 tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988 but also others, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on climate change does change based on location.
-Another example is @bevitori2015, who investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
+@calderwood2020 also tests the effect of geographic location and type of communication regarding climate change.
+Building prominently on @putnam1988, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
+He finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location.
+Elsewhere, @bevitori2015 investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
 The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
 
-While these findings hold for the US, they suffice to argue that presidents can raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance.
+While these findings are US specific, they indicate that presidents raise different points about the Amazon at local, national, or international settings, depending on who they assume their audience is at that specific instance.
 That entails the same president can combine, substitute, or change how they talk about the Amazon and these views can reflect, or not, the current political scenario, issues in the agenda, or talk to a different policy cycle at times.
@@
 
-In "Journey towards Progress", Hirschman (1963) analyzes three policy problems in three different Latin American countries.
+In "Journey towards Progress", @hirschman1963 analyzes three policy problems in three different Latin American countries.
 The author draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
-Pressing problems can be either privileged or neglected depending on the degree of pressure exercised by the interested group.
-Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, changing level of government control in society, or top policymakers shifting interests [@hirschman1963, pp.388-91].
+Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested group.
+Problems can change from pressing to chosen across time and in space as a function of solutions becoming available, a change of level of government control in society, or a shift of interests from top policymakers [@hirschman1963, pp.388-91].
 Choosing a problem, though, entails a decision on how to represent it [@bacchi2009].
-As Bacchi puts "policy has a cultural dimension.
-It takes shape within specific historical and national or international contexts" [-@bacchi2009, pp.10].
+As Bacchi argues, policies have a cultural dimension as "it takes shape within specific historical and national or international contexts".
+[-@bacchi2009, pp.10].
 The existence or proposal of a policy generally implies that there is a (public) problem that needs (governmental) action to be fixed.
@@
 Hirschman exemplifies chosen problems with the case of the construction of Brasilia [-@hirschman1975, pp.388].
-But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
-How to represent a policy is a matter of choice.
-And different representations speak to different audiences.
+But building Brasilia can also be constructed as solving a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
+Different representations speak to different audiences.
 
-We understand that depending on how the problem is represented to be, it can be a solution of problems that are considered pressing.
+Depending on how the problem is represented to be, it can be a solution of problems that are considered pressing.
 Different problem-constructions can address the demands of different constituencies and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
@@
 One avenue through which governments can emphasize the representations of a problem is discourse.
-We assume that problem-construction at the level of discourse is varied.
+Working on the case of gender discourse, Pike proposes a discursive spectrum approach, where "language serves as an entry point to reveal the range and complexity of attitudes"[-@pike2019, pp.
+287].
+Thus, we assume that problem-construction at the level of discourse is varied.
 They are not monolithic in time, across location, or even by the same speaker.
@@
 We argue that presidents can employ specific problem-constructions that build objects as specific problems depending on the context.
-In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connect the region to issues of sovereignty, economic integration, social development, or environmental conservation.
+In the specific case of the Brazilian Amazon, we contend that Amazonian problem-construction connects the region to pressing national issues such as sovereignty, economic integration, social development, or environmental conservation.
 Presidents choose to represent the region as a particular problem.
-As Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
+As @bacchi2009, we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
 Thus, the ways a president speaks are culturally and historically mediated and need to be embedded in the wider history of the region and country.
-We consider this an advancement in relation to scholars looking at American presidential speeches, as they just count mentions to climate change [@calderwood2019; @calderwood2020; @brown2017] or environment [@bevitori2015] without embedding them in the histories of the issue in the country.
 
@@
 To operationalize our theoretical framework, we adopt a mixed-methods approach using manual coding and supervised machine learning.
-We explain our research design and each step of the procedure in this section.
+We explain our research design and each step of the procedure in this section, but a full-fledged extended methodology is available in the abstract.
 
@@
 
+````{=tex}
 \begin{landscape}
@@
 \end{landscape}
+````
 
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006][^3].
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006][^2].
 After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set, we use the model to automatically code the remaining 1007 Amazonian statements.
@@
 
-[^3]: For more information on this please see the extended methodology.
+[^2]: For more information on this please see the extended methodology.
 The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the validation set.
@@
 We open with a broad overview of the evolution of the incidence of Amazon in all presidential speeches since 1985.
-In section 4.2, we focus on speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1.
+In section 4.2, we focus unpack speeches that mention the Amazon, introducing the specific problem-constructions we presented in section 2.1.
 Finally, we run a multinomial model to show how problem constructions change as the speaker moves further away from the Amazon region.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^4], economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation[^3] , economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
-These points coincide with exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
+These points coincide with events that help us explain the rises and falls of the Amazon in presidential discourse.
 
-[^4]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
+[^3]:  The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
 Nevertheless, matching deforestation with speech dates is a complicated endeavor.
@@
 For the subsequent years, the consolidated figures for a given year came out in August of the subsequent year.
-However, it also seems to be the case that the executive government have access to the data before everyone else.
-In addition, other sources indicating if deforestation is going up or down, as fire data or lower resolution deforestation data (DETER for example), or even other sources, circulated within the year the data covered.
-The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures[@fearnside1990], and a New York Times article about the issue with deforestation rates for 1988 was written with comments by an INPE scientist [@simons1988].
+However, it also seems to be the case that the executive government has access to the data before everyone else.
+In addition, other sources indicating if deforestation is going up or down, such as fire data or lower resolution deforestation data (DETER for example), or even other sources, circulated within the year the data covered.
+The year of 1988 is particularly indicative of these complications: a report dating 1988 was circulating with deforestation and fire figures [@fearnside1990], and a New York Times article about the issue with deforestation rates for 1988 was written with comments by an INPE scientist [@simons1988].
 Hence, we believe the most appropriate way of matching is without any lags on deforestation.
+
+Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
+The predicted share curve controls incidence for deforestation[^4], economic situation, and speaker (see appendix for methodological details).
+We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
+These points coincide with exogenous events that helps us explain the rises and falls of the Amazon in presidential discourse.
 
@@
 During the Cardoso years (1994-2002), Amazonian speeches averaged at about 16% without strong variation.
-There were no big international or domestic events that drove the topic up.
-At the level of policy, though, we saw the birth of the National System of Protected Areas in 2001, and of the Amazon Regional Protected Areas Program.
-While the former created the legal framework for different types of protected areas to be created, the latter established a transnational partnership to finance the implementation of protected areas in the Amazon [@andonova2014].
+There were no major international or domestic events that drove the topic up.
 
 We observe an increase from 8.5% in 2004 to 22.8% in the year of the Copenhagen Summit, 2009.
-This coincides with the Presidency of Lula and the steepest decrease in deforestation rates in Brazilian history.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" [@franchini2019], when stakes about climate change were high.
+This coincides with the Presidency of Lula and the steepest decrease in deforestation rates since data is available.
+Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” [@franchini2019], when stakes about climate change were high.
 A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
 From 2010 to 2014, we identify a steady decrease from 18.2% to 8.2%, which is followed by a sharp increase in the year of the COP, reaching 19.2%.
-These are the years when Brazil entered a long period of political and economic instability that lingers until today.
-Brazil went to the COP in Paris with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation after the 2011 Forest Code was adopted and former environmental minister Marina Silva ended her alliance with the worker's party because of disagreements related to the priority of environmental policy.
+Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for presidency on her own agenda in 2010.
+These are also the years when Brazil entered a long period of political and economic instability, which led to the impeachment of Dilma Roussef .
+Brazil went to the Paris COP with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation since Marina Silva left the government and the 2011 New Forest Code was approved.
 
-We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
-As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts, reaching unprecedented coverage.
+We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro’s presidency, 2019.
+As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts reach unprecedented coverage.
 Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019.
 President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda.
-President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
+President Bolsonaro retrieves Brazil’s hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
 
-We do find evidence that deforestation rates, economic situation, elections, and simply presidential preferences affect the incidence of Amazon in speeches: the smoothed curve portrays lower proportions overall.
-However, international events and media coverage also correlate with local maxima of our curve, suggesting presidents do speak more about the Amazon in preparation or reaction to these events.
+The local maxima of the graphs, both controlled and real, suggest that international events and media coverage also correlate with presidents speaking about the Amazon.
 We are yet to inspect, though, whether specific problem constructions about the Amazon change over time.
@@
 
-Figure 2 portrays plots with the proportions of different problem constructions over time.
-We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
-At the level of the Amazonian statement, though, presidents might mix two or more together.
-These are what we call mixed types, in opposition to pure types.
-There are 16 mix types in total, and figure 2 portrays the most frequent of them.
+Figure 2 portrays plots with the proportions of different mixed and pure problem constructions over time.
+We conceptualize four pure problem constructions: sovereignty, economic integration, social development, and conservation.
+At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement .
+These are what we call mixed types.
 Pure problem constructions dominate, with their joint average at 55.8%.
-Among the four pure types as well as the mixed types, we observe a strong variation over time, suggesting the narratives do respond differently to factors that affect Amazonian statements discussed in the section above.
+We observe a strong variation over time for most of these constructions, suggesting the narratives do respond differently to factors that affect Amazonian statements, some of which was discussed in the section above.
 
@@
 The plots reveal several trends.
-We start by pure-types.
+We start with analyzing pure types.
 Pure economic integration statements, which were dominant, decreased in incidence as of the late 1990s.
-Concurently, pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2010.
+Concurrently , pure conservation as well as pure social development increased; both surpassing the proportion of economic integration problem-construction in 2010.
+President Cardoso deemed as responsible for solving the national problem of inflation, was the main user of the economic integration problem construction.
+With the end of his presidency, environmental conservation starts increasing.
 @capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher change of being caught for illegal deforestation.
-As of the mid 2010s, we observe a reversal of the trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+This correlates with our findings: a higher incidence of the Amazon as a topic overall can generate a perception of more attention from the top, and a shift from economic integration to conservation can generate a perception of higher chance of being caught for illegal deforestation.
 
-Figure 3 (below) shows these shift and reversal more clearly and highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
-Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration appears the most, in detriment of social development and environmental conservation.
-The starkest decrease relates to social development construction between Temer's and Bolsonaro's administration.
+As of the mid 2010s, we a reverse of this trend with a twist: economic integration starts picking up again in detriment of conservation and social development problem constructions, but with sovereignty increasing steadily.
+Figure 3 (below) shows these shifts and reversal more clearly.
+It highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula’s presidential mandate.
+Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration reaches their actual maximum and a new local maximum (respectively).
 
@@
 
-We now move to mixed types, which average at 17.7% for all presidents in our sample: overall, presidents prefer pure problem-constructions.
+We now move to mixed types, which average at 17.7% for all presidents.
+Overall, presidents prefer pure problem-constructions.
 While there is some variation in time for each single mixed type, some of them have low counts and interpretations are not adequate.
 We focus our discussion on those with higher incidence.
-First, the most frequent mix overall is that of economic integration with environmental conservation, which averages at 29.15% in relation to mixed types only, and at 6.8% in relation to all Amazonian statements.
-Overall, we observe an increase along time, reaching its pike in the early 2010.
+First, the most frequent mix overall is that of economic integration with environmental conservation, which averages at 29.15% in relation to mixed types only, and at 6.8% in relation to all problem-constructions.
+We observe an increase in time, reaching its peak in the early 2010.
 President Dilma was the most frequent user of this mix.
@@
 
+We interpret the appearance of mixed types as more complex understandings of Amazonian problems.
 All other mixed types appeared less than 2.6% on average in relation to all statements.
-We can also interpret mixed types, though, by looking at what compose them the most along time.
+We can also interpret mixed types, though, by looking at what composes them time.
 Mixed types using conservation were quite frequent in the lead up and aftermath of the 1992 Earth Summit.
 This includes the mix type we label sustainable development, which constructs the Amazon as a problem of economic integration, social development, and environmental conservation.
-We interpret the appearance of mixed types as more complex understandings of Amazonian problems.
 This follows a global agenda of understanding interconnections of social, environmental, and economic domains.
-As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas as Millennium Development Goals and the Sustainable Development Goals.
-Nevertheless, as in pure types, we also observe the comeback of sovereignty being used in mixed types, mostly in detriment of conservation social development.
-This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions 11% above presidential averages: 29.4% and 31.3% respectively.
-While the former frequently mixed conservation with other problem constructions, the latter prefers mixing with sovereignty.
-The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types.
+As we show that Amazonian incidence in discourse does respond to global issues, this is not a surprise given agendas such as the Millennium Development Goals and the Sustainable Development Goals.
 
@@
 
-@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
-Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
-The costs for said economic and political benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
-Political stability, thus, can be seen as a product of the trade-off between both.
-Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy.
-With the strengthening of environmentalism in the 1990s, its most strong form being the policies adopted in the 2000s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
-
-While unprecedented, this new balance was not long-standing.
-Democratic decay is slow and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation related statements in the mid 2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3) .
-The hard increase in sovereignty comes in the early 2010s.
-As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.
-At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
-
-This is not to say that those who preceded President Bolsonaro are like him.
-They are not, and we have shown how he is different from others already.
-But the political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro's problem-construction is the strongest form of this shift.
-Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+We also observe the comeback of sovereignty being used in mixed types, mostly in detriment of conservation social development.
+This becomes more apparent in a comparison between Lula and Bolsonaro, the two presidents that mix the most with proportions more than 11% above presidential averages: 29.4% and 31.3% respectively.
+While the former frequently mixed conservation with other problem constructions, the latter prefers mixing with sovereignty.
+The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types.
+Now that we’ve inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
 
@@
 
-# 5 Discussion
+# 5 Discussion: The Amazon frontier, environmentalism, and democracy
+
+@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
+Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
+The costs for said economic benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
+Political stability, thus, can be seen as a product of the trade-off between both.
+Policies during the military dictatorship were strongly geared towards integrating the Amazon to the national territory and international economy.
+These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted.
+Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that [@hecht1990].
+
+The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse in Amazonian States compared to Brasilia and other States.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what “they want to hear”.
+If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
+Or, as @putnam1988 puts, what’s the actual overlap between international and domestic overlap.
+The domestic policies and transnational support that led to the decrease of deforestation from 2004 to 2012 happened concurrently to a period of strong economic growth and social development in Brazil and worldwide.
+With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration and the rise of social and conservation problem constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
+
+While unprecedented, this new balance was not long-standing.
+Democratic decay is slow, and the embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
+We observe the decrease in conservation related statements in the mid 2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3).
+The hard increase in sovereignty comes in the early 2010s.
+As we conceptualize and operationalize sovereignty as boundary-making vis-à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks to indigenous and traditional populations.
+At the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code are seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
+The political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
+Bolsonaro’s problem-construction is the strongest form of this shift.
 
@@
 
-## Extended Methodology
-
-This appendix details the methodology employed by the authors in the article.
-
-## The Dataset
-
-We update a dataset provided by Cezar (2020), which builds upon the archives of the Brazilian Presidential Library.
-The dataset contains all official remarks by Brazilian Presidents from 1985 to 2019.
-We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches.
-Overall, it covers a total of 8 presidents (Sarney, Collor, Franco, Cardoso, Silva, Rousseff, Temer, and Bolsonaro) across 8 mandates (Collor and Dilma were impeached and vice presidents Franco and Temer took over).
-
-We start by cleaning the dataset by removing all accents, non-standard Latin characters, and extra spaces.
-We then identify all speeches about the Amazon as a region, peoples, or forest out of the 6130 speeches.
-Our dictionary is composed of a single lexicon stem: "amazon".
-In Portuguese, it captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says "the forest" or uses a pronoun, he or she could be referring to the Amazon.
-Also, it is likely that whenever a president mentions "deforestation" or derived vocabulary, he or she is speaking about the Amazon.
-However, as we cannot be sure all the time in those instances (i.e.
-mentions of "the forest" or "deforestation" could be referring to the Atlantic Forest or the Cerrado).
-We opt for the safer side and make sure speeches we gather are indeed about the Amazon as a region, forest, or people by only capturing "amazon" related lexicon.
-We find that 946 speeches are, at least partially, about the Amazon from the 6130.
-
-Using the poldis R package, we extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-By doing so we create our unit of analysis: an Amazonian statement.
-We use Amazon statements as our unit of analysis for three main reasons.
-First, presidential speeches can be long and cover a wide variety of topics.
-For example, the average word count for speeches that mention the stem "amazon" are 2355 words.
-Working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-A single speech can have more than one Amazonian statement and this statement might be embedded within a different part of the speech.
-Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
-Finally, other authors adopting similar strategies, opt for picking an arbitrary number of words before and after the mention (Kentikellenis and Voeten, 2021).
-We opt for picking two sentences before and two sentences after, rather than words because a sentence, because sentences usually contain a cohesive idea.
-Opting for a word threshold, might cut a sentence in the middle and yield an incomplete idea.
-Nevertheless, this process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified previously.
-Notice that an Amazonian statement can contain two or more matches of the stem "amazon" (i.e.
-two consecutive sentences in which one of the words covered by the stem appears).
-In this case, we get two sentences before the first match and two sentences after the last match.
-On average, an Amazonian statement contains 123 words.
-
-## Operationalization
-
-We proceed to operationalize how the Amazon is constructed as a problem.
-To do so, we develop and apply a qualitative codebook to Amazonian statements.
-We do so for two reasons.
-First, and foremost, we believe that a dictionary and other "bag of words" methods might not capture nuances in the texts.
-These nuances include Amazonian statements that negate certain aspects about the Amazon or statements in which the matched words might not be not directed at the Amazonian region, peoples, or forest.
-Second, we chose to look at the statements and inductively develop a codebook to verify if the insights from the literature hold within presidential speeches and, if not, add or remove codes, as well as discuss which statements should, and not, be included in each code and why.
-
-After revising the literature (section 2), we went through a random sample of the speeches to develop the codebook.
-The three policy-cycles (sovereignty, economic integration, and conservation) were clearly identifiable in the speeches.
-However, once the coding began to take place, however, we noticed two things.
-One, that some of the Amazon statements were not about Amazon per se.
-That is, our strategy to identify Amazonian statements yielded a few false positives.
-These are statements that mention the stem "amazon", but are not about the Brazilian Amazon region, people, or forest.
-For example, the president might greet the Governor of the Amazonas in a speech or make a reference to the Venezuelan Amazon.
-We coded these statements as false positives.
-Two, we noticed speeches often refer to social development using a different vocabulary of policies and objectives.
-Those references often differ from references to conservation or economic integration.
-Hence, we created the code category 'social development' as explained below.
-We consider this to be a finding, but rather than emerging from our analysis, it emerged from codebook development.
-contain a full description of each code category and the coding practices that inform our procedure.
-
-Table 1 -- Qualitative Codebook
-
-Sovereignty Description: This code constructs the Amazon region and/or forest as an issue of national sovereignty.
-We understand claims of sovereignty as a particular narrative that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as a particular narrative that raises concerns about wrong perspectives and criticism from foreign and non-state actors about governments' actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian and foreign presence in the region needs to be monitored closely.
-
-Coding practice: we apply this code to references to sovereignty that meaningfully reflect the description above.
-Simple mentions to the Brazilian Armed Forces, frontiers, or military technology (e.g.
-SIPAM-SIVAM), are not automatically, by themselves, understood as constructing the Amazon as a problem of sovereignty.
-When presidents question the authority or interests of someone's arguments about Amazon, for example, we apply this code as it raises concerns about wrong perspective and criticism.
-When presidents claim external actors want to internationalize the Amazon territory, we apply this code as it touches upon external threats to territory.
-
-Example: "Senhores deputados.
-Elo fundamental para que o Brasil realmente rume em direção à prosperidade.
-Queria primeiro dizer, senhor Hu Chunhua, eu quero agradecer as palavras do seu embaixador no Brasil reconhecendo a nossa soberania sobre a região Amazônica, no episódio ocorrido há pouco, por ocasião do encontro do G7.
-Muito obrigado ao governo chinês.
-Para nós, não têm preço esse reconhecimento público e suas palavras sobre essa região tão importante para o mundo e para o Brasil." (Bolsonaro 25/10/2019) Economic Integration Description: This code constructs the Amazon region and/or forest as an issue of economic integration.
-It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.
-
-Coding practice: We apply this code to references to economic integration that meaningfully reflect the description above.
-Simple mentions of development, integration, investment, and technology are not automatically coded as economic integration.
-However, direct mentions of the words "economic development" are coded here.
-We avoid overlap between this code and social development by considering integration references as targeting infrastructure rather than peoples' rights.
-For example, developing infrastructure for internet, radio, and energy are coded as economic integration.
-However, if the presidents speak about people's access and rights to information (internet and radio) and electricity, we code as social development.
-Relatedly, improving macro-structural conditions of the job market is coded as economic integration,, while people's right to a dignified job is coded as social development.
-Importantly, we make the analytical choice to include micro-finance instruments as credits and loans in economic development, while grants or donations fall within social development.
-
-Example: "Se me permitem, na Amazônia -que durante tanto tempo ficou adormecida, por falta de uma ação integrada- nós temos já algumas ações muito estruturadoras.
-Nós, na Amazônia, estamos fazendo uma ligação que passa por Manaus, passa por Boa Vista, Caracaraí, até chegar lá em cima, que é aquela lista vermelha, que vai lá para cima, na direção da Venezuela,é a estrada 174.
-Essa estrada dará possibilidade da produção da Zona Franca de Manaus ser competitiva, não aqui dentro, mas lá fora mesmo, como é a vocação natural da Zona Franca, exporte, e poderá exportar pelo Caribe." (FHC 2/7/1997) Social Development Description: This code constructs the Amazon region and/or forest as an issue of social development.
-It advances the view that Amazon is full of citizens who should have their rights guaranteed.
-This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
-This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.
-
-Coding practice: We apply this code to references to social development that meaningfully capture the description above.
-Simple mentions to development are not automatically coded as social development.
-However, direct mentions supporting "social development" are coded here.
-An illustrative example relates to speeches outlining the role of the armed forces in providing health services for faraway populations, which we code as social development but not sovereignty.
-
-Example: "Mas como o Estado não tem que ter lucro, o Estado precisa garantir a cidadania, nós achamos que o cidadão que mora às margens do rio Amazonas, a 600 Km de Manaus, ele tem que ter direito a ter luz na sua casa, a ter geladeira, a ter televisão e a ver sua novela.
-Já investimos 14 bilhões de reais nesse programa, em três anos e meio.
-Sabe quantos postes nós já colocamos?
-Um milhão de quilômetros de fio." (Lula 20/11/2009) Conservation Description: This code constructs the Amazon region and/or forest as an issue of conservation.
-This narrative focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous peoples should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created.
-
-Coding practice: We apply this code to references to conservation that meaningfully capture the description above.
-Simple mentions of biodiesel, renewable energies, climate change, or sustainable development are not automatically coded as constructing the Amazon as a conservation problem.
-However, calls for more demarcation of territory are coded as constructing the Amazon as a conservation problem.
-While general references to tourism are coded as economic integration, references to eco-tourism are coded here.
-
-Example: "Adotei medidas de caráter emergencial, suspendi a exportação de madeiras em toras, suspendi incentivos fiscais e creditícios na Amazônia a projetos que podiam causar danos ambientais e instituí a obrigatoriedade do licenciamento para a atividade de extração de ouro com a proibição da utilização do mercúrio.
-Dando início à reestruturação do sistema governamental de controle e preservação do meio ambiente, criei o Instituto Brasileiro do Meio Ambiente e Recursos Naturais, IBAMA, que está entregue à capacidade do Dr.
-Fernando César Mesquita." (Sarney, 20/7/1989) False positive Description: statements that were assigned as Amazonian but are about the Amazon.
-
-Example: "cumprimentar os presidentes de bancos publicos do banco do brasil alexandre abreu do bndes luciano coutinho da caixa miriam belchior do banco do nordeste marcos costa holanda do banco da amazonia valmir pedro rossi o vicepresidente do banco do brasil cesar borges da diretoria de infraestrutura queria cumprimentar as senhoras e os senhores dirigentes de agencias reguladoras dirigir um cumprimento especial ao senhor robson andrade presidente da confederacao nacional da industria por intermedio de quem cumprimento todos os empresarios das federacoes aqui presentes" (Rousseff, 9/7/2015)
-
-Each code is mutually exclusive in its conceptualization, meaning that they cover different forms of constructing the Amazon as a problem.
-Each Amazonian statement, though, might be assigned to one or more codes.
-A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration or a problem of social development and conservation, and so on.
-Amazonian statements, thus, can be either coded as a single code (ideal types) or one or more codes (mixed types).
-
-With this codebook in hands, then, each one of us manually coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazon Statements identified.
-We coded all statements separately from each other, following inter-coder reliability procedures.
-After reading a statement, we assigned the value of one or zero to each one of the four code categories in table 1.
-Inter-coder agreement for each of the four main categories was 85%, on average.
-Most of the disagreements were on economic integration versus social development and related to the difference in emphasizing infrastructure versus emphasizing peoples' rights.
-For each non-matching code, the co-authors discussed and sorted their disagreements to finalize the putting together a training set so that a supervised machine-learning model classifies the rest.
-
-## Supervised Machine-Learning
-
-We use this hand-coded set to train a model that codes the remaining Amazonian statements in our text corpus using R.
-To select the best approach, we use the hand-coded data to compare how several supervised-machine learning methods perform in identifying false positive observations from the training set.
-To do so, we do some simple text pre-processing in R such as removing stopwords, punctuations, signs, and empty spaces using the TM package.
-Then, we split the hand coded sample into a randomly selected training set and a validation set.
-The training set contains 80% of the observations in the hand-coded sample (806 observations) while the validation set contains the other 20% of the observations (201 observations).
-
-We use this training set to train models support-vector machine( SVM) models to label text data on the validation set.
-Table 2, below, describes how the model performs in labeling observations in the validation set in regard to accuracy and AUC scores (Area Under the Curve)..
-The SVM training algorithm is a non-probabilistic binary linear classifier that classifies documents by assigning points in mapped space to maximize the width of the gap between categories (Meyer et al.
-2021).
-SVM is a particularly appropriate machine-learning algorithm for binary text labeling since it relies on maximizing distances between two categories (see also Noble 2006).
-We rely on the e1071 package to run the SVM model due to its flexibility in regard to parameter choices and because it helps users tune parameters to better fit the label patterns in the text data.
-Once the model parameters are tuned to better fit the patterns for each code, we expect the model to perform considerably better in labeling the remaining 1007 statements automatically.
-
-Table 2 - SVM Model Performance
-
-Accuracy AUC False Positives 0.946 0.69 Sovereignty 0.866 0.59 Economic Integration 0.678 0.68 Social Development 0.792 0.66 Conservation 0.802 0.78
-
-After the SVM models are tuned, the probability that a certain Amazonian statement belongs to a code category is returned.
-Statements that have a probability of 0.45 or more of belonging to a code category are labeled 1 (i.e.
-belonging to a category) and statements that have a probability of 0.45 or less of belonging to a code category are labeled 0 (i.e.
-not belonging to a category).
-We find that a 0.5 threshold can be too strict while a 0.4 may generate a few false positives and, for this reason, we set the threshold at 0.45.
-The final trained models excel to label observations in some categories in comparison to others.
-We also take a random sample of 101 (10% of the automatically labeled Amazonian statements to check how the model performed.
-We find that the model performs much better than the metrics above appear to indicate in comparison to how the authors would hand code these observations.
-The final models automatically label, out of the remaining 1007 statements, 84 statements as sovereignty, 437 as economic integration, 186 as social development, and 300 as conservation.
-The model also identified 41 false positive Amazon statements out of the 1007 labeled.
-Moreover, the proportions of the automatically labeled Amazonian statements for all categories in regard to the number of observations in the set, including observations that were not labeled but were not false positives (i.e.
-others), are similar to the proportions of the coded statements for the hand coded training set.
-
-After merging the data altogether for analysis, we chose to delete the false positive Amazonian statements for analysis since these are not meaningful statements about the Amazon as a forest, peoples, or region.
-In total there were 119 false positives out of the 2014 Amazonian statements.
-The final dataset for analysis contains 1895 Amazonian statements.
-Out of these, 237 statements are labeled as national sovereignty, 810 as economic integration, 418 as social development, and 567 as environmental conservation.
-We then added metadata about each of the speeches from which these Amazonian statements were taken from.
-The metadata includes variables such as the president (speaker), the year, the speech title, and the full text for the broader speech.
-Lastly, we use poldis once again to extract locations from texts.
-These locations can represent the Brazilian state in which certain speech was given, or international country or forum (e.g.
-United Nations).
-
 ## Multinomial Modeling
-
-To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves.
-To test whether different problem constructions change according to location, we run a multinomial regression model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-We code 4 different location categories for where speeches take place, they are: Amazonian states, non-Amazonian states, Brasilia, and International.
-In the model, we also control for annual deforestation rates, annual inflation rates, and election years in the model as these are variables which could mitigate the correlations between problem construction and location.
-Annual deforestation rates data were taken from the Satellite Monitoring of Deforestation Program (PRODES).
-However, since annual deforestation rates are calculated from 1988, we input the rates of 1988 to 1985, 1986, and 1987 because these rates are consistent with most estimates (see Prates and Bracha 2010).
-The average annual inflation data is taken from the Worldwide Inflation Data.
-Election years are input as a dummy variable in which election years are marked 1 and non-election years are marked 0.
-After the model is run, post estimation tests such as the Chi-square test shows us that the model selected is highly statistically significant in explaining variance in data in comparison to a null model (i.e.
-our model explains a considerable amount of the variance).
-The likelihood ratio test also shows that the model does not suffer with issues of multicollinearity.
 
@@
 ```
-
-## Limitations
-
-These procedures come with its limitations.
-Our codebook is developed using specific Amazon related vocabulary.
-For example, a statement will be coded as economic integration if it is a meaningful support to the Zona Franca of Manaus or a Dam in the Amazon.
-However, the economy is generally a topic that presidents speak about.
-Hence, high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
-Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
-Nevertheless, our dataset covers only what is considered an official remark.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently start to appear in social media.
-Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.

### 2022-04-13 Draft_April_2022/Full_draft_20220401.rmd
added bar plot for multinomial regression and missing references

@@
 The sovereignty policy-cycle in the Amazon advances the view that the Brazilian Amazon belongs to Brazil while any foreign or non-state, presence in the region is part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combatting alleged disinformation from actors perceived as a threat.
+The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combating alleged disinformation from actors perceived as a threat.
 
@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations [], we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations [^2], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
 The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+
+[^2]: For an overview on how inflation and political discourse in Brazil see @porto2007, @malheiros1995, and @fonseca2021.
+For a few studies on racist and anti-racist discourses in Brazil see @hunt2004, @silva2019, and @djik2020.
 
@@
 We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in MAnaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
+This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
                                        "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
@@
 
-The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
-The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
-That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
-
 ```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
@@
 p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-# post estimation tests
-chi_square <- chisq.test(ama_model$mx_cat, predict(model))
+
 # too much information... Let's just focus on what we want here...
-
 md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
@@
   column_spec(4, width = "5cm", latex_valign = "m")
+```
 
+The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
+The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
+
+```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+logit2prob <- function(logit){
+  odds <- exp(logit)
+  prob <- odds / (1 + odds)
+  return(prob)
+}
+md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
+                      "Brasilia" = c(-1.024, -1.002, -0.206),
+                      "International" = c(-0.612, -1.583, -1.427),
+                      "Other_States" = c(0.023, -0.041, 0.324))
+md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
+md_plot$International <- logit2prob(md_plot$International)
+md_plot$Other_States <- logit2prob(md_plot$Other_States)
+mplot <- md_plot %>% tidyr::pivot_longer(Brasilia:Other_States) %>%
+  rename(Location = name, Probability = value) %>% 
+  ggplot(aes(Construction, Probability)) +
+  geom_bar(aes(color = Location, fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
+  labs(x = "", y = "Probability",
+       title = "Probability for problem constructions across locations",
+       subtitle = "Reference location is Amazonian States")
+mplot
 ```

### 2022-04-13 Draft_April_2022/Full_draft_20220401.rmd
Added standard errors for regression table

@@
                                            "Sovereignty vs Environmental Conservation"),
-                 "Brasilia vs Amazonian States" = c("-1.024***","-1.002***", "-0.206"),
-                 "International vs Amazonian States" = c("-0.612***", "-1.583***", "-1.427***"),
-                 "Other States vs Amazonian States" = c("0.023", "-0.041", "0.324"),
-                 "Election Year" = c("-0.241", "0.028", "-0.684**"),
-                 "Annual Deforestation" = c("0.063***", "-0.031*", "0.004"),
-                 "Average Inflation" = c("-0.001***", "-0.001***", "-0.0001"))
+                 "Brasilia vs Amazonian States" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)"),
+                 "International vs Amazonian States" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)"),
+                 "Other States vs Amazonian States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)"),
+                 "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)"),
+                 "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)"),
+                 "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)"))
 
@@
 ```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-logit2prob <- function(logit){
+logit2prob <- function(logit) {
   odds <- exp(logit)

### 2022-04-13 Draft_April_2022/Full_draft_20220401.rmd
Added tible for extended methodology

@@
 
-kbl(t(md), booktabs = T,caption = "Table 2 - Amazon Problem-Construction by Location", align = "c")%>% kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
+kbl(t(md), booktabs = T,caption = "Table 2 - Amazon Problem-Construction by Location", align = "c") %>%
+  kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
   column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m")%>%
@@
                      dep.var.labels.include = FALSE)
+full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
+                                           "SOV-EI", "SD-CON", "Other"),
+                  "Brasilia" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)", "-0.341 (0.248)",
+                                 "-1.019*** (0.273)", "0.420 (0.257)", "-1.197*** (0.330)", "-1.212*** (0.342)",
+                                 "0.860*** (0.318)", "-0.892*** (0.172)"),
+                  "International" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)", "-0.265 (0.292)",
+                                      "-0.980*** (0.336)", "-0.451 (0.367)", "-1.110*** (0.407)", "-1.105*** (0.395)",
+                                      "-0.117 (0.328)", "-0.774*** (0.202)"),
+                  "Other States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)", "0.149 (0.296)", "0.071 (0.292)",
+                                     "0.823*** (0.306)", "-0.466 (0.373)", "-0.136 (0.366)", "-0.074 (0.354)", 
+                                     "-0.159 (0.206)"),
+                  "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)",  "-0.059 (0.253)",
+                                      "-0.254 (0.281)", "-0.573 (0.406)", "0.064 (0.367)", "-1.243** (0.547)",
+                                      "-0.067 (0.405)", "-0.451** (0.194)"),
+                  "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)", "0.023 (0.017)",
+                                             "0.047** (0.019)", "0.005 (0.027)", "-0.013 (0.026)", "-0.001 (0.028)",
+                                             "0.011 (0.026)", "0.059*** (0.013)"),
+                  "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)",
+                                          "-0.0001*** (0.0002)", "-0.0005** (0.0002)", "0.0002 (0.0002)",
+                                          "-0.001** (0.0004)", "-0.0004 (0.0004)", "-0.001* (0.0004)",
+                                          "-0.0002* (0.0001)"))
+kbl(t(full_md), booktabs = T,caption = "Multinomial Regression Full", align = "c") %>%
+  kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
+  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m")%>%
+  column_spec(2, width="5cm", latex_valign = "m") %>%
+  column_spec(3, width = "5cm", latex_valign = "m") %>%
+  column_spec(4, width = "5cm", latex_valign = "m")
 ```

### 2022-04-13 Draft_April_2022/Full_draft_20220401.rmd
Updated plots and code in rmd file, but text was added to google docs

@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")+
+        legend.position = "bottom") +
   facet_wrap(~location_cat, scales= "free_y", ncol=2)
@@
        title = "Probability for problem constructions across locations",
-       subtitle = "Reference location is Amazonian States")
+       subtitle = "Reference location is Amazonian States") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")
 mplot

### 2022-04-14 Draft_April_2022/Full_draft_20220401.rmd
#text changes

--- 2022-04-13 Draft_April_2022/Full_draft_20220401.rmd
@@
 We need to exploit the Amazon's natural resources.
-We need to provide better living standards for the people living in the Amazon.
+We need to provide better living standards for the people in the Amazon.
 We need to preserve the Amazon as a standing ecosystem.
@@
 
-The conservationist problem-construction advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
+The conservationist policy-cycle advances the view that Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through protection of their territories and rights to self-determination [@hochstetler2007].
 The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations , we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation or race relations [@hunt2004, @silva2019, and @djik2020], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
 The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-
-Problem-construction at the level of discourse is also more varied.
-They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations [^2], we only find one systematic analysis of Amazonian discourse.
-@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-
-[^2]: For an overview on how inflation and political discourse in Brazil see @porto2007, @malheiros1995, and @fonseca2021.
-For a few studies on racist and anti-racist discourses in Brazil see @hunt2004, @silva2019, and @djik2020.
 
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006][^2].
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006][^3].
 After the SVM model is trained and tuned, and the model shows to appropriately fit the validation set, we use the model to automatically code the remaining 1007 Amazonian statements.
@@
 
-[^2]: For more information on this please see the extended methodology.
+[^3]: For more information on this please see the extended methodology.
 The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the validation set.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^3] , economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation[^4] , economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
@@
 
-[^3]:  The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
+[^4]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
 Nevertheless, matching deforestation with speech dates is a complicated endeavor.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^4], economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation[\^4], economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
@@
 This coincides with the Presidency of Lula and the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” [@franchini2019], when stakes about climate change were high.
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" [@franchini2019], when stakes about climate change were high.
 A somewhat different pattern can be identified in the lead up to the 2015 Paris COP, which was also building up to become a key-turn in climate politics after the failures of Copenhagen.
@@
 
-We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro’s presidency, 2019.
-As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon blasts reach unprecedented coverage.
+We subsequently observe a steady increase from 6.4% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
+As the narrative of the climate crisis picks up in the late 2010s, international media attention about the Amazon reaches unprecedented coverage.
 Pictures of the Amazon on fire and of the red sky afternoon in São Paulo circulated in social media and international media outlets in 2019.
 President Bolsonaro engages in an international debacle with President Macron and others, which drove the topic up strongly in the presidential agenda.
-President Bolsonaro retrieves Brazil’s hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
+President Bolsonaro retrieves Brazil's hosting status for COP25, and a strong process of dismantling of environmental governance starts taking place.
 
@@
 Figure 3 (below) shows these shifts and reversal more clearly.
-It highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula’s presidential mandate.
+It highlights the decrease of economic integration and increase of social and conservation problem constructions preceding Lula's presidential mandate.
 Relatedly, figure 3 also shows that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty and economic integration reaches their actual maximum and a new local maximum (respectively).
@@
 The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types.
-Now that we’ve inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+Now that we've inspected and de veloped pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
 
@@
 
-```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
 pure_types_time_location <- ama_mx %>%
@@
 ```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
 logit2prob <- function(logit) {
@@
   ggplot(aes(Construction, Probability)) +
-  geom_bar(aes(color = Location, fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
+  geom_bar(aes(fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
+    scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
   labs(x = "", y = "Probability",
        title = "Probability for problem constructions across locations",
-       subtitle = "Reference location is Amazonian States")
+       subtitle = "Reference category is environmental conservation problem-construction in Amazonian States") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")
 mplot
@@
 
-# 5 Discussion: The Amazon frontier, environmentalism, and democracy
+# 5 Discussion: The Amazon frontier and democracy
 
@@
 The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse in Amazonian States compared to Brasilia and other States.
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what “they want to hear”.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
 If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
-Or, as @putnam1988 puts, what’s the actual overlap between international and domestic overlap.
+Or, as @putnam1988 puts, what's the actual overlap between international and domestic overlap.
 The domestic policies and transnational support that led to the decrease of deforestation from 2004 to 2012 happened concurrently to a period of strong economic growth and social development in Brazil and worldwide.
@@
 While unprecedented, this new balance was not long-standing.
-Democratic decay is slow, and the embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
+Democratic decay is slow, and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
 We observe the decrease in conservation related statements in the mid 2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3).
@@
 The political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro’s problem-construction is the strongest form of this shift.
+Bolsonaro's problem-construction is the strongest form of this shift.
 

### 2022-04-14 Draft_April_2022/Full_draft_20220401.rmd
Corrected a few footnotes, added note for regression tibble, and re-added sections 4.3 and conclusion

@@
 csl: chicago.csl
-abstract: This paper ...
+#abstract: This paper ...
 ---
@@
 They are not monolithic in time, across location, or even by the same speaker.
-While governmental discourses in Brazil have been studied for topic such as inflation or race relations [@hunt2004, @silva2019, and @djik2020], we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topic such as inflation [@porto2007, @malheiros1995, and @fonseca2021] or race relations [@htun2004, @silva2019, and @djik2020], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
@@
 
-kbl(codebook, booktabs = T,caption = "Table 1 - Amazonian Problem-Construction Codebook")%>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
-  column_spec(1, width="3cm", bold=TRUE)%>%
-  column_spec(2, width="9cm") %>%
-  column_spec(3, width = "9cm")
+kbl(codebook, booktabs = T, caption = "Table 1 - Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
 
@@
 
-[^3]: For more information on this please see the extended methodology.
-The document includes a detailed discussion of how the SVM algorithm was chosen over other algorithms based on evaluation of performance of trained models for labeling the validation set.
+[^2]: For more information on this please see the extended methodology.
+The document includes a detailed discussion of how the SVM algorithm and the performance of trained models for labeling the validation set.
 The extended methodology also includes a more detailed codebook table with further coding guidelines.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[^4] , economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation[^3] , economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
@@
 
-[^4]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
+[^3]: The reasoning here is that knowledge of high or low deforestation rates might drive presidents to speak about the Amazon.
 Nevertheless, matching deforestation with speech dates is a complicated endeavor.
@@
 Figure 1 shows the proportion of speeches that mentions the Amazon in relation to all speeches in each year.
-The predicted share curve controls incidence for deforestation[\^4], economic situation, and speaker (see appendix for methodological details).
+The predicted share curve controls incidence for deforestation, economic situation, and speaker (see appendix for methodological details).
 We observe various local maxima: 1989, 1992, 2005, 2009, 2015, and 2019.
@@
 
+Figure 5, below, illustrates the share of pure-type problem construction by locations in Brazil.
+We divide locations into Amazonian states (i.e.
+all the Brazilian states in which the Amazon biome is present), non-Amazonian states (other Brazilian states), Brasilia (the capital of Brazil where the federal government is located), and international (countries outside of Brazil).
+The plots reveal several trends.
+Presidents consistently construct the Amazon as an issue of pure economic integration within Amazonian states more often than all other constructions in time.
+Relatedly, we observe a steady decrease since the mid-1980s in pure conservation constructions in Amazonian states.
+This differentiates Amazonian states from national or international settings, where the relationship among problem-constructions appears less hierarchical.
+In Brasilia, for once, the conservation problem construction remains the most frequent since the mid 2000s.
+Outside of Brazil, conservation was the most used construction from the mid-2000s to the mid-2010s.
+Nonetheless, pure social development constructions, which increased in the early-2000s to become the second most used construction within Amazonian states, disappeared around 2015.
+In line with this, we also see a large increase in the frequency of social development constructions in Brasilia and non-Amazonian states from the mid-2000s to the mid-2010s, but not internationally.
+This implies that constructing the Amazon as an issue of social development is a construction deployed within the country.
+Alternatively, while there is some variation in the frequency in which pure sovereignty constructions were employed in Amazonian States, other States, and Brasilia, this problem-construction has been increasing since the early 2010s in all these settings.
+In international settings, however, pure sovereignty did not appear until the mid-2000s.
+As with social development, sovereignty seems to be employed domestically as a problem-construction for the Amazon.
+
 ```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
@@
 
-Figure 5, above, illustrates the share of pure-type problem construction by locations in Brazil.
-We divide locations into Amazonian states (i.e.
-all the Brazilian states in which the Amazon biome is present), non-Amazonian states (other brazilian states), Brasilia (the capital city in Brazil), and international (countries outside of Brazil).
-Notice that, consistently, presidents construct the Amazon as an issue of pure economic integration within Amazonian states more often than all other constructions in time.
-Alternatively, we see that pure conservation becomes increasingly less frequent in time for Amazonian states.
-As well, pure social development constructions, which were fairly frequent from the early-2000s and onwards, disappeared around 2015 after the mid-2010s in Amazonian states.
-Nonetheless, we see a large increase from the mid-2000s to the mid-2010s in the frequency in which presidents constructed the Amazon as an issue of pure social development in Brasilia and non-Amazonian states.
-In Brasilia, also, pure conservation constructions went down drastically during the 1990s, but increased steadily from the mid-2000s onwards.
-Interestingly, presidents most often constructed the Amazon as an issue of pure environmental conservation internationally only from the mid 2000s until the mid-2010s.
-Moreover, pure sovereignty constructions did appear in international settings until the mid-2000s.
+To ensure these results are robust, we run a multinomial regression.
+Our dependent variable is problem constructions (categorical), while our main dependent variable is location (categorical).
+The reference category for the multinomial model is environmental conservation in Amazonian states.
+As in section 4.1, we add controls for deforestation rates (numerical), inflation (numerical), and election year.
+Table 2 displays our results in log odds.
+Since the model accounts for both mixed and pure-type Amazonian problem constructions, and this makes for a large table, we only display the results for pure-types to facilitate visualization [^4].
+Figure 6 shows the relative probability of problem-constructions and location in relation to environmental conservation in Amazonian states.
+For example, the bar for economic integration in other states represents a 50% percent probability of using this problem-construction in relation to our reference category.
+Hence, the lower the probabilities displayed in bars in figure 6, the less likely presidents are to construct the Amazon as an issue of environmental conservation in Amazonian states.
 
-Table 2, below, displays the multinomial regression coefficients for the correlation between diverse problem constructions and locations.
-The regression coefficients express the log odds, that is, the logarithm odds to the reference categories.
-The reference categories are Amazonian states for location and environmental conservation for problem construction.
-To facilitate visualization, since the model has many more columns (i.e.
-types of problem construction), we only display the model results for the pure-type constructions, however, the model does account for both pure and mixed-type constructions.
-We keep the results for the control variables for election year, annual deforestation rates, and average yearly inflation in the table.
+[^4]: Please find the full regression table in the appendix below.
 
@@
 
-kbl(t(md), booktabs = T,caption = "Table 2 - Amazon Problem-Construction by Location", align = "c") %>%
+kbl(t(md), booktabs = T, caption = "Table 2 - Amazon Problem-Construction by Location", align = "c") %>%
   kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
-  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m")%>%
+  footnote(general = "The multinomial regression coefficients (in log odds) and standard errors (in parentheses) are displayed.
+The asterisk marks the level of statistical significance for coefficient, multiple asterisks denote a statistically significant P value above the 95th percentile.") %>%
+  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m") %>%
   column_spec(2, width="5cm", latex_valign = "m") %>%
@@
 
-The results indicate that the presidents are more likely to construct it as an environmental conservation problem far away from the Amazon.
-The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
-That is, presidents are more likely to construct the Amazon as an issue of environmental conservation in international settings and in Brasilia than in Amazonian states.
-
 ```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 logit2prob <- function(logit) {
@@
 
-Sovereignty in the Amazon is an issue within Brazil.
-The negative statistically significant coefficient for constructing the Amazon as a problem of pure sovereignty in international settings, in relation to conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
-The lack of statistically significant correlations between pure sovereignty constructions and Brasilia or other non-Amazonian states, corroborates that the Amazon as an issue of sovereignty is an internally performed issue.
+The results of our model corroborate some of the visible patterns in figure 5.
+Presidents are more likely to construct the Amazon as an issue of environmental conservation when they are far away from the Amazon.
+The negative statistically significant coefficients of problem constructions such as pure economic integration and pure social development in both international settings and Brasilia, in relation to environmental conservation problem constructions in Amazonian states, indicate that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+Figure 6 shows that in international settings, constructions of social development are 33% less likely than in Amazonian states.
+As well, we see that economic integration constructions are 15% less likely in international settings.
+In Brasilia, both economic integration and social development constructions are 13% less likely than in Amazonian states.
 
-Constructing the Amazon as an issue of economic integration correlates with increases in deforestation rates.
-Some of the control variables correlate with some Amazonian problem constructions in interesting ways.
+Constructing the Amazon as an issue of sovereignty happens within Brazil.
+The negative statistically significant coefficient (table 2) for constructing the Amazon as a problem of pure sovereignty in international settings, in relation to Amazonian states, indicates that presidents are less likely to construct the Amazon as an issue of economic integration and social development in those locations.
+Figure 6 illustrates that presidents are 21% less likely to construct the Amazon as an issue of sovereignty internationally in relation to Amazonian states.
+The probabilities of sovereignty constructions around 0.5 (equal probability) for Brasilia and other non-Amazonian states corroborates that the Amazon as an issue of sovereignty is an internally performed issue.
+
+Nevertheless, we see that some of the control variables (table 2) correlate with some Amazonian problem constructions in interesting ways.
 For example, pure sovereignty constructions correlate negatively with election years in relation to conservation.
-That is, in election years conservation constructions are more likely to take place in comparison to sovereignty.
-As well, annual deforestation rates correlate positively with economic integration constructions in relation to conservation.
-This indicates that as deforestation increases, presidents are also more likely to construct the Amazon as an issue of economic integration, or vice-versa.
+Also, annual deforestation rates also correlate positively with economic integration constructions in relation to conservation.
+This indicates that the Amazon is more likely to be constructed as an issue of economic integration as deforestation increases.
 
-@putnam1988 seminal article on the two level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
-The author argues that both domestic and international levels need to be taken into consideration when analyzing how, often, domestic politics became entangled in international negotiations.
-The Amazon, as a region and a forest, has been the topic of international negotiations, national debates, and local policy implementation; though how the Amazon has been constructed as an issue differs on each of these three levels.
-While in Brasilia or internationally different presidents might construct the Amazon as an issue of conservation, the same presidents might construct the Amazon as an issue of economic integration or social development at the local level.
-This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" differ.
-The three level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not for local electorates.
-Such might help explain diverse local implementation gaps between public policy negotiated outside and implemented within the Amazon as perceptions and expectations about the issues the same policy addresses might differ [@alesina2009; @lopez2020].
+The Amazon, as a region and a forest, has been the topic of international negotiations, national debates, and local policy implementation; though our results show that how the Amazon has been constructed as an issue differs on each of these three levels.
+@putnam1988 seminal article on the two-level game between domestic and international politics analyzes how negotiations at both levels make policies possible.
+The author argues that both domestic and international levels should be considered.
+Agreements are made in the overlap between the position of domestic actors and international actors; so negotiators play a two-level game to maximize the area of overlap, bringing both to a more moderate position in issues [@putnam1988].
+This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” could differ as well.
+The three level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not for local electorates.
 
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
-This democratic game contributes to the advancement of ambiguous public policies thought from the outside to the Amazon or contradictory policies from Amazon to the outside.
-Take, for example, the rural credit offered to local agricultural producers in Amazonian states went from 500 million reais in 1999 to over 4 billion by 2012 [@capobianco2021].
-During the same period, the money spent in fighting deforestation in the Amazonian states also increased from ...
-in ...
-to ...
-in ...
-These policies match diverse local, national, and international expectations and match solutions to different problem constructions presented at each of these levels.
+This three-level game led to different policies being negotiated and maximized at the interplay between the levels.
+Take, for once, how the Brazilian government successfully funded domestic public policy with international support since the 1990s (e.g.
+1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g.
+2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD1 billion for environmental conservation in the Amazon [@silva-muller2022].
+Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued.
+During the same time rural credit offered to local agricultural producers in Amazonian states, it went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+Now-a-days, it has reached unprecedented levels.
 
@@
 
+This paper answers how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
+Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to outcomes such as policies and environmental outcomes.
+Empirically, we build the first comprehensive overview of the Amazon in presidential discourse.
+
 # References
@@
 # too much information... Let's just focus on what we want here...
-stargazer::stargazer(model, type = "text",
-                     covariate.labels = c("Brasilia", "International", "Non-AM state",
-                                          "Election", "Deforestation", "Inflation"),
-                     column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-                                       "Sov-EI", "SD-Con", "Other"),
-                     dep.var.labels.include = FALSE)
+# stargazer::stargazer(model, type = "text",
+#                      covariate.labels = c("Brasilia", "International", "Non-AM state",
+#                                           "Election", "Deforestation", "Inflation"),
+#                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
+#                                        "Sov-EI", "SD-Con", "Other"),
+#                      dep.var.labels.include = FALSE)
 full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
@@
 kbl(t(full_md), booktabs = T,caption = "Multinomial Regression Full", align = "c") %>%
-  kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
-  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m")%>%
-  column_spec(2, width="5cm", latex_valign = "m") %>%
-  column_spec(3, width = "5cm", latex_valign = "m") %>%
-  column_spec(4, width = "5cm", latex_valign = "m")
+  kable_styling(latex_options = c("striped", "scale_down"),
+                position= "center", font_size = 9, full_width = TRUE) %>%
+  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
+  column_spec(2, width="2 cm", latex_valign = "m") %>%
+  column_spec(3, width = "2 cm", latex_valign = "m") %>%
+  column_spec(4, width = "2 cm", latex_valign = "m") %>%
+  column_spec(5, width="2 cm", latex_valign = "m") %>%
+  column_spec(6, width = "2 cm", latex_valign = "m") %>%
+  column_spec(7, width = "2 cm", latex_valign = "m") %>% 
+  column_spec(8, width="2 cm", latex_valign = "m") %>%
+  column_spec(9, width = "2 cm", latex_valign = "m") %>%
+  column_spec(10, width = "2 cm", latex_valign = "m") %>% 
+  column_spec(11, width = "2 cm", latex_valign = "m")
 ```

### 2022-04-14 Draft_April_2022/Full_draft_20220401.rmd
#finalversions

@@
 
-kbl(codebook, booktabs = T, caption = "Table 1 - Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
+kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
 
@@
 
-kbl(t(md), booktabs = T, caption = "Table 2 - Amazon Problem-Construction by Location", align = "c") %>%
+kbl(t(md), booktabs = T, caption = "Amazon Problem-Construction by Location", align = "c") %>%
   kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
-  footnote(general = "The multinomial regression coefficients (in log odds) and standard errors (in parentheses) are displayed.
-The asterisk marks the level of statistical significance for coefficient, multiple asterisks denote a statistically significant P value above the 95th percentile.") %>%
+  footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>%
   column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m") %>%
@@
 
-# References
-
 # Appendix
 
-## Multinomial Modeling
+````{=tex}
+\begin{landscape}
 
 ```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
-# data on deforestation rates per year (PRODES)
-# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
-# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
-# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
-# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
-# inflation rates per year Brazil (average for year)
-# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
-# post estimation tests
+
 chi_square <- chisq.test(ama_model$mx_cat, predict(model))
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
-# library(lmtest)
-# lrtest(null_model, model) # We very much reject the hypothesis
-# (i.e. the more complex model is significantly better than the null model).
-# too much information... Let's just focus on what we want here...
-# stargazer::stargazer(model, type = "text",
-#                      covariate.labels = c("Brasilia", "International", "Non-AM state",
-#                                           "Election", "Deforestation", "Inflation"),
-#                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-#                                        "Sov-EI", "SD-Con", "Other"),
-#                      dep.var.labels.include = FALSE)
+
 full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
@@
                 position= "center", font_size = 9, full_width = TRUE) %>%
+                footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>%
   column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
@@
 ```
+
+\end{landscape}
+````
+
+# References

### 2022-04-14 messy_files/Text from multinomial regression.R

@@ -1,0 +1,61 @@
+````{=tex}
+\begin{landscape}
+
+```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
+# data on deforestation rates per year (PRODES)
+# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
+# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
+# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
+# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
+# inflation rates per year Brazil (average for year)
+# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
+# post estimation tests
+chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
+# Chi-square p value (p-value < 0.001) tells us that our model explains a
+# significant amount of the variation in the data in comparison with a null model.
+# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
+# library(lmtest)
+# lrtest(null_model, model) # We very much reject the hypothesis
+# (i.e. the more complex model is significantly better than the null model).
+# too much information... Let's just focus on what we want here...
+# stargazer::stargazer(model, type = "text",
+#                      covariate.labels = c("Brasilia", "International", "Non-AM state",
+#                                           "Election", "Deforestation", "Inflation"),
+#                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
+#                                        "Sov-EI", "SD-Con", "Other"),
+#                      dep.var.labels.include = FALSE)
+full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
+                                           "SOV-EI", "SD-CON", "Other"),
+                  "Brasilia" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)", "-0.341 (0.248)",
[…]

### 2022-05-10 Draft_April_2022/Full_draft_20220401.rmd
Started imporving plots according to feedback

@@
 Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
-  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
-  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
-  scale_y_continuous(labels = percent_format())+
+  geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
+  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
+  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+  geom_vline(xintercept = 1988, linetype="dotted") +
+  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summmit"), size = 3) + 
+  geom_vline(xintercept = 1992, linetype="dotted") +
+  geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summmit"), size = 3) + 
+  geom_vline(xintercept = 2009, linetype="dotted") +
+  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summmit"), size = 3) + 
+  geom_vline(xintercept = 2015, linetype="dotted") +
+  scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
+  scale_y_continuous(labels = percent_format()) +
   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-       caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
+       caption = "Predicted share controls for deforestation rates, inflation, and president.",
+       color='Y series') +
   theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
 prob_construction_year <- ama_mx %>%
-  count(year, mx_cat)%>%
+  filter(!(mx_cat == "Other" | mx_cat == "Other Mixed-types")) %>% 
+  count(year, mx_cat) %>%
   group_by(year) %>%
@@
         legend.position = "none") +
-  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
+  facet_wrap(~ mx_cat, ncol = 2)
 prob_construction_year
@@
 pure_types_time <- ama_mx %>%
-  count(president, mx_cat2, mx_cat, year) %>%
-  group_by(president, year) %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
   mutate(perc = n / sum(n)) %>% 
   filter(mx_cat2 == "Pure-types") %>% 
-  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
-  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
-  scale_y_continuous(labels = percent_format(accuracy=1)) +
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_smooth(aes(fill = mx_cat), size = .5) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
   labs(x = "", y = "", title ="Share of each pure type by year",
@@
 md_plot$Other_States <- logit2prob(md_plot$Other_States)
-mplot <- md_plot %>% tidyr::pivot_longer(Brasilia:Other_States) %>%
-  rename(Location = name, Probability = value) %>% 
-  ggplot(aes(Construction, Probability)) +
-  geom_bar(aes(fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
+mplot <- md_plot %>%
+  tidyr::pivot_longer(Brasilia:Other_States) %>%
+  mutate(Probability = round(value, digit = 2)) %>% 
+  rename(Location = name) %>% 
+  ggplot(aes(Location, Probability, fill = Construction)) +
+  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  geom_text(aes(label = Probability), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
+  geom_hline(yintercept = 0.5, linetype = "dotted", color = "red") +
   labs(x = "", y = "Probability",

### 2022-05-11 Draft_April_2022/Full_draft_20220401.rmd
Harmonized scales for figure 4 as well

@@
         legend.position = "bottom") +
-  facet_wrap(~location_cat, scales= "free_y", ncol=2)
+  facet_wrap(~location_cat, ncol=2)
 pure_types_time_location

### 2022-05-13 Draft_April_2022/Full_draft_20220401.rmd
Added notes about multinomial regression possible issues

@@
   mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
+                                            "Pure Social Development", "Pure Sovereignty",
+                                            "Economic Conservation",
                                             "Economic and Social Development", "Sovereign Conservation",
@@
 p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-
 # too much information... Let's just focus on what we want here...
@@
   column_spec(4, width = "5cm", latex_valign = "m")
+
+# #####
+# # Mixed effects multinomial regression with model controls for president
+# # Should we consider this method? We might have time effects?
+# # See: https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.1522?casa_token=Ui3Ya1qHE7cAAAAA:_a4xLBxFfsU5I2C7eP0hY-__55UurKhRfvpShTCCdiYO8aVmVV9aqJMWYzrLAg2DXAP5czu5h3yu-sUT 
+# m1 <- mclogit::mblogit(mx_cat ~ location_cat + election_year + def_year + AAI,
+#                        random = ~ 1|president, data = ama_model)
+# summary(m1)
+# # what about the independence of our response categories? Maybe we should fit a mutinomial probit model
+# # the package MNP does this but it is not clear that MNP is better even if IIA (see: file:///Users/henriquesposito/Downloads/Choosing_between_multinomial_logit_and_multinomial_probit_models_for_analysis_of_unordered_choice_data_accessible.pdf)
+# m2 <- MNP::mnp(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model)
+# summary(m2)
+# #####
 ```

### 2022-05-16 Draft_April_2022/Full_draft_20220401.rmd
Updates to plots used in analysis sections according to feedback

--- 2022-05-11 Draft_April_2022/Full_draft_20220401.rmd
@@
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
+# Load data
 pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-```
-
-```{r data prep for prob_construction, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+# Prepare data for problem constructions
 sov <- ama %>% 
@@
   rename (other = n)
-temp <- ei %>% left_join(other) %>% 
+temp <- ei %>% 
+  left_join(other) %>% 
   left_join(con) %>% 
@@
   replace(is.na(.), 0)
-```
-
-```{r data prep for mixed_types, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+# Get mixed types in
 ama_mx <-  ama %>%
@@
                                    |Sovereign Integration|Social Conservation|Other Mixed-types",
-                                   mx_cat) ~ "Mixed-types"))
+                                   mx_cat) ~ "Mixed-types"),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
 ```
@@
 perc1 <- pop %>%
-  count(amazon_speech, year)%>%
-  group_by(year)%>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
   mutate(perc=n / sum(n)) %>%
-  select(c(perc,amazon_speech, year))
-pop2 <- pop %>% count(amazon_speech, year, president) %>%
-  group_by(year, president) %>%
-  left_join(perc1) %>%
-  filter(amazon_speech==1)
-pop2 <- left_join(pop2, AAI, by = "year")
-pop2 <- left_join(pop2, amazon_def_year, by = "year")
-model <- lm(perc ~ AAI+ def_year + president, data=pop2)
-pop2$predicted = predict(model, pop2)
-Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
-  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
+######## Issue is with biblioteca presidencial, not with scarping btw ######
+# summary(as.factor(pop$year))
+# Simple plot
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  scale_y_continuous(labels = percent_format()) +
   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-  geom_vline(xintercept = 1988, linetype="dotted") +
-  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summmit"), size = 3) + 
-  geom_vline(xintercept = 1992, linetype="dotted") +
-  geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summmit"), size = 3) + 
-  geom_vline(xintercept = 2009, linetype="dotted") +
-  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summmit"), size = 3) + 
-  geom_vline(xintercept = 2015, linetype="dotted") +
-  scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
-  scale_y_continuous(labels = percent_format()) +
+  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+  geom_vline(xintercept = c(1988, 1992, 2009, 2015),
+             linetype = "dotted") +
   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-       caption = "Predicted share controls for deforestation rates, inflation, and president.",
+       caption = "",
        color='Y series') +
@@
         legend.position = "bottom")
+# # # With a few lines under the
+# cat1 <- ama_mx %>%
+#   mutate(cat = ifelse(mx_cat2 == "Mixed-types", "Mixed-types", paste(mx_cat))) %>%
+#   count(cat, year) %>%
+#   group_by(year) %>%
+#   mutate(perc = n / sum(n),
+#          perc_type = ifelse(perc == 1, 0.25, perc)) %>% 
+#   arrange(year) %>%
+#   select(c(cat, year, perc_type))
+# year_share <- merge(perc1, cat1, "year") %>%
+#   mutate(year_perc = perc*perc_type)
+# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = perc)) +
+#   geom_line(aes(y = perc)) +
+#   scale_y_continuous(labels = percent_format()) +
+#   geom_line(aes(x = year, y = year_perc, fill = cat, group = cat, color = cat)) +
+#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
+#              linetype = "dotted") +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
+#        caption = "",
+#        color='Y series') +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
+# # For filling the area under the line
+# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = year_perc, fill = cat)) +
+#   geom_line() +
+#   geom_area() +
+#   scale_y_continuous(labels = percent_format()) +
+#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+#   geom_vline(xintercept = 1988, linetype = "dotted") +
+#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+#   geom_vline(xintercept = 1992, linetype = "dotted") +
+#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) +
+#   geom_vline(xintercept = 2009, linetype = "dotted") +
+#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+#   geom_vline(xintercept = 2015, linetype = "dotted") +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
+#        caption = "",
+#        color = 'Y series') +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
+# # Controling for inflation and deforastation
+# pop2 <- pop %>% count(amazon_speech, year, president) %>%
+#   group_by(year, president) %>%
+#   left_join(perc1) %>%
+#   filter(amazon_speech==1)
+# pop2 <- left_join(pop2, AAI, by = "year")
+# pop2 <- left_join(pop2, amazon_def_year, by = "year")
+# model <- lm(perc ~ AAI+ def_year + president, data=pop2)
+# pop2$predicted = predict(model, pop2)
+# Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
+#   geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
+#   geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
+#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+#   geom_vline(xintercept = 1988, linetype="dotted") +
+#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) + 
+#   geom_vline(xintercept = 1992, linetype="dotted") +
+#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) + 
+#   geom_vline(xintercept = 2009, linetype="dotted") +
+#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) + 
+#   geom_vline(xintercept = 2015, linetype="dotted") +
+#   scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
+#   scale_y_continuous(labels = percent_format()) +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
+#        caption = "Predicted share controls for deforestation rates, inflation, and president.",
+#        color='Y series') +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
 Amazon_year
@@
 ```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
+                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
+                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
+                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
+                           "Rousseff", "Temer", "Bolsonaro"))
 pure_types_time <- ama_mx %>%
@@
   ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), size = .5) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
+        legend.position = "bottom") +
+  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.44,
+           fill = c("mediumpurple4", "mediumorchid1", "mediumpurple4", "mediumorchid1",
+                    "mediumpurple4", "mediumorchid1", "mediumpurple4", "mediumorchid1"),
+           alpha = 0.1) +
+  annotate(geom = "text", x = hp$label, y = 0.4, angle = 40,
+           label = hp$presid, alpha = 0.4)
 pure_types_time
@@
 mixed_types_presid <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(president, mx_cat) %>%
+  count(president, mx_cat, mx_cat2) %>%
   group_by(president) %>%
   mutate(perc = n / sum(n)) %>% 
-  mutate(president = factor(president,
-                            levels = c("Sarney", "Collor", "Itamar", "FHC", "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x=president, y=perc, fill=mx_cat,label= scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat="identity", position="stack") +
-  geom_text(size = 3, position = position_stack(vjust=.5)) +
+  filter(mx_cat2 == "Mixed-types") %>% 
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 3, position = position_stack(vjust = .5)) +
   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
   labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
-       subtitle = "Sample composed of Amazonian statements that were coded as a mixed-type (n=431)",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
        caption = "") +
@@
 The combination of sovereignty with economic integration, which was also characteristic of the military dictatorship policies for the region, reaches its highest level with Bolsonaro: 22.7% of all mixed types.
-Now that we've inspected and de veloped pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
+Now that we've inspected and developed pure and mixed types, we can check if these specific problem constructions vary depending on where the president is speaking.
 
@@
   mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
+                                            "Pure Social Development", "Pure Sovereignty",
+                                            "Economic Conservation",
                                             "Economic and Social Development", "Sovereign Conservation",
                                             "Sustainable Development","Sovereign Integration",
-                                            "Social Conservation", "Other")),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+                                            "Social Conservation", "Other")))
 # model
-model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE, trace = FALSE)
+model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
+                  data = ama_model, model = TRUE, trace = FALSE)
 # summary statistics
@@
 p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-
-# too much information... Let's just focus on what we want here...
+# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
+iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
+iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
+                data = iia_data, model = TRUE, trace = FALSE)
+iia_summary <- summary(iia)
+iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
+# Model coefficients, and p-values, are statistically identical even when we drop the largest
+# factor category from model. Therefore, we can proceed with a multinomial logit model,
+# instead of a multinomial probit model, since the independence of irrelevant alternatives 
+# Other post estimation tests
+chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
+# Chi-square p value (p-value < 0.001) tells us that our model explains a
+# significant amount of the variation in the data in comparison with a null model.
+# But too much information on the summary tables... Let's just focus on what we want here:
 md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",

### 2022-05-18 Replication_Files/data_preparation.R
Fixed minor coding mistakes in datasets for location referent to "Guiana"

@@ -1,4 +1,4 @@
-# In this script we prepare the data with some text pre-processing,
+1# In this script we prepare the data with some text pre-processing,
 # by extracting Amazonian statements, and 
 # by adding locations for all speeches.
 
@@ -35,13 +35,8 @@ Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text)
 #Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
 #Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
 
-# Get 2 sentences before and 2 sentences after
-context2 <- function(string, var) {
-  match <- paste0("([^.]+\\.){0,2}[^.]+(", string, ").*?\\.([^.]+\\.){0,2}")
-  s <- stringr::str_extract_all(var, match)
-  s
-}
-Amazon_speeches$AM2 <- context2("amazon", var = Amazon_speeches$text)
+# Get 2 sentences before and 2 sentences after with poldis
+Amazon_speeches$AM2 <- poldis::context("amazon", Amazon_speeches$text, "sentences", 2)
 
 # Get and save long data coding
 amazon_speeches_long <- Amazon_speeches %>%

### 2022-05-18 Draft_May_2022/Full_draft_20220510.rmd
Updated rmd to match google docs for may version in correct folder. All graphs and figures were added.

---
title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically. Both of them are PhD candidates at The Geneva Graduate Institute. Livio is affiliated to the Albert Hirschman Centre on Democracy. Henrique is affiliated to the Centre for International Environmental Studies.]
date: "May 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon Rainforest is one of the most important ecosystems in the world, and most of this biome is located in Brazil. Albeit the importance of understanding the relationship between the social construction of the Amazon and its effects on environmental outcomes, we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments. Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level. Building on Hirschman’s conceptualization of chosen problems (1963), we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse. Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985. We find that, first, international environmental events appear to drive presidents to speak more about the Amazon. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards. Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
library(skimr)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(nnet)
library(stargazer)
library(kableExtra)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
pop <-  pop %>% select(-c(title, date, text, location))
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))
# Prepare data for problem constructions
sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)
ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)
sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)
con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)
other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)
temp <- ei %>% 
  left_join(other) %>% 
  left_join(con) %>% 
  left_join(sd) %>% 
  left_join(sov) %>% 
  replace(is.na(.), 0)
# Get mixed types in
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
                                      mixed_type == '0_0_0_0' ~ "Other",
                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                            mixed_type) ~ "Other Mixed-types"),
         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
                    "Social Conservation", "Other Mixed-types")),
         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
                             grepl("^Other$", mx_cat) ~ "Other",
                             grepl("Economic Conservation|Economic and Social Development|
                                   |Sovereign Conservation|Sustainable Development|
                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
                                   mx_cat) ~ "Mixed-types"),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
```

\pagebreak

# 1 Introduction

We need to protect the Amazon from foreign interests. We need to exploit the Amazon’s natural resources. We need to provide better living standards for the people in the Amazon. We need to preserve the Amazon as a standing ecosystem. Historically, the Brazilian federal government proposed diverse constructions of the Amazon as a region, forest, or peoples. Each of these constructions contain an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem. These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.

Different governments along Brazilian history have been described as proponents of a specific view of the Amazon (Drummond & Barros-Platiau 2016; Padua 2012; Franchini & Viola 2019; Capobianco 2019; Pereira & Viola 2021). For example, while the military dictatorship is associated with both national sovereignty and then economic integration, President Sarney and President Lula are often tied to environmental conservation. However, governments are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of one specific problem. Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes (Waroux et al. 2021), we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between and within governments.

In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses. Building on Hirschman’s concept of chosen problems (1963) and Bacchi’s concept of problem-representation in policy (2009), we propose a framework to identify problem-constructions in political discourses. Although problem-construction takes place in a series of instances, we analyze the case of discourses by Brazilian presidents since 1985. We opt for presidential speeches for two reasons. First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences (Zarefsky 2004). It legitimizes ways of thinking about the Amazon. In turn, policy perception is key for policy adoption and implementation (Alesina and Giuliano 2009; López et al. 2020). This is especially pertinent as deforestation rates in Brazil are associated with expectations from government, generated from material and discursive governmental practices (Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021), and are a crucial factor in decisions to deforest at the ground (Campbell 2015). Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on where they are. Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York. Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.

To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985. We subset the dataset by identifying Amazonian related statements within these speeches. We find that 2014 sections in these discourses refer to the Amazon at least once. We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem. We use this codebook to manually code a randomly selected training set of the Amazonian related statements. We train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements. We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.

We find that, first, international environmental events appear to drive presidents to speak more about the Amazon. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards. Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.

# 2 Conceptual framework and contribution

## 2.1 Chosen problems, presidential discourse, and policy issues

Governments often have a choice in how they construct problems and what policy solutions they implement. In “Journey towards Progress”, Hirschman (1963) draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion). Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups. Chosen problems are those governments select at their discretion. Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers (Hirschman 1963, 388–91). As Bacchi argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”. (2009, 10). The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed. The alleged problem is not always explicitly stated in policy. Hirschman exemplifies chosen problems with the case of the construction of Brasilia (1975, 388). But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three. It is up to the discretion of the government to highlight or not the implicit problem a policy solves.

Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with. Relative to how the policy is represented to be, it can be a solution of problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context. Putnam’s (1988) seminal article on the two-level game can help us make sense of this variation. The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups. Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural cadaster for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.  The same policy, then, can solve the problem of environmental conservation as well as economic integration.

This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests. Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases (see Drummond & Barros-Platiau 2016; Padua 2012; Franchini & Viola 2019; Capobianco 2019; Pereira & Viola 2021). In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy (Drummond & Platiau 2016). The governments from the late 1980s up to 2009, are more associated with environmental conservation. The presidencies of Dilma and Temer are connected to the decline of environmental policies, while Bolsonaro to the complete dismantling of environmental policies. While these works are important to understand how different governments acted towards the Amazon, the classification of specific governments into periods or policy cycles represents them as monolithic: they associate specific governments to one specific view of the Amazon. The presidency of Lula, often associated with environmental conservation because we saw an unprecedented decrease in deforestation. At the same time, during his terms governmental credits to agricultural expansion and the cattle industry surpassed BRL 578 billion (Capobianco, 2021, 106). This sum is about 20 times more than the budget of the Ministry of the Environment for this entire period. There is more variation within governments than the literature suggests.

An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue and. While the relationship between presidential speeches and policy is not causal (Lawrence 2004), they have the power to introduce and justify public policy, as well as shape its perception to broad audiences (Zarefsky 2004). Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem (Eshbaugh-Soha 2010; Rottinghaus 2009; Krebs and Jackson 2007), they direct the range of what is included in national debates (Druckman and Holmes 2004). As presidents speak in varied locations to varied audiences, it is very likely that they chose to frame similar issues differently.

The possibility of different problem-constructions at the level of presidential speeches has important consequences for democracy. If presidents can promote different problem-constructions in different places, it is important to understand to what extent the implemented agenda correlates with their local, federal, or international problem-constructions. Pacheco (2019) proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy. Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries. The costs for said economic benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in. Political stability, thus, can be seen as a product of the trade-off between both. Policies during the military dictatorship were strongly geared toward integrating the Amazon into the national territory and international economy. These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted. Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that (Hecht and Cockburn 1990). With the return of democracy in the 1980s, violence could not be used at the same extent as before and policies had to respond to growing environmental concern.

Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well. When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally (Brice and Smith 2021; Harris 2021; Miranda 2021), but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon. Deforestation rates in Brazil are more responsive to the government’s environmental policy than exogenous factors as market fluctuations (Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021). Ethnographic research has also shown that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground (Campbell 2015).

The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped. Calderwood (2019), for instance, examines 2919 mentions of climate change in American official presidential speeches since 1989. Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change. He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects. Calderwood (2020) also tests the effect of geographic location and type of communication regarding climate change. Building prominently on Putnam (1988), he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt. The author finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location. Elsewhere, Bevitori (2015) investigates how the ‘environment’ has been constructed in American presidential discourse since 1960 using a more automated approach. The author finds that mentions of the environment are typically co-selected with the pronoun ‘our’, as well as with ‘economy’, ‘clean’, and ‘preserve’. These studies corroborate the possibilities of variation depending on the audience, but we are yet to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change. While these findings are US specific, they indicate that presidents raise different points about the environment at local, national, or international settings, depending on who they assume their audience is at that specific instance. Nevertheless, as Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history. Mentions to the lexicon as ‘environment’, ‘preserve’, or ‘climate change’ should be tied to the larger meaning of policies in the United States and elsewhere.

On the other hand, there is also an empirical gap in terms of how the Amazon has been constructed as a problem along time and geographic location. While governmental discourses in Brazil have been studied for topics such as inflation or race relations, we only find one systematic analysis of Amazonian discourse. Barros (2020) investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen. The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).

We propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy issue and connects it to presidential speeches. Governments choose what problems to solve and what policies to implement. The same policies can be represented as solving different problems implying a degree of social construction (Bacchi 2009). Governments can choose to emphasize or not one or more implicit problems that a policy solves depending on which interest group they are in communication with. The variation in problem-construction suggests that Brazilian governments are more diverse in their positions as the literature suggests. An interesting site to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for democracy, and for environmental outcomes. As presidents speak in different places and to different audiences, it is an empirical site prone to identify variation.

## 2.2 Problem-construction in Amazonian historiography

To identify possible problem-constructions and their connection to the wider socio-cultural history of the country, we build on Amazonian historiography. We understand Amazonian historiography as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.

### National Sovereignty

In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites” (1990, 1). These dreams of fortunes to be found in the Amazon are composed of the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else. It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as “a (...) form of nation building (...)” (Hecht and Cockburn 1990, preface). The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory. In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” (Hecht 2013, 8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian. While Brazilian military diplomacy was very successful, the process did not come without its traumas. A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn 1990). This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat during the Cold War (Garfield 2013).

As we move from a world where non-state actors gain importance in environmental governance and international politics generally (Silva-Muller and Faul 2022; Andonova 2014; Westerwinter 2021), the sovereignty problem becomes more varied. Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end (Hochstetler 2021; Capobianco 2019; Franchini and Viola 2019). Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before. Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of ‘internationalizing’ the Amazon. This might come both from foreign actors as well as domestic non-state actors. The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil while any foreign or non-state presence in the region is part of a broad strategy to take the region. The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combating alleged disinformation from actors perceived as a threat.

### Economic Integration

The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon. In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2014). First, nature should be conquered by men. Second, exploiting natural resources would render the Amazon region a global powerhouse. Third, such a project would integrate the region with the rest of the country. Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, and the establishment of tax-free zones to attract industry. The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2014), leading to a series of national and international enterprises settling in the Amazon region. Capobianco (2019) describes the period from the 1950s to the 1980s in a similar fashion, referring to a wider range of policies of economic integration such as the establishment of the tax-free zone of Manaus in the 1970s. The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized. These policy solutions are often centralized by the federal government (Becker 2005) and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.

### Social Development

Closely related to economic integration, a problem-construction that is often neglected while describing policy cycles is social development. Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and constitutional rights when speaking about the Amazon. This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.

### Environmental Conservation

The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions (Drummond and Barros-Platiau 2006). A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region (Acker 2021; Capobianco 2021; Hecht and Cockburn 1990). This process accelerated in the late 1980s, with the birth of modern environmentalism (Viola 1987) in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco 2021). Hochstetler and Keck (2007) argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism. They define it as an emphasis on the local livelihoods of people while protecting nature. Capobianco (2019) argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies as establishment of conservation units in the Amazon in 2001. The environmental conservation problem-constructions emphasizes the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination (Hochstetler and Keck 2007). The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.

# 3 Methodology: operationalizing Amazonian problem-constructions

## 3.1 Codebook and Data

To analyze how presidents construct the Amazon as a problem in time, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library. We update the dataset by scraping and adding all official speeches from 2020 and 2021. The final dataset encompasses 6130 speeches for all the presidents of Brazil since 1985. Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest out of the 6130 speeches. We do so by detecting all speeches in which the stem “amazon” appears. In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others. We find that 946 speeches are, at least partially, about the Amazon from the 6130.

Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears. We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea. By doing so we create our unit of analysis: an Amazonian statement. We use Amazon statements as our unit of analysis for two main reasons. First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose. Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis. This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified. When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match. On average, an Amazonian statement contains 123 words.

We develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix). In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem. Nevertheless, each Amazonian statement might be assigned to one or more codes. A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation. Amazonian statements, thus, can be either coded as pure-types or mixed-types. Mixed-types are relevant as constructions and policies are often multifaceted while portraying the Amazon as a combination of these problem-constructions. Figure 1 portrays this operationalization strategy.

```{r figure1, echo=FALSE, fig.cap="Figure 1: Operationalization of Problem-constructions", out.width = '100%'}
knitr::include_graphics("figure1.png")
```

With the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements. This amount refers to 50% of all the Amazon Statements identified. We chose to hand code half of the observations because since there are several nuances in discourse in how presidents talk about the amazon in time and as a problem, we conservatively code a relatively large training set for the subsequent automated machine learning. As well, this allows a robust validation set to verify the models. Still, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding. Intercoder agreement for each of the four main categories was 85%, on average. For each non-matching coded observation, the co-authors discussed and sorted their disagreements. The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).

We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [Meyer et al. (2021); Noble (2006)] . The SVM model is first trained using the hand coded training set and then employed to classify observations in the hand coded validation set. The trained SVM model was, on average 82%, accurate in classifying observations in the validation set before being tuned. After the SVM model is tuned, we use the model to automatically code the remaining 1007 Amazonian statements. The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements. Finally, we extract locations for all speeches in the data. These locations represent the Brazilian state in which certain speech was given or an international country.

## 3.2 Analysis and Limitations

To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents. We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves. To test whether different problem constructions change according to location, we run a multinomial logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable. Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case (Kwak and Alan Clayton-Matthews 2002). In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model. We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.

This approach also comes with limitations. Our codebook is developed using specific Amazon-related vocabulary. For example, a statement will be coded as economic integration if it is meaningful support to the tax-free zone of Manaus or a Dam in the Amazon. However, the economy is generally a topic that presidents speak about. Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time. Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”. We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”. Hence, we might be missing statements about Amazon that do not refer to it. However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica. Nevertheless, our dataset covers only what is considered an official remark. Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently started to appear on social media. Problem- construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.

# 4 The Amazon in Presidential Speeches

## 4.1 The rises and falls of the Amazon as a topic in presidential speeches

Mentions of the Amazon across official presidential speeches vary in time. Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches each year. We observe various local maxima: 1989, 1992, 2009, 2015, and 2019. These points, usually, coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time. For example, in 1985 the Amazon appeared in about 4% of all the presidential speeches. By 1989, the Amazon appeared in 32% of all speeches. This is the period when the Brazilian Constitution was written. Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and the protection of their territories (Hecht and Cockburn 1990). These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory. Besides,  other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered and the New York Times published an article with pictures of the Amazon burning (Simons and Times 1988). Both incidents caught unprecedented international attention and Sarney responded to these publicly with a set of policies to address deforestation (Capobianco 2021).

```{r Figure 2: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc=n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
######## Issue is with biblioteca presidencial, not with scarping btw ######
# summary(as.factor(pop$year))
# Simple plot
Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  scale_y_continuous(labels = percent_format()) +
  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
  geom_vline(xintercept = c(1988, 1992, 2009, 2015),
             linetype = "dotted") +
  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
       subtitle = "Sample composed by 6130 presidential speeches since 1985",
       caption = "",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
           alpha = 0.1) +
  annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
           label = hp$presid, alpha = 0.4)
# # # With a few lines under the
# cat1 <- ama_mx %>%
#   mutate(cat = ifelse(mx_cat2 == "Mixed-types", "Mixed-types", paste(mx_cat))) %>%
#   count(cat, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc_type = ifelse(perc == 1, 0.25, perc)) %>% 
#   arrange(year) %>%
#   select(c(cat, year, perc_type))
# year_share <- merge(perc1, cat1, "year") %>%
#   mutate(year_perc = perc*perc_type)
# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(y = perc)) +
#   scale_y_continuous(labels = percent_format()) +
#   geom_line(aes(x = year, y = year_perc, fill = cat, group = cat, color = cat)) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
#              linetype = "dotted") +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "",
#        color='Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# # For filling the area under the line
# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = year_perc, fill = cat)) +
#   geom_line() +
#   geom_area() +
#   scale_y_continuous(labels = percent_format()) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_vline(xintercept = 1988, linetype = "dotted") +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
#   geom_vline(xintercept = 1992, linetype = "dotted") +
#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) +
#   geom_vline(xintercept = 2009, linetype = "dotted") +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
#   geom_vline(xintercept = 2015, linetype = "dotted") +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "",
#        color = 'Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# # Controling for inflation and deforastation
# pop2 <- pop %>% count(amazon_speech, year, president) %>%
#   group_by(year, president) %>%
#   left_join(perc1) %>%
#   filter(amazon_speech==1)
# pop2 <- left_join(pop2, AAI, by = "year")
# pop2 <- left_join(pop2, amazon_def_year, by = "year")
# model <- lm(perc ~ AAI+ def_year + president, data=pop2)
# pop2$predicted = predict(model, pop2)
# Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
#   geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
#   geom_vline(xintercept = 1988, linetype="dotted") +
#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) + 
#   geom_vline(xintercept = 1992, linetype="dotted") +
#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) + 
#   geom_vline(xintercept = 2009, linetype="dotted") +
#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) + 
#   geom_vline(xintercept = 2015, linetype="dotted") +
#   scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
#   scale_y_continuous(labels = percent_format()) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
#        caption = "Predicted share controls for deforestation rates, inflation, and president.",
#        color='Y series') +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
Amazon_year
```

In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches. The 1992 Earth Summit, held in Brazil, and prepared by various state and non-state actors in the region, brought international attention to environmental topics. One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (Capobianco 2021). Throughout the 1990s and 2000s, however, the Amazon appeared, on average, on 15% of all speeches. By the end of the 2000s, we see another spike in the Amazon appearing in official speeches. This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available. Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high (Franchini and Viola 2019).

From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches. The Amazon appeared in 8% of official speeches in 2014. In 2015, the Amazon appeared in 19% of speeches.  This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen. Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010. These are also the years when Brazil entered a long period of political and economic instability, which led to the impeachment of Dilma Roussef. Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation since Marina Silva left the government and the 2011 New Forest Code was approved. By 2016, however, mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.

We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro’s presidency, 2019. At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets (cite). This brought environmental issues as high priorities in Bolsonaro’s governing agenda. At the same time, President Bolsonaro retrieves Brazil’s hosting status for COP25 and begins to dismantle Brazilian environmental governance (cite).

## 4.2 How has the Amazon been constructed as a problem?

### Pure-type problem constructions

We conceptualize four pure problem constructions: sovereignty, economic integration, social development, and conservation. At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement. Pure problem constructions dominate, average around 56% of all amazonian statements across time. As above, we observe a strong variation over time for most of these constructions. Figure 3, below, illustrates the share of each pure type in time.

```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
pure_types_time <- ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>% 
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure type by year",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = c(0.85, 0.8)) +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
           alpha = 0.1) +
  annotate(geom = "text", x = hp$label, y = 0.02, vjus = 0.3,
           label = hp$presid, alpha = 0.4)
pure_types_time
```

The plot reveals several trends. Pure economic integration constructions, for example,  dominated constructions from 1985 to the late 2000s. This is especially pertinent during the Cardoso administration as the Amazon was constructed overwhelmingly as an issue of economic integration. This changed during the Lula presidency. During his terms, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased. These constructions surpassed economic integration around 2010. These trends in discourse continued during the Rousseff administration. Capobianco (2021), for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.  A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being país to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.

From the mid-2010s onwards, we start to see a reverse of this trend: economic integration problem construction increases while conservation and social development constructions decrease instead. Interestingly, sovereignty starts to increase steadily from 2010 onwards and by 2019 sovereignty constructions surpass social development.  construction. Figure 3 also highlights that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty constructions reached their peak since 1985.

### Mixed-type problem constructions

Although presidents prefer pure problem-constructions, presidents also construct the Amazon as multifaceted issues. Mixed-type problem constructions in discourse offer more complex understandings of the Amazon as an issue. Constructing the Amazon as multiple issues averages at 18% of all constructions for presidents. While there is some variation in time and some mixed-types rarely appear, we focus our discussion on those mixed-types with higher incidence. Figure 4, below, displays the average mixed-types in time.

```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mixed_types_presid <- ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 3, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "right")
mixed_types_presid
# mixed_types_time <- ama_mx %>%
#   count(mx_cat, mx_cat2, year) %>%
#   group_by(year) %>%
#   mutate(perc = n / sum(n),
#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
#   filter(mx_cat2 == "Mixed-types") %>% 
#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
#        caption = "") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom") +
#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
#            alpha = 0.1) +
#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
#            label = hp$presid, alpha = 0.4)
# mixed_types_time
```

The most frequent mixed-type problem construction of the Amazon in discourse across presidents and in time is economic corsevation. The mixed-type is composed of Amazonian statements that are coded both as economic integration and environmental conservation. Economic conservation averages at 6.8% in relation to all Amazonian statements. The mixed type generally increased in time with Bolsonaro employing the mixed-type higher than others, followed by Lula. The second most common mixed-type across presidents and in time mixes economic integration and social development and appears, on average, 5.4% of all statements. Notoriously, Lula employs such a mix-type more frequently than other presidents. In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than all other presidents. While Lula, on the one hand, often mixes economic integration with conservation and social development when constructing the Amazon as an issue in discourse, Bolsonaro, on the other hand, often mixes sovereignty with other problem constructions. Indeed, we see that Bolsonaro constructs the Amazon as an issue of sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region (Hecht and Cockburn 1990).

## 4.3 The Amazonian multi-level game, boasting policy outside and talking to people inside

Problem constructions depend on where presidents speak. To facilitate analysis and make sense of locations, we divide locations into Amazonian states (i.e. all the Brazilian states in which the Amazon biome is present), non Amazonian states (other Brazilian states), Brasilia (the capital of Brazil where the federal government is located), Amazonian countries (neighboring countries where the biome is present), and international countries (countries outside of Brazil). To analyze the relationship between location and problem construction, we run a multinomial regression. Our dependent variable is problem-constructions (categorical), while our main dependent variable is location (categorical). The reference category for the multinomial model is, thus, environmental conservation in international states. We control for deforestation rates (numerical), inflation (numerical), and election year. Since the model accounts for both mixed and pure-type Amazonian constructions, and this makes for a large table, we focus the analysis on pure-types to facilitate visualization (see full regression table in appendix).

Figure 5, below, shows the relative probability of problem-constructions by location in relation to environmental conservation internationally derived from the regression model. The plot illustrates the percentage of constructing the Amazon as a certain issue according to location in relation to the reference category. From the figure we see, for example, that presidents are 33% more likely to construct the Amazon as an issue of economic integration within other Amazonian countries in comparison to other countries. Although without the same strength, the finding also holds at the state level within Brazil, as presidents are 11% more likely to construct the Amazon as an issue of economic integration within Amazonian states and 15% more likely in non Amazonian states. Interestingly, presidents are less likely to construct the Amazon as an issue of economic integration in Brasilia than internationally. That is, when speaking internationally or in Brasilia, presidents often construct the Amazon as an issue of environmental conservation.

```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year)
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation",
                                            "Economic and Social Development", "Sovereign Conservation",
                                            "Sustainable Development","Sovereign Integration",
                                            "Social Conservation", "Other")),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname", location),
                                     "Amazonian Countries", location_cat),
                               levels = c("International", "Amazonian States",
                                          "Amazonian Countries", "Brasilia", "Non Amazonian States"))) # separating Amazonian countries
# model
model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                  data = ama_model, model = TRUE, trace = FALSE)
# summary statistics
model_summary <- summary(model)
p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
                data = iia_data, model = TRUE, trace = FALSE)
iia_summary <- summary(iia)
iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
# Model coefficients, and p-values, are statistically identical even when we drop the largest
# factor category from model. Therefore, we can proceed with a multinomial logit model,
# instead of a multinomial probit model, since the independence of irrelevant alternatives 
# Other post estimation tests
chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
# Chi-square p value (p-value < 0.001) tells us that our model explains a
# significant amount of the variation in the data in comparison with a null model.
# But too much information on the summary tables... Let's just focus on what we want here:
logit2prob <- function(logit) {
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
} # to transform log odds in probabilities
md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
                      "Amazonian_Countries" = c(1.3411972, 1.2460915, 0.9310706),
                      "Amazonian_States" = c(0.4578251, 1.4725563, 1.6281365),
                      "Non_Amazonian_States" = c(0.6198104, 1.5838611, 1.9830952),
                      "Brasilia" = c(-0.29279984, 0.59564579, 1.38333572))
md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
md_plot$'Amazonian States' <- logit2prob(md_plot$Amazonian_States)
md_plot$'Non Amazonian States' <- logit2prob(md_plot$Non_Amazonian_States)
md_plot$'Amazonian Countries' <- logit2prob(md_plot$Amazonian_Countries)
mplot <- md_plot %>%
  select(-c("Amazonian_Countries", "Amazonian_States", "Non_Amazonian_States")) %>% 
  tidyr::pivot_longer('Amazonian Countries':Brasilia) %>%
  mutate(Percentage = 100*round(value, digit = 2)-50) %>%
  mutate(Location = factor(name, levels = c("Amazonian Countries", "Amazonian States",
                           "Non Amazonian States", "Brasilia"))) %>% 
  ggplot(aes(x = Location, y = Percentage, fill = Construction)) +
  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  scale_y_continuous(breaks = seq(-15, 40, 10), limits = c(-15, 40)) +
  geom_text(aes(label = Percentage), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "red") +
  labs(x = "", y = "Percentage",
       title = "Percentage for problem constructions across locations",
       subtitle = "Reference location is International and category is environmental conservation problem-construction") +
    theme(panel.background = element_rect("white", "black", .5, "solid"),
          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
          axis.text = element_text(color = "black", size = 10),
          title = element_text(color = "black", size = 10, face = "bold"),
          legend.title = element_blank(),
          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
          legend.position = c(0.50, 0.16))
mplot
```

Along these lines, constructing the Amazon as an issue of social development takes place, overwhelmingly, within Brazil or other Amazonian countries. Presidents are at least 14% more likely to construct the Amazon as an issue of social development in these locations than internationally. The same is true for sovereignty,  whereas constructing the Amazon as an issue of sovereignty takes place within Brazil or in neighboring Amazonian countries. Notice, as well, how Amazonian constructions within Amazonia states and non Amazonian states are strikingly similar. This indicates that presidents are consistent when constructing the Amazon locally across the federation when outside of Brasilia.

The Amazon, as a region and a forest, has historically been the topic of international, national, supranational, and local debates, negotiation and policies. Our findings show that how the amazon is constructed as a problem varies across these levels. This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” could differ as well. The multi-level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not for local electorates. Local electorates who, ultimately, elect presidents.

This multi-level game leads to different policies being negotiated, often simultaneously, so that the overlap at the interplay between the levels is maximized. Take, for once, how the Brazilian government successfully funded domestic public policy with international support since the 1990s (e.g. 1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g. 2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD1 billion for environmental conservation in the Amazon (Silva-Muller and Faul 2022). Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued. During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 (Capobianco 2021). Nowadays, it has reached unprecedented levels.

# 5 Discussion and Conclusion

The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse in Amazonian States compared to Brasilia and other States. Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what “they want to hear”. If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands. Or, as Putnam (1988) puts it, what’s the actual overlap between the international and domestic overlap. The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide. With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration and the rise of social and conservation problem-constructions as a new relationship between granting local livelihoods their rights and economic exploitation.

While unprecedented, this new balance was not long-standing. Democratic decay is slow, and the embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office. We observe the decrease in conservation-related statements in the mid-2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3). The hard increase in sovereignty comes in the early 2010s. As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks on indigenous and traditional populations. On the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists. The political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest. Bolsonaro’s problem-construction is the strongest form of this shift.

In sum, this paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985. Our findings show that these constructions are not monolithic within governments, in time, or across different locations. Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to outcomes such as policies and environmental outcomes. Empirically, we build the first comprehensive overview of the Amazon in presidential discourse. Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level, further research on the relationship between the social construction of the Amazon, one of the worlds most important standing ecosystems, and its effects on environmental outcomes is pressing.

# Appendix

````{=tex}
\begin{landscape}

```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}

codebook <- tibble::tibble("Problem Construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty. We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory. Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon. In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration. It advances the view that the Amazon needs to be developed and connected to the national economy. This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development. It advances the view that Amazon is full of citizens who should have their rights guaranteed. This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house). This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light. Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation. This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region. The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered. It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity. I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting. I would like to thank the Chinese government. For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil. (Bolsonaro 25/10/2019)",
                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions. We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway. This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas. We have invested over 14 billion reais in this program, in three and a half years. Do you know how many electrical lines we have already built? One million kilometers of lines. (Lula 20/11/2009)",
                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process. This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr. Mesquita (Sarney 20/07/1989)"))

kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")

```

\end{landscape}
````

````{=tex}
\begin{landscape}

```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}

full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
                                           "SOV-EI", "SD-CON", "Other"),
                  "Amazonian States" = c("0.458 (0.193)", "1.473*** (0.215)",
                  "1.623*** (0.235)", "-0.056 (0.292)", "1.625*** (0.198)",
                  "0.960*** (0.284)", "1.192*** (0.271)", "1.345*** (0.290)",
                  "0.129 (0.323)", "0.999*** (0.207)"),
                  "Amazonian Countries" = c("1.341*** (0.212)", "1.246*** (0.308)",
                  "0.931** (0.383)", "0.304 (0.394)", "1.569*** (0.288)",
                  "0.613*** (0.090)", "0.949*** (0.0857)", "2.609*** (0.345)",
                  "0.660** (0.332)", "1.760*** (0.226)"),
                  "Brasilia" = c("-0.293** (0.183)","0.596*** (0.210)",
                  "1.383*** (0.209)", "-0.245 (0.265)", "0.823*** (0.193)",
                  "0.890*** (0.237)", "0.123 (0.277)", "0.276 (0.310)",
                  "-0.594** (0.317)", "0.0649 (0.202)"),
                  "Non Amazonian States" = c("0.620** (0.212)", "1.584*** (0.219)", "1.983*** (0.238)",
                  "0.242 (0.311)", "1.637*** (0.223)", "1.309*** (0.283)",
                  "0.871*** (0.308)", "1.418*** (0.323)", "0.217 (0.342)", "0.849*** (0.231)"),
                  "Election Year" = c("-0.517*** (0.160)", "-0.007 (0.192)",
                  "-0.733*** (0.277)",
                  "-0.016 (0.232)", "-0.453* (0.255)", "-0.691* (0.378)",
                  "0.080 (0.343)", 
                  "-1.400*** (0.429)","0.0008 (0.378)", "-0.713*** (0.170)"),
                  "Annual Deforestation" = c("0.082*** (0.011)", "-0.037** (0.015)",
                  "0.001 (0.018)", 
                  "0.0197 (0.0170)", "0.060*** (0.017)", "0.012 (0.024)",
                  "-0.026 (0.026)", 
                  "-0.007 (0.027)", "-0.002 (0.027)", "0.076*** (0.0120)"),
                  "Average Inflation" = c("-0.0005*** (0.0001)", "-0.0005*** (0.0001)",
                  "-0.0001 (0.0002)", "-0.0006*** (0.0001)", "-0.0005** (0.0002)",
                  "0.0001 (0.0002)", "-0.0008** (0.0004)", "-0.0004 (0.0004)",
                  "-0.0006* (0.0004)", "-0.0003*** (0.0001)"))
kbl(t(full_md), booktabs = T,caption = "Multinomial Regression Full", align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down"),
                position= "center", font_size = 9, full_width = TRUE) %>%
                footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>% 
  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
  column_spec(2, width="2 cm", latex_valign = "m") %>%
  column_spec(3, width = "2 cm", latex_valign = "m") %>%
  column_spec(4, width = "2 cm", latex_valign = "m") %>%
  column_spec(5, width="2 cm", latex_valign = "m") %>%
  column_spec(6, width = "2 cm", latex_valign = "m") %>%
  column_spec(7, width = "2 cm", latex_valign = "m") %>% 
  column_spec(8, width="2 cm", latex_valign = "m") %>%
  column_spec(9, width = "2 cm", latex_valign = "m") %>%
  column_spec(10, width = "2 cm", latex_valign = "m") %>% 
  column_spec(11, width = "2 cm", latex_valign = "m")
```

\end{landscape}
````

# References

### 2022-05-19 Draft_May_2022/Full_draft_20220510.rmd
Some more changes to code in files

@@
 Both of them are PhD candidates at The Geneva Graduate Institute.
-Livio is affiliated to the Albert Hirschman Centre on Democracy.
-Henrique is affiliated to the Centre for International Environmental Studies.]
+Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Instituteis affiliated to the Albert Hirschman Centre on Democracy.
+Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute affiliated to the Centre for International Environmental Studies.]
 date: "May 2022"
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
+adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data
+amazon_def_year <- rbind(adr, amazon_def_year) 
 hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom") +
-  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
-           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
-           alpha = 0.1) +
-  annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
-           label = hp$presid, alpha = 0.4)
+        legend.position = "bottom")
+# # Same plot but annotated
+# Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+#   geom_line(color = "darkgreen") +
+#   scale_y_continuous(labels = percent_format()) +
+#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
+#              linetype = "dotted") +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
+#        caption = "",
+#        color='Y series') +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom") +
+#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
+#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
+#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
+#            alpha = 0.1) +
+#   annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
+#            label = hp$presid, alpha = 0.4) +
+#   annotate(geom = "segment", x = amazon_def_year$year, y = amazon_def_year$def_year)
 # # # With a few lines under the
@@
 ```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-amazon_def_year <- rbind(adr, amazon_def_year)
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge

### 2022-05-20 Draft_May_2022/Full_draft_20220510.rmd
Added latest draft version to rmd file

@@
 - Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically.
-Both of them are PhD candidates at The Geneva Graduate Institute.
-Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Instituteis affiliated to the Albert Hirschman Centre on Democracy.
-Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute affiliated to the Centre for International Environmental Studies.]
-date: "May 2022"
+Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Institute and affiliated to the Albert Hirschman Centre on Democracy.
+Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
+date: "20 May 2022"
 output:
   pdf_document: default
+  fig_caption: yes
   html_document:
@@
     reference_docx: template.docx
+header-includes:
+   - \usepackage{floatrow}
+   - \floatsetup[figure]{capposition=top}
 always_allow_html: TRUE
@@
                                       mixed_type == '0_1_0_1' ~ "Economic Conservation",
-                                      mixed_type == '0_1_1_0' ~ "Economic and Social Development",
+                                      mixed_type == '0_1_1_0' ~ "Social Economic",
                                       mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
-                                      mixed_type == '0_1_1_1' ~ "Sustainable Development",
-                                      mixed_type == '1_1_0_0' ~ "Sovereign Integration",
+                                      mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
+                                      mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
                                       mixed_type == '0_0_1_1' ~ "Social Conservation",
@@
          levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
-                    "Pure Sovereignty", "Other", "Economic Conservation", "Economic and Social Development",
-                    "Sovereign Conservation","Sustainable Development","Sovereign Integration",
-                    "Social Conservation", "Other Mixed-types")),
+                    "Pure Sovereignty", "Other", "Economic Conservation", 
+                    "Social Economic", "Sovereign Conservation", "Economic, Social,\nand Conservation",
+                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
          mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
@@
                              grepl("^Other$", mx_cat) ~ "Other",
-                             grepl("Economic Conservation|Economic and Social Development|
-                                   |Sovereign Conservation|Sustainable Development|
-                                   |Sovereign Integration|Social Conservation|Other Mixed-types",
+                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
+                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
+                                   |Social Conservation|Other Mixed-types",
                                    mx_cat) ~ "Mixed-types"),
@@
 
-Different governments along Brazilian history have been described as proponents of a specific view of the Amazon (Drummond & Barros-Platiau 2016; Padua 2012; Franchini & Viola 2019; Capobianco 2019; Pereira & Viola 2021).
-For example, while the military dictatorship is associated with both national sovereignty and then economic integration, President Sarney and President Lula are often tied to environmental conservation.
+Different governments along Brazilian history have been described as proponents of a specific view of the Amazon (@Drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021).
+While the military dictatorship is associated with both national sovereignty and then economic integration, President Sarney's presidency is often tied to environmental conservation.
 However, governments are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of one specific problem.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes (Waroux et al.
-2021), we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between and within governments.
+Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes (@lepolaindewaroux2021), we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
 
@@
 We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences (Zarefsky 2004).
+First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences (@zarefsky2004).
 It legitimizes ways of thinking about the Amazon.
-In turn, policy perception is key for policy adoption and implementation (Alesina and Giuliano 2009; López et al.
-2020).
-This is especially pertinent as deforestation rates in Brazil are associated with expectations from government, generated from material and discursive governmental practices (Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021), and are a crucial factor in decisions to deforest at the ground (Campbell 2015).
-Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on where they are.
+In turn, policy perception is key for policy adoption and implementation (@alesina2009; @lopez2020).
+This is especially pertinent to deforestation in Brazil as expectations from governments’ response, generated from material and discursive governmental practices (@assuncao2015; @capobianco2019; @capobianco2021), are a crucial factor in decisions to deforest at the ground (@campbell2015).
+Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
 Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better how the Amazon is socially constructed.
+Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is socially constructed.
 
-To investigate how the Brazilian Amazon has been constructed as a problem in political discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
+To investigate how the Brazilian Amazon has been constructed as a problem in presidential discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
 We subset the dataset by identifying Amazonian related statements within these speeches.
@@
 We train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data, tying our findings to endogenous and exogenous events related to deforestation.
+We then conduct a descriptive and inferential analysis of this data.
 
-We find that, first, international environmental events appear to drive presidents to speak more about the Amazon.
-Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards.
+Our findings are threefold.
+First, we find that international environmental events appear to drive presidents to speak more about the Amazon.
+Second, while constructing the Amazon as a problem of economic integration dominated presidential discourses from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew from 2000s onwards briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
+Unprecedentedly, constructing the Amazon as an issue of sovereignty became more pertinent from 2010 onwards.
 Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
@@
 Governments often have a choice in how they construct problems and what policy solutions they implement.
-In “Journey towards Progress”, Hirschman (1963) draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
+In “Journey towards Progress”, @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
 Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
 Chosen problems are those governments select at their discretion.
-Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers (Hirschman 1963, 388–91).
-As Bacchi argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
-(2009, 10).
+Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers (@hirschman1963, p.
+388–91).
+As @bacchi2009 argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
+(p.
+10).
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
 The alleged problem is not always explicitly stated in policy.
-Hirschman exemplifies chosen problems with the case of the construction of Brasilia (1975, 388).
+@hirschman1975 exemplifies chosen problems with the case of the construction of Brasilia (p.
+388).
 But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
@@
 The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
-Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural cadaster for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
+Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
 The same policy, then, can solve the problem of environmental conservation as well as economic integration.
@@
 This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests.
-Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases (see Drummond & Barros-Platiau 2016; Padua 2012; Franchini & Viola 2019; Capobianco 2019; Pereira & Viola 2021).
-In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy (Drummond & Platiau 2016).
+Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases (see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021).
+In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy (@drummond2006).
 The governments from the late 1980s up to 2009, are more associated with environmental conservation.
@@
 The presidency of Lula, often associated with environmental conservation because we saw an unprecedented decrease in deforestation.
-At the same time, during his terms governmental credits to agricultural expansion and the cattle industry surpassed BRL 578 billion (Capobianco, 2021, 106).
-This sum is about 20 times more than the budget of the Ministry of the Environment for this entire period.
-There is more variation within governments than the literature suggests.
+At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period (@capobianco2021, p.
+106).
+That is, there is more variation within governments than the literature suggests.
 
 An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue and.
-While the relationship between presidential speeches and policy is not causal (Lawrence 2004), they have the power to introduce and justify public policy, as well as shape its perception to broad audiences (Zarefsky 2004).
+While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences (@zarefsky2004).
 Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem (Eshbaugh-Soha 2010; Rottinghaus 2009; Krebs and Jackson 2007), they direct the range of what is included in national debates (Druckman and Holmes 2004).
@@
 If presidents can promote different problem-constructions in different places, it is important to understand to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
-Pacheco (2019) proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
+@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
 Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
@@
 These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted.
-Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that (Hecht and Cockburn 1990).
+Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that (@hecht1990).
 With the return of democracy in the 1980s, violence could not be used at the same extent as before and policies had to respond to growing environmental concern.
@@
 Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally (Brice and Smith 2021; Harris 2021; Miranda 2021), but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
-Deforestation rates in Brazil are more responsive to the government’s environmental policy than exogenous factors as market fluctuations (Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021).
-Ethnographic research has also shown that policy expectations, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest at the ground (Campbell 2015).
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally (@brice2021; @harris2021; @miranda2021), but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
+Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations (@assuncao2015; @capobianco2019; @capobianco2021).
+Ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground (@campbell2015).
 
@@
 
-Closely related to economic integration, a problem-construction that is often neglected while describing policy cycles is social development.
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and constitutional rights when speaking about the Amazon.
+Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles is social development.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights when speaking about the Amazon.
 This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.
@@
 We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches for all the presidents of Brazil since 1985.
-Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest out of the 6130 speeches.
+The final dataset encompasses 6130 speeches for all the presidents of Brazil.
+Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
 We do so by detecting all speeches in which the stem “amazon” appears.
@@
 Mixed-types are relevant as constructions and policies are often multifaceted while portraying the Amazon as a combination of these problem-constructions.
-Figure 1 portrays this operationalization strategy.
+Figure 1, below, portrays this operationalization strategy.
 
-```{r figure1, echo=FALSE, fig.cap="Figure 1: Operationalization of Problem-constructions", out.width = '100%'}
-knitr::include_graphics("figure1.png")
+\begin{landscape}
+
+```{r figure1, echo=FALSE, fig.cap="Operationalization of Problem-constructions", out.width = '100%', include=TRUE}
+knitr::include_graphics("figure1pic.png")
 ```
+
+\end{landscape}
 
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [Meyer et al.
-(2021); Noble (2006)] .
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories (Meyer et al.
+(2021); Noble (2006)) .
 The SVM model is first trained using the hand coded training set and then employed to classify observations in the hand coded validation set.
@@
 
-Mentions of the Amazon across official presidential speeches vary in time.
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches each year.
-We observe various local maxima: 1989, 1992, 2009, 2015, and 2019.
+The frequency in which the Amazon appears across all official presidential speeches varies in time.
+Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches per year.
+We observe five local maxima: 1989, 1992, 2009, 2015, and 2019.
 These points, usually, coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
-For example, in 1985 the Amazon appeared in about 4% of all the presidential speeches.
-By 1989, the Amazon appeared in 32% of all speeches.
+For instance, in 1985 the Amazon appeared in about 4% of all the presidential speeches but by 1988 this had increased to around 14%.
 This is the period when the Brazilian Constitution was written.
@@
 These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-Besides,  other factors are likely to explain this increase: in 1988 Chico Mendes was brutally murdered and the New York Times published an article with pictures of the Amazon burning (Simons and Times 1988).
-Both incidents caught unprecedented international attention and Sarney responded to these publicly with a set of policies to address deforestation (Capobianco 2021).
+However, in 1989, the Amazon appeared in 32% of all speeches.
+This spike is likely explained by the brutal murder of Chico Mendes and the very end of 1988 (Simons and Times 1988).
+An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation (Capobianco 2021).
 
-```{r Figure 2: Amazonian speeches by year, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 perc1 <- pop %>%
@@
   scale_y_continuous(labels = percent_format()) +
-  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
+  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
@@
   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-  geom_vline(xintercept = c(1988, 1992, 2009, 2015),
+  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
              linetype = "dotted") +
@@
 In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
-The 1992 Earth Summit, held in Brazil, and prepared by various state and non-state actors in the region, brought international attention to environmental topics.
+The 1992 Earth Summit, held in Brazil brought international attention to environmental topics in the Amazon.
 One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (Capobianco 2021).
-Throughout the 1990s and 2000s, however, the Amazon appeared, on average, on 15% of all speeches.
-By the end of the 2000s, we see another spike in the Amazon appearing in official speeches.
+Throughout the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon appeared, on average, on 15% of all speeches.
+Exceptionally, in 2009 we see another spike in the Amazon appearing in official speeches.
 This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
@@
 From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-The Amazon appeared in 8% of official speeches in 2014.
-In 2015, the Amazon appeared in 19% of speeches.
+From 2010 to 2014, mentions of the Amazon went down from 18% to 8% in official speeches.
+Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
+In 2011, the New Forest Code, which regularized land ownership of many illegally deforested areas, was also approved.
+These are also the years when Brazil entered a long period of political and economic instability, which eventually led to the impeachment of Dilma Roussef.
+Though, in 2015, the Amazon appeared in 19% of speeches.
 This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
-These are also the years when Brazil entered a long period of political and economic instability, which led to the impeachment of Dilma Roussef.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen, and a perception that there was a turn towards less conservation since Marina Silva left the government and the 2011 New Forest Code was approved.
-By 2016, however, mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
+Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation.
+By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
 
@@
 At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets (cite).
-This brought environmental issues as high priorities in Bolsonaro’s governing agenda.
-At the same time, President Bolsonaro retrieves Brazil’s hosting status for COP25 and begins to dismantle Brazilian environmental governance (cite).
+This brought issues related to environmental conservation as high priorities in Bolsonaro’s governing agenda with efforts to dismantle key pillars of Brazilian environmental governance (cite).
+At the same time, President Bolsonaro retrieves Brazil’s hosting status for COP25.
+In short, relevant international events drive interest and alter how pressing the “Amazon problem” is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers (see Hirschman 1963).
 
@@
 At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement.
-Pure problem constructions dominate, average around 56% of all amazonian statements across time.
+Pure problem constructions dominate, with an average of  56% of all amazonian statements across time.
 As above, we observe a strong variation over time for most of these constructions.
@@
 
-```{r Figure 3: pure types in time , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 mmt1 <- ama_mx %>%
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = c(0.85, 0.8)) +
+        legend.position = "bottom") +
   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
@@
 
-The plot reveals several trends.
-Pure economic integration constructions, for example,  dominated constructions from 1985 to the late 2000s.
-This is especially pertinent during the Cardoso administration as the Amazon was constructed overwhelmingly as an issue of economic integration.
+Amazonian constructions are not monolithic in time nor within governments.
+The same governments construct the Amazon as different issues in discourse.
+For instance, pure economic integration constructions  dominated constructions from 1985 to the late 2000s.
+This is especially pertinent during the Cardoso administration as the Amazon was constructed, overwhelmingly, as an issue of economic integration.
 This changed during the Lula presidency.
@@
 Capobianco (2021), for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being país to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.
+A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being paid to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.
 
@@
 Interestingly, sovereignty starts to increase steadily from 2010 onwards and by 2019 sovereignty constructions surpass social development.
-construction.
-Figure 3 also highlights that while the reversal precedes the mandate of President Bolsonaro, it was with him and his dismantling of social and environmental policies that sovereignty constructions reached their peak since 1985.
+Figure 3 also highlights that, while the reversal precedes the mandate of President Bolsonaro, it was with him that sovereignty constructions reached unprecedented levels since the establishment of Brazilian democracy.
 
@@
 
-Although presidents prefer pure problem-constructions, presidents also construct the Amazon as multifaceted issues.
+Although presidents prefer pure problem-constructions, they also construct the Amazon as multifaceted issues.
 Mixed-type problem constructions in discourse offer more complex understandings of the Amazon as an issue.
-Constructing the Amazon as multiple issues averages at 18% of all constructions for presidents.
-While there is some variation in time and some mixed-types rarely appear, we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the average mixed-types in time.
+Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
+While there is some variation in time, some mixed-types rarely appear, thus, we focus our discussion on those mixed-types with higher incidence.
+Figure 4, below, displays the average mixed-types by president.
 
-```{r Figure 4: mixed-types by president , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 mixed_types_presid <- ama_mx %>%
@@
 
-The most frequent mixed-type problem construction of the Amazon in discourse across presidents and in time is economic corsevation.
-The mixed-type is composed of Amazonian statements that are coded both as economic integration and environmental conservation.
+The most frequent mixed-type problem construction of the Amazon in time is economic corsevation.
+The mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
 Economic conservation averages at 6.8% in relation to all Amazonian statements.
-The mixed type generally increased in time with Bolsonaro employing the mixed-type higher than others, followed by Lula.
-The second most common mixed-type across presidents and in time mixes economic integration and social development and appears, on average, 5.4% of all statements.
-Notoriously, Lula employs such a mix-type more frequently than other presidents.
-In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than all other presidents.
-While Lula, on the one hand, often mixes economic integration with conservation and social development when constructing the Amazon as an issue in discourse, Bolsonaro, on the other hand, often mixes sovereignty with other problem constructions.
-Indeed, we see that Bolsonaro constructs the Amazon as an issue of sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region (Hecht and Cockburn 1990).
+The mixed type generally increased in time, with Bolsonaro employing the mixed-type higher than all other presidents.
+The second most common mixed-type in time mixes social development and economic integration and appears, on average, in 5.4% of all statements.
+Notoriously, Lula employs such a mix-type more frequently than all other presidents.
+In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
+While Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
+Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region (Hecht and Cockburn 1990).
 
@@
 
-Figure 5, below, shows the relative probability of problem-constructions by location in relation to environmental conservation internationally derived from the regression model.
-The plot illustrates the percentage of constructing the Amazon as a certain issue according to location in relation to the reference category.
-From the figure we see, for example, that presidents are 33% more likely to construct the Amazon as an issue of economic integration within other Amazonian countries in comparison to other countries.
-Although without the same strength, the finding also holds at the state level within Brazil, as presidents are 11% more likely to construct the Amazon as an issue of economic integration within Amazonian states and 15% more likely in non Amazonian states.
+Figure 5, below, shows the percentage of problem-constructions by location derived from the regression model.
+The plot illustrates the percentage likelihood of constructing the Amazon as a certain issue according to location in relation to the reference category, environmental conservation internationally.
+From the figure we see, for example, that presidents are 29% more likely to construct the Amazon as an issue of economic integration within other Amazonian countries in comparison to other international settings.
+Although without the same strength, the finding also holds at the state level within Brazil as presidents are 11% more likely to construct the Amazon as an issue of economic integration within Amazonian states and 15% more likely in non Amazonian states.
 Interestingly, presidents are less likely to construct the Amazon as an issue of economic integration in Brasilia than internationally.
@@
 
-```{r Figure 6: probability for constructions across locations, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
@@
                                             "Pure Social Development", "Pure Sovereignty",
-                                            "Economic Conservation",
-                                            "Economic and Social Development", "Sovereign Conservation",
-                                            "Sustainable Development","Sovereign Integration",
-                                            "Social Conservation", "Other")),
+                                            "Economic Conservation", "Social Economic",
+                                            "Sovereign Conservation", "Economic, Social,\nand Conservation",
+                                            "Economic Sovereignty", "Social Conservation", "Other")),
          location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname", location),
@@
   labs(x = "", y = "Percentage",
-       title = "Percentage for problem constructions across locations",
-       subtitle = "Reference location is International and category is environmental conservation problem-construction") +
+       title = "Percentage for problem constructions across locations\nin relation to environmental conservation problem constructions Internationally",
+       subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
     theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
 Notice, as well, how Amazonian constructions within Amazonia states and non Amazonian states are strikingly similar.
-This indicates that presidents are consistent when constructing the Amazon locally across the federation when outside of Brasilia.
+This indicates that presidents are consistent when constructing the Amazon locally across the federation, when outside of Brasilia.
 
+How the amazon is constructed as a problem varies across levels.
 The Amazon, as a region and a forest, has historically been the topic of international, national, supranational, and local debates, negotiation and policies.
-Our findings show that how the amazon is constructed as a problem varies across these levels.
 This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” could differ as well.
@@
 Local electorates who, ultimately, elect presidents.
-
 This multi-level game leads to different policies being negotiated, often simultaneously, so that the overlap at the interplay between the levels is maximized.
@@
 1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g.
-2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD1 billion for environmental conservation in the Amazon (Silva-Muller and Faul 2022).
+2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD 1 billion for environmental conservation in the Amazon (Silva-Muller and Faul 2022).
 Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued.
@@
 
-The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse in Amazonian States compared to Brasilia and other States.
+The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse within Brazilian states and Amazonian countries compared to Brasilia or internationally.
 Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what “they want to hear”.
@@
 The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide.
-With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration and the rise of social and conservation problem-constructions as a new relationship between granting local livelihoods their rights and economic exploitation.
+With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration problem-construction and the rise of social and conservation constructions as a new balance between granting local livelihoods their rights and economic exploitation.
 
@@
 Democratic decay is slow, and the embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation-related statements in the mid-2010s, and the soft increase of sovereignty both pure and in mixes already late 2000s (figure 3).
-The hard increase in sovereignty comes in the early 2010s.
-As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as attacks on indigenous and traditional populations.
+We observe the decrease in conservation-related statements in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.
+As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as not only attacks to international interference in the Amazon but also on indigenous and traditional populations.
 On the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
@@
 Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to outcomes such as policies and environmental outcomes.
-Empirically, we build the first comprehensive overview of the Amazon in presidential discourse.
-Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level, further research on the relationship between the social construction of the Amazon, one of the worlds most important standing ecosystems, and its effects on environmental outcomes is pressing.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to policies and environmental outcomes.
+Empirically, we provide the first comprehensive overview of the Amazon in presidential discourse.
+Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment, further research on the relationship between the social construction of the Amazon, one of the worlds most important standing ecosystems, and its effects on environmental outcomes is pressing.
 
@@
 
-```{r codebook, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 
@@
 
-```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
+```{r full regression results, fig.cap="Multinomial Regression Results", echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
 

### 2022-05-23 Draft_May_2022/Full_draft_20220510.rmd
added remaining references

@@
 Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level.
-Building on Hirschman’s conceptualization of chosen problems (1963), we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse.
+Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse.
 Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985.
@@
 
-Different governments along Brazilian history have been described as proponents of a specific view of the Amazon (@Drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021).
-While the military dictatorship is associated with both national sovereignty and then economic integration, President Sarney's presidency is often tied to environmental conservation.
+Different governments along Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+While the military dictatorship is associated with both national sovereignty and then economic integration, Sarney's and Lula's presidencies are often tied to environmental conservation.
 However, governments are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of one specific problem.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes (@lepolaindewaroux2021), we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
+Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
 
 In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on Hirschman’s concept of chosen problems (1963) and Bacchi’s concept of problem-representation in policy (2009), we propose a framework to identify problem-constructions in political discourses.
+Building on @hirschman1963 concept of chosen problems and @bacchi2009 concept of problem-representation in policy, we propose a framework to identify problem-constructions in political discourses.
 Although problem-construction takes place in a series of instances, we analyze the case of discourses by Brazilian presidents since 1985.
 We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences (@zarefsky2004).
+First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
 It legitimizes ways of thinking about the Amazon.
-In turn, policy perception is key for policy adoption and implementation (@alesina2009; @lopez2020).
-This is especially pertinent to deforestation in Brazil as expectations from governments’ response, generated from material and discursive governmental practices (@assuncao2015; @capobianco2019; @capobianco2021), are a crucial factor in decisions to deforest at the ground (@campbell2015).
+In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
+This is especially pertinent to deforestation in Brazil as expectations from governments’ response, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
 Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
@@
 
+This article proceeds as follows: first, we propose a conceptual framework to understand problem-construction in discourses.
+We then review Amazonian historiography literature to identify the main phases and their underlying problem construction.
+In the methodology section, we explain how the framework is operationalized and present the codebook.
+We proceed to describe, visualize and interpret our findings in the analysis section.
+Finally, we conclude with a discussion connecting our findings to the democratic game and environmental outcomes.
+
 # 2 Conceptual framework and contribution
@@
 Chosen problems are those governments select at their discretion.
-Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers (@hirschman1963, p.
-388–91).
-As @bacchi2009 argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
-(p.
-10).
+Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
+As @bacchi2009[p.
+10] argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
 The alleged problem is not always explicitly stated in policy.
-@hirschman1975 exemplifies chosen problems with the case of the construction of Brasilia (p.
-388).
-But building Brasilia can solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
+@hirschman1975[p.
+388] exemplifies chosen problems with the case of the construction of Brasilia.
+Building Brasilia could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
 It is up to the discretion of the government to highlight or not the implicit problem a policy solves.
@@
 Relative to how the policy is represented to be, it can be a solution of problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-Putnam’s (1988) seminal article on the two-level game can help us make sense of this variation.
+@putnam1988 seminal article on the two-level game can help us make sense of this variation.
 The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
@@
 This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests.
-Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases (see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021).
-In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy (@drummond2006).
+Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy [@drummond2006].
 The governments from the late 1980s up to 2009, are more associated with environmental conservation.
@@
 The presidency of Lula, often associated with environmental conservation because we saw an unprecedented decrease in deforestation.
-At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period (@capobianco2021, p.
-106).
+At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
+106].
 That is, there is more variation within governments than the literature suggests.
@@
 An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue and.
-While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences (@zarefsky2004).
-Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem (Eshbaugh-Soha 2010; Rottinghaus 2009; Krebs and Jackson 2007), they direct the range of what is included in national debates (Druckman and Holmes 2004).
+While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem [@eshbaugh2010; @rottinghaus2009; @krebs2007], they direct the range of what is included in national debates [@druckman2004].
 As presidents speak in varied locations to varied audiences, it is very likely that they chose to frame similar issues differently.
@@
 These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted.
-Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that (@hecht1990).
+Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that [@hecht1990].
 With the return of democracy in the 1980s, violence could not be used at the same extent as before and policies had to respond to growing environmental concern.
@@
 Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally (@brice2021; @harris2021; @miranda2021), but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
-Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations (@assuncao2015; @capobianco2019; @capobianco2021).
-Ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground (@campbell2015).
+When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
+Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
+Ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground [@campbell2015].
 
 The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-Calderwood (2019), for instance, examines 2919 mentions of climate change in American official presidential speeches since 1989.
+@calderwood2019, for instance, examines 2919 mentions of climate change in American official presidential speeches since 1989.
 Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change.
 He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-Calderwood (2020) also tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on Putnam (1988), he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
+@calderwood2020 also tests the effect of geographic location and type of communication regarding climate change.
+Building prominently on @putnam1988, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
 The author finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location.
-Elsewhere, Bevitori (2015) investigates how the ‘environment’ has been constructed in American presidential discourse since 1960 using a more automated approach.
+Elsewhere, @bevitori2015 investigates how the ‘environment’ has been constructed in American presidential discourse since 1960 using a more automated approach.
 The author finds that mentions of the environment are typically co-selected with the pronoun ‘our’, as well as with ‘economy’, ‘clean’, and ‘preserve’.
@@
 While these findings are US specific, they indicate that presidents raise different points about the environment at local, national, or international settings, depending on who they assume their audience is at that specific instance.
-Nevertheless, as Bacchi (2009), we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
+Nevertheless, as @bacchi2009, we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
 Mentions to the lexicon as ‘environment’, ‘preserve’, or ‘climate change’ should be tied to the larger meaning of policies in the United States and elsewhere.
@@
 While governmental discourses in Brazil have been studied for topics such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
-Barros (2020) investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
+@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
 The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
@@
 Governments choose what problems to solve and what policies to implement.
-The same policies can be represented as solving different problems implying a degree of social construction (Bacchi 2009).
+The same policies can be represented as solving different problems implying a degree of social construction [@bacchi2009].
 Governments can choose to emphasize or not one or more implicit problems that a policy solves depending on which interest group they are in communication with.
@@
 
-In The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon, Hecht and Cockburn write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites” (1990, 1).
+In *The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon*, @hecht1990[p.
+1] write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites”.
 These dreams of fortunes to be found in the Amazon are composed of the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as “a (...) form of nation building (...)” (Hecht and Cockburn 1990, preface).
+It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as “a (...) form of nation building (...)” [hecht1990, preface].
 The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” (Hecht 2013, 8), and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
+In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht2013, p.
+8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
 While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil (Hecht and Cockburn 1990).
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat during the Cold War (Garfield 2013).
+A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil [@hecht1990].
+This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat during the Cold War [@garfield2013].
 
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally (Silva-Muller and Faul 2022; Andonova 2014; Westerwinter 2021), the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end (Hochstetler 2021; Capobianco 2019; Franchini and Viola 2019).
+As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
+Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
 Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
@@
 The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions (Acker 2014).
+In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
 First, nature should be conquered by men.
@@
 Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, and the establishment of tax-free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources (Acker 2014), leading to a series of national and international enterprises settling in the Amazon region.
-Capobianco (2019) describes the period from the 1950s to the 1980s in a similar fashion, referring to a wider range of policies of economic integration such as the establishment of the tax-free zone of Manaus in the 1970s.
+The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
+@capobianco2019 describes the period from the 1950s to the 1980s in a similar fashion, referring to a wider range of policies of economic integration such as the establishment of the tax-free zone of Manaus in the 1970s.
 The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions are often centralized by the federal government (Becker 2005) and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+These policy solutions are often centralized by the federal government [@becker2005] and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
 
@@
 
-Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles is social development.
+Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles or phases.
 Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights when speaking about the Amazon.
@@
 
-The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions (Drummond and Barros-Platiau 2006).
-A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region (Acker 2021; Capobianco 2021; Hecht and Cockburn 1990).
-This process accelerated in the late 1980s, with the birth of modern environmentalism (Viola 1987) in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco 2021).
-Hochstetler and Keck (2007) argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
+The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions [@drummond2006].
+A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
+This process accelerated in the late 1980s, with the birth of modern environmentalism [@viola1987] in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
+@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
 They define it as an emphasis on the local livelihoods of people while protecting nature.
-Capobianco (2019) argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies as establishment of conservation units in the Amazon in 2001.
-The environmental conservation problem-constructions emphasizes the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination (Hochstetler and Keck 2007).
+@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies as establishment of conservation units in the Amazon in 2001.
+The environmental conservation problem-constructions emphasizes the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
 The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
@@
 
-To analyze how presidents construct the Amazon as a problem in time, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+To analyze how presidents construct the Amazon as a problem in time, we build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
 We update the dataset by scraping and adding all official speeches from 2020 and 2021.
@@
 
-Using the poldis R package, we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
 We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
@@
 
-```{r figure1, echo=FALSE, fig.cap="Operationalization of Problem-constructions", out.width = '100%', include=TRUE}
+```{r figure1, echo=FALSE, fig.cap="Operationalization of problem-constructions", out.width = '100%', include=TRUE}
 knitr::include_graphics("figure1pic.png")
@@
 
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories (Meyer et al.
-(2021); Noble (2006)) .
+We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006] .
 The SVM model is first trained using the hand coded training set and then employed to classify observations in the hand coded validation set.
@@
 To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-We control proportions for factors that might affect the incidence of the Amazon in speeches and portray both real and controlled curves.
 To test whether different problem constructions change according to location, we run a multinomial logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case (Kwak and Alan Clayton-Matthews 2002).
+Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case [@kwak2002].
 In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
@@
 This is the period when the Brazilian Constitution was written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and the protection of their territories (Hecht and Cockburn 1990).
+Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and the protection of their territories [@hecht1990].
 These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
 However, in 1989, the Amazon appeared in 32% of all speeches.
-This spike is likely explained by the brutal murder of Chico Mendes and the very end of 1988 (Simons and Times 1988).
-An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation (Capobianco 2021).
+This spike is likely explained by the brutal murder of Chico Mendes and the very end of 1988.
+An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021].
 
@@
 The 1992 Earth Summit, held in Brazil brought international attention to environmental topics in the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation (Capobianco 2021).
+One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
 Throughout the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon appeared, on average, on 15% of all speeches.
@@
 This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high (Franchini and Viola 2019).
+Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high [@franchini2019].
 
@@
 We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro’s presidency, 2019.
-At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets (cite).
-This brought issues related to environmental conservation as high priorities in Bolsonaro’s governing agenda with efforts to dismantle key pillars of Brazilian environmental governance (cite).
+At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets.
+This brought issues related to environmental conservation as high priorities in Bolsonaro’s governing agenda with efforts to dismantle key pillars of Brazilian environmental governance.
 At the same time, President Bolsonaro retrieves Brazil’s hosting status for COP25.
-In short, relevant international events drive interest and alter how pressing the “Amazon problem” is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers (see Hirschman 1963).
+In short, relevant international events drive interest and alter how pressing the “Amazon problem” is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers.
 
@@
 At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement.
+Figure 3, below, illustrates the share of each pure type in time.
 Pure problem constructions dominate, with an average of  56% of all amazonian statements across time.
 As above, we observe a strong variation over time for most of these constructions.
-Figure 3, below, illustrates the share of each pure type in time.
 
@@
        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
+       caption = "Curves in the plot were smoothed using loess method.") +
   theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
            alpha = 0.1) +
-  annotate(geom = "text", x = hp$label, y = 0.02, vjus = 0.3,
+  annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
            label = hp$presid, alpha = 0.4)
@@
 The same governments construct the Amazon as different issues in discourse.
-For instance, pure economic integration constructions  dominated constructions from 1985 to the late 2000s.
+Pure economic integration constructions  dominated constructions from 1985 to the late 2000s.
 This is especially pertinent during the Cardoso administration as the Amazon was constructed, overwhelmingly, as an issue of economic integration.
-This changed during the Lula presidency.
-During his terms, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased.
+However, during Lula's terms in office, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased.
 These constructions surpassed economic integration around 2010.
 These trends in discourse continued during the Rousseff administration.
-Capobianco (2021), for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
+@capobianco2021, for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
 A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being paid to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.
@@
   geom_bar(stat = "identity", position = "stack") +
-  geom_text(size = 3, position = position_stack(vjust = .5)) +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
 While Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
-Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region (Hecht and Cockburn 1990).
+Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region [@hecht1990].
 
@@
   labs(x = "", y = "Percentage",
-       title = "Percentage for problem constructions across locations\nin relation to environmental conservation problem constructions Internationally",
+       title = "Percentage for problem constructions across locations in relation\nto environmental conservation problem constructions Internationally",
        subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-          legend.position = c(0.50, 0.16))
+          legend.position = c(0.5, 0.15))
 mplot
@@
 1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g.
-2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD 1 billion for environmental conservation in the Amazon (Silva-Muller and Faul 2022).
+2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD 1 billion for environmental conservation in the Amazon [@silva-muller2022].
 Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued.
-During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 (Capobianco 2021).
+During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
 Nowadays, it has reached unprecedented levels.
@@
 The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse within Brazilian states and Amazonian countries compared to Brasilia or internationally.
-Whereas presidential discourses at the top matter to define and justify public policy (Zarefsky 2004), presidents shape their discourses according to who their audience might be and what “they want to hear”.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what “they want to hear”.
 If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
-Or, as Putnam (1988) puts it, what’s the actual overlap between the international and domestic overlap.
+Or, as @putnam1988 puts it, what’s the actual overlap between the international and domestic overlap.
 The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide.
@@
                 position= "center", font_size = 9, full_width = TRUE) %>%
-                footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>%
+                footnote(general = c("The multinomial regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
+                "*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
   column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%

### 2022-05-25 amazon_def_presentation/amazon_def_presentation.Rmd
Added a first draft of a paper presentation

---
title: "How has the Brazilian Amazon been constructed as a problem?"
subtitle: "The Economy, the environment, the people, and the nation in the presidential speeches since 1985"
author: "<large>Henrique Sposito and Livio Silva-Muller</large>"
institute: "<small>Albert Hirscman Centre on Democracy | Geneva Graduate Institute</small>"
date: "<small>`r format(Sys.Date(), '%A, %e %B, %Y')`<small>"
output:
  xaringan::moon_reader:
    css: 
      - "default"
      - "assets/iheid-xaringan-style.css"
      - "https://cdnjs.cloudflare.com/ajax/libs/animate.css/4.1.1/animate.min.css"
      - "ninjutsu"
    chakra: "https://remarkjs.com/downloads/remark-latest.min.js"
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      beforeInit: "assets/macros.js"
      countIncrementalSlides: false
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>`
---
class: center middle

## How has the Brazilian Amazon been constructed as a problem in discourse over time, by geographical location, and between/within governments?

![:scale 50%](assets/Images/presid.jpeg)

*Motivation*: Connecting the social-cultural construction of the Amazon and to the effects on environmental outcomes

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, servr.daemon = TRUE)
knitr::opts_chunk$set(cache=TRUE, autodep = TRUE, fig.retina = 3, message = FALSE, warning = FALSE)
library(knitr)
library(iheiddown)
library(sjPlot)
#devtools::install_github("mitchelloharawild/icons")
library(icons)
#devtools::install_github("gadenbuie/xaringanExtra")
library(xaringanExtra)
xaringanExtra::use_tile_view()
xaringanExtra::use_editable(expires = 1)
```

```{css echo=FALSE}
.highlight-last-item > ul > li, 
.highlight-last-item > ol > li {
  opacity: 0.5;
}
.highlight-last-item > ul > li:last-of-type,
.highlight-last-item > ol > li:last-of-type {
  opacity: 1;
}
```

```{r, load_refs, include=FALSE, cache=FALSE}
# Initializes the bibliography
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear", # Bibliography style
           max.names = 3, # Max author names displayed in bibliography
           sorting = "nyt", #Name, year, title sorting
           cite.style = "authoryear", # citation style
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("assets/myBib.bib", check = FALSE)
# Note: don't forget to clear the knitr cache to account for changes in the
# bibliography.
```
---
class: split two

Conceptual framework

--

## Chosen problems, presidential discourse, and policy issues
.pull-left[<i class="fas fa-broom"></i>
  - @hirschman1963 chosen versus pressing problem and @bacchi2009 problem representation
  - 
  -
  -
]

--

## Problem-construction in Amazonian historiography
.pull-right[<i class="fas fa-list"></i>
  - National Sovereignty [see @hecht1990]
  - Economic Integration [see @acker2014]
  - Environmetal Conservation []
  - What about social development?
]

---
class: split two

## Data and Methods

--

## Operationalization

.pull-left[<i class="fas fa-list"></i>
  - Dataset containing all 6130 official remarks by presidents since 1985
  - Sub-set of 2014 “amazonian statements”
  - hand-coding and supervised machine learning
  - 
]

--

## Limitations

.pull-right[<i class="fas fa-list"></i>
  -
]

---

The rises and falls of the Amazon as a topic in presidential speeches

---

How has the Amazon been constructed as a problem?

**Pure-type problem constructions**

---

How has the Amazon been constructed as a problem?

**Mixed-type problem constructions**

---

The Amazonian multi-level game: boasting policy outside and talking to people inside

---

Discussion

- The Amazon and Democracy

---

Thank you!

---

# References

```{r refs, echo=FALSE, results="asis"}
RefManageR::PrintBibliography(myBib)
```

### 2022-05-25 Draft_May_2022/Full_draft_20220510.rmd
Updated presentation draft

@@
 library(RColorBrewer)
-library(kableExtra)
 library(nnet)

### 2022-05-25 amazon_def_presentation/amazon_def_presentation.Rmd
Updated presentation draft

@@
 author: "<large>Henrique Sposito and Livio Silva-Muller</large>"
-institute: "<small>Albert Hirscman Centre on Democracy | Geneva Graduate Institute</small>"
 date: "<small>`r format(Sys.Date(), '%A, %e %B, %Y')`<small>"
@@
 
-## How has the Brazilian Amazon been constructed as a problem in discourse over time, by geographical location, and between/within governments?
+# The Brazilian Amazon as a problem in discourse over time, by geographical location, and between/within governments
 
-![:scale 50%](assets/Images/presid.jpeg)
+![:scale 40%](assets/Images/presid.jpeg)
 
-*Motivation*: Connecting the social-cultural construction of the Amazon and to the effects on environmental outcomes
+How does the social-cultural construction of the Amazon matters to environmental outcomes?
 
@@
 
+```{r data, include=FALSE}
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(scales)
+library(RColorBrewer)
+library(nnet)
+# Load data
+pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
+pop <-  pop %>% select(-c(title, date, text, location))
+ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
+ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
+AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
+adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data
+amazon_def_year <- rbind(adr, amazon_def_year) 
+hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
+                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
+                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
+                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
+                           "Rousseff", "Temer", "Bolsonaro"))
+# Prepare data for problem constructions
+sov <- ama %>% 
+  filter(sov==1) %>% 
+  count(sov, year) %>%
+  group_by(year) %>%
+  select(-c(sov))%>%
+  rename (sov = n)
+ei <- ama %>% 
+  filter(ei==1) %>% 
+  count(ei, year) %>%
+  group_by(year) %>%
+  select(-c(ei))%>%
+  rename (ei = n) %>%
+  ungroup() %>%
+  tibble::add_row(year = 2017, ei = 0) %>%
+  tibble::add_row(year = 2018, ei = 0)
+sd <- ama %>% 
+  filter(sd==1) %>% 
+  count(sd, year) %>%
+  group_by(year) %>%
+  select(-c(sd))%>%
+  rename (sd = n)
+con <- ama %>% 
+  filter(con==1) %>% 
+  count(con, year) %>%
+  group_by(year) %>%
+  select(-c(con))%>%
+  rename (con = n)
+other <- ama %>% 
+  filter(other==1) %>% 
+  count(other, year) %>%
+  group_by(year) %>%
+  select(-c(other))%>%
+  rename (other = n)
+temp <- ei %>% 
+  left_join(other) %>% 
+  left_join(con) %>% 
+  left_join(sd) %>% 
+  left_join(sov) %>% 
+  replace(is.na(.), 0)
+# Get mixed types in
+ama_mx <-  ama %>%
+  unite(mixed_type, sov:con, sep="_") %>%
+  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
+                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
+                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
+                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
+                                      mixed_type == '0_0_0_0' ~ "Other",
+                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
+                                      mixed_type == '0_1_1_0' ~ "Social Economic",
+                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
+                                      mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
+                                      mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
+                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
+                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
+                                            mixed_type) ~ "Other Mixed-types"),
+         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
+                    "Pure Sovereignty", "Other", "Economic Conservation", 
+                    "Social Economic", "Sovereign Conservation", "Economic, Social,\nand Conservation",
+                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
+         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
+                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
+                             grepl("^Other$", mx_cat) ~ "Other",
+                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
+                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
+                                   |Social Conservation|Other Mixed-types",
+                                   mx_cat) ~ "Mixed-types"),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+```
+
 ```{css echo=FALSE}
@@
 
-```{r, load_refs, include=FALSE, cache=FALSE}
-# Initializes the bibliography
-library(RefManageR)
-BibOptions(check.entries = FALSE,
-           bib.style = "authoryear", # Bibliography style
-           max.names = 3, # Max author names displayed in bibliography
-           sorting = "nyt", #Name, year, title sorting
-           cite.style = "authoryear", # citation style
-           style = "markdown",
-           hyperlink = FALSE,
-           dashed = FALSE)
-myBib <- ReadBib("assets/myBib.bib", check = FALSE)
-# Note: don't forget to clear the knitr cache to account for changes in the
-# bibliography.
-```
 ---
@@
 
-Conceptual framework
+# Conceptual framework
 
 --
+.pull-left[**Theory**
 
-## Chosen problems, presidential discourse, and policy issues
-.pull-left[<i class="fas fa-broom"></i>
-  - @hirschman1963 chosen versus pressing problem and @bacchi2009 problem representation
-  - 
-  -
-  -
+- Chosen problems (Hirschman 1963; Bacchi 2009)
+
+- Presidential discourse (Zarefsky 2004)
+
+- Policy issues (Drummond and Barros-Platiau 2006)
 ]
@@
 --
+.pull-right[**Problem-construction**
 
-## Problem-construction in Amazonian historiography
-.pull-right[<i class="fas fa-list"></i>
-  - National Sovereignty [see @hecht1990]
-  - Economic Integration [see @acker2014]
-  - Environmetal Conservation []
+- National Sovereignty (Hecht and Cockburn 1990)
+
+- Economic Integration (Acker 2014)
+
+- Environmetal Conservation (Hochstetler and Keck 2007)
+
 - What about social development?
@@
 
-## Data and Methods
+# Data and Methods
 
 --
+.pull-left[
 
-## Operationalization
+- Dataset containing all 6130 official remarks by presidents since 1985
 
-.pull-left[<i class="fas fa-list"></i>
-  - Dataset containing all 6130 official remarks by presidents since 1985
-  - Sub-set of 2014 “amazonian statements”
-  - hand-coding and supervised machine learning
-  - 
+- Subset of 2014 “amazonian statements”
+
+- Hand-coding and supervised machine learning
+
+- Limitations
 ]
@@
 --
+.pull-right[*Operationalization*
 
-## Limitations
-
-.pull-right[<i class="fas fa-list"></i>
-  -
+![:scale 120%](assets/Images/figure1pic.png)
 ]
@@
 
-The rises and falls of the Amazon as a topic in presidential speeches
+# The rises and falls of the Amazon as a topic in presidential speeches
+
+.center[
+```{r Figure 2, echo=FALSE, fig.height=6.5, fig.width=11}
+perc1 <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc=n / sum(n)) %>%
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  scale_y_continuous(labels = percent_format()) +
+  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
+  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
+             linetype = "dotted") +
+  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+       subtitle = "Sample composed by 6130 presidential speeches since 1985",
+       caption = "",
+       color='Y series') +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")
+Amazon_year
+```
+]
+---
+
+# How has the Amazon been constructed as a problem? *Pure-type problem constructions*
+
+.center[
+```{r Figure 3, echo=FALSE, fig.height=6.5, fig.width=11}
+pure_types_time <- ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>% 
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure type by year",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom") +
+  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
+           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
+                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
+           alpha = 0.1) +
+  annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
+           label = hp$presid, alpha = 0.4)
+pure_types_time
+```
+]
+---
+
+# How has the Amazon been constructed as a problem? *Mixed-type problem constructions*
+
+.center[
+```{r Figure 4, echo=FALSE, fig.height=6.5, fig.width=11}
+mixed_types_presid <- ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "right")
+mixed_types_presid
+```
+]
+---
+
+# The Amazonian multi-level game: boasting policy outside and talking to people inside
+
+.center[
+```{r Figure 5, echo=FALSE, fig.height=6.5, fig.width=11}
+logit2prob <- function(logit) {
+  odds <- exp(logit)
+  prob <- odds / (1 + odds)
+  return(prob)
+} # to transform log odds in probabilities
+md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
+                      "Amazonian_Countries" = c(1.3411972, 1.2460915, 0.9310706),
+                      "Amazonian_States" = c(0.4578251, 1.4725563, 1.6281365),
+                      "Non_Amazonian_States" = c(0.6198104, 1.5838611, 1.9830952),
+                      "Brasilia" = c(-0.29279984, 0.59564579, 1.38333572))
+md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
+md_plot$'Amazonian States' <- logit2prob(md_plot$Amazonian_States)
+md_plot$'Non Amazonian States' <- logit2prob(md_plot$Non_Amazonian_States)
+md_plot$'Amazonian Countries' <- logit2prob(md_plot$Amazonian_Countries)
+mplot <- md_plot %>%
+  select(-c("Amazonian_Countries", "Amazonian_States", "Non_Amazonian_States")) %>% 
+  tidyr::pivot_longer('Amazonian Countries':Brasilia) %>%
+  mutate(Percentage = 100*round(value, digit = 2)-50) %>%
+  mutate(Location = factor(name, levels = c("Amazonian Countries", "Amazonian States",
+                           "Non Amazonian States", "Brasilia"))) %>% 
+  ggplot(aes(x = Location, y = Percentage, fill = Construction)) +
+  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  scale_y_continuous(breaks = seq(-15, 40, 10), limits = c(-15, 40)) +
+  geom_text(aes(label = Percentage), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
+  geom_hline(yintercept = 0, linetype = "dotted", color = "red") +
+  labs(x = "", y = "Percentage",
+       title = "Percentage for problem constructions across locations in relation\nto environmental conservation problem constructions Internationally",
+       subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+          legend.position = c(0.5, 0.15))
+mplot
+```
+]
+---
+
+# Discussion: The Amazon, Democracy, and Environment
+
+.pull-left[
+
+- Amazonian frontier
+
+- Multi-level game
+
+- Contributions
+]
+
+.pull-right[
+![:scale 100%](assets/Images/photolivio.png)
+]
 
 ---
-
-How has the Amazon been constructed as a problem?
-
-**Pure-type problem constructions**
-
----
-
-How has the Amazon been constructed as a problem?
-
-**Mixed-type problem constructions**
-
----
-
-The Amazonian multi-level game: boasting policy outside and talking to people inside
-
----
-
-Discussion
-
-- The Amazon and Democracy
-
----
-
-Thank you!
-
----
-
 # References
@@
 ```{r refs, echo=FALSE, results="asis"}
-RefManageR::PrintBibliography(myBib)
+RefManageR::ReadBib("assets/myBib.bib")
 ```

### 2022-05-29 amazon_def_presentation/amazon_def_presentation.Rmd
Further updates to power point

--- 2022-05-25 amazon_def_presentation/amazon_def_presentation.Rmd
@@
 title: "How has the Brazilian Amazon been constructed as a problem?"
-subtitle: "The Economy, the environment, the people, and the nation in the presidential speeches since 1985"
+subtitle: "The economy, the environment, the people, and the nation in the presidential speeches since 1985"
 author: "<large>Henrique Sposito and Livio Silva-Muller</large>"
-institute: "<small>Albert Hirscman Centre on Democracy | Geneva Graduate Institute</small>"
 date: "<small>`r format(Sys.Date(), '%A, %e %B, %Y')`<small>"
@@
 ---
-class: center middle
+class: split two middle
 
-## How has the Brazilian Amazon been constructed as a problem in discourse over time, by geographical location, and between/within governments?
+.pull-left[
+## The Brazilian Amazon as a problem in presidential discourse:
+- in time
+- by geographical location
+- between/within governments
+]
 
-![:scale 50%](assets/Images/presid.jpeg)
+.pull-right[
+![:scale 120%](assets/Images/presid.jpeg)
+]
 
-*Motivation*: Connecting the social-cultural construction of the Amazon and to the effects on environmental outcomes
+- The social-cultural construction of the Amazon and environmental outcomes
 
@@
 
-Conceptual framework
+# Conceptual framework
 
 --
+.pull-left[**Theory**
 
-## Chosen problems, presidential discourse, and policy issues
-.pull-left[<i class="fas fa-broom"></i>
-  - @hirschman1963 chosen versus pressing problem and @bacchi2009 problem representation
-  - 
-  -
-  -
+- Chosen problems (Hirschman 1963; Bacchi 2009)
+
+- Presidential discourse (Zarefsky 2004)
 ]
@@
 --
+.pull-right[**Problem-construction**
 
-## Problem-construction in Amazonian historiography
-.pull-right[<i class="fas fa-list"></i>
-  - National Sovereignty [see @hecht1990]
-  - Economic Integration [see @acker2014]
-  - Environmetal Conservation []
-  - What about social development?
+- National sovereignty (Hecht and Cockburn 1990)
+
+- Economic integration (Acker 2014)
+
+- Environmental conservation (Hochstetler and Keck 2007)
+
+- And social development?
 ]
@@
 ---
-class: split two
+class: split two middle
 
-## Data and Methods
+# Data and Methods
 
 --
+.pull-left[
 
-## Operationalization
+- Dataset containing all 6130 official remarks by presidents since 1985
 
-.pull-left[<i class="fas fa-list"></i>
-  - Dataset containing all 6130 official remarks by presidents since 1985
-  - Sub-set of 2014 “amazonian statements”
-  - hand-coding and supervised machine learning
-  - 
+- Subset of 2014 “amazonian statements”
+
+- Hand-coding and supervised machine learning
+
+- Limitations
 ]
@@
 --
+.pull-right[
 
-## Limitations
-
-.pull-right[<i class="fas fa-list"></i>
-  -
+![:scale 200%](assets/Images/figure1pic.png)
 ]
@@
 
-The rises and falls of the Amazon as a topic in presidential speeches
+# The rises and falls of the Amazon as a topic in presidential speeches
+
+.center[
+```{r Figure 2, echo=FALSE, fig.height=6.5, fig.width=12}
+perc1 <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc=n / sum(n)) %>%
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  scale_y_continuous(labels = percent_format()) +
+  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
+  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
+             linetype = "dotted") +
+  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+       subtitle = "Sample composed by 6130 presidential speeches since 1985",
+       caption = "",
+       color='Y series') +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")
+Amazon_year
+```
+]
+---
+
+# How has the Amazon been constructed as a problem? *Pure-type problem constructions*
+
+.center[
+```{r Figure 3, echo=FALSE, fig.height=6.5, fig.width=12}
+pure_types_time <- ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>% 
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure type by year",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom") +
+  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
+           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
+                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
+           alpha = 0.1) +
+  annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
+           label = hp$presid, alpha = 0.4)
+pure_types_time
+```
+]
+---
+
+# How has the Amazon been constructed as a problem? *Mixed-type problem constructions*
+
+.center[
+```{r Figure 4, echo=FALSE, fig.height=6.5, fig.width=12}
+mixed_types_presid <- ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "right")
+mixed_types_presid
+```
+]
+---
+
+# The Amazonian multi-level game: boasting policy outside and talking to people inside
+
+.center[
+```{r Figure 5, echo=FALSE, fig.height=6.5, fig.width=12}
+logit2prob <- function(logit) {
+  odds <- exp(logit)
+  prob <- odds / (1 + odds)
+  return(prob)
+} # to transform log odds in probabilities
+md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
+                      "Amazonian_Countries" = c(1.3411972, 1.2460915, 0.9310706),
+                      "Amazonian_States" = c(0.4578251, 1.4725563, 1.6281365),
+                      "Non_Amazonian_States" = c(0.6198104, 1.5838611, 1.9830952),
+                      "Brasilia" = c(-0.29279984, 0.59564579, 1.38333572))
+md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
+md_plot$'Amazonian States' <- logit2prob(md_plot$Amazonian_States)
+md_plot$'Non Amazonian States' <- logit2prob(md_plot$Non_Amazonian_States)
+md_plot$'Amazonian Countries' <- logit2prob(md_plot$Amazonian_Countries)
+mplot <- md_plot %>%
+  select(-c("Amazonian_Countries", "Amazonian_States", "Non_Amazonian_States")) %>% 
+  tidyr::pivot_longer('Amazonian Countries':Brasilia) %>%
+  mutate(Percentage = 100*round(value, digit = 2)-50) %>%
+  mutate(Location = factor(name, levels = c("Amazonian Countries", "Amazonian States",
+                           "Non Amazonian States", "Brasilia"))) %>% 
+  ggplot(aes(x = Location, y = Percentage, fill = Construction)) +
+  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  scale_y_continuous(breaks = seq(-15, 40, 10), limits = c(-15, 40)) +
+  geom_text(aes(label = Percentage), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
+  geom_hline(yintercept = 0, linetype = "dotted", color = "red") +
+  labs(x = "", y = "Percentage",
+       title = "Percentage for problem constructions across locations in relation\nto environmental conservation problem constructions Internationally",
+       subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+          legend.position = c(0.5, 0.15))
+mplot
+```
+]
+---
+class: split two middle
+
+# The Amazon, democracy, and the environment
+
+.pull-left[
+
+- Amazonian frontier
+
+- Multi-level game
+
+- Contributions
+]
+
+.pull-right[
+![:scale 120%](assets/Images/photolivio.png)
+]
 
@@
 
-How has the Amazon been constructed as a problem?
-
-**Pure-type problem constructions**
+background-image: url(https://media.giphy.com/media/xUPGcxpCV81ebKh7Vu/giphy.gif)
+background-size: contain
 
 ---
-
-How has the Amazon been constructed as a problem?
-
-**Mixed-type problem constructions**
-
----
-
-The Amazonian multi-level game: boasting policy outside and talking to people inside
-
----
-
-Discussion
-
-- The Amazon and Democracy
-
----
-
-Thank you!
-
----
-
 # References

### 2022-05-31 Draft_April_2022/Full_draft_20220401.rmd

--- 2022-05-11 Draft_April_2022/Full_draft_20220401.rmd
@@
 Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
-  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
-  geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-  geom_vline(xintercept = 1988, linetype="dotted") +
-  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summmit"), size = 3) + 
-  geom_vline(xintercept = 1992, linetype="dotted") +
-  geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summmit"), size = 3) + 
-  geom_vline(xintercept = 2009, linetype="dotted") +
-  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summmit"), size = 3) + 
-  geom_vline(xintercept = 2015, linetype="dotted") +
-  scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
-  scale_y_continuous(labels = percent_format()) +
+  geom_line(size=.85, aes(x=year, y=perc, color="Real share"))+
+  geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share"))+
+  scale_color_manual(values=c("Real share"="darkolivegreen", "Predicted share"= "gray40"))+
+  scale_y_continuous(labels = percent_format())+
   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-       caption = "Predicted share controls for deforestation rates, inflation, and president.",
-       color='Y series') +
+       caption = "Predicted share controls for deforestation rates, inflation, and president.", color='Y series') +
   theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
 prob_construction_year <- ama_mx %>%
-  filter(!(mx_cat == "Other" | mx_cat == "Other Mixed-types")) %>% 
-  count(year, mx_cat) %>%
+  count(year, mx_cat)%>%
   group_by(year) %>%
@@
         legend.position = "none") +
-  facet_wrap(~ mx_cat, ncol = 2)
+  facet_wrap(~ mx_cat, ncol=3, scales="free_y")
 prob_construction_year
@@
 pure_types_time <- ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
-  group_by(year) %>%
+  count(president, mx_cat2, mx_cat, year) %>%
+  group_by(president, year) %>%
   mutate(perc = n / sum(n)) %>% 
   filter(mx_cat2 == "Pure-types") %>% 
-  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), size = .5) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
+  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
+  scale_y_continuous(labels = percent_format(accuracy=1)) +
   labs(x = "", y = "", title ="Share of each pure type by year",
@@
         legend.position = "bottom") +
-  facet_wrap(~location_cat, ncol=2)
+  facet_wrap(~location_cat, scales= "free_y", ncol=2)
 pure_types_time_location
@@
 md_plot$Other_States <- logit2prob(md_plot$Other_States)
-mplot <- md_plot %>%
-  tidyr::pivot_longer(Brasilia:Other_States) %>%
-  mutate(Probability = round(value, digit = 2)) %>% 
-  rename(Location = name) %>% 
-  ggplot(aes(Location, Probability, fill = Construction)) +
-  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
+mplot <- md_plot %>% tidyr::pivot_longer(Brasilia:Other_States) %>%
+  rename(Location = name, Probability = value) %>% 
+  ggplot(aes(Construction, Probability)) +
+  geom_bar(aes(fill = Location), stat = "identity", position = position_dodge(0.8), width = 0.7) +
     scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  geom_text(aes(label = Probability), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
-  geom_hline(yintercept = 0.5, linetype = "dotted", color = "red") +
   labs(x = "", y = "Probability",

### 2022-06-09 Draft_June_2022/Full_draft_20220608.rmd
#june_draft_folder_structure

--- 2022-05-25 Draft_May_2022/Full_draft_20220510.rmd
@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "20 May 2022"
+date: "8 June 2022"
 output:
@@
 We need to preserve the Amazon as a standing ecosystem.
-Historically, the Brazilian federal government proposed diverse constructions of the Amazon as a region, forest, or peoples.
-Each of these constructions contain an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
+Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.Different governmental programs contained an assumptions of what had to be solved in the Amazon, or in other words, it represents the Amazon as a particular problem.
 These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
@@
 
-## 2.1 Chosen problems, presidential discourse, and policy issues
+## 2.1 Chosen problems, presidential discourse, and policy objects
 
@@
 Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-As @bacchi2009[p.
-10] argues, though, policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
+
+Additionally, @bacchi2009[p.
+10] argues that policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in policy.
-@hirschman1975[p.
+The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.@hirschman1975[p.
 388] exemplifies chosen problems with the case of the construction of Brasilia.
@@
 It is up to the discretion of the government to highlight or not the implicit problem a policy solves.
+A same policy object (e.g.
+Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.
 
@@
 Relative to how the policy is represented to be, it can be a solution of problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-@putnam1988 seminal article on the two-level game can help us make sense of this variation.
+@putnam1988 seminal article on the two-level game can help us make sense of this variation conceptually.
 The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
@@
 This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests.
-Several scholars describe federal governments' as proponents of specific policies for the Amazon Forest and region, using the vocabulary of policy cycles, periods, or phases [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy.
+Several scholars describe federal governments' as proponents of specific policies for the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
 In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy [@drummond2006].
@@
 While these works are important to understand how different governments acted towards the Amazon, the classification of specific governments into periods or policy cycles represents them as monolithic: they associate specific governments to one specific view of the Amazon.
-The presidency of Lula, often associated with environmental conservation because we saw an unprecedented decrease in deforestation.
+The presidency of Lula, often associated with environmental conservation because of the unprecedented decrease in deforestation.
 At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
@@
 
-An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue and.
+An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue.
 While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
@@
 If presidents can promote different problem-constructions in different places, it is important to understand to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
-@pacheco2019 proposes that we see the Amazon frontier as a key analytic category to understand the Brazilian state and democracy.
+@pacheco2019 proposes that the Amazon is key to understand Brazilian state and democracy.
 Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
@@
 Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground [@campbell2015].
+Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
+Relatedly, ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground [@campbell2015].
+Thus, understanding diversity in presidential speeches is a first step to connect it to concrete environmental outcomes.
 
@@
 To identify possible problem-constructions and their connection to the wider socio-cultural history of the country, we build on Amazonian historiography.
-We understand Amazonian historiography as the body of research by social and environmental scientists that tells the story of diverse policies adopted to solve problems in the region.
+We understand Amazonian historiography as the body of research conducted by social and environmental scientists that tells the story of diverse governmental programs that approaches the Amazon region, forest, and its people as a policy object demanding dedicated action.
 
@@
 Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles or phases.
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights when speaking about the Amazon.
+While this might be related to social policies being more geared towards the whole nation, there are instances of specific social policies for the Amazon.Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights when speaking about the Amazon.
 This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.
@@
 To analyze the relationship between location and problem construction, we run a multinomial regression.
-Our dependent variable is problem-constructions (categorical), while our main dependent variable is location (categorical).
+Our dependent variable is problem-constructions (categorical), while our main independent variable is location (categorical).
 The reference category for the multinomial model is, thus, environmental conservation in international states.

### 2022-06-09 Draft_June_2022/Full_draft_20220608.rmd
#weaved in policy object #added references in 2.1 and 3 #added references from environmental politics

@@
 output:
-  pdf_document: default
-  fig_caption: yes
   html_document:
     df_print: paged
+  fig_caption: yes
+  pdf_document: default
   word_document:
@@
 We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon’s natural resources.
+We need to exploit the Amazon's natural resources.
 We need to provide better living standards for the people in the Amazon.
@@
 We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
 It legitimizes ways of thinking about the Amazon.
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations from governments’ response, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
+This is especially pertinent to deforestation in Brazil as expectations from governments' response, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
 Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
@@
 Governments often have a choice in how they construct problems and what policy solutions they implement.
-In “Journey towards Progress”, @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
+In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
 Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
@@
 
-Additionally, @bacchi2009[p.
-10] argues that policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
+Additionally, @bacchi2009 [p.
+10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts".
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.@hirschman1975[p.
+The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.\@hirschman1975[p.
 388] exemplifies chosen problems with the case of the construction of Brasilia.
@@
 The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
+Relatedly, @hochstetler2012 argue that international commitments in the Brazilian case shift as a function of domestic cost-benefit calculations, as the country as a large emitter does not abide to the global commons framings.
 Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
@@
 An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue.
-While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004].
+While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
 Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem [@eshbaugh2010; @rottinghaus2009; @krebs2007], they direct the range of what is included in national debates [@druckman2004].
@@
 When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
-Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
+Deforestation rates in Brazil are more responsive to the government's environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
 Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
-Relatedly, ethnographic research has also shown that expectations about governments’ response are a crucial factor in decisions to deforest at the ground [@campbell2015].
+Relatedly, ethnographic research has also shown that expectations about governments' response are a crucial factor in decisions to deforest at the ground [@campbell2015].
 Thus, understanding diversity in presidential speeches is a first step to connect it to concrete environmental outcomes.
@@
 The author finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location.
-Elsewhere, @bevitori2015 investigates how the ‘environment’ has been constructed in American presidential discourse since 1960 using a more automated approach.
-The author finds that mentions of the environment are typically co-selected with the pronoun ‘our’, as well as with ‘economy’, ‘clean’, and ‘preserve’.
+Elsewhere, @bevitori2015 investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
+The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
 These studies corroborate the possibilities of variation depending on the audience, but we are yet to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
@@
 Nevertheless, as @bacchi2009, we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
-Mentions to the lexicon as ‘environment’, ‘preserve’, or ‘climate change’ should be tied to the larger meaning of policies in the United States and elsewhere.
+Mentions to the lexicon as 'environment', 'preserve', or 'climate change' should be tied to the larger meaning of policies in the United States and elsewhere.
 
@@
 The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
+We also find one analysis of Bolsonaro's rhetoric about the Amazon, but the study relies on a reduced sample without transparent explanations of how speeches were selected [@marquardt2022].
 
@@
 
-In *The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon*, @hecht1990[p.
-1] write that all over the world tropical forests are destroyed, but “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites”.
+In *The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon*, @hecht1990 [p.
+1] write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites".
 These dreams of fortunes to be found in the Amazon are composed of the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as “a (...) form of nation building (...)” [hecht1990, preface].
+It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" [hecht1990, preface].
 The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht2013, p.
+In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht2013, p.
 8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
@@
 A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil [@hecht1990].
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil’s sovereignty over the Amazon from the communist threat during the Cold War [@garfield2013].
+This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War [@garfield2013].
 
@@
 Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of ‘internationalizing’ the Amazon.
+Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
 This might come both from foreign actors as well as domestic non-state actors.
@@
 Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles or phases.
-While this might be related to social policies being more geared towards the whole nation, there are instances of specific social policies for the Amazon.Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights when speaking about the Amazon.
+While this might be related to social policies being more geared towards the whole nation, there are instances of specific social policies for the Amazon.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights when speaking about the Amazon.
 This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.
@@
 Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
-We do so by detecting all speeches in which the stem “amazon” appears.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We do so by detecting all speeches in which the stem "amazon" appears.
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
 We find that 946 speeches are, at least partially, about the Amazon from the 6130.
 
-Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
 We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
@@
 This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
+When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
 On average, an Amazonian statement contains 123 words.
 
-We develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
+We follow the procedures outlined by @grimmer2022 for supervised classification.First, we develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
 In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
@@
 \end{landscape}
+````
 
-With the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
+Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
 This amount refers to 50% of all the Amazon Statements identified.
@@
 As well, this allows a robust validation set to verify the models.
-Still, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
+As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable enough.
+Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
 Intercoder agreement for each of the four main categories was 85%, on average.
 For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
-The manually coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
 
+Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
 We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006] .
@@
 Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
 Hence, we might be missing statements about Amazon that do not refer to it.
@@
 This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high [@franchini2019].
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
 
@@
 
-We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro’s presidency, 2019.
+We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
 At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets.
-This brought issues related to environmental conservation as high priorities in Bolsonaro’s governing agenda with efforts to dismantle key pillars of Brazilian environmental governance.
-At the same time, President Bolsonaro retrieves Brazil’s hosting status for COP25.
-In short, relevant international events drive interest and alter how pressing the “Amazon problem” is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers.
+This brought issues related to environmental conservation as high priorities in Bolsonaro's governing agenda with efforts to dismantle key pillars of Brazilian environmental governance.
+At the same time, President Bolsonaro retrieves Brazil's hosting status for COP25.
+In short, relevant international events drive interest and alter how pressing the "Amazon problem" is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers.
 
@@
 The Amazon, as a region and a forest, has historically been the topic of international, national, supranational, and local debates, negotiation and policies.
-This implies not only that audiences’ priorities in each setting change, but that which policies are appropriate to solve the “Amazon issue” could differ as well.
+This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" could differ as well.
 The multi-level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not for local electorates.
@@
 The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse within Brazilian states and Amazonian countries compared to Brasilia or internationally.
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what “they want to hear”.
+Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
 If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
-Or, as @putnam1988 puts it, what’s the actual overlap between the international and domestic overlap.
+Or, as @putnam1988 puts it, what's the actual overlap between the international and domestic overlap.
 The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide.
@@
 While unprecedented, this new balance was not long-standing.
-Democratic decay is slow, and the embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
+Democratic decay is slow, and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
 We observe the decrease in conservation-related statements in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.

### 2022-06-09 Draft_June_2022/Full_draft_20220608.rmd
Added location in km to manaus data, word frequencies, and fixed other minor coding issues found

--- 2022-06-09 Draft_June_2022/Full_draft_20220608.rmd
@@
 library(kableExtra)
+library(tm)
+library(tidytext)
+library(topicmodels)
+library(tibble)
 Sys.setlocale("LC_ALL", "C")
@@
 # Load data
-pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
-pop <-  pop %>% select(-c(title, date, text, location))
+##### We are missing many observations for Collor from 1991 and 1992...
+##### These are not in the repository for some reason...
+##### Should we try and complete or should we at least disclose these in a footnote?
+pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
+pop <- pop %>% select(-c(title, date, location))
 ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
+location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>% 
+  select(-location_cat)
+ama <- left_join(ama, location_km, by = "location")
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data
@@
         legend.position = "bottom")
-# # Same plot but annotated
-# Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(color = "darkgreen") +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
-#              linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom") +
-#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
-#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
-#            alpha = 0.1) +
-#   annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
-#            label = hp$presid, alpha = 0.4) +
-#   annotate(geom = "segment", x = amazon_def_year$year, y = amazon_def_year$def_year)
-# # # With a few lines under the
-# cat1 <- ama_mx %>%
-#   mutate(cat = ifelse(mx_cat2 == "Mixed-types", "Mixed-types", paste(mx_cat))) %>%
-#   count(cat, year) %>%
-#   group_by(year) %>%
-#   mutate(perc = n / sum(n),
-#          perc_type = ifelse(perc == 1, 0.25, perc)) %>% 
-#   arrange(year) %>%
-#   select(c(cat, year, perc_type))
-# year_share <- merge(perc1, cat1, "year") %>%
-#   mutate(year_perc = perc*perc_type)
-# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(aes(y = perc)) +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_line(aes(x = year, y = year_perc, fill = cat, group = cat, color = cat)) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
-#              linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# # For filling the area under the line
-# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = year_perc, fill = cat)) +
-#   geom_line() +
-#   geom_area() +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_vline(xintercept = 1988, linetype = "dotted") +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_vline(xintercept = 1992, linetype = "dotted") +
-#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) +
-#   geom_vline(xintercept = 2009, linetype = "dotted") +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = 2015, linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color = 'Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# # Controling for inflation and deforastation
-# pop2 <- pop %>% count(amazon_speech, year, president) %>%
-#   group_by(year, president) %>%
-#   left_join(perc1) %>%
-#   filter(amazon_speech==1)
-# pop2 <- left_join(pop2, AAI, by = "year")
-# pop2 <- left_join(pop2, amazon_def_year, by = "year")
-# model <- lm(perc ~ AAI+ def_year + president, data=pop2)
-# pop2$predicted = predict(model, pop2)
-# Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
-#   geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_vline(xintercept = 1988, linetype="dotted") +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) + 
-#   geom_vline(xintercept = 1992, linetype="dotted") +
-#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) + 
-#   geom_vline(xintercept = 2009, linetype="dotted") +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) + 
-#   geom_vline(xintercept = 2015, linetype="dotted") +
-#   scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
-#   scale_y_continuous(labels = percent_format()) +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "Predicted share controls for deforestation rates, inflation, and president.",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
 Amazon_year
+
+# Word frequency year
+popc <- filter(pop, amazon_speech == 1) %>%
+  select(year, text) %>% 
+  group_by(year) %>% 
+  rename(doc_id = year)
+popc$text <- stringr::str_replace_all(popc$text, "meio ambiente", "meioambiente")
+popc$text <- stringr::str_replace_all(popc$text, "forcas armadas", "forcasarmadas")
+popc$text <- stringr::str_replace_all(popc$text, "estados unidos", "estadosunidos")
+popc$text <- stringr::str_replace_all(popc$text, "rio de janeiro", "riodejaneiro")
+popc$text <- stringr::str_replace_all(popc$text, "direitos humanos", "direitoshumanos")
+popc$text <- stringr::str_replace_all(popc$text, "rio grande do sul", "riograndedosul")
+popc$text <- stringr::str_replace_all(popc$text, "copa do mundo", "copadomundo")
+popc$text <- stringr::str_replace_all(popc$text, "sao paulo", "saopaulo")
+popc$text <- stringr::str_replace_all(popc$text, "rio grande do norte", "riograndedonorte")
+popc$text <- stringr::str_replace_all(popc$text, "floresta amazonica", "florestaamazonica")
+popc$text <- stringr::str_replace_all(popc$text, "regiao amazonica", "regiaoamazonica")
+popc$text <- stringr::str_replace_all(popc$text, "mato grosso|mato-grosso", "matogrosso")
+popc$text <- stringr::str_replace_all(popc$text, "minas gerais", "minasgerais")
+popc$text <- stringr::str_remove_all(popc$text, " [a-z] ")
+popc$text <- tm::removeWords(tm::removePunctuation(popc$text),
+                             c(tm::stopwords("pt"), 
+                               "nao", "amazonas", "voce", "vao", "dar", "du",
+                               "our", "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
+                               "no", "hoje", "presidente", "governador", 
+                               "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
+                               "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
+                               "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
+                               "cumprimentar", "gente", "estado", "querido", "queria",
+                               "todos", "companheiro", "senhores", "alguns",
+                               "companheiras", "companheiros", "companheira", "entao",
+                               "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
+                               "grosso","ministro", "ministra", "josé", "jose",
+                               "palacio", "planalto", "pronunciamento", "sobre",
+                               "ministros", "luiz", "disse", "fizemos", "nesse",
+                               "antonio", "vou", "eduardo braga", "pais", "coisa",
+                               "então", "pouco", "pode", "sera", "dias",
+                               "outro", "onde", "discurso", "parte", "fala",
+                               "anos", "cada", "todo", "visite site", "disse",
+                               "site secretaria", "minas gerais", "lula silva",
+                               "inácio lula", "amapa", "bahia", "é", "lá", "et", "in",
+                               "httpwwwimprensaplanaltogovbr", "secretaria", "visitesite",
+                               "ta", "tudo", "pessoas", "falar", "neves", "tancredo",
+                               "brasiliadf", "cardoso", "httpwwwinfoplanaltogovbr", 
+                               "sip", "and", "to", "en", "des", "el", "le", "les", "dia",
+                               "palavra dorsdne", "fernando henrique", "dorsdne eete",
+                               "inacio lula", "lula silva", "inacio", "republica",
+                               "quegente", "muitas vezes", "ainda", "realmente",
+                               "assim", "possa", "coisas", "apenas", "acho", "ano",
+                               "vez", "portanto", "todas", "questao", "lado", "outros",
+                               "prezado", "vem", "sempre", "sarney", "luis", "serao", 
+                               "tao", "meses", "quase", "diante", "brasil", "sendo",
+                               "rsdneennoerqe", "brasil", "neste", "digo", "quase", 
+                               "queremos", "nesse", "nessa", "mim", "eete", "obrigado", "muita"))
+popc <- tm::VCorpus(tm::DataframeSource(popc))
+popn <- tidytext::tidy(popc) %>%
+  unnest_tokens(word, text) %>% 
+  group_by(id, word) %>% 
+  summarise(count = n()) %>% 
+  arrange(-count) %>% 
+  slice(1:10)
+popn <- aggregate(popn$word, list(popn$id), paste, collapse=", ") %>% 
+  rename(Year = "Group.1", Terms = "x")
+tibble(popn)
+##### LDA per year just in case
+pop_dtm  <- DocumentTermMatrix(popc)
+pop_lda <- topicmodels::LDA(pop_dtm, k = 10, control = list(seed = 1234))
+pop_lday <- tidy(pop_lda, matrix = "gamma") %>%
+  arrange(desc(gamma)) %>%
+  group_by(document) %>%
+  filter(row_number() %in% 1:1) %>% # get the top 3 topics per speaker
+  arrange(document) %>%
+  mutate(gamma = round(gamma, 1)) %>%
+  distinct() %>% 
+  rename (Year = document)
+pop_10 <- tidy(pop_lda, matrix = "beta") %>%
+  arrange(desc(beta)) %>%
+  group_by(topic) %>%
+  filter(row_number() %in% 1:10) %>%
+  arrange(topic)
+pop_10 <- aggregate(pop_10$term, list(pop_10$topic), paste, collapse=", ") %>%
+  rename(topic = "Group.1", Terms = "x")
+popt <- dplyr::left_join(pop_10, pop_lday, by = "topic") %>%
+  select(Year, Terms) %>% 
+  arrange(Year)
+tibble(popt)
 ```
@@
                                             "Economic Conservation", "Social Economic",
-                                            "Sovereign Conservation", "Economic, Social,\nand Conservation",
+                                            "Sovereign Conservation", 
+                                            "Economic, Social,\nand Conservation",
                                             "Economic Sovereignty", "Social Conservation", "Other")),
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname", location),
-                                     "Amazonian Countries", location_cat),
+         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
+                                     location, ignore.case = TRUE), # minor coding issues to fix
+                               "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat), # minor coding issues to fix
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries", location_cat),
                                levels = c("International", "Amazonian States",
-                                          "Amazonian Countries", "Brasilia", "Non Amazonian States"))) # separating Amazonian countries
+                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
 # model

### 2022-06-09 messy_files/others/data_exploration_2_context.Rmd
Added location in km to manaus data, word frequencies, and fixed other minor coding issues found

--- 2022-02-07 others/data_exploration_2_context.Rmd
@@
                                           "roraima", "manaus", "rondônia", "ministros", "luiz", 
-                                          "antonio", "vou", "eduardo braga", "rio de janeiro",
-                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", 
+                                          "antonio", "vou", "eduardo braga",
+                                          "então", "pouco", "pode", "sul", "norte", 
                                           "mato grosso", "outro", "onde", "discurso", "parte", 

### 2022-06-09 Draft_June_2022/Full_draft_20220608.tex

--- 2022-06-09 Draft_June_2022/Full_draft_20220608.rmd
@@
----
-title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
-author:
-- Livio Silva-Muller
-- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically.
-Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Institute and affiliated to the Albert Hirschman Centre on Democracy.
-Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "8 June 2022"
-output:
-  html_document:
-    df_print: paged
-  fig_caption: yes
-  pdf_document: default
-  word_document:
-    reference_docx: template.docx
-header-includes:
-   - \usepackage{floatrow}
-   - \floatsetup[figure]{capposition=top}
-always_allow_html: TRUE
-bibliography: references.bib
-csl: chicago.csl
-abstract: The Amazon Rainforest is one of the most important ecosystems in the world, and most of this biome is located in Brazil.
-Albeit the importance of understanding the relationship between the social construction of the Amazon and its effects on environmental outcomes, we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
-Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level.
-Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse.
-Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985.
-We find that, first, international environmental events appear to drive presidents to speak more about the Amazon.
-Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards.
-Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
----
-
-```{r setup, include=FALSE, warning=FALSE, message=FALSE}
-knitr::opts_chunk$set(include = FALSE)
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(skimr)
-library(scales)
-library(RColorBrewer)
-library(nnet)
-library(stargazer)
-library(kableExtra)
-Sys.setlocale("LC_ALL", "C")
-options(stringsAsFactors = FALSE, scipen = 999)
-```
-
-```{r data, message=FALSE, warning=FALSE, include=FALSE}
-# Load data
-pop<- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
-pop <-  pop %>% select(-c(title, date, text, location))
-ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
-ama <-  ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
-AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data
-amazon_def_year <- rbind(adr, amazon_def_year) 
-hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
-                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
-                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
-                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
-                           "Rousseff", "Temer", "Bolsonaro"))
-# Prepare data for problem constructions
-sov <- ama %>% 
-  filter(sov==1) %>% 
-  count(sov, year) %>%
-  group_by(year) %>%
-  select(-c(sov))%>%
-  rename (sov = n)
-ei <- ama %>% 
-  filter(ei==1) %>% 
-  count(ei, year) %>%
-  group_by(year) %>%
-  select(-c(ei))%>%
-  rename (ei = n) %>%
-  ungroup() %>%
-  tibble::add_row(year = 2017, ei = 0) %>%
-  tibble::add_row(year = 2018, ei = 0)
-sd <- ama %>% 
-  filter(sd==1) %>% 
-  count(sd, year) %>%
-  group_by(year) %>%
-  select(-c(sd))%>%
-  rename (sd = n)
-con <- ama %>% 
-  filter(con==1) %>% 
-  count(con, year) %>%
-  group_by(year) %>%
-  select(-c(con))%>%
-  rename (con = n)
-other <- ama %>% 
-  filter(other==1) %>% 
-  count(other, year) %>%
-  group_by(year) %>%
-  select(-c(other))%>%
-  rename (other = n)
-temp <- ei %>% 
-  left_join(other) %>% 
-  left_join(con) %>% 
-  left_join(sd) %>% 
-  left_join(sov) %>% 
-  replace(is.na(.), 0)
-# Get mixed types in
-ama_mx <-  ama %>%
-  unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
-                                      mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
-                                      mixed_type == '0_0_1_0' ~ "Pure Social Development",
-                                      mixed_type == '0_0_0_1' ~ "Pure Conservation",
-                                      mixed_type == '0_0_0_0' ~ "Other",
-                                      mixed_type == '0_1_0_1' ~ "Economic Conservation",
-                                      mixed_type == '0_1_1_0' ~ "Social Economic",
-                                      mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
-                                      mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
-                                      mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
-                                      mixed_type == '0_0_1_1' ~ "Social Conservation",
-                                      grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
-                                            mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
-                    "Pure Sovereignty", "Other", "Economic Conservation", 
-                    "Social Economic", "Sovereign Conservation", "Economic, Social,\nand Conservation",
-                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
-         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
-                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
-                             grepl("^Other$", mx_cat) ~ "Other",
-                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
-                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
-                                   |Social Conservation|Other Mixed-types",
-                                   mx_cat) ~ "Mixed-types"),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
-```
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985},
+  pdfauthor={Livio Silva-Muller; Henrique Sposito},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{floatrow}
+\floatsetup[figure]{capposition=top}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+
+\title{How has the Brazilian Amazon been constructed as a problem? The
+economy, the environment, the people, and the nation in the presidential
+speeches since 1985}
+\author{Livio Silva-Muller \and Henrique Sposito\footnote{Both
+  co-authors contributed equally to the article; names are ordered
+  alphabetically. Livio is a PhD Candidate in Anthropology and Sociology
+  at the Geneva Graduate Institute and affiliated to the Albert
+  Hirschman Centre on Democracy. Henrique is a PhD Candidate in
+  International Relations and Political Sciences at the Geneva Graduate
+  Institute and affiliated to the Centre for International Environmental
+  Studies.}}
+\date{8 June 2022}
+
+\begin{document}
+\maketitle
+\begin{abstract}
+The Amazon Rainforest is one of the most important ecosystems in the
+world, and most of this biome is located in Brazil. Albeit the
+importance of understanding the relationship between the social
+construction of the Amazon and its effects on environmental outcomes, we
+lack empirical accounts of how the Brazilian Amazon has been constructed
+as a problem in discourses over time, by geographical location, and
+between, or within, governments. Discursive problem-construction within
+democracies legitimize ways of thinking and acting towards the
+environment while affecting decisions to deforest, or not, at the local
+level. Building on Hirschman (1963) and Bacchi (2009) conceptualization
+of chosen problems, we propose a framework to investigate how the
+Brazilian Amazon has been constructed as a problem in political
+discourse. Combining hand-coding and supervised machine learning, we
+classify statements about the Amazon forest or region in 6130 official
+presidential speeches since 1985. We find that, first, international
+environmental events appear to drive presidents to speak more about the
+Amazon. Second, while the Amazon as a problem of economic integration
+dominated discourses from 1985 to the mid-2000s, environmental
+conservation and social development constructions briefly surpasses
+economic integration from 2010 to 2015. Constructing the Amazon as an
+issue of sovereignty also became more pertinent from 2010 onwards.
+Finally, using a multinomial regression model, we find that presidents
+are more likely to construct the Amazon as a problem of environmental
+conservation, than economic integration or social development, as
+presidents move away from the Amazon region.
+\end{abstract}
 
@@
 
-# 1 Introduction
-
-We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon's natural resources.
-We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.
-Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.Different governmental programs contained an assumptions of what had to be solved in the Amazon, or in other words, it represents the Amazon as a particular problem.
-These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
-
-Different governments along Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship is associated with both national sovereignty and then economic integration, Sarney's and Lula's presidencies are often tied to environmental conservation.
-However, governments are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of one specific problem.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
-
-In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems and @bacchi2009 concept of problem-representation in policy, we propose a framework to identify problem-constructions in political discourses.
-Although problem-construction takes place in a series of instances, we analyze the case of discourses by Brazilian presidents since 1985.
-We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
-It legitimizes ways of thinking about the Amazon.
-In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations from governments' response, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
-Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
-Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is socially constructed.
-
-To investigate how the Brazilian Amazon has been constructed as a problem in presidential discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazonian related statements within these speeches.
-We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
-We train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data.
-
-Our findings are threefold.
-First, we find that international environmental events appear to drive presidents to speak more about the Amazon.
-Second, while constructing the Amazon as a problem of economic integration dominated presidential discourses from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew from 2000s onwards briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
-Unprecedentedly, constructing the Amazon as an issue of sovereignty became more pertinent from 2010 onwards.
-Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
-
-This article proceeds as follows: first, we propose a conceptual framework to understand problem-construction in discourses.
-We then review Amazonian historiography literature to identify the main phases and their underlying problem construction.
-In the methodology section, we explain how the framework is operationalized and present the codebook.
-We proceed to describe, visualize and interpret our findings in the analysis section.
-Finally, we conclude with a discussion connecting our findings to the democratic game and environmental outcomes.
-
-# 2 Conceptual framework and contribution
-
-## 2.1 Chosen problems, presidential discourse, and policy objects
-
-Governments often have a choice in how they construct problems and what policy solutions they implement.
-In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
-Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
-Chosen problems are those governments select at their discretion.
-Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-
-Additionally, @bacchi2009 [p.
-10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts".
-The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.\@hirschman1975[p.
-388] exemplifies chosen problems with the case of the construction of Brasilia.
-Building Brasilia could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
-It is up to the discretion of the government to highlight or not the implicit problem a policy solves.
-A same policy object (e.g.
-Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.
-
-Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-Relative to how the policy is represented to be, it can be a solution of problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-@putnam1988 seminal article on the two-level game can help us make sense of this variation conceptually.
-The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
-Relatedly, @hochstetler2012 argue that international commitments in the Brazilian case shift as a function of domestic cost-benefit calculations, as the country as a large emitter does not abide to the global commons framings.
-Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
-The same policy, then, can solve the problem of environmental conservation as well as economic integration.
-
-This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests.
-We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy.
-Several scholars describe federal governments' as proponents of specific policies for the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy [@drummond2006].
-The governments from the late 1980s up to 2009, are more associated with environmental conservation.
-The presidencies of Dilma and Temer are connected to the decline of environmental policies, while Bolsonaro to the complete dismantling of environmental policies.
-While these works are important to understand how different governments acted towards the Amazon, the classification of specific governments into periods or policy cycles represents them as monolithic: they associate specific governments to one specific view of the Amazon.
-The presidency of Lula, often associated with environmental conservation because of the unprecedented decrease in deforestation.
-At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
-106].
-That is, there is more variation within governments than the literature suggests.
-
-An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue.
-While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
-Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem [@eshbaugh2010; @rottinghaus2009; @krebs2007], they direct the range of what is included in national debates [@druckman2004].
-As presidents speak in varied locations to varied audiences, it is very likely that they chose to frame similar issues differently.
-
-The possibility of different problem-constructions at the level of presidential speeches has important consequences for democracy.
-If presidents can promote different problem-constructions in different places, it is important to understand to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
-@pacheco2019 proposes that the Amazon is key to understand Brazilian state and democracy.
-Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
-The costs for said economic benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
-Political stability, thus, can be seen as a product of the trade-off between both.
-Policies during the military dictatorship were strongly geared toward integrating the Amazon into the national territory and international economy.
-These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted.
-Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that [@hecht1990].
-With the return of democracy in the 1980s, violence could not be used at the same extent as before and policies had to respond to growing environmental concern.
-
-Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
-Deforestation rates in Brazil are more responsive to the government's environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
-Relatedly, ethnographic research has also shown that expectations about governments' response are a crucial factor in decisions to deforest at the ground [@campbell2015].
-Thus, understanding diversity in presidential speeches is a first step to connect it to concrete environmental outcomes.
-
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-@calderwood2019, for instance, examines 2919 mentions of climate change in American official presidential speeches since 1989.
-Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change.
-He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-@calderwood2020 also tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-The author finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location.
-Elsewhere, @bevitori2015 investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
-The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
-These studies corroborate the possibilities of variation depending on the audience, but we are yet to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
-While these findings are US specific, they indicate that presidents raise different points about the environment at local, national, or international settings, depending on who they assume their audience is at that specific instance.
-Nevertheless, as @bacchi2009, we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
-Mentions to the lexicon as 'environment', 'preserve', or 'climate change' should be tied to the larger meaning of policies in the United States and elsewhere.
-
-On the other hand, there is also an empirical gap in terms of how the Amazon has been constructed as a problem along time and geographic location.
-While governmental discourses in Brazil have been studied for topics such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
-@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-We also find one analysis of Bolsonaro's rhetoric about the Amazon, but the study relies on a reduced sample without transparent explanations of how speeches were selected [@marquardt2022].
-
-We propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy issue and connects it to presidential speeches.
-Governments choose what problems to solve and what policies to implement.
-The same policies can be represented as solving different problems implying a degree of social construction [@bacchi2009].
-Governments can choose to emphasize or not one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-The variation in problem-construction suggests that Brazilian governments are more diverse in their positions as the literature suggests.
-An interesting site to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for democracy, and for environmental outcomes.
-As presidents speak in different places and to different audiences, it is an empirical site prone to identify variation.
-
-## 2.2 Problem-construction in Amazonian historiography
-
-To identify possible problem-constructions and their connection to the wider socio-cultural history of the country, we build on Amazonian historiography.
-We understand Amazonian historiography as the body of research conducted by social and environmental scientists that tells the story of diverse governmental programs that approaches the Amazon region, forest, and its people as a policy object demanding dedicated action.
-
-### National Sovereignty
-
-In *The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon*, @hecht1990 [p.
-1] write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites".
-These dreams of fortunes to be found in the Amazon are composed of the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" [hecht1990, preface].
-The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht2013, p.
-8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil [@hecht1990].
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War [@garfield2013].
-
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
-Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-This might come both from foreign actors as well as domestic non-state actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil while any foreign or non-state presence in the region is part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combating alleged disinformation from actors perceived as a threat.
-
-### Economic Integration
-
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
-First, nature should be conquered by men.
-Second, exploiting natural resources would render the Amazon region a global powerhouse.
-Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, and the establishment of tax-free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
-@capobianco2019 describes the period from the 1950s to the 1980s in a similar fashion, referring to a wider range of policies of economic integration such as the establishment of the tax-free zone of Manaus in the 1970s.
-The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions are often centralized by the federal government [@becker2005] and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
-
-### Social Development
-
-Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles or phases.
-While this might be related to social policies being more geared towards the whole nation, there are instances of specific social policies for the Amazon.
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights when speaking about the Amazon.
-This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.
-
-### Environmental Conservation
-
-The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions [@drummond2006].
-A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s, with the birth of modern environmentalism [@viola1987] in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
-They define it as an emphasis on the local livelihoods of people while protecting nature.
-@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies as establishment of conservation units in the Amazon in 2001.
-The environmental conservation problem-constructions emphasizes the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
-The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
-
-# 3 Methodology: operationalizing Amazonian problem-constructions
-
-## 3.1 Codebook and Data
-
-To analyze how presidents construct the Amazon as a problem in time, we build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
-We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches for all the presidents of Brazil.
-Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 946 speeches are, at least partially, about the Amazon from the 6130.
-
-Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
-By doing so we create our unit of analysis: an Amazonian statement.
-We use Amazon statements as our unit of analysis for two main reasons.
-First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
-This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
-On average, an Amazonian statement contains 123 words.
-
-We follow the procedures outlined by @grimmer2022 for supervised classification.First, we develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
-In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
-Nevertheless, each Amazonian statement might be assigned to one or more codes.
-A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation.
-Amazonian statements, thus, can be either coded as pure-types or mixed-types.
-Mixed-types are relevant as constructions and policies are often multifaceted while portraying the Amazon as a combination of these problem-constructions.
-Figure 1, below, portrays this operationalization strategy.
-
-````{=tex}
+\hypertarget{introduction}{%
+\section{1 Introduction}\label{introduction}}
+
+We need to protect the Amazon from foreign interests. We need to exploit
+the Amazon's natural resources. We need to provide better living
+standards for the people in the Amazon. We need to preserve the Amazon
+as a standing ecosystem. Historically, the Brazilian government
+approached the Amazon region, forest and its people as a policy
+object.Different governmental programs contained an assumptions of what
+had to be solved in the Amazon, or in other words, it represents the
+Amazon as a particular problem. These specific problems touch on shared
+imaginaries of the Amazon as part of the larger socio-cultural history
+of the country as, for example, in relation to issues of national
+sovereignty, economic integration, social development, or environmental
+conservation.
+
+Different governments along Brazilian history have been described as
+proponents of a specific view of the Amazon (Drummond and Barros-Platiau
+2006; Pádua 2012; Franchini and Viola 2019; Capobianco 2019; Pereira and
+Viola 2021). While the military dictatorship is associated with both
+national sovereignty and then economic integration, Sarney's and Lula's
+presidencies are often tied to environmental conservation. However,
+governments are usually represented monolithically, advancing a view
+that specific governments see the Amazon as an instance of one specific
+problem. Albeit the current calls to understand the environment as a
+social-cultural construction and to identify the effect of culture on
+environmental outcomes (Waroux et al. 2021), we lack empirical accounts
+of how the Brazilian Amazon has been constructed as a problem in
+discourses over time, by geographical location, and between, or within,
+governments.
+
+In this article, we investigate how the Brazilian Amazon has been
+constructed as a problem in political discourses. Building on Hirschman
+(1963) concept of chosen problems and Bacchi (2009) concept of
+problem-representation in policy, we propose a framework to identify
+problem-constructions in political discourses. Although
+problem-construction takes place in a series of instances, we analyze
+the case of discourses by Brazilian presidents since 1985. We opt for
+presidential speeches for two reasons. First, presidential discourses
+have the power to introduce and justify public policy, as well as shape
+its perception to broad audiences (Zarefsky 2004; Gillion 2016). It
+legitimizes ways of thinking about the Amazon. In turn, policy
+perception is key for policy adoption and implementation (Alesina and
+Giuliano 2009; López et al. 2020). This is especially pertinent to
+deforestation in Brazil as expectations from governments' response,
+generated from material and discursive governmental practices (Assunção,
+Gandour, and Rocha 2015; Capobianco 2019, 2021), are a crucial factor in
+decisions to deforest at the ground (Campbell 2015). Second, we argue
+that presidents can employ specific problem-constructions that build
+objects as specific problems depending on who they speak to.
+Presidential discourses take place in different sites, from launching a
+new bridge in a small municipality in the middle of the Amazon to a
+keynote speech in a business association in São Paulo or at the UN
+general assembly in New York. Working with presidential discourses
+allows us to identify this variation in meaningful ways and better
+understand how the Amazon is socially constructed.
+
+To investigate how the Brazilian Amazon has been constructed as a
+problem in presidential discourses, we create a dataset containing 6130
+official presidential speeches by all Brazilian presidents since 1985.
+We subset the dataset by identifying Amazonian related statements within
+these speeches. We find that 2014 sections in these discourses refer to
+the Amazon at least once. We then develop a codebook grounded on
+Amazonian historiography to code how each of these statements constructs
+the Amazon as a particular problem. We use this codebook to manually
+code a randomly selected training set of the Amazonian related
+statements. We train a supervised machine-learning model in the
+hand-coded set and automatically label the remaining set of Amazonian
+statements. We then conduct a descriptive and inferential analysis of
+this data.
+
+Our findings are threefold. First, we find that international
+environmental events appear to drive presidents to speak more about the
+Amazon. Second, while constructing the Amazon as a problem of economic
+integration dominated presidential discourses from 1985 to the
+mid-2000s, environmental conservation and social development
+constructions steadily grew from 2000s onwards briefly surpassing
+economic integration as more common problem constructions from 2010 to
+2015. Unprecedentedly, constructing the Amazon as an issue of
+sovereignty became more pertinent from 2010 onwards. Finally, using a
+multinomial regression model, we find that presidents are more likely to
+construct the Amazon as a problem of environmental conservation, than
+economic integration or social development, as presidents move away from
+the Amazon region.
+
+This article proceeds as follows: first, we propose a conceptual
+framework to understand problem-construction in discourses. We then
+review Amazonian historiography literature to identify the main phases
+and their underlying problem construction. In the methodology section,
+we explain how the framework is operationalized and present the
+codebook. We proceed to describe, visualize and interpret our findings
+in the analysis section. Finally, we conclude with a discussion
+connecting our findings to the democratic game and environmental
+outcomes.
+
+\hypertarget{conceptual-framework-and-contribution}{%
+\section{2 Conceptual framework and
+contribution}\label{conceptual-framework-and-contribution}}
+
+\hypertarget{chosen-problems-presidential-discourse-and-policy-objects}{%
+\subsection{2.1 Chosen problems, presidential discourse, and policy
+objects}\label{chosen-problems-presidential-discourse-and-policy-objects}}
+
+Governments often have a choice in how they construct problems and what
+policy solutions they implement. In ``Journey towards Progress'',
+Hirschman (1963) draws a conceptual distinction between pressing
+problems (pressured from outside parties to the government) and chosen
+problems (chosen by the government at their own discretion). Pressing
+problems can be either privileged or neglected, depending on the degree
+of pressure exercised by the interested groups. Chosen problems are
+those governments select at their discretion. Problems can change from
+pressing to chosen across time and in space as a function of (a)
+solutions becoming available, (b) a change of level of government
+control in society, or (c) a shift of interests from top policymakers
+(Hirschman 1963).
+
+Additionally, Bacchi (2009, 10) argues that policies have a cultural
+dimension as ``it takes shape within specific historical and national or
+international contexts''. The existence or proposal of a policy implies
+that there is a (public) problem that needs (governmental) action to be
+fixed. The alleged problem is not always explicitly stated in policy:
+policies are represented as solutions for implicit
+problems.@hirschman1975{[}p.~388{]} exemplifies chosen problems with the
+case of the construction of Brasilia. Building Brasilia could solve a
+problem of regional inequality, a problem of a dormant economy without
+state investment, a problem of political representation, or all three.
+It is up to the discretion of the government to highlight or not the
+implicit problem a policy solves. A same policy object (e.g.~Brasilia,
+the Amazon, criminality, poverty), thus, can be constructed as pressing
+or not depending on how a government represents it.
+
+Governments can choose to emphasize (or not) one or more implicit
+problems that a policy solves depending on which interest group they are
+in communication with. Relative to how the policy is represented to be,
+it can be a solution of problems that are considered pressing or not for
+different groups and it is up to the discretion of the political actor
+to construct a particular problem in a particular way given context.
+Putnam (1988) seminal article on the two-level game can help us make
+sense of this variation conceptually. The author argues that the
+outcomes of international negotiations lie within the overlap between
+the pressure of domestic groups and international groups. Taking the
+example of the 2012 Forest Code and the Amazon, President Dilma could
+emphasize its rural character for environmentalists at the Paris Summit,
+or the amnesty for deforestation for agricultural elites. The same
+policy, then, can solve the problem of environmental conservation as
+well as economic integration.
+
+This variation in problem-construction suggests that governments are
+more diverse in their positions as the literature suggests. We
+conceptualize the Amazon region, forest, and people to be a policy
+object, this is a specific issue that deserves dedicated policy. Several
+scholars describe federal governments' as proponents of specific
+policies for the Amazon (see Drummond and Barros-Platiau 2006; Pádua
+2012; Franchini and Viola 2019; Capobianco 2019; Pereira and Viola
+2021). In this literature, the 1964 military dictatorship is associated
+with securing national sovereignty in the region by populating it and
+integrating it to the national economy (Drummond and Barros-Platiau
+2006). The governments from the late 1980s up to 2009, are more
+associated with environmental conservation. The presidencies of Dilma
+and Temer are connected to the decline of environmental policies, while
+Bolsonaro to the complete dismantling of environmental policies. While
+these works are important to understand how different governments acted
+towards the Amazon, the classification of specific governments into
+periods or policy cycles represents them as monolithic: they associate
+specific governments to one specific view of the Amazon. The presidency
+of Lula, often associated with environmental conservation because of the
+unprecedented decrease in deforestation. At the same time, during his
+terms governmental credits to agricultural expansion and the cattle
+industry were 20 times more than the budget of the Ministry of the
+Environment for this entire period (Capobianco 2021, 106). That is,
+there is more variation within governments than the literature suggests.
+
+An interesting site to study the relationship between varied
+problem-construction and policy issues is presidential speeches as they
+legitimize ways of thinking about an issue. While the relationship
+between presidential speeches and policy is not causal, they have the
+power to introduce and justify public policy, as well as shape its
+perception to broad audiences (Zarefsky 2004; Gillion 2016). Even if
+presidential discourse might not persuade public opinion regarding a
+proposed solution for a problem (Eshbaugh-Soha 2010; Rottinghaus 2009;
+Krebs and Jackson 2007), they direct the range of what is included in
+national debates (Druckman and Holmes 2004). As presidents speak in
+varied locations to varied audiences, it is very likely that they chose
+to frame similar issues differently.
+
+The possibility of different problem-constructions at the level of
+presidential speeches has important consequences for democracy. If
+presidents can promote different problem-constructions in different
+places, it is important to understand to what extent the implemented
+agenda correlates with their local, federal, or international
+problem-constructions. Pacheco (2019) proposes that the Amazon is key to
+understand Brazilian state and democracy. Specifically, the author
+states that the natural richness of the region has been instrumentally
+transformed in political support through resource exploration by
+different governments over the last centuries. The costs for said
+economic benefits are the livelihoods of indigenous and traditional
+populations and the ecosystems they reside in. Political stability,
+thus, can be seen as a product of the trade-off between both. Policies
+during the military dictatorship were strongly geared toward integrating
+the Amazon into the national territory and international economy. These
+were times when deforestation increased, but political stability was
+achieved as those bearing the costs of said deforestation were being
+targeted. Generally high levels of violence in the region, epitomized in
+the assassination of Chico Mendes, serve as evidence for that (Hecht and
+Cockburn 1990). With the return of democracy in the 1980s, violence
+could not be used at the same extent as before and policies had to
+respond to growing environmental concern.
+
+Relatedly, the possibility of different problem-constructions has
+consequences for environmental outcomes as well. When Brazilian
+presidents speak about the Amazon it not only makes headlines,
+nationally and internationally (Brice and Smith 2021; Harris 2021;
+Miranda 2021), but also incites responses, shapes expectations, and
+feeds into the behavior of many actors involved in the Amazon.
+Deforestation rates in Brazil are more responsive to the government's
+environmental policy, generated from material and discursive
+governmental practices, than exogenous factors as market fluctuations
+(Assunção, Gandour, and Rocha 2015; Capobianco 2019, 2021).
+Specifically, Capobianco finds that that the perception of higher risk
+of being caught for deforestation in the Amazon is the main mechanism
+through which environmental policy is effective. Relatedly, ethnographic
+research has also shown that expectations about governments' response
+are a crucial factor in decisions to deforest at the ground (Campbell
+2015). Thus, understanding diversity in presidential speeches is a first
+step to connect it to concrete environmental outcomes.
+
+The connection between presidential discourse and the environment has
+been studied in the case of the United States but remains conceptually
+underdeveloped. Calderwood (2019), for instance, examines 2919 mentions
+of climate change in American official presidential speeches since 1989.
+Among various findings, one that stands out is that American presidents
+frequently side-step the environmental aspects of climate change. He
+also identifies a shift from economic to security framing of climate
+issues, side-lining its environmental aspects. Calderwood (2020) also
+tests the effect of geographic location and type of communication
+regarding climate change. Building prominently on Putnam (1988), he
+hypothesizes that presidents are more likely to mention climate change
+in foreign locations, and that location influences the specific
+discursive approach and tone they adopt. The author finds evidence in
+support of his hypothesis, suggesting American presidential discourse at
+the top on global warming changes based on location. Elsewhere, Bevitori
+(2015) investigates how the `environment' has been constructed in
+American presidential discourse since 1960 using a more automated
+approach. The author finds that mentions of the environment are
+typically co-selected with the pronoun `our', as well as with `economy',
+`clean', and `preserve'. These studies corroborate the possibilities of
+variation depending on the audience, but we are yet to tie vocabulary to
+specific problem-constructions based on wider shared meanings of
+environment and climate change. While these findings are US specific,
+they indicate that presidents raise different points about the
+environment at local, national, or international settings, depending on
+who they assume their audience is at that specific instance.
+Nevertheless, as Bacchi (2009), we argue that problem-constructions
+touch on shared meanings about the region that are available to the
+speaker as part of larger social-cultural history. Mentions to the
+lexicon as `environment', `preserve', or `climate change' should be tied
+to the larger meaning of policies in the United States and elsewhere.
+
+On the other hand, there is also an empirical gap in terms of how the
+Amazon has been constructed as a problem along time and geographic
+location. While governmental discourses in Brazil have been studied for
+topics such as inflation or race relations, we only find one systematic
+analysis of Amazonian discourse. Barros (2020) investigates Amazonian
+discourse in the Brazilian Congress with the objective of identifying
+the arguments put forth by congressmen. The main finding is that the
+economic value of the Amazon for the cattle industry is the most salient
+narrative, leading the author to conclude there is a mismatch between
+the international debate (which focuses on preservation) and the
+national debate (which focuses on economic development).
+
+We propose a conceptual framework that accepts the possibility of varied
+problem-construction for the same policy issue and connects it to
+presidential speeches. Governments choose what problems to solve and
+what policies to implement. The same policies can be represented as
+solving different problems implying a degree of social construction
+(Bacchi 2009). Governments can choose to emphasize or not one or more
+implicit problems that a policy solves depending on which interest group
+they are in communication with. The variation in problem-construction
+suggests that Brazilian governments are more diverse in their positions
+as the literature suggests. An interesting site to study the
+relationship between varied problem-construction and policy is
+presidential speeches as they legitimize ways of thinking about an
+issue, matter for democracy, and for environmental outcomes. As
+presidents speak in different places and to different audiences, it is
+an empirical site prone to identify variation.
+
+\hypertarget{problem-construction-in-amazonian-historiography}{%
+\subsection{2.2 Problem-construction in Amazonian
+historiography}\label{problem-construction-in-amazonian-historiography}}
+
+To identify possible problem-constructions and their connection to the
+wider socio-cultural history of the country, we build on Amazonian
+historiography. We understand Amazonian historiography as the body of
+research conducted by social and environmental scientists that tells the
+story of diverse governmental programs that approaches the Amazon
+region, forest, and its people as a policy object demanding dedicated
+action.
+
+\hypertarget{national-sovereignty}{%
+\subsubsection{National Sovereignty}\label{national-sovereignty}}
+
+In \emph{The Fate of the Forest: Developers, Destroyers, and Defenders
+of the Amazon}, Hecht and Cockburn (1990, 1) write that all over the
+world tropical forests are destroyed, but ``what imbues the case of the
+Amazon with such passion is the symbolic content of the dreams it
+ignites''. These dreams of fortunes to be found in the Amazon are
+composed of the imaginaries of bandeirantes from the southeast of Brazil
+and colonizers from everywhere else. It rendered the territory the venue
+for aspiration and the object of an intense scramble in the subsequent
+centuries, defined as ``a (\ldots) form of nation building (\ldots)''
+{[}hecht1990, preface{]}. The Portuguese empire and subsequently the
+Brazilian monarchy were concerned with establishing their territory. In
+the process of securing Amazonian borders, Brazil thwarted ``the
+imperial ambitions of France, Britain, the United States, Belgium,
+Bolivia, and Peru'' (Hecht 2013, 8), and when the dust settled and the
+scramble was over, half of the Amazon emerged Brazilian. While Brazilian
+military diplomacy was very successful, the process did not come without
+its traumas. A significant experience was the negotiations with Bolivia
+in 1902 to secure the Amazonian state of Acre, during which they found
+out about American attempts to trick Brazil (Hecht and Cockburn 1990).
+This case was still part of the memory of the generals who led the
+country during the military dictatorship of 1964 and wanted to protect
+Brazil's sovereignty over the Amazon from the communist threat during
+the Cold War (Garfield 2013).
+
+As we move from a world where non-state actors gain importance in
+environmental governance and international politics generally
+(Silva-Muller and Faul 2022; Andonova 2014; Westerwinter 2021), the
+sovereignty problem becomes more varied. Multiple non-state actors
+(NGOs, foundations, IOs, and so on) join the conversation about
+Amazonian policies more substantially as the military dictatorship
+starts to end (Hochstetler 2021; Capobianco 2019; Franchini and Viola
+2019). Threads to national sovereignty, consequently, can be interpreted
+as coming from a different set of actors than before. Allegedly false
+claims about the Brazilian Amazon in international and domestic fora,
+for instance, are often tied to strategies of `internationalizing' the
+Amazon. This might come both from foreign actors as well as domestic
+non-state actors. The sovereignty problem-construction advances the view
+that the Brazilian Amazon belongs to Brazil while any foreign or
+non-state presence in the region is part of a broad strategy to take the
+region. The policy solutions to the issue of sovereignty, included the
+monitoring of the borders, strict regimes related to entry in the
+region, assertions of ownership nationally and internationally, and
+combating alleged disinformation from actors perceived as a threat.
+
+\hypertarget{economic-integration}{%
+\subsubsection{Economic Integration}\label{economic-integration}}
+
+The Vargas dictatorship (1937-46) and the military dictatorship
+(1964-89) took over the task of modernizing the Amazon. In 1966, the
+Brazilian Military launched Operation Amazon, a policy to modernize the
+region based on a set of assumptions (Acker 2014). First, nature should
+be conquered by men. Second, exploiting natural resources would render
+the Amazon region a global powerhouse. Third, such a project would
+integrate the region with the rest of the country. Concretely, this
+meant a series of infrastructure projects, such as roads and dams,
+incentives for settlers to develop ranches and expand the agricultural
+frontier, and the establishment of tax-free zones to attract industry.
+The capital to conduct such changes, paradoxically, came from national
+and international sources (Acker 2014), leading to a series of national
+and international enterprises settling in the Amazon region. Capobianco
+(2019) describes the period from the 1950s to the 1980s in a similar
+fashion, referring to a wider range of policies of economic integration
+such as the establishment of the tax-free zone of Manaus in the 1970s.
+The economic integration problem-construction advances the view that the
+Brazilian Amazon needs to be developed and modernized. These policy
+solutions are often centralized by the federal government (Becker 2005)
+and have at their core the development of the necessary infrastructure
+(physical, fiscal, or monetary) to integrate the region into the
+national and international economy.
+
+\hypertarget{social-development}{%
+\subsubsection{Social Development}\label{social-development}}
+
+Closely related to economic integration, social development is a
+problem-construction that is often neglected while describing policy
+cycles or phases. While this might be related to social policies being
+more geared towards the whole nation, there are instances of specific
+social policies for the Amazon.Governments can emphasize the lack of
+hospitals, sanitation, and schools concerning peoples' dignity,
+standards of living, and other constitutional rights when speaking about
+the Amazon. This is not only relevant as a construction, but speaks,
+minimally, to democratic concerns over providing electorates, especially
+in the Amazonian region, with better standards of living than
+previously.
+
+\hypertarget{environmental-conservation}{%
+\subsubsection{Environmental
+Conservation}\label{environmental-conservation}}
+
+The rapid economic changes in the region in the 1960s, 1970s, and 1980s
+were matched with the birth of environmental institutions (Drummond and
+Barros-Platiau 2006). A common explanation for the creation of these
+institutions in the Amazonian literature is the impression of the lack
+of control over the market engendered years of centralized economic
+integration in the region (Acker 2021; Capobianco 2021; Hecht and
+Cockburn 1990). This process accelerated in the late 1980s, with the
+birth of modern environmentalism (Viola 1987) in the 1980s, epitomized
+in the 1992 Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco
+2021). Hochstetler and Keck (2007) argue that during preparations for
+the summit, a new form of Brazilian environmentalism emerged:
+socio-environmentalism. They define it as an emphasis on the local
+livelihoods of people while protecting nature. Capobianco (2019) argues
+in a similar line, establishing socio-environmentalism as the main
+government response in the 1990s and early 2000s in a series of policies
+as establishment of conservation units in the Amazon in 2001. The
+environmental conservation problem-constructions emphasizes the Amazon
+should be preserved, deforestation should be halted, and the sustainable
+practices of indigenous and local peoples should be maintained through
+the protection of their territories and rights to self-determination
+(Hochstetler and Keck 2007). The policy solution implies more investment
+in command-and-control infrastructure (as remote-sensing technology for
+environmental outcome measurement), more investment in the valuation of
+standing ecosystems through incentive schemes, and more policies
+facilitating indigenous environmental practices.
+
+\hypertarget{methodology-operationalizing-amazonian-problem-constructions}{%
+\section{3 Methodology: operationalizing Amazonian
+problem-constructions}\label{methodology-operationalizing-amazonian-problem-constructions}}
+
+\hypertarget{codebook-and-data}{%
+\subsection{3.1 Codebook and Data}\label{codebook-and-data}}
+
+To analyze how presidents construct the Amazon as a problem in time, we
+build upon the dataset provided by (Cezar 2020) which contains all
+official speeches by Brazilian Presidents from 1985 to 2019 scrapped
+from the archives of the Brazilian Presidential Library. We update the
+dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches for all the presidents of
+Brazil. Then, we proceed to identify all speeches that refer to the
+Amazon as a region, people, or forest in these speeches. We do so by
+detecting all speeches in which the stem ``amazon'' appears. In
+Portuguese, the stem captures terms such as ``Amazonia'', ``Amazonica'',
+``Amazonidas'', ``Amazonense(s)'', ``Amazonas'', among others. We find
+that 946 speeches are, at least partially, about the Amazon from the
+6130.
+
+Using the poldis R package (Sposito 2021), we proceed to extract two
+sentences before and two sentences after the sentence in which the stem
+``amazon'' appears. We opt for picking two sentences before and two
+sentences after, rather than words, because sentences usually contain a
+cohesive idea. By doing so we create our unit of analysis: an Amazonian
+statement. We use Amazon statements as our unit of analysis for two main
+reasons. First, working at the level of statements allows us to identify
+only passages that are meaningful for our specific purpose. Second, it
+increases the number of our observations and its variety meaningfully,
+allowing for more specificity in our analysis. This process yields 2014
+unique Amazonian statements across the 946 speeches about the Amazon
+identified. When an Amazonian statement contains two or more matches of
+the stem ``amazon'', we get two sentences before the first match and two
+sentences after the last match. On average, an Amazonian statement
+contains 123 words.
+
+We follow the procedures outlined by Grimmer, Roberts, and Stewart
+(2022) for supervised classification.First, we develop a codebook to
+code Amazonian statements in one or more problem-constructions (see
+codebook in appendix). In their conceptualization, each
+problem-construction is mutually exclusive, meaning that they cover
+different forms of constructing the Amazon as a problem. Nevertheless,
+each Amazonian statement might be assigned to one or more codes. A
+statement can, for example, construct the Amazon as a problem of
+sovereignty and a problem of economic integration, or a problem of
+social development and conservation. Amazonian statements, thus, can be
+either coded as pure-types or mixed-types. Mixed-types are relevant as
+constructions and policies are often multifaceted while portraying the
+Amazon as a combination of these problem-constructions. Figure 1, below,
+portrays this operationalization strategy.
+
 \begin{landscape}
 
-```{r figure1, echo=FALSE, fig.cap="Operationalization of problem-constructions", out.width = '100%', include=TRUE}
-knitr::include_graphics("figure1pic.png")
-```
+\begin{figure}
+\includegraphics[width=1\linewidth]{figure1pic} \caption{Operationalization of problem-constructions}\label{fig:figure1}
+\end{figure}
 
 \end{landscape}
-````
-
-Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazon Statements identified.
-We chose to hand code half of the observations because since there are several nuances in discourse in how presidents talk about the amazon in time and as a problem, we conservatively code a relatively large training set for the subsequent automated machine learning.
-As well, this allows a robust validation set to verify the models.
-As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable enough.
-Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-Intercoder agreement for each of the four main categories was 85%, on average.
-For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
-
-Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006] .
-The SVM model is first trained using the hand coded training set and then employed to classify observations in the hand coded validation set.
-The trained SVM model was, on average 82%, accurate in classifying observations in the validation set before being tuned.
-After the SVM model is tuned, we use the model to automatically code the remaining 1007 Amazonian statements.
-The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements.
-Finally, we extract locations for all speeches in the data.
-These locations represent the Brazilian state in which certain speech was given or an international country.
-
-## 3.2 Analysis and Limitations
-
-To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-To test whether different problem constructions change according to location, we run a multinomial logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case [@kwak2002].
-In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
-We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.
-
-This approach also comes with limitations.
-Our codebook is developed using specific Amazon-related vocabulary.
-For example, a statement will be coded as economic integration if it is meaningful support to the tax-free zone of Manaus or a Dam in the Amazon.
-However, the economy is generally a topic that presidents speak about.
-Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
-Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
-Nevertheless, our dataset covers only what is considered an official remark.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently started to appear on social media.
-Problem- construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.
-
-# 4 The Amazon in Presidential Speeches
-
-## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
-
-The frequency in which the Amazon appears across all official presidential speeches varies in time.
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches per year.
-We observe five local maxima: 1989, 1992, 2009, 2015, and 2019.
-These points, usually, coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
-For instance, in 1985 the Amazon appeared in about 4% of all the presidential speeches but by 1988 this had increased to around 14%.
+
+Second, with the codebook in hand, each one of the authors, separately,
+hand-coded the same set of 1007 randomly selected Amazonian statements.
+This amount refers to 50\% of all the Amazon Statements identified. We
+chose to hand code half of the observations because since there are
+several nuances in discourse in how presidents talk about the amazon in
+time and as a problem, we conservatively code a relatively large
+training set for the subsequent automated machine learning. As well,
+this allows a robust validation set to verify the models. As the size of
+the training set should increase with the number of categories (Grimmer,
+Roberts, and Stewart 2022), we deemed four categories and 50\% of the
+statements as reliable enough. Also, automating the coding of half of
+the observations saved the authors over one month of work in comparison
+to manual coding. Intercoder agreement for each of the four main
+categories was 85\%, on average. For each non-matching coded
+observation, the co-authors discussed and sorted their disagreements.
+
+Third, the hand-coded data is then randomly divided into a training set,
+containing 80\% of the hand-coded observations (806 observations), and a
+validation set, containing the remaining 20\% of the hand-coded data
+(201 observations). We chose to employ a support-vector machine (SVM)
+algorithm to label texts, that is, a non- probabilistic linear
+classifier that classifies documents by assigning points in mapped space
+to maximize the gap between binary categories (Meyer et al. 2021; Noble
+2006) . The SVM model is first trained using the hand coded training set
+and then employed to classify observations in the hand coded validation
+set. The trained SVM model was, on average 82\%, accurate in classifying
+observations in the validation set before being tuned. After the SVM
+model is tuned, we use the model to automatically code the remaining
+1007 Amazonian statements. The final dataset for analysis, excluding
+false positive matches, contains 1895 coded Amazonian statements.
+Finally, we extract locations for all speeches in the data. These
+locations represent the Brazilian state in which certain speech was
+given or an international country.
+
+\hypertarget{analysis-and-limitations}{%
+\subsection{3.2 Analysis and
+Limitations}\label{analysis-and-limitations}}
+
+To analyze our data, we first present a series of different plots on
+proportions of Amazonian statements and problem-constructions over time
+and by presidents. To test whether different problem constructions
+change according to location, we run a multinomial logit model in which
+different problem constructions (as categories) are the dependent
+variable and location is the independent variable. Multinomial logit is
+an appropriate method for modeling data in which the dependent variable
+of interest is categorical, unordered, and has many categories, as is
+our case (Kwak and Clayton-Matthews 2002). In our model, we also control
+for annual deforestation rates, annual inflation rates, and election
+years in the model. We interpret the plots and model considering
+multiple Amazon related events and policies over the last 30 years, as
+well as their correlations with different presidents and locations,
+while embedding problem-construction in contemporary happenings.
+
+This approach also comes with limitations. Our codebook is developed
+using specific Amazon-related vocabulary. For example, a statement will
+be coded as economic integration if it is meaningful support to the
+tax-free zone of Manaus or a Dam in the Amazon. However, the economy is
+generally a topic that presidents speak about. Hence, the high incidence
+of economic integration in Amazonian statements can also be related to
+the higher importance of this problem-construction in Brazil in time.
+Moreover, we classify statements as Amazonian based on a dictionary
+composed of a single lexicon stem: ``amazon''. We chose to do so knowing
+that a few speeches about the Amazon might not contain the lexicon
+``Amazon'', for example, when the president says, ``the forest'' or
+``deforestation''. Hence, we might be missing statements about Amazon
+that do not refer to it. However, we consider this safer as we cannot be
+sure that mentions of the forest or deforestation do not correspond to
+other biomes such as the Cerrado or the Mata Atlantica. Nevertheless,
+our dataset covers only what is considered an official remark.
+Presidents, though, give interviews, appear in debates, talk at campaign
+rallies, and more recently started to appear on social media. Problem-
+construction within presidential discourse, thus, also happens in
+different sites for which we do not account for in this paper.
+
+\hypertarget{the-amazon-in-presidential-speeches}{%
+\section{4 The Amazon in Presidential
+Speeches}\label{the-amazon-in-presidential-speeches}}
+
+\hypertarget{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}{%
+\subsection{4.1 The rises and falls of the Amazon as a topic in
+presidential
+speeches}\label{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}}
+
+The frequency in which the Amazon appears across all official
+presidential speeches varies in time. Figure 2, below, shows the
+proportion of speeches that mentions the Amazon in relation to all
+speeches per year. We observe five local maxima: 1989, 1992, 2009, 2015,
+and 2019. These points, usually, coincide with events that help us
+explain the rises and falls of the Amazon in presidential discourse in
+time. For instance, in 1985 the Amazon appeared in about 4\% of all the
+presidential speeches but by 1988 this had increased to around 14\%.
 This is the period when the Brazilian Constitution was written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and the protection of their territories [@hecht1990].
-These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-However, in 1989, the Amazon appeared in 32% of all speeches.
-This spike is likely explained by the brutal murder of Chico Mendes and the very end of 1988.
-An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021].
-
-```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc1 <- pop %>%
-  count(amazon_speech, year) %>%
-  group_by(year) %>%
-  mutate(perc=n / sum(n)) %>%
-  filter(amazon_speech == 1) %>% 
-  select(c(perc, amazon_speech, year))
-######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
-######## Issue is with biblioteca presidencial, not with scarping btw ######
-# summary(as.factor(pop$year))
-# Simple plot
-Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(color = "darkgreen") +
-  scale_y_continuous(labels = percent_format()) +
-  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
-  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
-             linetype = "dotted") +
-  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-       subtitle = "Sample composed by 6130 presidential speeches since 1985",
-       caption = "",
-       color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
-# # Same plot but annotated
-# Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(color = "darkgreen") +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
-#              linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom") +
-#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
-#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
-#            alpha = 0.1) +
-#   annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
-#            label = hp$presid, alpha = 0.4) +
-#   annotate(geom = "segment", x = amazon_def_year$year, y = amazon_def_year$def_year)
-# # # With a few lines under the
-# cat1 <- ama_mx %>%
-#   mutate(cat = ifelse(mx_cat2 == "Mixed-types", "Mixed-types", paste(mx_cat))) %>%
-#   count(cat, year) %>%
-#   group_by(year) %>%
-#   mutate(perc = n / sum(n),
-#          perc_type = ifelse(perc == 1, 0.25, perc)) %>% 
-#   arrange(year) %>%
-#   select(c(cat, year, perc_type))
-# year_share <- merge(perc1, cat1, "year") %>%
-#   mutate(year_perc = perc*perc_type)
-# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(aes(y = perc)) +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_line(aes(x = year, y = year_perc, fill = cat, group = cat, color = cat)) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = c(1988, 1992, 2009, 2015),
-#              linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# # For filling the area under the line
-# Amazon_year <- year_share %>% ggplot(., aes(x = year, y = year_perc, fill = cat)) +
-#   geom_line() +
-#   geom_area() +
-#   scale_y_continuous(labels = percent_format()) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_vline(xintercept = 1988, linetype = "dotted") +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-#   geom_vline(xintercept = 1992, linetype = "dotted") +
-#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) +
-#   geom_vline(xintercept = 2009, linetype = "dotted") +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-#   geom_vline(xintercept = 2015, linetype = "dotted") +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "",
-#        color = 'Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# # Controling for inflation and deforastation
-# pop2 <- pop %>% count(amazon_speech, year, president) %>%
-#   group_by(year, president) %>%
-#   left_join(perc1) %>%
-#   filter(amazon_speech==1)
-# pop2 <- left_join(pop2, AAI, by = "year")
-# pop2 <- left_join(pop2, amazon_def_year, by = "year")
-# model <- lm(perc ~ AAI+ def_year + president, data=pop2)
-# pop2$predicted = predict(model, pop2)
-# Amazon_year <- pop2 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(size=.85, aes(x=year, y=perc, color="Real share")) +
-#   geom_line(size=.45, aes(x=year, y=predicted, color= "Predicted share")) +
-#   geom_text(aes(x = 1988, y = 0.34, label = "Chico Mendes/NYT"), size = 3) +
-#   geom_vline(xintercept = 1988, linetype="dotted") +
-#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) + 
-#   geom_vline(xintercept = 1992, linetype="dotted") +
-#   geom_text(aes(x = 2009, y = 0.25, label = "Copenhagen Summit"), size = 3) + 
-#   geom_vline(xintercept = 2009, linetype="dotted") +
-#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) + 
-#   geom_vline(xintercept = 2015, linetype="dotted") +
-#   scale_color_manual(values = c("Real share" = "darkolivegreen", "Predicted share" = "gray40")) +
-#   scale_y_continuous(labels = percent_format()) +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
-#        caption = "Predicted share controls for deforestation rates, inflation, and president.",
-#        color='Y series') +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-Amazon_year
-```
-
-In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
-The 1992 Earth Summit, held in Brazil brought international attention to environmental topics in the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-Throughout the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon appeared, on average, on 15% of all speeches.
-Exceptionally, in 2009 we see another spike in the Amazon appearing in official speeches.
-This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
-
-From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-From 2010 to 2014, mentions of the Amazon went down from 18% to 8% in official speeches.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
-In 2011, the New Forest Code, which regularized land ownership of many illegally deforested areas, was also approved.
-These are also the years when Brazil entered a long period of political and economic instability, which eventually led to the impeachment of Dilma Roussef.
-Though, in 2015, the Amazon appeared in 19% of speeches.
-This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation.
-By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
-
-We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
-At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets.
-This brought issues related to environmental conservation as high priorities in Bolsonaro's governing agenda with efforts to dismantle key pillars of Brazilian environmental governance.
-At the same time, President Bolsonaro retrieves Brazil's hosting status for COP25.
-In short, relevant international events drive interest and alter how pressing the "Amazon problem" is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers.
-
-## 4.2 How has the Amazon been constructed as a problem?
-
-### Pure-type problem constructions
-
-We conceptualize four pure problem constructions: sovereignty, economic integration, social development, and conservation.
-At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement.
-Figure 3, below, illustrates the share of each pure type in time.
-Pure problem constructions dominate, with an average of 56% of all amazonian statements across time.
-As above, we observe a strong variation over time for most of these constructions.
-
-```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
-pure_types_time <- ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat2 == "Pure-types") %>% 
-  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure type by year",
-       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "Curves in the plot were smoothed using loess method.") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom") +
-  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
-           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
-           alpha = 0.1) +
-  annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
-           label = hp$presid, alpha = 0.4)
-pure_types_time
-```
-
-Amazonian constructions are not monolithic in time nor within governments.
-The same governments construct the Amazon as different issues in discourse.
-Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
-This is especially pertinent during the Cardoso administration as the Amazon was constructed, overwhelmingly, as an issue of economic integration.
-However, during Lula's terms in office, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased.
-These constructions surpassed economic integration around 2010.
-These trends in discourse continued during the Rousseff administration.
-@capobianco2021, for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being paid to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.
-
-From the mid-2010s onwards, we start to see a reverse of this trend: economic integration problem construction increases while conservation and social development constructions decrease instead.
-Interestingly, sovereignty starts to increase steadily from 2010 onwards and by 2019 sovereignty constructions surpass social development.
-Figure 3 also highlights that, while the reversal precedes the mandate of President Bolsonaro, it was with him that sovereignty constructions reached unprecedented levels since the establishment of Brazilian democracy.
-
-### Mixed-type problem constructions
-
-Although presidents prefer pure problem-constructions, they also construct the Amazon as multifaceted issues.
-Mixed-type problem constructions in discourse offer more complex understandings of the Amazon as an issue.
-Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
-While there is some variation in time, some mixed-types rarely appear, thus, we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the average mixed-types by president.
-
-```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mixed_types_presid <- ama_mx %>%
-  count(president, mx_cat, mx_cat2) %>%
-  group_by(president) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x = president, y = perc, fill = mx_cat,
-             label = scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat = "identity", position = "stack") +
-  geom_text(size = 2, position = position_stack(vjust = .5)) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
-       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "right")
-mixed_types_presid
-# mixed_types_time <- ama_mx %>%
-#   count(mx_cat, mx_cat2, year) %>%
-#   group_by(year) %>%
-#   mutate(perc = n / sum(n),
-#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
-#   filter(mx_cat2 == "Mixed-types") %>% 
-#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
-#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
-#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
-#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-#        caption = "") +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom") +
-#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
-#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
-#            alpha = 0.1) +
-#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
-#            label = hp$presid, alpha = 0.4)
-# mixed_types_time
-```
-
-The most frequent mixed-type problem construction of the Amazon in time is economic corsevation.
-The mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
-Economic conservation averages at 6.8% in relation to all Amazonian statements.
-The mixed type generally increased in time, with Bolsonaro employing the mixed-type higher than all other presidents.
-The second most common mixed-type in time mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-Notoriously, Lula employs such a mix-type more frequently than all other presidents.
-In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
-While Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
-Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region [@hecht1990].
-
-## 4.3 The Amazonian multi-level game, boasting policy outside and talking to people inside
-
-Problem constructions depend on where presidents speak.
-To facilitate analysis and make sense of locations, we divide locations into Amazonian states (i.e.
-all the Brazilian states in which the Amazon biome is present), non Amazonian states (other Brazilian states), Brasilia (the capital of Brazil where the federal government is located), Amazonian countries (neighboring countries where the biome is present), and international countries (countries outside of Brazil).
-To analyze the relationship between location and problem construction, we run a multinomial regression.
-Our dependent variable is problem-constructions (categorical), while our main independent variable is location (categorical).
-The reference category for the multinomial model is, thus, environmental conservation in international states.
-We control for deforestation rates (numerical), inflation (numerical), and election year.
-Since the model accounts for both mixed and pure-type Amazonian constructions, and this makes for a large table, we focus the analysis on pure-types to facilitate visualization (see full regression table in appendix).
-
-Figure 5, below, shows the percentage of problem-constructions by location derived from the regression model.
-The plot illustrates the percentage likelihood of constructing the Amazon as a certain issue according to location in relation to the reference category, environmental conservation internationally.
-From the figure we see, for example, that presidents are 29% more likely to construct the Amazon as an issue of economic integration within other Amazonian countries in comparison to other international settings.
-Although without the same strength, the finding also holds at the state level within Brazil as presidents are 11% more likely to construct the Amazon as an issue of economic integration within Amazonian states and 15% more likely in non Amazonian states.
-Interestingly, presidents are less likely to construct the Amazon as an issue of economic integration in Brasilia than internationally.
-That is, when speaking internationally or in Brasilia, presidents often construct the Amazon as an issue of environmental conservation.
-
-```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
-ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
-  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty",
-                                            "Economic Conservation", "Social Economic",
-                                            "Sovereign Conservation", "Economic, Social,\nand Conservation",
-                                            "Economic Sovereignty", "Social Conservation", "Other")),
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname", location),
-                                     "Amazonian Countries", location_cat),
-                               levels = c("International", "Amazonian States",
-                                          "Amazonian Countries", "Brasilia", "Non Amazonian States"))) # separating Amazonian countries
-# model
-model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
-                  data = ama_model, model = TRUE, trace = FALSE)
-# summary statistics
-model_summary <- summary(model)
-p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
-iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
-iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
-                data = iia_data, model = TRUE, trace = FALSE)
-iia_summary <- summary(iia)
-iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
-# Model coefficients, and p-values, are statistically identical even when we drop the largest
-# factor category from model. Therefore, we can proceed with a multinomial logit model,
-# instead of a multinomial probit model, since the independence of irrelevant alternatives 
-# Other post estimation tests
-chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# But too much information on the summary tables... Let's just focus on what we want here:
-logit2prob <- function(logit) {
-  odds <- exp(logit)
-  prob <- odds / (1 + odds)
-  return(prob)
-} # to transform log odds in probabilities
-md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
-                      "Amazonian_Countries" = c(1.3411972, 1.2460915, 0.9310706),
-                      "Amazonian_States" = c(0.4578251, 1.4725563, 1.6281365),
-                      "Non_Amazonian_States" = c(0.6198104, 1.5838611, 1.9830952),
-                      "Brasilia" = c(-0.29279984, 0.59564579, 1.38333572))
-md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
-md_plot$'Amazonian States' <- logit2prob(md_plot$Amazonian_States)
-md_plot$'Non Amazonian States' <- logit2prob(md_plot$Non_Amazonian_States)
-md_plot$'Amazonian Countries' <- logit2prob(md_plot$Amazonian_Countries)
-mplot <- md_plot %>%
-  select(-c("Amazonian_Countries", "Amazonian_States", "Non_Amazonian_States")) %>% 
-  tidyr::pivot_longer('Amazonian Countries':Brasilia) %>%
-  mutate(Percentage = 100*round(value, digit = 2)-50) %>%
-  mutate(Location = factor(name, levels = c("Amazonian Countries", "Amazonian States",
-                           "Non Amazonian States", "Brasilia"))) %>% 
-  ggplot(aes(x = Location, y = Percentage, fill = Construction)) +
-  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  scale_y_continuous(breaks = seq(-15, 40, 10), limits = c(-15, 40)) +
-  geom_text(aes(label = Percentage), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
-  geom_hline(yintercept = 0, linetype = "dotted", color = "red") +
-  labs(x = "", y = "Percentage",
-       title = "Percentage for problem constructions across locations in relation\nto environmental conservation problem constructions Internationally",
-       subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-          legend.position = c(0.5, 0.15))
-mplot
-```
-
-Along these lines, constructing the Amazon as an issue of social development takes place, overwhelmingly, within Brazil or other Amazonian countries.
-Presidents are at least 14% more likely to construct the Amazon as an issue of social development in these locations than internationally.
-The same is true for sovereignty, whereas constructing the Amazon as an issue of sovereignty takes place within Brazil or in neighboring Amazonian countries.
-Notice, as well, how Amazonian constructions within Amazonia states and non Amazonian states are strikingly similar.
-This indicates that presidents are consistent when constructing the Amazon locally across the federation, when outside of Brasilia.
-
-How the amazon is constructed as a problem varies across levels.
-The Amazon, as a region and a forest, has historically been the topic of international, national, supranational, and local debates, negotiation and policies.
-This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" could differ as well.
-The multi-level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not for local electorates.
-Local electorates who, ultimately, elect presidents.
-This multi-level game leads to different policies being negotiated, often simultaneously, so that the overlap at the interplay between the levels is maximized.
-Take, for once, how the Brazilian government successfully funded domestic public policy with international support since the 1990s (e.g.
-1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g.
-2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD 1 billion for environmental conservation in the Amazon [@silva-muller2022].
-Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued.
-During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-Nowadays, it has reached unprecedented levels.
-
-# 5 Discussion and Conclusion
-
-The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse within Brazilian states and Amazonian countries compared to Brasilia or internationally.
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
-If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
-Or, as @putnam1988 puts it, what's the actual overlap between the international and domestic overlap.
-The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide.
-With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration problem-construction and the rise of social and conservation constructions as a new balance between granting local livelihoods their rights and economic exploitation.
-
-While unprecedented, this new balance was not long-standing.
-Democratic decay is slow, and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation-related statements in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.
-As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as not only attacks to international interference in the Amazon but also on indigenous and traditional populations.
-On the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
-The political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro's problem-construction is the strongest form of this shift.
-
-In sum, this paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to policies and environmental outcomes.
-Empirically, we provide the first comprehensive overview of the Amazon in presidential discourse.
-Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment, further research on the relationship between the social construction of the Amazon, one of the worlds most important standing ecosystems, and its effects on environmental outcomes is pressing.
-
-# Appendix
-
-````{=tex}
+Indigenous and traditional populations were instrumental in advocating
+for constitutional environmental rights and the protection of their
+territories (Hecht and Cockburn 1990). These were eventually enshrined
+in article 225, which gives all Brazilians a right to a balanced
+environment, and in article 231, which grants indigenous and traditional
+populations a right over their territory. However, in 1989, the Amazon
+appeared in 32\% of all speeches. This spike is likely explained by the
+brutal murder of Chico Mendes and the very end of 1988. An incident that
+caught unprecedented international attention and Sarney responded to
+this with a set of policies to address deforestation (Capobianco 2021).
+
+\begin{figure}
+\centering
+\includegraphics{Full_draft_20220608_files/figure-latex/Figure 2-1.pdf}
+\caption{Amazonian speeches by year}
+\end{figure}
+
+In 1990 the Amazon appeared in 12\% of all speeches and, by 1992, this
+increased to 25\% of all speeches. The 1992 Earth Summit, held in Brazil
+brought international attention to environmental topics in the Amazon.
+One of the big announcements, for example, was the consolidation of the
+first transnational partnership for the Amazon, the G7 Pilot Programme,
+which brought a high number of financial resources to the region for
+public policy implementation (Capobianco 2021). Throughout the 1990s and
+2000s, during the Cardoso and Lula administrations, the Amazon appeared,
+on average, on 15\% of all speeches. Exceptionally, in 2009 we see
+another spike in the Amazon appearing in official speeches. This spike
+coincides with the 2009 Copenhagen Summit as well as the steepest
+decrease in deforestation rates since data is available. Lula led the
+delegation to Copenhagen with a self-image of ``we do not promise, we
+deliver'' when the stakes about climate change were high (Franchini and
+Viola 2019).
+
+From 2010 to 2018, with the exception of 2015, we see a general decrease
+in mentions of the Amazon in all official presidential speeches. From
+2010 to 2014, mentions of the Amazon went down from 18\% to 8\% in
+official speeches. Disagreements related to the priority of
+environmental preservation over economic development, most notably in
+the case of Itaipu Dam, led the environmental minister Marina Silva to
+resign and run for the presidency on her agenda in 2010. In 2011, the
+New Forest Code, which regularized land ownership of many illegally
+deforested areas, was also approved. These are also the years when
+Brazil entered a long period of political and economic instability,
+which eventually led to the impeachment of Dilma Roussef. Though, in
+2015, the Amazon appeared in 19\% of speeches. This spike coincides with
+the Paris summit which became a key turn in climate politics after the
+failures of Copenhagen. Brazil went to the Paris Summit with
+deforestation numbers slightly higher than Copenhagen and a perception
+that there was a turn towards less conservation. By 2016 mentions of the
+Amazon in official speeches went down to 6\%, the lowest share since
+1985.
+
+We subsequently observe a steady increase from 6\% in 2016 to almost
+24\% in the first year of Bolsonaro's presidency, 2019. At the time,
+international and national media brought unprecedented attention to
+Brazilian environmental issues as the record burning of the Amazon, and
+of the red sky afternoon in São Paulo circulated on social media and
+international media outlets. This brought issues related to
+environmental conservation as high priorities in Bolsonaro's governing
+agenda with efforts to dismantle key pillars of Brazilian environmental
+governance. At the same time, President Bolsonaro retrieves Brazil's
+hosting status for COP25. In short, relevant international events drive
+interest and alter how pressing the ``Amazon problem'' is perceived to
+be in society, therefore, cause a momentary shift of interest from top
+policymakers.
+
+\hypertarget{how-has-the-amazon-been-constructed-as-a-problem}{%
+\subsection{4.2 How has the Amazon been constructed as a
+problem?}\label{how-has-the-amazon-been-constructed-as-a-problem}}
+
+\hypertarget{pure-type-problem-constructions}{%
+\subsubsection{Pure-type problem
+constructions}\label{pure-type-problem-constructions}}
+
+We conceptualize four pure problem constructions: sovereignty, economic
+integration, social development, and conservation. At the level of the
+speech, though, presidents might mix multiple problem construction in an
+Amazonian statement. Figure 3, below, illustrates the share of each pure
+type in time. Pure problem constructions dominate, with an average of
+56\% of all amazonian statements across time. As above, we observe a
+strong variation over time for most of these constructions.
+
+\begin{figure}
+\centering
+\includegraphics{Full_draft_20220608_files/figure-latex/Figure 3-1.pdf}
+\caption{Pure types in time}
+\end{figure}
+
+Amazonian constructions are not monolithic in time nor within
+governments. The same governments construct the Amazon as different
+issues in discourse. Pure economic integration constructions dominated
+constructions from 1985 to the late 2000s. This is especially pertinent
+during the Cardoso administration as the Amazon was constructed,
+overwhelmingly, as an issue of economic integration. However, during
+Lula's terms in office, constructions of the Amazon purely as an
+economic issue decreased in discourse while constructions of the Amazon
+as issues of pure conservation as well as of pure social development
+increased. These constructions surpassed economic integration around
+2010. These trends in discourse continued during the Rousseff
+administration. Capobianco (2021), for example, argues that the
+unprecedented decrease in deforestation we observed from 2004 to 2012
+was a product of an increase in the perception of stronger federal
+policies and presence in the Amazon region, which in turn engendered a
+perception of higher risk of being caught and fined for deforestation. A
+higher incidence of the Amazon, as a topic in overall presidential
+speeches, generates a perception that more attention is being paid to
+the Amazon from the top while the shift from constructing the Amazon as
+an issue of economic integration to an issue of environmental
+conservation generates a perception that illegal deforestation will be
+increasingly monitored.
+
+From the mid-2010s onwards, we start to see a reverse of this trend:
+economic integration problem construction increases while conservation
+and social development constructions decrease instead. Interestingly,
+sovereignty starts to increase steadily from 2010 onwards and by 2019
+sovereignty constructions surpass social development. Figure 3 also
+highlights that, while the reversal precedes the mandate of President
+Bolsonaro, it was with him that sovereignty constructions reached
+unprecedented levels since the establishment of Brazilian democracy.
+
+\hypertarget{mixed-type-problem-constructions}{%
+\subsubsection{Mixed-type problem
+constructions}\label{mixed-type-problem-constructions}}
+
+Although presidents prefer pure problem-constructions, they also
+construct the Amazon as multifaceted issues. Mixed-type problem
+constructions in discourse offer more complex understandings of the
+Amazon as an issue. Constructing the Amazon as multiple issues averages
+at 18\% of all constructions in time. While there is some variation in
+time, some mixed-types rarely appear, thus, we focus our discussion on
+those mixed-types with higher incidence. Figure 4, below, displays the
+average mixed-types by president.
+
+\begin{figure}
+\centering
+\includegraphics{Full_draft_20220608_files/figure-latex/Figure 4-1.pdf}
+\caption{Mixed-types by president}
+\end{figure}
+
+The most frequent mixed-type problem construction of the Amazon in time
+is economic corsevation. The mixed-type is composed of Amazonian
+statements that construct the Amazon as problems of both economic
+integration and environmental conservation. Economic conservation
+averages at 6.8\% in relation to all Amazonian statements. The mixed
+type generally increased in time, with Bolsonaro employing the
+mixed-type higher than all other presidents. The second most common
+mixed-type in time mixes social development and economic integration and
+appears, on average, in 5.4\% of all statements. Notoriously, Lula
+employs such a mix-type more frequently than all other presidents. In
+fact, both Lula and Bolsonaro construct the Amazon as multifaceted
+issues in discourse more frequently than other presidents. While Lula,
+on the one hand, often mixes economic integration with environmental
+conservation and social development when constructing the Amazon as an
+issue, Bolsonaro, on the other hand, often mixes national sovereignty
+with other problem constructions. Indeed, we see that Bolsonaro
+constructs the Amazon as an issue of national sovereignty and economic
+integration more than any other president, which was also characteristic
+of the military dictatorship discourses and policies for the region
+(Hecht and Cockburn 1990).
+
+\hypertarget{the-amazonian-multi-level-game-boasting-policy-outside-and-talking-to-people-inside}{%
+\subsection{4.3 The Amazonian multi-level game, boasting policy outside
+and talking to people
+inside}\label{the-amazonian-multi-level-game-boasting-policy-outside-and-talking-to-people-inside}}
+
+Problem constructions depend on where presidents speak. To facilitate
+analysis and make sense of locations, we divide locations into Amazonian
+states (i.e.~all the Brazilian states in which the Amazon biome is
+present), non Amazonian states (other Brazilian states), Brasilia (the
+capital of Brazil where the federal government is located), Amazonian
+countries (neighboring countries where the biome is present), and
+international countries (countries outside of Brazil). To analyze the
+relationship between location and problem construction, we run a
+multinomial regression. Our dependent variable is problem-constructions
+(categorical), while our main independent variable is location
+(categorical). The reference category for the multinomial model is,
+thus, environmental conservation in international states. We control for
+deforestation rates (numerical), inflation (numerical), and election
+year. Since the model accounts for both mixed and pure-type Amazonian
+constructions, and this makes for a large table, we focus the analysis
+on pure-types to facilitate visualization (see full regression table in
+appendix).
+
+Figure 5, below, shows the percentage of problem-constructions by
+location derived from the regression model. The plot illustrates the
+percentage likelihood of constructing the Amazon as a certain issue
+according to location in relation to the reference category,
+environmental conservation internationally. From the figure we see, for
+example, that presidents are 29\% more likely to construct the Amazon as
+an issue of economic integration within other Amazonian countries in
+comparison to other international settings. Although without the same
+strength, the finding also holds at the state level within Brazil as
+presidents are 11\% more likely to construct the Amazon as an issue of
+economic integration within Amazonian states and 15\% more likely in non
+Amazonian states. Interestingly, presidents are less likely to construct
+the Amazon as an issue of economic integration in Brasilia than
+internationally. That is, when speaking internationally or in Brasilia,
+presidents often construct the Amazon as an issue of environmental
+conservation.
+
+\begin{figure}
+\centering
+\includegraphics{Full_draft_20220608_files/figure-latex/Figure 5-1.pdf}
+\caption{Percent of problem constructions across locations}
+\end{figure}
+
+Along these lines, constructing the Amazon as an issue of social
+development takes place, overwhelmingly, within Brazil or other
+Amazonian countries. Presidents are at least 14\% more likely to
+construct the Amazon as an issue of social development in these
+locations than internationally. The same is true for sovereignty,
+whereas constructing the Amazon as an issue of sovereignty takes place
+within Brazil or in neighboring Amazonian countries. Notice, as well,
+how Amazonian constructions within Amazonia states and non Amazonian
+states are strikingly similar. This indicates that presidents are
+consistent when constructing the Amazon locally across the federation,
+when outside of Brasilia.
+
+How the amazon is constructed as a problem varies across levels. The
+Amazon, as a region and a forest, has historically been the topic of
+international, national, supranational, and local debates, negotiation
+and policies. This implies not only that audiences' priorities in each
+setting change, but that which policies are appropriate to solve the
+``Amazon issue'' could differ as well. The multi-level game entails that
+conservation might be a desirable construction when speaking
+internationally about the Amazon, or in Brasilia, but not for local
+electorates. Local electorates who, ultimately, elect presidents. This
+multi-level game leads to different policies being negotiated, often
+simultaneously, so that the overlap at the interplay between the levels
+is maximized. Take, for once, how the Brazilian government successfully
+funded domestic public policy with international support since the 1990s
+(e.g.~1992 Programa Piloto para Proteção das Florestas Tropicais), by
+creating a federal fund for the protected areas (e.g.~2001 Amazon Region
+Protected Areas program), and by assuring international funds with the
+establishment of the Amazon Fund in 2008 which provided over USD 1
+billion for environmental conservation in the Amazon (Silva-Muller and
+Faul 2022). Still, this does not mean, though, that the national agenda
+of economic integration or social development was not pursued. During
+the same time rural credit offered to local agricultural producers in
+Amazonian states, went up from 500 million reais a year in 1999 to over
+4 billion a year by 2012 (Capobianco 2021). Nowadays, it has reached
+unprecedented levels.
+
+\hypertarget{discussion-and-conclusion}{%
+\section{5 Discussion and Conclusion}\label{discussion-and-conclusion}}
+
+The Amazon frontier as an analytic category can help us shed light on
+the differences we identify between the discourse within Brazilian
+states and Amazonian countries compared to Brasilia or internationally.
+Whereas presidential discourses at the top matter to define and justify
+public policy (Zarefsky 2004), presidents shape their discourses
+according to who their audience might be and what ``they want to hear''.
+If presidents promote an agenda of economic and social development
+within Brazil that diverges from the one the president promotes outside
+of Brazil, the question for democracy becomes to what extent the
+implemented agenda responds to domestic versus international demands.
+Or, as Putnam (1988) puts it, what's the actual overlap between the
+international and domestic overlap. The domestic policies and
+transnational support that led to the decrease in deforestation from
+2004 to 2012 happened concurrently with a period of strong economic
+growth and social development in Brazil and worldwide. With the
+strengthening of environmentalism and indigenous participation in
+politics in the late 1980s and 1990s, we can interpret the fall of
+economic integration problem-construction and the rise of social and
+conservation constructions as a new balance between granting local
+livelihoods their rights and economic exploitation.
+
+While unprecedented, this new balance was not long-standing. Democratic
+decay is slow, and the embryo of Bolsonaro's Amazonian discourse was
+breeding half a decade before he took office. We observe the decrease in
+conservation-related statements in the mid-2010s, and a hard increase of
+sovereignty constructions in the early 2010s. As we conceptualize and
+operationalize sovereignty as boundary-making vis- à-vis internal and
+external perceived threats to the Amazon, we interpret this increase as
+not only attacks to international interference in the Amazon but also on
+indigenous and traditional populations. On the policy side, the Itaipu
+Dam in the late 2000s and the 2011 Forest code is seen as a turning
+point: political opposition to conservation got particularly organized
+and managed to lobby the executive and conquer this policy wins, which
+were largely opposed by environmentalists. The political forces in
+Brazilian democracy that drive these changes in problem-construction
+were long in the making, as the earlier and softer shifts in discourse
+suggest. Bolsonaro's problem-construction is the strongest form of this
+shift.
+
+In sum, this paper investigates how the Amazon has been constructed as a
+problem in Brazilian presidential speeches since 1985. Our findings show
+that these constructions are not monolithic within governments, in time,
+or across different locations. Conceptually, this contributes to
+understanding the social construction of the Amazon in discourses and
+how these might relate to policies and environmental outcomes.
+Empirically, we provide the first comprehensive overview of the Amazon
+in presidential discourse. Given the importance of discursive
+problem-construction within democracies to legitimize ways of thinking
+and acting towards the environment, further research on the relationship
+between the social construction of the Amazon, one of the worlds most
+important standing ecosystems, and its effects on environmental outcomes
+is pressing.
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
 \begin{landscape}
 
-```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
-codebook <- tibble::tibble("Problem Construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
-                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+\begin{table}
+
+\caption{\label{tab:codebook}Amazonian Problem-Construction Codebook}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{9}{11}\selectfont
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{9cm}>{\raggedright\arraybackslash}p{9cm}}
+\toprule
+Problem Construction & Description & Example\\
+\midrule
+\textbf{\cellcolor{gray!6}{National Sovereignty}} & \cellcolor{gray!6}{This code constructs the Amazon region and/or forest as an issue of national sovereignty.
 We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
+Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments<U+2019> actions related to the Brazilian Amazon.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.} & \cellcolor{gray!6}{Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
+I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019)}\\
+\textbf{Economic Integration} & This code constructs the Amazon region and/or forest as an issue of economic integration.
 It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.
+& If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
+This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)\\
+\textbf{\cellcolor{gray!6}{Social Development}} & \cellcolor{gray!6}{This code constructs the Amazon region and/or forest as an issue of social development.
 It advances the view that Amazon is full of citizens who should have their rights guaranteed.
@@
 This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
-This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
-I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
-I would like to thank the Chinese government.
-For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
-(Bolsonaro 25/10/2019)",
-                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
-We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
-                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+Finally, this includes referrals to culture and the right to vote.} & \cellcolor{gray!6}{The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
 We have invested over 14 billion reais in this program, in three and a half years.
@@
 One million kilometers of lines.
-(Lula 20/11/2009)",
-                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+(Lula 20/11/2009)}\\
+\textbf{Environmental Conservation} & This code constructs the Amazon region and/or forest as an issue of conservation.
+This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
+The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created.
+& I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
 This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
-Mesquita (Sarney 20/07/1989)"))
-
-kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
-
-```
+Mesquita (Sarney 20/07/1989)\\
+\bottomrule
+\end{tabu}}
+\end{table}
 
 \end{landscape}
-````
-
-````{=tex}
+
 \begin{landscape}
 
-```{r full regression results, fig.cap="Multinomial Regression Results", echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
-
-full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
-                                           "SOV-EI", "SD-CON", "Other"),
-                  "Amazonian States" = c("0.458 (0.193)", "1.473*** (0.215)",
-                  "1.623*** (0.235)", "-0.056 (0.292)", "1.625*** (0.198)",
-                  "0.960*** (0.284)", "1.192*** (0.271)", "1.345*** (0.290)",
-                  "0.129 (0.323)", "0.999*** (0.207)"),
-                  "Amazonian Countries" = c("1.341*** (0.212)", "1.246*** (0.308)",
-                  "0.931** (0.383)", "0.304 (0.394)", "1.569*** (0.288)",
-                  "0.613*** (0.090)", "0.949*** (0.0857)", "2.609*** (0.345)",
-                  "0.660** (0.332)", "1.760*** (0.226)"),
-                  "Brasilia" = c("-0.293** (0.183)","0.596*** (0.210)",
-                  "1.383*** (0.209)", "-0.245 (0.265)", "0.823*** (0.193)",
-                  "0.890*** (0.237)", "0.123 (0.277)", "0.276 (0.310)",
-                  "-0.594** (0.317)", "0.0649 (0.202)"),
-                  "Non Amazonian States" = c("0.620** (0.212)", "1.584*** (0.219)", "1.983*** (0.238)",
-                  "0.242 (0.311)", "1.637*** (0.223)", "1.309*** (0.283)",
-                  "0.871*** (0.308)", "1.418*** (0.323)", "0.217 (0.342)", "0.849*** (0.231)"),
-                  "Election Year" = c("-0.517*** (0.160)", "-0.007 (0.192)",
-                  "-0.733*** (0.277)",
-                  "-0.016 (0.232)", "-0.453* (0.255)", "-0.691* (0.378)",
-                  "0.080 (0.343)", 
-                  "-1.400*** (0.429)","0.0008 (0.378)", "-0.713*** (0.170)"),
-                  "Annual Deforestation" = c("0.082*** (0.011)", "-0.037** (0.015)",
-                  "0.001 (0.018)", 
-                  "0.0197 (0.0170)", "0.060*** (0.017)", "0.012 (0.024)",
-                  "-0.026 (0.026)", 
-                  "-0.007 (0.027)", "-0.002 (0.027)", "0.076*** (0.0120)"),
-                  "Average Inflation" = c("-0.0005*** (0.0001)", "-0.0005*** (0.0001)",
-                  "-0.0001 (0.0002)", "-0.0006*** (0.0001)", "-0.0005** (0.0002)",
-                  "0.0001 (0.0002)", "-0.0008** (0.0004)", "-0.0004 (0.0004)",
-                  "-0.0006* (0.0004)", "-0.0003*** (0.0001)"))
-kbl(t(full_md), booktabs = T,caption = "Multinomial Regression Full", align = "c") %>%
-  kable_styling(latex_options = c("striped", "scale_down"),
-                position= "center", font_size = 9, full_width = TRUE) %>%
-                footnote(general = c("The multinomial regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
-                "*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
-  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
-  column_spec(2, width="2 cm", latex_valign = "m") %>%
-  column_spec(3, width = "2 cm", latex_valign = "m") %>%
-  column_spec(4, width = "2 cm", latex_valign = "m") %>%
-  column_spec(5, width="2 cm", latex_valign = "m") %>%
-  column_spec(6, width = "2 cm", latex_valign = "m") %>%
-  column_spec(7, width = "2 cm", latex_valign = "m") %>% 
-  column_spec(8, width="2 cm", latex_valign = "m") %>%
-  column_spec(9, width = "2 cm", latex_valign = "m") %>%
-  column_spec(10, width = "2 cm", latex_valign = "m") %>% 
-  column_spec(11, width = "2 cm", latex_valign = "m")
-```
+\begin{table}
+
+\caption{\label{tab:full regression results}Multinomial Regression Full}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{9}{11}\selectfont
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}m{3 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}>{\centering\arraybackslash}m{2 cm}}
+\toprule
+\textbf{\cellcolor{gray!6}{Dependent Variable}} & \cellcolor{gray!6}{EI} & \cellcolor{gray!6}{SD} & \cellcolor{gray!6}{SOV} & \cellcolor{gray!6}{EI-CON} & \cellcolor{gray!6}{EI-SD} & \cellcolor{gray!6}{SOV-CON} & \cellcolor{gray!6}{SD-EI-CON} & \cellcolor{gray!6}{SOV-EI} & \cellcolor{gray!6}{SD-CON} & \cellcolor{gray!6}{Other}\\
+\textbf{Amazonian States} & 0.458 (0.193) & 1.473*** (0.215) & 1.623*** (0.235) & -0.056 (0.292) & 1.625*** (0.198) & 0.960*** (0.284) & 1.192*** (0.271) & 1.345*** (0.290) & 0.129 (0.323) & 0.999*** (0.207)\\
+\textbf{\cellcolor{gray!6}{Amazonian Countries}} & \cellcolor{gray!6}{1.341*** (0.212)} & \cellcolor{gray!6}{1.246*** (0.308)} & \cellcolor{gray!6}{0.931** (0.383)} & \cellcolor{gray!6}{0.304 (0.394)} & \cellcolor{gray!6}{1.569*** (0.288)} & \cellcolor{gray!6}{0.613*** (0.090)} & \cellcolor{gray!6}{0.949*** (0.0857)} & \cellcolor{gray!6}{2.609*** (0.345)} & \cellcolor{gray!6}{0.660** (0.332)} & \cellcolor{gray!6}{1.760*** (0.226)}\\
+\textbf{Brasilia} & -0.293** (0.183) & 0.596*** (0.210) & 1.383*** (0.209) & -0.245 (0.265) & 0.823*** (0.193) & 0.890*** (0.237) & 0.123 (0.277) & 0.276 (0.310) & -0.594** (0.317) & 0.0649 (0.202)\\
+\textbf{\cellcolor{gray!6}{Non Amazonian States}} & \cellcolor{gray!6}{0.620** (0.212)} & \cellcolor{gray!6}{1.584*** (0.219)} & \cellcolor{gray!6}{1.983*** (0.238)} & \cellcolor{gray!6}{0.242 (0.311)} & \cellcolor{gray!6}{1.637*** (0.223)} & \cellcolor{gray!6}{1.309*** (0.283)} & \cellcolor{gray!6}{0.871*** (0.308)} & \cellcolor{gray!6}{1.418*** (0.323)} & \cellcolor{gray!6}{0.217 (0.342)} & \cellcolor{gray!6}{0.849*** (0.231)}\\
+\addlinespace
+\textbf{Election Year} & -0.517*** (0.160) & -0.007 (0.192) & -0.733*** (0.277) & -0.016 (0.232) & -0.453* (0.255) & -0.691* (0.378) & 0.080 (0.343) & -1.400*** (0.429) & 0.0008 (0.378) & -0.713*** (0.170)\\
+\textbf{\cellcolor{gray!6}{Annual Deforestation}} & \cellcolor{gray!6}{0.082*** (0.011)} & \cellcolor{gray!6}{-0.037** (0.015)} & \cellcolor{gray!6}{0.001 (0.018)} & \cellcolor{gray!6}{0.0197 (0.0170)} & \cellcolor{gray!6}{0.060*** (0.017)} & \cellcolor{gray!6}{0.012 (0.024)} & \cellcolor{gray!6}{-0.026 (0.026)} & \cellcolor{gray!6}{-0.007 (0.027)} & \cellcolor{gray!6}{-0.002 (0.027)} & \cellcolor{gray!6}{0.076*** (0.0120)}\\
+\textbf{Average Inflation} & -0.0005*** (0.0001) & -0.0005*** (0.0001) & -0.0001 (0.0002) & -0.0006*** (0.0001) & -0.0005** (0.0002) & 0.0001 (0.0002) & -0.0008** (0.0004) & -0.0004 (0.0004) & -0.0006* (0.0004) & -0.0003*** (0.0001)\\
+\bottomrule
+\multicolumn{11}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{11}{l}{\rule{0pt}{1em}The multinomial regression coefficients are displayed in log odds and standard errors are displayed in parentheses.}\\
+\multicolumn{11}{l}{\rule{0pt}{1em}*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1}\\
+\end{tabu}}
+\end{table}
 
 \end{landscape}
-````
-
-# References
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-acker2014}{}}%
+Acker, Antoine. 2014. {``{"}O maior incêndio do planeta{"}: como a
+Volkswagen e o regime militar brasileiro acidentalmente ajudaram a
+transformar a Amazônia em uma arena política global.''} \emph{Revista
+Brasileira de História} 34 (December): 13--33.
+\url{https://doi.org/10.1590/S0102-01882014000200002}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-acker2021}{}}%
+---------. 2021. {``Amazon Development,''} Oxford research encyclopedia
+of latin american history.,.
+\url{https://doi.org/10.1093/acrefore/9780199366439.013.837}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-alesina2009}{}}%
+Alesina, Alberto F., and Paola Giuliano. 2009. {``Preferences for
+Redistribution.''} \url{https://www.nber.org/papers/w14825}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-andonova2014}{}}%
+Andonova, Liliana B. 2014. {``Boomerangs to Partnerships? Explaining
+State Participation in Transnational Partnerships for Sustainability.''}
+\emph{Comparative Political Studies} 47 (3): 481--515.
+\url{https://doi.org/10.1177/0010414013509579}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-assuncao2015}{}}%
+Assunção, Juliano, Clarissa Gandour, and Rudi Rocha. 2015.
+{``Deforestation Slowdown in the Brazilian Amazon: Prices or
+Policies?''} \emph{Environment and Development Economics} 20 (6):
+697--722. \url{https://doi.org/10.1017/S1355770X15000078}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bacchi2009}{}}%
+Bacchi, Carol Lee. 2009. \emph{Analysing Policy: What's the Problem
+Represented to Be?} Pearson.
+
+\leavevmode\vadjust pre{\hypertarget{ref-barros2020}{}}%
+Barros, Antonio Teixeira de. 2020. {``Discursos parlamentares sobre a
+Amazônia: sobre o que falam os deputados brasileiros.''} \emph{Política
+\& Sociedade} 19 (46): 299--331.
+\url{https://doi.org/10.5007/2175-7984.2020.e66962}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-becker2005}{}}%
+Becker, Bertha K. 2005. {``Geopolítica da Amazônia.''} \emph{Estudos
+Avançados} 19 (April): 71--86.
+\url{https://doi.org/10.1590/S0103-40142005000100005}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bevitori2015}{}}%
+Bevitori, Cinzia. 2015. {``Discursive Constructions of the Environment
+in American Presidential Speeches 1960{\textendash}2013: A Diachronic
+Corpus-Assisted Study.''} \emph{Corpora and Discourse Studies}, 110--33.
+\url{https://doi.org/10.1057/9781137431738_6}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brice2021}{}}%
+Brice, and Smith. 2021. {``The Amazon Is Fast Approaching a Point of No
+Return.''} \emph{Bloomberg.com}, July.
+\url{https://www.bloomberg.com/news/features/2021-07-29/amazon-rainforest-deforestation-land-grabs-surge-under-bolsonaro-in-brazil}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calderwood2019}{}}%
+Calderwood, Kevin J. 2019. {``Discourse in the Balance: American
+Presidential Discourse about Climate Change.''} \emph{Communication
+Studies} 70 (2): 235--52.
+\url{https://doi.org/10.1080/10510974.2019.1572636}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calderwood2020}{}}%
+---------. 2020. {``Going Global: Climate Change Discourse in
+Presidential Communications.''} \emph{Environmental Communication} 14
+(1): 52--67. \url{https://doi.org/10.1080/17524032.2019.1592005}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-campbell2015}{}}%
+Campbell, Jeremy M. 2015. \emph{Conjuring Property: Speculation and
+Environmental Futures in the Brazilian Amazon}. Illustrated edition.
+Seattle: University of Washington Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-capobianco2019}{}}%
+Capobianco, João Paulo. 2019. {``Avances y retrocesos de la
+sostenibilidad en la Amazonia: un análisis de la gobernanza
+socioambiental en la Amazonia,''} January.
+\url{https://gredos.usal.es/handle/10366/139311}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-capobianco2021}{}}%
+---------. 2021. \emph{Amazônia: Uma Década de Esperança}. 1ª edição.
+São Paulo: Estação Liberdade.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cezar2020}{}}%
+Cezar, Rodrigo Fagundes. 2020. {``Brazilian Presidential Speeches from
+1985 to July 2020.''}
+\url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/M9UU09}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-druckman2004}{}}%
+Druckman, James N, and Justin W Holmes. 2004. {``Does Presidential
+Rhetoric Matter? Priming and Presidential Approval.''}
+\emph{Presidential Studies Quarterly} 34 (4): 755--78.
+
+\leavevmode\vadjust pre{\hypertarget{ref-drummond2006}{}}%
+Drummond, Jose, and Ana Flavia Barros-Platiau. 2006. {``Brazilian
+Environmental Laws and Policies, 1934-2002: A Critical Overview.''}
+\emph{Law \textless Html{\_}ent Glyph={"}@amp;{"}
+Ascii={"}\&amp;{"}/\textgreater{} Policy} 28 (1): 83--108.
+\url{https://doi.org/10.1111/j.1467-9930.2005.00218.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eshbaugh2010}{}}%
+Eshbaugh-Soha, Matthew. 2010. {``How Policy Conditions the Impact of
+Presidential Speeches on Legislative Success.''} \emph{Social Science
+Quarterly} 91 (2): 415--35.
+
+\leavevmode\vadjust pre{\hypertarget{ref-franchini2019}{}}%
+Franchini, Matias Alejandro, and Eduardo Viola. 2019. {``Myths and
+Images in Global Climate Governance, Conceptualization and the Case of
+Brazil (1989 - 2019).''} \emph{Revista Brasileira de Política
+Internacional} 62 (September).
+\url{https://doi.org/10.1590/0034-7329201900205}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-garfield2013}{}}%
+Garfield, Seth. 2013. \emph{In Search of the Amazon: Brazil, the United
+States, and the Nature of a Region}. Durham: Duke University Press
+Books.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gillion2016}{}}%
+Gillion, Daniel Q. 2016. \emph{Governing with Words: The Political
+Dialogue on Race, Public Policy, and Inequality in America}. Cambridge:
+Cambridge University Press.
+\url{https://doi.org/10.1017/CBO9781316412299}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grimmer2022}{}}%
+Grimmer, Justin, Margaret E. Roberts, and Brandon M. Stewart. 2022.
+\emph{Text as Data: A New Framework for Machine Learning and the Social
+Sciences}. Princeton, New Jersey Oxford: Princeton University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harris2021}{}}%
+Harris, Bryan. 2021. {``Drought Puts Amazon at Risk of {`}Large-Scale
+Dieback{'}, Researchers Warn.''} \emph{Financial Times}, July.
+\url{https://www.ft.com/content/02071ae7-dcf5-4c61-9c3c-b55f5aef8b0e}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hecht2013}{}}%
+Hecht, Susanna B. 2013. \emph{The Scramble for the Amazon and the
+{"}Lost Paradise{"} of Euclides Da Cunha}. First edition. Chicago:
+University of Chicago Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hecht1990}{}}%
+Hecht, Susanna B., and Alexander Cockburn. 1990. \emph{The Fate of the
+Forest: Developers, Destroyers, and Defenders of the Amazon, Updated
+Edition}. Chicago, IL: University of Chicago Press.
+\url{https://press.uchicago.edu/ucp/books/book/chicago/F/bo10387801.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hirschman1963}{}}%
+Hirschman, Albert O. 1963. \emph{Journeys Toward Progress: Studies of
+Economic Policy-Making in Latin America}. Twentieth Century Fund.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2021}{}}%
+Hochstetler, Kathryn. 2021. {``Climate Institutions in Brazil: Three
+Decades of Building and Dismantling Climate Capacity.''}
+\emph{Environmental Politics} 30 (sup1): 49--70.
+\url{https://doi.org/10.1080/09644016.2021.1957614}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2007}{}}%
+Hochstetler, Kathryn, and Margaret E. Keck. 2007. \emph{Greening Brazil:
+Environmental Activism in State and Society}.
+\url{https://doi.org/10.1215/9780822390596}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-krebs2007}{}}%
+Krebs, Ronald R, and Patrick Thaddeus Jackson. 2007. {``Twisting Tongues
+and Twisting Arms: The Power of Political Rhetoric.''} \emph{European
+Journal of International Relations} 13 (1): 35--66.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kwak2002}{}}%
+Kwak, Chanyeong, and Alan Clayton-Matthews. 2002. {``Multinomial
+Logistic Regression.''} \emph{Nursing Research} 51 (6): 404--10.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lopez2020}{}}%
+López, Matias, Graziella Moraes Silva, Chana Teeger, and Pedro Marques.
+2020. {``Economic and Cultural Determinants of Elite Attitudes Toward
+Redistribution.''} \emph{Socio-Economic Review}, May.
+\url{https://doi.org/10.1093/ser/mwaa015}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-meyer2021}{}}%
+Meyer, David, Evgenia Dimitriadou, Kurt Hornik, Andreas Weingessel, and
+Friedrich Leisch. 2021. \emph{E1071: Misc Functions of the Department of
+Statistics, Probability Theory Group (Formerly: E1071), TU Wien}.
+\url{https://CRAN.R-project.org/package=e1071}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miranda2021}{}}%
+Miranda, David. 2021. {``Bolsonaro{'}s 1,000km Amazon Railway Will Cause
+Climate Chaos. It Must Be Stopped.''} \emph{The Guardian}, July.
+\url{https://www.theguardian.com/commentisfree/2021/jul/28/bolsonaro-amazon-railway-climate-chaos-must-be-stopped}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-noble2006}{}}%
+Noble, William S. 2006. {``What Is a Support Vector Machine?''}
+\emph{Nature Biotechnology} 24 (12): 1565--67.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pacheco2019}{}}%
+Pacheco, João. 2019. \emph{Ecxterminio y Tutela: Procesos de Formación
+de Alteridades En El Brasil}. UNSAM Edita. Ciencias sociales.
+\url{http://www.unsamedita.unsam.edu.ar/product/exterminio-y-tutela-procesos-de-formacion-de-alteridades-en-el-brasil/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-padua2012}{}}%
+Pádua, José Augusto. 2012. {``Environmentalism in Brazil: A Historical
+Perspective.''} \emph{A Companion to Global Environmental History} 1:
+455--73.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pereira2021}{}}%
+Pereira, Joana Castro, and Eduardo Viola. 2021. \emph{Climate Change and
+Biodiversity Governance in the Amazon: At the Edge of Ecological
+Collapse?} Routledge.
+
+\leavevmode\vadjust pre{\hypertarget{ref-putnam1988}{}}%
+Putnam, Robert D. 1988. {``Diplomacy and Domestic Politics: The Logic of
+Two-Level Games.''} \emph{International Organization} 42 (3): 427--60.
+\url{http://www.jstor.org/stable/2706785}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rottinghaus2009}{}}%
+Rottinghaus, Brandon. 2009. {``Strategic Leaders: Determining Successful
+Presidential Opinion Leadership Tactics Through Public Appeals.''}
+\emph{Political Communication} 26 (3): 296--316.
+
+\leavevmode\vadjust pre{\hypertarget{ref-silva-muller2022}{}}%
+Silva-Muller, Livio, and Moira V. Faul. 2022. {``Protecting the Amazon
+and Its People: The Role of Civil Society in the Local Effectiveness of
+Transnational Partnerships.''} In. Routledge.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sposito2021}{}}%
+Sposito, Henrique. 2021. \emph{Poldis: Tools for Analyzing Political
+Discourse}. \url{https://github.com/henriquesposito/poldis}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-viola1987}{}}%
+Viola, Eduardo J. 1987. {``O Movimento Ecológico No Brasil, 1974-1986:
+Do Ambientalismo à Ecopolítica.''} \emph{Revista Brasileira de Ciencias
+Sociais} 3 (93): 5--26.
+\url{http://anpocs.com/images/stories/RBCS/03/rbcs03_01.pdf}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lepolaindewaroux2021}{}}%
+Waroux, Yann de, Rachael D. Garrett, Mollie Chapman, Cecilie Friis,
+Jeffrey Hoelle, Leonie Hodel, Kelly Hopping, and Julie Gwendolin
+Zaehringer. 2021. {``The Role of Culture in Land System Science.''}
+\emph{Journal of Land Use Science} 16 (4): 450--66.
+\url{https://doi.org/10.1080/1747423X.2021.1950229}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-westerwinter2021}{}}%
+Westerwinter, Oliver. 2021. {``Transnational Public-Private Governance
+Initiatives in World Politics: Introducing a New Dataset.''} \emph{The
+Review of International Organizations} 16 (1): 137--74.
+\url{https://doi.org/10.1007/s11558-019-09366-w}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zarefsky2004}{}}%
+Zarefsky, David. 2004. {``Presidential Rhetoric and the Power of
+Definition.''} \emph{Presidential Studies Quarterly} 34 (3): 607--19.
+\url{https://www.jstor.org/stable/27552615}.
+
+\end{CSLReferences}
+
+\end{document}

### 2022-06-10 Draft_June_2022/Full_draft_20220608.rmd
forget cached

@@
 library(tibble)
+library(readxl)
 Sys.setlocale("LC_ALL", "C")
@@
                                             "Economic Sovereignty", "Social Conservation", "Other")),
+         env_vs_all <- ifelse(mx_cat == "Pure Conservation", 1, 0),
          location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
@@
 # model
-model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
-                  data = ama_model, model = TRUE, trace = FALSE)
+model <- glm(env_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+             family = binomial(link = 'logit'), data = ama_model)
 # summary statistics
 model_summary <- summary(model)
-p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
-# Independence of Irrelevant Alternatives (Hausman-McFadden) test, in practice
-iia_data <- filter(ama_model, mx_cat != "Pure Economic Integration")
-iia <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI,
-                data = iia_data, model = TRUE, trace = FALSE)
-iia_summary <- summary(iia)
-iia_p_values <- round((1 - pnorm(abs(summary(iia)$coefficients/summary(iia)$standard.errors)))*2, 5)
-# Model coefficients, and p-values, are statistically identical even when we drop the largest
-# factor category from model. Therefore, we can proceed with a multinomial logit model,
-# instead of a multinomial probit model, since the independence of irrelevant alternatives 
-# Other post estimation tests
-chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# But too much information on the summary tables... Let's just focus on what we want here:
-logit2prob <- function(logit) {
-  odds <- exp(logit)
-  prob <- odds / (1 + odds)
-  return(prob)
-} # to transform log odds in probabilities
 md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),

### 2022-06-10 Draft_June_2022/Full_draft_20220608.rmd
Updated regression and added figures for distance to manaus and problem construction

@@
 output:
+  pdf_document: default
+  fig_caption: yes
   html_document:
     df_print: paged
-  fig_caption: yes
-  pdf_document: default
   word_document:
@@
 library(dplyr)
-library(ggplot2)
 library(tidyr)
@@
 library(RColorBrewer)
-library(nnet)
 library(stargazer)
@@
 library(readxl)
+library(ggplot2)
 Sys.setlocale("LC_ALL", "C")
@@
   ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) + # to add CI here set se to TRUE
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
         legend.position = "bottom") +
-  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
+  ggplot2::annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
@@
            alpha = 0.1) +
-  annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
+  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
            label = hp$presid, alpha = 0.4)
@@
                                             "Economic Sovereignty", "Social Conservation", "Other")),
-         env_vs_all <- ifelse(mx_cat == "Pure Conservation", 1, 0),
+         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
+         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
+         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
+         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
          location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
@@
                                           "Amazonian Countries", "Brasilia", "Non Amazonian States")))
-# model
-model <- glm(env_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-             family = binomial(link = 'logit'), data = ama_model)
-# summary statistics
-model_summary <- summary(model)
-md_plot <- data.frame("Construction" = c("Economic Integration", "Social Development", "Sovereignty"),
-                      "Amazonian_Countries" = c(1.3411972, 1.2460915, 0.9310706),
-                      "Amazonian_States" = c(0.4578251, 1.4725563, 1.6281365),
-                      "Non_Amazonian_States" = c(0.6198104, 1.5838611, 1.9830952),
-                      "Brasilia" = c(-0.29279984, 0.59564579, 1.38333572))
-md_plot$Brasilia <- logit2prob(md_plot$Brasilia)
-md_plot$'Amazonian States' <- logit2prob(md_plot$Amazonian_States)
-md_plot$'Non Amazonian States' <- logit2prob(md_plot$Non_Amazonian_States)
-md_plot$'Amazonian Countries' <- logit2prob(md_plot$Amazonian_Countries)
-mplot <- md_plot %>%
-  select(-c("Amazonian_Countries", "Amazonian_States", "Non_Amazonian_States")) %>% 
-  tidyr::pivot_longer('Amazonian Countries':Brasilia) %>%
-  mutate(Percentage = 100*round(value, digit = 2)-50) %>%
-  mutate(Location = factor(name, levels = c("Amazonian Countries", "Amazonian States",
-                           "Non Amazonian States", "Brasilia"))) %>% 
-  ggplot(aes(x = Location, y = Percentage, fill = Construction)) +
-  geom_bar(stat = "identity", position = position_dodge(0.8), width = 0.7) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  scale_y_continuous(breaks = seq(-15, 40, 10), limits = c(-15, 40)) +
-  geom_text(aes(label = Percentage), vjust = 1.5, size = 3, position = position_dodge(0.8)) +
-  geom_hline(yintercept = 0, linetype = "dotted", color = "red") +
-  labs(x = "", y = "Percentage",
-       title = "Percentage for problem constructions across locations in relation\nto environmental conservation problem constructions Internationally",
-       subtitle = "Bars reflect how much more (or less) likely are specific problem constructions in a specific location in relation to reference category") +
+# plot
+mplot <- ama_model %>%
+  select(con_vs_all, km_to_manaus) %>%
+  ggplot(aes(x = km_to_manaus, y = con_vs_all)) +
+  geom_smooth(se = FALSE, size = .5, color = "darkgreen") +
+  scale_y_continuous(labels = percent_format()) +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
+  labs(x = "Distance to Manaus (km)",
+       y = "Environmental conservation",
+       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
+       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
+       caption = "Curve in the plot is smoothed using loess method.") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+mplot
+mplot_all <- ama_model %>%
+  select(con_vs_all, EI_vs_all, SD_vs_all, sov_vs_all, km_to_manaus) %>%
+  rename("Pure Conservation" = con_vs_all,
+         "Pure Economic Integration" = EI_vs_all,
+         "Pure Social Development" = SD_vs_all, 
+         "Pure Sovereignty" = sov_vs_all) %>% 
+  pivot_longer(-km_to_manaus, names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = km_to_manaus, y = value, color = variable)) +
+  geom_smooth(se = FALSE, size = .5) +
+  scale_y_continuous(labels = percent_format()) +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
+  labs(x = "Distance to Manaus (km)",
+       y = "Problem Construction",
+       title = "Amazon problem constructions in relation to distance to Manaus",
+       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
+       caption = "Curve in the plot is smoothed using loess method.") +
     theme(panel.background = element_rect("white", "black", .5, "solid"),
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-          legend.position = c(0.5, 0.15))
-mplot
+          legend.position = "bottom")
+mplot_all
+# model
+model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+             family = binomial(link = 'logit'), data = ama_model)
+# summary statistics
+summary(model)
 ```

### 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
added regression plot

@@
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.\@hirschman1975[p.
+The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.
+@hirschman1975 [p.
 388] exemplifies chosen problems with the case of the construction of Brasilia.
@@
                                           "Amazonian Countries", "Brasilia", "Non Amazonian States")))
-# plot
-mplot <- ama_model %>%
-  select(con_vs_all, km_to_manaus) %>%
-  ggplot(aes(x = km_to_manaus, y = con_vs_all)) +
-  geom_smooth(se = FALSE, size = .5, color = "darkgreen") +
-  scale_y_continuous(labels = percent_format()) +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
+# model
+model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+             family = binomial(link = 'logit'), data = ama_model)
+# summary statistics
+stargazer::stargazer(model, type = "text")
+# Plot model
+ama_model$predicted = predict(model, ama_model, type = "response")
+ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
+  geom_smooth(size = .5, color = "darkgreen") +
     labs(x = "Distance to Manaus (km)",
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-mplot
-mplot_all <- ama_model %>%
-  select(con_vs_all, EI_vs_all, SD_vs_all, sov_vs_all, km_to_manaus) %>%
-  rename("Pure Conservation" = con_vs_all,
-         "Pure Economic Integration" = EI_vs_all,
-         "Pure Social Development" = SD_vs_all, 
-         "Pure Sovereignty" = sov_vs_all) %>% 
-  pivot_longer(-km_to_manaus, names_to = "variable", values_to = "value") %>% 
-  ggplot(aes(x = km_to_manaus, y = value, color = variable)) +
-  geom_smooth(se = FALSE, size = .5) +
-  scale_y_continuous(labels = percent_format()) +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76, 9678.78, 15904.47), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris", "Cape Town", "Beijing"), alpha = 0.4) +
-  labs(x = "Distance to Manaus (km)",
-       y = "Problem Construction",
-       title = "Amazon problem constructions in relation to distance to Manaus",
-       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
-       caption = "Curve in the plot is smoothed using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-          legend.position = "bottom")
-mplot_all
-# model
-model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-             family = binomial(link = 'logit'), data = ama_model)
-# summary statistics
-summary(model)
+
 ```

### 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
More changes with rmd

@@
 # Load data
-##### We are missing many observations for Collor from 1991 and 1992...
-##### These are not in the repository for some reason...
-##### Should we try and complete or should we at least disclose these in a footnote?
+# Add a footnote about 1992 missing obs
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
@@
                                          mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
+         levels = c("Pure Economic Integration", "Pure Conservation",
+                    "Pure Social Development",
                     "Pure Sovereignty", "Other", "Economic Conservation", 
-                    "Social Economic", "Sovereign Conservation", "Economic, Social,\nand Conservation",
-                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
+                    "Social Economic", "Sovereign Conservation",
+                    "Economic, Social,\nand Conservation",
+                    "Economic Sovereignty", "Social Conservation",
+                    "Other Mixed-types")),
          mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
-                                   |Pure Social Development|Pure Sovereignty", mx_cat) ~ "Pure-types",
+                                   |Pure Social Development|Pure Sovereignty",
+                                   mx_cat) ~ "Pure-types",
                              grepl("^Other$", mx_cat) ~ "Other",
@@
   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-  geom_vline(xintercept = c(1988.7, 1992, 2009, 2015),
+  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015),
              linetype = "dotted") +
@@
 Amazon_year
-
-# Word frequency year
-popc <- filter(pop, amazon_speech == 1) %>%
-  select(year, text) %>% 
-  group_by(year) %>% 
-  rename(doc_id = year)
-popc$text <- stringr::str_replace_all(popc$text, "meio ambiente", "meioambiente")
-popc$text <- stringr::str_replace_all(popc$text, "forcas armadas", "forcasarmadas")
-popc$text <- stringr::str_replace_all(popc$text, "estados unidos", "estadosunidos")
-popc$text <- stringr::str_replace_all(popc$text, "rio de janeiro", "riodejaneiro")
-popc$text <- stringr::str_replace_all(popc$text, "direitos humanos", "direitoshumanos")
-popc$text <- stringr::str_replace_all(popc$text, "rio grande do sul", "riograndedosul")
-popc$text <- stringr::str_replace_all(popc$text, "copa do mundo", "copadomundo")
-popc$text <- stringr::str_replace_all(popc$text, "sao paulo", "saopaulo")
-popc$text <- stringr::str_replace_all(popc$text, "rio grande do norte", "riograndedonorte")
-popc$text <- stringr::str_replace_all(popc$text, "floresta amazonica", "florestaamazonica")
-popc$text <- stringr::str_replace_all(popc$text, "regiao amazonica", "regiaoamazonica")
-popc$text <- stringr::str_replace_all(popc$text, "mato grosso|mato-grosso", "matogrosso")
-popc$text <- stringr::str_replace_all(popc$text, "minas gerais", "minasgerais")
-popc$text <- stringr::str_remove_all(popc$text, " [a-z] ")
-popc$text <- tm::removeWords(tm::removePunctuation(popc$text),
-                             c(tm::stopwords("pt"), 
-                               "nao", "amazonas", "voce", "vao", "dar", "du",
-                               "our", "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
-                               "no", "hoje", "presidente", "governador", 
-                               "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
-                               "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
-                               "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
-                               "cumprimentar", "gente", "estado", "querido", "queria",
-                               "todos", "companheiro", "senhores", "alguns",
-                               "companheiras", "companheiros", "companheira", "entao",
-                               "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
-                               "grosso","ministro", "ministra", "josé", "jose",
-                               "palacio", "planalto", "pronunciamento", "sobre",
-                               "ministros", "luiz", "disse", "fizemos", "nesse",
-                               "antonio", "vou", "eduardo braga", "pais", "coisa",
-                               "então", "pouco", "pode", "sera", "dias",
-                               "outro", "onde", "discurso", "parte", "fala",
-                               "anos", "cada", "todo", "visite site", "disse",
-                               "site secretaria", "minas gerais", "lula silva",
-                               "inácio lula", "amapa", "bahia", "é", "lá", "et", "in",
-                               "httpwwwimprensaplanaltogovbr", "secretaria", "visitesite",
-                               "ta", "tudo", "pessoas", "falar", "neves", "tancredo",
-                               "brasiliadf", "cardoso", "httpwwwinfoplanaltogovbr", 
-                               "sip", "and", "to", "en", "des", "el", "le", "les", "dia",
-                               "palavra dorsdne", "fernando henrique", "dorsdne eete",
-                               "inacio lula", "lula silva", "inacio", "republica",
-                               "quegente", "muitas vezes", "ainda", "realmente",
-                               "assim", "possa", "coisas", "apenas", "acho", "ano",
-                               "vez", "portanto", "todas", "questao", "lado", "outros",
-                               "prezado", "vem", "sempre", "sarney", "luis", "serao", 
-                               "tao", "meses", "quase", "diante", "brasil", "sendo",
-                               "rsdneennoerqe", "brasil", "neste", "digo", "quase", 
-                               "queremos", "nesse", "nessa", "mim", "eete", "obrigado", "muita"))
-popc <- tm::VCorpus(tm::DataframeSource(popc))
-popn <- tidytext::tidy(popc) %>%
-  unnest_tokens(word, text) %>% 
-  group_by(id, word) %>% 
-  summarise(count = n()) %>% 
-  arrange(-count) %>% 
-  slice(1:10)
-popn <- aggregate(popn$word, list(popn$id), paste, collapse=", ") %>% 
-  rename(Year = "Group.1", Terms = "x")
-tibble(popn)
-##### LDA per year just in case
-pop_dtm  <- DocumentTermMatrix(popc)
-pop_lda <- topicmodels::LDA(pop_dtm, k = 10, control = list(seed = 1234))
-pop_lday <- tidy(pop_lda, matrix = "gamma") %>%
-  arrange(desc(gamma)) %>%
-  group_by(document) %>%
-  filter(row_number() %in% 1:1) %>% # get the top 3 topics per speaker
-  arrange(document) %>%
-  mutate(gamma = round(gamma, 1)) %>%
-  distinct() %>% 
-  rename (Year = document)
-pop_10 <- tidy(pop_lda, matrix = "beta") %>%
-  arrange(desc(beta)) %>%
-  group_by(topic) %>%
-  filter(row_number() %in% 1:10) %>%
-  arrange(topic)
-pop_10 <- aggregate(pop_10$term, list(pop_10$topic), paste, collapse=", ") %>%
-  rename(topic = "Group.1", Terms = "x")
-popt <- dplyr::left_join(pop_10, pop_lday, by = "topic") %>%
-  select(Year, Terms) %>% 
-  arrange(Year)
-tibble(popt)
 ```
@@
 ```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
 pure_types_time <- ama_mx %>%
@@
 mixed_types_presid
-# mixed_types_time <- ama_mx %>%
-#   count(mx_cat, mx_cat2, year) %>%
-#   group_by(year) %>%
-#   mutate(perc = n / sum(n),
-#          perc = ifelse(perc == 1, 0.25, perc)) %>% # Issue with 1992 
-#   filter(mx_cat2 == "Mixed-types") %>% 
-#   ggplot(aes(x = as.numeric(year), y = perc, color = mx_cat)) +
-#   geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
-#   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-#   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-#   labs(x = "", y = "", title ="Share of mixed type problem-constructions in time",
-#        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-#        caption = "") +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom") +
-#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.12,
-#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
-#            alpha = 0.1) +
-#   annotate(geom = "text", x = hp$label, y = 0.10, angle = 40,
-#            label = hp$presid, alpha = 0.4)
-# mixed_types_time
 ```
@@
        title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
-       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
+       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
        caption = "Curve in the plot is smoothed using loess method.") +
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
 ```

### 2022-06-13 Draft_May_2022/Full_draft_20220510.rmd
More changes with rmd

@@
   mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro")))
   ggplot(aes(x = president, y = perc, fill = mx_cat,

### 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
#new_model_alternative

--- 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
@@
 
-# Word frequency year
-popc <- filter(pop, amazon_speech == 1) %>%
-  select(year, text) %>% 
-  group_by(year) %>% 
-  rename(doc_id = year)
-popc$text <- stringr::str_replace_all(popc$text, "meio ambiente", "meioambiente")
-popc$text <- stringr::str_replace_all(popc$text, "forcas armadas", "forcasarmadas")
-popc$text <- stringr::str_replace_all(popc$text, "estados unidos", "estadosunidos")
-popc$text <- stringr::str_replace_all(popc$text, "rio de janeiro", "riodejaneiro")
-popc$text <- stringr::str_replace_all(popc$text, "direitos humanos", "direitoshumanos")
-popc$text <- stringr::str_replace_all(popc$text, "rio grande do sul", "riograndedosul")
-popc$text <- stringr::str_replace_all(popc$text, "copa do mundo", "copadomundo")
-popc$text <- stringr::str_replace_all(popc$text, "sao paulo", "saopaulo")
-popc$text <- stringr::str_replace_all(popc$text, "rio grande do norte", "riograndedonorte")
-popc$text <- stringr::str_replace_all(popc$text, "floresta amazonica", "florestaamazonica")
-popc$text <- stringr::str_replace_all(popc$text, "regiao amazonica", "regiaoamazonica")
-popc$text <- stringr::str_replace_all(popc$text, "mato grosso|mato-grosso", "matogrosso")
-popc$text <- stringr::str_replace_all(popc$text, "minas gerais", "minasgerais")
-popc$text <- stringr::str_remove_all(popc$text, " [a-z] ")
-popc$text <- tm::removeWords(tm::removePunctuation(popc$text),
-                             c(tm::stopwords("pt"), 
-                               "nao", "amazonas", "voce", "vao", "dar", "du",
-                               "our", "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
-                               "no", "hoje", "presidente", "governador", 
-                               "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
-                               "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
-                               "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
-                               "cumprimentar", "gente", "estado", "querido", "queria",
-                               "todos", "companheiro", "senhores", "alguns",
-                               "companheiras", "companheiros", "companheira", "entao",
-                               "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
-                               "grosso","ministro", "ministra", "josé", "jose",
-                               "palacio", "planalto", "pronunciamento", "sobre",
-                               "ministros", "luiz", "disse", "fizemos", "nesse",
-                               "antonio", "vou", "eduardo braga", "pais", "coisa",
-                               "então", "pouco", "pode", "sera", "dias",
-                               "outro", "onde", "discurso", "parte", "fala",
-                               "anos", "cada", "todo", "visite site", "disse",
-                               "site secretaria", "minas gerais", "lula silva",
-                               "inácio lula", "amapa", "bahia", "é", "lá", "et", "in",
-                               "httpwwwimprensaplanaltogovbr", "secretaria", "visitesite",
-                               "ta", "tudo", "pessoas", "falar", "neves", "tancredo",
-                               "brasiliadf", "cardoso", "httpwwwinfoplanaltogovbr", 
-                               "sip", "and", "to", "en", "des", "el", "le", "les", "dia",
-                               "palavra dorsdne", "fernando henrique", "dorsdne eete",
-                               "inacio lula", "lula silva", "inacio", "republica",
-                               "quegente", "muitas vezes", "ainda", "realmente",
-                               "assim", "possa", "coisas", "apenas", "acho", "ano",
-                               "vez", "portanto", "todas", "questao", "lado", "outros",
-                               "prezado", "vem", "sempre", "sarney", "luis", "serao", 
-                               "tao", "meses", "quase", "diante", "brasil", "sendo",
-                               "rsdneennoerqe", "brasil", "neste", "digo", "quase", 
-                               "queremos", "nesse", "nessa", "mim", "eete", "obrigado", "muita"))
-popc <- tm::VCorpus(tm::DataframeSource(popc))
-popn <- tidytext::tidy(popc) %>%
-  unnest_tokens(word, text) %>% 
-  group_by(id, word) %>% 
-  summarise(count = n()) %>% 
-  arrange(-count) %>% 
-  slice(1:10)
-popn <- aggregate(popn$word, list(popn$id), paste, collapse=", ") %>% 
-  rename(Year = "Group.1", Terms = "x")
-tibble(popn)
-##### LDA per year just in case
-pop_dtm  <- DocumentTermMatrix(popc)
-pop_lda <- topicmodels::LDA(pop_dtm, k = 10, control = list(seed = 1234))
-pop_lday <- tidy(pop_lda, matrix = "gamma") %>%
-  arrange(desc(gamma)) %>%
-  group_by(document) %>%
-  filter(row_number() %in% 1:1) %>% # get the top 3 topics per speaker
-  arrange(document) %>%
-  mutate(gamma = round(gamma, 1)) %>%
-  distinct() %>% 
-  rename (Year = document)
-pop_10 <- tidy(pop_lda, matrix = "beta") %>%
-  arrange(desc(beta)) %>%
-  group_by(topic) %>%
-  filter(row_number() %in% 1:10) %>%
-  arrange(topic)
-pop_10 <- aggregate(pop_10$term, list(pop_10$topic), paste, collapse=", ") %>%
-  rename(topic = "Group.1", Terms = "x")
-popt <- dplyr::left_join(pop_10, pop_lday, by = "topic") %>%
-  select(Year, Terms) %>% 
-  arrange(Year)
-tibble(popt)
 ```
@@
 # model
-model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-             family = binomial(link = 'logit'), data = ama_model)
+
+model_logit <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,family=binomial(link = "logit"), data = ama_model)
+
+model_lm <- lm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI, data = ama_model)
+
 # summary statistics
-stargazer::stargazer(model, type = "text")
+stargazer::stargazer(model_lm, type = "text")
+
+plot_model(model_lm)
+summary(model_lm)
+
 # Plot model
-ama_model$predicted = predict(model, ama_model, type = "response")
+
+ama_model$predicted = predict(model_lm, ama_model, type = "response")
 ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
+  geom_jitter(alpha=.5)+
   geom_smooth(size = .5, color = "darkgreen") +
-    labs(x = "Distance to Manaus (km)",
-       y = "Environmental conservation",
-       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
-       subtitle = "Distance as a straight line from state, or country, capital to Manaus in kilometers",
+    labs(x = "Distance from the Amazon (km)",
+       y = "Share of environmental conservation",
+       title = "Amazon constructions as an issue of  environmental conservation\nin relation to distance from the Amazon",
+       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",
        caption = "Curve in the plot is smoothed using loess method.") +

### 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
Updated plots and regressions to give a better overview of each problem construction

--- 2022-06-13 Draft_June_2022/Full_draft_20220608.rmd
@@
 library(tidyr)
-library(skimr)
 library(scales)
@@
 library(kableExtra)
-library(tm)
-library(tidytext)
-library(topicmodels)
 library(tibble)
@@
 # Load data
-# Add a footnote about 1992 missing obs
+##### We are missing many observations for Collor from late 1991 and 1992...
+##### These are not in the repository for some reason, this is an issue not on our side.
+##### We should we at least disclose these in a footnote.
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
@@
 AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
+location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>% 
+  select(-location_cat) %>%
+  distinct()
+ama <- left_join(ama, location_km, by = "location")
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>% 
-  select(-location_cat)
-ama <- left_join(ama, location_km, by = "location")
-adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data
+adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
+# Missing year data
 amazon_def_year <- rbind(adr, amazon_def_year) 
@@
                                          mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation",
-                    "Pure Social Development",
+         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
                     "Pure Sovereignty", "Other", "Economic Conservation", 
@@
                     "Economic, Social,\nand Conservation",
-                    "Economic Sovereignty", "Social Conservation",
-                    "Other Mixed-types")),
+                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
          mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
@@
                                    mx_cat) ~ "Mixed-types"),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+                                      year), 1, 0))
 ```
@@
   select(c(perc, amazon_speech, year))
-######## We have an issue with data here btw, 1992 only has 4 obs in the population... #######
-######## Issue is with biblioteca presidencial, not with scarping btw ######
-# summary(as.factor(pop$year))
 # Simple plot
@@
 Amazon_year
+# # comparison with inequality, crime and inflation in speeches
+# pop <- pop %>%
+#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
+#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
+#                               text, ignore.case = TRUE), 1, 0),
+#          inf = ifelse(grepl("inflacao|inflaçao",
+#                              text, ignore.case = TRUE), 1, 0),
+#          unemploy = ifelse(grepl("desempreg",
+#                              text, ignore.case = TRUE), 1, 0))
+# perc2 <- pop %>%
+#   count(desigual, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(desigual == 1) %>%
+#   select(c(perc, desigual, year))
+# perc3 <- pop %>%
+#   count(crime, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(crime == 1) %>%
+#   select(c(perc, crime, year))
+# perc4 <- pop %>%
+#   count(inf, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(inf == 1) %>%
+#   select(c(perc, inf, year))
+# perc5 <- pop %>%
+#   count(unemploy, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(unemploy == 1) %>%
+#   select(c(perc, unemploy, year))
+# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
+#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
+#             "Unemployment Speech" = "purple")
+# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+#   geom_line(aes(color = "Amazon Speech")) +
+#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
+#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
+#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
+#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
+#   scale_y_continuous(labels = percent_format()) +
+#   scale_color_manual(values = colors) +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
+#        caption = "",
+#        color = "Legend\n") +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
+# Amazon_vs_other
+# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
+#                                                            "Criminality", "Inflation",
+#                                                            "Unemployment"),
+#                                        "Mean share in time" = c(mean(perc1$perc),
+#                                                                 mean(perc2$perc),
+#                                                                 mean(perc3$perc),
+#                                                                 mean(perc4$perc),
+#                                                                 mean(perc5$perc)))
+# Amazon_vs_other_mean
 ```
@@
 ```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
 pure_types_time <- ama_mx %>%
@@
            alpha = 0.1) +
-  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjus = 0.3, hjust = 0.3, angle = 25,
+  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjust = 0.3, hjust = 0.3, angle = 25,
            label = hp$presid, alpha = 0.4)
@@
                                levels = c("International", "Amazonian States",
-                                          "Amazonian Countries", "Brasilia", "Non Amazonian States")))
+                                          "Amazonian Countries", "Brasilia",
+                                          "Non Amazonian States")))
 # model
-model <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-             family = binomial(link = 'logit'), data = ama_model)
-# summary statistics
-stargazer::stargazer(model, type = "text")
+model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+# # summary statistics, in appendix for now
+# stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
+#                      type = "text") # Negative for EI and SD
+# # simple pooled OLS with time effects vs random effects
+# ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+#                 data = ama_model, model = "pooling", index = c("year"))
+# random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+#                    data = ama_model, model = "random", index = c("year"))
+# summary(ols)
+# summary(random) # does not change when it comes independent variable
+# # Colinearity test
+# car::vif(model_logit_con) # All good!
 # Plot model
-ama_model$predicted = predict(model, ama_model, type = "response")
-ggplot(ama_model, aes(x = km_to_manaus, y = predicted)) + 
+ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
+# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
+# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
+# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
+# Plot all regressions, just in case
+# ama_model_all <- ama_model %>% 
+#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
+# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
+#   geom_smooth(se = FALSE, size = .5)
+ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
+  geom_jitter(alpha=.5)+
   geom_smooth(size = .5, color = "darkgreen") +
-    labs(x = "Distance to Manaus (km)",
-       y = "Environmental conservation",
-       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance to Manaus",
-       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  labs(x = "Distance from the Amazon (km)",
+       y = "Share of environmental conservation",
+       title = "Amazon constructions as an issue of environmental conservation\nin relation to distance from the Amazon",
+       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",
        caption = "Curve in the plot is smoothed using loess method.") +
@@
 
-full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
-                                           "SOV-EI", "SD-CON", "Other"),
-                  "Amazonian States" = c("0.458 (0.193)", "1.473*** (0.215)",
-                  "1.623*** (0.235)", "-0.056 (0.292)", "1.625*** (0.198)",
-                  "0.960*** (0.284)", "1.192*** (0.271)", "1.345*** (0.290)",
-                  "0.129 (0.323)", "0.999*** (0.207)"),
-                  "Amazonian Countries" = c("1.341*** (0.212)", "1.246*** (0.308)",
-                  "0.931** (0.383)", "0.304 (0.394)", "1.569*** (0.288)",
-                  "0.613*** (0.090)", "0.949*** (0.0857)", "2.609*** (0.345)",
-                  "0.660** (0.332)", "1.760*** (0.226)"),
-                  "Brasilia" = c("-0.293** (0.183)","0.596*** (0.210)",
-                  "1.383*** (0.209)", "-0.245 (0.265)", "0.823*** (0.193)",
-                  "0.890*** (0.237)", "0.123 (0.277)", "0.276 (0.310)",
-                  "-0.594** (0.317)", "0.0649 (0.202)"),
-                  "Non Amazonian States" = c("0.620** (0.212)", "1.584*** (0.219)", "1.983*** (0.238)",
-                  "0.242 (0.311)", "1.637*** (0.223)", "1.309*** (0.283)",
-                  "0.871*** (0.308)", "1.418*** (0.323)", "0.217 (0.342)", "0.849*** (0.231)"),
-                  "Election Year" = c("-0.517*** (0.160)", "-0.007 (0.192)",
-                  "-0.733*** (0.277)",
-                  "-0.016 (0.232)", "-0.453* (0.255)", "-0.691* (0.378)",
-                  "0.080 (0.343)", 
-                  "-1.400*** (0.429)","0.0008 (0.378)", "-0.713*** (0.170)"),
-                  "Annual Deforestation" = c("0.082*** (0.011)", "-0.037** (0.015)",
-                  "0.001 (0.018)", 
-                  "0.0197 (0.0170)", "0.060*** (0.017)", "0.012 (0.024)",
-                  "-0.026 (0.026)", 
-                  "-0.007 (0.027)", "-0.002 (0.027)", "0.076*** (0.0120)"),
-                  "Average Inflation" = c("-0.0005*** (0.0001)", "-0.0005*** (0.0001)",
-                  "-0.0001 (0.0002)", "-0.0006*** (0.0001)", "-0.0005** (0.0002)",
-                  "0.0001 (0.0002)", "-0.0008** (0.0004)", "-0.0004 (0.0004)",
-                  "-0.0006* (0.0004)", "-0.0003*** (0.0001)"))
-kbl(t(full_md), booktabs = T,caption = "Multinomial Regression Full", align = "c") %>%
+model_comp <- tibble::tibble("Dependent Variable" = c("Environmental Conservation", 
+"Economic Integration", "Social Development", "National Sovereignty"),
+"Distance to Manaus(km)" = c("0.0001*** (0.00002)", "-0.0001** (0.00002)", "-0.0001** (0.00004)", "0.00001 (0.00002)"),
+"Election Year" = c("0.288* (0.157)", "-0.022 (0.133)", "0.329* (0.171)", "-0.449* (0.269)"),
+"Deforestation Year" = c("-0.032*** (0.011)", "0.041*** (0.008)", "-0.072*** (0.013)", "-0.032* (0.017)"),
+"Annual Average Inflation" = c("0.0004*** (0.0001)", "-0.0002** (0.0001)", "-0.0002 (0.0002)", "0.0002 (0.0002)"),
+"Constant" = c("-1.718*** (0.191)", "-1.569*** (0.160)", "-0.910*** (0.214)", "-2.301*** (0.289)"))
+kbl(t(model_comp), booktabs = T,caption = "Logistic Regression Models Compared", align = "c") %>%
   kable_styling(latex_options = c("striped", "scale_down"),
                 position= "center", font_size = 9, full_width = TRUE) %>%
-                footnote(general = c("The multinomial regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
+                footnote(general = c("The regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
                 "*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
@@
   column_spec(4, width = "2 cm", latex_valign = "m") %>%
-  column_spec(5, width="2 cm", latex_valign = "m") %>%
-  column_spec(6, width = "2 cm", latex_valign = "m") %>%
-  column_spec(7, width = "2 cm", latex_valign = "m") %>% 
-  column_spec(8, width="2 cm", latex_valign = "m") %>%
-  column_spec(9, width = "2 cm", latex_valign = "m") %>%
-  column_spec(10, width = "2 cm", latex_valign = "m") %>% 
-  column_spec(11, width = "2 cm", latex_valign = "m")
+  column_spec(5, width="2 cm", latex_valign = "m")
 ```

### 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
Updated plot labs to make them more intuitive

@@
   labs(x = "Distance from the Amazon (km)",
-       y = "Share of environmental conservation",
-       title = "Amazon constructions as an issue of environmental conservation\nin relation to distance from the Amazon",
-       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",
+       y = "The Amazon as an issue of environmental conservation",
+       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
+       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
        caption = "Curve in the plot is smoothed using loess method.") +

### 2022-06-15 Draft_June_2022/Full_draft_20220608.rmd
Added littels 2 x 2 table

--- 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
@@
          election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
-                                      year), 1, 0))
+                                      year), 1, 0),
+                  location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
+                                     location, ignore.case = TRUE), # minor coding issues to fix
+                               "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat), # minor coding issues to fix
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries", location_cat),
+                               levels = c("International", "Amazonian States",
+                                          "Amazonian Countries", "Brasilia",
+                                          "Non Amazonian States")))
+# # Table of Amazonian speeches internationally vs. in Brazil
+# amazon_in_out <- pop %>% select(amazon_speech, location_cat)
+# table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+# amazon_in_out <- mutate(amazon_in_out,
+#                         location_cat = ifelse(grepl("International", location_cat), 0, 1))
+# amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+# rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
+# colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
+# amazon_in_out
 ```
@@
 ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
-  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
-                                            "Pure Social Development", "Pure Sovereignty",
-                                            "Economic Conservation", "Social Economic",
-                                            "Sovereign Conservation", 
-                                            "Economic, Social,\nand Conservation",
-                                            "Economic Sovereignty", "Social Conservation", "Other")),
-         con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
          EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
          SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
-         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0),
-         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
-                                     location, ignore.case = TRUE), # minor coding issues to fix
-                               "Non Amazonian States", location_cat),
-         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
-                               "International", location_cat), # minor coding issues to fix
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries", location_cat),
-                               levels = c("International", "Amazonian States",
-                                          "Amazonian Countries", "Brasilia",
-                                          "Non Amazonian States")))
+         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))
 # model

### 2022-06-16 Draft_June_2022/Full_draft_20220608.rmd
Added plot for figure 2 across location (commented out) and added regression models plot for pure problem constructions

--- 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
@@
          election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
-                                      year), 1, 0))
+                                      year), 1, 0),
+                  location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
+                                     location, ignore.case = TRUE), # minor coding issues to fix
+                               "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat), # minor coding issues to fix
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries", location_cat),
+                               levels = c("International", "Amazonian States",
+                                          "Amazonian Countries", "Brasilia",
+                                          "Non Amazonian States")))
+# # Table of Amazonian speeches internationally vs. in Brazil
+# amazon_in_out <- pop %>% select(amazon_speech, location_cat)
+# table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+# amazon_in_out <- mutate(amazon_in_out,
+#                         location_cat = ifelse(grepl("International|Non Identified",
+#                                               location_cat), 0, 1))
+# amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+# rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
+# colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
+# amazon_in_out
 ```
@@
   group_by(year) %>%
-  mutate(perc=n / sum(n)) %>%
+  mutate(perc = n / sum(n)) %>%
   filter(amazon_speech == 1) %>% 
@@
 # Amazon_vs_other_mean
+# # Same plot with location
+# perc_in <- pop %>%
+#   mutate(location_cat = ifelse(grepl("International|Non Identified", location_cat),
+#                                "Outside of Brazil", "Within Brazil")) %>%
+#   count(amazon_speech, year, location_cat) %>%
+#   group_by(year) %>%
+#   mutate(perc = n / sum(n)) %>%
+#   filter(amazon_speech == 1) %>% 
+#   select(c(perc, amazon_speech, year, location_cat))
+# Amazon_year_in <- perc_in %>% ggplot(., aes(x = year, y = perc, fill = location_cat)) +
+#   geom_line(aes(color = location_cat)) +
+#   scale_y_continuous(labels = percent_format()) +
+#   geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
+#   geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
+#   geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
+#   geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
+#   geom_vline(xintercept = c(1988.9, 1992, 2009, 2015),
+#              linetype = "dotted") +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985",
+#        caption = "",
+#        color='Y series') +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
+# Amazon_year_in
 ```
@@
 ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
-# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
-# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
-# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
+ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
+ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
+ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
 # Plot all regressions, just in case
-# ama_model_all <- ama_model %>% 
-#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
-# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
-#   geom_smooth(se = FALSE, size = .5)
-ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
-  geom_jitter(alpha=.5)+
-  geom_smooth(size = .5, color = "darkgreen") +
+ama_model_all <- ama_model %>%
+  rename("Environmental Conservation" = predicted_con,
+         "Economic Integration" = predicted_ei,
+         "Social development" = predicted_sd,
+         "National Sovereignty" = predicted_sov) %>% 
+  pivot_longer('Environmental Conservation':'National Sovereignty',
+               names_to = "Construction", values_to = "Share")
+ggplot(ama_model_all, aes(x = km_to_manaus, y = Share, color = Construction)) +
+  geom_smooth(size = .5) +
   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.4,
                     label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
   labs(x = "Distance from the Amazon (km)",
-       y = "The Amazon as an issue of environmental conservation",
-       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
+       y = "Share of problem construction",
+       title = "How is the Amazon constructed as an issue across locations?",
        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+# # Environmental conservation and location
+# ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
+#   geom_jitter(alpha=.5)+
+#   geom_smooth(size = .5, color = "darkgreen") +
+#   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+#   ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+#                     label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+#   labs(x = "Distance from the Amazon (km)",
+#        y = "The Amazon as an issue of environmental conservation",
+#        title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
+#        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
+#        caption = "Curve in the plot is smoothed using loess method.") +
+#     theme(panel.background = element_rect("white", "black", .5, "solid"),
+#           panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#           axis.text = element_text(color = "black", size = 10),
+#           title = element_text(color = "black", size = 10, face = "bold"),
+#           legend.title = element_blank(),
+#           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
 ```

### 2022-08-23 Draft_June_2022/Full_draft_20220608.rmd
#newplots #newtext #cleanedchunks

--- 2022-06-15 Draft_June_2022/Full_draft_20220608.rmd
@@
 library(ggplot2)
+library(gridExtra)
 Sys.setlocale("LC_ALL", "C")
@@
 # amazon_in_out <- mutate(amazon_in_out,
-#                         location_cat = ifelse(grepl("International", location_cat), 0, 1))
+#                         location_cat = ifelse(grepl("International|Non Identified",
+#                                               location_cat), 0, 1))
 # amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
@@
 # amazon_in_out
+
+amazon_in_out <- pop %>% select(amazon_speech, location_cat)
+table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+amazon_in_out <- mutate(amazon_in_out,
+                         location_cat = ifelse(grepl("International", location_cat), 0, 1))
+amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
+rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
+colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
+amazon_in_out
 ```
@@
 We need to preserve the Amazon as a standing ecosystem.
-Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.Different governmental programs contained an assumptions of what had to be solved in the Amazon, or in other words, it represents the Amazon as a particular problem.
+Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.
+Different governmental programs contained an assumptions of what had to be solved in the Amazon, or in other words, it represented the Amazon as a particular problem.
 These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
@@
 @calderwood2020 also tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988, he hypothesizes that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-The author finds evidence in support of his hypothesis, suggesting American presidential discourse at the top on global warming changes based on location.
+Building prominently on @putnam1988, he demonstrates that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
 Elsewhere, @bevitori2015 investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
@@
 
-# 4 The Amazon in Presidential Speeches
+# 4 How has the Amazon been constructed as a problem?
+
+We break down our analysis in three sub-sections.
+First, we describe when, where and how often do presidents speak about the Amazon or do not speak about the Amazon.
+Second, we zoom in speeches about the Amazon and demonstrate how they vary by problem-construction.
+Finally, we model which specific problem-constructions are more likely to appear in which locations using logistic regressions with multiple controls.
 
@@
 
-The frequency in which the Amazon appears across all official presidential speeches varies in time.
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches per year.
-We observe five local maxima: 1989, 1992, 2009, 2015, and 2019.
+When, where, and how often do presidents speak about the Amazon?
+Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
+On average, presidents speak about the Amazon in 15% of their speeches.
+Mentioning the Amazon outside of Brazil is a rarer event than mentioning it inside Brazil.The frequency in which the Amazon appears across presidential speeches (inside, outside, and overall), though, varies in time.
+
+Globally, we observe five local maxima both inside and outside Brazil: 1989, 1992, 2009,2015, and 2019.
 These points, usually, coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
@@
 However, in 1989, the Amazon appeared in 32% of all speeches.
-This spike is likely explained by the brutal murder of Chico Mendes and the very end of 1988.
+This spike is likely explained by the brutal murder of Chico Mendes at the very end of 1988.
 An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021].
@@
 ```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+
 perc1 <- pop %>%
@@
   group_by(year) %>%
-  mutate(perc=n / sum(n)) %>%
+  mutate(perc = n / sum(n)) %>%
   filter(amazon_speech == 1) %>% 
   select(c(perc, amazon_speech, year))
-# Simple plot
+
+perc_in <- pop %>%
+   mutate(location_cat = ifelse(grepl("International|Non Identified", location_cat),
+                                "Outside of Brazil", "In Brazil")) %>%
+   count(amazon_speech, year, location_cat) %>%
+   group_by(year) %>%
+   mutate(perc = n / sum(n)) %>%
+   filter(amazon_speech == 1) %>%
+   select(c(perc, amazon_speech, year, location_cat))
+
+# Plot with All
+
 Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
   geom_line(color = "darkgreen") +
+  geom_line(aes(y=mean(perc)), color="black", size=.5)+
   scale_y_continuous(labels = percent_format()) + 
-  geom_text(aes(x = 1988.7, y = 0.34, label = "Chico Mendes"), size = 3) +
-  geom_text(aes(x = 1992, y = 0.27, label = "Earth Summit"), size = 3) +
-  geom_text(aes(x = 2009, y = 0.24, label = "Copenhagen Summit"), size = 3) +
-  geom_text(aes(x = 2015, y = 0.21, label = "Paris Summit"), size = 3) +
-  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015),
-             linetype = "dotted") +
-  labs(x = "", y = "", title ="Share of speeches mentioning the Amazon by year",
-       subtitle = "Sample composed by 6130 presidential speeches since 1985",
+  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.26, label = "Sao Paulo darkened \n by smoke", size=3) +
+  labs(x = "", y = "",
+       subtitle = "All speeches inside and outside Brazil (n=6130)",
        caption = "",
@@
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
         legend.position = "bottom")
-Amazon_year
+
+# location plots
+
+Amazon_year_in <- perc_in %>% filter(location_cat== "In Brazil") %>% 
+  ggplot(., aes(x = year, y = perc))+
+  geom_line(color="darkgreen")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5)+
+  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  scale_y_continuous(labels = percent_format())+
+  labs(x = "", y = "",
+       subtitle = "Speeches in Brazil (n=4416)",
+       color='Y series') +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
+        legend.position = "")
+
+Amazon_year_out <- perc_in %>% filter(location_cat== "Outside of Brazil") %>% 
+  ggplot(., aes(x = year, y = perc))+
+  geom_line(color="darkgreen")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5)+
+  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  scale_y_continuous(labels = percent_format())+
+  labs(x = "", y = "",
+       subtitle = "Speeches outside of Brazil (n=1714)",
+       caption= "Black lines portray the means.",
+       color='Y series') +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
+        legend.position = "")
+
+grid.arrange(Amazon_year, arrangeGrob(Amazon_year_in, Amazon_year_out, ncol=2), nrow=2, top="Speeches mentioning the Amazon since 1985")
+
+```
+
+```{r comparison with inequality, crime, and inflation eval=FALSE, include=FALSE}
+
 # # comparison with inequality, crime and inflation in speeches
@@
 # Amazon_vs_other_mean
+
+# comparison with inequality, crime and inflation in speeches
+# pop <- pop %>%
+#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
+#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
+#                               text, ignore.case = TRUE), 1, 0),
+#          inf = ifelse(grepl("inflacao|inflaçao",
+#                              text, ignore.case = TRUE), 1, 0),
+#          unemploy = ifelse(grepl("desempreg",
+#                              text, ignore.case = TRUE), 1, 0))
+# perc2 <- pop %>%
+#   count(desigual, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(desigual == 1) %>%
+#   select(c(perc, desigual, year))
+# perc3 <- pop %>%
+#   count(crime, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(crime == 1) %>%
+#   select(c(perc, crime, year))
+# perc4 <- pop %>%
+#   count(inf, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(inf == 1) %>%
+#   select(c(perc, inf, year))
+# perc5 <- pop %>%
+#   count(unemploy, year) %>%
+#   group_by(year) %>%
+#   mutate(perc=n / sum(n)) %>%
+#   filter(unemploy == 1) %>%
+#   select(c(perc, unemploy, year))
+# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
+#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
+#             "Unemployment Speech" = "purple")
+# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+#   geom_line(aes(color = "Amazon Speech")) +
+#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
+#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
+#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
+#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
+#   scale_y_continuous(labels = percent_format()) +
+#   scale_color_manual(values = colors) +
+#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
+#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
+#        caption = "",
+#        color = "Legend\n") +
+#   theme(panel.background = element_rect("white", "black", .5, "solid"),
+#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#         axis.text = element_text(color = "black", size = 10),
+#         title = element_text(color = "black", size = 10, face = "bold"),
+#         legend.title = element_blank(),
+#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+#         legend.position = "bottom")
+# Amazon_vs_other
+# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
+#                                                            "Criminality", "Inflation",
+#                                                            "Unemployment"),
+#                                        "Mean share in time" = c(mean(perc1$perc),
+#                                                                 mean(perc2$perc),
+#                                                                 mean(perc3$perc),
+#                                                                 mean(perc4$perc),
+#                                                                 mean(perc5$perc)))
+# Amazon_vs_other_mean
+
 ```
@@
 The 1992 Earth Summit, held in Brazil brought international attention to environmental topics in the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-Throughout the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon appeared, on average, on 15% of all speeches.
-Exceptionally, in 2009 we see another spike in the Amazon appearing in official speeches.
+One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].Throughout the rest of 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average.
+In 2009 we see another spike in the Amazon appearing in official speeches.
 This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
@@
 At the same time, President Bolsonaro retrieves Brazil's hosting status for COP25.
-In short, relevant international events drive interest and alter how pressing the "Amazon problem" is perceived to be in society, therefore, cause a momentary shift of interest from top policymakers.
+In short, relevant events drive interest and alter how pressing the "Amazon problem" is perceived to be in society, therefore, events cause a momentary shift of interest.These events seem to drive the topic up inside and outside Brazil.
 
-## 4.2 How has the Amazon been constructed as a problem?
+## 4.2 Problem-constructions in time
 
@@
 
+When presidents speak about the Amazon, what are they saying?
 We conceptualize four pure problem constructions: sovereignty, economic integration, social development, and conservation.
@@
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure type by year",
+  labs(x = "", y = "", title ="Share of each pure-type problem-construc by year",
        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
@@
 Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
-This is especially pertinent during the Cardoso administration as the Amazon was constructed, overwhelmingly, as an issue of economic integration.
+This is especially pertinent during the Cardoso administration.
 However, during Lula's terms in office, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased.
@@
 @capobianco2021, for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-A higher incidence of the Amazon, as a topic in overall presidential speeches, generates a perception that more attention is being paid to the Amazon from the top while the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored.
+A higher incidence of the Amazon as a topic in overall presidential speeches (figure 2), generates a perception that more attention is being paid to the Amazon from the top.
+While the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored (figure 3).
 
@@
 While there is some variation in time, some mixed-types rarely appear, thus, we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the average mixed-types by president.
+Figure 4, below, displays the yearly averages of mixed-types.
 
-```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure x, echo=FALSE, fig.cap="Mixed-types by president", message=FALSE, warning=FALSE, paged.print=FALSE}
+
 mixed_types_presid <- ama_mx %>%
@@
   scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed type problem-constructions by president",
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
@@
         legend.position = "right")
+
 mixed_types_presid
@@
 
-The most frequent mixed-type problem construction of the Amazon in time is economic corsevation.
-The mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
-Economic conservation averages at 6.8% in relation to all Amazonian statements.
-The mixed type generally increased in time, with Bolsonaro employing the mixed-type higher than all other presidents.
+```{r test, eval=FALSE, fig.cap="Mixed-types by year", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+mixed_types_year <- ama_mx %>%
+  count(year, mx_cat, mx_cat2) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  ggplot(aes(x = year, y = perc, color = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by year",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "")+
+    facet_wrap(~mx_cat)
+
+mixed_types_year
+
+```
+
+The most frequent mixed-type problem construction of the Amazon in time is economic conservation, which has increased slightly in time.
+This mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
+
+(How do we interpret this increase?)
+
 The second most common mixed-type in time mixes social development and economic integration and appears, on average, in 5.4% of all statements.
@@
 In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
+
+(How do we interpret this increase?)
+
 While Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
@@
 
-## 4.3 The Amazonian multi-level game, boasting policy outside and talking to people inside
+Generally, the increase of mixed-types makes sense given the rise of a global agenda understanding interconnections of social, environmental, and economic domains.
+As we show that Amazonian incidence in discourse does respond to global events as summits, this is not a surprise given agendas such as the Millennium Development Goals and the Sustainable Development Goals.
+
+Taken together, pure and mixed-types tell similar stories.
+
+## 4.3 The Amazonian multi-level game: boasting policy outside and talking to people inside
 
@@
                    family=binomial(link = "logit"), data = ama_model)
-# # summary statistics, in appendix for now
-# stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
+# summary statistics, in appendix for now
+#stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
 #                     type = "text") # Negative for EI and SD
-# # simple pooled OLS with time effects vs random effects
-# ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-#                 data = ama_model, model = "pooling", index = c("year"))
-# random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-#                    data = ama_model, model = "random", index = c("year"))
-# summary(ols)
-# summary(random) # does not change when it comes independent variable
-# # Colinearity test
-# car::vif(model_logit_con) # All good!
+# simple pooled OLS with time effects vs random effects
+ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                data = ama_model, model = "pooling", index = c("year"))
+random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   data = ama_model, model = "random", index = c("year"))
+summary(ols)
+summary(random) # does not change when it comes independent variable
+# Colinearity test
+car::vif(model_logit_con) # All good!
 # Plot model
 ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
-# ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
-# ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
-# ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
-# Plot all regressions, just in case
-# ama_model_all <- ama_model %>% 
-#   pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
-# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
-#   geom_smooth(se = FALSE, size = .5)
-ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
+ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
+ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
+ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
+
+# Environmental conservation and location
+
+env_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) +
   geom_jitter(alpha=.5)+
@@
        y = "The Amazon as an issue of environmental conservation",
-       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
+       title = "Share of speeches that constructed the as an issue of pure environmental conservation\nin relation to distance from Manaus",
        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
@@
           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+
+env_loc
+
+```
+
+```{r Plot all regressions eval=FALSE, include=FALSE}
+
+# ama_model_all <- ama_model %>% rename("Environmental Conservation" = predicted_con,
+#          "Economic Integration" = predicted_ei,
+#          "Social development" = predicted_sd,
+#          "National Sovereignty" = predicted_sov) %>% 
+#   pivot_longer('Environmental Conservation':'National Sovereignty',
+#                names_to = "Construction", values_to = "Share") %>% 
+#   ggplot(ama_model_all, aes(x = km_to_manaus, y = Share, color = Construction)) +
+#   geom_smooth(size = .5) + pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
+# 
+# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
+#   geom_smooth(se = FALSE, size = .5)
+# ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
+#   geom_jitter(alpha=.5)+
+#   geom_smooth(size = .5, color = "darkgreen") +
+#   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+#   ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.4,
+#                     label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+#   labs(x = "Distance from the Amazon (km)",
+#        y = "Share of problem construction",
+#        title = "How is the Amazon constructed as an issue across locations?",
+#        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
+#        caption = "Curve in the plot is smoothed using loess method.") +
+#     theme(panel.background = element_rect("white", "black", .5, "solid"),
+#           panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+#           axis.text = element_text(color = "black", size = 10),
+#           title = element_text(color = "black", size = 10, face = "bold"),
+#           legend.title = element_blank(),
+#           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+
 ```

### 2022-08-23 Draft_June_2022/Full_draft_20220608.rmd
Updated code chunk names (should avoid multple words) and plots for in and out the amazon (figure 2)

@@
 perc_in <- pop %>%
-   mutate(location_cat = ifelse(grepl("International|Non Identified", location_cat),
+   mutate(location_cat = ifelse(grepl("International|Non Identified",
+                                      location_cat),
                                 "Outside of Brazil", "In Brazil")) %>%
+  filter(location_cat == "In Brazil") %>% 
+  count(amazon_speech, year, location_cat) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>%
+  select(c(perc, amazon_speech, year, location_cat))
+
+perc_out <- pop %>%
+   mutate(location_cat = ifelse(grepl("International|Non Identified",
+                                      location_cat),
+                                "Outside of Brazil", "In Brazil")) %>%
+  filter(location_cat == "Outside of Brazil") %>% 
   count(amazon_speech, year, location_cat) %>%
@@
 # location plots
-
-Amazon_year_in <- perc_in %>% filter(location_cat== "In Brazil") %>% 
+Amazon_year_in <- perc_in %>%
   ggplot(., aes(x = year, y = perc))+
@@
   labs(x = "", y = "",
-       subtitle = "Speeches in Brazil (n=4416)",
+       subtitle = "Speeches in Brazil (n=4344)",
        color='Y series') +
@@
 
-Amazon_year_out <- perc_in %>% filter(location_cat== "Outside of Brazil") %>% 
+Amazon_year_out <- perc_out %>% 
   ggplot(., aes(x = year, y = perc))+
@@
   labs(x = "", y = "",
-       subtitle = "Speeches outside of Brazil (n=1714)",
+       subtitle = "Speeches outside of Brazil (n=1786)",
        caption= "Black lines portray the means.",
@@
 
-```{r comparison with inequality, crime, and inflation eval=FALSE, include=FALSE}
+```{r comparison, eval=FALSE, include=FALSE}
 
@@
 # Amazon_vs_other_mean
-
-# comparison with inequality, crime and inflation in speeches
+# #comparison with inequality, crime and inflation in speeches
 # pop <- pop %>%
@@
 
-```{r Plot all regressions eval=FALSE, include=FALSE}
+```{r regressions, eval=FALSE, include=FALSE}
 

### 2022-08-26 Draft_June_2022/Full_draft_20220608.rmd
#new text throughtout #changes to plots

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
+title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches in transnational politics since 1985
 author:
@@
 output:
+  word_document:
+    reference_docx:
+  fig_caption: yes
+  pdf_document: default
   html_document:
     df_print: paged
-  fig_caption: yes
-  pdf_document: default
-  word_document:
-    reference_docx: template.docx
 header-includes:
@@
 csl: chicago.csl
-abstract: The Amazon Rainforest is one of the most important ecosystems in the world, and most of this biome is located in Brazil.
-Albeit the importance of understanding the relationship between the social construction of the Amazon and its effects on environmental outcomes, we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
-Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level.
-Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse.
-Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985.
-We find that, first, international environmental events appear to drive presidents to speak more about the Amazon.
+abstract: Presidential speeches legitimize ways of thinking about the environment transnationally, while affecting decisions at the local level.Albeit the importance of understanding the relationship between the social construction of the environment and its effects on environmental outcomes, research on presidential discourse is scarce.
+We lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
+Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how heads of government construct the environment in transnational political discourse.
+Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in all 6130 official presidential speeches since 1985.
+We interpret our findings in light of policies adopted and important events.
+First, we find national and international events drive the frequency of the Amazon as a topic in presidential speeches equally inside and outside Brazil.
 Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards.
-Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
+Constructing the Amazon as an issue of sovereignty also became more pertinent after 2010.
+Finally, we find that the farthest presidents are from the Amazon, the more likely they are to state the Amazon needs to be preserved.
+Conceptually, we argue that these are evidence of presidents maximizing contradictory political outcomes domestically and internationally.
 ---
@@
 Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.
-Different governmental programs contained an assumptions of what had to be solved in the Amazon, or in other words, it represented the Amazon as a particular problem.
+Different governmental programs contain an assumptions of what has to be solved in the Amazon, or in other words, it represents the Amazon, implicitly or explicitly, as a particular problem.
 These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
@@
 While the military dictatorship is associated with both national sovereignty and then economic integration, Sarney's and Lula's presidencies are often tied to environmental conservation.
-However, governments are usually represented monolithically, advancing a view that specific governments see the Amazon as an instance of one specific problem.
+This monolithic representation advances a view that specific governments see the Amazon as an instance of one specific problem, hiding within government diversity of both policies and perspectives.
 Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
 
-In this article, we investigate how the Brazilian Amazon has been constructed as a problem in political discourses.
-Building on @hirschman1963 concept of chosen problems and @bacchi2009 concept of problem-representation in policy, we propose a framework to identify problem-constructions in political discourses.
-Although problem-construction takes place in a series of instances, we analyze the case of discourses by Brazilian presidents since 1985.
+In this article, we investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
+Building on @hirschman1963 concept of chosen problems and @bacchi2009 concept of problem-representation in policy, we propose a framework to identify problem-constructions.
+Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
+Importantly, scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy[@abers2019, @silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets[@rajão2020, @assuncao2015], and many others.
+Nevertheless, the role of president remains understudied.
+
 We opt for presidential speeches for two reasons.
@@
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations from governments' response, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
+This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
 Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
 Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is socially constructed.
-
-To investigate how the Brazilian Amazon has been constructed as a problem in presidential discourses, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
+Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is socially constructed in trasnational politics.
+
+To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
 We subset the dataset by identifying Amazonian related statements within these speeches.
@@
 We train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data.
-
-Our findings are threefold.
-First, we find that international environmental events appear to drive presidents to speak more about the Amazon.
-Second, while constructing the Amazon as a problem of economic integration dominated presidential discourses from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew from 2000s onwards briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
-Unprecedentedly, constructing the Amazon as an issue of sovereignty became more pertinent from 2010 onwards.
-Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
+We then conduct a descriptive and inferential analysis of this data, tying patterns in the data to Amazonian policies and deforestation outcomes along time.
+
+Our empirical findings are threefold.
+First, we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
+the assassination of Chico Mendes) as well as international events (UNFCCC Summits).
+Second, the same government adopts a diverse range of problem-constructions along time.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
+Hence, there is an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.
+In turn, constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
+Finally, using a logit model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.Conceptually, we interpret this findings as evidence of presidents maximizing political outcomes in contradictory ways: talking to people domestically, boasting environmental policy internationally.
 
@@
 We proceed to describe, visualize and interpret our findings in the analysis section.
-Finally, we conclude with a discussion connecting our findings to the democratic game and environmental outcomes.
+Finally, we conclude with a discussion connecting our findings to to Brazilian environmentalism.
 
@@
 
+We start this section by building our conceptual framework based on existing literature. We then moved to the specific problem-constructions that are embedded in Amazonian historiography.
+
 ## 2.1 Chosen problems, presidential discourse, and policy objects
 
-Governments often have a choice in how they construct problems and what policy solutions they implement.
+Governments have a choice in how they construct problems and what policy solutions they implement.
 In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
@@
 
-Additionally, @bacchi2009 [p.
+On the other hand, @bacchi2009 [p.
 10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts".
@@
 The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.
-@hirschman1975 [p.
-388] exemplifies chosen problems with the case of the construction of Brasilia.
-Building Brasilia could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three.
-It is up to the discretion of the government to highlight or not the implicit problem a policy solves.
+Coming back to @hirschman1975 [p.
+388], the author exemplifies chosen problems with the case of the construction of Brasilia.
+Nevertheless, building Brasilia (the policy) could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three depending on how governments speak about it.
+We argue that it is up to the discretion of the government to highlight or not the implicit problem a policy solves.
 A same policy object (e.g.
 Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.
-
+Policies are socially constructed in governmental discourse.
+
+What drives governmental choices of which underlying problem should be highlighted?
 Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with.
@@
 @putnam1988 seminal article on the two-level game can help us make sense of this variation conceptually.
-The author argues that the outcomes of international negotiations lie within the overlap between the pressure of domestic groups and international groups.
-Relatedly, @hochstetler2012 argue that international commitments in the Brazilian case shift as a function of domestic cost-benefit calculations, as the country as a large emitter does not abide to the global commons framings.
-Taking the example of the 2012 Forest Code and the Amazon, President Dilma could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
+The author argues that the outcomes of international negotiations lie within the overlap between the agenda (and pressure) of domestic groups and international groups.
+If policies are socially constructed, and consequently their implicit problem can vary, governments can in theory constructed it to meet the expectations of both.
+Taking the example of the 2012 Forest Code and the Amazon, policy-makers could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
 The same policy, then, can solve the problem of environmental conservation as well as economic integration.
 
-This variation in problem-construction suggests that governments are more diverse in their positions as the literature suggests.
-We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy.
+This variation in problem-construction entails that governments are more diverse in their positions than the literature suggests.
+We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
 Several scholars describe federal governments' as proponents of specific policies for the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
@@
 The presidency of Lula, often associated with environmental conservation because of the unprecedented decrease in deforestation.
-At the same time, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
+Nevertheless, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
 106].
@@
 
-An interesting site to study the relationship between varied problem-construction and policy issues is presidential speeches as they legitimize ways of thinking about an issue.
+An interesting site to study the relationship between varied problem-construction and policy objects is presidential speeches as they legitimize ways of thinking about an issue.
 While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
@@
 
-The possibility of different problem-constructions at the level of presidential speeches has important consequences for democracy.
-If presidents can promote different problem-constructions in different places, it is important to understand to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
-@pacheco2019 proposes that the Amazon is key to understand Brazilian state and democracy.
-Specifically, the author states that the natural richness of the region has been instrumentally transformed in political support through resource exploration by different governments over the last centuries.
-The costs for said economic benefits are the livelihoods of indigenous and traditional populations and the ecosystems they reside in.
-Political stability, thus, can be seen as a product of the trade-off between both.
-Policies during the military dictatorship were strongly geared toward integrating the Amazon into the national territory and international economy.
-These were times when deforestation increased, but political stability was achieved as those bearing the costs of said deforestation were being targeted.
-Generally high levels of violence in the region, epitomized in the assassination of Chico Mendes, serve as evidence for that [@hecht1990].
-With the return of democracy in the 1980s, violence could not be used at the same extent as before and policies had to respond to growing environmental concern.
-
+The possibility of different problem-constructions at the level of presidential speeches has important implications for democracy.
+With globalization and the increase of transnational processes, presidents have the opportunity of promoting different problem-constructions trasnnationally.
+It is important to understand, thus, to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
 Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well.
@@
 Deforestation rates in Brazil are more responsive to the government's environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
+Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective (2021).
 Relatedly, ethnographic research has also shown that expectations about governments' response are a crucial factor in decisions to deforest at the ground [@campbell2015].
@@
 The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-@calderwood2019, for instance, examines 2919 mentions of climate change in American official presidential speeches since 1989.
+@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
 Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change.
@@
 On the other hand, there is also an empirical gap in terms of how the Amazon has been constructed as a problem along time and geographic location.
-While governmental discourses in Brazil have been studied for topics such as inflation or race relations, we only find one systematic analysis of Amazonian discourse.
+While governmental discourses in Brazil have been studied for topics such as inflation or race relations[@malheiros1995, @htun2004, @silva2019], we only find one systematic analysis of Amazonian discourse.
 @barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
@@
 
-We propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy issue and connects it to presidential speeches.
+In sum, we propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy issue and connects it to presidential speeches.
 Governments choose what problems to solve and what policies to implement.
@@
 
-As we move from a world where non-state actors gain importance in environmental governance and international politics generally [@silva-muller2022; @andonova2014; @westerwinter2021], the sovereignty problem becomes more varied.
+As we move from a world where non-state actors gain importance in environmental governance and transnational politics generally [@silva-muller2022; @andonova2014; @keck1998], the sovereignty problem becomes more varied.
 Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
@@
 
-Closely related to economic integration, social development is a problem-construction that is often neglected while describing policy cycles or phases.
-While this might be related to social policies being more geared towards the whole nation, there are instances of specific social policies for the Amazon.
 Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights when speaking about the Amazon.
-This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.
+This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.While related to economic integration, social development is a problem-construction that focusses more on rights and citizenship.
+Importantly, though, the literature on policy cycles in the region is silent about social develop.
+This category was identified in speeches and constructed by the researchers inductively.
+This might be related to social policies being more geared towards the whole nation, rather than thought specifically for the Amazon region.
+Nevertheless, as it appeared quite frequently in discourse, we include it in our codebook.
 
@@
 To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-To test whether different problem constructions change according to location, we run a multinomial logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
+To test whether different problem constructions change according to location, we run a logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
 Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case [@kwak2002].
 In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
-We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, as well as their correlations with different presidents and locations, while embedding problem-construction in contemporary happenings.
+We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, mostly with support of existing literature, as well as their correlations with different presidents and locations.
 
@@
 On average, presidents speak about the Amazon in 15% of their speeches.
-Mentioning the Amazon outside of Brazil is a rarer event than mentioning it inside Brazil.The frequency in which the Amazon appears across presidential speeches (inside, outside, and overall), though, varies in time.
+Mentions to the Amazon outside of Brazil are slightly more frequent than mentions inside Brazil.The frequency in which the Amazon appears across presidential speeches (inside, outside, and overall), though, varies in time.
 
 Globally, we observe five local maxima both inside and outside Brazil: 1989, 1992, 2009,2015, and 2019.
-These points, usually, coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
-For instance, in 1985 the Amazon appeared in about 4% of all the presidential speeches but by 1988 this had increased to around 14%.
+These points coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
+In 1985 the Amazon appeared in about 4% of all the presidential speeches but by 1988 this had increased to around 14%.
 This is the period when the Brazilian Constitution was written.
@@
 However, in 1989, the Amazon appeared in 32% of all speeches.
-This spike is likely explained by the brutal murder of Chico Mendes at the very end of 1988.
+This spike is likely explained by the brutal murder of Chico Mendes at the last days of 1988.
 An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021].
+Importantly, one of the responses was Sarney's invitation to host the 1992 Earth Summit[@keck1998].
 
@@
   annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "Sao Paulo darkened \n by smoke", size=3) +
+  annotate("text", x = 2019, y = 0.26, label = "Red Sky afternoon \n in Sao Paulo", size=3) +
   labs(x = "", y = "",
@@
        subtitle = "Speeches in Brazil (n=4344)",
+       caption= " ",
        color='Y series') +
@@
 In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
-The 1992 Earth Summit, held in Brazil brought international attention to environmental topics in the Amazon.
+The 1992 Earth Summit in Brazil brought international attention to environmental topics related to the Amazon.
 One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].Throughout the rest of 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average.
@@
 From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-From 2010 to 2014, mentions of the Amazon went down from 18% to 8% in official speeches.
+From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
 Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
@@
 This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation.
+Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
 By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
@@
 At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets.
-This brought issues related to environmental conservation as high priorities in Bolsonaro's governing agenda with efforts to dismantle key pillars of Brazilian environmental governance.
+Bolsonaro's dismantling of environmental governance, including threats to leave the Paris Agreement, gained strong media attention and the topic became prominent in his speeches.
 At the same time, President Bolsonaro retrieves Brazil's hosting status for COP25.
-In short, relevant events drive interest and alter how pressing the "Amazon problem" is perceived to be in society, therefore, events cause a momentary shift of interest.These events seem to drive the topic up inside and outside Brazil.
+
+The frequency of the topic Amazon in domestic and international speeches is similar.
+High increases in the topic frequency, as well, are similar in domestic and international speeches.
+The aforementioned events that coincide with high frequencies are both of domestic and international nature.
+We interpret this as evidence that relevant events drive interest and alter how pressing the "Amazon problem" is perceived both nationally and internationally.
+This does not mean, though, that when presidents speak about the Amazon, they say similar things.
+In the next sub-section, we dissect the content of their speech and whether specific events and policies drive specific problem-constructions.
 
@@
 
-When presidents speak about the Amazon, what are they saying?
-We conceptualize four pure problem constructions: sovereignty, economic integration, social development, and conservation.
+As detailed in section 2.2, we conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
 At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement.
-Figure 3, below, illustrates the share of each pure type in time.
+Figure 3, below, illustrates the share of each pure-type in time.
 Pure problem constructions dominate, with an average of 56% of all amazonian statements across time.
-As above, we observe a strong variation over time for most of these constructions.
+Again, we observe a strong variation over time for most of these constructions.
 
@@
            label = hp$presid, alpha = 0.4)
+
 pure_types_time
@@
 
-Amazonian constructions are not monolithic in time nor within governments.
-The same governments construct the Amazon as different issues in discourse.
+Figure 2 portrays a discursive shift from developing the Amazon economically, to conserving it and providing services to Amazonian citizens.
 Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
@@
 These trends in discourse continued during the Rousseff administration.
-@capobianco2021, for example, argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
+If interpreted in light of deforestation rates since 1988, this trend is particularly interesting.
+The overall development of environmental conservation in figure 3 suggests a negative correlation with deforestation rates.
+When deforestation rates increased (1988 to 2004, and from 2012 until 2021), environmental conservation decreased.
+When deforestation rates decreased (2004 to 2012), environmental conservation in presidential speeches increased.
+The opposite is true foe economic integration problem-constructions, which increased as deforestation rates increased, and decreased when deforestation rates decreased.
+
+A possible explanation for this can be found in the logic of the policies adopted.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
 A higher incidence of the Amazon as a topic in overall presidential speeches (figure 2), generates a perception that more attention is being paid to the Amazon from the top.
-While the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored (figure 3).
-
-From the mid-2010s onwards, we start to see a reverse of this trend: economic integration problem construction increases while conservation and social development constructions decrease instead.
-Interestingly, sovereignty starts to increase steadily from 2010 onwards and by 2019 sovereignty constructions surpass social development.
-Figure 3 also highlights that, while the reversal precedes the mandate of President Bolsonaro, it was with him that sovereignty constructions reached unprecedented levels since the establishment of Brazilian democracy.
+While the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned (figure 3).
+A further explanation might be related to boasting about policy outcomes: when deforestation is high, presidents are more likely to focus on economic integration as its product.
+We scrutinize this possibility further in section 4.3.
+
+Figure 3 also portrays that presidents moved from employing problem-constructions more consistently in the 1980s and 1990s, to a more diverse strategy in the 2000s and 2010s.
+The distances among the different constructions was never as small as in the 2010s.Again, considering the policies, this makes sense.
+During the same time that the policies which reduced deforestation drastically were adopted, the rural credit offered to agricultural producers in Amazonian states, went up from 500 million BRL per year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+The increase of the environmental conservation and social development problem-constructions, thus, never dominated discourse as clearly as economic integration did until the early 2000s.
+
+From the mid-2010s onwards, we observe a reversal of the identified trend: economic integration problem construction increases while conservation and social development constructions decrease again This is also aligned with the argument that Rousseff's administration changed its priorities.
+The 2012 Forest Code, which pardoned many deforesters, is an illustrative example of this change.
+The twist in this reversal is that sovereignty starts to increase steadily after 2010, and by 2019 sovereignty constructions surpass social development.
+While in the 1990s economic integration dominated solely, in the mid-2010s, problem constructions that highlight the Amazon as Brazilian increased.
+The reversal precedes the mandate of President Bolsonaro, but it was during his presidency that sovereignty constructions reached unprecedented levels since the establishment of Brazilian democracy.
 
@@
 
-Although presidents prefer pure problem-constructions, they also construct the Amazon as multifaceted issues.
-Mixed-type problem constructions in discourse offer more complex understandings of the Amazon as an issue.
+Although presidents prefer pure problem-constructions, they also construct the Amazon as multifaceted issues (see figure 1).
+Mixed-type problem constructions in discourse offer more complex understandings of the Amazon.
 Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
@@
 Figure 4, below, displays the yearly averages of mixed-types.
-
-```{r Figure x, echo=FALSE, fig.cap="Mixed-types by president", message=FALSE, warning=FALSE, paged.print=FALSE}
+While our analysis of mixed-types largely confirms the analysis of pure-types, it sheds lights in a few distinct trends and variations of specific presidents.
+
+```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
   filter(mx_cat2 == "Mixed-types") %>%
+  filter(mx_cat != "Other Mixed-types") %>%
   ggplot(aes(x = year, y = perc, color = mx_cat,
@@
 This mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
-
-(How do we interpret this increase?)
-
-The second most common mixed-type in time mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-Notoriously, Lula employs such a mix-type more frequently than all other presidents.
-In fact, both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
-
-(How do we interpret this increase?)
-
-While Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
+This is largely aligned with findings from figure 3, which showed the prevalence of economic integration and environmental conservation.
+It's increase in time might suggest presidents increasingly negate the dictum between the economy and the environment that prevailed in the previous years.
+The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
+This is not surprising, though.
+As developing countries like Brazil repeatedly claimed a "right to develop" when it came to negotiating strong climate commitments and policy, a focus on social development and economic integration is reflective of that.
+
+Both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
+Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue.
+Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
 Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region [@hecht1990].
 
-Generally, the increase of mixed-types makes sense given the rise of a global agenda understanding interconnections of social, environmental, and economic domains.
+Generally, the increase of mixed-types is expected given the rise of a global agenda understanding interconnections of social, environmental, and economic domains.
 As we show that Amazonian incidence in discourse does respond to global events as summits, this is not a surprise given agendas such as the Millennium Development Goals and the Sustainable Development Goals.
-
-Taken together, pure and mixed-types tell similar stories.
+In light of the events identified as drivers of higher frequencies of the Amazon as an overall topic (figure 2), the intensification of the UNFCCC process post-Copenhagen might explain the increase in sovereignty problem-constructions.
+Unexpectedly, the 1992 Earth Summit in Rio de Janeiro did not lead to an increase in environmental conservation overall.
+Thus, there is no clear correlation between events described in figure 2 and the frequencies of specific problem-constructions.
+Our analysis of pure-types and mixed-types also suggest that governments do not defend a single problem-construction for the Amazon.
+The same governments construct the Amazon as different issues in discourse, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
+It remains to be tested whether the variation in problem-construction correlates with the audience of speeches.
 
@@
 
-Problem constructions depend on where presidents speak.
-To facilitate analysis and make sense of locations, we divide locations into Amazonian states (i.e.
-all the Brazilian states in which the Amazon biome is present), non Amazonian states (other Brazilian states), Brasilia (the capital of Brazil where the federal government is located), Amazonian countries (neighboring countries where the biome is present), and international countries (countries outside of Brazil).
-To analyze the relationship between location and problem construction, we run a multinomial regression.
-Our dependent variable is problem-constructions (categorical), while our main independent variable is location (categorical).
-The reference category for the multinomial model is, thus, environmental conservation in international states.
-We control for deforestation rates (numerical), inflation (numerical), and election year.
-Since the model accounts for both mixed and pure-type Amazonian constructions, and this makes for a large table, we focus the analysis on pure-types to facilitate visualization (see full regression table in appendix).
-
-Figure 5, below, shows the percentage of problem-constructions by location derived from the regression model.
-The plot illustrates the percentage likelihood of constructing the Amazon as a certain issue according to location in relation to the reference category, environmental conservation internationally.
-From the figure we see, for example, that presidents are 29% more likely to construct the Amazon as an issue of economic integration within other Amazonian countries in comparison to other international settings.
-Although without the same strength, the finding also holds at the state level within Brazil as presidents are 11% more likely to construct the Amazon as an issue of economic integration within Amazonian states and 15% more likely in non Amazonian states.
-Interestingly, presidents are less likely to construct the Amazon as an issue of economic integration in Brasilia than internationally.
-That is, when speaking internationally or in Brasilia, presidents often construct the Amazon as an issue of environmental conservation.
+To test whether problem-constructions depend on where presidents speak, we run four separate logistic regressions and compare them.
+Each model takes the share of a specific problem-construction versus all other problem-constructions as their dependent variable.This means we try to predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
+Our main independent variable is the kilometer distance between where the speech took place, and the Amazon forest.
+The rationale behind this is that as we move further away from the region, audiences of the speech might have different interests on it.
+While speeches inside the Amazon might focus on social development, for example, speeches in the United Nations in New York might highlight environmental conservation.
+We control for deforestation rates (numerical), inflation (numerical), and election year (dummy).
+Since the model accounts for both mixed and pure-type Amazonian constructions, and this makes for a large table, we focus the analysis on pure-types to facilitate visualization.
 
 ```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
@@
          sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))
+
 # model
+
 model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
@@
                    family=binomial(link = "logit"), data = ama_model)
-# summary statistics, in appendix for now
-#stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov,
-#                     type = "text") # Negative for EI and SD
+
+# Plot model
+ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
+ama_model$"Economic Integration" = predict(model_logit_ei, ama_model, type = "response")
+ama_model$"Social Development" = predict(model_logit_sd, ama_model, type = "response")
+ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
+
+plot_loc <- ama_model %>% gather(key=p_c, value = pred, 21:23)
+
+plot_loc$p_c <-factor(plot_loc$p_c, levels =c("Economic Integration", "Environmental Conservation", "Social Development"))
+
+all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
+  geom_jitter(alpha=.2)+
+  geom_smooth(size = .5) +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  scale_y_continuous(labels = percent_format()) + 
+  labs(x = "Distance from the Amazon (km)",
+       y = "",
+       title = "Predicted share of each problem-construction as a function of distance from the Amazon",
+       subtitle="Sovereignty was removed because of statistical insignificance (table 2).", 
+       caption = "Curve in the plot is estimated using loess method.") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+          legend.position="bottom")
+
+all_loc
+
+```
+
+Table 2 presents the output of our four logistic regression models, and figure 5 depicts the predicted probabilities as functions of distance.
+We find a statistically significant relationship between constructing the Amazon as an issue of environmental conservation and distance from the Amazon: the farthest away the president is from the Amazon, the more likely the president is to state we need to conserve it.
+The opposite is true for economic integration and social development, with statistical significant negative relationships.
+This means that while speaking inside the Amazon, presidents focus more on social and economic development.In the case of sovereignty, though, there is no significant relationship present.This relationships also hold within Brazil: when speaking outside the Amazon but still inside Brazil, presidents forgo social and economic development in favor of conservation.
+
+Our models also suggest that deforestation plays an important role.
+When it comes to environmental conservation constructions, presidents are more likely to deploy this problem construction if deforestation decreases.
+Relatedly, when deforestation increases, economic integration problem constructions are more likely.
+This is largely aligned with @franchini2019 argument about mythological self-image, which states that Brazil creates an image of itself as strong climate leadership because of good results achieved from 2004 to 2012.
+On the other hand, the positive correlation between economic integration and deforestation, might relate to the problem-construction being employed as a justification for bad rates, as figure 3 also suggests.
+
+```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
+# summary statistics
+
+md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
+                         type = "text",
+                         digits = 10, 
+                         dep.var.labels = c("Conservation", "Economic Integration", "Social Development", "Sovereignty"),
+                         covariate.labels = c("Distance from the Amazon (km)", "Election year", "Yearly Deforestation", "Yearly   Inflation"),
+                         no.space = TRUE)
+
+```
+
+```{r regressions, eval=FALSE, include=FALSE}
+
+# single pc and loc
+
+env_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) +
+  geom_jitter(alpha=.2)+
+  geom_smooth(size = .5, color = "darkgreen") +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  scale_y_continuous(labels = percent_format()) + 
+  labs(x = "Distance from the Amazon (km)",
+       y = "",
+       title = "Probability of constructing the Amazon as an issue of environmental conservation",
+       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
+       caption = "Curve in the plot is smoothed using loess method.") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+
+ei_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_ei)) +
+  geom_jitter(alpha=.2)+
+  geom_smooth(size = .5, color = "red") +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  scale_y_continuous(labels = percent_format()) + 
+  labs(x = "Distance from the Amazon (km)",
+       y = "",
+       title = "Probability of constructing the Amazon as an issue of environmental conservation",
+       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
+       caption = "Curve in the plot is smoothed using loess method.") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+
+sd_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_sd)) +
+  geom_jitter(alpha=.2)+
+  geom_smooth(size = .5, color = "red") +
+  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
+                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  scale_y_continuous(labels = percent_format()) + 
+  labs(x = "Distance from the Amazon (km)",
+       y = "",
+       title = "Probability of constructing the Amazon as an issue of environmental conservation",
+       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
+       caption = "Curve in the plot is smoothed using loess method.") +
+    theme(panel.background = element_rect("white", "black", .5, "solid"),
+          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+          axis.text = element_text(color = "black", size = 10),
+          title = element_text(color = "black", size = 10, face = "bold"),
+          legend.title = element_blank(),
+          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
+
+# Negative for EI and SD
 # simple pooled OLS with time effects vs random effects
@@
 summary(random) # does not change when it comes independent variable
+
 # Colinearity test
 car::vif(model_logit_con) # All good!
-# Plot model
-ama_model$predicted_con = predict(model_logit_con, ama_model, type = "response")
-ama_model$predicted_ei = predict(model_logit_ei, ama_model, type = "response")
-ama_model$predicted_sd = predict(model_logit_sd, ama_model, type = "response")
-ama_model$predicted_sov = predict(model_logit_sov, ama_model, type = "response")
-
-# Environmental conservation and location
-
-env_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) +
-  geom_jitter(alpha=.5)+
-  geom_smooth(size = .5, color = "darkgreen") +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
-  labs(x = "Distance from the Amazon (km)",
-       y = "The Amazon as an issue of environmental conservation",
-       title = "Share of speeches that constructed the as an issue of pure environmental conservation\nin relation to distance from Manaus",
-       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
-       caption = "Curve in the plot is smoothed using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
-env_loc
-
-```
-
-```{r regressions, eval=FALSE, include=FALSE}
 
@@
 
-Along these lines, constructing the Amazon as an issue of social development takes place, overwhelmingly, within Brazil or other Amazonian countries.
-Presidents are at least 14% more likely to construct the Amazon as an issue of social development in these locations than internationally.
-The same is true for sovereignty, whereas constructing the Amazon as an issue of sovereignty takes place within Brazil or in neighboring Amazonian countries.
-Notice, as well, how Amazonian constructions within Amazonia states and non Amazonian states are strikingly similar.
-This indicates that presidents are consistent when constructing the Amazon locally across the federation, when outside of Brasilia.
-
 How the amazon is constructed as a problem varies across levels.
@@
 This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" could differ as well.
-The multi-level game entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not for local electorates.
-Local electorates who, ultimately, elect presidents.
-This multi-level game leads to different policies being negotiated, often simultaneously, so that the overlap at the interplay between the levels is maximized.
-Take, for once, how the Brazilian government successfully funded domestic public policy with international support since the 1990s (e.g.
-1992 Programa Piloto para Proteção das Florestas Tropicais), by creating a federal fund for the protected areas (e.g.
-2001 Amazon Region Protected Areas program), and by assuring international funds with the establishment of the Amazon Fund in 2008 which provided over USD 1 billion for environmental conservation in the Amazon [@silva-muller2022].
-Still, this does not mean, though, that the national agenda of economic integration or social development was not pursued.
+The multi-level game identified in this sub-section, entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not at the local level, where presidents highlight economic and social development.
+Overall, we interpret these results as evidence of maximizing political outcomes: boasting policy outside, while talking to people inside.
+
+# 5 Discussion and Conclusion
+
+In sum, this paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
+Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relates to policies and environmental outcomes.
+Empirically, we provide the first comprehensive overview of the Amazon in presidential discourse.
+Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
+the assassination of Chico Mendes) as well as international events (UNFCCC Summits).
+Second, the same government adopts a diverse range of problem-construction.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
+Hence, there is an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.Unprecedentedly, constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
+Finally, using a logit model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
+
+Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment, we believe our findings reveals important facets of Brazilian environmentalism along time.
+If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question becomes to what extent the implemented agenda responds to domestic versus international demands.
+In light of the multiple policies being negotiated simultaneously, economic and social development inside versus environmental conservation outside, is a strategy to maximize political outcomes.
+It convinces local electorates while it cashes in trasnational funds for policy.
+This can be exemplified by scrutinizing the outcomes of negotiations abroad.
+The Brazilian government successfully funded domestic public policy in several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Regional Protected Areas Program by the World Bank and others; and the 2008 Amazon Fund which provided over USD 1 billion for en [@silva-muller2022].
+Concurrently, the national agenda of economic integration or social development was pursued.
 During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-Nowadays, it has reached unprecedented levels.
-
-# 5 Discussion and Conclusion
-
-The Amazon frontier as an analytic category can help us shed light on the differences we identify between the discourse within Brazilian states and Amazonian countries compared to Brasilia or internationally.
-Whereas presidential discourses at the top matter to define and justify public policy [@zarefsky2004], presidents shape their discourses according to who their audience might be and what "they want to hear".
-If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question for democracy becomes to what extent the implemented agenda responds to domestic versus international demands.
-Or, as @putnam1988 puts it, what's the actual overlap between the international and domestic overlap.
-The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 happened concurrently with a period of strong economic growth and social development in Brazil and worldwide.
-With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s, we can interpret the fall of economic integration problem-construction and the rise of social and conservation constructions as a new balance between granting local livelihoods their rights and economic exploitation.
-
-While unprecedented, this new balance was not long-standing.
+
+The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 took place in a period of strong economic growth and social development in Brazil and worldwide.
+With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s (@hochstetler2007), we can interpret the fall of economic integration problem-construction and the rise of social and conservation constructions as a new balance between granting local livelihoods their rights and economic exploitation.
+This new balance was both unprecedented and not long-standing, as the dismantling of environmental policy in favor of infrastructure and agricultural expansion initiated in the 2010s.
+
 Democratic decay is slow, and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation-related statements in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.
+We observe the decrease in conservation problem-constructions in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.
+Bolsonaro is a response to political re-organization of national and international actors - to which Roussef and Temer were already responding in discourse- rather than the cause of change.
 As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as not only attacks to international interference in the Amazon but also on indigenous and traditional populations.
@@
 
-In sum, this paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these might relate to policies and environmental outcomes.
-Empirically, we provide the first comprehensive overview of the Amazon in presidential discourse.
-Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment, further research on the relationship between the social construction of the Amazon, one of the worlds most important standing ecosystems, and its effects on environmental outcomes is pressing.
+In light of these findings, we outline three avenues for future research.
+First, scholars should create more robust identification strategies to connect environmental discourse to actual environmental outcomes at the local level.
+While we hold that presidents are particular important, other actors as mayors and ministers could also be scrutinized.
+Second, research can expand to the realm of presidential speeches that take place outside official settings.
+Social media, specially in Brazil, has become crucial in communication between audiences as their leaders.
+Relatedly, social media complicates the boundaries between official and unofficial settings as presidents speaking in a particular location can be recorded and videos travel wide.
+Finally, qualitative researchers could unpack the ways through which the environment enter presidential speeches.
+Speech-writing is a process that includes more than one actor, and the decisions to speak or not about the environment are probably argued thoroughly.
 

### 2022-09-01 Draft_September_2022/Full_draft_20220901.rmd
#newfolder

--- 2022-08-26 Draft_June_2022/Full_draft_20220608.rmd
@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "8 June 2022"
+date: "1 September 2022"
 output:
+  pdf_document: default
+  fig_caption: yes
+  html_document:
+    df_print: paged
   word_document:
     reference_docx:
-  fig_caption: yes
-  pdf_document: default
-  html_document:
-    df_print: paged
 header-includes:
@@
   geom_line(color = "darkgreen") +
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
   scale_y_continuous(labels = percent_format()) + 
@@
 
+Amazon_year
+
 # location plots
@@
   geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
   geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
@@
   geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
-  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
   scale_y_continuous(labels = percent_format())+
@@
 
-grid.arrange(Amazon_year, arrangeGrob(Amazon_year_in, Amazon_year_out, ncol=2), nrow=2, top="Speeches mentioning the Amazon since 1985")
+grid.arrange(Amazon_year_in, Amazon_year_out, ncol=2, top="Speeches mentioning the Amazon since 1985")
 
@@
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
-  geom_jitter(alpha=.2)+
-  geom_smooth(size = .5) +
+  geom_jitter(alpha=.2, size=1)+
+  geom_smooth(size = .5, se=FALSE) +
   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
@@
 
-```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
@@
 md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
-                         type = "text",
+                         type = 'text',
                          digits = 10, 
@@
                 position= "center", font_size = 9, full_width = TRUE) %>%
-                footnote(general = c("The regression coefficients are displayed in log odds and standard errors are displayed in parentheses.",
-                "*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
+                footnote(general = c("*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
   column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%

### 2022-09-02 Draft_June_2022/Full_draft_20220608.rmd
#allfiguresandtablein #unnecessarycoderemoved #knittingtopdfwell

@@
 output:
+  pdf_document: default
+  fig_caption: yes
+  html_document:
+    df_print: paged
   word_document:
     reference_docx:
-  fig_caption: yes
-  pdf_document: default
-  html_document:
-    df_print: paged
 header-includes:
@@
   geom_line(color = "darkgreen") +
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
   scale_y_continuous(labels = percent_format()) + 
+  annotate("text", x = 1985, y = 0.16, label = "15.4%", size = 3.5)+
   annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
@@
   annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "Red Sky afternoon \n in Sao Paulo", size=3) +
+  annotate("text", x = 2019, y = 0.26, label = "August Fires", size=3) +
   labs(x = "", y = "",
-       subtitle = "All speeches inside and outside Brazil (n=6130)",
-       caption = "",
+       title = "Share of speeches that mention the Amazon per year (n=6130)",
+       subtitle = "We annotate five local maxima with highest frequencies.",
        color='Y series') +
@@
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
         legend.position = "bottom")
@@
   geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
-  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  annotate("text", x = 1985, y = 0.17, label = "16.17%", size = 3.5)+
   scale_y_continuous(labels = percent_format())+
   labs(x = "", y = "",
-       subtitle = "Speeches in Brazil (n=4344)",
-       caption= " ",
+       title = "Share of speeches inside Brazil that mention the Amazon per year",
+       subtitle= " 4344 speeches out of 6130",
        color='Y series') +
@@
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
         legend.position = "")
@@
   geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5)+
-  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  annotate("text", x = 1985, y = 0.165, label = "15.49%", size = 3.5)+  
   scale_y_continuous(labels = percent_format())+
   labs(x = "", y = "",
-       subtitle = "Speeches outside of Brazil (n=1786)",
-       caption= "Black lines portray the means.",
+ title = "Share of speeches outside Brazil that mention the Amazon per year",
+       subtitle= " 1786 speeches out of 6130",
        color='Y series') +
@@
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
-  geom_jitter(alpha=.2)+
-  geom_smooth(size = .5) +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  geom_jitter(alpha=1, size=1)+
+  geom_smooth(size = .5, se=FALSE) +
+  geom_vline(xintercept = c(1933.78, 2771.49, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76), y = c(0.5,0.55,0.5,0.55),
+                    label = c("Brasilia","Rio de Janeiro\nSão Paulo", "New York", "Paris"), alpha = 0.4) +
   scale_y_continuous(labels = percent_format()) + 

### 2022-09-02 Draft_September_2022/Full_draft_20220901.rmd
#allfiguresandtablein #unnecessarycoderemoved #knittingtopdfwell

@@
 library(gridExtra)
+
 Sys.setlocale("LC_ALL", "C")
@@
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
+
 # Missing year data
+
 amazon_def_year <- rbind(adr, amazon_def_year) 
@@
                            "Rousseff", "Temer", "Bolsonaro"))
+
+amazon_def_year$area <- amazon_def_year$def_year*1000
+
 # Prepare data for problem constructions
@@
   replace(is.na(.), 0)
+
 # Get mixed types in
@@
                                           "Non Amazonian States")))
-# # Table of Amazonian speeches internationally vs. in Brazil
-# amazon_in_out <- pop %>% select(amazon_speech, location_cat)
-# table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
-# amazon_in_out <- mutate(amazon_in_out,
-#                         location_cat = ifelse(grepl("International|Non Identified",
-#                                               location_cat), 0, 1))
-# amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
-# rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
-# colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
-# amazon_in_out
-
-amazon_in_out <- pop %>% select(amazon_speech, location_cat)
-table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
-amazon_in_out <- mutate(amazon_in_out,
-                         location_cat = ifelse(grepl("International", location_cat), 0, 1))
-amazon_in_out <- table(amazon_in_out$amazon_speech, amazon_in_out$location_cat)
-rownames(amazon_in_out) <- c("Not Amazon Speech", "Amazon Speech")
-colnames(amazon_in_out) <- c("Outside of Brazil", "Within Brazil")
-amazon_in_out
+
 ```
@@
 
-```{r Figure 2, fig.cap="Amazonian speeches by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+```{r Figure 2, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 
@@
   select(c(perc, amazon_speech, year))
+
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  scale_y_continuous(labels = percent_format()) + 
+  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.26, label = "August Fires", size=3) +
+  labs(x = "", y = "",
+       title = "Share of speeches that mention the Amazon per year (n=6130)",
+       subtitle = "We annotate five local maxima with highest frequencies.",
+       color='Y series') +
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "bottom")
+Amazon_year
+
+```
+
+In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
+The 1992 Earth Summit in Brazil brought international attention to environmental topics related to the Amazon.
+One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].Throughout the rest of 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average.
+In 2009 we see another spike in the Amazon appearing in official speeches.
+This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
+
+From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
+From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
+Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
+In 2011, the New Forest Code, which regularized land ownership of many illegally deforested areas, was also approved.
+These are also the years when Brazil entered a long period of political and economic instability, which eventually led to the impeachment of Dilma Roussef.
+Though, in 2015, the Amazon appeared in 19% of speeches.
+This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
+Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
+By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
+
+```{r Figure 3, fig.cap="Amazonian speeches in time and space", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
 
@@
 
-# Plot with All
-
-Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(color = "darkgreen") +
+# location plots
+Amazon_year_in <- perc_in %>%
+  ggplot(., aes(x = year, y = perc))+
+  geom_line(color="darkgreen")+
   geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  scale_y_continuous(labels = percent_format()) + 
-  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "Red Sky afternoon \n in Sao Paulo", size=3) +
+  annotate("text", x = 1985, y = 0.17, label = "16.17%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.35, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.35, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.23, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.20, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.25, label = "August Fires", size=3) +
+  scale_y_continuous(labels = percent_format())+
   labs(x = "", y = "",
-       subtitle = "All speeches inside and outside Brazil (n=6130)",
-       caption = "",
+       title = "Share of speeches inside Brazil",
+       subtitle= " 4344 speeches out of 6130",
        color='Y series') +
@@
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
-        legend.position = "bottom")
-
-Amazon_year
-
-# location plots
-Amazon_year_in <- perc_in %>%
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "")
+
+Amazon_year_out <- perc_out %>% 
   ggplot(., aes(x = year, y = perc))+
   geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
-  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  annotate("text", x = 1985, y = 0.165, label = "15.49%", size = 3.5)+  
+  annotate("text", x = 1988.7, y = 0.33, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.33, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.25, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.19, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.24, label = "August Fires", size=3) +
   scale_y_continuous(labels = percent_format())+
   labs(x = "", y = "",
-       subtitle = "Speeches in Brazil (n=4344)",
-       caption= " ",
+ title = "Share of speeches outside Brazil",
+       subtitle= " 1786 speeches out of 6130",
        color='Y series') +
@@
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
         legend.position = "")
 
-Amazon_year_out <- perc_out %>% 
-  ggplot(., aes(x = year, y = perc))+
-  geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype= "dotted")+
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "",
-       subtitle = "Speeches outside of Brazil (n=1786)",
-       caption= "Black lines portray the means.",
-       color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
-        legend.position = "")
-
-grid.arrange(Amazon_year_in, Amazon_year_out, ncol=2, top="Speeches mentioning the Amazon since 1985")
-
-```
-
-```{r comparison, eval=FALSE, include=FALSE}
-
-# # comparison with inequality, crime and inflation in speeches
-# pop <- pop %>%
-#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
-#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
-#                               text, ignore.case = TRUE), 1, 0),
-#          inf = ifelse(grepl("inflacao|inflaçao",
-#                              text, ignore.case = TRUE), 1, 0),
-#          unemploy = ifelse(grepl("desempreg",
-#                              text, ignore.case = TRUE), 1, 0))
-# perc2 <- pop %>%
-#   count(desigual, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(desigual == 1) %>%
-#   select(c(perc, desigual, year))
-# perc3 <- pop %>%
-#   count(crime, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(crime == 1) %>%
-#   select(c(perc, crime, year))
-# perc4 <- pop %>%
-#   count(inf, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(inf == 1) %>%
-#   select(c(perc, inf, year))
-# perc5 <- pop %>%
-#   count(unemploy, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(unemploy == 1) %>%
-#   select(c(perc, unemploy, year))
-# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
-#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
-#             "Unemployment Speech" = "purple")
-# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(aes(color = "Amazon Speech")) +
-#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
-#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
-#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
-#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
-#   scale_y_continuous(labels = percent_format()) +
-#   scale_color_manual(values = colors) +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
-#        caption = "",
-#        color = "Legend\n") +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# Amazon_vs_other
-# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
-#                                                            "Criminality", "Inflation",
-#                                                            "Unemployment"),
-#                                        "Mean share in time" = c(mean(perc1$perc),
-#                                                                 mean(perc2$perc),
-#                                                                 mean(perc3$perc),
-#                                                                 mean(perc4$perc),
-#                                                                 mean(perc5$perc)))
-# Amazon_vs_other_mean
-# #comparison with inequality, crime and inflation in speeches
-# pop <- pop %>%
-#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
-#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
-#                               text, ignore.case = TRUE), 1, 0),
-#          inf = ifelse(grepl("inflacao|inflaçao",
-#                              text, ignore.case = TRUE), 1, 0),
-#          unemploy = ifelse(grepl("desempreg",
-#                              text, ignore.case = TRUE), 1, 0))
-# perc2 <- pop %>%
-#   count(desigual, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(desigual == 1) %>%
-#   select(c(perc, desigual, year))
-# perc3 <- pop %>%
-#   count(crime, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(crime == 1) %>%
-#   select(c(perc, crime, year))
-# perc4 <- pop %>%
-#   count(inf, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(inf == 1) %>%
-#   select(c(perc, inf, year))
-# perc5 <- pop %>%
-#   count(unemploy, year) %>%
-#   group_by(year) %>%
-#   mutate(perc=n / sum(n)) %>%
-#   filter(unemploy == 1) %>%
-#   select(c(perc, unemploy, year))
-# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
-#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
-#             "Unemployment Speech" = "purple")
-# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-#   geom_line(aes(color = "Amazon Speech")) +
-#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
-#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
-#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
-#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
-#   scale_y_continuous(labels = percent_format()) +
-#   scale_color_manual(values = colors) +
-#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
-#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
-#        caption = "",
-#        color = "Legend\n") +
-#   theme(panel.background = element_rect("white", "black", .5, "solid"),
-#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#         axis.text = element_text(color = "black", size = 10),
-#         title = element_text(color = "black", size = 10, face = "bold"),
-#         legend.title = element_blank(),
-#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-#         legend.position = "bottom")
-# Amazon_vs_other
-# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
-#                                                            "Criminality", "Inflation",
-#                                                            "Unemployment"),
-#                                        "Mean share in time" = c(mean(perc1$perc),
-#                                                                 mean(perc2$perc),
-#                                                                 mean(perc3$perc),
-#                                                                 mean(perc4$perc),
-#                                                                 mean(perc5$perc)))
-# Amazon_vs_other_mean
-
-```
-
-In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
-The 1992 Earth Summit in Brazil brought international attention to environmental topics related to the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].Throughout the rest of 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average.
-In 2009 we see another spike in the Amazon appearing in official speeches.
-This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
-
-From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
-In 2011, the New Forest Code, which regularized land ownership of many illegally deforested areas, was also approved.
-These are also the years when Brazil entered a long period of political and economic instability, which eventually led to the impeachment of Dilma Roussef.
-Though, in 2015, the Amazon appeared in 19% of speeches.
-This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
-By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
+grid.arrange(Amazon_year_in, Amazon_year_out, nrow=2)
+
+```
 
@@
 
-```{r Figure 3, fig.cap="Pure types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 4, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
 mmt1 <- ama_mx %>%
@@
   mutate(perc = n / sum(n)) # averages in relation to full sample
+
 pure_types_time <- ama_mx %>%
@@
   ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size =1, linetype="solid") +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure-type problem-construc by year",
+  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
        subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
@@
         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom") +
-  ggplot2::annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.40,
-           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
-                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
-           alpha = 0.1) +
-  ggplot2::annotate(geom = "text", x = hp$label, y = 0.01, vjust = 0.3, hjust = 0.3, angle = 25,
-           label = hp$presid, alpha = 0.4)
-
+        legend.position = "bottom")
 pure_types_time
+
 ```
@@
 
+```{r Figure 5, fig.cap="Deforestation rates since 1988", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
+def_rates <- ggplot(amazon_def_year, aes(x = year)) +
+  geom_line(aes(y = area), color= "darkolivegreen", linetype="dotted", size= 1.5)+
+  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.75)+
+  annotate("text", x = 2004, y = 29000, label = "2004 Plan to Combat\nand Control Deforestation", size = 4.5) +
+  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 4.5) +
+  labs(x = "",
+     y = "Deforestation in squared kilometers",
+     title = "Deforestation rates since 1988",
+     subtitle= "Data from INPE, Brazilian Ministry of Science and Technology.",
+     color = "",
+     caption= "Black curve smoothed using loess.")+
+  theme(panel.background = element_rect("white", "black", .5, "solid"),
+        panel.grid.major = element_line(color = "grey", size = 0.2, linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "none")
+
+def_rates
+
+```
+
 A possible explanation for this can be found in the logic of the policies adopted.
@@
 
-```{r Figure 4, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 6, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
 
-```{r test, eval=FALSE, fig.cap="Mixed-types by year", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-
-mixed_types_year <- ama_mx %>%
-  count(year, mx_cat, mx_cat2) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  filter(mx_cat != "Other Mixed-types") %>%
-  ggplot(aes(x = year, y = perc, color = mx_cat,
-             label = scales::percent(perc, accuracy=.1))) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size = .5) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by year",
-       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "")+
-    facet_wrap(~mx_cat)
-
-mixed_types_year
-
-```
-
 The most frequent mixed-type problem construction of the Amazon in time is economic conservation, which has increased slightly in time.
@@
 
-```{r Figure 5, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 7, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 
@@
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
-  geom_jitter(alpha=.2, size=1)+
+  geom_jitter(alpha=1, size=1)+
   geom_smooth(size = .5, se=FALSE) +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
+  geom_vline(xintercept = c(1933.78, 2771.49, 5075.48, 8306.76), linetype = "dotted") +
+  ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76), y = c(0.5,0.55,0.5,0.55),
+                    label = c("Brasilia","Sao Paulo", "New York", "Paris"), alpha = 0.4) +
   scale_y_continuous(labels = percent_format()) + 
@@
        title = "Predicted share of each problem-construction as a function of distance from the Amazon",
-       subtitle="Sovereignty was removed because of statistical insignificance (table 2).", 
+       subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
        caption = "Curve in the plot is estimated using loess method.") +
@@
 
-```{r Table 2, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+\begin{landscape}
+```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
@@
 md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
-                         type = 'text',
                          digits = 10, 
@@
 
-```{r regressions, eval=FALSE, include=FALSE}
-
-# single pc and loc
-
-env_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) +
-  geom_jitter(alpha=.2)+
-  geom_smooth(size = .5, color = "darkgreen") +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
-  scale_y_continuous(labels = percent_format()) + 
-  labs(x = "Distance from the Amazon (km)",
-       y = "",
-       title = "Probability of constructing the Amazon as an issue of environmental conservation",
-       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
-       caption = "Curve in the plot is smoothed using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
-ei_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_ei)) +
-  geom_jitter(alpha=.2)+
-  geom_smooth(size = .5, color = "red") +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
-  scale_y_continuous(labels = percent_format()) + 
-  labs(x = "Distance from the Amazon (km)",
-       y = "",
-       title = "Probability of constructing the Amazon as an issue of environmental conservation",
-       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
-       caption = "Curve in the plot is smoothed using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
-sd_loc <- ggplot(ama_model, aes(x = km_to_manaus, y = predicted_sd)) +
-  geom_jitter(alpha=.2)+
-  geom_smooth(size = .5, color = "red") +
-  geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.5,
-                    label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
-  scale_y_continuous(labels = percent_format()) + 
-  labs(x = "Distance from the Amazon (km)",
-       y = "",
-       title = "Probability of constructing the Amazon as an issue of environmental conservation",
-       subtitle = "If outside of the Amazon, distance measured as a straight line from state or country's capital to Manaus in kilometers",
-       caption = "Curve in the plot is smoothed using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
-# Negative for EI and SD
-# simple pooled OLS with time effects vs random effects
-ols <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                data = ama_model, model = "pooling", index = c("year"))
-random <- plm::plm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                   data = ama_model, model = "random", index = c("year"))
-summary(ols)
-summary(random) # does not change when it comes independent variable
-
-# Colinearity test
-car::vif(model_logit_con) # All good!
-
-# ama_model_all <- ama_model %>% rename("Environmental Conservation" = predicted_con,
-#          "Economic Integration" = predicted_ei,
-#          "Social development" = predicted_sd,
-#          "National Sovereignty" = predicted_sov) %>% 
-#   pivot_longer('Environmental Conservation':'National Sovereignty',
-#                names_to = "Construction", values_to = "Share") %>% 
-#   ggplot(ama_model_all, aes(x = km_to_manaus, y = Share, color = Construction)) +
-#   geom_smooth(size = .5) + pivot_longer(predicted_con:predicted_sov, names_to = "variable", values_to = "value")
-# 
-# ggplot(ama_model_all, aes(x = km_to_manaus, y = value, color = variable)) +
-#   geom_smooth(se = FALSE, size = .5)
-# ggplot(ama_model, aes(x = km_to_manaus, y = predicted_con)) + 
-#   geom_jitter(alpha=.5)+
-#   geom_smooth(size = .5, color = "darkgreen") +
-#   geom_vline(xintercept = c(1933.78, 5075.48, 8306.76), linetype = "dotted") +
-#   ggplot2::annotate(geom = "text", x = c(1933.78, 5075.48, 8306.76), y = 0.4,
-#                     label = c("Brasilia", "New York", "Paris"), alpha = 0.4) +
-#   labs(x = "Distance from the Amazon (km)",
-#        y = "Share of problem construction",
-#        title = "How is the Amazon constructed as an issue across locations?",
-#        subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
-#        caption = "Curve in the plot is smoothed using loess method.") +
-#     theme(panel.background = element_rect("white", "black", .5, "solid"),
-#           panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-#           axis.text = element_text(color = "black", size = 10),
-#           title = element_text(color = "black", size = 10, face = "bold"),
-#           legend.title = element_blank(),
-#           plot.subtitle = element_text(color = "black", size = 9, face = "plain"))
-
-```
-
+\end{landscape}
 How the amazon is constructed as a problem varies across levels.
@@
 
-````{=tex}
-\begin{landscape}
-
-```{r full regression results, fig.cap="Multinomial Regression Results", echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
-
-model_comp <- tibble::tibble("Dependent Variable" = c("Environmental Conservation", 
-"Economic Integration", "Social Development", "National Sovereignty"),
-"Distance to Manaus(km)" = c("0.0001*** (0.00002)", "-0.0001** (0.00002)", "-0.0001** (0.00004)", "0.00001 (0.00002)"),
-"Election Year" = c("0.288* (0.157)", "-0.022 (0.133)", "0.329* (0.171)", "-0.449* (0.269)"),
-"Deforestation Year" = c("-0.032*** (0.011)", "0.041*** (0.008)", "-0.072*** (0.013)", "-0.032* (0.017)"),
-"Annual Average Inflation" = c("0.0004*** (0.0001)", "-0.0002** (0.0001)", "-0.0002 (0.0002)", "0.0002 (0.0002)"),
-"Constant" = c("-1.718*** (0.191)", "-1.569*** (0.160)", "-0.910*** (0.214)", "-2.301*** (0.289)"))
-kbl(t(model_comp), booktabs = T,caption = "Logistic Regression Models Compared", align = "c") %>%
-  kable_styling(latex_options = c("striped", "scale_down"),
-                position= "center", font_size = 9, full_width = TRUE) %>%
-                footnote(general = c("*** for p-value < 0.01, ** for p-value < 0.05, * for p-value < 0.1")) %>% 
-  column_spec(1, width="3 cm", bold=TRUE, latex_valign = "m") %>%
-  column_spec(2, width="2 cm", latex_valign = "m") %>%
-  column_spec(3, width = "2 cm", latex_valign = "m") %>%
-  column_spec(4, width = "2 cm", latex_valign = "m") %>%
-  column_spec(5, width="2 cm", latex_valign = "m")
-```
-
-\end{landscape}
-````
-
 # References

### 2022-09-02 Draft_September_2022/Full_draft_20220901.rmd
Updated text for new changes

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches in transnational politics since 1985
+title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985 in Brazil
 author:
 - Livio Silva-Muller
-- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically.
+- Henrique Sposito^[Both co-authors contributed equally to the article.
+Names are ordered alphabetically.
 Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Institute and affiliated to the Albert Hirschman Centre on Democracy.
@@
   pdf_document: default
+  latex_engine: xelatex
   fig_caption: yes
@@
     df_print: paged
-  word_document:
-    reference_docx:
+fontsize: 12pt
+mainfont: Times New Roman
 header-includes:
@@
    - \floatsetup[figure]{capposition=top}
+   - \usepackage{float}
+   - \floatplacement{figure}{H}
+   - \usepackage[T1]{fontenc}
+   - \usepackage[utf8]{inputenc}
+   - |
+    ```{=latex}
+    \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
+    \providecommand{\wordcount}[1]{\text{Word Count:}#1} 
+    ```
 always_allow_html: TRUE
@@
 csl: chicago.csl
-abstract: Presidential speeches legitimize ways of thinking about the environment transnationally, while affecting decisions at the local level.Albeit the importance of understanding the relationship between the social construction of the environment and its effects on environmental outcomes, research on presidential discourse is scarce.
-We lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
-Building on @hirschman1963 and @bacchi2009 conceptualization of chosen problems, we propose a framework to investigate how heads of government construct the environment in transnational political discourse.
-Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in all 6130 official presidential speeches since 1985.
-We interpret our findings in light of policies adopted and important events.
-First, we find national and international events drive the frequency of the Amazon as a topic in presidential speeches equally inside and outside Brazil.
-Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty also became more pertinent after 2010.
-Finally, we find that the farthest presidents are from the Amazon, the more likely they are to state the Amazon needs to be preserved.
-Conceptually, we argue that these are evidence of presidents maximizing contradictory political outcomes domestically and internationally.
+abstract: Presidential speeches influence the ways we think about, and act towards, the environment transnationally.
+Still, these remain understudied in this context.
+We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses along time and space.
+Using supervised machine learning, we classify statements about the Amazon in 6130 presidential speeches since 1985.
+We find that national and international events drive the frequency of the Amazon as a topic in presidential speeches inside and outside Brazil.
+While constructing the Amazon a problem of economic integration dominates discourses until the mid-2000s, environmental conservation and social development constructions increase in relevance and temporarily surpass economic integration from 2010 to 2015.
+In turn, constructing the Amazon as an issue of sovereignty steadily increases since 2010.
+Lastly, the farthest presidents are from the Amazon, the more likely they are to construct the Amazon as an issue of environmental conservation.
 ---
+
+```{=latex}
+\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, and deforestation}
+```
+
+```{=latex}
+\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
+```
 
@@
 library(gridExtra)
-
 Sys.setlocale("LC_ALL", "C")
@@
 # Load data
-##### We are missing many observations for Collor from late 1991 and 1992...
-##### These are not in the repository for some reason, this is an issue not on our side.
-##### We should we at least disclose these in a footnote.
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
@@
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-
 # Missing year data
-
 amazon_def_year <- rbind(adr, amazon_def_year) 
@@
                            "Rousseff", "Temer", "Bolsonaro"))
-
 amazon_def_year$area <- amazon_def_year$def_year*1000
-
 # Prepare data for problem constructions
@@
   replace(is.na(.), 0)
-
 # Get mixed types in
@@
                                          mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation", "Pure Social Development",
+         levels = c("Pure Economic Integration", "Pure Conservation",
+                    "Pure Social Development",
                     "Pure Sovereignty", "Other", "Economic Conservation", 
@@
 
+```{r theme, include=FALSE, warning=FALSE, message=FALSE}
+# custom ploting theme for all plots
+theme_am <- function(x) {
+  theme(text = element_text(size=12,  family="Times"),
+        panel.background = element_rect("white", "black", .5, "solid"),
+                  panel.grid.major = element_line(color = "grey", size = 0.2,
+                                                  linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "none")
+}
+```
+
 \pagebreak
@@
 We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon's natural resources.
+We need to exploit the Amazon’s natural resources.
 We need to provide better living standards for the people in the Amazon.
 We need to preserve the Amazon as a standing ecosystem.
-Historically, the Brazilian government approached the Amazon region, forest and its people as a policy object.
-Different governmental programs contain an assumptions of what has to be solved in the Amazon, or in other words, it represents the Amazon, implicitly or explicitly, as a particular problem.
-These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country as, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
+Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
+These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
 
-Different governments along Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship is associated with both national sovereignty and then economic integration, Sarney's and Lula's presidencies are often tied to environmental conservation.
-This monolithic representation advances a view that specific governments see the Amazon as an instance of one specific problem, hiding within government diversity of both policies and perspectives.
+Different governments throughout Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
+While the military dictatorship is associated with understanding the Amazona as issues of national sovereignty and economic integration, Sarney’s and Lula’s presidencies are often tied to environmental conservation views.
+These monolithic representations advance that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
 Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
+Building on @hirschman1963 conceptualization of chosen problems and @bacchi2009 theory of problem-representation in policy, we propose a framework for identifying problem-constructions in discourse and investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
+We understand transnationalism^[ We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998]
 
-In this article, we investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
-Building on @hirschman1963 concept of chosen problems and @bacchi2009 concept of problem-representation in policy, we propose a framework to identify problem-constructions.
 Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Importantly, scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy[@abers2019, @silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets[@rajão2020, @assuncao2015], and many others.
-Nevertheless, the role of president remains understudied.
-
+Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015], and many others.
+Nevertheless, the role of the president remains understudied.
 We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
+First, presidential discourses have the power to introduce and justify the public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
 It legitimizes ways of thinking about the Amazon.
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest at the ground [@campbell2015].
-Second, we argue that presidents can employ specific problem-constructions that build objects as specific problems depending on who they speak to.
-Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a keynote speech in a business association in São Paulo or at the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is socially constructed in trasnational politics.
+This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest on the ground [@campbell2015].
+Second, we argue that presidents can deploy problem-constructions that build policy objects as different problems depending on whom they are speaking to.
+Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a speech at the UN general assembly in New York.
+Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is discursively constructed in transnational politics.
 
 To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazonian related statements within these speeches.
+We subset the dataset by identifying Amazonian-related statements within these speeches.
 We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs the Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of the Amazonian related statements.
-We train a supervised machine-learning model in the hand-coded set and automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data, tying patterns in the data to Amazonian policies and deforestation outcomes along time.
+We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
+We use this codebook to manually code a randomly selected training set of Amazonian-related statements.
+We train a supervised machine-learning model to automatically label the remaining set of Amazonian statements.
+We then conduct a descriptive and inferential analysis of this data, tying patterns in the data to Amazonian policies and deforestation outcomes over time.
 
@@
 the assassination of Chico Mendes) as well as international events (UNFCCC Summits).
-Second, the same government adopts a diverse range of problem-constructions along time.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
-Hence, there is an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.
-In turn, constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
-Finally, using a logit model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.Conceptually, we interpret this findings as evidence of presidents maximizing political outcomes in contradictory ways: talking to people domestically, boasting environmental policy internationally.
+Second, the same government adopts a diverse range of problem-constructions over time.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2011 to 2016.
+Constructing the Amazon as an issue of sovereignty has increasingly become more pertinent after 2010.
+Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move away from the Amazon region.
+That is, presidents, talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.
 
@@
 In the methodology section, we explain how the framework is operationalized and present the codebook.
-We proceed to describe, visualize and interpret our findings in the analysis section.
-Finally, we conclude with a discussion connecting our findings to to Brazilian environmentalism.
+We proceed to describe, visualize, and interpret our findings in the analysis section.
+Finally, we conclude with a discussion connecting our findings to past and present environmental policies.
 
@@
 
-We start this section by building our conceptual framework based on existing literature. We then moved to the specific problem-constructions that are embedded in Amazonian historiography.
+## 2.1 Chosen problems, presidential discourses, and policy objects
 
-## 2.1 Chosen problems, presidential discourse, and policy objects
-
-Governments have a choice in how they construct problems and what policy solutions they implement.
-In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured from outside parties to the government) and chosen problems (chosen by the government at their own discretion).
+In “Journey towards Progress”, @hirschman1963 draws a conceptual distinction between pressing problems (pressured by outside parties to the government) and chosen problems (chosen by the government at their discretion).
 Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
 Chosen problems are those governments select at their discretion.
-Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change of level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
+Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
+The author exemplifies chosen problems with the case of the construction of Brasilia.
 
-On the other hand, @bacchi2009 [p.
-10] argues that policies have a cultural dimension as "it takes shape within specific historical and national or international contexts".
-The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
+@bacchi2009 [p.
+10] argues that policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
+The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed, this is a policy object.
+We conceptualize policy objects as a problem that demands dedicated policy attention.
 The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.
-Coming back to @hirschman1975 [p.
-388], the author exemplifies chosen problems with the case of the construction of Brasilia.
-Nevertheless, building Brasilia (the policy) could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three depending on how governments speak about it.
-We argue that it is up to the discretion of the government to highlight or not the implicit problem a policy solves.
-A same policy object (e.g.
-Brasilia, the Amazon, criminality, poverty), thus, can be constructed as pressing or not depending on how a government represents it.
-Policies are socially constructed in governmental discourse.
+Building Brasilia (the policy object), thus, could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three depending on how governments speak about it.
 
-What drives governmental choices of which underlying problem should be highlighted?
 Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-Relative to how the policy is represented to be, it can be a solution of problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
+Relative to how the policy is represented to be, it can be a solution to problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
 @putnam1988 seminal article on the two-level game can help us make sense of this variation conceptually.
 The author argues that the outcomes of international negotiations lie within the overlap between the agenda (and pressure) of domestic groups and international groups.
-If policies are socially constructed, and consequently their implicit problem can vary, governments can in theory constructed it to meet the expectations of both.
-Taking the example of the 2012 Forest Code and the Amazon, policy-makers could emphasize its rural character for environmentalists at the Paris Summit, or the amnesty for deforestation for agricultural elites.
-The same policy, then, can solve the problem of environmental conservation as well as economic integration.
+If policies are socially constructed, and consequently their implicit problem can vary, governments can in theory construct them to meet the expectations of both.
+Consequently, this entails that governments are more diverse in their opinions, rather than monolithic.
 
-This variation in problem-construction entails that governments are more diverse in their positions than the literature suggests.
-We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-Several scholars describe federal governments' as proponents of specific policies for the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-In this literature, the 1964 military dictatorship is associated with securing national sovereignty in the region by populating it and integrating it to the national economy [@drummond2006].
-The governments from the late 1980s up to 2009, are more associated with environmental conservation.
-The presidencies of Dilma and Temer are connected to the decline of environmental policies, while Bolsonaro to the complete dismantling of environmental policies.
-While these works are important to understand how different governments acted towards the Amazon, the classification of specific governments into periods or policy cycles represents them as monolithic: they associate specific governments to one specific view of the Amazon.
-The presidency of Lula, often associated with environmental conservation because of the unprecedented decrease in deforestation.
-Nevertheless, during his terms governmental credits to agricultural expansion and the cattle industry were 20 times more than the budget of the Ministry of the Environment for this entire period [@capobianco2021, p.
-106].
-That is, there is more variation within governments than the literature suggests.
+An interesting site to study the relationship between problem-construction and policy objects is presidential speeches, as they legitimize ways of thinking about an issue.
+While the relationship between presidential speeches and policy may not be causal, they have the power to introduce and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004; @gillion2016].
+As presidents speak across several locations to various audiences, they frame similar issues differently.
 
-An interesting site to study the relationship between varied problem-construction and policy objects is presidential speeches as they legitimize ways of thinking about an issue.
-While the relationship between presidential speeches and policy is not causal, they have the power to introduce and justify public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
-Even if presidential discourse might not persuade public opinion regarding a proposed solution for a problem [@eshbaugh2010; @rottinghaus2009; @krebs2007], they direct the range of what is included in national debates [@druckman2004].
-As presidents speak in varied locations to varied audiences, it is very likely that they chose to frame similar issues differently.
-
-The possibility of different problem-constructions at the level of presidential speeches has important implications for democracy.
-With globalization and the increase of transnational processes, presidents have the opportunity of promoting different problem-constructions trasnnationally.
-It is important to understand, thus, to what extent the implemented agenda correlates with their local, federal, or international problem-constructions.
-Relatedly, the possibility of different problem-constructions has consequences for environmental outcomes as well.
-When Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of many actors involved in the Amazon.
-Deforestation rates in Brazil are more responsive to the government's environmental policy, generated from material and discursive governmental practices, than exogenous factors as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Specifically, Capobianco finds that that the perception of higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective (2021).
-Relatedly, ethnographic research has also shown that expectations about governments' response are a crucial factor in decisions to deforest at the ground [@campbell2015].
-Thus, understanding diversity in presidential speeches is a first step to connect it to concrete environmental outcomes.
+The possibility of different problem-constructions in presidential speeches has important implications for democracy.
+With globalization and the increase of transnational processes, presidents have the opportunity of promoting different problem-constructions transnationally.
+It is important to understand, thus, to what extent the implemented policy agenda correlates with problem-constructions promoted at the local, federal, or international levels.
+Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
+Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices than exogenous factors such as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
+Specifically, @capobianco2021 finds that the perception of a higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
+Furthermore, ethnographic research has also shown that expectations about governments’ responses are a crucial factor in decisions to deforest on the ground [@campbell2015].
+Understanding variation in presidential speeches is the first step to connecting it to concrete environmental outcomes.
 
 The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
-Among various findings, one that stands out is that American presidents frequently side-step the environmental aspects of climate change.
-He also identifies a shift from economic to security framing of climate issues, side-lining its environmental aspects.
-@calderwood2020 also tests the effect of geographic location and type of communication regarding climate change.
-Building prominently on @putnam1988, he demonstrates that presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-Elsewhere, @bevitori2015 investigates how the 'environment' has been constructed in American presidential discourse since 1960 using a more automated approach.
-The author finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
-These studies corroborate the possibilities of variation depending on the audience, but we are yet to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
-While these findings are US specific, they indicate that presidents raise different points about the environment at local, national, or international settings, depending on who they assume their audience is at that specific instance.
-Nevertheless, as @bacchi2009, we argue that problem-constructions touch on shared meanings about the region that are available to the speaker as part of larger social-cultural history.
-Mentions to the lexicon as 'environment', 'preserve', or 'climate change' should be tied to the larger meaning of policies in the United States and elsewhere.
+[@calderwood2019], for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
+Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change, even as frames move from focusing on economics to focusing on security aspects of climate change.
+Building on @putnam1988, @calderwood2020 demonstrates that American presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
+Elsewhere, @bevitori2015 finds that mentions of the environment are typically co-selected with the pronoun ‘our’, as well as with ‘economy’, ‘clean’, and ‘preserve’.
+While these studies corroborate the possibilities of variation depending on the audience, they fail to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
+That is, problem-constructions touch on shared meanings available to both the speaker and the audiences as part of larger social-cultural history [see @bacchi2009], therefore, mentions to the lexicon as ‘environment’, ‘preserve’, or ‘climate change should be tied to the larger meaning of policies in the United States.
 
-On the other hand, there is also an empirical gap in terms of how the Amazon has been constructed as a problem along time and geographic location.
-While governmental discourses in Brazil have been studied for topics such as inflation or race relations[@malheiros1995, @htun2004, @silva2019], we only find one systematic analysis of Amazonian discourse.
-@barros2020 investigates Amazonian discourse in the Brazilian Congress with the objective of identifying the arguments put forth by congressmen.
-The main finding is that the economic value of the Amazon for the cattle industry is the most salient narrative, leading the author to conclude there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-We also find one analysis of Bolsonaro's rhetoric about the Amazon, but the study relies on a reduced sample without transparent explanations of how speeches were selected [@marquardt2022].
+There is also an empirical gap in terms of how the Amazon, specifically, has been constructed as a problem along time and geographic location in political discourses.
+Whereas governmental discourses in Brazil have been studied for topics such as inflation or race relations [see @silva2019], the environment remains absent.
+An exception is @barros2020, who investigates Amazonian discourse in the Brazilian Congress.
+The author finds that the economic value of the Amazon for the cattle industry is the most salient narrative put forward by congressmen and concludes that there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
 
-In sum, we propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy issue and connects it to presidential speeches.
-Governments choose what problems to solve and what policies to implement.
+This variation in problem-construction entails that the same governments are more diverse in their positions than the literature suggests.
+Scholars often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+In this literature, the 1964 military dictatorship is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
+The governments from the late 1980s up to 2009 are associated with a turn towards policies that focus on environmental conservation.
+The presidencies of Dilma and Temer are connected to the decline of conservationist policies, while Bolsonaro to the dismantling of environmental policies.
+Whereas these works are important to understand how different governments acted toward the Amazon, the classification of specific governments into policy periods, or policy cycles, represents them as monolithic: they associate specific governments with one specific view of the Amazon.
+
+We propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy object and connects it to presidential speeches.
+Governments often choose what problems to solve and what policies to implement.
 The same policies can be represented as solving different problems implying a degree of social construction [@bacchi2009].
-Governments can choose to emphasize or not one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-The variation in problem-construction suggests that Brazilian governments are more diverse in their positions as the literature suggests.
-An interesting site to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for democracy, and for environmental outcomes.
-As presidents speak in different places and to different audiences, it is an empirical site prone to identify variation.
+Governments can emphasize, or not, implicit problems that a policy solves depending on which interest group they are in communication with.
+The variation in problem-construction suggests that Brazilian governments are more diverse in their positions than the literature suggests.
+An interesting site to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for policymaking, and environmental outcomes.
+As presidents speak in different places and to diverse audiences, it is an empirical site prone to identifying variation.
 
@@
 
-To identify possible problem-constructions and their connection to the wider socio-cultural history of the country, we build on Amazonian historiography.
-We understand Amazonian historiography as the body of research conducted by social and environmental scientists that tells the story of diverse governmental programs that approaches the Amazon region, forest, and its people as a policy object demanding dedicated action.
+We rely on the Amazonian historiography literature to identify possible problem-constructions and their connection to the socio-cultural history of the country.
+We refer to Amazonian historiography as the body of research conducted by social and environmental scientists that tell the story of diverse governmental programs that approach the Amazon region, forest, and its people as a policy object demanding dedicated action.
+From this literature, we identify three historical-political-social constructions: national sovereignty, economic integration, and environmental conservation.
+We also argue that a fourth one is missing, social development, that focuses on the rights and dignity of the inhabitants of the Amazonian region.
 
@@
 
-In *The Fate of the Forest: Developers, Destroyers, and Defenders of the Amazon*, @hecht1990 [p.
-1] write that all over the world tropical forests are destroyed, but "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites".
-These dreams of fortunes to be found in the Amazon are composed of the imaginaries of bandeirantes from the southeast of Brazil and colonizers from everywhere else.
-It rendered the territory the venue for aspiration and the object of an intense scramble in the subsequent centuries, defined as "a (...) form of nation building (...)" [hecht1990, preface].
-The Portuguese empire and subsequently the Brazilian monarchy were concerned with establishing their territory.
-In the process of securing Amazonian borders, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht2013, p.
-8], and when the dust settled and the scramble was over, half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas.
-A significant experience was the negotiations with Bolivia in 1902 to secure the Amazonian state of Acre, during which they found out about American attempts to trick Brazil [@hecht1990].
-This case was still part of the memory of the generals who led the country during the military dictatorship of 1964 and wanted to protect Brazil's sovereignty over the Amazon from the communist threat during the Cold War [@garfield2013].
-
-As we move from a world where non-state actors gain importance in environmental governance and transnational politics generally [@silva-muller2022; @andonova2014; @keck1998], the sovereignty problem becomes more varied.
-Multiple non-state actors (NGOs, foundations, IOs, and so on) join the conversation about Amazonian policies more substantially as the military dictatorship starts to end [@hochstetler2021; @capobianco2019; @franchini2019].
-Threads to national sovereignty, consequently, can be interpreted as coming from a different set of actors than before.
-Allegedly false claims about the Brazilian Amazon in international and domestic fora, for instance, are often tied to strategies of 'internationalizing' the Amazon.
-This might come both from foreign actors as well as domestic non-state actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil while any foreign or non-state presence in the region is part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty, included the monitoring of the borders, strict regimes related to entry in the region, assertions of ownership nationally and internationally, and combating alleged disinformation from actors perceived as a threat.
+@hecht1990 [p.
+1] write that “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites”.
+In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+8], and when the dust settled and the scramble was over, over half of the Amazon emerged Brazilian.
+While Brazilian military diplomacy was very successful, the process did not come without its traumas as the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
+These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 aimed at protecting Brazil’s sovereignty over the Amazon.
+As we move from a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
+Threats to national sovereignty, consequently, broaden from state actors to a wide set of actors.
+Claims of attempts to ‘internationalize’ the Brazilian Amazon, for instance, are targeted at foreign actors as well as domestic non-state actors.
+The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
+The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
 
@@
 The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on a set of assumptions [@acker2014].
-First, nature should be conquered by men.
-Second, exploiting natural resources would render the Amazon region a global powerhouse.
-Third, such a project would integrate the region with the rest of the country.
-Concretely, this meant a series of infrastructure projects, such as roads and dams, incentives for settlers to develop ranches and expand the agricultural frontier, and the establishment of tax-free zones to attract industry.
-The capital to conduct such changes, paradoxically, came from national and international sources [@acker2014], leading to a series of national and international enterprises settling in the Amazon region.
-@capobianco2019 describes the period from the 1950s to the 1980s in a similar fashion, referring to a wider range of policies of economic integration such as the establishment of the tax-free zone of Manaus in the 1970s.
+In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on three assumptions @acker2021.
+First, it assumes that nature should be conquered by men.
+Second, it assumes that exploiting natural resources would render the Amazon region economically profitable.
+Third, it assumes that populating the region was necessary to integrate it into the country and exert control over the territory.
+Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
+@capobianco2019 describes the period from the 1950s to the 1980s in relation to the wider range of policies of economic integration, often centralized by the federal government [see @becker2005].
 The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions are often centralized by the federal government [@becker2005] and have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+
+### Environmental Conservation
+
+The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
+A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
+This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
+@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
+They define it as an emphasis on the local livelihoods of traditional populations while protecting nature.
+@capobianco2019 argues that socio-environmentalism informed a series of policies throughout the 1990s and early 2000s towards preserving the forest, such as the establishment of several conservation units in the Amazon in 2001.
+The environmental conservation problem-constructions emphasize the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
+The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
 
@@
 
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights when speaking about the Amazon.
-This is not only relevant as a construction, but speaks, minimally, to democratic concerns over providing electorates, especially in the Amazonian region, with better standards of living than previously.While related to economic integration, social development is a problem-construction that focusses more on rights and citizenship.
-Importantly, though, the literature on policy cycles in the region is silent about social develop.
-This category was identified in speeches and constructed by the researchers inductively.
-This might be related to social policies being more geared towards the whole nation, rather than thought specifically for the Amazon region.
-Nevertheless, as it appeared quite frequently in discourse, we include it in our codebook.
-
-### Environmental Conservation
-
-The rapid economic changes in the region in the 1960s, 1970s, and 1980s were matched with the birth of environmental institutions [@drummond2006].
-A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s, with the birth of modern environmentalism [@viola1987] in the 1980s, epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
-They define it as an emphasis on the local livelihoods of people while protecting nature.
-@capobianco2019 argues in a similar line, establishing socio-environmentalism as the main government response in the 1990s and early 2000s in a series of policies as establishment of conservation units in the Amazon in 2001.
-The environmental conservation problem-constructions emphasizes the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
-The policy solution implies more investment in command-and-control infrastructure (as remote-sensing technology for environmental outcome measurement), more investment in the valuation of standing ecosystems through incentive schemes, and more policies facilitating indigenous environmental practices.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
+@acker2021 [p.
+10], for example, argues that during the military dictatorship attempts to populate the Amazon was seen, among other things, as a solution for the country’s growing social inequalities elsewhere.
+As democracy established itself in Brazil, the settlers from the military dictatorship became electorates with constitutional rights.
+@hochstetler2007 argue that with the transition to democracy, the mobilization of diverse social movements to demand social equality and conservation was an integral part of the socio-environmentalism movement in Brazil.
+Whereas indigenous rights and preservation of the forest go hand in hand, it is not clear that providing better standards of livings to the large and poor populations of the state and preservation do; perhaps this is also why there was never an open consensus about socio-environmentalism in Brazil [@hochstetler2007].
+While related to economic integration and environmental conservation, social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
+The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
 
@@
 
-To analyze how presidents construct the Amazon as a problem in time, we build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
 We update the dataset by scraping and adding all official speeches from 2020 and 2021.
@@
 Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
+We do so by detecting all speeches in which the stem “amazon” appears.
+In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
 We find that 946 speeches are, at least partially, about the Amazon from the 6130.
 
-Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences before and two sentences after, rather than words, because sentences usually contain a cohesive idea.
+Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+We opt for picking two sentences before and two sentences after, rather than words because sentences usually contain a cohesive idea.
 By doing so we create our unit of analysis: an Amazonian statement.
@@
 First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-Second, it increases the number of our observations and its variety meaningfully, allowing for more specificity in our analysis.
+Second, it increases the number of our observations and their variety meaningfully, allowing for more specificity in our analysis.
 This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
+When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
 On average, an Amazonian statement contains 123 words.
 
-We follow the procedures outlined by @grimmer2022 for supervised classification.First, we develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
+Our approach to text coding has three steps.
+First, we develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
 In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
@@
 As well, this allows a robust validation set to verify the models.
-As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable enough.
+As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
 Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
@@
 Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-We chose to employ a support-vector machine (SVM) algorithm to label texts, that is, a non- probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories [@meyer2021; @noble2006] .
-The SVM model is first trained using the hand coded training set and then employed to classify observations in the hand coded validation set.
+We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts [@meyer2021; @noble2006].
+The SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set.
 The trained SVM model was, on average 82%, accurate in classifying observations in the validation set before being tuned.
@@
 The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements.
-Finally, we extract locations for all speeches in the data.
-These locations represent the Brazilian state in which certain speech was given or an international country.
 
@@
 
-To analyze our data, we first present a series of different plots on proportions of Amazonian statements and problem-constructions over time and by presidents.
-To test whether different problem constructions change according to location, we run a logit model in which different problem constructions (as categories) are the dependent variable and location is the independent variable.
-Multinomial logit is an appropriate method for modeling data in which the dependent variable of interest is categorical, unordered, and has many categories, as is our case [@kwak2002].
+To analyze our data, we first present a series of different plots on the proportions of Amazonian statements and problem-constructions over time and by presidents.
+To test whether problem-constructions depend on where presidents speak, we run four separate logistic regressions.
+Each model takes the share of a specific problem-construction versus all other problem-constructions as their dependent variable.
+This means we try to predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
+Our main independent variable is the distance, in kilometers, between the state capital (within Brazil) or the country capital (outside of Brazil) to Manaus (the capital of the Amazonas State and centrally located in the region).
 In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
-We interpret the plots and model considering multiple Amazon related events and policies over the last 30 years, mostly with support of existing literature, as well as their correlations with different presidents and locations.
+We interpret the plots and model considering multiple Amazon-related events and policies over the last 30 years, with the support of existing literature, and their correlations with different presidents and locations.
 
-This approach also comes with limitations.
+This approach comes with limitations.
 Our codebook is developed using specific Amazon-related vocabulary.
-For example, a statement will be coded as economic integration if it is meaningful support to the tax-free zone of Manaus or a Dam in the Amazon.
+For example, a statement will be coded as economic integration if it is meaningful support for the tax-free zone of Manaus or a Dam in the Amazon.
 However, the economy is generally a topic that presidents speak about.
 Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
 Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Mata Atlantica.
-Nevertheless, our dataset covers only what is considered an official remark.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and more recently started to appear on social media.
-Problem- construction within presidential discourse, thus, also happens in different sites for which we do not account for in this paper.
+However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
+Finally, our dataset covers only what is considered an official speech.
+Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
+Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account in this paper.
 
 # 4 How has the Amazon been constructed as a problem?
-
-We break down our analysis in three sub-sections.
-First, we describe when, where and how often do presidents speak about the Amazon or do not speak about the Amazon.
-Second, we zoom in speeches about the Amazon and demonstrate how they vary by problem-construction.
-Finally, we model which specific problem-constructions are more likely to appear in which locations using logistic regressions with multiple controls.
 
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents speak about the Amazon in 15% of their speeches.
-Mentions to the Amazon outside of Brazil are slightly more frequent than mentions inside Brazil.The frequency in which the Amazon appears across presidential speeches (inside, outside, and overall), though, varies in time.
-
-Globally, we observe five local maxima both inside and outside Brazil: 1989, 1992, 2009,2015, and 2019.
-These points coincide with events that help us explain the rises and falls of the Amazon in presidential discourse in time.
-In 1985 the Amazon appeared in about 4% of all the presidential speeches but by 1988 this had increased to around 14%.
-This is the period when the Brazilian Constitution was written.
-Indigenous and traditional populations were instrumental in advocating for constitutional environmental rights and the protection of their territories [@hecht1990].
-These were eventually enshrined in article 225, which gives all Brazilians a right to a balanced environment, and in article 231, which grants indigenous and traditional populations a right over their territory.
-However, in 1989, the Amazon appeared in 32% of all speeches.
-This spike is likely explained by the brutal murder of Chico Mendes at the last days of 1988.
-An incident that caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021].
-Importantly, one of the responses was Sarney's invitation to host the 1992 Earth Summit[@keck1998].
+On average, presidents mention the Amazon in 15% ^[For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).] of their speeches .
+Mentions of the Amazon outside of Brazil are slightly more frequent than mentions inside Brazil (Figure 3).
+The frequency in which the Amazon appears across presidential speeches inside, outside, and overall, though, varies similarly across time.
 
 ```{r Figure 2, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
 perc1 <- pop %>%
@@
   select(c(perc, amazon_speech, year))
-
 Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
@@
        color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
+  theme_am()
 Amazon_year
-
 ```
 
-In 1990 the Amazon appeared in 12% of all speeches and, by 1992, this increased to 25% of all speeches.
+We observe five local maxima both inside and outside Brazil: 1989, 1992, 2009, 2015, and 2019.
+These points coincide with internal and external events that help us explain the rises and falls of the Amazon in presidential discourse.
+From 1985 to 1988, the mentions of the Amazon in official speeches increased from 4% to 14%.
+During this period the latest Brazilian Constitution, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990], was written.
+In 1989, however, the Amazon appeared in 32% of all speeches.
+This spike correlates with the brutal murder of Chico Mendes in the last days of 1988.
+The incident caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021], including accepting to host the 1992 Earth Summit [@keck1998].
+
+1990-91 the Amazon appeared in 12% to 14% of all speeches but, by 1992, this average increased to 25%.
 The 1992 Earth Summit in Brazil brought international attention to environmental topics related to the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Programme, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].Throughout the rest of 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average.
-In 2009 we see another spike in the Amazon appearing in official speeches.
-This spike coincides with the 2009 Copenhagen Summit as well as the steepest decrease in deforestation rates since data is available.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
-
-From 2010 to 2018, with the exception of 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of Itaipu Dam, led the environmental minister Marina Silva to resign and run for the presidency on her agenda in 2010.
-In 2011, the New Forest Code, which regularized land ownership of many illegally deforested areas, was also approved.
-These are also the years when Brazil entered a long period of political and economic instability, which eventually led to the impeachment of Dilma Roussef.
-Though, in 2015, the Amazon appeared in 19% of speeches.
-This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
-By 2016 mentions of the Amazon in official speeches went down to 6%, the lowest share since 1985.
+One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Program, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
+Throughout the rest of the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another spike in mentions of the Amazon.
+This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 5, below, illustrates.
+Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high [@franchini2019].
 
 ```{r Figure 3, fig.cap="Amazonian speeches in time and space", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
 perc_in <- pop %>%
@@
   select(c(perc, amazon_speech, year, location_cat))
-
 perc_out <- pop %>%
@@
   select(c(perc, amazon_speech, year, location_cat)) 
-
 # location plots
@@
        color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "")
-
+  theme_am()
 Amazon_year_out <- perc_out %>% 
@@
        color='Y series') +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "")
-
+  theme_am()
 grid.arrange(Amazon_year_in, Amazon_year_out, nrow=2)
-
 ```
 
-We subsequently observe a steady increase from 6% in 2016 to almost 24% in the first year of Bolsonaro's presidency, 2019.
-At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon, and of the red sky afternoon in São Paulo circulated on social media and international media outlets.
-Bolsonaro's dismantling of environmental governance, including threats to leave the Paris Agreement, gained strong media attention and the topic became prominent in his speeches.
-At the same time, President Bolsonaro retrieves Brazil's hosting status for COP25.
+From 2010 to 2018, except for 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
+From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
+Disagreements related to the priority of environmental preservation over economic development, most notably in the case of approval of the New Forest Code in 2012, which regularized land ownership of many illegally deforested areas, were frequent.
+The period was also marked by of political and economic instability which culminated in the impeachment of Rousseff.
+In 2015, the Amazon appeared in 19% of all speeches.
+This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
+Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
+By 2016 mentions of Amazon in official speeches went down to 6%, the lowest share since 1985.
 
-The frequency of the topic Amazon in domestic and international speeches is similar.
-High increases in the topic frequency, as well, are similar in domestic and international speeches.
-The aforementioned events that coincide with high frequencies are both of domestic and international nature.
-We interpret this as evidence that relevant events drive interest and alter how pressing the "Amazon problem" is perceived both nationally and internationally.
-This does not mean, though, that when presidents speak about the Amazon, they say similar things.
-In the next sub-section, we dissect the content of their speech and whether specific events and policies drive specific problem-constructions.
+We subsequently observe a steady increase from 6% in 2016 to 24% in 2019, the first year of Bolsonaro’s presidency.
+At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon leading up to the red sky afternoon in São Paulo in August 2019.
+Alongside this, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
+Bolsonaro went on to retrieve Brazil’s hosting status for COP25.
+
+The frequency in which the Amazon appears in domestic and international speeches varies in similar ways as the spikes in the topic frequency, led by the events discussed above, appear within and outside Brazil.
+We interpret this as evidence that relevant events drive interest and alter how pressing the “Amazon problem” is perceived both nationally and internationally.
+This does not mean, though, that when presidents speak about the Amazon, they highlight the same issues.
 
@@
 
+Our subsequent analysis of pure-types and mixed-types suggests that governments do not defend a view of the Amazon.
+The same governments construct the Amazon as various pure and mixed type problems, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
+
 ### Pure-type problem constructions
 
-As detailed in section 2.2, we conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
-At the level of the speech, though, presidents might mix multiple problem construction in an Amazonian statement.
-Figure 3, below, illustrates the share of each pure-type in time.
-Pure problem constructions dominate, with an average of 56% of all amazonian statements across time.
-Again, we observe a strong variation over time for most of these constructions.
+We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
+Figure 4, below, illustrates the share of each pure-type in time.
+Pure problem constructions dominate, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
+Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
+This is especially pertinent during the Cardoso administration.
+Brazilian presidents after Cardoso moved from employing one problem-constructions consistently to a more diverse strategy.
+During Lula’s terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon as issues of environmental conservation and social development increased.
+Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during the Rousseff administration.
+Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or time in discourses as economic integration was until the early 2000s.
+Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching its highest frequencies with the presidencies of Bolsonaro.
 
 ```{r Figure 4, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 mmt1 <- ama_mx %>%
@@
   mutate(perc = n / sum(n)) # averages in relation to full sample
-
 pure_types_time <- ama_mx %>%
@@
        caption = "Curves in the plot were smoothed using loess method.") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "bottom")
+  theme_am() +
+  theme(legend.position = "bottom")
 pure_types_time
-
 ```
 
-Figure 2 portrays a discursive shift from developing the Amazon economically, to conserving it and providing services to Amazonian citizens.
-Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
-This is especially pertinent during the Cardoso administration.
-However, during Lula's terms in office, constructions of the Amazon purely as an economic issue decreased in discourse while constructions of the Amazon as issues of pure conservation as well as of pure social development increased.
-These constructions surpassed economic integration around 2010.
-These trends in discourse continued during the Rousseff administration.
-If interpreted in light of deforestation rates since 1988, this trend is particularly interesting.
-The overall development of environmental conservation in figure 3 suggests a negative correlation with deforestation rates.
-When deforestation rates increased (1988 to 2004, and from 2012 until 2021), environmental conservation decreased.
-When deforestation rates decreased (2004 to 2012), environmental conservation in presidential speeches increased.
-The opposite is true foe economic integration problem-constructions, which increased as deforestation rates increased, and decreased when deforestation rates decreased.
+The trends identified in Figure 4 are especially interesting considering policies related to deforestation in the Amazon and deforestation rates portrayed in Figure 5, below.
+First, deforestation rates have a strong negative correlation with environmental conservation.
+When deforestation rates increased from 1988 to 2004, and from 2012 until 2021, environmental conservation constructions decreased.
+As deforestation rates decreased from 2004 to 2012, environmental conservation constructions in presidential speeches increased.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, engendered a perception of a higher risk of being caught and fined for deforestation.
+The shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned.
+Second and relatedly, deforestation rates have a positive and strong correlation with economic integration.
+When deforestation increased from 1988 to 2004 and from 2012 to 2021, so did economic integration.
+When deforestation decreased from 2004 to 2012, economic integration decreased as well.
+This suggests that presidents might boast policy outcomes related to economic integration as justifications for deforestation.
 
 ```{r Figure 5, fig.cap="Deforestation rates since 1988", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 def_rates <- ggplot(amazon_def_year, aes(x = year)) +
@@
   geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.75)+
-  annotate("text", x = 2004, y = 29000, label = "2004 Plan to Combat\nand Control Deforestation", size = 4.5) +
-  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 4.5) +
-  labs(x = "",
-     y = "Deforestation in squared kilometers",
+  annotate("text", x = 2004, y = 29000,
+           label = "2004 Plan to Combatand Control Deforestation", size = 3) +
+  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 3) +
+  labs(x = "", y = "Deforestation in squared kilometers",
        title = "Deforestation rates since 1988",
@@
        caption= "Black curve smoothed using loess.")+
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.2, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "none")
-
+  theme_am()
 def_rates
-
 ```
-
-A possible explanation for this can be found in the logic of the policies adopted.
-@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region, which in turn engendered a perception of higher risk of being caught and fined for deforestation.
-A higher incidence of the Amazon as a topic in overall presidential speeches (figure 2), generates a perception that more attention is being paid to the Amazon from the top.
-While the shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned (figure 3).
-A further explanation might be related to boasting about policy outcomes: when deforestation is high, presidents are more likely to focus on economic integration as its product.
-We scrutinize this possibility further in section 4.3.
-
-Figure 3 also portrays that presidents moved from employing problem-constructions more consistently in the 1980s and 1990s, to a more diverse strategy in the 2000s and 2010s.
-The distances among the different constructions was never as small as in the 2010s.Again, considering the policies, this makes sense.
-During the same time that the policies which reduced deforestation drastically were adopted, the rural credit offered to agricultural producers in Amazonian states, went up from 500 million BRL per year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-The increase of the environmental conservation and social development problem-constructions, thus, never dominated discourse as clearly as economic integration did until the early 2000s.
-
-From the mid-2010s onwards, we observe a reversal of the identified trend: economic integration problem construction increases while conservation and social development constructions decrease again This is also aligned with the argument that Rousseff's administration changed its priorities.
-The 2012 Forest Code, which pardoned many deforesters, is an illustrative example of this change.
-The twist in this reversal is that sovereignty starts to increase steadily after 2010, and by 2019 sovereignty constructions surpass social development.
-While in the 1990s economic integration dominated solely, in the mid-2010s, problem constructions that highlight the Amazon as Brazilian increased.
-The reversal precedes the mandate of President Bolsonaro, but it was during his presidency that sovereignty constructions reached unprecedented levels since the establishment of Brazilian democracy.
 
@@
 
-Although presidents prefer pure problem-constructions, they also construct the Amazon as multifaceted issues (see figure 1).
-Mixed-type problem constructions in discourse offer more complex understandings of the Amazon.
+At the level of the speech presidents might mix multiple problem constructions.
+Although presidents prefer pure problem-constructions, they also construct the Amazon as a multifaceted issue.
+Mixed-type problem constructions in discourse offer more intricate understandings of the Amazon as a problem.
 Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
-While there is some variation in time, some mixed-types rarely appear, thus, we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the yearly averages of mixed-types.
-While our analysis of mixed-types largely confirms the analysis of pure-types, it sheds lights in a few distinct trends and variations of specific presidents.
+Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
+Figure 6, below, displays the averages of mixed-types constructions by presidents.
 
 ```{r Figure 6, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 mixed_types_presid <- ama_mx %>%
@@
        caption = "") +
-  theme(panel.background = element_rect("white", "black", .5, "solid"),
-        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "right")
-
+  theme_am() +
+  theme(legend.position = "right")
 mixed_types_presid
@@
 
-The most frequent mixed-type problem construction of the Amazon in time is economic conservation, which has increased slightly in time.
-This mixed-type is composed of Amazonian statements that construct the Amazon as problems of both economic integration and environmental conservation.
-This is largely aligned with findings from figure 3, which showed the prevalence of economic integration and environmental conservation.
-It's increase in time might suggest presidents increasingly negate the dictum between the economy and the environment that prevailed in the previous years.
+The most frequent mixed-type problem construction of the Amazon is economic conservation.
+This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased in time.
+Its increase over time suggests that later presidents, along with being more diverse in how they constructed the amazon as an issue (see Figure 3), increasingly find ways to reconcile the dictum between the economy and the environment that prevailed in the previous years.
 The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-This is not surprising, though.
-As developing countries like Brazil repeatedly claimed a "right to develop" when it came to negotiating strong climate commitments and policy, a focus on social development and economic integration is reflective of that.
+This is not surprising, as developing countries like Brazil repeatedly claim a “right to develop” when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
+Nonetheless, there is a general increase of mixed-types in time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
 
-Both Lula and Bolsonaro construct the Amazon as multifaceted issues in discourse more frequently than other presidents.
-Lula, on the one hand, often mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue.
-Bolsonaro, on the other hand, often mixes national sovereignty with other problem constructions.
-Indeed, we see that Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration more than any other president, which was also characteristic of the military dictatorship discourses and policies for the region [@hecht1990].
-
-Generally, the increase of mixed-types is expected given the rise of a global agenda understanding interconnections of social, environmental, and economic domains.
-As we show that Amazonian incidence in discourse does respond to global events as summits, this is not a surprise given agendas such as the Millennium Development Goals and the Sustainable Development Goals.
-In light of the events identified as drivers of higher frequencies of the Amazon as an overall topic (figure 2), the intensification of the UNFCCC process post-Copenhagen might explain the increase in sovereignty problem-constructions.
-Unexpectedly, the 1992 Earth Summit in Rio de Janeiro did not lead to an increase in environmental conservation overall.
-Thus, there is no clear correlation between events described in figure 2 and the frequencies of specific problem-constructions.
-Our analysis of pure-types and mixed-types also suggest that governments do not defend a single problem-construction for the Amazon.
-The same governments construct the Amazon as different issues in discourse, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
-It remains to be tested whether the variation in problem-construction correlates with the audience of speeches.
+Both Lula and Bolsonaro construct the Amazon as a multifaceted issue more frequently than other presidents.
+Lula usually mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
 
@@
 
-To test whether problem-constructions depend on where presidents speak, we run four separate logistic regressions and compare them.
-Each model takes the share of a specific problem-construction versus all other problem-constructions as their dependent variable.This means we try to predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
-Our main independent variable is the kilometer distance between where the speech took place, and the Amazon forest.
-The rationale behind this is that as we move further away from the region, audiences of the speech might have different interests on it.
+The Amazon region, forests, and peoples have historically been the topic of local, national, and international debates.
+This implies that audiences’ priorities in each setting change and which policies are appropriate to solve the “Amazon issue” differ as well.
+As presidents move away from the Amazon, audiences might have different stakes and interests in it.
 While speeches inside the Amazon might focus on social development, for example, speeches in the United Nations in New York might highlight environmental conservation.
-We control for deforestation rates (numerical), inflation (numerical), and election year (dummy).
-Since the model accounts for both mixed and pure-type Amazonian constructions, and this makes for a large table, we focus the analysis on pure-types to facilitate visualization.
+To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run four logistic regressions, one for each pure-type construction as a dependent variable.
+We focus on pure-type constructions as these represent most constructions and avoid ambiguity.
+The independent variable for all models is the distance between the state country capital to Manaus.
+Figure 7, below, depicts the predicted probabilities from the models (see Table 1) as functions of distance.
 
 ```{r Figure 7, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
 ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
-ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
+ama_model <- filter(ama_model, location_cat != "Non Identified",
+                    mx_cat != "Other Mixed-types") %>%
   mutate(con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
@@
          sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))
-
 # model
-
 model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
@@
                    family=binomial(link = "logit"), data = ama_model)
-
 # Plot model
@@
 ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
-
-plot_loc <- ama_model %>% gather(key=p_c, value = pred, 21:23)
-
-plot_loc$p_c <-factor(plot_loc$p_c, levels =c("Economic Integration", "Environmental Conservation", "Social Development"))
-
+plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:24)
+plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
+                                               "Environmental Conservation",
+                                               "Social Development"))
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
@@
   geom_vline(xintercept = c(1933.78, 2771.49, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76), y = c(0.5,0.55,0.5,0.55),
+  ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76),
+                    y = c(0.5,0.55,0.5,0.55),
                     label = c("Brasilia","Sao Paulo", "New York", "Paris"), alpha = 0.4) +
@@
        caption = "Curve in the plot is estimated using loess method.") +
-    theme(panel.background = element_rect("white", "black", .5, "solid"),
-          panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
-          axis.text = element_text(color = "black", size = 10),
-          title = element_text(color = "black", size = 10, face = "bold"),
-          legend.title = element_blank(),
-          plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-          legend.position="bottom")
-
+    theme_am() +
+  theme(legend.position = "bottom")
 all_loc
-
 ```
 
-Table 2 presents the output of our four logistic regression models, and figure 5 depicts the predicted probabilities as functions of distance.
-We find a statistically significant relationship between constructing the Amazon as an issue of environmental conservation and distance from the Amazon: the farthest away the president is from the Amazon, the more likely the president is to state we need to conserve it.
-The opposite is true for economic integration and social development, with statistical significant negative relationships.
-This means that while speaking inside the Amazon, presidents focus more on social and economic development.In the case of sovereignty, though, there is no significant relationship present.This relationships also hold within Brazil: when speaking outside the Amazon but still inside Brazil, presidents forgo social and economic development in favor of conservation.
-
-Our models also suggest that deforestation plays an important role.
-When it comes to environmental conservation constructions, presidents are more likely to deploy this problem construction if deforestation decreases.
-Relatedly, when deforestation increases, economic integration problem constructions are more likely.
-This is largely aligned with @franchini2019 argument about mythological self-image, which states that Brazil creates an image of itself as strong climate leadership because of good results achieved from 2004 to 2012.
-On the other hand, the positive correlation between economic integration and deforestation, might relate to the problem-construction being employed as a justification for bad rates, as figure 3 also suggests.
+Table 1, below, shows a statistically significant relationship between constructing the Amazon as an issue of environmental conservation and distance from the Amazon.
+That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
+The opposite is true for both economic integration and social development, with statistically significant negative relationships.
+When speaking within the Amazon, presidents focus on social development and economic integration.
+This entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not at the local level, where presidents highlight economic and social development.
+This multi-level game implies that presidents talk to the economic and social needs of the people domestically while boasting about environmentalism internationally.
 
@@
 ```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
 # summary statistics
-
-md<-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd, model_logit_sov, 
-                         digits = 10, 
-                         dep.var.labels = c("Conservation", "Economic Integration", "Social Development", "Sovereignty"),
-                         covariate.labels = c("Distance from the Amazon (km)", "Election year", "Yearly Deforestation", "Yearly   Inflation"),
-                         no.space = TRUE)
-
+md <-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
+                          model_logit_sov, digits = 10, 
+                          dep.var.labels = c("Conservation", "Economic Integration",
+                                             "Social Development", "Sovereignty"),
+                          covariate.labels = c("Distance from the Amazon (km)",
+                                               "Election year", "Yearly Deforestation",
+                                               "Yearly   Inflation"), no.space = TRUE)
 ```
@@
 \end{landscape}
-How the amazon is constructed as a problem varies across levels.
-The Amazon, as a region and a forest, has historically been the topic of international, national, supranational, and local debates, negotiation and policies.
-This implies not only that audiences' priorities in each setting change, but that which policies are appropriate to solve the "Amazon issue" could differ as well.
-The multi-level game identified in this sub-section, entails that conservation might be a desirable construction when speaking internationally about the Amazon, or in Brasilia, but not at the local level, where presidents highlight economic and social development.
-Overall, we interpret these results as evidence of maximizing political outcomes: boasting policy outside, while talking to people inside.
+
+Our models also suggest that deforestation plays an important role.
+Presidents are, for example, more likely to construct the Amazon as an issue of environmental conservation as deforestation decreases.
+Alternatively, as deforestation increases, presidents are more likely to construct the amazon as an issue of economic integration.
+This indicates that Brazil creates a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
+In the same fashion, economic integration problem-constructions are likely deployed as a justification for increasing deforestation rates.
 
@@
 
-In sum, this paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-Our findings show that these constructions are not monolithic within governments, in time, or across different locations.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relates to policies and environmental outcomes.
-Empirically, we provide the first comprehensive overview of the Amazon in presidential discourse.
+This paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
 Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
@@
 Second, the same government adopts a diverse range of problem-construction.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2010 to 2015.
-Hence, there is an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.Unprecedentedly, constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
-Finally, using a logit model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, temporarily surpassing economic integration as a more common problem construction from 2010 to 2015.
+This implies an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.
+Constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
+Finally, we find that presidents are more likely to construct the Amazon as an environmental conservation problem than economic integration or social development, as presidents move away from the Amazon region.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relate to policies and environmental outcomes.
+Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as an issue in presidential discourse.
 
-Given the importance of discursive problem-construction within democracies to legitimize ways of thinking and acting towards the environment, we believe our findings reveals important facets of Brazilian environmentalism along time.
-If presidents promote an agenda of economic and social development within Brazil that diverges from the one the president promotes outside of Brazil, the question becomes to what extent the implemented agenda responds to domestic versus international demands.
-In light of the multiple policies being negotiated simultaneously, economic and social development inside versus environmental conservation outside, is a strategy to maximize political outcomes.
-It convinces local electorates while it cashes in trasnational funds for policy.
-This can be exemplified by scrutinizing the outcomes of negotiations abroad.
-The Brazilian government successfully funded domestic public policy in several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Regional Protected Areas Program by the World Bank and others; and the 2008 Amazon Fund which provided over USD 1 billion for en [@silva-muller2022].
+Discursive problem-construction within democracies legitimizes ways of thinking and acting towards the environment.
+If presidents promote an agenda of economic and social development within Brazil that diverges from the one promoted outside of Brazil, to what extent does the implemented agenda respond to domestic versus international demands?
+The Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Regional Protected Areas Program by the World Bank and others; and the 2008 Amazon Fund which provided over USD 1 billion [@silva-muller2022].
 Concurrently, the national agenda of economic integration or social development was pursued.
-During the same time rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+Multiple contradictory policies negotiated simultaneously, imply that presidents construct policy objects as issues important to local electorates within the Amazon while, at the same time, highlighting aspects important for international actors elsewhere.
 
-The domestic policies and transnational support that led to the decrease in deforestation from 2004 to 2012 took place in a period of strong economic growth and social development in Brazil and worldwide.
-With the strengthening of environmentalism and indigenous participation in politics in the late 1980s and 1990s (@hochstetler2007), we can interpret the fall of economic integration problem-construction and the rise of social and conservation constructions as a new balance between granting local livelihoods their rights and economic exploitation.
-This new balance was both unprecedented and not long-standing, as the dismantling of environmental policy in favor of infrastructure and agricultural expansion initiated in the 2010s.
+The decrease in deforestation that took place in Brazil from 2004 to 2012, was accompanied by a period of strong economic growth.
+With the strengthening of environmentalism, through the participation of indigenous and civil society in politics [@hochstetler2007], the fall of economic integration problem-construction and the rise of both social development and environmental conservation constructions in the 2000s suggest a new balance between granting local livelihoods their rights and economic development.
+This new balance was both unprecedented and not long-standing.
+Unprecedented because never before the environment and people were equally present as the economy in presidential discourse.
+Not long-standing because the dismantling of environmental policy in favor of infrastructure and agricultural expansion was already on its way in the late 2010s.
+The Belo Monte Dam in the late 2000s and the 2012 New Forest Code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and won these battles even though they were largely opposed by environmentalists.
 
-Democratic decay is slow, and the embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
-We observe the decrease in conservation problem-constructions in the mid-2010s, and a hard increase of sovereignty constructions in the early 2010s.
-Bolsonaro is a response to political re-organization of national and international actors - to which Roussef and Temer were already responding in discourse- rather than the cause of change.
-As we conceptualize and operationalize sovereignty as boundary-making vis- à-vis internal and external perceived threats to the Amazon, we interpret this increase as not only attacks to international interference in the Amazon but also on indigenous and traditional populations.
-On the policy side, the Itaipu Dam in the late 2000s and the 2011 Forest code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and conquer this policy wins, which were largely opposed by environmentalists.
-The political forces in Brazilian democracy that drive these changes in problem-construction were long in the making, as the earlier and softer shifts in discourse suggest.
-Bolsonaro's problem-construction is the strongest form of this shift.
+The steady increase of sovereignty starting in 2010 brings an eerie twist.
+As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
+The embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
+Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change.
+The political forces in Brazilian democracy that drove these policy and discursive changes in problem-construction were long in the making, Bolsonaro’s problem-constructions and policies are the strongest forms of this shift.
 
-In light of these findings, we outline three avenues for future research.
-First, scholars should create more robust identification strategies to connect environmental discourse to actual environmental outcomes at the local level.
-While we hold that presidents are particular important, other actors as mayors and ministers could also be scrutinized.
-Second, research can expand to the realm of presidential speeches that take place outside official settings.
-Social media, specially in Brazil, has become crucial in communication between audiences as their leaders.
-Relatedly, social media complicates the boundaries between official and unofficial settings as presidents speaking in a particular location can be recorded and videos travel wide.
-Finally, qualitative researchers could unpack the ways through which the environment enter presidential speeches.
-Speech-writing is a process that includes more than one actor, and the decisions to speak or not about the environment are probably argued thoroughly.
+\newpage
+# References
+
+<div id="refs"></div>
 
@@
 ```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
 codebook <- tibble::tibble("Problem Construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
@@
 kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
-
 ```
@@
 ````
-
-# References

### 2022-09-03 Draft_September_2022/Full_draft_20220901.rmd
More updates to article

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985 in Brazil
+title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985
 author:
@@
 ```{=latex}
-\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, and deforestation}
+\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
 ```
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15% ^[For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).] of their speeches .
-Mentions of the Amazon outside of Brazil are slightly more frequent than mentions inside Brazil (Figure 3).
-The frequency in which the Amazon appears across presidential speeches inside, outside, and overall, though, varies similarly across time.
+On average, presidents mention the Amazon in 15% ^[For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).] of their speeches.
+The frequency in which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
 
@@
 Throughout the rest of the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another spike in mentions of the Amazon.
-This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 5, below, illustrates.
+This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 3, below, illustrates.
 Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high [@franchini2019].
 
-```{r Figure 3, fig.cap="Amazonian speeches in time and space", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc_in <- pop %>%
-   mutate(location_cat = ifelse(grepl("International|Non Identified",
-                                      location_cat),
-                                "Outside of Brazil", "In Brazil")) %>%
-  filter(location_cat == "In Brazil") %>% 
-  count(amazon_speech, year, location_cat) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(amazon_speech == 1) %>%
-  select(c(perc, amazon_speech, year, location_cat))
-perc_out <- pop %>%
-   mutate(location_cat = ifelse(grepl("International|Non Identified",
-                                      location_cat),
-                                "Outside of Brazil", "In Brazil")) %>%
-  filter(location_cat == "Outside of Brazil") %>% 
-  count(amazon_speech, year, location_cat) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(amazon_speech == 1) %>%
-  select(c(perc, amazon_speech, year, location_cat)) 
-# location plots
-Amazon_year_in <- perc_in %>%
-  ggplot(., aes(x = year, y = perc))+
-  geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  annotate("text", x = 1985, y = 0.17, label = "16.17%", size = 3.5)+
-  annotate("text", x = 1988.7, y = 0.35, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.35, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.23, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.20, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.25, label = "August Fires", size=3) +
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "",
-       title = "Share of speeches inside Brazil",
-       subtitle= " 4344 speeches out of 6130",
-       color='Y series') +
+```{r Figure 3, fig.cap="Deforestation rates since 1988", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+def_rates <- ggplot(amazon_def_year, aes(x = year)) +
+  geom_line(aes(y = area), color= "darkolivegreen", linetype="dotted", size= 1.5)+
+  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.75)+
+  annotate("text", x = 2004, y = 29000,
+           label = "2004 Plan to Combatand Control Deforestation", size = 3) +
+  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 3) +
+  labs(x = "", y = "Deforestation in squared kilometers",
+       title = "Deforestation rates since 1988",
+       subtitle= "Data from INPE, Brazilian Ministry of Science and Technology.",
+       color = "",
+       caption= "Black curve smoothed using loess.")+
   theme_am()
-Amazon_year_out <- perc_out %>% 
-  ggplot(., aes(x = year, y = perc))+
-  geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  annotate("text", x = 1985, y = 0.165, label = "15.49%", size = 3.5)+  
-  annotate("text", x = 1988.7, y = 0.33, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.33, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.25, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.19, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.24, label = "August Fires", size=3) +
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "",
- title = "Share of speeches outside Brazil",
-       subtitle= " 1786 speeches out of 6130",
-       color='Y series') +
-  theme_am()
-grid.arrange(Amazon_year_in, Amazon_year_out, nrow=2)
+def_rates
 ```
@@
 
-The trends identified in Figure 4 are especially interesting considering policies related to deforestation in the Amazon and deforestation rates portrayed in Figure 5, below.
+The trends identified are especially interesting considering Amazonian policies and deforestation rates portrayed in Figure 3, above.
 First, deforestation rates have a strong negative correlation with environmental conservation.
@@
 
-```{r Figure 5, fig.cap="Deforestation rates since 1988", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-def_rates <- ggplot(amazon_def_year, aes(x = year)) +
-  geom_line(aes(y = area), color= "darkolivegreen", linetype="dotted", size= 1.5)+
-  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.75)+
-  annotate("text", x = 2004, y = 29000,
-           label = "2004 Plan to Combatand Control Deforestation", size = 3) +
-  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 3) +
-  labs(x = "", y = "Deforestation in squared kilometers",
-       title = "Deforestation rates since 1988",
-       subtitle= "Data from INPE, Brazilian Ministry of Science and Technology.",
-       color = "",
-       caption= "Black curve smoothed using loess.")+
-  theme_am()
-def_rates
-```
-
 ### Mixed-type problem constructions
@@
 Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
-Figure 6, below, displays the averages of mixed-types constructions by presidents.
+Figure 5, below, displays the averages of mixed-types constructions by presidents.
 
-```{r Figure 6, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 5, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 mixed_types_presid <- ama_mx %>%
@@
 This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased in time.
-Its increase over time suggests that later presidents, along with being more diverse in how they constructed the amazon as an issue (see Figure 3), increasingly find ways to reconcile the dictum between the economy and the environment that prevailed in the previous years.
+Its increase over time suggests that later presidents, along with being more diverse in how they constructed the amazon as an issue (see Figure 4), increasingly find ways to reconcile the dictum between the economy and the environment that prevailed in the previous years.
 The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
@@
 The independent variable for all models is the distance between the state country capital to Manaus.
-Figure 7, below, depicts the predicted probabilities from the models (see Table 1) as functions of distance.
+Figure 6, below, depicts the predicted probabilities from the models (see Table 1) as functions of distance.
 
-```{r Figure 7, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 6, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
@@
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
-  geom_jitter(alpha=1, size=1)+
+  geom_jitter(alpha=1, size=1) +
   geom_smooth(size = .5, se=FALSE) +
@@
   ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76),
-                    y = c(0.5,0.55,0.5,0.55),
-                    label = c("Brasilia","Sao Paulo", "New York", "Paris"), alpha = 0.4) +
+                    y = c(0.45,0.5,0.47,0.5),
+                    label = c("Brasilia", "Sao Paulo", "New York", "Paris"), alpha = 0.4) +
   scale_y_continuous(labels = percent_format()) +
@@
 \begin{landscape}
+
 ```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
@@
 ````
+
+```{r Figure 7, fig.cap="Amazonian speeches in time and space", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+perc_in <- pop %>%
+   mutate(location_cat = ifelse(grepl("International|Non Identified",
+                                      location_cat),
+                                "Outside of Brazil", "In Brazil")) %>%
+  filter(location_cat == "In Brazil") %>% 
+  count(amazon_speech, year, location_cat) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>%
+  select(c(perc, amazon_speech, year, location_cat))
+perc_out <- pop %>%
+   mutate(location_cat = ifelse(grepl("International|Non Identified",
+                                      location_cat),
+                                "Outside of Brazil", "In Brazil")) %>%
+  filter(location_cat == "Outside of Brazil") %>% 
+  count(amazon_speech, year, location_cat) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>%
+  select(c(perc, amazon_speech, year, location_cat)) 
+# location plots
+Amazon_year_in <- perc_in %>%
+  ggplot(., aes(x = year, y = perc))+
+  geom_line(color="darkgreen")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  annotate("text", x = 1985, y = 0.17, label = "16.17%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.39, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.36, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.28, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.24, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.28, label = "August Fires", size=3) +
+  scale_y_continuous(labels = percent_format())+
+  labs(x = "", y = "",
+       title = "Share of speeches inside Brazil",
+       subtitle= " 4344 speeches out of 6130",
+       color='Y series') +
+  theme_am()
+Amazon_year_out <- perc_out %>% 
+  ggplot(., aes(x = year, y = perc))+
+  geom_line(color="darkgreen")+
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  annotate("text", x = 1985, y = 0.165, label = "15.49%", size = 3.5)+  
+  annotate("text", x = 1988.7, y = 0.39, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1992, y = 0.36, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.28, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.24, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.28, label = "August Fires", size=3)+
+  scale_y_continuous(labels = percent_format())+
+  labs(x = "", y = "",
+ title = "Share of speeches outside Brazil",
+       subtitle= " 1786 speeches out of 6130",
+       color='Y series') +
+  theme_am()
+grid.arrange(Amazon_year_in, Amazon_year_out, nrow=2)
+```

### 2022-09-07 Draft_September_2022/Full_draft_20220901.rmd
#corrections on references #problem construction -> problem-construction #added acknowledgements and declaration of interest #knitting nicely!

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "1 September 2022"
+date: "7 September 2022"
 output:
@@
 amazon_def_year$area <- amazon_def_year$def_year*1000
-# Prepare data for problem constructions
+# Prepare data for problem-constructions
 sov <- ama %>% 
@@
 Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015], and many others.
+Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015], and many others.
 Nevertheless, the role of the president remains understudied.
@@
 Second, the same government adopts a diverse range of problem-constructions over time.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem constructions from 2011 to 2016.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem-constructions from 2011 to 2016.
 Constructing the Amazon as an issue of sovereignty has increasingly become more pertinent after 2010.
@@
 This article proceeds as follows: first, we propose a conceptual framework to understand problem-construction in discourses.
-We then review Amazonian historiography literature to identify the main phases and their underlying problem construction.
+We then review Amazonian historiography literature to identify the main phases and their underlying problem-construction.
 In the methodology section, we explain how the framework is operationalized and present the codebook.
@@
   annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.27, label = "Earth Summit", size = 3)+
+  annotate("text", x = 1992.5, y = 0.27, label = "Earth Summit", size = 3)+
   annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
   annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "August Fires", size=3) +
+  annotate("text", x = 2019, y = 0.26, label = "2019 Record August Fires", size=3) +
   labs(x = "", y = "",
-       title = "Share of speeches that mention the Amazon per year (n=6130)",
-       subtitle = "We annotate five local maxima with highest frequencies.",
+       title = "Share of speeches that mention the Amazon per year",
+       subtitle = "Sample composed by all 6130 speeches since 1985",
        color='Y series') +
@@
 def_rates <- ggplot(amazon_def_year, aes(x = year)) +
-  geom_line(aes(y = area), color= "darkolivegreen", linetype="dotted", size= 1.5)+
-  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.75)+
-  annotate("text", x = 2004, y = 29000,
-           label = "2004 Plan to Combatand Control Deforestation", size = 3) +
+  geom_line(aes(y = area), color= "darkolivegreen", linetype="twodash", size= 0.5)+
+  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.5)+
+  annotate("text", x = 2005, y = 29000,
+           label = "2004 Plan to Combat and Control Deforestation", size = 3) +
   annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 3) +
@@
 
-### Pure-type problem constructions
+### Pure-type problem-constructions
 
-We conceptualize four problem constructions: sovereignty, economic integration, social development, and conservation.
+We conceptualize four problem-constructions: sovereignty, economic integration, social development, and conservation.
 Figure 4, below, illustrates the share of each pure-type in time.
-Pure problem constructions dominate, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
+Pure problem-constructions dominate, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem-constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
 Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
@@
   ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size =1, linetype="solid") +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size =0.75, linetype="solid") +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
 
-### Mixed-type problem constructions
+### Mixed-type problem-constructions
 
-At the level of the speech presidents might mix multiple problem constructions.
+At the level of the speech presidents might mix multiple problem-constructions.
 Although presidents prefer pure problem-constructions, they also construct the Amazon as a multifaceted issue.
-Mixed-type problem constructions in discourse offer more intricate understandings of the Amazon as a problem.
+Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
 Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
@@
 
-The most frequent mixed-type problem construction of the Amazon is economic conservation.
+The most frequent mixed-type problem-construction of the Amazon is economic conservation.
 This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased in time.
@@
 
-```{r Figure 6, fig.cap="Percent of problem constructions across locations", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure 6, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
@@
   geom_smooth(size = .5, se=FALSE) +
-  geom_vline(xintercept = c(1933.78, 2771.49, 5075.48, 8306.76), linetype = "dotted") +
-  ggplot2::annotate(geom = "text", x = c(1933.78,2771.49 , 5075.48, 8306.76),
-                    y = c(0.45,0.5,0.47,0.5),
-                    label = c("Brasilia", "Sao Paulo", "New York", "Paris"), alpha = 0.4) +
   scale_y_continuous(labels = percent_format()) +
@@
        y = "",
-       title = "Predicted share of each problem-construction as a function of distance from the Amazon",
+       title = "Predicted share of each problem-construction as a function of\ndistance from the Amazon",
        subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
-       caption = "Curve in the plot is estimated using loess method.") +
+       caption = "Curves in the plots are estimated using loess method.") +
     theme_am() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom")+
+  facet_wrap(~p_c, ncol=3)
+
 all_loc
@@
                                                "Election year", "Yearly Deforestation",
-                                               "Yearly   Inflation"), no.space = TRUE)
+                                               "Yearly   Inflation"), no.space = TRUE,
+                          title = "Logistic Regressions Output")
 ```
@@
 Second, the same government adopts a diverse range of problem-construction.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, temporarily surpassing economic integration as a more common problem construction from 2010 to 2015.
+While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, temporarily surpassing economic integration as a more common problem-construction from 2010 to 2015.
 This implies an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.
@@
 
-\newpage
+# Acknowledgements
+
+The authors are extremely grateful to Graziella Moraes Silva and James Hollway for their support.
+The authors would also like to thank Matias, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
+
+# Disclosure Statement
+
+The authors report there are no competing interests to declare.
+
 # References
@@
 <div id="refs"></div>
+\newpage
 
 # Appendix
-
-````{=tex}
-\begin{landscape}
-
-```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble("Problem Construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
-                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
-We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
-It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
-It advances the view that Amazon is full of citizens who should have their rights guaranteed.
-This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
-This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
-This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
-I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
-I would like to thank the Chinese government.
-For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
-(Bolsonaro 25/10/2019)",
-                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
-We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
-                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
-We have invested over 14 billion reais in this program, in three and a half years.
-Do you know how many electrical lines we have already built?
-One million kilometers of lines.
-(Lula 20/11/2009)",
-                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
-This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
-Mesquita (Sarney 20/07/1989)"))
-
-kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
-```
-
-\end{landscape}
-````
 
@@
 ```
+
+````{=tex}
+\begin{landscape}
+
+```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+codebook <- tibble::tibble("problem-construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
+                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
+Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
+It advances the view that the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
+It advances the view that Amazon is full of citizens who should have their rights guaranteed.
+This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
+This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
+Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
+This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
+The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
+I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019)",
+                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
+This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
+                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+We have invested over 14 billion reais in this program, in three and a half years.
+Do you know how many electrical lines we have already built?
+One million kilometers of lines.
+(Lula 20/11/2009)",
+                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
+Mesquita (Sarney 20/07/1989)"))
+
+kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
+```
+
+\end{landscape}
+````

### 2022-09-09 Draft_September_2022/Full_draft_20220901.rmd
#implementedgrammarcorrectionsfromAnna #polishedfigure4 #correctedafewplotannotations

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "7 September 2022"
+date: "9 September 2022"
 output:
-  pdf_document: default
+  html_document:
+    df_print: paged
   latex_engine: xelatex
   fig_caption: yes
-  html_document:
-    df_print: paged
+  pdf_document: default
 fontsize: 12pt
@@
    - |
-    ```{=latex}
     \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
     \providecommand{\wordcount}[1]{\text{Word Count:}#1} 
-    ```
 always_allow_html: TRUE
@@
 csl: chicago.csl
-abstract: Presidential speeches influence the ways we think about, and act towards, the environment transnationally.
-Still, these remain understudied in this context.
+abstract: Presidential speeches influence the ways we think about and act towards the environment transnationally, but they are understudied.
 We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses along time and space.
 Using supervised machine learning, we classify statements about the Amazon in 6130 presidential speeches since 1985.
-We find that national and international events drive the frequency of the Amazon as a topic in presidential speeches inside and outside Brazil.
-While constructing the Amazon a problem of economic integration dominates discourses until the mid-2000s, environmental conservation and social development constructions increase in relevance and temporarily surpass economic integration from 2010 to 2015.
+We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches inside and outside Brazil.
+While constructing the Amazon as a problem of economic integration dominates discourses until the mid-2000s, environmental conservation and social development constructions increase in relevance and temporarily surpass economic integration from 2010 to 2015.
 In turn, constructing the Amazon as an issue of sovereignty steadily increases since 2010.
-Lastly, the farthest presidents are from the Amazon, the more likely they are to construct the Amazon as an issue of environmental conservation.
+Lastly, the farthest away presidents are from the Amazon itself, the more likely they are to construct the Amazon as an issue of environmental conservation.
 ---
@@
   unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure Sovereignty",
+  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure National Sovereignty",
                                    mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                    mixed_type == '0_0_1_0' ~ "Pure Social Development",
-                                   mixed_type == '0_0_0_1' ~ "Pure Conservation",
+                                   mixed_type == '0_0_0_1' ~ "Pure Environmental Conservation",
                                    mixed_type == '0_0_0_0' ~ "Other",
@@
                                          mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Conservation",
+         levels = c("Pure Economic Integration", "Pure Environmental Conservation",
                     "Pure Social Development",
-                    "Pure Sovereignty", "Other", "Economic Conservation", 
+                    "Pure National Sovereignty", "Other", "Economic Conservation", 
                     "Social Economic", "Sovereign Conservation",
@@
                     "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
-         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Conservation|
-                                   |Pure Social Development|Pure Sovereignty",
+         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Environmental Conservation|
+                                   |Pure Social Development|Pure National Sovereignty",
                                    mx_cat) ~ "Pure-types",
@@
 
-We need to protect the Amazon from foreign interests.
+*We need to protect the Amazon from foreign interests.
 We need to exploit the Amazon’s natural resources.
 We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.
-Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
+We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
 These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
@@
 We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-While the military dictatorship is associated with understanding the Amazona as issues of national sovereignty and economic integration, Sarney’s and Lula’s presidencies are often tied to environmental conservation views.
+While the military dictatorship is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s and Lula’s presidencies are often tied to environmental conservation views.
 These monolithic representations advance that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
@@
 Second, we argue that presidents can deploy problem-constructions that build policy objects as different problems depending on whom they are speaking to.
-Presidential discourses take place in different sites, from launching a new bridge in a small municipality in the middle of the Amazon to a speech at the UN general assembly in New York.
+Presidential discourses take place in different settings, from launching a new bridge in a small municipality in the middle of the Amazon to a speech at the UN general assembly in New York.
 Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is discursively constructed in transnational politics.
@@
 To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazonian-related statements within these speeches.
+We subset the dataset by identifying Amazon-related statements within these speeches.
 We find that 2014 sections in these discourses refer to the Amazon at least once.
 We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of Amazonian-related statements.
+We use this codebook to manually code a randomly selected training set of Amazon-related statements.
 We train a supervised machine-learning model to automatically label the remaining set of Amazonian statements.
@@
 First, we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (UNFCCC Summits).
+the assassination of Chico Mendes) as well as international events (Climate Summits).
 Second, the same government adopts a diverse range of problem-constructions over time.
@@
 Constructing the Amazon as an issue of sovereignty has increasingly become more pertinent after 2010.
-Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move away from the Amazon region.
-That is, presidents, talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.
+Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move farther away from the Amazon region.
+That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relates to policies.
+Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
 
@@
 Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
-Chosen problems are those governments select at their discretion.
+Chosen problems are those that governments select at their discretion.
 Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-The author exemplifies chosen problems with the case of the construction of Brasilia.
+Hirschman exemplifies chosen problems with the case of the construction of Brasilia.
 
 @bacchi2009 [p.
-10] argues that policies have a cultural dimension as “it takes shape within specific historical and national or international contexts”.
+10] argues that policies have a cultural dimension as they take“ shape within specific historical and national or international contexts”.
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed, this is a policy object.
-We conceptualize policy objects as a problem that demands dedicated policy attention.
-The alleged problem is not always explicitly stated in policy: policies are represented as solutions for implicit problems.
+We conceptualize policy objects as a problems that demand dedicated policy attention.
+The alleged problem is not always explicitly stated in a policy: policies are represented as solutions for implicit problems.
 Building Brasilia (the policy object), thus, could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three depending on how governments speak about it.
@@
 Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-Relative to how the policy is represented to be, it can be a solution to problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-@putnam1988 seminal article on the two-level game can help us make sense of this variation conceptually.
-The author argues that the outcomes of international negotiations lie within the overlap between the agenda (and pressure) of domestic groups and international groups.
-If policies are socially constructed, and consequently their implicit problem can vary, governments can in theory construct them to meet the expectations of both.
+Depending on how the policy is represented to be, it can be portrayed as a solution to problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
+@putnam1988's seminal article on the two-level game can help us make sense of this variation conceptually.
+The author argues that the outcomes of international negotiations lie within the overlap between the agenda (and pressure) of domestic and international groups.
+If policies are socially constructed, governments can in theory construct them to meet the expectations of both.
 Consequently, this entails that governments are more diverse in their opinions, rather than monolithic.
 
-An interesting site to study the relationship between problem-construction and policy objects is presidential speeches, as they legitimize ways of thinking about an issue.
+An interesting context to study the relationship between problem-construction and policy objects is presidential speeches, as they legitimize ways of thinking about an issue.
 While the relationship between presidential speeches and policy may not be causal, they have the power to introduce and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004; @gillion2016].
@@
 
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-[@calderwood2019], for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
-Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change, even as frames move from focusing on economics to focusing on security aspects of climate change.
+The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
+Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change.
 Building on @putnam1988, @calderwood2020 demonstrates that American presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
@@
 There is also an empirical gap in terms of how the Amazon, specifically, has been constructed as a problem along time and geographic location in political discourses.
-Whereas governmental discourses in Brazil have been studied for topics such as inflation or race relations [see @silva2019], the environment remains absent.
+While governmental discourses in Brazil have been studied for topics such as inflation or race relations [see @silva2019], the environment remains largely absent.
 An exception is @barros2020, who investigates Amazonian discourse in the Brazilian Congress.
@@
 The presidencies of Dilma and Temer are connected to the decline of conservationist policies, while Bolsonaro to the dismantling of environmental policies.
-Whereas these works are important to understand how different governments acted toward the Amazon, the classification of specific governments into policy periods, or policy cycles, represents them as monolithic: they associate specific governments with one specific view of the Amazon.
+Although these works are important to understand how different governments have acted toward the Amazon, the classification of specific governments into policy periods, or policy cycles, represents them as monolithic: they associate specific governments with one specific view of the Amazon.
 
@@
 The variation in problem-construction suggests that Brazilian governments are more diverse in their positions than the literature suggests.
-An interesting site to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for policymaking, and environmental outcomes.
+An interesting context to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for policymaking, and environmental outcomes.
 As presidents speak in different places and to diverse audiences, it is an empirical site prone to identifying variation.
@@
 The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched Operation Amazon, a policy to modernize the region based on three assumptions @acker2021.
-First, it assumes that nature should be conquered by men.
-Second, it assumes that exploiting natural resources would render the Amazon region economically profitable.
+In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions @acker2021.
+First, it assumes that nature should be conquered by mankind Second, it assumes that exploiting natural resources would render the Amazon region economically profitable.
 Third, it assumes that populating the region was necessary to integrate it into the country and exert control over the territory.
-Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
-@capobianco2019 describes the period from the 1950s to the 1980s in relation to the wider range of policies of economic integration, often centralized by the federal government [see @becker2005].
-The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
+Concretely, this meant a series of major infrastructural projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
+@capobianco2019 and @becker2005 describe the period from the 1950s to the 1980s in similar vein, as one of often centralized economic policies by the federal government.The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
 These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
@@
 @capobianco2019 argues that socio-environmentalism informed a series of policies throughout the 1990s and early 2000s towards preserving the forest, such as the establishment of several conservation units in the Amazon in 2001.
-The environmental conservation problem-constructions emphasize the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
+The environmental conservation problem-constructions emphasize that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
 The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
@@
 @acker2021 [p.
-10], for example, argues that during the military dictatorship attempts to populate the Amazon was seen, among other things, as a solution for the country’s growing social inequalities elsewhere.
+10], for example, argues that during the military dictatorship attempts to populate the Amazon were seen, among other things, as a solution for the country’s growing social inequalities elsewhere.
 As democracy established itself in Brazil, the settlers from the military dictatorship became electorates with constitutional rights.
-@hochstetler2007 argue that with the transition to democracy, the mobilization of diverse social movements to demand social equality and conservation was an integral part of the socio-environmentalism movement in Brazil.
-Whereas indigenous rights and preservation of the forest go hand in hand, it is not clear that providing better standards of livings to the large and poor populations of the state and preservation do; perhaps this is also why there was never an open consensus about socio-environmentalism in Brazil [@hochstetler2007].
-While related to economic integration and environmental conservation, social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
+@hochstetler2007 argue that with the transition to democracy, the mobilization of diverse social movements to demand social equality and conservation was an integral part of the socio-environmentalist movement in Brazil.
+While indigenous rights and preservation of the forest go hand in hand, it is not clear whether providing better standards of livings to the large and poor populations of the state and preservation do; perhaps this is also why there was never an open consensus about socio-environmentalism in Brazil [@hochstetler2007].
+Although related to economic integration and environmental conservation, social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
 The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
@@
 In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
-We find that 946 speeches are, at least partially, about the Amazon from the 6130.
+We find that 946 speeches are, at least partially, about the Amazon out of the 6130.
 
@@
 We opt for picking two sentences before and two sentences after, rather than words because sentences usually contain a cohesive idea.
-By doing so we create our unit of analysis: an Amazonian statement.
+By doing so we create our unit of analysis: an Amazon statement.
 We use Amazon statements as our unit of analysis for two main reasons.
 First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-Second, it increases the number of our observations and their variety meaningfully, allowing for more specificity in our analysis.
+Second, it increases the number of observations and their variety meaningfully, allowing for more specificity in the analysis.
 This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
@@
 This amount refers to 50% of all the Amazon Statements identified.
-We chose to hand code half of the observations because since there are several nuances in discourse in how presidents talk about the amazon in time and as a problem, we conservatively code a relatively large training set for the subsequent automated machine learning.
+We chose to hand.code half of the observations because since there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem, we conservatively coded a relatively large training set for the subsequent automated machine learning.
 As well, this allows a robust validation set to verify the models.
@@
 Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-Intercoder agreement for each of the four main categories was 85%, on average.
+The intercoder agreement for each of the four main categories was 85%, on average.
 For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
@@
 Our codebook is developed using specific Amazon-related vocabulary.
-For example, a statement will be coded as economic integration if it is meaningful support for the tax-free zone of Manaus or a Dam in the Amazon.
-However, the economy is generally a topic that presidents speak about.
-Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil in time.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+For example, a statement will be coded as economic integration if it is meaningful support for the tax-free zone of Manaus or a dam in the Amazon.
+However, the economy is generally a topic that presidents speak about frequently.
+Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
 We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
@@
 On average, presidents mention the Amazon in 15% ^[For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).] of their speeches.
-The frequency in which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
+The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
 
@@
   annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
-  annotate("text", x = 1988.7, y = 0.34, label = "Chico Mendes", size = 3)+
+  annotate("text", x = 1988.7, y = 0.35, label = "The Murder of\nChico Mendes", size = 3)+
   annotate("text", x = 1992.5, y = 0.27, label = "Earth Summit", size = 3)+
@@
   annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "2019 Record August Fires", size=3) +
+  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
   labs(x = "", y = "",
@@
 From 1985 to 1988, the mentions of the Amazon in official speeches increased from 4% to 14%.
-During this period the latest Brazilian Constitution, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990], was written.
+During this period, the latest Brazilian Constitution, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990], was written.
 In 1989, however, the Amazon appeared in 32% of all speeches.
@@
 Disagreements related to the priority of environmental preservation over economic development, most notably in the case of approval of the New Forest Code in 2012, which regularized land ownership of many illegally deforested areas, were frequent.
-The period was also marked by of political and economic instability which culminated in the impeachment of Rousseff.
+The period was also marked by political and economic instability which culminated in the impeachment of Rousseff in 2016.
 In 2015, the Amazon appeared in 19% of all speeches.
@@
 We subsequently observe a steady increase from 6% in 2016 to 24% in 2019, the first year of Bolsonaro’s presidency.
-At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon leading up to the red sky afternoon in São Paulo in August 2019.
+At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon led up to a red sky afternoon in São Paulo in August 2019.
 Alongside this, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
@@
 
-The frequency in which the Amazon appears in domestic and international speeches varies in similar ways as the spikes in the topic frequency, led by the events discussed above, appear within and outside Brazil.
-We interpret this as evidence that relevant events drive interest and alter how pressing the “Amazon problem” is perceived both nationally and internationally.
+The frequency at which the Amazon appears in domestic and international speeches varies in similar ways as the maxima in the topic frequencies, led by the events discussed above, appear within and outside Brazil (see Figure 7 appendix).
+We interpret this as evidence that relevant events drive interest and alter how pressing the Amazon as a policy object is perceived both nationally and internationally.
 This does not mean, though, that when presidents speak about the Amazon, they highlight the same issues.
@@
 
-Our subsequent analysis of pure-types and mixed-types suggests that governments do not defend a view of the Amazon.
+Our subsequent analysis of pure-types and mixed-types suggests that governments do not defend a specific view of the Amazon.
 The same governments construct the Amazon as various pure and mixed type problems, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
@@
 Brazilian presidents after Cardoso moved from employing one problem-constructions consistently to a more diverse strategy.
-During Lula’s terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon as issues of environmental conservation and social development increased.
-Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during the Rousseff administration.
+During Lula’s terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon issues of environmental conservation and social development increased.
+Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during Rousseff's administration.
 Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or time in discourses as economic integration was until the early 2000s.
-Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching its highest frequencies with the presidencies of Bolsonaro.
+Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.
 
@@
   theme_am() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
+
 pure_types_time
@@
 
-At the level of the speech presidents might mix multiple problem-constructions.
+In a speech, presidents might mix multiple problem-constructions within a same statement about the Amazon.
 Although presidents prefer pure problem-constructions, they also construct the Amazon as a multifaceted issue.
@@
 
-The most frequent mixed-type problem-construction of the Amazon is economic conservation.
-This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased in time.
-Its increase over time suggests that later presidents, along with being more diverse in how they constructed the amazon as an issue (see Figure 4), increasingly find ways to reconcile the dictum between the economy and the environment that prevailed in the previous years.
+The most frequent mixed-type problem construction of the Amazon is economic conservation.
+This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
+This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue (see Figure 4), increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
 The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-This is not surprising, as developing countries like Brazil repeatedly claim a “right to develop” when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
-Nonetheless, there is a general increase of mixed-types in time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
+This is not surprising, as developing countries like Brazil repeatedly claim a “right to develop”, when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
+Nonetheless, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
 
 Both Lula and Bolsonaro construct the Amazon as a multifaceted issue more frequently than other presidents.
-Lula usually mixes economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
+Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
 
@@
 The Amazon region, forests, and peoples have historically been the topic of local, national, and international debates.
-This implies that audiences’ priorities in each setting change and which policies are appropriate to solve the “Amazon issue” differ as well.
-As presidents move away from the Amazon, audiences might have different stakes and interests in it.
+This implies that audiences’ priorities in each setting change and  consequently which policies are appropriate to solve the “Amazon issue” differ as well.
+As presidents physically move farther away from the Amazon, audiences might have different stakes and interests in it.
 While speeches inside the Amazon might focus on social development, for example, speeches in the United Nations in New York might highlight environmental conservation.
@@
                     mx_cat != "Other Mixed-types") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Conservation", 1, 0),
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
          EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
          SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
-         sov_vs_all = ifelse(mx_cat == "Pure Sovereignty", 1, 0))
+         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
 # model
@@
     theme_am() +
-  theme(legend.position = "bottom")+
+  theme(legend.position = "none")+
   facet_wrap(~p_c, ncol=3)
@@
 
-This paper investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
+This paper investigates how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
 Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (UNFCCC Summits).
+the assassination of Chico Mendes) as well as international events (Climate Summits).
 Second, the same government adopts a diverse range of problem-construction.
@@
 Not long-standing because the dismantling of environmental policy in favor of infrastructure and agricultural expansion was already on its way in the late 2010s.
-The Belo Monte Dam in the late 2000s and the 2012 New Forest Code is seen as a turning point: political opposition to conservation got particularly organized and managed to lobby the executive and won these battles even though they were largely opposed by environmentalists.
+The 2012 New Forest Code is seen as a turning point: political opposition to conservation organized itself and managed to lobby with the executive and won these battles even though they were largely opposed by environmentalists.
 
-The steady increase of sovereignty starting in 2010 brings an eerie twist.
+The steady increase of sovereignty problem-constructions starting in 2010 brings an eerie twist.
 As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
 The embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
-Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change.
+Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change in politics.
 The political forces in Brazilian democracy that drove these policy and discursive changes in problem-construction were long in the making, Bolsonaro’s problem-constructions and policies are the strongest forms of this shift.
@@
 The authors are extremely grateful to Graziella Moraes Silva and James Hollway for their support.
-The authors would also like to thank Matias, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
+The authors would also like to thank Matias, Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
 

### 2022-09-09 Draft_September_2022/Full_draft_20220901.rmd
#implementedgrammarcorrectionsfromAnna #polishedfigure4 #correctedafewplotannotations

@@
     theme_am() +
-  theme(legend.position = "none")+
+  theme(legend.position = "bottom")+
   facet_wrap(~p_c, ncol=3)

### 2022-09-10 Draft_September_2022/Full_draft_20220901.rmd
#lastchangesfromworddraft

--- 2022-09-09 Draft_September_2022/Full_draft_20220901.rmd
@@
 output:
+  pdf_document: default
+  latex_engine: xelatex
+  fig_caption: yes
   html_document:
     df_print: paged
-  latex_engine: xelatex
-  fig_caption: yes
-  pdf_document: default
 fontsize: 12pt
@@
 abstract: Presidential speeches influence the ways we think about and act towards the environment transnationally, but they are understudied.
-We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses along time and space.
+We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses across time and space.
 Using supervised machine learning, we classify statements about the Amazon in 6130 presidential speeches since 1985.
@@
 We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
-These specific problems touch on shared imaginaries of the Amazon as part of the larger socio-cultural history of the country, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
+These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
 
@@
 We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-While the military dictatorship is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s and Lula’s presidencies are often tied to environmental conservation views.
+While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s  (1985-1990) and Lula’s (2003-2010)presidencies are often tied to environmental conservation views.
 These monolithic representations advance that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
@@
 Building on @hirschman1963 conceptualization of chosen problems and @bacchi2009 theory of problem-representation in policy, we propose a framework for identifying problem-constructions in discourse and investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
-We understand transnationalism^[ We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998]
+We understand transnationalism^[ We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998].
 
@@
 While the relationship between presidential speeches and policy may not be causal, they have the power to introduce and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004; @gillion2016].
-As presidents speak across several locations to various audiences, they frame similar issues differently.
+As presidents speak across several locations to various audiences, they construct similar issues differently.
 
 The possibility of different problem-constructions in presidential speeches has important implications for democracy.
-With globalization and the increase of transnational processes, presidents have the opportunity of promoting different problem-constructions transnationally.
+With globalization, presidents have the opportunity of promoting different problem-constructions transnationally.
 It is important to understand, thus, to what extent the implemented policy agenda correlates with problem-constructions promoted at the local, federal, or international levels.
@@
 The governments from the late 1980s up to 2009 are associated with a turn towards policies that focus on environmental conservation.
-The presidencies of Dilma and Temer are connected to the decline of conservationist policies, while Bolsonaro to the dismantling of environmental policies.
+The presidencies of Dilma and Temer (2011-2018) are connected to the decline of conservationist policies, while Bolsonaro to the dismantling of environmental policies.
 Although these works are important to understand how different governments have acted toward the Amazon, the classification of specific governments into policy periods, or policy cycles, represents them as monolithic: they associate specific governments with one specific view of the Amazon.
@@
 Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-The intercoder agreement for each of the four main categories was 85%, on average.
+The intercoder agreement for hand-coded categories was 85%, on average.
 For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
@@
 In 1989, however, the Amazon appeared in 32% of all speeches.
-This spike correlates with the brutal murder of Chico Mendes in the last days of 1988.
+This maximum correlates with the brutal murder of Chico Mendes in the last days of 1988.
 The incident caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021], including accepting to host the 1992 Earth Summit [@keck1998].
@@
 One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Program, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-Throughout the rest of the 1990s and 2000s, during the Cardoso and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another spike in mentions of the Amazon.
+Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another maximum in mentions of the Amazon.
 This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 3, below, illustrates.
@@
 In 2015, the Amazon appeared in 19% of all speeches.
-This spike coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
+This maximum coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
 Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
@@
 Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during Rousseff's administration.
-Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or time in discourses as economic integration was until the early 2000s.
-Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.
+Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or periods in time in discourses as economic integration was until the early 2000s.
+Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
 
@@
 Alternatively, as deforestation increases, presidents are more likely to construct the amazon as an issue of economic integration.
-This indicates that Brazil creates a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
+This indicates that Brazil created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
 In the same fashion, economic integration problem-constructions are likely deployed as a justification for increasing deforestation rates.
@@
 The steady increase of sovereignty problem-constructions starting in 2010 brings an eerie twist.
-As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
 The embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.

### 2022-09-12 Draft_September_2022/Full_draft_20220901.rmd
#newparagraphontransnationalism

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "9 September 2022"
+date: "12 September 2022"
 output:
@@
 ```
-
 ```{=latex}
-\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
+\wordcount{ 8477 (including abstract, text, references, and and footnotes)}
 ```
-
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 *We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon’s natural resources.
+We need to exploit the Amazon's natural resources.
 We need to provide better living standards for the people in the Amazon.
@@
 We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s  (1985-1990) and Lula’s (2003-2010)presidencies are often tied to environmental conservation views.
+While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are often tied to environmental conservation views.
 These monolithic representations advance that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
@@
 Building on @hirschman1963 conceptualization of chosen problems and @bacchi2009 theory of problem-representation in policy, we propose a framework for identifying problem-constructions in discourse and investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
-We understand transnationalism^[ We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998].
+We understand transnationalism[^1] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998].
+
+[^1]: We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably
 
@@
 
-In “Journey towards Progress”, @hirschman1963 draws a conceptual distinction between pressing problems (pressured by outside parties to the government) and chosen problems (chosen by the government at their discretion).
+In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured by outside parties to the government) and chosen problems (chosen by the government at their discretion).
 Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
@@
 Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-Hirschman exemplifies chosen problems with the case of the construction of Brasilia.
+@hirschman1975 (favourite) example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia.
 
 @bacchi2009 [p.
-10] argues that policies have a cultural dimension as they take“ shape within specific historical and national or international contexts”.
+10] argues that policies have a cultural dimension as they take" shape within specific historical and national or international contexts".
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed, this is a policy object.
@@
 
-The possibility of different problem-constructions in presidential speeches has important implications for democracy.
+The possibility of different problem-constructions in presidential speeches has important implications for democracy and global politics.
 With globalization, presidents have the opportunity of promoting different problem-constructions transnationally.
+We understand transnationalism as relationships that transcend nation-states, from the local level to the international level encompassing non-state actors [@keck1998].
+The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020).
+Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
+This is partially because the forest is a key biome in global climate-mitigation.
 It is important to understand, thus, to what extent the implemented policy agenda correlates with problem-constructions promoted at the local, federal, or international levels.
-Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
-Deforestation rates in Brazil are more responsive to the government’s environmental policy, generated from material and discursive governmental practices than exogenous factors such as market fluctuations [@assuncao2015; @capobianco2019; @capobianco2021].
-Specifically, @capobianco2021 finds that the perception of a higher risk of being caught for deforestation in the Amazon is the main mechanism through which environmental policy is effective.
-Furthermore, ethnographic research has also shown that expectations about governments’ responses are a crucial factor in decisions to deforest on the ground [@campbell2015].
-Understanding variation in presidential speeches is the first step to connecting it to concrete environmental outcomes.
 
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
+The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
+@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
 Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change.
 Building on @putnam1988, @calderwood2020 demonstrates that American presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-Elsewhere, @bevitori2015 finds that mentions of the environment are typically co-selected with the pronoun ‘our’, as well as with ‘economy’, ‘clean’, and ‘preserve’.
+Elsewhere, @bevitori2015 finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
 While these studies corroborate the possibilities of variation depending on the audience, they fail to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
-That is, problem-constructions touch on shared meanings available to both the speaker and the audiences as part of larger social-cultural history [see @bacchi2009], therefore, mentions to the lexicon as ‘environment’, ‘preserve’, or ‘climate change should be tied to the larger meaning of policies in the United States.
+That is, problem-constructions touch on shared meanings available to both the speaker and the audiences as part of larger social-cultural history [see @bacchi2009], therefore, mentions to the lexicon as 'environment', 'preserve', or 'climate change should be tied to the larger meaning of policies in the United States.
 
@@
 @hecht1990 [p.
-1] write that “what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites”.
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+1] write that "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites".
+In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
 8], and when the dust settled and the scramble was over, over half of the Amazon emerged Brazilian.
 While Brazilian military diplomacy was very successful, the process did not come without its traumas as the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 aimed at protecting Brazil’s sovereignty over the Amazon.
+These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 aimed at protecting Brazil's sovereignty over the Amazon.
 As we move from a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
 Threats to national sovereignty, consequently, broaden from state actors to a wide set of actors.
-Claims of attempts to ‘internationalize’ the Brazilian Amazon, for instance, are targeted at foreign actors as well as domestic non-state actors.
+Claims of attempts to 'internationalize' the Brazilian Amazon, for instance, are targeted at foreign actors as well as domestic non-state actors.
 The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
@@
 
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
 However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
 @acker2021 [p.
-10], for example, argues that during the military dictatorship attempts to populate the Amazon were seen, among other things, as a solution for the country’s growing social inequalities elsewhere.
+10], for example, argues that during the military dictatorship attempts to populate the Amazon were seen, among other things, as a solution for the country's growing social inequalities elsewhere.
 As democracy established itself in Brazil, the settlers from the military dictatorship became electorates with constitutional rights.
@@
 Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
-We do so by detecting all speeches in which the stem “amazon” appears.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We do so by detecting all speeches in which the stem "amazon" appears.
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
 We find that 946 speeches are, at least partially, about the Amazon out of the 6130.
 
-Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
 We opt for picking two sentences before and two sentences after, rather than words because sentences usually contain a cohesive idea.
@@
 This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
-When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
+When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
 On average, an Amazonian statement contains 123 words.
@@
 However, the economy is generally a topic that presidents speak about frequently.
-Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
 Hence, we might be missing statements about Amazon that do not refer to it.
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15% ^[For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).] of their speeches.
+On average, presidents mention the Amazon in 15% [^2] of their speeches.
 The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
+
+[^2]: For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).
 
@@
 This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 3, below, illustrates.
-Lula led the delegation to Copenhagen with a self-image of “we do not promise, we deliver” when the stakes about climate change were high [@franchini2019].
+Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
 
@@
 
-We subsequently observe a steady increase from 6% in 2016 to 24% in 2019, the first year of Bolsonaro’s presidency.
+We subsequently observe a steady increase from 6% in 2016 to 24% in 2019, the first year of Bolsonaro's presidency.
 At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon led up to a red sky afternoon in São Paulo in August 2019.
-Alongside this, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
-Bolsonaro went on to retrieve Brazil’s hosting status for COP25.
+Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
+Bolsonaro went on to retrieve Brazil's hosting status for COP25.
 
@@
 Brazilian presidents after Cardoso moved from employing one problem-constructions consistently to a more diverse strategy.
-During Lula’s terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon issues of environmental conservation and social development increased.
+During Lula's terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon issues of environmental conservation and social development increased.
 Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during Rousseff's administration.
@@
 The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-This is not surprising, as developing countries like Brazil repeatedly claim a “right to develop”, when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
+This is not surprising, as developing countries like Brazil repeatedly claim a "right to develop", when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
 Nonetheless, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
@@
 The Amazon region, forests, and peoples have historically been the topic of local, national, and international debates.
-This implies that audiences’ priorities in each setting change and  consequently which policies are appropriate to solve the “Amazon issue” differ as well.
+This implies that audiences' priorities in each setting change and consequently which policies are appropriate to solve the "Amazon issue" differ as well.
 As presidents physically move farther away from the Amazon, audiences might have different stakes and interests in it.
@@
 Alternatively, as deforestation increases, presidents are more likely to construct the amazon as an issue of economic integration.
-This indicates that Brazil created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
+This indicates that Brazil, indeed, created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019], without any international obligations to do so[@hochstetler2012a].
 In the same fashion, economic integration problem-constructions are likely deployed as a justification for increasing deforestation rates.
@@
 The steady increase of sovereignty problem-constructions starting in 2010 brings an eerie twist.
-The embryo of Bolsonaro’s Amazonian discourse was breeding half a decade before he took office.
+The embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
 Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change in politics.
-The political forces in Brazilian democracy that drove these policy and discursive changes in problem-construction were long in the making, Bolsonaro’s problem-constructions and policies are the strongest forms of this shift.
+The political forces in Brazilian democracy that drove these policy and discursive changes in problem-construction were long in the making, Bolsonaro's problem-constructions and policies are the strongest forms of this shift.
 
@@
 
-<div id="refs"></div>
+::: {#refs}
+:::
+
 \newpage

### 2022-09-14 Draft_September_2022/Full_draft_20220901.rmd
#finalminorcorrections

@@
 We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem.
-These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country, for example, in relation to issues of national sovereignty, economic integration, social development, or environmental conservation.
+We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.
 
@@
 While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are often tied to environmental conservation views.
-These monolithic representations advance that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
+These monolithic representations advance the view that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
 Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
@@
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices [@assuncao2015; @capobianco2019; @capobianco2021], are a crucial factor in decisions to deforest on the ground [@campbell2015].
+This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021, @campbell2015].
 Second, we argue that presidents can deploy problem-constructions that build policy objects as different problems depending on whom they are speaking to.
@@
 First, we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (Climate Summits).
+the assassination of Chico Mendes) as well as international events (e.g.
+Climate Summits).
 Second, the same government adopts a diverse range of problem-constructions over time.
@@
 Chosen problems are those that governments select at their discretion.
-Problems can change from pressing to chosen across time and in space as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-@hirschman1975 (favourite) example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia.
+Problems can change from pressing to chosen as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
+@hirschman1975 's example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia., which was not particularly pressed by any interest group.
 
@@
 We refer to Amazonian historiography as the body of research conducted by social and environmental scientists that tell the story of diverse governmental programs that approach the Amazon region, forest, and its people as a policy object demanding dedicated action.
-From this literature, we identify three historical-political-social constructions: national sovereignty, economic integration, and environmental conservation.
+From this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
 We also argue that a fourth one is missing, social development, that focuses on the rights and dignity of the inhabitants of the Amazonian region.
@@
 The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions @acker2021.
+In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions[@acker2021] .
 First, it assumes that nature should be conquered by mankind Second, it assumes that exploiting natural resources would render the Amazon region economically profitable.
@@
 The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
-A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market engendered years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
+A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market, engendered by years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
 This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
@@
 The final dataset encompasses 6130 speeches for all the presidents of Brazil.
-Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest in these speeches.
+Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest.
 We do so by detecting all speeches in which the stem "amazon" appears.
@@
 Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences before and two sentences after, rather than words because sentences usually contain a cohesive idea.
+We opt for picking two sentences around, rather than words because sentences usually contain a cohesive idea.
 By doing so we create our unit of analysis: an Amazon statement.
@@
 This amount refers to 50% of all the Amazon Statements identified.
-We chose to hand.code half of the observations because since there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem, we conservatively coded a relatively large training set for the subsequent automated machine learning.
-As well, this allows a robust validation set to verify the models.
-As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
+We chose to hand code half of the observations because  there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem.As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
+This allows a robust validation set to verify the models.
 Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
@@
 This means we try to predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
-Our main independent variable is the distance, in kilometers, between the state capital (within Brazil) or the country capital (outside of Brazil) to Manaus (the capital of the Amazonas State and centrally located in the region).
+Our main independent variable is the distance (in kilometers) from  the state or country capital where the speech took place to Manaus (the capital of the Amazonas State and centrally located in the region).
 In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15% [^2] of their speeches.
+On average, presidents mention the Amazon in 15.4% [^2] of their speeches.
 The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
@@
 From 1985 to 1988, the mentions of the Amazon in official speeches increased from 4% to 14%.
-During this period, the latest Brazilian Constitution, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990], was written.
+During this period, the latest Brazilian Constitution was written, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990].
 In 1989, however, the Amazon appeared in 32% of all speeches.
@@
 From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of approval of the New Forest Code in 2012, which regularized land ownership of many illegally deforested areas, were frequent.
+Disagreements related to the priority of environmental preservation over economic development, most notably in the case of approval of the New Forest Code in 2012, were frequent.
+The 2012 Forest Code regularized land ownership of many illegally deforested areas.
 The period was also marked by political and economic instability which culminated in the impeachment of Rousseff in 2016.
@@
 As deforestation rates decreased from 2004 to 2012, environmental conservation constructions in presidential speeches increased.
-@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, engendered a perception of a higher risk of being caught and fined for deforestation.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, generated a perception of a higher risk of being caught and fined for deforestation.
 The shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned.
@@
 That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
-The opposite is true for both economic integration and social development, with statistically significant negative relationships.
+Second, the opposite is true for both economic integration and social development, with statistically significant negative relationships.
 When speaking within the Amazon, presidents focus on social development and economic integration.

### 2022-09-14 Draft_September_2022/Full_draft_20220901.rmd

--- 2022-09-12 Draft_September_2022/Full_draft_20220901.rmd
@@
 ```{=latex}
-\wordcount{ 8477 (including abstract, text, references, and and footnotes)}
+\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
 ```
@@
 We understand transnationalism as relationships that transcend nation-states, from the local level to the international level encompassing non-state actors [@keck1998].
-The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020).
-Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
+The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020 ).Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
 This is partially because the forest is a key biome in global climate-mitigation.
@@
 
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
+The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
 Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change.
@@
 Alternatively, as deforestation increases, presidents are more likely to construct the amazon as an issue of economic integration.
-This indicates that Brazil, indeed, created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019], without any international obligations to do so[@hochstetler2012a].
+This indicates that Brazil created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
 In the same fashion, economic integration problem-constructions are likely deployed as a justification for increasing deforestation rates.

### 2022-09-14 Draft_September_2022/Full_draft_20220901.rmd
#correctionsagain

--- 2022-09-14 Draft_September_2022/Full_draft_20220901.rmd
@@
 We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.
+We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.Different governments throughout Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
 
-Different governments throughout Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
 We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
@@
 In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021, @campbell2015].
+This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021; @campbell2015].
 Second, we argue that presidents can deploy problem-constructions that build policy objects as different problems depending on whom they are speaking to.
@@
 First, we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (e.g.
-Climate Summits).
+the assassination of Chico Mendes) as well as international events (e.g.Climate Summits).
 Second, the same government adopts a diverse range of problem-constructions over time.
@@
 Problems can change from pressing to chosen as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-@hirschman1975 's example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia., which was not particularly pressed by any interest group.
+@hirschman1975 example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia, which was not particularly pressed by any interest group.
 
@@
 Our main independent variable is the distance (in kilometers) from the state or country capital where the speech took place to Manaus (the capital of the Amazonas State and centrally located in the region).
-In our model, we also control for annual deforestation rates, annual inflation rates, and election years in the model.
 We interpret the plots and model considering multiple Amazon-related events and policies over the last 30 years, with the support of existing literature, and their correlations with different presidents and locations.
@@
 From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
-Disagreements related to the priority of environmental preservation over economic development, most notably in the case of approval of the New Forest Code in 2012, were frequent.
-The 2012 Forest Code regularized land ownership of many illegally deforested areas.
+Disagreements related to the priority of environmental preservation over economic development were frequent, most notably in the case of approval of the New Forest Code in 2012, which regularized land ownership of many illegally deforested areas.
 The period was also marked by political and economic instability which culminated in the impeachment of Rousseff in 2016.
@@
 As deforestation rates decreased from 2004 to 2012, environmental conservation constructions in presidential speeches increased.
-@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, generated a perception of a higher risk of being caught and fined for deforestation.
+@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, engendered a perception of a higher risk of being caught and fined for deforestation.
 The shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned.
@@
 That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
-Second, the opposite is true for both economic integration and social development, with statistically significant negative relationships.
+Second,the opposite is true for both economic integration and social development, with statistically significant negative relationships.
 When speaking within the Amazon, presidents focus on social development and economic integration.

### 2022-09-16 Draft_September_2022/Full_draft_20220901.rmd
#easychangesbasedonmatias'feedback

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985
+title: How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985
 author:
@@
 By doing so we create our unit of analysis: an Amazon statement.
-We use Amazon statements as our unit of analysis for two main reasons.
-First, working at the level of statements allows us to identify only passages that are meaningful for our specific purpose.
-Second, it increases the number of observations and their variety meaningfully, allowing for more specificity in the analysis.
-This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
+We use Amazon statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
 When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15.4% [^2] of their speeches.
+On average, presidents mention the Amazon in 15.4% of their speeches.
+For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).
 The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
-
-[^2]: For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).
 
@@
 Second and relatedly, deforestation rates have a positive and strong correlation with economic integration.
-When deforestation increased from 1988 to 2004 and from 2012 to 2021, so did economic integration.
+When deforestation increased from 1988 to 2004 and from 2012 to 2021, so did mentions to economic integration.
 When deforestation decreased from 2004 to 2012, economic integration decreased as well.
@@
        y = "",
-       title = "Predicted share of each problem-construction as a function of\ndistance from the Amazon",
+       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
        subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
@@
 ```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-# summary statistics
+
 md <-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,

### 2022-09-16 Draft_September_2022/Full_draft_20220901.rmd
#distancein1000sofkilometers

@@
          sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
+
 # model
+
 model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
@@
                    family=binomial(link = "logit"), data = ama_model)
+
 # Plot model
@@
 
+```{r Models for Table, include=FALSE}
+
+#models for table
+
+ama_model$thousand_km<- ama_model$km_to_manaus/1000
+
+model_logit_con2 <- glm(con_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_ei2 <- glm(EI_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sd2 <- glm(SD_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sov2 <- glm(sov_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+
+```
+
 Table 1, below, shows a statistically significant relationship between constructing the Amazon as an issue of environmental conservation and distance from the Amazon.
@@
 
-md <-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
-                          model_logit_sov, digits = 10, 
+md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
+                          model_logit_sov2, digits = 10, 
                           dep.var.labels = c("Conservation", "Economic Integration",
                                              "Social Development", "Sovereignty"),
-                          covariate.labels = c("Distance from the Amazon (km)",
+                          covariate.labels = c("Distance from the Amazon in 1000s of km",
                                                "Election year", "Yearly Deforestation",

### 2022-09-16 Draft_September_2022/Full_draft_20220901.rmd
#distancein1000sofkilometers

@@
 md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
-                          model_logit_sov2, digits = 10, 
+                          model_logit_sov2, digits = 6, 
                           dep.var.labels = c("Conservation", "Economic Integration",
@@
 We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about governments’ actions related to the Brazilian Amazon.
+Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon.
 In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.

### 2022-09-17 Draft_September_2022/Full_draft_20220901.rmd
#lessconvolutefigureone

@@
 We understand transnationalism as relationships that transcend nation-states, from the local level to the international level encompassing non-state actors [@keck1998].
-The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020 ).Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
+The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020).Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
 This is partially because the forest is a key biome in global climate-mitigation.
@@
 
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
+The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
+@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
 Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change.
@@
 all_loc
+
 ```

### 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
#added references

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: "12 September 2022"
+date: 20 September 2022"
 output:
@@
 Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015], and many others.
+Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015; @rajao2020 ], and many others.
 Nevertheless, the role of the president remains understudied.
@@
 While Brazilian military diplomacy was very successful, the process did not come without its traumas as the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 aimed at protecting Brazil's sovereignty over the Amazon.
+These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 at earlier regimes aimed at protecting Brazil's sovereignty over the Amazon [@hecht2020].
 As we move from a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.

### 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
#chunk transforming logit output in probabilities. #text updated.

@@
 
-Table 1, below, shows a statistically significant relationship between constructing the Amazon as an issue of environmental conservation and distance from the Amazon.
+Table 1, below, shows that for each 1000Km increase, we find an increase of 52.8% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
 That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
-Second,the opposite is true for both economic integration and social development, with statistically significant negative relationships.
+Second,the opposite is true for both economic integration (and social development): for an increase of 1000Km, we find a decrease of 48.5% (47.4%), respectively.
 When speaking within the Amazon, presidents focus on social development and economic integration.
@@
 ````
+
+```{r model probs, include=FALSE}
+
+# Increasing thousand_km by 1, will result in a 0.11555 in logit(probability) or log(p/1-p)
+# p/(1-p)=exp.0.1155
+# p/(1-p)=1.122435
+# p= 1.12243/2.1224
+# p=52.8%
+
+logit2prob <- function(logit){
+  odds <- exp(logit)
+  prob <- odds / (1 + odds)
+  return(prob)
+}
+
+logit2prob(coef(model_logit_con2))
+logit2prob(coef(model_logit_ei2))
+logit2prob(coef(model_logit_sd2))
+
+```
 

### 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
#tabmodelin

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: 20 September 2022"
+date: 20 September 2022
 output:
@@
 library(gridExtra)
+library(sjPlot)
+
 Sys.setlocale("LC_ALL", "C")
@@
 Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or periods in time in discourses as economic integration was until the early 2000s.
-Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
+Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.
+As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
 
@@
 ```{r Figure 6, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+
 ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
@@
 ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
-plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:24)
+plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:25)
+
 plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
                                                "Environmental Conservation",
-                                               "Social Development"))
+                                               "Social Development",
+                                               "National Sovereignty"))
 all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
@@
        title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
-       subtitle="Sovereignty was removed because of statistical insignificance (table 1).", 
        caption = "Curves in the plots are estimated using loess method.") +
@@
   theme(legend.position = "none")+
-  facet_wrap(~p_c, ncol=3)
+  facet_wrap(~p_c, ncol=2)
 
@@
 
-Table 1, below, shows that for each 1000Km increase, we find an increase of 52.8% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
+We convert log odds from Table 1, below, into probabilities [^2].
+It shows that for each 1000Km increase, we find an increase of 52.8% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
 That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
@@
 This multi-level game implies that presidents talk to the economic and social needs of the people domestically while boasting about environmentalism internationally.
+Finally, national sovereignty problem constructions do not appear to change with distance.
+
+[^2 See table 3 in appendix for all odds ratios and confidence intervals.]
 
@@
 logit2prob(coef(model_logit_sd2))
+logit2prob(coef(model_logit_sov2))
 
@@
 ````
+
+```{r Table 3, fig.cap="Table 3: Odds Ratios and Confidence Intervals", echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE, include= TRUE}
+
+tab_model(model_logit_con2,model_logit_ei2,model_logit_sd2,model_logit_sov2)
+
+```

### 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
#finaltextchanges

@@
 library(sjPlot)
+library(parameters)
 
@@
 Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move farther away from the Amazon region.
-That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relates to policies.
-Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
+That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses as a multi-level game and how these relates to policies.
 
@@
 For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
+Most disagreements related to different interpretations of the codebook, which were subsequently clarified.
 
@@
 Our main independent variable is the distance (in kilometers) from the state or country capital where the speech took place to Manaus (the capital of the Amazonas State and centrally located in the region).
-We interpret the plots and model considering multiple Amazon-related events and policies over the last 30 years, with the support of existing literature, and their correlations with different presidents and locations.
+The logic behind this relates to presidents playing multi-level games.
+We expect presidents to change how they construct the Amazon based on their believes of audiences' expectations.We interpret the plots and model considering multiple Amazon-related events and policies over the last 30 years, with the support of existing literature, and their correlations with different presidents and locations.
 
@@
 
-[^2 See table 3 in appendix for all odds ratios and confidence intervals.]
+[^2]: See table 3 in appendix for all odds ratios and confidence intervals.
 
@@
 
-The authors are extremely grateful to Graziella Moraes Silva and James Hollway for their support.
-The authors would also like to thank Matias, Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
+The authors are extremely grateful to Matias López, Graziella Moraes Silva, and James Hollway for their support.
+The authors would also like to thank Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
 
@@
 
-```{r Table 3, fig.cap="Table 3: Odds Ratios and Confidence Intervals", echo=FALSE, message=TRUE, warning=TRUE, paged.print=TRUE, include= TRUE}
+````{=tex}
+\begin{landscape}
+
+```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
@@
 ```
+
+\end{landscape}
+````

### 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
#finaltextchanges

@@
 Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move farther away from the Amazon region.
-That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses as a multi-level game and how these relates to policies.
+That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.
+Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relates to policies.
+Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
 

### 2022-09-20 Draft_September_2022/Full_draft_20220901.tex
#finaltextchanges

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\providecommand{\keywords}[1]{\textbf{Keywords:} #1}
\providecommand{\wordcount}[1]{\text{Word Count:}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985},
  pdfauthor={Livio Silva-Muller; Henrique Sposito},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{How has the Brazilian Amazon been constructed as a
problem:Presidential speeches and transnational politics since 1985}
\author{Livio Silva-Muller \and Henrique Sposito\footnote{Both
  co-authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Anthropology and Sociology
  at the Geneva Graduate Institute and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in
  International Relations and Political Sciences at the Geneva Graduate
  Institute and affiliated to the Centre for International Environmental
  Studies.}}
\date{20 September 2022}

\begin{document}
\maketitle
\begin{abstract}
Presidential speeches influence the ways we think about and act towards
the environment transnationally, but they are understudied. We propose a
framework to investigate how the Brazilian Amazon has been constructed
as a problem in discourses across time and space. Using supervised
machine learning, we classify statements about the Amazon in 6130
presidential speeches since 1985. We find that national and
international events drive the frequency at which the topic of the
Amazon is mentioned in presidential speeches inside and outside Brazil.
While constructing the Amazon as a problem of economic integration
dominates discourses until the mid-2000s, environmental conservation and
social development constructions increase in relevance and temporarily
surpass economic integration from 2010 to 2015. In turn, constructing
the Amazon as an issue of sovereignty steadily increases since 2010.
Lastly, the farthest away presidents are from the Amazon itself, the
more likely they are to construct the Amazon as an issue of
environmental conservation.
\end{abstract}

\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}

\wordcount{ 8470 (including abstract, text, references, and and footnotes)}

\pagebreak

\hypertarget{introduction}{%
\section{1 Introduction}\label{introduction}}

\emph{We need to protect the Amazon from foreign interests. We need to
exploit the Amazon's natural resources. We need to provide better living
standards for the people in the Amazon. We need to preserve the Amazon
as a standing ecosystem.} Each of these statements contains an implicit
assumption of what needs to be solved, or in other words, it represents
the Amazon as a particular problem: national sovereignty, economic
integration, social development, and environmental conservation,
respectively.These specific problems touch on common understandings of
the Amazon as part of the larger socio-cultural history of the
country.Different governments throughout Brazilian history have been
described as proponents of a specific view of the Amazon (Drummond and
Barros-Platiau 2006; Pádua 2012; Franchini and Viola 2019; Capobianco
2019; Pereira and Viola 2021).

We conceptualize the Amazon region, forest, and people to be a policy
object, this is a specific issue that deserves dedicated policy
attention. While the military dictatorship(1964-85) is associated with
understanding the Amazon as issues of national sovereignty and economic
integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are
often tied to environmental conservation views. These monolithic
representations advance the view that specific governments understand
and act towards the Amazon as one problem, hiding within government
diversity of both policies and perspectives. Albeit the current calls to
understand the environment as a social-cultural construction and to
identify the effect of culture on environmental outcomes (Waroux et al.
2021), we lack empirical accounts of how the Brazilian Amazon has been
constructed as a problem in discourses over time, by geographical
location, and between, or within, governments. Building on Hirschman
(1963) conceptualization of chosen problems and Bacchi (2009) theory of
problem-representation in policy, we propose a framework for identifying
problem-constructions in discourse and investigate how the Brazilian
Amazon has been constructed as a problem in transnational political
discourses. We understand transnationalism\footnote{We use the noun
  transnationalism, the adverb transnationally, and the adjective
  transnational interchangeably} as relationships that transcend
nation-states, from the local level to the supranational level
encompassing non-state actors (Keck and Sikkink 1998).

Although problem-construction takes place in a series of instances, we
analyze the case of speeches by Brazilian presidents since 1985.
Scholarly research about environmental policy in Brazil has focused on
the role of the environmental bureaucracy (Silva-Muller 2022),
non-governmental organizations (Keck and Sikkink 1998), legislation
(Soares-Filho et al. 2014), and international markets (Assunção,
Gandour, and Rocha 2015; Rajão et al. 2020 ), and many others.
Nevertheless, the role of the president remains understudied. We opt for
presidential speeches for two reasons. First, presidential discourses
have the power to introduce and justify the public policy, as well as
shape its perception to broad audiences (Zarefsky 2004; Gillion 2016).
It legitimizes ways of thinking about the Amazon. In turn, policy
perception is key for policy adoption and implementation (Alesina and
Giuliano 2009; López et al. 2020). This is especially pertinent to
deforestation in Brazil as expectations of local actors, generated from
material and discursive governmental practices, are a crucial factor in
decisions to deforest on the ground (Assunção, Gandour, and Rocha 2015;
Capobianco 2019, 2021; Campbell 2015). Second, we argue that presidents
can deploy problem-constructions that build policy objects as different
problems depending on whom they are speaking to. Presidential discourses
take place in different settings, from launching a new bridge in a small
municipality in the middle of the Amazon to a speech at the UN general
assembly in New York. Working with presidential discourses allows us to
identify this variation in meaningful ways and better understand how the
Amazon is discursively constructed in transnational politics.

To investigate how the Brazilian Amazon has been constructed as a
problem in presidential speeches, we create a dataset containing 6130
official presidential speeches by all Brazilian presidents since 1985.
We subset the dataset by identifying Amazon-related statements within
these speeches. We find that 2014 sections in these discourses refer to
the Amazon at least once. We then develop a codebook grounded on
Amazonian historiography to code how each of these statements constructs
Amazon as a particular problem. We use this codebook to manually code a
randomly selected training set of Amazon-related statements. We train a
supervised machine-learning model to automatically label the remaining
set of Amazonian statements. We then conduct a descriptive and
inferential analysis of this data, tying patterns in the data to
Amazonian policies and deforestation outcomes over time.

Our empirical findings are threefold. First, we find that the frequency
of the Amazon as a topic in speeches inside and outside Brazil is
equally driven by domestic events (e.g.~the assassination of Chico
Mendes) as well as international events (e.g.Climate Summits). Second,
the same government adopts a diverse range of problem-constructions over
time. While economic integration dominated discourse from 1985 to the
mid-2000s, environmental conservation and social development
constructions steadily grew in the 2000s, briefly surpassing economic
integration as more common problem-constructions from 2011 to 2016.
Constructing the Amazon as an issue of sovereignty has increasingly
become more pertinent after 2010. Finally, using logit models, we find
that presidents are more likely to construct the Amazon as a problem of
environmental conservation as presidents move farther away from the
Amazon region. That is, presidents talk to the economic and social needs
of the people domestically while boasting about environmental policy
internationally.Empirically, we provide the first comprehensive overview
of when, where, and how the Amazon is constructed as problems in
presidential speeches. Conceptually, this contributes to understanding
the social construction of the Amazon in discourses as a multi-level
game and how these relates to policies.

This article proceeds as follows: first, we propose a conceptual
framework to understand problem-construction in discourses. We then
review Amazonian historiography literature to identify the main phases
and their underlying problem-construction. In the methodology section,
we explain how the framework is operationalized and present the
codebook. We proceed to describe, visualize, and interpret our findings
in the analysis section. Finally, we conclude with a discussion
connecting our findings to past and present environmental policies.

\hypertarget{conceptual-framework-and-contribution}{%
\section{2 Conceptual framework and
contribution}\label{conceptual-framework-and-contribution}}

\hypertarget{chosen-problems-presidential-discourses-and-policy-objects}{%
\subsection{2.1 Chosen problems, presidential discourses, and policy
objects}\label{chosen-problems-presidential-discourses-and-policy-objects}}

In ``Journey towards Progress'', Hirschman (1963) draws a conceptual
distinction between pressing problems (pressured by outside parties to
the government) and chosen problems (chosen by the government at their
discretion). Pressing problems can be either privileged or neglected,
depending on the degree of pressure exercised by the interested groups.
Chosen problems are those that governments select at their discretion.
Problems can change from pressing to chosen as a function of (a)
solutions becoming available, (b) a change in the level of government
control in society, or (c) a shift of interests from top policymakers
(Hirschman 1963). Hirschman (1975) example of policymakers choosing a
problem is President's Kubitschek decision of building Brasilia, which
was not particularly pressed by any interest group.

Bacchi (2009, 10) argues that policies have a cultural dimension as they
take'' shape within specific historical and national or international
contexts''. The existence or proposal of a policy implies that there is
a (public) problem that needs (governmental) action to be fixed, this is
a policy object. We conceptualize policy objects as a problems that
demand dedicated policy attention. The alleged problem is not always
explicitly stated in a policy: policies are represented as solutions for
implicit problems. Building Brasilia (the policy object), thus, could
solve a problem of regional inequality, a problem of a dormant economy
without state investment, a problem of political representation, or all
three depending on how governments speak about it.

Governments can choose to emphasize (or not) one or more implicit
problems that a policy solves depending on which interest group they are
in communication with. Depending on how the policy is represented to be,
it can be portrayed as a solution to problems that are considered
pressing or not for different groups and it is up to the discretion of
the political actor to construct a particular problem in a particular
way given context. Putnam (1988)'s seminal article on the two-level game
can help us make sense of this variation conceptually. The author argues
that the outcomes of international negotiations lie within the overlap
between the agenda (and pressure) of domestic and international groups.
If policies are socially constructed, governments can in theory
construct them to meet the expectations of both. Consequently, this
entails that governments are more diverse in their opinions, rather than
monolithic.

An interesting context to study the relationship between
problem-construction and policy objects is presidential speeches, as
they legitimize ways of thinking about an issue. While the relationship
between presidential speeches and policy may not be causal, they have
the power to introduce and justify public policy, as well as shape issue
perception to broad audiences (Zarefsky 2004; Gillion 2016). As
presidents speak across several locations to various audiences, they
construct similar issues differently.

The possibility of different problem-constructions in presidential
speeches has important implications for democracy and global politics.
With globalization, presidents have the opportunity of promoting
different problem-constructions transnationally. We understand
transnationalism as relationships that transcend nation-states, from the
local level to the international level encompassing non-state actors
(Keck and Sikkink 1998). The environment and climate change, in
particular, have received particular trasnantional attention, as
narratives of global collective action dominated academic literature
(for an overview, see Aklin and Mildenberger (2020)).Relatedly, when
Brazilian presidents speak about the Amazon it not only makes headlines,
nationally and internationally (Brice and Smith 2021; Harris 2021;
Miranda 2021), but also incites responses, shapes expectations, and
feeds into the behavior of a myriad of related actors. This is partially
because the forest is a key biome in global climate-mitigation. It is
important to understand, thus, to what extent the implemented policy
agenda correlates with problem-constructions promoted at the local,
federal, or international levels.

The connection between presidential discourse and the environment has
been studied in the case of the United States but remains conceptually
underdeveloped. Calderwood (2019), for instance, examines 2019 mentions
of climate change in American official presidential speeches since 1989.
Among other things, the author finds that American presidents frequently
side-step the environmental aspects of climate change. Building on
Putnam (1988), Calderwood (2020) demonstrates that American presidents
are more likely to mention climate change in foreign locations, and that
location influences the specific discursive approach and tone they
adopt. Elsewhere, Bevitori (2015) finds that mentions of the environment
are typically co-selected with the pronoun `our', as well as with
`economy', `clean', and `preserve'. While these studies corroborate the
possibilities of variation depending on the audience, they fail to tie
vocabulary to specific problem-constructions based on wider shared
meanings of environment and climate change. That is,
problem-constructions touch on shared meanings available to both the
speaker and the audiences as part of larger social-cultural history (see
Bacchi 2009), therefore, mentions to the lexicon as `environment',
`preserve', or 'climate change should be tied to the larger meaning of
policies in the United States.

There is also an empirical gap in terms of how the Amazon, specifically,
has been constructed as a problem along time and geographic location in
political discourses. While governmental discourses in Brazil have been
studied for topics such as inflation or race relations (see Da Silva and
Larkins 2019), the environment remains largely absent. An exception is
Barros (2020), who investigates Amazonian discourse in the Brazilian
Congress. The author finds that the economic value of the Amazon for the
cattle industry is the most salient narrative put forward by congressmen
and concludes that there is a mismatch between the international debate
(which focuses on preservation) and the national debate (which focuses
on economic development).

This variation in problem-construction entails that the same governments
are more diverse in their positions than the literature suggests.
Scholars often describe federal governments as proponents of a cohesive
set of policies toward the Amazon (see Drummond and Barros-Platiau 2006;
Pádua 2012; Franchini and Viola 2019; Capobianco 2019; Pereira and Viola
2021). In this literature, the 1964 military dictatorship is associated
with securing sovereignty in the region by populating it and integrating
it into the national economy (Drummond and Barros-Platiau 2006). The
governments from the late 1980s up to 2009 are associated with a turn
towards policies that focus on environmental conservation. The
presidencies of Dilma and Temer (2011-2018) are connected to the decline
of conservationist policies, while Bolsonaro to the dismantling of
environmental policies. Although these works are important to understand
how different governments have acted toward the Amazon, the
classification of specific governments into policy periods, or policy
cycles, represents them as monolithic: they associate specific
governments with one specific view of the Amazon.

We propose a conceptual framework that accepts the possibility of varied
problem-construction for the same policy object and connects it to
presidential speeches. Governments often choose what problems to solve
and what policies to implement. The same policies can be represented as
solving different problems implying a degree of social construction
(Bacchi 2009). Governments can emphasize, or not, implicit problems that
a policy solves depending on which interest group they are in
communication with. The variation in problem-construction suggests that
Brazilian governments are more diverse in their positions than the
literature suggests. An interesting context to study the relationship
between varied problem-construction and policy is presidential speeches
as they legitimize ways of thinking about an issue, matter for
policymaking, and environmental outcomes. As presidents speak in
different places and to diverse audiences, it is an empirical site prone
to identifying variation.

\hypertarget{problem-construction-in-amazonian-historiography}{%
\subsection{2.2 Problem-construction in Amazonian
historiography}\label{problem-construction-in-amazonian-historiography}}

We rely on the Amazonian historiography literature to identify possible
problem-constructions and their connection to the socio-cultural history
of the country. We refer to Amazonian historiography as the body of
research conducted by social and environmental scientists that tell the
story of diverse governmental programs that approach the Amazon region,
forest, and its people as a policy object demanding dedicated action.
From this literature, we identify three historical-political
constructions: national sovereignty, economic integration, and
environmental conservation. We also argue that a fourth one is missing,
social development, that focuses on the rights and dignity of the
inhabitants of the Amazonian region.

\hypertarget{national-sovereignty}{%
\subsubsection{National Sovereignty}\label{national-sovereignty}}

S. B. Hecht and Cockburn (1990, 1) write that ``what imbues the case of
the Amazon with such passion is the symbolic content of the dreams it
ignites''. In the process of securing Amazonian borders since the 18th
century, Brazil thwarted ``the imperial ambitions of France, Britain,
the United States, Belgium, Bolivia, and Peru'' (S. B. Hecht and
Cockburn 1990, 8), and when the dust settled and the scramble was over,
over half of the Amazon emerged Brazilian. While Brazilian military
diplomacy was very successful, the process did not come without its
traumas as the negotiations with Bolivia in 1902 to secure the territory
of the state of Acre (S. B. Hecht and Cockburn 1990). These traumas were
referred to, and offered context, to Amazonian discourses and policies
during the military dictatorship of 1964 at earlier regimes aimed at
protecting Brazil's sovereignty over the Amazon (S. Hecht and Rajão
2020). As we move from a world where non-state actors gain importance in
environmental governance (Silva-Muller and Faul 2022; Andonova 2014;
Keck and Sikkink 1998), sovereignty-related problems become more varied.
Threats to national sovereignty, consequently, broaden from state actors
to a wide set of actors. Claims of attempts to `internationalize' the
Brazilian Amazon, for instance, are targeted at foreign actors as well
as domestic non-state actors. The sovereignty problem-construction
advances the view that the Brazilian Amazon belongs to Brazil and any
foreign or non-state presence in the region can be part of a broad
strategy to take the region. The policy solutions to the issue of
sovereignty included the monitoring of the borders and strict regimes
related to entry into the region.

\hypertarget{economic-integration}{%
\subsubsection{Economic Integration}\label{economic-integration}}

The Vargas dictatorship (1937-46) and the military dictatorship
(1964-89) took over the task of modernizing the Amazon. In 1966, the
Brazilian Military launched `Operation Amazon', a policy to modernize
the region based on three assumptions(Acker 2021) . First, it assumes
that nature should be conquered by mankind Second, it assumes that
exploiting natural resources would render the Amazon region economically
profitable. Third, it assumes that populating the region was necessary
to integrate it into the country and exert control over the territory.
Concretely, this meant a series of major infrastructural projects,
incentives for settlers to expand the agricultural frontier, and the
establishment of a tax-free zone in Manaus to attract industry.
Capobianco (2019) and Becker (2005) describe the period from the 1950s
to the 1980s in similar vein, as one of often centralized economic
policies by the federal government.The economic integration
problem-construction advances the view that the Brazilian Amazon needs
to be developed and modernized. These policy solutions have at their
core the development of the necessary infrastructure (physical, fiscal,
or monetary) to integrate the region into the national and international
economy.

\hypertarget{environmental-conservation}{%
\subsubsection{Environmental
Conservation}\label{environmental-conservation}}

The rapid economic changes in the region from the 1960s to the 1980s
were matched with the birth of environmental institutions (Drummond and
Barros-Platiau 2006). A common explanation for the creation of these
institutions in the Amazonian literature is the impression of the lack
of control over the market, engendered by years of centralized economic
integration in the region (Acker 2021; Capobianco 2021; S. B. Hecht and
Cockburn 1990). This process accelerated in the late 1980s with the
birth of modern environmentalism (Viola 1987), epitomized in the 1992
Earth Summit in Rio de Janeiro (Hochstetler 2021; Capobianco 2021).
Hochstetler and Keck (2007) argue that during preparations for the
summit, a new form of Brazilian environmentalism emerged:
socio-environmentalism. They define it as an emphasis on the local
livelihoods of traditional populations while protecting nature.
Capobianco (2019) argues that socio-environmentalism informed a series
of policies throughout the 1990s and early 2000s towards preserving the
forest, such as the establishment of several conservation units in the
Amazon in 2001. The environmental conservation problem-constructions
emphasize that the Amazon should be preserved, deforestation should be
halted, and the sustainable practices of indigenous and local peoples
should be maintained through the protection of their territories and
rights to self-determination (Hochstetler and Keck 2007). The policy
solution implies, for example, further investments in
command-and-control institutions, the valuation of standing ecosystems
through incentive schemes, and the creation of protected areas.

\hypertarget{social-development}{%
\subsubsection{Social Development}\label{social-development}}

Governments can emphasize the lack of hospitals, sanitation, and schools
concerning peoples' dignity, standards of living, and other
constitutional rights. However, such emphasis can be masked within both
the economic integration and environmental conservation accounts. Acker
(2021, 10), for example, argues that during the military dictatorship
attempts to populate the Amazon were seen, among other things, as a
solution for the country's growing social inequalities elsewhere. As
democracy established itself in Brazil, the settlers from the military
dictatorship became electorates with constitutional rights. Hochstetler
and Keck (2007) argue that with the transition to democracy, the
mobilization of diverse social movements to demand social equality and
conservation was an integral part of the socio-environmentalist movement
in Brazil. While indigenous rights and preservation of the forest go
hand in hand, it is not clear whether providing better standards of
livings to the large and poor populations of the state and preservation
do; perhaps this is also why there was never an open consensus about
socio-environmentalism in Brazil (Hochstetler and Keck 2007). Although
related to economic integration and environmental conservation, social
development is a problem-construction that focuses on constitutional
rights, citizenship, and dignity. The policy solution to social
development implies the policies to facilitate access to water,
sanitation, electricity, internet, and radio, as well as the
construction of schools and hospitals locally.

\hypertarget{methodology-operationalizing-amazonian-problem-constructions}{%
\section{3 Methodology: operationalizing Amazonian
problem-constructions}\label{methodology-operationalizing-amazonian-problem-constructions}}

\hypertarget{codebook-and-data}{%
\subsection{3.1 Codebook and Data}\label{codebook-and-data}}

To analyze how presidents construct the Amazon as a problem, we build
upon the dataset provided by (Cezar 2020) which contains all official
speeches by Brazilian Presidents from 1985 to 2019 scrapped from the
archives of the Brazilian Presidential Library. We update the dataset by
scraping and adding all official speeches from 2020 and 2021. The final
dataset encompasses 6130 speeches for all the presidents of Brazil.
Then, we proceed to identify all speeches that refer to the Amazon as a
region, people, or forest. We do so by detecting all speeches in which
the stem ``amazon'' appears. In Portuguese, the stem captures terms such
as ``Amazonia'', ``Amazonica'', ``Amazonidas'', ``Amazonense(s)'',
``Amazonas'', among others. We find that 946 speeches are, at least
partially, about the Amazon out of the 6130.

Using the poldis R package (Sposito 2021), we proceed to extract two
sentences before and two sentences after the sentence in which the stem
``amazon'' appears. We opt for picking two sentences around, rather than
words because sentences usually contain a cohesive idea. By doing so we
create our unit of analysis: an Amazon statement. We use Amazon
statements as our unit of analysis because it allows us to identify only
passages that are meaningful for our specific purpose.This process
yields 2014 unique Amazonian statements across the 946 speeches about
the Amazon identified. When an Amazonian statement contains two or more
matches of the stem ``amazon'', we get two sentences before the first
match and two sentences after the last match. On average, an Amazonian
statement contains 123 words.

Our approach to text coding has three steps. First, we develop a
codebook to code Amazonian statements in one or more
problem-constructions (see codebook in appendix). In their
conceptualization, each problem-construction is mutually exclusive,
meaning that they cover different forms of constructing the Amazon as a
problem. Nevertheless, each Amazonian statement might be assigned to one
or more codes. A statement can, for example, construct the Amazon as a
problem of sovereignty and a problem of economic integration, or a
problem of social development and conservation. Amazonian statements,
thus, can be either coded as pure-types or mixed-types. Mixed-types are
relevant as constructions and policies are often multifaceted while
portraying the Amazon as a combination of these problem-constructions.
Figure 1, below, portrays this operationalization strategy.

\begin{landscape}

\begin{figure}
\includegraphics[width=1\linewidth]{figure1pic} \caption{Operationalization of problem-constructions}\label{fig:figure1}
\end{figure}

\end{landscape}

Second, with the codebook in hand, each one of the authors, separately,
hand-coded the same set of 1007 randomly selected Amazonian statements.
This amount refers to 50\% of all the Amazon Statements identified. We
chose to hand code half of the observations because there are several
nuances in discourse in how presidents talk about the Amazon over time
and as a problem.As the size of the training set should increase with
the number of categories (Grimmer, Roberts, and Stewart 2022), we deemed
four categories and 50\% of the statements as reliable. This allows a
robust validation set to verify the models. Also, automating the coding
of half of the observations saved the authors over one month of work in
comparison to manual coding. The intercoder agreement for hand-coded
categories was 85\%, on average. For each non-matching coded
observation, the co-authors discussed and sorted their disagreements.
Most disagreements related to different interpretations of the codebook,
which were subsequently clarified.

Third, the hand-coded data is then randomly divided into a training set,
containing 80\% of the hand-coded observations (806 observations), and a
validation set, containing the remaining 20\% of the hand-coded data
(201 observations). We chose to employ a support-vector machine (SVM)
algorithm, a non-probabilistic linear classifier that classifies
documents by assigning points in mapped space to maximize the gap
between binary categories, to label texts (Meyer et al. 2021; Noble
2006). The SVM model is trained using the hand-coded training set and
then employed to classify observations in the validation set. The
trained SVM model was, on average 82\%, accurate in classifying
observations in the validation set before being tuned. After the SVM
model is tuned, we use the model to automatically code the remaining
1007 Amazonian statements. The final dataset for analysis, excluding
false positive matches, contains 1895 coded Amazonian statements.

\hypertarget{analysis-and-limitations}{%
\subsection{3.2 Analysis and
Limitations}\label{analysis-and-limitations}}

To analyze our data, we first present a series of different plots on the
proportions of Amazonian statements and problem-constructions over time
and by presidents. To test whether problem-constructions depend on where
presidents speak, we run four separate logistic regressions. Each model
takes the share of a specific problem-construction versus all other
problem-constructions as their dependent variable. This means we try to
predict the probability of a president constructing the Amazon as an
issue of (1) environmental conservation, (2) economic integration, (3)
social development, and (4) national sovereignty, separately, and in
relation to the remaining three problem-constructions. Our main
independent variable is the distance (in kilometers) from the state or
country capital where the speech took place to Manaus (the capital of
the Amazonas State and centrally located in the region). The logic
behind this relates to presidents playing multi-level games. We expect
presidents to change how they construct the Amazon based on their
believes of audiences' expectations.We interpret the plots and model
considering multiple Amazon-related events and policies over the last 30
years, with the support of existing literature, and their correlations
with different presidents and locations.

This approach comes with limitations. Our codebook is developed using
specific Amazon-related vocabulary. For example, a statement will be
coded as economic integration if it is meaningful support for the
tax-free zone of Manaus or a dam in the Amazon. However, the economy is
generally a topic that presidents speak about frequently. Hence, the
high incidence of economic integration in Amazonian statements can also
be related to the higher importance of this problem-construction in
Brazil overall Moreover, we classify statements as Amazonian based on a
dictionary composed of a single lexicon stem: ``amazon''. We chose to do
so knowing that a few speeches about the Amazon might not contain the
lexicon ``Amazon'', for example, when the president says, ``the forest''
or ``deforestation''. Hence, we might be missing statements about Amazon
that do not refer to it. However, we consider this safer as we cannot be
sure that mentions of the forest or deforestation do not correspond to
other biomes such as the Cerrado or the Atlantic Forest. Finally, our
dataset covers only what is considered an official speech. Presidents,
though, give interviews, appear in debates, talk at campaign rallies,
and, more recently, post on social media. Problem-construction within
presidential discourse, thus, also happens in different sites for which
we do not account in this paper.

\hypertarget{how-has-the-amazon-been-constructed-as-a-problem}{%
\section{4 How has the Amazon been constructed as a
problem?}\label{how-has-the-amazon-been-constructed-as-a-problem}}

\hypertarget{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}{%
\subsection{4.1 The rises and falls of the Amazon as a topic in
presidential
speeches}\label{the-rises-and-falls-of-the-amazon-as-a-topic-in-presidential-speeches}}

When, where, and how often do presidents speak about the Amazon? Figure
2, below, shows the proportion of speeches that mentions the Amazon in
relation to all speeches in a year. On average, presidents mention the
Amazon in 15.4\% of their speeches. For comparison purposes the averages
for other policy objects in the same corpus of speeches are: Inequality
(14.7\%), Criminality (17.3\%), Inflation (20.9\%), and Unemployment
(13.8\%). The frequency at which the Amazon appears across presidential
speeches inside, outside, and overall varies similarly across time (see
Figure 7 in appendix).

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 2-1.pdf}
\caption{Amazonian speeches in time}
\end{figure}

We observe five local maxima both inside and outside Brazil: 1989, 1992,
2009, 2015, and 2019. These points coincide with internal and external
events that help us explain the rises and falls of the Amazon in
presidential discourse. From 1985 to 1988, the mentions of the Amazon in
official speeches increased from 4\% to 14\%. During this period, the
latest Brazilian Constitution was written, which gave indigenous and
traditional populations space to advocate for constitutional
environmental rights and the protection of their territories (S. B.
Hecht and Cockburn 1990). In 1989, however, the Amazon appeared in 32\%
of all speeches. This maximum correlates with the brutal murder of Chico
Mendes in the last days of 1988. The incident caught unprecedented
international attention and Sarney responded to this with a set of
policies to address deforestation (Capobianco 2021), including accepting
to host the 1992 Earth Summit (Keck and Sikkink 1998).

1990-91 the Amazon appeared in 12\% to 14\% of all speeches but, by
1992, this average increased to 25\%. The 1992 Earth Summit in Brazil
brought international attention to environmental topics related to the
Amazon. One of the big announcements, for example, was the consolidation
of the first transnational partnership for the Amazon, the G7 Pilot
Program, which brought a high number of financial resources to the
region for public policy implementation (Capobianco 2021). Throughout
the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula
administrations, the Amazon as a topic did not diverge much from the
average until 2009, when we see another maximum in mentions of the
Amazon. This coincides with the 2009 Copenhagen Summit and the steepest
decrease in deforestation rates since data is available as Figure 3,
below, illustrates. Lula led the delegation to Copenhagen with a
self-image of ``we do not promise, we deliver'' when the stakes about
climate change were high (Franchini and Viola 2019).

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 3-1.pdf}
\caption{Deforestation rates since 1988}
\end{figure}

From 2010 to 2018, except for 2015, we see a general decrease in
mentions of the Amazon in all official presidential speeches. From 2010
to 2014, mentions of the Amazon went down from 18\% to 8\%.
Disagreements related to the priority of environmental preservation over
economic development were frequent, most notably in the case of approval
of the New Forest Code in 2012, which regularized land ownership of many
illegally deforested areas. The period was also marked by political and
economic instability which culminated in the impeachment of Rousseff in
2016. In 2015, the Amazon appeared in 19\% of all speeches. This maximum
coincides with the Paris summit which became a key turn in climate
politics after the failures of Copenhagen. Brazil went to the Paris
Summit with deforestation numbers slightly higher than Copenhagen and a
perception that there was a turn towards less conservation inside the
country. By 2016 mentions of Amazon in official speeches went down to
6\%, the lowest share since 1985.

We subsequently observe a steady increase from 6\% in 2016 to 24\% in
2019, the first year of Bolsonaro's presidency. At the time,
international and national media brought unprecedented attention to
Brazilian environmental issues as the record burning of the Amazon led
up to a red sky afternoon in São Paulo in August 2019. Alongside this,
Bolsonaro's dismantling of environmental governance and the threats to
leave the Paris Agreement had strong media attention, and, as a
response, the topic became prominent in his speeches. Bolsonaro went on
to retrieve Brazil's hosting status for COP25.

The frequency at which the Amazon appears in domestic and international
speeches varies in similar ways as the maxima in the topic frequencies,
led by the events discussed above, appear within and outside Brazil (see
Figure 7 appendix). We interpret this as evidence that relevant events
drive interest and alter how pressing the Amazon as a policy object is
perceived both nationally and internationally. This does not mean,
though, that when presidents speak about the Amazon, they highlight the
same issues.

\hypertarget{problem-constructions-in-time}{%
\subsection{4.2 Problem-constructions in
time}\label{problem-constructions-in-time}}

Our subsequent analysis of pure-types and mixed-types suggests that
governments do not defend a specific view of the Amazon. The same
governments construct the Amazon as various pure and mixed type
problems, which unravels a less cohesive story than that told by the
literature scrutinizing policy cycles.

\hypertarget{pure-type-problem-constructions}{%
\subsubsection{Pure-type
problem-constructions}\label{pure-type-problem-constructions}}

We conceptualize four problem-constructions: sovereignty, economic
integration, social development, and conservation. Figure 4, below,
illustrates the share of each pure-type in time. Pure
problem-constructions dominate, with an average of 56\% of all Amazonian
statements across time.We identify a discursive shift in
problem-constructions from developing the Amazon economically, to
conserving it and providing services to its citizens. Pure economic
integration constructions dominated constructions from 1985 to the late
2000s. This is especially pertinent during the Cardoso administration.
Brazilian presidents after Cardoso moved from employing one
problem-constructions consistently to a more diverse strategy. During
Lula's terms in office, constructing the Amazon purely as an issue of
economic integration decreased, while constructing the Amazon issues of
environmental conservation and social development increased.
Conservation and social development constructions surpassed economic
integration around 2010 and continued to dominate as Amazonian
constructions during Rousseff's administration. Still, environmental
conservation and social development problem-constructions were not as
dominant in terms of frequency or periods in time in discourses as
economic integration was until the early 2000s. Finally, we observe a
steady increase in sovereignty constructions in the late 2000s, reaching
the highest frequencies with the presidencies of Bolsonaro. As we
conceptualize and operationalize sovereignty as containing internal and
external perceived threats to the Amazon, we interpret this increase as
not only attacks on international interference in the Amazon but also on
indigenous and traditional populations.

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 4-1.pdf}
\caption{Pure-types in time}
\end{figure}

The trends identified are especially interesting considering Amazonian
policies and deforestation rates portrayed in Figure 3, above. First,
deforestation rates have a strong negative correlation with
environmental conservation. When deforestation rates increased from 1988
to 2004, and from 2012 until 2021, environmental conservation
constructions decreased. As deforestation rates decreased from 2004 to
2012, environmental conservation constructions in presidential speeches
increased. Capobianco (2021) argues that the unprecedented decrease in
deforestation we observed from 2004 to 2012 was a product of an increase
in the perception of stronger federal policies and police presence in
the Amazon region which, in turn, engendered a perception of a higher
risk of being caught and fined for deforestation. The shift from
constructing the Amazon as an issue of economic integration to an issue
of environmental conservation generates a perception that illegal
deforestation will be increasingly monitored and sanctioned. Second and
relatedly, deforestation rates have a positive and strong correlation
with economic integration. When deforestation increased from 1988 to
2004 and from 2012 to 2021, so did mentions to economic integration.
When deforestation decreased from 2004 to 2012, economic integration
decreased as well. This suggests that presidents might boast policy
outcomes related to economic integration as justifications for
deforestation.

\hypertarget{mixed-type-problem-constructions}{%
\subsubsection{Mixed-type
problem-constructions}\label{mixed-type-problem-constructions}}

In a speech, presidents might mix multiple problem-constructions within
a same statement about the Amazon. Although presidents prefer pure
problem-constructions, they also construct the Amazon as a multifaceted
issue. Mixed-type problem-constructions in discourse offer more
intricate understandings of the Amazon as a problem. Constructing the
Amazon as multiple issues averages at 18\% of all constructions in time.
Some mixed-types rarely appear so we focus our discussion on those
mixed-types with higher incidence. Figure 5, below, displays the
averages of mixed-types constructions by presidents.

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 5-1.pdf}
\caption{Mixed-types by president}
\end{figure}

The most frequent mixed-type problem construction of the Amazon is
economic conservation. This mixed-type construction, composed of
Amazonian statements that construct the Amazon as a problem of both
economic integration and environmental conservation, generally increased
over time. This increase suggests that later presidents, along with
being more diverse in how they construct the Amazon as an issue (see
Figure 4), increasingly find ways to reconcile the dictum between the
economy and the environment that had prevailed in the previous years.
The second most common mixed-type mixes social development and economic
integration and appears, on average, in 5.4\% of all statements. This is
not surprising, as developing countries like Brazil repeatedly claim a
``right to develop'', when it comes to negotiating strong climate
commitments and policies with a focus on both social development and
economic integration. Nonetheless, there is a general increase of
mixed-types over time, which is expected given the rise of global
agendas understanding interconnections of social, environmental, and
economic domains such as the Millennium Development Goals and the
Sustainable Development Goals.

Both Lula and Bolsonaro construct the Amazon as a multifaceted issue
more frequently than other presidents. Lula usually mixed economic
integration with environmental conservation and social development when
constructing the Amazon as an issue, while Bolsonaro constructs the
Amazon as an issue of national sovereignty and economic integration much
more than any other president, mimicking the military dictatorship
discourses and policies toward the region (S. B. Hecht and Cockburn
1990).

\hypertarget{the-amazonian-multi-level-game-boasting-policy-outside-and-talking-to-people-inside}{%
\subsection{4.3 The Amazonian multi-level game: boasting policy outside
and talking to people
inside}\label{the-amazonian-multi-level-game-boasting-policy-outside-and-talking-to-people-inside}}

The Amazon region, forests, and peoples have historically been the topic
of local, national, and international debates. This implies that
audiences' priorities in each setting change and consequently which
policies are appropriate to solve the ``Amazon issue'' differ as well.
As presidents physically move farther away from the Amazon, audiences
might have different stakes and interests in it. While speeches inside
the Amazon might focus on social development, for example, speeches in
the United Nations in New York might highlight environmental
conservation. To investigate the relationship between where presidents
speak and how they construct the Amazon as an issue, we run four
logistic regressions, one for each pure-type construction as a dependent
variable. We focus on pure-type constructions as these represent most
constructions and avoid ambiguity. The independent variable for all
models is the distance between the state country capital to Manaus.
Figure 6, below, depicts the predicted probabilities from the models
(see Table 1) as functions of distance.

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 6-1.pdf}
\caption{Logistic Regression predicted values}
\end{figure}

We convert log odds from Table 1, below, into probabilities \footnote{See
  table 3 in appendix for all odds ratios and confidence intervals.}. It
shows that for each 1000Km increase, we find an increase of 52.8\% in
the predicted probability of constructing the Amazon as an issue of
environmental preservation. That is, the farthest away the president is
from the Amazon region, the more likely the president is to construct it
as an issue of environmental conservation. Second,the opposite is true
for both economic integration (and social development): for an increase
of 1000Km, we find a decrease of 48.5\% (47.4\%), respectively. When
speaking within the Amazon, presidents focus on social development and
economic integration. This entails that conservation might be a
desirable construction when speaking internationally about the Amazon,
but not at the local level, where presidents highlight economic and
social development. This multi-level game implies that presidents talk
to the economic and social needs of the people domestically while
boasting about environmentalism internationally. Finally, national
sovereignty problem constructions do not appear to change with distance.

\begin{landscape}

% Table created by stargazer v.5.2.3 by Marek Hlavac, Social Policy Institute. E-mail: marek.hlavac at gmail.com
% Date and time: Tue, Sep 20, 2022 - 16:35:39
\begin{table}[!htbp] \centering 
  \caption{Logistic Regressions Output} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Conservation & Economic Integration & Social Development & Sovereignty \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 Distance from the Amazon in 1000s of km & 0.115554$^{***}$ & $-$0.056590$^{**}$ & $-$0.101285$^{**}$ & 0.009384 \\ 
  & (0.021453) & (0.023979) & (0.039849) & (0.038080) \\ 
  Election year & 0.287908$^{*}$ & $-$0.022328 & 0.328917$^{*}$ & $-$0.448696$^{*}$ \\ 
  & (0.156660) & (0.132762) & (0.171163) & (0.269325) \\ 
  Yearly Deforestation & $-$0.031739$^{***}$ & 0.040870$^{***}$ & $-$0.072349$^{***}$ & $-$0.031859$^{*}$ \\ 
  & (0.011298) & (0.008404) & (0.013232) & (0.016768) \\ 
  Yearly   Inflation & 0.000387$^{***}$ & $-$0.000231$^{**}$ & $-$0.000205 & 0.000215 \\ 
  & (0.000104) & (0.000104) & (0.000151) & (0.000177) \\ 
  Constant & $-$1.718459$^{***}$ & $-$1.568837$^{***}$ & $-$0.909845$^{***}$ & $-$2.300558$^{***}$ \\ 
  & (0.190667) & (0.159988) & (0.213791) & (0.280849) \\ 
 \hline \\[-1.8ex] 
Observations & 1,842 & 1,842 & 1,842 & 1,842 \\ 
Log Likelihood & $-$748.648200 & $-$1,022.790000 & $-$620.264400 & $-$399.290500 \\ 
Akaike Inf. Crit. & 1,507.296000 & 2,055.579000 & 1,250.529000 & 808.581000 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\end{landscape}

Our models also suggest that deforestation plays an important role.
Presidents are, for example, more likely to construct the Amazon as an
issue of environmental conservation as deforestation decreases.
Alternatively, as deforestation increases, presidents are more likely to
construct the amazon as an issue of economic integration. This indicates
that Brazil created a self-image of a strong climate leadership because
of the good results achieved from 2004 to 2012 (Franchini and Viola
2019). In the same fashion, economic integration problem-constructions
are likely deployed as a justification for increasing deforestation
rates.

\hypertarget{discussion-and-conclusion}{%
\section{5 Discussion and Conclusion}\label{discussion-and-conclusion}}

This paper investigates how the Brazilian Amazon has been constructed as
a problem in Brazilian presidential speeches since 1985. Our findings
are threefold: we find that the frequency of the Amazon as a topic in
speeches inside and outside Brazil is equally driven by domestic events
(e.g.~the assassination of Chico Mendes) as well as international events
(Climate Summits). Second, the same government adopts a diverse range of
problem-construction. While economic integration dominated discourse
from 1985 to the mid-2000s, environmental conservation and social
development constructions steadily grew in the 2000s, temporarily
surpassing economic integration as a more common problem-construction
from 2010 to 2015. This implies an overall movement from only exploiting
the Amazon for economic purposes to exploiting it and protecting it.
Constructing the Amazon as an issue of sovereignty became more pertinent
after 2010. Finally, we find that presidents are more likely to
construct the Amazon as an environmental conservation problem than
economic integration or social development, as presidents move away from
the Amazon region. Conceptually, this contributes to understanding the
social construction of the Amazon in discourses and how these relate to
policies and environmental outcomes. Empirically, we provide the first
comprehensive overview of when, where, and how the Amazon is constructed
as an issue in presidential discourse.

Discursive problem-construction within democracies legitimizes ways of
thinking and acting towards the environment. If presidents promote an
agenda of economic and social development within Brazil that diverges
from the one promoted outside of Brazil, to what extent does the
implemented agenda respond to domestic versus international demands? The
Brazilian government successfully funded domestic public policy with
transnational support on several occasions: the 1992 Pilot Programme of
the G7 for the Protection of Rainforest; the 2001 Amazon Regional
Protected Areas Program by the World Bank and others; and the 2008
Amazon Fund which provided over USD 1 billion (Silva-Muller and Faul
2022). Concurrently, the national agenda of economic integration or
social development was pursued. For instance, rural credit offered to
local agricultural producers in Amazonian states, went up from 500
million reais a year in 1999 to over 4 billion a year by 2012
(Capobianco 2021). Multiple contradictory policies negotiated
simultaneously, imply that presidents construct policy objects as issues
important to local electorates within the Amazon while, at the same
time, highlighting aspects important for international actors elsewhere.

The decrease in deforestation that took place in Brazil from 2004 to
2012, was accompanied by a period of strong economic growth. With the
strengthening of environmentalism, through the participation of
indigenous and civil society in politics (Hochstetler and Keck 2007),
the fall of economic integration problem-construction and the rise of
both social development and environmental conservation constructions in
the 2000s suggest a new balance between granting local livelihoods their
rights and economic development. This new balance was both unprecedented
and not long-standing. Unprecedented because never before the
environment and people were equally present as the economy in
presidential discourse. Not long-standing because the dismantling of
environmental policy in favor of infrastructure and agricultural
expansion was already on its way in the late 2010s. The 2012 New Forest
Code is seen as a turning point: political opposition to conservation
organized itself and managed to lobby with the executive and won these
battles even though they were largely opposed by environmentalists.

The steady increase of sovereignty problem-constructions starting in
2010 brings an eerie twist. The embryo of Bolsonaro's Amazonian
discourse was breeding half a decade before he took office. Bolsonaro is
a product of political re-organization of national and international
actors - to which Rousseff and Temer were already responding in
discourse - rather than the cause of change in politics. The political
forces in Brazilian democracy that drove these policy and discursive
changes in problem-construction were long in the making, Bolsonaro's
problem-constructions and policies are the strongest forms of this
shift.

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

The authors are extremely grateful to Matias López, Graziella Moraes
Silva, and James Hollway for their support. The authors would also like
to thank Mario, Federico, Rodrigo, and Anna for valuable comments on
earlier drafts of this paper.

\hypertarget{disclosure-statement}{%
\section{Disclosure Statement}\label{disclosure-statement}}

The authors report there are no competing interests to declare.

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-acker2021}{}}%
Acker, Antoine. 2021. {``Amazon Development,''} Oxford research
encyclopedia of latin american history.,.
\url{https://doi.org/10.1093/acrefore/9780199366439.013.837}.

\leavevmode\vadjust pre{\hypertarget{ref-aklin2020}{}}%
Aklin, Michaël, and Matto Mildenberger. 2020. {``Prisoners of the Wrong
Dilemma: Why Distributive Conflict, Not Collective Action, Characterizes
the Politics of Climate Change.''} \emph{Global Environmental Politics}
20 (4): 4--27. \url{https://doi.org/10.1162/glep_a_00578}.

\leavevmode\vadjust pre{\hypertarget{ref-alesina2009}{}}%
Alesina, Alberto F., and Paola Giuliano. 2009. {``Preferences for
Redistribution.''} \url{https://www.nber.org/papers/w14825}.

\leavevmode\vadjust pre{\hypertarget{ref-andonova2014}{}}%
Andonova, Liliana B. 2014. {``Boomerangs to Partnerships? Explaining
State Participation in Transnational Partnerships for Sustainability.''}
\emph{Comparative Political Studies} 47 (3): 481--515.
\url{https://doi.org/10.1177/0010414013509579}.

\leavevmode\vadjust pre{\hypertarget{ref-assuncao2015}{}}%
Assunção, Juliano, Clarissa Gandour, and Rudi Rocha. 2015.
{``Deforestation Slowdown in the Brazilian Amazon: Prices or
Policies?''} \emph{Environment and Development Economics} 20 (6):
697--722. \url{https://doi.org/10.1017/S1355770X15000078}.

\leavevmode\vadjust pre{\hypertarget{ref-bacchi2009}{}}%
Bacchi, Carol Lee. 2009. \emph{Analysing Policy: What's the Problem
Represented to Be?} Pearson.

\leavevmode\vadjust pre{\hypertarget{ref-barros2020}{}}%
Barros, Antonio Teixeira de. 2020. {``Discursos parlamentares sobre a
Amazônia: sobre o que falam os deputados brasileiros.''} \emph{Política
\& Sociedade} 19 (46): 299--331.
\url{https://doi.org/10.5007/2175-7984.2020.e66962}.

\leavevmode\vadjust pre{\hypertarget{ref-becker2005}{}}%
Becker, Bertha K. 2005. {``Geopolítica da Amazônia.''} \emph{Estudos
Avançados} 19 (April): 71--86.
\url{https://doi.org/10.1590/S0103-40142005000100005}.

\leavevmode\vadjust pre{\hypertarget{ref-bevitori2015}{}}%
Bevitori, Cinzia. 2015. {``Discursive Constructions of the Environment
in American Presidential Speeches 1960{\textendash}2013: A Diachronic
Corpus-Assisted Study.''} \emph{Corpora and Discourse Studies}, 110--33.
\url{https://doi.org/10.1057/9781137431738_6}.

\leavevmode\vadjust pre{\hypertarget{ref-brice2021}{}}%
Brice, and Smith. 2021. {``The Amazon Is Fast Approaching a Point of No
Return.''} \emph{Bloomberg.com}, July.
\url{https://www.bloomberg.com/news/features/2021-07-29/amazon-rainforest-deforestation-land-grabs-surge-under-bolsonaro-in-brazil}.

\leavevmode\vadjust pre{\hypertarget{ref-calderwood2019}{}}%
Calderwood, Kevin J. 2019. {``Discourse in the Balance: American
Presidential Discourse about Climate Change.''} \emph{Communication
Studies} 70 (2): 235--52.
\url{https://doi.org/10.1080/10510974.2019.1572636}.

\leavevmode\vadjust pre{\hypertarget{ref-calderwood2020}{}}%
---------. 2020. {``Going Global: Climate Change Discourse in
Presidential Communications.''} \emph{Environmental Communication} 14
(1): 52--67. \url{https://doi.org/10.1080/17524032.2019.1592005}.

\leavevmode\vadjust pre{\hypertarget{ref-campbell2015}{}}%
Campbell, Jeremy M. 2015. \emph{Conjuring Property: Speculation and
Environmental Futures in the Brazilian Amazon}. Illustrated edition.
Seattle: University of Washington Press.

\leavevmode\vadjust pre{\hypertarget{ref-capobianco2019}{}}%
Capobianco, João Paulo. 2019. {``Avances y retrocesos de la
sostenibilidad en la Amazonia: un análisis de la gobernanza
socioambiental en la Amazonia,''} January.
\url{https://gredos.usal.es/handle/10366/139311}.

\leavevmode\vadjust pre{\hypertarget{ref-capobianco2021}{}}%
---------. 2021. \emph{Amazônia: Uma Década de Esperança}. 1ª edição.
São Paulo: Estação Liberdade.

\leavevmode\vadjust pre{\hypertarget{ref-cezar2020}{}}%
Cezar, Rodrigo Fagundes. 2020. {``Brazilian Presidential Speeches from
1985 to July 2020.''}
\url{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/M9UU09}.

\leavevmode\vadjust pre{\hypertarget{ref-silva2019}{}}%
Da Silva, Antonio José Bacelar, and Erika Robb Larkins. 2019. {``The
Bolsonaro Election, Antiblackness, and Changing Race Relations in
Brazil.''} \emph{The Journal of Latin American and Caribbean
Anthropology} 24 (4): 893--913.

\leavevmode\vadjust pre{\hypertarget{ref-drummond2006}{}}%
Drummond, Jose, and Ana Flavia Barros-Platiau. 2006. {``Brazilian
Environmental Laws and Policies, 1934-2002: A Critical Overview.''}
\emph{Law and Policy} 28 (1): 83--108.
\url{https://doi.org/10.1111/j.1467-9930.2005.00218.x}.

\leavevmode\vadjust pre{\hypertarget{ref-franchini2019}{}}%
Franchini, Matias Alejandro, and Eduardo Viola. 2019. {``Myths and
Images in Global Climate Governance, Conceptualization and the Case of
Brazil (1989 - 2019).''} \emph{Revista Brasileira de Política
Internacional} 62 (September).
\url{https://doi.org/10.1590/0034-7329201900205}.

\leavevmode\vadjust pre{\hypertarget{ref-gillion2016}{}}%
Gillion, Daniel Q. 2016. \emph{Governing with Words: The Political
Dialogue on Race, Public Policy, and Inequality in America}. Cambridge:
Cambridge University Press.
\url{https://doi.org/10.1017/CBO9781316412299}.

\leavevmode\vadjust pre{\hypertarget{ref-grimmer2022}{}}%
Grimmer, Justin, Margaret E. Roberts, and Brandon M. Stewart. 2022.
\emph{Text as Data: A New Framework for Machine Learning and the Social
Sciences}. Princeton, New Jersey Oxford: Princeton University Press.

\leavevmode\vadjust pre{\hypertarget{ref-harris2021}{}}%
Harris, Bryan. 2021. {``Drought Puts Amazon at Risk of {`}Large-Scale
Dieback{'}, Researchers Warn.''} \emph{Financial Times}, July.
\url{https://www.ft.com/content/02071ae7-dcf5-4c61-9c3c-b55f5aef8b0e}.

\leavevmode\vadjust pre{\hypertarget{ref-hecht1990}{}}%
Hecht, Susanna B., and Alexander Cockburn. 1990. \emph{The Fate of the
Forest: Developers, Destroyers, and Defenders of the Amazon, Updated
Edition}. Chicago, IL: University of Chicago Press.
\url{https://press.uchicago.edu/ucp/books/book/chicago/F/bo10387801.html}.

\leavevmode\vadjust pre{\hypertarget{ref-hecht2020}{}}%
Hecht, Susanna, and Raoni Rajão. 2020. {``From {``}Green Hell{''} to
{``}Amazonia Legal{''}: Land Use Models and the Re-Imagination of the
Rainforest as a New Development Frontier.''} \emph{Land Use Policy} 96
(July): 103871. \url{https://doi.org/10.1016/j.landusepol.2019.02.030}.

\leavevmode\vadjust pre{\hypertarget{ref-hirschman1963}{}}%
Hirschman, Albert O. 1963. \emph{Journeys Toward Progress: Studies of
Economic Policy-Making in Latin America}. Twentieth Century Fund.

\leavevmode\vadjust pre{\hypertarget{ref-hirschman1975}{}}%
---------. 1975. {``Policymaking and Policy Analysis in Latin America: A
Return Journey.''} \emph{Policy Sciences} 6 (4): 385--402.
\url{https://www.jstor.org/stable/4531616}.

\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2021}{}}%
Hochstetler, Kathryn. 2021. {``Climate Institutions in Brazil: Three
Decades of Building and Dismantling Climate Capacity.''}
\emph{Environmental Politics} 30 (sup1): 49--70.
\url{https://doi.org/10.1080/09644016.2021.1957614}.

\leavevmode\vadjust pre{\hypertarget{ref-hochstetler2007}{}}%
Hochstetler, Kathryn, and Margaret E. Keck. 2007. \emph{Greening Brazil:
Environmental Activism in State and Society}.
\url{https://doi.org/10.1215/9780822390596}.

\leavevmode\vadjust pre{\hypertarget{ref-keck1998}{}}%
Keck, Margaret E., and Kathryn Sikkink. 1998. \emph{Activists Beyond
Borders: Advocacy Networks in International Politics}. 1st Edition.
Ithaca, N.Y: Cornell University Press.

\leavevmode\vadjust pre{\hypertarget{ref-lopez2020}{}}%
López, Matias, Graziella Moraes Silva, Chana Teeger, and Pedro Marques.
2020. {``Economic and Cultural Determinants of Elite Attitudes Toward
Redistribution.''} \emph{Socio-Economic Review}, May.
\url{https://doi.org/10.1093/ser/mwaa015}.

\leavevmode\vadjust pre{\hypertarget{ref-meyer2021}{}}%
Meyer, David, Evgenia Dimitriadou, Kurt Hornik, Andreas Weingessel, and
Friedrich Leisch. 2021. \emph{E1071: Misc Functions of the Department of
Statistics, Probability Theory Group (Formerly: E1071), TU Wien}.
\url{https://CRAN.R-project.org/package=e1071}.

\leavevmode\vadjust pre{\hypertarget{ref-miranda2021}{}}%
Miranda, David. 2021. {``Bolsonaro{'}s 1,000km Amazon Railway Will Cause
Climate Chaos. It Must Be Stopped.''} \emph{The Guardian}, July.
\url{https://www.theguardian.com/commentisfree/2021/jul/28/bolsonaro-amazon-railway-climate-chaos-must-be-stopped}.

\leavevmode\vadjust pre{\hypertarget{ref-noble2006}{}}%
Noble, William S. 2006. {``What Is a Support Vector Machine?''}
\emph{Nature Biotechnology} 24 (12): 1565--67.

\leavevmode\vadjust pre{\hypertarget{ref-padua2012}{}}%
Pádua, José Augusto. 2012. {``Environmentalism in Brazil: A Historical
Perspective.''} \emph{A Companion to Global Environmental History} 1:
455--73.

\leavevmode\vadjust pre{\hypertarget{ref-pereira2021}{}}%
Pereira, Joana Castro, and Eduardo Viola. 2021. \emph{Climate Change and
Biodiversity Governance in the Amazon: At the Edge of Ecological
Collapse?} Routledge.

\leavevmode\vadjust pre{\hypertarget{ref-putnam1988}{}}%
Putnam, Robert D. 1988. {``Diplomacy and Domestic Politics: The Logic of
Two-Level Games.''} \emph{International Organization} 42 (3): 427--60.
\url{http://www.jstor.org/stable/2706785}.

\leavevmode\vadjust pre{\hypertarget{ref-rajao2020}{}}%
Rajão, Raoni, Britaldo Soares-Filho, Felipe Nunes, Jan Börner, Lilian
Machado, Débora Assis, Amanda Oliveira, et al. 2020. {``The Rotten
Apples of Brazil's Agribusiness.''} \emph{Science} 369 (6501): 246--48.
\url{https://doi.org/10.1126/science.aba6646}.

\leavevmode\vadjust pre{\hypertarget{ref-silva-muller2022a}{}}%
Silva-Muller, Livio. 2022. {``Payment for Ecosystem Services and the
Practices of Environmental Fieldworkers in Policy Implementation: The
Case of Bolsa Floresta in the Brazilian Amazon.''} \emph{Land Use
Policy} 120 (September): 106251.
\url{https://doi.org/10.1016/j.landusepol.2022.106251}.

\leavevmode\vadjust pre{\hypertarget{ref-silva-muller2022}{}}%
Silva-Muller, Livio, and Moira V. Faul. 2022. {``Protecting the Amazon
and Its People: The Role of Civil Society in Local Effectiveness of
Trasnational Partnerships.''} In \emph{Partnerships for Sustainability
in Contemporary Global Governance}, 83--103. Routledge.
\url{https://doi.org/10.4324/9781003148371-6}.

\leavevmode\vadjust pre{\hypertarget{ref-soares-filho2014}{}}%
Soares-Filho, Britaldo, Raoni Rajão, Marcia Macedo, Arnaldo Carneiro,
William Costa, Michael Coe, Hermann Rodrigues, and Ane Alencar. 2014.
{``Cracking Brazil's Forest Code.''} \emph{Science} 344 (6182): 363--64.
\url{https://doi.org/10.1126/science.1246663}.

\leavevmode\vadjust pre{\hypertarget{ref-sposito2021}{}}%
Sposito, Henrique. 2021. \emph{Poldis: Tools for Analyzing Political
Discourse}. \url{https://github.com/henriquesposito/poldis}.

\leavevmode\vadjust pre{\hypertarget{ref-viola1987}{}}%
Viola, Eduardo J. 1987. {``O Movimento Ecológico No Brasil, 1974-1986:
Do Ambientalismo à Ecopolítica.''} \emph{Revista Brasileira de Ciencias
Sociais} 3 (93): 5--26.
\url{http://anpocs.com/images/stories/RBCS/03/rbcs03_01.pdf}.

\leavevmode\vadjust pre{\hypertarget{ref-lepolaindewaroux2021}{}}%
Waroux, Yann de, Rachael D. Garrett, Mollie Chapman, Cecilie Friis,
Jeffrey Hoelle, Leonie Hodel, Kelly Hopping, and Julie Gwendolin
Zaehringer. 2021. {``The Role of Culture in Land System Science.''}
\emph{Journal of Land Use Science} 16 (4): 450--66.
\url{https://doi.org/10.1080/1747423X.2021.1950229}.

\leavevmode\vadjust pre{\hypertarget{ref-zarefsky2004}{}}%
Zarefsky, David. 2004. {``Presidential Rhetoric and the Power of
Definition.''} \emph{Presidential Studies Quarterly} 34 (3): 607--19.
\url{https://www.jstor.org/stable/27552615}.

\end{CSLReferences}

\newpage

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\begin{figure}
\centering
\includegraphics{Full_draft_20220901_files/figure-latex/Figure 7-1.pdf}
\caption{Amazonian speeches in time and space}
\end{figure}

\begin{landscape}

\begin{table}

\caption{\label{tab:codebook}Amazonian Problem-Construction Codebook}
\centering
\resizebox{\linewidth}{!}{
\fontsize{9}{11}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{9cm}>{\raggedright\arraybackslash}p{9cm}}
\toprule
problem-construction & Description & Example\\
\midrule
\textbf{\cellcolor{gray!6}{National Sovereignty}} & \cellcolor{gray!6}{This code constructs the Amazon region and/or forest as an issue of national sovereignty. We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory. Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon. In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.} & \cellcolor{gray!6}{Congressman, the fundamental link for Brazil to really head in the direction to prosperity. I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting. I would like to thank the Chinese government. For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil. (Bolsonaro 25/10/2019)}\\
\textbf{Economic Integration} & This code constructs the Amazon region and/or forest as an issue of economic integration. It advances the view that the Amazon needs to be developed and connected to the national economy. This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes. & If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions. We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway. This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)\\
\textbf{\cellcolor{gray!6}{Social Development}} & \cellcolor{gray!6}{This code constructs the Amazon region and/or forest as an issue of social development. It advances the view that Amazon is full of citizens who should have their rights guaranteed. This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house). This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light. Finally, this includes referrals to culture and the right to vote.} & \cellcolor{gray!6}{The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas. We have invested over 14 billion reais in this program, in three and a half years. Do you know how many electrical lines we have already built? One million kilometers of lines. (Lula 20/11/2009)}\\
\textbf{Environmental Conservation} & This code constructs the Amazon region and/or forest as an issue of conservation. This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region. The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered. It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created. & I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process. This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr. Mesquita (Sarney 20/07/1989)\\
\bottomrule
\end{tabu}}
\end{table}

\end{landscape}

\begin{landscape}

<table style="border-collapse:collapse; border:none;">
<tr>
<th style="border-top: double; text-align:center; font-style:normal; font-weight:bold; padding:0.2cm;  text-align:left; ">&nbsp;</th>
<th colspan="3" style="border-top: double; text-align:center; font-style:normal; font-weight:bold; padding:0.2cm; ">con vs all</th>
<th colspan="3" style="border-top: double; text-align:center; font-style:normal; font-weight:bold; padding:0.2cm; ">EI vs all</th>
<th colspan="3" style="border-top: double; text-align:center; font-style:normal; font-weight:bold; padding:0.2cm; ">SD vs all</th>
<th colspan="3" style="border-top: double; text-align:center; font-style:normal; font-weight:bold; padding:0.2cm; ">sov vs all</th>
</tr>
<tr>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  text-align:left; ">Predictors</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  ">Odds Ratios</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  ">CI</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  ">p</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  ">Odds Ratios</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  ">CI</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  col7">p</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  col8">Odds Ratios</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  col9">CI</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  0">p</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  1">Odds Ratios</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  2">CI</td>
<td style=" text-align:center; border-bottom:1px solid; font-style:italic; font-weight:normal;  3">p</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; ">(Intercept)</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.18</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.12&nbsp;&ndash;&nbsp;0.26</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  "><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.21</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.15&nbsp;&ndash;&nbsp;0.28</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col7"><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col8">0.40</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col9">0.26&nbsp;&ndash;&nbsp;0.61</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  0"><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  1">0.10</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  2">0.06&nbsp;&ndash;&nbsp;0.17</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  3"><strong>&lt;0.001</strong></td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; ">thousand km</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.12</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.08&nbsp;&ndash;&nbsp;1.17</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  "><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.94</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.90&nbsp;&ndash;&nbsp;0.99</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col7"><strong>0.018</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col8">0.90</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col9">0.83&nbsp;&ndash;&nbsp;0.97</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  0"><strong>0.011</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  1">1.01</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  2">0.93&nbsp;&ndash;&nbsp;1.08</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  3">0.805</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; ">election year</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.33</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.98&nbsp;&ndash;&nbsp;1.81</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.066</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.98</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.75&nbsp;&ndash;&nbsp;1.27</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col7">0.866</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col8">1.39</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col9">0.99&nbsp;&ndash;&nbsp;1.93</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  0">0.055</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  1">0.64</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  2">0.37&nbsp;&ndash;&nbsp;1.06</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  3">0.096</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; ">def year</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.97</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">0.95&nbsp;&ndash;&nbsp;0.99</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  "><strong>0.005</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.04</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.02&nbsp;&ndash;&nbsp;1.06</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col7"><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col8">0.93</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col9">0.91&nbsp;&ndash;&nbsp;0.95</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  0"><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  1">0.97</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  2">0.94&nbsp;&ndash;&nbsp;1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  3">0.057</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; ">AAI</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.00&nbsp;&ndash;&nbsp;1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  "><strong>&lt;0.001</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  ">1.00&nbsp;&ndash;&nbsp;1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col7"><strong>0.026</strong></td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col8">1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  col9">1.00&nbsp;&ndash;&nbsp;1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  0">0.174</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  1">1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  2">1.00&nbsp;&ndash;&nbsp;1.00</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:center;  3">0.225</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; padding-top:0.1cm; padding-bottom:0.1cm; border-top:1px solid;">Observations</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left; border-top:1px solid;" colspan="3">1842</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left; border-top:1px solid;" colspan="3">1842</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left; border-top:1px solid;" colspan="3">1842</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left; border-top:1px solid;" colspan="3">1842</td>
</tr>
<tr>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; text-align:left; padding-top:0.1cm; padding-bottom:0.1cm;">R<sup>2</sup> Tjur</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left;" colspan="3">0.029</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left;" colspan="3">0.019</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left;" colspan="3">0.026</td>
<td style=" padding:0.2cm; text-align:left; vertical-align:top; padding-top:0.1cm; padding-bottom:0.1cm; text-align:left;" colspan="3">0.004</td>
</tr>

</table>

\end{landscape}

\end{document}

### 2022-09-21 Draft_September_2022/Full_draft_20220901.rmd
#textwithconfidenceintervalsandprobabilities

--- 2022-09-20 Draft_September_2022/Full_draft_20220901.rmd
@@
 ```
+
 ```{=latex}
@@
 ```
+
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 
-We convert log odds from Table 1, below, into probabilities [^2].
-It shows that for each 1000Km increase, we find an increase of 52.8% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
-That is, the farthest away the president is from the Amazon region, the more likely the president is to construct it as an issue of environmental conservation.
-Second,the opposite is true for both economic integration (and social development): for an increase of 1000Km, we find a decrease of 48.5% (47.4%), respectively.
+We convert log odds from Table 1, below, into probabilities and report the 95% confidence interval in the subsequent sentences [^2].
+First, we find that for each 1000Km increase in distance, there is an increase between 51.92% and 53.91% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
+That is, the farthest away presidents are from the Amazon region, the more likely they are to construct it as an issue of environmental conservation.
+Second,the opposite is true for economic integration (and social development): for an increase of 1000Km in distance, we find a decrease between 47.36% (45.35%) and 49.74% (49.23%), respectively.
 When speaking within the Amazon, presidents focus on social development and economic integration.
@@
 
+odd2prob <- function(x){
+  prob <- x / (1 + x)
+  return(prob)
+}
 ```
@@
 
-````{=tex}
-\begin{landscape}
-
-```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+```{r Table 3, eval=FALSE, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results="asis"}
 
@@
 
-\end{landscape}
-````
+```

### 2022-09-22 Draft_September_2022/Full_draft_20220901.rmd
Updated the last regression table with odds ratio and confidence intervals

@@
 library(gridExtra)
-library(sjPlot)
-library(parameters)
-
+library(modelsummary)
 Sys.setlocale("LC_ALL", "C")
@@
 
-\newpage
+# Appendix
 
-# Appendix
+````{=tex}
+\begin{landscape}
+
+```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+codebook <- tibble::tibble("problem-construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
+                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
+We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
+Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon.
+In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
+It advances the view that the Amazon needs to be developed and connected to the national economy.
+This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
+It advances the view that Amazon is full of citizens who should have their rights guaranteed.
+This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
+This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
+Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
+This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
+The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
+It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
+I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
+I would like to thank the Chinese government.
+For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
+(Bolsonaro 25/10/2019)",
+                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
+We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
+This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
+                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
+We have invested over 14 billion reais in this program, in three and a half years.
+Do you know how many electrical lines we have already built?
+One million kilometers of lines.
+(Lula 20/11/2009)",
+                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
+This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
+Mesquita (Sarney 20/07/1989)"))
+
+kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
+```
+
+\end{landscape}
+````
 
@@
 
-````{=tex}
-\begin{landscape}
+\newpage
 
-```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble("problem-construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
-                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
-We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
-It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
-It advances the view that Amazon is full of citizens who should have their rights guaranteed.
-This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
-This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
-This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
-I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
-I would like to thank the Chinese government.
-For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
-(Bolsonaro 25/10/2019)",
-                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
-We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
-                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
-We have invested over 14 billion reais in this program, in three and a half years.
-Do you know how many electrical lines we have already built?
-One million kilometers of lines.
-(Lula 20/11/2009)",
-                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
-This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
-Mesquita (Sarney 20/07/1989)"))
+```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, echo=FALSE, paged.print=TRUE, include=TRUE}
 
-kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
-```
-
-\end{landscape}
-````
-
-```{r Table 3, eval=FALSE, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results="asis"}
-
-tab_model(model_logit_con2,model_logit_ei2,model_logit_sd2,model_logit_sov2)
+modelsummary::modelsummary(list("Conservation" = model_logit_con2,
+                                "Economic Integration" = model_logit_ei2,
+                                "Social Development" = model_logit_sd2,
+                                "Sovereignty" = model_logit_sov2),
+                           title = "Odds Ratio and Confidence Intervals",
+                           exponentiate = TRUE, statistic = "conf.int")
 
 ```
-
-```

### 2022-09-22 Draft_September_2022/Full_draft_20220901.rmd
Updated table for model in appendix

@@
 
-\newpage
+````{=tex}
+\begin{landscape}
 
@@
                                 "Sovereignty" = model_logit_sov2),
-                           title = "Odds Ratio and Confidence Intervals",
-                           exponentiate = TRUE, statistic = "conf.int")
+                           exponentiate = TRUE, statistic = "conf.int",
+                           coef_rename = c("thousand_km" = "1000 km",
+                                        "def_year" = "Yearly Deforestation",
+                                        "AAI" = "Average Yearly Inflation",
+                                        "election_year" = "Election Year",
+                                        "(Intercept)" = "Constant"),
+                           stars = TRUE,
+                           title = "Odds Ratio and Confidence Intervals")
+```
 
-```
+\end{landscape}
+````

### 2022-09-23 Draft_September_2022/Full_draft_20220901.rmd
#grammarcorrections #addedmario'spaperasreference

@@
 csl: chicago.csl
-abstract: Presidential speeches influence the ways we think about and act towards the environment transnationally, but they are understudied.
+abstract: Presidential speeches influence the ways we think about and act towards the environment , but they are understudied.
 We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses across time and space.
-Using supervised machine learning, we classify statements about the Amazon in 6130 presidential speeches since 1985.
+Using supervised machine learning, we classify statements about the Amazon in 6130 transnational presidential speeches since 1985.
 We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches inside and outside Brazil.
@@
 ```
-
 ```{=latex}
@@
 ```
-
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are often tied to environmental conservation views.
+While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are often tied to environmental conservation.
 These monolithic representations advance the view that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments.
+Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between or within, governments.
 Building on @hirschman1963 conceptualization of chosen problems and @bacchi2009 theory of problem-representation in policy, we propose a framework for identifying problem-constructions in discourse and investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
@@
 Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015; @rajao2020 ], and many others.
+Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], international markets [@assuncao2015; @rajao2020 ], and many others.
 Nevertheless, the role of the president remains understudied.
@@
 @bacchi2009 [p.
-10] argues that policies have a cultural dimension as they take" shape within specific historical and national or international contexts".
+10] argues that policies have a cultural dimension as they take "shape within specific historical and national or international contexts".
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed, this is a policy object.
@@
 There is also an empirical gap in terms of how the Amazon, specifically, has been constructed as a problem along time and geographic location in political discourses.
-While governmental discourses in Brazil have been studied for topics such as inflation or race relations [see @silva2019], the environment remains largely absent.
+While governmental discourses in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the environment remains largely absent.
 An exception is @barros2020, who investigates Amazonian discourse in the Brazilian Congress.
@@
 8], and when the dust settled and the scramble was over, over half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas as the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 at earlier regimes aimed at protecting Brazil's sovereignty over the Amazon [@hecht2020].
-As we move from a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
-Threats to national sovereignty, consequently, broaden from state actors to a wide set of actors.
+While Brazilian military diplomacy was very successful, the process did not come without its traumas as for example the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
+These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 as earlier regimes aimed at protecting Brazil's sovereignty over the Amazon [@hecht2020].
+As we move to a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
+Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
 Claims of attempts to 'internationalize' the Brazilian Amazon, for instance, are targeted at foreign actors as well as domestic non-state actors.
@@
 Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences around, rather than words because sentences usually contain a cohesive idea.
-By doing so we create our unit of analysis: an Amazon statement.
-We use Amazon statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
+We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
+By doing so we create our unit of analysis: an Amazonian statement.
+We use Amazonian statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
 When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
@@
 Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazon Statements identified.
-We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem.As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
+This amount refers to 50% of all the Amazonian Statements identified.
+We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem.
+As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
 This allows a robust validation set to verify the models.
@@
 However, the economy is generally a topic that presidents speak about frequently.
-Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
+Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall.
+Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
 We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
@@
 On average, presidents mention the Amazon in 15.4% of their speeches.
-For comparison purposes the averages for other policy objects in the same corpus of speeches are: Inequality (14.7%), Criminality (17.3%), Inflation (20.9%), and Unemployment (13.8%).
+For comparison purposes the averages for other policy objects in the same corpus of speeches are: inequality (14.7%), criminality (17.3%), inflation (20.9%), and unemployment (13.8%).
 The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
@@
 
-We observe five local maxima both inside and outside Brazil: 1989, 1992, 2009, 2015, and 2019.
+Five local maxima stand out in the figure: 1989, 1992, 2009, 2015, and 2019.
 These points coincide with internal and external events that help us explain the rises and falls of the Amazon in presidential discourse.
@@
 
-Our subsequent analysis of pure-types and mixed-types suggests that governments do not defend a specific view of the Amazon.
+Our subsequent analysis suggests that governments do not defend a specific view of the Amazon.
 The same governments construct the Amazon as various pure and mixed type problems, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
@@
 We focus on pure-type constructions as these represent most constructions and avoid ambiguity.
-The independent variable for all models is the distance between the state country capital to Manaus.
+The independent variable for all models is the distance between the state's or country's capital to Manaus.
 Figure 6, below, depicts the predicted probabilities from the models (see Table 1) as functions of distance.
@@
 This paper investigates how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (Climate Summits).
+Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events as well as international events.
 Second, the same government adopts a diverse range of problem-construction.

### 2022-09-23 Draft_September_2022/Full_draft_20220901.rmd
#small changes suggested by Hollway

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: 20 September 2022
+date: 23 September 2022
 output:
@@
 csl: chicago.csl
-abstract: Presidential speeches influence the ways we think about and act towards the environment , but they are understudied.
+abstract: Presidential speeches can influence the ways people think about and act towards the environment , but they are understudied.
 We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses across time and space.
@@
 In turn, constructing the Amazon as an issue of sovereignty steadily increases since 2010.
-Lastly, the farthest away presidents are from the Amazon itself, the more likely they are to construct the Amazon as an issue of environmental conservation.
+Lastly, the farther away presidents are from the Amazon itself, the more likely they are to construct the Amazon as an issue of environmental conservation.
 ---
@@
 We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.Different governments throughout Brazilian history have been described as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.Different governments throughout Brazilian history have been identified as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
 
@@
 Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], international markets [@assuncao2015; @rajao2020 ], and many others.
+Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015; @rajao2020 ].
 Nevertheless, the role of the president remains understudied.
@@
 We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded on Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
+We then develop a codebook grounded in Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
 We use this codebook to manually code a randomly selected training set of Amazon-related statements.
@@
 While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem-constructions from 2011 to 2016.
-Constructing the Amazon as an issue of sovereignty has increasingly become more pertinent after 2010.
-Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents move farther away from the Amazon region.
+Constructing the Amazon as an issue of sovereignty has become more pertinent after 2010.
+Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents speak farther away from the Amazon region.
 That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
@@
 
-An interesting context to study the relationship between problem-construction and policy objects is presidential speeches, as they legitimize ways of thinking about an issue.
+An interesting context to study the relationship between problem-construction and policy objects is presidential speeches, as they influence ways of thinking about an issue.
 While the relationship between presidential speeches and policy may not be causal, they have the power to introduce and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004; @gillion2016].
@@
 From this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
-We also argue that a fourth one is missing, social development, that focuses on the rights and dignity of the inhabitants of the Amazonian region.
+We also argue a fourth, social development, that focuses on the rights and dignity of the inhabitants of the Amazonian region.
 
@@
 Each model takes the share of a specific problem-construction versus all other problem-constructions as their dependent variable.
-This means we try to predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
+This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
 Our main independent variable is the distance (in kilometers) from the state or country capital where the speech took place to Manaus (the capital of the Amazonas State and centrally located in the region).
@@
 Figure 4, below, illustrates the share of each pure-type in time.
-Pure problem-constructions dominate, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem-constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
-Pure economic integration constructions dominated constructions from 1985 to the late 2000s.
+Pure problem-constructions are most common, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem-constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
+Pure economic integration constructions are most common constructions from 1985 to the late 2000s.
 This is especially pertinent during the Cardoso administration.
@@
 Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
-Constructing the Amazon as multiple issues averages at 18% of all constructions in time.
+Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
 Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.

### 2022-09-23 Draft_September_2022/Full_draft_20220901.rmd
#finalchanges

@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985
+title: How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985
 author:
@@
 csl: chicago.csl
-abstract: Presidential speeches can influence the ways people think about and act towards the environment , but they are understudied.
-We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in discourses across time and space.
+abstract: Presidential speeches can influence the ways people think and act towards the environment , but they are understudied.
+We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem across time and space.
 Using supervised machine learning, we classify statements about the Amazon in 6130 transnational presidential speeches since 1985.
 We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches inside and outside Brazil.
-While constructing the Amazon as a problem of economic integration dominates discourses until the mid-2000s, environmental conservation and social development constructions increase in relevance and temporarily surpass economic integration from 2010 to 2015.
-In turn, constructing the Amazon as an issue of sovereignty steadily increases since 2010.
+While constructing the Amazon as a problem of economic integration are the most common until the mid-2000s, environmental conservation and social development constructions temporarily surpass economic integration from 2010 to 2015.
+In turn, constructing the Amazon as an issue of sovereignty increases since 2010.
 Lastly, the farther away presidents are from the Amazon itself, the more likely they are to construct the Amazon as an issue of environmental conservation.
@@
 ```{=latex}
-\wordcount{ 8470 (including abstract, text, references, and and footnotes)}
+\wordcount{ 8299 (including abstract, text, references, and and footnotes)}
 ```
@@
 By doing so we create our unit of analysis: an Amazonian statement.
-We use Amazonian statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements across the 946 speeches about the Amazon identified.
+We use Amazonian statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements about the Amazon.
 When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
@@
 This allows a robust validation set to verify the models.
-Also, automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
+Automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
 The intercoder agreement for hand-coded categories was 85%, on average.
-For each non-matching coded observation, the co-authors discussed and sorted their disagreements.
-Most disagreements related to different interpretations of the codebook, which were subsequently clarified.
+For each non-matching coded observation, the co-authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
 
@@
 The steady increase of sovereignty problem-constructions starting in 2010 brings an eerie twist.
-The embryo of Bolsonaro's Amazonian discourse was breeding half a decade before he took office.
+The embryo of Bolsonaro's Amazonian discourse was growing half a decade before he took office.
 Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change in politics.

### 2022-10-18 amazon_def_presentation/amazon_def_presentation.Rmd
Updated CIES presentation

--- 2022-05-25 amazon_def_presentation/amazon_def_presentation.Rmd
@@
 ---
-title: "How has the Brazilian Amazon been constructed as a problem?"
-subtitle: "The Economy, the environment, the people, and the nation in the presidential speeches since 1985"
+title: "How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985"
 author: "<large>Henrique Sposito and Livio Silva-Muller</large>"
-institute: "<small>Albert Hirscman Centre on Democracy | Geneva Graduate Institute</small>"
 date: "<small>`r format(Sys.Date(), '%A, %e %B, %Y')`<small>"
@@
       - "default"
-      - "assets/iheid-xaringan-style.css"
+      - "assets/am-xaringan-style.css"
       - "https://cdnjs.cloudflare.com/ajax/libs/animate.css/4.1.1/animate.min.css"
@@
 ---
-class: center middle
 
-## How has the Brazilian Amazon been constructed as a problem in discourse over time, by geographical location, and between/within governments?
+# How research get's made, a look under the hood
 
-![:scale 50%](assets/Images/presid.jpeg)
+- Collaborating in R with [GitHub](https://github.com/henriquesposito/amazondef)
 
-*Motivation*: Connecting the social-cultural construction of the Amazon and to the effects on environmental outcomes
+- This presentation
 
-```{r setup, include=FALSE}
+- This article
+
+```{r setup, include=FALSE, message=FALSE, warning=FALSE}
 options(htmltools.dir.version = FALSE, servr.daemon = TRUE)
 knitr::opts_chunk$set(cache=TRUE, autodep = TRUE, fig.retina = 3, message = FALSE, warning = FALSE)
-library(knitr)
-library(iheiddown)
-library(sjPlot)
-#devtools::install_github("mitchelloharawild/icons")
-library(icons)
-#devtools::install_github("gadenbuie/xaringanExtra")
+library(dplyr)
+library(tidyr)
+library(scales)
+library(RColorBrewer)
+library(stargazer)
+library(kableExtra)
+library(tibble)
+library(readxl)
+library(ggplot2)
+library(gridExtra)
+library(modelsummary)
 library(xaringanExtra)
@@
 ```{r, load_refs, include=FALSE, cache=FALSE}
-# Initializes the bibliography
 library(RefManageR)
-BibOptions(check.entries = FALSE,
-           bib.style = "authoryear", # Bibliography style
-           max.names = 3, # Max author names displayed in bibliography
-           sorting = "nyt", #Name, year, title sorting
-           cite.style = "authoryear", # citation style
-           style = "markdown",
-           hyperlink = FALSE,
-           dashed = FALSE)
-myBib <- ReadBib("assets/myBib.bib", check = FALSE)
-# Note: don't forget to clear the knitr cache to account for changes in the
-# bibliography.
+myBib <- ReadBib("assets/myBib.bib")
 ```
+
 ---
+
 class: split two
 
-Conceptual framework
+# The Brazilian Amazon, as a policy object
+
+.pull-left[
+
+**We need to protect the Amazon from foreign interests.**
+
+**We need to exploit the Amazon's natural resources.**
+
+**We need to provide better living standards for the people in the Amazon.**
+
+**We need to preserve the Amazon as a standing ecosystem.**
+
+]
+
+.pull-right[
+![:scale 120%](assets/Images/amazon_basin.jpeg)
+]
+
+---
+
+class: split two middle
+
+.pull-left[
+
+## Research Question:
+
+*How the Brazilian Amazon has been constructed as a problem in transnational presidential speeches since 1985?*
+
+]
+
+.pull-right[
+
+![:scale 120%](assets/Images/presid.jpeg)
+]
+
+```{r data, message=FALSE, warning=FALSE, include=FALSE}
+# Load data
+pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
+pop <-  pop %>% select(-c(title, date, location))
+ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
+ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
+AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
+location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
+  select(-location_cat) %>%
+  distinct()
+ama <- left_join(ama, location_km, by = "location")
+amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
+adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
+# Missing year data
+amazon_def_year <- rbind(adr, amazon_def_year) 
+hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
+                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
+                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
+                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
+                           "Rousseff", "Temer", "Bolsonaro"))
+amazon_def_year$area <- amazon_def_year$def_year*1000
+# Prepare data for problem-constructions
+sov <- ama %>% 
+  filter(sov==1) %>% 
+  count(sov, year) %>%
+  group_by(year) %>%
+  select(-c(sov))%>%
+  rename (sov = n)
+ei <- ama %>% 
+  filter(ei==1) %>% 
+  count(ei, year) %>%
+  group_by(year) %>%
+  select(-c(ei))%>%
+  rename (ei = n) %>%
+  ungroup() %>%
+  tibble::add_row(year = 2017, ei = 0) %>%
+  tibble::add_row(year = 2018, ei = 0)
+sd <- ama %>% 
+  filter(sd==1) %>% 
+  count(sd, year) %>%
+  group_by(year) %>%
+  select(-c(sd))%>%
+  rename (sd = n)
+con <- ama %>% 
+  filter(con==1) %>% 
+  count(con, year) %>%
+  group_by(year) %>%
+  select(-c(con))%>%
+  rename (con = n)
+other <- ama %>% 
+  filter(other==1) %>% 
+  count(other, year) %>%
+  group_by(year) %>%
+  select(-c(other))%>%
+  rename (other = n)
+temp <- ei %>% 
+  left_join(other) %>% 
+  left_join(con) %>% 
+  left_join(sd) %>% 
+  left_join(sov) %>% 
+  replace(is.na(.), 0)
+# Get mixed types in
+ama_mx <-  ama %>%
+  unite(mixed_type, sov:con, sep="_") %>%
+  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure National Sovereignty",
+                                   mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
+                                   mixed_type == '0_0_1_0' ~ "Pure Social Development",
+                                   mixed_type == '0_0_0_1' ~ "Pure Environmental Conservation",
+                                   mixed_type == '0_0_0_0' ~ "Other",
+                                   mixed_type == '0_1_0_1' ~ "Economic Conservation",
+                                   mixed_type == '0_1_1_0' ~ "Social Economic",
+                                   mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
+                                   mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
+                                   mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
+                                   mixed_type == '0_0_1_1' ~ "Social Conservation",
+                                   grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
+                                         mixed_type) ~ "Other Mixed-types"),
+         levels = c("Pure Economic Integration", "Pure Environmental Conservation",
+                    "Pure Social Development",
+                    "Pure National Sovereignty", "Other", "Economic Conservation", 
+                    "Social Economic", "Sovereign Conservation",
+                    "Economic, Social,\nand Conservation",
+                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
+         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Environmental Conservation|
+                                   |Pure Social Development|Pure National Sovereignty",
+                                   mx_cat) ~ "Pure-types",
+                             grepl("^Other$", mx_cat) ~ "Other",
+                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
+                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
+                                   |Social Conservation|Other Mixed-types",
+                                   mx_cat) ~ "Mixed-types"),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+                                      year), 1, 0),
+                  location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
+                                     location, ignore.case = TRUE), # minor coding issues to fix
+                               "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat), # minor coding issues to fix
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries", location_cat),
+                               levels = c("International", "Amazonian States",
+                                          "Amazonian Countries", "Brasilia",
+                                          "Non Amazonian States")))
+
+```
+
+```{r theme, include=FALSE, warning=FALSE, message=FALSE}
+# custom ploting theme for all plots
+theme_am <- function(x) {
+  theme(text = element_text(size=12,  family="Times"),
+        panel.background = element_rect("white", "black", .5, "solid"),
+                  panel.grid.major = element_line(color = "grey", size = 0.2,
+                                                  linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "none")
+}
+```
+
+---
+
+class: split two
+
+# Presidential discourses and chosen problems
 
@@
 
-## Chosen problems, presidential discourse, and policy issues
-.pull-left[<i class="fas fa-broom"></i>
-  - @hirschman1963 chosen versus pressing problem and @bacchi2009 problem representation
-  - 
-  -
-  -
+.pull-left[**Presidential Discourses**
+
+- Introduce, define, and justify the public policy `r Cite(myBib, "zarefsky2004")`
+
+- Shape perception and expectation about practices; this matters for deforestation outcomes `r Cite(myBib, c("capobianco2021", "campbell2015"))`
+
+- What about audiences and settings?
+
 ]
@@
 
-## Problem-construction in Amazonian historiography
-.pull-right[<i class="fas fa-list"></i>
-  - National Sovereignty [see @hecht1990]
-  - Economic Integration [see @acker2014]
-  - Environmetal Conservation []
-  - What about social development?
+.pull-right[**Conceptual framework**
+
+- Chosen vs. pressing problems `r Cite(myBib, "hirschman1963")`
+
+- Policies are represented as solutions for implicit problems shaped by history and culture `r Cite(myBib, "bacchi2009")`
+
+- *Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which group they are in communication with...*
+
 ]
@@
 ---
-class: split two
 
-## Data and Methods
+# Amazonian (recent) histories and policies, too cohesive?
 
@@
 
-## Operationalization
+.pull-left[**Amazonian historiography**
 
-.pull-left[<i class="fas fa-list"></i>
-  - Dataset containing all 6130 official remarks by presidents since 1985
-  - Sub-set of 2014 “amazonian statements”
-  - hand-coding and supervised machine learning
-  - 
+- National sovereignty `r Cite(myBib, "hecht1990")`
+
+- Economic integration `r Cite(myBib, "acker2014")`
+
+- Environmental conservation `r Cite(myBib, "hochstetler2007")`
+
+- What about social development?
+
 ]
@@
 
-## Limitations
+.pull-right[**Policy periods**
 
-.pull-right[<i class="fas fa-list"></i>
-  -
+- Military dictatorship (1964-85) `r Cite(myBib, "drummond2006")`
+
+- Environmental conservation (1985-2010ish) `r Cite(myBib, "capobianco2019")`
+
+- Decline and dismantling (2010ish-present) `r Cite(myBib, "pereira2021")`
+
 ]
@@
 
-The rises and falls of the Amazon as a topic in presidential speeches
+# Data and Methods (1/2)
+
+- Dataset containing all 6130 official speeches by presidents since 1985
+
+- Subset of 2014 “amazonian statements”
+
+- Hand-coding and supervised machine learning
+
+- Limitations
+
+--
+
+.right[
+
+![200%](https://media.giphy.com/media/JSueytO5O29yM/giphy.gif)
+
+***What?***
+
+]
 
@@
 
-How has the Amazon been constructed as a problem?
+# Data and Methods (2/2)
 
-**Pure-type problem constructions**
+.center[
+![:scale 90%](assets/Images/figure1pic.png)
+]
 
@@
 
-How has the Amazon been constructed as a problem?
+# The rises and falls of the Amazon as a topic in presidential speeches
 
-**Mixed-type problem constructions**
+.center[
+```{r Figure 1, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE, fig.height=6.5, fig.width=12}
+perc1 <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  scale_y_continuous(labels = percent_format()) + 
+  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.35,
+           label = "The Murder of\nChico Mendes", size = 3)+
+  annotate("text", x = 1992.5, y = 0.27, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
+  labs(x = "", y = "",
+       title = "Share of speeches that mention the Amazon per year",
+       subtitle = "Sample composed by all 6130 speeches since 1985",
+       color='Y series') +
+  theme_am()
+Amazon_year
+```
+]
 
@@
 
-The Amazonian multi-level game: boasting policy outside and talking to people inside
+# How has the Amazon been constructed as a problem? *Pure-type problem constructions*
+
+.center[
+```{r Figure 2, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+pure_types_time <- ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size =0.75, linetype="solid") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme_am() +
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
+
+pure_types_time
+```
+]
 
@@
 
-Discussion
+# How has the Amazon been constructed as a problem? *Mixed-type problem constructions*
 
-- The Amazon and Democracy
+.center[
+```{r Figure 3, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
+mixed_types_presid <- ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "right")
+mixed_types_presid
+```
+]
 
@@
 
-Thank you!
+# The Amazonian multi-level game: boasting policy outside and talking to people inside (1/2)
+
+.center[
+```{r Figure 4, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
+ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
+ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
+ama_model <- filter(ama_model, location_cat != "Non Identified",
+                    mx_cat != "Other Mixed-types") %>%
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
+         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
+         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
+         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
+# model
+model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+# Plot model
+ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
+ama_model$"Economic Integration" = predict(model_logit_ei, ama_model, type = "response")
+ama_model$"Social Development" = predict(model_logit_sd, ama_model, type = "response")
+ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
+plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:25)
+plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
+                                               "Environmental Conservation",
+                                               "Social Development",
+                                               "National Sovereignty"))
+ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
+  geom_jitter(alpha=1, size=1) +
+  geom_smooth(size = .5, se=FALSE) +
+  scale_y_continuous(labels = percent_format()) +
+  labs(x = "Distance from the Amazon (km)",
+       y = "",
+       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
+       caption = "Curves in the plots are estimated using loess method.") +
+    theme_am() +
+  theme(legend.position = "none")+
+  facet_wrap(~p_c, ncol=2)
+```
+]
+
+---
+
+# The Amazonian multi-level game: boasting policy outside and talking to people inside (2/2)
+
+```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+ama_model$thousand_km<- ama_model$km_to_manaus/1000
+model_logit_con2 <- glm(con_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_ei2 <- glm(EI_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sd2 <- glm(SD_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+model_logit_sov2 <- glm(sov_vs_all ~ thousand_km + election_year + def_year + AAI,
+                   family=binomial(link = "logit"), data = ama_model)
+md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
+                          model_logit_sov2, type = "text", digits = 6, 
+                          dep.var.labels = c("Conservation", "Economic Integration",
+                                             "Social Development", "Sovereignty"),
+                          covariate.labels = c("Distance from the Amazon in 1000s of km",
+                                               "Election year", "Yearly Deforestation",
+                                               "Yearly   Inflation"), no.space = TRUE,
+                          title = "Logistic Regressions Output")
+md
+```
+
+---
+
+class: split two
+
+# The Brazilian Amazon, democracy, and the environment (1/2)
+
+.pull-left[
+
+## Contributions:
+
+*Conceptually*: framework that connects the social construction of the Amazon to environmental outcomes
+
+*Empirically*: the first comprehensive overview of the Amazon as a problem in presidential discourse
+
+]
+
+.pull-right[
+
+![:scale 120%](assets/Images/photolivio.png)
+]
+
+---
+
+class: split two
+
+# The Brazilian Amazon, democracy, and the environment (2/2)
+
+.pull-left[
+
+***If presidents promote an agenda of economic and social development within Brazil that diverges from the environmental one promoted outside of Brazil, to what extent does the implemented agenda responds to domestic versus international demands?***
+
+]
+
+.pull-right[
+
+![:scale 100%](assets/Images/pasture_plate.png)
+
+]
+
+---
+
+.center[
+![:scale 70%](https://media.giphy.com/media/XHVmD4RyXgSjd8aUMb/giphy-downsized-large.gif)
+]
 
@@
 
-```{r refs, echo=FALSE, results="asis"}
-RefManageR::PrintBibliography(myBib)
+```{r refs1, echo=FALSE, results="asis"}
+RefManageR::PrintBibliography(myBib, start = 1, end = 4)
 ```
+
+---
+
+# References
+
+```{r refs2, echo=FALSE, results="asis"}
+RefManageR::PrintBibliography(myBib, start = 5)
+```

### 2022-10-19 amazon_def_presentation/amazon_def_presentation.Rmd
Updated slides for Amazon deforastation presentation

@@
 
-# How research get's made, a look under the hood
+#How research get's made
+
+** Let's take a look under the hood**
 
@@
 
-- This presentation
+- This [presentation](https://github.com/henriquesposito/amazondef/tree/main/amazon_def_presentation)
 
-- This article
+- This [article](https://github.com/henriquesposito/amazondef/tree/main/Draft_September_2022)
 
@@
 
+```{css, echo = F}
+.regression table {
+  font-size: 12px;     
+}
+```
+
 ---
@@
 
-# The Brazilian Amazon, as a policy object
+##The Brazilian Amazon, as a policy object
 
@@
 
-**We need to protect the Amazon from foreign interests.**
+*We need to protect the Amazon from foreign interests.*
 
-**We need to exploit the Amazon's natural resources.**
+*We need to exploit the Amazon's natural resources.*
 
-**We need to provide better living standards for the people in the Amazon.**
+*We need to provide better living standards for the people in the Amazon.*
 
-**We need to preserve the Amazon as a standing ecosystem.**
+*We need to preserve the Amazon as a standing ecosystem.*
 
@@
 
-## Research Question:
-
-*How the Brazilian Amazon has been constructed as a problem in transnational presidential speeches since 1985?*
+##How the Brazilian Amazon has been constructed as a problem in transnational presidential speeches since 1985?
 
@@
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
-# Load data
+#Load data
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
@@
 adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-# Missing year data
+#Missing year data
 amazon_def_year <- rbind(adr, amazon_def_year) 
@@
 amazon_def_year$area <- amazon_def_year$def_year*1000
-# Prepare data for problem-constructions
+#Prepare data for problem-constructions
 sov <- ama %>% 
@@
   replace(is.na(.), 0)
-# Get mixed types in
+#Get mixed types in
 ama_mx <-  ama %>%
@@
                   location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
-                                     location, ignore.case = TRUE), # minor coding issues to fix
+                                     location, ignore.case = TRUE), #minor coding issues to fix
                                "Non Amazonian States", location_cat),
          location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
-                               "International", location_cat), # minor coding issues to fix
+                               "International", location_cat), #minor coding issues to fix
          location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
@@
                                           "Non Amazonian States")))
-
 ```
@@
 ```{r theme, include=FALSE, warning=FALSE, message=FALSE}
-# custom ploting theme for all plots
+#custom ploting theme for all plots
 theme_am <- function(x) {
-  theme(text = element_text(size=12,  family="Times"),
+  theme(text = element_text(size=14,  family="Times"),
         panel.background = element_rect("white", "black", .5, "solid"),
@@
                                                   linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
+        axis.text = element_text(color = "black", size = 14),
+        title = element_text(color = "black", size = 18, face = "bold"),
         legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        plot.subtitle = element_text(color = "black", size = 14, face = "plain"),
         legend.position = "none")
@@
 
-# Presidential discourses and chosen problems
+##Presidential discourses and chosen problems
 
@@
 
-- Introduce, define, and justify the public policy `r Cite(myBib, "zarefsky2004")`
+- Introduce, define, and justify public policy `r Cite(myBib, "zarefsky2004")`
 
-- Shape perception and expectation about practices; this matters for deforestation outcomes `r Cite(myBib, c("capobianco2021", "campbell2015"))`
+- Shape perception and expectation about practices; important for deforestation `r Cite(myBib, c("capobianco2021", "campbell2015"))`
 
-- What about audiences and settings?
+- Audiences and settings?
 
@@
 
-- Policies are represented as solutions for implicit problems shaped by history and culture `r Cite(myBib, "bacchi2009")`
+- Discursive problems and solutions are shaped by history and culture `r Cite(myBib, "bacchi2009")`
 
-- *Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which group they are in communication with...*
+- *But policymakers can choose to emphasize problems that a policy solves depending who they are in communication with...*
 
@@
 
-# Amazonian (recent) histories and policies, too cohesive?
+##Amazonian (recent) histories and policies, too cohesive?
 
@@
 
-# Data and Methods (1/2)
+##Data and Methods (1/2)
 
@@
 - Subset of 2014 “amazonian statements”
+
+- Location
 
@@
 
-# Data and Methods (2/2)
+##Data and Methods (2/2)
 
@@
 
-# The rises and falls of the Amazon as a topic in presidential speeches
+##The Amazon in presidential speeches
 
 .center[
-```{r Figure 1, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE, fig.height=6.5, fig.width=12}
+```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE, fig.height=7, fig.width=14}
 perc1 <- pop %>%
@@
 
-# How has the Amazon been constructed as a problem? *Pure-type problem constructions*
+##The Amazon as a *pure* problem
 
 .center[
-```{r Figure 2, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
+```{r Figure 2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=7, fig.width=14}
 mmt1 <- ama_mx %>%
@@
   count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+  mutate(perc = n / sum(n)) #averages in relation to only mixed-types
 mmt2 <- ama_mx %>%
   count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
+  mutate(perc = n / sum(n)) #averages in relation to full sample
 pure_types_time <- ama_mx %>%
@@
 
-# How has the Amazon been constructed as a problem? *Mixed-type problem constructions*
+##The Amazon as a *mixed* problem
 
 .center[
-```{r Figure 3, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
+```{r Figure 3, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=7, fig.width=14}
 mixed_types_presid <- ama_mx %>%
@@
 
-# The Amazonian multi-level game: boasting policy outside and talking to people inside (1/2)
+##The Amazon multi-level game: talking to people inside?
 
 .center[
-```{r Figure 4, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=6.5, fig.width=12}
-ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
+```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, fig.height=7, fig.width=14}
+ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") #merge
+ama_model <- dplyr::left_join(ama_model, AAI, by = "year") #merge
 ama_model <- filter(ama_model, location_cat != "Non Identified",
@@
          sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
-# model
+#model
 model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
@@
                    family=binomial(link = "logit"), data = ama_model)
-# Plot model
+#Plot model
 ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
@@
        y = "",
-       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
+       title = "Predicted probability of each problem-construction as a function of distance from the Amazon",
        caption = "Curves in the plots are estimated using loess method.") +
@@
 
-# The Amazonian multi-level game: boasting policy outside and talking to people inside (2/2)
+class: regression
 
-```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+##The Amazon multi-level game: boasting policy outside?
+
+```{r Table 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 ama_model$thousand_km<- ama_model$km_to_manaus/1000
@@
                    family=binomial(link = "logit"), data = ama_model)
-md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
-                          model_logit_sov2, type = "text", digits = 6, 
+stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
+                          model_logit_sov2, type = "html", digits = 6, 
                           dep.var.labels = c("Conservation", "Economic Integration",
@@
                                                "Yearly   Inflation"), no.space = TRUE,
-                          title = "Logistic Regressions Output")
-md
+                          title = "Logistic Regression Models")
 ```
@@
 
-class: split two
-
-# The Brazilian Amazon, democracy, and the environment (1/2)
+class: split two middle
 
@@
 
-## Contributions:
+##Conceptually
 
-*Conceptually*: framework that connects the social construction of the Amazon to environmental outcomes
+A framework that connects the social construction of the Amazon to environmental outcomes
 
-*Empirically*: the first comprehensive overview of the Amazon as a problem in presidential discourse
+##Empirically
+
+The first comprehensive overview of the Amazon as a problem in presidential discourse
 
@@
 
-![:scale 120%](assets/Images/photolivio.png)
+![:scale 200%](assets/Images/photolivio.png)
 ]
@@
 
-class: split two
-
-# The Brazilian Amazon, democracy, and the environment (2/2)
+class: split two middle
 
@@
 
-***If presidents promote an agenda of economic and social development within Brazil that diverges from the environmental one promoted outside of Brazil, to what extent does the implemented agenda responds to domestic versus international demands?***
+##If presidents promote an agenda of economic and social development within Brazil that diverges from the environmental one promoted outside of Brazil, to what extent does the implemented agenda responds to domestic versus international demands?
 
@@
 
-# References
+#References
 

### 2022-10-21 Draft_September_2022/Full_draft_20220901.rmd
added working version note to article

@@
     \providecommand{\wordcount}[1]{\text{Word Count:}#1}
+    \providecommand{\wv}[1]{\textbf{This is a working version, please do not share or cite without the authors' permission.} #1}
 always_allow_html: TRUE
@@
 ```
+
 ```{=latex}
-\wordcount{ 8299 (including abstract, text, references, and and footnotes)}
+\wordcount{ 8299 (including abstract, text, references, and footnotes)}
 ```
+
+```{=latex}
+\wv{ }
+```
+
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}

### 2022-12-06 Submission/Models_pretest.Rmd
added pretest for models

---
title: "Models pretest"
author: "Henrique Sposito and Livio Silva-Muller"
date: "2022-12-06"
output:
  pdf_document: default
  html_document: default
  fig_caption: yes
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(modelsummary)
library(plm)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
  select(-location_cat) %>%
  distinct()
ama <- left_join(ama, location_km, by = "location")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
# Missing year data
amazon_def_year <- rbind(adr, amazon_def_year) 
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))
amazon_def_year$area <- amazon_def_year$def_year*1000
# Prepare data for problem-constructions
sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)
ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)
sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)
con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)
other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)
temp <- ei %>% 
  left_join(other) %>% 
  left_join(con) %>% 
  left_join(sd) %>% 
  left_join(sov) %>% 
  replace(is.na(.), 0)
# Get mixed types in
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure National Sovereignty",
                                   mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                   mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                   mixed_type == '0_0_0_1' ~ "Pure Environmental Conservation",
                                   mixed_type == '0_0_0_0' ~ "Other",
                                   mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                   mixed_type == '0_1_1_0' ~ "Social Economic",
                                   mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                   mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
                                   mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
                                   mixed_type == '0_0_1_1' ~ "Social Conservation",
                                   grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                         mixed_type) ~ "Other Mixed-types"),
         levels = c("Pure Economic Integration", "Pure Environmental Conservation",
                    "Pure Social Development",
                    "Pure National Sovereignty", "Other", "Economic Conservation", 
                    "Social Economic", "Sovereign Conservation",
                    "Economic, Social,\nand Conservation",
                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Environmental Conservation|
                                   |Pure Social Development|Pure National Sovereignty",
                                   mx_cat) ~ "Pure-types",
                             grepl("^Other$", mx_cat) ~ "Other",
                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
                                   |Social Conservation|Other Mixed-types",
                                   mx_cat) ~ "Mixed-types"),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
                  location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                     location, ignore.case = TRUE), # minor coding issues to fix
                               "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat), # minor coding issues to fix
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")))

```

````{=tex}
\begin{landscape}

```{r models, fig.cap="Logistic Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))

ama_model2 <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0))

# model
model_logit_con <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model)
model_logit_ei <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model)
model_logit_sd <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model)
model_logit_sov <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model)
model_logit_all <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2)

stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
                     model_logit_sov, model_logit_all, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions")
```

\end{landscape}
````

````{=tex}
\begin{landscape}

```{r models fe, fig.cap="Fixed-effects Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model fe
model_logit_con_fe <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_ei_fe <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_sd_fe <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_sov_fe <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
model_logit_all_fe <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model2,
                         model = "within", index = "year")

stargazer::stargazer(model_logit_con_fe, model_logit_ei_fe, model_logit_sd_fe,
                     model_logit_sov_fe, model_logit_all_fe, digits = 6,
                     no.space = TRUE, title = "Fixed-effects Regressions")
```

\end{landscape}
````

````{=tex}
\begin{landscape}

```{r models lagged, fig.cap="Logistic Regressions Output Lagged Deforestation", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year$year <- amazon_def_year$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
def_year = c(21.050, 21.050, 21.050, 21.050))
# Missing year data
amazon_def_year <- rbind(adr, amazon_def_year)

ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))

ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0))

# model
model_logit_con_lag <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model_lag)
model_logit_ei_lag <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model_lag)
model_logit_sd_lag <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model_lag)
model_logit_sov_lag <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model_lag)
model_logit_all_lag <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(model_logit_con_lag, model_logit_ei_lag, model_logit_sd_lag,
                     model_logit_sov_lag, model_logit_all_lag, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions with Lagged Year")
```

\end{landscape}
````

### 2022-12-06 Submission/Models_pretest.Rmd
added a 4 model with party ideology and vdem data

@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+#table(ama_model$president, ama_model$party)
+
+ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
+dplyr::filter(country_name == "Brazil") %>%
+dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
+tidyr::drop_na() %>%
+dplyr::rename(party = v2pashname) %>%
+group_by(party) %>%
+summarise(anti_pluralism = mean(v2xpa_antiplural),
+populism = mean(v2xpa_popul),
+left_right = mean(v2pariglef))
+
+ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)
+
+ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)
+
+# model
+model_logit_con_lag <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
+                       data = ama_model_lag)
+model_logit_ei_lag <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
+                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
+                      data = ama_model_lag)
+model_logit_sd_lag <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
+                        def_year + AAI + populism + anti_pluralism + left_right,
+                      family=binomial(link = "logit"), data = ama_model_lag)
+model_logit_sov_lag <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right,
+                       family=binomial(link = "logit"), data = ama_model_lag)
+model_logit_all_lag <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right,
+                       family=binomial(link = "logit"), data = ama_model2_lag)
+
+stargazer::stargazer(model_logit_con_lag, model_logit_ei_lag, model_logit_sd_lag,
+                     model_logit_sov_lag, model_logit_all_lag, digits = 6,
+                     no.space = TRUE,
+                     title = "Logistic Regressions with Lagged Year and Party Ideology")
+```
+
+\end{landscape}
+````

### 2022-12-07 Submission/Models_pretest.Rmd
one more model

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
   fig_caption: yes
@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+model_logit_con_pfe <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+model_logit_ei_pfe <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+model_logit_sd_pfe <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+model_logit_sov_pfe <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+model_logit_all_pfe <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model2_lag,
+                         model = "within", index = "president")
+
+stargazer::stargazer(model_logit_con_pfe, model_logit_ei_pfe, model_logit_sd_pfe,
+                     model_logit_sov_pfe, model_logit_all_pfe, digits = 6,
+                     no.space = TRUE,
+                     title = "Logistic Regressions with president fixed-effects")
+
+```
+
+\end{landscape}
+````

### 2022-12-07 Submission/Models_pretest.Rmd
president fixed effect, and changes to model names

--- 2022-12-06 Submission/Models_pretest.Rmd
@@
 # model
-model_logit_con <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
+a1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, family=binomial(link = "logit"),
                        data = ama_model)
-model_logit_ei <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
+a2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model)
-model_logit_sd <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
+a3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model)
-model_logit_sov <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
+a4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party,
                        family=binomial(link = "logit"), data = ama_model)
-model_logit_all <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
+a5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party,
@@
 
-stargazer::stargazer(model_logit_con, model_logit_ei, model_logit_sd,
-                     model_logit_sov, model_logit_all, digits = 6,
+stargazer::stargazer(a1, a2, a3,
+                     a4, a5, digits = 6,
                      no.space = TRUE, title = "Logistic Regressions")
@@
 # model fe
-model_logit_con_fe <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
+b1 <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, data = ama_model,
                          model = "within", index = "year")
-model_logit_ei_fe <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
+b2 <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, data = ama_model,
                          model = "within", index = "year")
-model_logit_sd_fe <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
+b3 <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, data = ama_model,
                          model = "within", index = "year")
-model_logit_sov_fe <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
+b4 <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, data = ama_model,
                          model = "within", index = "year")
-model_logit_all_fe <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
+b5 <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, data = ama_model2,
@@
 
-stargazer::stargazer(model_logit_con_fe, model_logit_ei_fe, model_logit_sd_fe,
-                     model_logit_sov_fe, model_logit_all_fe, digits = 6,
+stargazer::stargazer(b1, b2, b3,
+                     b4, b5, digits = 6,
                      no.space = TRUE, title = "Fixed-effects Regressions")
@@
 # model
-model_logit_con_lag <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
+c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party, family=binomial(link = "logit"),
                        data = ama_model_lag)
-model_logit_ei_lag <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
+c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model_lag)
-model_logit_sd_lag <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
+c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model_lag)
-model_logit_sov_lag <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
+c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party,
                        family=binomial(link = "logit"), data = ama_model_lag)
-model_logit_all_lag <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
+c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                          def_year + AAI + party,
@@
 
-stargazer::stargazer(model_logit_con_lag, model_logit_ei_lag, model_logit_sd_lag,
-                     model_logit_sov_lag, model_logit_all_lag, digits = 6,
+stargazer::stargazer(c1, c2, c3,
+                     c4, c5, digits = 6,
                      no.space = TRUE, title = "Logistic Regressions with Lagged Year")
@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+#table(ama_model$president, ama_model$party)
+
+ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
+dplyr::filter(country_name == "Brazil") %>%
+dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
+tidyr::drop_na() %>%
+dplyr::rename(party = v2pashname) %>%
+group_by(party) %>%
+summarise(anti_pluralism = mean(v2xpa_antiplural),
+populism = mean(v2xpa_popul),
+left_right = mean(v2pariglef))
+
+ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)
+
+ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)
+
+# model
+c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
+                       data = ama_model_lag)
+c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
+                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
+                      data = ama_model_lag)
+c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
+                        def_year + AAI + populism + anti_pluralism + left_right,
+                      family=binomial(link = "logit"), data = ama_model_lag)
+c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right,
+                       family=binomial(link = "logit"), data = ama_model_lag)
+c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
+                         def_year + AAI + populism + anti_pluralism + left_right,
+                       family=binomial(link = "logit"), data = ama_model2_lag)
+
+stargazer::stargazer(c1, c2, c3,
+                     c4, c5, digits = 6,
+                     no.space = TRUE,
+                     title = "Logistic Regressions with Lagged Year and Party Ideology")
+```
+
+\end{landscape}
+````
+
+````{=tex}
+\begin{landscape}
+
+```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+d1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+d2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+d3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+d4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model_lag,
+                         model = "within", index = "president")
+d5 <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model2_lag,
+                         model = "within", index = "president")
+
+stargazer::stargazer(d1, d2, d3,
+                     d4, d5, digits = 6,
+                     no.space = TRUE,
+                     title = "Logistic Regressions with president fixed-effects")
+
+```
+
+\end{landscape}
+````

### 2022-12-07 Submission/Models_pretest.Rmd
highlighted

@@
 stargazer::stargazer(d1, d2, d3,
-                     d4, d5, digits = 6,
+                     d4, d5, digits = 3,
                      no.space = TRUE,
-                     title = "Logistic Regressions with president fixed-effects")
-
+                     title = "Logistic Regressions with president fixed-effects",
+                      column.sep.width = ".001pt",
+                      font.size="small")
 ```

### 2022-12-08 Submission/Models_pretest.Rmd
Updated models

--- 2022-12-07 Submission/Models_pretest.Rmd
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
-# Missing year data
-amazon_def_year <- rbind(adr, amazon_def_year) 
+amazon_def_year$year <- amazon_def_year$year + 1
+adr <- data.frame(year = c(1985, 1986, 1987, 1988),
+def_year = c(21.050, 21.050, 21.050, 21.050))
+amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
 hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
@@
                                       year), 1, 0),
+         peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0),
                   location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
@@
                                           "Non Amazonian States")))
-
-```
-
-````{=tex}
-\begin{landscape}
-
-```{r models, fig.cap="Logistic Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
-dplyr::left_join(AAI, by = "year") %>%
-filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
-         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
-         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
-         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
-
-ama_model2 <- dplyr::select(pop, -text) %>%
-  dplyr::left_join(amazon_def_year, by = "year") %>%
-  dplyr::left_join(AAI, by = "year") %>%
-  filter(location_cat != "Non Identified") %>%
-  mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
-         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
-                               "International", location_cat),
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries",
-                                      location_cat),
-                               levels = c("Amazonian States",
-                                          "Amazonian Countries",
-                                          "International", "Brasilia",
-                                          "Non Amazonian States")),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
-                                      year), 1, 0))
-
-# model
-a1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, family=binomial(link = "logit"),
-                       data = ama_model)
-a2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + party, family=binomial(link = "logit"),
-                      data = ama_model)
-a3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + party,
-                      family=binomial(link = "logit"), data = ama_model)
-a4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party,
-                       family=binomial(link = "logit"), data = ama_model)
-a5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party,
-                       family=binomial(link = "logit"), data = ama_model2)
-
-stargazer::stargazer(a1, a2, a3,
-                     a4, a5, digits = 6,
-                     no.space = TRUE, title = "Logistic Regressions")
-```
-
-\end{landscape}
-````
-
-````{=tex}
-\begin{landscape}
-
-```{r models fe, fig.cap="Fixed-effects Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-# model fe
-b1 <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, data = ama_model,
-                         model = "within", index = "year")
-b2 <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, data = ama_model,
-                         model = "within", index = "year")
-b3 <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, data = ama_model,
-                         model = "within", index = "year")
-b4 <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, data = ama_model,
-                         model = "within", index = "year")
-b5 <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, data = ama_model2,
-                         model = "within", index = "year")
-
-stargazer::stargazer(b1, b2, b3,
-                     b4, b5, digits = 6,
-                     no.space = TRUE, title = "Fixed-effects Regressions")
-```
-
-\end{landscape}
-````
-
-````{=tex}
-\begin{landscape}
-
-```{r models lagged, fig.cap="Logistic Regressions Output Lagged Deforestation", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-amazon_def_year$year <- amazon_def_year$year + 1
-adr <- data.frame(year = c(1985, 1986, 1987, 1988),
-def_year = c(21.050, 21.050, 21.050, 21.050))
-# Missing year data
-amazon_def_year <- rbind(adr, amazon_def_year)
 
@@
          election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
-                                      year), 1, 0))
+                                      year), 1, 0),
+         peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0))
+
+#table(ama_model$president, ama_model$party)
+#ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
+#dplyr::filter(country_name == "Brazil") %>%
+#dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
+#tidyr::drop_na() %>%
+#dplyr::rename(party = v2pashname) %>%
+#group_by(party) %>%
+#summarise(anti_pluralism = mean(v2xpa_antiplural),
+#populism = mean(v2xpa_popul),
+#left_right = mean(v2pariglef))
+#ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)
+#ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)
+
+```
+
+````{=tex}
+\begin{landscape}
+
+```{r models, fig.cap="Logistic Regressions without controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
 # model
-c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party, family=binomial(link = "logit"),
+a1 <- glm(con_vs_all ~ as.factor(location_cat),
+family=binomial(link = "logit"),
                        data = ama_model_lag)
-c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + party, family=binomial(link = "logit"),
+a2 <- glm(EI_vs_all ~ as.factor(location_cat),
+family=binomial(link = "logit"),
                       data = ama_model_lag)
-c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + party,
+a3 <- glm(SD_vs_all ~ as.factor(location_cat),
                       family=binomial(link = "logit"), data = ama_model_lag)
-c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party,
+a4 <- glm(sov_vs_all ~ as.factor(location_cat),
                        family=binomial(link = "logit"), data = ama_model_lag)
-c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + party,
-                       family=binomial(link = "logit"), data = ama_model2_lag)
 
-stargazer::stargazer(c1, c2, c3,
-                     c4, c5, digits = 6,
-                     no.space = TRUE, title = "Logistic Regressions with Lagged Year")
+stargazer::stargazer(a1, a2, a3, a4, digits = 6, no.space = TRUE,
+                     title = "Logistic regressions without controls")
+
 ```
@@
 
-```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+```{r models lagged, fig.cap="Logistic Regressions with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
-#table(ama_model$president, ama_model$party)
+# model 2
+b1 <- glm(con_vs_all ~ as.factor(location_cat) + def_year + AAI +
+election_year + peak_year,
+family=binomial(link = "logit"),
+                       data = ama_model_lag)
+b2 <- glm(EI_vs_all ~ as.factor(location_cat) + def_year + AAI +
+election_year + peak_year,
+family=binomial(link = "logit"),
+                      data = ama_model_lag)
+b3 <- glm(SD_vs_all ~ as.factor(location_cat) + def_year + AAI +
+election_year + peak_year,
+                      family=binomial(link = "logit"), data = ama_model_lag)
+b4 <- glm(sov_vs_all ~ as.factor(location_cat) + def_year + AAI +
+election_year + peak_year,
+                       family=binomial(link = "logit"), data = ama_model_lag)
 
-ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
-dplyr::filter(country_name == "Brazil") %>%
-dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
-tidyr::drop_na() %>%
-dplyr::rename(party = v2pashname) %>%
-group_by(party) %>%
-summarise(anti_pluralism = mean(v2xpa_antiplural),
-populism = mean(v2xpa_popul),
-left_right = mean(v2pariglef))
+stargazer::stargazer(b1, b2, b3, b4, digits = 6, no.space = TRUE,
+                     title = "Logistic regressions with controls")
 
-ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)
-
-ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)
-
-# model
-c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
-                       data = ama_model_lag)
-c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
-                      data = ama_model_lag)
-c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
-                        def_year + AAI + populism + anti_pluralism + left_right,
-                      family=binomial(link = "logit"), data = ama_model_lag)
-c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + populism + anti_pluralism + left_right,
-                       family=binomial(link = "logit"), data = ama_model_lag)
-c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
-                         def_year + AAI + populism + anti_pluralism + left_right,
-                       family=binomial(link = "logit"), data = ama_model2_lag)
-
-stargazer::stargazer(c1, c2, c3,
-                     c4, c5, digits = 6,
-                     no.space = TRUE,
-                     title = "Logistic Regressions with Lagged Year and Party Ideology")
 ```
@@
 
-```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
-d1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year, data = ama_model_lag,
+# model 3
+c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
                          model = "within", index = "president")
-d2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year, data = ama_model_lag,
+c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
                          model = "within", index = "president")
-d3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year, data = ama_model_lag,
+c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
                          model = "within", index = "president")
-d4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year, data = ama_model_lag,
-                         model = "within", index = "president")
-d5 <- plm(amazon_speech ~ as.factor(location_cat) +
-                         def_year + AAI + election_year, data = ama_model2_lag,
+c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
                          model = "within", index = "president")
 
-stargazer::stargazer(d1, d2, d3,
-                     d4, d5, digits = 6,
-                     no.space = TRUE,
-                     title = "Logistic Regressions with president fixed-effects")
-
+stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Fixed-effects logistic regressions by president with controls",
+                      column.sep.width = ".001pt",
+                      font.size="small")
 ```

### 2022-12-08 Submission/Models_pretest.Rmd
new tests

@@
         peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0),
+        py_1989=ifelse(grepl("1989", year), 1, 0),
+        py_1992=ifelse(grepl("1992", year), 1, 0),
+        py_2009=ifelse(grepl("2009", year), 1, 0),
+        py_2015=ifelse(grepl("2015", year), 1, 0),
+        py_2019=ifelse(grepl("2019", year), 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
@@
          location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries",
+                                            location), "Amazonian States",
                                       location_cat),
                                levels = c("Amazonian States",
-                                          "Amazonian Countries",
                                           "International", "Brasilia",
@@
                       column.sep.width = ".001pt",
+                      font.size="small",
+                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
+                                             "Social Development", "National Sovereignty"),
+                          covariate.labels = c("Speech outside Brazil", "Speech in Brasilia", "Speech in Non-amazonian Brazilian States", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
+```
+
+\end{landscape}
+````
+
+````{=tex}
+\begin{landscape}
+
+```{r models president fixed effect w/ py, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+# model 3
+c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year + py_1989+ py_1992+ py_2009+ py_2015+ py_2019,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+
+stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Fixed-effects logistic regressions by president with controls and separate peak years",
+                      column.sep.width = ".001pt",
                       font.size="small")

### 2022-12-08 Submission/Models_pretest.Rmd
levels correct

@@
          location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian States",
+                                            location), "Amazonian Countries",
                                       location_cat),
                                levels = c("Amazonian States",
-                                          "International", "Brasilia",
-                                          "Non Amazonian States")))
+                                          "Non Amazonian States",
+                                          "Brasilia",
+                                          "Amazonian Countries",
+                                          "International")))
 
@@
                                              "Social Development", "National Sovereignty"),
-                          covariate.labels = c("Speech outside Brazil", "Speech in Brasilia", "Speech in Non-amazonian Brazilian States", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
+                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
 ```

### 2022-12-08 Submission/draft/draft_resubmission.rmd
Added draft folder to submission

--- 2022-10-21 Draft_September_2022/Full_draft_20220901.rmd
@@
 library(modelsummary)
+library(plm)
 Sys.setlocale("LC_ALL", "C")
@@
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
-pop <-  pop %>% select(-c(title, date, location))
 ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
@@
                                       year), 1, 0),
+        peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0),
+        py_1989=ifelse(grepl("1989", year), 1, 0),
+        py_1992=ifelse(grepl("1992", year), 1, 0),
+        py_2009=ifelse(grepl("2009", year), 1, 0),
+        py_2015=ifelse(grepl("2015", year), 1, 0),
+        py_2019=ifelse(grepl("2019", year), 1, 0),
         location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
@@
          location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries", location_cat),
-                               levels = c("International", "Amazonian States",
-                                          "Amazonian Countries", "Brasilia",
-                                          "Non Amazonian States")))
+                                            location), "Amazonian Countries",
+                                      location_cat),
+                               levels = c("Amazonian States",
+                                          "Non Amazonian States",
+                                          "Brasilia",
+                                          "Amazonian Countries",
+                                          "International")))
 
+ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
+dplyr::left_join(AAI, by = "year") %>%
+filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
+         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
+         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
+         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
 ```
@@
 
-\pagebreak
+# 3 Methods
 
-# 1 Introduction
+## 3.1 Data and Operationalization
 
-*We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon's natural resources.
-We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.* Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it represents the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.Different governments throughout Brazilian history have been identified as proponents of a specific view of the Amazon [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+We update the dataset by scraping and adding all official speeches from 2020 and 2021.
+The final dataset encompasses 6130 speeches.
+Then, we proceed to identify speeches that refer to the Amazon as a region, people, or forest.
+We do so by detecting all speeches in which the stem “amazon” appears.
+In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We find that 946 speeches are, at least partially, about the Amazon.
 
-We conceptualize the Amazon region, forest, and people to be a policy object, this is a specific issue that deserves dedicated policy attention.
-While the military dictatorship(1964-85) is associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010)presidencies are often tied to environmental conservation.
-These monolithic representations advance the view that specific governments understand and act towards the Amazon as one problem, hiding within government diversity of both policies and perspectives.
-Albeit the current calls to understand the environment as a social-cultural construction and to identify the effect of culture on environmental outcomes [@lepolaindewaroux2021], we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between or within, governments.
-Building on @hirschman1963 conceptualization of chosen problems and @bacchi2009 theory of problem-representation in policy, we propose a framework for identifying problem-constructions in discourse and investigate how the Brazilian Amazon has been constructed as a problem in transnational political discourses.
-We understand transnationalism[^1] as relationships that transcend nation-states, from the local level to the supranational level encompassing non-state actors [@keck1998].
-
-[^1]: We use the noun transnationalism, the adverb transnationally, and the adjective transnational interchangeably
-
-Although problem-construction takes place in a series of instances, we analyze the case of speeches by Brazilian presidents since 1985.
-Scholarly research about environmental policy in Brazil has focused on the role of the environmental bureaucracy [@silva-muller2022a], non-governmental organizations [@keck1998], legislation [@soares-filho2014], and international markets [@assuncao2015; @rajao2020 ].
-Nevertheless, the role of the president remains understudied.
-We opt for presidential speeches for two reasons.
-First, presidential discourses have the power to introduce and justify the public policy, as well as shape its perception to broad audiences [@zarefsky2004; @gillion2016].
-It legitimizes ways of thinking about the Amazon.
-In turn, policy perception is key for policy adoption and implementation [@alesina2009; @lopez2020].
-This is especially pertinent to deforestation in Brazil as expectations of local actors, generated from material and discursive governmental practices, are a crucial factor in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021; @campbell2015].
-Second, we argue that presidents can deploy problem-constructions that build policy objects as different problems depending on whom they are speaking to.
-Presidential discourses take place in different settings, from launching a new bridge in a small municipality in the middle of the Amazon to a speech at the UN general assembly in New York.
-Working with presidential discourses allows us to identify this variation in meaningful ways and better understand how the Amazon is discursively constructed in transnational politics.
-
-To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6130 official presidential speeches by all Brazilian presidents since 1985.
-We subset the dataset by identifying Amazon-related statements within these speeches.
-We find that 2014 sections in these discourses refer to the Amazon at least once.
-We then develop a codebook grounded in Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
-We use this codebook to manually code a randomly selected training set of Amazon-related statements.
-We train a supervised machine-learning model to automatically label the remaining set of Amazonian statements.
-We then conduct a descriptive and inferential analysis of this data, tying patterns in the data to Amazonian policies and deforestation outcomes over time.
-
-Our empirical findings are threefold.
-First, we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events (e.g.
-the assassination of Chico Mendes) as well as international events (e.g.Climate Summits).
-Second, the same government adopts a diverse range of problem-constructions over time.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, briefly surpassing economic integration as more common problem-constructions from 2011 to 2016.
-Constructing the Amazon as an issue of sovereignty has become more pertinent after 2010.
-Finally, using logit models, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation as presidents speak farther away from the Amazon region.
-That is, presidents talk to the economic and social needs of the people domestically while boasting about environmental policy internationally.Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses as a multi-level game and how these relates to policies.
-
-This article proceeds as follows: first, we propose a conceptual framework to understand problem-construction in discourses.
-We then review Amazonian historiography literature to identify the main phases and their underlying problem-construction.
-In the methodology section, we explain how the framework is operationalized and present the codebook.
-We proceed to describe, visualize, and interpret our findings in the analysis section.
-Finally, we conclude with a discussion connecting our findings to past and present environmental policies.
-
-# 2 Conceptual framework and contribution
-
-## 2.1 Chosen problems, presidential discourses, and policy objects
-
-In "Journey towards Progress", @hirschman1963 draws a conceptual distinction between pressing problems (pressured by outside parties to the government) and chosen problems (chosen by the government at their discretion).
-Pressing problems can be either privileged or neglected, depending on the degree of pressure exercised by the interested groups.
-Chosen problems are those that governments select at their discretion.
-Problems can change from pressing to chosen as a function of (a) solutions becoming available, (b) a change in the level of government control in society, or (c) a shift of interests from top policymakers [@hirschman1963].
-@hirschman1975 example of policymakers choosing a problem is President's Kubitschek decision of building Brasilia, which was not particularly pressed by any interest group.
-
-@bacchi2009 [p.
-10] argues that policies have a cultural dimension as they take "shape within specific historical and national or international contexts".
-The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed, this is a policy object.
-We conceptualize policy objects as a problems that demand dedicated policy attention.
-The alleged problem is not always explicitly stated in a policy: policies are represented as solutions for implicit problems.
-Building Brasilia (the policy object), thus, could solve a problem of regional inequality, a problem of a dormant economy without state investment, a problem of political representation, or all three depending on how governments speak about it.
-
-Governments can choose to emphasize (or not) one or more implicit problems that a policy solves depending on which interest group they are in communication with.
-Depending on how the policy is represented to be, it can be portrayed as a solution to problems that are considered pressing or not for different groups and it is up to the discretion of the political actor to construct a particular problem in a particular way given context.
-@putnam1988's seminal article on the two-level game can help us make sense of this variation conceptually.
-The author argues that the outcomes of international negotiations lie within the overlap between the agenda (and pressure) of domestic and international groups.
-If policies are socially constructed, governments can in theory construct them to meet the expectations of both.
-Consequently, this entails that governments are more diverse in their opinions, rather than monolithic.
-
-An interesting context to study the relationship between problem-construction and policy objects is presidential speeches, as they influence ways of thinking about an issue.
-While the relationship between presidential speeches and policy may not be causal, they have the power to introduce and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004; @gillion2016].
-As presidents speak across several locations to various audiences, they construct similar issues differently.
-
-The possibility of different problem-constructions in presidential speeches has important implications for democracy and global politics.
-With globalization, presidents have the opportunity of promoting different problem-constructions transnationally.
-We understand transnationalism as relationships that transcend nation-states, from the local level to the international level encompassing non-state actors [@keck1998].
-The environment and climate change, in particular, have received particular trasnantional attention, as narratives of global collective action dominated academic literature (for an overview, see @aklin2020).Relatedly, when Brazilian presidents speak about the Amazon it not only makes headlines, nationally and internationally [@brice2021; @harris2021; @miranda2021], but also incites responses, shapes expectations, and feeds into the behavior of a myriad of related actors.
-This is partially because the forest is a key biome in global climate-mitigation.
-It is important to understand, thus, to what extent the implemented policy agenda correlates with problem-constructions promoted at the local, federal, or international levels.
-
-The connection between presidential discourse and the environment has been studied in the case of the United States but remains conceptually underdeveloped.
-@calderwood2019, for instance, examines 2019 mentions of climate change in American official presidential speeches since 1989.
-Among other things, the author finds that American presidents frequently side-step the environmental aspects of climate change.
-Building on @putnam1988, @calderwood2020 demonstrates that American presidents are more likely to mention climate change in foreign locations, and that location influences the specific discursive approach and tone they adopt.
-Elsewhere, @bevitori2015 finds that mentions of the environment are typically co-selected with the pronoun 'our', as well as with 'economy', 'clean', and 'preserve'.
-While these studies corroborate the possibilities of variation depending on the audience, they fail to tie vocabulary to specific problem-constructions based on wider shared meanings of environment and climate change.
-That is, problem-constructions touch on shared meanings available to both the speaker and the audiences as part of larger social-cultural history [see @bacchi2009], therefore, mentions to the lexicon as 'environment', 'preserve', or 'climate change should be tied to the larger meaning of policies in the United States.
-
-There is also an empirical gap in terms of how the Amazon, specifically, has been constructed as a problem along time and geographic location in political discourses.
-While governmental discourses in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the environment remains largely absent.
-An exception is @barros2020, who investigates Amazonian discourse in the Brazilian Congress.
-The author finds that the economic value of the Amazon for the cattle industry is the most salient narrative put forward by congressmen and concludes that there is a mismatch between the international debate (which focuses on preservation) and the national debate (which focuses on economic development).
-
-This variation in problem-construction entails that the same governments are more diverse in their positions than the literature suggests.
-Scholars often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-In this literature, the 1964 military dictatorship is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
-The governments from the late 1980s up to 2009 are associated with a turn towards policies that focus on environmental conservation.
-The presidencies of Dilma and Temer (2011-2018) are connected to the decline of conservationist policies, while Bolsonaro to the dismantling of environmental policies.
-Although these works are important to understand how different governments have acted toward the Amazon, the classification of specific governments into policy periods, or policy cycles, represents them as monolithic: they associate specific governments with one specific view of the Amazon.
-
-We propose a conceptual framework that accepts the possibility of varied problem-construction for the same policy object and connects it to presidential speeches.
-Governments often choose what problems to solve and what policies to implement.
-The same policies can be represented as solving different problems implying a degree of social construction [@bacchi2009].
-Governments can emphasize, or not, implicit problems that a policy solves depending on which interest group they are in communication with.
-The variation in problem-construction suggests that Brazilian governments are more diverse in their positions than the literature suggests.
-An interesting context to study the relationship between varied problem-construction and policy is presidential speeches as they legitimize ways of thinking about an issue, matter for policymaking, and environmental outcomes.
-As presidents speak in different places and to diverse audiences, it is an empirical site prone to identifying variation.
-
-## 2.2 Problem-construction in Amazonian historiography
-
-We rely on the Amazonian historiography literature to identify possible problem-constructions and their connection to the socio-cultural history of the country.
-We refer to Amazonian historiography as the body of research conducted by social and environmental scientists that tell the story of diverse governmental programs that approach the Amazon region, forest, and its people as a policy object demanding dedicated action.
-From this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
-We also argue a fourth, social development, that focuses on the rights and dignity of the inhabitants of the Amazonian region.
-
-### National Sovereignty
-
-@hecht1990 [p.
-1] write that "what imbues the case of the Amazon with such passion is the symbolic content of the dreams it ignites".
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
-8], and when the dust settled and the scramble was over, over half of the Amazon emerged Brazilian.
-While Brazilian military diplomacy was very successful, the process did not come without its traumas as for example the negotiations with Bolivia in 1902 to secure the territory of the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies during the military dictatorship of 1964 as earlier regimes aimed at protecting Brazil's sovereignty over the Amazon [@hecht2020].
-As we move to a world where non-state actors gain importance in environmental governance [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
-Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
-Claims of attempts to 'internationalize' the Brazilian Amazon, for instance, are targeted at foreign actors as well as domestic non-state actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
-
-### Economic Integration
-
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon.
-In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions[@acker2021] .
-First, it assumes that nature should be conquered by mankind Second, it assumes that exploiting natural resources would render the Amazon region economically profitable.
-Third, it assumes that populating the region was necessary to integrate it into the country and exert control over the territory.
-Concretely, this meant a series of major infrastructural projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
-@capobianco2019 and @becker2005 describe the period from the 1950s to the 1980s in similar vein, as one of often centralized economic policies by the federal government.The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
-
-### Environmental Conservation
-
-The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
-A common explanation for the creation of these institutions in the Amazonian literature is the impression of the lack of control over the market, engendered by years of centralized economic integration in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-@hochstetler2007 argue that during preparations for the summit, a new form of Brazilian environmentalism emerged: socio-environmentalism.
-They define it as an emphasis on the local livelihoods of traditional populations while protecting nature.
-@capobianco2019 argues that socio-environmentalism informed a series of policies throughout the 1990s and early 2000s towards preserving the forest, such as the establishment of several conservation units in the Amazon in 2001.
-The environmental conservation problem-constructions emphasize that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
-The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
-
-### Social Development
-
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
-However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
-@acker2021 [p.
-10], for example, argues that during the military dictatorship attempts to populate the Amazon were seen, among other things, as a solution for the country's growing social inequalities elsewhere.
-As democracy established itself in Brazil, the settlers from the military dictatorship became electorates with constitutional rights.
-@hochstetler2007 argue that with the transition to democracy, the mobilization of diverse social movements to demand social equality and conservation was an integral part of the socio-environmentalist movement in Brazil.
-While indigenous rights and preservation of the forest go hand in hand, it is not clear whether providing better standards of livings to the large and poor populations of the state and preservation do; perhaps this is also why there was never an open consensus about socio-environmentalism in Brazil [@hochstetler2007].
-Although related to economic integration and environmental conservation, social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
-The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
-
-# 3 Methodology: operationalizing Amazonian problem-constructions
-
-## 3.1 Codebook and Data
-
-To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by [@cezar2020] which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
-We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches for all the presidents of Brazil.
-Then, we proceed to identify all speeches that refer to the Amazon as a region, people, or forest.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 946 speeches are, at least partially, about the Amazon out of the 6130.
-
-Using the poldis R package [@sposito2021], we proceed to extract two sentences before and two sentences after the sentence in which the stem "amazon" appears.
+Using the poldis R package (Sposito 2021), we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
 We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
+When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
 By doing so we create our unit of analysis: an Amazonian statement.
-We use Amazonian statements as our unit of analysis because it allows us to identify only passages that are meaningful for our specific purpose.This process yields 2014 unique Amazonian statements about the Amazon.
-When an Amazonian statement contains two or more matches of the stem "amazon", we get two sentences before the first match and two sentences after the last match.
+Amazonian statements represent text portions that are meaningful for our specific purpose.
+This process yields 2014 unique Amazonian statements about the Amazon.
 On average, an Amazonian statement contains 123 words.
 
-Our approach to text coding has three steps.
-First, we develop a codebook to code Amazonian statements in one or more problem-constructions (see codebook in appendix).
+Our approach to text coding is threefold.
+First, we follow the Amazonian historiography literature to develop a codebook to code Amazonian statements as one, or more, problem-constructions (see codebook in appendix).
 In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
-Nevertheless, each Amazonian statement might be assigned to one or more codes.
+Nonetheless, each Amazonian statement might be assigned to one or more codes.
 A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation.
 Amazonian statements, thus, can be either coded as pure-types or mixed-types.
-Mixed-types are relevant as constructions and policies are often multifaceted while portraying the Amazon as a combination of these problem-constructions.
 Figure 1, below, portrays this operationalization strategy.
@@
 This amount refers to 50% of all the Amazonian Statements identified.
-We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time and as a problem.
-As the size of the training set should increase with the number of categories [@grimmer2022], we deemed four categories and 50% of the statements as reliable.
-This allows a robust validation set to verify the models.
+We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time, and as a problem.
+As well, the size of the training set should increase with the number of categories (Grimmer, Roberts, and Stewart 2022).
+Since we have four categories, hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and for validation, of the models.
 Automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-The intercoder agreement for hand-coded categories was 85%, on average.
-For each non-matching coded observation, the co-authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
+Once coded, the average intercoder agreement for hand-coded categories was 85%.
+For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
 
 Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts [@meyer2021; @noble2006].
-The SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set.
-The trained SVM model was, on average 82%, accurate in classifying observations in the validation set before being tuned.
-After the SVM model is tuned, we use the model to automatically code the remaining 1007 Amazonian statements.
-The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements.
+We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts (Meyer et al.
+2021; Noble 2006).
+As a robustness check, the SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set.
+The trained SVM model was, on average, 82%, accurate in classifying observations in the validation set before being tuned.
+After the SVM model is tuned and the size of the training set is increased by including all hand coded observations, we use the model to automatically code the remaining 1007 Amazonian statements.
+The authors then randomly select 100 Amazonian statements automatically coded and find that the model is 97% accurate in coding these statements.
+The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements (add a footnote for false positives here)).
 
@@
 
-To analyze our data, we first present a series of different plots on the proportions of Amazonian statements and problem-constructions over time and by presidents.
-To test whether problem-constructions depend on where presidents speak, we run four separate logistic regressions.
-Each model takes the share of a specific problem-construction versus all other problem-constructions as their dependent variable.
-This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining three problem-constructions.
-Our main independent variable is the distance (in kilometers) from the state or country capital where the speech took place to Manaus (the capital of the Amazonas State and centrally located in the region).
-The logic behind this relates to presidents playing multi-level games.
-We expect presidents to change how they construct the Amazon based on their believes of audiences' expectations.We interpret the plots and model considering multiple Amazon-related events and policies over the last 30 years, with the support of existing literature, and their correlations with different presidents and locations.
+To analyze our data, we model the share of a specific pure problem-construction, versus all other problem-constructions, as the dependent variable, in relative to the settings in which a particular speech happens, as our independent variable.
+This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
+We chose to focus on pure constructions to provide unambiguous interpretation and robust correlations.
+We divide setting in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
+The level aggregation refers to geo-political settings that make sense in light of the Amazon, as a policy object.
+This aggregation combines different expectations presidents might have about transnational audiences in these settings.
+As well, Brasilia is a separate setting because of its’ unique location and since most presidential speeches are delivered in Brasilia.
+We control for yearly deforestation rates, inflation, election years, and peak years for Amazon appearing year in presidential speeches.
+Subsequently, we plot Amazonian statements and problem-constructions over time and by setting.
+We interpret the plots and model considering the literature alongside with multiple Amazon-related events and policies over the last 30 years.
 
-This approach comes with limitations.
-Our codebook is developed using specific Amazon-related vocabulary.
+```{r table 1, fig.cap="Models Description", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+
+models <- tibble::tibble("Models Description" = c("Fixed-effects logistic regressions indexed by president (controlling for time and ideology)."),
+                         "Dependent variables" = c("Pure environmental conservation; pure economic integration; pure social development; and pure national sovereignty."),
+                         "Independent Variables" = c("Amazonian states within Brazil (reference category); non-Amazonian Brazilian states; Brasilia; Amazonian countries; and international."),
+                         "Controls" = c("Yearly deforestation rates lagged by one year; average annual inflation; election years; and peak years for Amazon appearing year in presidential speeches (footnote)."))
+
+kbl(models, booktabs = T, caption = "Model description") %>%
+  kable_styling(latex_options = c("striped", "repeat_header",
+                                  "scale_down", "HOLD_position"),
+                position = "center", font_size = 9, full_width = TRUE)
+```
+
+The main limitations of our approach are threefold.
+First, related to our sub-setting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
+Hence, we might be missing statements about Amazon that do not refer to it.
+However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
+Moreover, our codebook is developed using specific Amazon related vocabulary.
 For example, a statement will be coded as economic integration if it is meaningful support for the tax-free zone of Manaus or a dam in the Amazon.
 However, the economy is generally a topic that presidents speak about frequently.
-Hence, the high incidence of economic integration in Amazonian statements can also be related to the higher importance of this problem-construction in Brazil overall.
-Moreover, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "Amazon", for example, when the president says, "the forest" or "deforestation".
-Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
-Finally, our dataset covers only what is considered an official speech.
+Hence, the high incidence of economic integration in Amazonian statements could also be related to the higher importance of this problem-construction in Brazil overall.
+
+Second, our dataset covers only what is considered an official speech.
 Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
-Problem-construction within presidential discourse, thus, also happens in different sites for which we do not account in this paper.
+Problem-construction within presidential discourse, thus, happens in different public and private venues for which we do not account in this paper.
+We believe that setting remains an important factor in changing expectations about audiences, especially for a historical analysis.
+Although we recognize that this, arguably, has begun to change with the advancement of communication technologies.
+Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question.
+Therefore, we are aware that a category as “international”, for instance, encompasses speeches delivered by presidents in a wide variety countries and institutions to a wider variety of audiences, which are not differentiated.
 
-# 4 How has the Amazon been constructed as a problem?
-
-## 4.1 The rises and falls of the Amazon as a topic in presidential speeches
-
-When, where, and how often do presidents speak about the Amazon?
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15.4% of their speeches.
-For comparison purposes the averages for other policy objects in the same corpus of speeches are: inequality (14.7%), criminality (17.3%), inflation (20.9%), and unemployment (13.8%).
-The frequency at which the Amazon appears across presidential speeches inside, outside, and overall varies similarly across time (see Figure 7 in appendix).
-
-```{r Figure 2, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc1 <- pop %>%
-  count(amazon_speech, year) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(amazon_speech == 1) %>% 
-  select(c(perc, amazon_speech, year))
-Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
-  geom_line(color = "darkgreen") +
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  scale_y_continuous(labels = percent_format()) + 
-  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
-  annotate("text", x = 1988.7, y = 0.35, label = "The Murder of\nChico Mendes", size = 3)+
-  annotate("text", x = 1992.5, y = 0.27, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
-  labs(x = "", y = "",
-       title = "Share of speeches that mention the Amazon per year",
-       subtitle = "Sample composed by all 6130 speeches since 1985",
-       color='Y series') +
-  theme_am()
-Amazon_year
-```
-
-Five local maxima stand out in the figure: 1989, 1992, 2009, 2015, and 2019.
-These points coincide with internal and external events that help us explain the rises and falls of the Amazon in presidential discourse.
-From 1985 to 1988, the mentions of the Amazon in official speeches increased from 4% to 14%.
-During this period, the latest Brazilian Constitution was written, which gave indigenous and traditional populations space to advocate for constitutional environmental rights and the protection of their territories [@hecht1990].
-In 1989, however, the Amazon appeared in 32% of all speeches.
-This maximum correlates with the brutal murder of Chico Mendes in the last days of 1988.
-The incident caught unprecedented international attention and Sarney responded to this with a set of policies to address deforestation [@capobianco2021], including accepting to host the 1992 Earth Summit [@keck1998].
-
-1990-91 the Amazon appeared in 12% to 14% of all speeches but, by 1992, this average increased to 25%.
-The 1992 Earth Summit in Brazil brought international attention to environmental topics related to the Amazon.
-One of the big announcements, for example, was the consolidation of the first transnational partnership for the Amazon, the G7 Pilot Program, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another maximum in mentions of the Amazon.
-This coincides with the 2009 Copenhagen Summit and the steepest decrease in deforestation rates since data is available as Figure 3, below, illustrates.
-Lula led the delegation to Copenhagen with a self-image of "we do not promise, we deliver" when the stakes about climate change were high [@franchini2019].
-
-```{r Figure 3, fig.cap="Deforestation rates since 1988", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-def_rates <- ggplot(amazon_def_year, aes(x = year)) +
-  geom_line(aes(y = area), color= "darkolivegreen", linetype="twodash", size= 0.5)+
-  geom_smooth(se=FALSE, color="black", aes(y=area), linetype="solid", size= 0.5)+
-  annotate("text", x = 2005, y = 29000,
-           label = "2004 Plan to Combat and Control Deforestation", size = 3) +
-  annotate("text", x = 2012.5, y = 3500, label = "2012 Forest Code ", size = 3) +
-  labs(x = "", y = "Deforestation in squared kilometers",
-       title = "Deforestation rates since 1988",
-       subtitle= "Data from INPE, Brazilian Ministry of Science and Technology.",
-       color = "",
-       caption= "Black curve smoothed using loess.")+
-  theme_am()
-def_rates
-```
-
-From 2010 to 2018, except for 2015, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-From 2010 to 2014, mentions of the Amazon went down from 18% to 8%.
-Disagreements related to the priority of environmental preservation over economic development were frequent, most notably in the case of approval of the New Forest Code in 2012, which regularized land ownership of many illegally deforested areas.
-The period was also marked by political and economic instability which culminated in the impeachment of Rousseff in 2016.
-In 2015, the Amazon appeared in 19% of all speeches.
-This maximum coincides with the Paris summit which became a key turn in climate politics after the failures of Copenhagen.
-Brazil went to the Paris Summit with deforestation numbers slightly higher than Copenhagen and a perception that there was a turn towards less conservation inside the country.
-By 2016 mentions of Amazon in official speeches went down to 6%, the lowest share since 1985.
-
-We subsequently observe a steady increase from 6% in 2016 to 24% in 2019, the first year of Bolsonaro's presidency.
-At the time, international and national media brought unprecedented attention to Brazilian environmental issues as the record burning of the Amazon led up to a red sky afternoon in São Paulo in August 2019.
-Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
-Bolsonaro went on to retrieve Brazil's hosting status for COP25.
-
-The frequency at which the Amazon appears in domestic and international speeches varies in similar ways as the maxima in the topic frequencies, led by the events discussed above, appear within and outside Brazil (see Figure 7 appendix).
-We interpret this as evidence that relevant events drive interest and alter how pressing the Amazon as a policy object is perceived both nationally and internationally.
-This does not mean, though, that when presidents speak about the Amazon, they highlight the same issues.
-
-## 4.2 Problem-constructions in time
-
-Our subsequent analysis suggests that governments do not defend a specific view of the Amazon.
-The same governments construct the Amazon as various pure and mixed type problems, which unravels a less cohesive story than that told by the literature scrutinizing policy cycles.
-
-### Pure-type problem-constructions
-
-We conceptualize four problem-constructions: sovereignty, economic integration, social development, and conservation.
-Figure 4, below, illustrates the share of each pure-type in time.
-Pure problem-constructions are most common, with an average of 56% of all Amazonian statements across time.We identify a discursive shift in problem-constructions from developing the Amazon economically, to conserving it and providing services to its citizens.
-Pure economic integration constructions are most common constructions from 1985 to the late 2000s.
-This is especially pertinent during the Cardoso administration.
-Brazilian presidents after Cardoso moved from employing one problem-constructions consistently to a more diverse strategy.
-During Lula's terms in office, constructing the Amazon purely as an issue of economic integration decreased, while constructing the Amazon issues of environmental conservation and social development increased.
-Conservation and social development constructions surpassed economic integration around 2010 and continued to dominate as Amazonian constructions during Rousseff's administration.
-Still, environmental conservation and social development problem-constructions were not as dominant in terms of frequency or periods in time in discourses as economic integration was until the early 2000s.
-Finally, we observe a steady increase in sovereignty constructions in the late 2000s, reaching the highest frequencies with the presidencies of Bolsonaro.
-As we conceptualize and operationalize sovereignty as containing internal and external perceived threats to the Amazon, we interpret this increase as not only attacks on international interference in the Amazon but also on indigenous and traditional populations.
-
-```{r Figure 4, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
-pure_types_time <- ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat2 == "Pure-types") %>%
-  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
-  geom_smooth(aes(fill = mx_cat), se = FALSE, size =0.75, linetype="solid") +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
-       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "Curves in the plot were smoothed using loess method.") +
-  theme_am() +
-  theme(legend.position = "bottom")+
-  guides(fill=guide_legend(nrow=2,byrow=TRUE))
-
-pure_types_time
-```
-
-The trends identified are especially interesting considering Amazonian policies and deforestation rates portrayed in Figure 3, above.
-First, deforestation rates have a strong negative correlation with environmental conservation.
-When deforestation rates increased from 1988 to 2004, and from 2012 until 2021, environmental conservation constructions decreased.
-As deforestation rates decreased from 2004 to 2012, environmental conservation constructions in presidential speeches increased.
-@capobianco2021 argues that the unprecedented decrease in deforestation we observed from 2004 to 2012 was a product of an increase in the perception of stronger federal policies and police presence in the Amazon region which, in turn, engendered a perception of a higher risk of being caught and fined for deforestation.
-The shift from constructing the Amazon as an issue of economic integration to an issue of environmental conservation generates a perception that illegal deforestation will be increasingly monitored and sanctioned.
-Second and relatedly, deforestation rates have a positive and strong correlation with economic integration.
-When deforestation increased from 1988 to 2004 and from 2012 to 2021, so did mentions to economic integration.
-When deforestation decreased from 2004 to 2012, economic integration decreased as well.
-This suggests that presidents might boast policy outcomes related to economic integration as justifications for deforestation.
-
-### Mixed-type problem-constructions
-
-In a speech, presidents might mix multiple problem-constructions within a same statement about the Amazon.
-Although presidents prefer pure problem-constructions, they also construct the Amazon as a multifaceted issue.
-Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
-Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
-Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
-Figure 5, below, displays the averages of mixed-types constructions by presidents.
-
-```{r Figure 5, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mixed_types_presid <- ama_mx %>%
-  count(president, mx_cat, mx_cat2) %>%
-  group_by(president) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x = president, y = perc, fill = mx_cat,
-             label = scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat = "identity", position = "stack") +
-  geom_text(size = 2, position = position_stack(vjust = .5)) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
-       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme_am() +
-  theme(legend.position = "right")
-mixed_types_presid
-```
-
-The most frequent mixed-type problem construction of the Amazon is economic conservation.
-This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
-This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue (see Figure 4), increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
-The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-This is not surprising, as developing countries like Brazil repeatedly claim a "right to develop", when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
-Nonetheless, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
-
-Both Lula and Bolsonaro construct the Amazon as a multifaceted issue more frequently than other presidents.
-Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
-
-## 4.3 The Amazonian multi-level game: boasting policy outside and talking to people inside
-
-The Amazon region, forests, and peoples have historically been the topic of local, national, and international debates.
-This implies that audiences' priorities in each setting change and consequently which policies are appropriate to solve the "Amazon issue" differ as well.
-As presidents physically move farther away from the Amazon, audiences might have different stakes and interests in it.
-While speeches inside the Amazon might focus on social development, for example, speeches in the United Nations in New York might highlight environmental conservation.
-To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run four logistic regressions, one for each pure-type construction as a dependent variable.
-We focus on pure-type constructions as these represent most constructions and avoid ambiguity.
-The independent variable for all models is the distance between the state's or country's capital to Manaus.
-Figure 6, below, depicts the predicted probabilities from the models (see Table 1) as functions of distance.
-
-```{r Figure 6, fig.cap="Logistic Regression predicted values", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-
-ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
-ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
-ama_model <- filter(ama_model, location_cat != "Non Identified",
-                    mx_cat != "Other Mixed-types") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
-         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
-         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
-         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
-
-# model
-
-model_logit_con <- glm(con_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_ei <- glm(EI_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_sd <- glm(SD_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_sov <- glm(sov_vs_all ~ km_to_manaus + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-
-# Plot model
-ama_model$"Environmental Conservation" = predict(model_logit_con, ama_model, type = "response")
-ama_model$"Economic Integration" = predict(model_logit_ei, ama_model, type = "response")
-ama_model$"Social Development" = predict(model_logit_sd, ama_model, type = "response")
-ama_model$"National Sovereignty" = predict(model_logit_sov, ama_model, type = "response")
-plot_loc <- ama_model %>% gather(key=p_c, value = pred, 22:25)
-
-plot_loc$p_c <-factor(plot_loc$p_c, levels = c("Economic Integration",
-                                               "Environmental Conservation",
-                                               "Social Development",
-                                               "National Sovereignty"))
-all_loc <- ggplot(plot_loc, aes(x = km_to_manaus, y=pred, color=p_c)) +
-  geom_jitter(alpha=1, size=1) +
-  geom_smooth(size = .5, se=FALSE) +
-  scale_y_continuous(labels = percent_format()) +
-  labs(x = "Distance from the Amazon (km)",
-       y = "",
-       title = "Predicted probability of each problem-construction as a function of\ndistance from the Amazon",
-       caption = "Curves in the plots are estimated using loess method.") +
-    theme_am() +
-  theme(legend.position = "none")+
-  facet_wrap(~p_c, ncol=2)
-
-all_loc
-
-```
-
-```{r Models for Table, include=FALSE}
-
-#models for table
-
-ama_model$thousand_km<- ama_model$km_to_manaus/1000
-
-model_logit_con2 <- glm(con_vs_all ~ thousand_km + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_ei2 <- glm(EI_vs_all ~ thousand_km + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_sd2 <- glm(SD_vs_all ~ thousand_km + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-model_logit_sov2 <- glm(sov_vs_all ~ thousand_km + election_year + def_year + AAI,
-                   family=binomial(link = "logit"), data = ama_model)
-
-```
-
-We convert log odds from Table 1, below, into probabilities and report the 95% confidence interval in the subsequent sentences [^2].
-First, we find that for each 1000Km increase in distance, there is an increase between 51.92% and 53.91% in the predicted probability of constructing the Amazon as an issue of environmental preservation.
-That is, the farthest away presidents are from the Amazon region, the more likely they are to construct it as an issue of environmental conservation.
-Second,the opposite is true for economic integration (and social development): for an increase of 1000Km in distance, we find a decrease between 47.36% (45.35%) and 49.74% (49.23%), respectively.
-When speaking within the Amazon, presidents focus on social development and economic integration.
-This entails that conservation might be a desirable construction when speaking internationally about the Amazon, but not at the local level, where presidents highlight economic and social development.
-This multi-level game implies that presidents talk to the economic and social needs of the people domestically while boasting about environmentalism internationally.
-Finally, national sovereignty problem constructions do not appear to change with distance.
-
-[^2]: See table 3 in appendix for all odds ratios and confidence intervals.
-
-````{=tex}
-\begin{landscape}
-
-```{r Table 1, fig.cap="Logistic Regressions Output", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-md <-stargazer::stargazer(model_logit_con2, model_logit_ei2, model_logit_sd2,
-                          model_logit_sov2, digits = 6, 
-                          dep.var.labels = c("Conservation", "Economic Integration",
-                                             "Social Development", "Sovereignty"),
-                          covariate.labels = c("Distance from the Amazon in 1000s of km",
-                                               "Election year", "Yearly Deforestation",
-                                               "Yearly   Inflation"), no.space = TRUE,
-                          title = "Logistic Regressions Output")
-```
-
-\end{landscape}
-````
-
-```{r model probs, include=FALSE}
-
-# Increasing thousand_km by 1, will result in a 0.11555 in logit(probability) or log(p/1-p)
-# p/(1-p)=exp.0.1155
-# p/(1-p)=1.122435
-# p= 1.12243/2.1224
-# p=52.8%
-
-logit2prob <- function(logit){
-  odds <- exp(logit)
-  prob <- odds / (1 + odds)
-  return(prob)
-}
-
-logit2prob(coef(model_logit_con2))
-logit2prob(coef(model_logit_ei2))
-logit2prob(coef(model_logit_sd2))
-logit2prob(coef(model_logit_sov2))
-
-odd2prob <- function(x){
-  prob <- x / (1 + x)
-  return(prob)
-}
-```
-
-Our models also suggest that deforestation plays an important role.
-Presidents are, for example, more likely to construct the Amazon as an issue of environmental conservation as deforestation decreases.
-Alternatively, as deforestation increases, presidents are more likely to construct the amazon as an issue of economic integration.
-This indicates that Brazil created a self-image of a strong climate leadership because of the good results achieved from 2004 to 2012 [@franchini2019].
-In the same fashion, economic integration problem-constructions are likely deployed as a justification for increasing deforestation rates.
-
-# 5 Discussion and Conclusion
-
-This paper investigates how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-Our findings are threefold: we find that the frequency of the Amazon as a topic in speeches inside and outside Brazil is equally driven by domestic events as well as international events.
-Second, the same government adopts a diverse range of problem-construction.
-While economic integration dominated discourse from 1985 to the mid-2000s, environmental conservation and social development constructions steadily grew in the 2000s, temporarily surpassing economic integration as a more common problem-construction from 2010 to 2015.
-This implies an overall movement from only exploiting the Amazon for economic purposes to exploiting it and protecting it.
-Constructing the Amazon as an issue of sovereignty became more pertinent after 2010.
-Finally, we find that presidents are more likely to construct the Amazon as an environmental conservation problem than economic integration or social development, as presidents move away from the Amazon region.
-Conceptually, this contributes to understanding the social construction of the Amazon in discourses and how these relate to policies and environmental outcomes.
-Empirically, we provide the first comprehensive overview of when, where, and how the Amazon is constructed as an issue in presidential discourse.
-
-Discursive problem-construction within democracies legitimizes ways of thinking and acting towards the environment.
-If presidents promote an agenda of economic and social development within Brazil that diverges from the one promoted outside of Brazil, to what extent does the implemented agenda respond to domestic versus international demands?
-The Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Regional Protected Areas Program by the World Bank and others; and the 2008 Amazon Fund which provided over USD 1 billion [@silva-muller2022].
-Concurrently, the national agenda of economic integration or social development was pursued.
-For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-Multiple contradictory policies negotiated simultaneously, imply that presidents construct policy objects as issues important to local electorates within the Amazon while, at the same time, highlighting aspects important for international actors elsewhere.
-
-The decrease in deforestation that took place in Brazil from 2004 to 2012, was accompanied by a period of strong economic growth.
-With the strengthening of environmentalism, through the participation of indigenous and civil society in politics [@hochstetler2007], the fall of economic integration problem-construction and the rise of both social development and environmental conservation constructions in the 2000s suggest a new balance between granting local livelihoods their rights and economic development.
-This new balance was both unprecedented and not long-standing.
-Unprecedented because never before the environment and people were equally present as the economy in presidential discourse.
-Not long-standing because the dismantling of environmental policy in favor of infrastructure and agricultural expansion was already on its way in the late 2010s.
-The 2012 New Forest Code is seen as a turning point: political opposition to conservation organized itself and managed to lobby with the executive and won these battles even though they were largely opposed by environmentalists.
-
-The steady increase of sovereignty problem-constructions starting in 2010 brings an eerie twist.
-The embryo of Bolsonaro's Amazonian discourse was growing half a decade before he took office.
-Bolsonaro is a product of political re-organization of national and international actors - to which Rousseff and Temer were already responding in discourse - rather than the cause of change in politics.
-The political forces in Brazilian democracy that drove these policy and discursive changes in problem-construction were long in the making, Bolsonaro's problem-constructions and policies are the strongest forms of this shift.
+Third, employing lagged deforestation as a control variable has several constraints.
+We assume presidential discourse, policies, and outcomes are co-constitutive.
+Though, we lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates.
+We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and general outcomes.
+Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations without making causality claims.
 
@@
 The authors are extremely grateful to Matias López, Graziella Moraes Silva, and James Hollway for their support.
-The authors would also like to thank Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
+The authors would also like to thank the Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
 
@@
 ````
-
-```{r Figure 7, fig.cap="Amazonian speeches in time and space", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc_in <- pop %>%
-   mutate(location_cat = ifelse(grepl("International|Non Identified",
-                                      location_cat),
-                                "Outside of Brazil", "In Brazil")) %>%
-  filter(location_cat == "In Brazil") %>% 
-  count(amazon_speech, year, location_cat) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(amazon_speech == 1) %>%
-  select(c(perc, amazon_speech, year, location_cat))
-perc_out <- pop %>%
-   mutate(location_cat = ifelse(grepl("International|Non Identified",
-                                      location_cat),
-                                "Outside of Brazil", "In Brazil")) %>%
-  filter(location_cat == "Outside of Brazil") %>% 
-  count(amazon_speech, year, location_cat) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(amazon_speech == 1) %>%
-  select(c(perc, amazon_speech, year, location_cat)) 
-# location plots
-Amazon_year_in <- perc_in %>%
-  ggplot(., aes(x = year, y = perc))+
-  geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  annotate("text", x = 1985, y = 0.17, label = "16.17%", size = 3.5)+
-  annotate("text", x = 1988.7, y = 0.39, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.36, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.28, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.24, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.28, label = "August Fires", size=3) +
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "",
-       title = "Share of speeches inside Brazil",
-       subtitle= " 4344 speeches out of 6130",
-       color='Y series') +
-  theme_am()
-Amazon_year_out <- perc_out %>% 
-  ggplot(., aes(x = year, y = perc))+
-  geom_line(color="darkgreen")+
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
-  annotate("text", x = 1985, y = 0.165, label = "15.49%", size = 3.5)+  
-  annotate("text", x = 1988.7, y = 0.39, label = "Chico Mendes", size = 3)+
-  annotate("text", x = 1992, y = 0.36, label = "Earth Summit", size = 3)+
-  annotate("text", x = 2009, y = 0.28, label = "Copenhagen Summit", size = 3)+
-  annotate("text", x = 2015, y = 0.24, label = "Paris Summit", size = 3)+
-  annotate("text", x = 2019, y = 0.28, label = "August Fires", size=3)+
-  scale_y_continuous(labels = percent_format())+
-  labs(x = "", y = "",
- title = "Share of speeches outside Brazil",
-       subtitle= " 1786 speeches out of 6130",
-       color='Y series') +
-  theme_am()
-grid.arrange(Amazon_year_in, Amazon_year_out, nrow=2)
-```
-
-````{=tex}
-\begin{landscape}
-
-```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, echo=FALSE, paged.print=TRUE, include=TRUE}
-
-modelsummary::modelsummary(list("Conservation" = model_logit_con2,
-                                "Economic Integration" = model_logit_ei2,
-                                "Social Development" = model_logit_sd2,
-                                "Sovereignty" = model_logit_sov2),
-                           exponentiate = TRUE, statistic = "conf.int",
-                           coef_rename = c("thousand_km" = "1000 km",
-                                        "def_year" = "Yearly Deforestation",
-                                        "AAI" = "Average Yearly Inflation",
-                                        "election_year" = "Election Year",
-                                        "(Intercept)" = "Constant"),
-                           stars = TRUE,
-                           title = "Odds Ratio and Confidence Intervals")
-```
-
-\end{landscape}
-````

### 2022-12-09 Submission/draft/draft_resubmission.rmd
More updates to methods section

@@
 
-To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
+To analyze how presidents construct the Amazon as a problem, we build upon Cezar’s 2020 dataset, which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
 We update the dataset by scraping and adding all official speeches from 2020 and 2021.
 The final dataset encompasses 6130 speeches.
-Then, we proceed to identify speeches that refer to the Amazon as a region, people, or forest.
+We, then, proceed to identify speeches that refer to the Amazon as a region, people, or forest.
 We do so by detecting all speeches in which the stem “amazon” appears.
@@
 
-Using the poldis R package (Sposito 2021), we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
+Using the poldis R package (Sposito 2021), we extract two sentences before and after the sentence in which the stem “amazon” appears.
 We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
-When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
-By doing so we create our unit of analysis: an Amazonian statement.
+When two or more matches of the stem “amazon” appear in successive sentences, we get two sentences before the first match and two sentences after the last match.
+This is how our unit of analysis, Amazonian statements, are generated.
 Amazonian statements represent text portions that are meaningful for our specific purpose.
@@
 
-Our approach to text coding is threefold.
-First, we follow the Amazonian historiography literature to develop a codebook to code Amazonian statements as one, or more, problem-constructions (see codebook in appendix).
-In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
-Nonetheless, each Amazonian statement might be assigned to one or more codes.
+Our approach to coding Amazonian statements is threefold.
+First, we follow the Amazonian historiography literature to develop a codebook to identify Amazonian problem-constructions (see codebook in appendix).
+In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
+However, an Amazonian statement can be coded as referring multiple problem constructions.
 A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation.
-Amazonian statements, thus, can be either coded as pure-types or mixed-types.
+Amazonian statements, thus, can be pure-type statements (i.e.
+constructs the Amazon as a single problem) or mixed-types (i.e.
+constructs the Amazon as multiple issues).
 Figure 1, below, portrays this operationalization strategy.
@@
 
-Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazonian Statements identified.
-We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time, and as a problem.
+Second, with the codebook in hand, each one of the authors separately hand-coded 1007 randomly selected Amazonian statements.
+This amount refers to 50% of all the Amazonian statements identified.
+We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and as a problem.
 As well, the size of the training set should increase with the number of categories (Grimmer, Roberts, and Stewart 2022).
-Since we have four categories, hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and for validation, of the models.
-Automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-Once coded, the average intercoder agreement for hand-coded categories was 85%.
+Hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and the validation, of the automated model.
+The average intercoder agreement for hand-coded categories was 85%.
 For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
 
-Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts (Meyer et al.
+Third, the hand-coded data is randomly divided into a training set, containing 80% of the data (806 observations), and a validation set, containing the remaining 20% of the data (201 observations).
+We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier for binary categories, to label texts (Meyer et al.
 2021; Noble 2006).
-As a robustness check, the SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set.
-The trained SVM model was, on average, 82%, accurate in classifying observations in the validation set before being tuned.
-After the SVM model is tuned and the size of the training set is increased by including all hand coded observations, we use the model to automatically code the remaining 1007 Amazonian statements.
-The authors then randomly select 100 Amazonian statements automatically coded and find that the model is 97% accurate in coding these statements.
-The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements (add a footnote for false positives here)).
+To validate the model, the SVM algorithm is trained using the hand-coded training set and then employed to classify observations in the validation set.
+The trained SVM model was, on average, 82%, accurate in coding observations in the validation set.
+The SVM model is, then, tuned, re-trained using all the 1007 hand-coded observations, and used to automatically code the remaining 1007 Amazonian statements.
+As a final robustness check, the authors also randomly select 100 Amazonian statements automatically coded and find that the automated model is 97% accurate in coding these statements.
+The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statement ^[We also trained the model to identify false positive Amazonian statements.
+These are statements in which the stem “Amazon” is matched but the statements is not meaningful in relations to the policy object.
+For example, cases in which a president acknowledges the presence of the governor of the Amazon state, but is not really speaking about the Amazon.].
+Automating the coding of half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.
 
@@
 
-To analyze our data, we model the share of a specific pure problem-construction, versus all other problem-constructions, as the dependent variable, in relative to the settings in which a particular speech happens, as our independent variable.
+To analyze our data, we model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable.
 This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
-We chose to focus on pure constructions to provide unambiguous interpretation and robust correlations.
-We divide setting in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
+We focus on pure problem constructions to provide unambiguous interpretation and more robust findings.
+We divide settings in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
 The level aggregation refers to geo-political settings that make sense in light of the Amazon, as a policy object.
 This aggregation combines different expectations presidents might have about transnational audiences in these settings.
-As well, Brasilia is a separate setting because of its’ unique location and since most presidential speeches are delivered in Brasilia.
-We control for yearly deforestation rates, inflation, election years, and peak years for Amazon appearing year in presidential speeches.
-Subsequently, we plot Amazonian statements and problem-constructions over time and by setting.
-We interpret the plots and model considering the literature alongside with multiple Amazon-related events and policies over the last 30 years.
+Brasilia is separated as a setting due to its’ unique geolocation and since most presidential speeches are delivered in Brasilia.
+The model controls for yearly deforestation rates, inflation, election years, and peak years for Amazon in presidential speeches.
+The analysis also plots Amazonian statements and problem-constructions over time and by setting.
+We interpret the models and plots considering the literature, Amazon-related events, and policies over the last 40 years.
 
@@
 We assume presidential discourse, policies, and outcomes are co-constitutive.
-Though, we lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates.
-We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and general outcomes.
-Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations without making causality claims.
+We lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates.
+We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and outcomes.
+Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations, without making causality claims.
 

### 2022-12-09 Submission/Models_pretest.Rmd

@@
                                levels = c("Amazonian States",
+                                          "Non Amazonian States",
+                                          "Brasilia",
                                           "Amazonian Countries",
-                                          "International", "Brasilia",
-                                          "Non Amazonian States")),
+                                          "International")),
          election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
@@
 
+ c5 <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + AAI + election_year, data = ama_model2_lag,
+                         model = "within", index = "president")
+
 stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
@@
                       dep.var.labels = c("Environmental Conservation", "Economic Integration",
-                                             "Social Development", "National Sovereignty"),
-                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
+                                             "Social Development", "National Sovereignty", "Amazonian   Speech"),
+                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Deforestation", "Inflation", "Election Year", "High-profile Events"))
 ```

### 2022-12-09 Replication_Files/data_preparation.R
Added 2022 data

@@ -1,4 +1,4 @@
-1# In this script we prepare the data with some text pre-processing,
+# In this script we prepare the data with some text pre-processing,
 # by extracting Amazonian statements, and 
 # by adding locations for all speeches.
 
@@ -6,9 +6,12 @@
 # devtools::install_github("henriquesposito/poldis")
 library(poldis)
 library(dplyr)
+library(readxl)
+
+BR_Presidential_Speeches <- read_excel("Submission/Data and replication/2022.xlsx")
 
 # Load data
-BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+#BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
 
 # Replace on title and text
 BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
@@ -32,23 +35,19 @@ BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Sp
 
 # get context and update amazon specific data
 Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text))
-#Amazon_speeches$context <- poldis::context("amazon", var = Amazon_speeches$text, level = "sentences")
-#Amazon_speeches$ccontext <- unlist(lapply(Amazon_speeches$context, function(x) paste(x, collapse = " | ")))
 
 # Get 2 sentences before and 2 sentences after with poldis
-Amazon_speeches$AM2 <- poldis::context("amazon", Amazon_speeches$text, "sentences", 2)
+Amazon_speeches$AM2 <- poldis::extract_context("amazon", Amazon_speeches$text, "sentences", 2)
 
 # Get and save long data coding
 amazon_speeches_long <- Amazon_speeches %>%
-  select(ID, president, year, party, title, date, text, AM2) %>% 
+  select(president, year, party, title, date, text, AM2) %>% 
   tidyr::unnest(cols = c(AM2))
 
 # save the data
-saveRDS(amazon_speeches_long, "amazon_speeches_long.Rds") # 2014 obs
+#saveRDS(amazon_speeches_long, "amazon_speeches_long.Rds") # 2014 obs
 
 # A few more things
[…]

### 2022-12-09 Replication_Files/supervised_machine_learning.R

@@ -1,11 +1,22 @@
-# Supervised Machine Learning Model - SVM
+# Supervised Machine Learning Model using SVM (support vector machine) algorithm
+
+# Load packages
+library(dplyr)
+library(stringr)
+library(glmnet)
+library(tm)
+library(yardstick)
+library(lsa)
+library(e1071)
+library(RTextTools)
+library(SnowballC)
 
 # Load final hand coded data
 final_hand_coded_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_hand_coded_data.Rds")
 # Load final labeling data
 final_unlabeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_unlabeled_data.Rds")
 
-# Split Data into Training and Testing in R 
+# Split Data into training and validations sets
 sample_size = floor(0.8*nrow(final_hand_coded_data))
 set.seed(1201)
 picked <- sample(seq_len(nrow(final_hand_coded_data)), size = sample_size)
@@ -14,10 +25,15 @@ vvalid = final_hand_coded_data[-picked,]
 
 # Create matrixes
 train_matrix <- create_matrix(ttrain["AM2"], weighting = weightTfIdf)
-valid_matrix <- create_matrix(vvalid["AM2"], originalMatrix = train_matrix, weighting = weightTfIdf)
-score_matrix <- create_matrix(final_unlabeled_data["AM2"], originalMatrix = train_matrix, weighting = weightTfIdf)
+valid_matrix <- create_matrix(vvalid["AM2"], originalMatrix = train_matrix,
+                              weighting = weightTfIdf)
+train_matrix_total <- create_matrix(final_hand_coded_data["AM2"],
+                                    weighting = weightTfIdf)
+score_matrix <- create_matrix(final_unlabeled_data["AM2"],
+                              originalMatrix = train_matrix_total,
+                              weighting = weightTfIdf)
 
-# Model fp
+# Model false positives
 tune_fp <- tune(svm, train_matrix, as.numeric(ttrain$false_positives),
                 ranges =list(cost=c(0.00001, 0.00005, 0.0001, 0.0005, 0.001,
                                     0.005, 0.01, 0.05, 0.1, 0.5, 1, 2,
[…]

### 2022-12-09 Replication_Files/data_preparation.R
added training set 22

@@ -8,10 +8,8 @@ library(poldis)
 library(dplyr)
 library(readxl)
 
-BR_Presidential_Speeches <- read_excel("Submission/Data and replication/2022.xlsx")
-
 # Load data
-#BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
 
 # Replace on title and text
 BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
@@ -45,7 +43,14 @@ amazon_speeches_long <- Amazon_speeches %>%
   tidyr::unnest(cols = c(AM2))
 
 # save the data
-#saveRDS(amazon_speeches_long, "amazon_speeches_long.Rds") # 2014 obs
+#saveRDS(amazon_speeches_long, "amazon_speeches_long.Rds") # 2048 obs
+
+# Get a sample for hand coding
+training_set_22 <- amazon_speeches_long %>%
+  select(AM2) %>%
+  dplyr::slice_sample(n = 1024)
+# export to Excel
+# xlsx::write.xlsx(training_set, file = "training_set.xlsx")
 
 # A few more things
 BR_Presidential_Speeches$text <- stringr::str_squish(BR_Presidential_Speeches$text)
@@ -87,10 +92,3 @@ summary(as.factor(BR_presid_speeches_final$location_cat))
 
 # save for analysis
 saveRDS(BR_presid_speeches_final, "BR_presid_speeches_final.Rds")
-
-# Get a sample for hand coding
-training_set <- amazon_speeches_long %>%
-  select(ID, AM2) %>%
-  dplyr::slice_sample(n = 1007)
-# export to Excel
-# xlsx::write.xlsx(training_set, file = "training_set.xlsx")

### 2022-12-09 messy_files/Text from multinomial regression.R

@@ -1,61 +1,0 @@
-````{=tex}
-\begin{landscape}
-
-```{r full regression results, echo=FALSE, message=FALSE, warning=FALSE, out.width="50%", paged.print=FALSE, include=TRUE}
-# data on deforestation rates per year (PRODES)
-# source: http://terrabrasilis.dpi.inpe.br/app/dashboard/deforestation/biomes/legal_amazon/rates
-# Since annual deforestation rates are calculated since 1988, we copy the rates of 1988 to 1985, 1986, and 1987.
-# These rates are consistent with most estimates (see for example Prates and Bracha 2010 -
-# https://www.scielo.br/j/ecos/a/59DMy3zmJdPHXzXRsHTkmNF/?lang=pt&format=pdf)
-# inflation rates per year Brazil (average for year)
-# source EU inflation: https://www.inflation.eu/en/inflation-rates/brazil/historic-inflation/cpi-inflation-brazil.aspx
-# post estimation tests
-chi_square <- chisq.test(ama_model$mx_cat, predict(model)) 
-# Chi-square p value (p-value < 0.001) tells us that our model explains a
-# significant amount of the variation in the data in comparison with a null model.
-# null_model <- multinom(mx_cat ~ 1, data = ama_model) # Null model for a likelihood ration test, just in case.
-# library(lmtest)
-# lrtest(null_model, model) # We very much reject the hypothesis
-# (i.e. the more complex model is significantly better than the null model).
-# too much information... Let's just focus on what we want here...
-# stargazer::stargazer(model, type = "text",
-#                      covariate.labels = c("Brasilia", "International", "Non-AM state",
-#                                           "Election", "Deforestation", "Inflation"),
-#                      column.labels = c("EI", "SD", "Sov", "EI-Con", "EI-SD", "Sov-Con", "SD-EI-Con",
-#                                        "Sov-EI", "SD-Con", "Other"),
-#                      dep.var.labels.include = FALSE)
-full_md <- tibble("Dependent Variable" = c("EI", "SD", "SOV", "EI-CON", "EI-SD", "SOV-CON", "SD-EI-CON",
-                                           "SOV-EI", "SD-CON", "Other"),
-                  "Brasilia" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)", "-0.341 (0.248)",
[…]

### 2022-12-12 Replication_Files/Final_data_prep_and_SVM.R
Updated data and replication script

@@ -1,0 +1,406 @@
+# In this script we prepare the data with some text pre-processing,
+# by extracting Amazonian statements, and 
+# by adding locations for all speeches.
+# We also run the SVM model and save the final data for analysis.
+
+# To install poldis run:
+# devtools::install_github("henriquesposito/poldis")
+library(poldis)
+library(dplyr)
+library(readxl)
+
+# Load data
+BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
+
+# Replace on title and text
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
+                                                          " - | -| -", "-")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
+                                                           " - | -| -", "-")
+
+# Replace "para" to avoid confusion with state name in Brazil
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
+                                                          "^para$", "pra")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
+                                                           "^para$", "pra")
+
+# Make it lower case, remove extra space, and add coma space
+BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- stringr::str_squish(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- stringr::str_squish(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- trimws(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- trimws(BR_Presidential_Speeches$title)
+
+# Make it latin SCII
[…]

### 2022-12-12 Replication_Files/data_preparation.R

@@ -26,6 +26,10 @@ BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$te
 BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
 BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
 BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- stringr::str_squish(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- stringr::str_squish(BR_Presidential_Speeches$title)
+BR_Presidential_Speeches$text <- trimws(BR_Presidential_Speeches$text)
+BR_Presidential_Speeches$title <- trimws(BR_Presidential_Speeches$title)
 
 # Make it latin SCII
 BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
@@ -35,12 +39,29 @@ BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Sp
 Amazon_speeches <- dplyr::filter(BR_Presidential_Speeches, grepl("amazon", text))
 
 # Get 2 sentences before and 2 sentences after with poldis
-Amazon_speeches$AM2 <- poldis::extract_context("amazon", Amazon_speeches$text, "sentences", 2)
+Amazon_speeches$AM2 <- poldis::extract_context("amazon", Amazon_speeches$text,
+                                               "sentences", 2)
 
 # Get and save long data coding
 amazon_speeches_long <- Amazon_speeches %>%
   select(president, year, party, title, date, text, AM2) %>% 
   tidyr::unnest(cols = c(AM2))
+
+# More cleaning
+amazon_speeches_long$text <- stringr::str_squish(amazon_speeches_long$text)
+amazon_speeches_long$title <- stringr::str_squish(amazon_speeches_long$title)
+amazon_speeches_long$text <- trimws(amazon_speeches_long$text)
+amazon_speeches_long$title <- trimws(amazon_speeches_long$title)
+
+# Get locations from title
+amazon_speeches_long$location <- poldis::extract_location(amazon_speeches_long$title)
+#summary(as.factor(amazon_speeches_long$location))
+
+# Get location from text if not found
+amazon_speeches_long$location <- ifelse(grepl("^NA$", amazon_speeches_long$location),
[…]

### 2022-12-12 Submission/Re-submission/draft/draft_resubmission.rmd
Added 2022 data
Updated data, SVM model, model, and scripts for 2022 data

--- 2022-12-09 Submission/draft/draft_resubmission.rmd
@@
 options(stringsAsFactors = FALSE, scipen = 999)
+```
+
+```{r theme, include=FALSE, warning=FALSE, message=FALSE}
+# custom ploting theme for all plots
+theme_am <- function(x) {
+  theme(text = element_text(size=12,  family="Times"),
+        panel.background = element_rect("white", "black", .5, "solid"),
+                  panel.grid.major = element_line(color = "grey", size = 0.2,
+                                                  linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "none")
+}
 ```
@@
         py_2019=ifelse(grepl("2019", year), 1, 0),
-        location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
-                                     location, ignore.case = TRUE), # minor coding issues to fix
-                               "Non Amazonian States", location_cat),
-         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
-                               "International", location_cat), # minor coding issues to fix
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries",
-                                      location_cat),
+         location_cat = factor(location_cat,
                                levels = c("Amazonian States",
@@
 
-```{r theme, include=FALSE, warning=FALSE, message=FALSE}
-# custom ploting theme for all plots
-theme_am <- function(x) {
-  theme(text = element_text(size=12,  family="Times"),
-        panel.background = element_rect("white", "black", .5, "solid"),
-                  panel.grid.major = element_line(color = "grey", size = 0.2,
-                                                  linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "none")
-}
-```
-
 # 3 Methods
 
-## 3.1 Data and Operationalization
+## 3.1 Problem-construction
+
+## 3.2 Data and Operationalization
 
@@
 
-## 3.2 Analysis and Limitations
+## 3.3 Analysis and Limitations
 
@@
 Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations, without making causality claims.
+
+# 4 Analysis
+
+```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+perc1 <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  scale_y_continuous(labels = percent_format()) + 
+  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.35, label = "The Murder of\nChico Mendes", size = 3)+
+  annotate("text", x = 1992.5, y = 0.27, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2015, y = 0.21, label = "Paris Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
+  labs(x = "", y = "",
+       title = "Share of speeches that mention the Amazon per year",
+       subtitle = "Sample composed by all 6130 speeches since 1985",
+       color='Y series') +
+  theme_am()
+Amazon_year
+```
+
+```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+pure_types_time <- ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_smooth(aes(fill = mx_cat), se = FALSE, size =0.75, linetype="solid") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme_am() +
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
+
+pure_types_time
+```
+
+```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mixed_types_presid <- ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
+       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "right")
+mixed_types_presid
+```
+
+````{=tex}
+\begin{landscape}
+
+```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+# model 3
+c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+
+stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Fixed-effects logistic regressions by president with controls",
+                      column.sep.width = ".001pt",
+                      font.size="small",
+                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
+                                             "Social Development", "National Sovereignty", "Amazonian   Speech"),
+                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Deforestation", "Inflation", "Election Year", "High-profile Events"))
+```
+
+\end{landscape}
+````
 

### 2022-12-12 Replication_Files/Final_data_prep_and_SVM.R

@@ -102,12 +102,13 @@ summary(as.factor(BR_Presidential_Speeches$location))
 # Get a excel file just to replace NAs
 # writexl::write_xlsx(BR_Presidential_Speeches, "BR_presid_speeches_final.xlsx")
 # Most of the NAs left are TV or Radio Announcements in case we want to mark these as such.
-BR_presid_speeches_final <- read_excel("data/BR_presid_speeches_final.xlsx")
-summary(as.factor(BR_presid_speeches_final$location))
+#BR_presid_speeches_final <- read_excel("data/BR_presid_speeches_final.xlsx")
+#summary(as.factor(BR_presid_speeches_final$location))
 
 # Last thing here, let's add a dummy variable for whether certain speech
 # mentions the stem "amazon" or not.
 # As well as let's add a different categorical variable for location.
+BR_presid_speeches_final <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/BR_presid_speeches_final.Rds")
 BR_presid_speeches_final <- BR_presid_speeches_final %>% 
   mutate(amazon_speech = ifelse(grepl("amazon", text), 1, 0),
          location_cat = case_when(grepl("Amazonas|Para|Roraima|Acre|Amapa|Rondonia|Mato-Grosso|Tocantins|Maranhao", location) ~ "Amazonian States",
@@ -115,8 +116,8 @@ BR_presid_speeches_final <- BR_presid_speeches_final %>%
                                   grepl("Distrito Federal", location) ~ "Brasilia",
                                   grepl("NA", location) ~ "Non Identified",
                                   !grepl("Amazonian States|Non Amazonian States|Brasilia|Non Identified", location) ~ "International"))
-summary(as.factor(BR_presid_speeches_final$amazon_speech))
-summary(as.factor(BR_presid_speeches_final$location_cat))
+#summary(as.factor(BR_presid_speeches_final$amazon_speech))
+#summary(as.factor(BR_presid_speeches_final$location_cat))
 
 # save for analysis
 #saveRDS(BR_presid_speeches_final, "BR_presid_speeches_final.Rds")
@@ -142,15 +143,15 @@ final_hand_coded_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files
 # Load final data to label (obs not randomly selected for hand coding)
 final_unlabeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_unlabeled_data1.Rds")
 
[…]

### 2023-01-16 Submission/Re-submission/draft/draft_resubmission.rmd
Updated figures and tables for re-submission

--- 2022-12-08 Submission/draft/draft_resubmission.rmd
@@
     \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
-    \providecommand{\wordcount}[1]{\text{Word Count:}#1}
-    \providecommand{\wv}[1]{\textbf{This is a working version, please do not share or cite without the authors' permission.} #1}
+    \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
 always_allow_html: TRUE
@@
 
-```{=latex}
-\wv{ }
-```
-
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 
+```{r theme, include=FALSE, warning=FALSE, message=FALSE}
+# custom ploting theme for all plots
+theme_am <- function(x) {
+  theme(text = element_text(size=12,  family="Times"),
+        panel.background = element_rect("white", "black", .5, "solid"),
+                  panel.grid.major = element_line(color = "grey", size = 0.2,
+                                                  linetype = "solid"),
+        axis.text = element_text(color = "black", size = 10),
+        title = element_text(color = "black", size = 10, face = "bold"),
+        legend.title = element_blank(),
+        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
+        legend.position = "none")
+}
+```
+
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
@@
 amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-amazon_def_year$year <- amazon_def_year$year + 1
+amazon_def_year_lag <- amazon_def_year
+# missing years are missed with first non missing value
+adr <- data.frame(year = c(1985, 1986, 1987), 
+                  def_year = c(21.050, 21.050, 21.050))
+amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
+amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
 adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                   def_year = c(21.050, 21.050, 21.050, 21.050))
-amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
+amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data 
 hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
@@
                            "Rousseff", "Temer", "Bolsonaro"))
-amazon_def_year$area <- amazon_def_year$def_year*1000
 # Prepare data for problem-constructions
@@
                                       year), 1, 0),
-        peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0),
-        py_1989=ifelse(grepl("1989", year), 1, 0),
-        py_1992=ifelse(grepl("1992", year), 1, 0),
-        py_2009=ifelse(grepl("2009", year), 1, 0),
-        py_2015=ifelse(grepl("2015", year), 1, 0),
-        py_2019=ifelse(grepl("2019", year), 1, 0),
-        location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
-                                     location, ignore.case = TRUE), # minor coding issues to fix
-                               "Non Amazonian States", location_cat),
-         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
-                               "International", location_cat), # minor coding issues to fix
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
-                                            location), "Amazonian Countries",
-                                      location_cat),
+        peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
+        # py_1989=ifelse(grepl("1989", year), 1, 0),
+        # py_1992=ifelse(grepl("1992", year), 1, 0),
+        # py_2009=ifelse(grepl("2009", year), 1, 0),
+        # py_2015=ifelse(grepl("2015", year), 1, 0),
+        # py_2019=ifelse(grepl("2019", year), 1, 0),
+         location_cat = factor(location_cat,
                                levels = c("Amazonian States",
@@
 
-ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
+ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
 dplyr::left_join(AAI, by = "year") %>%
-filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
+filter(location_cat != "Non Identified") %>%
   mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
@@
 
-```{r theme, include=FALSE, warning=FALSE, message=FALSE}
-# custom ploting theme for all plots
-theme_am <- function(x) {
-  theme(text = element_text(size=12,  family="Times"),
-        panel.background = element_rect("white", "black", .5, "solid"),
-                  panel.grid.major = element_line(color = "grey", size = 0.2,
-                                                  linetype = "solid"),
-        axis.text = element_text(color = "black", size = 10),
-        title = element_text(color = "black", size = 10, face = "bold"),
-        legend.title = element_blank(),
-        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
-        legend.position = "none")
-}
-```
+\pagebreak
+# 1. Intro
 
-# 3 Methods
+# 2. Theory
 
-## 3.1 Data and Operationalization
+# 3. Methods
 
-To analyze how presidents construct the Amazon as a problem, we build upon the dataset provided by (Cezar 2020) which contains all official speeches by Brazilian Presidents from 1985 to 2019 scrapped from the archives of the Brazilian Presidential Library.
-We update the dataset by scraping and adding all official speeches from 2020 and 2021.
-The final dataset encompasses 6130 speeches.
-Then, we proceed to identify speeches that refer to the Amazon as a region, people, or forest.
-We do so by detecting all speeches in which the stem “amazon” appears.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
-We find that 946 speeches are, at least partially, about the Amazon.
+## 3.1 Problem-construction
 
-Using the poldis R package (Sposito 2021), we proceed to extract two sentences before and two sentences after the sentence in which the stem “amazon” appears.
-We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
-When an Amazonian statement contains two or more matches of the stem “amazon”, we get two sentences before the first match and two sentences after the last match.
-By doing so we create our unit of analysis: an Amazonian statement.
-Amazonian statements represent text portions that are meaningful for our specific purpose.
-This process yields 2014 unique Amazonian statements about the Amazon.
-On average, an Amazonian statement contains 123 words.
-
-Our approach to text coding is threefold.
-First, we follow the Amazonian historiography literature to develop a codebook to code Amazonian statements as one, or more, problem-constructions (see codebook in appendix).
-In their conceptualization, each problem-construction is mutually exclusive, meaning that they cover different forms of constructing the Amazon as a problem.
-Nonetheless, each Amazonian statement might be assigned to one or more codes.
-A statement can, for example, construct the Amazon as a problem of sovereignty and a problem of economic integration, or a problem of social development and conservation.
-Amazonian statements, thus, can be either coded as pure-types or mixed-types.
-Figure 1, below, portrays this operationalization strategy.
+## 3.2 Data and Operationalization
 
@@
 
-Second, with the codebook in hand, each one of the authors, separately, hand-coded the same set of 1007 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazonian Statements identified.
-We chose to hand code half of the observations because there are several nuances in discourse in how presidents talk about the Amazon over time, and as a problem.
-As well, the size of the training set should increase with the number of categories (Grimmer, Roberts, and Stewart 2022).
-Since we have four categories, hand coding 50% of the statements mean we have a robust and reliable number of observations to be used for the training, and for validation, of the models.
-Automating the coding of half of the observations saved the authors over one month of work in comparison to manual coding.
-Once coded, the average intercoder agreement for hand-coded categories was 85%.
-For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
-
-Third, the hand-coded data is then randomly divided into a training set, containing 80% of the hand-coded observations (806 observations), and a validation set, containing the remaining 20% of the hand-coded data (201 observations).
-We chose to employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier that classifies documents by assigning points in mapped space to maximize the gap between binary categories, to label texts (Meyer et al.
-2021; Noble 2006).
-As a robustness check, the SVM model is trained using the hand-coded training set and then employed to classify observations in the validation set.
-The trained SVM model was, on average, 82%, accurate in classifying observations in the validation set before being tuned.
-After the SVM model is tuned and the size of the training set is increased by including all hand coded observations, we use the model to automatically code the remaining 1007 Amazonian statements.
-The authors then randomly select 100 Amazonian statements automatically coded and find that the model is 97% accurate in coding these statements.
-The final dataset for analysis, excluding false positive matches, contains 1895 coded Amazonian statements (add a footnote for false positives here)).
-
-## 3.2 Analysis and Limitations
-
-To analyze our data, we model the share of a specific pure problem-construction, versus all other problem-constructions, as the dependent variable, in relative to the settings in which a particular speech happens, as our independent variable.
-This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
-We chose to focus on pure constructions to provide unambiguous interpretation and robust correlations.
-We divide setting in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
-The level aggregation refers to geo-political settings that make sense in light of the Amazon, as a policy object.
-This aggregation combines different expectations presidents might have about transnational audiences in these settings.
-As well, Brasilia is a separate setting because of its’ unique location and since most presidential speeches are delivered in Brasilia.
-We control for yearly deforestation rates, inflation, election years, and peak years for Amazon appearing year in presidential speeches.
-Subsequently, we plot Amazonian statements and problem-constructions over time and by setting.
-We interpret the plots and model considering the literature alongside with multiple Amazon-related events and policies over the last 30 years.
+## 3.3 Analysis and Limitations
 
@@
 
-The main limitations of our approach are threefold.
-First, related to our sub-setting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “Amazon”, for example, when the president says, “the forest” or “deforestation”.
-Hence, we might be missing statements about Amazon that do not refer to it.
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
-Moreover, our codebook is developed using specific Amazon related vocabulary.
-For example, a statement will be coded as economic integration if it is meaningful support for the tax-free zone of Manaus or a dam in the Amazon.
-However, the economy is generally a topic that presidents speak about frequently.
-Hence, the high incidence of economic integration in Amazonian statements could also be related to the higher importance of this problem-construction in Brazil overall.
+# 4 Analysis
 
-Second, our dataset covers only what is considered an official speech.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
-Problem-construction within presidential discourse, thus, happens in different public and private venues for which we do not account in this paper.
-We believe that setting remains an important factor in changing expectations about audiences, especially for a historical analysis.
-Although we recognize that this, arguably, has begun to change with the advancement of communication technologies.
-Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question.
-Therefore, we are aware that a category as “international”, for instance, encompasses speeches delivered by presidents in a wide variety countries and institutions to a wider variety of audiences, which are not differentiated.
+## 4.1. In time
 
-Third, employing lagged deforestation as a control variable has several constraints.
-We assume presidential discourse, policies, and outcomes are co-constitutive.
-Though, we lag annual deforestation one year since data for the year usually gets publicly released later and, frequently, there is a time difference to when discourses might refer to certain deforestation rates.
-We do think discourses capture general problem constructions that can be used to introduce, discuss, and justify policy and general outcomes.
-Throughout the analysis we carefully discuss how presidential discourses might relate to deforestation rates and outcomes by pointing to the patterns and correlations without making causality claims.
+```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
+perc1 <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(amazon_speech == 1) %>% 
+  select(c(perc, amazon_speech, year))
+perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  geom_line(color = "darkgreen") +
+  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  scale_y_continuous(labels = percent_format()) + 
+  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
+  annotate("text", x = 1992.5, y = 0.26, label = "Earth Summit", size = 3)+
+  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
+  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
+  annotate("text", x = 2022, y = 0.225, label = "Murder\nof Bruno\nand Dom", size = 3)+
+  labs(x = "", y = "",
+       title = "Share of speeches that mention the Amazon per year",
+       subtitle = "Sample composed by all 6130 speeches since 1985",
+       color='Y series') +
+  theme_am()
+```
+
+## 4.2. Model
+
+````{=tex}
+\begin{landscape}
+
+```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+# model 3
+c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+
+stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Fixed-effects logistic regressions by president with controls",
+                      column.sep.width = ".001pt",
+                      font.size="small",
+                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
+                                             "Social Development", "National Sovereignty", "Amazonian   Speech"),
+                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Deforestation", "Inflation", "Election Year", "High-profile Events"))
+```
+
+\end{landscape}
+````
+
+## 4.3. Pure type
+
+```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  ggplot() +
+  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat, fill = mx_cat),
+              se = FALSE, size =0.75, linetype="solid") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme_am() +
+  facet_wrap("mx_cat") +
+  geom_smooth(amazon_def_year, mapping = aes(x = year, y = def_year/100),
+            color= "darkolivegreen", linetype="twodash", se = FALSE) +
+  annotate("text", x = 2002, y = 0.14, label = "27772 km2\ndeforested" , size = 2)+
+  annotate("text", x = 2013, y = 0.03, label = "4571 km2\ndeforested", size = 2)
+```
+
+# 5. Discussion
 
@@
 ````
+
+```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "right")
+```

### 2023-01-16 Replication_Files/Final_data_prep_and_SVM.R

@@ -99,7 +99,7 @@ BR_Presidential_Speeches$location <- ifelse(grepl("^NA$", BR_Presidential_Speech
                                             BR_Presidential_Speeches$location)
 summary(as.factor(BR_Presidential_Speeches$location))
 
-# Get a excel file just to replace NAs
+# Get a excel file just to replace NAs and review things...
 # writexl::write_xlsx(BR_Presidential_Speeches, "BR_presid_speeches_final.xlsx")
 # Most of the NAs left are TV or Radio Announcements in case we want to mark these as such.
 #BR_presid_speeches_final <- read_excel("data/BR_presid_speeches_final.xlsx")

### 2023-01-16 Submission/Re-submission/draft/draft_resubmission.rmd
More updates to re-submission figures

@@
 We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem across time and space.
-Using supervised machine learning, we classify statements about the Amazon in 6130 transnational presidential speeches since 1985.
-We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches inside and outside Brazil.
+Using supervised machine learning, we classify statements about the Amazon in 6240 transnational presidential speeches since 1985.
+We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches.
 While constructing the Amazon as a problem of economic integration are the most common until the mid-2000s, environmental conservation and social development constructions temporarily surpass economic integration from 2010 to 2015.
 In turn, constructing the Amazon as an issue of sovereignty increases since 2010.
-Lastly, the farther away presidents are from the Amazon itself, the more likely they are to construct the Amazon as an issue of environmental conservation.
+Lastly, presidents usually construct the Amazon as an issue of environmental conservation internationally.
+When speaking within the Amazonian region, presidents tend to construct the Amazon as an issue of social development and economic integration.
 ---
@@
         panel.background = element_rect("white", "black", .5, "solid"),
-                  panel.grid.major = element_line(color = "grey", size = 0.2,
+                  panel.grid.major = element_line(color = "grey", linewidth = 0.2,
                                                   linetype = "solid"),
@@
   geom_line(color = "darkgreen") +
-  geom_line(aes(y=mean(perc)), color="black", size=.5, linetype="dotted")+
+  geom_line(aes(y=mean(perc)), color="black", linewidth=.5, linetype="dotted")+
   scale_y_continuous(labels = percent_format()) + 
@@
   geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat, fill = mx_cat),
-              se = FALSE, size =0.75, linetype="solid") +
+              se = FALSE, linewidth =0.75, linetype="solid") +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
 ```
+
+In a speech, presidents might mix multiple problem-constructions within an Amazon statement.
+Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
+Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
+The most frequent mixed-type problem construction of the Amazon is economic conservation.
+This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
+This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
+The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
+This is not surprising, as developing countries like Brazil repeatedly claim a "right to develop", when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
+Nonetheless, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
+Furthermore, both Lula and Bolsonaro construct the Amazon as a multifaceted issue more frequently than other presidents.
+Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].

### 2023-01-18 Submission/Re-submission/draft/draft_resubmission.rmd
added commented out codes to help with certain plot changes, if necessary

@@
   theme_am() +
+  # theme(legend.position = "bottom")+
+  # guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
   facet_wrap("mx_cat") +
@@
               color= "darkolivegreen", linetype="twodash", se = FALSE) +
-  annotate("text", x = 2002, y = 0.14, label = "27772 km2\ndeforested" , size = 2)+
-  annotate("text", x = 2013, y = 0.03, label = "4571 km2\ndeforested", size = 2)
+  annotate("text", x = 1989, y = 0.16, label = "Deforastation", size = 2) +
+  annotate("text", x = 2001, y = 0.18, label = "27772 km2\ndeforested" , size = 2)+
+  annotate("text", x = 2014, y = 0.03, label = "4571 km2\ndeforested", size = 2)
 ```

### 2023-01-26 Submission/Re-submission/draft/draft_resubmission.rmd
New plots

--- 2023-01-16 Submission/Re-submission/draft/draft_resubmission.rmd
@@
   theme_am() +
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
+```
+```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+amazon_def_year <- amazon_def_year%>%
+  mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
+
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  filter(mx_cat=="Pure Environmental Conservation" | mx_cat=="Pure Economic Integration")%>%
+  ggplot() +
+  geom_smooth(aes(x=as.numeric(year), y = perc),
+              se = FALSE, linewidth =0.75, linetype="solid", color="black") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
+       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
+       caption = "Curves in the plot were smoothed using loess method.")+
+  theme_am()+
   facet_wrap("mx_cat") +
-  geom_smooth(amazon_def_year, mapping = aes(x = year, y = def_year/100),
-              color= "darkolivegreen", linetype="twodash", se = FALSE) +
-  annotate("text", x = 2002, y = 0.14, label = "27772 km2\ndeforested" , size = 2)+
-  annotate("text", x = 2013, y = 0.03, label = "4571 km2\ndeforested", size = 2)
+  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/80,fill=extremes),alpha=.5)+
+  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
+  annotate("text", x = 2008, y = 0.35, label = "27'772 km2\ndeforested" , size = 3, color="darkolivegreen", face="bold")+
+  annotate("text", x = 2016, y = 0.05, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")
+
 ```

### 2023-01-26 Submission/Re-submission/draft/draft_resubmission.rmd
facete outcome and setting

@@
 
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
 ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
+  count(mx_cat, mx_cat2,location_cat, year) %>%
   group_by(year) %>%
   mutate(perc = n / sum(n)) %>% 
+  filter(location_cat=="Amazonian States"|location_cat=="International")%>%
   filter(mx_cat2 == "Pure-types") %>%
-  filter(mx_cat=="Pure Environmental Conservation" | mx_cat=="Pure Economic Integration")%>%
   ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc),
+  geom_smooth(aes(x=as.numeric(year), y = perc, fill=),
               se = FALSE, linewidth =0.75, linetype="solid", color="black") +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1))+
+  facet_wrap(~location_cat+mx_cat, nrow=2)+
   labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
@@
   theme_am()+
-  facet_wrap("mx_cat") +
   geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/80,fill=extremes),alpha=.5)+
@@
   annotate("text", x = 2016, y = 0.05, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")
-
 ```

### 2023-01-26 Submission/Re-submission/draft/draft_resubmission.rmd
Started to update text in rmarkdown

--- 2023-01-18 Submission/Re-submission/draft/draft_resubmission.rmd
@@
 ---
-title: How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985
+title: How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985
 author:
@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: 23 September 2022
+date: 27 January 2023
 output:
@@
 csl: chicago.csl
-abstract: Presidential speeches can influence the ways people think and act towards the environment , but they are understudied.
-We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem across time and space.
+abstract: Presidential speeches can influence the ways people think and act towards the environment, but they are understudied.
+We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem across transationally across settings.
 Using supervised machine learning, we classify statements about the Amazon in 6240 transnational presidential speeches since 1985.
@@
 \pagebreak
-# 1. Intro
 
-# 2. Theory
+# 1. Introduction
 
-# 3. Methods
+*We need to protect the Amazon from foreign interests.
+We need to exploit the Amazon's natural resources.
+We need to provide better living standards for the people in the Amazon.
+We need to preserve the Amazon as a standing ecosystem*.
+Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it constructs the Amazon as a particular problem.
+Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a view of the region, its people, and forest [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+While the military dictatorship (1964-85) is, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are often tied to environmental conservation.
+Yet, such monolithic representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
 
-## 3.1 Problem-construction
+In this article, we show how the Brazilian Amazon has been constructed as a problem transnationally in presidential discourses since 1985.
+Building on @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism, we offer a framework that ties discursive problem issue representations to relationships that transcend nation-states to identify and explain variation in problems-constructions.
+We shift the focus from governmental policy to discourse to capture a broader range of understandings for policy objects, problems that demand dedicated policy attention, that introduce, shape, and justify outcomes to broad audiences [@zarefsky2004; @gillion2016].
+Although problem-constructions take place in a series of instances, we analyze the case of official presidential discourses.
+The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil [@pinto2016].
+Working with presidential discourses also allows us to identify variations in how the Amazon is discursively constructed in transnational politics beyond environmental policies.
+Whereas understudied in the Amazonian context, presidential speeches legitimize perceptions about the Amazon that are key for policy adoption and implementation [see @alesina2009; @lopez2020].
+This is especially pertinent for deforestation in the Amazon as expectations of local actors, generated from material and discursive governmental practices, are crucial in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021; @campbell2015].
+As crucial participants in transnational politics, presidents deploy different problem-constructions according to the transnational audiences they are speaking to.
+
+To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6240 official presidential speeches by all Brazilian presidents since 1985.
+Next, we identify all instances where presidents refer to the Amazon in their speeches.
+We develop a codebook grounded in Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
+With this codebook, we manually code a randomly selected training set of statements and use supervised machine-learning to label the remaining observations.
+We then conduct a descriptive analysis of when, where, and how presidents construct the Amazon as a problem.
+
+Our findings are threefold.
+First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international environmentally-related  events.
+Second, we find that presidents are more likely to construct the Amazon as an issue of environmental conservation outside of the Amazon region, this is especially true when presidents speak internationally.
+Within the Amazon region, presidents tend to construct the Amazon as an issue of social development and economic integration.
+Third, the same government adopts a diverse range of problem-construction.
+While the constructions of the Amazon as an issue of economic integration were more salient from 1985 to the mid-2000s, environmental conservation and social development problem-constructions steadily grew since the 2000s, temporarily surpassing economic integration as a more salient construction from 2010 to 2015.
+Constructing the Amazon as an issue of sovereignty steadily increased after 2010.
+This article provides the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
+
+# 2. Theory: problem-constructions, transnational settings, and presidential speeches
+
+## 2.1 Governments and problem-constructions
+
+Social scientists often describe federal governments as proponents of a cohesive set of policies toward the Amazon [@drummond2006; @padua2012; @franchini2019; @pereira2021].
+The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
+Whereas governments from the late-1980s up to the late-2000s are associated with a turn towards policies that focus on environmental conservation [@padua2012].
+The presidencies of Dilma (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, and Bolsonaro (2019-2022) is generally associated to the dismantling of environmental policies [@capobianco2019].
+Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into policy periods, or policy cycles, with one all-encompassing view of the Amazon.
+
+We know, however, that there is more variation within a specific government policy, especially if we consider the Amazon a policy object demanding dedicated policy attention.
+For instance, while many argue that environmental activism in Brazil emerged despite the military dictatorship [@hochstetler2000; @wood1993], @rajao2021 demonstrates how the strengthening of the Forest Code in 1964 was also a military priority.
+Furthermore, a substantial part of Lula’s administration (2003-2010) effectiveness in reducing deforestation in the Amazon was achieved because of deforestation leakage to other biomes (Garret, 2022).
+At the same time, Lula’s administration (2003-2010) provided record high subsidies to the expansion of agriculture in Brazil [@capobianco2021].
+That is, we must look at the Amazon beyond the environmental domain as a forest, region, and peoples.
+
+We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the Brazilian Amazon contain an explicit, or implicit assumption, of what the Amazon problem is.
+@bacchi2009[p.
+10] posits that policies have a cultural dimension as they take “shape within specific historical and national or international contexts”.
+The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
+The alleged problem is not always explicitly stated in a policy, but policies are represented as solutions for both explicit and implicit problems.
+If the Amazon is represented as an “environmental” problem, as is often the case in the literature, then it demands an “environmental” solution.
+Consequently, studies focus on understanding environmental policies [@capobianco2019], the work of environmental NGOs [@silva-muller2022], or the rise of global environmental governance [@andonova2022].
+Alternatively, studies looking into the developments of social and fiscal policy in the region during the last decades are scarce [@acker2017].
+We acknowledge the quality and importance of all these studies.
+Still, we argue that it is crucial for scholars to study the Amazon as a biological, social, political, and geographical policy object.
+We conceptualize the Amazon as a policy object that demands dedicated policy attention of a specific nature.
+Hence, governments can highlight diverse explicit and implicit problems related to a policy object that need political attention.
+This is what we label as problem-constructions.
+<!-- Are we missing a transition from problem-constructions generally to the case of speeeches? -->
+
+## 2.2 Transnational settings and the variation in problem-constructions
+
+The possibility of different problem-constructions for the same policy object in political discourses, requires an explanation of why they would vary.
+On the one hand, @putnam1988 theory of two-level games in international negotiations can be adapted to explain variation in presidential speeches.
+@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups.
+At the national level, interest groups pressure the government to adopt favorable policies.
+Internationally, the government seeks to fulfill domestic preferences “while minimizing the adverse consequences of foreign developments” [@putnam1988, p.
+434].
+While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups.
+
+This two-level approach is, for example, the avenue pursued by @calderwood2019 and @calderwood2020 who investigates variation in American presidential speeches about climate change.
+Consistent with the two-level games, the author finds that presidents are more likely to mention climate change outside the US, though the location of the speech (domestic or foreign) has a small effect on the content of the mention [@calderwood2020].
+However, the party affiliation of American presidents mediate how they speak about climate change [@calderwood2019].
+Thus, adopting a two-level approach to analyze diverse discursive constructions implies that whatever presidents say inside and outside, lies within the policy expectations of domestic and foreign interest groups.
+Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interest of different groups.
+
+On the other hand, @keck1998 theory of international politics as transnational networks, developed in the context of value-based advocacy groups, provides an alternative explanation for variation in problem-constructions.
+The authors reject the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
+Rather, international politics as transnational networks have “a structured and structuring dimension” [@keck1998, p.
+4]: state and non-state actors participate in and shape international politics.
+In this sense, the positions state actors as components of a transnational network derive from complex interactions in which their identities and goals that are malleable and can vary across time and space.
+
+Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
+Presidents can, for example, engage in information politics by creating politically meaningful information and/or moving it where they believe it can have an impact [@keck1998, p.
+24].
+As well, presidents can engage in leverage politics by leveraging institutions to realize symbolic or material gains.
+Transnational networks do not assume a consistent common denominator of problem-constructions.
+That is, presidents construct problems and attempt to inform or leverage transnational audiences for symbolic or material gains according to their expectations of said audience.
+This indicates that how presidents construct policy objects as problems can vary within the country (i.e.
+speaking at diverse states or different associations) as well as when speaking internationally (i.e.
+during a climate conference or after a catastrophe).
+We call these levels in which there could be variation in how presidents construct a problem a setting.
+The setting is a level of aggregation that encompasses one, or multiple, audiences and makes sense concerning the policy object under study, in this case, the Amazon.
+
+## 2.3 Problem-constructions and policy
+
+In addition to the setting where the speech takes place, it is natural that outcomes in policy adoption and implementation can affect when and how presidents construct problems.
+@gillion2016 argues that there are two types of outcomes that can affect presidential discourses: institutional and societal.
+An institutional outcome relates to how presidential discourses can shape policy coalitions and the policy agenda.
+While the relationship between presidential speeches and policy may not be causal, they have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
+This is particularly true in the Brazilian context where the executive branch of government, led by the president, have historically been the primary players in shaping public policy, especially after the 1988 constitution [@pinto2016].
+
+A societal outcome, instead, relates to how discourse informs attitudes and behavior of people on the ground and affects policy outcomes.
+In the case of deforestation, for example, Amazonian scholars argue that the expectations of local actors generated from governments’ decisions [@assuncao2015] and discourses [@capobianco2019; @capobianco2021; @campbell2015] are a crucial factor in choice to deforest on the ground.
+As presidents participate and shape transnational politics by constructing the Amazon as a certain issue, discourses define policy agendas, direct “political officials’ at multiple stages of the public policy-making process” [@gillion2016, 19], influence people’s decision on the ground, and justify previous decision or policy outcomes.
+
+Considering the possibility of varied problem-construction, the relationship between policy and discourse becomes endogenous and co-constituted: problem constructions in presidential speeches can justify past outcomes and/or lead to future outcomes.
+A bad track record in climate change policy outcomes can be justified with a good track record in energy security.
+This was, for example, the strategy adopted by President Bush during the Kyoto Protocol negotiations [@calderwood2020].
+As presidents participate in transnational networks, with malleable identities and goals, will refer to outcomes interchangeably, based on their expectations about the setting they are speaking at and the transnational audiences present.
+Policy outcomes, therefore, can be (re)constructed in presidential discourse in diverse forms to shape certain problem definitions and possible solutions.
+
+# 3. Research Design: operationalizing Amazonian problem-constructions
+
+## 3.1 Codebook (Amazonian historiography)
+
+To capture the cultural dimension and historical contexts behind problem constructions, we rely on the Amazonian historiography literature.
+We refer to Amazonian historiography as the body of research conducted by social and environmental scientists that tell the story of diverse governmental programs that studies the Amazon region, forest, and its people.
+Within this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
+We argue a fourth separate one also exists: social development.
+The social development construction focuses on the constitutional rights and dignity of the inhabitants of the Amazonian region.
+
+### National Sovereignty
+
+In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+8], and when the dust settled and the scramble was over, more than half of the Amazon territory emerged Brazilian.
+While the Brazilian military diplomacy following the scramble was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990].
+These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil’s sovereignty over the Amazon [@hecht2020].
+More recently, as we move to a world where non-state actors gain importance in international politics [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
+Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
+The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
+The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
+
+### Economic Integration
+
+The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@capobianco2019; @becker2005].
+In 1966, the Brazilian Military launched ‘Operation Amazon’, a policy to modernize the region based on three assumptions [@acker2021].
+First, it assumed that nature should be conquered by mankind.
+Second, it assumed that exploiting natural resources would render the Amazon region economically profitable.
+Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory.
+Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
+The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
+These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+
+### Environmental Conservation
+
+The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
+Arguably, the creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
+This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
+The environmental conservation problem-construction emphasizes that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
+The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
+
+### Social Development
+
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
+While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected.
+As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
+Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
+The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
 
 ## 3.2 Data and Operationalization
+
+To identify varied problem-constructions, we focus on presidential speeches.
+By focusing on presidential speeches, rather than specific policy domains, we analytically avoid hinging our analysis on an underlying assumption of what the problem is.
+Thus, we are not necessarily prioritizing an environmental, economic, or sovereignty-based view of the Amazon.
+We build upon @cezar2020 dataset, which contains all official speeches by Brazilian Presidents from 1985 to 2019.
+We update the dataset by scraping and adding all official speeches from 2020 to 2022.
+The final dataset encompasses 6240 speeches.
+We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
+We do so by detecting all speeches in which the stem “amazon” appears.
+In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We find that 968 speeches are, at least partially, about the Amazon.
+Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem “amazon” appears.
+We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
+This is how our unit of analysis, Amazonian statements, are generated.
+This process yields 2048 unique Amazonian statements about the Amazon.
+On average, an Amazonian statement contains 131 words.
+
+We code Amazonian statements in three steps.
+First, we develop a codebook for coding Amazonian problem-constructions identified with the Amazonian historiography (see appendix).
+In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
+However, an Amazonian statement can be coded as referring to multiple problem constructions (see Figure 1 below).
+Amazonian statements, thus, can be pure-type statements (i.e.
+constructs the Amazon as a single problem) or mixed-types (i.e.
+constructs the Amazon as multiple issues).
 
@@
 
+Second, with the codebook in hand, each one of the authors separately hand-coded 1024 randomly selected Amazonian statements.
+This amount refers to 50% of all the Amazonian statements identified.
+We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time.
+As well, since we have four different code categories, the size of the training set should be increased [see @grimmer2022].
+The hand-coding strategy provides a robust and reliable number of observations to be used for training and validation of the automated model.
+Once hand coding was completed, the average intercoder agreement for hand-coded categories was 85%.
+For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
+
+Third, the hand-coded data is randomly divided into a training set, containing 80% of the data (819 observations), and a validation set, containing the remaining 20% of the data (205 observations).
+We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier appropriate for binary categories, to label texts [@meyer2021; @noble2006].
+To validate the model, the SVM algorithm is trained using the hand-coded training set and employed to classify observations in the validation set.
+As a final robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
+Automating the coding of the remaining half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.
+The final dataset for analysis, excluding false positive matches, contains 1924 coded Amazonian statements.
+
 ## 3.3 Analysis and Limitations
+
+To analyze our data, we model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable.
+This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
+We focus on single problem constructions to provide unambiguous interpretations and more robust findings.
+We divide settings in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
+This level of aggregation refers to geo-political settings that make sense in light of the Amazon, as our policy object.
+This aggregation combines different expectations presidents can have about transnational audiences in each of these settings.
+Brasilia, specifically, is treated as a separate setting due to its unique location and since most presidential speeches are delivered there.
+The model controls for yearly deforestation rates, inflation, election years, and peak years for Amazon in presidential speeches.
+
+````{=tex}
+\begin{landscape}
 
@@
 
-models <- tibble::tibble("Models Description" = c("Fixed-effects logistic regressions indexed by president (controlling for time and ideology)."),
-                         "Dependent variables" = c("Pure environmental conservation; pure economic integration; pure social development; and pure national sovereignty."),
-                         "Independent Variables" = c("Amazonian states within Brazil (reference category); non-Amazonian Brazilian states; Brasilia; Amazonian countries; and international."),
-                         "Controls" = c("Yearly deforestation rates lagged by one year; average annual inflation; election years; and peak years for Amazon appearing year in presidential speeches (footnote)."))
+## Count average words in Amazonian Statements
+# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
+# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
+## 131 on average
+
+## Comparison with inflation, criminality, unemployment, and inequality
+# pop %>%
+#   mutate(desigual = ifelse(grepl("desigual", text,
+#                                  ignore.case = TRUE), 1, 0),
+#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
+#                               text, ignore.case = TRUE), 1, 0),
+#          inf = ifelse(grepl("inflacao|inflaçao",
+#                              text, ignore.case = TRUE), 1, 0),
+#          unemploy = ifelse(grepl("desempreg",
+#                              text, ignore.case = TRUE), 1, 0)) %>%
+#   summarise(desigual = mean(desigual),
+#             crime = mean(crime),
+#             inf = mean(inf),
+#             unemploy = mean(unemploy))
+
+models <- tibble::tribble(~"", ~Description,
+                          "Model", "",
+                          "Fixed-effects logistic regressions indexed by the president", "The regression method allows to control for variables not measured (e.g.
+ideology) related to individuals (i.e.
+presidents) [see @allison2009].",
+                          "Dependent variables", "",
+                          "Problem constructions", "Pure environmental conservation; pure economic integration; pure social development; and pure national sovereignty.",
+                          "Independent variable", "",
+                          "Settings", "Setting where speech occurs as (1) non-Amazonian Brazilian states, (2) Brasilia, (3) Amazonian countries, and (4) international, in relation to the reference category of Amazonian states within Brazil.",
+                          "Control variables", "",
+                          "Deforestation rates", "Lagged yearly deforestation rates as a control for the possible relationship between deforestation rates and Amazonian problem-constructions.",
+                          "Election year", "Election years are controls for possible discursive changes related to the Amazon for these years.",
+                          "Inflation rate",  "Average yearly inflation rates as a control for a possible relationship between economic conditions/fluctuations and problem constructions.",
+                          "High-profile environmental event", "Years in which high-profile environmental events occurred control for the frequency and, possibly, how the Amazon was constructed as a problem in discourse for those years.")
 
 kbl(models, booktabs = T, caption = "Model description") %>%
-  kable_styling(latex_options = c("striped", "repeat_header",
-                                  "scale_down", "HOLD_position"),
-                position = "center", font_size = 9, full_width = TRUE)
+kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% row_spec(c(1,3,5,7), bold = TRUE, italic = TRUE)
+# see also: pack_rows("Model", 1, 2)
+# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
 ```
+
+\end{landscape}
+````
+
+The main limitations of our approach are threefold.
+First, related to our subsetting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “amazon”, for example, when the president says, “the forest” or “deforestation”.
+However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
+
+Second, our dataset covers only what is considered an official speech.
+Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
+Problem-construction within presidential discourse, thus, happens in different public, private, and online settings for which we do not account or differentiate in this paper.
+Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question and the data at hand.
+Therefore, we are aware that a category as “international”, for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences, which are not differentiated.
+
+Third, as presidents participate and shape transnational politics, we assume that presidential discourse, policies, and outcomes are co-constitutive.
+Discourses capture general problem constructions that can be used to introduce, discuss, and/or justify policy and outcomes.
+Throughout the analysis we carefully discuss how presidential discourses relate to, for instance, deforestation rates and political outcomes by pointing at some of the patterns and correlations but without making any causal claims.
 
@@
   theme_am() +
-  # theme(legend.position = "bottom")+
-  # guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
-  facet_wrap("mx_cat") +
-  geom_smooth(amazon_def_year, mapping = aes(x = year, y = def_year/100),
-              color= "darkolivegreen", linetype="twodash", se = FALSE) +
-  annotate("text", x = 1989, y = 0.16, label = "Deforastation", size = 2) +
-  annotate("text", x = 2001, y = 0.18, label = "27772 km2\ndeforested" , size = 2)+
-  annotate("text", x = 2014, y = 0.03, label = "4571 km2\ndeforested", size = 2)
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
+```
+
+```{r Figure puretypetime, fig.cap="Pure-types across setting in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+amazon_def_year <- amazon_def_year%>%
+  mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
+ama_mx %>%
+  count(mx_cat, location_cat, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(location_cat == "Amazonian States"|
+           location_cat == "International",
+         mx_cat == "Pure Economic Integration"|
+           mx_cat == "Pure Environmental Conservation"|
+           mx_cat == "Pure Social Development") %>%
+  ggplot() +
+  geom_smooth(aes(x=as.numeric(year), y = perc, fill=),
+              se = FALSE, linewidth =0.75, linetype="solid", color="black") +
+  scale_y_continuous(labels = percent_format(accuracy = 1))+
+  facet_wrap(~location_cat+mx_cat, nrow=2)+
+  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
+       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
+       caption = "Curves in the plot were smoothed using loess method.")+
+  theme_am()+
+  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/100,fill=extremes),alpha=.5)+
+  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
+  annotate("text", x = 2008, y = 0.3, label = "27'772 km2\ndeforested" , size = 3, color="darkolivegreen", face="bold")+
+  annotate("text", x = 2016, y = 0.04, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")
 ```

### 2023-01-27 Submission/Re-submission/draft/draft_resubmission.rmd
full version

@@
 csl: chicago.csl
-abstract: Presidential speeches can influence the ways people think and act towards the environment, but they are understudied.
-We propose a framework to investigate how the Brazilian Amazon has been constructed as a problem across transationally across settings.
-Using supervised machine learning, we classify statements about the Amazon in 6240 transnational presidential speeches since 1985.
-We find that national and international events drive the frequency at which the topic of the Amazon is mentioned in presidential speeches.
-While constructing the Amazon as a problem of economic integration are the most common until the mid-2000s, environmental conservation and social development constructions temporarily surpass economic integration from 2010 to 2015.
-In turn, constructing the Amazon as an issue of sovereignty increases since 2010.
-Lastly, presidents usually construct the Amazon as an issue of environmental conservation internationally.
-When speaking within the Amazonian region, presidents tend to construct the Amazon as an issue of social development and economic integration.
+abstract: blank
 ---
@@
 ```
-
 ```{=latex}
-\wordcount{ 8299 (including abstract, text, references, and footnotes)}
+\wordcount{ 7685 (including abstract, text, references, and footnotes)}
 ```
-
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a view of the region, its people, and forest [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship (1964-85) is, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are often tied to environmental conservation.
+While the military dictatorship (1964-85) is, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010) presidencies are often tied to environmental conservation.
 Yet, such monolithic representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
@@
 For instance, while many argue that environmental activism in Brazil emerged despite the military dictatorship [@hochstetler2000; @wood1993], @rajao2021 demonstrates how the strengthening of the Forest Code in 1964 was also a military priority.
-Furthermore, a substantial part of Lula’s administration (2003-2010) effectiveness in reducing deforestation in the Amazon was achieved because of deforestation leakage to other biomes (Garret, 2022).
-At the same time, Lula’s administration (2003-2010) provided record high subsidies to the expansion of agriculture in Brazil [@capobianco2021].
+Furthermore, a substantial part of Lula's administration (2003-2010) effectiveness in reducing deforestation in the Amazon was achieved because of deforestation leakage to other biomes (Garret, 2022).
+At the same time, Lula's administration (2003-2010) provided record high subsidies to the expansion of agriculture in Brazil [@capobianco2021].
 That is, we must look at the Amazon beyond the environmental domain as a forest, region, and peoples.
@@
 We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the Brazilian Amazon contain an explicit, or implicit assumption, of what the Amazon problem is.
-@bacchi2009[p.
-10] posits that policies have a cultural dimension as they take “shape within specific historical and national or international contexts”.
+@bacchi2009 [p.
+10] posits that policies have a cultural dimension as they take "shape within specific historical and national or international contexts".
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
 The alleged problem is not always explicitly stated in a policy, but policies are represented as solutions for both explicit and implicit problems.
-If the Amazon is represented as an “environmental” problem, as is often the case in the literature, then it demands an “environmental” solution.
+If the Amazon is represented as an "environmental" problem, as is often the case in the literature, then it demands an "environmental" solution.
 Consequently, studies focus on understanding environmental policies [@capobianco2019], the work of environmental NGOs [@silva-muller2022], or the rise of global environmental governance [@andonova2022].
@@
 This is what we label as problem-constructions.
-<!-- Are we missing a transition from problem-constructions generally to the case of speeeches? -->
+<!-- Are we missing a transition from problem-constructions generally to the case of speeches?
+-->
 
@@
 At the national level, interest groups pressure the government to adopt favorable policies.
-Internationally, the government seeks to fulfill domestic preferences “while minimizing the adverse consequences of foreign developments” [@putnam1988, p.
+Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988, p.
 434].
@@
 The authors reject the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
-Rather, international politics as transnational networks have “a structured and structuring dimension” [@keck1998, p.
+Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p.
 4]: state and non-state actors participate in and shape international politics.
@@
 A societal outcome, instead, relates to how discourse informs attitudes and behavior of people on the ground and affects policy outcomes.
-In the case of deforestation, for example, Amazonian scholars argue that the expectations of local actors generated from governments’ decisions [@assuncao2015] and discourses [@capobianco2019; @capobianco2021; @campbell2015] are a crucial factor in choice to deforest on the ground.
-As presidents participate and shape transnational politics by constructing the Amazon as a certain issue, discourses define policy agendas, direct “political officials’ at multiple stages of the public policy-making process” [@gillion2016, 19], influence people’s decision on the ground, and justify previous decision or policy outcomes.
+In the case of deforestation, for example, Amazonian scholars argue that the expectations of local actors generated from governments' decisions [@assuncao2015] and discourses [@capobianco2019; @capobianco2021; @campbell2015] are a crucial factor in choice to deforest on the ground.
+As presidents participate and shape transnational politics by constructing the Amazon as a certain issue, discourses define policy agendas, direct "political officials' at multiple stages of the public policy-making process" [@gillion2016, 19], influence people's decision on the ground, and justify previous decision or policy outcomes.
 
@@
 
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
 8], and when the dust settled and the scramble was over, more than half of the Amazon territory emerged Brazilian.
 While the Brazilian military diplomacy following the scramble was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil’s sovereignty over the Amazon [@hecht2020].
+These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil's sovereignty over the Amazon [@hecht2020].
 More recently, as we move to a world where non-state actors gain importance in international politics [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
@@
 The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@capobianco2019; @becker2005].
-In 1966, the Brazilian Military launched ‘Operation Amazon’, a policy to modernize the region based on three assumptions [@acker2021].
+In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021].
 First, it assumed that nature should be conquered by mankind.
@@
 
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
 However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
@@
 We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
-We do so by detecting all speeches in which the stem “amazon” appears.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We do so by detecting all speeches in which the stem "amazon" appears.
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
 We find that 968 speeches are, at least partially, about the Amazon.
-Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem “amazon” appears.
+Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem "amazon" appears.
 We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
@@
 The main limitations of our approach are threefold.
-First, related to our subsetting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: “amazon”.
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon “amazon”, for example, when the president says, “the forest” or “deforestation”.
+First, related to our subsetting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
+We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "amazon", for example, when the president says, "the forest" or "deforestation".
 However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
@@
 Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question and the data at hand.
-Therefore, we are aware that a category as “international”, for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences, which are not differentiated.
+Therefore, we are aware that a category as "international", for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences, which are not differentiated.
 
@@
 
-# 4 Analysis
+# 4 How has the Brazilian Amazon been constructed as a problem?
 
-## 4.1. In time
+The subsequent analysis visualizes and models Amazonian statements and problem-constructions over time and by setting.
+We interpret these models and plots considering the literature, Amazon-related events, and policies since 1985.
+
+## 4.1 The Amazon as a general topic in presidential speeches
+
+When, where, and how often do presidents speak about the Amazon as a general topic?
+Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
+On average, presidents mention the Amazon in 15.4% of their speeches.
+For comparison purposes the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).
+This suggests the Amazon is a topic of relative high importance for presidents generally.
+However, five local maxima are above average[^1] in the figure:1989, 1992, 2009, 2019, and 2022.
+All of them coincide with environmentally related events that received wide coverage from international media.
+
+[^1]: We consider the years in which the Amazon appeared in over 20% of all official speeches.
 
@@
 
-## 4.2. Model
+In 1989 the Amazon appeared in 32% of all speeches.
+This coincides with the brutal murder of the environmental activist Chico Mendes in the last few days of 1988.
+The incident caught unprecedented international attention and then president Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
+One of the responses was the offer and acceptance to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
+During the summit, we saw the realization of the first transnational partnership for the Amazon, the G7 Pilot Program, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
+
+Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another maximum in mentions of the Amazon.
+The Copenhagen Summit was held in 2009 and, with the steep decrease in deforestation rates, Lula (2003-2010) led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019].
+From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
+Interestingly, this period was intense in terms of domestic legislation.
+The revision of the Forest Code, debated in 2010 and 2011, and approved in 2012, pardoned thousands of illegal deforesters in the Amazon.
+The period was also marked by political and economic instability which culminated in the impeachment of Rousseff (2011-2016) in 2016.
+By 2016 mentions of Amazon in official speeches went down to 6%, their lowest share since 1985.
+
+We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro's presidency.
+At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019.
+Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
+Bolsonaro went on to retrieve Brazil's hosting status for COP25.
+Finally, and unfortunately, in 2022, environmental activist, Bruno Mendes, and British journalist, Dom Phillips, were murdered and buried in the Amazon (McCoy 2022).
+
+## 4.2 Problem-constructions in time
+
+Although we observe variation in the frequency of the Amazon as a general topic, our conceptual framework foresees variation in specific problem-construction depending on a myriad of factors.
+In this subsection, we investigate how pure-types and mixed-types problem constructions evolved over time.The same president simultaneously constructs the Amazon as various problems, which unravels a less cohesive story than that told by the policy-cycle literature.
+Nevertheless, the overall balance between problem-constructions reveals longitudinal trends that speak to the importance of the environment, economy, social policy, and sovereignty.
+Figure 3, below, illustrates the share of each pure-type problem-constructions in time as these are the most common.
+
+Pure economic integration constructions were the most frequent from 1985 to 2009.
+This is especially pertinent during Cardoso's presidency (1995-2002), when economic integration was increasing while environmental conservation decreased.
+When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
+While this correlates with strong environmental policies being adopted in 2004, economic integration still ranked first.
+It was only in 2010, with President Dilma, that environmental conservation and social development problem-constructions surpassed economic integration.
+Interestingly, there is a steady increase of sovereignty problem-constructions starting in 2008 already.
+This reversal was not long-standing, though.
+With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration increases to become the most favored construction.These trends reveal a multi-faceted relationship between problem-constructions, which we summarize in three findings.
+
+```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+mmt1 <- ama_mx %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  count(mx_cat) %>%
+  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
+mmt2 <- ama_mx %>%
+  count(mx_cat)%>%
+  mutate(perc = n / sum(n)) # averages in relation to full sample
+ama_mx %>%
+  count(mx_cat, mx_cat2, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat2 == "Pure-types") %>%
+  ggplot() +
+  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
+              se = FALSE, linewidth =0.75, linetype="solid") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme_am()+
+  theme(legend.position = "bottom")
+```
+
+First, the same governments deploy contradictory constructions, but their relative frequencies reveal trends over time.
+The 1988 Brazilian Constitution foresaw the strengthening of environmentalism through the participation of indigenous peoples and civil society in policy-making [@keck1998], which was slowly confirmed, at least discursively.
+The fall of economic integration problem-construction and the rise of both social development and environmental conservation constructions in the 2000s suggest an unprecedented balance between granting local livelihoods their rights and economic development: never, since 1985, Amazonian constructions that focused on the environment and the constitutional rights of its people were more present than the economic integration in presidential discourses.
+While social development and environmental conservation did go down, we are now at a point in time where they appear almost as frequently as economic integration.
+
+Second, the steady increase of sovereignty problem-constructions starting in 2008 offers context for the Presidency of Bolsonaro.
+The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government.
+In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, stronger criticism of civil society in politics was often met by presidents with accusations of internationalization attempts.
+Thus, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making.
+Bolsonaro's problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
+
+Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
+Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
+Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
+Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
+Figure 4, below, displays the averages of mixed-types constructions by presidents.
+
+```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+ama_mx %>%
+  count(president, mx_cat, mx_cat2) %>%
+  group_by(president) %>%
+  mutate(perc = n / sum(n)) %>%
+  filter(mx_cat2 == "Mixed-types") %>%
+  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
+  ggplot(aes(x = president, y = perc, fill = mx_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "right")
+```
+
+Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation.
+This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
+This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.Mixed-types are particular interesting considering both Lula and Bolsonaro, who construct the Amazon as a multifaceted issue more frequently than other presidents.
+Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
+
+## 4.3 The Amazon in transnational settings
+
+By adapting transnational networks to discourse, we argue that presidents' expectations about transnational audiences in different settings explain variations in problem-constructions.
+To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run four logistic regressions, one for each pure-type construction as a dependent variable (see table 2 below).
+Multiple, often contradictory, problem-constructions are forwarded across settings as presidents participate and shape transnational politics, confirming what our conceptual frameworks foresee.
+We discuss three main findings:
+
+First, when speaking to international audiences (be it in governmental summits, bilateral visits, or fora) presidents are between 54.6% and 56.1%[2] more likely to construct the Amazon as an issue of environmental conservation, in relations to when they speaking inside Amazonian states within Brazil (reference category).
+When speaking within Amazonian countries and Amazonian states, our models suggest that the likelihood of deploying environmental conservation decreases drastically.
+We interpret this as evidence that presidents construct the Amazon as an environmental problem outside Brazil, because of their views of transnational audiences as possible funders of domestic policy and projects.
+The Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Region Protected Areas Program by the World Bank and others; the 2008 Amazon Fund which provided over USD 1 billion; multiple Global Environment Facility grants; as well as multiple bilateral and philanthropic grants [@silva-muller2022].
+They realize material and symbolic gains (leverage politics) by making use of information that argues in favor of the Amazon as an environmental problem (information politics).
+
+Second, economic integration and social development are more likely inside the Amazon than in an international setting.
+Concurrent with the successful environmental policies from the early 2000s, financed by transnational monies, presidents also pursued a national agenda of economic integration or social development.
+For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+The special fiscal regime in Manaus, designed to increase industry presence in the region, was maintained.
+More roads and dams (e.g.
+BR-163 and Belo Monte) were constructed during the period.
+Presidents likely highlight these policies as they see Amazonian populations as voters to whom they are accountable.
+We argue that presidents expect voters' to have socio-economic interests, rather than environmental ones, and therefore construct the Amazon accordingly.
 
@@
 
-## 4.3. Pure type
+When it comes to sovereignty, model four also reveals that sovereignty seems to be a problem construction used more within the country than outside.
+Interestingly, while we found that the frequency of the Amazon as a general topic is driven by environmental-related events (section 4.1), presidents do not necessarily respond to them with environmental problem-constructions.
+Rather, as such events bring strong international media coverage, Brazilian presidents match them with discursive attempts to highlight Brazil's sovereignty over the Amazonian territory.
+The 2019 August Fires are exemplary of these dynamics: in a series of responses directed to President Macron, Bolsonaro consistently highlighted Brazil's sovereignty in various speeches inside Brazil.
 
-```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
-ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat2 == "Pure-types") %>%
-  ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat, fill = mx_cat),
-              se = FALSE, linewidth =0.75, linetype="solid") +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
-       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
-       caption = "Curves in the plot were smoothed using loess method.") +
-  theme_am() +
-  theme(legend.position = "bottom")+
-  guides(fill=guide_legend(nrow=2,byrow=TRUE))
-```
-
-```{r Figure puretypetime, fig.cap="Pure-types across setting in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r setting vs outcome, fig.cap="Problem-constructions, settings, and policy outcomes", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 amazon_def_year <- amazon_def_year%>%
@@
          mx_cat == "Pure Economic Integration"|
-           mx_cat == "Pure Environmental Conservation"|
-           mx_cat == "Pure Social Development") %>%
+           mx_cat == "Pure Environmental Conservation") %>%
   ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc, fill=),
-              se = FALSE, linewidth =0.75, linetype="solid", color="black") +
+  geom_smooth(aes(x=as.numeric(year), y = perc, color=mx_cat),
+              se = FALSE, linewidth =0.75, linetype="solid") +
   scale_y_continuous(labels = percent_format(accuracy = 1))+
-  facet_wrap(~location_cat+mx_cat, nrow=2)+
+  facet_wrap(~location_cat+mx_cat)+
   labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
@@
   theme_am()+
-  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/100,fill=extremes),alpha=.5)+
+  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/120,fill=extremes),alpha=.5)+
   scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
-  annotate("text", x = 2008, y = 0.3, label = "27'772 km2\ndeforested" , size = 3, color="darkolivegreen", face="bold")+
-  annotate("text", x = 2016, y = 0.04, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")
+  annotate("text", x = 2009, y = 0.20, label = "27'772 km2\ndeforested" , size = 1.5, color="darkolivegreen", face="bold")+
+  annotate("text", x = 2015, y = 0.038, label = "4'571 km2\ndeforested", size = 1.5, color="darkolivegreen", face="bold")
 ```
 
-# 5. Discussion
+Finally, while our models take settings and policy outcomes (deforestation rates) as cummulative, we use figure 5 to reveal a complex relationship between policy outcomes, problem constructions and settings.
+We focus on problem-constructions over time inside Amazonian States and in International settings for simplicity.
+Figure 5 demonstrates that when deforestation rates improved (2004-2012),presidents preferred deploying environmental conservation both inside the Amazon as well as outside Brazil.
+As they worsen(2012-2021), the environmental conservation problem-construction stays steady inside Brazil, but decreases strongly outside.
+In line with our framework, this suggests presidents boast good outcomes whenever possible by highlighting the aligned problem construction.
+When outcomes are bad, we see other problem constructions increasing instead, likely deployed as means of sidestepping issues.
+
+Overall, we find that presidents promote economic integration and social development within Brazil that diverges from the environmental ones promoted outside of Brazil.
+They talk to the economic or social needs of the voters domestically, while boasting about environmentalism internationally.
+Sovereignty concerns, while closely tied to international politics, are more frequent inside the country.
+Two-level game theories cannot account for these variations.
+Rather, these results point to presidents as participants of transnational networks: they speak based on what they can expect of an audience given the context.
+
+# 5. Conclusion
+
+This paper investigates how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
+We have four main findings: first, the frequency of the Amazon as a general topic in speeches is driven by environmental related events that draw international attention.
+Socioeconomic politics in the region, contrarily, does not seem to draw attention or drive presidents to speak more.
+Second, we demonstrate how the same government adopts multiple problem-construction concurrently.
+The expectations of presidents about the audience of the speech, more than anything else, is the driver of variation of problem-construction.
+Third, and relatedly, we identify a long-term reduction trend of economic integration to a more balanced deployment of all problem-constructions.
+Finally, we demonstrate how domestic outcomes such as deforestation drive specific problem-constructions cunningly: they can be used to side-step problems to a specific audience.
+
+Overall, we interpret these results as evidence of presidents structuring and being structured by transnational networks.
+Conceptually, we believe a focus on problem-constructions in transnational settings complements sectoral studies of the Amazon, that focus on single domains of policy.
+Specifically, rather than assuming the Amazon represents an environmental problem, we start from the position that the region is a socio-economic-environmental policy object.
+Our analysis reveals how government perspectives are diverse and variation can be explained by the setting of speech and current policy outcomes.
+
+We see three broad avenues for future research.
+First, we have introduced a flexible framework and methods that ask when, where, and how questions about how policy objects are constructed.
+We expect to inspire some to investigate other policy objects in domains beyond the Brazilian Amazon (e.g.
+Cerrado Biome, Antarctic, Inequality, Criminality, etc.).
+Second, while we argue that presidential official discourse is important, the possibility of instant recordings and social media can change this in fundamental ways.
+We look forward to works that investigate how setting and audience interact with problem-construction in unofficial political communications.
+Finally, while we conceptualize the possibility of problem constructions having a direct effect on policy outcomes, our research design does not allow for such a test.
+It is possible, though, to design studies that test the causal relationship between presidential discourse and outcomes.
+In a forthcoming article, @ajzenman2020 propose an identification strategy that ties Bolsonaro's speech to covid-19 infections.
+We look forward to studies that identify how different problem constructions affect outcomes.
 
@@
 ````
-
-```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-ama_mx %>%
-  count(president, mx_cat, mx_cat2) %>%
-  group_by(president) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x = president, y = perc, fill = mx_cat,
-             label = scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat = "identity", position = "stack") +
-  geom_text(size = 2, position = position_stack(vjust = .5)) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
-       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme_am() +
-  theme(legend.position = "right")
-```
-
-In a speech, presidents might mix multiple problem-constructions within an Amazon statement.
-Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
-Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
-The most frequent mixed-type problem construction of the Amazon is economic conservation.
-This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
-This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
-The second most common mixed-type mixes social development and economic integration and appears, on average, in 5.4% of all statements.
-This is not surprising, as developing countries like Brazil repeatedly claim a "right to develop", when it comes to negotiating strong climate commitments and policies with a focus on both social development and economic integration.
-Nonetheless, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
-Furthermore, both Lula and Bolsonaro construct the Amazon as a multifaceted issue more frequently than other presidents.
-Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].

### 2023-01-30 Submission/Re-submission/draft/draft_resubmission.rmd
Updated location categories and added all mixed-types to both plots and regression as a separate, but encompassing, category

@@
                            "Rousseff", "Temer", "Bolsonaro"))
-# Prepare data for problem-constructions
-sov <- ama %>% 
-  filter(sov==1) %>% 
-  count(sov, year) %>%
-  group_by(year) %>%
-  select(-c(sov))%>%
-  rename (sov = n)
-ei <- ama %>% 
-  filter(ei==1) %>% 
-  count(ei, year) %>%
-  group_by(year) %>%
-  select(-c(ei))%>%
-  rename (ei = n) %>%
-  ungroup() %>%
-  tibble::add_row(year = 2017, ei = 0) %>%
-  tibble::add_row(year = 2018, ei = 0)
-sd <- ama %>% 
-  filter(sd==1) %>% 
-  count(sd, year) %>%
-  group_by(year) %>%
-  select(-c(sd))%>%
-  rename (sd = n)
-con <- ama %>% 
-  filter(con==1) %>% 
-  count(con, year) %>%
-  group_by(year) %>%
-  select(-c(con))%>%
-  rename (con = n)
-other <- ama %>% 
-  filter(other==1) %>% 
-  count(other, year) %>%
-  group_by(year) %>%
-  select(-c(other))%>%
-  rename (other = n)
-temp <- ei %>% 
-  left_join(other) %>% 
-  left_join(con) %>% 
-  left_join(sd) %>% 
-  left_join(sov) %>% 
-  replace(is.na(.), 0)
-# Get mixed types in
+
+# Get PC in
 ama_mx <-  ama %>%
   unite(mixed_type, sov:con, sep="_") %>%
-  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure National Sovereignty",
-                                   mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
-                                   mixed_type == '0_0_1_0' ~ "Pure Social Development",
-                                   mixed_type == '0_0_0_1' ~ "Pure Environmental Conservation",
-                                   mixed_type == '0_0_0_0' ~ "Other",
-                                   mixed_type == '0_1_0_1' ~ "Economic Conservation",
-                                   mixed_type == '0_1_1_0' ~ "Social Economic",
-                                   mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
-                                   mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
-                                   mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
-                                   mixed_type == '0_0_1_1' ~ "Social Conservation",
-                                   grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
-                                         mixed_type) ~ "Other Mixed-types"),
-         levels = c("Pure Economic Integration", "Pure Environmental Conservation",
+  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ 
+                                     "Pure National Sovereignty",
+                                   mixed_type == '0_1_0_0' ~ 
+                                     "Pure Economic Integration", 
+                                   mixed_type == '0_0_1_0' ~ 
                                      "Pure Social Development",
-                    "Pure National Sovereignty", "Other", "Economic Conservation", 
-                    "Social Economic", "Sovereign Conservation",
-                    "Economic, Social,\nand Conservation",
-                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
-         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Environmental Conservation|
-                                   |Pure Social Development|Pure National Sovereignty",
-                                   mx_cat) ~ "Pure-types",
-                             grepl("^Other$", mx_cat) ~ "Other",
-                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
-                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
-                                   |Social Conservation|Other Mixed-types",
-                                   mx_cat) ~ "Mixed-types"),
+                                   mixed_type == '0_0_0_1' ~ 
+                                     "Pure Environmental Conservation",
+                                   mixed_type == '0_0_0_0' ~ 
+                                     "Other",
+                                   TRUE ~ "Mixed-types"),
+         levels = c("Pure Economic Integration",
+                    "Pure Environmental Conservation",
+                    "Pure Social Development",
+                    "Pure National Sovereignty",
+                    "Other", "Mixed-types")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
@@
         peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
-        # py_1989=ifelse(grepl("1989", year), 1, 0),
-        # py_1992=ifelse(grepl("1992", year), 1, 0),
-        # py_2009=ifelse(grepl("2009", year), 1, 0),
-        # py_2015=ifelse(grepl("2015", year), 1, 0),
-        # py_2019=ifelse(grepl("2019", year), 1, 0),
-         location_cat = factor(location_cat,
+        location_cat = factor(case_when(location_cat == "International" ~ 
+                                          "Non Amazonian Countries",
+                                        location_cat == 
+                                          "Amazonian States" ~ 
+                                          "Amazonian States",
+                                        location_cat == "Amazonian Countries" ~ 
+                                          "Amazonian Countries",
+                                        TRUE ~ "Non Amazonian States"),
                               levels = c("Amazonian States",
                                          "Non Amazonian States",
-                                          "Brasilia",
                                          "Amazonian Countries",
-                                          "International")))
+                                         "Non Amazonian Countries")))
 
@@
          SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
-         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
+         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0),
+         mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
 ```
@@
 ## Count average words in Amazonian Statements
+## Need to use original text data
 # amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
@@
   scale_y_continuous(labels = percent_format()) + 
-  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1985, y = 0.165, label = "15.4%", size = 3.5)+
   annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
@@
 ```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-mmt1 <- ama_mx %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  count(mx_cat) %>%
-  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
-mmt2 <- ama_mx %>%
-  count(mx_cat)%>%
-  mutate(perc = n / sum(n)) # averages in relation to full sample
+summary(as.factor(ama_mx$mx_cat))
 ama_mx %>%
-  count(mx_cat, mx_cat2, year) %>%
+  count(mx_cat, year) %>%
   group_by(year) %>%
   mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat2 == "Pure-types") %>%
+  filter(mx_cat != "Other") %>%
   ggplot() +
@@
 
-Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
+<!-- Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
 Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
@@
 Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the averages of mixed-types constructions by presidents.
-
-```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-ama_mx %>%
-  count(president, mx_cat, mx_cat2) %>%
-  group_by(president) %>%
-  mutate(perc = n / sum(n)) %>%
-  filter(mx_cat2 == "Mixed-types") %>%
-  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
-  ggplot(aes(x = president, y = perc, fill = mx_cat,
-             label = scales::percent(perc, accuracy=.1))) +
-  geom_bar(stat = "identity", position = "stack") +
-  geom_text(size = 2, position = position_stack(vjust = .5)) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
-  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
-       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
-       caption = "") +
-  theme_am() +
-  theme(legend.position = "right")
-```
-
-Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation.
+Figure 4, below, displays the averages of mixed-types constructions by presidents.Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation.
 This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
@@
 Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
+-->
 
@@
                          model = "within", index = "president")
+c5 <- plm(mixed_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
 
-stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+stargazer::stargazer(c1, c2, c3, c4, c5, digits = 3, no.space = TRUE,
                      title = "Fixed-effects logistic regressions by president with controls",
@@
                       font.size="small",
-                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
-                                             "Social Development", "National Sovereignty", "Amazonian   Speech"),
-                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Deforestation", "Inflation", "Election Year", "High-profile Events"))
+                      dep.var.labels = c("Environmental Conservation",
+                                         "Economic Integration",
+                                         "Social Development",
+                                         "National Sovereignty",
+                                         "Mixed-types"),
+                     covariate.labels = c("Non Amazonian States",
+                                          "Amazonian Countries",
+                                          "Non Amazonian Countries",
+                                          "Deforestation",
+                                          "Inflation",
+                                          "Election Year",
+                                          "High-profile Events"))
 ```
@@
 ```{r setting vs outcome, fig.cap="Problem-constructions, settings, and policy outcomes", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-amazon_def_year <- amazon_def_year%>%
+amazon_def_year <- amazon_def_year %>%
   mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
@@
   filter(location_cat == "Amazonian States"|
-           location_cat == "International",
+           location_cat == "Non Amazonian Countries",
          mx_cat == "Pure Economic Integration"|

### 2023-01-31 Submission/Re-submission/draft/draft_resubmission.rmd
Updated text and plots to be consistent with new changes

@@
 
-## 3.1 Codebook (Amazonian historiography)
+## 3.1 Amazonian historiography
 
@@
 Within this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
-We argue a fourth separate one also exists: social development.
+Based on an inductive analysis of our empirical material, we argue that a fourth separate construction also exists: social development.
 The social development construction focuses on the constitutional rights and dignity of the inhabitants of the Amazonian region.
@@
 We code Amazonian statements in three steps.
-First, we develop a codebook for coding Amazonian problem-constructions identified with the Amazonian historiography (see appendix).
+First, we develop a codebook for coding Amazonian problem-constructions based on the Amazonian historiography (see Codebook in appendix).
 In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
@@
 
-To analyze our data, we model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable.
-This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, and (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
+To analyze our data, we first visualize when presidents speak more about the Amazon and how they construct the Amazon as a problem in time.
+We then model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable.
+This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
 We focus on single problem constructions to provide unambiguous interpretations and more robust findings.
-We divide settings in terms of non-Amazonian Brazilian states, Amazonian states within Brazil, Brasilia, Amazonian countries, and international.
+We divide settings in terms of non-Amazonian states, Amazonian states, Amazonian countries, and non-Amazonian countries.
 This level of aggregation refers to geo-political settings that make sense in light of the Amazon, as our policy object.
 This aggregation combines different expectations presidents can have about transnational audiences in each of these settings.
-Brasilia, specifically, is treated as a separate setting due to its unique location and since most presidential speeches are delivered there.
 The model controls for yearly deforestation rates, inflation, election years, and peak years for Amazon in presidential speeches.
@@
 Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question and the data at hand.
-Therefore, we are aware that a category as "international", for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences, which are not differentiated.
+Therefore, we are aware that a category as "non-Amazonain countries", for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences which are not differentiated.
 
@@
 Discourses capture general problem constructions that can be used to introduce, discuss, and/or justify policy and outcomes.
-Throughout the analysis we carefully discuss how presidential discourses relate to, for instance, deforestation rates and political outcomes by pointing at some of the patterns and correlations but without making any causal claims.
+Throughout the analysis we carefully discuss how presidential discourses could relate to certain outcomes by pointing at the patterns but without making causality claims.
 
@@
 Finally, and unfortunately, in 2022, environmental activist, Bruno Mendes, and British journalist, Dom Phillips, were murdered and buried in the Amazon (McCoy 2022).
+<!-- Discourses are also a response to political pressures; are not just problem-constructions but also a sort of justification... (Grazi's comment) -->
 
@@
 Although we observe variation in the frequency of the Amazon as a general topic, our conceptual framework foresees variation in specific problem-construction depending on a myriad of factors.
-In this subsection, we investigate how pure-types and mixed-types problem constructions evolved over time.The same president simultaneously constructs the Amazon as various problems, which unravels a less cohesive story than that told by the policy-cycle literature.
+In this subsection, we investigate how pure-types and mixed-types problem constructions evolved over time.
+The same president simultaneously constructs the Amazon as various problems, which unravels a less cohesive story than that told by the policy-cycle literature.
 Nevertheless, the overall balance between problem-constructions reveals longitudinal trends that speak to the importance of the environment, economy, social policy, and sovereignty.
-Figure 3, below, illustrates the share of each pure-type problem-constructions in time as these are the most common.
-
-Pure economic integration constructions were the most frequent from 1985 to 2009.
-This is especially pertinent during Cardoso's presidency (1995-2002), when economic integration was increasing while environmental conservation decreased.
-When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-While this correlates with strong environmental policies being adopted in 2004, economic integration still ranked first.
-It was only in 2010, with President Dilma, that environmental conservation and social development problem-constructions surpassed economic integration.
-Interestingly, there is a steady increase of sovereignty problem-constructions starting in 2008 already.
-This reversal was not long-standing, though.
-With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration increases to become the most favored construction.These trends reveal a multi-faceted relationship between problem-constructions, which we summarize in three findings.
+Figure 3, below, illustrates the share of each pure-type problem-constructions, along with the share of all mixed-types together, in time.
 
@@
 
-First, the same governments deploy contradictory constructions, but their relative frequencies reveal trends over time.
+Pure economic integration constructions were the most frequent from 1985 to 2009.
+This is especially pertinent during Cardoso's presidency (1995-2002), when economic integration was increasing while environmental conservation decreased.
+When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
+While this correlates with strong environmental policies being adopted in 2004, economic integration still ranked first.
+It was only in 2010, with President Dilma, that environmental conservation and social development problem-constructions surpassed economic integration.
+Interestingly, there is a steady increase of sovereignty problem-constructions starting in 2008 already.
+This reversal was not long-standing, though.
+With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration increases to become the most favored construction.
+
+The same governments deploy contradictory constructions, but their relative frequencies reveal trends over time.
 The 1988 Brazilian Constitution foresaw the strengthening of environmentalism through the participation of indigenous peoples and civil society in policy-making [@keck1998], which was slowly confirmed, at least discursively.
@@
 
-Second, the steady increase of sovereignty problem-constructions starting in 2008 offers context for the Presidency of Bolsonaro.
+The steady increase of sovereignty as salient problem-constructions starts in 2010, much before Bolsonaro was elected.
 The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government.
@@
 
-<!-- Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
+Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
 Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
-Constructing the Amazon as multiple issues averages at 18% of all constructions over time.
-Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence.
-Figure 4, below, displays the averages of mixed-types constructions by presidents.Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation.
-This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time.
-This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.Mixed-types are particular interesting considering both Lula and Bolsonaro, who construct the Amazon as a multifaceted issue more frequently than other presidents.
-Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].
--->
+Constructing the Amazon as multiple issues increases from 18%, in 1985, to 29%, in 2022, of all constructions.
+This general increase is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
+This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
 
@@
 By adapting transnational networks to discourse, we argue that presidents' expectations about transnational audiences in different settings explain variations in problem-constructions.
-To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run four logistic regressions, one for each pure-type construction as a dependent variable (see table 2 below).
+To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run five logistic regressions, one for each pure-type construction as a dependent variable and one for all mixed-type constructions (see table 2 below).
 Multiple, often contradictory, problem-constructions are forwarded across settings as presidents participate and shape transnational politics, confirming what our conceptual frameworks foresee.
-We discuss three main findings:
-
-First, when speaking to international audiences (be it in governmental summits, bilateral visits, or fora) presidents are between 54.6% and 56.1%[2] more likely to construct the Amazon as an issue of environmental conservation, in relations to when they speaking inside Amazonian states within Brazil (reference category).
-When speaking within Amazonian countries and Amazonian states, our models suggest that the likelihood of deploying environmental conservation decreases drastically.
-We interpret this as evidence that presidents construct the Amazon as an environmental problem outside Brazil, because of their views of transnational audiences as possible funders of domestic policy and projects.
-The Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Region Protected Areas Program by the World Bank and others; the 2008 Amazon Fund which provided over USD 1 billion; multiple Global Environment Facility grants; as well as multiple bilateral and philanthropic grants [@silva-muller2022].
-They realize material and symbolic gains (leverage politics) by making use of information that argues in favor of the Amazon as an environmental problem (information politics).
-
-Second, economic integration and social development are more likely inside the Amazon than in an international setting.
-Concurrent with the successful environmental policies from the early 2000s, financed by transnational monies, presidents also pursued a national agenda of economic integration or social development.
-For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-The special fiscal regime in Manaus, designed to increase industry presence in the region, was maintained.
-More roads and dams (e.g.
-BR-163 and Belo Monte) were constructed during the period.
-Presidents likely highlight these policies as they see Amazonian populations as voters to whom they are accountable.
-We argue that presidents expect voters' to have socio-economic interests, rather than environmental ones, and therefore construct the Amazon accordingly.
 
@@
 
-When it comes to sovereignty, model four also reveals that sovereignty seems to be a problem construction used more within the country than outside.
-Interestingly, while we found that the frequency of the Amazon as a general topic is driven by environmental-related events (section 4.1), presidents do not necessarily respond to them with environmental problem-constructions.
+On the one hand, when speaking at non-Amazonian countries (be it in governmental summits, bilateral visits, or fora), presidents are more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speaking within Amazonian states in Brazil (reference category).
+To a lesser extent, this also holds for when presidents speak in non-Amazonian states in Brazil.
+Alternatively, when speaking within Amazonian countries, the likelihood of deploying environmental conservation decreases drastically.
+We interpret this as evidence that presidents often construct the Amazon as an environmental problem outside of Amazonian states within Brazil, and of Amazonian neighboring countries, because of their views of transnational audiences as possible funders of domestic policy and projects.
+for instance, the Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Region Protected Areas Program by the World Bank and others; the 2008 Amazon Fund which provided over USD 1 billion; multiple Global Environment Facility grants; as well as multiple bilateral and philanthropic grants [@silva-muller2022].
+That is, they realize material and symbolic gains internationally, outside of Amazonian countries, by constructing the Amazon as an environmental problem.
+
+On the other hand, economic integration problem constructions are more likely to take place within Amazonian countries than within Amazonian states.
+Whereas social development constructions are less likely to take place within Amazonian countries and non-Amazonian countries.
+Concurrent with the successful environmental policies from the early 2000s, financed by transnational monies, presidents also pursued a national agenda of economic integration or social development.
+For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
+The special fiscal regime in Manaus, designed to increase industry presence in the region, was maintained.
+More roads and dams (e.g.
+BR-163 and Belo Monte) were constructed during the period.
+Presidents likely highlight these policies as they see Amazonian populations as voters to whom they are accountable.
+We argue that presidents expect voters' to have more immediate socio-economic interests, rather than environmental ones, and therefore construct the Amazon accordingly.
+
+Sovereignty problem constructions, interestingly, are more likely to take place when presidents speak at non-Amazonian states in Brazil or when relevant environmental-related events occur.
+While we found that the frequency of the Amazon as a general topic is driven by environmental-related events (section 4.1), presidents do not necessarily respond to them with specific problem-constructions.
 Rather, as such events bring strong international media coverage, Brazilian presidents match them with discursive attempts to highlight Brazil's sovereignty over the Amazonian territory.
-The 2019 August Fires are exemplary of these dynamics: in a series of responses directed to President Macron, Bolsonaro consistently highlighted Brazil's sovereignty in various speeches inside Brazil.
+
+Furthermore, constructions of the Amazon as a problem of economic integration increase as deforestation rates also increase; while constructions of the Amazon as a problem of environmental conservation increase as deforestation rates decrease.
+Although our models take settings and policy outcomes without differentiating for their different correlations as they vary in time, there is a complex relationship between problem constructions, settings, and time.
+For instance, figure 5, below, demonstrates that when deforestation rates decreased form 2004 to 2012, presidents preferred constructing the Amazon as an issue of environmental conservation both within Amazonian states and in non-Amazonian countries.
+As deforestation rates increased from 2012 to 2021, environmental conservation problem-construction remained steady within Amazonian states but decreased sharply in non-Amazonian countries.
+Alternatively, the positive relationship between economic integration problem constructions and deforestation rates from the model is driven by the same relationship within Amazonian states.
+When speaking at non-Amazonian countries, presidents are generally less likely to construct the Amazon as an issue of economic integration in time.
+In line with our framework, this suggests presidents boast positive policy outcomes whenever possible and wherever profitable by leveraging the aligned problem construction.
+Alternatively, presidents sidestep constructions whenever policy outcomes might be negative and wherever unlikely that the aligned problem-construction will be transformed in leverage.
 
@@
 
-Finally, while our models take settings and policy outcomes (deforestation rates) as cummulative, we use figure 5 to reveal a complex relationship between policy outcomes, problem constructions and settings.
-We focus on problem-constructions over time inside Amazonian States and in International settings for simplicity.
-Figure 5 demonstrates that when deforestation rates improved (2004-2012),presidents preferred deploying environmental conservation both inside the Amazon as well as outside Brazil.
-As they worsen(2012-2021), the environmental conservation problem-construction stays steady inside Brazil, but decreases strongly outside.
-In line with our framework, this suggests presidents boast good outcomes whenever possible by highlighting the aligned problem construction.
-When outcomes are bad, we see other problem constructions increasing instead, likely deployed as means of sidestepping issues.
-
-Overall, we find that presidents promote economic integration and social development within Brazil that diverges from the environmental ones promoted outside of Brazil.
-They talk to the economic or social needs of the voters domestically, while boasting about environmentalism internationally.
-Sovereignty concerns, while closely tied to international politics, are more frequent inside the country.
-Two-level game theories cannot account for these variations.
-Rather, these results point to presidents as participants of transnational networks: they speak based on what they can expect of an audience given the context.
+Overall, we find that presidents promote economic integration and social development within Brazil and neighboring Amazonian countries that diverges from the environmental one promoted non-Amazonian countries.
+That is, presidents might talk to the economic or social needs of the voters domestically, while boasting about environmentalism internationally.
+Presidents, as participants of transnational networks, speak based on what they can expect of an audience given the context.
 
@@
 We have four main findings: first, the frequency of the Amazon as a general topic in speeches is driven by environmental related events that draw international attention.
-Socioeconomic politics in the region, contrarily, does not seem to draw attention or drive presidents to speak more.
 Second, we demonstrate how the same government adopts multiple problem-construction concurrently.
@@
 Third, and relatedly, we identify a long-term reduction trend of economic integration to a more balanced deployment of all problem-constructions.
-Finally, we demonstrate how domestic outcomes such as deforestation drive specific problem-constructions cunningly: they can be used to side-step problems to a specific audience.
+Finally, we demonstrate how presidents promote economic integration and social development within Brazil and neighboring Amazonian countries that diverges from the environmental one promoted non-Amazonian countries.
 

### 2023-02-01 Submission/Re-submission/draft/draft_resubmission.rmd
all changes into markdown

@@
 
-*We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon's natural resources.
-We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem*.
-Each of these statements contains an implicit assumption of what needs to be solved, or in other words, it constructs the Amazon as a particular problem.
+> *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion.
+First of all, these NGOs should go plant trees in their own countries [...]" (President Lula, Cuiaba, 2007).*
+
+> *[...] It is essential that, when taking care of the environment, we do not overlook people: the Amazon region is home to more than 20 million inhabitants, including indigenous peoples and riverside dwellers [...]" (President Bolsonaro, New York City, 2022)*
+
+Each of the above statements contains an implicit or explicit assumption of what needs to be solved, or in other words, it constructs the Amazon as a particular problem.
 Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a view of the region, its people, and forest [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
@@
 
-In this article, we show how the Brazilian Amazon has been constructed as a problem transnationally in presidential discourses since 1985.
-Building on @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism, we offer a framework that ties discursive problem issue representations to relationships that transcend nation-states to identify and explain variation in problems-constructions.
-We shift the focus from governmental policy to discourse to capture a broader range of understandings for policy objects, problems that demand dedicated policy attention, that introduce, shape, and justify outcomes to broad audiences [@zarefsky2004; @gillion2016].
-Although problem-constructions take place in a series of instances, we analyze the case of official presidential discourses.
-The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil [@pinto2016].
-Working with presidential discourses also allows us to identify variations in how the Amazon is discursively constructed in transnational politics beyond environmental policies.
-Whereas understudied in the Amazonian context, presidential speeches legitimize perceptions about the Amazon that are key for policy adoption and implementation [see @alesina2009; @lopez2020].
+In this article, we show how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
+By adapting @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism (1998), we offer a framework that (1) explains transnational variation in problem-constructions as a function of speech setting and policies' outcomes, and (2) focuses on discourses rather than policies because they allow us to capture the diversity of ways policy goals are constructed to different audiences.
+
+Many analyses of Brazilian environmental policies approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
+Our framework and methodology identify and accounts for this variation.
+We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil's agricultural powerhouses, in a moment when deforestation is increasing, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
+Meanwhile, even President Bolsonaro at the United Nations General Assembly in New York City, spoke about protecting the Amazonian forests and its peoples.
+
+Our focus on presidential speeches affords us analytical leverage and it is crucial to understand policy.
+The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil (Pinto 2016).
+While presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the environment remains largely absent.
+Presidential speeches legitimize perceptions about the Amazon that are key for policy adoption and implementation [see @alesina2009; @lopez2020].
 This is especially pertinent for deforestation in the Amazon as expectations of local actors, generated from material and discursive governmental practices, are crucial in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021; @campbell2015].
-As crucial participants in transnational politics, presidents deploy different problem-constructions according to the transnational audiences they are speaking to.
-
-To investigate how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6240 official presidential speeches by all Brazilian presidents since 1985.
-Next, we identify all instances where presidents refer to the Amazon in their speeches.
-We develop a codebook grounded in Amazonian historiography to code how each of these statements constructs Amazon as a particular problem.
-With this codebook, we manually code a randomly selected training set of statements and use supervised machine-learning to label the remaining observations.
-We then conduct a descriptive analysis of when, where, and how presidents construct the Amazon as a problem.
 
 Our findings are threefold.
-First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international environmentally-related events.
-Second, we find that presidents are more likely to construct the Amazon as an issue of environmental conservation outside of the Amazon region, this is especially true when presidents speak internationally.
-Within the Amazon region, presidents tend to construct the Amazon as an issue of social development and economic integration.
-Third, the same government adopts a diverse range of problem-construction.
+First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international environmentally related events.
+Second, the same government adopts a diverse range of problem-construction.
 While the constructions of the Amazon as an issue of economic integration were more salient from 1985 to the mid-2000s, environmental conservation and social development problem-constructions steadily grew since the 2000s, temporarily surpassing economic integration as a more salient construction from 2010 to 2015.
 Constructing the Amazon as an issue of sovereignty steadily increased after 2010.
-This article provides the first comprehensive overview of when, where, and how the Amazon is constructed as problems in presidential speeches.
+Third, we find that presidents are more likely to construct the Amazon as an issue of environmental conservation when they speak at non-Amazonian countries outside of Brazil.
+Within the Amazon region and neighboring countries, presidents tend to construct the Amazon as an issue of social development and economic integration.
+This article provides the first comprehensive overview of when, how, and where the Amazon is constructed as problems in presidential speeches.
 
-# 2. Theory: problem-constructions, transnational settings, and presidential speeches
+# 2 Theory: problem-constructions, transnational settings, and presidential speeches
 
-## 2.1 Governments and problem-constructions
+## 2.1 Presidential speeches, policymaking, and problem-constructions
 
@@
 
+There is more variation within a specific government, though, than suggested by the policy-cycle approach[@bacchi1999].
+Political scientists have shown how governments have contradictory agrarian policies [@lopez2023], redistribution policies[@fairfield2017], health policies[@poncedeleon2021], and social policies[@niedzwiecki2017].
+We argue that the reason behind these monolithic representations of governments in literature about the Amazon by social scientists is conceptual.
+As a key biome in global climate-mitigation efforts, the Amazon has often been conceptualized within the logic of a global collective action effort to halt environmental problems.
+Many studies of the Brazilian Amazon contain an explicit, or implicit assumption, that the problem is of environmental nature.
+If the Amazon is thought of as an "environmental" problem, as is often the case in the literature, then it demands an "environmental" solution.
+Consequently, more frequently than not, studies focus on understanding environmental policies [@capobianco2019], the work of environmental NGOs [@silva-muller2022], or the rise of transnational partnerships [@andonova2022].
+We acknowledge the quality and importance of all these studies, but to build a comprehensive account of policies towards the region, we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
+
 We know, however, that there is more variation within a specific government policy, especially if we consider the Amazon a policy object demanding dedicated policy attention.
@@
 
-We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the Brazilian Amazon contain an explicit, or implicit assumption, of what the Amazon problem is.
 @bacchi2009 [p.
-10] posits that policies have a cultural dimension as they take "shape within specific historical and national or international contexts".
+2] places the question "what is the problem represented to be" in the center of policy studies .
+She argues that policies have a cultural dimension as they take "shape within specific historical and national or international contexts" @bacchi2009 [p.
+10].
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always explicitly stated in a policy, but policies are represented as solutions for both explicit and implicit problems.
-If the Amazon is represented as an "environmental" problem, as is often the case in the literature, then it demands an "environmental" solution.
-Consequently, studies focus on understanding environmental policies [@capobianco2019], the work of environmental NGOs [@silva-muller2022], or the rise of global environmental governance [@andonova2022].
-Alternatively, studies looking into the developments of social and fiscal policy in the region during the last decades are scarce [@acker2017].
-We acknowledge the quality and importance of all these studies.
-Still, we argue that it is crucial for scholars to study the Amazon as a biological, social, political, and geographical policy object.
-We conceptualize the Amazon as a policy object that demands dedicated policy attention of a specific nature.
-Hence, governments can highlight diverse explicit and implicit problems related to a policy object that need political attention.
-This is what we label as problem-constructions.
-<!-- Are we missing a transition from problem-constructions generally to the case of speeches?
--->
+The alleged problem is not always stated in a policy, but policies are represented as solutions for either explicit or implicit problems.
+Problem-representation matters for policy because it carries implications related to who is involved both in the root causes and in the solutions of the problem @bacchi2009.
+Following Bacchi, when speaking about a *policy object*, this is, a problem that demands dedicated policy attention, governments are either explicitly or implicitly constructing it as a problem of a certain kind.
+This is what we label as *problem-constructions*.\
+
+Presidential discourse is a good instance to identify problem-constructions over time.
+While the relationship between discourse and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
+This is particularly true in the Brazilian context where the executive branch of government, led by the president, have historically been the primary players in shaping public policy, especially after the 1988 constitution [@pinto2016].
+[more on presidents and their role in policies].
 
@@
 
-The possibility of different problem-constructions for the same policy object in political discourses, requires an explanation of why they would vary.
-On the one hand, @putnam1988 theory of two-level games in international negotiations can be adapted to explain variation in presidential speeches.
+The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary.
+Many analyses of Brazilian policies towards the Amazon approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
+By focusing on problem-constructions in presidential speeches, with an analytical strategy that distinguishes the location of the speech, we can move the empirical debate on the transnational nature of the Amazon forward.
+There are two main contenders for tying the problem-construction to international politics: Putnam's two-level game and Keck and Sikkink's transnational networks.
+
+@putnam1988 theory of two-level games in international negotiations can be adapted to explain variation in presidential speeches.
 @putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups.
@@
 
-On the other hand, @keck1998 theory of international politics as transnational networks, developed in the context of value-based advocacy groups, provides an alternative explanation for variation in problem-constructions.
+Putnam's theory of two-level games, though, is closer to a traditional view of policy, in which actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
+Relatedly, it views summits as the UNFCCC as a purely intergovernmental body and thus of international nature.
+Its contribution, then, is to propose a connection between the national and international spheres as avenues for state-actors only.
+While there is some evidence of two-level games at play, this view seems incompatible with both the possibility of contradictory policies and of varied problem-constructions, which is more aligned with a constructivist perspective of politics.
+Rather than seeing international politics as the domain of only nation states, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, spamming from the local level to the international level [@nye1971; @keck1998].
+In this context, international summits are considered a transnational setting, as the presence and participation of non-state actors constitutes them.
+
+@keck1998 theory of international politics as transnational networks, developed in the context of value-based advocacy groups, provides an alternative explanation for variation in problem-constructions.
 The authors reject the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
@@
 
+While their theory is developed in the context of value-based advocacy groups, the overall view of international politics as structured by actors and structuring actors, should hold as well for state actors as well.
 Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
-Presidents can, for example, engage in information politics by creating politically meaningful information and/or moving it where they believe it can have an impact [@keck1998, p.
+Transnational networks do not imply a consistent usage of problem-constructions across settings, as two-level games.
+That is, presidents construct problems and attempt to inform or leverage transnational audiences for symbolic or material gains according to their expectations of this audience.
+This indicates that how presidents construct policy objects as problems can vary, for instance, within the country ---speaking inside the Amazon versus outside--- because presidents identify these audiences as sources of different types of support.
+The same holds when speaking outside the country--- in Amazonian countries, non-Amazonian countries, and summits like Davos or UNFCCC--- where expectations and identities of audiences diverge completely from that of domestic actors.
+
+This variation depends on the tactics presidents choose.
+Presidents can engage in information politics by creating politically meaningful information and/or moving it where they believe it can have an impact [@keck1998, p.
 24].
-As well, presidents can engage in leverage politics by leveraging institutions to realize symbolic or material gains.
-Transnational networks do not assume a consistent common denominator of problem-constructions.
-That is, presidents construct problems and attempt to inform or leverage transnational audiences for symbolic or material gains according to their expectations of said audience.
-This indicates that how presidents construct policy objects as problems can vary within the country (i.e.
-speaking at diverse states or different associations) as well as when speaking internationally (i.e.
-during a climate conference or after a catastrophe).
-We call these levels in which there could be variation in how presidents construct a problem a setting.
-The setting is a level of aggregation that encompasses one, or multiple, audiences and makes sense concerning the policy object under study, in this case, the Amazon.
+In this regard, it is natural that presidents will always use policy adoption and outcomes in a cunning way, either to mask bad decisions or to boast successful ones.
+As well, presidents can engage in leverage politics by leveraging institutions to realize symbolic or material gains.  Material gains can be voters' support inside the Amazon or financial support in a UNFCCC Summit.
 
-## 2.3 Problem-constructions and policy
-
-In addition to the setting where the speech takes place, it is natural that outcomes in policy adoption and implementation can affect when and how presidents construct problems.
-@gillion2016 argues that there are two types of outcomes that can affect presidential discourses: institutional and societal.
-An institutional outcome relates to how presidential discourses can shape policy coalitions and the policy agenda.
-While the relationship between presidential speeches and policy may not be causal, they have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
-This is particularly true in the Brazilian context where the executive branch of government, led by the president, have historically been the primary players in shaping public policy, especially after the 1988 constitution [@pinto2016].
-
-A societal outcome, instead, relates to how discourse informs attitudes and behavior of people on the ground and affects policy outcomes.
-In the case of deforestation, for example, Amazonian scholars argue that the expectations of local actors generated from governments' decisions [@assuncao2015] and discourses [@capobianco2019; @capobianco2021; @campbell2015] are a crucial factor in choice to deforest on the ground.
-As presidents participate and shape transnational politics by constructing the Amazon as a certain issue, discourses define policy agendas, direct "political officials' at multiple stages of the public policy-making process" [@gillion2016, 19], influence people's decision on the ground, and justify previous decision or policy outcomes.
-
-Considering the possibility of varied problem-construction, the relationship between policy and discourse becomes endogenous and co-constituted: problem constructions in presidential speeches can justify past outcomes and/or lead to future outcomes.
-A bad track record in climate change policy outcomes can be justified with a good track record in energy security.
-This was, for example, the strategy adopted by President Bush during the Kyoto Protocol negotiations [@calderwood2020].
-As presidents participate in transnational networks, with malleable identities and goals, will refer to outcomes interchangeably, based on their expectations about the setting they are speaking at and the transnational audiences present.
-Policy outcomes, therefore, can be (re)constructed in presidential discourse in diverse forms to shape certain problem definitions and possible solutions.
+Our conceptual framework identifies problem-construction of the Brazilian Amazon in official presidential speeches and explains why and how it varies as a function of the setting where the speech takes place and policy outcomes.
+It advances the literature about the Amazon in two ways.
+First, we provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem constructions as the main dependent variable of our study.
+In so doing, we avoid assuming what type of problem it is and focus on how it has been represented.
+Second, by analytically distinguishing transnational settings, one of our main independent variables, we avoid a single focus on the Amazon as either a national or an international problem.
 
@@
 
-## 3.1 Amazonian historiography
+We start our research design by detailing how we operationalize the main variables of our theory.
+We then move to a section detailing our descriptive and inferential strategy.
+Along both sections, we explain the main limitations of our approach.
 
-To capture the cultural dimension and historical contexts behind problem constructions, we rely on the Amazonian historiography literature.
-We refer to Amazonian historiography as the body of research conducted by social and environmental scientists that tell the story of diverse governmental programs that studies the Amazon region, forest, and its people.
-Within this literature, we identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
-Based on an inductive analysis of our empirical material, we argue that a fourth separate construction also exists: social development.
+## 3.1 Data and operationalization strategy
+
+To identify problem-constructions in presidential speeches, we need a dataset containing all official presidential speeches by Brazilian presidents.
+We build upon @cezar2020 dataset, which contains all speeches from 1985 to 2019.
+We update the dataset by scraping and adding all official speeches from 2020 to 2022.
+The final dataset encompasses 6240 speeches, with their dates and speech location.
+We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
+We do so by detecting all speeches in which the stem "amazon" appears.
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
+We find that 968 speeches are, at least partially, about the Amazon.
+Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem "amazon" appears.
+We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
+This is how our unit of analysis, an Amazonian statements, are generated.
+This process yields 2048 unique Amazonian statements.
+On average, an Amazonian statement contains 131 words.
+
+### 3.1.1 Problem-construction in Amazonian Statements
+
+To test our conceptual framework, we need to operationalize our main dependent variable, these are the possible problem-constructions for a policy object.
+To identify and classify Amazonian speeches as specific types of problem constructions, we developed a codebook inductively and with assistance of the literature.
+We identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
+We argue a fourth separate one also exists: social development.
 The social development construction focuses on the constitutional rights and dignity of the inhabitants of the Amazonian region.
 
-### National Sovereignty
+#### National Sovereignty
 
@@
 
-### Economic Integration
+#### Economic Integration
 
@@
 
-### Environmental Conservation
+#### Environmental Conservation
 
@@
 This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-The environmental conservation problem-construction emphasizes that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination [@hochstetler2007].
+The environmental conservation problem-construction emphasizes that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination.
 The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
 
-### Social Development
+#### Social Development
 
@@
 
-## 3.2 Data and Operationalization
-
-To identify varied problem-constructions, we focus on presidential speeches.
-By focusing on presidential speeches, rather than specific policy domains, we analytically avoid hinging our analysis on an underlying assumption of what the problem is.
-Thus, we are not necessarily prioritizing an environmental, economic, or sovereignty-based view of the Amazon.
-We build upon @cezar2020 dataset, which contains all official speeches by Brazilian Presidents from 1985 to 2019.
-We update the dataset by scraping and adding all official speeches from 2020 to 2022.
-The final dataset encompasses 6240 speeches.
-We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 968 speeches are, at least partially, about the Amazon.
-Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
-This is how our unit of analysis, Amazonian statements, are generated.
-This process yields 2048 unique Amazonian statements about the Amazon.
-On average, an Amazonian statement contains 131 words.
-
-We code Amazonian statements in three steps.
-First, we develop a codebook for coding Amazonian problem-constructions based on the Amazonian historiography (see Codebook in appendix).
 In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
-However, an Amazonian statement can be coded as referring to multiple problem constructions (see Figure 1 below).
+However, an Amazonian statement can be coded as referring to multiple problem constructions (see Figure 1).
 Amazonian statements, thus, can be pure-type statements (i.e.
@@
 
-Second, with the codebook in hand, each one of the authors separately hand-coded 1024 randomly selected Amazonian statements.
+With the codebook in hand, each one of the authors separately hand-coded 1024 randomly selected Amazonian statements.
 This amount refers to 50% of all the Amazonian statements identified.
@@
 
-Third, the hand-coded data is randomly divided into a training set, containing 80% of the data (819 observations), and a validation set, containing the remaining 20% of the data (205 observations).
+Finally, the hand-coded data is randomly divided into a training set, containing 80% of the data (819 observations), and a validation set, containing the remaining 20% of the data (205 observations).
 We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier appropriate for binary categories, to label texts [@meyer2021; @noble2006].
@@
 Automating the coding of the remaining half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.
-The final dataset for analysis, excluding false positive matches, contains 1924 coded Amazonian statements.
+The final dataset for analysis, excluding false positive matches[^1], contains 1924 coded Amazonian statements.
 
-## 3.3 Analysis and Limitations
+[^1]: We also train the model to identify false positive matches in Amazonian statements.
+These are 124 Amazonian Statements that contain the stem "amazon", but are not necessarily meaningful as they might simply salute the governor of the Amazon, for example.
+We choose to remove these to reduce ambiguity and improve robustness of the findings.
 
-To analyze our data, we first visualize when presidents speak more about the Amazon and how they construct the Amazon as a problem in time.
-We then model the share of a specific pure problem-construction, as the dependent variable, relative to the settings in which a particular speech happens, as our independent variable.
-This means we predict the probability of a president constructing the Amazon as an issue of (1) environmental conservation, (2) economic integration, (3) social development, (4) national sovereignty, separately, and in relation to the remaining problem-constructions (see table 1 below).
-We focus on single problem constructions to provide unambiguous interpretations and more robust findings.
-We divide settings in terms of non-Amazonian states, Amazonian states, Amazonian countries, and non-Amazonian countries.
-This level of aggregation refers to geo-political settings that make sense in light of the Amazon, as our policy object.
-This aggregation combines different expectations presidents can have about transnational audiences in each of these settings.
-The model controls for yearly deforestation rates, inflation, election years, and peak years for Amazon in presidential speeches.
-
-````{=tex}
-\begin{landscape}
-
-```{r table 1, fig.cap="Models Description", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-
-## Count average words in Amazonian Statements
-## Need to use original text data
-# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
-# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
-## 131 on average
-
-## Comparison with inflation, criminality, unemployment, and inequality
-# pop %>%
-#   mutate(desigual = ifelse(grepl("desigual", text,
-#                                  ignore.case = TRUE), 1, 0),
-#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
-#                               text, ignore.case = TRUE), 1, 0),
-#          inf = ifelse(grepl("inflacao|inflaçao",
-#                              text, ignore.case = TRUE), 1, 0),
-#          unemploy = ifelse(grepl("desempreg",
-#                              text, ignore.case = TRUE), 1, 0)) %>%
-#   summarise(desigual = mean(desigual),
-#             crime = mean(crime),
-#             inf = mean(inf),
-#             unemploy = mean(unemploy))
-
-models <- tibble::tribble(~"", ~Description,
-                          "Model", "",
-                          "Fixed-effects logistic regressions indexed by the president", "The regression method allows to control for variables not measured (e.g.
-ideology) related to individuals (i.e.
-presidents) [see @allison2009].",
-                          "Dependent variables", "",
-                          "Problem constructions", "Pure environmental conservation; pure economic integration; pure social development; and pure national sovereignty.",
-                          "Independent variable", "",
-                          "Settings", "Setting where speech occurs as (1) non-Amazonian Brazilian states, (2) Brasilia, (3) Amazonian countries, and (4) international, in relation to the reference category of Amazonian states within Brazil.",
-                          "Control variables", "",
-                          "Deforestation rates", "Lagged yearly deforestation rates as a control for the possible relationship between deforestation rates and Amazonian problem-constructions.",
-                          "Election year", "Election years are controls for possible discursive changes related to the Amazon for these years.",
-                          "Inflation rate",  "Average yearly inflation rates as a control for a possible relationship between economic conditions/fluctuations and problem constructions.",
-                          "High-profile environmental event", "Years in which high-profile environmental events occurred control for the frequency and, possibly, how the Amazon was constructed as a problem in discourse for those years.")
-
-kbl(models, booktabs = T, caption = "Model description") %>%
-kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% row_spec(c(1,3,5,7), bold = TRUE, italic = TRUE)
-# see also: pack_rows("Model", 1, 2)
-# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
-```
-
-\end{landscape}
-````
-
-The main limitations of our approach are threefold.
-First, related to our subsetting and coding strategies, we classify statements as Amazonian based on a dictionary composed of a single lexicon stem: "amazon".
-We chose to do so knowing that a few speeches about the Amazon might not contain the lexicon "amazon", for example, when the president says, "the forest" or "deforestation".
-However, we consider this safer as we cannot be sure that mentions of the forest or deforestation do not correspond to other biomes such as the Cerrado or the Atlantic Forest.
-
-Second, our dataset covers only what is considered an official speech.
+One limitation of this approach is that our dataset covers only what is considered an official speech.
 Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
 Problem-construction within presidential discourse, thus, happens in different public, private, and online settings for which we do not account or differentiate in this paper.
-Furthermore, we aggregate levels to socio-political-cultural settings that make sense in light of the policy object in question and the data at hand.
-Therefore, we are aware that a category as "non-Amazonain countries", for instance, encompasses speeches delivered by presidents in a wide variety of countries, institutions, and venues to diverse audiences which are not differentiated.
 
-Third, as presidents participate and shape transnational politics, we assume that presidential discourse, policies, and outcomes are co-constitutive.
-Discourses capture general problem constructions that can be used to introduce, discuss, and/or justify policy and outcomes.
-Throughout the analysis we carefully discuss how presidential discourses could relate to certain outcomes by pointing at the patterns but without making causality claims.
+### 3.1.2 Operationalizing settings and policy outcomes
+
+Our explanation for variation in problem-constructions is based on first the setting of a speech and second the policy outcomes.
+
+#### Setting
+
+Presidents construct problems and attempt to inform or leverage audiences for symbolic or material gains according to their expectations of the speech audience.
+To operationalize the audience, we extract the location of the speech and create four distinct settings.
+We argue that each one of these settings encompasses an audience that presidents can have different expectations and views, given the Brazilian Amazon is our policy object.
+
+First, speeches can take place in Amazonian States inside Brazil.
+As a constituency with likely distinct demands than in other Brazilian states, presidents can try to communicate with them highlighting what presidents project their demands to be.
+Second, and consequently, Brazilian states outside the Amazon are another setting.
+In this case, as populations with some stake in the Amazon but not residing there, they might have different views of the Amazon.\
+
+The third setting encompasses speeches that take place in Amazonian Countries, these are other countries that also harbor the Amazon Rainforest (e.g.
+Peru, Colombia, Venezuela, etc.).
+We argue that in bilateral visits to Amazonian countries, presidents can view other countries as potential peers in pushing specific visions of the rainforest internationally.
+The last setting encompasses all speeches in non-Amazonian countries.
+This entails speeches that take place within multilateral mechanisms as the UNFCCC, international summits as the World Economic Forum, bilateral visits to the United States or France, and so on.
+We argue that in these contexts, presidents also deploy problem-constructions aligned with what presidents perceive as possible expected gains from international processes.
+
+While we would ideally control for the exact venue of the speech (multilateral mechanism, private fora, etc.), so we could have an even more precise identification of the audience, the location information of the speeches does not allow so.
+Nevertheless, we believe these four settings and their different audiences are already enough to demonstrate whether and how problem-construction indeed changes.
+
+#### Policy outcome
+
+We also expect presidents to have a cunning usage of policy outcomes.
+If outcomes are good, we argue that presidents will deploy aligned problem constructions to boast policy.
+If outcomes are bad, we argue presidents will mask them by highlighting a contradictory problem construction.
+We operationalize policy outcomes by using the yearly deforestation rates provided by INPE.
+We consider this a good option, as national and international actors do react to deforestation rates.
+In the late 1980s, for instance, there was strong media coverage in the USA of forest fires and deforestation figures.
+Similarly, in 2019, world press covered the August fires.
+We opt for lagging deforestation rates one year, as the consolidated numbers for 2007, for example, are published in 2008.
+
+Many scholars inquire and find causal relationships between discourse and policy outcomes.
+While our research design and data does not allow us to test so, we do make arguments that might suggest a direction in certain parts....[further develop this limitation]
+
+## 3.2 Data Analysis: descriptive and inferential methods
+
+As a dataset like this was never constructed before, we start with longitudinal descriptive statistics, which can reveal interesting trends.
+First, we identify years in which Amazon as a general topic has been discussed more frequently than others and possible drivers.
+To do so, we take the share of yearly speeches that mention Amazon independently of the specific problem construction.
+Next, we discuss the evolution of yearly problem-constructions in time by showing our data longitudinally.We conclude with four separate fixed-effect logistic regression models that predict the probability of each problem-construction relative to the setting in which a speech takes place and the policy outcome.
+
+The dependent variable of each model is the share of one pure-type problem construction against all other three problem constructions.
+We use four separate logistic regressions to provide unambiguous interpretations and comparisons, as a multinomial model would entail four categories on both dependent and independent variables.
+We include presidential fixed effects because we can expect individual-specific characteristics (i.e.
+presidential ideology) to have an effect on the outcome.
+If the president's political ideology is a good predictor of pure-type variation, it could indicate that the president is rather isolated from settings and that they can follow their own worldviews[^2].
+Fixed-effects control for this issue[@allison2009fixed], and other unit-unvarying characteristics.
+Our main explanatory variables, setting and policy outcomes, are included as described in section 3.1.2.  We add a third variable, which takes the value of 1 if the saliency of the Amazon as a general topic was above average that year.
+We do so to test peaks in the Amazon as a general topic driving any particular problem-construction.
+Finally, we add two standard controls: yearly inflation rate (numerical) and election year (dummy).
+
+[^2]: We would like to thank Reviewer#2 for this suggestion.
 
@@
 This suggests the Amazon is a topic of relative high importance for presidents generally.
-However, five local maxima are above average[^1] in the figure:1989, 1992, 2009, 2019, and 2022.
+However, five local maxima are above average[^3] in the figure:1989, 1992, 2009, 2019, and 2022.
 All of them coincide with environmentally related events that received wide coverage from international media.
 
-[^1]: We consider the years in which the Amazon appeared in over 20% of all official speeches.
+[^3]: We consider the years in which the Amazon appeared in over 20% of all official speeches.
 
@@
 
+```{r Repository, eval=FALSE, include=FALSE}
+## Count average words in Amazonian Statements
+## Need to use original text data
+# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
+# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
+## 131 on average
+
+## Comparison with inflation, criminality, unemployment, and inequality
+# pop %>%
+#   mutate(desigual = ifelse(grepl("desigual", text,
+#                                  ignore.case = TRUE), 1, 0),
+#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
+#                               text, ignore.case = TRUE), 1, 0),
+#          inf = ifelse(grepl("inflacao|inflaçao",
+#                              text, ignore.case = TRUE), 1, 0),
+#          unemploy = ifelse(grepl("desempreg",
+#                              text, ignore.case = TRUE), 1, 0)) %>%
+#   summarise(desigual = mean(desigual),
+#             crime = mean(crime),
+#             inf = mean(inf),
+#             unemploy = mean(unemploy))
+
+```
+
 In 1989 the Amazon appeared in 32% of all speeches.
@@
 Finally, and unfortunately, in 2022, environmental activist, Bruno Mendes, and British journalist, Dom Phillips, were murdered and buried in the Amazon (McCoy 2022).
-<!-- Discourses are also a response to political pressures; are not just problem-constructions but also a sort of justification... (Grazi's comment) -->
+<!-- Discourses are also a response to political pressures; are not just problem-constructions but also a sort of justification...
+(Grazi's comment) -->
 
@@
 ```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-summary(as.factor(ama_mx$mx_cat))
+#summary(as.factor(ama_mx$mx_cat))
 ama_mx %>%
@@
 
-# model 3
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
@@
                          model = "within", index = "president")
-c5 <- plm(mixed_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
-                         data = ama_model_lag,
-                         model = "within", index = "president")
 
-stargazer::stargazer(c1, c2, c3, c4, c5, digits = 3, no.space = TRUE,
+stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                      title = "Fixed-effects logistic regressions by president with controls",
@@
                                          "Social Development",
-                                         "National Sovereignty",
-                                         "Mixed-types"),
+                                         "National Sovereignty"),
                      covariate.labels = c("Non Amazonian States",

### 2023-02-01 Submission/Re-submission/draft/model_table.Rmd
all changes into markdown

---
title: "Model Table"
author: "Livio Silva-Muller"
date: "2023-02-01"
output: html_document
---

````{=tex}
\begin{landscape}

```{r table 1, fig.cap="Models Description", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}

models <- tibble::tribble(~"", ~Description,
                          "Model", "",
                          "Fixed-effects logistic regressions indexed by the president", "The regression method allows to control for variables not measured (e.g. ideology) related to individuals (i.e. presidents) [see @allison2009].",
                          "Dependent variables", "",
                          "Problem constructions", "Pure environmental conservation; pure economic integration; pure social development; and pure national sovereignty.",
                          "Independent variable", "",
                          "Settings", "Setting where speech occurs as (1) non-Amazonian Brazilian states, (2) Brasilia, (3) Amazonian countries, and (4) international, in relation to the reference category of Amazonian states within Brazil.",
                          "Control variables", "",
                          "Deforestation rates", "Lagged yearly deforestation rates as a control for the possible relationship between deforestation rates and Amazonian problem-constructions.",
                          "Election year", "Election years are controls for possible discursive changes related to the Amazon for these years.",
                          "Inflation rate",  "Average yearly inflation rates as a control for a possible relationship between economic conditions/fluctuations and problem constructions.",
                          "High-profile environmental event", "Years in which high-profile environmental events occurred control for the frequency and, possibly, how the Amazon was constructed as a problem in discourse for those years.")

kbl(models, booktabs = T, caption = "Model description") %>%
kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% row_spec(c(1,3,5,7), bold = TRUE, italic = TRUE)

```

\end{landscape}
````

### 2023-02-03 Submission/Re-submission/draft/draft_resubmission.rmd
new text

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: 27 January 2023
+date: 2 February 2023
 output:
@@
 > *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion.
-First of all, these NGOs should go plant trees in their own countries [...]" (President Lula, Cuiaba, 2007).*
+First of all, these NGOs should go plant trees in their own countries [...]"
+(President Lula, Cuiaba, 2007).*
 
-> *[...] It is essential that, when taking care of the environment, we do not overlook people: the Amazon region is home to more than 20 million inhabitants, including indigenous peoples and riverside dwellers [...]" (President Bolsonaro, New York City, 2022)*
+> *[...] It is essential that, when taking care of the environment, we do not overlook people: the Amazon region is home to more than 20 million inhabitants, including indigenous peoples and riverside dwellers [...]"
+(President Bolsonaro, New York City, 2022)*
 
@@
 Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a view of the region, its people, and forest [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship (1964-85) is, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010) presidencies are often tied to environmental conservation.
-Yet, such monolithic representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
+While the military dictatorship (1964-85) and Bolsonaro's presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010) presidencies are often tied to environmental conservation.
+Yet, such  representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
 
 In this article, we show how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
-By adapting @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism (1998), we offer a framework that (1) explains transnational variation in problem-constructions as a function of speech setting and policies' outcomes, and (2) focuses on discourses rather than policies because they allow us to capture the diversity of ways policy goals are constructed to different audiences.
+By combining @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism (1998), we offer a framework that (1) explains transnational variation in problem-constructions depending on speech setting and policies' outcomes, and (2) focuses on discourses rather than policies because they allow us to capture the diversity of ways policy goals are constructed to different audiences.
 
-Many analyses of Brazilian environmental policies approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
+Many analyses of Brazilian environmental policies approach it as a national or an international environmental problem, without a discussion of how important national actors behave differently in both scenarios.
 Our framework and methodology identify and accounts for this variation.
@@
 Our focus on presidential speeches affords us analytical leverage and it is crucial to understand policy.
-The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil (Pinto 2016).
-While presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the environment remains largely absent.
+The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil(Pinto 2016).
+While presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the Amazon forest and its peoples remains largely absent.
 Presidential speeches legitimize perceptions about the Amazon that are key for policy adoption and implementation [see @alesina2009; @lopez2020].
@@
 Our findings are threefold.
-First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international environmentally related events.
-Second, the same government adopts a diverse range of problem-construction.
-While the constructions of the Amazon as an issue of economic integration were more salient from 1985 to the mid-2000s, environmental conservation and social development problem-constructions steadily grew since the 2000s, temporarily surpassing economic integration as a more salient construction from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty steadily increased after 2010.
-Third, we find that presidents are more likely to construct the Amazon as an issue of environmental conservation when they speak at non-Amazonian countries outside of Brazil.
+First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international coverage of environmentally related events.
+Second, while the same government adopts a diverse range of problem-construction, we identify a process of convergence:  the constructions of the Amazon as an issue of economic integration were more salient from 1985 to the mid-2000s, but environmental conservation and social development problem-constructions steadily grew to temporarily surpass economic integration as from 2010 to 2015.
+Constructing the Amazon as an issue of sovereignty steadily increased after 2008, to the extent that all problem-constructions converge to being deployed in a balanced way after 2015.
+Third, we find a cumulative effect between speech setting and policy outcome.
+Presidents are more likely to construct the Amazon as an issue of environmental conservation when they speak at non-Amazonian countries outside of Brazil and deforestation figures are positive.
 Within the Amazon region and neighboring countries, presidents tend to construct the Amazon as an issue of social development and economic integration.
-This article provides the first comprehensive overview of when, how, and where the Amazon is constructed as problems in presidential speeches.
+When deforestation figures are negative, presidents tend to side-step environmental conservation.
+Overall...
 
 # 2 Theory: problem-constructions, transnational settings, and presidential speeches
+
+We divide our theoretical framework in two parts.
+We start with an explanation of what are problem-constructions, our dependent variable at large, and why presidential discourse are an interesting instance to identify them.
+Next, we argue that problem-constructions can vary depending on the transnational setting of the speech and on how good policy outcomes are in the moment of speech, our main independent variables.
 
@@
 
-We know, however, that there is more variation within a specific government policy, especially if we consider the Amazon a policy object demanding dedicated policy attention.
-For instance, while many argue that environmental activism in Brazil emerged despite the military dictatorship [@hochstetler2000; @wood1993], @rajao2021 demonstrates how the strengthening of the Forest Code in 1964 was also a military priority.
-Furthermore, a substantial part of Lula's administration (2003-2010) effectiveness in reducing deforestation in the Amazon was achieved because of deforestation leakage to other biomes (Garret, 2022).
-At the same time, Lula's administration (2003-2010) provided record high subsidies to the expansion of agriculture in Brazil [@capobianco2021].
-That is, we must look at the Amazon beyond the environmental domain as a forest, region, and peoples.
-
 @bacchi2009 [p.
@@
 
+ Many analyses of Brazilian policies towards the Amazon approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
 The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary.
-Many analyses of Brazilian policies towards the Amazon approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
 By focusing on problem-constructions in presidential speeches, with an analytical strategy that distinguishes the location of the speech, we can move the empirical debate on the transnational nature of the Amazon forward.
@@
 
-To test our conceptual framework, we need to operationalize our main dependent variable, these are the possible problem-constructions for a policy object.
+To test our conceptual framework, we need to operationalize our main dependent variable, the possible problem-constructions for a policy object.
 To identify and classify Amazonian speeches as specific types of problem constructions, we developed a codebook inductively and with assistance of the literature.
@@
 
-Our explanation for variation in problem-constructions is based on first the setting of a speech and second the policy outcomes.
+Our explanation for variation in problem-constructions is based on first the setting of a speech and second the policy outcomes. This comprise, at large, our main independent variables.
 
@@
 Second, and consequently, Brazilian states outside the Amazon are another setting.
-In this case, as populations with some stake in the Amazon but not residing there, they might have different views of the Amazon.\
+In this case, as populations with some stake in the Amazon but not residing there, they might have different views of the Amazon.
 
@@
 While we would ideally control for the exact venue of the speech (multilateral mechanism, private fora, etc.), so we could have an even more precise identification of the audience, the location information of the speeches does not allow so.
-Nevertheless, we believe these four settings and their different audiences are already enough to demonstrate whether and how problem-construction indeed changes.
+Nevertheless, we believe these four settings and their different audiences are already enough to demonstrate whether and how problem-construction indeed changes transnationally.
 
@@
 Many scholars inquire and find causal relationships between discourse and policy outcomes.
-While our research design and data does not allow us to test so, we do make arguments that might suggest a direction in certain parts....[further develop this limitation]
+Our research design and data does not allow us to test so.
+While we might suggest a particular direction in certain cases, none of our claims are linearly causal.
 
@@
 
-As a dataset like this was never constructed before, we start with longitudinal descriptive statistics, which can reveal interesting trends.
-First, we identify years in which Amazon as a general topic has been discussed more frequently than others and possible drivers.
+As a dataset like this was never constructed before, we start with longitudinal descriptive statistics, which  reveals interesting trends.
+First, we identify years in which Amazon as a general topic has been discussed more frequently and possible drivers.
 To do so, we take the share of yearly speeches that mention Amazon independently of the specific problem construction.
@@
 Fixed-effects control for this issue[@allison2009fixed], and other unit-unvarying characteristics.
-Our main explanatory variables, setting and policy outcomes, are included as described in section 3.1.2.  We add a third variable, which takes the value of 1 if the saliency of the Amazon as a general topic was above average that year.
+Our main explanatory variables, setting and policy outcomes, are included as described in section 3.1.2.
+We add a third variable, which takes the value of 1 if the salience of the Amazon as a general topic was above average that year.
 We do so to test peaks in the Amazon as a general topic driving any particular problem-construction.
@@
          mx_cat == "Pure Economic Integration"|
-           mx_cat == "Pure Environmental Conservation") %>%
+           mx_cat == "Pure Environmental Conservation"|
+           mx_cat == "Pure Social Development"|
+           mx_cat == "Pure National Sovereignty") %>%
   ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc, color=mx_cat),
+  geom_smooth(aes(x=as.numeric(year), y = perc, color=location_cat),
               se = FALSE, linewidth =0.75, linetype="solid") +
   scale_y_continuous(labels = percent_format(accuracy = 1))+
-  facet_wrap(~location_cat+mx_cat)+
+  facet_wrap(~mx_cat)+
   labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",

### 2023-02-03 Submission/Re-submission/draft/draft_resubmission.rmd
added new model and reorganized variables

@@
                               levels = c("Amazonian States",
+                                         "Amazonian Countries",
                                          "Non Amazonian States",
-                                         "Amazonian Countries",
                                          "Non Amazonian Countries")))
@@
          mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
+
+ama_model2_lag <- dplyr::select(pop, -text) %>%
+  dplyr::left_join(amazon_def_year, by = "year") %>%
+  dplyr::left_join(AAI, by = "year") %>%
+  filter(location_cat != "Non Identified")%>%
+  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat),
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries",
+                                      location_cat),
+                               levels = c("Amazonian States",
+                                          "Amazonian Countries",
+                                          "International", "Brasilia",
+                                          "Non Amazonian States")),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+                                      year), 1, 0),
+        location_cat = factor(case_when(location_cat == "International" ~ 
+                                          "Non Amazonian Countries",
+                                        location_cat == 
+                                          "Amazonian States" ~ 
+                                          "Amazonian States",
+                                        location_cat == "Amazonian Countries" ~ 
+                                          "Amazonian Countries",
+                                        TRUE ~ "Non Amazonian States"),
+                              levels = c("Amazonian States",
+                                         "Amazonian Countries",
+                                         "Non Amazonian States",
+                                         "Non Amazonian Countries")))
 ```
@@
                          model = "within", index = "president")
+c5 <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + AAI + election_year,
+                         data = ama_model2_lag,
+                         model = "within", index = "president")
 
-stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                      title = "Fixed-effects logistic regressions by president with controls",
-                      column.sep.width = ".001pt",
+                      column.sep.width = "-12pt",
                       font.size="small",
-                      dep.var.labels = c("Environmental Conservation",
+                      dep.var.labels = c("Amazon Speech",
+                                          "Environmental Conservation",
                                          "Economic Integration",
@@
                                          "National Sovereignty"),
-                     covariate.labels = c("Non Amazonian States",
-                                          "Amazonian Countries",
+                     covariate.labels = c("Amazonian Countries",
+                                          "Non Amazonian States",
                                           "Non Amazonian Countries",

### 2023-02-06 Submission/Re-submission/draft/draft_resubmission.rmd
Added unmeplayoment rate data

@@
                            "Rousseff", "Temer", "Bolsonaro"))
+urate <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/urate.Rds")
 
@@
 
-ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
+ama_model_lag <- dplyr::left_join(ama_mx,
+                                  amazon_def_year_lag, by = "year") %>%
   dplyr::left_join(AAI, by = "year") %>%
+  dplyr::left_join(urate, by = "year") %>%
   filter(location_cat != "Non Identified") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation",
+                             1, 0),
          EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
@@
   dplyr::left_join(AAI, by = "year") %>%
+  dplyr::left_join(urate, by = "year") %>%
   filter(location_cat != "Non Identified")%>%
@@
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + UR + election_year + peak_year,
                          data = ama_model_lag,
@@
 c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + UR + election_year + peak_year,
                          data = ama_model_lag,
@@
 c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + UR + election_year + peak_year,
                          data = ama_model_lag,
@@
 c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + UR + election_year + peak_year,
                          data = ama_model_lag,
@@
 c5 <- plm(amazon_speech ~ as.factor(location_cat) +
-                         def_year + AAI + election_year,
+                         def_year + AAI + UR + election_year,
                          data = ama_model2_lag,
@@
                                           "Inflation",
+                                          "Unemployment rate",
                                           "Election Year",

### 2023-02-06 messy_files/unemployment_rate_pnad.R

@@ -1,0 +1,21 @@
+# Source: https://www.scielo.br/j/ee/a/YQcXMRc5xjPBgPHZztrnKDj/?lang=pt
+# PNAD reconstructed data
+# Source: https://painel.ibge.gov.br/pnadc/
+# From 2012 onwards available
+unemployment_rate_pnad <- data.frame(year = c(1985, 1986, 1987, 1988, 1989,
+                                              1990, 1991, 1992, 1993, 1994,
+                                              1995, 1996, 1997, 1998, 1999,
+                                              2000, 2001, 2002, 2003, 2004,
+                                              2005, 2006, 2007, 2008, 2009,
+                                              2010, 2011, 2012, 2013, 2014,
+                                              2015, 2016, 2017, 2018, 2019,
+                                              2020, 2021, 2022),
+                                     UR = c(5.61, 4.60, 4.81, 5.29, 4.82,
+                                            5.13, 5.94, 7.16, 7.06, 6.93,
+                                            6.77, 7.51, 8.02, 9.24, 9.84,
+                                            9.38, 9.46, 9.82, 10.42, 10.42,
+                                            10.02, 9.58, 9.14, 8.46, 9.09,
+                                            8.19, 7.52, 7.3, 7.1, 6.8,
+                                            8.5, 11.5, 13.4, 12.8, 12.4,
+                                            13.1, 14.7, 9.8))
+saveRDS(unemployment_rate_pnad, "urate.Rds")

### 2023-02-07 Submission/Re-submission/draft/draft_resubmission.rmd
new data

--- 2023-02-03 Submission/Re-submission/draft/draft_resubmission.rmd
@@
 library(dplyr)
+library(readr)
 library(tidyr)
@@
 ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
-AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
 location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
@@
 amazon_def_year_lag <- amazon_def_year
+other_variables <- read_csv("~/Documents/GitHub/amazondef/Replication_Files/other_variables.csv")
 # missing years are missed with first non missing value
@@
                            "Rousseff", "Temer", "Bolsonaro"))
-
 # Get PC in
@@
                               levels = c("Amazonian States",
+                                         "Amazonian Countries",
                                          "Non Amazonian States",
-                                         "Amazonian Countries",
                                          "Non Amazonian Countries")))
 
-ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
-dplyr::left_join(AAI, by = "year") %>%
+ama_model_lag <- dplyr::left_join(ama_mx,
+                                  amazon_def_year_lag, by = "year") %>%
+  dplyr::left_join(other_variables, by = "year") %>%
   filter(location_cat != "Non Identified") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation",
+                             1, 0),
          EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
@@
          mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
+
+ama_model2_lag <- dplyr::select(pop, -text) %>%
+  dplyr::left_join(amazon_def_year, by = "year") %>%
+  dplyr::left_join(other_variables, by = "year") %>%
+  filter(location_cat != "Non Identified")%>%
+  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
+         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
+                               "International", location_cat),
+         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+                                            location), "Amazonian Countries",
+                                      location_cat),
+                               levels = c("Amazonian States",
+                                          "Amazonian Countries",
+                                          "International", "Brasilia",
+                                          "Non Amazonian States")),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+                                      year), 1, 0),
+        location_cat = factor(case_when(location_cat == "International" ~ 
+                                          "Non Amazonian Countries",
+                                        location_cat == 
+                                          "Amazonian States" ~ 
+                                          "Amazonian States",
+                                        location_cat == "Amazonian Countries" ~ 
+                                          "Amazonian Countries",
+                                        TRUE ~ "Non Amazonian States"),
+                              levels = c("Amazonian States",
+                                         "Amazonian Countries",
+                                         "Non Amazonian States",
+                                         "Non Amazonian Countries")))
 ```
@@
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation+  election_year,
                          data = ama_model_lag,
@@
 c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation +  election_year,
                          data = ama_model_lag,
@@
 c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation+ election_year,
                          data = ama_model_lag,
@@
 c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation +  election_year,
                          data = ama_model_lag,
                          model = "within", index = "president")
+c5 <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + inflation+  election_year,
+                         data = ama_model2_lag,
+                         model = "within", index = "president")
 
-stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
+stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                      title = "Fixed-effects logistic regressions by president with controls",
-                      column.sep.width = ".001pt",
+                      column.sep.width = "-12pt",
                       font.size="small",
-                      dep.var.labels = c("Environmental Conservation",
+                      dep.var.labels = c("Amazon Speech",
+                                          "Environmental Conservation",
                                          "Economic Integration",
@@
                                           "Inflation",
-                                          "Election Year",
-                                          "High-profile Events"))
+                                          "Election Year"))
 ```

### 2023-02-08 Submission/Re-submission/draft/draft_resubmission.rmd
aai instead of inflation

--- 2023-02-03 Submission/Re-submission/draft/draft_resubmission.rmd
@@
 amazon_def_year_lag <- amazon_def_year
+other_variables <- read_csv("~/Documents/GitHub/amazondef/Replication_Files/other_variables.csv")
+aai <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/AAI.Rds")
 # missing years are missed with first non missing value
@@
 
-ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
-dplyr::left_join(AAI, by = "year") %>%
+ama_model_lag <- dplyr::left_join(ama_mx,
+                                  amazon_def_year_lag, by = "year") %>%
+  dplyr::left_join(other_variables, by = "year") %>%
+      dplyr::left_join(aai, by = "year") %>%
   filter(location_cat != "Non Identified") %>%
-  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
+  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation",
+                             1, 0),
          EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
@@
   dplyr::left_join(amazon_def_year, by = "year") %>%
-  dplyr::left_join(AAI, by = "year") %>%
+    dplyr::left_join(aai, by = "year") %>%
+  dplyr::left_join(other_variables, by = "year") %>%
   filter(location_cat != "Non Identified")%>%
@@
                                       year), 1, 0),
+         peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
         location_cat = factor(case_when(location_cat == "International" ~ 
@@
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation+  election_year+ peak_year,
                          data = ama_model_lag,
@@
 c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation +  election_year+ peak_year,
                          data = ama_model_lag,
@@
 c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation+ election_year+ peak_year,
                          data = ama_model_lag,
@@
 c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + inflation +  election_year+ peak_year,
                          data = ama_model_lag,
@@
 c5 <- plm(amazon_speech ~ as.factor(location_cat) +
-                         def_year + AAI + election_year,
+                         def_year + inflation+  election_year,
                          data = ama_model2_lag,

### 2023-02-08 Submission/Re-submission/draft/draft_resubmission.rmd
Updated models and variables by adding missing years and scaling

--- 2023-02-07 Submission/Re-submission/draft/draft_resubmission.rmd
@@
 ```{r data, message=FALSE, warning=FALSE, include=FALSE}
-# Load data
+# Load data complete
 pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
+# Load coded data on Amazonian statements and remove extra variables
 ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
-ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
-location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
-  select(-location_cat) %>%
-  distinct()
-ama <- left_join(ama, location_km, by = "location")
-amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
-amazon_def_year_lag <- amazon_def_year
-other_variables <- read_csv("~/Documents/GitHub/amazondef/Replication_Files/other_variables.csv")
-# missing years are missed with first non missing value
-adr <- data.frame(year = c(1985, 1986, 1987), 
-                  def_year = c(21.050, 21.050, 21.050))
-amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
+ama <- ama %>%
+  select(-c(title, date, text, false_positives)) %>%
+  rename (ei= "EI", sd= "SD")
+# Load annual deforestation rates data, lag years, and fill data
+amazon_def_year_lag <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
 amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
+# Fill missing years are missed with first non missing value.
+# This is also consistent with def. rates from literature
 adr <- data.frame(year = c(1985, 1986, 1987, 1988),
@@
 amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data
-hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
-                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
-                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
-                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
-                           "Rousseff", "Temer", "Bolsonaro"))
-# Get PC in
+amazon_def_year_lag$def_year <- scales::rescale(amazon_def_year_lag$def_year) # scale def. rates
+# Load inflation data, annual
+aai <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/AAI.Rds")
+aai_2022 <- data.frame("year" = 2022, "AAI" = 5.79) # Add 2022 rates
+aai <- rbind(aai_2022, aai)
+aai$AAI <- scales::rescale(aai$AAI) # scale annual inflation
+# Code PCs as categories
 ama_mx <-  ama %>%
@@
                                       year), 1, 0),
-        peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
+        peak_year = ifelse(grepl("1989|1992|2009|2019", year), 1, 0),
         location_cat = factor(case_when(location_cat == "International" ~ 
@@
                                          "Non Amazonian Countries")))
-
+# Get peak years in Amazon speeches, as a control for modelling
+mean_perc <- pop %>%
+  count(amazon_speech, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(amazon_speech == 1) %>%
+  select(c(year, perc))
+mean_perc[mean_perc$perc > mean(mean_perc$perc) + sd(mean_perc$perc),] # 89, 92, 09, 19
+# Create/wrangle data for modelling PCs
 ama_model_lag <- dplyr::left_join(ama_mx,
                                   amazon_def_year_lag, by = "year") %>%
-  dplyr::left_join(other_variables, by = "year") %>%
+  dplyr::left_join(aai, by = "year") %>%
   filter(location_cat != "Non Identified") %>%
@@
          mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
-
+# Create/wrangle data for modelling Amazon speech proportions
 ama_model2_lag <- dplyr::select(pop, -text) %>%
-  dplyr::left_join(amazon_def_year, by = "year") %>%
-  dplyr::left_join(other_variables, by = "year") %>%
+  dplyr::left_join(amazon_def_year_lag, by = "year") %>%
+  dplyr::left_join(aai, by = "year") %>%
   filter(location_cat != "Non Identified")%>%
-  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
+  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
+                                            location, ignore.case = TRUE),
+                                      "Non Amazonian States", location_cat),
          location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                                "International", location_cat),
-         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
+         location_cat = ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                      location), "Amazonian Countries",
                                location_cat),
-                               levels = c("Amazonian States",
-                                          "Amazonian Countries",
-                                          "International", "Brasilia",
-                                          "Non Amazonian States")),
-         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
-                                      year), 1, 0),
          location_cat = factor(case_when(location_cat == "International" ~ 
@@
                                          "Non Amazonian States",
-                                         "Non Amazonian Countries")))
+                                         "Non Amazonian Countries")),
+         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+                                      year), 1, 0),
+         peak_year = ifelse(grepl("1989|1992|2009|2019", year), 1, 0))
 ```
@@
 On average, an Amazonian statement contains 131 words.
+
+```{r word_count, eval=FALSE, include=FALSE}
+# Total speeches
+nrow(pop) # 6240 speeches
+# Speeches about the Amazon
+sum(pop$amazon_speech) # 968 about Amazon
+# Amazonian statements
+final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/final_labeled_data.Rds")
+nrow(final_labeled_data) # 2048 Amazonian statements
+nrow(ama) # 1924 Amazon statements after removing false positives
+# Count average words in Amazonian Statements, using original text data
+amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
+sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048 # 131 words on average
+```
 
@@
 ```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-perc1 <- pop %>%
+pop %>%
   count(amazon_speech, year) %>%
@@
   filter(amazon_speech == 1) %>% 
-  select(c(perc, amazon_speech, year))
-perc1 %>% ggplot(., aes(x = year, y = perc)) +
+  select(c(perc, amazon_speech, year)) %>%
+  ggplot(., aes(x = year, y = perc)) +
   geom_line(color = "darkgreen") +
@@
   scale_y_continuous(labels = percent_format()) + 
-  annotate("text", x = 1985, y = 0.165, label = "15.4%", size = 3.5)+
+  annotate("text", x = 1985, y = 0.165, label = "15.5%", size = 3.5)+
   annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
@@
 
-```{r Repository, eval=FALSE, include=FALSE}
-## Count average words in Amazonian Statements
-## Need to use original text data
-# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
-# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
-## 131 on average
-
-## Comparison with inflation, criminality, unemployment, and inequality
-# pop %>%
-#   mutate(desigual = ifelse(grepl("desigual", text,
-#                                  ignore.case = TRUE), 1, 0),
-#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
-#                               text, ignore.case = TRUE), 1, 0),
-#          inf = ifelse(grepl("inflacao|inflaçao",
-#                              text, ignore.case = TRUE), 1, 0),
-#          unemploy = ifelse(grepl("desempreg",
-#                              text, ignore.case = TRUE), 1, 0)) %>%
-#   summarise(desigual = mean(desigual),
-#             crime = mean(crime),
-#             inf = mean(inf),
-#             unemploy = mean(unemploy))
-
+```{r comparisonq, eval=FALSE, include=FALSE}
+mean(mean_perc$perc) # 15.53 mean for Amazonian speeches
+# Comparison with inflation, criminality, unemployment, and inequality
+pop %>%
+  mutate(desigual = ifelse(grepl("desigual", text,
+                                 ignore.case = TRUE), 1, 0),
+         crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
+                              text, ignore.case = TRUE), 1, 0),
+         inf = ifelse(grepl("inflacao|inflaçao",
+                             text, ignore.case = TRUE), 1, 0),
+         unemploy = ifelse(grepl("desempreg",
+                             text, ignore.case = TRUE), 1, 0)) %>%
+  summarise(desigual = mean(desigual),
+            crime = mean(crime),
+            inf = mean(inf),
+            unemploy = mean(unemploy))
 ```
@@
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + inflation+  election_year,
+                         def_year + AAI + election_year + peak_year,
                          data = ama_model_lag,
@@
 c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + inflation +  election_year,
+                         def_year + AAI + election_year + peak_year,
                          data = ama_model_lag,
@@
 c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + inflation+ election_year,
+                         def_year + AAI + election_year + peak_year,
                          data = ama_model_lag,
@@
 c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + inflation +  election_year,
+                         def_year + AAI + election_year + peak_year,
                          data = ama_model_lag,
@@
 c5 <- plm(amazon_speech ~ as.factor(location_cat) +
-                         def_year + inflation+  election_year,
+                         def_year + AAI +  election_year,
                          data = ama_model2_lag,
@@
                                           "Inflation",
-                                          "Election Year"))
+                                          "Election Year",
+                                          "Peak years",
+                                          "Bottom years"))
 ```
@@
 Alternatively, presidents sidestep constructions whenever policy outcomes might be negative and wherever unlikely that the aligned problem-construction will be transformed in leverage.
-
-```{r setting vs outcome, fig.cap="Problem-constructions, settings, and policy outcomes", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
-amazon_def_year <- amazon_def_year %>%
-  mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
-ama_mx %>%
-  count(mx_cat, location_cat, year) %>%
-  group_by(year) %>%
-  mutate(perc = n / sum(n)) %>% 
-  filter(location_cat == "Amazonian States"|
-           location_cat == "Non Amazonian Countries",
-         mx_cat == "Pure Economic Integration"|
-           mx_cat == "Pure Environmental Conservation"|
-           mx_cat == "Pure Social Development"|
-           mx_cat == "Pure National Sovereignty") %>%
-  ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc, color=location_cat),
-              se = FALSE, linewidth =0.75, linetype="solid") +
-  scale_y_continuous(labels = percent_format(accuracy = 1))+
-  facet_wrap(~mx_cat)+
-  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
-       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
-       caption = "Curves in the plot were smoothed using loess method.")+
-  theme_am()+
-  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/120,fill=extremes),alpha=.5)+
-  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
-  annotate("text", x = 2009, y = 0.20, label = "27'772 km2\ndeforested" , size = 1.5, color="darkolivegreen", face="bold")+
-  annotate("text", x = 2015, y = 0.038, label = "4'571 km2\ndeforested", size = 1.5, color="darkolivegreen", face="bold")
-```
 

### 2023-02-09 Submission/Re-submission/draft/draft_resubmission.rmd
Added regression table in log odds

@@
 Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute and affiliated to the Centre for International Environmental Studies.]
-date: 2 February 2023
+date: 10 February 2023
 output:
@@
 First of all, these NGOs should go plant trees in their own countries [...]"
-(President Lula, Cuiaba, 2007).*
-
-> *[...] It is essential that, when taking care of the environment, we do not overlook people: the Amazon region is home to more than 20 million inhabitants, including indigenous peoples and riverside dwellers [...]"
-(President Bolsonaro, New York City, 2022)*
-
-Each of the above statements contains an implicit or explicit assumption of what needs to be solved, or in other words, it constructs the Amazon as a particular problem.
-Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a view of the region, its people, and forest [@drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship (1964-85) and Bolsonaro's presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney's (1985-1990) and Lula's (2003-2010) presidencies are often tied to environmental conservation.
-Yet, such  representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
-
-In this article, we show how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
-By combining @bacchi2009's theory of problem-representation and @keck1998's theory of transnationalism (1998), we offer a framework that (1) explains transnational variation in problem-constructions depending on speech setting and policies' outcomes, and (2) focuses on discourses rather than policies because they allow us to capture the diversity of ways policy goals are constructed to different audiences.
-
-Many analyses of Brazilian environmental policies approach it as a national or an international environmental problem, without a discussion of how important national actors behave differently in both scenarios.
-Our framework and methodology identify and accounts for this variation.
-We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil's agricultural powerhouses, in a moment when deforestation is increasing, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
-Meanwhile, even President Bolsonaro at the United Nations General Assembly in New York City, spoke about protecting the Amazonian forests and its peoples.
-
-Our focus on presidential speeches affords us analytical leverage and it is crucial to understand policy.
-The Brazilian executive branch of government, led by the president, has historically been the primary actor in shaping public policy in Brazil(Pinto 2016).
-While presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017], the Amazon forest and its peoples remains largely absent.
-Presidential speeches legitimize perceptions about the Amazon that are key for policy adoption and implementation [see @alesina2009; @lopez2020].
-This is especially pertinent for deforestation in the Amazon as expectations of local actors, generated from material and discursive governmental practices, are crucial in decisions to deforest on the ground [@assuncao2015; @capobianco2019; @capobianco2021; @campbell2015].
-
-Our findings are threefold.
-First, we find that the frequency in which the Amazon appears as a topic in presidential speeches is driven by domestic and international coverage of environmentally related events.
-Second, while the same government adopts a diverse range of problem-construction, we identify a process of convergence:  the constructions of the Amazon as an issue of economic integration were more salient from 1985 to the mid-2000s, but environmental conservation and social development problem-constructions steadily grew to temporarily surpass economic integration as from 2010 to 2015.
-Constructing the Amazon as an issue of sovereignty steadily increased after 2008, to the extent that all problem-constructions converge to being deployed in a balanced way after 2015.
-Third, we find a cumulative effect between speech setting and policy outcome.
-Presidents are more likely to construct the Amazon as an issue of environmental conservation when they speak at non-Amazonian countries outside of Brazil and deforestation figures are positive.
-Within the Amazon region and neighboring countries, presidents tend to construct the Amazon as an issue of social development and economic integration.
-When deforestation figures are negative, presidents tend to side-step environmental conservation.
-Overall...
+(President Lula, Cuiaba - MT, 2007).*
 
@@
 
-We divide our theoretical framework in two parts.
-We start with an explanation of what are problem-constructions, our dependent variable at large, and why presidential discourse are an interesting instance to identify them.
-Next, we argue that problem-constructions can vary depending on the transnational setting of the speech and on how good policy outcomes are in the moment of speech, our main independent variables.
-
 ## 2.1 Presidential speeches, policymaking, and problem-constructions
-
-Social scientists often describe federal governments as proponents of a cohesive set of policies toward the Amazon [@drummond2006; @padua2012; @franchini2019; @pereira2021].
-The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
-Whereas governments from the late-1980s up to the late-2000s are associated with a turn towards policies that focus on environmental conservation [@padua2012].
-The presidencies of Dilma (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, and Bolsonaro (2019-2022) is generally associated to the dismantling of environmental policies [@capobianco2019].
-Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into policy periods, or policy cycles, with one all-encompassing view of the Amazon.
-
-There is more variation within a specific government, though, than suggested by the policy-cycle approach[@bacchi1999].
-Political scientists have shown how governments have contradictory agrarian policies [@lopez2023], redistribution policies[@fairfield2017], health policies[@poncedeleon2021], and social policies[@niedzwiecki2017].
-We argue that the reason behind these monolithic representations of governments in literature about the Amazon by social scientists is conceptual.
-As a key biome in global climate-mitigation efforts, the Amazon has often been conceptualized within the logic of a global collective action effort to halt environmental problems.
-Many studies of the Brazilian Amazon contain an explicit, or implicit assumption, that the problem is of environmental nature.
-If the Amazon is thought of as an "environmental" problem, as is often the case in the literature, then it demands an "environmental" solution.
-Consequently, more frequently than not, studies focus on understanding environmental policies [@capobianco2019], the work of environmental NGOs [@silva-muller2022], or the rise of transnational partnerships [@andonova2022].
-We acknowledge the quality and importance of all these studies, but to build a comprehensive account of policies towards the region, we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
-
-@bacchi2009 [p.
-2] places the question "what is the problem represented to be" in the center of policy studies .
-She argues that policies have a cultural dimension as they take "shape within specific historical and national or international contexts" @bacchi2009 [p.
-10].
-The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-The alleged problem is not always stated in a policy, but policies are represented as solutions for either explicit or implicit problems.
-Problem-representation matters for policy because it carries implications related to who is involved both in the root causes and in the solutions of the problem @bacchi2009.
-Following Bacchi, when speaking about a *policy object*, this is, a problem that demands dedicated policy attention, governments are either explicitly or implicitly constructing it as a problem of a certain kind.
-This is what we label as *problem-constructions*.\
-
-Presidential discourse is a good instance to identify problem-constructions over time.
-While the relationship between discourse and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
-This is particularly true in the Brazilian context where the executive branch of government, led by the president, have historically been the primary players in shaping public policy, especially after the 1988 constitution [@pinto2016].
-[more on presidents and their role in policies].
 
@@
 
- Many analyses of Brazilian policies towards the Amazon approach it as a national problem or an international problem, without a discussion of how important national actors behave differently in both scenarios.
-The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary.
-By focusing on problem-constructions in presidential speeches, with an analytical strategy that distinguishes the location of the speech, we can move the empirical debate on the transnational nature of the Amazon forward.
-There are two main contenders for tying the problem-construction to international politics: Putnam's two-level game and Keck and Sikkink's transnational networks.
+# 3. Research Design
 
-@putnam1988 theory of two-level games in international negotiations can be adapted to explain variation in presidential speeches.
-@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups.
-At the national level, interest groups pressure the government to adopt favorable policies.
-Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988, p.
-434].
-While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups.
-
-This two-level approach is, for example, the avenue pursued by @calderwood2019 and @calderwood2020 who investigates variation in American presidential speeches about climate change.
-Consistent with the two-level games, the author finds that presidents are more likely to mention climate change outside the US, though the location of the speech (domestic or foreign) has a small effect on the content of the mention [@calderwood2020].
-However, the party affiliation of American presidents mediate how they speak about climate change [@calderwood2019].
-Thus, adopting a two-level approach to analyze diverse discursive constructions implies that whatever presidents say inside and outside, lies within the policy expectations of domestic and foreign interest groups.
-Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interest of different groups.
-
-Putnam's theory of two-level games, though, is closer to a traditional view of policy, in which actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
-Relatedly, it views summits as the UNFCCC as a purely intergovernmental body and thus of international nature.
-Its contribution, then, is to propose a connection between the national and international spheres as avenues for state-actors only.
-While there is some evidence of two-level games at play, this view seems incompatible with both the possibility of contradictory policies and of varied problem-constructions, which is more aligned with a constructivist perspective of politics.
-Rather than seeing international politics as the domain of only nation states, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, spamming from the local level to the international level [@nye1971; @keck1998].
-In this context, international summits are considered a transnational setting, as the presence and participation of non-state actors constitutes them.
-
-@keck1998 theory of international politics as transnational networks, developed in the context of value-based advocacy groups, provides an alternative explanation for variation in problem-constructions.
-The authors reject the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
-Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p.
-4]: state and non-state actors participate in and shape international politics.
-In this sense, the positions state actors as components of a transnational network derive from complex interactions in which their identities and goals that are malleable and can vary across time and space.
-
-While their theory is developed in the context of value-based advocacy groups, the overall view of international politics as structured by actors and structuring actors, should hold as well for state actors as well.
-Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
-Transnational networks do not imply a consistent usage of problem-constructions across settings, as two-level games.
-That is, presidents construct problems and attempt to inform or leverage transnational audiences for symbolic or material gains according to their expectations of this audience.
-This indicates that how presidents construct policy objects as problems can vary, for instance, within the country ---speaking inside the Amazon versus outside--- because presidents identify these audiences as sources of different types of support.
-The same holds when speaking outside the country--- in Amazonian countries, non-Amazonian countries, and summits like Davos or UNFCCC--- where expectations and identities of audiences diverge completely from that of domestic actors.
-
-This variation depends on the tactics presidents choose.
-Presidents can engage in information politics by creating politically meaningful information and/or moving it where they believe it can have an impact [@keck1998, p.
-24].
-In this regard, it is natural that presidents will always use policy adoption and outcomes in a cunning way, either to mask bad decisions or to boast successful ones.
-As well, presidents can engage in leverage politics by leveraging institutions to realize symbolic or material gains.  Material gains can be voters' support inside the Amazon or financial support in a UNFCCC Summit.
-
-Our conceptual framework identifies problem-construction of the Brazilian Amazon in official presidential speeches and explains why and how it varies as a function of the setting where the speech takes place and policy outcomes.
-It advances the literature about the Amazon in two ways.
-First, we provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem constructions as the main dependent variable of our study.
-In so doing, we avoid assuming what type of problem it is and focus on how it has been represented.
-Second, by analytically distinguishing transnational settings, one of our main independent variables, we avoid a single focus on the Amazon as either a national or an international problem.
-
-# 3. Research Design: operationalizing Amazonian problem-constructions
-
-We start our research design by detailing how we operationalize the main variables of our theory.
-We then move to a section detailing our descriptive and inferential strategy.
-Along both sections, we explain the main limitations of our approach.
-
-## 3.1 Data and operationalization strategy
-
-To identify problem-constructions in presidential speeches, we need a dataset containing all official presidential speeches by Brazilian presidents.
-We build upon @cezar2020 dataset, which contains all speeches from 1985 to 2019.
-We update the dataset by scraping and adding all official speeches from 2020 to 2022.
-The final dataset encompasses 6240 speeches, with their dates and speech location.
-We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
-We do so by detecting all speeches in which the stem "amazon" appears.
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 968 speeches are, at least partially, about the Amazon.
-Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem "amazon" appears.
-We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
-This is how our unit of analysis, an Amazonian statements, are generated.
-This process yields 2048 unique Amazonian statements.
-On average, an Amazonian statement contains 131 words.
+## 3.1 Data
 
@@
 
-### 3.1.1 Problem-construction in Amazonian Statements
-
-To test our conceptual framework, we need to operationalize our main dependent variable, the possible problem-constructions for a policy object.
-To identify and classify Amazonian speeches as specific types of problem constructions, we developed a codebook inductively and with assistance of the literature.
-We identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
-We argue a fourth separate one also exists: social development.
-The social development construction focuses on the constitutional rights and dignity of the inhabitants of the Amazonian region.
-
-#### National Sovereignty
-
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
-8], and when the dust settled and the scramble was over, more than half of the Amazon territory emerged Brazilian.
-While the Brazilian military diplomacy following the scramble was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil's sovereignty over the Amazon [@hecht2020].
-More recently, as we move to a world where non-state actors gain importance in international politics [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
-Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
-
-#### Economic Integration
-
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@capobianco2019; @becker2005].
-In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021].
-First, it assumed that nature should be conquered by mankind.
-Second, it assumed that exploiting natural resources would render the Amazon region economically profitable.
-Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory.
-Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
-The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
-
-#### Environmental Conservation
-
-The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
-Arguably, the creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
-The environmental conservation problem-construction emphasizes that the Amazon should be preserved, deforestation should be halted, and the sustainable practices of indigenous and local peoples should be maintained through the protection of their territories and rights to self-determination.
-The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
-
-#### Social Development
-
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
-However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
-While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected.
-As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
-Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
-The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
-
-In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
-However, an Amazonian statement can be coded as referring to multiple problem constructions (see Figure 1).
-Amazonian statements, thus, can be pure-type statements (i.e.
-constructs the Amazon as a single problem) or mixed-types (i.e.
-constructs the Amazon as multiple issues).
+## 3.2 Operationalizing Amazonian problem-constructions
 
@@
 
-With the codebook in hand, each one of the authors separately hand-coded 1024 randomly selected Amazonian statements.
-This amount refers to 50% of all the Amazonian statements identified.
-We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time.
-As well, since we have four different code categories, the size of the training set should be increased [see @grimmer2022].
-The hand-coding strategy provides a robust and reliable number of observations to be used for training and validation of the automated model.
-Once hand coding was completed, the average intercoder agreement for hand-coded categories was 85%.
-For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
+## 3.3 Operationalizing Settings and Pressingness
 
-Finally, the hand-coded data is randomly divided into a training set, containing 80% of the data (819 observations), and a validation set, containing the remaining 20% of the data (205 observations).
-We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier appropriate for binary categories, to label texts [@meyer2021; @noble2006].
-To validate the model, the SVM algorithm is trained using the hand-coded training set and employed to classify observations in the validation set.
-As a final robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
-Automating the coding of the remaining half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.
-The final dataset for analysis, excluding false positive matches[^1], contains 1924 coded Amazonian statements.
+## 3.4 Inferential and Descriptive Analysis
 
-[^1]: We also train the model to identify false positive matches in Amazonian statements.
-These are 124 Amazonian Statements that contain the stem "amazon", but are not necessarily meaningful as they might simply salute the governor of the Amazon, for example.
-We choose to remove these to reduce ambiguity and improve robustness of the findings.
+# 4. Analysis: How has the Brazilian Amazon been constructed as a problem?
 
-One limitation of this approach is that our dataset covers only what is considered an official speech.
-Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
-Problem-construction within presidential discourse, thus, happens in different public, private, and online settings for which we do not account or differentiate in this paper.
+## 4.1 The Amazon as a transnational problem
 
-### 3.1.2 Operationalizing settings and policy outcomes
+````{=tex}
+\begin{landscape}
 
-Our explanation for variation in problem-constructions is based on first the setting of a speech and second the policy outcomes. This comprise, at large, our main independent variables.
+```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+# Run models
+c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
+                         def_year + AAI + election_year + peak_year,
+                         data = ama_model_lag,
+                         model = "within", index = "president")
+c5 <- plm(amazon_speech ~ as.factor(location_cat) +
+                         def_year + AAI +  election_year,
+                         data = ama_model2_lag,
+                         model = "within", index = "president")
+# Calculate the custom CIs
+ci1 <- exp(confint(c1))
+ci2 <- exp(confint(c2))
+ci3 <- exp(confint(c3))
+ci4 <- exp(confint(c4))
+ci5 <- exp(confint(c5))
+# Regression table                       
+stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Odds-ration for fixed-effects logistic regressions indexed by president",
+                     ci = T, apply.coef = exp,
+                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
+                     t.auto=F, p.auto=F,
+                      column.sep.width = "-12pt",
+                      font.size="small",
+                      dep.var.labels = c("Amazon Speech",
+                                         "Environmental Conservation",
+                                         "Economic Integration",
+                                         "Social Development",
+                                         "National Sovereignty"),
+                     covariate.labels = c("Amazonian Countries",
+                                          "Non Amazonian States",
+                                          "Non Amazonian Countries",
+                                          "Deforestation",
+                                          "Inflation",
+                                          "Election Year",
+                                          "Peak years"))
+```
 
-#### Setting
+\end{landscape}
+````
 
-Presidents construct problems and attempt to inform or leverage audiences for symbolic or material gains according to their expectations of the speech audience.
-To operationalize the audience, we extract the location of the speech and create four distinct settings.
-We argue that each one of these settings encompasses an audience that presidents can have different expectations and views, given the Brazilian Amazon is our policy object.
-
-First, speeches can take place in Amazonian States inside Brazil.
-As a constituency with likely distinct demands than in other Brazilian states, presidents can try to communicate with them highlighting what presidents project their demands to be.
-Second, and consequently, Brazilian states outside the Amazon are another setting.
-In this case, as populations with some stake in the Amazon but not residing there, they might have different views of the Amazon.
-
-The third setting encompasses speeches that take place in Amazonian Countries, these are other countries that also harbor the Amazon Rainforest (e.g.
-Peru, Colombia, Venezuela, etc.).
-We argue that in bilateral visits to Amazonian countries, presidents can view other countries as potential peers in pushing specific visions of the rainforest internationally.
-The last setting encompasses all speeches in non-Amazonian countries.
-This entails speeches that take place within multilateral mechanisms as the UNFCCC, international summits as the World Economic Forum, bilateral visits to the United States or France, and so on.
-We argue that in these contexts, presidents also deploy problem-constructions aligned with what presidents perceive as possible expected gains from international processes.
-
-While we would ideally control for the exact venue of the speech (multilateral mechanism, private fora, etc.), so we could have an even more precise identification of the audience, the location information of the speeches does not allow so.
-Nevertheless, we believe these four settings and their different audiences are already enough to demonstrate whether and how problem-construction indeed changes transnationally.
-
-#### Policy outcome
-
-We also expect presidents to have a cunning usage of policy outcomes.
-If outcomes are good, we argue that presidents will deploy aligned problem constructions to boast policy.
-If outcomes are bad, we argue presidents will mask them by highlighting a contradictory problem construction.
-We operationalize policy outcomes by using the yearly deforestation rates provided by INPE.
-We consider this a good option, as national and international actors do react to deforestation rates.
-In the late 1980s, for instance, there was strong media coverage in the USA of forest fires and deforestation figures.
-Similarly, in 2019, world press covered the August fires.
-We opt for lagging deforestation rates one year, as the consolidated numbers for 2007, for example, are published in 2008.
-
-Many scholars inquire and find causal relationships between discourse and policy outcomes.
-Our research design and data does not allow us to test so.
-While we might suggest a particular direction in certain cases, none of our claims are linearly causal.
-
-## 3.2 Data Analysis: descriptive and inferential methods
-
-As a dataset like this was never constructed before, we start with longitudinal descriptive statistics, which  reveals interesting trends.
-First, we identify years in which Amazon as a general topic has been discussed more frequently and possible drivers.
-To do so, we take the share of yearly speeches that mention Amazon independently of the specific problem construction.
-Next, we discuss the evolution of yearly problem-constructions in time by showing our data longitudinally.We conclude with four separate fixed-effect logistic regression models that predict the probability of each problem-construction relative to the setting in which a speech takes place and the policy outcome.
-
-The dependent variable of each model is the share of one pure-type problem construction against all other three problem constructions.
-We use four separate logistic regressions to provide unambiguous interpretations and comparisons, as a multinomial model would entail four categories on both dependent and independent variables.
-We include presidential fixed effects because we can expect individual-specific characteristics (i.e.
-presidential ideology) to have an effect on the outcome.
-If the president's political ideology is a good predictor of pure-type variation, it could indicate that the president is rather isolated from settings and that they can follow their own worldviews[^2].
-Fixed-effects control for this issue[@allison2009fixed], and other unit-unvarying characteristics.
-Our main explanatory variables, setting and policy outcomes, are included as described in section 3.1.2.
-We add a third variable, which takes the value of 1 if the salience of the Amazon as a general topic was above average that year.
-We do so to test peaks in the Amazon as a general topic driving any particular problem-construction.
-Finally, we add two standard controls: yearly inflation rate (numerical) and election year (dummy).
-
-[^2]: We would like to thank Reviewer#2 for this suggestion.
-
-# 4 How has the Brazilian Amazon been constructed as a problem?
-
-The subsequent analysis visualizes and models Amazonian statements and problem-constructions over time and by setting.
-We interpret these models and plots considering the literature, Amazon-related events, and policies since 1985.
-
-## 4.1 The Amazon as a general topic in presidential speeches
-
-When, where, and how often do presidents speak about the Amazon as a general topic?
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-On average, presidents mention the Amazon in 15.4% of their speeches.
-For comparison purposes the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).
-This suggests the Amazon is a topic of relative high importance for presidents generally.
-However, five local maxima are above average[^3] in the figure:1989, 1992, 2009, 2019, and 2022.
-All of them coincide with environmentally related events that received wide coverage from international media.
-
-[^3]: We consider the years in which the Amazon appeared in over 20% of all official speeches.
+## 4.2 Amazonian speeches in time
 
@@
 
-In 1989 the Amazon appeared in 32% of all speeches.
-This coincides with the brutal murder of the environmental activist Chico Mendes in the last few days of 1988.
-The incident caught unprecedented international attention and then president Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
-One of the responses was the offer and acceptance to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
-During the summit, we saw the realization of the first transnational partnership for the Amazon, the G7 Pilot Program, which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
-
-Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula administrations, the Amazon as a topic did not diverge much from the average until 2009, when we see another maximum in mentions of the Amazon.
-The Copenhagen Summit was held in 2009 and, with the steep decrease in deforestation rates, Lula (2003-2010) led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019].
-From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-Interestingly, this period was intense in terms of domestic legislation.
-The revision of the Forest Code, debated in 2010 and 2011, and approved in 2012, pardoned thousands of illegal deforesters in the Amazon.
-The period was also marked by political and economic instability which culminated in the impeachment of Rousseff (2011-2016) in 2016.
-By 2016 mentions of Amazon in official speeches went down to 6%, their lowest share since 1985.
-
-We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro's presidency.
-At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019.
-Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
-Bolsonaro went on to retrieve Brazil's hosting status for COP25.
-Finally, and unfortunately, in 2022, environmental activist, Bruno Mendes, and British journalist, Dom Phillips, were murdered and buried in the Amazon (McCoy 2022).
-<!-- Discourses are also a response to political pressures; are not just problem-constructions but also a sort of justification...
-(Grazi's comment) -->
-
-## 4.2 Problem-constructions in time
-
-Although we observe variation in the frequency of the Amazon as a general topic, our conceptual framework foresees variation in specific problem-construction depending on a myriad of factors.
-In this subsection, we investigate how pure-types and mixed-types problem constructions evolved over time.
-The same president simultaneously constructs the Amazon as various problems, which unravels a less cohesive story than that told by the policy-cycle literature.
-Nevertheless, the overall balance between problem-constructions reveals longitudinal trends that speak to the importance of the environment, economy, social policy, and sovereignty.
-Figure 3, below, illustrates the share of each pure-type problem-constructions, along with the share of all mixed-types together, in time.
+## 4.3 Amazonian problem-constructions in time
 
@@
 
-Pure economic integration constructions were the most frequent from 1985 to 2009.
-This is especially pertinent during Cardoso's presidency (1995-2002), when economic integration was increasing while environmental conservation decreased.
-When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-While this correlates with strong environmental policies being adopted in 2004, economic integration still ranked first.
-It was only in 2010, with President Dilma, that environmental conservation and social development problem-constructions surpassed economic integration.
-Interestingly, there is a steady increase of sovereignty problem-constructions starting in 2008 already.
-This reversal was not long-standing, though.
-With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration increases to become the most favored construction.
-
-The same governments deploy contradictory constructions, but their relative frequencies reveal trends over time.
-The 1988 Brazilian Constitution foresaw the strengthening of environmentalism through the participation of indigenous peoples and civil society in policy-making [@keck1998], which was slowly confirmed, at least discursively.
-The fall of economic integration problem-construction and the rise of both social development and environmental conservation constructions in the 2000s suggest an unprecedented balance between granting local livelihoods their rights and economic development: never, since 1985, Amazonian constructions that focused on the environment and the constitutional rights of its people were more present than the economic integration in presidential discourses.
-While social development and environmental conservation did go down, we are now at a point in time where they appear almost as frequently as economic integration.
-
-The steady increase of sovereignty as salient problem-constructions starts in 2010, much before Bolsonaro was elected.
-The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government.
-In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, stronger criticism of civil society in politics was often met by presidents with accusations of internationalization attempts.
-Thus, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making.
-Bolsonaro's problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
-
-Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon.
-Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem.
-Constructing the Amazon as multiple issues increases from 18%, in 1985, to 29%, in 2022, of all constructions.
-This general increase is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.
-This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.
-
-## 4.3 The Amazon in transnational settings
-
-By adapting transnational networks to discourse, we argue that presidents' expectations about transnational audiences in different settings explain variations in problem-constructions.
-To investigate the relationship between where presidents speak and how they construct the Amazon as an issue, we run five logistic regressions, one for each pure-type construction as a dependent variable and one for all mixed-type constructions (see table 2 below).
-Multiple, often contradictory, problem-constructions are forwarded across settings as presidents participate and shape transnational politics, confirming what our conceptual frameworks foresee.
-
-````{=tex}
-\begin{landscape}
-
-```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
-                         data = ama_model_lag,
-                         model = "within", index = "president")
-c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
-                         data = ama_model_lag,
-                         model = "within", index = "president")
-c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
-                         data = ama_model_lag,
-                         model = "within", index = "president")
-c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
-                         data = ama_model_lag,
-                         model = "within", index = "president")
-c5 <- plm(amazon_speech ~ as.factor(location_cat) +
-                         def_year + AAI +  election_year,
-                         data = ama_model2_lag,
-                         model = "within", index = "president")
-
-stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
-                     title = "Fixed-effects logistic regressions by president with controls",
-                      column.sep.width = "-12pt",
-                      font.size="small",
-                      dep.var.labels = c("Amazon Speech",
-                                          "Environmental Conservation",
-                                         "Economic Integration",
-                                         "Social Development",
-                                         "National Sovereignty"),
-                     covariate.labels = c("Amazonian Countries",
-                                          "Non Amazonian States",
-                                          "Non Amazonian Countries",
-                                          "Deforestation",
-                                          "Inflation",
-                                          "Election Year",
-                                          "Peak years",
-                                          "Bottom years"))
-```
-
-\end{landscape}
-````
-
-On the one hand, when speaking at non-Amazonian countries (be it in governmental summits, bilateral visits, or fora), presidents are more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speaking within Amazonian states in Brazil (reference category).
-To a lesser extent, this also holds for when presidents speak in non-Amazonian states in Brazil.
-Alternatively, when speaking within Amazonian countries, the likelihood of deploying environmental conservation decreases drastically.
-We interpret this as evidence that presidents often construct the Amazon as an environmental problem outside of Amazonian states within Brazil, and of Amazonian neighboring countries, because of their views of transnational audiences as possible funders of domestic policy and projects.
-for instance, the Brazilian government successfully funded domestic public policy with transnational support on several occasions: the 1992 Pilot Programme of the G7 for the Protection of Rainforest; the 2001 Amazon Region Protected Areas Program by the World Bank and others; the 2008 Amazon Fund which provided over USD 1 billion; multiple Global Environment Facility grants; as well as multiple bilateral and philanthropic grants [@silva-muller2022].
-That is, they realize material and symbolic gains internationally, outside of Amazonian countries, by constructing the Amazon as an environmental problem.
-
-On the other hand, economic integration problem constructions are more likely to take place within Amazonian countries than within Amazonian states.
-Whereas social development constructions are less likely to take place within Amazonian countries and non-Amazonian countries.
-Concurrent with the successful environmental policies from the early 2000s, financed by transnational monies, presidents also pursued a national agenda of economic integration or social development.
-For instance, rural credit offered to local agricultural producers in Amazonian states, went up from 500 million reais a year in 1999 to over 4 billion a year by 2012 [@capobianco2021].
-The special fiscal regime in Manaus, designed to increase industry presence in the region, was maintained.
-More roads and dams (e.g.
-BR-163 and Belo Monte) were constructed during the period.
-Presidents likely highlight these policies as they see Amazonian populations as voters to whom they are accountable.
-We argue that presidents expect voters' to have more immediate socio-economic interests, rather than environmental ones, and therefore construct the Amazon accordingly.
-
-Sovereignty problem constructions, interestingly, are more likely to take place when presidents speak at non-Amazonian states in Brazil or when relevant environmental-related events occur.
-While we found that the frequency of the Amazon as a general topic is driven by environmental-related events (section 4.1), presidents do not necessarily respond to them with specific problem-constructions.
-Rather, as such events bring strong international media coverage, Brazilian presidents match them with discursive attempts to highlight Brazil's sovereignty over the Amazonian territory.
-
-Furthermore, constructions of the Amazon as a problem of economic integration increase as deforestation rates also increase; while constructions of the Amazon as a problem of environmental conservation increase as deforestation rates decrease.
-Although our models take settings and policy outcomes without differentiating for their different correlations as they vary in time, there is a complex relationship between problem constructions, settings, and time.
-For instance, figure 5, below, demonstrates that when deforestation rates decreased form 2004 to 2012, presidents preferred constructing the Amazon as an issue of environmental conservation both within Amazonian states and in non-Amazonian countries.
-As deforestation rates increased from 2012 to 2021, environmental conservation problem-construction remained steady within Amazonian states but decreased sharply in non-Amazonian countries.
-Alternatively, the positive relationship between economic integration problem constructions and deforestation rates from the model is driven by the same relationship within Amazonian states.
-When speaking at non-Amazonian countries, presidents are generally less likely to construct the Amazon as an issue of economic integration in time.
-In line with our framework, this suggests presidents boast positive policy outcomes whenever possible and wherever profitable by leveraging the aligned problem construction.
-Alternatively, presidents sidestep constructions whenever policy outcomes might be negative and wherever unlikely that the aligned problem-construction will be transformed in leverage.
-
-Overall, we find that presidents promote economic integration and social development within Brazil and neighboring Amazonian countries that diverges from the environmental one promoted non-Amazonian countries.
-That is, presidents might talk to the economic or social needs of the voters domestically, while boasting about environmentalism internationally.
-Presidents, as participants of transnational networks, speak based on what they can expect of an audience given the context.
-
 # 5. Conclusion
-
-This paper investigates how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-We have four main findings: first, the frequency of the Amazon as a general topic in speeches is driven by environmental related events that draw international attention.
-Second, we demonstrate how the same government adopts multiple problem-construction concurrently.
-The expectations of presidents about the audience of the speech, more than anything else, is the driver of variation of problem-construction.
-Third, and relatedly, we identify a long-term reduction trend of economic integration to a more balanced deployment of all problem-constructions.
-Finally, we demonstrate how presidents promote economic integration and social development within Brazil and neighboring Amazonian countries that diverges from the environmental one promoted non-Amazonian countries.
-
-Overall, we interpret these results as evidence of presidents structuring and being structured by transnational networks.
-Conceptually, we believe a focus on problem-constructions in transnational settings complements sectoral studies of the Amazon, that focus on single domains of policy.
-Specifically, rather than assuming the Amazon represents an environmental problem, we start from the position that the region is a socio-economic-environmental policy object.
-Our analysis reveals how government perspectives are diverse and variation can be explained by the setting of speech and current policy outcomes.
-
-We see three broad avenues for future research.
-First, we have introduced a flexible framework and methods that ask when, where, and how questions about how policy objects are constructed.
-We expect to inspire some to investigate other policy objects in domains beyond the Brazilian Amazon (e.g.
-Cerrado Biome, Antarctic, Inequality, Criminality, etc.).
-Second, while we argue that presidential official discourse is important, the possibility of instant recordings and social media can change this in fundamental ways.
-We look forward to works that investigate how setting and audience interact with problem-construction in unofficial political communications.
-Finally, while we conceptualize the possibility of problem constructions having a direct effect on policy outcomes, our research design does not allow for such a test.
-It is possible, though, to design studies that test the causal relationship between presidential discourse and outcomes.
-In a forthcoming article, @ajzenman2020 propose an identification strategy that ties Bolsonaro's speech to covid-19 infections.
-We look forward to studies that identify how different problem constructions affect outcomes.
 
@@
 
-The authors are extremely grateful to Matias López, Graziella Moraes Silva, and James Hollway for their support.
-The authors would also like to thank the Mario, Federico, Rodrigo, and Anna for valuable comments on earlier drafts of this paper.
+The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support.
+The authors would also like the two anonymous reviewers for their comments and suggestions.
+Finally, we would like to thank Anna, Federico, Mario, and Rodrigo for their invaluable help.
 
@@
 
-The authors report there are no competing interests to declare.
+The authors report that there are no competing interests to declare.
 

### 2023-02-09 Submission/Re-submission/draft/draft_resubmission.rmd
More updates to file

@@
 library(dplyr)
-library(readr)
 library(tidyr)
@@
 library(tibble)
-library(readxl)
 library(ggplot2)
-library(gridExtra)
-library(modelsummary)
 library(plm)
@@
   annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
-  annotate("text", x = 2022, y = 0.225, label = "Murder\nof Bruno\nand Dom", size = 3)+
   labs(x = "", y = "",

### 2023-02-09 Submission/Re-submission/draft/draft_resubmission.rmd
Added odds ratio table to appendix

@@
 
-```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+```{r models president fixed effect, fig.cap="Log odds for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 # Run models
@@
                          model = "within", index = "president")
-# Calculate the custom CIs
-ci1 <- exp(confint(c1))
-ci2 <- exp(confint(c2))
-ci3 <- exp(confint(c3))
-ci4 <- exp(confint(c4))
-ci5 <- exp(confint(c5))
 # Regression table                       
 stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
-                     title = "Odds-ration for fixed-effects logistic regressions indexed by president",
-                     ci = T, apply.coef = exp,
-                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
-                     t.auto=F, p.auto=F,
+                     title = "Log odds for fixed-effects logistic regressions indexed by president",
                       column.sep.width = "-12pt",
@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r log odds, fig.cap = "Odds-ration for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+# Calculate the custom CIs
+ci1 <- exp(confint(c1))
+ci2 <- exp(confint(c2))
+ci3 <- exp(confint(c3))
+ci4 <- exp(confint(c4))
+ci5 <- exp(confint(c5))
+# Regression table                       
+stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
+                     title = "Odds-ratio for fixed-effects logistic regressions indexed by president",
+                     ci = T, apply.coef = exp,
+                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
+                     t.auto=F, p.auto=F,
+                      column.sep.width = "-12pt",
+                      font.size="small",
+                      dep.var.labels = c("Amazon Speech",
+                                         "Environmental Conservation",
+                                         "Economic Integration",
+                                         "Social Development",
+                                         "National Sovereignty"),
+                     covariate.labels = c("Amazonian Countries",
+                                          "Non Amazonian States",
+                                          "Non Amazonian Countries",
+                                          "Deforestation",
+                                          "Inflation",
+                                          "Election Year",
+                                          "Peak years"))
+```
+
+\end{landscape}
+````

### 2023-02-09 Submission/Re-submission/draft/draft_resubmission.rmd
Fixed issues with titles and legends in plots

@@
        title = "Share of speeches that mention the Amazon per year",
-       subtitle = "Sample composed by all 6130 speeches since 1985",
+       subtitle = "Sample composed by all 6240 speeches since 1985",
        color='Y series') +
@@
 
-```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure pure, fig.cap="Pure-types and miyed-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 #summary(as.factor(ama_mx$mx_cat))
@@
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
+  labs(x = "", y = "", title ="Share of pure-types and mixed-types problem-constructions by year",
        subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",

### 2023-02-13 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
shortened version

---
title: How has the Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article. Names are ordered alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.]
date: 13 February 2023
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
fontsize: 12pt
mainfont: Times New Roman
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage[T1]{fontenc}
   - \usepackage[utf8]{inputenc}
   - |
    \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
    \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is often approached as a transnational environmental problem without a discussion of how key actors see it differently in space and time. We combine theories of problem-representation and transnationalism to analyze where, when, and how the Brazilian Amazon has been constructed as a problem. We develop a framework that explains variation in transnational problem-constructions based on speech setting and problem pressingness. To test our framework, we use supervised machine learning to classify statements about the Amazon in 6240 presidential speeches since 1985. We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) pressing, presidents are likelier to highlight issues of environmental conservation (or economic integration). Furthermore, we show how we are moving from a period when the binary between seeing the Amazon as an environmental or an economic issue has been overcome, to a moment when diverse problem-constructions are deployed.

---

```{=latex}
\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
```

```{=latex}
\wordcount{ 8765 (including abstract, text, references, and footnotes)}
```

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

```{r theme, include=FALSE, warning=FALSE, message=FALSE}
# custom ploting theme for all plots
theme_am <- function(x) {
  theme(text = element_text(size=12,  family="Times"),
        panel.background = element_rect("white", "black", .5, "solid"),
                  panel.grid.major = element_line(color = "grey", linewidth = 0.2,
                                                  linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "none")
}
```

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data complete
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
# Load coded data on Amazonian statements and remove extra variables
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>%
  select(-c(title, date, text, false_positives)) %>%
  rename (ei= "EI", sd= "SD")
# Load annual deforestation rates data, lag years, and fill data
amazon_def_year_lag <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
# Fill missing years are missed with first non missing value.
# This is also consistent with def. rates from literature
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                  def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data
amazon_def_year_lag$def_year <- scales::rescale(amazon_def_year_lag$def_year) # scale def. rates
# Load inflation data, annual
aai <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/AAI.Rds")
aai_2022 <- data.frame("year" = 2022, "AAI" = 5.79) # Add 2022 rates
aai <- rbind(aai_2022, aai)
aai$AAI <- scales::rescale(aai$AAI) # scale annual inflation
# Code PCs as categories
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ 
                                     "Pure National Sovereignty",
                                   mixed_type == '0_1_0_0' ~ 
                                     "Pure Economic Integration", 
                                   mixed_type == '0_0_1_0' ~ 
                                     "Pure Social Development",
                                   mixed_type == '0_0_0_1' ~ 
                                     "Pure Environmental Conservation",
                                   mixed_type == '0_0_0_0' ~ 
                                     "Other",
                                   TRUE ~ "Mixed-types"),
         levels = c("Pure Economic Integration",
                    "Pure Environmental Conservation",
                    "Pure Social Development",
                    "Pure National Sovereignty",
                    "Other", "Mixed-types")),
        election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
        peak_year = ifelse(grepl("1989|1992|2009|2019", year), 1, 0),
        location_cat = factor(case_when(location_cat == "International" ~ 
                                          "Non Amazonian Countries",
                                        location_cat == 
                                          "Amazonian States" ~ 
                                          "Amazonian States",
                                        location_cat == "Amazonian Countries" ~ 
                                          "Amazonian Countries",
                                        TRUE ~ "Non Amazonian States"),
                              levels = c("Amazonian States",
                                         "Amazonian Countries",
                                         "Non Amazonian States",
                                         "Non Amazonian Countries")))
# Get peak years in Amazon speeches, as a control for modelling
mean_perc <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(amazon_speech == 1) %>%
  select(c(year, perc))
mean_perc[mean_perc$perc > mean(mean_perc$perc) + sd(mean_perc$perc),] # 89, 92, 09, 19
# Create/wrangle data for modelling PCs
ama_model_lag <- dplyr::left_join(ama_mx,
                                  amazon_def_year_lag, by = "year") %>%
  dplyr::left_join(aai, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation",
                             1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0),
         mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
# Create/wrangle data for modelling Amazon speech proportions
ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year_lag, by = "year") %>%
  dplyr::left_join(aai, by = "year") %>%
  filter(location_cat != "Non Identified")%>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul",
                                            location, ignore.case = TRUE),
                                      "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                     location), "Amazonian Countries",
                               location_cat),
         location_cat = factor(case_when(location_cat == "International" ~ 
                                          "Non Amazonian Countries",
                                        location_cat == 
                                          "Amazonian States" ~ 
                                          "Amazonian States",
                                        location_cat == "Amazonian Countries" ~ 
                                          "Amazonian Countries",
                                        TRUE ~ "Non Amazonian States"),
                               levels = c("Amazonian States",
                                         "Amazonian Countries",
                                         "Non Amazonian States",
                                         "Non Amazonian Countries")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
         peak_year = ifelse(grepl("1989|1992|2009|2019", year), 1, 0))
```

\pagebreak

> *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion. First of all, these NGOs should go plant trees in their own countries [...]" 
(President Lula, Cuiaba - MT, 2007).*

# 1. Introduction

Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a single view of the region, its people, and forest [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021]. While the military dictatorship (1964-85) and Bolsonaro’s presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are associated with environmental conservation. Yet, such representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies. In this article, we show where, when, and how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.

By combining @bacchi1999’s theory of problem representation and @keck1998's theory of transnationalism, we place the way the objects of policies are constructed in discourse at the center of our analysis. We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem pressingness as actors participate and shape transnational politics. We focus on transnational speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem. While many analyses of Brazilian environmental discourse and policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007]. Our framework and methodology help identify and account for these variations. We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil’s agricultural powerhouses, in a moment when the environmental problem is pressing, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.

To answer our question, we create a dataset containing 6240 official speeches by all Brazilian presidents since 1985. Next, we identify all instances where the presidents mention the Amazon. Using an inductive approach, we develop a codebook to categorize how each statement constructs the Amazon as one or multiple problems related to national sovereignty, economic integration, social development, or environmental conservation. Then, we manually code a random subset of the statements and use supervised machine learning to label the remaining. Finally, we conduct a descriptive and inferential analysis of the coded data.

We have four main findings. First, we find that presidents adopt different Amazonian constructions  in different settings according to how they expect to leverage audiences for symbolic and/or  material gains. Second, presidents often focus on alternative problem-constructions when general aligned problems become more pressing; whereas they boast about positive outcomes when aligned problems are less pressing. Third, we also find that high-profile environmental related events, which receive strong international media attention, drive up the importance of the Amazon as a general topic in presidential speeches. Alternatively, relevant Amazonian-related policies  appear to not to attract much attention. Finally, we find that while all presidents deploy multiple problem-constructions across space and over time, we are now in a period when the dictum between understanding the Amazon as an environment or as an economic issue has been overcome, at least discursively. Conceptually, our research shows how focusing on problem-constructions highlight what certain objects of policy are assumed to be, and when they are ignored or privileged, based on the transnational setting of the speech and the pressingness of aligned problems.

We begin our article by outlining the connection between problem-constructions, transnationalism, and presidential speeches. Next, we present our research design including data description and methodological approach. We open our analysis with our inferential analysis and move to explain developments over time. We conclude by summarizing the empirical and conceptual contributions of the article as well as providing avenues for future research.

# 2. Theory: problem-constructions, transnational settings, and problem pressingness

We divide our theoretical framework in two parts. We start with an explanation of what are problem-constructions and why presidential speeches are an interesting instance to identify them. Next, we argue that problem-constructions can vary depending on the transnational setting of the speech and on the pressingness of its problem.

## 2.1 Problem representation in presidential discourse

Social scientists often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021]. The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006]. Whereas, governments from the late-1980s up to the late-2000s are associated with a turn towards policies that focus on environmental conservation of the Amazon [@padua2012]. The presidencies of Rousseff (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, while Bolsonaro (2019-2022) with the dismantling of environmental policies [@capobianco2019]. Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into cohesive policy periods, or policy cycles, with one all-encompassing understanding of the Amazon.

We argue that the reason behind these monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the “Amazon problem” is. There is more variation within a specific government, though, than suggested by the policy cycle approach. Social scientists have shown how governments have contradictory policies [@lopez2023; @fairfield2017; @poncedeleon2021]. In the case of the Amazon, it has often been seen as a key biome in global climate-mitigation, and consequently, as an environmental problem. If the Amazon is thought of as an “environmental” problem, then it demands an “environmental” solution. However, in order to build a more comprehensive account of the Amazon as forest, region, and peoples we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.

@bacchi1999 [p. 2] places the question of “what is the problem represented to be” in the center of policy studies. These objects of policies have a cultural dimension as they take “shape within specific historical and national or international contexts” [@bacchi2009, p. 10]. The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed. Hence, discourse represents objects of policies as instances of a specific problem, which can be explicit or implicit. Problem-representation matters because it carries implications related to who is involved both in the root causes and in the solutions of the problem [@bacchi1999].

Following Bacchi, we place discourse about policy objects in the center of our conceptual framework. We define policy objects as political objects that demand dedicated political attention. We argue that by deciding to speak about a policy object, governments are making a deliberate choice. When speaking about policy objects, governments make a choice to represent, or construct it, as a specific problem. The problem might be either explicitly stated, or implicitly hidden in the underlined solution. This is what we label as problem-constructions.

Presidential discourses are a good instance to identify problem-constructions over time. While the relationship between presidential and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004]. This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution[@macaulay2017]. In  Brazil’s hybrid system, often referred to Coalitional Presidencialism [@couto2021], presidents build legislative support for a broad agendas through the distribution of positions in the state bureaucracies. This means that presidents have enough power and support to implement the agenda they deem appropriate. We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.

## 2.2 Transnational settings, pressingness, and variation in problem-constructions

The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary. There are two notable contenders for tying the problem-construction to international politics: Putnam’s two-level game and Keck and Sikkink’s transnational networks.

@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups. At the national level, interest groups pressure the government to adopt favorable policies. Internationally, the government seeks to fulfill domestic preferences “while minimizing the adverse consequences of foreign developments” [@putnam1988 p. 434]. While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups. Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interest of different groups. Adopting two-level games to explain American presidential speeches, @calderwood2019 and @calderwood2020 find supporting evidence of this theory.

The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups. This view seems incompatible with the possibility of contradictory policies and of varied problem-constructions depending on specific historical contexts, timing, and places. Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, spamming from the local level to the international level [@nye1971; @keck1998]. In this context, international summits are considered a transnational setting because non-state actors participate and shape them. We view, for instance, summits as the United Nations Framework Convention of Climate Change (UNFCCC) not only as a purely intergovernmental body, but as a transnational space composed of international media, corporations, non-governmental organizations, and social movements.

@keck1998 theory of international politics as transnational networks rejects the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups. Rather, international politics as transnational networks have “a structured and structuring dimension” [@keck1998, p. 4]: state and non-state actors participate in and shape international politics.

While their theory is developed in the context of value-based advocacy groups, this is non-state actors, the overall view of international politics as structured and structuring, should hold for state actors as well. Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors. They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p. 24]. Or, they can leverage institutions to realize symbolic or material gains. In this sense, the positions of actors as components of a transnational network derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.

Problem-constructions are choices made by presidents when speaking. If malleable identities across space and time are a defining feature of transnational politics, it follows that presidents' choice of problem-constructions depend on the president's views of an audience at a certain period. Specifically, how pressing a problem is in a certain space and/or at a certain time.

*Space*

Presidents construct problems and attempt to inform and/or leverage transnational audiences for symbolic or material gains according to their expectations of that audience. We conceptualize spaces in terms of settings. Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study. This indicates that how presidents construct policy objects as problems can vary, for instance, within the country — speaking inside the Amazon region versus outside — because presidents identify these audiences as sources of different types of support and demand. The same holds when speaking outside the country — in Amazonian countries, non-Amazonian countries, and international summits — where expectations and identities of audiences could diverge completely from that of domestic actors. In each one of these settings different problems might be more pressing and the president's expectations about what can be leveraged for material and symbolic gains might drive how a problem is implicitly or explicitly constructed.

*Time*

How presidents construct policy objects can also vary in time because the pressingness of certain problems changes as new information arises. We conceptualize time as the perceived pressingness of a broad and related issue to those surrounding a policy object. This indicates, for instance, that as climate change becomes more pressing and widespread as a broad issue, it is more likely that actors will consider climate change when discussing various forms of public policy. It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change. Conversely, today, if fossil fuel subsidies are discussed, climate change will likely be an issue given the increased pressingness of the topic in comparison to the 1980s.

While time and space might interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change pressing, certain transnational actors would likely mention it as a problem independently of the perceived  pressingness of a climate breakdown at the time. Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.

Our conceptual framework, thus, combines Bacchi’s theory of problem-representation and Keck and Sikkink’s theory of transnationalism to account for diverse problem-constructions. It helps to advance the literature about the Amazon in two ways: We provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions. In doing so, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented as a problem. Furthermore, many analyses of Brazilian environmental policies dissect its national and international nature but fail to adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007]. Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time. Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017]. When it comes to the environment, studies tend to focus primarily  on Bolsonaro’s discourse [@marquardt2022; @mendes2022] or policies [see @capelari2023]. We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there really is.

# 3. Research design

To create a dataset containing all Brazilian presidential speeches,we update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.The final dataset contains 6,240 speeches with their date and location. We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem “amazon”. In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others. We find that 968 speeches are, at least partially, about the Amazon.

We use the poldis R package [@sposito2021]  to extract two sentences before and after each reference to the Amazon in the presidential speeches. We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea. These sentences form our unit of analysis: 2048 unique Amazonian statements, with an average length of 131 words.

```{r word_count, eval=FALSE, include=FALSE}
# Total speeches
nrow(pop) # 6240 speeches
# Speeches about the Amazon
sum(pop$amazon_speech) # 968 about Amazon
# Amazonian statements
final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/final_labeled_data.Rds")
nrow(final_labeled_data) # 2048 Amazonian statements
nrow(ama) # 1924 Amazon statements after removing false positives
# Count average words in Amazonian Statements, using original text data
amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048 # 131 words on average
```

## 3.1 Operationalizing Amazonian problem-constructions

We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development. While the three former are in the literature, we argue a fourth one, social development, exists.

*National Sovereignty* 
In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p. 8]. While the Brazilian military diplomacy was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990]. These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil’s sovereignty over the Amazon [@rajao2020]. More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become more varied. Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors. The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region. The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.

*Economic Integration* 
The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005]. In 1966, the Brazilian Military launched ‘Operation Amazon’, a policy to modernize the region based on three assumptions [@acker2021]. First, it assumed that nature should be conquered by mankind. Second, it assumed that exploiting natural resources would render the Amazon region economically profitable. Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory. Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry. The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized. These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.

*Environmental Conservation*
The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006]. The creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990]. This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987]. The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted. The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.

*Social Development*
As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights. Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights. However, such emphasis can be masked within both the economic integration and environmental conservation accounts. While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected. Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity. The policy solution implies enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.

An Amazonian statement can be coded as referring to multiple problem-constructions (see Figure 1 below). Amazonian statements, thus, can be pure-type statements (i.e. they construct the Amazon as a single problem) or mixed-types (i.e. they construct the Amazon as multiple issues).

````{=tex}
\begin{landscape}

```{r figure1, echo=FALSE, fig.cap="Operationalization of problem-constructions", out.width = '100%', include=TRUE}
knitr::include_graphics("figure1pic.png")
```

\end{landscape}
````

Using a random sample of 1024 Amazonian statements and the codebook (see appendix), we hand-coded 50% of our data to train a machine learning model, yielding an average intercoder agreement of 85%. Any disagreements in coding were resolved through discussion and refinement of the codebook. We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and thus the training set size should be increased [see @grimmer2022].

We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations). We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories[@meyer2021; @noble2006], to train a model to label text. The model was validated by testing it on the validation set and it was 95% accurate in coding these statements. The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements. ^[We also train the model to identify false positive matches in Amazonian statements. These are statements that contain the stem “amazon” but are not meaningful as they might salute the governor of the Amazon, for example.]

## 3.3 Operationalizing settings and pressingness

Our explanation for variation in problem-constructions is based on the setting of a speech and the pressingness of an aligned problem. This comprises our independent variables.

*Settings*

To operationalize settings, we extract the location of the speech and create four distinct settings: Amazonian states within Brazil, non-Amazonian states within Brazil, Amazonian countries, and non-Amazonian countries. Each one of these settings encompasses audiences that can have different expectations in reference to our policy object, the Brazilian Amazon. When speaking at Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon. Such expectations might be distinct from the ones audiences in Brazil, but outside of the Amazonian region, have for the same policy object. During visits to Amazonian countries, presidents may view them as peers facing similar challenges and adjust their speeches accordingly. Conversely, when speaking in non-Amazonian countries or at international events such as the UNFCCC or visits to the US or France, presidents may tailor their speeches to align with what they perceive as possible symbolic or material gains from the audience.

This operationalization of settings comes with limitations. While we would ideally like to capture the exact venue of the speech (i.e. multilateral mechanism, private fora, bilateral visit, bridge inauguration), it is difficult to programmatically code exact locations from thousands of speeches that often mention multiple locations in the same text. Nevertheless, we believe the four settings coded are already enough to demonstrate whether, and how, problem-construction might change transnationally.

*Pressingness*

Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their pressingness over time. To capture the pressingness of problems, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates. When deforestation rates are high, the problem of environmental conservation can be perceived as more pressing. Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more pressing. We opt for lagging deforestation rates by one year as the consolidated rates for a certain year are published in the following year. Since both annual deforestation rates and annual inflation rates come in different measurements (i.e. percentage and kilometers square) we scale these values to facilitate interpretation of coefficients. Scaling variables do not affect statistical inference in regression models.

This approach to operationalizing pressingness also has its limitations. Ideally, we would like to add additional proxies of pressingness for social and sovereignty issues. However, social development indicators (e.g. life expectancy, education levels, access to sanitation) generally increased over time in Brazil. In terms of national sovereignty, the way we conceptualize the problem-construction entails internal and external threats which are not easily measured. Despite these limitations, we can draw some conclusions from the pressingness of environmental and economic issues and their aligned problem-constructions.

## 3.4 Inferential and descriptive strategies

We use fixed-effect logistic regression models (indexed by president) to predict the probability of a speech mentioning the Amazon (model 1) and each of the four problem-constructions (models 2-5). The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes (i.e. ideology). For instance, if a president’s political ideology predicts variation in our dependent variables, fixed-effects could control for such issues along other unit-unvarying characteristics [@allison2009].

The dependent variables of the model are the share of speeches that mention the Amazon (model 1) and the share of a problem-construction (models 2-5). We chose to model each construction separately, and to focus on pure-types (i.e. statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust coefficients. Our main explanatory variables are settings and pressignness, as described above.

We also add two control variables in the models: election years and peak years. In the case of election years, we control for the possibility of presidents constructing the Amazon in systematically different ways in those years. In the case of peak years, these are years in which the Amazon was disproportionately more mentioned as a share of all presidential speeches. We calculate these by capturing years in which mentions of the Amazon are above one standard deviation from their mean share.

We wrap the analysis with a descriptive and longitudinal analysis of Amazonian speeches in time, considering the findings of the models. It is important to outline that we do not make any causal claims. Many scholars inquire and find causal relationships between discourse and outcomes. Our research design and data do not allow us to do so. Instead, we focus on the relationships in themselves rather than their order or cause.

# 4. How has the Brazilian Amazon been constructed as a problem?

We open our analysis with the models predicting the probability of presidents mentioning the Amazon in speeches (model 1) and of presidents employing certain problem-construction (model 2-5). Subsequently, we plot and discuss the longitudinal developments of Amazonian speeches and of problem-constructions considering the model results.

## 4.1 The Amazon as a transnational problem: setting and pressingness

We argue that presidents’ expectations about an audience at a certain setting and the pressingness of specific problems explain variations in when the Amazon becomes a  problem and how it is constructed as a type of problem it is. Our models, below, confirm the relationships expected by our framework.

````{=tex}
\begin{landscape}

```{r models president fixed effect, fig.cap="Log odds for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
# Run models
c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c5 <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI +  election_year,
                         data = ama_model2_lag,
                         model = "within", index = "president")
# Regression table                       
stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Log odds for fixed-effects logistic regressions indexed by president",
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                         "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Election Year",
                                          "Peak years"))
```

\end{landscape}
````

As we argue that the effects of setting and pressingness are cumulative, we start by first scrutinizing the relationship between the former and problem-construction. Model 1 addresses the question of when the Amazon is a problem to begin with. We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian States within Brazil. The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.

The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings. In terms of environmental conservation (model 2), we observe that when speaking at non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category). To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil where they are more likely to construct the Amazon as an issue of environmental conservation. While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: both are less likely outside Brazil. Finally, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they are speaking elsewhere.

Overall, we interpret these results as evidence that presidents construct the Amazon as different problems based on their expectations of an audience at certain settings. When it comes to non-Amazonian countries, it is likely that Brazilian presidents construct the Amazon as an issue of environmental conservation to leverage financial support for the Amazonian region. The Brazilian government successfully funded domestic public policy with transnational financial support on several occasions since the 1990s, most notably with the Amazon Fund or policies in the Amazon which provided over USD 1 billion for the region along with multiple bilateral and philanthropic grants [@silva-muller2022]. That is, presidents realize material and symbolic gains outside of Brazil and of Amazonian countries, by constructing the Amazon as an environmental problem.

In turn, when speaking within the Brazilian Amazon, presidents see their audiences as local constituencies. Therefore, presidents never stopped pursuing a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds. For example, rural credit offered to local agricultural producers in Amazonian states went up from 500 million reais a year in 1999, to over 4 billion reais a year by 2012 [@capobianco2021]. As well, the special fiscal regime in Manaus, designed to increase industry presence in the region, was largely maintained. Moreover, additional roads and dams (e.g. the BR-163 highway and the Belo Monte dam and hydroelectric power plant) were constructed during the same period. Presidents likely highlight and push for economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.

We also argue that the pressingness of an aligned problem in time influences the likelihood of the president mentioning the Amazon and what they will say. We find evidence across our models that this holds. For instance, we find that presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the pressingness of environmental problems (model 1). The opposite is true for inflation. As inflation increases, and so the pressingness of economic problems, presidents are more likely to generally mention the  Amazon in speeches (model 1). This relationship is even more interesting when we look at how amazonian constructions vary in presidential speeches as environmental or economic problems become more pressing (models 2-3). We find strong evidence that when the pressingness of environmental problems increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases. Alternatively, as the pressingness of economic problems increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation  increases.

In line with our framework, the pressingness of aligned problems relates to problem-constructions in intricate ways. By opting for an alternative problem-construction to that which is pressing, presidents likely side-step issues as they get more pressing, while boosting positive aligned outcomes to attempt and collect benefits as aligned issues become less pressing.

## 4.2 Amazonian speeches in time

Looking at speeches that mention the Amazon in time (the dependent variable of model 1) reviews several interesting trends. Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year. By investigating its development in time, we can identify instances when the Amazon in itself becomes more pressing as a problem, and when not. On average, presidents mention the Amazon in 15.5% of their speeches ^[For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).]. This suggests the Amazon is a topic of relative high importance for presidents generally. However, we observe four peak years (one standard deviation from the mean) in the figure: 1989, 1992, 2009, and 2019. We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.

```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year)) %>%
  ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  geom_line(aes(y=mean(perc)), color="black", linewidth=.5, linetype="dotted")+
  scale_y_continuous(labels = percent_format()) + 
  annotate("text", x = 1985, y = 0.165, label = "15.5%", size = 3.5)+
  annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
  annotate("text", x = 1992.5, y = 0.26, label = "Earth Summit", size = 3)+
  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
  labs(x = "", y = "",
       title = "Share of speeches that mention the Amazon per year",
       subtitle = "Sample composed by all 6240 speeches since 1985",
       color='Y series') +
  theme_am()
```

```{r comparisonq, eval=FALSE, include=FALSE}
mean(mean_perc$perc) # 15.53 mean for Amazonian speeches
# Comparison with inflation, criminality, unemployment, and inequality
pop %>%
  mutate(desigual = ifelse(grepl("desigual", text,
                                 ignore.case = TRUE), 1, 0),
         crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
                              text, ignore.case = TRUE), 1, 0),
         inf = ifelse(grepl("inflacao|inflaçao",
                             text, ignore.case = TRUE), 1, 0),
         unemploy = ifelse(grepl("desempreg",
                             text, ignore.case = TRUE), 1, 0)) %>%
  summarise(desigual = mean(desigual),
            crime = mean(crime),
            inf = mean(inf),
            unemploy = mean(unemploy))
```

In 1989 the Amazon appeared in 32% of all speeches. This coincides with the brutal murder of the environmental activist Chico Mendes in the last days of 1988. The incident caught unprecedented transnational media attention and then President Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021]. One of the responses was the offer and acceptance to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992. During the summit, we saw the realization of the first transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest (PPG7), which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].

Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, the Amazon as a topic did not diverge much from the average. This is aligned with our model as the pressingness of the environmental problem was high during the period. In 2009, however, we observed another peak which coincided with the Copenhagen Summit. Lula led the delegation to the summit with a strong climate leadership self-image of “we deliver” [@franchini2019], in a moment when deforestation rates have been decreasing since 2005. From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches. In this period,  the pressingness of environmental problems was increasing as deforestation rates were rising. The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016. By 2016 mentions of Amazon in official speeches went down to 6%, their lowest share since 1985.

We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro’s presidency. At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019. Right after being elected in 2018, Bolsonaro went on to retrieve Brazil’s hosting status for COP25. Alongside, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches. This event also drove the proportion of speeches mentioning the Amazon up.

The figure 2, above, also shows that the frequency in which the Amazon is mentioned, as a general topic in speeches, is not related by proposed policy solutions. In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022]. In 2004, President Lula decreed the creation of Brazil’s Plan to Combat and Control Deforestation in the Brazilian Amazon. In 2008, Brazil announced the Amazon Fund, the largest fund of this kind ever created. Finally, in 2012, the revision of the Forest Code, debated in 2010 and 2011, pardoned thousands of illegal deforesters in the Amazon [@sant2021]. Yet, these policy landmarks do not seem to be systematically meaningful for when Amazon is mentioned as a general problem more often.

The longitudinal trends in Amazonian speeches reveal a dynamic that our models did not capture: we find that all peak years relate to high-profile environmental events within the country that gained large repercussions within and outside of the country. These are events that received distinct coverage from transnational actors as media and civil society outside of Brazil, which is likely one of the reasons why it temporarily drives the topic up. This suggests that the Amazon is mentioned more in presidential speeches as transnational attention towards it increases. While our measure of pressingness of the environmental problem does not capture these events, these events change how pressing of a problem the Amazon is in certain years. In doing so, these events bring outside attention to the Amazon to which the president's response is more likely to be in the form of reaffirming Brazil’s sovereignty over the Amazon (model 5). That is, presidents tend to construct the Amazon as an issue of national sovereignty and side-step the aligned environmental conservation constructions around high-profile environmentally related events.

## 4.3 Amazonian problem-constructions in time

While we identified the effects of setting and pressingness on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. In this section, we investigate how pure-types and mixed-types problem-constructions evolved over time. Figure 3, below, illustrates the annual share of pure-types problem-constructions.

```{r Figure pure, fig.cap="Pure-types constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat != "Other",
         mx_cat != "Mixed-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of pure-types problem-constructions by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  theme(legend.position = "bottom") +
  scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
                                  "Social Development", "National Sovereinty"))
```

Pure economic integration constructions were the most frequent from 1985 to 2009. This is especially pertinent during Cardoso’s presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased. This was a period when the pressingness of the environmental problem grew as deforestation rates were increasing, so presidents were more likely to avoid environmental conservation constructions. When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased. During this period, the pressingness of environmental problems decreased along with deforestation rates, so presidents are more likely to employ environmental conservation constructions. From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration. However, this reversal was not long-standing. With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored again.

We also notice a steady increase of sovereignty as salient problem-constructions from 2008 onwards, much before Bolsonaro was elected. This might relate to policy developments that were taking place. The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government [@horochovski2016]. In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil’s sovereignty over the Amazon while rebating  broad criticism from civil society actors with accusations of internationalization attempts. Therefore, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making. Bolsonaro’s problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.

Our operationalization of problem-constructions also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement. Figure 4, below, shows that constructing the Amazon as multiple issues increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions. Mixed-type problem-constructions in discourse offer more complex and balanced understandings of the Amazon as a problem. The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.  Indeed, we observe an increase in policies that attempt to address environmental and social problems, for instance, at the same time. Examples of this are payment for ecosystem services conditioned for low income populations residing in the Amazon [@silva-muller2022a]. Relatedly, this is aligned with transnational processes as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.

```{r Figure mixed, fig.cap="Mixed-types problem constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat == "Mixed-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  scale_color_manual(values = "yellow3")
```

We interpret the balance in pure-types and the increase in mixed-types as evidence that presidents increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years decades. We see in these findings the possibility of the Amazon becoming an increasingly coherent transnational problem, where audiences do not only recognize it as a single pure-type but an intricate policy object.

# 5. Conclusion

This paper investigated where, when, and how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985. We have four main empirical findings. First, we find that presidents construct the Amazon as different problems depending on where they speak. When presidents speak outside the country and far away from the Amazon, they are more likely to construct the Amazon as an issue of environmental conservation. Within the country or the Amazonian region, presidents prefer constructing the Amazon as issues of social development and economic integration. Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not pressing (e.g. low deforestation rates). When environmental related problems become more pressing (e.g. rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as different issues as economic integration. Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency in which the Amazon appears in discourse. Relevant Amazonian related policies, in turn, appear not to affect how much discursive attention is paid to the Amazon by presidents. Finally, we find that we are now in a period where the dictum between seeing the Amazon as an environment or an economic issue has been overcome, at least discursively, as Amazonian problem-constructions have become more mixed and balanced lately.

The conceptual implications of our findings are at least threefold. First, we provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions. In so doing, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented. We show that investigating problem-representation to begin with, can highlight the extent to which certain perspectives of problems are assumed, ignored or privileged. Second, while many analyses of Brazilian environmental policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios (Hoschstetler and Keck, 2004). Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time. In doing so, we can contextualize problem-constructions in space and show how they vary. Third, we argue that another key factor in explaining variation in problem-construction is the pressingness of specific problems in time. As the environmental crisis increases in its salience, important actors are less likely to ignore it. They need to find strategies, such as side-stepping issues or boasting positive outcomes, in order to remain credible to their audiences.

In terms of future research, we see at least three possibilities. First, we have introduced a flexible framework that can be extended to cover other policy objects. We expect to inspire some to investigate other policy objects in domains beyond the Brazilian Amazon (e.g. Cerrado biome, Antarctic, inequality, criminality, etc.). This opens up the possibility of interesting time and space  comparisons. Relatedly, as we find evidence that problem-constructions in Amazonian countries differ from other settings, scholars should investigate how Amazonian problem-constructions in other Amazonian countries differ, and not, from the ones we see in the Brazilian case. Second, while we argue that settings are important to explaining variation in problem-constructions, social media can change this in fundamental ways. As short videos of presidential discourses travel more rapidly than ever, social media might contribute to diminishing the importance of physical settings. This could make presidents less likely to afford very diverging problem-constructions anymore. Alternatively, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences. We look forward to works that investigate how setting and audience interact with problem-construction in unofficial political communications in the era of social media. Finally, while we do not explicitly conceptualize the possibility of problem-constructions having a direct effect on policy outcomes, it is possible, though, to design studies that test the causal relationship between presidential discourse and outcomes. In a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro’s speech to covid-19 infections. We look forward to studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.

# Acknowledgements

The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support. The authors would also like the two anonymous reviewers for their comments and suggestions. Finally, we would like to thank Anna, Federico, Mario, and Rodrigo for their invaluable help.

# Disclosure Statement

The authors report that there are no competing interests to declare.

# References

::: {#refs}
:::

# Appendix

````{=tex}
\begin{landscape}

```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
codebook <- tibble::tibble("problem-construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty. We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory. Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon. In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration. It advances the view that the Amazon needs to be developed and connected to the national economy. This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development. It advances the view that Amazon is full of citizens who should have their rights guaranteed. This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house). This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light. Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation. This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region. The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered. It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity. I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting. I would like to thank the Chinese government. For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil. (Bolsonaro 25/10/2019)",
                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions. We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway. This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas. We have invested over 14 billion reais in this program, in three and a half years. Do you know how many electrical lines we have already built? One million kilometers of lines. (Lula 20/11/2009)",
                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process. This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr. Mesquita (Sarney 20/07/1989)"))

kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
```

\end{landscape}
````

````{=tex}
\begin{landscape}

```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
# Calculate the custom CIs
ci1 <- exp(confint(c1))
ci2 <- exp(confint(c2))
ci3 <- exp(confint(c3))
ci4 <- exp(confint(c4))
ci5 <- exp(confint(c5))
# Regression table                       
stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Odds-ratio for fixed-effects logistic regressions indexed by president",
                     ci = T, apply.coef = exp,
                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
                     t.auto=F, p.auto=F,
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                         "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Election Year",
                                          "Peak years"))
```

\end{landscape}
````

### 2023-02-14 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
with changes

@@
 - Livio Silva-Muller
-- Henrique Sposito^[Both co-authors contributed equally to the article.
+- Henrique Sposito^[Both authors contributed equally to the article.
 Names are ordered alphabetically.
@@
 We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) pressing, presidents are likelier to highlight issues of environmental conservation (or economic integration).
-Furthermore, we show how we are moving from a period when the binary between seeing the Amazon as an environmental or an economic issue has been overcome, to a moment when diverse problem-constructions are deployed.
+Furthermore, we show how we are moving from a period when the Amazon as a binary of either environmental or an economic issue has been overcome, to a moment when diverse problem-constructions are deployed.
 
@@
 While the military dictatorship (1964-85) and Bolsonaro’s presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are associated with environmental conservation.
-Yet, such representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
+Yet, such representations advance the view that governments act consistently towards the Amazon as a specific problem, masking government diversity of in policies and discourse.
 In this article, we show where, when, and how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
@@
 We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem pressingness as actors participate and shape transnational politics.
-We focus on transnational speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem.
+We focus on speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem.
 While many analyses of Brazilian environmental discourse and policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
@@
 
-To answer our question, we create a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
+To answer how the Amazon has been constructed as a problem, we create a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
 Next, we identify all instances where the presidents mention the Amazon.
@@
 We have four main findings.
-First, we find that presidents adopt different Amazonian constructions  in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
-Second, presidents often focus on alternative problem-constructions when general aligned problems become more pressing; whereas they boast about positive outcomes when aligned problems are less pressing.
-Third, we also find that high-profile environmental related events, which receive strong international media attention, drive up the importance of the Amazon as a general topic in presidential speeches.
+First, we find that presidents adopt different constructions of the Amazon in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
+Second, presidents often focus on alternative problem-constructions when problems become more pressing; whereas they boast about positive outcomes when problems are less pressing.
+Third, we find that high-profile environmental related events, which receive strong international media attention, increase the importance of the Amazon in presidential speeches.
 Alternatively, relevant Amazonian-related policies appear to not to attract much attention.
@@
 Social scientists have shown how governments have contradictory policies [@lopez2023; @fairfield2017; @poncedeleon2021].
-In the case of the Amazon, it has often been seen as a key biome in global climate-mitigation, and consequently, as an environmental problem.
+The Amazon has often been seen as a key biome in global climate-mitigation, and consequently, as an environmental problem.
 If the Amazon is thought of as an “environmental” problem, then it demands an “environmental” solution.
-However, in order to build a more comprehensive account of the Amazon as forest, region, and peoples we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
+However, to build a more comprehensive account of the Amazon as forest, region, and peoples we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
 
@@
 
-Following Bacchi, we place discourse about policy objects in the center of our conceptual framework.
-We define policy objects as political objects that demand dedicated political attention.
-We argue that by deciding to speak about a policy object, governments are making a deliberate choice.
-When speaking about policy objects, governments make a choice to represent, or construct it, as a specific problem.
+Following Bacchi, we place discourse about policy objects at the center of our conceptual framework.
+We define policy objects as objects that demand dedicated political attention and argue that by deciding to speak about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem.
 The problem might be either explicitly stated, or implicitly hidden in the underlined solution.
@@
 Presidential discourses are a good instance to identify problem-constructions over time.
-While the relationship between presidential and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
+While the relationship between presidential speeches and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
 This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution[@macaulay2017].
-In  Brazil’s hybrid system, often referred to Coalitional Presidencialism [@couto2021], presidents build legislative support for a broad agendas through the distribution of positions in the state bureaucracies.
+In Brazil’s hybrid system, often referred to Coalitional Presidencialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies.
 This means that presidents have enough power and support to implement the agenda they deem appropriate.
@@
 While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups.
-Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interest of different groups.
+Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups.
 Adopting two-level games to explain American presidential speeches, @calderwood2019 and @calderwood2020 find supporting evidence of this theory.
@@
 
-While their theory is developed in the context of value-based advocacy groups, this is non-state actors, the overall view of international politics as structured and structuring, should hold for state actors as well.
-Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
+While their theory is developed in the context of value-based advocacy groups, hence non-state actors, the overall view of international politics as structured and structuring, should hold for state actors as well.
+Important participants of transnational networks, as presidents, can use myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
 They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p.
 24].
-Or, they can leverage institutions to realize symbolic or material gains.
-In this sense, the positions of actors as components of a transnational network derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.
+They can also leverage institutions to realize symbolic or material gains.
+In this sense, the positions of actors in transnational networks derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.
 
@@
 Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study.
-This indicates that how presidents construct policy objects as problems can vary, for instance, within the country — speaking inside the Amazon region versus outside — because presidents identify these audiences as sources of different types of support and demand.
-The same holds when speaking outside the country — in Amazonian countries, non-Amazonian countries, and international summits — where expectations and identities of audiences could diverge completely from that of domestic actors.
-In each one of these settings different problems might be more pressing and the president's expectations about what can be leveraged for material and symbolic gains might drive how a problem is implicitly or explicitly constructed.
+This indicates that how presidents construct policy objects as problems can vary, for instance, within the country — speaking inside the Amazon region versus outside — because presidents identify these audiences as sources of distinct types of support and demand.
+The same holds true when speaking abroad — in Amazonian countries, non-Amazonian countries, and at international summits — where presidents’ expectations and identities of an audiences could diverge completely from that of domestic actors.
+In each one of these settings different problems might be more pressing and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.
 
@@
 
-How presidents construct policy objects can also vary in time because the pressingness of certain problems changes as new information arises.
+How presidents construct policy objects can also vary over time because the pressingness of certain problems changes as new information arises.
 We conceptualize time as the perceived pressingness of a broad and related issue to those surrounding a policy object.
-This indicates, for instance, that as climate change becomes more pressing and widespread as a broad issue, it is more likely that actors will consider climate change when discussing various forms of public policy.
-It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change.
-Conversely, today, if fossil fuel subsidies are discussed, climate change will likely be an issue given the increased pressingness of the topic in comparison to the 1980s.
+This indicates, for instance, that as climate change becomes more pressing and mainstreamed as a broad issue, it is more likely that actors will consider it when discussing various forms of public policy.
+It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased global attention.
 
@@
 Our conceptual framework, thus, combines Bacchi’s theory of problem-representation and Keck and Sikkink’s theory of transnationalism to account for diverse problem-constructions.
-It helps to advance the literature about the Amazon in two ways: We provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions.
+We help to advance the literature about the Amazon in two ways.
+First, we provide an outlook of the region, its people and forest beyond its environmental issues by focusing on different problem-constructions.
 In doing so, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented as a problem.
-Furthermore, many analyses of Brazilian environmental policies dissect its national and international nature but fail to adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
+Second, many analyses of Brazilian environmental policies dissect its national and international nature but do not adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
 Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
@@
 We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development.
-While the three former are in the literature, we argue a fourth one, social development, exists.
+While the three formers are present in the literature, we argue a fourth one exists in speeches: social development.
 
@@
 In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
-8].
-While the Brazilian military diplomacy was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990].
-These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil’s sovereignty over the Amazon [@rajao2020].
+8], and secured the Amazon as Brazilian.
+While military diplomacy was very successful, the process did not come without its issues and sovereignty in the Amazon became one of the main military concerns[@rajao2020].
 More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become more varied.
@@
 *Environmental Conservation*
-The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
+The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
 The creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
@@
 Each one of these settings encompasses audiences that can have different expectations in reference to our policy object, the Brazilian Amazon.
-When speaking at Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon.
-Such expectations might be distinct from the ones audiences in Brazil, but outside of the Amazonian region, have for the same policy object.
-During visits to Amazonian countries, presidents may view them as peers facing similar challenges and adjust their speeches accordingly.
+When speaking in Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon.
+Such expectations might be distinct from the ones’ audiences in non-Amazonian Brazilian States.
+Furthermore, during visits to Amazonian countries, presidents may perceive them as peers facing similar challenges and adjust their speeches accordingly.
 Conversely, when speaking in non-Amazonian countries or at international events such as the UNFCCC or visits to the US or France, presidents may tailor their speeches to align with what they perceive as possible symbolic or material gains from the audience.
@@
 In the case of election years, we control for the possibility of presidents constructing the Amazon in systematically different ways in those years.
-In the case of peak years, these are years in which the Amazon was disproportionately more mentioned as a share of all presidential speeches.
+In the case of peak years, these are years in which the Amazon was mentioned more often as a share of all presidential speeches.
 We calculate these by capturing years in which mentions of the Amazon are above one standard deviation from their mean share.
@@
 The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings.
-In terms of environmental conservation (model 2), we observe that when speaking at non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
+In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
 To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil where they are more likely to construct the Amazon as an issue of environmental conservation.
@@
 
-## 4.2 Amazonian speeches in time
+## 4.2 Amazonian speeches over time
 
-Looking at speeches that mention the Amazon in time (the dependent variable of model 1) reviews several interesting trends.
+Looking at speeches that mention the Amazon over time (the dependent variable of model 1) reviews several interesting trends.
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
@@
 The incident caught unprecedented transnational media attention and then President Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
-One of the responses was the offer and acceptance to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
+One of the responses was to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
 During the summit, we saw the realization of the first transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest (PPG7), which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
 
-Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, the Amazon as a topic did not diverge much from the average.
+Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, there were no peaks.
 This is aligned with our model as the pressingness of the environmental problem was high during the period.
@@
 
-The figure 2, above, also shows that the frequency in which the Amazon is mentioned, as a general topic in speeches, is not related by proposed policy solutions.
+The figure 2, above, also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, is not related to proposed policy solutions.
 In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022].
@@
 When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-During this period, the pressingness of environmental problems decreased along with deforestation rates, so presidents are more likely to employ environmental conservation constructions.
+During this period, the pressingness of environmental problems decreased along with deforestation rates, so presidents were more likely to employ environmental conservation constructions.
 From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration.
-However, this reversal was not long-standing.
-With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored again.
+However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored again.
 
@@
 When presidents speak outside the country and far away from the Amazon, they are more likely to construct the Amazon as an issue of environmental conservation.
-Within the country or the Amazonian region, presidents prefer constructing the Amazon as issues of social development and economic integration.
+Within the country or the Amazonian region, presidents prefer constructing the Amazon as an issue of social development and economic integration.
 Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not pressing (e.g.
@@
 When environmental related problems become more pressing (e.g.
-rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as different issues as economic integration.
-Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency in which the Amazon appears in discourse.
-Relevant Amazonian related policies, in turn, appear not to affect how much discursive attention is paid to the Amazon by presidents.
-Finally, we find that we are now in a period where the dictum between seeing the Amazon as an environment or an economic issue has been overcome, at least discursively, as Amazonian problem-constructions have become more mixed and balanced lately.
+rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
+Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourse.
+Relevant Amazonian related policies, in turn, do not affect the discursive attention presidents pay to the Amazon.
+Finally, we find that we are now in a period when the Amazon as a binary of either environmental or an economic issue has been overcome, at least discursively, and Amazonian problem-constructions have become more mixed and balanced lately.
 
@@
 First, we have introduced a flexible framework that can be extended to cover other policy objects.
-We expect to inspire some to investigate other policy objects in domains beyond the Brazilian Amazon (e.g.
+We expect to inspire investigations of other policy objects in domains beyond the Brazilian Amazon (e.g.
 Cerrado biome, Antarctic, inequality, criminality, etc.).
-This opens up the possibility of interesting time and space  comparisons.
-Relatedly, as we find evidence that problem-constructions in Amazonian countries differ from other settings, scholars should investigate how Amazonian problem-constructions in other Amazonian countries differ, and not, from the ones we see in the Brazilian case.
+Relatedly, as we find evidence that problem-constructions in Amazonian countries differ from other settings, scholars could investigate how Amazonian problem-constructions in other Amazonian countries differ, and not, from the ones we see in the Brazilian case.
 Second, while we argue that settings are important to explaining variation in problem-constructions, social media can change this in fundamental ways.

### 2023-02-14 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
newest

@@
 csl: chicago.csl
-abstract: The Amazon is often approached as a transnational environmental problem without a discussion of how key actors see it differently in space and time.
+abstract: The Amazon is often approached as a transnational environmental problem without a discussion of how key actors represent it differently in space and time.
 We combine theories of problem-representation and transnationalism to analyze where, when, and how the Brazilian Amazon has been constructed as a problem.
-We develop a framework that explains variation in transnational problem-constructions based on speech setting and problem pressingness.
-To test our framework, we use supervised machine learning to classify statements about the Amazon in 6240 presidential speeches since 1985.
-We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) pressing, presidents are likelier to highlight issues of environmental conservation (or economic integration).
+We develop a framework that explains variation in transnational problem-constructions based on speech setting and problem urgency To test our framework, we use supervised machine learning to classify statements about the Amazon in 6240 presidential speeches since 1985.
+We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) urgent, presidents are likelier to highlight issues of environmental conservation (or economic integration).
 Furthermore, we show how we are moving from a period when the Amazon as a binary of either environmental or an economic issue has been overcome, to a moment when diverse problem-constructions are deployed.
@@
 ```{=latex}
-\wordcount{ 8765 (including abstract, text, references, and footnotes)}
+\wordcount{ 8190 (including abstract, text, references, and footnotes)}
 ```
@@
 > *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion.
-First of all, these NGOs should go plant trees in their own countries [...]"
-(President Lula, Cuiaba - MT, 2007).*
+First of all, these NGOs should go plant trees in their own countries [...]" (President Lula, Cuiaba - MT, 2007).*
 
@@
 
-Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a single view of the region, its people, and forest [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-While the military dictatorship (1964-85) and Bolsonaro’s presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are associated with environmental conservation.
-Yet, such representations advance the view that governments act consistently towards the Amazon as a specific problem, masking government diversity of in policies and discourse.
-In this article, we show where, when, and how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
+*We need to protect the Amazon from foreign interests.
+We need to exploit the Amazon's natural resources.
+We need to provide better living standards for the people in the Amazon.
+We need to preserve the Amazon as a standing ecosystem.* Each of these statements represent the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.
+These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.
+Brazilian governments have been portrayed in the literature as having held differing views on the Amazon, with some prioritizing national sovereignty and economic integration (military dictatorship and Bolsonaro), while others prioritize environmental conservation (Sarney and Lula).
+However, this oversimplifies government policies and discourse, which in reality are more intricate and contradictory.
 
 By combining @bacchi1999’s theory of problem representation and @keck1998's theory of transnationalism, we place the way the objects of policies are constructed in discourse at the center of our analysis.
-We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem pressingness as actors participate and shape transnational politics.
+We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem urgency as actors participate and shape transnational politics.
 We focus on speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem.
@@
 Our framework and methodology help identify and account for these variations.
-We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil’s agricultural powerhouses, in a moment when the environmental problem is pressing, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
+We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil’s agricultural powerhouses, in a moment when the environmental problem is urgent, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
 
@@
 We have four main findings.
-First, we find that presidents adopt different constructions of the Amazon in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
-Second, presidents often focus on alternative problem-constructions when problems become more pressing; whereas they boast about positive outcomes when problems are less pressing.
-Third, we find that high-profile environmental related events, which receive strong international media attention, increase the importance of the Amazon in presidential speeches.
+First, presidents adopt different constructions of the Amazon in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
+Second, presidents often focus on alternative problem-constructions when problems become more urgent; whereas they boast about positive outcomes when problems are less urgent.
+Third, high-profile environmental related events, which receive strong international media attention, increase the importance of the Amazon in presidential speeches.
 Alternatively, relevant Amazonian-related policies appear to not to attract much attention.
-Finally, we find that while all presidents deploy multiple problem-constructions across space and over time, we are now in a period when the dictum between understanding the Amazon as an environment or as an economic issue has been overcome, at least discursively.
-Conceptually, our research shows how focusing on problem-constructions highlight what certain objects of policy are assumed to be, and when they are ignored or privileged, based on the transnational setting of the speech and the pressingness of aligned problems.
+Finally, while all presidents deploy multiple problem-constructions across space and over time, we are now in a period when the dictum between understanding the Amazon as an environment or as an economic issue has been overcome, at least discursively.
+Conceptually, our research shows how focusing on problem-constructions highlight what certain objects of policy are assumed to be, and when they are ignored or privileged, based on the transnational setting of the speech and the urgency of aligned problems.
 
@@
 
-# 2. Theory: problem-constructions, transnational settings, and problem pressingness
+# 2. Theory: problem-constructions, transnational settings, and problem urgency
 
-We divide our theoretical framework in two parts.
-We start with an explanation of what are problem-constructions and why presidential speeches are an interesting instance to identify them.
-Next, we argue that problem-constructions can vary depending on the transnational setting of the speech and on the pressingness of its problem.
-
-## 2.1 Problem representation in presidential discourse
+## 2.1 Problem-representation in presidential discourse
 
@@
 The presidencies of Rousseff (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, while Bolsonaro (2019-2022) with the dismantling of environmental policies [@capobianco2019].
-Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into cohesive policy periods, or policy cycles, with one all-encompassing understanding of the Amazon.
+Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into cohesive policy periods, or policy cycles, masking government diversity in policies and discourse.
 
@@
 
-## 2.2 Transnational settings, pressingness, and variation in problem-constructions
+## 2.2 Transnational settings, urgency, and variation in problem-constructions
 
@@
 If malleable identities across space and time are a defining feature of transnational politics, it follows that presidents' choice of problem-constructions depend on the president's views of an audience at a certain period.
-Specifically, how pressing a problem is in a certain space and/or at a certain time.
+Specifically, how urgent a problem is in a certain space and/or at a certain time.
 
@@
 The same holds true when speaking abroad — in Amazonian countries, non-Amazonian countries, and at international summits — where presidents’ expectations and identities of an audiences could diverge completely from that of domestic actors.
-In each one of these settings different problems might be more pressing and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.
+In each one of these settings different problems might be more urgent and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.
 
@@
 
-How presidents construct policy objects can also vary over time because the pressingness of certain problems changes as new information arises.
-We conceptualize time as the perceived pressingness of a broad and related issue to those surrounding a policy object.
-This indicates, for instance, that as climate change becomes more pressing and mainstreamed as a broad issue, it is more likely that actors will consider it when discussing various forms of public policy.
+How presidents construct policy objects can also vary over time because the urgency of certain problems changes as new information arises.
+We conceptualize time as the perceived urgency of a broad and related issue to those surrounding a policy object.
+This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider it when discussing various forms of public policy.
 It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased global attention.
 
-While time and space might interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change pressing, certain transnational actors would likely mention it as a problem independently of the perceived pressingness of a climate breakdown at the time.
+While time and space might interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, certain transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
 Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
@@
 
-## 3.3 Operationalizing settings and pressingness
+## 3.2 Operationalizing settings and urgency
 
-Our explanation for variation in problem-constructions is based on the setting of a speech and the pressingness of an aligned problem. This comprises our independent variables.
+Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of an aligned problem. This comprises our independent variables.
 
@@
 
-*Pressingness*
+*Urgency*
 
-Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their pressingness over time.
-To capture the pressingness of problems, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
-When deforestation rates are high, the problem of environmental conservation can be perceived as more pressing.
-Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more pressing.
+Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their urgency over time.
+To capture the urgency of problems, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
+When deforestation rates are high, the problem of environmental conservation can be perceived as more urgent.
+Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more urgent.
 We opt for lagging deforestation rates by one year as the consolidated rates for a certain year are published in the following year.
@@
 
-This approach to operationalizing pressingness also has its limitations.
-Ideally, we would like to add additional proxies of pressingness for social and sovereignty issues.
+This approach to operationalizing urgency also has its limitations.
+Ideally, we would like to add additional proxies of urgency for social and sovereignty issues.
 However, social development indicators (e.g.
@@
 In terms of national sovereignty, the way we conceptualize the problem-construction entails internal and external threats which are not easily measured.
-Despite these limitations, we can draw some conclusions from the pressingness of environmental and economic issues and their aligned problem-constructions.
+Despite these limitations, we can draw some conclusions from the urgency of environmental and economic issues and their aligned problem-constructions.
 
-## 3.4 Inferential and descriptive strategies
+## 3.3 Inferential and descriptive strategies
 
@@
 statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust coefficients.
-Our main explanatory variables are settings and pressignness, as described above.
+Our main explanatory variables are settings and urgency, as described above.
 
@@
 
-## 4.1 The Amazon as a transnational problem: setting and pressingness
+## 4.1 The Amazon as a transnational problem: setting and urgency
 
-We argue that presidents’ expectations about an audience at a certain setting and the pressingness of specific problems explain variations in when the Amazon becomes a  problem and how it is constructed as a type of problem it is.
+We argue that presidents’ expectations about an audience at a certain setting and the urgency of specific problems explain variations in when the Amazon becomes a  problem and how it is constructed as a type of problem it is.
 Our models, below, confirm the relationships expected by our framework.
@@
 
-As we argue that the effects of setting and pressingness are cumulative, we start by first scrutinizing the relationship between the former and problem-construction.
+As we argue that the effects of setting and urgency are cumulative, we start by first scrutinizing the relationship between the former and problem-construction.
 Model 1 addresses the question of when the Amazon is a problem to begin with.
@@
 
-We also argue that the pressingness of an aligned problem in time influences the likelihood of the president mentioning the Amazon and what they will say.
+We also argue that the urgency of an aligned problem in time influences the likelihood of the president mentioning the Amazon and what they will say.
 We find evidence across our models that this holds.
-For instance, we find that presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the pressingness of environmental problems (model 1).
+For instance, we find that presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the urgency of environmental problems (model 1).
 The opposite is true for inflation.
-As inflation increases, and so the pressingness of economic problems, presidents are more likely to generally mention the  Amazon in speeches (model 1).
-This relationship is even more interesting when we look at how amazonian constructions vary in presidential speeches as environmental or economic problems become more pressing (models 2-3).
-We find strong evidence that when the pressingness of environmental problems increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
-Alternatively, as the pressingness of economic problems increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation  increases.
+As inflation increases, and so the urgency of economic problems, presidents are more likely to generally mention the  Amazon in speeches (model 1).
+This relationship is even more interesting when we look at how amazonian constructions vary in presidential speeches as environmental or economic problems become more urgent (models 2-3).
+We find strong evidence that when the urgency of environmental problems increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
+Alternatively, as the urgency of economic problems increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation  increases.
 
-In line with our framework, the pressingness of aligned problems relates to problem-constructions in intricate ways.
-By opting for an alternative problem-construction to that which is pressing, presidents likely side-step issues as they get more pressing, while boosting positive aligned outcomes to attempt and collect benefits as aligned issues become less pressing.
+In line with our framework, the urgency of aligned problems relates to problem-constructions in intricate ways.
+By opting for an alternative problem-construction to that which is urgent, presidents likely side-step issues as they get more urgent, while boosting positive aligned outcomes to attempt and collect benefits as aligned issues become less urgent.
 
@@
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-By investigating its development in time, we can identify instances when the Amazon in itself becomes more pressing as a problem, and when not.
+By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not.
 On average, presidents mention the Amazon in 15.5% of their speeches ^[For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).].
@@
 Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, there were no peaks.
-This is aligned with our model as the pressingness of the environmental problem was high during the period.
+This is aligned with our model as the urgency of the environmental problem was high during the period.
 In 2009, however, we observed another peak which coincided with the Copenhagen Summit.
@@
 From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-In this period,  the pressingness of environmental problems was increasing as deforestation rates were rising.
+In this period,  the urgency of environmental problems was increasing as deforestation rates were rising.
 The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016.
@@
 This suggests that the Amazon is mentioned more in presidential speeches as transnational attention towards it increases.
-While our measure of pressingness of the environmental problem does not capture these events, these events change how pressing of a problem the Amazon is in certain years.
+While our measure of urgency of the environmental problem does not capture these events, these events change how urgent of a problem the Amazon is in certain years.
 In doing so, these events bring outside attention to the Amazon to which the president's response is more likely to be in the form of reaffirming Brazil’s sovereignty over the Amazon (model 5).
@@
 
-While we identified the effects of setting and pressingness on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
+While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
 In this section, we investigate how pure-types and mixed-types problem-constructions evolved over time.
@@
 This is especially pertinent during Cardoso’s presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
-This was a period when the pressingness of the environmental problem grew as deforestation rates were increasing, so presidents were more likely to avoid environmental conservation constructions.
+This was a period when the urgency of the environmental problem grew as deforestation rates were increasing, so presidents were more likely to avoid environmental conservation constructions.
 When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-During this period, the pressingness of environmental problems decreased along with deforestation rates, so presidents were more likely to employ environmental conservation constructions.
+During this period, the urgency of environmental problems decreased along with deforestation rates, so presidents were more likely to employ environmental conservation constructions.
 From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration.
@@
 Within the country or the Amazonian region, presidents prefer constructing the Amazon as an issue of social development and economic integration.
-Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not pressing (e.g.
+Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
 low deforestation rates).
-When environmental related problems become more pressing (e.g.
+When environmental related problems become more urgent (e.g.
 rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
@@
 In doing so, we can contextualize problem-constructions in space and show how they vary.
-Third, we argue that another key factor in explaining variation in problem-construction is the pressingness of specific problems in time.
+Third, we argue that another key factor in explaining variation in problem-construction is the urgency of specific problems in time.
 As the environmental crisis increases in its salience, important actors are less likely to ignore it.

### 2023-02-14 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Added random effects table by presidents and settings to appendix

@@
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + election_year,
                          data = ama_model_lag,
@@
 c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + election_year,
                          data = ama_model_lag,
@@
 c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + election_year,
                          data = ama_model_lag,
@@
 c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + election_year,
                          data = ama_model_lag,
@@
                                           "Inflation",
-                                          "Election Year",
-                                          "Peak years"))
+                                          "Election Year"))
 ```
@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r presid set, fig.cap="Random-effects logistic regressions for seeting and president indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+# Run models
+ama_model_lag$president <- factor(ama_model_lag$president,
+                                  levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                             "Lula", "Dilma", "Temer", "Bolsonaro"))
+ama_model2_lag$president <- factor(ama_model2_lag$president,
+                                   levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                              "Lula", "Dilma", "Temer", "Bolsonaro"))
+ps1 <- plm(con_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps5 <- plm(amazon_speech ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model2_lag,
+                         model = "random", index = "year")
+# Regression table                       
+stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
+                     title = "Random-effects logistic regressions for settings and president indexed by year",
+                      column.sep.width = "-12pt",
+                      font.size="small",
+                      dep.var.labels = c("Amazon Speech",
+                                         "Environmental Conservation",
+                                         "Economic Integration",
+                                         "Social Development",
+                                         "National Sovereignty"),
+                     covariate.labels = c("Amazonian Countries",
+                                          "Non Amazonian States",
+                                          "Non Amazonian Countries",
+                                          "Franco", "Collor", "Cardoso", "Lula",
+                                          "Rousseff", "Temer", "Bolsonaro"))
+```
+
+\end{landscape}
+````

### 2023-02-15 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
new plot on setting and presidents

--- 2023-02-14 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
@@
 ```{r models president fixed effect, fig.cap="Log odds for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-# Run models
+
 c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
-                         def_year + AAI + election_year + peak_year,
+                         def_year + AAI + election_year,
                          data = ama_model_lag,
@@
                          model = "within", index = "president")
-# Regression table                       
+
 stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
@@
 
+```{r presidents and settings for Amazon speeches, eval=FALSE, include=FALSE}
+ama_model_lag %>%
+  count(location_cat, president)%>%
+  group_by(president)%>%
+  mutate(perc = n / sum(n),
+         president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro")))%>%
+  ggplot(aes(x = president, y = perc, fill = location_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 3, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of speeches in each setting by president",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "right")
+```
+
+```{r presidents and settings for all, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+ama_model2_lag %>%
+  count(location_cat, president)%>%
+  group_by(president)%>%
+  mutate(perc = n / sum(n),
+         president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                                  "Lula", "Dilma", "Temer", "Bolsonaro")))%>%
+  ggplot(aes(x = president, y = perc, fill = location_cat,
+             label = scales::percent(perc, accuracy=.1))) +
+  geom_bar(stat = "identity", position = "stack") +
+  geom_text(size = 2, position = position_stack(vjust = .5)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
+  labs(x = "", y = "", title ="Share of speeches in each setting by president",
+       subtitle = "Sample composed by all 6240 speeches since 1985",
+       caption = "") +
+  theme_am() +
+  theme(legend.position = "bottom")
+```
+
 ````{=tex}
@@
 
-```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-# Calculate the custom CIs
+```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE, results="asis"}
+
 ci1 <- exp(confint(c1))
@@
 ci5 <- exp(confint(c5))
-# Regression table                       
+
 stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
@@
 ````
+
+````{=tex}
+\begin{landscape}
+
+```{r presid set, fig.cap="Random-effects logistic regressions for seeting and president indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+
+ama_model_lag$president <- factor(ama_model_lag$president,
+                                  levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                             "Lula", "Dilma", "Temer", "Bolsonaro"))
+ama_model2_lag$president <- factor(ama_model2_lag$president,
+                                   levels = c("Sarney", "Collor", "Itamar", "FHC",
+                                              "Lula", "Dilma", "Temer", "Bolsonaro"))
+ps1 <- plm(con_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps5 <- plm(amazon_speech ~ as.factor(location_cat) + as.factor(president),
+                         data = ama_model2_lag,
+                         model = "random", index = "year")
+
+stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
+                     title = "Random-effects logistic regressions for settings and president indexed by year",
+                      column.sep.width = "-12pt",
+                      font.size="small",
+                      dep.var.labels = c("Amazon Speech",
+                                         "Environmental Conservation",
+                                         "Economic Integration",
+                                         "Social Development",
+                                         "National Sovereignty"),
+                     covariate.labels = c("Amazonian Countries",
+                                          "Non Amazonian States",
+                                          "Non Amazonian Countries",
+                                          "Franco", "Collor", "Cardoso", "Lula",
+                                          "Rousseff", "Temer", "Bolsonaro"))
+```
+
+\end{landscape}
+````

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission.rmd
normalized measures

@@
 csl: chicago.csl
-abstract: blank
+abstract: The Amazon forest, peoples, and region are often approached as an transnational environmental problem without a discussion how key actors might see it differently in space and time.
+We combine theories of problem-representation and transnationalism to analyze where, when, and how the Brazilian Amazon has been constructed as a problem.
+We develop a framework that explains variation in transnational discursive problem-constructions based on speech setting and problem pressingness.
+To test our framework, we use supervised machine learning to classify statements about the Amazon in 6240 presidential speeches since 1985.
+We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) pressing, they are more likely to construct the amazon as an issue of environmental conservation (or economic integration).
+Furthermore, we show how we are moving into a period where the dictum between seeing the Amazon as an environment or an economic issue has been overcome, to a moment when diverse and complex problem-constructions are deployed.
 ---
@@
 ```{=latex}
-\wordcount{ 7685 (including abstract, text, references, and footnotes)}
+\wordcount{ 10000 (including abstract, text, references, and footnotes)}
 ```
@@
          levels = c("Pure Economic Integration",
-                    "Pure Environmental Conservation",
-                    "Pure Social Development",
-                    "Pure National Sovereignty",
-                    "Other", "Mixed-types")),
-        election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
+
                                       year), 1, 0),
@@
 
-# 1. Introduction
-
 > *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion.
@@
 
-# 2 Theory: problem-constructions, transnational settings, and presidential speeches
+# 1. Introduction
 
-## 2.1 Presidential speeches, policymaking, and problem-constructions
+Scholars studying the Brazilian Amazon often identify different governments throughout Brazilian history as proponents of a single view of the region, its people, and forest [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+While the military dictatorship (1964-85) and Bolsonaro’s presidency (2019-2022) are, for example, associated with understanding the Amazon as issues of national sovereignty and economic integration, Sarney’s (1985-1990) and Lula’s (2003-2010) presidencies are associated with environmental conservation.
+Yet, such representations advance the view that governments understood and acted consistently towards the Amazon as a specific problem, masking government diversity of discursive constructions and policies.
+In this article, we show where, when, and how the Brazilian Amazon has been constructed as a problem in presidential discourses since 1985.
 
-## 2.2 Transnational settings and the variation in problem-constructions
+By combining @bacchi1999’s theory of problem representation and @keck1998's theory of transnationalism, we place the way the objects of policies are constructed in discourse at the center of our analysis.
+We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem pressingness as actors participate and shape transnational politics.
+We focus on transnational speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem.
+While many analyses of Brazilian environmental discourse and policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
+Our framework and methodology help identify and account for these variations.
+We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil’s agricultural powerhouses, in a moment when the environmental problem is pressing, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
 
-# 3. Research Design
+To investigate where, when, and how the Brazilian Amazon has been constructed as a problem in presidential speeches, we create a dataset containing 6240 official presidential speeches by all Brazilian presidents since 1985.
+Next, we identify all instances where presidents refer to the Amazon in their speeches.
+Using an inductive strategy that goes back and forth between the speeches and the Amazonian literature, we develop a codebook to code how each one of these statements constructs the Amazon as one, or multiple, particular problems related to national sovereignty, economic integration, social development, or environmental conservation.
+With this codebook in hand, we manually code a randomly selected set of statements and use supervised machine learning to label the remaining observations.
+We then conduct an inferential and descriptive analysis of the coded data.
+
+We have four main findings.
+First, we find that presidents adopt different Amazonian constructions  in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
+When presidents speak outside (or inside) the Amazon, they are more likely to construct the Amazon as an issue of environmental conservation (or economic integration).
+Second, presidents often focus on alternative problem-constructions when general aligned problems become more pressing; whereas they boast about positive outcomes when aligned problems are less pressing.
+When aligned environmental problems are pressing, presidents are likely to construct the Amazon as a different issue such as economic integration.
+Third, we also find that high-profile environmental related events, which receive strong international media attention, drive up the importance of the Amazon as a general topic in presidential speeches.
+Alternatively, relevant Amazonian related policies  appear to not to attract much attention.
+Finally, we find that while all presidents deploy multiple problem-constructions across space and over time, we are now in a period when the dictum between understanding the Amazon as an environment or as an economic issue has been overcome, at least discursively, as Amazonian problem-constructions have become more mixed and balanced.
+Conceptually, our research shows how focusing on problem-constructions highlight what certain objects of policy are assumed to be, and when they are ignored or privileged, based on the transnational setting of the speech and the pressingness of aligned problems.
+
+In what follows, we start our article by outlining our conceptual framework connecting problem-constructions, transnationalism, and presidential speeches.
+We then move to a research design section where we describe our data and explain our methodological approach.
+We open our analysis with our inferential analysis and move to explain developments over time.
+We conclude by summarizing the empirical and conceptual contributions of the article as well as providing avenues for future research.
+
+# 2. Theory: problem-constructions, transnational settings, and problem pressingness
+
+We divide our theoretical framework in two parts.
+We start with an explanation of what are problem-constructions and why presidential speeches are an interesting instance to identify them.
+Next, we argue that problem-constructions can vary depending on the transnational setting of the speech and on the pressingness of its problem.
+
+## 2.1 Problem representation in presidential discourse
+
+Social scientists often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
+Whereas, governments from the late-1980s up to the late-2000s are associated with a turn towards policies that focus on environmental conservation of the Amazon [@padua2012].
+The presidencies of Rousseff (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, while Bolsonaro (2019-2022) with the dismantling of environmental policies [@capobianco2019].
+Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into cohesive policy periods, or policy cycles, with one all-encompassing understanding of the Amazon.
+
+We argue that the reason behind these monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the “Amazon problem” is.
+There is more variation within a specific government, though, than suggested by the policy cycle approach.
+Social scientists have shown how governments have contradictory agrarian policies (López 2023), redistribution policies [@fairfield2017], health policies [@poncedeleon2021], and social policies [@niedzwiecki2017].
+In the case of the Amazon, it has often been seen as a key biome in global climate-mitigation, and consequently, as an environmental problem.
+If the Amazon is thought of as an “environmental” problem, then it demands an “environmental” solution.
+However, in order to build a more comprehensive account of the Amazon as forest, region, and peoples we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
+
+@bacchi1999 [p.
+2] places the question of “what is the problem represented to be” in the center of policy studies.
+The author argues that “objects or targets of policy [do not exist] independently of the way they are spoken about or represented” [@bacchi1999, p.
+1].
+These objects of policies have a cultural dimension as they take “shape within specific historical and national or international contexts” [@bacchi2009, p.
+10].
+The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
+Hence, discourse represents objects of policies as instances of a specific problem, which can be explicit or implicit.
+Problem-representation matters because it carries implications related to who is involved both in the root causes and in the solutions of the problem [@bacchi1999].
+
+Following Bacchi, we place discourse about policy objects in the center of our conceptual framework.
+We define policy objects as political objects that demand dedicated political attention.
+We argue that by deciding to speak about a policy object, governments are making a deliberate choice.
+When speaking about policy objects, governments make a choice to represent, or construct it, as a specific problem.
+The problem might be either explicitly stated, or implicitly hidden in the underlined solution.
+This is what we label as problem-constructions.
+
+Presidential discourses are a good instance to identify problem-constructions over time.
+While the relationship between presidential and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
+This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution [@pinto2016].
+In  Brazil’s hybrid system, often referred to Coalitional Presidencialism [@couto2021], presidents build legislative support for a broad agendas through the distribution of positions in the state bureaucracies.
+This means that presidents have enough power and support to implement the agenda they deem appropriate.
+Presidential authority and engagement in Brazil, in the form of discursive constructions, bureaucratic appointments, and coalition building, were essential drivers of the policy agenda for diverse issues from human rights to disarmament [@macaulay2017].
+We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.
+
+## 2.2 Transnational settings, pressingness, and variation in problem-constructions
+
+The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary.
+There are two notable contenders for tying the problem-construction to international politics: Putnam’s two-level game and Keck and Sikkink’s transnational networks.
+
+@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups.
+At the national level, interest groups pressure the government to adopt favorable policies.
+Internationally, the government seeks to fulfill domestic preferences “while minimizing the adverse consequences of foreign developments” [@putnam1988 p.
+434].
+While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups.
+
+This two-level approach is, for example, the avenue pursued by @calderwood2019 and @calderwood2020 who investigates variation in American presidential speeches about climate change.
+Consistent with the two-level games, the author finds that presidents are more likely to mention climate change outside the US, though the location of the speech (domestic or foreign) can have a small effect on the content of the mention [@calderwood2020].
+The party affiliation of American presidents also mediates how they speak about climate change [@calderwood2019].
+Thus, adopting a two-level approach to analyze diverse discursive constructions implies that whatever presidents say inside and outside lies within the policy expectations of domestic and foreign interest groups.
+Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interest of different groups.
+
+The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
+Its contribution is to propose a connection between the national and international spheres as avenues for state-actors.
+While there is some evidence of two-level games at play, this view seems incompatible with the possibility of contradictory policies and of varied problem-constructions depending on specific historical contexts, timing, and places.
+Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, spamming from the local level to the international level [@nye1971; @keck1998].
+In this context, international summits are considered a transnational setting because non-state actors participate and shape them.
+We view, for instance, summits as the United Nations Framework Convention of Climate Change (UNFCCC) not only as a purely intergovernmental body, but as a transnational space composed of international media, corporations, non-governmental organizations, and social movements.
+
+@keck1998 theory of international politics as transnational networks reject the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
+Rather, international politics as transnational networks have “a structured and structuring dimension” [@keck1998, p.
+4]: state and non-state actors participate in and shape international politics.
+
+While their theory is developed in the context of value-based advocacy groups, this is non-state actors, the overall view of international politics as structured and structuring, should hold for state actors as well.
+Important participants of transnational networks, as presidents, have a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
+They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p.
+24].
+Or, they can leverage institutions to realize symbolic or material gains.
+In this sense, the positions of actors as components of a transnational network derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.
+
+Problem-constructions are choices made by presidents when speaking.
+If malleable identities across space and time are a defining feature of transnational politics, it follows that presidents' choice of problem-constructions depend on the president's views of an audience at a certain period.
+Specifically, how pressing a problem is in a certain space and/or at a certain time.
+
+*Space*
+
+Presidents construct problems and attempt to inform and/or leverage transnational audiences for symbolic or material gains according to their expectations of that audience.
+We conceptualize spaces in terms of settings.
+Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study.
+This indicates that how presidents construct policy objects as problems can vary, for instance, within the country — speaking inside the Amazon region versus outside — because presidents identify these audiences as sources of different types of support and demand.
+The same holds when speaking outside the country — in Amazonian countries, non-Amazonian countries, and international summits — where expectations and identities of audiences could diverge completely from that of domestic actors.
+In each one of these settings different problems might be more pressing and the president's expectations about what can be leveraged for material and symbolic gains might drive how a problem is implicitly or explicitly constructed.
+
+*Time*
+
+How presidents construct policy objects can also vary in time because the pressingness of certain problems change as new information arises.
+We conceptualize time as the perceived pressingness of a broad and related issue to those surrounding a policy object.
+This indicates, for instance, that as climate change becomes more pressing and widespread as a broad issue, it is more likely that transnational actors will consider climate change when discussing various forms of public policy.
+It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change.
+Conversely, today, if fossil fuel subsidies are discussed, climate change will likely be an issue given the increased pressingness of the topic in comparison to the 1980s.
+
+While time and space might interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change pressing, certain transnational actors would likely mention it as a problem independently of the perceived  pressingness of a climate breakdown at the time.
+Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
+
+Our conceptual framework, thus, combines Bacchi’s theory of problem-representation and Keck and Sikkink’s theory of transnationalism to account for diverse problem-constructions.
+It explains how and why problem-constructions vary depending on actors’ expectations of a specific audience in a certain setting at a specific moment in time.
+Audiences relate to the location of the speech and actors’ expectation of what gains can be achieved in that setting.
+Time concerns to what extent that problem is pressing, or not, at that moment.
+Conceptually, we provide an explanation that, differently than two-level games, accepts the possibility of diverse, or even contradictory, speeches in space.
+We tie this to pressingness, which accounts for how problems evolve over time.
+
+Our framework also helps to advance the literature about the Amazon.
+We provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions.
+In doing so, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented as a problem.
+Furthermore, many analyses of Brazilian environmental policies dissect its national and international nature but fail to adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
+Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
+Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017].
+When it comes to the environment, studies tend to focus primarily  on Bolsonaro’s discourse [see @marquardt2022; @mendes2022] or policies [see @capelari2023].
+We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there really is.
+
+# 3. Research design
+
+We start this section by detailing the data and how we operationalize the main variables of our framework.
+We then move to a section explaining our descriptive and inferential strategy.
+We discuss the limitations of our approach in each subsection.
 
 ## 3.1 Data
+
+To create a dataset containing all Brazilian presidential speeches, we build upon @cezar2020's dataset which contains all speeches from 1985 to 2019.
+We update the dataset by scraping and adding all official speeches from 2020 to 2022.
+The final dataset encompasses 6240 speeches, with their dates and speech location.
+We proceed to identify speeches that refer to the Amazon as a region, people, or forest.
+We do so by detecting all speeches in which the stem “amazon” appears.
+In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+We find that 968 speeches are, at least partially, about the Amazon.
+
+Using the poldis R package [@sposito2021], we extract two sentences before and after the sentence in which the stem “amazon” appears.
+We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
+This is how our unit of analysis, Amazonian statements, are generated.
+One speech can contain none or multiple Amazonian statements.
+This process yields 2048 unique Amazonian statements.
+On average, an Amazonian statement contains 131 words.
+
+Our dataset covers only what is considered an official speech.
+Presidents, though, give interviews, appear in debates, talk at campaign rallies, and, more recently, post on social media.
+Problem-construction within presidential discourse, thus, happens in different public, private, and online venues for which we do not account for in this paper.
 
@@
 
+To test our conceptual framework, we need to operationalize the possible problem-constructions for the Amazon policy object.
+To classify Amazonian statements as specific types of problem-constructions, we developed a codebook inductively and with assistance of the literature.
+We identify three historical-political constructions: national sovereignty, economic integration, and environmental conservation.
+We argue a fourth separate one also exists: social development.
+The social development construction focuses on the constitutional rights and dignity of the inhabitants of the Amazonian region.
+
+*National Sovereignty:* In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+8], and when the dust settled and the scramble was over, more than half of the Amazon territory emerged Brazilian.
+While the Brazilian military diplomacy following the scramble was very successful, the process did not come without its traumas as, for example, the negotiations with Bolivia in 1902 to secure the state of Acre [@hecht1990].
+These traumas were referred to, and offered context, to Amazonian discourses and policies that highlighted Brazil’s sovereignty over the Amazon [@rajao2020].
+More recently, as we move to a world where non-state actors gain importance in international politics [@silva-muller2022; @andonova2014; @keck1998], sovereignty-related problems become more varied.
+Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
+The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
+The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
+
+*Economic Integration:* The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@capobianco2019; @becker2005].
+In 1966, the Brazilian Military launched ‘Operation Amazon’, a policy to modernize the region based on three assumptions [@acker2021].
+First, it assumed that nature should be conquered by mankind.
+Second, it assumed that exploiting natural resources would render the Amazon region economically profitable.
+Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory.
+Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
+The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
+These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+
+*Environmental Conservation:* The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of environmental institutions [@drummond2006].
+The creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
+This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987], epitomized in the 1992 Earth Summit in Rio de Janeiro [@hochstetler2021; @capobianco2021].
+The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted.
+The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
+
+*Social Development:* As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
+While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected.
+Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
+The policy solution to social development implies the policies to facilitate access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals locally.
+
+In their conceptualization, each problem-construction is mutually exclusive; that is, they cover different forms of constructing the Amazon as a problem.
+However, an Amazonian statement can be coded as referring to multiple problem-constructions (see Figure 1 below).
+Amazonian statements, thus, can be pure-type statements (i.e.
+they construct the Amazon as a single problem) or mixed-types (i.e.
+they construct the Amazon as multiple issues).
+
 ````{=tex}
@@
 
+With the codebook in hand (see Codebook in appendix), each one of the authors separately hand-coded 1024 randomly selected Amazonian statements.
+This amount refers to 50% of all the Amazonian statements identified.
+We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time.
+As well, since we have four different code categories, the size of the training set should be increased [see @grimmer2022].
+Our hand-coding strategy provides a robust and reliable number of observations to be used for training and validation of the automated model.
+Once hand coding was completed, the average intercoder agreement for hand-coded categories was 85%.
+For each non-matching coded observation, the authors discussed and sorted their disagreements, which were subsequently specified in the codebook.
+
+The hand-coded data was then randomly divided into a training set, containing 80% of the data (819 observations), and a validation set, containing the remaining 20% of the data (205 observations).
+We employ a support-vector machine (SVM) algorithm, a non-probabilistic linear classifier appropriate for binary categories, to label texts [@meyer2021; @noble2006].
+To validate the model, the SVM algorithm is trained using the hand-coded training set and employed to classify observations in the validation set.
+As a final robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
+Automating the coding of the remaining half of the observations is estimated to have saved the authors over one month of work in comparison to manual coding.
+The final dataset for analysis, excluding false positive matches ^[We also train the model to identify false positive matches in Amazonian statements.
+These are 124 Amazonian Statements that contain the stem “amazon” but are not necessarily meaningful as they might simply salute the governor of the Amazon, for example.], contains 1924 coded Amazonian statements.
+
 ## 3.3 Operationalizing Settings and Pressingness
+
+Our explanation for variation in problem-constructions is based on the setting of a speech and the pressingness of an aligned problem. This comprises our independent variables.
+
+*Settings*
+
+Presidents construct problems and attempt to inform or leverage symbolic or material gains according to their expectations of an audience.
+To operationalize settings, we extract the location of the speech and create four distinct settings: Amazonian states within Brazil, non-Amazonian states within Brazil, Amazonian countries, and non-Amazonian countries.
+
+Each one of these settings encompasses audiences that can have different expectations in reference to our policy object, the Brazilian Amazon.
+When speaking at Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon.
+Such expectations might be distinct from the ones audiences in Brazil, but outside of the Amazonian region, have for the same policy object.
+
+In the same vein, audiences within Amazonian Countries, these are other countries that also harbor the Amazon Rainforest (e.g.
+Peru, Colombia, Venezuela, Equator), might have distinct expectations about the policy object in relation to audiences in other countries outside of the Amazonian region (and within Brazil).
+In bilateral visits to Amazonian countries, presidents can view other Amazonian countries as potential peers governing a transnational policy object and, therefore, shape the ways in which they speak about the Amazon as a problem to those audiences.
+Alternatively, when speaking at non-Amazonian countries, these also entail speeches that take place within multilateral mechanisms such as the UNFCCC, international summits as the World Economic Forum annual meeting in Davos, or bilateral visits to the United States or France, presidents deploy problem-constructions aligned with what presidents perceive as possible expected symbolic or material gains from such audiences.
+
+This operationalization of settings comes with limitations.
+While we would ideally like to capture the exact venue of the speech (i.e.
+multilateral mechanism, private fora, bilateral visit, bridge inauguration), it is difficult to programmatically code exact locations from thousands of speeches that often mention multiple locations in the same text.
+Nevertheless, we believe the four settings coded are already enough to demonstrate whether, and how, problem-construction might change transnationally.
+
+*Pressingness*
+
+Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their pressingness over time.
+To capture the pressingness of problems, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
+When deforestation rates are high, the problem of environmental conservation can be perceived as more pressing.
+Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more pressing.
+We opt for lagging deforestation rates by one year as the consolidated rates for a certain year are published in the following year.
+We do not lag inflation since data for it is widely available on a monthly basis.
+Inflation is taken at the country level, and not at the regional level for Amazonian states, for two reasons.
+First, we could not find separate inflation data for many of the Amazonian states in Brazil.
+Second, it is national level data that makes up headlines and often drives price changes across the country.
+Since both annual deforestation rates and annual inflation rates come in different measurements (i.e.
+percentage and kilometers square) we scale these values to facilitate interpretation of coefficients.
+Scaling variables do not affect statistical inference in regression models.
+
+This approach to operationalizing pressingness also has its limitations.
+Ideally, we would like to add additional proxies of pressingness for social and sovereignty issues.
+However, social development indicators (e.g.
+life expectancy, education levels, access to sanitation) generally increased over time in Brazil.
+In terms of national sovereignty, the way we conceptualize the problem-construction entails internal and external threats which are not easily measured.
+Despite these limitations, we can draw some conclusions from the pressingness of environmental and economic issues and their aligned problem-constructions.
 
@@
 
-# 4. Analysis: How has the Brazilian Amazon been constructed as a problem?
+We start our analysis with the inferential portion with five separate fixed-effect logistic regression models that predict the probability of a speech mentioning the Amazon generally (model 1), and of each problem-construction (models 2-5).
+The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes (i.e.
+ideology).
+For instance, if a president’s political ideology predicts variation in our dependent variables, fixed-effects could control for such issues along other unit-unvarying characteristics [@allison2009].
 
-## 4.1 The Amazon as a transnational problem
+The dependent variables of the model are the share of speeches that mention the Amazon (model 1) and the share of a problem-construction (models 2-5).
+We chose to model each construction separately, and to focus on pure-types (i.e.
+statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust coefficients.
+Our main explanatory variables are settings (i.e.
+Amazonian states within Brazil, non-Amazonian states within Brazil, Amazonian countries, and non-Amazonian countries) and pressingness of an aligned issue (i.e.
+lagged deforestation rates and average annual inflation), as described above.
+
+We also add two control variables in the models: election years and peak years.
+In the case of election years, we control for the possibility of presidents constructing the Amazon in systematically different ways in those years.
+In the case of peak years, these are years in which the Amazon was disproportionately more mentioned as a share of all presidential speeches.
+We calculate these by capturing years in which mentions of the Amazon are above one standard deviation from their mean share.
+Controls for peak years are only added to the models that focus on how the Amazon is constructed as a problem (i.e.
+models 2-5) for endogeneity reasons since we also model based on the share of Amazonian speeches (i.e.model 1).
+
+It is important to outline that we do not make any causal claims.
+Many scholars inquire and find causal relationships between discourse and outcomes.
+Our research design and data does not allow us to do so.
+While we might point to particular directions for correlations between where speeches happen, how pressing aligned issues might be at certain times, and at certain specific policy outcomes, none of our claims are linearly causal.
+Instead, we carefully  focus on the relationships in themselves rather than their order or cause.
+
+We wrap the analysis with a descriptive and longitudinal analysis of Amazonian speeches in time, considering the findings of the models.
+We, first, identify when presidents speak more, or less, about the Amazon.
+We do so by visualizing the frequency in which Amazon appears in relation to all presidential speeches since 1985.
+This helps us identify instances when presidents mention the Amazon more frequently, as well as, when it is not mentioned.
+In other words, when the Amazon might, or not, be perceived as a problem.
+Next, we discuss how the Amazon has been constructed as a problem since 1985.
+We show the evolution of yearly problem-constructions in time by taking the annual share of each problem-construction in Amazonian statements.
+
+# 4. How has the Brazilian Amazon been constructed as a problem?
+
+We open our analysis with the models predicting the probability of presidents mentioning the Amazon in speeches (model 1) and of presidents employing certain problem-construction (model 2-5).
+Subsequently, we plot and discuss the longitudinal developments of Amazonian speeches and of problem-constructions considering the model results.
+
+## 4.1 The Amazon as a transnational problem: setting and pressingness
+
+By combining Bacchi’s theory of problem-representation and Keck and Sikkink’s theory of transnationalism, we argue that presidents’ expectations about an audience at a certain setting and the pressingness of specific problems explain variations in when the Amazon becomes a  problem and how it is constructed as a type of problem it is.
+Our models, below, confirm the relationships expected by our framework.
+Multiple, often contradictory, problem-constructions are forwarded across settings as presidents participate and shape transnational politics.
 
@@
 
+As we argue that the effects of setting and pressingness are cumulative, we start by first scrutinizing the relationship between the former and problem-construction.
+Model 1 addresses the question of when the Amazon is a problem to begin with.
+We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian States within Brazil.
+The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.
+
+The following models (2-5) address the question of how the Amazon is constructed as a problem in presidential speeches depending on where presidents are speaking.
+In terms of environmental conservation (model 2), we observe that when speaking at non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
+To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil where they are more likely to construct the Amazon as an issue of environmental conservation.
+While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction.
+Social development problem-constructions are less likely to be deployed outside of Brazil, in both Amazonian and non-Amazonian countries, than within Brazil.
+Relatedly, economic integration problem-constructions become less likely to be deployed as we move far away from the Amazon states within and neighboring Amazonian countries.
+Finally, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they are speaking elsewhere.
+
+Overall, we interpret these results as evidence that presidents construct the Amazon as different problems based on their expectations of an audience at certain settings.
+When it comes to non-Amazonian countries, it is likely that Brazilian presidents construct the Amazon as an issue of environmental conservation to leverage financial support for the Amazonian region.
+The Brazilian government successfully funded domestic public policy with transnational financial support on several occasions since the 1990s, most notably with the Amazon Fund or policies in the Amazon which provided over USD 1 billion for the region along with multiple bilateral and philanthropic grants [@silva-muller2022].
+That is, presidents realize material and symbolic gains outside of Brazil and of Amazonian countries, by constructing the Amazon as an environmental problem.
+
+In turn, when speaking within the Brazilian Amazon, presidents see their audiences as local constituencies.
+Therefore, it is no surprise that presidents never stopped pursuing a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds.
+For example, rural credit offered to local agricultural producers in Amazonian states went up from 500 million reais a year in 1999, to over 4 billion reais a year by 2012 [@capobianco2021].
+As well, the special fiscal regime in Manaus, designed to increase industry presence in the region, was largely maintained.
+Moreover, additional roads and dams (e.g.
+the BR-163 highway and the Belo Monte dam and hydroelectric power plant) were constructed during the same period.
+Presidents likely highlight and push for economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.
+
+We also argue that the pressingness of an aligned problem in time influences the likelihood of the president mentioning the Amazon and what they will say.
+We find evidence across our models that this holds.
+For instance, we find that presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the pressingness of environmental problems (model 1).
+The opposite is true for inflation.
+As inflation increases, and so the pressingness of economic problems, presidents are more likely to generally mention the  Amazon in speeches (model 1).
+This relationship is even more interesting when we look at how amazonian constructions vary in presidential speeches as environmental or economic problems become more pressing (models 2-3).
+We find strong evidence that when the pressingness of environmental problems increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
+Alternatively, as the pressingness of economic problems increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation  increases.
+
+In line with our framework, the pressingness of aligned problems relates to problem-constructions in intricate ways.
+Presidents often opt for an alternative problem-construction than the construction that aligns with the more pressing issues.
+By opting for an alternative problem-construction to that which is pressing, presidents can side-step an issue and shift the focus to something else.
+In turn, when issues are not pressing, presidents often opt for employing aligned constructions.
+This entails that presidents attempt to collect symbolic and material rewards for positive aligned outcomes.
+
+Overall, our models suggest that presidents’ promotion of economic integration and social development within Brazil, and neighboring Amazonian countries to a certain extent, diverge from the promotion of environmental constructions in non-Amazonian countries.
+That is, presidents talk to the economic or social needs of audiences within Brazil, while focusing on environmentalism outside (and far away) of the Amazon.
+Additionally the pressingness of environmental and economic problems in time drive opposite problem-constructions.
+That is, presidents likely side-step issues as they get more pressing, while boosting positive aligned outcomes to attempt and collect benefits as aligned issues become less pressing.
+
 ## 4.2 Amazonian speeches in time
+
+Looking at speeches that mention the Amazon in time (the dependent variable of model 1) reviews several interesting trends.
+Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
+By investigating its development in time, we can identify instances when the Amazon in itself becomes more pressing as a problem, and when not.
+On average, presidents mention the Amazon in 15.5% of their speeches ^[For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).].
+This suggests the Amazon is a topic of relative high importance for presidents generally.
+However, we observe four peak years in the figure: 1989, 1992, 2009, and 2019.
+As discussed above, peak years represent years in which the Amazon is mentioned, on average, more than one standard deviation from the mean.
+We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.
 
@@
 
+In 1989 the Amazon appeared in 32% of all speeches.
+This coincides with the brutal murder of the environmental activist Chico Mendes in the last days of 1988.
+The incident caught unprecedented transnational media attention and then President Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
+One of the responses was the offer and acceptance to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
+During the summit, we saw the realization of the first transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest (PPG7), which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
+
+Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, the Amazon as a topic did not diverge much from the average.
+This is aligned with our model as the pressingness of the environmental problem was high during the period.
+In 2009, however, we observed another peak which coincided with the Copenhagen Summit.
+Lula led the delegation to the summit with a strong climate leadership self-image of “we deliver” [@franchini2019], in a moment when deforestation rates have been decreasing since 2005.
+From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
+In this period,  the pressingness of environmental problems was increasing as deforestation rates were rising.
+The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016.
+By 2016 mentions of Amazon in official speeches went down to 6%, their lowest share since 1985.
+
+We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro’s presidency.
+At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019.
+Right after being elected in 2018, Bolsonaro went on to retrieve Brazil’s hosting status for COP25.
+Alongside, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
+Finally, although not technically a peak year, in 2022 environmental activist, Bruno Mendes, and British journalist, Dom Phillips, were murdered in the Amazon [@mccoy2022].
+This event also drove the proportion of speeches mentioning the Amazon up.
+
+The figure 2, above, also shows that the frequency in which the Amazon is mentioned, as a general topic in speeches, is not related by proposed policy solutions.
+In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022].
+In 2004, President Lula decreed the creation of Brazil’s Plan to Combat and Control Deforestation in the Brazilian Amazon.
+In 2008, Brazil announced the Amazon Fund, the largest fund of this kind ever created.
+Finally, in 2012, the revision of the Forest Code, debated in 2010 and 2011, pardoned thousands of illegal deforesters in the Amazon [@sant2021].
+Yet, these policy landmarks do not seem to be systematically meaningful for when Amazon is mentioned as a general problem more often.
+
+The longitudinal trends in Amazonian speeches reveal a dynamic that our models did not capture: we find that all peak years relate to high-profile environmental events within the country that gained large repercussions within and outside of the country.
+These are events that received distinct coverage from transnational actors as media and civil society outside of Brazil, which is likely one of the reasons why it temporarily drives the topic up.
+This suggests that the Amazon is mentioned more in presidential speeches as transnational attention towards it increases.
+While our measure of pressingness of the environmental problem does not capture these events, these events change how pressing of a problem the Amazon is in certain years.
+In doing so, these events bring outside attention to the Amazon to which the president's response is more likely to be in the form of reaffirming Brazil’s sovereignty over the Amazon (model 5).
+That is, presidents tend to construct the Amazon as an issue of national sovereignty and side-step the aligned environmental conservation constructions around high-profile environmentally related events.
+
 ## 4.3 Amazonian problem-constructions in time
 
-```{r Figure pure, fig.cap="Pure-types and miyed-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+While we identified the effects of setting and pressingness on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
+In this section, we investigate how pure-types and mixed-types problem-constructions evolved over time.
+Figure 3, below, illustrates the annual share of pure-types problem-constructions.
+
+```{r Figure pure, fig.cap="Pure-types constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 #summary(as.factor(ama_mx$mx_cat))
@@
   mutate(perc = n / sum(n)) %>% 
-  filter(mx_cat != "Other") %>%
+  filter(mx_cat != "Other",
+         mx_cat != "Mixed-types") %>%
   ggplot() +
@@
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  labs(x = "", y = "", title ="Share of pure-types and mixed-types problem-constructions by year",
+  labs(x = "", y = "", title ="Share of pure-types problem-constructions by year",
        subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
        caption = "Curves in the plot were smoothed using loess method.") +
-  theme_am()+
-  theme(legend.position = "bottom")
+  theme_am() +
+  theme(legend.position = "bottom") +
+  scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
+                                  "Social Development", "National Sovereinty"))
 ```
 
+Pure economic integration constructions were the most frequent from 1985 to 2009.
+This is especially pertinent during Cardoso’s presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
+This was a period when the pressingness of the environmental problem grew as deforestation rates were increasing, so presidents were more likely to avoid environmental conservation constructions.
+When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
+During this period, the pressingness of environmental problems decreased along with deforestation rates, so presidents are more likely to employ environmental conservation constructions.
+From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration.
+However, this reversal was not long-standing.
+With the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored again.
+
+We also notice a steady increase of sovereignty as salient problem-constructions from 2008 onwards, much before Bolsonaro was elected.
+This might relate to policy developments that were taking place.
+The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government [@horochovski2016; @castelo2015].
+In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil’s sovereignty over the Amazon while rebating  broad criticism from civil society actors with accusations of internationalization attempts.
+Therefore, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making.
+Bolsonaro’s problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
+
+Our operationalization of problem-constructions also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
+Figure 4, below, shows that constructing the Amazon as multiple issues increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
+Mixed-type problem-constructions in discourse offer more complex and balanced understandings of the Amazon as a problem.
+The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.
+Indeed, we observe an increase in policies that attempt to address environmental and social problems, for instance, at the same time.
+Examples of this are payment for ecosystem services conditioned for low income populations residing in the Amazon, as Bolsa Floresta [@silva-muller2022] or Bolsa Verde [@abers2019].
+Relatedly, this is aligned with transnational processes as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
+
+```{r Figure mixed, fig.cap="Mixed-types problem constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+#summary(as.factor(ama_mx$mx_cat))
+ama_mx %>%
+  count(mx_cat, year) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n)) %>% 
+  filter(mx_cat == "Mixed-types") %>%
+  ggplot() +
+  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
+              se = FALSE, linewidth =0.75, linetype="solid") +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
+       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
+       caption = "Curves in the plot were smoothed using loess method.") +
+  theme_am() +
+  scale_color_manual(values = "yellow3")
+```
+
+We interpret the balance in pure-types and the increase in mixed-types as evidence that presidents increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years decades.
+We see in these findings the possibility of the Amazon becoming an increasingly coherent transnational problem, where audiences do not only recognize it as a single pure-type but an intricate policy object.
+
 # 5. Conclusion
+
+This paper investigated where, when, and how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
+We have four main empirical findings.
+First, we find that presidents construct the Amazon as different problems depending on where they speak.
+When presidents speak outside the country and far away from the Amazon, they are more likely to construct the Amazon as an issue of environmental conservation.
+Within the country or the Amazonian region, presidents prefer constructing the Amazon as issues of social development and economic integration.
+Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not pressing (e.g.
+low deforestation rates).
+When environmental related problems become more pressing (e.g.
+rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as different issues as economic integration.
+Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency in which the Amazon appears in discourse.
+Relevant Amazonian related policies, in turn, appear not to affect how much discursive attention is paid to the Amazon by presidents.
+Finally, we find that we are now in a period where the dictum between seeing the Amazon as an environment or an economic issue has been overcome, at least discursively, as Amazonian problem-constructions have become more mixed and balanced lately.
+
+Our framework also helps to advance the Amazonian literature in two ways.
+First, we provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions.
+In so doing, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented.
+Second, while many analyses of Brazilian environmental policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios (Hoschstetler and Keck, 2004).
+Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
+In doing so, we can contextualize problem-constructions in time and space.
+
+The conceptual implications of our findings are threefold.
+First, we argue that a focus on problem-constructions complements policy studies Investigating problem-representation to begin with, can highlight the extent at which certain perspectives of problems are ignored or privileged.
+Second, we argue that transnational setting is a key factor that drives problem-construction.
+While existing studies identify a convergence in positions because of interest group pressure, we account for diverging, and even contradictory, problem-constructions in discourse.
+This is because state and non-state actors have expectations of a particular audience.
+Third, we argue that another key factor in explaining variation in problem-construction is the pressingness of specific problems in time.
+As the environmental crisis increases in its salience, important actors are less likely to simply ignore it.
+They need to find strategies, such as side-stepping issues or boasting positive outcomes, in order to remain credible to their audiences.
+
+In terms of future research, we see at least three possibilities.
+First, we have introduced a flexible framework that can be extended to cover other policy objects.
+We expect to inspire some to investigate other policy objects in domains beyond the Brazilian Amazon (e.g.
+Cerrado Biome, Antarctic, Inequality, Criminality, etc.).
+This opens up the possibility of interesting time and space  comparisons.
+Relatedly, as we find evidence that problem-constructions in Amazonian countries differ from other settings, scholars should investigate how Amazonian problem-constructions in other Amazonian countries differ, and not, from the ones we see in the Brazilian case.
+Second, while we argue that settings are important to explaining variation in problem-constructions, social media can change this in fundamental ways.
+As short videos of presidential discourses travel more rapidly than ever, social media might contribute to diminishing the importance of physical settings.
+This could make presidents less likely to afford very diverging problem-constructions anymore.
+Alternatively, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences.
+We look forward to works that investigate how setting and audience interact with problem-construction in unofficial political communications in the era of social media.
+Finally, while we do not explicitly conceptualize the possibility of problem-constructions having a direct effect on policy outcomes, it is possible, though, to design studies that test the causal relationship between presidential discourse and outcomes.
+In a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro’s speech to covid-19 infections.
+We look forward to studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.
 
@@
 
-```{r log odds, fig.cap = "Odds-ration for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
+```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 # Calculate the custom CIs

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission.rmd
revoming changes

@@
          levels = c("Pure Economic Integration",
-
+                    "Pure Environmental Conservation",
+                    "Pure Social Development",
+                    "Pure National Sovereignty",
+                    "Other", "Mixed-types")),
+        election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                       year), 1, 0),

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
all new changes

@@
 ---
-title: How has the Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985
+title: One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985
 author:
@@
 Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.]
-date: 13 February 2023
+date: 17 February 2023
 output:
@@
 csl: chicago.csl
-abstract: The Amazon is often approached as a transnational environmental problem without a discussion of how key actors represent it differently in space and time.
-We combine theories of problem-representation and transnationalism to analyze where, when, and how the Brazilian Amazon has been constructed as a problem.
-We develop a framework that explains variation in transnational problem-constructions based on speech setting and problem urgency To test our framework, we use supervised machine learning to classify statements about the Amazon in 6240 presidential speeches since 1985.
-We find that when presidents speak outside (or inside) the Amazon and environmental problems are less (or more) urgent, presidents are likelier to highlight issues of environmental conservation (or economic integration).
-Furthermore, we show how we are moving from a period when the Amazon as a binary of either environmental or an economic issue has been overcome, to a moment when diverse problem-constructions are deployed.
-
+abstract: The Amazon is a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns.
+Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem.
+We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches.
+To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they speak and when.
+Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985.
+We find that presidents often construct the Amazon as an environmental problem when speaking far away from the Amazon, whereas they usually construct it as economic or social problems when in the Amazon.
+Furthermore, presidents increasingly construct the Amazon as multiple problems rather than only economic or environmental problems.
 ---
@@
 ```{=latex}
-\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
+\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
 ```
-
 ```{=latex}
@@
 
-> *"[...] I will fight against the NGOs on this issue of associating the increase in deforestation to our agricultural expansion.
-First of all, these NGOs should go plant trees in their own countries [...]" (President Lula, Cuiaba - MT, 2007).*
+# Introduction
 
-# 1. Introduction
+The Brazilian Amazon, which covers around 60% of the whole biome, is home to over 28 million people.
+The Rainforest spans over seven international borders and contains enormous amounts of highly valued minerals such as iron ore and gold.
+Its most inhabited city, Manaus, enjoys a distinct fiscal regime designed to create jobs in the region and connect its economy to the rest of the country.
+At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas.
+The Brazilian Amazon is, thus, a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns.
+Despite this complexity, governments are often portrayed in the literature about policies in the Amazon as having a single understanding of what the Amazon problem is and consequently, proposing coherent policies for the region.
+Although it is helpful to compare variation across different governments, this analysis oversimplifies policies and discourse within governments misrepresenting what, in reality, is more intricate and inconsistent.
+In this article, we ask how has the Amazon been constructed as a political problem since 1985?
 
-*We need to protect the Amazon from foreign interests.
-We need to exploit the Amazon's natural resources.
-We need to provide better living standards for the people in the Amazon.
-We need to preserve the Amazon as a standing ecosystem.* Each of these statements represent the Amazon as a particular problem: national sovereignty, economic integration, social development, and environmental conservation, respectively.
-These specific problems touch on common understandings of the Amazon as part of the larger socio-cultural history of the country.
-Brazilian governments have been portrayed in the literature as having held differing views on the Amazon, with some prioritizing national sovereignty and economic integration (military dictatorship and Bolsonaro), while others prioritize environmental conservation (Sarney and Lula).
-However, this oversimplifies government policies and discourse, which in reality are more intricate and contradictory.
-
-By combining @bacchi1999’s theory of problem representation and @keck1998's theory of transnationalism, we place the way the objects of policies are constructed in discourse at the center of our analysis.
-We offer a framework that explains variation in discursive problem-constructions depending on speech setting and problem urgency as actors participate and shape transnational politics.
-We focus on speeches, rather than policies, because they allow us to capture the diversity of ways the Amazon, as a policy object that demands dedicated attention, has been discursively constructed as a problem.
-While many analyses of Brazilian environmental discourse and policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
-Our framework and methodology help identify and account for these variations.
-We show, for instance, that when speaking to farmers in Cuiaba, one of Brazil’s agricultural powerhouses, in a moment when the environmental problem is urgent, it is likely that any president would sidestep environmental issues, as President Lula did in the opening epigraph.
-
-To answer how the Amazon has been constructed as a problem, we create a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
-Next, we identify all instances where the presidents mention the Amazon.
-Using an inductive approach, we develop a codebook to categorize how each statement constructs the Amazon as one or multiple problems related to national sovereignty, economic integration, social development, or environmental conservation.
-Then, we manually code a random subset of the statements and use supervised machine learning to label the remaining.
-Finally, we conduct a descriptive and inferential analysis of the coded data.
+We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as Presidents, construct objects of policies as particular problems depending on where and when they participate in politics.
+To examine this variation, we created a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
+Drawing from the socio-cultural history of the Brazilian Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon.
+These problem-constructions relate to national sovereignty, economic integration, social development, or environmental conservation.
+We employ supervised machine learning to classify how the Amazon related statements construct it as a problem, and then conduct an inferential and descriptive analysis of the data.
+A systematic focus on presidential speeches is important because while many scholars recognize decisions to deforest on the ground are derived from what the government says and does [@capobianco2021; @campbell2015], we lack empirical accounts of the Amazon in presidential discourse.
 
 We have four main findings.
-First, presidents adopt different constructions of the Amazon in different settings according to how they expect to leverage audiences for symbolic and/or  material gains.
-Second, presidents often focus on alternative problem-constructions when problems become more urgent; whereas they boast about positive outcomes when problems are less urgent.
-Third, high-profile environmental related events, which receive strong international media attention, increase the importance of the Amazon in presidential speeches.
-Alternatively, relevant Amazonian-related policies appear to not to attract much attention.
-Finally, while all presidents deploy multiple problem-constructions across space and over time, we are now in a period when the dictum between understanding the Amazon as an environment or as an economic issue has been overcome, at least discursively.
-Conceptually, our research shows how focusing on problem-constructions highlight what certain objects of policy are assumed to be, and when they are ignored or privileged, based on the transnational setting of the speech and the urgency of aligned problems.
+First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation.
+Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration.
+Second, presidents are more likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
+lowering deforestation rates).
+When environmental related issues become more urgent (e.g.
+rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
+Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses, but does not systematically change how the Amazon is constructed as a problem.
+Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
 
-We begin our article by outlining the connection between problem-constructions, transnationalism, and presidential speeches.
-Next, we present our research design including data description and methodological approach.
-We open our analysis with our inferential analysis and move to explain developments over time.
-We conclude by summarizing the empirical and conceptual contributions of the article as well as providing avenues for future research.
+Empirically, we contribute to the literature about the Amazon by providing the first overview of where, how, and when the Amazon has been constructed as a problem in presidential speeches.
+We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an aligned issue is.
+Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important actors behave differently inside and outside the country, by doing so we reveal how the Amazon as a problem varies in transnational politics.
+Conceptually, problem-constructions highlight the extent to which Amazonian problems are ignored or privileged in transnational politics, and avoids assumptions of the Amazon as a solely environmental problem.
+
+This article is divided into 4 sections.
+First, we outline the connection between problem-constructions, transnationalism, and presidential speeches.
+Next, we present our research design including the description of our data and methodological approaches.
+In the third part, dedicated to the analysis, we display the results of our inferential models and move to explain developments in problem-constructions over time.
+We conclude by summarizing the empirical and conceptual contributions of the article.
 
@@
 
-Social scientists often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
+Scholars writing about policies in the Brazilian Amazon often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
 The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
@@
 The presidencies of Rousseff (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, while Bolsonaro (2019-2022) with the dismantling of environmental policies [@capobianco2019].
-Although these works are important to understand how different governments acted towards the Amazon, they represent governments monolithically by bundling them into cohesive policy periods, or policy cycles, masking government diversity in policies and discourse.
+These works are important to understand how different governments acted towards the Amazon, but they represent governments monolithically by bundling them into cohesive policy cycles.
 
-We argue that the reason behind these monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the “Amazon problem” is.
-There is more variation within a specific government, though, than suggested by the policy cycle approach.
-Social scientists have shown how governments have contradictory policies [@lopez2023; @fairfield2017; @poncedeleon2021].
-The Amazon has often been seen as a key biome in global climate-mitigation, and consequently, as an environmental problem.
-If the Amazon is thought of as an “environmental” problem, then it demands an “environmental” solution.
-However, to build a more comprehensive account of the Amazon as forest, region, and peoples we need a framework that assumes the possibility of varied problem-constructions beyond Amazonian environmental nature.
+Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies and discourse [see @lopez2023; @fairfield2017; @poncedeleon2021] than suggested by the literature above.
+We argue that the reason behind monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is.
+Because of the Amazon Rainforest role in global climate-mitigation, , and consequently, as an environmental problem.
+If the Amazon is thought of as an environmental problem, then it demands an environmental solution.
+The Amazon region, its peoples, and forests, though, are a historically complex object of policies that comprise economic, social, and sovereignty concerns.
 
 @bacchi1999 [p.
-2] places the question of “what is the problem represented to be” in the center of policy studies.
-These objects of policies have a cultural dimension as they take “shape within specific historical and national or international contexts” [@bacchi2009, p.
-10].
+63] places the question of "what is the problem represented to be" in the center of policy studies.
 The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-Hence, discourse represents objects of policies as instances of a specific problem, which can be explicit or implicit.
-Problem-representation matters because it carries implications related to who is involved both in the root causes and in the solutions of the problem [@bacchi1999].
+Hence, discourse represents, implicitly or explicitly, objects of policies as instances of a specific problem.Problem-representation matters because it carries implications related to who is involved both in the root causes and in the solutions of the problem [@bacchi1999].
+It also helps us shed light on what problems are ignored or privileged.
 
@@
 Presidential discourses are a good instance to identify problem-constructions over time.
-While the relationship between presidential speeches and policy may not be linearly causal, speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
-This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution[@macaulay2017].
-In Brazil’s hybrid system, often referred to Coalitional Presidencialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies.
-This means that presidents have enough power and support to implement the agenda they deem appropriate.
+Presidential speeches and policy share a co-constitutive relationship as speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
+This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution [@macaulay2017].
+In Brazil's hybrid system, often referred to as a Coalitional Presidentialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies.
+This means that presidents often have enough power and support to implement the agenda they deem appropriate.
 We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.
@@
 
-The possibility of different problem-constructions for the same policy object in political discourse, requires an explanation of why they vary.
-There are two notable contenders for tying the problem-construction to international politics: Putnam’s two-level game and Keck and Sikkink’s transnational networks.
+The possibility of different problem-constructions for the same policy object in political discourse requires an explanation of why they vary.
+There are two potential theories for explaining variation in problem-construction in international/transnational politics: Putnam's two-level game and Keck and Sikkink's transnational networks.
 
-@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests (and pressure) of domestic and international groups.
+@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests of domestic and international groups.
 At the national level, interest groups pressure the government to adopt favorable policies.
-Internationally, the government seeks to fulfill domestic preferences “while minimizing the adverse consequences of foreign developments” [@putnam1988 p.
+Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988 p.
 434].
-While the theory has been expanded to cover multi-levels games [see @collinson1999], its core remains the same: the outcome of negotiations should lie within the overlap of diverse interest groups.
+The theory has been expanded to cover multi-levels games [@collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups.
 Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups.
-Adopting two-level games to explain American presidential speeches, @calderwood2019 and @calderwood2020 find supporting evidence of this theory.
+Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found supporting evidence that location does not change the content of the speech, but can lead presidents to side-step the issue.
 
 The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
-This view seems incompatible with the possibility of contradictory policies and of varied problem-constructions depending on specific historical contexts, timing, and places.
-Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, spamming from the local level to the international level [@nye1971; @keck1998].
-In this context, international summits are considered a transnational setting because non-state actors participate and shape them.
+This view seems incompatible with the possibility of contradictory policies and of varied problem-constructions.
+Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, from the local level to the international level [@nye1971; @keck1998].
+In this context, international summits are considered a transnational setting because non-state actors participate in and shape them.
 We view, for instance, summits as the United Nations Framework Convention of Climate Change (UNFCCC) not only as a purely intergovernmental body, but as a transnational space composed of international media, corporations, non-governmental organizations, and social movements.
 
-@keck1998 theory of international politics as transnational networks rejects the dichotomy of international and domestic levels arguing that the identity and goals of state and non-state actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
-Rather, international politics as transnational networks have “a structured and structuring dimension” [@keck1998, p.
+While @keck1998 theory is developed in the context of value-based advocacy groups, hence non-state actors, the overall view of international politics holds for state actors.
+Their theory rejects the dichotomy of international and domestic levels and argues that the identity and goals of transnational actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
+Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p.
 4]: state and non-state actors participate in and shape international politics.
 
-While their theory is developed in the context of value-based advocacy groups, hence non-state actors, the overall view of international politics as structured and structuring, should hold for state actors as well.
-Important participants of transnational networks, as presidents, can use myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
+Important participants of transnational networks, as presidents, can use a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
 They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p.
@@
 
-Problem-constructions are choices made by presidents when speaking.
-If malleable identities across space and time are a defining feature of transnational politics, it follows that presidents' choice of problem-constructions depend on the president's views of an audience at a certain period.
+Problem-constructions are choices transnational actors have of how to represent objects of policies as problems.
+If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors', as presidents, choice of problem-constructions depend on their views of an audience at a certain period.
 Specifically, how urgent a problem is in a certain space and/or at a certain time.
@@
 
-Presidents construct problems and attempt to inform and/or leverage transnational audiences for symbolic or material gains according to their expectations of that audience.
-We conceptualize spaces in terms of settings.
+Transnational actors construct problems and attempt to inform and/or leverage audiences for symbolic or material gains according to their expectations of that audience.
+We conceptualize space in terms of settings.
 Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study.
-This indicates that how presidents construct policy objects as problems can vary, for instance, within the country — speaking inside the Amazon region versus outside — because presidents identify these audiences as sources of distinct types of support and demand.
-The same holds true when speaking abroad — in Amazonian countries, non-Amazonian countries, and at international summits — where presidents’ expectations and identities of an audiences could diverge completely from that of domestic actors.
+This indicates how transnational actors construct policy objects as problems can vary, for instance, within the country --- speaking inside the Amazon region versus outside --- because presidents identify these audiences as distinct.
+The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where presidents' expectations and identities of an audience could diverge completely from that of domestic actors.
 In each one of these settings different problems might be more urgent and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.
@@
 
-How presidents construct policy objects can also vary over time because the urgency of certain problems changes as new information arises.
-We conceptualize time as the perceived urgency of a broad and related issue to those surrounding a policy object.
-This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider it when discussing various forms of public policy.
-It is likely that when speaking about subsidies for fossil fuel companies in the 1980s, presidents would not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased global attention.
+How presidents construct policy objects varies over time as the urgency of certain problems changes not only across settings but in time as new information arises.
+We conceptualize time as the urgency of a broad and related issues to those surrounding a policy object.
+This is largely defined by factors exogenous to the speaker.
+This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider mentioning climate change when discussing various forms of public policy.
+For instance, when speaking about subsidies for fossil fuel companies in the 1980s, presidents would likely not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased relevance of the topic.
 
-While time and space might interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, certain transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
+While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, certain transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
 Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
 
-Our conceptual framework, thus, combines Bacchi’s theory of problem-representation and Keck and Sikkink’s theory of transnationalism to account for diverse problem-constructions.
-We help to advance the literature about the Amazon in two ways.
-First, we provide an outlook of the region, its people and forest beyond its environmental issues by focusing on different problem-constructions.
-In doing so, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented as a problem.
-Second, many analyses of Brazilian environmental policies dissect its national and international nature but do not adopt methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
-Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
+Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions.
+We help to advance the literature about the Amazon in three main ways.
+First, we provide an outlook of the region, its people, and forest beyond its environmental nature by focusing on different problem-constructions.
+In doing so, we take a step back and avoid assuming what type of problem the Amazon is.
+Instead, we focus on how the Amazon has been represented as a problem.
+Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
+Our focus on presidential speeches afford us the analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
 Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017].
-When it comes to the environment, studies tend to focus primarily on Bolsonaro’s discourse [@marquardt2022; @mendes2022] or policies [see @capelari2023].
-We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there really is.
+When it comes to the environment, studies tend to focus primarily on Bolsonaro's discourse [@marquardt2022; @mendes2022].
+We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there is.
+
+If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances.
+While there might exist convergences of priorities over time, as problems become more urgent, contradictions become possible.
+This does not mean that policies and priorities change instantaneously and consequently do not matter.
+Rather, presidents will focus on representing issues in forms aligned with what their perception of an audience are.
 
@@
 
-To create a dataset containing all Brazilian presidential speeches,we update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.The final dataset contains 6,240 speeches with their date and location.
-We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem “amazon”.
-In Portuguese, the stem captures terms such as “Amazonia”, “Amazonica”, “Amazonidas”, “Amazonense(s)”, “Amazonas”, among others.
+To create a dataset containing all Brazilian presidential speeches, we update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.
+The final dataset contains 6240 speeches with their date and state or country location.
+We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem "amazon".
+In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
 We find that 968 speeches are, at least partially, about the Amazon.
@@
 
-*National Sovereignty* 
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted “the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru” [@hecht1990, p.
+*National Sovereignty* In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
 8], and secured the Amazon as Brazilian.
@@
 
-*Economic Integration* 
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005].
-In 1966, the Brazilian Military launched ‘Operation Amazon’, a policy to modernize the region based on three assumptions [@acker2021].
+*Economic Integration* The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005].
+In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021].
 First, it assumed that nature should be conquered by mankind.
@@
 The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions have at their core the development of the necessary infrastructure (physical, fiscal, or monetary) to integrate the region into the national and international economy.
+These policy solutions have at their core the development of the necessary infrastructure to integrate the region into the national and international economy.
 
-*Environmental Conservation*
-The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
-The creation of these institutions stemmed from the impression of the lack of control over the environment following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
+*Environmental Conservation* The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
+The creation of these institutions stemmed from the impression of the lack of control over the environment, following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
 This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987].
 The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted.
-The policy solution implies, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
+The policy solutions imply, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
 
-*Social Development*
-As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples’ dignity, standards of living, and other constitutional rights.
+*Social Development* As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
+Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
 However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
@@
 Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
-The policy solution implies enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.
+The policy solutions imply enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.
 
@@
 
-Using a random sample of 1024 Amazonian statements and the codebook (see appendix), we hand-coded 50% of our data to train a machine learning model, yielding an average intercoder agreement of 85%.
-Any disagreements in coding were resolved through discussion and refinement of the codebook.
+We randomly select a sample of 1024 Amazonian statements (50% of our data) and each author hand-codes it separately.
+Once manual coding was finished, the average intercoder agreement was 86%, the authors resolved disagreements through discussion and refined the codebook (see appendix).
+We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations) to train a machine learning algorithm.
 We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and thus the training set size should be increased [see @grimmer2022].
 
-We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations).
-We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories[@meyer2021; @noble2006], to train a model to label text.
-The model was validated by testing it on the validation set and it was 95% accurate in coding these statements.
-The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements.
-^[We also train the model to identify false positive matches in Amazonian statements.
-These are statements that contain the stem “amazon” but are not meaningful as they might salute the governor of the Amazon, for example.]
+We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text.
+The model was validated by testing it on the validation set.
+As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
+The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements [^1].
+Automating the code saved the authors about two months.
+
+[^1]: We also train the model to identify false positive matches in Amazonian statements.
+These are statements that contain the stem "amazon" but are not meaningful as they might salute the governor of the Amazon, for example.
 
@@
 
-Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of an aligned problem. This comprises our independent variables.
+Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of an aligned issue. This comprises our independent variables.
 
@@
 When speaking in Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon.
-Such expectations might be distinct from the ones’ audiences in non-Amazonian Brazilian States.
+Such expectations might be distinct from the ones' audiences in non-Amazonian Brazilian states.
 Furthermore, during visits to Amazonian countries, presidents may perceive them as peers facing similar challenges and adjust their speeches accordingly.
@@
 multilateral mechanism, private fora, bilateral visit, bridge inauguration), it is difficult to programmatically code exact locations from thousands of speeches that often mention multiple locations in the same text.
-Nevertheless, we believe the four settings coded are already enough to demonstrate whether, and how, problem-construction might change transnationally.
+Nevertheless, we believe the four settings coded are enough to demonstrate whether, and how, problem-construction might change transnationally.
 
@@
 Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their urgency over time.
-To capture the urgency of problems, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
+To capture the urgency of aligned issues, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
 When deforestation rates are high, the problem of environmental conservation can be perceived as more urgent.
@@
 
-We use fixed-effect logistic regression models (indexed by president) to predict the probability of a speech mentioning the Amazon (model 1) and each of the four problem-constructions (models 2-5).
-The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes (i.e.
-ideology).
-For instance, if a president’s political ideology predicts variation in our dependent variables, fixed-effects could control for such issues along other unit-unvarying characteristics [@allison2009].
+We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon (model 1) and each of the four problem-constructions (models 2-5).
+The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes.
+Presidents' political ideology can affect their preferred problem-construction.
+As well, presidents might have preferences for a specific setting given their agenda[^2].
+Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].
+
+[^2]: Figure 5 (in appendix) confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.
 
@@
 We chose to model each construction separately, and to focus on pure-types (i.e.
-statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust coefficients.
+statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust findings.
 Our main explanatory variables are settings and urgency, as described above.
-
-We also add two control variables in the models: election years and peak years.
-In the case of election years, we control for the possibility of presidents constructing the Amazon in systematically different ways in those years.
-In the case of peak years, these are years in which the Amazon was mentioned more often as a share of all presidential speeches.
-We calculate these by capturing years in which mentions of the Amazon are above one standard deviation from their mean share.
+We add one control, election years, due to the possibility of presidents constructing the Amazon in systematically different ways during campaigns.
 
@@
 
-## 4.1 The Amazon as a transnational problem: setting and urgency
+## 4.1 The Amazon problem: setting and urgency
 
-We argue that presidents’ expectations about an audience at a certain setting and the urgency of specific problems explain variations in when the Amazon becomes a  problem and how it is constructed as a type of problem it is.
-Our models, below, confirm the relationships expected by our framework.
+Following our framework, we argue that presidents' expectations about an audience at a certain setting and the urgency of specific aligned issues explain variations in when the Amazon is a problem and what type of problem it is.
+Our models, below, confirm the expected relationships.
 
@@
 
-As we argue that the effects of setting and urgency are cumulative, we start by first scrutinizing the relationship between the former and problem-construction.
+We start by first scrutinizing the relationship between the setting and problem-construction.
 Model 1 addresses the question of when the Amazon is a problem to begin with.
-We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian States within Brazil.
+We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian states within Brazil.
 The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.
@@
 In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
-To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil where they are more likely to construct the Amazon as an issue of environmental conservation.
-While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: both are less likely outside Brazil.
-Finally, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they are speaking elsewhere.
+To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil, where they are more likely to construct the Amazon as an issue of environmental conservation.
+While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: constructing the Amazon as issues of economic integration and social development are less likely to take place when presidents speak in outside of Brazil and other Amazonian countries.
+Lastly, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they speak elsewhere.
 
-Overall, we interpret these results as evidence that presidents construct the Amazon as different problems based on their expectations of an audience at certain settings.
-When it comes to non-Amazonian countries, it is likely that Brazilian presidents construct the Amazon as an issue of environmental conservation to leverage financial support for the Amazonian region.
-The Brazilian government successfully funded domestic public policy with transnational financial support on several occasions since the 1990s, most notably with the Amazon Fund or policies in the Amazon which provided over USD 1 billion for the region along with multiple bilateral and philanthropic grants [@silva-muller2022].
+We interpret these findings to be consistent with our conceptual framework: presidents construct the Amazon as different problems based on their expectations of settings.
+When it comes to non-Amazonian countries, it is likely that Brazilian presidents construct the Amazon as an issue of environmental conservation to leverage financial support for policies in the Amazonian region.
+The Brazilian government successfully funded domestic public policy with transnational financial support on several occasions since the 1990s, most notably with the Amazon Fund which provided over USD 1 billion for the region[@silva-muller2022].
 That is, presidents realize material and symbolic gains outside of Brazil and of Amazonian countries, by constructing the Amazon as an environmental problem.
@@
 In turn, when speaking within the Brazilian Amazon, presidents see their audiences as local constituencies.
-Therefore, presidents never stopped pursuing a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds.
+Presidents pursue a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds.
 For example, rural credit offered to local agricultural producers in Amazonian states went up from 500 million reais a year in 1999, to over 4 billion reais a year by 2012 [@capobianco2021].
@@
 Presidents likely highlight and push for economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.
+Thus, we interpret this as evidence that presidents view settings as distinct policymaking instances.
 
-We also argue that the urgency of an aligned problem in time influences the likelihood of the president mentioning the Amazon and what they will say.
-We find evidence across our models that this holds.
-For instance, we find that presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the urgency of environmental problems (model 1).
+We also argue that the urgency of an aligned issue in time influences the likelihood of the president mentioning the Amazon and what they will say.
+We find evidence across our models that this holds in unexpected ways.
+Presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the urgency of environmental related issues (model 1).
 The opposite is true for inflation.
 As inflation increases, and so the urgency of economic problems, presidents are more likely to generally mention the Amazon in speeches (model 1).
-This relationship is even more interesting when we look at how amazonian constructions vary in presidential speeches as environmental or economic problems become more urgent (models 2-3).
-We find strong evidence that when the urgency of environmental problems increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
-Alternatively, as the urgency of economic problems increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation  increases.
+This relationship is more intricate when we look at how amazonian constructions vary in presidential speeches as environmental or economic issues become more urgent (models 2-3).
+We find evidence that when the urgency of environmental related issues increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
+Alternatively, as the urgency of related economic issues increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation increases.
 
 In line with our framework, the urgency of aligned problems relates to problem-constructions in intricate ways.
-By opting for an alternative problem-construction to that which is urgent, presidents likely side-step issues as they get more urgent, while boosting positive aligned outcomes to attempt and collect benefits as aligned issues become less urgent.
+We interpret that, by opting for an alternative problem-construction to an aligned one which is urgent, presidents often side-step issues as they get more urgent, while boosting about positive aligned outcomes to attempt and collect benefits as aligned issues become less urgent.
 
@@
 
-Looking at speeches that mention the Amazon over time (the dependent variable of model 1) reviews several interesting trends.
+Looking at speeches that mention the Amazon over time (model 1) reviews several interesting trends.
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
 By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not.
-On average, presidents mention the Amazon in 15.5% of their speeches ^[For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).].
+On average, presidents mention the Amazon in 15.5% of their speeches [^3].
 This suggests the Amazon is a topic of relative high importance for presidents generally.
@@
 We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.
+
+[^3]: For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).
 
@@
 Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, there were no peaks.
-This is aligned with our model as the urgency of the environmental problem was high during the period.
 In 2009, however, we observed another peak which coincided with the Copenhagen Summit.
-Lula led the delegation to the summit with a strong climate leadership self-image of “we deliver” [@franchini2019], in a moment when deforestation rates have been decreasing since 2005.
+Lula led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019], in a moment when deforestation rates have been decreasing since 2005.
 From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
@@
 
-We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro’s presidency.
+We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro's presidency.
 At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019.
-Right after being elected in 2018, Bolsonaro went on to retrieve Brazil’s hosting status for COP25.
-Alongside, Bolsonaro’s dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the topic became prominent in his speeches.
+Right after being elected in 2018, Bolsonaro went on to retrieve Brazil's hosting status for COP25.
+Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the Amazon became prominent in his speeches.
 This event also drove the proportion of speeches mentioning the Amazon up.
 
-The figure 2, above, also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, is not related to proposed policy solutions.
+The figure 2, above, also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, does not coincide with proposed environmental policy solutions.
 In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022].
-In 2004, President Lula decreed the creation of Brazil’s Plan to Combat and Control Deforestation in the Brazilian Amazon.
+In 2004, President Lula decreed the creation of Brazil's Plan to Combat and Control Deforestation in the Brazilian Amazon.
 In 2008, Brazil announced the Amazon Fund, the largest fund of this kind ever created.
@@
 
-The longitudinal trends in Amazonian speeches reveal a dynamic that our models did not capture: we find that all peak years relate to high-profile environmental events within the country that gained large repercussions within and outside of the country.
+The longitudinal trends in Amazonian speeches reveal a dynamic that our models did not capture: we find that all peak years coincide with high-profile environmental events within the country that gain large repercussions within and outside of the country.
 These are events that received distinct coverage from transnational actors as media and civil society outside of Brazil, which is likely one of the reasons why it temporarily drives the topic up.
@@
 While our measure of urgency of the environmental problem does not capture these events, these events change how urgent of a problem the Amazon is in certain years.
-In doing so, these events bring outside attention to the Amazon to which the president's response is more likely to be in the form of reaffirming Brazil’s sovereignty over the Amazon (model 5).
-That is, presidents tend to construct the Amazon as an issue of national sovereignty and side-step the aligned environmental conservation constructions around high-profile environmentally related events.
 
@@
 While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
-In this section, we investigate how pure-types and mixed-types problem-constructions evolved over time.
-Figure 3, below, illustrates the annual share of pure-types problem-constructions.
+Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.Interestingly, and to begin with, peak years identified in Figure 2 do not coincide with increases of specific problem-constructions in Figure 3.
 
@@
   scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
-                                  "Social Development", "National Sovereinty"))
+                              	"Social Development", "National Sovereignty"))+
+  guides(color=guide_legend(nrow=2,byrow=TRUE))
 ```
@@
 Pure economic integration constructions were the most frequent from 1985 to 2009.
-This is especially pertinent during Cardoso’s presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
-This was a period when the urgency of the environmental problem grew as deforestation rates were increasing, so presidents were more likely to avoid environmental conservation constructions.
+This is especially pertinent during Cardoso's presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
+This was a period when the urgency of the environmental problem grew as deforestation rates increased so, following our model findings, Cardoso was more likely to avoid environmental conservation constructions.
 When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-During this period, the urgency of environmental problems decreased along with deforestation rates, so presidents were more likely to employ environmental conservation constructions.
+During this period, deforestation rates sharply decreased and so did the urgency of environmental problems.
+Lula was, therefore, more likely to employ environmental conservation constructions.
 From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration.
-However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored again.
+However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), a period of sharp increase in deforestation rates, economic integration constructions become the most favored Amazonian problem-construction again.
 
-We also notice a steady increase of sovereignty as salient problem-constructions from 2008 onwards, much before Bolsonaro was elected.
+We also identify a steady increase of sovereignty as salient problem-constructions from 2008 onwards, much before Bolsonaro was elected.
 This might relate to policy developments that were taking place.
-The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of government [@horochovski2016].
-In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil’s sovereignty over the Amazon while rebating  broad criticism from civil society actors with accusations of internationalization attempts.
+The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of the government [@horochovski2016].
+In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil's sovereignty over the Amazon while rebating broad criticism from civil society actors with accusations of internationalization attempts.
 Therefore, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making.
-Bolsonaro’s problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
+Bolsonaro's problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
 
-Our operationalization of problem-constructions also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
-Figure 4, below, shows that constructing the Amazon as multiple issues increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
-Mixed-type problem-constructions in discourse offer more complex and balanced understandings of the Amazon as a problem.
+Our operationalization of problem-constructions (see Figure 1) also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
+Figure 4, below, shows that constructing the Amazon as multiple issues generally increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
+Mixed-type problem-constructions in discourse offer more complex and multifaceted understandings of the Amazon as a problem.
 The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.
-Indeed, we observe an increase in policies that attempt to address environmental and social problems, for instance, at the same time.
+Indeed, we observe an increase in policies that attempt to address environmental, economic, and social problems, for instance.
 Examples of this are payment for ecosystem services conditioned for low income populations residing in the Amazon [@silva-muller2022a].
-Relatedly, this is aligned with transnational processes as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
+Relatedly, this is aligned with transnational processes such as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
 
-```{r Figure mixed, fig.cap="Mixed-types problem constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure mixed, fig.cap="Mixed-types problem-constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
 #summary(as.factor(ama_mx$mx_cat))
@@
           	se = FALSE, linewidth =0.75, linetype="solid") +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1), limits=c(0,.4)) +
   labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
@@
 
-We interpret the balance in pure-types and the increase in mixed-types as evidence that presidents increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years decades.
-We see in these findings the possibility of the Amazon becoming an increasingly coherent transnational problem, where audiences do not only recognize it as a single pure-type but an intricate policy object.
+We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the binary between economic and the environmental ways of seeing the Amazon that had prevailed in the previous years decades.
+We interpret this as evidence of the Amazon becoming increasingly recognized as an intricate policy object in transnational politics.
 
-# 5. Conclusion
+# 5 Conclusion
 
-This paper investigated where, when, and how the Brazilian Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.
-We have four main empirical findings.
-First, we find that presidents construct the Amazon as different problems depending on where they speak.
-When presidents speak outside the country and far away from the Amazon, they are more likely to construct the Amazon as an issue of environmental conservation.
-Within the country or the Amazonian region, presidents prefer constructing the Amazon as an issue of social development and economic integration.
-Second, we find that presidents are likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
-low deforestation rates).
+This paper investigated how the Amazon has been constructed as a political problem over time through Brazilian presidential speeches.
+We have four main findings.
+First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation.
+Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration.
+Second, we find that presidents are more likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
+lowering deforestation rates).
 When environmental related problems become more urgent (e.g.
 rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
-Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourse.
-Relevant Amazonian related policies, in turn, do not affect the discursive attention presidents pay to the Amazon.
-Finally, we find that we are now in a period when the Amazon as a binary of either environmental or an economic issue has been overcome, at least discursively, and Amazonian problem-constructions have become more mixed and balanced lately.
+Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses, but does not affect systematically how the Amazon is constructed as a problem.
+Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
 
-The conceptual implications of our findings are at least threefold.
-First, we provide an outlook of the region, its people and forest beyond its environmental nature by focusing on different problem-constructions.
-In so doing, we avoid assuming what type of problem the Amazon is and, instead, focus on how it has been represented.
-We show that investigating problem-representation to begin with, can highlight the extent to which certain perspectives of problems are assumed, ignored or privileged.
-Second, while many analyses of Brazilian environmental policies intend to dissect its national and international nature, they rarely adopt methodological strategies that distinguish how important actors behave differently in both scenarios (Hoschstetler and Keck, 2004).
-Our focus on presidential speeches affords us analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
-In doing so, we can contextualize problem-constructions in space and show how they vary.
-Third, we argue that another key factor in explaining variation in problem-construction is the urgency of specific problems in time.
-As the environmental crisis increases in its salience, important actors are less likely to ignore it.
-They need to find strategies, such as side-stepping issues or boasting positive outcomes, in order to remain credible to their audiences.
+Overall, our findings suggest that we must move beyond assuming the Amazon is a single issue to identify how discourse and policy reflects its environmental, social, economic, and sovereignty-related complexity.By doing so, we can better understand the cohesive, the negotiated, and the contrasting discourses and policies forwarded by transnational actors as they perceive transnational settings as distinct policymaking instances.
+By capturing this variation in discourse, we can better understand why, when, and how, various overlapping policies directed at the same object are developed and implemented.
+Concretely, this implies that even as the environmental crisis becomes more salient, we will likely not see coherent and cohesive environmental, economic, and social discourses or policies towards the Brazilian Amazon.
 
-In terms of future research, we see at least three possibilities.
-First, we have introduced a flexible framework that can be extended to cover other policy objects.
-We expect to inspire investigations of other policy objects in domains beyond the Brazilian Amazon (e.g.
-Cerrado biome, Antarctic, inequality, criminality, etc.).
-Relatedly, as we find evidence that problem-constructions in Amazonian countries differ from other settings, scholars could investigate how Amazonian problem-constructions in other Amazonian countries differ, and not, from the ones we see in the Brazilian case.
-Second, while we argue that settings are important to explaining variation in problem-constructions, social media can change this in fundamental ways.
-As short videos of presidential discourses travel more rapidly than ever, social media might contribute to diminishing the importance of physical settings.
-This could make presidents less likely to afford very diverging problem-constructions anymore.
-Alternatively, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences.
-We look forward to works that investigate how setting and audience interact with problem-construction in unofficial political communications in the era of social media.
-Finally, while we do not explicitly conceptualize the possibility of problem-constructions having a direct effect on policy outcomes, it is possible, though, to design studies that test the causal relationship between presidential discourse and outcomes.
-In a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro’s speech to covid-19 infections.
-We look forward to studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.
+In terms of future research, we see at least three possibilities.First, scholars should investigate how problem-constructions change across settings and over time for other Amazonian countries or other policy objects, and in comparative ways.
+For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome[@villoria2022].
+By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem".
+Moreover, social media can change political communications in fundamental ways.
+The spread of political communications in social media could, on the one hand, contribute to diminishing the importance of physical settings and make presidents less likely to afford diverging problem-constructions.
+On the other hand, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences.
+We look forward to works that investigate variation in problem-constructions in the era of social media.
+Finally, in a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro's speech to covid-19 infections.
+While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.
 
@@
   theme_am() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom")+
+  guides(fill=guide_legend(nrow=2,byrow=TRUE))
 ```

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
legend of figures

@@
 
+We start by first scrutinizing the relationship between the setting and problem-construction.
+Model 1 addresses the question of when the Amazon is a problem to begin with.
+We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian states within Brazil.
+The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.
+
+The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings.
+In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
+To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil, where they are more likely to construct the Amazon as an issue of environmental conservation.
+While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: constructing the Amazon as issues of economic integration and social development are less likely to take place when presidents speak in outside of Brazil and other Amazonian countries.
+Lastly, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they speak elsewhere.
+
 ````{=tex}
@@
 ````
-
-We start by first scrutinizing the relationship between the setting and problem-construction.
-Model 1 addresses the question of when the Amazon is a problem to begin with.
-We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian states within Brazil.
-The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.
-
-The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings.
-In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
-To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil, where they are more likely to construct the Amazon as an issue of environmental conservation.
-While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: constructing the Amazon as issues of economic integration and social development are less likely to take place when presidents speak in outside of Brazil and other Amazonian countries.
-Lastly, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they speak elsewhere.
 
@@
           	se = FALSE, linewidth =0.75, linetype="solid") +
-  scale_y_continuous(labels = percent_format(accuracy = 1), limits=c(0,.4)) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
   labs(x = "", y = "", title ="Share of mixed-types problem-constructions by year",
@@
   scale_color_manual(values = "yellow3")
+
 ```
@@
 The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support.
-The authors would also like the two anonymous reviewers for their comments and suggestions.
-Finally, we would like to thank Anna, Federico, Mario, and Rodrigo for their invaluable help.
+The authors would also like to thank the anonymous reviewers, Anna, Federico, Mario, and Rodrigo for their invaluable help.
 

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Updated article by addding lag analysis in appendix and footnote in text

@@
 library(plm)
+library(timetk)
+library(lubridate)
 Sys.setlocale("LC_ALL", "C")
@@
 While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
-Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.Interestingly, and to begin with, peak years identified in Figure 2 do not coincide with increases of specific problem-constructions in Figure 3.
+Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.
+Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 ^[4].
+
+^[4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data.
+Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix.
+The plots illustrate no significant autocorrelations between peak years and problem-constructions.
 
@@
 In terms of future research, we see at least three possibilities.First, scholars should investigate how problem-constructions change across settings and over time for other Amazonian countries or other policy objects, and in comparative ways.
-For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome[@villoria2022].
+For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome [@villoria2022].
 By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem".
@@
 ````
+
+```{r peak years test, fig.cap="Lag analysis for problem-constructions and for year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+ama_mx %>%
+  count(year, mx_cat) %>%
+  group_by(year) %>%
+  mutate(perc = n / sum(n),
+         year = lubridate::as_date(year)) %>% 
+  select(-n) %>%
+  filter(mx_cat != "Other") %>%
+  group_by(mx_cat) %>% 
+  plot_acf_diagnostics(.date_var = year,
+                       .value = perc,
+                       .show_white_noise_bars = TRUE,
+                       .interactive = FALSE)
+```

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
footnote correction

@@
 Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.
-Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 ^[4].
+Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 [^4].
 
-^[4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data.
-Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix.
-The plots illustrate no significant autocorrelations between peak years and problem-constructions.
+[^4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data.
+Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix.The plots illustrate no significant autocorrelations between peak years and problem-constructions.
 

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Removed space in footnotes in text to improve word count

@@
 As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
-The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements [^1].
+The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1].
 Automating the code saved the authors about two months.
@@
 By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not.
-On average, presidents mention the Amazon in 15.5% of their speeches [^3].
+On average, presidents mention the Amazon in 15.5% of their speeches[^3].
 This suggests the Amazon is a topic of relative high importance for presidents generally.
@@
 Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.
-Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 [^4].
+Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3[^4].
 

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
new version

@@
 ---
-title: One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985
+title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
+  Presidential Discourse since 1985"
 author:
-- Livio Silva-Muller
-- Henrique Sposito^[Both authors contributed equally to the article.
-Names are ordered alphabetically.
-Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy.
-Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.]
-date: 17 February 2023
+- "Livio Silva-Muller"
+- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
+  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
+  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
+  and Political Sciences and affiliated to the Centre for International Environmental
+  Studies.]
+date: "17 February 2023"
 output:
-  pdf_document: default
+  word_document: default
   latex_engine: xelatex
@@
     df_print: paged
+  pdf_document: default
 fontsize: 12pt
@@
   \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
-always_allow_html: TRUE
+always_allow_html: yes
 bibliography: references.bib
 csl: chicago.csl
-abstract: The Amazon is a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns.
+abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns.
 Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem.
 We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches.
-To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they speak and when.
+To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics.
 Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985.
-We find that presidents often construct the Amazon as an environmental problem when speaking far away from the Amazon, whereas they usually construct it as economic or social problems when in the Amazon.
-Furthermore, presidents increasingly construct the Amazon as multiple problems rather than only economic or environmental problems.
+We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon.
+Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
 ---
@@
 ```{=latex}
-\wordcount{ 8190 (including abstract, text, references, and footnotes)}
+\wordcount{ 7900 (including text, endnotes, footnotes and references)}
 ```
@@
 The Brazilian Amazon, which covers around 60% of the whole biome, is home to over 28 million people.
-The Rainforest spans over seven international borders and contains enormous amounts of highly valued minerals such as iron ore and gold.
+The Rainforest spans over seven international borders.
 Its most inhabited city, Manaus, enjoys a distinct fiscal regime designed to create jobs in the region and connect its economy to the rest of the country.
-At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas.
+At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas, rendering it an important component of global climate mitigation.
 The Brazilian Amazon is, thus, a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns.
-Despite this complexity, governments are often portrayed in the literature about policies in the Amazon as having a single understanding of what the Amazon problem is and consequently, proposing coherent policies for the region.
-Although it is helpful to compare variation across different governments, this analysis oversimplifies policies and discourse within governments misrepresenting what, in reality, is more intricate and inconsistent.
+Despite this complexity, the literature about policies in the Amazon often portray governments as having a single understanding of what the Amazon problem is and, consequently, proposing coherent policies for the region.
+Although this literature is helpful to compare variation across different governments, such analyses oversimplifies policies within governments misrepresenting what, in reality, is more intricate and inconsistent.
 In this article, we ask how has the Amazon been constructed as a political problem since 1985?
 
-We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as Presidents, construct objects of policies as particular problems depending on where and when they participate in politics.
+We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as presidents, construct objects of policies as particular problems depending on where and when they participate in politics.
 To examine this variation, we created a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
-Drawing from the socio-cultural history of the Brazilian Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon.
-These problem-constructions relate to national sovereignty, economic integration, social development, or environmental conservation.
-We employ supervised machine learning to classify how the Amazon related statements construct it as a problem, and then conduct an inferential and descriptive analysis of the data.
-A systematic focus on presidential speeches is important because while many scholars recognize decisions to deforest on the ground are derived from what the government says and does [@capobianco2021; @campbell2015], we lack empirical accounts of the Amazon in presidential discourse.
+Drawing from the socio-cultural history of the Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon.
+These problem-constructions touch upon national sovereignty, economic integration, social development, or environmental conservation.
+We employ supervised machine learning to classify how Amazon related statements construct the Amazon as a problem.
+We then conduct an inferential and descriptive analysis of the data.
+A systematic focus on presidential speeches is important because many scholars recognize decisions to deforest on the ground are derived from government's policies and discourse [@capobianco2021; @campbell2015].
+Still, we lack empirical accounts of the Amazon in presidential discourse.
 
@@
 Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration.
-Second, presidents are more likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
-lowering deforestation rates).
-When environmental related issues become more urgent (e.g.
-rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
-Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses, but does not systematically change how the Amazon is constructed as a problem.
+Second, presidents are more likely to construct the Amazon as an environmental conservation problem when deforestation rates decrease.
+When deforestation rates increase, presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
+Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses.
+However, these events does not systematically change how the Amazon is constructed as a problem.
 Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
@@
 Empirically, we contribute to the literature about the Amazon by providing the first overview of where, how, and when the Amazon has been constructed as a problem in presidential speeches.
-We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an aligned issue is.
-Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important actors behave differently inside and outside the country, by doing so we reveal how the Amazon as a problem varies in transnational politics.
+Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important transnational actors behave differently inside and outside the country.
+We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an issue is.
 Conceptually, problem-constructions highlight the extent to which Amazonian problems are ignored or privileged in transnational politics, and avoids assumptions of the Amazon as a solely environmental problem.
 
-This article is divided into 4 sections.
+We divide this article into four sections.
 First, we outline the connection between problem-constructions, transnationalism, and presidential speeches.
@@
 
-# 2. Theory: problem-constructions, transnational settings, and problem urgency
+# 2. Theory: problem-construction and transnationalism
 
@@
 
-Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies and discourse [see @lopez2023; @fairfield2017; @poncedeleon2021] than suggested by the literature above.
-We argue that the reason behind monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is.
-Because of the Amazon Rainforest role in global climate-mitigation, , and consequently, as an environmental problem.
-If the Amazon is thought of as an environmental problem, then it demands an environmental solution.
-The Amazon region, its peoples, and forests, though, are a historically complex object of policies that comprise economic, social, and sovereignty concerns.
+Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies than suggested by the literature above [see @lopez2023; @fairfield2017; @poncedeleon2021].
+We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is.
+Because of the Amazon Rainforest role in global climate-mitigation, the Amazon is often assumed to be an environmental problem that demands environmental solutions.
+The Amazon region, its peoples, and forests, though, are a historically complex object of policies that also comprise economic, social, and sovereignty concerns.
 
@@
 Following Bacchi, we place discourse about policy objects at the center of our conceptual framework.
-We define policy objects as objects that demand dedicated political attention and argue that by deciding to speak about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem.
+We define policy objects as objects that demand dedicated political attention and argue that by speaking about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem.
 The problem might be either explicitly stated, or implicitly hidden in the underlined solution.
@@
 
-Presidential discourses are a good instance to identify problem-constructions over time.
+Presidential discourses are a good instance to identify problem-constructions over time and across spaces.
 Presidential speeches and policy share a co-constitutive relationship as speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
@@
 In Brazil's hybrid system, often referred to as a Coalitional Presidentialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies.
-This means that presidents often have enough power and support to implement the agenda they deem appropriate.
+They also have vast decree powers to adopt policy unilaterally[@pereira2008].
+This means that presidents often have enough power and support to implement the agenda they deem appropriate, especially in the case of climate change[@hochstetler2021].
 We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.
 
-## 2.2 Transnational settings, urgency, and variation in problem-constructions
+## 2.2 Settings, urgency and variation in problem-constructions
 
-The possibility of different problem-constructions for the same policy object in political discourse requires an explanation of why they vary.
+The possibility of different problem-constructions for the same policy object requires an explanation of why they vary.
 There are two potential theories for explaining variation in problem-construction in international/transnational politics: Putnam's two-level game and Keck and Sikkink's transnational networks.
@@
 434].
-The theory has been expanded to cover multi-levels games [@collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups.
+The theory has been expanded to cover multi-levels games [see @collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups.
 Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups.
-Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found supporting evidence that location does not change the content of the speech, but can lead presidents to side-step the issue.
+Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found little support that location changes the content of presidential speeches.
 
 The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
-This view seems incompatible with the possibility of contradictory policies and of varied problem-constructions.
+This view seems incompatible with the possibility of varied problem-constructions for the same policy object.
 Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, from the local level to the international level [@nye1971; @keck1998].
-In this context, international summits are considered a transnational setting because non-state actors participate in and shape them.
-We view, for instance, summits as the United Nations Framework Convention of Climate Change (UNFCCC) not only as a purely intergovernmental body, but as a transnational space composed of international media, corporations, non-governmental organizations, and social movements.
+In this context, international summits, for example, are considered a transnational space because they are composed of international media, corporations, non-governmental organizations, social movements, and various state actors.
 
-While @keck1998 theory is developed in the context of value-based advocacy groups, hence non-state actors, the overall view of international politics holds for state actors.
+Although @keck1998's theory is developed in the context of value-based advocacy groups( i.e.
+non-state actors), the overall view of international politics holds for state and other non-state actors.
 Their theory rejects the dichotomy of international and domestic levels and argues that the identity and goals of transnational actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
@@
 Important participants of transnational networks, as presidents, can use a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
-They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p.
-24].
-They can also leverage institutions to realize symbolic or material gains.
+They can create politically meaningful information and move it where they believe it can have an impact or leverage institutions to realize symbolic or material gains[@keck1998].
 In this sense, the positions of actors in transnational networks derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.
@@
 Problem-constructions are choices transnational actors have of how to represent objects of policies as problems.
-If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors', as presidents, choice of problem-constructions depend on their views of an audience at a certain period.
-Specifically, how urgent a problem is in a certain space and/or at a certain time.
+If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors' choice of problem-constructions depend on their views of an audience at a certain period.
+Specifically, how urgent a problem is in a certain space or at a certain time.
 
@@
 
-Transnational actors construct problems and attempt to inform and/or leverage audiences for symbolic or material gains according to their expectations of that audience.
+Transnational actors construct problems and attempt to inform or leverage audiences for symbolic and material gains according to their expectations of that audience.
 We conceptualize space in terms of settings.
 Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study.
-This indicates how transnational actors construct policy objects as problems can vary, for instance, within the country --- speaking inside the Amazon region versus outside --- because presidents identify these audiences as distinct.
-The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where presidents' expectations and identities of an audience could diverge completely from that of domestic actors.
-In each one of these settings different problems might be more urgent and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.
+This indicates how transnational actors construct policy objects as problems can vary for instance, within the country --- speaking inside the Amazon region versus outside --- because transnational actors identify these audiences as distinct.
+The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where transnational actors' expectations and identities of an audience could diverge completely from that of domestic actors.
+In each one of these settings transnational actors' expectations might influence how a problem is implicitly or explicitly constructed.
 
@@
 
-How presidents construct policy objects varies over time as the urgency of certain problems changes not only across settings but in time as new information arises.
-We conceptualize time as the urgency of a broad and related issues to those surrounding a policy object.
+How transnational actors construct policy objects varies as the urgency of certain problems changes as new information arises over time.
+We conceptualize time as the urgency of broad and related issues to those surrounding a policy object.
 This is largely defined by factors exogenous to the speaker.
@@
 
-While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, certain transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
-Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
+While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
+Accordingly, transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
 
-Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions.
-We help to advance the literature about the Amazon in three main ways.
-First, we provide an outlook of the region, its people, and forest beyond its environmental nature by focusing on different problem-constructions.
+If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances.
+While there might exist convergences of priorities over time, as problems become more urgent, contradictions are possible.
+This does not mean that policies and priorities change instantaneously and consequently do not matter.
+Rather, transnational actors will focus on representing issues based on their perception of an audience.
+
+Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions in Brazilian presidential speeches.
+We help to advance the literature about the Amazon in three ways.
+First, we provide an outlook of the region, its people, and forest beyond its environmental nature.
 In doing so, we take a step back and avoid assuming what type of problem the Amazon is.
 Instead, we focus on how the Amazon has been represented as a problem.
-Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007].
+Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both policymaking instances.
 Our focus on presidential speeches afford us the analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
@@
 
-If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances.
-While there might exist convergences of priorities over time, as problems become more urgent, contradictions become possible.
-This does not mean that policies and priorities change instantaneously and consequently do not matter.
-Rather, presidents will focus on representing issues in forms aligned with what their perception of an audience are.
-
 # 3. Research design
 
-To create a dataset containing all Brazilian presidential speeches, we update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.
+## 3.1 Data
+
+We update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.
 The final dataset contains 6240 speeches with their date and state or country location.
@@
 
-## 3.1 Operationalizing Amazonian problem-constructions
+## 3.2 Operationalizing Amazonian problem-constructions
 
 We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development.
-While the three formers are present in the literature, we argue a fourth one exists in speeches: social development.
+While the three formers are present in the literature, we argue a fourth one exists: social development.
+Amazonian statements can construct the Amazon as a single problem ( i.e.
+pure-type statements), or can construct the amazon as referring to multiple problem-constructions (i.e.
+mixed-types), as Figure 1 (below) details.
 
-*National Sovereignty* In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
-8], and secured the Amazon as Brazilian.
+*National Sovereignty*
+
+In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
+8], and secured most of the Amazon as Brazilian.
 While military diplomacy was very successful, the process did not come without its issues and sovereignty in the Amazon became one of the main military concerns[@rajao2020].
-More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become more varied.
+More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become varied.
 Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region.
-The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.
+The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and foreign or non-state presence in the region are concerning.
+The policy solutions that implicitly represent this problem include the monitoring of the borders and strict regimes related to entry into the region.
 
-*Economic Integration* The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005].
+*Economic Integration*
+
+The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005].
 In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021].
@@
 The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions have at their core the development of the necessary infrastructure to integrate the region into the national and international economy.
+These policy solutions have at their core the development of the necessary infrastructure (physical and fiscal) to integrate the region into the economy.
 
-*Environmental Conservation* The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
+*Environmental Conservation*
+
+The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
 The creation of these institutions stemmed from the impression of the lack of control over the environment, following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987].
+This process accelerated in the late 1980s with the new forms of environmentalism [@viola1987].
 The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted.
-The policy solutions imply, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
+The policy solutions imply further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
 
-*Social Development* As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
+*Social Development*
+
+As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
 Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
@@
 The policy solutions imply enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.
-
-An Amazonian statement can be coded as referring to multiple problem-constructions (see Figure 1 below).
-Amazonian statements, thus, can be pure-type statements (i.e.
-they construct the Amazon as a single problem) or mixed-types (i.e.
-they construct the Amazon as multiple issues).
 
@@
 
-We randomly select a sample of 1024 Amazonian statements (50% of our data) and each author hand-codes it separately.
-Once manual coding was finished, the average intercoder agreement was 86%, the authors resolved disagreements through discussion and refined the codebook (see appendix).
+We randomly selected a sample of 1024 Amazonian statements (50% of our data) and each author hand-coded these separately.
+Once manual coding was finished, the authors resolved disagreements through discussion and refined the codebook (in appendix).
 We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations) to train a machine learning algorithm.
-We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and thus the training set size should be increased [see @grimmer2022].
+We chose to hand code half of the observations because there are multiple categories of how presidents talk about the Amazon, and the training set size should be increased [see @grimmer2022].
 
@@
 The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1].
-Automating the code saved the authors about two months.
+Automating the code saved the authors over one month of work.
 
@@
 
-## 3.2 Operationalizing settings and urgency
+## 3.3 Operationalizing settings and urgency
 
-Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of an aligned issue. This comprises our independent variables.
+Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of issues. This comprises our independent variables.
 
@@
 To operationalize settings, we extract the location of the speech and create four distinct settings: Amazonian states within Brazil, non-Amazonian states within Brazil, Amazonian countries, and non-Amazonian countries.
-Each one of these settings encompasses audiences that can have different expectations in reference to our policy object, the Brazilian Amazon.
-When speaking in Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Brazilian Amazon.
-Such expectations might be distinct from the ones' audiences in non-Amazonian Brazilian states.
-Furthermore, during visits to Amazonian countries, presidents may perceive them as peers facing similar challenges and adjust their speeches accordingly.
-Conversely, when speaking in non-Amazonian countries or at international events such as the UNFCCC or visits to the US or France, presidents may tailor their speeches to align with what they perceive as possible symbolic or material gains from the audience.
+Each one of these settings encompasses audiences that have different expectations in reference to our policy object, the Amazon.
+When speaking in Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Amazon.
+Such expectations might be distinct from the ones' audiences in non-Amazonian states within Brazil.
+Furthermore, during visits to Amazonian countries, presidents may perceive them as peers facing similar challenges related to the Amazon and adjust their speeches accordingly.
+Conversely, when speaking in non-Amazonian countries (e.g.
+international summits or bilateral visits), presidents may tailor their speeches to align with what they perceive as possible symbolic or material gains from the audience.
 
@@
 multilateral mechanism, private fora, bilateral visit, bridge inauguration), it is difficult to programmatically code exact locations from thousands of speeches that often mention multiple locations in the same text.
-Nevertheless, we believe the four settings coded are enough to demonstrate whether, and how, problem-construction might change transnationally.
+Nevertheless, we believe the four settings coded are enough to demonstrate whether, and how, problem-construction changes transnationally.
 
@@
 
-Beyond setting, timing matters because issues aligned to certain problem-constructions vary in their urgency over time.
-To capture the urgency of aligned issues, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
+To capture the urgency of issues, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
 When deforestation rates are high, the problem of environmental conservation can be perceived as more urgent.
 Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more urgent.
-We opt for lagging deforestation rates by one year as the consolidated rates for a certain year are published in the following year.
+We lag deforestation rates by one year as rates for certain years are only published in the following year.
 Since both annual deforestation rates and annual inflation rates come in different measurements (i.e.
@@
 
-This approach to operationalizing urgency also has its limitations.
-Ideally, we would like to add additional proxies of urgency for social and sovereignty issues.
+This approach to operationalizing urgency also has limitations.
+Ideally, we would like to add proxies of urgency for social and sovereignty issues.
 However, social development indicators (e.g.
@@
 In terms of national sovereignty, the way we conceptualize the problem-construction entails internal and external threats which are not easily measured.
-Despite these limitations, we can draw some conclusions from the urgency of environmental and economic issues and their aligned problem-constructions.
+Therefore, we limit our analysis of urgency to environmental and economic issues.
 
-## 3.3 Inferential and descriptive strategies
+## 3.4 Inferential and descriptive strategies
 
-We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon (model 1) and each of the four problem-constructions (models 2-5).
+We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon and each of the four problem-constructions.
 The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes.
-Presidents' political ideology can affect their preferred problem-construction.
-As well, presidents might have preferences for a specific setting given their agenda[^2].
+Both presidents' political ideology and setting preferences[^2] could affect problem-construction.
 Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].
@@
 
-The dependent variables of the model are the share of speeches that mention the Amazon (model 1) and the share of a problem-construction (models 2-5).
+The dependent variables of the model are the share of speeches that mention the Amazon (model 1) and the share of each problem-construction (models 2-5).
 We chose to model each construction separately, and to focus on pure-types (i.e.
@@
 
-We wrap the analysis with a descriptive and longitudinal analysis of Amazonian speeches in time, considering the findings of the models.
+We wrap the analysis with a descriptive analysis of Amazonian speeches in time, considering the findings of the models.
 It is important to outline that we do not make any causal claims.
@@
 Our research design and data do not allow us to do so.
-Instead, we focus on the relationships in themselves rather than their order or cause.
+Instead, we focus on the relationships in themselves rather than their order.
 
-# 4. How has the Brazilian Amazon been constructed as a problem?
-
-We open our analysis with the models predicting the probability of presidents mentioning the Amazon in speeches (model 1) and of presidents employing certain problem-construction (model 2-5).
-Subsequently, we plot and discuss the longitudinal developments of Amazonian speeches and of problem-constructions considering the model results.
+# 4. How has the Amazon been constructed as a problem?
 
@@
 
-Following our framework, we argue that presidents' expectations about an audience at a certain setting and the urgency of specific aligned issues explain variations in when the Amazon is a problem and what type of problem it is.
-Our models, below, confirm the expected relationships.
-
+Following our framework, we argue that presidents' expectations about an audience at a certain setting and the urgency of specific issues explain variations in when the Amazon is a problem and what type of problem it is.
 We start by first scrutinizing the relationship between the setting and problem-construction.
-Model 1 addresses the question of when the Amazon is a problem to begin with.
+The first model (1) addresses the question of when the Amazon is a problem to begin with.
 We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian states within Brazil.
-The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region and biome.
+The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region.
 
 The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings.
-In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries, be it in international summits, bilateral meetings, or fora, presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
-To a lesser extent, this also holds for when presidents speak in non-Amazonian states within Brazil, where they are more likely to construct the Amazon as an issue of environmental conservation.
-While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest the opposite direction: constructing the Amazon as issues of economic integration and social development are less likely to take place when presidents speak in outside of Brazil and other Amazonian countries.
-Lastly, when it comes to national sovereignty (model 5), the problem-constructions are more likely to take place when presidents speak at non-Amazonian states in Brazil than when they speak elsewhere.
+In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries (e.g.
+in international summits or bilateral meetings) presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
+To a lesser extent, presidents are also more likely to construct the Amazon as an issue of environmental conservation when speaking in non-Amazonian states within Brazil.
+While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest that presidents are less likely to construct the Amazon as problems of economic integration or social development when speaking outside of the Amazon.
+Lastly, presidents are more likely to construct the Amazon as an issue of national sovereignty when speaking in non-Amazonian states within Brazil.
 
@@
 
-In turn, when speaking within the Brazilian Amazon, presidents see their audiences as local constituencies.
+In turn, when speaking within the Brazilian Amazon, presidents likely see their audiences as local constituencies.
 Presidents pursue a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds.
 For example, rural credit offered to local agricultural producers in Amazonian states went up from 500 million reais a year in 1999, to over 4 billion reais a year by 2012 [@capobianco2021].
-As well, the special fiscal regime in Manaus, designed to increase industry presence in the region, was largely maintained.
+As well, the special fiscal regime in Manaus, designed to increase industry in the region, was largely maintained.
 Moreover, additional roads and dams (e.g.
 the BR-163 highway and the Belo Monte dam and hydroelectric power plant) were constructed during the same period.
-Presidents likely highlight and push for economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.
-Thus, we interpret this as evidence that presidents view settings as distinct policymaking instances.
+Presidents highlight economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.
+We interpret this as evidence that presidents view settings as distinct policymaking instances.
 
-We also argue that the urgency of an aligned issue in time influences the likelihood of the president mentioning the Amazon and what they will say.
+We also argue that the urgency of issues in time influences the likelihood of the president mentioning the Amazon and what they will say.
 We find evidence across our models that this holds in unexpected ways.
-Presidents are less likely to generally mention the Amazon in speeches when deforestation rates increase and so the urgency of environmental related issues (model 1).
+Presidents are less likely to generally mention the Amazon in speeches when the urgency of environmental related issues increase ( i.e.
+rising deforestation rates) (model 1).
 The opposite is true for inflation.
 As inflation increases, and so the urgency of economic problems, presidents are more likely to generally mention the Amazon in speeches (model 1).
-This relationship is more intricate when we look at how amazonian constructions vary in presidential speeches as environmental or economic issues become more urgent (models 2-3).
-We find evidence that when the urgency of environmental related issues increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases and the probability of constructing it as an issue of economic integration increases.
-Alternatively, as the urgency of related economic issues increases, the probability of presidents constructing the Amazon as an issue of economic integration decreases and the probability of constructing it as an issue of environmental conservation increases.
-
-In line with our framework, the urgency of aligned problems relates to problem-constructions in intricate ways.
-We interpret that, by opting for an alternative problem-construction to an aligned one which is urgent, presidents often side-step issues as they get more urgent, while boosting about positive aligned outcomes to attempt and collect benefits as aligned issues become less urgent.
+This relationship is more intricate when we look at how amazonian constructions vary in presidential speeches as environmental or economic issues become more urgent.
+We find evidence that when the urgency of environmental related issues increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases (model 2) and the probability of constructing it as an issue of economic integration increases (model 3).
+Alternatively, as the urgency of related economic issues increases, the probability of constructing the Amazon as an issue of environmental conservation increases (model 2) and the probability of presidents constructing it as an issue of economic integration decreases (model 3).
+Thus, the urgency of issues relates to problem-constructions in intricate ways.
+We interpret that by opting for an alternative problem-construction to an issue which is urgent, presidents side-step problems.
+In turn, by opting for an aligned problem-construction to an issue which is not urgent, presidents boast about positive outcomes.
 
@@
 
-Looking at speeches that mention the Amazon over time (model 1) reviews several interesting trends.
 Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not.
+By investigating its development in time, we can identify instances when the Amazon as a general object of policy becomes more urgent as a problem, and when not.
 On average, presidents mention the Amazon in 15.5% of their speeches[^3].
-This suggests the Amazon is a topic of relative high importance for presidents generally.
 However, we observe four peak years (one standard deviation from the mean) in the figure: 1989, 1992, 2009, and 2019.
-We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.
+The longitudinal trends in Amazonian speeches reveal a dynamic that model 1 does not show: peak years coincide with high-profile environmental events that gain large repercussions within and outside of the country.
 
-[^3]: For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).
+[^3]: For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).This suggests the Amazon is a topic of relative high importance for presidents generally.
 
@@
 The incident caught unprecedented transnational media attention and then President Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
-One of the responses was to host the 1992 Earth Summit [@keck1998], which also led to a peak in 1992.
-During the summit, we saw the realization of the first transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest (PPG7), which brought a high number of financial resources to the region for public policy implementation [@capobianco2021].
+One of the responses was to host the 1992 Earth Summit [@keck1998], which also coincided with a peak in 1992.
+During the summit, the Brazilian government announced the first large transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest, which brought a high number of financial resources to the region for public policy implementation [@hochstetler2007].
 
-Throughout the rest of the 1990s and 2000s, during the Cardoso (1995-2002) and Lula presidencies, there were no peaks.
-In 2009, however, we observed another peak which coincided with the Copenhagen Summit.
-Lula led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019], in a moment when deforestation rates have been decreasing since 2005.
+The next peak is 2009, which coincides with the Copenhagen Summit.With deforestation rates decreasing since 2005, Lula led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019].
 From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
 In this period, the urgency of environmental problems was increasing as deforestation rates were rising.
-The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016.
-By 2016 mentions of Amazon in official speeches went down to 6%, their lowest share since 1985.
+The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016, when mentions of the Amazon were at their lowest share.
 
@@
 Right after being elected in 2018, Bolsonaro went on to retrieve Brazil's hosting status for COP25.
-Alongside this, Bolsonaro's dismantling of environmental governance and the threats to leave the Paris Agreement had strong media attention, and, as a response, the Amazon became prominent in his speeches.
-This event also drove the proportion of speeches mentioning the Amazon up.
+Alongside this, Bolsonaro's dismantling of environmental governance[@capelari2023] and the threats to leave the Paris Agreement had strong media attention.
 
-The figure 2, above, also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, does not coincide with proposed environmental policy solutions.
+Figure 2 also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, does not coincide with proposed environmental policy solutions.
 In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022].
@@
 Finally, in 2012, the revision of the Forest Code, debated in 2010 and 2011, pardoned thousands of illegal deforesters in the Amazon [@sant2021].
-Yet, these policy landmarks do not seem to be systematically meaningful for when Amazon is mentioned as a general problem more often.
-
-The longitudinal trends in Amazonian speeches reveal a dynamic that our models did not capture: we find that all peak years coincide with high-profile environmental events within the country that gain large repercussions within and outside of the country.
-These are events that received distinct coverage from transnational actors as media and civil society outside of Brazil, which is likely one of the reasons why it temporarily drives the topic up.
-This suggests that the Amazon is mentioned more in presidential speeches as transnational attention towards it increases.
-While our measure of urgency of the environmental problem does not capture these events, these events change how urgent of a problem the Amazon is in certain years.
+Yet, these environmental policy landmarks do not seem influenced systematically when the Amazon as a general object of policy appears in presidential speeches.
 
@@
 
-While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends.
 Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.
-Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3[^4].
+Peak years identified in Figure 2 do not coincide with increases of specific problem-constructions in Figure 3[^4].
 
-[^4]: We also run lag analysis to uncover hidden patterns and identify seasonality in our data.
-Autocorrelation and partial autocorrelation plots for the proportion of problem-constructions in time are displayed in the appendix.The plots illustrate no significant autocorrelations between peak years and problem-constructions.
+[^4]: We run lag analysis to uncover hidden patterns and find no significant autocorrelations between peak years and problem-constructions (see appendix).
 
@@
 
-Pure economic integration constructions were the most frequent from 1985 to 2009.
-This is especially pertinent during Cardoso's presidency (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
-This was a period when the urgency of the environmental problem grew as deforestation rates increased so, following our model findings, Cardoso was more likely to avoid environmental conservation constructions.
-When Lula took office (2003-2010), construction of the Amazon as an issue of environmental conservation and social development increased.
-During this period, deforestation rates sharply decreased and so did the urgency of environmental problems.
-Lula was, therefore, more likely to employ environmental conservation constructions.
-From around 2010 until the mid-2010s, especially during the Rousseff (2011-2016) administration, we see a reversal at the top whereas environmental conservation and social development problem-constructions surpass economic integration.
-However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), a period of sharp increase in deforestation rates, economic integration constructions become the most favored Amazonian problem-construction again.
+Economic integration problem-constructions were the most frequent from 1985 to 2009.
+This is especially pertinent during Cardoso's presidencies (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
+When Lula took office (2003-2010), constructions of the Amazon as problems of environmental conservation and social development increased.
+From around 2010 until the mid-2010s, especially during the Rousseff administration (2011-2016), environmental conservation and social development problem-constructions surpassed economic integration.
+However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored Amazonian problem-construction again.
+We also identify a steady increase of sovereignty as salient problem-constructions from 2008 onwards.
 
-We also identify a steady increase of sovereignty as salient problem-constructions from 2008 onwards, much before Bolsonaro was elected.
-This might relate to policy developments that were taking place.
-The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of the government [@horochovski2016].
+While environmental policies did not coincide with peak years in general mentions to the Amazon (Figure 2), the trends identified above suggest problem-constructions might relate to policy.
+There is ample evidence that ties Lula's environmental policies to the unprecedented decrease in deforestation between 2004 and 2012[@arima2014; @assunção2015].
+This was also accompanied by a period of strong economic growth and large-scale social policies until the mid-2010s.
+The fall of economic integration and the rise of both social development and environmental conservation problem-constructions suggest an unprecedented balance between granting local livelihoods their social rights, environmental protection, and economic development.
+
+In turn, policy developments taking place in the late 2000s might help us understand the steady rise of national sovereignty problem-constructions starting in 2008.The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of the government [@horochovski2016].
 In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil's sovereignty over the Amazon while rebating broad criticism from civil society actors with accusations of internationalization attempts.
@@
 Bolsonaro's problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
-
-Our operationalization of problem-constructions (see Figure 1) also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
-Figure 4, below, shows that constructing the Amazon as multiple issues generally increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
-Mixed-type problem-constructions in discourse offer more complex and multifaceted understandings of the Amazon as a problem.
-The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.
-Indeed, we observe an increase in policies that attempt to address environmental, economic, and social problems, for instance.
-Examples of this are payment for ecosystem services conditioned for low income populations residing in the Amazon [@silva-muller2022a].
-Relatedly, this is aligned with transnational processes such as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
 
@@
 
+Our operationalization of problem-constructions also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
+Figure 4, below, shows that constructing the Amazon as multiple issues generally increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
+Mixed-type problem-constructions in discourse offer more complex and multifaceted understandings of the Amazon as a problem.
+The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.
+Indeed, we observe an increase in policies that attempt to address environmental, economic, and social problems, such as payment for ecosystem services conditioned for low income populations residing in the Amazon [@silva-muller2022a].
+Relatedly, this is in line with transnational processes such as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
+
 We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the binary between economic and the environmental ways of seeing the Amazon that had prevailed in the previous years decades.
@@
 
-This paper investigated how the Amazon has been constructed as a political problem over time through Brazilian presidential speeches.
+We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the dichotomy between economic and the environmental ways of representing the Amazon as a problem.
+This suggests that the Amazon is becoming increasingly recognized as an intricate policy object in transnational politics.
+
+# 5 Conclusion
+
+This paper investigated how the Amazon has been constructed as a political problem over time and across spaces in Brazilian presidential speeches.
 We have four main findings.
@@
 
-Overall, our findings suggest that we must move beyond assuming the Amazon is a single issue to identify how discourse and policy reflects its environmental, social, economic, and sovereignty-related complexity.By doing so, we can better understand the cohesive, the negotiated, and the contrasting discourses and policies forwarded by transnational actors as they perceive transnational settings as distinct policymaking instances.
-By capturing this variation in discourse, we can better understand why, when, and how, various overlapping policies directed at the same object are developed and implemented.
-Concretely, this implies that even as the environmental crisis becomes more salient, we will likely not see coherent and cohesive environmental, economic, and social discourses or policies towards the Brazilian Amazon.
+Overall, our findings suggest that we must move beyond assuming the Amazon is a single issue to identify how both discourse and policy reflects its environmental, social, economic, and sovereignty-related complexity.
+By doing so, we can better understand the cohesive, the negotiated, and the contrasting problem-constructions forwarded by transnational actors in distinct policymaking instances.
+By capturing this variation in discourse, we can better understand why, when, and how, various overlapping policies directed at the same object are developed.
+Concretely, this implies that even as the environmental crisis becomes more salient, we might not see coherent and cohesive environmental, economic, and social discourses or policies towards the Brazilian Amazon.
 
-In terms of future research, we see at least three possibilities.First, scholars should investigate how problem-constructions change across settings and over time for other Amazonian countries or other policy objects, and in comparative ways.
+In terms of future research, we see at least three possibilities.First, scholars should investigate comparatively how problem-constructions change across settings and over time for other Amazonian countries or other policy objects.
 For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome [@villoria2022].
 By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem".
-Moreover, social media can change political communications in fundamental ways.
+Second, social media can change political communications in fundamental ways.
 The spread of political communications in social media could, on the one hand, contribute to diminishing the importance of physical settings and make presidents less likely to afford diverging problem-constructions.
 On the other hand, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences.
-We look forward to works that investigate variation in problem-constructions in the era of social media.
+We look forward to works that investigate variation in problem-constructions given the advent of social media.
 Finally, in a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro's speech to covid-19 infections.
-While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes in more direct ways.
+While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes.
 

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Added random-effects for presidents' party ideology

@@
 output:
-  word_document: default
+  pdf_document: default
   latex_engine: xelatex
@@
     df_print: paged
-  pdf_document: default
+  word_document: default
 fontsize: 12pt
@@
 
-```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE, results="asis"}
+```{r presid set, fig.cap="Random-effects logistic regressions for setting and presidents' party ideology indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
-ci1 <- exp(confint(c1))
-ci2 <- exp(confint(c2))
-ci3 <- exp(confint(c3))
-ci4 <- exp(confint(c4))
-ci5 <- exp(confint(c5))
+left_right_VDEM <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/V-Dem-CPD-Party-V2.rds") %>% 
+  dplyr::filter(country_name == "Brazil", 
+                year >= 1985) %>%
+  dplyr::select(year, v2pashname, v2pariglef) %>%
+  tidyr::drop_na() %>%
+  dplyr::rename(party = v2pashname) %>%
+  group_by(party) %>%
+  summarise(left_right = mean(v2pariglef))
 
-stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
-                     title = "Odds-ratio for fixed-effects logistic regressions indexed by president",
-                     ci = T, apply.coef = exp,
-                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
-                     t.auto=F, p.auto=F,
+ama_model_lag <- dplyr::left_join(ama_model_lag, left_right_VDEM, by = "party")
+ama_model2_lag <- dplyr::left_join(ama_model2_lag, left_right_VDEM, by = "party")
+
+ps1 <- plm(con_vs_all ~ as.factor(location_cat) + left_right,
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + left_right,
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + left_right,
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + left_right,
+                         data = ama_model_lag,
+                         model = "random", index = "year")
+ps5 <- plm(amazon_speech ~ as.factor(location_cat) + left_right,
+                         data = ama_model2_lag,
+                         model = "random", index = "year")
+
+stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
+                     title = "Random-effects logistic regressions for setting and presidents' party ideology indexed by year",
                       column.sep.width = "-12pt",
@@
                                           "Non Amazonian Countries",
-                                          "Deforestation",
-                                          "Inflation",
-                                          "Election Year"))
-```
-
-\end{landscape}
-````
-
-````{=tex}
-\begin{landscape}
-
-```{r presid set, fig.cap="Random-effects logistic regressions for seeting and president indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
-
-ama_model_lag$president <- factor(ama_model_lag$president,
-                                  levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                             "Lula", "Dilma", "Temer", "Bolsonaro"))
-ama_model2_lag$president <- factor(ama_model2_lag$president,
-                                   levels = c("Sarney", "Collor", "Itamar", "FHC",
-                                              "Lula", "Dilma", "Temer", "Bolsonaro"))
-ps1 <- plm(con_vs_all ~ as.factor(location_cat) + as.factor(president),
-                         data = ama_model_lag,
-                         model = "random", index = "year")
-ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + as.factor(president),
-                         data = ama_model_lag,
-                         model = "random", index = "year")
-ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + as.factor(president),
-                         data = ama_model_lag,
-                         model = "random", index = "year")
-ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + as.factor(president),
-                         data = ama_model_lag,
-                         model = "random", index = "year")
-ps5 <- plm(amazon_speech ~ as.factor(location_cat) + as.factor(president),
-                         data = ama_model2_lag,
-                         model = "random", index = "year")
-
-stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
-                     title = "Random-effects logistic regressions for settings and president indexed by year",
-                      column.sep.width = "-12pt",
-                      font.size="small",
-                      dep.var.labels = c("Amazon Speech",
-                                         "Environmental Conservation",
-                                         "Economic Integration",
-                                         "Social Development",
-                                         "National Sovereignty"),
-                     covariate.labels = c("Amazonian Countries",
-                                          "Non Amazonian States",
-                                          "Non Amazonian Countries",
-                                          "Franco", "Collor", "Cardoso", "Lula",
-                                          "Rousseff", "Temer", "Bolsonaro"))
+                                          "President's party left-right scale (VDEM)"))
 ```

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
final version

@@
 abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns.
-Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem.
-We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches.
-To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics.
-Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985.
-We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon.
-Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
+Despite this complexity, governments are often portrayed as having a single understanding of the region as a political problem.
+In this article, we investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985.To do so, we develop a framework that accounts for how important transnational actors, as presidents, construct policy objects as particular problems depending on where and when they participate in politics.
+We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon.
+Furthermore, presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
 ---
@@
 ```{=latex}
-\wordcount{ 7900 (including text, endnotes, footnotes and references)}
+\wordcount{ 7969 (including abstract, text, endnotes, and references)}
 ```
@@
 The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes.
-Both presidents' political ideology and setting preferences[^2] could affect problem-construction.
+Both presidents' political ideology and setting preferences could affect problem-construction[^2].
 Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].
 
-[^2]: Figure 5 (in appendix) confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.
+[^2]: We conducted more direct tests of these effects and added results in the appendix.
+While table 3 shows the limited effect of presidents' party ideology; figure 5 confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.
 
@@
 
-We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the dichotomy between economic and the environmental ways of representing the Amazon as a problem.
-This suggests that the Amazon is becoming increasingly recognized as an intricate policy object in transnational politics.
-
-# 5 Conclusion
-
 This paper investigated how the Amazon has been constructed as a political problem over time and across spaces in Brazilian presidential speeches.

### 2023-02-18 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
final
submission documents

@@
 We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon.
-Furthermore, presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
+Furthermore, presidents are  increasingly mixing problem-constructions and constructing the Amazon as a complex and multifaceted object of policy.
 ---
@@
 
-# Introduction
+# 1. Introduction
 
@@
 
-# 5 Conclusion
+# 5. Conclusion
 
@@
 While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes.
-
-# Acknowledgements
-
-The authors are extremely grateful to Graziella Moraes Silva, James Hollway, and Matias López for their support.
-The authors would also like to thank the anonymous reviewers, Anna, Federico, Mario, and Rodrigo for their invaluable help.
 

### 2023-08-16 messy_files/data/final_data_preparation_script.R
Moved private files to private repo

@@ -1,105 +1,0 @@
-# Prepare final data for anylsis
-# Amazon statements dataset
-library(dplyr)
-final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/final_labeled_data.Rds")
-final_labeled_data$false_positives <- as.factor(ifelse(final_labeled_data$false_positives > 0.45, 1, 0))
-final_labeled_data$sov <- as.factor(ifelse(as.numeric(final_labeled_data$sov) > 0.45, 1, 0))
-final_labeled_data$EI <- as.factor(ifelse(as.numeric(final_labeled_data$EI) > 0.45, 1, 0))
-final_labeled_data$SD <- as.factor(ifelse(as.numeric(final_labeled_data$SD) > 0.45, 1, 0))
-final_labeled_data$con <- as.factor(ifelse(as.numeric(final_labeled_data$con) > 0.45, 1, 0))
-summary(final_labeled_data)
-fp <- dplyr::filter(final_labeled_data, false_positives == "1" & sov == "0" & EI == "0" & SD == "0" & con == "0")
-final_data <- dplyr::anti_join(final_labeled_data, fp, "AM2")
-# Add other variable
-final_data$other <- ifelse(final_data$sov == "0" & final_data$EI == "0" & final_data$SD == "0" & final_data$con == "0", 1, 0)
-summary(final_data)
-# re-assign location with new version of extract_location()
-# function that does not contain "Brazil" as a match
-final_data$location <- poldis::extract_location(final_data$title)
-summary(as.factor(final_data$location))
-# if NA for location in title, use full text
-final_data$location <- ifelse(grepl("^NA$", final_data$location),
-                              poldis::extract_location(final_data$text),
-                              final_data$location)
-summary(as.factor(final_data$location))
-# a few obs were not matched still, let's see them
-final_data$location <- ifelse(nchar(final_data$location) > 40, "NA", final_data$location)
-summary(as.factor(final_data$location))
-nm <- final_data %>% dplyr::filter(location == "NA") %>% select(AM2, text)
-View(nm) # we can hand code some of these
-nm$location_na <- c("NA", "NA", "NA", "Amazonas", "Amazonas",
-                    "Bahia", "Para", "Para", "Acre", "Acre", "Minas Gerais", 
-                    "Rio Grande do Sul", "Rio Grande do Sul", "Para", 
-                    "Para", "Para", "Para", "Para", "Para", "Para", "Para",
[…]

### 2023-08-16 messy_files/others/SVM_model_final.R

@@ -1,411 +1,0 @@
-# SVM model classification final
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-library(lsa)
-library(e1071)
-library(RTextTools)
-library(SnowballC)
-
-##### First, let's try to tune the model parameters in the Economic Integration variable
-# Get hand coded final training set
-training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get validation dataset
-validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-t <- select(training_set_final, AM2) # save for later
-# get validation standardized
-v <- select(validation_final, AM2) # save for merge later
-validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
-validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
-validation_final$AM2 <- tolower(validation_final$AM2)
-validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
-validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
-validation_final$AM2 <- trimws(validation_final$AM2)
-# Rbind train and validation data
-tdata <- rbind(training_set_final[,-1], validation_final)
-tdata$AM2 <- tm::removeWords(tdata$AM2, tm::stopwords("pt"))
-tdata$AM2 <- SnowballC::wordStem(tdata$AM2, 'pt')
-tdata$AM2 <- tm::stripWhitespace(tdata$AM2)
-trainData <- tdata[1:605,]
-testData <- tdata[606:819,]
-# create matrix
-t_matrix <- create_matrix(trainData$AM2, weighting = weightTfIdf)
-s_matrix <- create_matrix(testData$AM2, originalMatrix = t_matrix, weighting = weightTfIdf)
-# model ei
[…]

### 2023-08-16 messy_files/others/alternative_text_classification_models.R

@@ -1,202 +1,0 @@
-# Run and compare alternative models to classify texts
-# Load packages
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-library(tidymodels)
-library(textrecipes)
-library(RTextTools)
-library(lsa)
-library(ggplot2)
-library(discrim)
-library(naivebayes)
-
-# First let's just get the data ready!
-# Get hand coded final training set
-training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-# Split the training set into train and test for testing
-data <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives)
-train_size <- floor(0.75 * nrow(data))
-in_rows <- sample(c(1:nrow(data)), size = train_size, replace = FALSE)
-train <- data[in_rows, ]
-test <- data[-in_rows, ]
-
-##### Now let's run a simple linear model based on a LSA topic model
-# Clean and get a dtm
-txtcorp_lsa <- VCorpus(VectorSource(as.character(data$AM2)))
-txtcorp_lsa <- tm::tm_map(txtcorp_lsa, removeWords, stopwords('pt'))
-TDM_lsa <- TermDocumentMatrix(txtcorp_lsa, control = list(weighting = weightTfIdf))
-# Get 20 latent topics
-lsaTDM <- lsa(TDM_lsa, 20) # This takes a few minutes
-# Extract the document LSA values
-docVectors <- as.data.frame(lsaTDM$dk)
-# Append the target var
-docVectors$false_positives <- data$false_positives
-# Sample train and test data (avoid overfitting)
-train_lsa <- docVectors[in_rows,]
-pred_score_lsa <- docVectors[-in_rows,]
-# Fit the simple model
-set.seed(1234)
[…]

### 2023-08-16 messy_files/others/clean_combined_training_set.R

@@ -1,85 +1,0 @@
-# Get and wrangle combined training set
-library(readxl)
-training_set_combined <- read_excel("data/training_set_combined.xlsx")
-library(dplyr)
-summary(as.factor(training_set_combined$decision_falsepositive)) # We have 3 ones ...
-summary(as.factor(training_set_combined$decision_code)) # Not consistent
-# Fix data issues first
-training_set_combined$decision_falsepositive[103] <- "false positive"
-training_set_combined$decision_falsepositive[225] <- "false positive"
-training_set_combined$decision_code <- gsub("ecnomic|only economic", "economic",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("consevation", "conservation",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("soverignty|sovereigty|sovereingty", "sovereignty",
-                                            training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub("only", "", training_set_combined$decision_code)
-training_set_combined$decision_code <- gsub(" and ", ", ", training_set_combined$decision_code)
-# Get categories back in as variables 
-ts <- training_set_combined %>%
-  mutate(false_positives = ifelse(grepl("^false positive$", decision_falsepositive), 1, 0),
-         sov = ifelse(grepl("sovereignty", decision_code), 1, substring(code_henrique, 0, 1)),
-         EI = ifelse(grepl("economic", decision_code), 1, substring(code_henrique, 2, 2)),
-         SD = ifelse(grepl("social", decision_code), 1, substring(code_henrique, 3, 3)),
-         con = ifelse(grepl("conservation", decision_code), 1, substring(code_henrique, 4, 4))) %>%
-  select(-c(ID, decision_falsepositive, code_henrique, code_livio, decision_code)) %>%
-  mutate_all(~replace(., is.na(.), 0))
-# Save data
-# saveRDS(ts, "training_set_final.Rds")
-
-# Check intercoder reliability for each category (without false positives)
-check_reliability <- training_set_combined %>%
-  filter(!grepl("^false positive$", decision_falsepositive)) %>% 
-  mutate(code_livio = ifelse(is.na(code_livio), "0000", code_livio), 
-         code_check = ifelse(code_henrique == code_livio, 1, 0),
[…]

### 2023-08-16 messy_files/others/data_wrangling.R

@@ -1,85 +1,0 @@
-# Data Wrangling
-
-# This script explains how the data was coded and where it comes from.
-# It is intended for transparency, rather than reproduciability.
-# For more information on the data, please contact the authors.
-# The dataset is available in the repository,
-# feel free to use but cite us.
-
-# # Load packages
-# library(dplyr)
-# library(stringr)
-# #Load poldis
-# remotes::install_github(henriquesposito/poldis)
-# # Get Data, join and save into repository
-# # This portion explains how/where data was gathered and wrangled before it was saved into the package.
-# # It is commented out as it is here for transparency rather than reproduciability.
-# # Please contact authors for access to original datasets for reproduction.
-#
-# # Load BR_oral from AP repository
-# # load("~/GitHub/authenticity_performances/data/BR_oral.rda") # your path my differ here
-# # Select only some variables
-# BR_oral <- BR_oral %>%
-#   dplyr::select("presid", "date", "party", "text") %>%
-#   rename(president = "presid", year = "date")
-#
-# # Wrangle data
-# # Get exact dates 
-# BR_oral$date <- poldis::extract_date(BR_oral$text)
-# # There are a lot of NAs... It seems some dates in text are missing the year...
-# # Get titles (first sentence)
-# BR_oral$title <- poldis::extract_title(BR_oral$text)
-# # For dates that are missing the year, let's complete them!
-# d <- BR_oral$title
-# d <- stringr::str_extract(d, "(\\S+)\\s*DE\\s*(\\S+)")
-# d <- paste0(d, "-", BR_oral$year)
-# d <- gsub(" DE ", "-", d)
-# # load months data from poldis
-# # load("~/GitHub/poldis/R/sysdata.rda") # your path might differ
-# months <- as.data.frame(months)
-# for (k in seq_len(nrow(months))) {
-#   d <- gsub(paste0(months$months[k]),
-#               paste0(months$number[k]),
-#               d, ignore.case = TRUE,
-#               perl = T)
-# }
-# d <- stringr::str_replace_all(d, "NA-", "?-?-")
-# d <- ifelse(stringr::str_detect(d, "[A-Z]|[a-z]"), paste0("?-?-", BR_oral$year), d)
-# # Let's complete our dates column now
-# BR_oral$date <- ifelse(is.na(BR_oral$date), d, BR_oral$date)
-# 
[…]

### 2023-08-16 messy_files/others/test_validation_model.R

@@ -1,258 +1,0 @@
-# Validation set
-# Here we compare how the LSA/GLM model compares to the SVM when we use
-# our training set to label a validation set hand-coded
-
-############## LSA/GLM
-# LSA and GLM simple models to classify data
-# Load packages
-library(dplyr)
-library(stringr)
-library(glmnet)
-library(tm)
-library(yardstick)
-library(lsa)
-# Get hand coded final training set
-training_set_final <- readRDS("~/Documents/GitHub/amazondef/data/training_set_final.Rds")
-# Get validation dataset
-validation_final <- readRDS("~/Documents/GitHub/amazondef/data/validation_final.Rds")
-# Get training texts standardized
-training_set_final$AM2 <- stringi::stri_trans_general(training_set_final$AM2, 'latin-ascii')
-training_set_final$AM2 <- stringr::str_squish(training_set_final$AM2)
-training_set_final$AM2 <- tolower(training_set_final$AM2)
-training_set_final$AM2 <- tm::removeNumbers(training_set_final$AM2)
-training_set_final$AM2 <- tm::removePunctuation(training_set_final$AM2)
-training_set_final$AM2 <- trimws(training_set_final$AM2)
-train <- training_set_final %>% select(AM2, sov, EI, SD, con, false_positives) # save to combine later
-# Get validation texts standardize
-validation_final$AM2 <- stringi::stri_trans_general(validation_final$AM2, 'latin-ascii')
-validation_final$AM2 <- stringr::str_squish(validation_final$AM2)
-validation_final$AM2 <- tolower(validation_final$AM2)
-validation_final$AM2 <- tm::removeNumbers(validation_final$AM2)
-validation_final$AM2 <- tm::removePunctuation(validation_final$AM2)
-validation_final$AM2 <- trimws(validation_final$AM2)
-# Rbind train and validation data
-score <- rbind(train, validation_final) # Need this cause we are working with matrixes
-
-##### Now let's run a simple linear model based on a LSA topic model
-# Clean and get a dtm
-txtcorp_lsa <- VCorpus(VectorSource(as.character(score$AM2)))
[…]

### 2023-08-16 messy_files/others/training_data_merge.R

@@ -1,37 +1,0 @@
-# First, load datasets
-library(readxl)
-training_set_Sposito <- read_excel("data/training_set_Sposito.xlsx")
-training_set_livio <- read_excel("data/training_set_livio.xlsx")
-# get variable names standardized
-library(dplyr)
-l <- training_set_livio %>%
-  dplyr::slice_head(n = 605) %>%
-  rename(sov = sovereignty, ED = 'economic development', SD = 'social development',
-         con = conservation, cm2 = 'comment 2') %>% 
-  dplyr::mutate(comments = paste0("1 -", comment, " 2 - ", cm2)) %>% 
-  dplyr::select(AM2, sov, ED, SD, con, comments)
-l <- tibble::rownames_to_column(l, "ID")
-
-h <- training_set_Sposito %>%
-  rename(sov = Sovereignty, ED = 'Economic Development', SD = 'Social Development',
-         con = Conservation, comments = Comments) %>% 
-  dplyr::select(AM2, sov, ED, SD, con, comments)
-h <- tibble::rownames_to_column(h, "ID")
-
-# Get and merge only the comments data for later
-comments <- data.frame(comments = paste0(l$comments, " 3 - ", h$comments))
-
-# Add the same comments for both datasets
-l <- select(l, -comments)
-l$comments <- comments$comments
-h <- select(h, -comments)
-h$comments <- comments$comments
-
-# Merge and remove duplicates
-ts <- rbind(l, h)
-ts <- ts %>% 
-  dplyr::distinct() %>%
-  dplyr::mutate(dup = duplicated())
-  
-# Save data in excel format
-xlsx::write.xlsx(ts, file = "ts.xlsx")

### 2023-08-16 messy_files/unemployment_rate_pnad.R

@@ -1,21 +1,0 @@
-# Source: https://www.scielo.br/j/ee/a/YQcXMRc5xjPBgPHZztrnKDj/?lang=pt
-# PNAD reconstructed data
-# Source: https://painel.ibge.gov.br/pnadc/
-# From 2012 onwards available
-unemployment_rate_pnad <- data.frame(year = c(1985, 1986, 1987, 1988, 1989,
-                                              1990, 1991, 1992, 1993, 1994,
-                                              1995, 1996, 1997, 1998, 1999,
-                                              2000, 2001, 2002, 2003, 2004,
-                                              2005, 2006, 2007, 2008, 2009,
-                                              2010, 2011, 2012, 2013, 2014,
-                                              2015, 2016, 2017, 2018, 2019,
-                                              2020, 2021, 2022),
-                                     UR = c(5.61, 4.60, 4.81, 5.29, 4.82,
-                                            5.13, 5.94, 7.16, 7.06, 6.93,
-                                            6.77, 7.51, 8.02, 9.24, 9.84,
-                                            9.38, 9.46, 9.82, 10.42, 10.42,
-                                            10.02, 9.58, 9.14, 8.46, 9.09,
-                                            8.19, 7.52, 7.3, 7.1, 6.8,
-                                            8.5, 11.5, 13.4, 12.8, 12.4,
-                                            13.1, 14.7, 9.8))
-saveRDS(unemployment_rate_pnad, "urate.Rds")

### 2023-08-16 Article code, models, and figures/Which Amazon Problem article codes, models, and figures.Rmd
Re-structured repo to make it publicly available to anyone intereted in reproduce our article findings

--- 2023-02-18 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
@@
 ---
-title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
-  Presidential Discourse since 1985"
-author:
-- "Livio Silva-Muller"
-- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
-  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
-  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
-  and Political Sciences and affiliated to the Centre for International Environmental
-  Studies.]
+title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 - Article codes, models, and figures for replication"
+author: "Henrique Sposito"
 date: "17 February 2023"
@@
 always_allow_html: yes
-bibliography: references.bib
-csl: chicago.csl
 abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns.
@@
 
-```{=latex}
-\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
-```
-```{=latex}
-\wordcount{ 7969 (including abstract, text, endnotes, and references)}
-```
+# Article code, models, and figures
+
+This file makes publicly available all the codes, models, and figures used in the article titled ["Which Amazon Problem?
+Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985"](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639) by Livio Silva-Muller and Henrique Sposito.
+The article has been published open source on Environmental Politics, please check it out!
+Both authors contributed equally to the article.
+Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy.
+Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.
+If you are using this data, codes, or figures, please cite:
+
+Silva-Muller, Livio, and Henrique Sposito. "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985." *Environmental Politics* (2023): 1-24.
+
 ```{r setup, include=FALSE, warning=FALSE, message=FALSE}
@@
 # Load data complete
-pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
+pop <- readRDS("~/Documents/GitHub/amazondef/Replication data/BR_presid_speeches_final.Rds")
 # Load coded data on Amazonian statements and remove extra variables
-ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
+ama <- readRDS("~/Documents/GitHub/amazondef/Replication data/final_data_as.Rds")
 ama <- ama %>%
@@
 # Load annual deforestation rates data, lag years, and fill data
-amazon_def_year_lag <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
+amazon_def_year_lag <- readRDS("~/Documents/GitHub/amazondef/Replication data/amazon_def_year.Rds")
 amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
@@
 # Load inflation data, annual
-aai <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/AAI.Rds")
+aai <- readRDS("~/Documents/GitHub/amazondef/Replication data/AAI.Rds")
 aai_2022 <- data.frame("year" = 2022, "AAI" = 5.79) # Add 2022 rates
@@
 
-\pagebreak
-
-# 1. Introduction
-
-The Brazilian Amazon, which covers around 60% of the whole biome, is home to over 28 million people.
-The Rainforest spans over seven international borders.
-Its most inhabited city, Manaus, enjoys a distinct fiscal regime designed to create jobs in the region and connect its economy to the rest of the country.
-At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas, rendering it an important component of global climate mitigation.
-The Brazilian Amazon is, thus, a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns.
-Despite this complexity, the literature about policies in the Amazon often portray governments as having a single understanding of what the Amazon problem is and, consequently, proposing coherent policies for the region.
-Although this literature is helpful to compare variation across different governments, such analyses oversimplifies policies within governments misrepresenting what, in reality, is more intricate and inconsistent.
-In this article, we ask how has the Amazon been constructed as a political problem since 1985?
-
-We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as presidents, construct objects of policies as particular problems depending on where and when they participate in politics.
-To examine this variation, we created a dataset containing 6240 official speeches by all Brazilian presidents since 1985.
-Drawing from the socio-cultural history of the Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon.
-These problem-constructions touch upon national sovereignty, economic integration, social development, or environmental conservation.
-We employ supervised machine learning to classify how Amazon related statements construct the Amazon as a problem.
-We then conduct an inferential and descriptive analysis of the data.
-A systematic focus on presidential speeches is important because many scholars recognize decisions to deforest on the ground are derived from government's policies and discourse [@capobianco2021; @campbell2015].
-Still, we lack empirical accounts of the Amazon in presidential discourse.
-
-We have four main findings.
-First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation.
-Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration.
-Second, presidents are more likely to construct the Amazon as an environmental conservation problem when deforestation rates decrease.
-When deforestation rates increase, presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
-Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses.
-However, these events does not systematically change how the Amazon is constructed as a problem.
-Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
-
-Empirically, we contribute to the literature about the Amazon by providing the first overview of where, how, and when the Amazon has been constructed as a problem in presidential speeches.
-Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important transnational actors behave differently inside and outside the country.
-We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an issue is.
-Conceptually, problem-constructions highlight the extent to which Amazonian problems are ignored or privileged in transnational politics, and avoids assumptions of the Amazon as a solely environmental problem.
-
-We divide this article into four sections.
-First, we outline the connection between problem-constructions, transnationalism, and presidential speeches.
-Next, we present our research design including the description of our data and methodological approaches.
-In the third part, dedicated to the analysis, we display the results of our inferential models and move to explain developments in problem-constructions over time.
-We conclude by summarizing the empirical and conceptual contributions of the article.
-
-# 2. Theory: problem-construction and transnationalism
-
-## 2.1 Problem-representation in presidential discourse
-
-Scholars writing about policies in the Brazilian Amazon often describe federal governments as proponents of a cohesive set of policies toward the Amazon [see @drummond2006; @padua2012; @franchini2019; @capobianco2019; @pereira2021].
-The 1964 military dictatorship, for example, is associated with securing sovereignty in the region by populating it and integrating it into the national economy [@drummond2006].
-Whereas, governments from the late-1980s up to the late-2000s are associated with a turn towards policies that focus on environmental conservation of the Amazon [@padua2012].
-The presidencies of Rousseff (2011-2016) and Temer (2016-2018) are connected to the de-prioritizing of environmental conservation policies, while Bolsonaro (2019-2022) with the dismantling of environmental policies [@capobianco2019].
-These works are important to understand how different governments acted towards the Amazon, but they represent governments monolithically by bundling them into cohesive policy cycles.
-
-Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies than suggested by the literature above [see @lopez2023; @fairfield2017; @poncedeleon2021].
-We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is.
-Because of the Amazon Rainforest role in global climate-mitigation, the Amazon is often assumed to be an environmental problem that demands environmental solutions.
-The Amazon region, its peoples, and forests, though, are a historically complex object of policies that also comprise economic, social, and sovereignty concerns.
-
-@bacchi1999 [p.
-63] places the question of "what is the problem represented to be" in the center of policy studies.
-The existence or proposal of a policy implies that there is a (public) problem that needs (governmental) action to be fixed.
-Hence, discourse represents, implicitly or explicitly, objects of policies as instances of a specific problem.Problem-representation matters because it carries implications related to who is involved both in the root causes and in the solutions of the problem [@bacchi1999].
-It also helps us shed light on what problems are ignored or privileged.
-
-Following Bacchi, we place discourse about policy objects at the center of our conceptual framework.
-We define policy objects as objects that demand dedicated political attention and argue that by speaking about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem.
-The problem might be either explicitly stated, or implicitly hidden in the underlined solution.
-This is what we label as problem-constructions.
-
-Presidential discourses are a good instance to identify problem-constructions over time and across spaces.
-Presidential speeches and policy share a co-constitutive relationship as speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004].
-This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution [@macaulay2017].
-In Brazil's hybrid system, often referred to as a Coalitional Presidentialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies.
-They also have vast decree powers to adopt policy unilaterally[@pereira2008].
-This means that presidents often have enough power and support to implement the agenda they deem appropriate, especially in the case of climate change[@hochstetler2021].
-We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.
-
-## 2.2 Settings, urgency and variation in problem-constructions
-
-The possibility of different problem-constructions for the same policy object requires an explanation of why they vary.
-There are two potential theories for explaining variation in problem-construction in international/transnational politics: Putnam's two-level game and Keck and Sikkink's transnational networks.
-
-@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests of domestic and international groups.
-At the national level, interest groups pressure the government to adopt favorable policies.
-Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988 p.
-434].
-The theory has been expanded to cover multi-levels games [see @collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups.
-Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups.
-Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found little support that location changes the content of presidential speeches.
-
-The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups.
-This view seems incompatible with the possibility of varied problem-constructions for the same policy object.
-Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, from the local level to the international level [@nye1971; @keck1998].
-In this context, international summits, for example, are considered a transnational space because they are composed of international media, corporations, non-governmental organizations, social movements, and various state actors.
-
-Although @keck1998's theory is developed in the context of value-based advocacy groups( i.e.
-non-state actors), the overall view of international politics holds for state and other non-state actors.
-Their theory rejects the dichotomy of international and domestic levels and argues that the identity and goals of transnational actors are not derived from their structural location vis-a-vis domestic and foreign interest groups.
-Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p.
-4]: state and non-state actors participate in and shape international politics.
-
-Important participants of transnational networks, as presidents, can use a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors.
-They can create politically meaningful information and move it where they believe it can have an impact or leverage institutions to realize symbolic or material gains[@keck1998].
-In this sense, the positions of actors in transnational networks derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.
-
-Problem-constructions are choices transnational actors have of how to represent objects of policies as problems.
-If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors' choice of problem-constructions depend on their views of an audience at a certain period.
-Specifically, how urgent a problem is in a certain space or at a certain time.
-
-*Space*
-
-Transnational actors construct problems and attempt to inform or leverage audiences for symbolic and material gains according to their expectations of that audience.
-We conceptualize space in terms of settings.
-Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study.
-This indicates how transnational actors construct policy objects as problems can vary for instance, within the country --- speaking inside the Amazon region versus outside --- because transnational actors identify these audiences as distinct.
-The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where transnational actors' expectations and identities of an audience could diverge completely from that of domestic actors.
-In each one of these settings transnational actors' expectations might influence how a problem is implicitly or explicitly constructed.
-
-*Time*
-
-How transnational actors construct policy objects varies as the urgency of certain problems changes as new information arises over time.
-We conceptualize time as the urgency of broad and related issues to those surrounding a policy object.
-This is largely defined by factors exogenous to the speaker.
-This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider mentioning climate change when discussing various forms of public policy.
-For instance, when speaking about subsidies for fossil fuel companies in the 1980s, presidents would likely not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased relevance of the topic.
-
-While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time.
-Accordingly, transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.
-
-If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances.
-While there might exist convergences of priorities over time, as problems become more urgent, contradictions are possible.
-This does not mean that policies and priorities change instantaneously and consequently do not matter.
-Rather, transnational actors will focus on representing issues based on their perception of an audience.
-
-Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions in Brazilian presidential speeches.
-We help to advance the literature about the Amazon in three ways.
-First, we provide an outlook of the region, its people, and forest beyond its environmental nature.
-In doing so, we take a step back and avoid assuming what type of problem the Amazon is.
-Instead, we focus on how the Amazon has been represented as a problem.
-Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both policymaking instances.
-Our focus on presidential speeches afford us the analytical leverage to identify transnational variation, as speeches take place in multiple settings over time.
-Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017].
-When it comes to the environment, studies tend to focus primarily on Bolsonaro's discourse [@marquardt2022; @mendes2022].
-We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there is.
-
-# 3. Research design
-
-## 3.1 Data
-
-We update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022.
-The final dataset contains 6240 speeches with their date and state or country location.
-We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem "amazon".
-In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others.
-We find that 968 speeches are, at least partially, about the Amazon.
-
-We use the poldis R package [@sposito2021] to extract two sentences before and after each reference to the Amazon in the presidential speeches.
-We opt for picking two sentences around, rather than words, because sentences usually contain a cohesive idea.
-These sentences form our unit of analysis: 2048 unique Amazonian statements, with an average length of 131 words.
-
 ```{r word_count, eval=FALSE, include=FALSE}
@@
 # Amazonian statements
-final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/final_labeled_data.Rds")
+final_labeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication data/final_labeled_data.Rds")
 nrow(final_labeled_data) # 2048 Amazonian statements
@@
 # Count average words in Amazonian Statements, using original text data
-amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
+amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication data/amazon_speeches_long.Rds")
 sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048 # 131 words on average
 ```
-
-## 3.2 Operationalizing Amazonian problem-constructions
-
-We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development.
-While the three formers are present in the literature, we argue a fourth one exists: social development.
-Amazonian statements can construct the Amazon as a single problem ( i.e.
-pure-type statements), or can construct the amazon as referring to multiple problem-constructions (i.e.
-mixed-types), as Figure 1 (below) details.
-
-*National Sovereignty*
-
-In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p.
-8], and secured most of the Amazon as Brazilian.
-While military diplomacy was very successful, the process did not come without its issues and sovereignty in the Amazon became one of the main military concerns[@rajao2020].
-More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become varied.
-Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors.
-The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and foreign or non-state presence in the region are concerning.
-The policy solutions that implicitly represent this problem include the monitoring of the borders and strict regimes related to entry into the region.
-
-*Economic Integration*
-
-The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005].
-In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021].
-First, it assumed that nature should be conquered by mankind.
-Second, it assumed that exploiting natural resources would render the Amazon region economically profitable.
-Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory.
-Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry.
-The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized.
-These policy solutions have at their core the development of the necessary infrastructure (physical and fiscal) to integrate the region into the economy.
-
-*Environmental Conservation*
-
-The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006].
-The creation of these institutions stemmed from the impression of the lack of control over the environment, following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990].
-This process accelerated in the late 1980s with the new forms of environmentalism [@viola1987].
-The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted.
-The policy solutions imply further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.
-
-*Social Development*
-
-As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights.
-Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights.
-However, such emphasis can be masked within both the economic integration and environmental conservation accounts.
-While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected.
-Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity.
-The policy solutions imply enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.
-
-````{=tex}
-\begin{landscape}
-
-```{r figure1, echo=FALSE, fig.cap="Operationalization of problem-constructions", out.width = '100%', include=TRUE}
-knitr::include_graphics("figure1pic.png")
-```
-
-\end{landscape}
-````
-
-We randomly selected a sample of 1024 Amazonian statements (50% of our data) and each author hand-coded these separately.
-Once manual coding was finished, the authors resolved disagreements through discussion and refined the codebook (in appendix).
-We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations) to train a machine learning algorithm.
-We chose to hand code half of the observations because there are multiple categories of how presidents talk about the Amazon, and the training set size should be increased [see @grimmer2022].
-
-We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text.
-The model was validated by testing it on the validation set.
-As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would.
-The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1].
-Automating the code saved the authors over one month of work.
-
-[^1]: We also train the model to identify false positive matches in Amazonian statements.
-These are statements that contain the stem "amazon" but are not meaningful as they might salute the governor of the Amazon, for example.
-
-## 3.3 Operationalizing settings and urgency
-
-Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of issues. This comprises our independent variables.
-
-*Settings*
-
-To operationalize settings, we extract the location of the speech and create four distinct settings: Amazonian states within Brazil, non-Amazonian states within Brazil, Amazonian countries, and non-Amazonian countries.
-Each one of these settings encompasses audiences that have different expectations in reference to our policy object, the Amazon.
-When speaking in Amazonian states presidents face audiences that likely have distinct social, economic, or environmental demands in relation to the Amazon.
-Such expectations might be distinct from the ones' audiences in non-Amazonian states within Brazil.
-Furthermore, during visits to Amazonian countries, presidents may perceive them as peers facing similar challenges related to the Amazon and adjust their speeches accordingly.
-Conversely, when speaking in non-Amazonian countries (e.g.
-international summits or bilateral visits), presidents may tailor their speeches to align with what they perceive as possible symbolic or material gains from the audience.
-
-This operationalization of settings comes with limitations.
-While we would ideally like to capture the exact venue of the speech (i.e.
-multilateral mechanism, private fora, bilateral visit, bridge inauguration), it is difficult to programmatically code exact locations from thousands of speeches that often mention multiple locations in the same text.
-Nevertheless, we believe the four settings coded are enough to demonstrate whether, and how, problem-construction changes transnationally.
-
-*Urgency*
-
-To capture the urgency of issues, we use two proxies: lagged deforestation rates in the Brazilian Amazon and annual inflation rates.
-When deforestation rates are high, the problem of environmental conservation can be perceived as more urgent.
-Relatedly, when inflation is high, the problem of economic integration issues can be perceived as more urgent.
-We lag deforestation rates by one year as rates for certain years are only published in the following year.
-Since both annual deforestation rates and annual inflation rates come in different measurements (i.e.
-percentage and kilometers square) we scale these values to facilitate interpretation of coefficients.
-Scaling variables do not affect statistical inference in regression models.
-
-This approach to operationalizing urgency also has limitations.
-Ideally, we would like to add proxies of urgency for social and sovereignty issues.
-However, social development indicators (e.g.
-life expectancy, education levels, access to sanitation) generally increased over time in Brazil.
-In terms of national sovereignty, the way we conceptualize the problem-construction entails internal and external threats which are not easily measured.
-Therefore, we limit our analysis of urgency to environmental and economic issues.
-
-## 3.4 Inferential and descriptive strategies
-
-We use fixed-effect logistic regression models to predict the probability of a speech mentioning the Amazon and each of the four problem-constructions.
-The fixed-effects models are indexed by the president, since each president might have individual-specific characteristics that can influence outcomes.
-Both presidents' political ideology and setting preferences could affect problem-construction[^2].
-Fixed-effects models help to control for these possible individual-specific issues and other unit-unvarying characteristics [@allison2009].
-
-[^2]: We conducted more direct tests of these effects and added results in the appendix.
-While table 3 shows the limited effect of presidents' party ideology; figure 5 confirms presidents have a similar share of speeches by setting, weakening the possibility of presidents picking settings according to their agendas.
-
-The dependent variables of the model are the share of speeches that mention the Amazon (model 1) and the share of each problem-construction (models 2-5).
-We chose to model each construction separately, and to focus on pure-types (i.e.
-statements that construct the Amazon as a single problem), to provide unambiguous interpretations and more robust findings.
-Our main explanatory variables are settings and urgency, as described above.
-We add one control, election years, due to the possibility of presidents constructing the Amazon in systematically different ways during campaigns.
-
-We wrap the analysis with a descriptive analysis of Amazonian speeches in time, considering the findings of the models.
-It is important to outline that we do not make any causal claims.
-Many scholars inquire and find causal relationships between discourse and outcomes.
-Our research design and data do not allow us to do so.
-Instead, we focus on the relationships in themselves rather than their order.
-
-# 4. How has the Amazon been constructed as a problem?
-
-## 4.1 The Amazon problem: setting and urgency
-
-Following our framework, we argue that presidents' expectations about an audience at a certain setting and the urgency of specific issues explain variations in when the Amazon is a problem and what type of problem it is.
-We start by first scrutinizing the relationship between the setting and problem-construction.
-The first model (1) addresses the question of when the Amazon is a problem to begin with.
-We model the probability of a speech generally mentioning the Amazon in relation to the reference category, Amazonian states within Brazil.
-The findings are intuitive: the likelihood of mentioning the Amazon in speeches decreases as presidents move away from the region.
-
-The following models (2-5) address the question of how the Amazon is constructed as a problem in different settings.
-In terms of environmental conservation (model 2), we observe that when speaking in non-Amazonian countries (e.g.
-in international summits or bilateral meetings) presidents are much more likely to construct the Amazon as an issue of environmental conservation, in relation to when they speak within Amazonian states in Brazil (reference category).
-To a lesser extent, presidents are also more likely to construct the Amazon as an issue of environmental conservation when speaking in non-Amazonian states within Brazil.
-While the results for economic integration (model 3) and social development (model 4) problem-constructions are not as robust, they are strong enough to suggest that presidents are less likely to construct the Amazon as problems of economic integration or social development when speaking outside of the Amazon.
-Lastly, presidents are more likely to construct the Amazon as an issue of national sovereignty when speaking in non-Amazonian states within Brazil.
 
@@
 
-We interpret these findings to be consistent with our conceptual framework: presidents construct the Amazon as different problems based on their expectations of settings.
-When it comes to non-Amazonian countries, it is likely that Brazilian presidents construct the Amazon as an issue of environmental conservation to leverage financial support for policies in the Amazonian region.
-The Brazilian government successfully funded domestic public policy with transnational financial support on several occasions since the 1990s, most notably with the Amazon Fund which provided over USD 1 billion for the region[@silva-muller2022].
-That is, presidents realize material and symbolic gains outside of Brazil and of Amazonian countries, by constructing the Amazon as an environmental problem.
-
-In turn, when speaking within the Brazilian Amazon, presidents likely see their audiences as local constituencies.
-Presidents pursue a national agenda of economic integration and social development within Brazil while, concurrently, financing environmental policies with transnational funds.
-For example, rural credit offered to local agricultural producers in Amazonian states went up from 500 million reais a year in 1999, to over 4 billion reais a year by 2012 [@capobianco2021].
-As well, the special fiscal regime in Manaus, designed to increase industry in the region, was largely maintained.
-Moreover, additional roads and dams (e.g.
-the BR-163 highway and the Belo Monte dam and hydroelectric power plant) were constructed during the same period.
-Presidents highlight economic and social problem-constructions within the Amazon as they speak to voters to whom they are constitutionally accountable and who are perceived as more interested in socio-economic problems than environmental ones.
-We interpret this as evidence that presidents view settings as distinct policymaking instances.
-
-We also argue that the urgency of issues in time influences the likelihood of the president mentioning the Amazon and what they will say.
-We find evidence across our models that this holds in unexpected ways.
-Presidents are less likely to generally mention the Amazon in speeches when the urgency of environmental related issues increase ( i.e.
-rising deforestation rates) (model 1).
-The opposite is true for inflation.
-As inflation increases, and so the urgency of economic problems, presidents are more likely to generally mention the Amazon in speeches (model 1).
-This relationship is more intricate when we look at how amazonian constructions vary in presidential speeches as environmental or economic issues become more urgent.
-We find evidence that when the urgency of environmental related issues increases, the probability of presidents constructing the Amazon as an environmental conservation problem decreases (model 2) and the probability of constructing it as an issue of economic integration increases (model 3).
-Alternatively, as the urgency of related economic issues increases, the probability of constructing the Amazon as an issue of environmental conservation increases (model 2) and the probability of presidents constructing it as an issue of economic integration decreases (model 3).
-Thus, the urgency of issues relates to problem-constructions in intricate ways.
-We interpret that by opting for an alternative problem-construction to an issue which is urgent, presidents side-step problems.
-In turn, by opting for an aligned problem-construction to an issue which is not urgent, presidents boast about positive outcomes.
-
-## 4.2 Amazonian speeches over time
-
-Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year.
-By investigating its development in time, we can identify instances when the Amazon as a general object of policy becomes more urgent as a problem, and when not.
-On average, presidents mention the Amazon in 15.5% of their speeches[^3].
-However, we observe four peak years (one standard deviation from the mean) in the figure: 1989, 1992, 2009, and 2019.
-The longitudinal trends in Amazonian speeches reveal a dynamic that model 1 does not show: peak years coincide with high-profile environmental events that gain large repercussions within and outside of the country.
-
-[^3]: For comparison purposes, the averages for other policy objects in the same corpus of speeches are inequality (13.7%), criminality (17.3%), inflation (19.1%), and unemployment (13.3%).This suggests the Amazon is a topic of relative high importance for presidents generally.
-
 ```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
@@
 
-In 1989 the Amazon appeared in 32% of all speeches.
-This coincides with the brutal murder of the environmental activist Chico Mendes in the last days of 1988.
-The incident caught unprecedented transnational media attention and then President Sarney (1985-1989) responded to this with a set of policies to address deforestation [@capobianco2021].
-One of the responses was to host the 1992 Earth Summit [@keck1998], which also coincided with a peak in 1992.
-During the summit, the Brazilian government announced the first large transnational partnership for the Amazon, the Pilot Programme of the G7 for the Protection of Rainforest, which brought a high number of financial resources to the region for public policy implementation [@hochstetler2007].
-
-The next peak is 2009, which coincides with the Copenhagen Summit.With deforestation rates decreasing since 2005, Lula led the delegation to the summit with a strong climate leadership self-image of "we deliver" [@franchini2019].
-From 2010 to 2016, except for 2015 when the Paris summit took place, we see a general decrease in mentions of the Amazon in all official presidential speeches.
-In this period, the urgency of environmental problems was increasing as deforestation rates were rising.
-The period was also marked by political and economic instability which culminated in the impeachment of President Rousseff in 2016, when mentions of the Amazon were at their lowest share.
-
-We subsequently observe a steady increase reaching 24% in 2019, the first year of Bolsonaro's presidency.
-At the time, international and national media brought attention to record burning of the Amazon, which led up to a red sky afternoon in São Paulo in August 2019.
-Right after being elected in 2018, Bolsonaro went on to retrieve Brazil's hosting status for COP25.
-Alongside this, Bolsonaro's dismantling of environmental governance[@capelari2023] and the threats to leave the Paris Agreement had strong media attention.
-
-Figure 2 also shows that the frequency at which the Amazon is mentioned, as a general topic in speeches, does not coincide with proposed environmental policy solutions.
-In 2000, for instance, Brazil adopted a strong legislation regulating the creation of protected areas [@silva-muller2022].
-In 2004, President Lula decreed the creation of Brazil's Plan to Combat and Control Deforestation in the Brazilian Amazon.
-In 2008, Brazil announced the Amazon Fund, the largest fund of this kind ever created.
-Finally, in 2012, the revision of the Forest Code, debated in 2010 and 2011, pardoned thousands of illegal deforesters in the Amazon [@sant2021].
-Yet, these environmental policy landmarks do not seem influenced systematically when the Amazon as a general object of policy appears in presidential speeches.
-
-## 4.3 Amazonian problem-constructions in time
-
-Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985.
-Peak years identified in Figure 2 do not coincide with increases of specific problem-constructions in Figure 3[^4].
-
-[^4]: We run lag analysis to uncover hidden patterns and find no significant autocorrelations between peak years and problem-constructions (see appendix).
-
 ```{r Figure pure, fig.cap="Pure-types constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
@@
 
-Economic integration problem-constructions were the most frequent from 1985 to 2009.
-This is especially pertinent during Cardoso's presidencies (1995-2002), when construction of the Amazon as an issue of economic integration increased while environmental conservation constructions decreased.
-When Lula took office (2003-2010), constructions of the Amazon as problems of environmental conservation and social development increased.
-From around 2010 until the mid-2010s, especially during the Rousseff administration (2011-2016), environmental conservation and social development problem-constructions surpassed economic integration.
-However, with the presidencies of Temer (2016-2018) and Bolsonaro (2019-2022), economic integration constructions become the most favored Amazonian problem-construction again.
-We also identify a steady increase of sovereignty as salient problem-constructions from 2008 onwards.
-
-While environmental policies did not coincide with peak years in general mentions to the Amazon (Figure 2), the trends identified above suggest problem-constructions might relate to policy.
-There is ample evidence that ties Lula's environmental policies to the unprecedented decrease in deforestation between 2004 and 2012[@arima2014; @assunção2015].
-This was also accompanied by a period of strong economic growth and large-scale social policies until the mid-2010s.
-The fall of economic integration and the rise of both social development and environmental conservation problem-constructions suggest an unprecedented balance between granting local livelihoods their social rights, environmental protection, and economic development.
-
-In turn, policy developments taking place in the late 2000s might help us understand the steady rise of national sovereignty problem-constructions starting in 2008.The revision of the Forest Code, adopted in 2012, inaugurated a new phase of strong representation of agri-businesses in government and congress and, consequently, strong civil society criticism of the government [@horochovski2016].
-In a period when sovereignty-related issues broadened from nation-states to a wider set of actors, presidents might become more assertive about Brazil's sovereignty over the Amazon while rebating broad criticism from civil society actors with accusations of internationalization attempts.
-Therefore, the political forces in Brazilian politics that drove policy and discursive changes in problem-construction were long in the making.
-Bolsonaro's problem-constructions, characterized by a unique combination of economic integration and sovereignty, is the strongest form of this shift.
-
 ```{r Figure mixed, fig.cap="Mixed-types problem-constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
@@
 
-Our operationalization of problem-constructions also foresees the possibility of presidents mixing multiple constructions within the same Amazonian Statement.
-Figure 4, below, shows that constructing the Amazon as multiple issues generally increased from 18%, in 1985, to 29%, in 2022, as a share of all constructions.
-Mixed-type problem-constructions in discourse offer more complex and multifaceted understandings of the Amazon as a problem.
-The increase in mixed-type constructions suggests that later presidents see the Amazon as an important mix of environmental, economic, social, and sovereignty-related problems.
-Indeed, we observe an increase in policies that attempt to address environmental, economic, and social problems, such as payment for ecosystem services conditioned for low income populations residing in the Amazon [@silva-muller2022a].
-Relatedly, this is in line with transnational processes such as the Millennium Development Goals and the Sustainable Development goals, that highlight the importance of forward human well-being in the economic, social, and environmental spheres.
-
-We interpret the increased balance in pure-types and the general increase in mixed-types Amazonian problem-construction as evidence that presidents increasingly find ways to reconcile the binary between economic and the environmental ways of seeing the Amazon that had prevailed in the previous years decades.
-We interpret this as evidence of the Amazon becoming increasingly recognized as an intricate policy object in transnational politics.
-
-# 5. Conclusion
-
-This paper investigated how the Amazon has been constructed as a political problem over time and across spaces in Brazilian presidential speeches.
-We have four main findings.
-First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation.
-Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration.
-Second, we find that presidents are more likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g.
-lowering deforestation rates).
-When environmental related problems become more urgent (e.g.
-rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration.
-Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses, but does not affect systematically how the Amazon is constructed as a problem.
-Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.
-
-Overall, our findings suggest that we must move beyond assuming the Amazon is a single issue to identify how both discourse and policy reflects its environmental, social, economic, and sovereignty-related complexity.
-By doing so, we can better understand the cohesive, the negotiated, and the contrasting problem-constructions forwarded by transnational actors in distinct policymaking instances.
-By capturing this variation in discourse, we can better understand why, when, and how, various overlapping policies directed at the same object are developed.
-Concretely, this implies that even as the environmental crisis becomes more salient, we might not see coherent and cohesive environmental, economic, and social discourses or policies towards the Brazilian Amazon.
-
-In terms of future research, we see at least three possibilities.First, scholars should investigate comparatively how problem-constructions change across settings and over time for other Amazonian countries or other policy objects.
-For example, recent literature demonstrates that reductions in deforestation in the Amazon lead to increased deforestation in the Cerrado biome [@villoria2022].
-By comparing the Amazonian statements and Cerrado statements, we could identify to what extent other problems are ignored in favour of the "Amazon problem".
-Second, social media can change political communications in fundamental ways.
-The spread of political communications in social media could, on the one hand, contribute to diminishing the importance of physical settings and make presidents less likely to afford diverging problem-constructions.
-On the other hand, micro-targeting of social media algorithms could enhance how different problem-constructions are distributed to audiences.
-We look forward to works that investigate variation in problem-constructions given the advent of social media.
-Finally, in a forthcoming article, Ajzenman, Cavalcanti, and Da Mata (2020) propose an identification strategy that ties Bolsonaro's speech to covid-19 infections.
-While we do not explicitly conceptualize how various problem-constructions might directly affect outcomes, we look forward to similar studies that identify how different problem-constructions affect (environmental) outcomes.
-
-# Disclosure Statement
-
-The authors report that there are no competing interests to declare.
-
-# References
-
-::: {#refs}
-:::
-
-# Appendix
+# Appendix code, models, and figures
 
@@
 
-```{r codebook, fig.cap="Codebook", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
-codebook <- tibble::tibble("problem-construction" = c("National Sovereignty", "Economic Integration","Social Development", "Environmental Conservation"),
-                           Description = c("This code constructs the Amazon region and/or forest as an issue of national sovereignty.
-We understand claims of sovereignty as a particular problem-construction that touches on imaginaries of external threats to territory.
-Relatedly, we also understand sovereignty as raising concerns about wrong perspectives and criticism from foreign and non-state actors about government action related to the Brazilian Amazon.
-In all, it advances the view that the Amazon is Brazilian, foreign, and non-state presence in the region needs to be monitored closely.","This code constructs the Amazon region and/or forest as an issue of economic integration.
-It advances the view that the Amazon needs to be developed and connected to the national economy.
-This includes expanding the agricultural frontier through incentives, creating a diverse set of infrastructure (roads, dams, internet, radio, energy), fostering differing industries (tourism, mining, cattle, agriculture and so on) through tax-free zones, as well as facilitating the exploitation of natural resources for developmental purposes.", "This code constructs the Amazon region and/or forest as an issue of social development.
-It advances the view that Amazon is full of citizens who should have their rights guaranteed.
-This refers to the construction of schools and universities (right to education), of hospitals (right to health), and of housing (right to house).
-This also includes guarantees of a dignified life with decent employment, access to water and sanitation, as well as access to electricity, internet, radio, and light.
-Finally, this includes referrals to culture and the right to vote.", "This code constructs the Amazon region and/or forest as an issue of conservation.
-This problem-construction focuses on the value of a standing forest and of the preserved ecosystem in the region.
-The conservationist narrative advances the view that Amazon should be preserved, deforestation should be halted, and the practices of indigenous and traditional populations should be maintained and fostered.
-It advances the view that the emission of greenhouse gasses should be halted, that renewable energy should be supported, and that protected areas should be created."), Example = c("Congressman, the fundamental link for Brazil to really head in the direction to prosperity.
-I would like first, Hu Chunhua,  to thank you for the words of your ambassador to Brazil recognizing our sovereignty over the Amazonian region during that recent episode in the G7 meeting.
-I would like to thank the Chinese government.
-For us, this type of public acknowledgement is priceless in your words about this region that is so important to the world and to Brazil.
-(Bolsonaro 25/10/2019)",
-                                       "If you allow me, in the Amazon - which for a long time stayed asleep due to the lack of coordinated actions - have already taken a few structuring actions.
-We, in the Amazon, are connecting Manuas, Boa Vista, Caracarai, until up there, the red line [in a map] that goes all the way up in the direction of Venezuela, that is the so-called  BR-174 highway.
-This highway will allow production in the Tax Free Zone in Manaus to be competitive, not within, but outside, that is the vocation of the the Tax Free Zone to export; and we can even do it through the Caribbean (Cardoso 02/07/1997)",
-                                       "The state does not work for profits, the state needs to guarantee dignity, we find that a citizen who lives in the riverside of the Amazon river, 600 kilometers from Manaus, has the right to have the electricity in their house, to owe a fridge, to owe a television where to watch the soap operas.
-We have invested over 14 billion reais in this program, in three and a half years.
-Do you know how many electrical lines we have already built?
-One million kilometers of lines.
-(Lula 20/11/2009)",
-                                       "I have put in place emergency measures, I have suspended the exports of wood logs, I have suspended the fiscal incentives and credits to projects that could damage the environment in the amazon and I have made a license mandatory to gold mining that prohibits utilizing mercury in the process.
-This began the restructuring of the governmental system of control and preservation of the environment, I have created the Brazilian Institute for the Environment and Natural Resources [IBAMA], which will be headed by Dr.
-Mesquita (Sarney 20/07/1989)"))
-
-kbl(codebook, booktabs = T, caption = "Amazonian Problem-Construction Codebook") %>% kable_styling(latex_options = c("striped", "repeat_header", "scale_down"),position= "center", font_size = 9, full_width = TRUE) %>% column_spec(1, width="3cm", bold=TRUE) %>% column_spec(2, width="9cm") %>% column_spec(3, width = "9cm")
-```
-
-\end{landscape}
-````
-
-````{=tex}
-\begin{landscape}
-
 ```{r presid set, fig.cap="Random-effects logistic regressions for setting and presidents' party ideology indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}
 
-left_right_VDEM <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/V-Dem-CPD-Party-V2.rds") %>% 
+left_right_VDEM <- readRDS("~/Documents/GitHub/amazondef/Replication data/V-Dem-CPD-Party-V2.rds") %>% 
   dplyr::filter(country_name == "Brazil", 

### 2023-08-16 Data preparation/data_preparation.R

@@ -2,7 +2,7 @@
 # by extracting Amazonian statements, and 
 # by adding locations for all speeches.
 
-# Install poldis
+# To install poldis run:
 # devtools::install_github("henriquesposito/poldis")
 library(poldis)
 library(dplyr)
@@ -12,12 +12,16 @@ library(readxl)
 BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
 
 # Replace on title and text
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text, " - | -| -", "-")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, " - | -| -", "-")
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
+                                                          " - | -| -", "-")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
+                                                           " - | -| -", "-")
 
 # Replace "para" to avoid confusion with state name in Brazil
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,"^para$", "pra")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title, "^para$", "pra")
+BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
+                                                          "^para$", "pra")
+BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
+                                                           "^para$", "pra")
 
 # Make it lower case, remove extra space, and add coma space
 BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
@@ -32,8 +36,10 @@ BR_Presidential_Speeches$text <- trimws(BR_Presidential_Speeches$text)
 BR_Presidential_Speeches$title <- trimws(BR_Presidential_Speeches$title)
 
 # Make it latin SCII
-BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text, id = "latin-ascii")
-BR_Presidential_Speeches$title <- stringi::stri_trans_general(BR_Presidential_Speeches$title, id = "latin-ascii")
+BR_Presidential_Speeches$text <- stringi::stri_trans_general(BR_Presidential_Speeches$text,
[…]

### 2023-08-16 Replication_Files/Final_data_prep_and_SVM.R

@@ -1,423 +1,0 @@
-# In this script we prepare the data with some text pre-processing,
-# by extracting Amazonian statements, and 
-# by adding locations for all speeches.
-# We also run the SVM model and save the final data for analysis.
-
-# To install poldis run:
-# devtools::install_github("henriquesposito/poldis")
-library(poldis)
-library(dplyr)
-library(readxl)
-
-# Load data
-BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/data/BR_Presidential_Speeches.Rds")
-
-# Replace on title and text
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
-                                                          " - | -| -", "-")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
-                                                           " - | -| -", "-")
-
-# Replace "para" to avoid confusion with state name in Brazil
-BR_Presidential_Speeches$text <- stringr::str_replace_all(BR_Presidential_Speeches$text,
-                                                          "^para$", "pra")
-BR_Presidential_Speeches$title <- stringr::str_replace_all(BR_Presidential_Speeches$title,
-                                                           "^para$", "pra")
-
-# Make it lower case, remove extra space, and add coma space
-BR_Presidential_Speeches$text <- tolower(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- tolower(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- tm::stripWhitespace(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- tm::stripWhitespace(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- textclean::add_comma_space(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- textclean::add_comma_space(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- stringr::str_squish(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- stringr::str_squish(BR_Presidential_Speeches$title)
-BR_Presidential_Speeches$text <- trimws(BR_Presidential_Speeches$text)
-BR_Presidential_Speeches$title <- trimws(BR_Presidential_Speeches$title)
-
-# Make it latin SCII
[…]

### 2023-08-16 Supervised Machine Learning /supervised_machine_learning.R

@@ -1,4 +1,4 @@
-# Supervised Machine Learning Model using SVM (support vector machine) algorithm
+#### Supervised Machine Learning Model using SVM (support vector machine) algorithm
 
 # Load packages
 library(dplyr)
@@ -11,10 +11,27 @@ library(e1071)
 library(RTextTools)
 library(SnowballC)
 
-# Load final hand coded data
-final_hand_coded_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_hand_coded_data.Rds")
-# Load final labeling data
-final_unlabeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_unlabeled_data.Rds")
+# Load final hand coded data (hand-coded by authors)
+# notice that this data is anonymized; that is, it only contains the
+# Amazonian statement and no other identifying info.
+final_hand_coded_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_hand_coded_data1.Rds")
+
+# Load final data to label (obs not randomly selected for hand coding)
+final_unlabeled_data <- readRDS("~/Documents/GitHub/amazondef/Replication Files/final_unlabeled_data1.Rds")
+
+# Wrapper function to clean Amazonian statement
+clean_text <- function(v) {
+  out <- stringi::stri_trans_general(v, 'latin-ascii')
+  out <- tolower(out)
+  out <- tm::removeNumbers(out)
+  out <- tm::removePunctuation(out)
+  out <- tm::removeWords(out, stopwords('pt'))
+  out <- stringr::str_squish(out)
+  out <- trimws(out)
+}
+
+final_hand_coded_data$AM2 <- clean_text(final_hand_coded_data$AM2)
+final_unlabeled_data$AM2 <- clean_text(final_unlabeled_data$AM2)
 
 # Split Data into training and validations sets
 sample_size = floor(0.8*nrow(final_hand_coded_data))
@@ -54,7 +71,7 @@ pred_fp_v <- ifelse(pred_fp_v > 0.45, 1, 0)
 # get metrics
 table(pred = pred_fp_v, true = vvalid$false_positives)
 yardstick::accuracy(table(true = vvalid$false_positives, pred = pred_fp_v))
-#roc_svm_fp <- data.frame(cbind(tpred = as.numeric(pred_fp_v), label = as.numeric(vvalid$false_positives)))
+#roc_svm_fp <- data.frame(cbind(tpred = as.numeric(pred_fp_v),label = as.numeric(vvalid$false_positives)))
[…]

### 2023-08-16 Article code, models, and figures/Which Amazon Problem article codes, models, and figures.Rmd
Added latest updates to figures

@@
 library(lubridate)
+library(geomtextpath)
 Sys.setlocale("LC_ALL", "C")
@@
 
-```{r Figure pure, fig.cap="Pure-types constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
+```{r Figure pure, echo=FALSE, fig.cap="Pure-types constructions in time", message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
 #summary(as.factor(ama_mx$mx_cat))
@@
      	mx_cat != "Mixed-types") %>%
-  ggplot() +
-  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
-          	se = FALSE, linewidth =0.75, linetype="solid") +
+  mutate(mx_cat=case_when(
+    mx_cat== "Pure Economic Integration" ~"Economic Integration",
+    mx_cat== "Pure National Sovereignty" ~"National Sovereignty",
+    mx_cat== "Pure Social Development"~"Social Development",
+    mx_cat== "Pure Environmental Conservation"~"Environmental Conservation"))%>%
+  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
+  geom_textsmooth(aes(label=mx_cat,hjust=mx_cat), fontface="bold", size=4)+
+  scale_hjust_manual(values=c(0.075,0.075,.5,.5))+
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
@@
   theme_am() +
-  theme(legend.position = "bottom") +
+  theme(legend.position = "none") +
   scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
@@
   group_by(mx_cat) %>%
+  mutate(mx_cat=case_when(
+    mx_cat== "Pure Economic Integration" ~"Economic Integration",
+    mx_cat== "Pure National Sovereignty" ~"National Sovereignty",
+    mx_cat== "Pure Social Development"~"Social Development",
+    mx_cat== "Pure Environmental Conservation"~"Environmental Conservation"))%>%
+  drop_na(mx_cat) %>%
   plot_acf_diagnostics(.date_var = year,

### 2023-08-16 Article code, models, and figures/Which Amazon Problem article codes, models, and figures.Rmd
Updated readme and article replication rmd

@@
 
-This file makes publicly available all the codes, models, and figures used in the article titled ["Which Amazon Problem?
+This file makes publicly available all the codes, models, and figures used in the final version of the article titled ["Which Amazon Problem?
 Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985"](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639) by Livio Silva-Muller and Henrique Sposito.
-The article has been published open source on Environmental Politics, please check it out!
+The article has been published open source on Environmental Politics, please check it out in this [link](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639)!
 Both authors contributed equally to the article.
-Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy.
-Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.
+[Livio](https://github.com/liviosilvamuller) is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy.
+[Henrique](http://henriquesposito.com/) is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.
 If you are using this data, codes, or figures, please cite:
